### 2019-09-16 protocol.Rmd
participant and data section

---
title: "Project Protocol"
author: "Stephanie"
date: "27/08/2019"
output:
  pdf_document:
    toc: yes
    toc_depth: '3'
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The following document is a template for the study protocol.
Guiding principles for a project protocol for human research
 - The purpose of a research proposal/protocol is to provide the scientific and academic background and context of a research project.
 - Not all headings or sub-headings in this template are relevant for each research project.
 - Clinical trial proposals may use alternative protocol templates e.g. SPIRIT statement.
 - Use language that is understandable to non-technical reviewers.
 - If conducting research involving biospecimens and children ensure the relevant aspects of the Transplantation and Anatomy Act are applied.

##	Title
Assessing the effectiveness of different visualisation methods for Australian spatial data.
 - Including acronym (if appropriate) and version number

##	Project team roles & responsibilities

|          Researcher          |    Role                    |    Affiliation                                                                |   |   |
|:----------------------------:|----------------------------|-------------------------------------------------------------------------------|---|---|
|    Stephanie Kobakian        |    Masters Student         | Faculty of Science and Engineering (QUT)                                      |   |   |
|    Prof. Kerrie Mengersen    |    Principal Supervisor    | Faculty of Science and Engineering (QUT)                                      |   |   |
|    Dr. Earl Duncan           |    Associate Supervisor    | Faculty of Science and Engineering (QUT)                                      |   |   |
|    Prof. Dianne Cook         |    External Supervisor     |    Department of Econometrics and   Business Statistics, Monash University    |   |   |
|                              |                            |                                                                               |   |   |
|                              |                            |                                                                               |   |   |

 - Names, affiliations, positions and responsibilities of investigators and other key project team members (as required in addition to that outlined in your ethics application)

##	Background information

###	Project outline

This project will test the effectiveness of two types of spatial displays: a choropleth map, and a hexagon map. It will contrast the effectiveness of communicating information when each geographic region is represented by a hexagon, rather than its geographical shape. The purpose of these displays is to convey the spatial distribution of the disease occurrence, or incidence. This can allow for detecting hot spots corresponding to outbreaks, or spatial trends, for example, indicating occurrence is related to latitude or even rural vs urban differences. Effectiveness of the display will be measured by accurate and efficient perception of these patterns.

###	Introduction/background information

Dorling (2011) suggests alternative map displays that aim for ‘equitable representation design’ present each member of a society equally. They are considered more ‘socially just’ but also help to present an honest display of the experiences of the whole population (Dent, 1972). This work aims to determine if using a coloured hexagon display is a more effective method of communicating the spatial relationship between a set of areas on a map.

###	Rationale/justification (i.e. how the research will fill any gaps, contribute to the field of research or contribute to existing or improved practice)

This work is motivated by the newly developed Australian Cancer Atlas where information regarding cancer incidence and mortality is provided to the community through a web page. We are interested to know whether providing the spatial distribution in a hexagon map is more effective for communication than the traditional choropleth map.
The responses of participants will be contrasted when shown the same information in both a geographic and hexagon map display and asked to find the same real distribution in a collection of maps arranged in a line up. The rate of participants who pick the maps in the line ups that display the true spatial relationship will be used to contrast the effectiveness of the displays. We hope that this will show a hexagon map is an effective method for communicating spatial relationships.

##	Study objectives

###	Hypotheses

Participants will pick the map of a true distribution in a line up of null maps more often when the information is presented in a hexagon map, as opposed to a geographic map line up.

###	Research questions/ aims

1.	Measure the accuracy in spotting a real spatial distribution from a line-up of null maps
2.	Contrast the accuracy when participants pick from geographic or hexagon maps

###	Outcome measures

Experiment information collected:
 - Choice of plot in each line up
 - Reason for choice of plot
 - Time taken to answer
 - Perceived difficulty of question

Factors:
 - Plot type ( Hexagon/ Geographic )
 - Spatial dependence structure (Normal errors / Chi-squared errors )

We will record demographic information to consider the impacts of:
 - gender (female / male / other),
 - degree education level achieved (high school / bachelors / masters / doctorate / other),
 - age range (18-25 / 25-35 / 35-45 / 45-55 / 55+ / other)
 - lived in Australia (Yes / No / Other)

 - These measures form the main data that will be analysed and will be linked to your aims and hypotheses
 - An outcome measure might be the change that is attributable to an intervention; or the means by which you will judge whether your research question has been addressed.  
 - In qualitative research an outcome measure, still linked to the aims, could be specific insights, an explanation or understanding, a perspective or theoretical standpoint derived from interpretation of the data.

#	Study design

Each participant will first see three test displays, they will then undertake an online survey linked to them through the online crowdsource platform Figure-Eight.
Within the experiment:
A line up protocol will be used to arrange 20 maps into one display. Each display will be created by a combination of plot type, error distribution and spatial dependence, the possible levels of the factors are:
- Plot type: Geography, Hexagons
- Error distribution: Normal, Chi-Square
- Spatial Dependence: Rurality level, North to South, East to West
Allowing each factor combination to be considered will provide 12 (2*2*3) line up displays to be seen by all participants.
The order of these displays will be randomised for each participant. ??

 - Study type/design
 - Randomisation
 - Study methodology (eg rationale for choices of method/s; tied to project aims/objectives)
 - Research project setting (physical sites, online forums and alternatives)

#	Study population

###	Participants (who, how many)
We will aim to survey 100 participants.
Participants will be approached via their dashboard through their Figure-Eight accounts.

###	Inclusions and exclusion criteria
The platform will advertise this survey to participants that fulfill the following:
 - level 2 or level 3 on the Figure-Eight Platform. 
 - at least 18 years old
 - trained and qualified to annotating images.

###	Recruitment strategies, timeframe (as required in addition to that outlined in your ethics application)
Recruitment will take place via advertising on the Figure-Eight dashboards.
The Figure-Eight platform will advertise this as a “job” to potential participants, they will not be under any obligation to complete this task. We will have the opportunity to wait until enough participants have completed the survey and provided their judgements.

###	Consent approach/es (to provision of information to participants and/or consent (as required in addition to that outlined in the HREA), if necessary, the type of consent provided to different participant groups, when and where, and any arrangements to confirm that consent, if necessary, details of who will be confirming or re-negotiating consent with participants and the process/es that will be undertaken)
Participants will be shown instructions which will provide sufficient information about the task when they select to do the survey. These instructions will explain the survey to participants, and give them an example of the questions they will answer. 
Contact information for the researchers will be made available to the participants.
Their continuation to the survey, and completion of the test questions will be considered consent.
This page will also explain the use and storage of the data they contribute. The data will be the answers they provide, which will be publicly available on github at https://github.com/srkobakian/experiment.

###	Participant withdrawal
Participants will not be able to withdraw the

##	Procedures

###	Screening of participants
Yes. Participants will need to have achieved contributor level two on the Figure-Eight platofrm, this is a smaller group of more experienced, higher accuracy contributors.
Test questions are the most important quality control mechanism in the Figure-Eight Platform. Participants will complete them to practice and prepare for the experiment questions, they will need to reach an accuracy threshold we will set, to be allowed to participate in answering the experiment survey questions.

Contributors that fail quiz mode are not paid and are permanently disqualified from working on your job. Participants will need to reach an accuracy threshold we will set to be allowed to answer the questions in our survey. Test questions will also be included as the job progresses so we can be sure quality remains high.

###	Data collection (what information are you going to collect, as required in addition to that outlined in your ethics application) 
As the survey is conducted through the Figure-Eight platform, the human data will be collected in the form of an IP address, Contributor ID, Trust Score and Channel. Some sources believe an IP address is identifiable information, as such it will not be held publicly online when the data is held on github. We will also ask for information regarding gender, education level achieved, and age range to understand perception of different groups.

###	Data collection/gathering techniques: How will you collect/gather the information?

###	Impact of and response to missing data e.g. extrapolation; participant withdrawal
If participants want to provide and "I don't know" answer they will be able to select this.
If there are more than 50% XXX of questions that are skipped we will remove this survey and consider this withdrawal.

##	Statistical plan
XXX
###	Sample size determination and power; or how will determine that data saturation has occurred or data are sufficient for the purpose.

###	Data analysis and Statistical methods (including how will you measure, manipulate and/or analyse the information that you collect/gather, matching and sampling strategies, accounting for potential bias, confounding factors and missing information)

##	Outcome measures An expansion of the various observations, data and measures that will be made during the study and which will contribute to establishing success or otherwise in addressing the research question.

##	Data management and record keeping
As the data will be held publicly online, it will be accessible under a license for people to reuse. It will also be held accessible to QUT researchers

###	Confidentially and privacy (including linkages)
All data will be deidentified, there is no need to protect confidentiality when the data has been anonymised.

###	Data security (including how will you store)

###	Training

###	Record retention (how you will archive/destroy the information that you collect)

###	Secondary use (including providing access, disclosing)

##	Resources
ACEMS funding - $500 to pay 100 participants equally.

##	Results, outcomes and future plans
 - Plans for return of results of research to participants
 - Publication plan
 - Other potential uses of the data at the end of the project
 - Project closure processes 
 - Plans for sharing and/or future use of data and/or follow-up research

##	References

##	Appendices 
 - These may include surveys, questionnaires, interview schedules, recruitment materials, manual of operations, etc

### 2019-09-16 R/00_pilot.R
change colour schemes

@@ -37,14 +37,14 @@ sa3_centroids <- sa3 %>%
   sf::st_drop_geometry() %>% filter(!is.na(longitude))
 
 # Create hexagon location grid
-grid <- create_grid(centroids = sa3_centroids, hex_size = 0.45, buffer_dist = 2)
+grid <- create_grid(centroids = sa3_centroids, hex_size = 0.5, buffer_dist = 2)
 
 # Allocate polygon centroids to hexagon grid points
 allocated <- allocate(
   centroids = sa3_centroids,
   sf_id = "sa3_name_2016",
   hex_grid = grid,
-  hex_size = 0.45, # same size used in create_grid
+  hex_size = 0.5, # same size used in create_grid
   hex_filter = 10,
   width = 30,
   focal_points = capital_cities,
@@ -57,9 +57,9 @@ hexagons <- fortify_hexagon(data = allocated, sf_id = "sa3_name_2016", hex_size 
 # Convert hexagons to polygons for plotting
 # This will order the areas by the sf_id, this results in alphabetical order
 hexagons_sf <- hexagons %>% 
-  select(sa3_name_2016, sa3_code_2016, long, lat) %>% 
+  select(sa3_name_2016, long, lat) %>% 
   sf::st_as_sf(coords = c("long", "lat"), crs = 4283) %>%
-  group_by(sa3_code_2016) %>% 
+  group_by(sa3_name_2016) %>% 
   summarise(do_union = FALSE) %>%
   st_cast("POLYGON")
 
@@ -117,10 +117,19 @@ var.sim <- predict(var.g.dummy, newdata=sa3_centroids, nsim=16)
 # add trend models to simulated errors
 sa3_centroids$size <- (sa3$areasqkm_2016)/10000
 
+
+
+###########################################################
+###########################################################
+              # CREATE SPATIAL RELATIONSHIPS #
+###########################################################
+
+
 sa3_centroids <- sa3_centroids %>% 
   as_tibble %>% 
   mutate(ns = latitude/10, # North to south trend
-    ns = (-longitude + latitude)/10) # North west to south east trend
+    nw_se = ((longitude - min(longitude))^2 + abs(latitude)^2/100
+      )) # North west to south east trend
 
 
 ###########################################################
[…]

### 2019-10-14 pilot_ns.R
Create the line up plots, normal errors

@@ -1,0 +1,217 @@
+
+###############################################################################
+######################         NORTH TO SOUTH         #########################
+
+# First source the simulated points
+source('~/experiment/R/00_pilot.R', echo = TRUE)
+
+# use an underlying spatial covariance model
+# add a north to south model
+sa3_ns_pop <- sa3_centroids %>% mutate(ns = abs(latitude-min(latitude)))
+
+### Start with shapes - geographies
+aus_geo_ns_pop <- sa3 %>% 
+  select(sa3_name_2016) %>% 
+  # Add the 16 simulated values for each area
+  left_join(., sa3_long) %>% 
+  left_join(., sa3_ns_pop)
+
+### Start with shapes - hexagons
+aus_hex_ns_pop <- hexagons_sf %>% 
+  select(sa3_name_2016) %>% 
+  # Add the 16 simulated values for each area
+  left_join(., sa3_long) %>% 
+  left_join(., sa3_ns_pop)
+
+############################################################################### 
+
+# Add the distribution will be added to one of the null plots
+
+# Choose a location for the true data in the plot
+pos <- sample(1:16, 1)
+
+aus_geo_sa3 <- aus_geo_ns_pop %>%
+  mutate(true = ns) %>% 
+  mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
+  # add the spatial trend model to the null data plot
+  # scale the null data around the mean of the data
+  mutate(value = ifelse(simulation == pos, true + value, (mean(true) + value*sd(true))))
+
+aus_hex_sa3 <- aus_hex_ns_pop %>% 
+  mutate(true = ns) %>% 
+  mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
+  # add the spatial trend model to the null data plot
+  # scale the null data around the mean of the data
+  mutate(value = ifelse(simulation == pos, true + value, (mean(true) + value*sd(true))))
+
+
+############################################################################### 
+############################   Population ns       ############################
+############################################################################### 
+
+aus_geo_ns <- aus_geo_sa3 %>% 
+  ggplot() + 
+  geom_sf(aes(fill = value), colour = NA) + 
+  scale_fill_distiller(type = "div", palette = "RdYlGn") + 
+  facet_grid(~ simulation) + theme_minimal() +
[…]

### 2019-10-14 pilot_nwse.R

@@ -1,0 +1,229 @@
+
+###############################################################################
+######################    NORTH WEST TO SOUTH EAST    #########################
+
+# First source the simulated points
+source('~/experiment/R/00_pilot.R', echo = TRUE)
+
+# use an underlying spatial covariance model
+# add a north to south model
+sa3_nwse_pop <- sa3_centroids %>% 
+  mutate(lat = abs(latitude-min(latitude)),
+    long = abs(longitude-min(longitude)),
+    nwse = lat*long) %>% select(-lat, -long)
+
+###############################################################################
+######################         NORTH TO SOUTH         #########################
+
+# First source the simulated points
+source('~/experiment/R/00_pilot.R', echo = TRUE)
+
+# use an underlying spatial covariance model
+# add a north to south model
+sa3_nwse_pop <- sa3_centroids %>% mutate(nwse = abs(latitude-min(latitude)))
+
+### Start with shapes - geographies
+aus_geo_nwse_pop <- sa3 %>% 
+  select(sa3_name_2016) %>% 
+  # Add the 16 simulated values for each area
+  left_join(., sa3_long) %>% 
+  left_join(., sa3_nwse_pop)
+
+### Start with shapes - hexagons
+aus_hex_nwse_pop <- hexagonwse_sf %>% 
+  select(sa3_name_2016) %>% 
+  # Add the 16 simulated values for each area
+  left_join(., sa3_long) %>% 
+  left_join(., sa3_nwse_pop)
+
+############################################################################### 
+
+# Add the distribution will be added to one of the null plots
+
+# Choose a location for the true data in the plot
+pos <- sample(1:16, 1)
+
+aus_geo_sa3 <- aus_geo_nwse_pop %>%
+  mutate(true = nwse) %>% 
+  mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
+  # add the spatial trend model to the null data plot
+  # scale the null data around the mean of the data
+  mutate(value = ifelse(simulation == pos, true + value, (mean(true) + value*sd(true))))
+
+aus_hex_sa3 <- aus_hex_nwse_pop %>% 
+  mutate(true = nwse) %>% 
+  mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
+  # add the spatial trend model to the null data plot
+  # scale the null data around the mean of the data
[…]

### 2019-10-14 pilot_popdensity.R

@@ -1,0 +1,257 @@
+###############################################################################
+######################       POPULATION DENSITY       #########################
+
+# First source the simulated points
+source('~/experiment/R/00_pilot.R', echo = TRUE)
+
+# use an underlying spatial covariance model
+# add a population density model
+
+# Use the Estimated Residential Population (ERP)
+ERP <- read_csv("data/ERP.csv")
+ERP_sa3_16 <- ERP %>% 
+  filter(`Geography Level` == "Statistical Area Level 3") %>% 
+  filter(Time == 2016) %>% select(sa3_name_2016 = Region, ERP = Value)
+
+ERP_sa3_16 <- sa3 %>% st_drop_geometry() %>% select(sa3_name_2016, areasqkm_2016) %>% 
+  left_join(., ERP_sa3_16)
+
+ERP_sa3_16 <- ERP_sa3_16 %>% 
+  mutate(pop_density = (ERP/areasqkm_2016),
+    pop_density_scaled = pop_density/max(pop_density))
+
+###########################################################
+################# Smooth pop density ######################
+###########################################################
+
+# This distribution will be added to one of the null plots
+
+sa3_smooth_pop <- as_tibble(ERP_sa3_16) %>% 
+  mutate(s1_popdens16 = map_dbl(1:nrow(sa3), spatial_smoother, 
+    values_vector = pop_density, area_weight = 0.5, neighbours_list = sa3_neighbours)) %>% 
+  mutate(s2_popdens16 =  map_dbl(1:nrow(sa3), spatial_smoother, 
+    values_vector = s1_popdens16, area_weight = 0.5, neighbours_list = sa3_neighbours)) %>% 
+  mutate(s3_popdens16 =  map_dbl(1:nrow(sa3), spatial_smoother, 
+    values_vector = s2_popdens16, area_weight = 0.5, neighbours_list = sa3_neighbours)) %>% 
+  mutate(s4_popdens16 =  map_dbl(1:nrow(sa3), spatial_smoother, 
+    values_vector = s3_popdens16, area_weight = 0.5, neighbours_list = sa3_neighbours)) 
+
+
+### Start with shapes - geographies
+aus_geo_smooth_pop <- sa3 %>% 
+  select(sa3_name_2016) %>% 
+  # Add the 16 simulated values for each area
+  left_join(., sa3_long) %>% 
+  left_join(., sa3_smooth_pop) %>% 
[…]

### 2019-10-14 protocol.Rmd
Create the line up plots, normal errors

@@
 - Spatial Dependence: Rurality level, North to South, East to West
-Allowing each factor combination to be considered will provide 12 (2*2*3) line up displays to be seen by all participants.
+Allowing each factor combination to be considered will provide 12 (2x2x3) line up displays to be seen by all participants.
 The order of these displays will be randomised for each participant. ??

### 2019-10-14 R/00_pilot.R

@@ -26,33 +26,30 @@ sa3 <- sa3 %>%
   filter(!is.na(cent_long)) %>% 
   filter(!(sa3_name_2016 %in% Islands))
 
-# plot with area sqkm
-ggplot(sa3) + geom_sf(aes(fill = areasqkm_2016))
-
-###########################################################
-# Create hexagon map of sa3
-# Centroids
-sa3_centroids <- sa3 %>% 
-  select(sa3_name_2016, longitude = cent_long, latitude = cent_lat) %>% 
+# derive centroids
+sa3_centroids <- sa3 %>%
+  select(sa3_name_2016, longitude = cent_long, latitude = cent_lat) %>%
   sf::st_drop_geometry() %>% filter(!is.na(longitude))
 
-# Create hexagon location grid
-grid <- create_grid(centroids = sa3_centroids, hex_size = 0.5, buffer_dist = 2)
+# add trend models to simulated errors
+sa3_centroids$logsize <- log(sa3$areasqkm_2016)
 
-# Allocate polygon centroids to hexagon grid points
-allocated <- allocate(
-  centroids = sa3_centroids,
+
+###########################################################
+####################    HEXMAP   ##########################
+# Create hexagon map of sa3
+allocated <- create_hexmap(
+  shp = sa3,
+  buffer_dist = 2,
   sf_id = "sa3_name_2016",
-  hex_grid = grid,
   hex_size = 0.5, # same size used in create_grid
   hex_filter = 10,
-  width = 30,
+  f_width = 30,
   focal_points = capital_cities,
-  verbose = TRUE
-)
+  verbose = TRUE)
 
-# same column used in create_centroids
-hexagons <- fortify_hexagon(data = allocated, sf_id = "sa3_name_2016", hex_size = 0.45)
+# same column used in create_hexmap
+hexagons <- fortify_hexagon(data = allocated, sf_id = "sa3_name_2016", hex_size = 0.5)
 
 # Convert hexagons to polygons for plotting
 # This will order the areas by the sf_id, this results in alphabetical order
@@ -61,235 +58,203 @@ hexagons_sf <- hexagons %>%
   sf::st_as_sf(coords = c("long", "lat"), crs = 4283) %>%
   group_by(sa3_name_2016) %>% 
   summarise(do_union = FALSE) %>%
-  st_cast("POLYGON")
+  st_cast("POLYGON") %>%
+  st_cast("MULTIPOLYGON")
 
[…]

### 2019-10-14 pilot_ns.R

@@ -1,0 +1,217 @@
+
+###############################################################################
+######################         NORTH TO SOUTH         #########################
+
+# First source the simulated points
+source('~/experiment/R/00_pilot.R', echo = TRUE)
+
+# use an underlying spatial covariance model
+# add a north to south model
+sa3_ns_pop <- sa3_centroids %>% mutate(ns = abs(latitude-min(latitude)))
+
+### Start with shapes - geographies
+aus_geo_ns_pop <- sa3 %>% 
+  select(sa3_name_2016) %>% 
+  # Add the 16 simulated values for each area
+  left_join(., sa3_long) %>% 
+  left_join(., sa3_ns_pop)
+
+### Start with shapes - hexagons
+aus_hex_ns_pop <- hexagons_sf %>% 
+  select(sa3_name_2016) %>% 
+  # Add the 16 simulated values for each area
+  left_join(., sa3_long) %>% 
+  left_join(., sa3_ns_pop)
+
+############################################################################### 
+
+# Add the distribution will be added to one of the null plots
+
+# Choose a location for the true data in the plot
+pos <- sample(1:16, 1)
+
+aus_geo_sa3 <- aus_geo_ns_pop %>%
+  mutate(true = ns) %>% 
+  mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
+  # add the spatial trend model to the null data plot
+  # scale the null data around the mean of the data
+  mutate(value = ifelse(simulation == pos, true + value, (mean(true) + value*sd(true))))
+
+aus_hex_sa3 <- aus_hex_ns_pop %>% 
+  mutate(true = ns) %>% 
+  mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
+  # add the spatial trend model to the null data plot
+  # scale the null data around the mean of the data
+  mutate(value = ifelse(simulation == pos, true + value, (mean(true) + value*sd(true))))
+
+
+############################################################################### 
+############################   Population ns       ############################
+############################################################################### 
+
+aus_geo_ns <- aus_geo_sa3 %>% 
+  ggplot() + 
+  geom_sf(aes(fill = value), colour = NA) + 
+  scale_fill_distiller(type = "div", palette = "RdYlGn", trans = "log") + 
[…]

### 2019-10-14 pilot_nwse.R

@@ -1,0 +1,229 @@
+
+###############################################################################
+######################    NORTH WEST TO SOUTH EAST    #########################
+
+# First source the simulated points
+source('~/experiment/R/00_pilot.R', echo = TRUE)
+
+# use an underlying spatial covariance model
+# add a north to south model
+sa3_nwse_pop <- sa3_centroids %>% 
+  mutate(lat = abs(latitude-min(latitude)),
+    long = abs(longitude-min(longitude)),
+    nwse = lat*long) %>% select(-lat, -long)
+
+###############################################################################
+######################         NORTH TO SOUTH         #########################
+
+# First source the simulated points
+source('~/experiment/R/00_pilot.R', echo = TRUE)
+
+# use an underlying spatial covariance model
+# add a north to south model
+sa3_nwse_pop <- sa3_centroids %>% mutate(nwse = abs(latitude-min(latitude)))
+
+### Start with shapes - geographies
+aus_geo_nwse_pop <- sa3 %>% 
+  select(sa3_name_2016) %>% 
+  # Add the 16 simulated values for each area
+  left_join(., sa3_long) %>% 
+  left_join(., sa3_nwse_pop)
+
+### Start with shapes - hexagons
+aus_hex_nwse_pop <- hexagonwse_sf %>% 
+  select(sa3_name_2016) %>% 
+  # Add the 16 simulated values for each area
+  left_join(., sa3_long) %>% 
+  left_join(., sa3_nwse_pop)
+
+############################################################################### 
+
+# Add the distribution will be added to one of the null plots
+
+# Choose a location for the true data in the plot
+pos <- sample(1:16, 1)
+
+aus_geo_sa3 <- aus_geo_nwse_pop %>%
+  mutate(true = nwse) %>% 
+  mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
+  # add the spatial trend model to the null data plot
+  # scale the null data around the mean of the data
+  mutate(value = ifelse(simulation == pos, true + value, (mean(true) + value*sd(true))))
+
+aus_hex_sa3 <- aus_hex_nwse_pop %>% 
+  mutate(true = nwse) %>% 
+  mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
+  # add the spatial trend model to the null data plot
+  # scale the null data around the mean of the data
[…]

### 2019-10-14 pilot_popdensity.R

@@ -1,0 +1,257 @@
+###############################################################################
+######################       POPULATION DENSITY       #########################
+
+# First source the simulated points
+source('~/experiment/R/00_pilot.R', echo = TRUE)
+
+# use an underlying spatial covariance model
+# add a population density model
+
+# Use the Estimated Residential Population (ERP)
+ERP <- read_csv("data/ERP.csv")
+ERP_sa3_16 <- ERP %>% 
+  filter(`Geography Level` == "Statistical Area Level 3") %>% 
+  filter(Time == 2016) %>% select(sa3_name_2016 = Region, ERP = Value)
+
+ERP_sa3_16 <- sa3 %>% st_drop_geometry() %>% select(sa3_name_2016, areasqkm_2016) %>% 
+  left_join(., ERP_sa3_16)
+
+ERP_sa3_16 <- ERP_sa3_16 %>% 
+  mutate(pop_density = (ERP/areasqkm_2016),
+    pop_density_scaled = pop_density/max(pop_density))
+
+###########################################################
+################# Smooth pop density ######################
+###########################################################
+
+# This distribution will be added to one of the null plots
+
+sa3_smooth_pop <- as_tibble(ERP_sa3_16) %>% 
+  mutate(s1_popdens16 = map_dbl(1:nrow(sa3), spatial_smoother, 
+    values_vector = pop_density, area_weight = 0.5, neighbours_list = sa3_neighbours)) %>% 
+  mutate(s2_popdens16 =  map_dbl(1:nrow(sa3), spatial_smoother, 
+    values_vector = s1_popdens16, area_weight = 0.5, neighbours_list = sa3_neighbours)) %>% 
+  mutate(s3_popdens16 =  map_dbl(1:nrow(sa3), spatial_smoother, 
+    values_vector = s2_popdens16, area_weight = 0.5, neighbours_list = sa3_neighbours)) %>% 
+  mutate(s4_popdens16 =  map_dbl(1:nrow(sa3), spatial_smoother, 
+    values_vector = s3_popdens16, area_weight = 0.5, neighbours_list = sa3_neighbours)) 
+
+
+### Start with shapes - geographies
+aus_geo_smooth_pop <- sa3 %>% 
+  select(sa3_name_2016) %>% 
+  # Add the 16 simulated values for each area
+  left_join(., sa3_long) %>% 
+  left_join(., sa3_smooth_pop) %>% 
[…]

### 2019-10-14 protocol.Rmd
Need statistical plan

@@
 
-The following document is a template for the study protocol.
-Guiding principles for a project protocol for human research
- - The purpose of a research proposal/protocol is to provide the scientific and academic background and context of a research project.
- - Not all headings or sub-headings in this template are relevant for each research project.
- - Clinical trial proposals may use alternative protocol templates e.g. SPIRIT statement.
- - Use language that is understandable to non-technical reviewers.
- - If conducting research involving biospecimens and children ensure the relevant aspects of the Transplantation and Anatomy Act are applied.
-
-##	Title
+#	Title
 Assessing the effectiveness of different visualisation methods for Australian spatial data.
@@
 
-##	Project team roles & responsibilities
+#	Project team roles & responsibilities
 
@@
 |    Prof. Dianne Cook         |    External Supervisor     |    Department of Econometrics and   Business Statistics, Monash University    |   |   |
-|                              |                            |                                                                               |   |   |
-|                              |                            |                                                                               |   |   |
+|                              |                            |
 
- - Names, affiliations, positions and responsibilities of investigators and other key project team members (as required in addition to that outlined in your ethics application)
+#	Background information
 
-##	Background information
-
-###	Project outline
+##	Project outline
 
@@
 
-###	Introduction/background information
+##	Introduction/background information
 
@@
 
-###	Rationale/justification (i.e. how the research will fill any gaps, contribute to the field of research or contribute to existing or improved practice)
+##	Rationale/justification (i.e. how the research will fill any gaps, contribute to the field of research or contribute to existing or improved practice)
 
@@
 
-##	Study objectives
+#	Study objectives
 
-###	Hypotheses
+##	Hypotheses
 
@@
 
-###	Research questions/ aims
+##	Research questions/ aims
 
@@
 
-###	Outcome measures
+##	Outcome measures
 
 Experiment information collected:
+
 - Choice of plot in each line up
@@
 Factors:
+
 - Plot type ( Hexagon/ Geographic )
@@
 We will record demographic information to consider the impacts of:
+
 - gender (female / male / other),
@@
 - lived in Australia (Yes / No / Other)
-
- - These measures form the main data that will be analysed and will be linked to your aims and hypotheses
- - An outcome measure might be the change that is attributable to an intervention; or the means by which you will judge whether your research question has been addressed.  
- - In qualitative research an outcome measure, still linked to the aims, could be specific insights, an explanation or understanding, a perspective or theoretical standpoint derived from interpretation of the data.
 
@@
 Each display will be created by a combination of plot type, error distribution and spatial dependence, the possible levels of the factors are:
+
  - Plot type: Geography, Hexagons
@@
  - Spatial Dependence: Rurality level, North to South, East to West
+
 Allowing each factor combination to be considered will provide 12 (2x2x3) line up displays to be seen by all participants.
-The order of these displays will be randomised for each participant. ??
 
@@
 
-###	Participants (who, how many)
+##	Participants
 We will aim to survey 100 participants.
@@
 
-###	Inclusions and exclusion criteria
+##	Inclusions and exclusion criteria
 The platform will advertise this survey to participants that fulfill the following:
@@
 
-###	Recruitment strategies, timeframe (as required in addition to that outlined in your ethics application)
+##	Recruitment strategies, timeframe (as required in addition to that outlined in your ethics application)
 Recruitment will take place via advertising on the Figure-Eight dashboards.
@@
 
-###	Consent approach/es (to provision of information to participants and/or consent (as required in addition to that outlined in the HREA), if necessary, the type of consent provided to different participant groups, when and where, and any arrangements to confirm that consent, if necessary, details of who will be confirming or re-negotiating consent with participants and the process/es that will be undertaken)
+##	Consent approaches
+
 Participants will be shown instructions which will provide sufficient information about the task when they select to do the survey.
@@
 Contact information for the researchers will be made available to the participants.
-Their continuation to the survey, and completion of the test questions will be considered consent.
+Participants will be asked to provide consent via a checkbox question.
+They will then continue to the survey, and complete the test questions.
 This page will also explain the use and storage of the data they contribute.
@@
 
-###	Participant withdrawal
-Participants will not be able to withdraw the
+##	Participant withdrawal
+Participants will be able to withdraw by leaving the survey at any time.
+XXX will they still be paid?
 
-##	Procedures
+#	Procedures
 
-###	Screening of participants
-Yes. Participants will need to have achieved contributor level two on the Figure-Eight platofrm, this is a smaller group of more experienced, higher accuracy contributors.
+##	Screening of participants
+Participants will need to have achieved contributor level two on the Figure-Eight platofrm, this is a smaller group of more experienced, higher accuracy contributors.
 Test questions are the most important quality control mechanism in the Figure-Eight Platform.
@@
 
-###	Data collection (what information are you going to collect, as required in addition to that outlined in your ethics application) 
-As the survey is conducted through the Figure-Eight platform, the human data will be collected in the form of an IP address, Contributor ID, Trust Score and Channel.
+##	Data collection
+As the survey is conducted through the Figure-Eight platform, the human data will also be collected in the form of an IP address, Contributor ID, Trust Score and Channel.
 Some sources believe an IP address is identifiable information, as such it will not be held publicly online when the data is held on github.
@@
 
-###	Data collection/gathering techniques: How will you collect/gather the information?
+##	Data collection/gathering techniques: 
+Data will be collected through survey distribution via a web application.
+Participants will access the application via link from a Figure-Eight "job".
 
-###	Impact of and response to missing data e.g. extrapolation; participant withdrawal
+##	Impact of, and response to, missing data
 If participants want to provide and "I don't know" answer they will be able to select this.
-If there are more than 50% XXX of questions that are skipped we will remove this survey and consider this withdrawal.
+If there are more than 50% of questions that are incomplete we will remove this survey and consider this withdrawal.
 
-##	Statistical plan
  XXX
-###	Sample size determination and power; or how will determine that data saturation has occurred or data are sufficient for the purpose.
 
-###	Data analysis and Statistical methods (including how will you measure, manipulate and/or analyse the information that you collect/gather, matching and sampling strategies, accounting for potential bias, confounding factors and missing information)
+#	Statistical plan
+XXX
 
-##	Outcome measures An expansion of the various observations, data and measures that will be made during the study and which will contribute to establishing success or otherwise in addressing the research question.
+##	Sample size determination and power; or how will determine that data saturation has occurred or data are sufficient for the purpose.
 
-##	Data management and record keeping
+##	Data analysis and Statistical methods
+
+(including how will you measure, manipulate and/or analyse the information that you collect/gather, matching and sampling strategies, accounting for potential bias, confounding factors and missing information)
+
+#	Outcome measures
+
+An expansion of the various observations, data and measures that will be made during the study and which will contribute to establishing success or otherwise in addressing the research question.
+
+#	Data management and record keeping
 As the data will be held publicly online, it will be accessible under a license for people to reuse. It will also be held accessible to QUT researchers
 
-###	Confidentially and privacy (including linkages)
+##	Confidentially and privacy (including linkages)
 All data will be deidentified, there is no need to protect confidentiality when the data has been anonymised.
 
-###	Data security (including how will you store)
+##	Data security (including how will you store)
 
-###	Training
+##	Training
 
-###	Record retention (how you will archive/destroy the information that you collect)
+##	Record retention (how you will archive/destroy the information that you collect)
 
-###	Secondary use (including providing access, disclosing)
+##	Secondary use (including providing access, disclosing)
 
-##	Resources
+#	Resources
 ACEMS funding - $500 to pay 100 participants equally.
 
-##	Results, outcomes and future plans
+#	Results, outcomes and future plans
  - Plans for return of results of research to participants
@@
 
-##	References
+#	References
 
-##	Appendices 
+#	Appendices 
  - These may include surveys, questionnaires, interview schedules, recruitment materials, manual of operations, etc

### 2019-10-14 R/00_pilot.R
20 simulations

@@ -83,7 +83,7 @@ var.g.dummy <- gstat(formula = z ~ 1,
   nmax = 20)
 
 # Create underlying spatially dependent data for 16 null plots
-var.sim <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 16) %>% 
+var.sim <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 20) %>% 
   left_join(sa3_centroids, ., by=c("longitude", "latitude"))
 
 

### 2019-10-14 pilot_ns.R

@@ -28,7 +28,7 @@ aus_hex_ns_pop <- hexagons_sf %>%
 # Add the distribution will be added to one of the null plots
 
 # Choose a location for the true data in the plot
-pos <- sample(1:16, 1)
+pos <- sample(1:20, 1)
 
 aus_geo_sa3 <- aus_geo_ns_pop %>%
   mutate(true = ns) %>% 

### 2019-10-14 pilot_nwse.R

@@ -25,14 +25,14 @@ sa3_nwse_pop <- sa3_centroids %>% mutate(nwse = abs(latitude-min(latitude)))
 ### Start with shapes - geographies
 aus_geo_nwse_pop <- sa3 %>% 
   select(sa3_name_2016) %>% 
-  # Add the 16 simulated values for each area
+  # Add the 20 simulated values for each area
   left_join(., sa3_long) %>% 
   left_join(., sa3_nwse_pop)
 
 ### Start with shapes - hexagons
 aus_hex_nwse_pop <- hexagonwse_sf %>% 
   select(sa3_name_2016) %>% 
-  # Add the 16 simulated values for each area
+  # Add the 20 simulated values for each area
   left_join(., sa3_long) %>% 
   left_join(., sa3_nwse_pop)
 

### 2019-10-14 pilot_popdensity.R

@@ -48,7 +48,7 @@ aus_geo_smooth_pop <- sa3 %>%
 ### Start with shapes - hexagons
 aus_hex_smooth_pop <- hexagons_sf %>% 
   select(sa3_name_2016) %>% 
-  # Add the 16 simulated values for each area
+  # Add the 20 simulated values for each area
   left_join(., sa3_long) %>% 
   left_join(., sa3_smooth_pop) %>% 
   gather("iteration", "smoother_density", contains("popdens"))
@@ -58,7 +58,7 @@ aus_hex_smooth_pop <- hexagons_sf %>%
 # Add the distribution will be added to one of the null plots
 
 # Choose a location for the true data in the plot
-pos <- sample(1:16, 1)
+pos <- sample(1:20, 1)
 
 aus_geo_sa3 <- aus_geo_smooth_pop %>%
   mutate(true = smoother_density) %>% 

### 2019-10-14 R/00_pilot.R
LINE UP PLOTS

@@ -26,6 +26,11 @@ sa3 <- sa3 %>%
   filter(!is.na(cent_long)) %>% 
   filter(!(sa3_name_2016 %in% Islands))
 
+# Make list of Tasmanian sa3 areas
+Tasmania <- sa3 %>% st_drop_geometry() %>% 
+  filter(state_name_2016 == "Tasmania") %>%
+  select(sa3_name_2016) %>% pull()
+
 # derive centroids
 sa3_centroids <- sa3 %>%
   select(sa3_name_2016, longitude = cent_long, latitude = cent_lat) %>%
@@ -212,10 +217,9 @@ tas <- tas_sims %>%
   scale_fill_distiller(type = "div", palette = "RdYlGn") +
   facet_wrap(~simulation) + 
   transition_states(states = groups, wrap = FALSE)
-tas_anim <- animate(tas, nframes = 20, duration = 15)
+#tas_anim <- animate(tas, nframes = 20, duration = 15)
 
-anim_save(filename = "figures/tas_simulation.gif", 
-  animation = tas_anim)
+#anim_save(filename = "figures/tas_simulation.gif", animation = tas_anim)
 
 ###########################################################
 

### 2019-10-14 pilot_ns.R

@@ -3,26 +3,37 @@
 ######################         NORTH TO SOUTH         #########################
 
 # First source the simulated points
-source('~/experiment/R/00_pilot.R', echo = TRUE)
+#source('~/experiment/R/00_pilot.R', echo = TRUE)
+
+# only use the most smoothed
+sa3_min <- sa3_long %>% 
+  filter(groups == "smooth5") %>%
+  pull(value) %>% min()
+sa3_max <- sa3_long %>% 
+  filter(groups == "smooth5") %>%
+  pull(value) %>% max()
 
 # use an underlying spatial covariance model
 # add a north to south model
-sa3_ns_pop <- sa3_centroids %>% mutate(ns = abs(latitude-min(latitude)))
+sa3_ns <- sa3_centroids %>% 
+  mutate(ns = abs(latitude-min(latitude))) %>% 
+  mutate(ns = scales::rescale(ns, to = c(sa3_min,sa3_max)))
 
 ### Start with shapes - geographies
-aus_geo_ns_pop <- sa3 %>% 
+aus_geo_ns <- sa3 %>% 
   select(sa3_name_2016) %>% 
   # Add the 16 simulated values for each area
   left_join(., sa3_long) %>% 
-  left_join(., sa3_ns_pop)
+  left_join(., sa3_ns)
 
 ### Start with shapes - hexagons
-aus_hex_ns_pop <- hexagons_sf %>% 
+aus_hex_ns <- hexagons_sf %>% 
   select(sa3_name_2016) %>% 
   # Add the 16 simulated values for each area
   left_join(., sa3_long) %>% 
-  left_join(., sa3_ns_pop)
+  left_join(., sa3_ns)
 
+  
 ############################################################################### 
 
 # Add the distribution will be added to one of the null plots
@@ -30,14 +41,14 @@ aus_hex_ns_pop <- hexagons_sf %>%
 # Choose a location for the true data in the plot
 pos <- sample(1:16, 1)
 
-aus_geo_sa3 <- aus_geo_ns_pop %>%
+aus_geo_sa3 <- aus_geo_ns %>%
   mutate(true = ns) %>% 
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the null data around the mean of the data
[…]

### 2019-10-14 pilot_nwse.R

@@ -3,14 +3,24 @@
 ######################    NORTH WEST TO SOUTH EAST    #########################
 
 # First source the simulated points
-source('~/experiment/R/00_pilot.R', echo = TRUE)
+#source('~/experiment/R/00_pilot.R', echo = TRUE)
+
+# only use the most smoothed
+sa3_min <- sa3_long %>% 
+  filter(groups == "smooth5") %>%
+  pull(value) %>% min()
+sa3_max <- sa3_long %>% 
+  filter(groups == "smooth5") %>%
+  pull(value) %>% max()
 
 # use an underlying spatial covariance model
 # add a north to south model
-sa3_nwse_pop <- sa3_centroids %>% 
+sa3_nwse <- sa3_centroids %>% 
   mutate(lat = abs(latitude-min(latitude)),
     long = abs(longitude-min(longitude)),
-    nwse = lat*long) %>% select(-lat, -long)
+    nwse = lat*long) %>% 
+  mutate(nwse = scales::rescale(nwse, to = c(sa3_min, sa3_max))) %>%
+  select(-lat, -long)
 
 ###############################################################################
 ######################         NORTH TO SOUTH         #########################
@@ -20,21 +30,21 @@ source('~/experiment/R/00_pilot.R', echo = TRUE)
 
 # use an underlying spatial covariance model
 # add a north to south model
-sa3_nwse_pop <- sa3_centroids %>% mutate(nwse = abs(latitude-min(latitude)))
+sa3_nwse <- sa3_centroids %>% mutate(nwse = abs(latitude-min(latitude)))
 
 ### Start with shapes - geographies
-aus_geo_nwse_pop <- sa3 %>% 
+aus_geo_nwse <- sa3 %>% 
   select(sa3_name_2016) %>% 
   # Add the 16 simulated values for each area
   left_join(., sa3_long) %>% 
-  left_join(., sa3_nwse_pop)
+  left_join(., sa3_nwse)
 
 ### Start with shapes - hexagons
-aus_hex_nwse_pop <- hexagonwse_sf %>% 
+aus_hex_nwse <- hexagonwse_sf %>% 
   select(sa3_name_2016) %>% 
   # Add the 16 simulated values for each area
   left_join(., sa3_long) %>% 
-  left_join(., sa3_nwse_pop)
+  left_join(., sa3_nwse)
 
[…]

### 2019-10-14 pilot_popdensity.R

@@ -2,7 +2,15 @@
 ######################       POPULATION DENSITY       #########################
 
 # First source the simulated points
-source('~/experiment/R/00_pilot.R', echo = TRUE)
+#source('~/experiment/R/00_pilot.R', echo = TRUE)
+
+# only use the most smoothed
+ sa3_min <- sa3_long %>% 
+  filter(groups == "smooth5") %>%
+  pull(value) %>% min()
+ sa3_max <- sa3_long %>% 
+   filter(groups == "smooth5") %>%
+   pull(value) %>% max()
 
 # use an underlying spatial covariance model
 # add a population density model
@@ -17,8 +25,8 @@ ERP_sa3_16 <- sa3 %>% st_drop_geometry() %>% select(sa3_name_2016, areasqkm_2016
   left_join(., ERP_sa3_16)
 
 ERP_sa3_16 <- ERP_sa3_16 %>% 
-  mutate(pop_density = (ERP/areasqkm_2016),
-    pop_density_scaled = pop_density/max(pop_density))
+  mutate(pop_density = (ERP/areasqkm_2016))  %>% 
+  mutate(pop_density = scales::rescale(pop_density, to = c(sa3_min,sa3_max)))
 
 ###########################################################
 ################# Smooth pop density ######################
@@ -149,10 +157,10 @@ ggsave(filename = "figures/pop/aus_hex_popdens.png", plot = aus_hex_popdens, dev
 
 
 tas_geo_sa3 <- aus_geo_sa3 %>%
-  filter(state_name_2016 == "Tasmania")
+  filter(sa3_name_2016 %in% Tasmania)
 
 tas_hex_sa3 <- aus_hex_sa3 %>%
-  filter(state_name_2016 == "Tasmania")
+  filter(sa3_name_2016 %in% Tasmania)
 
 ###############################################################################
 tas_geo_sa3 %>% 

### 2019-10-14 protocol.Rmd

@@
 A line up protocol will be used to arrange 20 maps into one display.
-Each display will be created by a combination of plot type, error distribution and spatial dependence, the possible levels of the factors are:
+Each display will be created by a combination of plot type, error distribution and spatial dependence.
+We will contrast the sets of different plot designs, hexagon tilemap and geography in the lineups created using the same data, and same null positions within the lineup. 
+We will compare the length of time taken and the accuracy with which participants report their choice.
+
+The possible levels of the factors are:
 
@@
 
+The design of this study is based on work by Hofmann, Follett, Majumder and Cook.
+
+> The probability that an observer picks the data plot just by chance, i.e.
+when it is really *not* different from the other null plots, is 1=m.
+If an observer is able to identify the data plot from the lineup, we reject the null hypothesis.
+This sets our Type I error rate, a, at a level of 1=m.
+
 ##	Sample size determination and power; or how will determine that data saturation has occurred or data are sufficient for the purpose.
+
+To be able to effectively evaluate the use of a hexagon tilemap we will contrast the proportion of times the real data plot was chosen in a line up of maps.
+The same data will be used to create 19 null data plots and one real data plot. This data will be displayed to users in both geographic maps and hexagon tile maps.
+
+We will have aim to collect results from 100 participants (n=100), who will have tried to pick the real data in a line up of simulated data.
+
+Let X be the corresponding random variable X, where i.e. X = # times out of n independent repetitions that the data plot is picked from the lineup.
+
+Under the null hypothesis, X has a Binomial distribution: $X ~ B_{n,1=m}$. 
+The p-value of a lineup is the probability to have x or more observers picking the data plot, under the assumption that the null hypothesis is true:
+$p-value = P(X \geq x|H_0) = 1- B_{n,1/m}(x-1)$
+
+The authors also define how to estimate the power of a lineup: the ratio of correct identifications of the real data, x, out of n viewings.
 
@@
 
+Information will be collected regarding the design
 (including how will you measure, manipulate and/or analyse the information that you collect/gather, matching and sampling strategies, accounting for potential bias, confounding factors and missing information)
+
+This will be analysed using a generalised linear model, with random effects capturing the differences between the 100 participants.
+The main effects used will consider the spatial distribution of the errors, gender, degree education level achieved, age range and whether the participant has lived in Australia.
+
+Each lineup will have similar hypotheses:
+$H_0:$ there is no real structure visible in the data plot
+$H_1:$ there is real structure visible in the data plot
+
+Each lineup is a set of m = 20 plots.
+One plot contains data with a real structure.
+The probability that an observer picks the data plot when it is really *not* different from the 19 null plots, is $1/m = 1/20$.
+
+If a participant is able to identify the data plot from the lineup, we reject the null hypothesis.
+Type I error rate, $\alpha$, is set to a level of $1/m = 1/20 = 0.05$.
+
+Compare the percentage of times users select the real data in a lineup for the same set of data presented in choropleth maps and hexagon tile maps.
+Compare percentages of correct responses $\hat{\pi}_C$ and $\hat{\pi}_H$:
+
+Where $C$ denotes the use of choropleth maps and $H$ denotes the use of hexagon tile maps.
+
+The percentage of correct responses where the respondent identified the real data in a choropleth map is denoted by $\hat{\pi}_C = (x_C +1)/(n_{100} + 1)$, similarly for hexagon tile maps: $\hat{\pi}_H = (x_H +1)/(n_{100} + 1)$.
 
@@
 
+The collection of multiple responses from each person as they complete
+several different lineup tasks, allows estimates of their perceptual ability and allows them to correct power differences between competing designs: by modeling power using a subject-specific random intercept in a generalized linear model.
+
 #	Data management and record keeping
@@
 
-##	Confidentially and privacy (including linkages)
+##	Confidentially and privacy
 All data will be deidentified, there is no need to protect confidentiality when the data has been anonymised.
@@
 #	Resources
-ACEMS funding - $500 to pay 100 participants equally.
+This work will be supported by ACEMS funding - $500 to pay 100 participants equally.
 

### 2019-10-15 protocol.Rmd
clean lineups folder

@@
 title: "Project Protocol"
-author: "Stephanie"
-date: "27/08/2019"
 output:
@@
     toc: yes
-    toc_depth: '3'
     number_sections: yes
+  word_document:
+    toc: yes
+bibliography: protocol.bib
+link-citations: yes
 ---
@@
 Assessing the effectiveness of different visualisation methods for Australian spatial data.
- - Including acronym (if appropriate) and version number
 
@@
 
-Dorling (2011) suggests alternative map displays that aim for ‘equitable representation design’ present each member of a society equally.
-They are considered more ‘socially just’ but also help to present an honest display of the experiences of the whole population (Dent, 1972).
+@ACTUC suggests alternative map displays that aim for ‘equitable representation design’ present each member of a society equally.
+They are considered more ‘socially just’ but also help to present an honest display of the experiences of the whole population [@NISCC].
 This work aims to determine if using a coloured hexagon display is a more effective method of communicating the spatial relationship between a set of areas on a map.
 
-##	Rationale/justification (i.e. how the research will fill any gaps, contribute to the field of research or contribute to existing or improved practice)
+##	Rationale/justification
 
@@
 
- - Study type/design
- - Randomisation
- - Study methodology (eg rationale for choices of method/s; tied to project aims/objectives)
- - Research project setting (physical sites, online forums and alternatives)
-
 #	Study population
@@
 
-##	Recruitment strategies, timeframe (as required in addition to that outlined in your ethics application)
+##	Recruitment strategies, timeframe 
 Recruitment will take place via advertising on the Figure-Eight dashboards.
@@
 
- XXX
+#	Statistical plan
 
-#	Statistical plan
-XXX
-
-The design of this study is based on work by Hofmann, Follett, Majumder and Cook.
-
-> The probability that an observer picks the data plot just by chance, i.e.
-when it is really *not* different from the other null plots, is 1=m.
-If an observer is able to identify the data plot from the lineup, we reject the null hypothesis.
-This sets our Type I error rate, a, at a level of 1=m.
+The design of this study is based on work by Hofmann, Follett, Majumder and Cook [-@GTPCCD].
 
@@
 
+This sets our Type I error rate, $\alpha$, at a level of $1/m$.
 The authors also define how to estimate the power of a lineup: the ratio of correct identifications of the real data, x, out of n viewings.
@@
 
-The collection of multiple responses from each person as they complete
-several different lineup tasks, allows estimates of their perceptual ability and allows them to correct power differences between competing designs: by modeling power using a subject-specific random intercept in a generalized linear model.
+The collection of multiple responses from each person as they complete several different lineup tasks, allows estimates of their perceptual ability and allows them to correct power differences between competing designs: by modeling power using a subject-specific random intercept in a generalized linear model.
 
@@
 
-##	Data security (including how will you store)
+##	Data security
+All the survey information will be stored on github, a publicly available site, as well as on site at QUT.
 
-##	Training
+##	Record retention
+The records of data and analysis undertaken will be stored on github as well as on site at QUT.
 
-##	Record retention (how you will archive/destroy the information that you collect)
-
-##	Secondary use (including providing access, disclosing)
+##	Secondary use 
+The analysis scripts and the data collected will be available for secondary use. Thisn their consent form. will be disclosed to participants
 

### 2019-10-15 R/00_pilot.R

@@ -18,7 +18,8 @@ set.seed(19941030)
 ####################     DATA    ##########################
 # Geography of sa3 areas
 sa3 <- absmapsdata::sa32016
-sa3 <- st_simplify(sa3, preserveTopology = TRUE, dTolerance = 0.001)
+sa3 <- rmapshaper::ms_simplify(sa3, 
+  keep = 0.5, keep_shapes = TRUE, explode = FALSE, drop_null_geometries = TRUE)
 
 # filter out Islands
 Islands <- c("Cocos (Keeling) Islands",	"Christmas Island", "Norfolk Island", "Lord Howe Island")
@@ -80,7 +81,7 @@ hex <- left_join(hexagons_sf, sa3_centroids)
 
 # Manual null data creation
 # Change this parameter to change strength of spatial dependency
-cov.Decay <- 0.5
+cov.Decay <- 0.7
 # Specify the spatial model
 var.g.dummy <- gstat(formula = z ~ 1, 
   locations = ~ longitude + latitude, 
@@ -118,7 +119,7 @@ spatial_smoother <- function(area_number, values_vector, area_weight = 0.5, neig
   return(smoothed_value)
 }
 
-sims <- colnames(var.sim)[5:20]
+sims <- colnames(var.sim)[5:24]
 
 
 ###########################################################
@@ -155,7 +156,8 @@ smoothing <- bind_rows(
 
 sa3_long <- smoothing %>%
   select(-longitude, -latitude, -logsize) %>% 
-  gather(key = "simulation", value = "value", -sa3_name_2016, -groups)
+  gather(key = "simulation", value = "value", -sa3_name_2016, -groups) %>%
+  mutate(simulation = as.numeric(gsub("sim", "", simulation)))
 
 smoothed_alpha <- c(
     smooth1 = "#7a0177",
@@ -175,11 +177,11 @@ s_plot <- sa3_long %>%
   scale_fill_manual(values = smoothed_alpha)
 
 s_plot
-ggsave(filename = "figures/simulation.png", 
+ggsave(filename = "figures/simulation_densities.png", 
   plot = s_plot, device = "png", dpi = 300,
   height = 12, width = 12)
 
-###########################################################
+##########################################################
 
 ## Tasmania plots
 library(gganimate)
@@ -189,34 +191,20 @@ tas_sims <- sa3 %>%
[…]

### 2019-10-15 pilot_ns.R

@@ -3,7 +3,7 @@
 ######################         NORTH TO SOUTH         #########################
 
 # First source the simulated points
-#source('~/experiment/R/00_pilot.R', echo = TRUE)
+# source('~/experiment/R/00_pilot.R', echo = TRUE)
 
 # only use the most smoothed
 sa3_min <- sa3_long %>% 
@@ -13,6 +13,7 @@ sa3_max <- sa3_long %>%
   filter(groups == "smooth5") %>%
   pull(value) %>% max()
 
+
 # use an underlying spatial covariance model
 # add a north to south model
 sa3_ns <- sa3_centroids %>% 
@@ -20,7 +21,7 @@ sa3_ns <- sa3_centroids %>%
   mutate(ns = scales::rescale(ns, to = c(sa3_min,sa3_max)))
 
 ### Start with shapes - geographies
-aus_geo_ns <- sa3 %>% 
+aus_geo_ns <- sa3 %>%
   select(sa3_name_2016) %>% 
   # Add the 16 simulated values for each area
   left_join(., sa3_long) %>% 
@@ -46,14 +47,18 @@ aus_geo_sa3 <- aus_geo_ns %>%
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the null data around the mean of the data
-  mutate(value = ifelse(simulation == pos, true + value, (mean(true) + value*sd(true))))
+  mutate(value = ifelse(simulation == pos,
+    scales::rescale((value+true), c(sa3_min, sa3_max)), 
+    scales::rescale((value), c(sa3_min, sa3_max))))
 
 aus_hex_sa3 <- aus_hex_ns %>% 
   mutate(true = ns) %>% 
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
-  # scale the null data around the mean of the data
-  mutate(value = ifelse(simulation == pos, true + value, (mean(true) + value*sd(true))))
+  # scale the new data around the distribution of null data
+  mutate(value = ifelse(simulation == pos,
+    scales::rescale((value+true), c(sa3_min, sa3_max)), 
+    scales::rescale((value), c(sa3_min, sa3_max))))
 
 
 ############################################################################### 
@@ -64,7 +69,7 @@ aus_geo_ns <- aus_geo_sa3 %>%
   ggplot() + 
[…]

### 2019-10-15 pilot_nwse.R

@@ -30,7 +30,6 @@ source('~/experiment/R/00_pilot.R', echo = TRUE)
 
 # use an underlying spatial covariance model
 # add a north to south model
-sa3_nwse <- sa3_centroids %>% mutate(nwse = abs(latitude-min(latitude)))
 
 ### Start with shapes - geographies
 aus_geo_nwse <- sa3 %>% 
@@ -40,7 +39,7 @@ aus_geo_nwse <- sa3 %>%
   left_join(., sa3_nwse)
 
 ### Start with shapes - hexagons
-aus_hex_nwse <- hexagonwse_sf %>% 
+aus_hex_nwse <- hexagons_sf %>% 
   select(sa3_name_2016) %>% 
   # Add the 20 simulated values for each area
   left_join(., sa3_long) %>% 
@@ -58,15 +57,18 @@ aus_geo_sa3 <- aus_geo_nwse %>%
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the null data around the mean of the data
-  mutate(value = ifelse(simulation == pos, true + value, (mean(true) + value*sd(true))))
+  mutate(value = ifelse(simulation == pos,
+    scales::rescale((value+true), c(sa3_min, sa3_max)), 
+    scales::rescale((value), c(sa3_min, sa3_max))))
 
 aus_hex_sa3 <- aus_hex_nwse %>% 
   mutate(true = nwse) %>% 
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the null data around the mean of the data
-  mutate(value = ifelse(simulation == pos, true + value, (mean(true) + value*sd(true))))
-
+  mutate(value = ifelse(simulation == pos,
+    scales::rescale((value+true), c(sa3_min, sa3_max)), 
+    scales::rescale((value), c(sa3_min, sa3_max))))
 
 ############################################################################### 
 ############################   Population ns       ############################
@@ -82,7 +84,7 @@ aus_geo_nwse <- aus_geo_sa3 %>%
     strip.background = element_rect(fill = "black", colour = NA),
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank())
[…]

### 2019-10-15 pilot_popdensity.R

@@ -73,14 +73,18 @@ aus_geo_sa3 <- aus_geo_smooth_pop %>%
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the null data around the mean of the data
-  mutate(value = ifelse(simulation == pos, true + value, (mean(true) + value*sd(true))))
+  mutate(value = ifelse(simulation == pos,
+    scales::rescale((value+true), c(sa3_min, sa3_max)), 
+    scales::rescale((value), c(sa3_min, sa3_max))))
 
 aus_hex_sa3 <- aus_hex_smooth_pop %>% 
   mutate(true = smoother_density) %>% 
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the null data around the mean of the data
-  mutate(value = ifelse(simulation == pos, true + value, (mean(true) + value*sd(true))))
+  mutate(value = ifelse(simulation == pos,
+    scales::rescale((value+true), c(sa3_min, sa3_max)), 
+    scales::rescale((value), c(sa3_min, sa3_max))))
 
 
 ############################################################################### 
@@ -130,7 +134,7 @@ aus_geo_popdens <- aus_geo_sa3 %>%
     strip.background = element_rect(fill = "black", colour = NA),
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank())
-ggsave(filename = "figures/pop/aus_geo_popdens.png", plot = aus_geo_popdens, device = "png", dpi = 300,
+ggsave(filename = "figures/lineups/aus_geo_popdens.png", plot = aus_geo_popdens, device = "png", dpi = 300,
   height = 12, width = 12)
 
 
@@ -145,7 +149,7 @@ aus_hex_popdens <- aus_hex_sa3 %>%
     strip.background = element_rect(fill = "black", colour = NA),
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank())
-ggsave(filename = "figures/pop/aus_hex_popdens.png", plot = aus_hex_popdens, device = "png", dpi = 300,
+ggsave(filename = "figures/lineups/aus_hex_popdens.png", plot = aus_hex_popdens, device = "png", dpi = 300,
   height = 12, width = 12)
 
 
@@ -220,7 +224,7 @@ tas_popdens <- ggplot(tas_geo_sa3) +
[…]

### 2019-10-16 protocol.Rmd
cities and single city dists

@@
 #	Title
-Assessing the effectiveness of different visualisation methods for Australian spatial data.
+Assessing the effectiveness of visualisation methods for spatial distributions affected by small areas with high population densities.
 
@@
 The purpose of these displays is to convey the spatial distribution of the disease occurrence, or incidence.
-This can allow for detecting hot spots corresponding to outbreaks, or spatial trends, for example, indicating occurrence is related to latitude or even rural vs urban differences.
-Effectiveness of the display will be measured by accurate and efficient perception of these patterns.
+This can allow for detecting hot spots corresponding to outbreaks, or spatial trends, for example, indicating occurrence is related to rural vs urban differences or localised to a single population dense region.
+Effectiveness of the display will be measured by accurate and efficient detection of these patterns.
 
@@
 
-Participants will pick the map of a true distribution in a line up of null maps more often when the information is presented in a hexagon map, as opposed to a geographic map line up.
+When participants see the same data set displayed a line up as a hexagon tile map and geographic map, participants will pick the map that displays a pattern influenced by population density more often when the information is presented in a hexagon tile map.
 
@@
 
-1.	Measure the accuracy in spotting a real spatial distribution from a line-up of null maps
-2.	Contrast the accuracy when participants pick from geographic or hexagon maps
+1.	Measure the accuracy in spotting a real population density related spatial distribution from a line-up of null maps
+2.	Contrast the accuracy and efficiency when participants pick from geographic or hexagon maps
 
@@
 
-- Plot type ( Hexagon/ Geographic )
-- Spatial dependence structure (Normal errors / Chi-squared errors )
+- Plot type ( Hexagon / Geographic )
+- Spatial dependence structure ( Difference in a single city / Related to population density / North to South )
 
@@
  - Plot type: Geography, Hexagons
- - Error distribution: Normal, Chi-Square
- - Spatial Dependence: Rurality level, North to South, East to West
+ - Spatial Dependence: Difference in a single city, Related to population density, North to South
 
@@
 Participants will be able to withdraw by leaving the survey at any time.
-XXX will they still be paid?
 
@@
 ##	Data analysis and Statistical methods
-
-Information will be collected regarding the design
-(including how will you measure, manipulate and/or analyse the information that you collect/gather, matching and sampling strategies, accounting for potential bias, confounding factors and missing information)
 

### 2019-10-16 pilot_cities.R

@@ -1,6 +1,6 @@
 
 ###############################################################################
-######################         NORTH TO SOUTH         #########################
+######################     cities CITY DIFFERENCE     #########################
 
 # First source the simulated points
 # source('~/experiment/R/00_pilot.R', echo = TRUE)
@@ -15,26 +15,31 @@ sa3_max <- sa3_long %>%
 
 
 # use an underlying spatial covariance model
-# add a north to south model
-sa3_ns <- sa3_centroids %>% 
-  mutate(ns = abs(latitude-min(latitude))) %>% 
-  mutate(ns = scales::rescale(ns, to = c(sa3_min,sa3_max)))
+# increase the values of Brisbane, depending on distance from Brisbane city
+# allocated: the data set containing the allocated hexagon centroid for each sa3
+max_dist <- 1478314 # furthest area from any focal point
+
+sa3_cities <- allocated %>% 
+  select(sa3_name_2016, longitude, latitude, points, focal_dist) %>% 
+  mutate(cities = sqrt(max_dist - focal_dist)) %>%
+  # keep a reasonable scale to match null plots
+  mutate(cities = scales::rescale(cities, to = c(sa3_min, sa3_max)))
 
 ### Start with shapes - geographies
-aus_geo_ns <- sa3 %>%
+aus_geo_cities <- sa3 %>%
   select(sa3_name_2016) %>% 
   # Add the 16 simulated values for each area
   left_join(., sa3_long) %>% 
-  left_join(., sa3_ns)
+  left_join(., sa3_cities)
 
 ### Start with shapes - hexagons
-aus_hex_ns <- hexagons_sf %>% 
+aus_hex_cities <- hexagons_sf %>% 
   select(sa3_name_2016) %>% 
   # Add the 16 simulated values for each area
   left_join(., sa3_long) %>% 
-  left_join(., sa3_ns)
+  left_join(., sa3_cities)
 
-  
+
 ############################################################################### 
 
 # Add the distribution will be added to one of the null plots
@@ -42,22 +47,20 @@ aus_hex_ns <- hexagons_sf %>%
 # Choose a location for the true data in the plot
 pos <- sample(1:20, 1)
 
-aus_geo_sa3 <- aus_geo_ns %>%
-  mutate(true = ns) %>% 
[…]

### 2019-10-16 pilot_nwse.R

@@ -18,9 +18,10 @@ sa3_max <- sa3_long %>%
 sa3_nwse <- sa3_centroids %>% 
   mutate(lat = abs(latitude-min(latitude)),
     long = abs(longitude-min(longitude)),
-    nwse = lat*long) %>% 
+    nwse = (2*lat)-long) %>% 
   mutate(nwse = scales::rescale(nwse, to = c(sa3_min, sa3_max))) %>%
   select(-lat, -long)
+
 
 ###############################################################################
 ######################         NORTH TO SOUTH         #########################
@@ -78,7 +79,7 @@ aus_geo_nwse <- aus_geo_sa3 %>%
   ggplot() + 
   geom_sf(aes(fill = value), colour = NA) + 
   scale_fill_distiller(type = "div", palette = "RdYlGn") + 
-  facet_grid(~ simulation) + theme_minimal() +
+  facet_wrap(~ simulation) + theme_minimal() +
   theme(plot.background = element_rect(fill = "black"),
     panel.background = element_rect(fill = "black", colour = NA),
     strip.background = element_rect(fill = "black", colour = NA),
@@ -92,7 +93,7 @@ aus_hex_nwse <- aus_hex_sa3 %>%
   ggplot() + 
   geom_sf(aes(fill = value), colour = NA) + 
  scale_fill_distiller(type = "div", palette = "RdYlGn") + 
-  facet_grid(~ simulation) + theme_minimal() +
+  facet_wrap(~ simulation) + theme_minimal() +
   theme(plot.background = element_rect(fill = "black"),
     panel.background = element_rect(fill = "black", colour = NA),
     strip.background = element_rect(fill = "black", colour = NA),
@@ -100,39 +101,6 @@ aus_hex_nwse <- aus_hex_sa3 %>%
     panel.grid.minor = element_blank())
 ggsave(filename = "figures/lineups/aus_hex_nwse.png", plot = aus_hex_nwse, device = "png", dpi = 300,
   height = 9, width = 18)
-
-
-############################################################################### 
-#########################    Population density ns    #########################
-############################################################################### 
-
-aus_geo_nwse <- aus_geo_sa3 %>% 
-  ggplot() + 
-  geom_sf(aes(fill = value), colour = NA) + 
[…]

### 2019-10-16 pilot_popdensity.R

@@ -51,7 +51,7 @@ aus_geo_smooth_pop <- sa3 %>%
   # Add the 16 simulated values for each area
   left_join(., sa3_long) %>% 
   left_join(., sa3_smooth_pop) %>% 
-  gather("iteration", "smoother_density", contains("popdens"))
+  gather("groups", "smoother_density", contains("popdens"))
 
 ### Start with shapes - hexagons
 aus_hex_smooth_pop <- hexagons_sf %>% 
@@ -59,7 +59,7 @@ aus_hex_smooth_pop <- hexagons_sf %>%
   # Add the 20 simulated values for each area
   left_join(., sa3_long) %>% 
   left_join(., sa3_smooth_pop) %>% 
-  gather("iteration", "smoother_density", contains("popdens"))
+  gather("groups", "smoother_density", contains("popdens"))
 
 ############################################################################### 
 
@@ -182,8 +182,8 @@ smoothed_alpha <- c(
   s6_popdens16 = "#ffffff")         
 
 spop_plot <- tas_geo_sa3 %>%
-  mutate(groups = factor(iteration, levels = c("s1_popdens16", "s2_popdens16", "s3_popdens16","s4_popdens16", "s5_popdens16", "s6_popdens16"))) %>% 
-  group_by(groups, iteration) %>% 
+  mutate(groups = factor(groups, levels = c("s1_popdens16", "s2_popdens16", "s3_popdens16","s4_popdens16", "s5_popdens16", "s6_popdens16"))) %>% 
+  group_by(groups, groups) %>% 
   mutate(mean_value  = mean(smoother_density)) %>% 
   ggplot() + 
   geom_density(aes(x= smoother_density, fill = groups), alpha = 0.3) +
@@ -195,7 +195,7 @@ tas_smoothed <- tas_geo_sa3 %>%
   ggplot() + 
   geom_sf(aes(fill = smoother_density)) + 
   scale_fill_distiller(type = "div", palette = "RdYlGn") +
-  facet_wrap(~iteration)
+  facet_wrap(~groups)
 ggsave(filename = "figures/pop/tas_smoothed.png", plot = tas_smoothed, device = "png", dpi = 300,
   height = 6, width = 6)
 
@@ -203,7 +203,7 @@ ggsave(filename = "figures/pop/tas_smoothed.png", plot = tas_smoothed, device = 
 hex_smoothed <- tas_hex_sa3 %>% 
[…]

### 2019-10-16 pilot_single.R

@@ -1,0 +1,104 @@
+
+###############################################################################
+######################     SINGLE CITY DIFFERENCE     #########################
+
+# First source the simulated points
+# source('~/experiment/R/00_pilot.R', echo = TRUE)
+
+# only use the most smoothed
+sa3_min <- sa3_long %>% 
+  filter(groups == "smooth5") %>%
+  pull(value) %>% min()
+sa3_max <- sa3_long %>% 
+  filter(groups == "smooth5") %>%
+  pull(value) %>% max()
+
+sa3_mean <- sa3_long %>% 
+  filter(groups == "smooth5") %>%
+  pull(value) %>% mean()
+
+
+# use an underlying spatial covariance model
+# increase the values of Brisbane, depending on distance from Brisbane city
+# allocated: the data set containing the allocated hexagon centroid for each sa3
+max_dist <- 1478314 # furthest area with Brisbane focal point
+
+sa3_single <- allocated %>% 
+  select(sa3_name_2016, longitude, latitude, points, focal_dist) %>% 
+  mutate(single = ifelse(points == "Brisbane", scales::rescale(sqrt(max_dist - focal_dist), to = c(sa3_mean, sa3_max)), NA))
+    
+    
+### Start with shapes - geographies
+aus_geo_single <- sa3 %>%
+  select(sa3_name_2016) %>% 
+  # Add the 16 simulated values for each area
+  left_join(., sa3_long) %>% 
+  left_join(., sa3_single)
+
+### Start with shapes - hexagons
+aus_hex_single <- hexagons_sf %>% 
+  select(sa3_name_2016) %>% 
+  # Add the 16 simulated values for each area
+  left_join(., sa3_long) %>% 
+  left_join(., sa3_single)
+
+
+############################################################################### 
+
+# Add the distribution will be added to one of the null plots
+
+# Choose a location for the true data in the plot
+pos <- sample(1:12, 1)
+
+aus_geo_sa3 <- aus_geo_single %>%
+  mutate(true = single) %>% 
+  mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
+  # add the spatial trend model to the null data plot
+  # scale the null data around the mean of the data
+  mutate(value = ifelse(simulation == pos, ifelse(!is.na(true), true, value), 
+    scales::rescale((value), c(sa3_min, sa3_max))))
+
+aus_hex_sa3 <- aus_hex_single %>% 
[…]

### 2019-10-16 R/00_pilot.R
single city and all cities

@@ -60,7 +60,7 @@ hexagons <- fortify_hexagon(data = allocated, sf_id = "sa3_name_2016", hex_size 
 # Convert hexagons to polygons for plotting
 # This will order the areas by the sf_id, this results in alphabetical order
 hexagons_sf <- hexagons %>% 
-  select(sa3_name_2016, long, lat) %>% 
+  select(sa3_name_2016, long, lat, points, focal_dist) %>% 
   sf::st_as_sf(coords = c("long", "lat"), crs = 4283) %>%
   group_by(sa3_name_2016) %>% 
   summarise(do_union = FALSE) %>%
@@ -81,15 +81,15 @@ hex <- left_join(hexagons_sf, sa3_centroids)
 
 # Manual null data creation
 # Change this parameter to change strength of spatial dependency
-cov.Decay <- 0.7
+cov.Decay <- 0.5
 # Specify the spatial model
 var.g.dummy <- gstat(formula = z ~ 1, 
   locations = ~ longitude + latitude, 
   dummy = T, beta = 1, model = vgm(psill = 1, model = "Gau", range = cov.Decay),
-  nmax = 20)
+  nmax = 12)
 
 # Create underlying spatially dependent data for 16 null plots
-var.sim <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 20) %>% 
+var.sim <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
   left_join(sa3_centroids, ., by=c("longitude", "latitude"))
 
 
@@ -119,7 +119,7 @@ spatial_smoother <- function(area_number, values_vector, area_weight = 0.5, neig
   return(smoothed_value)
 }
 
-sims <- colnames(var.sim)[5:24]
+sims <- colnames(var.sim)[5:length(colnames(var.sim))]
 
 
 ###########################################################
@@ -192,7 +192,7 @@ tas_sims <- sa3 %>%
   left_join(., sa3_long)
 
 tas <- tas_sims %>% 
-  ggplot() + geom_sf(aes(fill = value)) + scale_fill_distiller(type = "div", palette = "RdYlGn") +
+  ggplot() + geom_sf(aes(fill = value)) + scale_fill_distiller(type = "div", palette = "RdYlBu") +
   facet_grid(groups~simulation)
 ggsave(filename = "figures/tas_simulation.png", plot = tas, device = "png", dpi = 300,
   height = 6, width = 6)
[…]

### 2019-10-16 pilot_cities.R

@@ -23,7 +23,7 @@ sa3_cities <- allocated %>%
   select(sa3_name_2016, longitude, latitude, points, focal_dist) %>% 
   mutate(cities = sqrt(max_dist - focal_dist)) %>%
   # keep a reasonable scale to match null plots
-  mutate(cities = scales::rescale(cities, to = c(sa3_min, sa3_max)))
+  mutate(cities = scales::rescale(cities, to = c(sa3_mean, sa3_max)))
 
 ### Start with shapes - geographies
 aus_geo_cities <- sa3 %>%
@@ -79,7 +79,7 @@ aus_geo_cities_plot <- aus_geo_sa3 %>%
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank())
 ggsave(filename = "figures/cities/aus_geo_cities.png", plot = aus_geo_cities_plot, device = "png", dpi = 300,
-  height = 9, width = 18)
+  height = 9, width = 9)
 
 
 aus_hex_cities_plot <- aus_hex_sa3 %>% 
@@ -93,113 +93,5 @@ aus_hex_cities_plot <- aus_hex_sa3 %>%
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank())
 ggsave(filename = "figures/cities/aus_hex_cities.png", plot = aus_hex_cities_plot, device = "png", dpi = 300,
-  height = 9, width = 18)
-
-
-
-
-############################################################################### 
-############################       Tasmania        ############################
-############################################################################### 
-
-
-tas_geo_sa3 <- aus_geo_sa3 %>%
-  filter(sa3_name_2016 %in% Tasmania)
-
-tas_hex_sa3 <- aus_hex_sa3 %>%
-  filter(sa3_name_2016 %in% Tasmania)
-
-###############################################################################
-tas_geo_sa3 %>% 
-  ggplot() + geom_density(aes(x = cities)) + 
-  scale_fill_distiller(type = "div", palette = "RdYlBu")
-ggsave(filename = "figures/cities/density.png", plot = tas_cities, device = "png", dpi = 300,
-  height = 6, width = 6)
-
-
-spop_plot <- tas_geo_sa3 %>%
-  group_by(groups) %>% 
-  mutate(mean_value  = mean(cities)) %>% 
-  ggplot() + 
-  geom_density(aes(x= cities, fill = groups), alpha = 0.3) +
-  geom_vline(aes(xintercept = mean_value), colour = "black") + 
-  scale_fill_manual(values = cities_alpha)
[…]

### 2019-10-16 pilot_single.R

@@ -83,7 +83,7 @@ aus_geo_single_plot <- aus_geo_sa3 %>%
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank())
 ggsave(filename = "figures/single/aus_geo_single.png", plot = aus_geo_single_plot, device = "png", dpi = 300,
-  height = 9, width = 18)
+  height = 9, width = 9)
 
 
 aus_hex_single_plot <- aus_hex_sa3 %>% 
@@ -98,7 +98,7 @@ aus_hex_single_plot <- aus_hex_sa3 %>%
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank())
 ggsave(filename = "figures/single/aus_hex_single.png", plot = aus_hex_single_plot, device = "png", dpi = 300,
-  height = 9, width = 18)
+  height = 9, width = 9)
 
 
 

### 2019-10-16 pilot_cities.R
single city and all cities

@@ -79,7 +79,7 @@ aus_geo_cities_plot <- aus_geo_sa3 %>%
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank())
 ggsave(filename = "figures/cities/aus_geo_cities.png", plot = aus_geo_cities_plot, device = "png", dpi = 300,
-  height = 9, width = 18)
+  height = 18, width = 18)
 
 
 aus_hex_cities_plot <- aus_hex_sa3 %>% 
@@ -93,113 +93,5 @@ aus_hex_cities_plot <- aus_hex_sa3 %>%
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank())
 ggsave(filename = "figures/cities/aus_hex_cities.png", plot = aus_hex_cities_plot, device = "png", dpi = 300,
-  height = 9, width = 18)
-
-
-
-
-############################################################################### 
-############################       Tasmania        ############################
-############################################################################### 
-
-
-tas_geo_sa3 <- aus_geo_sa3 %>%
-  filter(sa3_name_2016 %in% Tasmania)
-
-tas_hex_sa3 <- aus_hex_sa3 %>%
-  filter(sa3_name_2016 %in% Tasmania)
-
-###############################################################################
-tas_geo_sa3 %>% 
-  ggplot() + geom_density(aes(x = cities)) + 
-  scale_fill_distiller(type = "div", palette = "RdYlBu")
-ggsave(filename = "figures/cities/density.png", plot = tas_cities, device = "png", dpi = 300,
-  height = 6, width = 6)
-
-
-spop_plot <- tas_geo_sa3 %>%
-  group_by(groups) %>% 
-  mutate(mean_value  = mean(cities)) %>% 
-  ggplot() + 
-  geom_density(aes(x= cities, fill = groups), alpha = 0.3) +
-  geom_vline(aes(xintercept = mean_value), colour = "black") + 
-  scale_fill_manual(values = cities_alpha)
-spop_plot
-
-tas_cities <- tas_geo_sa3 %>% 
-  ggplot() + 
-  geom_sf(aes(fill = cities)) + 
-  scale_fill_distiller(type = "div", palette = "RdYlBu") +
-  facet_wrap(~groups)
-ggsave(filename = "figures/cities/tas_cities.png", plot = tas_cities, device = "png", dpi = 300,
-  height = 6, width = 6)
-
-
[…]

### 2019-10-16 pilot_single.R

@@ -83,7 +83,7 @@ aus_geo_single_plot <- aus_geo_sa3 %>%
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank())
 ggsave(filename = "figures/single/aus_geo_single.png", plot = aus_geo_single_plot, device = "png", dpi = 300,
-  height = 9, width = 18)
+  height = 18, width = 18)
 
 
 aus_hex_single_plot <- aus_hex_sa3 %>% 
@@ -98,7 +98,7 @@ aus_hex_single_plot <- aus_hex_sa3 %>%
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank())
 ggsave(filename = "figures/single/aus_hex_single.png", plot = aus_hex_single_plot, device = "png", dpi = 300,
-  height = 9, width = 18)
+  height = 18, width = 18)
 
 
 

### 2019-10-16 pilot_cities.R
new title

@@ -21,9 +21,9 @@ max_dist <- 1478314 # furthest area from any focal point
 
 sa3_cities <- allocated %>% 
   select(sa3_name_2016, longitude, latitude, points, focal_dist) %>% 
-  mutate(cities = sqrt(max_dist - focal_dist)) %>%
+  mutate(cities = (scales::rescale(max_dist - focal_dist,to = c(0,1))^10)) %>%
   # keep a reasonable scale to match null plots
-  mutate(cities = scales::rescale(cities, to = c(sa3_mean, sa3_max)))
+  mutate(cities = scales::rescale(cities, to = c(sa3_min, sa3_max)))
 
 ### Start with shapes - geographies
 aus_geo_cities <- sa3 %>%

### 2019-10-16 R/00_pilot.R
use a ranking for distance

@@ -12,7 +12,7 @@ library(sugarbag)
 library(tidyverse)
 library(viridis)
 
-set.seed(19941030)
+set.seed(19941031)
 
 ###########################################################
 ####################     DATA    ##########################
@@ -42,20 +42,26 @@ sa3_centroids$logsize <- log(sa3$areasqkm_2016)
 
 
 ###########################################################
+################    AUSTRALIA    ##########################
+
+aus_underlay <- st_union(sa3$geometry)
+
+
+###########################################################
 ####################    HEXMAP   ##########################
 # Create hexagon map of sa3
 allocated <- create_hexmap(
   shp = sa3,
   buffer_dist = 2,
   sf_id = "sa3_name_2016",
-  hex_size = 0.5, # same size used in create_grid
+  hex_size = 0.6, # same size used in create_grid
   hex_filter = 10,
   f_width = 30,
   focal_points = capital_cities,
   verbose = TRUE)
 
 # same column used in create_hexmap
-hexagons <- fortify_hexagon(data = allocated, sf_id = "sa3_name_2016", hex_size = 0.5)
+hexagons <- fortify_hexagon(data = allocated, sf_id = "sa3_name_2016", hex_size = 0.6)
 
 # Convert hexagons to polygons for plotting
 # This will order the areas by the sf_id, this results in alphabetical order
@@ -81,11 +87,10 @@ hex <- left_join(hexagons_sf, sa3_centroids)
 
 # Manual null data creation
 # Change this parameter to change strength of spatial dependency
-cov.Decay <- 0.5
 # Specify the spatial model
 var.g.dummy <- gstat(formula = z ~ 1, 
   locations = ~ longitude + latitude, 
-  dummy = T, beta = 1, model = vgm(psill = 1, model = "Gau", range = cov.Decay),
+  dummy = T, beta = 1, model = vgm(psill = 1, model = "Gau", range = 0.5),
   nmax = 12)
 
 # Create underlying spatially dependent data for 16 null plots
@@ -137,21 +142,11 @@ sa3_sims3 <- sa3_sims2 %>%
   mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
[…]

### 2019-10-16 pilot_cities.R

@@ -1,17 +1,20 @@
 
 ###############################################################################
-######################     cities CITY DIFFERENCE     #########################
+######################          CITY DIFFERENCE       #########################
 
 # First source the simulated points
 # source('~/experiment/R/00_pilot.R', echo = TRUE)
 
 # only use the most smoothed
 sa3_min <- sa3_long %>% 
-  filter(groups == "smooth5") %>%
+  filter(groups == "smooth3") %>%
   pull(value) %>% min()
 sa3_max <- sa3_long %>% 
-  filter(groups == "smooth5") %>%
+  filter(groups == "smooth3") %>%
   pull(value) %>% max()
+sa3_mean <- sa3_long %>% 
+  filter(groups == "smooth3") %>%
+  pull(value) %>% mean()
 
 
 # use an underlying spatial covariance model
@@ -21,9 +24,12 @@ max_dist <- 1478314 # furthest area from any focal point
 
 sa3_cities <- allocated %>% 
   select(sa3_name_2016, longitude, latitude, points, focal_dist) %>% 
-  mutate(cities = (scales::rescale(max_dist - focal_dist,to = c(0,1))^10)) %>%
-  # keep a reasonable scale to match null plots
-  mutate(cities = scales::rescale(cities, to = c(sa3_min, sa3_max)))
+  mutate(cities = (max_dist - focal_dist)^8,
+         dist_rank = rank(focal_dist),
+         cities = ifelse(dist_rank == 50, -2, 
+                         scales::rescale(cities, to = c(mean(sa3_min, sa3_mean), sa3_max))))
+
+ggplot(sa3_cities) + geom_histogram(aes(x = cities))
 
 ### Start with shapes - geographies
 aus_geo_cities <- sa3 %>%
@@ -45,30 +51,39 @@ aus_hex_cities <- hexagons_sf %>%
 # Add the distribution will be added to one of the null plots
 
 # Choose a location for the true data in the plot
-pos <- sample(1:20, 1)
+set.seed(19941031)
+pos <- sample(1:12, 1)
 
-aus_geo_sa3 <- aus_geo_cities %>%
+aus_geo_sa3_cities <- aus_geo_cities %>%
   mutate(true = cities) %>% 
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the null data around the mean of the data
-  mutate(value = ifelse(simulation == pos, true, 
[…]

### 2019-10-16 pilot_ns.R

@@ -7,11 +7,15 @@
 
 # only use the most smoothed
 sa3_min <- sa3_long %>% 
-  filter(groups == "smooth5") %>%
+  filter(groups == "smooth3") %>%
   pull(value) %>% min()
 sa3_max <- sa3_long %>% 
-  filter(groups == "smooth5") %>%
+  filter(groups == "smooth3") %>%
   pull(value) %>% max()
+
+sa3_mean <- sa3_long %>% 
+  filter(groups == "smooth3") %>%
+  pull(value) %>% mean()
 
 
 # use an underlying spatial covariance model
@@ -40,7 +44,8 @@ aus_hex_ns <- hexagons_sf %>%
 # Add the distribution will be added to one of the null plots
 
 # Choose a location for the true data in the plot
-pos <- sample(1:20, 1)
+set.seed(19941030)
+pos <- sample(1:12, 1)
 
 aus_geo_sa3 <- aus_geo_ns %>%
   mutate(true = ns) %>% 
@@ -120,7 +125,7 @@ spop_plot <- tas_geo_sa3 %>%
   ggplot() + 
   geom_density(aes(x= ns, fill = groups), alpha = 0.3) +
   geom_vline(aes(xintercept = mean_value), colour = "black") + 
-  scale_fill_manual(values = ns_alpha)
+  scale_fill_manual(values = smoothed_alpha)
 spop_plot
 
 tas_ns <- tas_geo_sa3 %>% 
@@ -185,7 +190,7 @@ tas_ns <- tas_geo_sa3 %>%
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank())
 ggsave(filename = "figures/lineups/tas/ns_geo.png", 
-  plot = tas_ns, dpi=300, device = "png", width = 12, height = 12)
+  plot = tas_ns, dpi=300, device = "png", height = 18, width = 18)
 
 hex_ns <- tas_hex_sa3 %>% 
   ggplot() + 
@@ -198,5 +203,5 @@ hex_ns <- tas_hex_sa3 %>%
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank())
 ggsave(filename = "figures/lineups/tas/ns_hex.png", 
-  plot = hex_ns, dpi=300, device = "png", width = 12, height = 12)
+  plot = hex_ns, dpi=300, device = "png", height = 18, width = 18)
 

### 2019-10-16 pilot_single.R

@@ -7,14 +7,14 @@
 
 # only use the most smoothed
 sa3_min <- sa3_long %>% 
-  filter(groups == "smooth5") %>%
+  filter(groups == "smooth3") %>%
   pull(value) %>% min()
 sa3_max <- sa3_long %>% 
-  filter(groups == "smooth5") %>%
+  filter(groups == "smooth3") %>%
   pull(value) %>% max()
 
 sa3_mean <- sa3_long %>% 
-  filter(groups == "smooth5") %>%
+  filter(groups == "smooth3") %>%
   pull(value) %>% mean()
 
 
@@ -25,7 +25,8 @@ max_dist <- 1478314 # furthest area with Brisbane focal point
 
 sa3_single <- allocated %>% 
   select(sa3_name_2016, longitude, latitude, points, focal_dist) %>% 
-  mutate(single = ifelse(points == "Brisbane", scales::rescale(sqrt(max_dist - focal_dist), to = c(sa3_mean, sa3_max)), NA))
+  mutate(single = ifelse(points == "Brisbane", scales::rescale(
+    (max_dist - focal_dist)^10, to = c(sa3_mean, sa3_max)), NA))
     
     
 ### Start with shapes - geographies
@@ -48,30 +49,38 @@ aus_hex_single <- hexagons_sf %>%
 # Add the distribution will be added to one of the null plots
 
 # Choose a location for the true data in the plot
+set.seed(19941030)
 pos <- sample(1:12, 1)
 
-aus_geo_sa3 <- aus_geo_single %>%
+aus_geo_sa3_single <- aus_geo_single %>%
   mutate(true = single) %>% 
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the null data around the mean of the data
-  mutate(value = ifelse(simulation == pos, ifelse(!is.na(true), true, value), 
+  mutate(value = ifelse(
+    simulation == pos, ifelse(!is.na(true), true, value), 
     scales::rescale((value), c(sa3_min, sa3_max))))
 
-aus_hex_sa3 <- aus_hex_single %>% 
+aus_hex_sa3_single <- aus_hex_single %>% 
   mutate(true = single) %>% 
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the new data around the distribution of null 
[…]

### 2019-10-16 pilot_cities.R
use a ranking for distance

@@ -1,17 +1,20 @@
 
 ###############################################################################
-######################     cities CITY DIFFERENCE     #########################
+######################          CITY DIFFERENCE       #########################
 
 # First source the simulated points
 # source('~/experiment/R/00_pilot.R', echo = TRUE)
 
 # only use the most smoothed
 sa3_min <- sa3_long %>% 
-  filter(groups == "smooth5") %>%
+  filter(groups == "smooth3") %>%
   pull(value) %>% min()
 sa3_max <- sa3_long %>% 
-  filter(groups == "smooth5") %>%
+  filter(groups == "smooth3") %>%
   pull(value) %>% max()
+sa3_mean <- sa3_long %>% 
+  filter(groups == "smooth3") %>%
+  pull(value) %>% mean()
 
 
 # use an underlying spatial covariance model
@@ -21,9 +24,12 @@ max_dist <- 1478314 # furthest area from any focal point
 
 sa3_cities <- allocated %>% 
   select(sa3_name_2016, longitude, latitude, points, focal_dist) %>% 
-  mutate(cities = (scales::rescale(max_dist - focal_dist,to = c(0,1))^10)) %>%
-  # keep a reasonable scale to match null plots
-  mutate(cities = scales::rescale(cities, to = c(sa3_min, sa3_max)))
+  mutate(cities = (max_dist - focal_dist)^8,
+         dist_rank = rank(focal_dist),
+         cities = ifelse(dist_rank == 50, -2, 
+                         scales::rescale(cities, to = c(mean(c(sa3_min, sa3_mean)), sa3_max))))
+
+ggplot(sa3_cities) + geom_histogram(aes(x = cities))
 
 ### Start with shapes - geographies
 aus_geo_cities <- sa3 %>%
@@ -45,30 +51,39 @@ aus_hex_cities <- hexagons_sf %>%
 # Add the distribution will be added to one of the null plots
 
 # Choose a location for the true data in the plot
-pos <- sample(1:20, 1)
+set.seed(19941031)
+pos <- sample(1:12, 1)
 
-aus_geo_sa3 <- aus_geo_cities %>%
+aus_geo_sa3_cities <- aus_geo_cities %>%
   mutate(true = cities) %>% 
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the null data around the mean of the data
[…]

### 2019-10-17 pilot_cities.R
use pdf outputs

@@ -2,18 +2,20 @@
 ###############################################################################
 ######################          CITY DIFFERENCE       #########################
 
+# Which map shows the most areas coloured red?
+
 # First source the simulated points
 # source('~/experiment/R/00_pilot.R', echo = TRUE)
 
 # only use the most smoothed
 sa3_min <- sa3_long %>% 
-  filter(groups == "smooth3") %>%
+  filter(groups == "smooth1") %>%
   pull(value) %>% min()
 sa3_max <- sa3_long %>% 
-  filter(groups == "smooth3") %>%
+  filter(groups == "smooth1") %>%
   pull(value) %>% max()
 sa3_mean <- sa3_long %>% 
-  filter(groups == "smooth3") %>%
+  filter(groups == "smooth1") %>%
   pull(value) %>% mean()
 
 
@@ -24,10 +26,12 @@ max_dist <- 1478314 # furthest area from any focal point
 
 sa3_cities <- allocated %>% 
   select(sa3_name_2016, longitude, latitude, points, focal_dist) %>% 
-  mutate(cities = (max_dist - focal_dist)^8,
-         dist_rank = rank(focal_dist),
-         cities = ifelse(dist_rank == 50, -2, 
-                         scales::rescale(cities, to = c(mean(c(sa3_min, sa3_mean)), sa3_max))))
+  mutate(city_distance = (max_dist - focal_dist)^8,
+         dist = scales::rescale(city_distance,
+                                     to = c(0,1)),
+         cities = ifelse(dist < 0.92, NA, 
+                         scales::rescale(city_distance,
+                        to = c(sa3_mean, sa3_max))))
 
 
 ggplot(sa3_cities) + geom_histogram(aes(x = cities))
@@ -61,8 +65,10 @@ aus_geo_sa3_cities <- aus_geo_cities %>%
   # add the spatial trend model to the null data plot
   # scale the null data around the mean of the data
   mutate(value = ifelse(simulation == pos, 
-                        scales::rescale((value+true), c(1, sa3_max)), 
-                        scales::rescale((value), c(sa3_min, sa3_max))))
+         # for the true data plot, keep random values if not close enough to cities
+         ifelse(is.na(cities), value, true),
+         # for all others rescale to the same range
+         scales::rescale((value), c(sa3_min, sa3_max))))
 
 aus_hex_sa3_cities <- aus_hex_cities %>% 
   mutate(true = cities) %>% 
[…]

### 2019-10-18 pilot_cities.R
cities refined

@@ -64,7 +64,7 @@ sa3_cities <- allocated %>%
   mutate(city_distance = (max_dist - focal_dist)^8,
          dist = scales::rescale(city_distance,
                                      to = c(0,1)),
-         cities = ifelse(dist < 0.92, NA, 
+         cities = ifelse(dist < 0.85, NA, 
                          scales::rescale(city_distance,
                         to = c(sa3_mean, sa3_max))))
 
@@ -98,19 +98,21 @@ aus_geo_sa3_cities <- aus_geo_cities %>%
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the null data around the mean of the data
+  group_by(simulation) %>% 
   mutate(value = ifelse(simulation == pos, 
          # for the true data plot, keep random values if not close enough to cities
          ifelse(is.na(cities), value, true),
          # for all others rescale to the same range
          scales::rescale((value), c(sa3_min, sa3_max))))
 
-pos <- 1
+pos <- 6
 
 aus_hex_sa3_cities <- aus_hex_cities %>% 
   mutate(true = cities) %>% 
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the new data around the distribution of null data
+  group_by(simulation) %>% 
   mutate(value = ifelse(simulation == pos, 
                         # for the true data plot, keep random values if not close enough to cities
                         ifelse(is.na(cities), value, true),

### 2019-10-18 pilot_ns.R

@@ -92,7 +92,7 @@ aus_geo_sa3_ns <- aus_geo_ns %>%
   # add the spatial trend model to the null data plot
   # scale the null data around the mean of the data
   mutate(value = ifelse(simulation == pos,
-    scales::rescale((value), c(sa3_min, sa3_max)+true), 
+    scales::rescale((value+true), c(sa3_min, sa3_max)), 
     scales::rescale((value), c(sa3_min, sa3_max))))
 
 pos <- 8
@@ -103,7 +103,7 @@ aus_hex_sa3_ns <- aus_hex_ns %>%
   # add the spatial trend model to the null data plot
   # scale the new data around the distribution of null data
   mutate(value = ifelse(simulation == pos,
-    scales::rescale((value), c(sa3_min, sa3_max)+true), 
+    scales::rescale((value+true), c(sa3_min, sa3_max)), 
     scales::rescale((value), c(sa3_min, sa3_max))))
 
 

### 2019-10-18 pilot_single.R

@@ -85,13 +85,14 @@ aus_hex_single <- hexagons_sf %>%
 # Add the distribution will be added to one of the null plots
 
 # Choose a location for the true data in the plot
-pos <- 4
+pos <- 11
 
 aus_geo_sa3_single <- aus_geo_single %>%
   mutate(true = single) %>% 
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the null data around the mean of the data
+  group_by(simulation) %>% 
   mutate(value = ifelse(
     simulation == pos, ifelse(!is.na(true), true, value), 
     scales::rescale((value), c(sa3_min, sa3_max))))
@@ -102,6 +103,7 @@ aus_hex_sa3_single <- aus_hex_single %>%
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the new data around the distribution of null 
+  group_by(simulation) %>% 
   mutate(value = ifelse(
     simulation == pos, ifelse(!is.na(true), true, value), 
     scales::rescale((value), c(sa3_min, sa3_max))))
@@ -110,7 +112,8 @@ aus_hex_sa3_single <- aus_hex_single %>%
 ############################                       ############################
 ############################################################################### 
 
-ggplot(aus_hex_sa3_single) + geom_histogram(aes(x=value)) + facet_wrap(~simulation)
+ggplot(aus_hex_sa3_single %>%  filter(groups == "smooth3")) + 
+  geom_histogram(aes(x=value)) + facet_wrap(~simulation)
 
 
 ############################################################################### 

### 2019-10-18 pilot_ns.R
single cities

@@ -84,7 +84,7 @@ aus_hex_ns <- hexagons_sf %>%
 # Add the distribution will be added to one of the null plots
 
 # Choose a location for the true data in the plot
-pos <- 10
+pos <- 8
 
 aus_geo_sa3_ns <- aus_geo_ns %>%
   mutate(true = ns) %>% 

### 2019-10-18 pilot_nwse.R

@@ -2,16 +2,57 @@
 ###############################################################################
 ######################    NORTH WEST TO SOUTH EAST    #########################
 
-# First source the simulated points
-#source('~/experiment/R/00_pilot.R', echo = TRUE)
+
+set.seed(2017)
+var.g.dummy <- gstat(formula = z ~ 1, 
+                     locations = ~ longitude + latitude, 
+                     dummy = T, beta = 1, model = vgm(psill = 1, model = "Gau", range = 0.3),
+                     nmax = 12)
+
+# Create underlying spatially dependent data for 12 null plots
+var.sim <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
+
+# use an underlying spatial covariance model
+
+sa3_sims1 <- as_tibble(var.sim) %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
+                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+
+sa3_sims2 <- sa3_sims1 %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
+                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+
+sa3_sims3 <- sa3_sims2 %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
+                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+
+
+smoothing <- bind_rows(
+  "smooth1" = sa3_sims1,
+  "smooth2" = sa3_sims2, 
+  "smooth3" = sa3_sims3, .id = "groups")
+
+
+sa3_long <- smoothing %>%
+  select(-longitude, -latitude, -logsize) %>% 
+  gather(key = "simulation", value = "value", -sa3_name_2016, -groups) %>%
+  mutate(simulation = as.numeric(gsub("sim", "", simulation)))
+
+
 
 # only use the most smoothed
 sa3_min <- sa3_long %>% 
-  filter(groups == "smooth5") %>%
+  filter(groups == "smooth3") %>%
   pull(value) %>% min()
 sa3_max <- sa3_long %>% 
-  filter(groups == "smooth5") %>%
+  filter(groups == "smooth3") %>%
[…]

### 2019-10-18 pilot_single.R

@@ -58,10 +58,16 @@ sa3_mean <- sa3_long %>%
 # allocated: the data set containing the allocated hexagon centroid for each sa3
 max_dist <- 1478314 # furthest area with Brisbane focal point
 
+city_list1 <- c("Brisbane", "Sydney", "Perth")
+  
 sa3_single <- allocated %>% 
   select(sa3_name_2016, longitude, latitude, points, focal_dist) %>% 
-  mutate(single = ifelse(points == "Brisbane", scales::rescale(
-    (max_dist - focal_dist)^10, to = c(sa3_mean, sa3_max)), NA))
+  mutate(city_distance = (max_dist - focal_dist)^8,
+         # only for desired cities
+         dist = ifelse(points %in% city_list1, 
+                       scales::rescale(city_distance, to = c(0,1)), NA),
+         single = ifelse(dist < 0.85, NA,
+                         scales::rescale(city_distance, to = c(sa3_mean, sa3_max))))
     
     
 ### Start with shapes - geographies

### 2019-10-18 protocol.Rmd
new title
flip direction of nwse

@@
 #	Title
-Assessing the effectiveness of visualisation methods for spatial distributions affected by small areas with high population densities.
+Assessing the effectiveness of hexagon tile maps for communicating spatial distributions of disease for Australia.
 
@@
 #	Data management and record keeping
-As the data will be held publicly online, it will be accessible under a license for people to reuse. It will also be held accessible to QUT researchers
+
+During the project, datasets produced from the project and that are approved for public access will be made available via QUT's Research Data Finder.
+These will be deidentified and require only the necessary answers for the research to be reproducible.
 
 ##	Confidentially and privacy
-All data will be deidentified, there is no need to protect confidentiality when the data has been anonymised.
+Datasets produced from the project and that will not be available for public access will contain demographic information about the participants.
+If there are participants with unique sets of demographics, their data will be combined with larger categories to minimise the risks of reidentification.
 
 ##	Data security
-All the survey information will be stored on github, a publicly available site, as well as on site at QUT.
+
+Responses to the survey will be stored securely using a private google drive accessible only to the researchers during the study through their password protected google drive accounts.
+This will contain potentially identifiable information if the respondents provide personal demographic information.
 
 ##	Record retention
-The records of data and analysis undertaken will be stored on github as well as on site at QUT.
+
+To ensure records are retained during and following the study the responses will be stored on the google drive immediately following the submission by participants.
+At the conclusion of the survey, the data will remain in the password protected google drive account.
+
+During the analysis phase the researchers Stephanie and Dianne will make copies of the survey responses to their work devices (laptop computers), that are password protected.
+
+This data set will also be deidentified and saved on the QUT network drives, which are automatically backed-up nightly in two physical locations. 
+The records of data analysis undertaken and the deidentified data will be stored on github as well as on QUT network drives.
 
 ##	Secondary use
-The analysis scripts and the data collected will be available for secondary use. Thisn their consent form. will be disclosed to participants
+
+The analysis scripts and the data collected will be available for secondary use by other researchers to reproduce these results and also be used in future studies.
+This will be communicated to participants in their consent form.
 

### 2019-10-18 pilot_nwse.R
flip direction of nwse

@@ -59,7 +59,7 @@ sa3_mean <- sa3_long %>%
 sa3_nwse <- sa3_centroids %>% 
   mutate(lat = abs(latitude-min(latitude)),
     long = abs(longitude-min(longitude)),
-    nwse = (2*lat)-long) %>% 
+    nwse = (-2*lat)+long) %>% 
   mutate(nwse = scales::rescale(nwse, to = c(sa3_min, sa3_max))) %>%
   select(-lat, -long)
 
@@ -96,8 +96,9 @@ aus_geo_sa3 <- aus_geo_nwse %>%
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the null data around the mean of the data
+  group_by(simulation) %>% 
   mutate(value = ifelse(simulation == pos,
-    scales::rescale((value+true), c(sa3_min, sa3_max)), 
+    scales::rescale((value+true), c(sa3_mean, sa3_max)), 
     scales::rescale((value), c(sa3_min, sa3_max))))
 
 aus_hex_sa3 <- aus_hex_nwse %>% 
@@ -105,8 +106,9 @@ aus_hex_sa3 <- aus_hex_nwse %>%
   mutate(simulation = as.numeric(gsub("sim", "", simulation))) %>% 
   # add the spatial trend model to the null data plot
   # scale the null data around the mean of the data
+  group_by(simulation) %>% 
   mutate(value = ifelse(simulation == pos,
-    scales::rescale((value+true), c(sa3_min, sa3_max)), 
+    scales::rescale((value+true), c(sa3_mean, sa3_max)), 
     scales::rescale((value), c(sa3_min, sa3_max))))
 
 ############################################################################### 
@@ -123,7 +125,7 @@ aus_geo_nwse <- aus_geo_sa3 %>%
     strip.background = element_rect(fill = "black", colour = NA),
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank())
-ggsave(filename = "figures/lineups/aus_geo_nwse.pdf", plot = aus_geo_nwse, device = "pdf", dpi = 300,
+ggsave(filename = "figures/nwse/aus_geo_nwse.pdf", plot = aus_geo_nwse, device = "pdf", dpi = 300,
   height = 9, width = 18)
 
 
@@ -137,5 +139,5 @@ aus_hex_nwse <- aus_hex_sa3 %>%
[…]

### 2019-10-18 protocol.Rmd
data management

@@
 ##	Confidentially and privacy
-Datasets produced from the project and that will not be available for public access will contain demographic information about the participants.
+
+Datasets produced from the project and that will *not* be available for public access will contain original demographic information about the participants and their Figure-Eight contributor ID.
+
+Datasets produced from the project and that *will be* available for public access on github will be deidentified and only contain the responses to survey.
 If there are participants with unique sets of demographics, their data will be combined with larger categories to minimise the risks of reidentification.

### 2019-10-18 protocol.Rmd
tweaked data privacy

--- 2019-10-18 protocol.Rmd
@@
 
-During the project, datasets produced from the project and that are approved for public access will be made available via QUT's Research Data Finder.
-These will be deidentified and require only the necessary answers for the research to be reproducible.
+Research expectations today require that publications use reproducible research protocols, requiring data to be available.
+De-identified, and privatised data will be made available will be made available via QUT's Research Data Finder, and, if required by the publisher, once the results are published also available on the journal article web site.
 
 ##	Confidentially and privacy
-Datasets produced from the project and that will not be available for public access will contain demographic information about the participants.
+
+Datasets produced from the project and that will *not* be available for public access will contain original demographic information about the participants and only the anonymous Figure-Eight contributor ID.
+
+Datasets produced from the project and that *will be* available for public access on github will be de-identified and only contain the responses to survey.
 If there are participants with unique sets of demographics, their data will be combined with larger categories to minimise the risks of reidentification.
@@
 Responses to the survey will be stored securely using a private google drive accessible only to the researchers during the study through their password protected google drive accounts.
-This will contain potentially identifiable information if the respondents provide personal demographic information.
+This will contain the demographic information, at the coarse resolution specified in the data collection.
 
@@
 
-This data set will also be deidentified and saved on the QUT network drives, which are automatically backed-up nightly in two physical locations. 
-The records of data analysis undertaken and the deidentified data will be stored on github as well as on QUT network drives.
+This data set will also be de-identified, by removing the demographic data, and saved on the QUT network drives, which are automatically backed-up nightly in two physical locations.
+The records of data analysis undertaken and the de-identified data will be stored on github as well as on QUT network drives.
 
@@
 
-The analysis scripts and the data collected will be available for secondary use by other researchers to reproduce these results and also be used in future studies.
-This will be communicated to participants in their consent form.
+The analysis scripts and the de-identified data will be available for secondary use by other researchers to reproduce these results and also use in future studies.
+Participants will be asked to provide consent for this usage in the consent form.
 

### 2019-10-18 pilot_cities.R
add training set

@@ -64,7 +64,7 @@ sa3_cities <- allocated %>%
   mutate(city_distance = (max_dist - focal_dist)^8,
          dist = scales::rescale(city_distance,
                                      to = c(0,1)),
-         cities = ifelse(dist < 0.85, NA, 
+         cities = ifelse(dist < 0.9, NA, 
                          scales::rescale(city_distance,
                         to = c(sa3_mean, sa3_max))))
 

### 2019-10-18 training.R

@@ -1,0 +1,146 @@
+
+###############################################################################
+######################         TRAINING PLOTS         #########################
+
+
+###############################################################################
+######################    NORTH WEST TO SOUTH EAST    #########################
+
+
+set.seed(2017)
+var.g.dummy <- gstat(formula = z ~ 1, 
+                     locations = ~ longitude + latitude, 
+                     dummy = T, beta = 1, model = vgm(psill = 1, model = "Gau", range = 0.3),
+                     nmax = 3)
+
+# Create underlying spatially dependent data for 12 null plots
+var.sim <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 3) %>% 
+  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
+
+
+sims <- colnames(var.sim)[5:length(colnames(var.sim))]
+
+# use an underlying spatial covariance model
+
+sa3_sims1 <- as_tibble(var.sim) %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
+                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+
+sa3_sims2 <- sa3_sims1 %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
+                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+
+sa3_sims3 <- sa3_sims2 %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
+                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+
+
+smoothing <- bind_rows(
+  "smooth1" = sa3_sims1,
+  "smooth2" = sa3_sims2, 
+  "smooth3" = sa3_sims3, .id = "groups")
+
+
+sa3_long <- smoothing %>%
+  select(-longitude, -latitude, -logsize) %>% 
+  gather(key = "simulation", value = "value", -sa3_name_2016, -groups) %>%
+  mutate(simulation = as.numeric(gsub("sim", "", simulation)))
+
+
+
+# only use the most smoothed
+sa3_min <- sa3_long %>% 
+  filter(groups == "smooth3") %>%
+  pull(value) %>% min()
+sa3_max <- sa3_long %>% 
+  filter(groups == "smooth3") %>%
+  pull(value) %>% max()
+
[…]

### 2019-10-18 protocol.Rmd
outcomes

@@
 
-When participants see the same data set displayed a line up as a hexagon tile map and geographic map, participants will pick the map that displays a pattern influenced by population density more often when the information is presented in a hexagon tile map.
+A hexagon tile map display allows people to detect the impact of a disease in highly populated small areas with higher accuracy and efficiency, in comparison to the accuracy and efficiency of detections made when viewing a choropleth map.
 
@@
 
-1.	Measure the accuracy in spotting a real population density related spatial distribution from a line-up of null maps
-2.	Contrast the accuracy and efficiency when participants pick from geographic or hexagon maps
+1. Show that spatial disease trends, that impact highly populated small areas, are detected with higher accuracy when viewed in a hexagon tile map display.
 
@@
 
-Experiment information collected:
+For each plot evaluation the subject will provide these responses:
 
-- Choice of plot in each line up
+- Their choice of plot from a lineup
 - Reason for choice of plot
-- Time taken to answer
-- Perceived difficulty of question
-
-Factors:
-
-- Plot type ( Hexagon / Geographic )
-- Spatial dependence structure ( Difference in a single city / Related to population density / North to South )
-
-We will record demographic information to consider the impacts of:
-
-- gender (female / male / other),
-- degree education level achieved (high school / bachelors / masters / doctorate / other),
-- age range (18-25 / 25-35 / 35-45 / 45-55 / 55+ / other)
-- lived in Australia (Yes / No / Other)
+- Time taken to respond
+- Perceived difficulty in making a choice
 
@@
 
-The possible levels of the factors are:
+The levels of the factors are:
 
@@
 ##	Data collection
-As the survey is conducted through the Figure-Eight platform, the human data will also be collected in the form of an IP address, Contributor ID, Trust Score and Channel.
-Some sources believe an IP address is identifiable information, as such it will not be held publicly online when the data is held on github.
-We will also ask for information regarding gender, education level achieved, and age range to understand perception of different groups.
+
+As the survey is conducted through the Figure-Eight platform, IP Address Contributor ID, Trust Score and Channel(add link to Figure 8 details page ) will be provided.
+In addition to the experimental design and response variables:
+
+- Plot type ( Hexagon / Geographic )
+- Trend model ( Two hotspots / Multiple hotspots / spatial trend )
+- Choice of plot in each line up
+- Reason for choice of plot
+- Time taken to answer
+- Perceived difficulty of question
+
+the survey of participants will provide this demographic information:
+
+- Gender (female / male / other),
+- Degree education level achieved (high school / bachelors / masters / doctorate / other),
+- Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
+- Lived in Australia (Yes / No / other)
 
@@
 
-An expansion of the various observations, data and measures that will be made during the study and which will contribute to establishing success or otherwise in addressing the research question.
+## Response variables
 
-The collection of multiple responses from each person as they complete several different lineup tasks, allows estimates of their perceptual ability and allows them to correct power differences between competing designs: by modeling power using a subject-specific random intercept in a generalized linear model.
+### Accuracy
+
+To measure the accuracy of the detections, the plot chosen for each lineup evaluated will be compared to the position of the real spatial trend plot in the lineup.
+
+A correct result occurs when the chosen plot matches the position of the real plot, this will be recorded in an additional binary variable called $collect$.
+
+The accuracy of the choices for each display will be calculated as a proportion: 
+$accuracy = number correct/number shown$.
+
+### Efficiency
+
+High efficiency occurs when a small amount of time is taken to evaluate each lineup.
+This will be measured as the inverse of the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.
+
+The efficiency of the choices for each display will be calculated by the time taken as a fraction of the maximum time taken by all respondents to respond:
+$efficiency = time taken/maximumtime taken$.
+
+## Model
+
+Response Variables:
+Accuracy and Efficiency
+
+Design:
+We will model the difference between the accuracy and efficiency when evaluating hexagon tile maps and geographic maps.
+
+Random Effects:
+The collection of multiple responses from each person as they complete several different lineup tasks, allows estimates of their perceptual ability using a subject-specific random intercept in a generalized linear model.
+
+Cofactors:
+responses to the questions regarding the difficulty of making a choice and the reason for the choice of plot in the line up.
+
+Interactions:
 

### 2019-10-18 protocol.Rmd
Model specification

@@
 
+Main Effects:
+Spatial trend
+
 Random Effects:
@@
 Interactions:
+Design and Difficulty: The interaction between the perceived difficulty of evaluating hexagon tile maps and geographic maps will be included to measure whether particiants feel differently about the designs.
+
+Spatial Trend and Difficulty: The interaction between the spatial trend used in the lineup of hexagon tile maps and geographic maps will be included to measure whether particiants feel differently about finding different spatial trends.
 

### 2019-10-18 protocol.Rmd
changes

--- 2019-10-18 protocol.Rmd
@@
 
-A correct result occurs when the chosen plot matches the position of the real plot, this will be recorded in an additional binary variable called $collect$.
-
-The accuracy of the choices for each display will be calculated as a proportion: 
-$accuracy = number correct/number shown$.
+A correct result occurs when the chosen plot matches the position of the real plot, this will be recorded in an additional binary variable; $1 = correct;~ 0 = incorrect$.
 
@@
 High efficiency occurs when a small amount of time is taken to evaluate each lineup.
-This will be measured as the inverse of the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.
-
-The efficiency of the choices for each display will be calculated by the time taken as a fraction of the maximum time taken by all respondents to respond:
-$efficiency = time taken/maximumtime taken$.
+This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.
 
 ## Model
+
+A multilevel linear model with be fitted to the data with elements as specified below.
 
@@
 
-Design:
-We will model the difference between the accuracy and efficiency when evaluating hexagon tile maps and geographic maps.
+Main Effects:
+Design, Trend
 
@@
 
-Cofactors:
-responses to the questions regarding the difficulty of making a choice and the reason for the choice of plot in the line up.
+Possible Interactions:
+Design and Trend, Design and Difficulty, Design and Reason
 
-Interactions:
+Possible covariates:
+Responses to the questions regarding the difficulty of making a choice and the reason for the choice of plot in the line up.
 

### 2019-10-18 protocol.Rmd
aims

@@
 
-1. Show that spatial disease trends, that impact highly populated small areas, are detected with higher accuracy when viewed in a hexagon tile map display.
+1. Are spatial disease trends, that impact highly populated small areas,  detected with higher accuracy when viewed in a hexagon tile map display?
+2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when using a hexagon tile map display?
+3. Do people find hexagon tile maps more difficult to read than choropleth maps?
+4. Are the reasons for choosing a plot different depending on the type of display?
+5. Does an Australian resident find the choropleth map easier to read than the hexagon tile map?
 
@@
 We will aim to survey 100 participants.
-Participants will be approached via their dashboard through their Figure-Eight accounts.
+It will be advertised to potential participants via their dashboard through their Figure-Eight accounts.
 

### 2019-10-20 R/survey_app.R
Survey app and multiple distributions per plots

@@ -1,0 +1,88 @@
+###############################################################################
+##############################    SURVEY APP     ##############################
+###############################################################################
+
+# demographics and scene questions
+
+taipanQuestions <- function(demographics, scene){
+  structure(
+    list(demographics = demographics, scene = scene),
+    class = "taipanQuestions"
+  )
+}
+questions <- taipanQuestions(
+  demographics =
+    div(
+      # Contributor ID
+      textInput("contributor", label = "For payment, provide Figure Eight Contributor ID:", 
+                placeholder = "Contributor ID"),
+      # Question 1, gender
+      selectInput("gender",
+                  h3("Select your gender:"),
+                  choices = list("Choose one" = 1, 
+                                 "Female" = 2, 
+                                 "Male" = 3), 
+                  selected = 1),
+      # Question 2, education
+      selectInput("education",
+                  h3("Select the highest level of education achieved:"),
+                  choices = list("Choose one" = 1, 
+                                 "High School Diploma" = 2,
+                                 "Bachelors Degree" = 3,
+                                 "Master Degree" = 4,
+                                 "Doctorate" = 4
+                  ), 
+                  selected = 1),
+      # Question 3, age range
+      selectInput("age",
+                  h3("Select your age range:"),
+                  choices = list("Choose one" = 1, 
+                                 "18 - 24" = 2,
+                                 "25 - 34" = 3,
+                                 "35 - 44" = 4,
+                                 "45 - 54" = 5,
+                                 "55+" = 6
+                  ), 
+                  selected = 1),
+      # Question 4, Australia
+      selectInput("australia",
+                  h3("Have you lived in Australia?"),
+                  choices = list("Choose one" = 1, 
+                                 "Yes" = 2,
+                                 "No" = 3), 
+                  selected = 1)
+    ),
+  scene =
+    div(
+      # Question 1, the choice of plot
+      selectInput("select",
+                  h3("Which map is most different from the others?"),
+                  choices = list("Choose a map" = 0,
+                                 "1" = 1, 
+                                 "2" = 2,
+                                 "3" = 3, 
+                                 "4" = 4, 
+                                 "5" = 5,
+                                 "6" = 6, 
+                                 "7" = 7, 
+                                 "8" = 8,
+                                 "9" = 9, 
+                                 "10" = 10, 
+                                 "11" = 11,
[…]

### 2019-10-20 pilot_cities.R

@@ -2,56 +2,52 @@
 ###############################################################################
 ######################          CITY DIFFERENCE       #########################
 
-# Which map shows the most areas coloured red?
+# Create and smooth 8 null data simulations: all cities different to rural areas
+
 
 set.seed(2015)
 var.g.dummy <- gstat(formula = z ~ 1, 
                      locations = ~ longitude + latitude, 
-                     dummy = T, beta = 1, model = vgm(psill = 1, model = "Gau", range = 0.3),
+                     dummy = T, beta = 1, model = vgm(psill = 1, model = "Gau", range = 0.5),
                      nmax = 12)
 
-# Create underlying spatially dependent data for 12 null plots
-var.sim <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
-  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
+# Create underlying spatially dependent data for 12 null plots for 8 simulations
+var.sim_cities <- map(1:8, function(seed){
+  set.seed(seed)
+  predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+  left_join(sa3_centroids, ., by=c("longitude", "latitude"))})
 
 # use an underlying spatial covariance model
 
-sa3_sims1 <- as_tibble(var.sim) %>% 
+sa3_cities_sims1 <- map(var.sim_cities, function(data){
+  data %>% as_tibble %>% 
   mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
-                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+                           values_vector = ., area_weight = 0.4, neighbours_list = sa3_neighbours))})
 
-sa3_sims2 <- sa3_sims1 %>% 
-  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
-                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+sa3_cities_sims2 <- map(sa3_cities_sims1, function(data){
+  data %>% as_tibble %>% 
+    mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
+                             values_vector = ., area_weight = 0.4, neighbours_list = sa3_neighbours))})
 
-sa3_sims3 <- sa3_sims2 %>% 
-  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
[…]

### 2019-10-20 pilot_nwse.R

@@ -7,7 +7,7 @@ set.seed(2017)
 var.g.dummy <- gstat(formula = z ~ 1, 
                      locations = ~ longitude + latitude, 
                      dummy = T, beta = 1, model = vgm(psill = 1, model = "Gau", range = 0.3),
-                     nmax = 12)
+                     nmax = 6)
 
 # Create underlying spatially dependent data for 12 null plots
 var.sim <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
@@ -38,6 +38,17 @@ sa3_long <- smoothing %>%
   select(-longitude, -latitude, -logsize) %>% 
   gather(key = "simulation", value = "value", -sa3_name_2016, -groups) %>%
   mutate(simulation = as.numeric(gsub("sim", "", simulation)))
+
+sims <- paste0("sim", 1:24)
+
+#####################################################################
+#### Split into two groups
+
+sa3_long_nwse1 <- sa3_long_nwse %>% 
+  filter(simulation < 13)
+
+sa3_long_nwse2 <- sa3_long_nwse %>% 
+  filter(simulation > 12) %>% mutate(simulation = simulation-12)
 
 
 

### 2019-10-20 pilot_single.R

@@ -8,7 +8,7 @@ set.seed(2016)
 var.g.dummy <- gstat(formula = z ~ 1, 
                      locations = ~ longitude + latitude, 
                      dummy = T, beta = 1, model = vgm(psill = 1, model = "Gau", range = 0.3),
-                     nmax = 12)
+                     nmax = 6)
 
 # Create underlying spatially dependent data for 12 null plots
 var.sim <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
@@ -39,6 +39,18 @@ sa3_long <- smoothing %>%
   select(-longitude, -latitude, -logsize) %>% 
   gather(key = "simulation", value = "value", -sa3_name_2016, -groups) %>%
   mutate(simulation = as.numeric(gsub("sim", "", simulation)))
+
+sims <- paste0("sim", 1:24)
+
+#####################################################################
+#### Split into two groups
+
+sa3_long_single1 <- sa3_long_single %>% 
+  filter(simulation < 13)
+
+sa3_long_single2 <- sa3_long_single %>% 
+  filter(simulation > 12) %>% mutate(simulation = simulation-12)
+
 
 # only use the most smoothed
 sa3_min <- sa3_long %>% 

### 2019-10-20 taipan1/server.R

@@ -1,0 +1,186 @@
+library(shiny)
+library(ggplot2)
+library(purrr)
+
+getInputID <- function(input){
+  if(!inherits(input, "shiny.tag")){
+    return()
+  }
+  c(
+    if(!is.null(input$attribs$id)){list(list(id=input$attribs$id, type = input$name))}else{NULL},
+    do.call("c", map(input$children, getInputID))
+  )
+}
+
+shinyServer(
+  function(input, output, session) {
+    questions <- readRDS("data/questions.Rds")
+    image_list <- list.files("www/app_images", full.names = TRUE)
+    
+    v <- reactiveValues(
+      imageNum = 1,
+      responses = list()
+    )
+    
+    current_img <- reactive({
+      image_list[v$imageNum]
+    })
+    
+    
+    output$out_img <- renderImage({
+      list(src = current_img(), id = "taipan_current_img")
+    }, deleteFile = FALSE)
+    
+    sceneInputs <- getInputID(questions$scene)
+    demographicsInputs <- getInputID(questions$demographics)
+    
+    scene_vals <- reactive({
+      vals <- map(sceneInputs, function(id){input[[id$id]]})
+      names(vals) <- map_chr(sceneInputs, "id")
+      vals
+    })
+    
+    demographic_vals <- reactive({
+      vals <- map(demographicsInputs, function(id){input[[id$id]]})
+      names(vals) <- map_chr(demographicsInputs, "id")
+      vals
+    })
+    
+    output$ui_save <- renderUI({
+      actionLink(
+        "btn_saveImage",
+        box(
+          "Save Image",
+          width = 4,
+          background = "blue"
+          
+        )
+      )
+    })
+    
+    output$ui_d_save <- renderUI({
+      actionLink(
+        "btn_saveInfo",
+        box(
+          "Save Info",
+          width = 12,
+          background = "blue"
+          
+        )
+      )
+    })
+    
+    output$ui_btn_next <- renderUI({
+      if (v$imageNum != length(image_list)) {
+        actionLink(
+          "btn_next",
+          box(
+            "Next Image",
+            width = 4,
+            background = "green"
+          )
+        )
+      }
+      else {
+        column(3)
+      }
+    })
+    
+    output$ui_btn_prev <- renderUI({
+      if (v$imageNum != 1) {
+        actionLink(
+          "btn_prev",
+          box(
+            "Previous Image",
+            width = 4,
+            background = "green"
+          )
+        )
+      }
+      else {
+        column(3)
+      }
+    })
+    
[…]

### 2019-10-20 taipan1/ui.R

@@ -1,0 +1,66 @@
+library(shiny)
+library(shinydashboard)
+
+shinyUI(
+  dashboardPage(
+    dashboardHeader(
+      title = "taipan",
+      tags$li(class = "dropdown", downloadLink("btn_export", span(icon("save"), "Submit Survey"))),
+      tags$li(class = "dropdown", a(href="https://github.com/srkobakian/experiment", target="_blank", span(icon("github"), "More Info")))
+    ),  
+    dashboardSidebar(
+      sidebarMenu(
+        menuItem("About you", tabName = "About_you", icon = icon("dashboard")),
+        menuItem("Questions", tabName = "Questions", icon = icon("th"))
+      )
+    ),
+    dashboardBody(
+      tabItems(
+        tabItem(tabName = "About_you",
+                  box(
+                  title = "Demographics",
+                  questions$demographics,
+                  div(uiOutput("ui_d_save")),
+                  width = 12,
+                  status = "info",
+                  solidHeader = TRUE,
+                  collapsible = TRUE
+                )
+        ),
+        
+        tabItem(tabName = "Questions",
+                includeScript("www/img_size.js"),
+                includeCSS("www/taipan.css"),
+                column(6,
+                       box(
+                         title = textOutput("out_img_info"),
+                         div(class = "taipan_image_div",
+                             imageOutput("out_img",
+                                         inline = TRUE)
+                         ),
+                         width = 12,
+                         status = "primary",
+                         collapsible = FALSE
+                       )),
+                
+                column(6,
+                       box(
+                         title = "Questions",
+                         questions$scene,
+                         div(
+                           uiOutput("ui_btn_prev"),
+                           uiOutput("ui_save"),
+                           uiOutput("ui_btn_next")),
+                         width = 12,
+                         status = "info",
+                         solidHeader = TRUE,
+                         collapsible = TRUE
+                       ),
+                       
+                )
+        )
+        
+      )
+      )
+  )
+)

### 2019-10-20 training.R
lineup questions

@@ -144,3 +144,67 @@ aus_hex_red <- aus_hex_sa3_red %>%
         panel.grid.minor = element_blank())
 ggsave(filename = "figures/red/aus_hex_red.pdf", plot = aus_hex_red, device = "pdf", dpi = 300,
        height = 9, width = 18)
+
+lineup_questions <- taipanQuestions(
+  demographics =
+    div(
+      # Contributor ID
+      textInput("contributor", label = "For payment, provide Figure Eight Contributor ID:", 
+                placeholder = "id"),
+      # Question 1, gender
+      selectInput("gender",
+                  h3("Select your gender:"),
+                  choices = list("Choose one" = 1, 
+                                 "Female" = 2, 
+                                 "Male" = 3), 
+                  selected = 1),
+      # Question 2, education
+      selectInput("education",
+                  h3("Select the highest level of education achieved:"),
+                  choices = list("Choose one" = 1, 
+                                 "High School Diploma" = 2,
+                                 "Bachelors Degree" = 3,
+                                 "Master Degree" = 4,
+                                 "Doctorate" = 4
+                  ), 
+                  selected = 1),
+      # Question 3, age range
+      selectInput("education",
+                  h3("Select your age range:"),
+                  choices = list("Choose one" = 1, 
+                                 "18 - 24" = 2,
+                                 "25 - 34" = 3,
+                                 "35 - 44" = 4,
+                                 "45 - 54" = 5,
+                                 "55+" = 6
+                  ), 
+                  selected = 1),
+      # Question 4, Australia
+      selectInput("australia",
+                  h3("Have you lived in Australia?"),
+                  choices = list("Choose one" = 1, 
+                                 "Yes" = 2,
+                                 "No" = 3), 
+                  selected = 1)
+    ),
+  scene =
+    div(
+      # Question 1, the choice of plot
+      selectInput("select",
+                  h3("Which map is most different from the others?"),
+                  choices = list("Choice 1" = 1, "Choice 2" = 2,
+                                 "Choice 3" = 3), selected = 1),
+      # Question 2, reason for their choice
+      checkboxGroupInput("reason",
+                         h3("What makes your chosen map different?:"),
+                         choices = list(
+                           "more red areas" = 1,
+                           "more blue areas" = 2,
+                           "greater range of colours" = 3,
+                           "other" = 4)),
+      # Question 3, certainty around their choice
[…]

### 2019-10-21 pilot_cities.R
All cities trend plots - may need more smoothing

@@ -74,18 +74,20 @@ geo_list <- sample(1:8, 4)
 hex_list <- seq(1:8)[-geo_list]
 
 ### Start with shapes - geographies
-aus_geo_cities <- map(sa3_cities[geo_list], ~sa3 %>%
-                        select(sa3_name_2016) %>% 
-                        # Add the 16 simulated values for each area
-                        left_join(., sa3_long, by = c("sa3_name_2016")) %>% 
-                        left_join(., .x, by = c("sa3_name_2016")))
+aus_geo_cities <- map(1:4, function(num) {
+  sa3 %>%
+    select(sa3_name_2016) %>% 
+    # Add the 16 simulated values for each area
+    left_join(sa3_long_cities[geo_list][[num]], ., by = c("sa3_name_2016")) %>% 
+    left_join(., sa3_cities[geo_list][[num]], by = c("sa3_name_2016"))})
 
 ### Start with shapes - hexagons
-aus_hex_cities <- map(sa3_cities[hex_list], ~hexagons_sf %>%
-                        select(sa3_name_2016) %>% 
-                        # Add the 16 simulated values for each area
-                        left_join(., sa3_long, by = c("sa3_name_2016")) %>% 
-                        left_join(., .x, by = c("sa3_name_2016")))
+aus_hex_cities <- map(1:4, function(num) {
+  hexagons_sf %>%
+    select(sa3_name_2016) %>% 
+    # Add the 16 simulated values for each area
+    left_join(sa3_long_cities[hex_list][[num]], ., by = c("sa3_name_2016")) %>% 
+    left_join(., sa3_cities[hex_list][[num]], by = c("sa3_name_2016"))})
 
 
 ############################################################################### 
@@ -123,7 +125,7 @@ ggplot(map_dfr(aus_hex_sa3_cities, as_tibble)) + geom_histogram(aes(x=value)) + 
 ############################################################################### 
 
 geo_plot <- function(data, pos, plotnum){
-  plota <- ggplot(data) + 
+  plota <- st_as_sf(data) %>% ungroup() %>% ggplot() + 
     geom_sf(aes(fill = value), colour = NA) + 
     scale_fill_distiller(type = "div", palette = "RdYlBu") + 
     facet_wrap(~ simulation) + theme_minimal() + guides(fill = FALSE) +
[…]

### 2019-10-21 protocol.Rmd
tweaking study design

@@
 A line up protocol will be used to arrange 20 maps into one display.
-Each display will be created by a combination of plot type, error distribution and spatial dependence.
+Each display will be created by a combination of plot type, spatial error distribution and spatial trend model.
 We will contrast the sets of different plot designs, hexagon tilemap and geography in the lineups created using the same data, and same null positions within the lineup. 
@@
  - Plot type: Geography, Hexagons
- - Spatial Dependence: Difference in a single city, Related to population density, North to South
+ - Trend: Locations in two population centres, Locations in multiple population centres, South-East to North-West
 
-Allowing each factor combination to be considered will provide 12 (2x2x3) line up displays to be seen by all participants.
+Factor combinations to be examined by each participant amount to 6 (2x3) lineup displays.
+A participant cannot see the same data for both plot types.
+Four simulated sets of data will be generated for each treatment.
+This will generate 24 lineups (12 will be geographic maps, and 12 will be hexagon tile maps).
+Participants will evaluate 12 lineups, 6 of each plot type.
 
@@
 ##	Participants
-We will aim to survey 100 participants.
-It will be advertised to potential participants via their dashboard through their Figure-Eight accounts.
+We plan to collect responses from 100 participants. It will be advertised to potential participants via their dashboard through their Figure-Eight accounts.
 
@@
  - at least 18 years old
- - trained and qualified to annotating images.
+ - trained and qualified to annotate images.
 

### 2019-10-21 protocol.Rmd
tweaking study population

@@
 ##	Participants
-We plan to collect responses from 100 participants. It will be advertised to potential participants via their dashboard through their Figure-Eight accounts.
+We plan to collect responses from 100 participants.
 
@@
 The platform will advertise this survey to participants that fulfill the following:
+
  - level 2 or level 3 on the Figure-Eight Platform. 
@@
 The Figure-Eight platform will advertise this as a “job” to potential participants, they will not be under any obligation to complete this task.
-We will have the opportunity to wait until enough participants have completed the survey and provided their judgements.
+We will have the opportunity to wait until enough participants have completed the survey and provided their responses.
 

### 2019-10-21 protocol.Rmd
procedures

@@
 Recruitment will take place via advertising on the Figure-Eight dashboards.
-The Figure-Eight platform will advertise this as a “job” to potential participants, they will not be under any obligation to complete this task.
-We will have the opportunity to wait until enough participants have completed the survey and provided their responses.
+The Figure-Eight platform will advertise this as a "job" to potential participants, they will not be under any obligation to complete this task.
+We keep advertising until enough participants have completed the survey, then remove the advertisements and close the survey.
 
@@
 ##	Participant withdrawal
-Participants will be able to withdraw by leaving the survey at any time.
+Participants can withdraw from the experiment at any time by quitting the survey.
 
@@
 ##	Screening of participants
+
 Participants will need to have achieved contributor level two on the Figure-Eight platofrm, this is a smaller group of more experienced, higher accuracy contributors.
+
 Test questions are the most important quality control mechanism in the Figure-Eight Platform.
@@
 
-Contributors that fail quiz mode are not paid and are permanently disqualified from working on your job.
-Participants will need to reach an accuracy threshold we will set to be allowed to answer the questions in our survey.
-Test questions will also be included as the job progresses so we can be sure quality remains high.
+The Figure Eight procedures are followed: *Contributors that fail quiz mode are not paid and are permanently disqualified from working on your job.
+Participants will need to achieve a pre-determined accuracy threshold to be allowed to answer the questions in our survey.*
 

### 2019-10-21 protocol.Rmd
procedures modified

@@
 
-As the survey is conducted through the Figure-Eight platform, IP Address Contributor ID, Trust Score and Channel(add link to Figure 8 details page ) will be provided.
-In addition to the experimental design and response variables:
+As the survey is conducted through the Figure-Eight platform, which will record IP Address of computer used to access the survey, Contributor ID, Trust Score and Channel.
+In addition, we will record the responses of participants:
 
-- Plot type ( Hexagon / Geographic )
-- Trend model ( Two hotspots / Multiple hotspots / spatial trend )
 - Choice of plot in each line up
@@
 
-the survey of participants will provide this demographic information:
+and participants will be asked provide this demographic information:
 
@@
 - Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
-- Lived in Australia (Yes / No / other)
+- Lived at least for one year in Australia (Yes / No )
 
-##	Data collection/gathering techniques: 
+The experimental design variables, Plot Type, Trend Model and simulation number will also be saved for each display shown to participants.
+
+##	Data collection/gathering techniques
+
 Data will be collected through survey distribution via a web application.
-Participants will access the application via link from a Figure-Eight "job".
+Participants will access the application via a link from the Figure-Eight "job".
 
 ##	Impact of, and response to, missing data
-If participants want to provide and "I don't know" answer they will be able to select this.
-If there are more than 50% of questions that are incomplete we will remove this survey and consider this withdrawal.
+
+Participants have the option to not respond to any question.
+
+If there are 50% or more of unanswered survey questions (excluding demographic information) we will remove this participant's responses before data analysis.
 

### 2019-10-21 R/survey_app.R
refine qs

@@ -15,13 +15,15 @@ questions <- taipanQuestions(
     div(
       # Contributor ID
       textInput("contributor", label = "For payment, provide Figure Eight Contributor ID:", 
-                placeholder = "Contributor ID"),
+                placeholder = "id"),
       # Question 1, gender
       selectInput("gender",
-                  h3("Select your gender:"),
+                  h3("Select your preferred pronoun:"),
                   choices = list("Choose one" = 1, 
-                                 "Female" = 2, 
-                                 "Male" = 3), 
+                                 "She" = 2, 
+                                 "He" = 3,
+                                 "They" = 4,
+                                 "other = 5"), 
                   selected = 1),
       # Question 2, education
       selectInput("education",
@@ -30,18 +32,20 @@ questions <- taipanQuestions(
                                  "High School Diploma" = 2,
                                  "Bachelors Degree" = 3,
                                  "Master Degree" = 4,
-                                 "Doctorate" = 4
+                                 "Doctorate" = 5,
+                                 "Other" = 6
                   ), 
                   selected = 1),
       # Question 3, age range
-      selectInput("age",
+      selectInput("education",
                   h3("Select your age range:"),
                   choices = list("Choose one" = 1, 
                                  "18 - 24" = 2,
                                  "25 - 34" = 3,
                                  "35 - 44" = 4,
                                  "45 - 54" = 5,
-                                 "55+" = 6
+                                 "55+" = 6,
+                                 "Other" = 7
                   ), 
                   selected = 1),
       # Question 4, Australia
@@ -49,7 +53,8 @@ questions <- taipanQuestions(
                   h3("Have you lived in Australia?"),
                   choices = list("Choose one" = 1, 
                                  "Yes" = 2,
-                                 "No" = 3), 
+                                 "No" = 3, 
+                                 "Other" = 4), 
                   selected = 1)
     ),
   scene =
@@ -57,32 +62,33 @@ questions <- taipanQuestions(
       # Question 1, the choice of plot
       selectInput("select",
                   h3("Which map is most different from the others?"),
-                  choices = list("Choose a map" = 0,
-                                 "1" = 1, 
+                  choices = list("Choose a plot number:" = 0,
+                                 "1" = 1,
                                  "2" = 2,
-                                 "3" = 3, 
-                                 "4" = 4, 
+                                 "3" = 3,
+                                 "4" = 4,
                                  "5" = 5,
-                                 "6" = 6, 
[…]

### 2019-10-21 taipan1/ui.R

@@ -31,7 +31,7 @@ shinyUI(
         tabItem(tabName = "Questions",
                 includeScript("www/img_size.js"),
                 includeCSS("www/taipan.css"),
-                column(6,
+                column(8,
                        box(
                          title = textOutput("out_img_info"),
                          div(class = "taipan_image_div",
@@ -43,13 +43,12 @@ shinyUI(
                          collapsible = FALSE
                        )),
                 
-                column(6,
+                column(4,
                        box(
                          title = "Questions",
                          questions$scene,
                          div(
                            uiOutput("ui_btn_prev"),
-                           uiOutput("ui_save"),
                            uiOutput("ui_btn_next")),
                          width = 12,
                          status = "info",

### 2019-10-21 protocol.Rmd

@@
 
-##	Sample size determination and power; or how will determine that data saturation has occurred or data are sufficient for the purpose.
+##	Sample size determination and power
+<!--; or how will determine that data saturation has occurred or data are sufficient for the purpose.-->
 
-To be able to effectively evaluate the use of a hexagon tilemap we will contrast the proportion of times the real data plot was chosen in a line up of maps.
-The same data will be used to create 19 null data plots and one real data plot. This data will be displayed to users in both geographic maps and hexagon tile maps.
+To be able to effectively evaluate the use of a hexagon tilemap we will contrast the proportion of times the plot of the data was chosen from the field of null plots.
 
-We will have aim to collect results from 100 participants (n=100), who will have tried to pick the real data in a line up of simulated data.
+The same data will be used to create 11 null data plots and one data plot. This data will be displayed to users in both geographic maps and hexagon tile maps.
 
+We will have aim to collect results from 100 participants ($n=100$), who been asked to choose the plot that is most different from the others. Each participant will evaluate 12 lineups.
+
+By chance, the data plot will be detected with probability, $1/12=0.083$.
+This corresponds to about 2 detections out of 20, generally this would be $n/12$ detections.
+Let's suppose the alternative hypothesis has probability of detection $p_A (>1/12)$.
+If we expect the data to be detected twice as often as by chance, $p_A=1/6$.
+To determine the probability of observing $n/12$ detections, given $p_A$, we can use a binomial distribution, where $k=ceiling(n/12)$, to calculate the power:
+
+$$P(X>k|p=p_A,n) = {n \choose k} p_A^k (1-p_A)^{n-k}$$
+
+If $p_A=1/6$ we would need almost 100 evaluations for each lineup to expect at least $n/12$ detections.
+With $p_A=0.25$ approximately 50 evaluations should yield sufficient detections.
+We will use a pilot study to estimate $p_A$.
+
+<!--
 Let X be the corresponding random variable X, where i.e. X = # times out of n independent repetitions that the data plot is picked from the lineup.
@@
 The authors also define how to estimate the power of a lineup: the ratio of correct identifications of the real data, x, out of n viewings.
+-->
+
+```{r echo=FALSE, eval=FALSE}
+# Code to compute the power for given sample size and alternative p
+library(tidyverse)
+library(nullabor)
+library(viridis)
+n <- 20:100
+k <- ceiling(n/12)
+pA <- seq(1/12, 1/2, 0.01)
+g <- expand.grid(n, k, pA)
+pow <- tibble(n=g[,1], k=g[,2], pA=g[,3]) 
+pow <- pow %>% 
+  mutate(prob = pbinom(k, n, pA, lower.tail=FALSE)) 
+ggplot(pow, aes(x=n, y=pA, colour=prob, group=pA)) + 
+  geom_point() +
+  scale_colour_viridis_c()
+```
 

### 2019-10-21 pilot_three.R
Three cities trend on four null data sets, hex and geographies

@@ -1,0 +1,333 @@
+###############################################################################
+######################          CITY DIFFERENCE       #########################
+
+# Which map shows the most areas coloured red?
+
+set.seed(2016)
+var.g.dummy <- gstat(formula = z ~ 1, 
+                     locations = ~ longitude + latitude, 
+                     dummy = T, beta = 1, model = vgm(psill = 1, model = "Gau", range = 0.3),
+                     nmax = 12)
+
+# Create underlying spatially dependent data for 12 null plots
+# use an underlying spatial covariance model
+var.sim1 <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
+var.sim2 <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
+var.sim3 <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
+var.sim4 <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
+
+###############################################################################
+######################          SMOOTH        #########################
+
+sa3_sims1_1 <- as_tibble(var.sim1) %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
+                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+sa3_sims1_2 <- sa3_sims1_1 %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
+                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+sa3_sims1_3 <- sa3_sims1_2 %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
+                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+sa3_sims1_4 <- sa3_sims1_3 %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
[…]

### 2019-10-21 pilot_cities.R
final figures, all 24

@@ -184,7 +184,7 @@ sa3_cities <- allocated %>%
                                 to = c(0,1)),
          cities = ifelse(dist < 0.85, NA, 
                          scales::rescale(city_distance,
-                                         to = c(-1, 3))))
+                                         to = c(1, 3))))
 
 
 ### Start with shapes - geographies

### 2019-10-21 pilot_nwse.R

@@ -1,98 +1,239 @@
-
 ###############################################################################
-######################    NORTH WEST TO SOUTH EAST    #########################
+######################  NORTH WEST - SOUTH EAST TREND   #######################
 
+# Which map shows the most areas coloured red?
 
-set.seed(2017)
+set.seed(2016)
 var.g.dummy <- gstat(formula = z ~ 1, 
                      locations = ~ longitude + latitude, 
                      dummy = T, beta = 1, model = vgm(psill = 1, model = "Gau", range = 0.3),
-                     nmax = 6)
+                     nmax = 12)
 
 # Create underlying spatially dependent data for 12 null plots
-var.sim <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+# use an underlying spatial covariance model
+var.sim1 <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
+var.sim2 <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
+var.sim3 <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
+var.sim4 <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
   left_join(sa3_centroids, ., by=c("longitude", "latitude"))
 
-# use an underlying spatial covariance model
+###############################################################################
+######################          SMOOTH        #########################
 
-sa3_sims1 <- as_tibble(var.sim) %>% 
+sa3_sims1_1 <- as_tibble(var.sim1) %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
+                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+sa3_sims1_2 <- sa3_sims1_1 %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
[…]

### 2019-10-21 pilot_single.R

@@ -1,170 +1,0 @@
-
-###############################################################################
-######################     SINGLE CITY DIFFERENCE     #########################
-
-# Which map contains more red ares in only one state?
-
-set.seed(2016)
-var.g.dummy <- gstat(formula = z ~ 1, 
-                     locations = ~ longitude + latitude, 
-                     dummy = T, beta = 1, model = vgm(psill = 1, model = "Gau", range = 0.3),
-                     nmax = 6)
-
-# Create underlying spatially dependent data for 12 null plots
-var.sim <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
-  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
-
-# use an underlying spatial covariance model
-
-sa3_sims1 <- as_tibble(var.sim) %>% 
-  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
-                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
-
-sa3_sims2 <- sa3_sims1 %>% 
-  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
-                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
-
-sa3_sims3 <- sa3_sims2 %>% 
-  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
-                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
-
-
-smoothing <- bind_rows(
-  "smooth1" = sa3_sims1,
-  "smooth2" = sa3_sims2, 
-  "smooth3" = sa3_sims3, .id = "groups")
-
-
-sa3_long <- smoothing %>%
-  select(-longitude, -latitude, -logsize) %>% 
-  gather(key = "simulation", value = "value", -sa3_name_2016, -groups) %>%
-  mutate(simulation = as.numeric(gsub("sim", "", simulation)))
-
-sims <- paste0("sim", 1:24)
-
-#####################################################################
-#### Split into two groups
-
-sa3_long_single1 <- sa3_long_single %>% 
-  filter(simulation < 13)
-
-sa3_long_single2 <- sa3_long_single %>% 
-  filter(simulation > 12) %>% mutate(simulation = simulation-12)
-
-
-# only use the most smoothed
[…]

### 2019-10-21 pilot_three.R

@@ -315,8 +315,7 @@ hex_plot_three <- function(data, position, min, max) {
   return(aus_hex_three_plot)
 }
 
-
-three_positions <- c(12,3,9,4)
+three_positions <- c(8, 9, 5, 12)
 min_list <- list(sa3_min1,sa3_min2,sa3_min3,sa3_min4)
 max_list <- list(sa3_max1,sa3_max2,sa3_max3,sa3_max4)
 geo_list <- list(aus_geo_three1, aus_geo_three2, aus_geo_three3, aus_geo_three4)

### 2019-10-21 protocol.Rmd

@@
 
-##	Data analysis and Statistical methods
+##	Data analysis and statistical methods
 
-This will be analysed using a generalised linear model, with random effects capturing the differences between the 100 participants.
-The main effects used will consider the spatial distribution of the errors, gender, degree education level achieved, age range and whether the participant has lived in Australia.
+The results will be analysed using a generalised linear model, with a subject random effect. There will be two main effects: plot type and trend model.
 
-Each lineup will have similar hypotheses:
+Each lineup has the same hypotheses:
 $H_0:$ there is no real structure visible in the data plot

### 2019-10-21 pilot_cities.R
png group A and B

@@ -268,9 +268,9 @@ geo_plot_cities <- function(data, position, min, max) {
           panel.grid.minor = element_blank())
   
   
-  ggsave(filename = paste0("figures/final/aus_geo_cities_", position, ".pdf"), 
+  ggsave(filename = paste0("figures/final/aus_geo_cities_", position, ".png"), 
          plot = aus_geo_cities_plot,
-         device = "pdf", dpi = 300,
+         device = "png", dpi = 300,
          height = 14, width = 18)
   return(aus_geo_cities_plot)
 }
@@ -301,9 +301,9 @@ hex_plot_cities <- function(data, position, min, max) {
           panel.grid.major = element_blank(),
           panel.grid.minor = element_blank()) 
   
-  ggsave(filename = paste0("figures/final/aus_hex_cities_", position, ".pdf"), 
+  ggsave(filename = paste0("figures/final/aus_hex_cities_", position, ".png"), 
          plot = aus_hex_cities_plot,
-         device = "pdf", dpi = 300,
+         device = "png", dpi = 300,
          height = 14, width = 18)
   return(aus_hex_cities_plot)
 }

### 2019-10-21 pilot_nwse.R

@@ -267,9 +267,9 @@ geo_plot_nwse <- function(data, position, min, max) {
           panel.grid.minor = element_blank())
   
   
-  ggsave(filename = paste0("figures/final/aus_geo_nwse_", position, ".pdf"), 
+  ggsave(filename = paste0("figures/final/aus_geo_nwse_", position, ".png"), 
          plot = aus_geo_nwse_plot,
-         device = "pdf", dpi = 300,
+         device = "png", dpi = 300,
          height = 14, width = 18)
   return(aus_geo_nwse_plot)
 }
@@ -300,9 +300,9 @@ hex_plot_nwse <- function(data, position, min, max) {
           panel.grid.major = element_blank(),
           panel.grid.minor = element_blank()) 
   
-  ggsave(filename = paste0("figures/final/aus_hex_nwse_", position, ".pdf"), 
+  ggsave(filename = paste0("figures/final/aus_hex_nwse_", position, ".png"), 
          plot = aus_hex_nwse_plot,
-         device = "pdf", dpi = 300,
+         device = "png", dpi = 300,
          height = 14, width = 18)
   return(aus_hex_nwse_plot)
 }

### 2019-10-21 pilot_three.R

@@ -275,9 +275,9 @@ geo_plot_three <- function(data, position, min, max) {
           panel.grid.minor = element_blank())
   
   
-  ggsave(filename = paste0("figures/final/aus_geo_three_", position, ".pdf"), 
+  ggsave(filename = paste0("figures/final/aus_geo_three_", position, ".png"), 
          plot = aus_geo_three_plot,
-         device = "pdf", dpi = 300,
+         device = "png", dpi = 300,
          height = 14, width = 18)
   return(aus_geo_three_plot)
 }
@@ -308,9 +308,9 @@ hex_plot_three <- function(data, position, min, max) {
           panel.grid.major = element_blank(),
           panel.grid.minor = element_blank()) 
   
-  ggsave(filename = paste0("figures/final/aus_hex_three_", position, ".pdf"), 
+  ggsave(filename = paste0("figures/final/aus_hex_three_", position, ".png"), 
          plot = aus_hex_three_plot,
-         device = "pdf", dpi = 300,
+         device = "png", dpi = 300,
          height = 14, width = 18)
   return(aus_hex_three_plot)
 }

### 2019-10-21 taipan1/server.R

@@ -14,8 +14,19 @@ getInputID <- function(input){
 
 shinyServer(
   function(input, output, session) {
+    
+    # Load survey questions
     questions <- readRDS("data/questions.Rds")
-    image_list <- list.files("www/app_images", full.names = TRUE)
+    
+    # Load survey images
+    if (TRUE){
+      image_list <-list.files("www/app_images/groupA", full.names = TRUE)
+      image_list <- sample(image_list, length(image_list))
+    } else {
+      image_list <- list.files("www/app_images/groupB", full.names = TRUE)
+      image_list <- sample(image_list, length(image_list))
+    }
+    
     
     v <- reactiveValues(
       imageNum = 1,
@@ -51,7 +62,7 @@ shinyServer(
         "btn_saveImage",
         box(
           "Save Image",
-          width = 4,
+          width = 6,
           background = "blue"
           
         )
@@ -76,7 +87,7 @@ shinyServer(
           "btn_next",
           box(
             "Next Image",
-            width = 4,
+            width = 6,
             background = "green"
           )
         )
@@ -92,7 +103,7 @@ shinyServer(
           "btn_prev",
           box(
             "Previous Image",
-            width = 4,
+            width = 6,
             background = "green"
           )
         )
@@ -159,6 +170,8 @@ shinyServer(
       v$responses[[basename(current_img())]][["demographic"]] <- demographic_vals()
     })
     
+    
+    # change this to upload rows to survey google spreadsheet
     output$btn_export <- downloadHandler(
       filename = function() {
         paste('experiment-export-', Sys.Date(), '.csv', sep='')

### 2019-10-21 protocol.Rmd
Change to lineup of 12

@@
 Within the experiment:
-A line up protocol will be used to arrange 20 maps into one display.
+A line up protocol will be used to arrange 12 maps into one display.
 Each display will be created by a combination of plot type, spatial error distribution and spatial trend model.
@@
 
-Each lineup is a set of m = 20 plots.
+Each lineup is a set of m = 12 plots.
 One plot contains data with a real structure.
-The probability that an observer picks the data plot when it is really *not* different from the 19 null plots, is $1/m = 1/20$.
+The probability that an observer picks the data plot when it is really *not* different from the 11 null plots, is $1/m = 1/12$.
 
 If a participant is able to identify the data plot from the lineup, we reject the null hypothesis.
-Type I error rate, $\alpha$, is set to a level of $1/m = 1/20 = 0.05$.
+Type I error rate, $\alpha$, is set to a level of $1/m = 1/12 = 0.083$.
 

### 2019-10-21 protocol.Rmd
sample size calculations

--- 2019-10-21 protocol.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(
+  echo = FALSE,
+  warning = FALSE,
+  error = FALSE, 
+  message = FALSE)
 ```
@@
 By chance, the data plot will be detected with probability, $1/12=0.083$.
-This corresponds to about 2 detections out of 20, generally this would be $n/12$ detections.
+This corresponds to about 2 detections out of 20 evaluatoins, and generally this is $n/12$ detections from $n$ evaluations.
 Let's suppose the alternative hypothesis has probability of detection $p_A (>1/12)$.
 If we expect the data to be detected twice as often as by chance, $p_A=1/6$.
-To determine the probability of observing $n/12$ detections, given $p_A$, we can use a binomial distribution, where $k=ceiling(n/12)$, to calculate the power:
+To determine the probability of observing $n/12$ detections, for one lineup, given $p_A$, we can use a binomial distribution, where $k=ceiling(n/12)$, to calculate the power:
 
-$$P(X>k|p=p_A,n) = {n \choose k} p_A^k (1-p_A)^{n-k}$$
-
-If $p_A=1/6$ we would need almost 100 evaluations for each lineup to expect at least $n/12$ detections.
-With $p_A=0.25$ approximately 50 evaluations should yield sufficient detections.
-We will use a pilot study to estimate $p_A$.
+$$P(X\geq k|p=p_A,n) = \sum_{j=k}^{n}{n \choose j} p_A^j (1-p_A)^{n-j}$$
 
@@
 
-```{r echo=FALSE, eval=FALSE}
+```{r echo=FALSE, eval=TRUE, fig.height=5, fig.width=6, out.width="70%"}
 # Code to compute the power for given sample size and alternative p
@@
 library(viridis)
-n <- 20:100
-k <- ceiling(n/12)
-pA <- seq(1/12, 1/2, 0.01)
-g <- expand.grid(n, k, pA)
-pow <- tibble(n=g[,1], k=g[,2], pA=g[,3]) 
+library(knitr)
+n <- 20:50
+pA <- seq(1/12, 1/3, 0.002)
+g <- expand.grid(n, pA)
+pow <- tibble(n=g[,1], k=as.integer(ceiling(g[,1]/12)), pA=g[,2]) 
 pow <- pow %>% 
-  mutate(prob = pbinom(k, n, pA, lower.tail=FALSE)) 
-ggplot(pow, aes(x=n, y=pA, colour=prob, group=pA)) + 
-  geom_point() +
-  scale_colour_viridis_c()
+  mutate(prob = pbinom(k-1, n, pA, lower.tail=FALSE)) 
+ggplot(pow, aes(x=n, y=pA, fill=prob, group=pA)) + 
+  geom_tile() +
+  scale_fill_viridis_c("power") +
+  geom_hline(yintercept=0.1666667, colour="black") +
+  ylab("detect rate (pA)") + xlab("sample size (n)") +
+  theme_bw()
+pow %>% filter(near(pA, 0.167, 0.001)) %>% filter(prob>0.9) %>% top_n(n=10) %>% kable(digits=3)
 ```
+
+The table above shows the sample sizes yielding above 90% chance of detection ($p_d$) in a single lineup assuming $p_A=1/6=0.167$ we would need approximately 50 evaluations for each lineup.
+
+If 4 lineups are evaluated for each trend model, the chance that none produce a detection is $(1-p_d)^4$, which for $p_D>0.9$ is effectively 0.
 

### 2019-10-21 protocol.Rmd
statistical analysis

@@
 
-##	Data analysis and statistical methods
-
-The results will be analysed using a generalised linear model, with a subject random effect. There will be two main effects: plot type and trend model.
-
-Each lineup has the same hypotheses:
-$H_0:$ there is no real structure visible in the data plot
-$H_1:$ there is real structure visible in the data plot
-
-Each lineup is a set of m = 12 plots.
-One plot contains data with a real structure.
-The probability that an observer picks the data plot when it is really *not* different from the 11 null plots, is $1/m = 1/12$.
-
-If a participant is able to identify the data plot from the lineup, we reject the null hypothesis.
-Type I error rate, $\alpha$, is set to a level of $1/m = 1/12 = 0.083$.
-
-Compare the percentage of times users select the real data in a lineup for the same set of data presented in choropleth maps and hexagon tile maps.
-Compare percentages of correct responses $\hat{\pi}_C$ and $\hat{\pi}_H$:
-
-Where $C$ denotes the use of choropleth maps and $H$ denotes the use of hexagon tile maps.
-
-The percentage of correct responses where the respondent identified the real data in a choropleth map is denoted by $\hat{\pi}_C = (x_C +1)/(n_{100} + 1)$, similarly for hexagon tile maps: $\hat{\pi}_H = (x_H +1)/(n_{100} + 1)$.
-
 #	Outcome measures
 
-## Response variables
-
-### Accuracy
+## Accuracy
 
@@
 
-### Efficiency
+## Efficiency
 
@@
 
-## Model
+##	Data analysis and statistical methods
 
-A multilevel linear model with be fitted to the data with elements as specified below.
+### Graphical analysis
 
-Response Variables:
-Accuracy and Efficiency
+For each lineup we will compute
 
-Main Effects:
-Design, Trend
+- accuracy: the proportion of subjects who detected the data plot
+- efficiency: average time taken to respond
 
-Random Effects:
-The collection of multiple responses from each person as they complete several different lineup tasks, allows estimates of their perceptual ability using a subject-specific random intercept in a generalized linear model.
+Side-by-side dot plots will be made of accuracy (efficiency) against plot type, facetted by trend model type.
 
-Possible Interactions:
-Design and Trend, Design and Difficulty, Design and Reason
+Similar plots will be made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.
 
-Possible covariates:
-Responses to the questions regarding the difficulty of making a choice and the reason for the choice of plot in the line up.
+Plots will be made in R~[@RCore], with the `ggplot2` package~[@ggplot2].
+
+### Modeling
+
+The results will be analysed using a generalised linear model, with a subject random effect.
+There will be two main effects: plot type and trend model, which gives the fixed effects part of the model to be
+
+$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3$$
+
+where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the plot type effect, $\delta_j$ is the trend model effect.
+We are allowing for an interaction between plot type and trend model.
+Because the response is binary, a logistic model is used.
+
+A similar model will be constructed for the efficiency, using a log time, and normal errors.
+
+The feedback and demographic variables will possibly be incorporated as covariates.
+
+Computation will be done using R~[@RCore], with the `lme4` package~[@lme4].
 
@@
 
+#	Appendices
+
+A document on the web app is attached.
+
 #	References
-
-#	Appendices 
- - These may include surveys, questionnaires, interview schedules, recruitment materials, manual of operations, etc

### 2019-10-22 protocol.Rmd
last modifications to results, outcomes, ...

@@
 
+#	Outcome measures
+
+## Accuracy
+
+To measure the accuracy of the detections, the plot chosen for each lineup evaluated will be compared to the position of the real spatial trend plot in the lineup.
+
+A correct result occurs when the chosen plot matches the position of the real plot, this will be recorded in an additional binary variable; $1 = correct;~ 0 = incorrect$.
+
+## Efficiency
+
+High efficiency occurs when a small amount of time is taken to evaluate each lineup.
+This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.
+
 #	Statistical plan
@@
 
-#	Outcome measures
-
-## Accuracy
-
-To measure the accuracy of the detections, the plot chosen for each lineup evaluated will be compared to the position of the real spatial trend plot in the lineup.
-
-A correct result occurs when the chosen plot matches the position of the real plot, this will be recorded in an additional binary variable; $1 = correct;~ 0 = incorrect$.
-
-## Efficiency
-
-High efficiency occurs when a small amount of time is taken to evaluate each lineup.
-This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.
-
 ##	Data analysis and statistical methods
@@
 
-Plots will be made in R~[@RCore], with the `ggplot2` package~[@ggplot2].
+Plots will be made in R [@RCore], with the `ggplot2` package [@ggplot2].
 
@@
 
-Computation will be done using R~[@RCore], with the `lme4` package~[@lme4].
+Computation will be done using R [@RCore], with the `lme4` package [@lme4].
 
@@
 #	Resources
-This work will be supported by ACEMS funding - $500 to pay 100 participants equally.
+
+Each participant will earn $AUD5 for their work.
 
 #	Results, outcomes and future plans
- - Plans for return of results of research to participants
- - Publication plan
- - Other potential uses of the data at the end of the project
- - Project closure processes 
- - Plans for sharing and/or future use of data and/or follow-up research
+
+## Plans for return of results of research to participants
+
+There is no intention to provide the results to participants. This might compromise their ability to participate in future experiments.
+
+## Publication plan
+
+We intend to publish this work as a research article in a top journal, along with de-identified data as required by the journal's reproducibility policy.
+
+## Other potential uses of the data at the end of the project
+
+We do not intend to re-use this data, we don't see any major reasons for others to use this data.
+It may be possible that the data may be aggregated with many other studies to examine effects of education, age and gender on reading data plots.
+
+## Project closure processes
+
+The project will be closed once the journal article is published.
+
+## Plans for sharing and/or future use of data and/or follow-up research
+
+Details are provided in the Data Management Plan. The results from this study might inform design of future studies.
 

### 2019-10-22 R/survey_app.R
Scaled three city plots

@@ -4,30 +4,34 @@
 
 # demographics and scene questions
 
-taipanQuestions <- function(demographics, scene){
+surveyQuestions <- function(demographics, scene){
   structure(
     list(demographics = demographics, scene = scene),
     class = "taipanQuestions"
   )
 }
-questions <- taipanQuestions(
+questions <- surveyQuestions(
   demographics =
     div(
       # Contributor ID
-      textInput("contributor", label = "For payment, provide Figure Eight Contributor ID:", 
+      textInput("contributor", "For payment, provide Figure Eight Contributor ID:", 
                 placeholder = "id"),
+      radioButtons("consent", "Do you consent to your responses being analysed for this survey project?\n
+                   For more information click the More Info button.", 
+                   choices = c("Yes, I consent" = 1,"No, I do not consent" = 2),
+                   selected = character(0)),
       # Question 1, gender
       selectInput("gender",
-                  h3("Select your preferred pronoun:"),
+                  "Select your preferred pronoun:",
                   choices = list("Choose one" = 1, 
                                  "She" = 2, 
                                  "He" = 3,
                                  "They" = 4,
-                                 "other = 5"), 
+                                 "Other" = 5), 
                   selected = 1),
       # Question 2, education
       selectInput("education",
-                  h3("Select the highest level of education achieved:"),
+                  "Select the highest level of education achieved:",
                   choices = list("Choose one" = 1, 
                                  "High School Diploma" = 2,
                                  "Bachelors Degree" = 3,
@@ -38,7 +42,7 @@ questions <- taipanQuestions(
                   selected = 1),
       # Question 3, age range
       selectInput("education",
-                  h3("Select your age range:"),
+                  "Select your age range:",
                   choices = list("Choose one" = 1, 
                                  "18 - 24" = 2,
                                  "25 - 34" = 3,
@@ -50,7 +54,7 @@ questions <- taipanQuestions(
                   selected = 1),
       # Question 4, Australia
       selectInput("australia",
-                  h3("Have you lived in Australia?"),
+                  "Have you lived in Australia?",
                   choices = list("Choose one" = 1, 
                                  "Yes" = 2,
                                  "No" = 3, 
@@ -61,7 +65,7 @@ questions <- taipanQuestions(
     div(
       # Question 1, the choice of plot
       selectInput("select",
-                  h3("Which map is most different from the others?"),
+                  "Which map is most different from the others?",
                   choices = list("Choose a plot number:" = 0,
[…]

### 2019-10-22 pilot_three.R

@@ -184,65 +184,100 @@ city_list2 <- sample(x = cities, size = 3)
 city_list3 <- sample(x = cities, size = 3)
 city_list4 <- sample(x = cities, size = 3)
 
-sa3_three <- allocated %>% 
+sa3_three_1 <- allocated %>% 
   select(sa3_name_2016, longitude, latitude, points, focal_dist) %>% 
   mutate(city_distance = (max_dist - focal_dist)^8,
          # only for desired three
-         dist = ifelse(points %in% city_list, 
+         dist = ifelse(points %in% city_list1, 
                        scales::rescale(city_distance, to = c(0,1)), NA),
          three = ifelse(dist < 0.85, NA,
                         scales::rescale(city_distance, to = c(1, 3.2))))
+
+
+sa3_three_2 <- allocated %>% 
+  select(sa3_name_2016, longitude, latitude, points, focal_dist) %>% 
+  mutate(city_distance = (max_dist - focal_dist)^8,
+         # only for desired three
+         dist = ifelse(points %in% city_list2, 
+                       scales::rescale(city_distance, to = c(0,1)), NA),
+         three = ifelse(dist < 0.85, NA,
+                        scales::rescale(city_distance, to = c(1, 3.2))))
+
+sa3_three_3 <- allocated %>% 
+  select(sa3_name_2016, longitude, latitude, points, focal_dist) %>% 
+  mutate(city_distance = (max_dist - focal_dist)^8,
+         # only for desired three
+         dist = ifelse(points %in% city_list3, 
+                       scales::rescale(city_distance, to = c(0,1)), NA),
+         three = ifelse(dist < 0.85, NA,
+                        scales::rescale(city_distance, to = c(1, 3.2))))
+
+sa3_three_4 <- allocated %>% 
+  select(sa3_name_2016, longitude, latitude, points, focal_dist) %>% 
+  mutate(city_distance = (max_dist - focal_dist)^8,
+         # only for desired three
+         dist = ifelse(points %in% city_list4, 
+                       scales::rescale(city_distance, to = c(0,1)), NA),
+         three = ifelse(dist < 0.85, NA,
+                        scales::rescale(city_distance, to = c(1, 3.2))))
+
+bind_rows("sa3_three_1" = sa3_three_1, 
+          "sa3_three_2" = sa3_three_2, 
+          "sa3_three_3" = sa3_three_3, 
[…]

### 2019-10-22 R/survey_app.R
app data collection completed

@@ -16,8 +16,9 @@ questions <- surveyQuestions(
       # Contributor ID
       textInput("contributor", "For payment, provide Figure Eight Contributor ID:", 
                 placeholder = "id"),
+      p("For more information click the More Info button"),
       radioButtons("consent", "Do you consent to your responses being analysed for this survey project?\n
-                   For more information click the More Info button.", 
+                   .", 
                    choices = c("Yes, I consent" = 1,"No, I do not consent" = 2),
                    selected = character(0)),
       # Question 1, gender
@@ -41,7 +42,7 @@ questions <- surveyQuestions(
                   ), 
                   selected = 1),
       # Question 3, age range
-      selectInput("education",
+      selectInput("age",
                   "Select your age range:",
                   choices = list("Choose one" = 1, 
                                  "18 - 24" = 2,

### 2019-10-22 pilot_three.R

@@ -226,7 +226,7 @@ bind_rows("sa3_three_1" = sa3_three_1,
           "sa3_three_3" = sa3_three_3, 
           "sa3_three_4" = sa3_three_4, 
           .id = "sets") %>% 
-ggplot() + geom_histogram(aes(x = three)) + facet_grid(points ~ sets)
+  ggplot() + geom_histogram(aes(x = three)) + facet_grid(points ~ sets)
 
 
 ### Start with shapes - geographies

### 2019-10-22 taipan1/server.R

@@ -1,6 +1,8 @@
 library(shiny)
 library(ggplot2)
 library(purrr)
+# Load survey questions
+questions <- readRDS("data/questions.Rds")
 
 getInputID <- function(input){
   if(!inherits(input, "shiny.tag")){
@@ -15,9 +17,6 @@ getInputID <- function(input){
 shinyServer(
   function(input, output, session) {
     
-    # Load survey questions
-    questions <- readRDS("data/questions.Rds")
-    
     # Load survey images
     if (TRUE){
       image_list <-list.files("www/app_images/groupA", full.names = TRUE)
@@ -30,7 +29,9 @@ shinyServer(
     
     v <- reactiveValues(
       imageNum = 1,
-      responses = list()
+      responses = list(),
+      time = Sys.time(),
+      plot_order = 1
     )
     
     current_img <- reactive({
@@ -57,18 +58,6 @@ shinyServer(
       vals
     })
     
-    output$ui_save <- renderUI({
-      actionLink(
-        "btn_saveImage",
-        box(
-          "Save Image",
-          width = 6,
-          background = "blue"
-          
-        )
-      )
-    })
-    
     output$ui_d_save <- renderUI({
       actionLink(
         "btn_saveInfo",
@@ -87,7 +76,7 @@ shinyServer(
           "btn_next",
           box(
             "Next Image",
-            width = 6,
+            width = 12,
             background = "green"
           )
         )
@@ -97,21 +86,6 @@ shinyServer(
       }
     })
     
-    output$ui_btn_prev <- renderUI({
-      if (v$imageNum != 1) {
-        actionLink(
-          "btn_prev",
-          box(
-            "Previous Image",
-            width = 6,
-            background = "green"
-          )
-        )
-      }
-      else {
-        column(3)
-      }
-    })
     
     # Update the scene values when images change
     observeEvent(current_img(), {
@@ -138,27 +112,16 @@ shinyServer(
       v$responses[[basename(current_img())]][["demographic"]] <- demographic_vals()
     })
     
-    observeEvent(input$btn_prev, {
-      v$responses[[basename(current_img())]][["scene"]] <- scene_vals()
-      v$responses[[basename(current_img())]][["demographic"]] <- demographic_vals()
-      v$imageNum <- pmax(1, v$imageNum - 1)
-    })
-    
     observeEvent(input$btn_next, {
       v$responses[[basename(current_img())]][["scene"]] <- scene_vals()
[…]

### 2019-10-22 taipan1/ui.R

@@ -1,15 +1,19 @@
 library(shiny)
 library(shinydashboard)
 
+# Load survey questions
+questions <- readRDS("data/questions.Rds")
+
 shinyUI(
   dashboardPage(
     dashboardHeader(
       title = "taipan",
-      tags$li(class = "dropdown", downloadLink("btn_export", span(icon("save"), "Submit Survey"))),
+      tags$li(class = "dropdown", actionLink("btn_export", span(icon("save"), "Submit Survey"))),
       tags$li(class = "dropdown", a(href="https://github.com/srkobakian/experiment", target="_blank", span(icon("github"), "More Info")))
     ),  
     dashboardSidebar(
       sidebarMenu(
+        id = "tabs",
         menuItem("About you", tabName = "About_you", icon = icon("dashboard")),
         menuItem("Questions", tabName = "Questions", icon = icon("th"))
       )
@@ -48,7 +52,6 @@ shinyUI(
                          title = "Questions",
                          questions$scene,
                          div(
-                           uiOutput("ui_btn_prev"),
                            uiOutput("ui_btn_next")),
                          width = 12,
                          status = "info",

### 2019-10-22 R/survey_app.R
survey app load questions

@@ -88,7 +88,8 @@ questions <- surveyQuestions(
                            "None of these reasons" = 0,
                            "Clusters of colour" = 1,
                            "Colour trend across the areas" = 2,
-                           "Big differences between neighbours" = 3)),
+                           "Big differences between neighbours" = 3,
+                           "All areas have similar colours" = 4)),
       # Question 3, certainty around their choice
       sliderInput("certainty", "How certain are you that the chosen map is different? 
                                   1 = Very uncertain, 3 = Neutral, 5 = Very certain",

### 2019-10-22 taipan1/server.R

@@ -2,7 +2,7 @@ library(shiny)
 library(ggplot2)
 library(purrr)
 # Load survey questions
-questions <- readRDS("data/questions.Rds")
+#questions <- readRDS("data/questions.Rds")
 
 getInputID <- function(input){
   if(!inherits(input, "shiny.tag")){

### 2019-10-22 pilot_cities.R
changed naming convention

@@ -184,7 +184,8 @@ sa3_cities <- allocated %>%
                                 to = c(0,1)),
          cities = ifelse(dist < 0.85, NA, 
                          scales::rescale(city_distance,
-                                         to = c(1, 3))))
+                                         to = c(min(sa3_min1,sa3_min2,sa3_min3,sa3_min4), 
+                                                max(sa3_max1,sa3_max2,sa3_max3,sa3_max4)))))
 
 
 ### Start with shapes - geographies
@@ -268,7 +269,7 @@ geo_plot_cities <- function(data, position, min, max) {
           panel.grid.minor = element_blank())
   
   
-  ggsave(filename = paste0("figures/final/aus_geo_cities_", position, ".png"), 
+  ggsave(filename = paste0("figures/final/aus_cities_", position, "_geo.png"), 
          plot = aus_geo_cities_plot,
          device = "png", dpi = 300,
          height = 14, width = 18)
@@ -301,7 +302,7 @@ hex_plot_cities <- function(data, position, min, max) {
           panel.grid.major = element_blank(),
           panel.grid.minor = element_blank()) 
   
-  ggsave(filename = paste0("figures/final/aus_hex_cities_", position, ".png"), 
+  ggsave(filename = paste0("figures/final/aus_cities_", position, "_hex.png"), 
          plot = aus_hex_cities_plot,
          device = "png", dpi = 300,
          height = 14, width = 18)

### 2019-10-22 pilot_nwse.R

@@ -267,7 +267,7 @@ geo_plot_nwse <- function(data, position, min, max) {
           panel.grid.minor = element_blank())
   
   
-  ggsave(filename = paste0("figures/final/aus_geo_nwse_", position, ".png"), 
+  ggsave(filename = paste0("figures/final/aus_nwse_", position, "_geo.png"), 
          plot = aus_geo_nwse_plot,
          device = "png", dpi = 300,
          height = 14, width = 18)
@@ -300,7 +300,7 @@ hex_plot_nwse <- function(data, position, min, max) {
           panel.grid.major = element_blank(),
           panel.grid.minor = element_blank()) 
   
-  ggsave(filename = paste0("figures/final/aus_hex_nwse_", position, ".png"), 
+  ggsave(filename = paste0("figures/final/aus_nwse_", position, "_hex.png"), 
          plot = aus_hex_nwse_plot,
          device = "png", dpi = 300,
          height = 14, width = 18)

### 2019-10-22 pilot_three.R

@@ -311,7 +311,7 @@ geo_plot_three <- function(data, position, min, max) {
           panel.grid.minor = element_blank())
   
   
-  ggsave(filename = paste0("figures/final/aus_geo_three_", position, ".png"), 
+  ggsave(filename = paste0("figures/final/aus_three_", position, "_geo.png"), 
          plot = aus_geo_three_plot,
          device = "png", dpi = 300,
          height = 14, width = 18)
@@ -345,7 +345,7 @@ hex_plot_three <- function(data, position, min, max) {
           panel.grid.major = element_blank(),
           panel.grid.minor = element_blank()) 
   
-  ggsave(filename = paste0("figures/final/aus_hex_three_", position, ".png"), 
+  ggsave(filename = paste0("figures/final/aus_three_", position, "_hex.png"), 
          plot = aus_hex_three_plot,
          device = "png", dpi = 300,
          height = 14, width = 18)

### 2019-10-22 pilot_three.R
Major cities

@@ -178,7 +178,7 @@ sa3_mean4 <- sa3_long4  %>% pull(value) %>% mean()
 max_dist <- 1478314 # furthest area from any focal point
 
 set.seed(2019)
-cities <- c("Canberra","Sydney","Darwin","Brisbane","Melbourne","Adelaide","Hobart","Perth")
+cities <- c("Sydney","Brisbane","Melbourne","Adelaide","Perth", "Hobart")
 city_list1 <- sample(x = cities, size = 3)
 city_list2 <- sample(x = cities, size = 3)
 city_list3 <- sample(x = cities, size = 3)

### 2019-10-23 taipan1/server.R
Update to app consent

@@ -2,7 +2,6 @@ library(shiny)
 library(ggplot2)
 library(purrr)
 # Load survey questions
-#questions <- readRDS("data/questions.Rds")
 
 getInputID <- function(input){
   if(!inherits(input, "shiny.tag")){
@@ -129,11 +128,16 @@ shinyServer(
     })
     
     observeEvent(input$btn_saveInfo, {
-      showNotification(h3("Demographic information has been saved."), type = "default")
+      
+      if (!(isTRUE(v$responses[[basename(current_img())]][["demographic"]]$consent))) {
+        showNotification(h3("Consent must be given before you can proceed to questions."), type = "error", duration = 1)
+      } else{
+      showNotification(h3("Demographic information has been saved."), type = "message", duration = 1)
       v$responses[[basename(current_img())]][["demographic"]] <- demographic_vals()
       
       # Switch to the survey tab
       updateTabItems(session = session, inputId = "tabs", selected = "Questions")
+      }
     })
     
     

### 2019-10-23 taipan1/ui.R

@@ -2,7 +2,105 @@ library(shiny)
 library(shinydashboard)
 
 # Load survey questions
-questions <- readRDS("data/questions.Rds")
+
+surveyQuestions <- function(demographics, scene){
+  structure(
+    list(demographics = demographics, scene = scene),
+    class = "taipanQuestions"
+  )
+}
+questions <- surveyQuestions(
+  demographics =
+    div(
+      # Contributor ID
+      textInput("contributor", "For payment, provide Figure Eight Contributor ID:", 
+                placeholder = "id"),
+      tags$b("Title:"),
+      p("Assessing the effectiveness of different visualisation methods for Australian spatial data."),
+      p("Principal Investigators:", tags$br(),
+        "Stephanie Kobakian - stephaie.kobakian@monash.edu", tags$br(),
+        "DProf Kerrie Mengersen - k.megersen@qut.edu.au", tags$br(),
+        "For more information click the More Info button."),
+      radioButtons("consent", "Do you consent to your responses being analysed for this survey project?\n
+                   .", 
+                   choices = c("Yes, I consent to my responses being used for research purposes and allow them to be published online in a de-identified form." = 1,
+                               "No, I do not consent to my responses being used for research purposes and allow them to be published online in a de-identified form." = 2),
+                   selected = character(0)),
+      # Question 1, gender
+      selectInput("gender",
+                  "Select your preferred pronoun:",
+                  choices = list("Choose one" = 1, 
+                                 "She" = 2, 
+                                 "He" = 3,
+                                 "They" = 4,
+                                 "Other" = 5), 
+                  selected = 1),
+      # Question 2, education
+      selectInput("education",
+                  "Select the highest level of education achieved:",
+                  choices = list("Choose one" = 1, 
+                                 "High School Diploma" = 2,
+                                 "Bachelors Degree (Undergraduate)" = 3,
+                                 "Masters Degree (Post graduate)" = 4,
+                                 "Doctorate (Post graduate)" = 5,
+                                 "Other" = 6
+                  ), 
+                  selected = 1),
+      # Question 3, age range
+      selectInput("age",
+                  "Select your age range:",
+                  choices = list("Choose one" = 1, 
+                                 "18 - 24" = 2,
+                                 "25 - 34" = 3,
+                                 "35 - 44" = 4,
+                                 "45 - 54" = 5,
+                                 "55+" = 6,
+                                 "Other" = 7
+                  ), 
+                  selected = 1),
+      # Question 4, Australia
[…]

### 2019-10-23 protocol.Rmd
table of investigators

@@
 |          Researcher          |    Role                    |    Affiliation                                                                |   |   |
-|:----------------------------:|----------------------------|-------------------------------------------------------------------------------|---|---|
+|:------------------------------------------|:--------------------------------------|:-------------------------------------------------------------------------------|---|---|
 |    Stephanie Kobakian        |    Masters Student         | Faculty of Science and Engineering (QUT)                                      |   |   |
@@
 |    Prof. Dianne Cook         |    External Supervisor     |    Department of Econometrics and   Business Statistics, Monash University    |   |   |
-|                              |                            |
 

### 2019-10-23 R/survey_app.R
pilot study app

@@ -100,3 +100,13 @@ questions <- surveyQuestions(
 saveRDS(questions, file = "data/questions.Rds")
 saveRDS(questions, file = "taipan1/data/questions.Rds")
 
+
+
+
+textInput("contributor", "For payment, provide Figure Eight Contributor ID:", 
+          placeholder = "id"),
+
+p("Assessing the effectiveness of hexagon tile maps for communicating spatial distributions of disease for Australia."),
+p("If you have questions, please contact Stephanie Kobakian - stephanie.kobakian@monash.edu"),
+p("If you have concerns about the ethical conduct of the research project you can contact the Research Ethics Advisory Team on +61 7 3138 5123 or email humanethics@qut.edu.au"),
+

### 2019-10-23 taipan1/server.R
Consent fixed

@@ -128,15 +128,16 @@ shinyServer(
     })
     
     observeEvent(input$btn_saveInfo, {
-      
-      if (!(isTRUE(v$responses[[basename(current_img())]][["demographic"]]$consent))) {
-        showNotification(h3("Consent must be given before you can proceed to questions."), type = "error", duration = 1)
-      } else{
-      showNotification(h3("Demographic information has been saved."), type = "message", duration = 1)
       v$responses[[basename(current_img())]][["demographic"]] <- demographic_vals()
       
-      # Switch to the survey tab
-      updateTabItems(session = session, inputId = "tabs", selected = "Questions")
+      if (v$responses[[basename(current_img())]][["demographic"]]$consent==1) {
+        showNotification(h3("Demographic information has been saved."), type = "message", duration = 1)
+        
+        # Switch to the survey tab
+        updateTabItems(session = session, inputId = "tabs", selected = "Questions")
+      } else{
+      showNotification(h3("Consent must be given before you can proceed to questions."), type = "error", duration = 1)
+      
       }
     })
     

### 2019-10-23 taipan1/ui.R
radio button reasons

@@ -79,16 +79,16 @@ questions <- surveyQuestions(
                                  "10" = 10,
                                  "11" = 11,
                                  "12" = 12
-                  ), selected = 1),
+                  ), selected = 0),
       # Question 2, reason for their choice
-      checkboxGroupInput("reason",
+      radioButtons("reason",
                          "What makes your chosen map different?:",
                          choices = list(
                            "None of these reasons" = 0,
                            "Clusters of colour" = 1,
                            "Colour trend across the areas" = 2,
                            "Big differences between neighbours" = 3,
-                           "All areas have similar colours" = 4)),
+                           "All areas have similar colours" = 4), selected = 0),
       # Question 3, certainty around their choice
       sliderInput("certainty", "How certain are you that the chosen map is different? 
                                   1 = Very uncertain, 3 = Neutral, 5 = Very certain",

### 2019-10-23 taipan1/server.R
hopefully fixed sample size calculations

@@ -119,6 +119,7 @@ shinyServer(
       v$responses[[basename(current_img())]][["demographic"]] <- demographic_vals()
       
       v$imageNum <- pmin(length(image_list), v$imageNum + 1)
+      reset("select")
     })
       
     output$out_img_info <- renderText({

### 2019-10-23 taipan1/ui.R
use google sheets

@@ -1,5 +1,6 @@
 library(shiny)
 library(shinydashboard)
+library(googlesheets)
 
 # Load survey questions
 
@@ -64,7 +65,7 @@ questions <- surveyQuestions(
   scene =
     div(
       # Question 1, the choice of plot
-      selectInput("select",
+      selectInput("choice",
                   "Which map is most different from the others?",
                   choices = list("Choose a plot number:" = 0,
                                  "1" = 1,

### 2019-10-23 protocol.Rmd

@@
 By chance, the data plot will be detected with probability, $1/12=0.083$.
-This corresponds to about 2 detections out of 20 evaluatoins, and generally this is $n/12$ detections from $n$ evaluations.
-Let's suppose the alternative hypothesis has probability of detection $p_A (>1/12)$.
+Assuming a binomial distribution we can determine the critical value that would indicate the number of detections from $n$ evaluations, corresponding to a rejection of $H_0: p=0.083$.
+For example, with 50 evaluations, with significance level 0.05, if there are 8 or more detections, it is better than chance, say $C$.
+
+This critical value can be used to estimate the sample size needed, for the study, by computing the power, the probability of rejecting $H_0: 0.083$, for alternative values of $p=p_A$.
 If we expect the data to be detected twice as often as by chance, $p_A=1/6$.
-To determine the probability of observing $n/12$ detections, for one lineup, given $p_A$, we can use a binomial distribution, where $k=ceiling(n/12)$, to calculate the power:
+To determine the probability of observing $C$ detections from $n$ evaluations, for one lineup, to calculate the power:
 
-$$P(X\geq k|p=p_A,n) = \sum_{j=k}^{n}{n \choose j} p_A^j (1-p_A)^{n-j}$$
+$$P(X\geq C|p=p_A,n) = \sum_{j=C}^{n}{n \choose j} p_A^j (1-p_A)^{n-j}$$
 
@@
 pA <- seq(1/12, 1/3, 0.002)
-g <- expand.grid(n, pA)
-pow <- tibble(n=g[,1], k=as.integer(ceiling(g[,1]/12)), pA=g[,2]) 
-pow <- pow %>% 
-  mutate(prob = pbinom(k-1, n, pA, lower.tail=FALSE)) 
+pow <- sample_size(n, 12, pA)
+#g <- expand.grid(n, pA)
+#pow <- tibble(n=g[,1], k=as.integer(ceiling(g[,1]/12)), pA=g[,2]) 
+#pow <- pow %>% 
+#  mutate(prob = pbinom(k-1, n, pA, lower.tail=FALSE)) 
 ggplot(pow, aes(x=n, y=pA, fill=prob, group=pA)) + 
@@
   theme_bw()
-pow %>% filter(near(pA, 0.167, 0.001)) %>% filter(prob>0.9) %>% top_n(n=10) %>% kable(digits=3)
+pow %>% filter(near(pA, 0.167, 0.001)) %>% filter(prob>0.7) %>% top_n(n=10) %>% kable(digits=3)
 ```
 
-The table above shows the sample sizes yielding above 90% chance of detection ($p_d$) in a single lineup assuming $p_A=1/6=0.167$ we would need approximately 50 evaluations for each lineup.
+The table above shows the sample sizes yielding above 70% chance of detection ($p_d$) in a single lineup assuming $p_A=1/6=0.167$ we would need approximately 50 evaluations for each lineup.
 
-If 4 lineups are evaluated for each trend model, the chance that none produce a detection is $(1-p_d)^4$, which for $p_D>0.9$ is effectively 0.
+If 4 lineups are evaluated for each trend model, the chance that none produce a detection is $1-(1-p_d)^4$, which is effectively 0.
+With 100 participants, giving 50 evaluations per lineup, if there is an effect size twice as high as chance, then we should see it in the results.
 

### 2019-10-23 R/survey_app.R
wooo! it works

@@ -103,10 +103,20 @@ saveRDS(questions, file = "taipan1/data/questions.Rds")
 
 
 
-textInput("contributor", "For payment, provide Figure Eight Contributor ID:", 
-          placeholder = "id"),
+#textInput("contributor", "For payment, provide Figure Eight Contributor ID:", 
+#          placeholder = "id"),
+#
+#p("Assessing the effectiveness of hexagon tile maps for communicating spatial distributions of disease for Australia."),
+#p("If you have questions, please contact Stephanie Kobakian - stephanie.kobakian@monash.edu"),
+#p("If you have concerns about the ethical conduct of the research project you can contact the Research Ethics Advisory Team on +61 7 3138 5123 or email humanethics@qut.edu.au"),
 
-p("Assessing the effectiveness of hexagon tile maps for communicating spatial distributions of disease for Australia."),
-p("If you have questions, please contact Stephanie Kobakian - stephanie.kobakian@monash.edu"),
-p("If you have concerns about the ethical conduct of the research project you can contact the Research Ethics Advisory Team on +61 7 3138 5123 or email humanethics@qut.edu.au"),
 
+
+img_row <- function(img, image_name){
+  scene_row <- img$scene %>%
+    map_dfc(function(x){ifelse(is.null(x),NA , return(x))})
+  demographic_row <- img$demographic %>%
+    map_dfc(function(x){ifelse(is.null(x),NA , return(x))})
+  df <- dplyr::bind_cols(image_name = image_name, scene_row, demographic_row)
+  return(df)
+}

### 2019-10-23 taipan1/server.R

@@ -88,21 +88,14 @@ shinyServer(
     
     # Update the scene values when images change
     observeEvent(current_img(), {
-      map(sceneInputs,
-          function(io){
-            # Update scene inputs
-            val <- v$responses[[basename(current_img())]][["scene"]][[io$id]]
-            if(!is.null(val)){
-              session$sendInputMessage(
-                io$id,
-                list(
-                  value = val,
-                  selected = val
-                )
-              )
-            }
-          }
-      )
+      
+      # return scene questions to original state
+      updateSelectInput(session, "choice",
+                        selected = 0)
+      updateSelectInput(session, "reason",
+                        selected = 0)
+      updateSelectInput(session, "certainty",
+                        selected = 3)
       
     })
     
@@ -119,7 +112,6 @@ shinyServer(
       v$responses[[basename(current_img())]][["demographic"]] <- demographic_vals()
       
       v$imageNum <- pmin(length(image_list), v$imageNum + 1)
-      reset("select")
     })
       
     output$out_img_info <- renderText({

### 2019-12-17 analysis/analysis_fe.Rmd
survey report

---
title: "Untitled"
author: "Stephanie"
date: "05/12/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data

```{r}
library(tidyverse)
library(readr)
fe <- read_xlsx("experiment-export.xlsx", sheet=2) %>%
  filter(!is.na(contributor)) %>%
  mutate(contributor = factor(contributor))
```

# Check IDs
```{r}
count(fe, contributor, sort=TRUE) %>% mutate(submissions = n/12) %>% filter(submissions > 1)
```

# Compare to figure eight report

```{r}
contributors <- f1463460 %>% 
  select(contributor = `_worker_id`, 
  country = `_country`,
  validation1 = please_enter_the_unique_validation_code_shown_when_you_completed_the_survey) %>% 
  mutate(contributor = as_factor(contributor))

check <- fe %>% select(contributor, consent, validation) %>% distinct(.keep_all = TRUE) %>% 
left_join(contributors)
```

```{r}
# Load Libraries
library(tidyverse)
library(lubridate)
library(broom)
library(readxl)
library(lme4)
library(ggthemes)

invthm <- theme(
    panel.background = element_rect(fill = "transparent", colour = NA), 
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.key = element_rect(fill = "transparent", colour = NA),
    text = element_text(colour = "white", size = 20),
    axis.text = element_text(colour = "white", size = 20)
  )

###############################################################################
# Check data set 
fe %>% count(contributor)

# add data replication number
replicate <- bind_cols(replicate = sort(rep(1:12, 2)), image_name = (list.files("figures/final"))) %>% 
  mutate(replicate = as.factor(replicate))

fe <-  fe %>% left_join(., replicate, by = "image_name")

fe %>% count(group, image_name)

#remove duplilcated entries due to submit button
fe <- fe %>% group_by(group, contributor, image_name) %>%
  slice(1) %>% ungroup() %>% 
  arrange(group, contributor)

image_smry <- fe %>% count(group, contributor, order, sort = TRUE)

image_smry %>% ggplot() + geom_col(aes(x = contributor, y = n, fill = order)) + coord_flip()
# This shows multiple submission of scores by some participants

# Fix for unique contributor names
fe <-  fe %>% 
  mutate(id = paste0(group, group_indices(., group, contributor)))

```

### 2019-12-17 survey/survey.Rmd
survey report

---
title: Visual Inference Test of the Hexagon Tile Map for Spatial Distributions
affiliation:
  author-columnar: true         ## one column per author
  #institution-columnar: true  ## one column per institution (multiple autors eventually)
  # wide: true                  ## one column wide author/affiliation fields

  institution:
    - name: Queensland University of Technology
      department: Science and Engineering Faculty
      location: Brisbane, Australia
      email: stephanie.kobakian@qut.edu.au
      mark: 1
      author:
        - name: Stephanie Kobakian
    - name: Monash University
      department: Econometrics and Business Statistics Faculty
      location: Melbourne, Australia
      email: dicook@monash.edu
      mark: 1
      author:
        - name: Dianne Cook
keywords: ["statistics", "visual inference", "geospatial", "population"]
abstract: |
  The abstract goes here.
  On multiple lines eventually.

bibliography: mybibfile.bib
output: rticles::ieee_article
---

Introduction
=============
<!-- no \IEEEPARstart -->
<!-- You must have at least 2 lines in the paragraph with the drop letter -->
<!-- (should never be an issue) -->
Geo-spatial statistics are often presented on the geographic map base. To present geo-spatial population statistics, information for individuals within each geographic region are often aggregated. A choropleth map is the common display to present aggreagated statistics for subdivisions of the geography, and they are often used to present statistics regarding the population. 
This visualisation method involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic. 
In Australia, there are sets of administrative boundaries that define subdivisions of the population at various granularities.

When presenting population statistics on a geographic map base, the size of the regions can allow errornous conclusions to be drawn about the state of the statistic over the entire population.
This occurs as large regions filled with a consistent colour or pettern can draw the attention of map readers, and small regions are not paid equal attention. XXX

Background and Motivation
=============

## Australian Cancer Atlas
- Communicating spatial distributions
- Trend over geographic space
- Trend over communities and populations

The Australian Cancer Atlas explores the burden of cancer on Australian communities. There are many cancer types presented, and can be explored on an individual or aggregate level. 
The Australian communities examined are Statistical Areas at Level 2 (SA2) used by the Australian Bureau of Statistics.
Bayesian spatial smoothing has been applied to incorporate the statistics of neighbouring areas, for both privacy and stability of the estimates.
The statistics that can be mapped are the diagnoses (Standardised Incidence Rates) and excess deaths for each SA2, communicated as the difference from the Australian average of the statistics.
The values of the statistic for each are communicated using a diverging colour scheme. Dark blue represents areas with values much less than the Australian average, and represents areas much greater than the Australian average.

## Visual Inference
- Communicating data through visualisations
- Effective displays for types of data
- Testing the effectiveness

Classical statistical inferences involves hypothesis testing, the process of rejecting a null hypothesis in favour of an alternative. This approach relies on data, the appropriate distributions and their assumptions.

## Line up protocol

The lineup protocol presents a method for visual inference testing.

> "In this framework, plots take on the role of test statistics, and human cognition the role of statistical tests." @SIEDAMD

The line up protocol involves placing a "guilty" data visualisation in a lineup of "innocents". Where the guilty data set contains structure, and the innocents are equivalent to a null data set. 
In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the group innocents.
The guilty data is identified as different from the innocent data with probability $1/m$, where $m$ is the number of null plots plus 1 to account account for the guilty data set. When the guilty data set is chosen, the null hypothesis that it was innocent is rejected with a $1/m$ chance or type I error of being wrong.

The lineup protocol can be used in a variety of tsting scenarios. The choropleth map is best used for testing spatial structure in a data set.

## Population focussed displays

Map creators have the ability to present spatial statistics in alternative displays that can highlight the population.
This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
The same data will be shown on a choropleth map, and on a hexagon tile map.
Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.

Methodology
============

A survey was created to test the effectiveness of the hexagon tile map display.

Experimental Design:
Three trends were tested, in each of the two displays.
For each of the

Line up protocol:

<!--
The line-up protocol works like a police line-up: the suspect (test
statistic plot) is hidden in a set of decoys. If the observer, who has not
seen the suspect, can pick it out as being noticeably different, there is
evidence that it is not innocent.
-->

- Experimental design

  - The overall structure and operation of the experiment or observational experience.
  - The subject populations: The groups studied in the research including the size of each group and any features of the subjects which may be relevant to the topic being researched. 
  - The  variables that were changed between groups and the variables measured as a result of the changes.
  - The conditions under which the research was undertaken and any factors or variations in conditions which may have an impact on the results.
  - The methods of data analysis used in order to analyse and collate the results. 
  - Any limitations of the data collected

Results
============

1. Type  
1. Trend
1. Interaction of type and trend
1. Demographics of participants

## Probability of detection:

## Time taken

## Modeling

Discussion
============

Conclusion
============
The conclusion goes here.

<!-- conference papers do not normally have an appendix -->

Acknowledgment {#acknowledgment}
==============

The authors would like to thank...

Bibliography styles
===================

Here are two sample references: @Feynman1963118 [@Dirac1953888].

\newpage
References {#references .numbered}
==========

<!--This section outlines the topic and the question that the researcher aims to answer through the research.  It also outlines the reasons for researching this question, explaining how the answers could be useful or significant in some way. -->

<!-- An example of a floating figure using the graphicx package. -->
<!-- Note that \label must occur AFTER (or within) \caption. -->
<!-- For figures, \caption should occur after the \includegraphics. -->
<!-- Note that IEEEtran v1.7 and later has special internal code that -->
<!-- is designed to preserve the operation of \label within \caption -->
<!-- even when the captionsoff option is in effect. However, because -->
<!-- of issues like this, it may be the safest practice to put all your -->
<!-- \label just after \caption rather than within \caption{}. -->

<!-- Reminder: the "draftcls" or "draftclsnofoot", not "draft", class -->
<!-- option should be used if it is desired that the figures are to be -->
<!-- displayed while in draft mode. -->

<!-- \begin{figure}[!t] -->
<!-- \centering -->
<!-- \includegraphics[width=2.5in]{myfigure} -->
<!-- where an .eps filename suffix will be assumed under latex,  -->
<!-- and a .pdf suffix will be assumed for pdflatex; or what has been declared -->
<!-- via \DeclareGraphicsExtensions. -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure} -->

<!-- Note that the IEEE typically puts floats only at the top, even when this -->
<!-- results in a large percentage of a column being occupied by floats. -->

<!-- An example of a double column floating figure using two subfigures. -->
<!-- (The subfig.sty package must be loaded for this to work.) -->
<!-- The subfigure \label commands are set within each subfloat command, -->
<!-- and the \label for the overall figure must come after \caption. -->
<!-- \hfil is used as a separator to get equal spacing. -->
<!-- Watch out that the combined width of all the subfigures on a  -->
<!-- line do not exceed the text width or a line break will occur. -->

<!-- \begin{figure*}[!t] -->
<!-- \centering -->
<!-- \subfloat[Case I]{\includegraphics[width=2.5in]{box}% -->
<!-- \label{fig_first_case}} -->
<!-- \hfil -->
<!-- \subfloat[Case II]{\includegraphics[width=2.5in]{box}% -->
<!-- \label{fig_second_case}} -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure*} -->

<!-- Note that often IEEE papers with subfigures do not employ subfigure -->
<!-- captions (using the optional argument to \subfloat[]), but instead will -->
<!-- reference/describe all of them (a), (b), etc., within the main caption. -->
<!-- Be aware that for subfig.sty to generate the (a), (b), etc., subfigure -->
<!-- labels, the optional argument to \subfloat must be present. If a -->
<!-- subcaption is not desired, just leave its contents blank, -->
<!-- e.g., \subfloat[]. -->

<!-- An example of a floating table. Note that, for IEEE style tables, the -->
<!-- \caption command should come BEFORE the table and, given that table -->
<!-- captions serve much like titles, are usually capitalized except for words -->
<!-- such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to -->
<!-- and up, which are usually not capitalized unless they are the first or -->
<!-- last word of the caption. Table text will default to \footnotesize as -->
<!-- the IEEE normally uses this smaller font for tables. -->
<!-- The \label must come after \caption as always. -->

<!-- \begin{table}[!t] -->
<!-- % increase table row spacing, adjust to taste -->
<!-- \renewcommand{\arraystretch}{1.3} -->
<!-- if using array.sty, it might be a good idea to tweak the value of -->
<!-- \extrarowheight as needed to properly center the text within the cells -->
<!-- \caption{An Example of a Table} -->
<!-- \label{table_example} -->
<!-- \centering -->
<!-- % Some packages, such as MDW tools, offer better commands for making tables -->
<!-- % than the plain LaTeX2e tabular which is used here. -->
<!-- \begin{tabular}{|c||c|} -->
<!-- \hline -->
<!-- One & Two\\ -->
<!-- \hline -->
<!-- Three & Four\\ -->
<!-- \hline -->
<!-- \end{tabular} -->
<!-- \end{table} -->

<!-- Note that the IEEE does not put floats in the very first column -->
<!-- - or typically anywhere on the first page for that matter. Also, -->
<!-- in-text middle ("here") positioning is typically not used, but it -->
<!-- is allowed and encouraged for Computer Society conferences (but -->
<!-- not Computer Society journals). Most IEEE journals/conferences use -->
<!-- top floats exclusively.  -->
<!-- Note that, LaTeX2e, unlike IEEE journals/conferences, places -->
<!-- footnotes above bottom floats. This can be corrected via the -->
<!-- \fnbelowfloat command of the stfloats package. -->

### 2019-12-17 survey/survey.tex
survey report

%% template.tex
%% from
%% bare_conf.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE!
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[conference,final,]{IEEEtran}
% Some Computer Society conferences also require the compsoc mode option,
% but others use the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at:
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%

%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

%% BEGIN MY ADDITIONS %%

\usepackage[unicode=true]{hyperref}

\hypersetup{
            pdftitle={Visual Inference Test of the Hexagon Tile Map for Spatial Distributions},
            pdfkeywords={statistics, visual inference, geospatial, population},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}

% Pandoc syntax highlighting

% Pandoc header

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%% END MY ADDITIONS %%

\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Visual Inference Test of the Hexagon Tile Map for Spatial Distributions}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations

\author{

%% ---- classic IEEETrans wide authors' list ----------------
 % -- end affiliation.wide
%% ----------------------------------------------------------

%% ---- classic IEEETrans one column per institution --------
 %% -- end if/affiliation.institution-columnar
%% ----------------------------------------------------------

%% ---- one column per author, classic/default IEEETrans ----
 % -- beg affiliation.author-columnar
  %% -- beg for/affiliation.institution.author
\IEEEauthorblockN{
Stephanie Kobakian
}
\IEEEauthorblockA{Queensland University of Technology\\
Science and Engineering Faculty\\
Brisbane, Australia
\\stephanie.kobakian@qut.edu.au
}
 %% -- end for/affiliation.institution.author
\and
  %% -- beg for/affiliation.institution.author
\IEEEauthorblockN{
Dianne Cook
}
\IEEEauthorblockA{Monash University\\
Econometrics and Business Statistics Faculty\\
Melbourne, Australia
\\dicook@monash.edu
}
 %% -- end for/affiliation.institution.author
 %% -- end for/affiliation.institution
 %% -- end if/affiliation.institution-columnar
%% ----------------------------------------------------------

}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
%
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3},
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The abstract goes here. On multiple lines eventually.
\end{abstract}

% keywords
\begin{IEEEkeywords}
statistics; visual inference; geospatial; population
\end{IEEEkeywords}

% use for special paper notices

% make the title area
\maketitle

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Geo-spatial statistics are often presented on the geographic map base.
To present geo-spatial population statistics, information for
individuals within each geographic region are often aggregated. A
choropleth map is the common display to present aggreagated statistics
for subdivisions of the geography, and they are often used to present
statistics regarding the population. This visualisation method involves
drawing the administrative boundaries and filling them with colour to
communicate the value of the statistic. In Australia, there are sets of
administrative boundaries that define subdivisions of the population at
various granularities.

When presenting population statistics on a geographic map base, the size
of the regions can allow errornous conclusions to be drawn about the
state of the statistic over the entire population. This occurs as large
regions filled with a consistent colour or pettern can draw the
attention of map readers, and small regions are not paid equal
attention. XXX

\hypertarget{background-and-motivation}{%
\section{Background and Motivation}\label{background-and-motivation}}

\hypertarget{australian-cancer-atlas}{%
\subsection{Australian Cancer Atlas}\label{australian-cancer-atlas}}

\begin{itemize}
\tightlist
\item
  Communicating spatial distributions
\item
  Trend over geographic space
\item
  Trend over communities and populations
\end{itemize}

The Australian Cancer Atlas explores the burden of cancer on Australian
communities. There are many cancer types presented, and can be explored
on an individual or aggregate level. The Australian communities examined
are Statistical Areas at Level 2 (SA2) used by the Australian Bureau of
Statistics. Bayesian spatial smoothing has been applied to incorporate
the statistics of neighbouring areas, for both privacy and stability of
the estimates. The statistics that can be mapped are the diagnoses
(Standardised Incidence Rates) and excess deaths for each SA2,
communicated as the difference from the Australian average of the
statistics. The values of the statistic for each are communicated using
a diverging colour scheme. Dark blue represents areas with values much
less than the Australian average, and represents areas much greater than
the Australian average.

\hypertarget{visual-inference}{%
\subsection{Visual Inference}\label{visual-inference}}

\begin{itemize}
\tightlist
\item
  Communicating data through visualisations
\item
  Effective displays for types of data
\item
  Testing the effectiveness
\end{itemize}

Classical statistical inferences involves hypothesis testing, the
process of rejecting a null hypothesis in favour of an alternative. This
approach relies on data, the appropriate distributions and their
assumptions.

\hypertarget{line-up-protocol}{%
\subsection{Line up protocol}\label{line-up-protocol}}

The lineup protocol presents a method for visual inference testing.

\begin{quote}
``In this framework, plots take on the role of test statistics, and
human cognition the role of statistical tests.'' Buja et al. (2009)
\end{quote}

The line up protocol involves placing a ``guilty'' data visualisation in
a lineup of ``innocents''. Where the guilty data set contains structure,
and the innocents are equivalent to a null data set. In a grid of
visualisations, an observer is asked to pick the display that is most
different, if they select the data set containing structure, they have
identified the guilty hidden within the group innocents. The guilty data
is identified as different from the innocent data with probability
\(1/m\), where \(m\) is the number of null plots plus 1 to account
account for the guilty data set. When the guilty data set is chosen, the
null hypothesis that it was innocent is rejected with a \(1/m\) chance
or type I error of being wrong.

The lineup protocol can be used in a variety of tsting scenarios. The
choropleth map is best used for testing spatial structure in a data set.

\hypertarget{population-focussed-displays}{%
\subsection{Population focussed
displays}\label{population-focussed-displays}}

Map creators have the ability to present spatial statistics in
alternative displays that can highlight the population. This work aims
to show that a hexagon tile map display is a viable alternative to the
geographic map base for presenting population statistics. The same data
will be shown on a choropleth map, and on a hexagon tile map. Comparing
the results of participants who see the choropleth to those who see a
hexagon tile map will show that population related distributions are
spotted more frequently in a hexagon tile map display.

\hypertarget{methodology}{%
\section{Methodology}\label{methodology}}

A survey was created to test the effectiveness of the hexagon tile map
display.

Experimental Design: Three trends were tested, in each of the two
displays. For each of the

Line up protocol:

\begin{itemize}
\item
  Experimental design

  \begin{itemize}
  \tightlist
  \item
    The overall structure and operation of the experiment or
    observational experience.
  \item
    The subject populations: The groups studied in the research
    including the size of each group and any features of the subjects
    which may be relevant to the topic being researched.
  \item
    The variables that were changed between groups and the variables
    measured as a result of the changes.
  \item
    The conditions under which the research was undertaken and any
    factors or variations in conditions which may have an impact on the
    results.
  \item
    The methods of data analysis used in order to analyse and collate
    the results.
  \item
    Any limitations of the data collected
  \end{itemize}
\end{itemize}

\hypertarget{results}{%
\section{Results}\label{results}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Type\\
\item
  Trend
\item
  Interaction of type and trend
\item
  Demographics of participants
\end{enumerate}

\hypertarget{probability-of-detection}{%
\subsection{Probability of detection:}\label{probability-of-detection}}

\hypertarget{time-taken}{%
\subsection{Time taken}\label{time-taken}}

\hypertarget{modeling}{%
\subsection{Modeling}\label{modeling}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

The conclusion goes here.

\hypertarget{acknowledgment}{%
\section{Acknowledgment}\label{acknowledgment}}

The authors would like to thank\ldots{}

\hypertarget{bibliography-styles}{%
\section{Bibliography styles}\label{bibliography-styles}}

Here are two sample references: ({\textbf{???}}; {\textbf{???}}).

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-SIEDAMD}{}%
Buja, Andreas, Dianne Cook, Heike Hofmann, Michael Lawrence, Eun-Kyung
Lee, Deborah F. Swayne, and Hadley Wlckham. 2009. ``Statistical
Inference for Exploratory Data Analysis and Model Diagnostics.''
\emph{Philosophical Transactions: Mathematical, Physical and Engineering
Sciences} 367 (1906): 4361--83.
\url{http://www.jstor.org/stable/40485732}.

\end{document}

### 2019-12-17 analysis/analysis.R

@@ -149,9 +149,19 @@ ggplot(d_smry, aes(x=type, y=pdetect, colour = trend)) +
 #ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in")
 
 # Numerical summary
-d_smry %>% spread(type, pdetect) %>%
+diffs <- d_smry %>% spread(type, pdetect) %>%
   mutate(dif = Hexagons - Geography)
 # Need to do the t-tests for these
+
+ggplot(diffs) + 
+  geom_point(aes(Geography, Hexagons, colour = trend)) +
+  geom_abline(slope = 1) +
+  xlim(0,1) + ylim(0,1) + coord_equal()
+
+# Probability of detection using map types
+test_dt <- t.test(pdetect ~ type, data = d_smry, alternative = "less")
+
+test_dt$p.value
 
 # All contributors
 contrib_smry <- d %>% 
@@ -169,9 +179,7 @@ ggplot(contrib_smry, aes(x=type, y=pdetect, colour = trend)) +
   guides(colour = FALSE)
 
 ###########################################################
-# Time taken to answer for each lineup
-# May need to account for first plot shown, that they 
-# may take more time because filling in demographics
+
 d_time <- d %>% 
   group_by(trend, type, location, replicate) %>%
   summarise(m = mean(time_taken), s = sd(time_taken))
@@ -193,11 +201,41 @@ ggsave(filename = "figures/pilot/replicate_change_time.png", plot = repl_plot_t,
 ###########################################################
 # Need to check certainty next
 
+ggplot(d, aes(x = trend, y = certainty)) +
+  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) + geom_jitter(height = 0.1, alpha = 0.4)
+# certainty wasn't affected by the trend
+
+ggplot(d %>% mutate(detect = as_factor(detect)), aes(x = detect, y = certainty)) +
+  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) + geom_jitter(height = 0.1, alpha = 0.4)
+# certainty was slightly higher for correct detections
+
+
+
+
+
 ###########################################################
 # Qualitative analysis of reason
+d <- d %>% 
+  mutate(reason = ifelse(reason =="0.0", "no reason", reason)) 
+
+ggplot(d) + geom_bar(aes(x = reason)) +  
+  facet_grid(trend ~ detect) +  
+  scale_colour_brewer(palette = "Paired") +
[…]

### 2019-12-17 analysis/analysis_fe.Rmd

@@
 library(tidyverse)
-library(readr)
+library(readxl)
 fe <- read_xlsx("experiment-export.xlsx", sheet=2) %>%

### 2019-12-19 survey/survey.Rmd
draft design

@@
 ---
-title: Visual Inference Test of the Hexagon Tile Map for Spatial Distributions
+title: "Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference with crowdsourcing?"
 affiliation:
@@
   # wide: true                  ## one column wide author/affiliation fields
-
   institution:
@@
   On multiple lines eventually.
-
+dev: png
 bibliography: mybibfile.bib
@@
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(
+  echo = FALSE,
+  warning = FALSE,
+  error = FALSE, 
+  message = FALSE)
+```
 
@@
 To present geo-spatial population statistics, information for individuals within each geographic region are often aggregated.
-A choropleth map is the common display to present aggreagated statistics for subdivisions of the geography, and they are often used to present statistics regarding the population.
+A choropleth map is the common display to present aggreagated statistics for geographic units, and they are often used to present statistics regarding the population.
 This visualisation method involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic. 
-In Australia, there are sets of administrative boundaries that define subdivisions of the population at various granularities.
+In Australia, there are many sets of administrative boundaries that define subdivisions of the population at various granularities.
 
 When presenting population statistics on a geographic map base, the size of the regions can allow errornous conclusions to be drawn about the state of the statistic over the entire population.
-This occurs as large regions filled with a consistent colour or pettern can draw the attention of map readers, and small regions are not paid equal attention. XXX
+This occurs as large regions filled with a consistent colour or pettern can draw the attention of map readers, and small regions are not paid equal attention.
 
@@
 
-The Australian Cancer Atlas explores the burden of cancer on Australian communities. There are many cancer types presented, and can be explored on an individual or aggregate level. 
-The Australian communities examined are Statistical Areas at Level 2 (SA2) used by the Australian Bureau of Statistics.
+The Australian Cancer Atlas explores the burden of cancer on Australian communities. There are many cancer types presented, and they can be explored on an individual or aggregate level. 
+The Australian communities examined are Statistical Areas at Level 2 (SA2)[@abs2016] used by the Australian Bureau of Statistics.
 Bayesian spatial smoothing has been applied to incorporate the statistics of neighbouring areas, for both privacy and stability of the estimates.
@@
 
-## Population focussed displays
-
-Map creators have the ability to present spatial statistics in alternative displays that can highlight the population.
-This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
-The same data will be shown on a choropleth map, and on a hexagon tile map.
-Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.
-
-Methodology
-============
-
-A survey was created to test the effectiveness of the hexagon tile map display.
-
-Experimental Design:
-Three trends were tested, in each of the two displays.
-For each of the
-
-Line up protocol:
-
 <!--
@@
 
-- Experimental design
+## Population focussed displays
 
-  - The overall structure and operation of the experiment or observational experience.
-  - The subject populations: The groups studied in the research including the size of each group and any features of the subjects which may be relevant to the topic being researched. 
-  - The  variables that were changed between groups and the variables measured as a result of the changes.
-  - The conditions under which the research was undertaken and any factors or variations in conditions which may have an impact on the results.
-  - The methods of data analysis used in order to analyse and collate the results. 
-  - Any limitations of the data collected
+Map creators have the ability to present spatial statistics in alternative displays that can highlight the population.
+This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
+The same data were shown on a choropleth map, and on a hexagon tile map.
+Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.
+
+Study Design
+============
+
+## Aims
+
+This study aims to answer several questions around the presentation of spatial distributions:
+
+1. Are spatial disease trends, that impact highly populated small areas, detected with higher accuracy when viewed in a hexagon tile map display?
+
+2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when
+using a hexagon tile map display?
+3. Do people find hexagon tile maps more difficult to read than choropleth maps?
+4. Are the reasons for choosing a plot different depending on the type of display?
+5. Does an Australian resident find the choropleth map easier to read than the hexagon tile map?
+
+## Methodology
+
+A survey was created to test the effectiveness of the hexagon tile map display.
+
+The online crowdsource platform Figure-Eight was used to recruit participants. 
+A line up protocol was implemented to arrange 12 maps in each display. 
+Individual displays were created by a combination of plot type, and spatial trend model.
+
+The researchers contrasted the different plot designs, as hexagon tilemap
+and geography in the lineups were created using the same data, and same null positions within the lineup.
+
+The researchers compared the length of time taken, and the accuracy of the participants choices.
+
+## The participants
+
+There were 95 participants in the study. 
+We recruited participants using the Figure-Eight crowd source platform by advertising this survey to participants that fulfilled the following crtieria:
+
+• level 2 or level 3 on the Figure-Eight Platform.
+• at least 18 years old
+
+Participants then selected our task from the list of tasks available to them.
+
+## The variables being manipulated and measured?
+
+The variables that were changed between groups were the type of plot shown and the trend model.
+
+Each participant was randomly allocated to either group A or group B when they begun the survey. This resulted in 42 participants allocated to group A, and 53 participants allocated to group B.
+
+The levels of the factors measured in the experiment were:
+• Plot type: *Geography, Hexagons*
+• Trend: *Locations in two population centres, Locations in multiple population centres, South-East to North-West*
+
+Factor combinations examined by each participant amount to 6 (2x3) lineup displays.
+A participant did see the same data for both plot types. Four simulated sets of data were generated for each treatment.
+This will generate 24 lineups (12 were geographic maps, and 12 were hexagon tile maps). Participants will evaluate 12 lineups, 6 of each plot type. Appendix A shows the experimental design visually.
+For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants.
+
+The variables measured as a result of the changes were the probability of detection each display and the time taken to submit responses.
+To measure the accuracy of the detections, the plot chosen for each lineup evaluated was compared to the position of the real spatial trend plot in the lineup.
+A correct result occurs when the chosen plot matches the position of the real plot, this was recorded in an additional binary variable; 1 = correct; 0 = incorrect.
+High efficiency occurs when a small amount of time is taken to evaluate each lineup.
+This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.
+
+## Participant training
+Each participant saw three test displays orienting them to the task. Participants proceeded to the survey, this involved evaluating 12 displays.
+
+## Experiment procudure and data collection
+The participant submitted demographic questions and provided consent before evaluating the lineups.
+
+Demographics were collected regarding the study participants:
+• Gender (female / male / other),
+• Degree education level achieved (high school / bachelors / masters / doctorate / other),
+• Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
+• Lived at least for one year in Australia (Yes / No )
+
+Participants then moved to the evaulation phase.
+The set of images differed for group A and group B.
+After being allocated each individual was shown the 12 displays in randomised order.
+
+Three questions were asked regarding each display:
+- Plot choice
+- Reason
+- Difficulty
+
+After completing the 12 evaluations, the participants were asked to submit their responses.
+
+Data was collected through a web application containing the online survey.
+Each participant used the internet to access the survey.
+
+The data collection took place using a secure link between the survey web application and the googlesheet used to store results.
+The application would first connect to the googlesheet using the googlesheets [@sheets] R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
+
+## The methods of data analysis used
+The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R [@RCore].
+
+For each of the 12 lineup displays the researchers calculated:
+• accuracy: the proportion of subjects who detected the data plot
+• efficiency: average time taken to respond
+
+### Visualisations
+Side-by-side dot plots were made of accuracy (efficiency) against plot type, facetted by trend model type.
+
+Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.
+
+Plots will be made in R (R Core Team 2019), with the ggplot2 package (Wickham 2016).
+
+### Modeling
+
+The results will be analysed using a generalised linear model, with a subject random effect.
+There will be two main effects: plot type and trend model, which gives the fixed effects part of the model to be
+
+$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3$$
+
+where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the plot type effect, $\delta_j$ is the trend model effect.
+We are allowing for an interaction between plot type and trend model.
+Because the response is binary, a logistic model is used.
+
+A similar model will be constructed for the efficiency, using a log time, and normal errors.
+
+The feedback and demographic variables will possibly be incorporated as covariates.
+
+Computation will be done using R [@RCore], with the `lme4` package [@lme4].
+
+## Limitations of the data collection
+
+This required internet connection for participants to access the survey
+
+Ethics approval for the online survey was granted by QUT’s Ethics Committee (Ethics Application Number: 1900000991).
+All applicants provided informed consent in line with QUT regulations prior to participating in this research.
 
@@
 1. Demographics of participants
+
+```{r data}
+###############################################################################
+
+# Load Libraries
+library(tidyverse)
+library(lubridate)
+library(broom)
+library(readxl)
+library(lme4)
+library(ggthemes)
+
+invthm <- theme(
+  panel.background = element_rect(fill = "transparent", colour = NA), 
+  plot.background = element_rect(fill = "transparent", colour = NA),
+  legend.background = element_rect(fill = "transparent", colour = NA),
+  legend.key = element_rect(fill = "transparent", colour = NA),
+  text = element_text(colour = "white", size = 20),
+  axis.text = element_text(colour = "white", size = 20)
+)
+
+# Downloaded data
+d <- read_xlsx("../experiment-export.xlsx", sheet=2) %>%
+  filter(!is.na(contributor)) %>%
+  mutate(contributor = factor(contributor))
+```
+
+```{r}
+###############################################################################
+# Check data set 
+# d %>% count(contributor, sort=TRUE)
+# Need to clean multiple entries, 48, 24
+# remove duplicated entries due to submit button
+d <- d %>% group_by(group, contributor, image_name) %>%
+  slice(1) %>% ungroup() %>% 
+  arrange(group, contributor, plot_order)
+
+# Now remove contributors who did not provide answers to most questions
+keep <- d %>% count(contributor, sort = TRUE) %>% filter(n > 10)
+d <- d %>% 
+  filter(contributor %in% keep$contributor) %>%
+  filter(contributor != "1234567890")
+
+n_contributors <- d %>% count(contributor, sort=TRUE) %>% summarise(n_contributors = length(contributor))
+```
+The survey responses from participants were kept only if the participant submitted answers for all 12 displays. This resulted in `r n_contributors` surveyed.
+
+```{r}
+###############################################################################
+# Augment
+# add data replication number
+#d %>% count(image_name) %>% print(n=24)
+# image code <--> rep
+replicate <- tibble(image_name = c("aus_cities_12_geo.png", "aus_cities_12_hex.png", 
+                                   "aus_cities_3_geo.png", "aus_cities_3_hex.png",
+                                   "aus_cities_4_geo.png", "aus_cities_4_hex.png",
+                                   "aus_cities_9_geo.png", "aus_cities_9_hex.png",
+                                   "aus_nwse_2_geo.png", "aus_nwse_2_hex.png",
+                                   "aus_nwse_3_geo.png", "aus_nwse_3_hex.png",
+                                   "aus_nwse_5_geo.png", "aus_nwse_5_hex.png",
+                                   "aus_nwse_6_geo.png", "aus_nwse_6_hex.png",
+                                   "aus_three_12_geo.png", "aus_three_12_hex.png",
+                                   "aus_three_5_geo.png", "aus_three_5_hex.png",
+                                   "aus_three_8_geo.png", "aus_three_8_hex.png",
+                                   "aus_three_9_geo.png", "aus_three_9_hex.png"),
+                    replicate = c(1, 1, 2, 2, 3, 3, 4, 4, 
+                                  1, 1, 2, 2, 3, 3, 4, 4,
+                                  1, 1, 2, 2, 3, 3, 4, 4))
+# Add rep info to data
+d <- d %>% left_join(., replicate, by = "image_name")
+#d %>% count(group, image_name, sort=TRUE)`
+
+###############################################################################
+# Tidy for analysis
+d <- d %>% 
+  separate(image_name, c("nothing", "trend", "location", "type"), remove=FALSE) %>%
+  select(-nothing) %>%
+  mutate(location = as.numeric(location), 
+    # detect measures the accuracy of the choice
+         detect = ifelse(location == choice, 1, 0)) %>% 
+  mutate(trend = case_when(
+    trend == "cities" ~ "all cities",
+    trend == "three" ~ "three cities",
+    trend == "nwse" ~ "NW-SE")) %>% 
+  mutate(trend = fct_relevel(trend, "NW-SE","three cities","all cities")) %>% 
+  mutate(type = case_when(
+    type == "hex" ~"Hexagons",
+    TRUE~"Geography"
+  ))
+
+plots <- d %>% group_by(group, trend, type, location) %>%
+  # pdetect measures the aggregated accuracy of the choices
+  summarise(pdetect = length(detect[detect == 1])/length(detect))
+
+plots %>% ggplot(aes(x = group, y = pdetect)) + 
+  geom_boxplot() + 
+  geom_jitter(width = 0.1) +
+  ylim(c(0,1))
+
+```
+
+```{r}
+# Check contributor performance
+contribs <- d %>% group_by(group, contributor) %>%
+  # pdetect measures the aggregated accuracy of the choices
+  summarise(pdetect = length(detect[detect == 1])/length(detect))
+
+# contribs %>% count(group)
+# contribs %>% arrange(pdetect)
+
+```
+
+```{r}
+# Plot performance
+contribs %>% ggplot(aes(x = group, y = pdetect, label = contributor)) + 
+  geom_boxplot() + 
+  geom_jitter(width = 0.1) +
+  ylim(c(0,1))
+```
+
+```{r}
+
+# Create one record for each contributor, to examine demographics
+dem_contribs <- d %>%
+  group_by(contributor) %>%
+  slice(1) %>% ungroup()
+
+```
+
+```{r}
+
+###############################################################################
+# Demographics of contributors
+dem_contribs %>% count(gender)
+dem_contribs %>% count(age)
+dem_contribs %>% count(education)
+dem_contribs %>% count(australia)
+
+```
+
+```{r}
+
+###############################################################################
+# Detectability rate for each lineup (image)
+d_smry <- d %>% group_by(trend, type, location, replicate) %>%
+  # pdetect measures the aggregated accuracy of the choices
+  summarise(pdetect = length(detect[detect == 1])/length(detect)) %>%
+  ungroup()
+
+# Plot summary
+ggplot(d_smry, aes(x=type, y=pdetect, colour = trend)) +
+  geom_point(size = 3) +  
+  geom_line(size = 1, aes(group = replicate)) +  
+  facet_wrap(~trend) +  
+  scale_colour_brewer(palette = "Paired") +
+  xlab("Type of areas visualised") +
+  ylab("Detection rate") + 
+  ylim(0,1) + #invthm + 
+  guides(colour = FALSE)
+
+```
+11 of the 12 real distribution plots were found more often in the hexagon display.
+This was better than expected. As even geographic distributions were spotted in the hexagon lineup.
+
+```{r}
+##ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in", bg = "transparent")
+##ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in")
+
+# Numerical summary
+diffs <- d_smry %>% spread(type, pdetect) %>%
+  mutate(dif = Hexagons - Geography)
+# Need to do the t-tests for these
+
+ggplot(diffs) + 
+  geom_point(aes(Geography, Hexagons, colour = trend)) +
+  geom_abline(slope = 1) +
+  xlim(0,1) + ylim(0,1) + coord_equal()
+
+# Probability of detection using map types
+test_dt <- t.test(pdetect ~ type, data = d_smry, alternative = "less")
+
+test_dt$p.value
+
+```
+
+```{r}
+
+d_time <- d %>% 
+  group_by(trend, type, location, replicate) %>%
+  summarise(m = mean(time_taken), s = sd(time_taken))
+#d_time %>% print(n=24)
+
+ggplot(d, aes(x=time_taken, fill = trend)) +
+  geom_density(alpha = 0.4)
+
+# Visual summary
+ggplot(d_time, aes(x=type, y=m, colour = trend)) +
+  geom_point(size = 3) +  
+  geom_line(size = 1, aes(group = replicate)) +  
+  facet_wrap(~trend) +  
+  scale_colour_brewer(palette = "Paired") +
+  xlab("Type of areas visualised") +
+  ylab("Average time taken") + 
+  guides(colour = FALSE)
+
+#ggsave(filename = "figures/pilot/replicate_change_time.png", plot = repl_plot_t, device = "png", dpi = 300, width = 12, height = 8, units = "in", bg = "transparent")
+##ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in")
+
+```
+
+```{r}
+
+###########################################################
+# Need to check certainty next
+
+ggplot(d, aes(x = trend, y = certainty)) +
+  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75))
+# certainty wasn't affected by the trend
+
+ggplot(d %>% mutate(detect = as_factor(detect)), aes(x = detect, y = certainty)) +
+  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75))
+# certainty was slightly higher for correct detections
+
+```
+
+```{r}
+###########################################################
+# Qualitative analysis of reason
+d <- d %>% 
+  mutate(reason = ifelse(reason =="0.0", "no reason", reason))
+
+ggplot(d) + geom_bar(aes(x = reason)) +  
+  facet_grid(trend ~ detect) +  
+  scale_colour_brewer(palette = "Paired") +
+  xlab("Type of areas visualised") + 
+  guides(colour = FALSE) + coord_flip()
+
+```
 
@@
 ===================
-
-Here are two sample references: @Feynman1963118 [@Dirac1953888].
 
@@
 <!-- \includegraphics[width=2.5in]{myfigure} -->
-<!-- where an .eps filename suffix will be assumed under latex,  -->
-<!-- and a .pdf suffix will be assumed for pdflatex; or what has been declared -->
+<!-- where an .eps filename suffix were assumed under latex,  -->
+<!-- and a .pdf suffix were assumed for pdflatex; or what has been declared -->
 <!-- via \DeclareGraphicsExtensions. -->

### 2019-12-19 survey/survey.tex
draft design

@@
 
+\usepackage{graphicx}
+% We will generate all images so they have a width \maxwidth. This means
+% that they will get their normal width if they fit onto the page, but
+% are scaled down if they would overflow the margins.
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
+\else\Gin@nat@width\fi}
+\makeatother
+\let\Oldincludegraphics\includegraphics
+\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
+
 \usepackage[unicode=true]{hyperref}
@@
 choropleth map is the common display to present aggreagated statistics
-for subdivisions of the geography, and they are often used to present
-statistics regarding the population. This visualisation method involves
-drawing the administrative boundaries and filling them with colour to
-communicate the value of the statistic. In Australia, there are sets of
+for geographic units, and they are often used to present statistics
+regarding the population. This visualisation method involves drawing the
+administrative boundaries and filling them with colour to communicate
+the value of the statistic. In Australia, there are many sets of
 administrative boundaries that define subdivisions of the population at
@@
 attention of map readers, and small regions are not paid equal
-attention. XXX
+attention.
 
@@
 The Australian Cancer Atlas explores the burden of cancer on Australian
-communities. There are many cancer types presented, and can be explored
-on an individual or aggregate level. The Australian communities examined
-are Statistical Areas at Level 2 (SA2) used by the Australian Bureau of
+communities. There are many cancer types presented, and they can be
+explored on an individual or aggregate level. The Australian communities
+examined are Statistical Areas at Level 2 (SA2)(``Australian Statistical
+Geography Standard (ASGS)'' 2018) used by the Australian Bureau of
 Statistics. Bayesian spatial smoothing has been applied to incorporate
@@
 geographic map base for presenting population statistics. The same data
-will be shown on a choropleth map, and on a hexagon tile map. Comparing
-the results of participants who see the choropleth to those who see a
+were shown on a choropleth map, and on a hexagon tile map. Comparing the
+results of participants who see the choropleth to those who see a
 hexagon tile map will show that population related distributions are
@@
 
+\hypertarget{study-design}{%
+\section{Study Design}\label{study-design}}
+
+\hypertarget{aims}{%
+\subsection{Aims}\label{aims}}
+
+This study aims to answer several questions around the presentation of
+spatial distributions:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  Are spatial disease trends, that impact highly populated small areas,
+  detected with higher accuracy when viewed in a hexagon tile map
+  display?
+\item
+  Are people faster in detecting spatial disease trends, that impact
+  highly populated small areas, when using a hexagon tile map display?
+\item
+  Do people find hexagon tile maps more difficult to read than
+  choropleth maps?
+\item
+  Are the reasons for choosing a plot different depending on the type of
+  display?
+\item
+  Does an Australian resident find the choropleth map easier to read
+  than the hexagon tile map?
+\end{enumerate}
+
 \hypertarget{methodology}{%
-\section{Methodology}\label{methodology}}
+\subsection{Methodology}\label{methodology}}
 
@@
 
-Experimental Design: Three trends were tested, in each of the two
-displays. For each of the
+The online crowdsource platform Figure-Eight was used to recruit
+participants. A line up protocol was implemented to arrange 12 maps in
+each display. Individual displays were created by a combination of plot
+type, and spatial trend model.
 
-Line up protocol:
+The researchers contrasted the different plot designs, as hexagon
+tilemap and geography in the lineups were created using the same data,
+and same null positions within the lineup.
 
-\begin{itemize}
-\item
-  Experimental design
+The researchers compared the length of time taken, and the accuracy of
+the participants choices.
 
-  \begin{itemize}
-  \tightlist
-  \item
-    The overall structure and operation of the experiment or
-    observational experience.
-  \item
-    The subject populations: The groups studied in the research
-    including the size of each group and any features of the subjects
-    which may be relevant to the topic being researched.
-  \item
-    The variables that were changed between groups and the variables
-    measured as a result of the changes.
-  \item
-    The conditions under which the research was undertaken and any
-    factors or variations in conditions which may have an impact on the
-    results.
-  \item
-    The methods of data analysis used in order to analyse and collate
-    the results.
-  \item
-    Any limitations of the data collected
-  \end{itemize}
-\end{itemize}
+\hypertarget{the-participants}{%
+\subsection{The participants}\label{the-participants}}
+
+There were 95 participants in the study. We recruited participants using
+the Figure-Eight crowd source platform by advertising this survey to
+participants that fulfilled the following crtieria:
+
+• level 2 or level 3 on the Figure-Eight Platform. • at least 18 years
+old
+
+Participants then selected our task from the list of tasks available to
+them.
+
+\hypertarget{the-variables-being-manipulated-and-measured}{%
+\subsection{The variables being manipulated and
+measured?}\label{the-variables-being-manipulated-and-measured}}
+
+The variables that were changed between groups were the type of plot
+shown and the trend model.
+
+Each participant was randomly allocated to either group A or group B
+when they begun the survey. This resulted in 42 participants allocated
+to group A, and 53 participants allocated to group B.
+
+The levels of the factors measured in the experiment were: • Plot type:
+\emph{Geography, Hexagons} • Trend: \emph{Locations in two population
+centres, Locations in multiple population centres, South-East to
+North-West}
+
+Factor combinations examined by each participant amount to 6 (2x3)
+lineup displays. A participant did see the same data for both plot
+types. Four simulated sets of data were generated for each treatment.
+This will generate 24 lineups (12 were geographic maps, and 12 were
+hexagon tile maps). Participants will evaluate 12 lineups, 6 of each
+plot type. Appendix A shows the experimental design visually. For each
+of the six geographic displays and six hexagon displays, two of each
+trend model were shown to participants.
+
+The variables measured as a result of the changes were the probability
+of detection each display and the time taken to submit responses. To
+measure the accuracy of the detections, the plot chosen for each lineup
+evaluated was compared to the position of the real spatial trend plot in
+the lineup. A correct result occurs when the chosen plot matches the
+position of the real plot, this was recorded in an additional binary
+variable; 1 = correct; 0 = incorrect. High efficiency occurs when a
+small amount of time is taken to evaluate each lineup. This will be
+measured as the numeric variable measuring the length of time taken to
+submit the answers to the evaluation of each line up.
+
+\hypertarget{participant-training}{%
+\subsection{Participant training}\label{participant-training}}
+
+Each participant saw three test displays orienting them to the task.
+Participants proceeded to the survey, this involved evaluating 12
+displays.
+
+\hypertarget{experiment-procudure-and-data-collection}{%
+\subsection{Experiment procudure and data
+collection}\label{experiment-procudure-and-data-collection}}
+
+The participant submitted demographic questions and provided consent
+before evaluating the lineups.
+
+Demographics were collected regarding the study participants: • Gender
+(female / male / other), • Degree education level achieved (high school
+/ bachelors / masters / doctorate / other), • Age range (18-24 / 25-34 /
+35-44 / 45-54 / 55+ / other) • Lived at least for one year in Australia
+(Yes / No )
+
+Participants then moved to the evaulation phase. The set of images
+differed for group A and group B. After being allocated each individual
+was shown the 12 displays in randomised order.
+
+Three questions were asked regarding each display: - Plot choice -
+Reason - Difficulty
+
+After completing the 12 evaluations, the participants were asked to
+submit their responses.
+
+Data was collected through a web application containing the online
+survey. Each participant used the internet to access the survey.
+
+The data collection took place using a secure link between the survey
+web application and the googlesheet used to store results. The
+application would first connect to the googlesheet using the
+googlesheets (Bryan and Zhao 2018) R package, and interacted again at
+the completion of the survey by adding the participant's responses to
+the 12 displays as 12 rows of data in the googlesheet.
+
+\hypertarget{the-methods-of-data-analysis-used}{%
+\subsection{The methods of data analysis
+used}\label{the-methods-of-data-analysis-used}}
+
+The data analysis methods used in order to analyse and collate the
+results included downloading the survey submissions and opening them
+into the analysis software R ({\textbf{???}}).
+
+For each of the 12 lineup displays the researchers calculated: •
+accuracy: the proportion of subjects who detected the data plot •
+efficiency: average time taken to respond
+
+\hypertarget{visualisations}{%
+\subsubsection{Visualisations}\label{visualisations}}
+
+Side-by-side dot plots were made of accuracy (efficiency) against plot
+type, facetted by trend model type.
+
+Similar plots were made of the feedback and demographic variables -
+reason for choice, reported difficulty, gender, age, education, having
+lived in Australia - against the design variables.
+
+Plots will be made in R (R Core Team 2019), with the ggplot2 package
+(Wickham 2016).
+
+\hypertarget{modeling}{%
+\subsubsection{Modeling}\label{modeling}}
+
+The results will be analysed using a generalised linear model, with a
+subject random effect. There will be two main effects: plot type and
+trend model, which gives the fixed effects part of the model to be
+
+\[\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3\]
+
+where \(y_{ij} = 0, 1\) whether the subject detected the data plot,
+\(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the plot type effect,
+\(\delta_j\) is the trend model effect. We are allowing for an
+interaction between plot type and trend model. Because the response is
+binary, a logistic model is used.
+
+A similar model will be constructed for the efficiency, using a log
+time, and normal errors.
+
+The feedback and demographic variables will possibly be incorporated as
+covariates.
+
+Computation will be done using R ({\textbf{???}}), with the
+\texttt{lme4} package ({\textbf{???}}).
+
+\hypertarget{limitations-of-the-data-collection}{%
+\subsection{Limitations of the data
+collection}\label{limitations-of-the-data-collection}}
+
+This required internet connection for participants to access the survey
+
+Ethics approval for the online survey was granted by QUT's Ethics
+Committee (Ethics Application Number: 1900000991). All applicants
+provided informed consent in line with QUT regulations prior to
+participating in this research.
 
@@
 
+The survey responses from participants were kept only if the participant
+submitted answers for all 12 displays. This resulted in 95 surveyed.
+
+\includegraphics{survey_files/figure-latex/unnamed-chunk-2-1.pdf}
+
+\includegraphics{survey_files/figure-latex/unnamed-chunk-4-1.pdf}
+
+\begin{verbatim}
+## # A tibble: 2 x 2
+##   gender     n
+##   <chr>  <int>
+## 1 He        70
+## 2 She       25
+\end{verbatim}
+
+\begin{verbatim}
+## # A tibble: 6 x 2
+##   age         n
+##   <chr>   <int>
+## 1 18 - 24    15
+## 2 25 - 34    37
+## 3 35 - 44    23
+## 4 45 - 54    11
+## 5 55+         6
+## 6 NA          3
+\end{verbatim}
+
+\begin{verbatim}
+## # A tibble: 3 x 2
+##   education       n
+##   <chr>       <int>
+## 1 Bach           56
+## 2 High School    25
+## 3 Masters        14
+\end{verbatim}
+
+\begin{verbatim}
+## # A tibble: 2 x 2
+##   australia     n
+##   <chr>     <int>
+## 1 No           93
+## 2 Yes           2
+\end{verbatim}
+
+\includegraphics{survey_files/figure-latex/unnamed-chunk-7-1.pdf} 11 of
+the 12 real distribution plots were found more often in the hexagon
+display. This was better than expected. As even geographic distributions
+were spotted in the hexagon lineup.
+
+\includegraphics{survey_files/figure-latex/unnamed-chunk-8-1.pdf}
+
+\begin{verbatim}
+## [1] 0.004079185
+\end{verbatim}
+
+\includegraphics{survey_files/figure-latex/unnamed-chunk-9-1.pdf}
+\includegraphics{survey_files/figure-latex/unnamed-chunk-9-2.pdf}
+
+\includegraphics{survey_files/figure-latex/unnamed-chunk-10-1.pdf}
+\includegraphics{survey_files/figure-latex/unnamed-chunk-10-2.pdf}
+
+\includegraphics{survey_files/figure-latex/unnamed-chunk-11-1.pdf}
+
 \hypertarget{probability-of-detection}{%
@@
 
-\hypertarget{modeling}{%
-\subsection{Modeling}\label{modeling}}
+\hypertarget{modeling-1}{%
+\subsection{Modeling}\label{modeling-1}}
 
@@
 
-Here are two sample references: ({\textbf{???}}; {\textbf{???}}).
-
 \newpage
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-abs2016}{}%
+``Australian Statistical Geography Standard (ASGS).'' 2018.
+\emph{Australian Bureau of Statistics}. Australian Government.
+\href{\%7Bhttps://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)\%7D}{\{https://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian   Statistical Geography Standard (ASGS)\}}.
+
+\leavevmode\hypertarget{ref-sheets}{}%
+Bryan, Jennifer, and Joanna Zhao. 2018. \emph{Googlesheets: Manage
+Google Spreadsheets from R}.
+\url{https://CRAN.R-project.org/package=googlesheets}.
+
 \leavevmode\hypertarget{ref-SIEDAMD}{}%

### 2019-12-19 survey/survey.Rmd
small change?

@@
 # Downloaded data
-d <- read_xlsx("../experiment-export.xlsx", sheet=2) %>%
+d <- read_xlsx("data/experiment-export.xlsx", sheet=2) %>%
   filter(!is.na(contributor)) %>%

### 2019-12-19 survey/survey.tex
small change?

@@
 \hypersetup{
-            pdftitle={Visual Inference Test of the Hexagon Tile Map for Spatial Distributions},
+            pdftitle={Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference with crowdsourcing?},
             pdfkeywords={statistics, visual inference, geospatial, population},
@@
 % Do not put math or special symbols in the title.
-\title{Visual Inference Test of the Hexagon Tile Map for Spatial Distributions}
+\title{Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison
+using visual inference with crowdsourcing?}
 
@@
 \emph{Australian Bureau of Statistics}. Australian Government.
-\href{\%7Bhttps://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)\%7D}{\{https://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian   Statistical Geography Standard (ASGS)\}}.
+\url{\%7Bhttps://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)\%7D}.
 

### 2019-12-19 survey/survey.Rmd
aims clarified

--- 2019-12-19 survey/survey.Rmd
@@
 
-## Aims
-
 This study aims to answer several questions around the presentation of spatial distributions:
@@
 using a hexagon tile map display?
-3. Do people find hexagon tile maps more difficult to read than choropleth maps?
-4. Are the reasons for choosing a plot different depending on the type of display?
-5. Does an Australian resident find the choropleth map easier to read than the hexagon tile map?
 
-## Methodology
+additional considerations
+ Do people find hexagon tile maps more difficult to read than choropleth maps?
+ Are the reasons for choosing a plot different depending on the type of display?
+
+## Experimental design
 
@@
 
-## The variables being manipulated and measured?
+## The variables being manipulated and measured
 
@@
 This required internet connection for participants to access the survey
-
-Ethics approval for the online survey was granted by QUT’s Ethics Committee (Ethics Application Number: 1900000991).
-All applicants provided informed consent in line with QUT regulations prior to participating in this research.
 
@@
 
+Ethics approval for the online survey was granted by QUT’s Ethics Committee (Ethics Application Number: 1900000991).
+All applicants provided informed consent in line with QUT regulations prior to participating in this research.
+
 Bibliography styles

### 2019-12-25 paper/paper.Rmd
paper

---
title: "Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference"
affiliation:
  author-columnar: true         ## one column per author
  #institution-columnar: true  ## one column per institution (multiple autors eventually)
  # wide: true                  ## one column wide author/affiliation fields
  institution:
    - name: Queensland University of Technology
      department: Science and Engineering Faculty
      location: Brisbane, Australia
      email: stephanie.kobakian@qut.edu.au
      mark: 1
      author:
        - name: Stephanie Kobakian
    - name: Monash University
      department: Econometrics and Business Statistics Faculty
      location: Melbourne, Australia
      email: dicook@monash.edu
      mark: 1
      author:
        - name: Dianne Cook
keywords: ["statistics", "visual inference", "geospatial", "population"]
abstract: |
  The abstract goes here.
  On multiple lines eventually.
dev: png
bibliography: mybibfile.bib
output: rticles::ieee_article
editor_options: 
  chunk_output_type: inline
link-citations: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  error = FALSE, 
  message = FALSE)
```

Introduction
=============
<!-- no \IEEEPARstart -->
<!-- (should never be an issue) -->

<!-- General: comparison of displays, motivate hexagon tile map, enough info to motivate aims -->
<!-- geographies on choropleth -->
Geospatial statistics are often presented on the geographic map base. 
A choropleth map is the common display to present aggreagated statistics for geographic units, and they are often used to present statistics regarding the population. 
Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic. 
In Australia, there are sets of administrative boundaries that define subdivisions of the population at various granularities.
The set of Australia statistical areas presents an example of a heterogrenous distribution of area.
The rural communicates on a much larger geographic space than small inner city communities.
This has the negative effect of incorrectly showing the spatial distribution of the statistic, especially when a spatial distribution is related to the size of the areas, or the population density.

An alternative display can also be used to effectively communicate a spatial distribution for a set of heterogeneous areas.
Viewers of spatial distributions may come to incorrect conclusions.

Motivation
=============

<!-- Find a new display for the Cancer Atlas -->

## Australian Cancer Atlas

The Australian Cancer Atlas explores the burden of cancer on Australian communities. There are many cancer types presented, and they can be explored on an individual or aggregate level. 
The Australian communities are examined at the Statistical Areas at Level 2 (SA2)[@abs2016] used by the Australian Bureau of Statistics.
Bayesian spatial smoothing has been applied to incorporate the statistics of neighbouring areas, for both privacy and stability of the estimates.
The statistics that can be mapped are the diagnoses (Standardised Incidence Rates) and excess deaths for each SA2, communicated as the difference from the Australian average of the statistics.
The values of the statistic for each are communicated using a diverging colour scheme.

The Australian Cancer Atlas communicates the trends in the distributions of cancer over geographic space. It uses a choropleth map display and diverging colour scheme to draw attention to relationships between neighbouring areas.

Background
=============

## Methodology

Spatial visualisations
 - Choropleth
However, the issue of using a choropleth map base becomes obvious when considering the distributions.
 Position is extremely important for analysis of a visualisation.

## Population focussed displays

Map creators have the ability to present spatial statistics in alternative displays that can highlight the population.
This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
The same data were shown on a choropleth map, and on a hexagon tile map.
Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.

When presenting population statistics on a geographic map base, the size of the regions can allow errornous conclusions to be drawn about the state of the statistic over the entire population.
This occurs as large regions filled with a consistent colour or pettern can draw the attention of map readers, and small regions are not paid equal attention.
A choropleth map is not the only display that can be used for presenting geospatial data. 
Alternative maps include various cartograms, and tesselated tile maps. They allow other variables to be included in the display to highlight the staistical values of various geographic areas.

<!-- Cartogram -->

<!-- Why not a cartogram-->

<!-- Tesselated tile gram & hexagon tile map-->

<!-- Specific problem for Australia -->

<!-- Figure Choro and Hex tile for Aus-->

## Visual Inference
- Communicating data through visualisations
- Effective displays for types of data
- Protocol for testing the effectiveness

Classical statistical inference involves hypothesis testing, the process of rejecting a null hypothesis in favour of an alternative. This approach relies on data, the appropriate distributions and their assumptions. 
Visual inference null hypothesis: independence in the variables (absence of all features), alternative hypothesis: Relationship between the variables (presence of some feature).
<!--
GTPCCD
In visual inference, data plots are considered to be test statistics, and these are compared with plots of data generated from a null hypothesis using a lineup

The null hypothesis underlying a
lineup is that there is no real structure visible in the data plot, that any
patterns seen are consistent with randomness, or from a known model.
If the null hypothesis is true then the plot of the data will not be distinguishable
from the plots of null data.

Different lineups are created, using the same data, same null plots and
positions within the lineup, but different plot designs.

Comparing how
long viewers take and how accurately they report the feature of interest
will assess which design is better for the task.
-->

<!--
A null dataset
is a sample from the null distribution, i.e. an example of an innocent
dataset, and a null plot is a plot of a null dataset, showing what an
innocent might look like.

testing can be adapted to work visually instead of numerically.[@GIIV]
Graphical Inference for Infovis
Chloropleth maps Is there a spatial trend?

Simulation. We might be interested in a more specific set of hypothesis:
does time increase linearly with distance from target?
Does accuracy decrease exponentially as number of distractors
increases? In those cases we have a probabilistic model and we
can generate null data sets by sampling from the distribution implied
by the model. This approach is used in Section 4.2.
-->

The lineup protocol is used for visual inference testing.
1. simulate null plots 
2. Insert data with structure into a random location
3. Ask uninvolved person to select the most different plot
4. If location is chosen correctly, the existence of a feature is significant at $\alpha = 1/N$.

> "In this framework, plots take on the role of test statistics, and human cognition the role of statistical tests." @SIEDAMD

The line up protocol involves placing a "guilty" data visualisation in a lineup of "innocents". Where the guilty data set contains structure, and the innocents are equivalent to a null data set. 
In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the group innocents.
The guilty data is identified as different from the innocent data with probability $1/m$, where $m$ is the number of null plots plus 1 to account account for the guilty data set. When the guilty data set is chosen, the null hypothesis that it was innocent is rejected with a $1/m$ chance or type I error of being wrong.

The lineup protocol can be used in a variety of testing scenarios. The choropleth map is best used for testing spatial structure in a data set.

<!--
The line-up protocol works like a police line-up: the suspect (test
statistic plot) is hidden in a set of decoys. If the observer, who has not
seen the suspect, can pick it out as being noticeably different, there is
evidence that it is not innocent.
-->

Study Design
============

This study aims to answer several questions around the presentation of spatial distributions:

1. Are spatial disease trends, that impact highly populated small areas, detected with higher accuracy when viewed in a hexagon tile map display?

2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when
using a hexagon tile map display?

additional considerations when completing this experimental task included exploration of the difficulty experienced by participants

<!--
 Do people find hexagon tile maps more difficult to read than choropleth maps?
 Are the reasons for choosing a plot different depending on the type of display?
-->

## Experimental design

The most common display for spatial cancer data is the choropleth map.
This will be the comparative visualisation for presenting the lineups [@VVSIALM].
Most geographic distributions will have some degree of spatial autcorrelation between neighbours.
This feature will exist in all plots in the lineup displays, the plot that contains the trend feature shown in only one set of data will also be affected by spatial autocorrelation.
A reasonable amount of null plots $N-1$ in the lineup was chosen to ensure data is well hidden. For the detailed choropleth of Australian SA2 areas, we set $N = 12$ to not overwhelm participants.
A line up protocol was implemented to arrange 12 maps in each display. 
Individual displays were created by a combination of map type, and spatial trend model.

The hypotheses for each lineup are
$H_0$ : All plots look the same
$H_a$ : One plot looks different to the other plots

Recruited participants to be uninvolved judges with no prior knowledge of the data to avoid discrimination or advantages.
The online crowdsource platform Figure-Eight was used to recruit participants.

The researchers contrasted the different plot designs, as hexagon tilemap and geography in the lineups were created using the same data, and same null positions within the lineup.

Let $n$ be the number of independent observers and $x_i$ the
number of observers who picked plot $i$, $i = \{1,...,m\}$

Then $x_i, x_2, ..., x_m$ follows a multinomial
distribution$Mult_{\pi_1, \pi_2, ...., \pi_m}(x_i, x_2, ..., x_m)$ with 
$\sum_i \pi_i = 1$, where $\pi_i$ is the probability that plot $i$ is picked by an
observer, which we can estimate as $\hat{\pi}_i = x_i/n$.
The researchers compared the length of time taken, and the accuracy of the participants choices.
The power of a lineup can therefore be estimated as the ratio of correct
identifications $x$ out of $n$ viewings.

## The variables being manipulated and measured

The variables that were changed between groups were the type of plot shown and the trend model.

Each participant was randomly allocated to either Group A or Group B when they begun the survey. This resulted in 42 participants allocated to Group A, and 53 participants allocated to Group B.

The levels of the factors measured in the experiment were:
- Map type: *Choropleth, Hexagon tile*
- Trend: *Locations in three population centres, Locations in multiple population centres, South-East to North-West*

Factor combinations examined by each participant amount to 6 (2x3) lineup displays.
A participant did see the same data for both map types. Four simulated sets of data were generated for each treatment.
This will generate 24 lineups (12 were geographic maps, and 12 were hexagon tile maps). Participants will evaluate 12 lineups, 6 of each map type. Appendix A shows the experimental design visually.
For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants.

\begin{table}[]
\caption{The Experimental Design}
\label{tab:my-table}
\begin{tabular}{|l|l|l|}
\hline
Trend & Map type & Replicates \\ \hline
NW-SE & Choropleth & 2 \\ \hline
 & Hexagon tile & 2 \\ \hline
Three cities & Choropleth & 2 \\ \hline
 & Hexagon tile & 2 \\ \hline
All cities & Choropleth & 2 \\ \hline
 & Hexagon tile & 2 \\ \hline
\end{tabular}
\end{table}

The variables measured as a result of the changes were the probability of detection each display and the time taken to submit responses.
To measure the accuracy of the detections, the plot chosen for each lineup evaluated was compared to the position of the real spatial trend plot in the lineup. A correct result occurs when the chosen plot matches the position of the real plot, this was recorded in an additional binary variable; 1 = correct; 0 = incorrect.
High efficiency occurs when a small amount of time is taken to evaluate each lineup. This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.

## Simulation process

The underlying spatial correlation model was created to provide spatial autocorrelation between neighbouring areas using the longitude and latitude values for the Statistical Areas.
formula = z ~ 1, locations = ~ longitude + latitude

Simulated spatially dependent data using the model on the centroids of each area, for 12 null plots in 12 lineups.

12 sets of data were created.
In these 12 sets of data, each of the 144 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas.

For each of the 144 individual maps, the values attributed to each geographic area are rescaled to show a similar colour scale from deep blue to dark red within each map.

A random location was selected for each set of lineup data.
In this location, a trend model was overlaid on the null set of spatially correlated data.
Each set of lineup data was used to produce a choropleth maps and hexagon tile maps. These matched pairs were split between Group A and Group B.

## Participants

There were 95 participants involved in the study. 
We recruited participants using the Figure-Eight crowd source platform by advertising this survey to participants that fulfilled the following crtieria:

- level 2 or level 3 on the Figure-Eight Platform.
- at least 18 years old

Participants then selected our task from the list of tasks available to them.

Each participant was trained using three test displays orienting them to the evaluation task.
Participants then proceeded to the survey, this involved evaluating 12 displays.

## Experiment procudure and data collection

The participant answered demographic questions and provided consent before evaluating the lineups.

Demographics were collected regarding the study participants:
- Gender (female / male / other),
- Degree education level achieved (high school / bachelors / masters / doctorate / other),
- Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
- Lived at least for one year in Australia (Yes / No )

Participants then moved to the evaulation phase.
The set of images differed for Group A and Group B.
After being allocated to a group, each individual was shown the 12 displays in randomised order.

Three questions were asked regarding each display:
- Plot choice
- Reason
- Difficulty

After completing the 12 evaluations, the participants were asked to submit their responses.

Data was collected through a web application containing the online survey.
Each participant used the internet to access the survey.
The data collection took place using a secure link between the survey web application and the googlesheet used to store results. The application would first connect to the googlesheet using the googlesheets [@sheets] R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.

## The methods of data analysis used
The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R [@RCore].

For each of the 12 lineup displays the researchers calculated:
- accuracy: the proportion of subjects who detected the data plot
- efficiency: average time taken to respond

### Visualisations
Side-by-side dot plots were made of accuracy (efficiency) against map type, facetted by trend model type.

Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.

Plots will be made in R (R Core Team 2019), with the ggplot2 package (Wickham 2016).

### Modeling

The results will be analysed using a generalised linear model, with a subject random effect to account for differences in individuals. There will be two main effects: map type and trend model, which gives the fixed effects part of the model to be

$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3$$

where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect. We are allowing for an interaction between map type and trend model. Because the response is binary, a logistic model is used.

A similar model will be constructed for the efficiency, using a log time, and normal errors.

The feedback and demographic variables will possibly be incorporated as covariates.

Computation will be done using R [@RCore], with the `lme4` package [@lme4].

## Limitations of the data collection

This required internet connection for participants to access the survey

Results
============

```{r data}
# Load Libraries
library(tidyverse)
library(lubridate)
library(broom)
library(readxl)
library(lme4)
library(ggthemes)
library(RColorBrewer)

invthm <- theme(
  panel.background = element_rect(fill = "transparent", colour = NA), 
  plot.background = element_rect(fill = "transparent", colour = NA),
  legend.background = element_rect(fill = "transparent", colour = NA),
  legend.key = element_rect(fill = "transparent", colour = NA),
  text = element_text(colour = "white", size = 20),
  axis.text = element_text(colour = "white", size = 20)
)

trend_colours <- c("NW-SE" = "#B2DF8A",
  "three cities" = "#A6CEE3",
  "all cities" = "#1F78B4")

# Downloaded data
d <- read_xlsx("data/experiment-export.xlsx", sheet=2) %>%
  filter(!is.na(contributor)) %>%
  mutate(contributor = factor(contributor))

# Check data set 
# Need to clean multiple entries, 48, 24
# remove duplicated entries due to submit button
d <- d %>% group_by(group, contributor, image_name) %>%
  slice(1) %>% ungroup() %>% 
  arrange(group, contributor, plot_order)

# Now remove contributors who did not provide answers to most questions
keep <- d %>% count(contributor, sort = TRUE) %>% filter(n > 10)
d <- d %>% 
  filter(contributor %in% keep$contributor) %>%
  filter(contributor != "1234567890")

n_contributors <- d %>% count(contributor, sort=TRUE) %>% 
  summarise(n_contributors = length(contributor))

d <- d %>% mutate(certainty = factor(as.character(certainty),
  levels = c("1", "2", "3", "4","5"), ordered=TRUE))
```

The survey responses from participants were kept only if the participant submitted answers for all 12 displays. This resulted in 95 participants.

```{r reps}
# Augment
# add data replication number
# d %>% count(image_name) %>% print(n=24)
# image code <--> rep
replicate <- tibble(image_name = c("aus_cities_12_geo.png", "aus_cities_12_hex.png", 
                                   "aus_cities_3_geo.png", "aus_cities_3_hex.png",
                                   "aus_cities_4_geo.png", "aus_cities_4_hex.png",
                                   "aus_cities_9_geo.png", "aus_cities_9_hex.png",
                                   "aus_nwse_2_geo.png", "aus_nwse_2_hex.png",
                                   "aus_nwse_3_geo.png", "aus_nwse_3_hex.png",
                                   "aus_nwse_5_geo.png", "aus_nwse_5_hex.png",
                                   "aus_nwse_6_geo.png", "aus_nwse_6_hex.png",
                                   "aus_three_12_geo.png", "aus_three_12_hex.png",
                                   "aus_three_5_geo.png", "aus_three_5_hex.png",
                                   "aus_three_8_geo.png", "aus_three_8_hex.png",
                                   "aus_three_9_geo.png", "aus_three_9_hex.png"),
                    replicate = c(1, 1, 2, 2, 3, 3, 4, 4, 
                                  1, 1, 2, 2, 3, 3, 4, 4,
                                  1, 1, 2, 2, 3, 3, 4, 4))
# Add rep info to data
d <- d %>% left_join(., replicate, by = "image_name")
#d %>% count(group, image_name, sort=TRUE)`

contribs_responses <- d %>%
  group_by(group, contributor) %>% 
  filter(sum(choice) == 0) %>% 
  summarise(pdetect = mean(detect, na.rm = TRUE))

d <- d %>% 
  filter(!(contributor %in% contribs_responses$contributor))
```

The contributors who detected no plots correctly were analysed further. Three of these contribuotrs gave no choices for any of the twelve displays. They were also removed for the rest of the analysis. The contributors who gave various plot choices and reasons for the twelve displays were kept.

## Demographics:

```{r demogs}
# Create one record for each contributor, to examine demographics
dem_contribs <- d %>%
  group_by(contributor) %>%
  slice(1) %>% ungroup()

###############################################################################
# Demographics of contributors
#dem_contribs %>% count(gender)
dem_contribs %>% count(age, name = "participants")
dem_contribs %>% count(gender, education) %>% 
  spread(gender, n) %>% 
  mutate(`Col. Total` = He + She) %>% 
  gather("Gender", "Amount", He:`Col. Total`) %>% 
  spread(education, Amount) %>% 
  mutate(`Row Total` = Bach + `High School`, Masters,
    Gender = factor(Gender, levels = c("He", "She", "Col. Total"), labels = c("He", "She", "Col. Total"))) %>% knitr::kable(format = "latex")
```
70 of the 95 participants were male, and 25 female and only two of the participants had lived in Australia before.

70 of the participants achieved a Bachelors or Masters degree.

# Accuracy

The detection rate is used to find the accuracy for participants reporting the real data trend model. The accuracy can be seen from many views.

```{r pdetection_group}
# Tidy for analysis
d <- d %>% 
  separate(image_name, c("nothing", "trend", "location", "type", "extra"), remove=FALSE) %>%
  select(-nothing, -extra) %>%
  mutate(location = as.numeric(location), 
    # detect measures the accuracy of the choice
         detect = ifelse(location == choice, 1, 0)) %>% 
  mutate(trend = case_when(
    trend == "nwse" ~ "NW-SE",
    trend == "cities" ~ "all cities",
    trend == "three" ~ "three cities")) %>% 
  mutate(trend = fct_relevel(trend, "NW-SE","three cities","all cities")) %>% 
  mutate(type = case_when(
    type == "hex" ~"Hexagon tiles",
    TRUE~"Choropleth")) %>% 
    mutate(detect_f = factor(detect, levels = c(0,1), labels = c("Incorrect", "Correct")))

plots <- d %>% group_by(group, trend, type, location) %>%
  # pdetect measures the aggregated accuracy of the choices
  summarise(pdetect = length(detect[detect == 1])/length(detect)) 
```

```{r pdetection_trend, eval = FALSE}
plots %>% ggplot(aes(x = group, y = pdetect)) + 
  geom_boxplot() + 
  geom_jitter(width = 0.1) +
  ylab("Detection rate") + 
  ylim(c(0,1))

plots %>% ggplot(aes(x = trend, y = pdetect, fill = trend)) + 
  geom_boxplot() + 
  scale_fill_manual(values = trend_colours) +
  geom_jitter(width = 0.1) +
  ylab("Detection rate") + 
  ylim(c(0,1))

plots %>% ggplot(aes(x = type, y = pdetect)) + 
  geom_boxplot() + 
  geom_jitter(width = 0.1) +
  ylab("Detection rate") + 
  ylim(c(0,1))
```

```{r detection_compare, fig.cap = "Each point shows the probability of detection for the lineup display, separated by the trend model hidden in the lineup. The points for the same data set are linked to show the difference in the detection rate when the same data was seen in each display. 11 of the 12 real distribution plots were found more often in the hexagon display."}
# Detectability rate for each lineup (image)
d_smry <- d %>% group_by(trend, type, replicate) %>%
  # pdetect measures the aggregated accuracy of the choices
  summarise(pdetect = length(detect[detect == 1])/length(detect)) %>%
  ungroup()

# Plot summary
ggplot(d_smry, aes(x=type, y=pdetect, colour = trend)) +
  geom_point(size = 3) +  
  geom_line(size = 1, aes(group = replicate)) +  
  facet_wrap(~trend) +  
  scale_colour_manual(values = trend_colours) +
  xlab("Type of areas visualised") +
  ylab("Detection rate") + 
  ylim(0,1) +
  guides(colour = FALSE)
```

```{r detection_compare_table}
d %>% 
  group_by(trend, type, replicate) %>%
  summarise(mean = round(mean(time_taken),2), std.dev = round(sd(time_taken), 2)) %>% 
  knitr::kable(format = "latex")
```

```{r ttest}
# Numerical summary
diffs <- d_smry %>% spread(type, pdetect) %>%
  mutate(dif = `Hexagon tiles` - `Choropleth`)

# Probability of detection using map types
test_dt <- t.test(pdetect ~ type, data = d_smry, alternative = "less")
```

A t-test shows the difference between the detection rates for the two types of displays.
The value of `r test_dt$p.value` shows that it is very unlikely the difference is due to chance.

## Speed

```{r time, fig.cap = "The time taken to evaluate each display is broken into five second windows. The height of the histogram bars show how many evaulations were submitted within each time window. The distributions for the choropleth and hexagon tile maps are very similar. Both have a large peak at 0-5 seconds, and then a secondary peak at 10-20 seconds. No response took over one minute."}
d_time <- d %>% 
  group_by(trend, type, location, replicate) %>%
  summarise(m = mean(time_taken), s = sd(time_taken))
#d_time %>% print(n=24)

ggplot(d, 
  aes(x = time_taken, fill = detect_f)) + xlim(0,65) +
  scale_fill_brewer(palette = "Dark2") +
  geom_histogram(alpha = 0.4, binwidth = 5, boundary = 0, position = "dodge") + 
  labs(x = "Time taken (Seconds)", y = "Amount of evaluations") + facet_wrap(~ type)
```

```{r time_compare, fig.cap = "Each point shows the average time taken for participants to evalute the lineup display, separated by the trend model hidden in the lineup. The points for the same data set are linked to show the difference in the avergae time taken when the same data was seen in each display. There is a lot of variation in the time taken. The shortest average time (15 seconds), and the longest average time (23 seconds) both occured when evaluating three cities"}
# Visual summary
ggplot(d_time, aes(x = type, y = m, colour = trend)) +
  geom_point(size = 3) +  
  geom_line(size = 1, aes(group = replicate)) +  
  facet_wrap(~ trend) +  
  scale_colour_manual(values = trend_colours) +
  xlab("Type of areas visualised") +
  ylab("Average time taken") + 
  guides(colour = FALSE)
```

## Certainty

```{r, fig.cap = "The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays. Participants were more likely to choose a high certainty when considering a Choropleth map. The default certainty of 3 was chosen most for the Hexagon tile map displays."}
d <- d %>% 
  mutate(certainty = as_factor(certainty))

ggplot(d,
  aes(x = certainty, fill = detect)) +
  scale_fill_brewer(palette = "Set2") +
  geom_bar(position = "dodge") + facet_wrap(~type) + guides(fill = FALSE)
```

Certainty levels are measured on a five point scale—they are subjective
assessments by the participant ‘how certain are you about your choice?’.

```{r, fig.cap = "The amount of times each level of certainty was chosen by participants. The columns shown whether a viewer correctly selected the real trend data plot when viewing hexagon tile map or choropleth displays."}
ggplot(d,
  aes(x = certainty)) +
  scale_fill_manual(values = trend_colours) +
  geom_bar(position = "dodge") + facet_grid(type ~ detect)
# certainty wasn't affected by the trend
```

```{r, fig.cap = "The amount of times each level of certainty was chosen by participants. The columns shown whether a viewer correctly selected the real trend data plot when viewing hexagon tile map or choropleth displays. The rows show the type of the trend model added in the real data plot. The default certainty level of 3 was chosen most frequently when incorrect. Then shown a NW-SE or all cities trend participants felt more certain of their correct choice."}
ggplot(d, 
  aes(x = certainty, fill = trend)) +
  scale_fill_manual(values = trend_colours) +
  geom_bar(position = "dodge") + facet_grid(trend ~ detect)
```

## Reason

```{r, fig.cap = "The most common reason for choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps. Clusters were the most common reason when viewing a Hexagon Tile map, trend was the most common choice for choropleth displays except for the all cities display."}
###########################################################
# Qualitative analysis of reason
d <- d %>% 
  mutate(reason = fct_infreq(ifelse(reason =="0.0", "no reason", reason)))

ggplot(d) + 
  geom_bar(aes(x = reason)) +  
  facet_grid(trend ~ type) +  
  scale_colour_manual(values = trend_colours) +
  xlab("Type of areas visualised") + 
  guides(colour = FALSE) + coord_flip()
```

## Contributors

```{r fig.cap = "The probablity of detection acheived by the contributors in each group is shown by the points. Group B has a larger range and a smaller inter-quartile range. Group A and  both had 3 people who did not find any of the data maps in the displays."}
# Check contributor performance
contribs <- d %>% group_by(group, contributor) %>% 
  # pdetect measures the aggregated accuracy of the choices
  summarise(pdetect = mean(detect, na.rm = TRUE))

# Plot performance
contribs %>% ggplot(aes(x = group, y = pdetect)) + 
  geom_boxplot() + 
  geom_jitter(width = 0.1, height = 0, alpha = 0.7) + 
  ylab("Detection rate") + 
  ylim(0,1)
```

## Reason

```{r}
###########################################################
# Qualitative analysis of reason
d <- d %>% 
  mutate(reason = ifelse(reason =="0.0", "no reason", reason))

ggplot(d %>% mutate(detect = factor(detect, levels = c(0,1), 
  labels = c("Incorrect", "Correct")))) + 
  geom_bar(aes(x = reason)) +  
  facet_grid(trend ~ detect) +  
  scale_colour_manual(values = trend_colours) +
  xlab("Type of areas visualised") + 
  guides(colour = FALSE) + coord_flip()
```

```{r choices, fig.height = 12, fig.width = 12, fig.cap = "Each facet is associated with one lineup, the height of the bars count the choices made by the participants considering each lineup. The bars coloured with black outlines show the map which contained a trend model, these are the correct choices. The numbers differentiate the replicates of each trend model and type of map display. Participants were able to select 0 to indicate they did not want to choose a map. "}
detect_colours <- c("Incorrect" = "#33A02C", "Correct" = "#B2DF8A")
d %>% mutate(repl = paste(type, trend, " (", replicate, ") " ,  sep = "")) %>% 
  ggplot() + 
  geom_bar(aes(x = choice, fill = detect_f, color = detect_f), boundary = 0) + 
  facet_wrap(~ repl, 
    drop = TRUE, as.table = TRUE, ncol = 4) +
  scale_colour_grey(start = 0.9, end = 0.1) +
  scale_fill_manual(values = detect_colours) +
  theme(legend.position = "bottom") + guides(colour = FALSE, fill = FALSE) +
  labs(x = "Choice of plot in lineup", y = "Amount of choices")
```

The choices made by participants are examined in Figure \ref{fig:choices}.
Participants were misled by the choropleth display, but not the hexagon display for all cities displays except (2). The maps with a North West to South East trend was chosen with much greater frequency in all displays. All of three cities displays, except (4), were detected in the hexagon display. All except one lineup had at least one participant select the correct map in the lineup as shown in Figure \ref{fig:choices}.

## Anomolies

## Modeling the difference

A generalized linear mixed effects model can account for each individual participants’ abilities as it includes a subject-specific random intercept. As each participant provides results from 12 lineups.

### Detection Rates

```{r}
# Modelling 
glm1 <- glm(formula = detect_f ~ type * trend,
  family = binomial(link = "logit"), data = d)

preds <- predict(glm1, newdata = d, se=T)
pfit <- exp(preds$fit)/(1+exp(preds$fit))
se.bands.logit = tibble(upper = (preds$fit+2*preds$se.fit), lower = (preds$fit-2*preds$se.fit))
se.bands = exp(se.bands.logit)/(1+exp(se.bands.logit))

tidy(glm1) %>% mutate(p.value = round(p.value, 3))

anova(glm1, test="Chisq")

d_glm <- d %>% select(group:certainty, detect, detect_f) %>%
  bind_cols(as_tibble(se.bands)) %>% 
  mutate(pfit, 
    predicted = ifelse(pfit > 0.5, 1, 0),
    predicted = factor(predicted, levels = c(0,1), labels = c("Incorrect", "Correct")))

table(d_glm$predicted, d_glm$detect_f)
```

```{r}
# Mixed effects models
lmer1 <- lmer(detect ~ type*trend + (1|contributor), data = d)
lmer1_d <- augment(lmer1, d)

preds_lmer <- predict(lmer1, newdata = d)
pfit_lmer <- exp(preds_lmer)/(1+exp(preds_lmer))

glance(lmer1)
tidy(lmer1)

d_lmer <- d %>% select(group:certainty, detect, detect_f) %>%
  bind_cols(as_tibble(se.bands)) %>% 
  mutate(pfit_lmer, 
    predicted = ifelse(pfit_lmer > 0.5, 1, 0),
    predicted = factor(predicted, levels = c(0,1), labels = c("Incorrect", "Correct")))

table(d_lmer$predicted, d_lmer$detect_f)

# Hexagon maps have better chance of correct detection
# Allowing for contributor effects to vary: 0.12 strong residual
```

For a base model of Choropleth map, using a NW-SE trend model.
The detection rate for Hexagon tile maps using a NW-SE trend model changes the log odds of the detection by 0.42.

### Certainty

```{r}
# Modelling 
lm1 <- lm(formula = as.numeric(certainty) ~ type, data = d)
lm1_d <- augment(lm1, d)
```

```{r}
# Mixed effects models
lmer1 <- lmer(detect ~ type*trend + (1|contributor), data = d)
lmer1

# Hexagon maps have better chance of correct detection
# Allowing for contributor effects to vary: 0.12 strong residual
```

Discussion
============

Conclusion
============
how do the results found generalise to other work
- Not just for Aus (Canada new Zealand could also use this effective display)

- For USA alternative methods can also be helpful

<!-- conference papers do not normally have an appendix -->

Supplementary Materials
============

## Training

## Survey application

## Subject specific anomolies (0% detection)

Acknowledgment {#acknowledgment}
==============

The authors would like to thank...

Ethics approval for the online survey was granted by QUT’s Ethics Committee (Ethics Application Number: 1900000991). All applicants provided informed consent in line with QUT regulations prior to participating in this research.

Bibliography styles
===================

\newpage
References {#references .numbered}
==========

<!-- An example of a floating figure using the graphicx package. -->
<!-- Note that \label must occur AFTER (or within) \caption. -->
<!-- For figures, \caption should occur after the \includegraphics. -->
<!-- Note that IEEEtran v1.7 and later has special internal code that -->
<!-- is designed to preserve the operation of \label within \caption -->
<!-- even when the captionsoff option is in effect. However, because -->
<!-- of issues like this, it may be the safest practice to put all your -->
<!-- \label just after \caption rather than within \caption{}. -->

<!-- Reminder: the "draftcls" or "draftclsnofoot", not "draft", class -->
<!-- option should be used if it is desired that the figures are to be -->
<!-- displayed while in draft mode. -->

<!-- \begin{figure}[!t] -->
<!-- \centering -->
<!-- \includegraphics[width=2.5in]{myfigure} -->
<!-- where an .eps filename suffix were assumed under latex,  -->
<!-- and a .pdf suffix were assumed for pdflatex; or what has been declared -->
<!-- via \DeclareGraphicsExtensions. -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure} -->

<!-- Note that the IEEE typically puts floats only at the top, even when this -->
<!-- results in a large percentage of a column being occupied by floats. -->

<!-- An example of a double column floating figure using two subfigures. -->
<!-- (The subfig.sty package must be loaded for this to work.) -->
<!-- The subfigure \label commands are set within each subfloat command, -->
<!-- and the \label for the overall figure must come after \caption. -->
<!-- \hfil is used as a separator to get equal spacing. -->
<!-- Watch out that the combined width of all the subfigures on a  -->
<!-- line do not exceed the text width or a line break will occur. -->

<!-- \begin{figure*}[!t] -->
<!-- \centering -->
<!-- \subfloat[Case I]{\includegraphics[width=2.5in]{box}% -->
<!-- \label{fig_first_case}} -->
<!-- \hfil -->
<!-- \subfloat[Case II]{\includegraphics[width=2.5in]{box}% -->
<!-- \label{fig_second_case}} -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure*} -->

<!-- Note that often IEEE papers with subfigures do not employ subfigure -->
<!-- captions (using the optional argument to \subfloat[]), but instead will -->
<!-- reference/describe all of them (a), (b), etc., within the main caption. -->
<!-- Be aware that for subfig.sty to generate the (a), (b), etc., subfigure -->
<!-- labels, the optional argument to \subfloat must be present. If a -->
<!-- subcaption is not desired, just leave its contents blank, -->
<!-- e.g., \subfloat[]. -->

### 2019-12-25 paper/paper.tex
paper

--- 2019-12-19 survey/survey.tex
@@
 \hypersetup{
-            pdftitle={Visual Inference Test of the Hexagon Tile Map for Spatial Distributions},
+            pdftitle={Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference},
             pdfkeywords={statistics, visual inference, geospatial, population},
@@
 % Do not put math or special symbols in the title.
-\title{Visual Inference Test of the Hexagon Tile Map for Spatial Distributions}
+\title{Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison
+using visual inference}
 
@@
 
-Geo-spatial statistics are often presented on the geographic map base.
-To present geo-spatial population statistics, information for
-individuals within each geographic region are often aggregated. A
+Geospatial statistics are often presented on the geographic map base. A
 choropleth map is the common display to present aggreagated statistics
 for geographic units, and they are often used to present statistics
-regarding the population. This visualisation method involves drawing the
+regarding the population. Creating a choropleth map involves drawing the
 administrative boundaries and filling them with colour to communicate
-the value of the statistic. In Australia, there are many sets of
+the value of the statistic. In Australia, there are sets of
 administrative boundaries that define subdivisions of the population at
-various granularities.
-
-When presenting population statistics on a geographic map base, the size
-of the regions can allow errornous conclusions to be drawn about the
-state of the statistic over the entire population. This occurs as large
-regions filled with a consistent colour or pettern can draw the
-attention of map readers, and small regions are not paid equal
-attention.
-
-\hypertarget{background-and-motivation}{%
-\section{Background and Motivation}\label{background-and-motivation}}
+various granularities. The set of Australia statistical areas presents
+an example of a heterogrenous distribution of area. The rural
+communicates on a much larger geographic space than small inner city
+communities. This has the negative effect of incorrectly showing the
+spatial distribution of the statistic, especially when a spatial
+distribution is related to the size of the areas, or the population
+density.
+
+An alternative display can also be used to effectively communicate a
+spatial distribution for a set of heterogeneous areas. Viewers of
+spatial distributions may come to incorrect conclusions.
+
+\hypertarget{motivation}{%
+\section{Motivation}\label{motivation}}
 
@@
 \subsection{Australian Cancer Atlas}\label{australian-cancer-atlas}}
-
-\begin{itemize}
-\tightlist
-\item
-  Communicating spatial distributions
-\item
-  Trend over geographic space
-\item
-  Trend over communities and populations
-\end{itemize}
 
@@
 explored on an individual or aggregate level. The Australian communities
-examined are Statistical Areas at Level 2 (SA2)(``Australian Statistical
-Geography Standard (ASGS)'' 2018) used by the Australian Bureau of
+are examined at the Statistical Areas at Level 2 (SA2)(``Australian
+Statistical Geography Standard (ASGS)''
+\protect\hyperlink{ref-abs2016}{2018}) used by the Australian Bureau of
 Statistics. Bayesian spatial smoothing has been applied to incorporate
@@
 statistics. The values of the statistic for each are communicated using
-a diverging colour scheme. Dark blue represents areas with values much
-less than the Australian average, and represents areas much greater than
-the Australian average.
+a diverging colour scheme.
+
+The Australian Cancer Atlas communicates the trends in the distributions
+of cancer over geographic space. It uses a choropleth map display and
+diverging colour scheme to draw attention to relationships between
+neighbouring areas.
+
+\hypertarget{background}{%
+\section{Background}\label{background}}
+
+\hypertarget{methodology}{%
+\subsection{Methodology}\label{methodology}}
+
+Spatial visualisations - Choropleth However, the issue of using a
+choropleth map base becomes obvious when considering the distributions.
+Position is extremely important for analysis of a visualisation.
+
+\hypertarget{population-focussed-displays}{%
+\subsection{Population focussed
+displays}\label{population-focussed-displays}}
+
+Map creators have the ability to present spatial statistics in
+alternative displays that can highlight the population. This work aims
+to show that a hexagon tile map display is a viable alternative to the
+geographic map base for presenting population statistics. The same data
+were shown on a choropleth map, and on a hexagon tile map. Comparing the
+results of participants who see the choropleth to those who see a
+hexagon tile map will show that population related distributions are
+spotted more frequently in a hexagon tile map display.
+
+When presenting population statistics on a geographic map base, the size
+of the regions can allow errornous conclusions to be drawn about the
+state of the statistic over the entire population. This occurs as large
+regions filled with a consistent colour or pettern can draw the
+attention of map readers, and small regions are not paid equal
+attention. A choropleth map is not the only display that can be used for
+presenting geospatial data. Alternative maps include various cartograms,
+and tesselated tile maps. They allow other variables to be included in
+the display to highlight the staistical values of various geographic
+areas.
 
@@
 \item
-  Testing the effectiveness
+  Protocol for testing the effectiveness
 \end{itemize}
 
-Classical statistical inferences involves hypothesis testing, the
-process of rejecting a null hypothesis in favour of an alternative. This
+Classical statistical inference involves hypothesis testing, the process
+of rejecting a null hypothesis in favour of an alternative. This
 approach relies on data, the appropriate distributions and their
-assumptions.
-
-\hypertarget{line-up-protocol}{%
-\subsection{Line up protocol}\label{line-up-protocol}}
-
-The lineup protocol presents a method for visual inference testing.
+assumptions. Visual inference null hypothesis: independence in the
+variables (absence of all features), alternative hypothesis:
+Relationship between the variables (presence of some feature).
+
+The lineup protocol is used for visual inference testing. 1. simulate
+null plots 2. Insert data with structure into a random location 3. Ask
+uninvolved person to select the most different plot 4. If location is
+chosen correctly, the existence of a feature is significant at
+\(\alpha = 1/N\).
 
@@
 ``In this framework, plots take on the role of test statistics, and
-human cognition the role of statistical tests.'' Buja et al. (2009)
+human cognition the role of statistical tests.'' Buja et al.
+(\protect\hyperlink{ref-SIEDAMD}{2009})
 \end{quote}
@@
 
-The lineup protocol can be used in a variety of tsting scenarios. The
+The lineup protocol can be used in a variety of testing scenarios. The
 choropleth map is best used for testing spatial structure in a data set.
-
-\hypertarget{population-focussed-displays}{%
-\subsection{Population focussed
-displays}\label{population-focussed-displays}}
-
-Map creators have the ability to present spatial statistics in
-alternative displays that can highlight the population. This work aims
-to show that a hexagon tile map display is a viable alternative to the
-geographic map base for presenting population statistics. The same data
-were shown on a choropleth map, and on a hexagon tile map. Comparing the
-results of participants who see the choropleth to those who see a
-hexagon tile map will show that population related distributions are
-spotted more frequently in a hexagon tile map display.
 
@@
 \section{Study Design}\label{study-design}}
-
-\hypertarget{aims}{%
-\subsection{Aims}\label{aims}}
 
@@
   highly populated small areas, when using a hexagon tile map display?
-\item
-  Do people find hexagon tile maps more difficult to read than
-  choropleth maps?
-\item
-  Are the reasons for choosing a plot different depending on the type of
-  display?
-\item
-  Does an Australian resident find the choropleth map easier to read
-  than the hexagon tile map?
 \end{enumerate}
 
-\hypertarget{methodology}{%
-\subsection{Methodology}\label{methodology}}
-
-A survey was created to test the effectiveness of the hexagon tile map
-display.
-
-The online crowdsource platform Figure-Eight was used to recruit
-participants. A line up protocol was implemented to arrange 12 maps in
-each display. Individual displays were created by a combination of plot
-type, and spatial trend model.
+additional considerations when completing this experimental task
+included exploration of the difficulty experienced by participants
+
+\hypertarget{experimental-design}{%
+\subsection{Experimental design}\label{experimental-design}}
+
+The most common display for spatial cancer data is the choropleth map.
+This will be the comparative visualisation for presenting the lineups
+(Majumder, Hofmann, and Cook \protect\hyperlink{ref-VVSIALM}{2013}).
+Most geographic distributions will have some degree of spatial
+autcorrelation between neighbours. This feature will exist in all plots
+in the lineup displays, the plot that contains the trend feature shown
+in only one set of data will also be affected by spatial
+autocorrelation. A reasonable amount of null plots \(N-1\) in the lineup
+was chosen to ensure data is well hidden. For the detailed choropleth of
+Australian SA2 areas, we set \(N = 12\) to not overwhelm participants. A
+line up protocol was implemented to arrange 12 maps in each display.
+Individual displays were created by a combination of map type, and
+spatial trend model.
+
+The hypotheses for each lineup are \(H_0\) : All plots look the same
+\(H_a\) : One plot looks different to the other plots
+
+Recruited participants to be uninvolved judges with no prior knowledge
+of the data to avoid discrimination or advantages. The online
+crowdsource platform Figure-Eight was used to recruit participants.
 
@@
 
-The researchers compared the length of time taken, and the accuracy of
-the participants choices.
-
-\hypertarget{the-participants}{%
-\subsection{The participants}\label{the-participants}}
-
-There were 95 participants in the study. We recruited participants using
-the Figure-Eight crowd source platform by advertising this survey to
-participants that fulfilled the following crtieria:
-
-• level 2 or level 3 on the Figure-Eight Platform. • at least 18 years
-old
-
-Participants then selected our task from the list of tasks available to
-them.
+Let \(n\) be the number of independent observers and \(x_i\) the number
+of observers who picked plot \(i\), \(i = \{1,...,m\}\)
+
+Then \(x_i, x_2, ..., x_m\) follows a multinomial
+distribution\(Mult_{\pi_1, \pi_2, ...., \pi_m}(x_i, x_2, ..., x_m)\)
+with \(\sum_i \pi_i = 1\), where \(\pi_i\) is the probability that plot
+\(i\) is picked by an observer, which we can estimate as
+\(\hat{\pi}_i = x_i/n\). The researchers compared the length of time
+taken, and the accuracy of the participants choices. The power of a
+lineup can therefore be estimated as the ratio of correct
+identifications \(x\) out of \(n\) viewings.
 
@@
 \subsection{The variables being manipulated and
-measured?}\label{the-variables-being-manipulated-and-measured}}
+measured}\label{the-variables-being-manipulated-and-measured}}
 
@@
 
-Each participant was randomly allocated to either group A or group B
+Each participant was randomly allocated to either Group A or Group B
 when they begun the survey. This resulted in 42 participants allocated
-to group A, and 53 participants allocated to group B.
-
-The levels of the factors measured in the experiment were: • Plot type:
-\emph{Geography, Hexagons} • Trend: \emph{Locations in two population
-centres, Locations in multiple population centres, South-East to
-North-West}
+to Group A, and 53 participants allocated to Group B.
+
+The levels of the factors measured in the experiment were: - Map type:
+\emph{Choropleth, Hexagon tile} - Trend: \emph{Locations in three
+population centres, Locations in multiple population centres, South-East
+to North-West}
 
 Factor combinations examined by each participant amount to 6 (2x3)
-lineup displays. A participant did see the same data for both plot
-types. Four simulated sets of data were generated for each treatment.
-This will generate 24 lineups (12 were geographic maps, and 12 were
-hexagon tile maps). Participants will evaluate 12 lineups, 6 of each
-plot type. Appendix A shows the experimental design visually. For each
-of the six geographic displays and six hexagon displays, two of each
-trend model were shown to participants.
+lineup displays. A participant did see the same data for both map types.
+Four simulated sets of data were generated for each treatment. This will
+generate 24 lineups (12 were geographic maps, and 12 were hexagon tile
+maps). Participants will evaluate 12 lineups, 6 of each map type.
+Appendix A shows the experimental design visually. For each of the six
+geographic displays and six hexagon displays, two of each trend model
+were shown to participants.
+
+\begin{table}[]
+\caption{The Experimental Design}
+\label{tab:my-table}
+\begin{tabular}{|l|l|l|}
+\hline
+Trend & Map type & Replicates \\ \hline
+NW-SE & Choropleth & 2 \\ \hline
+ & Hexagon tile & 2 \\ \hline
+Three cities & Choropleth & 2 \\ \hline
+ & Hexagon tile & 2 \\ \hline
+All cities & Choropleth & 2 \\ \hline
+ & Hexagon tile & 2 \\ \hline
+\end{tabular}
+\end{table}
 
@@
 
-\hypertarget{participant-training}{%
-\subsection{Participant training}\label{participant-training}}
-
-Each participant saw three test displays orienting them to the task.
-Participants proceeded to the survey, this involved evaluating 12
-displays.
+\hypertarget{simulation-process}{%
+\subsection{Simulation process}\label{simulation-process}}
+
+The underlying spatial correlation model was created to provide spatial
+autocorrelation between neighbouring areas using the longitude and
+latitude values for the Statistical Areas. formula = z \textasciitilde{}
+1, locations = \textasciitilde{} longitude + latitude
+
+Simulated spatially dependent data using the model on the centroids of
+each area, for 12 null plots in 12 lineups.
+
+12 sets of data were created. In these 12 sets of data, each of the 144
+maps were smoothed several times to replicate the spatial
+autocorrelation seen in cancer data sets presented in the Australian
+Cancer Atlas.
+
+For each of the 144 individual maps, the values attributed to each
+geographic area are rescaled to show a similar colour scale from deep
+blue to dark red within each map.
+
+A random location was selected for each set of lineup data. In this
+location, a trend model was overlaid on the null set of spatially
+correlated data. Each set of lineup data was used to produce a
+choropleth maps and hexagon tile maps. These matched pairs were split
+between Group A and Group B.
+
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+There were 95 participants involved in the study. We recruited
+participants using the Figure-Eight crowd source platform by advertising
+this survey to participants that fulfilled the following crtieria:
+
+\begin{itemize}
+\tightlist
+\item
+  level 2 or level 3 on the Figure-Eight Platform.
+\item
+  at least 18 years old
+\end{itemize}
+
+Participants then selected our task from the list of tasks available to
+them.
+
+Each participant was trained using three test displays orienting them to
+the evaluation task. Participants then proceeded to the survey, this
+involved evaluating 12 displays.
 
@@
 
-The participant submitted demographic questions and provided consent
+The participant answered demographic questions and provided consent
 before evaluating the lineups.
 
-Demographics were collected regarding the study participants: • Gender
-(female / male / other), • Degree education level achieved (high school
-/ bachelors / masters / doctorate / other), • Age range (18-24 / 25-34 /
-35-44 / 45-54 / 55+ / other) • Lived at least for one year in Australia
+Demographics were collected regarding the study participants: - Gender
+(female / male / other), - Degree education level achieved (high school
+/ bachelors / masters / doctorate / other), - Age range (18-24 / 25-34 /
+35-44 / 45-54 / 55+ / other) - Lived at least for one year in Australia
 (Yes / No )
@@
 Participants then moved to the evaulation phase. The set of images
-differed for group A and group B. After being allocated each individual
-was shown the 12 displays in randomised order.
+differed for Group A and Group B. After being allocated to a group, each
+individual was shown the 12 displays in randomised order.
 
@@
 Data was collected through a web application containing the online
-survey. Each participant used the internet to access the survey.
-
-The data collection took place using a secure link between the survey
-web application and the googlesheet used to store results. The
-application would first connect to the googlesheet using the
-googlesheets (Bryan and Zhao 2018) R package, and interacted again at
-the completion of the survey by adding the participant's responses to
-the 12 displays as 12 rows of data in the googlesheet.
+survey. Each participant used the internet to access the survey. The
+data collection took place using a secure link between the survey web
+application and the googlesheet used to store results. The application
+would first connect to the googlesheet using the googlesheets (Bryan and
+Zhao \protect\hyperlink{ref-sheets}{2018}) R package, and interacted
+again at the completion of the survey by adding the participant's
+responses to the 12 displays as 12 rows of data in the googlesheet.
 
@@
 results included downloading the survey submissions and opening them
-into the analysis software R ({\textbf{???}}).
-
-For each of the 12 lineup displays the researchers calculated: •
-accuracy: the proportion of subjects who detected the data plot •
+into the analysis software R (R Core Team
+\protect\hyperlink{ref-RCore}{2019}).
+
+For each of the 12 lineup displays the researchers calculated: -
+accuracy: the proportion of subjects who detected the data plot -
 efficiency: average time taken to respond
@@
 
-Side-by-side dot plots were made of accuracy (efficiency) against plot
+Side-by-side dot plots were made of accuracy (efficiency) against map
 type, facetted by trend model type.
@@
 The results will be analysed using a generalised linear model, with a
-subject random effect. There will be two main effects: plot type and
-trend model, which gives the fixed effects part of the model to be
+subject random effect to account for differences in individuals. There
+will be two main effects: map type and trend model, which gives the
+fixed effects part of the model to be
 
@@
 where \(y_{ij} = 0, 1\) whether the subject detected the data plot,
-\(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the plot type effect,
+\(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect,
 \(\delta_j\) is the trend model effect. We are allowing for an
-interaction between plot type and trend model. Because the response is
+interaction between map type and trend model. Because the response is
 binary, a logistic model is used.
@@
 
-Computation will be done using R ({\textbf{???}}), with the
-\texttt{lme4} package ({\textbf{???}}).
+Computation will be done using R (R Core Team
+\protect\hyperlink{ref-RCore}{2019}), with the \texttt{lme4} package
+(Bates et al. \protect\hyperlink{ref-lme4}{2015}).
 
@@
 This required internet connection for participants to access the survey
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+The survey responses from participants were kept only if the participant
+submitted answers for all 12 displays. This resulted in 95 participants.
+
+The contributors who detected no plots correctly were analysed further.
+Three of these contribuotrs gave no choices for any of the twelve
+displays. They were also removed for the rest of the analysis. The
+contributors who gave various plot choices and reasons for the twelve
+displays were kept.
+
+\hypertarget{demographics}{%
+\subsection{Demographics:}\label{demographics}}
+
+\begin{verbatim}
+## # A tibble: 6 x 2
+##   age     participants
+##   <chr>          <int>
+## 1 18 - 24           14
+## 2 25 - 34           37
+## 3 35 - 44           21
+## 4 45 - 54           11
+## 5 55+                6
+## 6 NA                 3
+\end{verbatim}
+
+\begin{tabular}{l|r|r|r|r}
+\hline
+Gender & Bach & High School & Masters & Row Total\\
+\hline
+Col. Total & 56 & 23 & 13 & 79\\
+\hline
+He & 39 & 19 & 9 & 58\\
+\hline
+She & 17 & 4 & 4 & 21\\
+\hline
+\end{tabular}
+
+70 of the 95 participants were male, and 25 female and only two of the
+participants had lived in Australia before.
+
+70 of the participants achieved a Bachelors or Masters degree.
+
+\hypertarget{accuracy}{%
+\section{Accuracy}\label{accuracy}}
+
+The detection rate is used to find the accuracy for participants
+reporting the real data trend model. The accuracy can be seen from many
+views.
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/detection_compare-1.pdf}
+\caption{Each point shows the probability of detection for the lineup
+display, separated by the trend model hidden in the lineup. The points
+for the same data set are linked to show the difference in the detection
+rate when the same data was seen in each display. 11 of the 12 real
+distribution plots were found more often in the hexagon display.}
+\end{figure}
+
+\begin{tabular}{l|l|r|r|r}
+\hline
+trend & type & replicate & mean & std.dev\\
+\hline
+NW-SE & Choropleth & 1 & 25.00 & 16.41\\
+\hline
+NW-SE & Choropleth & 2 & 21.12 & 15.28\\
+\hline
+NW-SE & Choropleth & 3 & 21.12 & 17.05\\
+\hline
+NW-SE & Choropleth & 4 & 21.20 & 14.52\\
+\hline
+NW-SE & Hexagon tiles & 1 & 19.53 & 14.56\\
+\hline
+NW-SE & Hexagon tiles & 2 & 21.95 & 16.42\\
+\hline
+NW-SE & Hexagon tiles & 3 & 22.02 & 16.12\\
+\hline
+NW-SE & Hexagon tiles & 4 & 18.17 & 14.51\\
+\hline
+three cities & Choropleth & 1 & 15.30 & 13.88\\
+\hline
+three cities & Choropleth & 2 & 25.22 & 14.36\\
+\hline
+three cities & Choropleth & 3 & 22.49 & 15.87\\
+\hline
+three cities & Choropleth & 4 & 18.68 & 13.74\\
+\hline
+three cities & Hexagon tiles & 1 & 20.37 & 17.02\\
+\hline
+three cities & Hexagon tiles & 2 & 19.95 & 16.59\\
+\hline
+three cities & Hexagon tiles & 3 & 20.02 & 17.19\\
+\hline
+three cities & Hexagon tiles & 4 & 18.02 & 16.93\\
+\hline
+all cities & Choropleth & 1 & 20.14 & 16.56\\
+\hline
+all cities & Choropleth & 2 & 22.75 & 14.72\\
+\hline
+all cities & Choropleth & 3 & 19.88 & 15.03\\
+\hline
+all cities & Choropleth & 4 & 19.33 & 16.15\\
+\hline
+all cities & Hexagon tiles & 1 & 19.83 & 15.87\\
+\hline
+all cities & Hexagon tiles & 2 & 16.96 & 14.65\\
+\hline
+all cities & Hexagon tiles & 3 & 19.21 & 15.27\\
+\hline
+all cities & Hexagon tiles & 4 & 20.03 & 15.11\\
+\hline
+\end{tabular}
+
+A t-test shows the difference between the detection rates for the two
+types of displays. The value of 0.0041593 shows that it is very unlikely
+the difference is due to chance.
+
+\hypertarget{speed}{%
+\subsection{Speed}\label{speed}}
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/time-1.pdf}
+\caption{The time taken to evaluate each display is broken into five
+second windows. The height of the histogram bars show how many
+evaulations were submitted within each time window. The distributions
+for the choropleth and hexagon tile maps are very similar. Both have a
+large peak at 0-5 seconds, and then a secondary peak at 10-20 seconds.
+No response took over one minute.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/time_compare-1.pdf}
+\caption{Each point shows the average time taken for participants to
+evalute the lineup display, separated by the trend model hidden in the
+lineup. The points for the same data set are linked to show the
+difference in the avergae time taken when the same data was seen in each
+display. There is a lot of variation in the time taken. The shortest
+average time (15 seconds), and the longest average time (23 seconds)
+both occured when evaluating three cities}
+\end{figure}
+
+\hypertarget{certainty}{%
+\subsection{Certainty}\label{certainty}}
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}
+\caption{The amount of times each level of certainty was chosen by
+participants when viewing hexagon tile map or choropleth displays.
+Participants were more likely to choose a high certainty when
+considering a Choropleth map. The default certainty of 3 was chosen most
+for the Hexagon tile map displays.}
+\end{figure}
+
+Certainty levels are measured on a five point scale---they are
+subjective assessments by the participant `how certain are you about
+your choice?'.
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/unnamed-chunk-2-1.pdf}
+\caption{The amount of times each level of certainty was chosen by
+participants. The columns shown whether a viewer correctly selected the
+real trend data plot when viewing hexagon tile map or choropleth
+displays.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/unnamed-chunk-3-1.pdf}
+\caption{The amount of times each level of certainty was chosen by
+participants. The columns shown whether a viewer correctly selected the
+real trend data plot when viewing hexagon tile map or choropleth
+displays. The rows show the type of the trend model added in the real
+data plot. The default certainty level of 3 was chosen most frequently
+when incorrect. Then shown a NW-SE or all cities trend participants felt
+more certain of their correct choice.}
+\end{figure}
+
+\hypertarget{reason}{%
+\subsection{Reason}\label{reason}}
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/unnamed-chunk-4-1.pdf}
+\caption{The most common reason for choice of plot when looking at each
+trend model shown in Choropleth and Hexagon Tile maps. Clusters were the
+most common reason when viewing a Hexagon Tile map, trend was the most
+common choice for choropleth displays except for the all cities
+display.}
+\end{figure}
+
+\hypertarget{contributors}{%
+\subsection{Contributors}\label{contributors}}
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf}
+\caption{The probablity of detection acheived by the contributors in
+each group is shown by the points. Group B has a larger range and a
+smaller inter-quartile range. Group A and both had 3 people who did not
+find any of the data maps in the displays.}
+\end{figure}
+
+\hypertarget{reason-1}{%
+\subsection{Reason}\label{reason-1}}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-6-1.pdf}
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/choices-1.pdf}
+\caption{Each facet is associated with one lineup, the height of the
+bars count the choices made by the participants considering each lineup.
+The bars coloured with black outlines show the map which contained a
+trend model, these are the correct choices. The numbers differentiate
+the replicates of each trend model and type of map display. Participants
+were able to select 0 to indicate they did not want to choose a map.}
+\end{figure}
+
+The choices made by participants are examined in Figure
+\ref{fig:choices}. Participants were misled by the choropleth display,
+but not the hexagon display for all cities displays except (2). The maps
+with a North West to South East trend was chosen with much greater
+frequency in all displays. All of three cities displays, except (4),
+were detected in the hexagon display. All except one lineup had at least
+one participant select the correct map in the lineup as shown in Figure
+\ref{fig:choices}.
+
+\hypertarget{anomolies}{%
+\subsection{Anomolies}\label{anomolies}}
+
+\hypertarget{modeling-the-difference}{%
+\subsection{Modeling the difference}\label{modeling-the-difference}}
+
+A generalized linear mixed effects model can account for each individual
+participants' abilities as it includes a subject-specific random
+intercept. As each participant provides results from 12 lineups.
+
+\hypertarget{detection-rates}{%
+\subsubsection{Detection Rates}\label{detection-rates}}
+
+\begin{verbatim}
+## # A tibble: 6 x 5
+##   term                                estimate std.error statistic p.value
+##   <chr>                                  <dbl>     <dbl>     <dbl>   <dbl>
+## 1 (Intercept)                           0.0217     0.147     0.147   0.883
+## 2 typeHexagon tiles                     0.420      0.211     1.99    0.047
+## 3 trendthree cities                    -3.25       0.412    -7.88    0    
+## 4 trendall cities                      -1.24       0.229    -5.41    0    
+## 5 typeHexagon tiles:trendthree cities   2.37       0.465     5.10    0    
+## 6 typeHexagon tiles:trendall cities     1.08       0.312     3.47    0.001
+\end{verbatim}
+
+\begin{verbatim}
+## Analysis of Deviance Table
+## 
+## Model: binomial, link: logit
+## 
+## Response: detect_f
+## 
+## Terms added sequentially (first to last)
+## 
+## 
+##            Df Deviance Resid. Df Resid. Dev  Pr(>Chi)    
+## NULL                        1103     1477.0              
+## type        1   83.526      1102     1393.5 < 2.2e-16 ***
+## trend       2  101.699      1100     1291.8 < 2.2e-16 ***
+## type:trend  2   35.517      1098     1256.2 1.939e-08 ***
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+\end{verbatim}
+
+\begin{verbatim}
+##            
+##             Incorrect Correct
+##   Incorrect       431     121
+##   Correct         242     310
+\end{verbatim}
+
+\begin{verbatim}
+## # A tibble: 1 x 6
+##   sigma logLik   AIC   BIC deviance df.residual
+##   <dbl>  <dbl> <dbl> <dbl>    <dbl>       <int>
+## 1 0.430  -675. 1367. 1407.    1321.        1096
+\end{verbatim}
+
+\begin{verbatim}
+## # A tibble: 8 x 5
+##   term                                estimate std.error statistic group      
+##   <chr>                                  <dbl>     <dbl>     <dbl> <chr>      
+## 1 (Intercept)                            0.505    0.0340     14.9  fixed      
+## 2 typeHexagon tiles                      0.103    0.0448      2.31 fixed      
+## 3 trendthree cities                     -0.467    0.0448    -10.4  fixed      
+## 4 trendall cities                       -0.277    0.0448     -6.19 fixed      
+## 5 typeHexagon tiles:trendthree cities    0.250    0.0633      3.95 fixed      
+## 6 typeHexagon tiles:trendall cities      0.239    0.0633      3.77 fixed      
+## 7 sd_(Intercept).contributor             0.118   NA          NA    contributor
+## 8 sd_Observation.Residual                0.430   NA          NA    Residual
+\end{verbatim}
+
+\begin{verbatim}
+##            
+##             Incorrect Correct
+##   Incorrect        49       1
+##   Correct         624     430
+\end{verbatim}
+
+For a base model of Choropleth map, using a NW-SE trend model. The
+detection rate for Hexagon tile maps using a NW-SE trend model changes
+the log odds of the detection by 0.42.
+
+\hypertarget{certainty-1}{%
+\subsubsection{Certainty}\label{certainty-1}}
+
+\begin{verbatim}
+## Linear mixed model fit by REML ['lmerMod']
+## Formula: detect ~ type * trend + (1 | contributor)
+##    Data: d
+## REML criterion at convergence: 1350.719
+## Random effects:
+##  Groups      Name        Std.Dev.
+##  contributor (Intercept) 0.1179  
+##  Residual                0.4296  
+## Number of obs: 1104, groups:  contributor, 92
+## Fixed Effects:
+##                         (Intercept)                    typeHexagon tiles  
+##                              0.5054                               0.1033  
+##                   trendthree cities                      trendall cities  
+##                             -0.4674                              -0.2772  
+## typeHexagon tiles:trendthree cities    typeHexagon tiles:trendall cities  
+##                              0.2500                               0.2391
+\end{verbatim}
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
+how do the results found generalise to other work - Not just for Aus
+(Canada new Zealand could also use this effective display)
+
+\begin{itemize}
+\tightlist
+\item
+  For USA alternative methods can also be helpful
+\end{itemize}
+
+\hypertarget{supplementary-materials}{%
+\section{Supplementary Materials}\label{supplementary-materials}}
+
+\hypertarget{training}{%
+\subsection{Training}\label{training}}
+
+\hypertarget{survey-application}{%
+\subsection{Survey application}\label{survey-application}}
+
+\hypertarget{subject-specific-anomolies-0-detection}{%
+\subsection{Subject specific anomolies (0\%
+detection)}\label{subject-specific-anomolies-0-detection}}
+
+\hypertarget{acknowledgment}{%
+\section{Acknowledgment}\label{acknowledgment}}
+
+The authors would like to thank\ldots{}
 
@@
 participating in this research.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Type\\
-\item
-  Trend
-\item
-  Interaction of type and trend
-\item
-  Demographics of participants
-\end{enumerate}
-
-The survey responses from participants were kept only if the participant
-submitted answers for all 12 displays. This resulted in 95 surveyed.
-
-\includegraphics{survey_files/figure-latex/unnamed-chunk-2-1.pdf}
-
-\includegraphics{survey_files/figure-latex/unnamed-chunk-4-1.pdf}
-
-\begin{verbatim}
-## # A tibble: 2 x 2
-##   gender     n
-##   <chr>  <int>
-## 1 He        70
-## 2 She       25
-\end{verbatim}
-
-\begin{verbatim}
-## # A tibble: 6 x 2
-##   age         n
-##   <chr>   <int>
-## 1 18 - 24    15
-## 2 25 - 34    37
-## 3 35 - 44    23
-## 4 45 - 54    11
-## 5 55+         6
-## 6 NA          3
-\end{verbatim}
-
-\begin{verbatim}
-## # A tibble: 3 x 2
-##   education       n
-##   <chr>       <int>
-## 1 Bach           56
-## 2 High School    25
-## 3 Masters        14
-\end{verbatim}
-
-\begin{verbatim}
-## # A tibble: 2 x 2
-##   australia     n
-##   <chr>     <int>
-## 1 No           93
-## 2 Yes           2
-\end{verbatim}
-
-\includegraphics{survey_files/figure-latex/unnamed-chunk-7-1.pdf} 11 of
-the 12 real distribution plots were found more often in the hexagon
-display. This was better than expected. As even geographic distributions
-were spotted in the hexagon lineup.
-
-\includegraphics{survey_files/figure-latex/unnamed-chunk-8-1.pdf}
-
-\begin{verbatim}
-## [1] 0.004079185
-\end{verbatim}
-
-\includegraphics{survey_files/figure-latex/unnamed-chunk-9-1.pdf}
-\includegraphics{survey_files/figure-latex/unnamed-chunk-9-2.pdf}
-
-\includegraphics{survey_files/figure-latex/unnamed-chunk-10-1.pdf}
-\includegraphics{survey_files/figure-latex/unnamed-chunk-10-2.pdf}
-
-\includegraphics{survey_files/figure-latex/unnamed-chunk-11-1.pdf}
-
-\hypertarget{probability-of-detection}{%
-\subsection{Probability of detection:}\label{probability-of-detection}}
-
-\hypertarget{time-taken}{%
-\subsection{Time taken}\label{time-taken}}
-
-\hypertarget{modeling-1}{%
-\subsection{Modeling}\label{modeling-1}}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-The conclusion goes here.
-
-\hypertarget{acknowledgment}{%
-\section{Acknowledgment}\label{acknowledgment}}
-
-The authors would like to thank\ldots{}
 
@@
 \href{\%7Bhttps://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)\%7D}{\{https://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian   Statistical Geography Standard (ASGS)\}}.
+
+\leavevmode\hypertarget{ref-lme4}{}%
+Bates, Douglas, Martin Mächler, Ben Bolker, and Steve Walker. 2015.
+``Fitting Linear Mixed-Effects Models Using lme4.'' \emph{Journal of
+Statistical Software} 67 (1): 1--48.
+\url{https://doi.org/10.18637/jss.v067.i01}.
 
@@
 
+\leavevmode\hypertarget{ref-VVSIALM}{}%
+Majumder, Mahbubul, Heike Hofmann, and Dianne Cook. 2013. ``Validation
+of Visual Statistical Inference, Applied to Linear Models.''
+\emph{Journal of the American Statistical Association} 108 (503):
+942--56. \url{https://doi.org/10.1080/01621459.2013.808157}.
+
+\leavevmode\hypertarget{ref-RCore}{}%
+R Core Team. 2019. \emph{R: A Language and Environment for Statistical
+Computing}. Vienna, Austria: R Foundation for Statistical Computing.
+\url{https://www.R-project.org/}.
+
 \end{document}

### 2020-01-02 paper/paper.Rmd
title change

@@
 ---
-title: "Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference"
+title: "Land doesn't get cancer, people do: an experiment comparing the effectiveness of two displays"
 affiliation:

### 2020-01-02 paper/paper.tex
title change

@@
 \hypersetup{
-            pdftitle={Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference},
+            pdftitle={Land doesn't get cancer, people do: an experiment comparing the effectiveness of two displays},
             pdfkeywords={statistics, visual inference, geospatial, population},
@@
 % Do not put math or special symbols in the title.
-\title{Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison
-using visual inference}
+\title{Land doesn't get cancer, people do: an experiment comparing the
+effectiveness of two displays}
 

### 2020-01-05 paper/paper.Rmd
paper changes

--- 2019-12-25 paper/paper.Rmd
@@
 ---
-title: "Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference"
+title: "Communicating human related spatial distributions: A comparison of spatial visualisations using visual inference."
 affiliation:
@@
 editor_options: 
-  chunk_output_type: inline
+  chunk_output_type: console
 link-citations: yes
@@
 
-## Australian Cancer Atlas
+## The Australian Cancer Atlas
 
-The Australian Cancer Atlas explores the burden of cancer on Australian communities. There are many cancer types presented, and they can be explored on an individual or aggregate level. 
-The Australian communities are examined at the Statistical Areas at Level 2 (SA2)[@abs2016] used by the Australian Bureau of Statistics.
-Bayesian spatial smoothing has been applied to incorporate the statistics of neighbouring areas, for both privacy and stability of the estimates.
+The Australian Cancer Atlas is an online interactive webtool created to explore the burden of cancer on Australian communities.
+There are many cancer types presented, and they can be explored on an individual or aggregate level.
+The Australian communities are examined at the Statistical Areas at Level 2 (SA2) [@abs2016] used by the Australian Bureau of Statistics.
+Bayesian spatial smoothing has been applied to incorporate the value of the statistics of the neighbouring areas.
+Spatial smoothing allows for the protection privacy and gives stability to the estimates.
 The statistics that can be mapped are the diagnoses (Standardised Incidence Rates) and excess deaths for each SA2, communicated as the difference from the Australian average of the statistics.
-The values of the statistic for each are communicated using a diverging colour scheme.
+The values of the statistic for each geographic area is communicated through the colour used to fill the areas, the colours are chosen for the diverging colour scheme.
 
@@
 
-## Methodology
-
-Spatial visualisations
- - Choropleth
-However, the issue of using a choropleth map base becomes obvious when considering the distributions.
- Position is extremely important for analysis of a visualisation.
-
 ## Population focussed displays
 
+Spatial visualisations communicate the distribution of statistics over geographic space.
+The most common display for spatial data is the choropleth map.
+However, the issue of using a choropleth map base becomes obvious when considering the distributions.
 Map creators have the ability to present spatial statistics in alternative displays that can highlight the population.
@@
 <!-- Figure Choro and Hex tile for Aus-->
+
+## Methodology
 
@@
 -->
+
+The mean of the detection rate for choropleth map, denoted as $\mu_C$, and the hexagon tile maps, $\mu_H$ will be contrasted. This leads to the following one sided hypothesis for this study:
+
+$H_0$ : $\mu_H$ = $\mu_C$
+$H_a$ : $\mu_H$ > $\mu_C$
+
+The detection rate $\hat\pi$ is calculated as the amount of people that made the choice of plot that contained the real data, out of the participants who saw data plot in the lineup of the null data plots.
+
+The difference in the detection rates for the two displays will be compared using the following:
+
+$$ \hat\pi_C - \hat\pi_H \pm t_{1-\alpha,n-1}\sqrt{\hat\pi_C(1-\hat\pi_C)/n_C + \hat\pi_H(1-\hat\pi_H)/n_H} $$
 
@@
 library(RColorBrewer)
+library(visreg)
+library(emmeans)
 
-invthm <- theme(
-  panel.background = element_rect(fill = "transparent", colour = NA), 
-  plot.background = element_rect(fill = "transparent", colour = NA),
-  legend.background = element_rect(fill = "transparent", colour = NA),
-  legend.key = element_rect(fill = "transparent", colour = NA),
-  text = element_text(colour = "white", size = 20),
-  axis.text = element_text(colour = "white", size = 20)
-)
-
-trend_colours <- c("NW-SE" = "#B2DF8A",
+trend_colours <- c(
+  "NW-SE" = "#B2DF8A",
   "three cities" = "#A6CEE3",
   "all cities" = "#1F78B4")
+
+type_colours <- c(
+  "Choro." = "#fcae91",
+  "Hex." = "#a50f15")
+
+detect_colours <- c(
+  "No" = "#66C2A5",
+  "Yes" = "#FC8D62")
 
@@
 
-# Now remove contributors who did not provide answers to most questions
+# Remove contributors who did not provide answers to most questions
 keep <- d %>% count(contributor, sort = TRUE) %>% filter(n > 10)
@@
   filter(contributor != "1234567890")
+
+# Remove contributors who did not provide any choices
+bad_contribs <- d %>% group_by(contributor) %>% 
+  summarise(sum0 = sum(choice)) %>% 
+  filter(sum0 == 0) %>% 
+  pull(contributor)
+
+d <- d %>% 
+  filter(!(contributor %in% bad_contribs))
 
@@
 
-The survey responses from participants were kept only if the participant submitted answers for all 12 displays. This resulted in 95 participants.
+The survey responses from participants were kept only if the participant submitted answers for all 12 displays. This resulted in 92 participants.
 
 ```{r reps}
-# Augment
-# add data replication number
-# d %>% count(image_name) %>% print(n=24)
-# image code <--> rep
 replicate <- tibble(image_name = c("aus_cities_12_geo.png", "aus_cities_12_hex.png", 
@@
 d <- d %>% left_join(., replicate, by = "image_name")
-#d %>% count(group, image_name, sort=TRUE)`
-
-contribs_responses <- d %>%
-  group_by(group, contributor) %>% 
-  filter(sum(choice) == 0) %>% 
-  summarise(pdetect = mean(detect, na.rm = TRUE))
-
-d <- d %>% 
-  filter(!(contributor %in% contribs_responses$contributor))
 ```
 
-The contributors who detected no plots correctly were analysed further.
-Three of these contribuotrs gave no choices for any of the twelve displays.
-They were also removed for the rest of the analysis.
 The contributors who gave various plot choices and reasons for the twelve displays were kept.
+The contributors who detected no plots correctly were analysed further. Three of these contribuotrs gave no choices for any of the twelve displays. They were also removed for the rest of the analysis.
 
-## Demographics:
-
-```{r demogs}
-# Create one record for each contributor, to examine demographics
-dem_contribs <- d %>%
-  group_by(contributor) %>%
-  slice(1) %>% ungroup()
-
-###############################################################################
-# Demographics of contributors
-#dem_contribs %>% count(gender)
-dem_contribs %>% count(age, name = "participants")
-dem_contribs %>% count(gender, education) %>% 
-  spread(gender, n) %>% 
-  mutate(`Col. Total` = He + She) %>% 
-  gather("Gender", "Amount", He:`Col. Total`) %>% 
-  spread(education, Amount) %>% 
-  mutate(`Row Total` = Bach + `High School`, Masters,
-    Gender = factor(Gender, levels = c("He", "She", "Col. Total"), labels = c("He", "She", "Col. Total"))) %>% knitr::kable(format = "latex")
-```
-70 of the 95 participants were male, and 25 female and only two of the participants had lived in Australia before.
-
-70 of the participants achieved a Bachelors or Masters degree.
+Of the 92 participants, 67 were male, and 25 female. Only two of the participants had lived in Australia before.
+The education level achieved by the participants was 70 Bachelors or Masters degree.
 
@@
 
-The detection rate is used to find the accuracy for participants reporting the real data trend model. The accuracy can be seen from many views.
+The detection rate for participants reporting the real data trend model is used to calculate the accuracy of the responses of participants.
 
@@
   mutate(type = case_when(
-    type == "hex" ~"Hexagon tiles",
-    TRUE~"Choropleth")) %>% 
-    mutate(detect_f = factor(detect, levels = c(0,1), labels = c("Incorrect", "Correct")))
+    type == "hex" ~"Hex.",
+    TRUE~"Choro.")) %>% 
+    mutate(detect_f = factor(detect, levels = c(0,1), labels = c("No", "Yes")))
 
@@
 
-```{r pdetection_trend, eval = FALSE}
-plots %>% ggplot(aes(x = group, y = pdetect)) + 
-  geom_boxplot() + 
-  geom_jitter(width = 0.1) +
-  ylab("Detection rate") + 
-  ylim(c(0,1))
-
-plots %>% ggplot(aes(x = trend, y = pdetect, fill = trend)) + 
-  geom_boxplot() + 
-  scale_fill_manual(values = trend_colours) +
-  geom_jitter(width = 0.1) +
-  ylab("Detection rate") + 
-  ylim(c(0,1))
-
-plots %>% ggplot(aes(x = type, y = pdetect)) + 
-  geom_boxplot() + 
-  geom_jitter(width = 0.1) +
-  ylab("Detection rate") + 
-  ylim(c(0,1))
-```
-
-```{r detection_compare, fig.cap = "Each point shows the probability of detection for the lineup display, separated by the trend model hidden in the lineup.
-The points for the same data set are linked to show the difference in the detection rate when the same data was seen in each display.
-11 of the 12 real distribution plots were found more often in the hexagon display."}
+```{r detection_compare, fig.cap = "The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models.
+Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup.
+The points for the same data set shown in a choroleth or haxgon tile map display are linked to show the difference in the detection rate."}
 # Detectability rate for each lineup (image)
@@
 ```
+The detection rates are usually higher when participants viewed the hexagon tile map displays.
+The difference was greater when viewing a three cities trend model.
+When the trend model affected all cities participants also detected the data display in the lineup of null plots more often.
+The North West to South East data plot was detected with similar rates when viewing the choropleth and  hexagon tile map displays, though for three of the replicates the participants detected the data display more often.
 
@@
   group_by(trend, type, replicate) %>%
-  summarise(mean = round(mean(time_taken),2), std.dev = round(sd(time_taken), 2)) %>% 
+  summarise(mean = round(mean(time_taken),2), 
+    std.dev = round(sd(time_taken), 2)) %>% 
   knitr::kable(format = "latex")
@@
 diffs <- d_smry %>% spread(type, pdetect) %>%
-  mutate(dif = `Hexagon tiles` - `Choropleth`)
+  mutate(dif = `Hex.` - `Choro.`)
 
@@
 
-```{r time, fig.cap = "The time taken to evaluate each display is broken into five second windows.
+```{r hist_height, fig.cap = "The time taken to evaluate each display is broken into five second windows.
 The height of the histogram bars show how many evaulations were submitted within each time window.
@@
 No response took over one minute."}
-d_time <- d %>% 
-  group_by(trend, type, location, replicate) %>%
-  summarise(m = mean(time_taken), s = sd(time_taken))
-#d_time %>% print(n=24)
-
-ggplot(d, 
-  aes(x = time_taken, fill = detect_f)) + xlim(0,65) +
+ggplot(d, aes(x = time_taken, fill = detect_f, group = detect_f)) + 
   scale_fill_brewer(palette = "Dark2") +
-  geom_histogram(alpha = 0.4, binwidth = 5, boundary = 0, position = "dodge") + 
-  labs(x = "Time taken (Seconds)", y = "Amount of evaluations") + facet_wrap(~ type)
+  geom_histogram(binwidth = 5, boundary = 0) +
+  facet_grid(type ~ trend) +
+  labs(x = "Time taken (Seconds)", y = "Amount of evaluations") + 
+  guides(fill = FALSE)
 ```
 
-```{r time_compare, fig.cap = "Each point shows the average time taken for participants to evalute the lineup display, separated by the trend model hidden in the lineup.
-The points for the same data set are linked to show the difference in the avergae time taken when the same data was seen in each display.
-There is a lot of variation in the time taken.
-The shortest average time (15 seconds), and the longest average time (23 seconds) both occured when evaluating three cities"}
-# Visual summary
-ggplot(d_time, aes(x = type, y = m, colour = trend)) +
-  geom_point(size = 3) +  
-  geom_line(size = 1, aes(group = replicate)) +  
-  facet_wrap(~ trend) +  
-  scale_colour_manual(values = trend_colours) +
-  xlab("Type of areas visualised") +
-  ylab("Average time taken") + 
+```{r hist_fill, fig.cap = "The time taken to evaluate each display is broken into five second windows.
+The height of the histogram bars show the proportion of evaulations that were submitted within each time window."}
+ggplot(d, aes(x = time_taken, fill = detect_f, group = detect_f)) + 
+  scale_fill_brewer(palette = "Dark2") +
+  geom_histogram(binwidth = 5, boundary = 0, position = "fill") +
+  facet_grid(type ~ trend) +
+  labs(x = "Time taken (Seconds)", y = "Proportion of evaluations") + 
+  guides(fill = FALSE)
+```
+
+```{r}
+ggplot(d, aes(x = time_taken, colour = detect_f, group = detect_f)) + 
+  scale_colour_brewer(palette = "Dark2") +
+  geom_freqpoly(binwidth = 3) +
+  facet_grid(type ~ trend) +
+  scale_fill_manual(values = detect_colours) +
+  labs(x = "Time taken (Seconds)", y = "Amount of evaluations") +
   guides(colour = FALSE)
@@
 ggplot(d,
-  aes(x = certainty, fill = detect)) +
+  aes(x = certainty, fill = detect_f)) +
   scale_fill_brewer(palette = "Set2") +
-  geom_bar(position = "dodge") + facet_wrap(~type) + guides(fill = FALSE)
+  geom_bar() + facet_wrap(~trend) + guides(fill = FALSE)
 ```
@@
 assessments by the participant ‘how certain are you about your choice?’.
-
-```{r, fig.cap = "The amount of times each level of certainty was chosen by participants.
-The columns shown whether a viewer correctly selected the real trend data plot when viewing hexagon tile map or choropleth displays."}
-ggplot(d,
-  aes(x = certainty)) +
-  scale_fill_manual(values = trend_colours) +
-  geom_bar(position = "dodge") + facet_grid(type ~ detect)
-# certainty wasn't affected by the trend
-```
-
-```{r, fig.cap = "The amount of times each level of certainty was chosen by participants.
-The columns shown whether a viewer correctly selected the real trend data plot when viewing hexagon tile map or choropleth displays.
-The rows show the type of the trend model added in the real data plot.
-The default certainty level of 3 was chosen most frequently when incorrect.
-Then shown a NW-SE or all cities trend participants felt more certain of their correct choice."}
-ggplot(d, 
-  aes(x = certainty, fill = trend)) +
-  scale_fill_manual(values = trend_colours) +
-  geom_bar(position = "dodge") + facet_grid(trend ~ detect)
-```
 
@@
 ggplot(d) + 
-  geom_bar(aes(x = reason)) +  
-  facet_grid(trend ~ type) +  
-  scale_colour_manual(values = trend_colours) +
+  geom_bar(aes(x = reason, fill = type), position = "dodge") +  
+  facet_grid(~detect_f) +  
+  scale_colour_manual(values = type_colours) +
   xlab("Type of areas visualised") + 
@@
 ggplot(d %>% mutate(detect = factor(detect, levels = c(0,1), 
-  labels = c("Incorrect", "Correct")))) + 
+  labels = c("No", "Yes")))) + 
   geom_bar(aes(x = reason)) +  
@@
 
-```{r choices, fig.height = 12, fig.width = 12, fig.cap = "Each facet is associated with one lineup, the height of the bars count the choices made by the participants considering each lineup.
-The bars coloured with black outlines show the map which contained a trend model, these are the correct choices.
+```{r choices, fig.height = 12, fig.width = 12, fig.cap = "Each facet is associated with one lineup, the height of the points show the proportion of the participants that made each choice when considering each lineup.
+The points coloureddark blue show the map which contained a trend model, these are the correct choices.
 The numbers differentiate the replicates of each trend model and type of map display.
@@
 "}
-detect_colours <- c("Incorrect" = "#33A02C", "Correct" = "#B2DF8A")
-d %>% mutate(repl = paste(type, trend, " (", replicate, ") " ,  sep = "")) %>% 
+d %>% 
+  count(type, trend, choice, replicate, choice, detect_f) %>% 
+  group_by(type, trend, replicate) %>% 
+  mutate(prop = n/sum(n)) %>% 
+  mutate(repl = paste(replicate, ": ", trend,  sep = "")) %>%
+  mutate(bottom = 0) %>% 
   ggplot() + 
-  geom_bar(aes(x = choice, fill = detect_f, color = detect_f), boundary = 0) + 
-  facet_wrap(~ repl, 
-    drop = TRUE, as.table = TRUE, ncol = 4) +
-  scale_colour_grey(start = 0.9, end = 0.1) +
-  scale_fill_manual(values = detect_colours) +
-  theme(legend.position = "bottom") + guides(colour = FALSE, fill = FALSE) +
-  labs(x = "Choice of plot in lineup", y = "Amount of choices")
+  geom_point(aes(x = choice, y = prop, color = detect_f), boundary = 0, size =2) + 
+  geom_segment(aes(x = choice, xend = choice, y = bottom, yend = prop, colour = detect_f)) +
+  facet_grid(replicate + type ~ trend, 
+    drop = TRUE, as.table = TRUE, scales = "free_y") +
+  labs(x = "Choice of plot in lineup", y = "Amount of choices") +
+  scale_colour_manual(values = detect_colours) +
+  scale_x_continuous(breaks = seq(from = 0, to = 12)) +
+  scale_y_continuous(breaks = seq(from = 0.0, to = 1.0, by = 0.1)) +
+  theme(legend.position = "bottom") + guides(colour = FALSE, fill = FALSE)
 ```
@@
 
+This includes the two main effects map type and trend model, which gives the fixed effects part of the model to be
+
+$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3$$
+
+where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
+We are allowing for an interaction between map type and trend model.
+Because the response is binary, a logistic model is used.
+
 ### Detection Rates
@@
 
-tidy(glm1) %>% mutate(p.value = round(p.value, 3))
+factors <- c("Design", "", "Trend", "", "Interactions", "")
+terms <- c("Choro", "Hex", "Three cities", "All cities", "Hex : Three cities", "Hex : All cities")
 
-anova(glm1, test="Chisq")
+tidy(glm1) %>% 
+  mutate(p.value = round(p.value, 4)) %>%
+  mutate(sig = case_when(
+    p.value <= 0.001 ~ "***", 
+    p.value <= 0.01 ~ "**", 
+    p.value <= 0.05 ~ "*", 
+    p.value <= 0.01 ~ ".",
+    TRUE ~ " ")) %>% 
+  mutate(term = terms,
+    factors = factors) %>% 
+  select(`_` = factors, 
+    terms = term, 
+    Estimate = estimate, 
+    Error = std.error, 
+    p.value, sig) %>% knitr::kable(format = "latex", 
+      align = "lrrrrl")
+```
 
+```{r}
 d_glm <- d %>% select(group:certainty, detect, detect_f) %>%
@@
     predicted = ifelse(pfit > 0.5, 1, 0),
-    predicted = factor(predicted, levels = c(0,1), labels = c("Incorrect", "Correct")))
+    predicted = factor(predicted, levels = c(0,1), 
+      labels = c("No", "Yes")))
 
 table(d_glm$predicted, d_glm$detect_f)
+```
+
+This gives the model:
+
+$$\widehat{y_{ij}} = 0.0217 + 0.42Hex -3.25_{three} -1.24_{all} + 2.37{Hex.three} + 1.08{Hex.all} $$
+
+```{r}
+emmean_obj1 <- emmeans(glm1, c("trend", "type"),
+                        type = "response")
+
+int_1 <- confint(emmean_obj1, by = c("trend"), adjust = "bonferroni")
+int_1 %>% 
+  ggplot(aes(x= type, y = prob, group = trend)) + 
+  geom_point(aes(col = type)) + 
+  geom_line(alpha = 0.5, lty = "dashed") + 
+  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL, col = type), 
+                width = 0.2) + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
+        strip.text.y = element_text(angle = 0),
+        legend.position = "none",
+        axis.title.x = element_blank()) + 
+  ylab("Estimated Marginal Mean")
 ```
@@
     predicted = ifelse(pfit_lmer > 0.5, 1, 0),
-    predicted = factor(predicted, levels = c(0,1), labels = c("Incorrect", "Correct")))
+    predicted = factor(predicted, levels = c(0,1), labels = c("No", "Yes")))
 
@@
 The detection rate for Hexagon tile maps using a NW-SE trend model changes the log odds of the detection by 0.42.
+
+```{r}
+# Mixed effects models
+lmer2 <- lmer(detect ~ (type|trend), data = d)
+lmer2_d <- augment(lmer2, d)
+
+preds_lmer2 <- predict(lmer2, newdata = d)
+pfit_lmer2 <- exp(preds_lmer2)/(1+exp(preds_lmer2))
+
+glance(lmer2)
+tidy(lmer2)
+
+d_lmer2 <- d %>% select(group:certainty, detect, detect_f) %>%
+  bind_cols(as_tibble(se.bands)) %>% 
+  mutate(pfit_lmer2, 
+    predicted = ifelse(pfit_lmer2 > 0.5, 1, 0),
+    predicted = factor(predicted, levels = c(0,1), labels = c("No", "Yes")))
+
+table(d_lmer2$predicted, d_lmer2$detect_f)
+```
+
+```{r}
+visreg(lmer2, "type", by = "trend", scale = "response", re.form = ~(type|trend))
+```
 
@@
 
+## Overall Performance
+
+```{r pdetection_trend, eval = FALSE}
+plots %>% ggplot(aes(x = group, y = pdetect)) + 
+  geom_boxplot() + 
+  geom_jitter(width = 0.1) +
+  ylab("Detection rate") + 
+  ylim(c(0,1))
+
+plots %>% ggplot(aes(x = trend, y = pdetect, fill = trend)) + 
+  geom_boxplot() + 
+  scale_fill_manual(values = trend_colours) +
+  geom_jitter(width = 0.1) +
+  ylab("Detection rate") + 
+  ylim(c(0,1))
+
+plots %>% ggplot(aes(x = type, y = pdetect)) + 
+  geom_boxplot() + 
+  geom_jitter(width = 0.1) +
+  ylab("Detection rate") + 
+  ylim(c(0,1))
+```
+
 ## Subject specific anomolies (0% detection)
+
+## Demographics:
+
+```{r demogs}
+# Create one record for each contributor, to examine demographics
+dem_contribs <- d %>%
+  group_by(contributor) %>%
+  slice(1) %>% ungroup()
+
+###############################################################################
+# Demographics of contributors
+#dem_contribs %>% count(gender)
+dem_contribs %>% ggplot() + geom_bar(aes(age))
+dem_contribs %>% count(gender)
+dem_contribs %>% count(education)
+dem_contribs %>% count(gender, education) %>% 
+  spread(gender, n) %>% 
+  mutate(`Col. Total` = He + She) %>% 
+  gather("Gender", "Amount", He:`Col. Total`) %>% 
+  spread(education, Amount) %>% 
+  mutate(`Row Total` = Bach + `High School`, Masters,
+    Gender = factor(Gender, levels = c("He", "She", "Col. Total"), labels = c("He", "She", "Col. Total"))) %>% knitr::kable(format = "latex")
+```
 

### 2020-01-05 paper/paper.tex
paper changes

--- 2019-12-25 paper/paper.tex
@@
 \hypersetup{
-            pdftitle={Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference},
+            pdftitle={Communicating human related spatial distributions: A comparison of spatial visualisations using visual inference.},
             pdfkeywords={statistics, visual inference, geospatial, population},
@@
 % Do not put math or special symbols in the title.
-\title{Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison
-using visual inference}
+\title{Communicating human related spatial distributions: A comparison of
+spatial visualisations using visual inference.}
 
@@
 
-\hypertarget{australian-cancer-atlas}{%
-\subsection{Australian Cancer Atlas}\label{australian-cancer-atlas}}
-
-The Australian Cancer Atlas explores the burden of cancer on Australian
-communities. There are many cancer types presented, and they can be
-explored on an individual or aggregate level. The Australian communities
-are examined at the Statistical Areas at Level 2 (SA2)(``Australian
-Statistical Geography Standard (ASGS)''
-\protect\hyperlink{ref-abs2016}{2018}) used by the Australian Bureau of
-Statistics. Bayesian spatial smoothing has been applied to incorporate
-the statistics of neighbouring areas, for both privacy and stability of
-the estimates. The statistics that can be mapped are the diagnoses
-(Standardised Incidence Rates) and excess deaths for each SA2,
+\hypertarget{the-australian-cancer-atlas}{%
+\subsection{The Australian Cancer
+Atlas}\label{the-australian-cancer-atlas}}
+
+The Australian Cancer Atlas is an online interactive webtool created to
+explore the burden of cancer on Australian communities. There are many
+cancer types presented, and they can be explored on an individual or
+aggregate level. The Australian communities are examined at the
+Statistical Areas at Level 2 (SA2) (``Australian Statistical Geography
+Standard (ASGS)'' \protect\hyperlink{ref-abs2016}{2018}) used by the
+Australian Bureau of Statistics. Bayesian spatial smoothing has been
+applied to incorporate the value of the statistics of the neighbouring
+areas. Spatial smoothing allows for the protection privacy and gives
+stability to the estimates. The statistics that can be mapped are the
+diagnoses (Standardised Incidence Rates) and excess deaths for each SA2,
 communicated as the difference from the Australian average of the
-statistics. The values of the statistic for each are communicated using
-a diverging colour scheme.
+statistics. The values of the statistic for each geographic area is
+communicated through the colour used to fill the areas, the colours are
+chosen for the diverging colour scheme.
 
@@
 
-\hypertarget{methodology}{%
-\subsection{Methodology}\label{methodology}}
-
-Spatial visualisations - Choropleth However, the issue of using a
-choropleth map base becomes obvious when considering the distributions.
-Position is extremely important for analysis of a visualisation.
-
 \hypertarget{population-focussed-displays}{%
@@
 
-Map creators have the ability to present spatial statistics in
-alternative displays that can highlight the population. This work aims
-to show that a hexagon tile map display is a viable alternative to the
-geographic map base for presenting population statistics. The same data
-were shown on a choropleth map, and on a hexagon tile map. Comparing the
-results of participants who see the choropleth to those who see a
-hexagon tile map will show that population related distributions are
-spotted more frequently in a hexagon tile map display.
+Spatial visualisations communicate the distribution of statistics over
+geographic space. The most common display for spatial data is the
+choropleth map. However, the issue of using a choropleth map base
+becomes obvious when considering the distributions. Map creators have
+the ability to present spatial statistics in alternative displays that
+can highlight the population. This work aims to show that a hexagon tile
+map display is a viable alternative to the geographic map base for
+presenting population statistics. The same data were shown on a
+choropleth map, and on a hexagon tile map. Comparing the results of
+participants who see the choropleth to those who see a hexagon tile map
+will show that population related distributions are spotted more
+frequently in a hexagon tile map display.
 
@@
 areas.
+
+\hypertarget{methodology}{%
+\subsection{Methodology}\label{methodology}}
 
@@
 included exploration of the difficulty experienced by participants
+
+The mean of the detection rate for choropleth map, denoted as \(\mu_C\),
+and the hexagon tile maps, \(\mu_H\) will be contrasted. This leads to
+the following one sided hypothesis for this study:
+
+\(H_0\) : \(\mu_H\) = \(\mu_C\) \(H_a\) : \(\mu_H\) \textgreater{}
+\(\mu_C\)
+
+The detection rate \(\hat\pi\) is calculated as the amount of people
+that made the choice of plot that contained the real data, out of the
+participants who saw data plot in the lineup of the null data plots.
+
+the difference in the detection rates for the two displays will be
+compared using the following:
+
+\[ \hat\pi_C - \hat\pi_H \pm t_{1-\alpha,n-1}\sqrt{\hat\pi_C(1-\hat\pi_C)/n_C + \hat\pi_H(1-\hat\pi_H)/n_H} \]
 
@@
 The survey responses from participants were kept only if the participant
-submitted answers for all 12 displays. This resulted in 95 participants.
+submitted answers for all 12 displays. This resulted in 92 participants.
 
@@
 
-\hypertarget{demographics}{%
-\subsection{Demographics:}\label{demographics}}
-
-\begin{verbatim}
-## # A tibble: 6 x 2
-##   age     participants
-##   <chr>          <int>
-## 1 18 - 24           14
-## 2 25 - 34           37
-## 3 35 - 44           21
-## 4 45 - 54           11
-## 5 55+                6
-## 6 NA                 3
-\end{verbatim}
-
-\begin{tabular}{l|r|r|r|r}
-\hline
-Gender & Bach & High School & Masters & Row Total\\
-\hline
-Col. Total & 56 & 23 & 13 & 79\\
-\hline
-He & 39 & 19 & 9 & 58\\
-\hline
-She & 17 & 4 & 4 & 21\\
-\hline
-\end{tabular}
-
-70 of the 95 participants were male, and 25 female and only two of the
+67 of the 92 participants were male, and 25 female and only two of the
 participants had lived in Australia before.
@@
 \includegraphics{paper_files/figure-latex/detection_compare-1.pdf}
-\caption{Each point shows the probability of detection for the lineup
-display, separated by the trend model hidden in the lineup. The points
-for the same data set are linked to show the difference in the detection
-rate when the same data was seen in each display. 11 of the 12 real
-distribution plots were found more often in the hexagon display.}
+\caption{Contrasting the detection rate achieved by participants when
+viewing the four replicates of the three trend models. Each point shows
+the probability of detection for the lineup display, the facets separate
+the trend models hidden in the lineup. The points for the same data set
+shown in a choroleth or haxgon tile map display are linked to show the
+difference in the detection rate.}
 \end{figure}
@@
 \hline
-NW-SE & Choropleth & 1 & 25.00 & 16.41\\
-\hline
-NW-SE & Choropleth & 2 & 21.12 & 15.28\\
-\hline
-NW-SE & Choropleth & 3 & 21.12 & 17.05\\
-\hline
-NW-SE & Choropleth & 4 & 21.20 & 14.52\\
-\hline
-NW-SE & Hexagon tiles & 1 & 19.53 & 14.56\\
-\hline
-NW-SE & Hexagon tiles & 2 & 21.95 & 16.42\\
-\hline
-NW-SE & Hexagon tiles & 3 & 22.02 & 16.12\\
-\hline
-NW-SE & Hexagon tiles & 4 & 18.17 & 14.51\\
-\hline
-three cities & Choropleth & 1 & 15.30 & 13.88\\
-\hline
-three cities & Choropleth & 2 & 25.22 & 14.36\\
-\hline
-three cities & Choropleth & 3 & 22.49 & 15.87\\
-\hline
-three cities & Choropleth & 4 & 18.68 & 13.74\\
-\hline
-three cities & Hexagon tiles & 1 & 20.37 & 17.02\\
-\hline
-three cities & Hexagon tiles & 2 & 19.95 & 16.59\\
-\hline
-three cities & Hexagon tiles & 3 & 20.02 & 17.19\\
-\hline
-three cities & Hexagon tiles & 4 & 18.02 & 16.93\\
-\hline
-all cities & Choropleth & 1 & 20.14 & 16.56\\
-\hline
-all cities & Choropleth & 2 & 22.75 & 14.72\\
-\hline
-all cities & Choropleth & 3 & 19.88 & 15.03\\
-\hline
-all cities & Choropleth & 4 & 19.33 & 16.15\\
-\hline
-all cities & Hexagon tiles & 1 & 19.83 & 15.87\\
-\hline
-all cities & Hexagon tiles & 2 & 16.96 & 14.65\\
-\hline
-all cities & Hexagon tiles & 3 & 19.21 & 15.27\\
-\hline
-all cities & Hexagon tiles & 4 & 20.03 & 15.11\\
+NW-SE & Choro. & 1 & 25.00 & 16.41\\
+\hline
+NW-SE & Choro. & 2 & 21.12 & 15.28\\
+\hline
+NW-SE & Choro. & 3 & 21.12 & 17.05\\
+\hline
+NW-SE & Choro. & 4 & 21.20 & 14.52\\
+\hline
+NW-SE & Hex. & 1 & 19.53 & 14.56\\
+\hline
+NW-SE & Hex. & 2 & 21.95 & 16.42\\
+\hline
+NW-SE & Hex. & 3 & 22.02 & 16.12\\
+\hline
+NW-SE & Hex. & 4 & 18.17 & 14.51\\
+\hline
+three cities & Choro. & 1 & 15.30 & 13.88\\
+\hline
+three cities & Choro. & 2 & 25.22 & 14.36\\
+\hline
+three cities & Choro. & 3 & 22.49 & 15.87\\
+\hline
+three cities & Choro. & 4 & 18.68 & 13.74\\
+\hline
+three cities & Hex. & 1 & 20.37 & 17.02\\
+\hline
+three cities & Hex. & 2 & 19.95 & 16.59\\
+\hline
+three cities & Hex. & 3 & 20.02 & 17.19\\
+\hline
+three cities & Hex. & 4 & 18.02 & 16.93\\
+\hline
+all cities & Choro. & 1 & 20.14 & 16.56\\
+\hline
+all cities & Choro. & 2 & 22.75 & 14.72\\
+\hline
+all cities & Choro. & 3 & 19.88 & 15.03\\
+\hline
+all cities & Choro. & 4 & 19.33 & 16.15\\
+\hline
+all cities & Hex. & 1 & 19.83 & 15.87\\
+\hline
+all cities & Hex. & 2 & 16.96 & 14.65\\
+\hline
+all cities & Hex. & 3 & 19.21 & 15.27\\
+\hline
+all cities & Hex. & 4 & 20.03 & 15.11\\
 \hline
@@
 \centering
-\includegraphics{paper_files/figure-latex/time-1.pdf}
+\includegraphics{paper_files/figure-latex/hist_height-1.pdf}
 \caption{The time taken to evaluate each display is broken into five
@@
 \centering
-\includegraphics{paper_files/figure-latex/time_compare-1.pdf}
-\caption{Each point shows the average time taken for participants to
-evalute the lineup display, separated by the trend model hidden in the
-lineup. The points for the same data set are linked to show the
-difference in the avergae time taken when the same data was seen in each
-display. There is a lot of variation in the time taken. The shortest
-average time (15 seconds), and the longest average time (23 seconds)
-both occured when evaluating three cities}
+\includegraphics{paper_files/figure-latex/hist_fill-1.pdf}
+\caption{The time taken to evaluate each display is broken into five
+second windows. The height of the histogram bars show the proportion of
+evaulations that were submitted within each time window.}
 \end{figure}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}
 
@@
 \centering
-\includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}
+\includegraphics{paper_files/figure-latex/unnamed-chunk-2-1.pdf}
 \caption{The amount of times each level of certainty was chosen by
@@
 
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/unnamed-chunk-2-1.pdf}
-\caption{The amount of times each level of certainty was chosen by
-participants. The columns shown whether a viewer correctly selected the
-real trend data plot when viewing hexagon tile map or choropleth
-displays.}
-\end{figure}
+\hypertarget{reason}{%
+\subsection{Reason}\label{reason}}
 
@@
 \includegraphics{paper_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{The amount of times each level of certainty was chosen by
-participants. The columns shown whether a viewer correctly selected the
-real trend data plot when viewing hexagon tile map or choropleth
-displays. The rows show the type of the trend model added in the real
-data plot. The default certainty level of 3 was chosen most frequently
-when incorrect. Then shown a NW-SE or all cities trend participants felt
-more certain of their correct choice.}
-\end{figure}
-
-\hypertarget{reason}{%
-\subsection{Reason}\label{reason}}
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/unnamed-chunk-4-1.pdf}
 \caption{The most common reason for choice of plot when looking at each
@@
 \centering
-\includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf}
+\includegraphics{paper_files/figure-latex/unnamed-chunk-4-1.pdf}
 \caption{The probablity of detection acheived by the contributors in
@@
 
-\includegraphics{paper_files/figure-latex/unnamed-chunk-6-1.pdf}
+\includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf}
 
@@
 \caption{Each facet is associated with one lineup, the height of the
-bars count the choices made by the participants considering each lineup.
-The bars coloured with black outlines show the map which contained a
-trend model, these are the correct choices. The numbers differentiate
-the replicates of each trend model and type of map display. Participants
-were able to select 0 to indicate they did not want to choose a map.}
+points show the proportion of the participants that made each choice
+when considering each lineup. The points coloureddark blue show the map
+which contained a trend model, these are the correct choices. The
+numbers differentiate the replicates of each trend model and type of map
+display. Participants were able to select 0 to indicate they did not
+want to choose a map.}
 \end{figure}
@@
 
+This includes the two main effects map type and trend model, which gives
+the fixed effects part of the model to be
+
+\[\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3\]
+
+where \(y_{ij} = 0, 1\) whether the subject detected the data plot,
+\(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect,
+\(\delta_j\) is the trend model effect. We are allowing for an
+interaction between map type and trend model. Because the response is
+binary, a logistic model is used.
+
 \hypertarget{detection-rates}{%
@@
 
-\begin{verbatim}
-## # A tibble: 6 x 5
-##   term                                estimate std.error statistic p.value
-##   <chr>                                  <dbl>     <dbl>     <dbl>   <dbl>
-## 1 (Intercept)                           0.0217     0.147     0.147   0.883
-## 2 typeHexagon tiles                     0.420      0.211     1.99    0.047
-## 3 trendthree cities                    -3.25       0.412    -7.88    0    
-## 4 trendall cities                      -1.24       0.229    -5.41    0    
-## 5 typeHexagon tiles:trendthree cities   2.37       0.465     5.10    0    
-## 6 typeHexagon tiles:trendall cities     1.08       0.312     3.47    0.001
-\end{verbatim}
-
-\begin{verbatim}
-## Analysis of Deviance Table
-## 
-## Model: binomial, link: logit
-## 
-## Response: detect_f
-## 
-## Terms added sequentially (first to last)
-## 
-## 
-##            Df Deviance Resid. Df Resid. Dev  Pr(>Chi)    
-## NULL                        1103     1477.0              
-## type        1   83.526      1102     1393.5 < 2.2e-16 ***
-## trend       2  101.699      1100     1291.8 < 2.2e-16 ***
-## type:trend  2   35.517      1098     1256.2 1.939e-08 ***
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-\end{verbatim}
+\begin{tabular}{l|r|r|r|r|l}
+\hline
+\_ & terms & Estimate & Error & p.value & sig\\
+\hline
+Design & Choro & 0.0217400 & 0.1474507 & 0.8828 & \\
+\hline
+ & Hex & 0.4200928 & 0.2110904 & 0.0466 & *\\
+\hline
+Trend & Three cities & -3.2519793 & 0.4124809 & 0.0000 & ***\\
+\hline
+ & All cities & -1.2398974 & 0.2293327 & 0.0000 & ***\\
+\hline
+Interactions & Hex : Three cities & 2.3683138 & 0.4645163 & 0.0000 & ***\\
+\hline
+ & Hex : All cities & 1.0825772 & 0.3123987 & 0.0005 & ***\\
+\hline
+\end{tabular}
 
@@
 ##      
-##             Incorrect Correct
-##   Incorrect       431     121
-##   Correct         242     310
+##        No Yes
+##   No  431 121
+##   Yes 242 310
 \end{verbatim}
+
+This gives the model:
+
+\[\widehat{y_{ij}} = 0.0217 + 0.42Hex -3.25_{three} -1.24_{all} + 2.37{Hex.three} + 1.08{Hex.all} \]
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-8-1.pdf}
 
@@
 ## 1 (Intercept)                   0.505    0.0340     14.9  fixed      
-## 2 typeHexagon tiles                      0.103    0.0448      2.31 fixed      
+## 2 typeHex.                      0.103    0.0448      2.31 fixed      
 ## 3 trendthree cities            -0.467    0.0448    -10.4  fixed      
 ## 4 trendall cities              -0.277    0.0448     -6.19 fixed      
-## 5 typeHexagon tiles:trendthree cities    0.250    0.0633      3.95 fixed      
-## 6 typeHexagon tiles:trendall cities      0.239    0.0633      3.77 fixed      
+## 5 typeHex.:trendthree cities    0.250    0.0633      3.95 fixed      
+## 6 typeHex.:trendall cities      0.239    0.0633      3.77 fixed      
 ## 7 sd_(Intercept).contributor    0.118   NA          NA    contributor
@@
 ##      
-##             Incorrect Correct
-##   Incorrect        49       1
-##   Correct         624     430
+##        No Yes
+##   No   49   1
+##   Yes 624 430
 \end{verbatim}
@@
 the log odds of the detection by 0.42.
+
+\begin{verbatim}
+## # A tibble: 1 x 6
+##   sigma logLik   AIC   BIC deviance df.residual
+##   <dbl>  <dbl> <dbl> <dbl>    <dbl>       <int>
+## 1 0.445  -685. 1380. 1405.    1365.        1099
+\end{verbatim}
+
+\begin{verbatim}
+## # A tibble: 5 x 5
+##   term                           estimate std.error statistic group   
+##   <chr>                             <dbl>     <dbl>     <dbl> <chr>   
+## 1 (Intercept)                       0.669    0.0501      13.4 fixed   
+## 2 sd_(Intercept).trend              0.456   NA           NA   trend   
+## 3 sd_typeHex..trend                 0.287   NA           NA   trend   
+## 4 cor_(Intercept).typeHex..trend   -0.989   NA           NA   trend   
+## 5 sd_Observation.Residual           0.445   NA           NA   Residual
+\end{verbatim}
+
+\begin{verbatim}
+##      
+##        No Yes
+##   No    0   0
+##   Yes 673 431
+\end{verbatim}
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-11-1.pdf}
 
@@
 ## Fixed Effects:
-##                         (Intercept)                    typeHexagon tiles  
+##                (Intercept)                    typeHex.  
 ##                     0.5054                      0.1033  
@@
 ##                    -0.4674                     -0.2772  
-## typeHexagon tiles:trendthree cities    typeHexagon tiles:trendall cities  
+## typeHex.:trendthree cities    typeHex.:trendall cities  
 ##                     0.2500                      0.2391
@@
 
+\hypertarget{overall-performance}{%
+\subsection{Overall Performance}\label{overall-performance}}
+
 \hypertarget{subject-specific-anomolies-0-detection}{%
@@
 detection)}\label{subject-specific-anomolies-0-detection}}
+
+\hypertarget{demographics}{%
+\subsection{Demographics:}\label{demographics}}
+
+\includegraphics{paper_files/figure-latex/demogs-1.pdf}
+
+\begin{verbatim}
+## # A tibble: 2 x 2
+##   gender     n
+##   <chr>  <int>
+## 1 He        67
+## 2 She       25
+\end{verbatim}
+
+\begin{verbatim}
+## # A tibble: 3 x 2
+##   education       n
+##   <chr>       <int>
+## 1 Bach           56
+## 2 High School    23
+## 3 Masters        13
+\end{verbatim}
+
+\begin{tabular}{l|r|r|r|r}
+\hline
+Gender & Bach & High School & Masters & Row Total\\
+\hline
+Col. Total & 56 & 23 & 13 & 79\\
+\hline
+He & 39 & 19 & 9 & 58\\
+\hline
+She & 17 & 4 & 4 & 21\\
+\hline
+\end{tabular}
 

### 2020-01-05 paper/paper.tex

@@
 
-the difference in the detection rates for the two displays will be
+The difference in the detection rates for the two displays will be
 compared using the following:
@@
 
-The contributors who detected no plots correctly were analysed further.
-Three of these contribuotrs gave no choices for any of the twelve
-displays. They were also removed for the rest of the analysis. The
-contributors who gave various plot choices and reasons for the twelve
-displays were kept.
-
-67 of the 92 participants were male, and 25 female and only two of the
-participants had lived in Australia before.
-
-70 of the participants achieved a Bachelors or Masters degree.
+The contributors who gave various plot choices and reasons for the
+twelve displays were kept. The contributors who detected no plots
+correctly were analysed further. Three of these contribuotrs gave no
+choices for any of the twelve displays. They were also removed for the
+rest of the analysis.
+
+Of the 92 participants, 67 were male, and 25 female. Only two of the
+participants had lived in Australia before. The education level achieved
+by the participants was 70 Bachelors or Masters degree.
 
@@
 
-The detection rate is used to find the accuracy for participants
-reporting the real data trend model. The accuracy can be seen from many
-views.
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/detection_compare-1.pdf}
-\caption{Contrasting the detection rate achieved by participants when
-viewing the four replicates of the three trend models. Each point shows
-the probability of detection for the lineup display, the facets separate
-the trend models hidden in the lineup. The points for the same data set
-shown in a choroleth or haxgon tile map display are linked to show the
-difference in the detection rate.}
-\end{figure}
+The detection rate for participants reporting the real data trend model
+is used to calculate the accuracy of the responses of participants.
+
+\includegraphics{paper_files/figure-latex/detection_compare-1.pdf} The
+detection rates are usually higher when participants viewed the hexagon
+tile map displays. The difference was greater when viewing a three
+cities trend model. When the trend model affected all cities
+participants also detected the data display in the lineup of null plots
+more often. The North West to South East data plot was detected with
+similar rates when viewing the choropleth and hexagon tile map displays,
+though for three of the replicates the participants detected the data
+display more often.
 

### 2020-01-06 paper/paper.Rmd
plot changes

@@
 abstract: |
-  The abstract goes here.
-  On multiple lines eventually.
+  Choosing a visualisation method may seem to be a simple task.
+The choropleth map display is commonly used for communicating spatial data.
+The visualisation method used to present geospatial data will influence the information derived by map users.
+Choosing an alternative display will influence the communication of the distribution.
+The hexagon tile map is presented as an alternative display.
+Visual inference is used to measure the power of design.
+The choropleth is used as a comparison point.
+The hexagon tile map display is an effective visualisation for communicatin=g population related distributions.
+The hexagon tile map display also allowed identification of the geographic distribution with values monotonically decreasing from North West toward South East areas of Australia.
 dev: png
@@
 editor_options: 
-  chunk_output_type: console
+  chunk_output_type: inline
 link-citations: yes
@@
 
+```{r libraries}
+# Load Libraries
+library(tidyverse)
+library(cowplot)
+library(png)
+library(grid)
+library(lubridate)
+library(broom)
+library(readxl)
+library(lme4)
+library(ggthemes)
+library(RColorBrewer)
+library(visreg)
+library(emmeans)
+```
+
 Introduction
@@
 <!-- geographies on choropleth -->
-Geospatial statistics are often presented on the geographic map base. 
-A choropleth map is the common display to present aggreagated statistics for geographic units, and they are often used to present statistics regarding the population. 
+A geographic map base is commonly used to present geospatial statistics.
+The statistics presented may also be aggreagated statistics for geographic units, in this case the choropleth map is the common display used.
+Choropleth maps are often used to present statistics regarding the population.
 Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic. 
-In Australia, there are sets of administrative boundaries that define subdivisions of the population at various granularities.
-The set of Australia statistical areas presents an example of a heterogrenous distribution of area.
-The rural communicates on a much larger geographic space than small inner city communities.
+The several sets of Australian statistical areas presents an example of a heterogrenous distribution.
+The rural communities in Australia operate on a much larger geographic space than small inner city communities.
 This has the negative effect of incorrectly showing the spatial distribution of the statistic, especially when a spatial distribution is related to the size of the areas, or the population density.
-
-An alternative display can also be used to effectively communicate a spatial distribution for a set of heterogeneous areas.
-Viewers of spatial distributions may come to incorrect conclusions.
+An alternative display can be used to effectively communicate a spatial distribution for a set of heterogeneous areas.
 
@@
 
-The Australian Cancer Atlas is an online interactive webtool created to explore the burden of cancer on Australian communities.
+The Australian Cancer Atlas is an online interactive web tool created to explore the burden of cancer on Australian communities.
 There are many cancer types presented, and they can be explored on an individual or aggregate level.
@@
 Spatial smoothing allows for the protection privacy and gives stability to the estimates.
-The statistics that can be mapped are the diagnoses (Standardised Incidence Rates) and excess deaths for each SA2, communicated as the difference from the Australian average of the statistics.
+The statistics mapped are the diagnoses (Standardised Incidence Rates) and excess deaths for each SA2, communicated as the difference from the Australian average of the statistics.
 The values of the statistic for each geographic area is communicated through the colour used to fill the areas, the colours are chosen for the diverging colour scheme.
-
 The Australian Cancer Atlas communicates the trends in the distributions of cancer over geographic space.
@@
 The most common display for spatial data is the choropleth map.
-However, the issue of using a choropleth map base becomes obvious when considering the distributions.
+However, the issue of using a choropleth map base becomes obvious when considering population related distributions.
 Map creators have the ability to present spatial statistics in alternative displays that can highlight the population.
 This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
-The same data were shown on a choropleth map, and on a hexagon tile map.
-Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.
-
 When presenting population statistics on a geographic map base, the size of the regions can allow errornous conclusions to be drawn about the state of the statistic over the entire population.
@@
 
+A cartogram transforms the geographic map base.
+The transformation begins with a choropleth map base, and the associated populations.
+There are several algorithms for transforming, they all involve shifting boundaries to increase or descrease the area of the geographic units on the map depending on the statistics.
 <!-- Why not a cartogram-->
+The shifts of the boundaries result in cartograms with accurate map area for each of the geographic units.
+The transformation will keep boundaries of neighbouring areas connected, but the result is unfamiliar shapes for each geographic unit.
 
 <!-- Tesselated tile gram & hexagon tile map-->
+Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units.
+The non-contiguous cartgoram method keep the shapes of geographic units intact, and change the size to communicate the values of statistics.
+This method breaks the spatial relationship between areas, and emphasises the difference between the statistic and the amount of land for each geographic unit.
+The Dorling cartogram is another method that does not retain the boundaries of geographic units.
+Each unit becomes one circle on the cartogram dispaly, these can be sized according to the value of a variable.
+Their neighbours can be illustrated by connecting the boundaries of the circles.
+These cartogram methods all allow two variables to be shown in the single display.
+
+```{r liver, fig.height = 9, fig.width = 6, fig.cap = "The smoothed average of liver cancer diagnoses for Australian males.
+The divering colour scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average."}
+ggdraw(ylim = c(0,2), xlim = c(0,1.3), clip = "on") +
+  draw_plot(rasterGrob(readPNG("figures/aus_liver_m.png")), -0.15, 0.9, 1.6, 1.2) +
+  draw_plot(rasterGrob(readPNG("figures/aus_liver_m_hex.png")), -0.15, -0.1, 1.6, 1.2) +
+  draw_plot_label(c("a", "b"), 
+    c(0.05, 0.05), c(1.95, 1), size = 20, color = "white") + 
+  theme(plot.background = element_rect(fill = "black"))
+```
 
 <!-- Specific problem for Australia -->
-
-<!-- Figure Choro and Hex tile for Aus-->
+Australia is an extreme case of heterogenous geographic units.
+To communicate information regarding the small inner city geographic units of Australian cities an alternative display must be employed.
+This will emphasise the value of the statistic that is relating to areas with high population levels.
+Figure \@ref(fig:liver) shows the distribution of the smoothed average amount of Liver cancer diagnoses for Australian Males from XXX years.
+The hexagon tile map (b) shows orange hexagons for the inner city Statistical Areas at Level 2 with higher than average levels of diagnoses in the capital cities of Melbourne and Sydney.
+These inner city areas are not visible on the choropleth map (a).
+There are still many light blue areas in both displays.
+The northern Queensland, and Northern Territory SA2's with higher than average rates are still visible but utilise less map space on the hexagon tile map.
 
 ## Methodology
+
+To test the
 
@@
 - Protocol for testing the effectiveness
+
+The same data were shown on a choropleth map, and on a hexagon tile map.
+Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.
 
@@
 where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
-We are allowing for an interaction between map type and trend model.
-Because the response is binary, a logistic model is used.
+We are allowing for an interaction between map type and trend model. As the response for whether the participant detected the data plot is binary, a logistic model is used.
 
@@
 
-This required internet connection for participants to access the survey
+The demographics of the participants showed a skew towards male participants. 
+The randomness of the group allocation also resulted in more participants being allocated to Group B.
+Due to the allocation of lineup displays the participants all saw six Choropleth displays and six Hexagon Tile Map displays.
 
@@
 ```{r data}
-# Load Libraries
-library(tidyverse)
-library(lubridate)
-library(broom)
-library(readxl)
-library(lme4)
-library(ggthemes)
-library(RColorBrewer)
-library(visreg)
-library(emmeans)
-
 trend_colours <- c(
   "NW-SE" = "#B2DF8A",
-  "three cities" = "#A6CEE3",
-  "all cities" = "#1F78B4")
+  "Three Cities" = "#A6CEE3",
+  "All Cities" = "#1F78B4")
 
@@
 
-detect_colours <- c(
+detect_f_colours <- c(
   "No" = "#66C2A5",
   "Yes" = "#FC8D62")
+
+detect_colours <- c(
+  "Detected? No" = "#66C2A5",
+  "Detected? Yes" = "#FC8D62")
 
@@
 d <- d %>% 
-  separate(image_name, c("nothing", "trend", "location", "type", "extra"), remove=FALSE) %>%
+  separate(image_name, c("nothing", "trend", "location", "type", "extra"), remove = FALSE) %>%
   select(-nothing, -extra) %>%
@@
     trend == "nwse" ~ "NW-SE",
-    trend == "cities" ~ "all cities",
-    trend == "three" ~ "three cities")) %>% 
-  mutate(trend = fct_relevel(trend, "NW-SE","three cities","all cities")) %>% 
+    trend == "cities" ~ "All Cities",
+    trend == "three" ~ "Three Cities")) %>% 
+  mutate(trend = fct_relevel(trend, "NW-SE","Three Cities","All Cities")) %>% 
   mutate(type = case_when(
@@
     TRUE~"Choro.")) %>% 
-    mutate(detect_f = factor(detect, levels = c(0,1), labels = c("No", "Yes")))
+    mutate(detect_f = factor(detect, levels = c(0,1), labels = c("Detected? No", "Detected? Yes")))
 
@@
 ```
+
 The detection rates are usually higher when participants viewed the hexagon tile map displays.
@@
 The North West to South East data plot was detected with similar rates when viewing the choropleth and  hexagon tile map displays, though for three of the replicates the participants detected the data display more often.
-
-```{r detection_compare_table}
-d %>% 
-  group_by(trend, type, replicate) %>%
-  summarise(mean = round(mean(time_taken),2), 
-    std.dev = round(sd(time_taken), 2)) %>% 
-  knitr::kable(format = "latex")
-```
 
@@
 
-```{r hist_height, fig.cap = "The time taken to evaluate each display is broken into five second windows.
+The amount of time taken for a participants to submit a response is explored. 
+The time considered was the amount of time it took for a participant to submit their choice of plot, the reason for their choice, and the perceived difficulty of the choice.
+The time was taken when each participant hit "Next".
+
+The relationship between time taken to submit, and the correct detection by the participant of the real data display in a lineup is considered in Figure \@ref(fig:hist_height).
+The bimodal distributions are similar across the type of display and the trend model hidden in the real data plot.
+The hexagon map displays have a peak for the group that took up to 5 seconds to submit a response.
+When viewing a choropleth map display, the second peak occured at around 20 seconds.
+The longest a participant took to respond was 60 seconds.
+
+```{r hist_height, fig.cap = "Six histograms show the distribution of the time taken to submit a response for each combination of trend and type of display.
+The time taken to evaluate each display is broken into five second windows.
 The height of the histogram bars show how many evaulations were submitted within each time window.
-The distributions for the choropleth and hexagon tile maps are very similar.
-Both have a large peak at 0-5 seconds, and then a secondary peak at 10-20 seconds.
-No response took over one minute."}
-ggplot(d, aes(x = time_taken, fill = detect_f, group = detect_f)) + 
-  scale_fill_brewer(palette = "Dark2") +
+The orange regions of the bars show the amount of correct detections, and the green regions are the amount of incorrect detections."}
+ggplot(d %>% rename(Detected = detect_f), 
+  aes(x = time_taken, fill = Detected, group = Detected)) + 
+  scale_fill_manual(values = detect_colours) +
   geom_histogram(binwidth = 5, boundary = 0) +
   facet_grid(type ~ trend) + 
-  labs(x = "Time taken (Seconds)", y = "Amount of evaluations") + 
-  guides(fill = FALSE)
+  theme(legend.position = "bottom") +
+  labs(x = "Time taken (Seconds)", y = "Amount of evaluations")
 ```
@@
 The height of the histogram bars show the proportion of evaulations that were submitted within each time window."}
-ggplot(d, aes(x = time_taken, fill = detect_f, group = detect_f)) + 
-  scale_fill_brewer(palette = "Dark2") +
+ggplot(d %>% rename(Detected = detect_f), 
+  aes(x = time_taken, fill = Detected, group = Detected)) +  
+  scale_fill_manual(values = detect_colours) +
   geom_histogram(binwidth = 5, boundary = 0, position = "fill") +
   facet_grid(type ~ trend) +
-  labs(x = "Time taken (Seconds)", y = "Proportion of evaluations") + 
-  guides(fill = FALSE)
-```
+  labs(x = "Time taken (Seconds)", y = "Proportion of evaluations")
 
-```{r}
 ggplot(d, aes(x = time_taken, colour = detect_f, group = detect_f)) +  
-  scale_colour_brewer(palette = "Dark2") +
+  scale_fill_manual(values = detect_colours) +
   geom_freqpoly(binwidth = 3) +
@@
 
+The proportion of correct and incorrect responses within each 5 second time window.
+For the NW-SE distribution, it is equally likely that quick responders will be correct or incorrect.
+It is more likely that participants picked the correct response if they took longer to respond.
+For the Choropelth
+
+However, these quick responders were likely to be either correct or incorrect. The quick responders viewing a choropleth display were unlikely to choose correctly, unless viewing a NW-SE trend model.
+
+The choropleth map displays that included a distribution of three cities was very difficult for participants.
+
 ## Certainty
 
-```{r, fig.cap = "The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
+```{r certainty, fig.cap = "The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
 Participants were more likely to choose a high certainty when considering a Choropleth map.
-The default certainty of 3 was chosen most for the Hexagon tile map displays."}
+The mid value of 3 was the default certainty, it was chosen most for the Hexagon tile map displays."}
 d <- d %>% 
-  mutate(certainty = as_factor(certainty))
+  mutate(certainty = as_factor(certainty)) %>% 
+  mutate(replicate_f = as_factor(replicate))
 
-ggplot(d,
-  aes(x = certainty, fill = detect_f)) +
-  scale_fill_brewer(palette = "Set2") +
-  geom_bar() + facet_wrap(~trend) + guides(fill = FALSE)
+ggplot(d %>% rename(Detected = detect_f), 
+   aes(x = certainty, fill = Detected)) +  
+  scale_fill_manual(values = detect_colours) +
+  geom_bar() + facet_grid(type ~ trend) +
+  theme(legend.position = "bottom")
 ```
@@
 Certainty levels are measured on a five point scale—they are subjective
-assessments by the participant ‘how certain are you about your choice?’.
+assessments by the participant ‘How certain are you about your choice?’.
 
@@
 
-```{r, fig.cap = "The most common reason for choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
-Clusters were the most common reason when viewing a Hexagon Tile map, trend was the most common choice for choropleth displays except for the all cities display."}
+```{r reason, fig.cap = "The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
+The facets show whether or not the choice was correct."}
 ###########################################################
@@
 d <- d %>% 
-  mutate(reason = fct_infreq(ifelse(reason =="0.0", "no reason", reason)))
+  mutate(reason = ifelse(reason =="0.0", "no reason", reason))
 
-ggplot(d) + 
-  geom_bar(aes(x = reason, fill = type), position = "dodge") +  
-  facet_grid(~detect_f) +  
-  scale_colour_manual(values = type_colours) +
+ggplot(d %>% mutate(Detected = factor(detect, levels = c(0,1), 
+  labels = c("Detected? No", "Detected? Yes")),
+  `Map Type` = type)) + 
+  geom_bar(aes(x = fct_infreq(reason), fill = `Map Type`)) +  
+  facet_grid(trend ~ Detected) +  
+  scale_fill_manual(values = type_colours) +
   xlab("Type of areas visualised") + 
-  guides(colour = FALSE) + coord_flip()
+  theme(legend.position = "bottom") + coord_flip()
 ```
+
+The most common choice made by participant was clusters, this response was expected when participants viewed the Hexagon display of the all cities and three cities distributions.
 
@@
 
-```{r fig.cap = "The probablity of detection acheived by the contributors in each group is shown by the points.
+```{r contributors, fig.cap = "The probablity of detection acheived by the contributors in each group is shown by the points.
 Group B has a larger range and a smaller inter-quartile range.
@@
 
-## Reason
-
-```{r}
-###########################################################
-# Qualitative analysis of reason
-d <- d %>% 
-  mutate(reason = ifelse(reason =="0.0", "no reason", reason))
-
-ggplot(d %>% mutate(detect = factor(detect, levels = c(0,1), 
-  labels = c("No", "Yes")))) + 
-  geom_bar(aes(x = reason)) +  
-  facet_grid(trend ~ detect) +  
-  scale_colour_manual(values = trend_colours) +
-  xlab("Type of areas visualised") + 
-  guides(colour = FALSE) + coord_flip()
-```
-
-```{r choices, fig.height = 12, fig.width = 12, fig.cap = "Each facet is associated with one lineup, the height of the points show the proportion of the participants that made each choice when considering each lineup.
-The points coloureddark blue show the map which contained a trend model, these are the correct choices.
+```{r choices, fig.cap = "Each facet is associated with one lineup, the height of the points show the proportion of the participants that made each choice when considering each lineup.
+The points coloured orange show the map which contained a trend model, these are the correct choices.
 The numbers differentiate the replicates of each trend model and type of map display.
-Participants were able to select 0 to indicate they did not want to choose a map.
-"}
+Participants were able to select 0 to indicate they did not want to choose a map.", fig.height = 12, fig.width=10}
 d %>% 
@@
   mutate(prop = n/sum(n)) %>% 
-  mutate(repl = paste(replicate, ": ", trend,  sep = "")) %>%
+  mutate(repl = paste("Rep:", replicate, ":\n", type,  sep = "")) %>%
   mutate(bottom = 0) %>% 
   ggplot() + 
-  geom_point(aes(x = choice, y = prop, color = detect_f), boundary = 0, size =2) + 
-  geom_segment(aes(x = choice, xend = choice, y = bottom, yend = prop, colour = detect_f)) +
-  facet_grid(replicate + type ~ trend, 
+  geom_point(aes(x = choice, y = prop, color = detect_f), size = 4) + 
+  geom_segment(aes(x = choice, xend = choice,y = bottom, yend = prop, colour = detect_f), size = 1) +
+  facet_grid(repl ~ trend, 
     drop = TRUE, as.table = TRUE, scales = "free_y") +
@@
   scale_y_continuous(breaks = seq(from = 0.0, to = 1.0, by = 0.1)) +
-  theme(legend.position = "bottom") + guides(colour = FALSE, fill = FALSE)
+  theme(legend.position = "bottom") + 
+  guides(colour = FALSE, fill = FALSE) +
+  theme(strip.text.y = element_text(angle = 0))
 ```
 
-The choices made by participants are examined in Figure \ref{fig:choices}.
+The choices made by participants are examined in Figure \@ref(fig:choices).
 Participants were misled by the choropleth display, but not the hexagon display for all cities displays except (2).
@@
 All of three cities displays, except (4), were detected in the hexagon display.
-All except one lineup had at least one participant select the correct map in the lineup as shown in Figure \ref{fig:choices}.
+All except one lineup had at least one participant select the correct map in the lineup as shown in Figure \@ref(fig:choices}.
 
@@
 
-A generalized linear mixed effects model can account for each individual participants’ abilities as it includes a subject-specific random intercept.
-As each participant provides results from 12 lineups.
+The likelihood of detecting the data plot in the lineup can be modelled using a generalized linear mixed effects model. 
+The base R [@RCore] `glm()` function implements generalised linear models. The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
 
-This includes the two main effects map type and trend model, which gives the fixed effects part of the model to be
-
-$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3$$
+$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij} + \epsilon_{i,j}, ~~~ i=1,2; ~j=1,2,3$$
 
@@
 Because the response is binary, a logistic model is used.
+This model can account for each individual participants’ abilities as it includes a subject-specific random intercept.
+As each participant provides results from 12 lineups.
 
@@
 
-```{r}
+The model specifies a logistic link, this means the predicted values from the `glm` model should be back-transformed to fit between 0 and 1. They are transformed with the link specified below:
+
+$$\mu = \frac{e^{\eta}}{1 + e^{\eta}}$$
+$$\eta = f(\tau_i,\delta_j)$$
+
+```{r modeling_glm1}
 # Modelling 
-glm1 <- glm(formula = detect_f ~ type * trend,
+glm1 <- glm(formula = detect ~ type * trend,
   family = binomial(link = "logit"), data = d)
@@
 factors <- c("Design", "", "Trend", "", "Interactions", "")
-terms <- c("Choro", "Hex", "Three cities", "All cities", "Hex : Three cities", "Hex : All cities")
+terms <- c("Intercept", "Hex", "Three cities", "All cities", "Hex : Three cities", "Hex : All cities")
 
@@
     Error = std.error, 
+    Stat = statistic,
     p.value, sig) %>% knitr::kable(format = "latex", 
@@
     predicted = factor(predicted, levels = c(0,1), 
-      labels = c("No", "Yes")))
+      labels = c("Predicted: No", "Predicted: Yes")))
 
@@
 
+The estimated marginal mean is the fitted value from a model over the treatment effects.
+The treatment effects considered in this model are map type displayed, trend model included, and the replicate.
+The `emmeans` package is used to calculate the estimated marginal mean.
+The value, between 0 and 1, can be interpretted as the probability of detecting the real data plot in the lineup, for each combination of map type, trend model and replicate.
+
 ```{r}
-emmean_obj1 <- emmeans(glm1, c("trend", "type"),
+glm2 <- glm(formula = detect ~ type * trend + replicate_f,
+  family = binomial(link = "logit"), data = d)
+
+emmean2 <- emmeans(glm2, c("trend", "type", "replicate_f"),
                         type = "response")
 
-int_1 <- confint(emmean_obj1, by = c("trend"), adjust = "bonferroni")
-int_1 %>% 
-  ggplot(aes(x= type, y = prob, group = trend)) + 
+int_2 <- confint(emmean2, by = c("type", "trend", "replicate_f"), adjust = "bonferroni")
+int_2 %>% 
+  ggplot(aes(x= replicate_f, y = prob, group = type)) + 
   geom_point(aes(col = type)) + 
   geom_line(alpha = 0.5, lty = "dashed") + 
-  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL, col = type), 
+  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL, col = replicate_f), 
                 width = 0.2) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
-        strip.text.y = element_text(angle = 0),
-        legend.position = "none",
-        axis.title.x = element_blank()) + 
+  facet_grid(trend ~ .) +
   ylab("Estimated Marginal Mean")
@@
 table(d_lmer2$predicted, d_lmer2$detect_f)
-```
-
-```{r}
-visreg(lmer2, "type", by = "trend", scale = "response", re.form = ~(type|trend))
 ```

### 2020-01-07 paper/paper.Rmd
beeswarm plot

--- 2020-01-05 paper/paper.Rmd
@@
 
+```{r eval=FALSE}
+# Di playing
+s <- d %>% group_by(type, trend, detect) %>%
+  summarise(m=median(time_taken), 
+            q1=quantile(time_taken, 0.25), 
+            q3=quantile(time_taken, 0.75))
+library(ggbeeswarm)
+ggplot() + 
+  geom_quasirandom(data=d, aes(x=type, y=time_taken), alpha=0.9) + 
+  #geom_hline(data=s, aes(yintercept=m, colour=type)) +
+  geom_point(data=s, aes(x=type, y=m, colour=type), size=5, alpha=0.7) +
+  #geom_errorbar(data=s, aes(x=type, ymin=q1, ymax=q3, colour=type), width=0.3, size=2) +
+  scale_colour_brewer(palette = "Dark2") +
+  facet_grid(trend~detect)
+```
+
 ## Certainty

### 2020-01-07 paper/paper.Rmd

--- 2020-01-06 paper/paper.Rmd
@@
 
-```{r hist_height, fig.cap = "Six histograms show the distribution of the time taken to submit a response for each combination of trend and type of display.
+```{r hist_height,  eval=FALSE, fig.cap = "Six histograms show the distribution of the time taken to submit a response for each combination of trend and type of display.
 The time taken to evaluate each display is broken into five second windows.
@@
 
-```{r hist_fill, fig.cap = "The time taken to evaluate each display is broken into five second windows.
+```{r hist_fill,  eval=FALSE, fig.cap = "The time taken to evaluate each display is broken into five second windows.
 The height of the histogram bars show the proportion of evaulations that were submitted within each time window."}
@@
   guides(colour = FALSE)
+```
+
+```{r}
+# Di playing
+s <- d %>% group_by(type, trend, detect) %>%
+  summarise(m=median(time_taken), 
+            q1=quantile(time_taken, 0.25), 
+            q3=quantile(time_taken, 0.75))
+library(ggbeeswarm)
+ggplot() + 
+  geom_quasirandom(data=d, aes(x=type, y=time_taken), alpha=0.9) + 
+  #geom_hline(data=s, aes(yintercept=m, colour=type)) +
+  geom_point(data=s, aes(x=type, y=m, colour=type), size=5, alpha=0.7) +
+  #geom_errorbar(data=s, aes(x=type, ymin=q1, ymax=q3, colour=type), width=0.3, size=2) +
+  scale_colour_brewer(palette = "Dark2") +
+  facet_grid(trend~detect)
 ```

### 2020-01-07 paper/paper.tex

@@
 \begin{abstract}
-The abstract goes here. On multiple lines eventually.
+Choosing a visualisation method may seem to be a simple task. The
+choropleth map display is commonly used for communicating spatial data.
+The visualisation method used to present geospatial data will influence
+the information derived by map users. Choosing an alternative display
+will influence the communication of the distribution. The hexagon tile
+map is presented as an alternative display. Visual inference is used to
+measure the power of design. The choropleth is used as a comparison
+point. The hexagon tile map display is an effective visualisation for
+communicatin=g population related distributions. The hexagon tile map
+display also allowed identification of the geographic distribution with
+values monotonically decreasing from North West toward South East areas
+of Australia.
 \end{abstract}
@@
 
-Geospatial statistics are often presented on the geographic map base. A
-choropleth map is the common display to present aggreagated statistics
-for geographic units, and they are often used to present statistics
-regarding the population. Creating a choropleth map involves drawing the
+A geographic map base is commonly used to present geospatial statistics.
+The statistics presented may also be aggreagated statistics for
+geographic units, in this case the choropleth map is the common display
+used. Choropleth maps are often used to present statistics regarding the
+population. Creating a choropleth map involves drawing the
 administrative boundaries and filling them with colour to communicate
-the value of the statistic. In Australia, there are sets of
-administrative boundaries that define subdivisions of the population at
-various granularities. The set of Australia statistical areas presents
-an example of a heterogrenous distribution of area. The rural
-communicates on a much larger geographic space than small inner city
-communities. This has the negative effect of incorrectly showing the
-spatial distribution of the statistic, especially when a spatial
-distribution is related to the size of the areas, or the population
-density.
-
-An alternative display can also be used to effectively communicate a
-spatial distribution for a set of heterogeneous areas. Viewers of
-spatial distributions may come to incorrect conclusions.
+the value of the statistic. The several sets of Australian statistical
+areas presents an example of a heterogrenous distribution. The rural
+communities in Australia operate on a much larger geographic space than
+small inner city communities. This has the negative effect of
+incorrectly showing the spatial distribution of the statistic,
+especially when a spatial distribution is related to the size of the
+areas, or the population density. An alternative display can be used to
+effectively communicate a spatial distribution for a set of
+heterogeneous areas.
 
@@
 
-The Australian Cancer Atlas is an online interactive webtool created to
+The Australian Cancer Atlas is an online interactive web tool created to
 explore the burden of cancer on Australian communities. There are many
@@
 areas. Spatial smoothing allows for the protection privacy and gives
-stability to the estimates. The statistics that can be mapped are the
-diagnoses (Standardised Incidence Rates) and excess deaths for each SA2,
+stability to the estimates. The statistics mapped are the diagnoses
+(Standardised Incidence Rates) and excess deaths for each SA2,
 communicated as the difference from the Australian average of the
@@
 communicated through the colour used to fill the areas, the colours are
-chosen for the diverging colour scheme.
-
-The Australian Cancer Atlas communicates the trends in the distributions
-of cancer over geographic space. It uses a choropleth map display and
-diverging colour scheme to draw attention to relationships between
-neighbouring areas.
+chosen for the diverging colour scheme. The Australian Cancer Atlas
+communicates the trends in the distributions of cancer over geographic
+space. It uses a choropleth map display and diverging colour scheme to
+draw attention to relationships between neighbouring areas.
 
@@
 choropleth map. However, the issue of using a choropleth map base
-becomes obvious when considering the distributions. Map creators have
-the ability to present spatial statistics in alternative displays that
-can highlight the population. This work aims to show that a hexagon tile
-map display is a viable alternative to the geographic map base for
-presenting population statistics. The same data were shown on a
-choropleth map, and on a hexagon tile map. Comparing the results of
-participants who see the choropleth to those who see a hexagon tile map
-will show that population related distributions are spotted more
-frequently in a hexagon tile map display.
-
-When presenting population statistics on a geographic map base, the size
-of the regions can allow errornous conclusions to be drawn about the
-state of the statistic over the entire population. This occurs as large
-regions filled with a consistent colour or pettern can draw the
-attention of map readers, and small regions are not paid equal
-attention. A choropleth map is not the only display that can be used for
-presenting geospatial data. Alternative maps include various cartograms,
-and tesselated tile maps. They allow other variables to be included in
-the display to highlight the staistical values of various geographic
-areas.
+becomes obvious when considering population related distributions. Map
+creators have the ability to present spatial statistics in alternative
+displays that can highlight the population. This work aims to show that
+a hexagon tile map display is a viable alternative to the geographic map
+base for presenting population statistics. When presenting population
+statistics on a geographic map base, the size of the regions can allow
+errornous conclusions to be drawn about the state of the statistic over
+the entire population. This occurs as large regions filled with a
+consistent colour or pettern can draw the attention of map readers, and
+small regions are not paid equal attention. A choropleth map is not the
+only display that can be used for presenting geospatial data.
+Alternative maps include various cartograms, and tesselated tile maps.
+They allow other variables to be included in the display to highlight
+the staistical values of various geographic areas.
+
+A cartogram transforms the geographic map base. The transformation
+begins with a choropleth map base, and the associated populations. There
+are several algorithms for transforming, they all involve shifting
+boundaries to increase or descrease the area of the geographic units on
+the map depending on the statistics. The shifts of the boundaries result
+in cartograms with accurate map area for each of the geographic units.
+The transformation will keep boundaries of neighbouring areas connected,
+but the result is unfamiliar shapes for each geographic unit.
+
+Alternative displays make the trade off between familiar shapes and
+representation of variables using the area of geographic units. The
+non-contiguous cartgoram method keep the shapes of geographic units
+intact, and change the size to communicate the values of statistics.
+This method breaks the spatial relationship between areas, and
+emphasises the difference between the statistic and the amount of land
+for each geographic unit. The Dorling cartogram is another method that
+does not retain the boundaries of geographic units. Each unit becomes
+one circle on the cartogram dispaly, these can be sized according to the
+value of a variable. Their neighbours can be illustrated by connecting
+the boundaries of the circles. These cartogram methods all allow two
+variables to be shown in the single display.
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/liver-1.pdf}
+\caption{The smoothed average of liver cancer diagnoses for Australian
+males. The divering colour scheme shows dark blue areas with much lower
+than average diagnoses, yellow areas with diagnoses around the
+Australian average, orange with above average and red shows diagnoses
+much higher than average.}
+\end{figure}
+
+Australia is an extreme case of heterogenous geographic units. To
+communicate information regarding the small inner city geographic units
+of Australian cities an alternative display must be employed. This will
+emphasise the value of the statistic that is relating to areas with high
+population levels. Figure @ref(fig:liver) shows the distribution of the
+smoothed average amount of Liver cancer diagnoses for Australian Males
+from XXX years. The hexagon tile map (b) shows orange hexagons for the
+inner city Statistical Areas at Level 2 with higher than average levels
+of diagnoses in the capital cities of Melbourne and Sydney. These inner
+city areas are not visible on the choropleth map (a). There are still
+many light blue areas in both displays. The northern Queensland, and
+Northern Territory SA2's with higher than average rates are still
+visible but utilise less map space on the hexagon tile map.
 
@@
 \subsection{Methodology}\label{methodology}}
+
+To test the
 
@@
 \end{itemize}
+
+The same data were shown on a choropleth map, and on a hexagon tile map.
+Comparing the results of participants who see the choropleth to those
+who see a hexagon tile map will show that population related
+distributions are spotted more frequently in a hexagon tile map display.
 
@@
 \(\delta_j\) is the trend model effect. We are allowing for an
-interaction between map type and trend model. Because the response is
-binary, a logistic model is used.
+interaction between map type and trend model. As the response for
+whether the participant detected the data plot is binary, a logistic
+model is used.
 
@@
 
-This required internet connection for participants to access the survey
+The demographics of the participants showed a skew towards male
+participants. The randomness of the group allocation also resulted in
+more participants being allocated to Group B. Due to the allocation of
+lineup displays the participants all saw six Choropleth displays and six
+Hexagon Tile Map displays.
 
@@
 
-\includegraphics{paper_files/figure-latex/detection_compare-1.pdf} The
-detection rates are usually higher when participants viewed the hexagon
-tile map displays. The difference was greater when viewing a three
-cities trend model. When the trend model affected all cities
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/detection_compare-1.pdf}
+\caption{The detection rates achieved by participants are contrasted
+when viewing the four replicates of the three trend models. Each point
+shows the probability of detection for the lineup display, the facets
+separate the trend models hidden in the lineup. The points for the same
+data set shown in a choroleth or haxgon tile map display are linked to
+show the difference in the detection rate.}
+\end{figure}
+
+The detection rates are usually higher when participants viewed the
+hexagon tile map displays. The difference was greater when viewing a
+three cities trend model. When the trend model affected all cities
 participants also detected the data display in the lineup of null plots
@@
 
-\begin{tabular}{l|l|r|r|r}
-\hline
-trend & type & replicate & mean & std.dev\\
-\hline
-NW-SE & Choro. & 1 & 25.00 & 16.41\\
-\hline
-NW-SE & Choro. & 2 & 21.12 & 15.28\\
-\hline
-NW-SE & Choro. & 3 & 21.12 & 17.05\\
-\hline
-NW-SE & Choro. & 4 & 21.20 & 14.52\\
-\hline
-NW-SE & Hex. & 1 & 19.53 & 14.56\\
-\hline
-NW-SE & Hex. & 2 & 21.95 & 16.42\\
-\hline
-NW-SE & Hex. & 3 & 22.02 & 16.12\\
-\hline
-NW-SE & Hex. & 4 & 18.17 & 14.51\\
-\hline
-three cities & Choro. & 1 & 15.30 & 13.88\\
-\hline
-three cities & Choro. & 2 & 25.22 & 14.36\\
-\hline
-three cities & Choro. & 3 & 22.49 & 15.87\\
-\hline
-three cities & Choro. & 4 & 18.68 & 13.74\\
-\hline
-three cities & Hex. & 1 & 20.37 & 17.02\\
-\hline
-three cities & Hex. & 2 & 19.95 & 16.59\\
-\hline
-three cities & Hex. & 3 & 20.02 & 17.19\\
-\hline
-three cities & Hex. & 4 & 18.02 & 16.93\\
-\hline
-all cities & Choro. & 1 & 20.14 & 16.56\\
-\hline
-all cities & Choro. & 2 & 22.75 & 14.72\\
-\hline
-all cities & Choro. & 3 & 19.88 & 15.03\\
-\hline
-all cities & Choro. & 4 & 19.33 & 16.15\\
-\hline
-all cities & Hex. & 1 & 19.83 & 15.87\\
-\hline
-all cities & Hex. & 2 & 16.96 & 14.65\\
-\hline
-all cities & Hex. & 3 & 19.21 & 15.27\\
-\hline
-all cities & Hex. & 4 & 20.03 & 15.11\\
-\hline
-\end{tabular}
-
 A t-test shows the difference between the detection rates for the two
@@
 
+The amount of time taken for a participants to submit a response is
+explored. The time considered was the amount of time it took for a
+participant to submit their choice of plot, the reason for their choice,
+and the perceived difficulty of the choice. The time was taken when each
+participant hit ``Next''.
+
+The relationship between time taken to submit, and the correct detection
+by the participant of the real data display in a lineup is considered in
+Figure @ref(fig:hist\_height). The bimodal distributions are similar
+across the type of display and the trend model hidden in the real data
+plot. The hexagon map displays have a peak for the group that took up to
+5 seconds to submit a response. When viewing a choropleth map display,
+the second peak occured at around 20 seconds. The longest a participant
+took to respond was 60 seconds.
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}
+
+The proportion of correct and incorrect responses within each 5 second
+time window. For the NW-SE distribution, it is equally likely that quick
+responders will be correct or incorrect. It is more likely that
+participants picked the correct response if they took longer to respond.
+For the Choropelth
+
+However, these quick responders were likely to be either correct or
+incorrect. The quick responders viewing a choropleth display were
+unlikely to choose correctly, unless viewing a NW-SE trend model.
+
+The choropleth map displays that included a distribution of three cities
+was very difficult for participants.
+
+\hypertarget{certainty}{%
+\subsection{Certainty}\label{certainty}}
+
 \begin{figure}
 \centering
-\includegraphics{paper_files/figure-latex/hist_height-1.pdf}
-\caption{The time taken to evaluate each display is broken into five
-second windows. The height of the histogram bars show how many
-evaulations were submitted within each time window. The distributions
-for the choropleth and hexagon tile maps are very similar. Both have a
-large peak at 0-5 seconds, and then a secondary peak at 10-20 seconds.
-No response took over one minute.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/hist_fill-1.pdf}
-\caption{The time taken to evaluate each display is broken into five
-second windows. The height of the histogram bars show the proportion of
-evaulations that were submitted within each time window.}
-\end{figure}
-
-\includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}
-
-\hypertarget{certainty}{%
-\subsection{Certainty}\label{certainty}}
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/unnamed-chunk-2-1.pdf}
+\includegraphics{paper_files/figure-latex/certainty-1.pdf}
 \caption{The amount of times each level of certainty was chosen by
@@
 Participants were more likely to choose a high certainty when
-considering a Choropleth map. The default certainty of 3 was chosen most
-for the Hexagon tile map displays.}
+considering a Choropleth map. The mid value of 3 was the default
+certainty, it was chosen most for the Hexagon tile map displays.}
 \end{figure}
@@
 Certainty levels are measured on a five point scale---they are
-subjective assessments by the participant `how certain are you about
+subjective assessments by the participant `How certain are you about
 your choice?'.
@@
 \centering
-\includegraphics{paper_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{The most common reason for choice of plot when looking at each
-trend model shown in Choropleth and Hexagon Tile maps. Clusters were the
-most common reason when viewing a Hexagon Tile map, trend was the most
-common choice for choropleth displays except for the all cities
-display.}
+\includegraphics{paper_files/figure-latex/reason-1.pdf}
+\caption{The amount of participants that selected each reason for their
+choice of plot when looking at each trend model shown in Choropleth and
+Hexagon Tile maps. The facets show whether or not the choice was
+correct.}
 \end{figure}
+
+The most common choice made by participant was clusters, this response
+was expected when participants viewed the Hexagon display of the all
+cities and three cities distributions.
 
@@
 \centering
-\includegraphics{paper_files/figure-latex/unnamed-chunk-4-1.pdf}
+\includegraphics{paper_files/figure-latex/contributors-1.pdf}
 \caption{The probablity of detection acheived by the contributors in
@@
 
-\hypertarget{reason-1}{%
-\subsection{Reason}\label{reason-1}}
-
-\includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf}
-
 \begin{figure}
@@
 points show the proportion of the participants that made each choice
-when considering each lineup. The points coloureddark blue show the map
+when considering each lineup. The points coloured orange show the map
 which contained a trend model, these are the correct choices. The
@@
 The choices made by participants are examined in Figure
-\ref{fig:choices}. Participants were misled by the choropleth display,
+@ref(fig:choices). Participants were misled by the choropleth display,
 but not the hexagon display for all cities displays except (2). The maps
@@
 one participant select the correct map in the lineup as shown in Figure
-\ref{fig:choices}.
+@ref(fig:choices\}.
 
@@
 
-A generalized linear mixed effects model can account for each individual
-participants' abilities as it includes a subject-specific random
-intercept. As each participant provides results from 12 lineups.
-
-This includes the two main effects map type and trend model, which gives
-the fixed effects part of the model to be
-
-\[\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3\]
+The likelihood of detecting the data plot in the lineup can be modelled
+using a generalized linear mixed effects model. The base R (R Core Team
+\protect\hyperlink{ref-RCore}{2019}) \texttt{glm()} function implements
+generalised linear models. The model used includes the two main effects
+map type and trend model, which gives the fixed effects model to be:
+
+\[\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij} + \epsilon_{i,j}, ~~~ i=1,2; ~j=1,2,3\]
 
@@
 interaction between map type and trend model. Because the response is
-binary, a logistic model is used.
+binary, a logistic model is used. This model can account for each
+individual participants' abilities as it includes a subject-specific
+random intercept. As each participant provides results from 12 lineups.
 
@@
 
-\begin{tabular}{l|r|r|r|r|l}
-\hline
-\_ & terms & Estimate & Error & p.value & sig\\
-\hline
-Design & Choro & 0.0217400 & 0.1474507 & 0.8828 & \\
-\hline
- & Hex & 0.4200928 & 0.2110904 & 0.0466 & *\\
-\hline
-Trend & Three cities & -3.2519793 & 0.4124809 & 0.0000 & ***\\
-\hline
- & All cities & -1.2398974 & 0.2293327 & 0.0000 & ***\\
-\hline
-Interactions & Hex : Three cities & 2.3683138 & 0.4645163 & 0.0000 & ***\\
-\hline
- & Hex : All cities & 1.0825772 & 0.3123987 & 0.0005 & ***\\
+The model specifies a logistic link, this means the predicted values
+from the \texttt{glm} model should be back-transformed to fit between 0
+and 1. They are transformed with the link specified below:
+
+\[\mu = \frac{e^{\eta}}{1 + e^{\eta}}\] \[\eta = f(\tau_i,\delta_j)\]
+
+\begin{tabular}{l|r|r|r|r|l|l}
+\hline
+\_ & terms & Estimate & Error & Stat & p.value & sig\\
+\hline
+Design & Intercept & 0.0217400 & 0.1474507 & 0.1474391 & 0.8828 & \\
+\hline
+ & Hex & 0.4200928 & 0.2110904 & 1.9901083 & 0.0466 & *\\
+\hline
+Trend & Three cities & -3.2519793 & 0.4124809 & -7.8839514 & 0.0000 & ***\\
+\hline
+ & All cities & -1.2398974 & 0.2293327 & -5.4065450 & 0.0000 & ***\\
+\hline
+Interactions & Hex : Three cities & 2.3683138 & 0.4645163 & 5.0984512 & 0.0000 & ***\\
+\hline
+ & Hex : All cities & 1.0825772 & 0.3123987 & 3.4653698 & 0.0005 & ***\\
 \hline
@@
 ##                 
-##        No Yes
-##   No  431 121
-##   Yes 242 310
+##                  Detected? No Detected? Yes
+##   Predicted: No           431           121
+##   Predicted: Yes          242           310
 \end{verbatim}
@@
 
-\includegraphics{paper_files/figure-latex/unnamed-chunk-8-1.pdf}
+The estimated marginal mean is the fitted value from a model over the
+treatment effects. The treatment effects considered in this model are
+map type displayed, trend model included, and the replicate. The
+\texttt{emmeans} package is used to calculate the estimated marginal
+mean. The value, between 0 and 1, can be interpretted as the probability
+of detecting the real data plot in the lineup, for each combination of
+map type, trend model and replicate.
+
+\includegraphics{paper_files/figure-latex/unnamed-chunk-3-1.pdf}
 
@@
 ## 2 typeHex.                      0.103    0.0448      2.31 fixed      
-## 3 trendthree cities            -0.467    0.0448    -10.4  fixed      
-## 4 trendall cities              -0.277    0.0448     -6.19 fixed      
-## 5 typeHex.:trendthree cities    0.250    0.0633      3.95 fixed      
-## 6 typeHex.:trendall cities      0.239    0.0633      3.77 fixed      
+## 3 trendThree Cities            -0.467    0.0448    -10.4  fixed      
+## 4 trendAll Cities              -0.277    0.0448     -6.19 fixed      
+## 5 typeHex.:trendThree Cities    0.250    0.0633      3.95 fixed      
+## 6 typeHex.:trendAll Cities      0.239    0.0633      3.77 fixed      
 ## 7 sd_(Intercept).contributor    0.118   NA          NA    contributor
@@
 ##      
-##        No Yes
+##       Detected? No Detected? Yes
 ##   No            49             1
@@
 ##      
-##        No Yes
+##       Detected? No Detected? Yes
 ##   No             0             0
@@
 \end{verbatim}
-
-\includegraphics{paper_files/figure-latex/unnamed-chunk-11-1.pdf}
 
@@
 ##                     0.5054                      0.1033  
-##          trendthree cities             trendall cities  
+##          trendThree Cities             trendAll Cities  
 ##                    -0.4674                     -0.2772  
-## typeHex.:trendthree cities    typeHex.:trendall cities  
+## typeHex.:trendThree Cities    typeHex.:trendAll Cities  
 ##                     0.2500                      0.2391

### 2020-01-07 paper/paper.Rmd
reasons table not plot

--- 2020-01-06 paper/paper.Rmd
@@
 library(emmeans)
+library(kableExtra)
 ```
@@
 
+```{r desc_stats, results = "asis"}
+types <- c("Choro.", "", "Hex.", "")
+
+d %>% group_by(type, trend) %>%
+  summarise(m = round(mean(detect),3),
+    std.dev = paste0("(", round(sd(detect),2),")")) %>% 
+  gather(stat, value, m, std.dev) %>% 
+  pivot_wider(names_from = "trend", values_from = "value") %>% 
+  arrange(type) %>% ungroup() %>% 
+  mutate(Type = types) %>% select(Type, `NW-SE`, `Three Cities`, `All Cities`) %>%
+  knitr::kable(., format = "latex", align = "lccc")
+```
+
+The probability of detection is explored for each of the combinations of trans and type of display.
+
 ## Speed
@@
 # Qualitative analysis of reason
-d <- d %>% 
-  mutate(reason = ifelse(reason =="0.0", "no reason", reason))
-
-ggplot(d %>% mutate(Detected = factor(detect, levels = c(0,1), 
-  labels = c("Detected? No", "Detected? Yes")),
-  `Map Type` = type)) + 
-  geom_bar(aes(x = fct_infreq(reason), fill = `Map Type`)) +  
-  facet_grid(trend ~ Detected) +  
-  scale_fill_manual(values = type_colours) +
-  xlab("Type of areas visualised") + 
-  theme(legend.position = "bottom") + coord_flip()
+d %>% 
+  mutate(reason = ifelse(reason =="0.0", "no reason", reason)) %>% 
+  mutate(Detected = gsub("Detected? ", "", detect_f)) %>% 
+  group_by(trend, Detected, type) %>% 
+  count(reason) %>% 
+  mutate(prop = round(n/sum(n), 3), r_prop = paste0(reason, ":", prop)) %>% 
+  top_n(1, n) %>% summarise(reasons = paste(reason, collapse=", ")) %>% 
+  pivot_wider(names_from = c("Detected"), values_from = c("reasons")) %>% 
+  arrange(trend, type) %>% 
+  select(Trend = trend, `Map Type` = type,
+    `Yes` = `Detected? Yes`, `No` = `Detected? No`) %>% 
+  knitr::kable(., format = "latex") %>% kable_styling("striped") %>%
+  add_header_above(c(" " = 2, "Detected:" = 2))
 ```
@@
 All of three cities displays, except (4), were detected in the hexagon display.
-All except one lineup had at least one participant select the correct map in the lineup as shown in Figure \@ref(fig:choices}.
+All except one lineup had at least one participant select the correct map in the lineup as shown in Figure \@ref(fig:choices).
 
@@
 $$\widehat{y_{ij}} = 0.0217 + 0.42Hex -3.25_{three} -1.24_{all} + 2.37{Hex.three} + 1.08{Hex.all} $$
-
-The estimated marginal mean is the fitted value from a model over the treatment effects.
-The treatment effects considered in this model are map type displayed, trend model included, and the replicate.
-The `emmeans` package is used to calculate the estimated marginal mean.
-The value, between 0 and 1, can be interpretted as the probability of detecting the real data plot in the lineup, for each combination of map type, trend model and replicate.
 

### 2020-01-08 paper/paper.Rmd
Add replicates table for exp design. Add examples of lineups

@@
 
-Introduction
-=============
-<!-- no \IEEEPARstart -->
-<!-- (should never be an issue) -->
-
-<!-- General: comparison of displays, motivate hexagon tile map, enough info to motivate aims -->
-<!-- geographies on choropleth -->
-A geographic map base is commonly used to present geospatial statistics.
-The statistics presented may also be aggreagated statistics for geographic units, in this case the choropleth map is the common display used.
-Choropleth maps are often used to present statistics regarding the population.
-Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic. 
-The several sets of Australian statistical areas presents an example of a heterogrenous distribution.
-The rural communities in Australia operate on a much larger geographic space than small inner city communities.
-This has the negative effect of incorrectly showing the spatial distribution of the statistic, especially when a spatial distribution is related to the size of the areas, or the population density.
-An alternative display can be used to effectively communicate a spatial distribution for a set of heterogeneous areas.
-
-Motivation
-=============
-
-<!-- Find a new display for the Cancer Atlas -->
-
-## The Australian Cancer Atlas
-
-The Australian Cancer Atlas is an online interactive web tool created to explore the burden of cancer on Australian communities.
-There are many cancer types presented, and they can be explored on an individual or aggregate level.
-The Australian communities are examined at the Statistical Areas at Level 2 (SA2) [@abs2016] used by the Australian Bureau of Statistics.
-Bayesian spatial smoothing has been applied to incorporate the value of the statistics of the neighbouring areas.
-Spatial smoothing allows for the protection privacy and gives stability to the estimates.
-The statistics mapped are the diagnoses (Standardised Incidence Rates) and excess deaths for each SA2, communicated as the difference from the Australian average of the statistics.
-The values of the statistic for each geographic area is communicated through the colour used to fill the areas, the colours are chosen for the diverging colour scheme.
-The Australian Cancer Atlas communicates the trends in the distributions of cancer over geographic space.
-It uses a choropleth map display and diverging colour scheme to draw attention to relationships between neighbouring areas.
-
-Background
-=============
-
-## Population focussed displays
-
-Spatial visualisations communicate the distribution of statistics over geographic space.
-The most common display for spatial data is the choropleth map.
-However, the issue of using a choropleth map base becomes obvious when considering population related distributions.
-Map creators have the ability to present spatial statistics in alternative displays that can highlight the population.
-This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
-When presenting population statistics on a geographic map base, the size of the regions can allow errornous conclusions to be drawn about the state of the statistic over the entire population.
-This occurs as large regions filled with a consistent colour or pettern can draw the attention of map readers, and small regions are not paid equal attention.
-A choropleth map is not the only display that can be used for presenting geospatial data. 
-Alternative maps include various cartograms, and tesselated tile maps. They allow other variables to be included in the display to highlight the staistical values of various geographic areas.
-
-<!-- Cartogram -->
-
-A cartogram transforms the geographic map base.
-The transformation begins with a choropleth map base, and the associated populations.
-There are several algorithms for transforming, they all involve shifting boundaries to increase or descrease the area of the geographic units on the map depending on the statistics.
-<!-- Why not a cartogram-->
-The shifts of the boundaries result in cartograms with accurate map area for each of the geographic units.
-The transformation will keep boundaries of neighbouring areas connected, but the result is unfamiliar shapes for each geographic unit.
-
-<!-- Tesselated tile gram & hexagon tile map-->
-Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units.
-The non-contiguous cartgoram method keep the shapes of geographic units intact, and change the size to communicate the values of statistics.
-This method breaks the spatial relationship between areas, and emphasises the difference between the statistic and the amount of land for each geographic unit.
-The Dorling cartogram is another method that does not retain the boundaries of geographic units.
-Each unit becomes one circle on the cartogram dispaly, these can be sized according to the value of a variable.
-Their neighbours can be illustrated by connecting the boundaries of the circles.
-These cartogram methods all allow two variables to be shown in the single display.
-
-```{r liver, fig.height = 9, fig.width = 6, fig.cap = "The smoothed average of liver cancer diagnoses for Australian males.
-The divering colour scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average."}
-ggdraw(ylim = c(0,2), xlim = c(0,1.3), clip = "on") +
-  draw_plot(rasterGrob(readPNG("figures/aus_liver_m.png")), -0.15, 0.9, 1.6, 1.2) +
-  draw_plot(rasterGrob(readPNG("figures/aus_liver_m_hex.png")), -0.15, -0.1, 1.6, 1.2) +
-  draw_plot_label(c("a", "b"), 
-    c(0.05, 0.05), c(1.95, 1), size = 20, color = "white") + 
-  theme(plot.background = element_rect(fill = "black"))
-```
-
-<!-- Specific problem for Australia -->
-Australia is an extreme case of heterogenous geographic units.
-To communicate information regarding the small inner city geographic units of Australian cities an alternative display must be employed.
-This will emphasise the value of the statistic that is relating to areas with high population levels.
-Figure \@ref(fig:liver) shows the distribution of the smoothed average amount of Liver cancer diagnoses for Australian Males from XXX years.
-The hexagon tile map (b) shows orange hexagons for the inner city Statistical Areas at Level 2 with higher than average levels of diagnoses in the capital cities of Melbourne and Sydney.
-These inner city areas are not visible on the choropleth map (a).
-There are still many light blue areas in both displays.
-The northern Queensland, and Northern Territory SA2's with higher than average rates are still visible but utilise less map space on the hexagon tile map.
-
-## Methodology
-
-To test the
-
-## Visual Inference
-- Communicating data through visualisations
-- Effective displays for types of data
-- Protocol for testing the effectiveness
-
-The same data were shown on a choropleth map, and on a hexagon tile map.
-Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.
-
-Classical statistical inference involves hypothesis testing, the process of rejecting a null hypothesis in favour of an alternative.
-This approach relies on data, the appropriate distributions and their assumptions.
-Visual inference null hypothesis: independence in the variables (absence of all features), alternative hypothesis: Relationship between the variables (presence of some feature).
-<!--
-GTPCCD
-In visual inference, data plots are considered to be test statistics, and these are compared with plots of data generated from a null hypothesis using a lineup
-
-The null hypothesis underlying a
-lineup is that there is no real structure visible in the data plot, that any
-patterns seen are consistent with randomness, or from a known model.
-If the null hypothesis is true then the plot of the data will not be distinguishable
-from the plots of null data.
-
-Different lineups are created, using the same data, same null plots and
-positions within the lineup, but different plot designs.
-
-Comparing how
-long viewers take and how accurately they report the feature of interest
-will assess which design is better for the task.
--->
-
-<!--
-A null dataset
-is a sample from the null distribution, i.e. an example of an innocent
-dataset, and a null plot is a plot of a null dataset, showing what an
-innocent might look like.
-
-testing can be adapted to work visually instead of numerically.[@GIIV]
-Graphical Inference for Infovis
-Chloropleth maps Is there a spatial trend?
-
-Simulation. We might be interested in a more specific set of hypothesis:
-does time increase linearly with distance from target?
-Does accuracy decrease exponentially as number of distractors
-increases? In those cases we have a probabilistic model and we
-can generate null data sets by sampling from the distribution implied
-by the model. This approach is used in Section 4.2.
--->
-
-The lineup protocol is used for visual inference testing.
-1. simulate null plots 
-2. Insert data with structure into a random location
-3. Ask uninvolved person to select the most different plot
-4. If location is chosen correctly, the existence of a feature is significant at $\alpha = 1/N$.
-
-> "In this framework, plots take on the role of test statistics, and human cognition the role of statistical tests." @SIEDAMD
-
-The line up protocol involves placing a "guilty" data visualisation in a lineup of "innocents". Where the guilty data set contains structure, and the innocents are equivalent to a null data set. 
-In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the group innocents.
-The guilty data is identified as different from the innocent data with probability $1/m$, where $m$ is the number of null plots plus 1 to account account for the guilty data set.
-When the guilty data set is chosen, the null hypothesis that it was innocent is rejected with a $1/m$ chance or type I error of being wrong.
-
-The lineup protocol can be used in a variety of testing scenarios. The choropleth map is best used for testing spatial structure in a data set.
-
-<!--
-The line-up protocol works like a police line-up: the suspect (test
-statistic plot) is hidden in a set of decoys. If the observer, who has not
-seen the suspect, can pick it out as being noticeably different, there is
-evidence that it is not innocent.
--->
-
-Study Design
-============
-
-This study aims to answer several questions around the presentation of spatial distributions:
-
-1. Are spatial disease trends, that impact highly populated small areas, detected with higher accuracy when viewed in a hexagon tile map display?
-
-2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when
-using a hexagon tile map display?
-
-additional considerations when completing this experimental task included exploration of the difficulty experienced by participants
-
-<!--
- Do people find hexagon tile maps more difficult to read than choropleth maps?
- Are the reasons for choosing a plot different depending on the type of display?
--->
-
-The mean of the detection rate for choropleth map, denoted as $\mu_C$, and the hexagon tile maps, $\mu_H$ will be contrasted. This leads to the following one sided hypothesis for this study:
-
-$H_0$ : $\mu_H$ = $\mu_C$
-$H_a$ : $\mu_H$ > $\mu_C$
-
-The detection rate $\hat\pi$ is calculated as the amount of people that made the choice of plot that contained the real data, out of the participants who saw data plot in the lineup of the null data plots.
-
-The difference in the detection rates for the two displays will be compared using the following:
-
-$$ \hat\pi_C - \hat\pi_H \pm t_{1-\alpha,n-1}\sqrt{\hat\pi_C(1-\hat\pi_C)/n_C + \hat\pi_H(1-\hat\pi_H)/n_H} $$
-
-## Experimental design
-
-The most common display for spatial cancer data is the choropleth map.
-This will be the comparative visualisation for presenting the lineups [@VVSIALM].
-Most geographic distributions will have some degree of spatial autcorrelation between neighbours.
-This feature will exist in all plots in the lineup displays, the plot that contains the trend feature shown in only one set of data will also be affected by spatial autocorrelation.
-A reasonable amount of null plots $N-1$ in the lineup was chosen to ensure data is well hidden. For the detailed choropleth of Australian SA2 areas, we set $N = 12$ to not overwhelm participants.
-A line up protocol was implemented to arrange 12 maps in each display. 
-Individual displays were created by a combination of map type, and spatial trend model.
-
-The hypotheses for each lineup are
-$H_0$ : All plots look the same
-$H_a$ : One plot looks different to the other plots
-
-Recruited participants to be uninvolved judges with no prior knowledge of the data to avoid discrimination or advantages.
-The online crowdsource platform Figure-Eight was used to recruit participants.
-
-The researchers contrasted the different plot designs, as hexagon tilemap and geography in the lineups were created using the same data, and same null positions within the lineup.
-
-Let $n$ be the number of independent observers and $x_i$ the
-number of observers who picked plot $i$, $i = \{1,...,m\}$
-
-Then $x_i, x_2, ..., x_m$ follows a multinomial
-distribution$Mult_{\pi_1, \pi_2, ...., \pi_m}(x_i, x_2, ..., x_m)$ with 
-$\sum_i \pi_i = 1$, where $\pi_i$ is the probability that plot $i$ is picked by an
-observer, which we can estimate as $\hat{\pi}_i = x_i/n$.
-The researchers compared the length of time taken, and the accuracy of the participants choices.
-The power of a lineup can therefore be estimated as the ratio of correct
-identifications $x$ out of $n$ viewings.
-
-## The variables being manipulated and measured
-
-The variables that were changed between groups were the type of plot shown and the trend model.
-
-Each participant was randomly allocated to either Group A or Group B when they begun the survey. This resulted in 42 participants allocated to Group A, and 53 participants allocated to Group B.
-
-The levels of the factors measured in the experiment were:
-- Map type: *Choropleth, Hexagon tile*
-- Trend: *Locations in three population centres, Locations in multiple population centres, South-East to North-West*
-
-Factor combinations examined by each participant amount to 6 (2x3) lineup displays.
-A participant did see the same data for both map types. Four simulated sets of data were generated for each treatment.
-This will generate 24 lineups (12 were geographic maps, and 12 were hexagon tile maps). Participants will evaluate 12 lineups, 6 of each map type. Appendix A shows the experimental design visually.
-For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants.
-
-\begin{table}[]
-\caption{The Experimental Design}
-\label{tab:my-table}
-\begin{tabular}{|l|l|l|}
-\hline
-Trend & Map type & Replicates \\ \hline
-NW-SE & Choropleth & 2 \\ \hline
- & Hexagon tile & 2 \\ \hline
-Three cities & Choropleth & 2 \\ \hline
- & Hexagon tile & 2 \\ \hline
-All cities & Choropleth & 2 \\ \hline
- & Hexagon tile & 2 \\ \hline
-\end{tabular}
-\end{table}
-
-The variables measured as a result of the changes were the probability of detection each display and the time taken to submit responses.
-To measure the accuracy of the detections, the plot chosen for each lineup evaluated was compared to the position of the real spatial trend plot in the lineup.
-A correct result occurs when the chosen plot matches the position of the real plot, this was recorded in an additional binary variable; 1 = correct; 0 = incorrect.
-High efficiency occurs when a small amount of time is taken to evaluate each lineup.
-This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.
-
-## Simulation process
-
-The underlying spatial correlation model was created to provide spatial autocorrelation between neighbouring areas using the longitude and latitude values for the Statistical Areas.
-formula = z ~ 1, locations = ~ longitude + latitude
-
-Simulated spatially dependent data using the model on the centroids of each area, for 12 null plots in 12 lineups.
-
-12 sets of data were created.
-In these 12 sets of data, each of the 144 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas.
-
-For each of the 144 individual maps, the values attributed to each geographic area are rescaled to show a similar colour scale from deep blue to dark red within each map.
-
-A random location was selected for each set of lineup data.
-In this location, a trend model was overlaid on the null set of spatially correlated data.
-Each set of lineup data was used to produce a choropleth maps and hexagon tile maps. These matched pairs were split between Group A and Group B.
-
-## Participants
-
-There were 95 participants involved in the study. 
-We recruited participants using the Figure-Eight crowd source platform by advertising this survey to participants that fulfilled the following crtieria:
-
-- level 2 or level 3 on the Figure-Eight Platform.
-- at least 18 years old
-
-Participants then selected our task from the list of tasks available to them.
-
-Each participant was trained using three test displays orienting them to the evaluation task.
-Participants then proceeded to the survey, this involved evaluating 12 displays.
-
-## Experiment procudure and data collection
-
-The participant answered demographic questions and provided consent before evaluating the lineups.
-
-Demographics were collected regarding the study participants:
-- Gender (female / male / other),
-- Degree education level achieved (high school / bachelors / masters / doctorate / other),
-- Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
-- Lived at least for one year in Australia (Yes / No )
-
-Participants then moved to the evaulation phase.
-The set of images differed for Group A and Group B.
-After being allocated to a group, each individual was shown the 12 displays in randomised order.
-
-Three questions were asked regarding each display:
-- Plot choice
-- Reason
-- Difficulty
-
-After completing the 12 evaluations, the participants were asked to submit their responses.
-
-Data was collected through a web application containing the online survey.
-Each participant used the internet to access the survey.
-The data collection took place using a secure link between the survey web application and the googlesheet used to store results.
-The application would first connect to the googlesheet using the googlesheets [@sheets] R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
-
-## The methods of data analysis used
-The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R [@RCore].
-
-For each of the 12 lineup displays the researchers calculated:
-- accuracy: the proportion of subjects who detected the data plot
-- efficiency: average time taken to respond
-
-### Visualisations
-Side-by-side dot plots were made of accuracy (efficiency) against map type, facetted by trend model type.
-
-Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.
-
-Plots will be made in R (R Core Team 2019), with the ggplot2 package (Wickham 2016).
-
-### Modeling
-
-The results will be analysed using a generalised linear model, with a subject random effect to account for differences in individuals.
-There will be two main effects: map type and trend model, which gives the fixed effects part of the model to be
-
-$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3$$
-
-where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
-We are allowing for an interaction between map type and trend model. As the response for whether the participant detected the data plot is binary, a logistic model is used.
-
-A similar model will be constructed for the efficiency, using a log time, and normal errors.
-
-The feedback and demographic variables will possibly be incorporated as covariates.
-
-Computation will be done using R [@RCore], with the `lme4` package [@lme4].
-
-## Limitations of the data collection
-
-The demographics of the participants showed a skew towards male participants. 
-The randomness of the group allocation also resulted in more participants being allocated to Group B.
-Due to the allocation of lineup displays the participants all saw six Choropleth displays and six Hexagon Tile Map displays.
-
-Results
-============
-
 ```{r data}
@@
 ```
-
-The survey responses from participants were kept only if the participant submitted answers for all 12 displays. This resulted in 92 participants.
 
@@
 
-The contributors who gave various plot choices and reasons for the twelve displays were kept.
-The contributors who detected no plots correctly were analysed further. Three of these contribuotrs gave no choices for any of the twelve displays. They were also removed for the rest of the analysis.
-
-Of the 92 participants, 67 were male, and 25 female. Only two of the participants had lived in Australia before.
-The education level achieved by the participants was 70 Bachelors or Masters degree.
-
-# Accuracy
-
-The detection rate for participants reporting the real data trend model is used to calculate the accuracy of the responses of participants.
-
 ```{r pdetection_group}
@@
 
+Introduction
+=============
+<!-- no \IEEEPARstart -->
+<!-- (should never be an issue) -->
+
+<!-- General: comparison of displays, motivate hexagon tile map, enough info to motivate aims -->
+<!-- geographies on choropleth -->
+A geographic map base is commonly used to present geospatial statistics.
+The statistics presented may also be aggreagated statistics for geographic units, in this case the choropleth map is the common display used.
+Choropleth maps are often used to present statistics regarding the population.
+Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic. 
+The several sets of Australian statistical areas presents an example of a heterogrenous distribution.
+The rural communities in Australia operate on a much larger geographic space than small inner city communities.
+This has the negative effect of incorrectly showing the spatial distribution of the statistic, especially when a spatial distribution is related to the size of the areas, or the population density.
+An alternative display can be used to effectively communicate a spatial distribution for a set of heterogeneous areas.
+
+Motivation
+=============
+
+<!-- Find a new display for the Cancer Atlas -->
+
+## The Australian Cancer Atlas
+
+The Australian Cancer Atlas is an online interactive web tool created to explore the burden of cancer on Australian communities.
+There are many cancer types presented, and they can be explored on an individual or aggregate level.
+The Australian communities are examined at the Statistical Areas at Level 2 (SA2) [@abs2016] used by the Australian Bureau of Statistics.
+Bayesian spatial smoothing has been applied to incorporate the value of the statistics of the neighbouring areas.
+Spatial smoothing allows for the protection privacy and gives stability to the estimates.
+The statistics mapped are the diagnoses (Standardised Incidence Rates) and excess deaths for each SA2, communicated as the difference from the Australian average of the statistics.
+The values of the statistic for each geographic area is communicated through the colour used to fill the areas, the colours are chosen for the diverging colour scheme.
+The Australian Cancer Atlas communicates the trends in the distributions of cancer over geographic space.
+It uses a choropleth map display and diverging colour scheme to draw attention to relationships between neighbouring areas.
+
+Background
+=============
+
+## Population focussed displays
+
+Spatial visualisations communicate the distribution of statistics over geographic space.
+The most common display for spatial data is the choropleth map.
+However, the issue of using a choropleth map base becomes obvious when considering population related distributions.
+Map creators have the ability to present spatial statistics in alternative displays that can highlight the population.
+This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
+When presenting population statistics on a geographic map base, the size of the regions can allow errornous conclusions to be drawn about the state of the statistic over the entire population.
+This occurs as large regions filled with a consistent colour or pettern can draw the attention of map readers, and small regions are not paid equal attention.
+A choropleth map is not the only display that can be used for presenting geospatial data. 
+Alternative maps include various cartograms, and tesselated tile maps. They allow other variables to be included in the display to highlight the staistical values of various geographic areas.
+
+<!-- Cartogram -->
+
+A cartogram transforms the geographic map base.
+The transformation begins with a choropleth map base, and the associated populations.
+There are several algorithms for transforming, they all involve shifting boundaries to increase or descrease the area of the geographic units on the map depending on the statistics.
+<!-- Why not a cartogram-->
+The shifts of the boundaries result in cartograms with accurate map area for each of the geographic units.
+The transformation will keep boundaries of neighbouring areas connected, but the result is unfamiliar shapes for each geographic unit.
+
+<!-- Tesselated tile gram & hexagon tile map-->
+Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units.
+The non-contiguous cartgoram method keep the shapes of geographic units intact, and change the size to communicate the values of statistics.
+This method breaks the spatial relationship between areas, and emphasises the difference between the statistic and the amount of land for each geographic unit.
+The Dorling cartogram is another method that does not retain the boundaries of geographic units.
+Each unit becomes one circle on the cartogram dispaly, these can be sized according to the value of a variable.
+Their neighbours can be illustrated by connecting the boundaries of the circles.
+These cartogram methods all allow two variables to be shown in the single display.
+
+```{r liver, fig.height = 9, fig.width = 6, fig.cap = "The smoothed average of liver cancer diagnoses for Australian males.
+The divering colour scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average."}
+ggdraw(ylim = c(0,2), xlim = c(0,1.3), clip = "on") +
+  draw_plot(rasterGrob(readPNG("figures/aus_liver_m.png")), -0.15, 0.9, 1.6, 1.2) +
+  draw_plot(rasterGrob(readPNG("figures/aus_liver_m_hex.png")), -0.15, -0.1, 1.6, 1.2) +
+  draw_plot_label(c("a", "b"), 
+    c(0.05, 0.05), c(1.95, 1), size = 20, color = "white") + 
+  theme(plot.background = element_rect(fill = "black"))
+```
+
+<!-- Specific problem for Australia -->
+Australia is an extreme case of heterogenous geographic units.
+To communicate information regarding the small inner city geographic units of Australian cities an alternative display must be employed.
+This will emphasise the value of the statistic that is relating to areas with high population levels.
+Figure \@ref(fig:liver) shows the distribution of the smoothed average amount of Liver cancer diagnoses for Australian Males from XXX years.
+The hexagon tile map (b) shows orange hexagons for the inner city Statistical Areas at Level 2 with higher than average levels of diagnoses in the capital cities of Melbourne and Sydney.
+These inner city areas are not visible on the choropleth map (a).
+There are still many light blue areas in both displays.
+The northern Queensland, and Northern Territory SA2's with higher than average rates are still visible but utilise less map space on the hexagon tile map.
+
+## Methodology
+
+To test the
+
+## Visual Inference
+- Communicating data through visualisations
+- Effective displays for types of data
+- Protocol for testing the effectiveness
+
+The same data were shown on a choropleth map, and on a hexagon tile map.
+Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.
+
+Classical statistical inference involves hypothesis testing, the process of rejecting a null hypothesis in favour of an alternative.
+This approach relies on data, the appropriate distributions and their assumptions.
+Visual inference null hypothesis: independence in the variables (absence of all features), alternative hypothesis: Relationship between the variables (presence of some feature).
+<!--
+GTPCCD
+In visual inference, data plots are considered to be test statistics, and these are compared with plots of data generated from a null hypothesis using a lineup
+
+The null hypothesis underlying a
+lineup is that there is no real structure visible in the data plot, that any
+patterns seen are consistent with randomness, or from a known model.
+If the null hypothesis is true then the plot of the data will not be distinguishable
+from the plots of null data.
+
+Different lineups are created, using the same data, same null plots and
+positions within the lineup, but different plot designs.
+
+Comparing how
+long viewers take and how accurately they report the feature of interest
+will assess which design is better for the task.
+-->
+
+<!--
+A null dataset
+is a sample from the null distribution, i.e. an example of an innocent
+dataset, and a null plot is a plot of a null dataset, showing what an
+innocent might look like.
+
+testing can be adapted to work visually instead of numerically.[@GIIV]
+Graphical Inference for Infovis
+Chloropleth maps Is there a spatial trend?
+
+Simulation. We might be interested in a more specific set of hypothesis:
+does time increase linearly with distance from target?
+Does accuracy decrease exponentially as number of distractors
+increases? In those cases we have a probabilistic model and we
+can generate null data sets by sampling from the distribution implied
+by the model. This approach is used in Section 4.2.
+-->
+
+The lineup protocol is used for visual inference testing.
+1. simulate null plots 
+2. Insert data with structure into a random location
+3. Ask uninvolved person to select the most different plot
+4. If location is chosen correctly, the existence of a feature is significant at $\alpha = 1/N$.
+
+> "In this framework, plots take on the role of test statistics, and human cognition the role of statistical tests." @SIEDAMD
+
+The line up protocol involves placing a "guilty" data visualisation in a lineup of "innocents". Where the guilty data set contains structure, and the innocents are equivalent to a null data set. 
+In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the group innocents.
+The guilty data is identified as different from the innocent data with probability $1/m$, where $m$ is the number of null plots plus 1 to account account for the guilty data set.
+When the guilty data set is chosen, the null hypothesis that it was innocent is rejected with a $1/m$ chance or type I error of being wrong.
+
+The lineup protocol can be used in a variety of testing scenarios. The choropleth map is best used for testing spatial structure in a data set.
+
+<!--
+The line-up protocol works like a police line-up: the suspect (test
+statistic plot) is hidden in a set of decoys. If the observer, who has not
+seen the suspect, can pick it out as being noticeably different, there is
+evidence that it is not innocent.
+-->
+
+Study Design
+============
+
+This study aims to answer several questions around the presentation of spatial distributions:
+
+1. Are spatial disease trends, that impact highly populated small areas, detected with higher accuracy when viewed in a hexagon tile map display?
+
+2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when
+using a hexagon tile map display?
+
+additional considerations when completing this experimental task included exploration of the difficulty experienced by participants
+
+<!--
+ Do people find hexagon tile maps more difficult to read than choropleth maps?
+ Are the reasons for choosing a plot different depending on the type of display?
+-->
+
+The mean of the detection rate for choropleth map, denoted as $\mu_C$, and the hexagon tile maps, $\mu_H$ will be contrasted. This leads to the following one sided hypothesis for this study:
+
+$H_0$ : $\mu_H$ = $\mu_C$
+$H_a$ : $\mu_H$ > $\mu_C$
+
+The detection rate $\hat\pi$ is calculated as the amount of people that made the choice of plot that contained the real data, out of the participants who saw data plot in the lineup of the null data plots.
+
+The difference in the detection rates for the two displays will be compared using the following:
+
+$$ \hat\pi_C - \hat\pi_H \pm t_{1-\alpha,n-1}\sqrt{\hat\pi_C(1-\hat\pi_C)/n_C + \hat\pi_H(1-\hat\pi_H)/n_H} $$
+
+## Experimental design
+
+The most common display for spatial cancer data is the choropleth map.
+This will be the comparative visualisation for presenting the lineups [@VVSIALM].
+Most geographic distributions will have some degree of spatial autcorrelation between neighbours.
+This feature will exist in all plots in the lineup displays, the plot that contains the trend feature shown in only one set of data will also be affected by spatial autocorrelation.
+A reasonable amount of null plots $N-1$ in the lineup was chosen to ensure data is well hidden. For the detailed choropleth of Australian SA2 areas, we set $N = 12$ to not overwhelm participants.
+A line up protocol was implemented to arrange 12 maps in each display. 
+Individual displays were created by a combination of map type, and spatial trend model.
+
+The hypotheses for each lineup are
+$H_0$ : All plots look the same
+$H_a$ : One plot looks different to the other plots
+
+Recruited participants to be uninvolved judges with no prior knowledge of the data to avoid discrimination or advantages.
+The online crowdsource platform Figure-Eight was used to recruit participants.
+
+The researchers contrasted the different plot designs, as hexagon tilemap and geography in the lineups were created using the same data, and same null positions within the lineup.
+
+Let $n$ be the number of independent observers and $x_i$ the
+number of observers who picked plot $i$, $i = \{1,...,m\}$
+
+Then $x_i, x_2, ..., x_m$ follows a multinomial
+distribution$Mult_{\pi_1, \pi_2, ...., \pi_m}(x_i, x_2, ..., x_m)$ with 
+$\sum_i \pi_i = 1$, where $\pi_i$ is the probability that plot $i$ is picked by an
+observer, which we can estimate as $\hat{\pi}_i = x_i/n$.
+The researchers compared the length of time taken, and the accuracy of the participants choices.
+The power of a lineup can therefore be estimated as the ratio of correct
+identifications $x$ out of $n$ viewings.
+
+## The variables being manipulated and measured
+
+The variables that were changed between groups were the type of plot shown and the trend model.
+
+Each participant was randomly allocated to either Group A or Group B when they begun the survey. This resulted in 42 participants allocated to Group A, and 53 participants allocated to Group B.
+
+The levels of the factors measured in the experiment were:
+- Map type: *Choropleth, Hexagon tile*
+- Trend: *Locations in three population centres, Locations in multiple population centres, South-East to North-West*
+
+Factor combinations examined by each participant amount to 6 (2x3) lineup displays.
+A participant did see the same data for both map types. Four simulated sets of data were generated for each treatment.
+This will generate 24 lineups (12 were geographic maps, and 12 were hexagon tile maps). Participants will evaluate 12 lineups, 6 of each map type. Appendix A shows the experimental design visually.
+For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants.
+
+```{r exp_design, results = "asis"}
+d %>% 
+  mutate(Trend = trend,
+    Group = group,
+    `Map Type` = type) %>% 
+  group_by(Group, Trend, `Map Type`) %>% 
+  summarise(Reps = paste0(sort(unique(replicate)), collapse = ", ")) %>% 
+  pivot_wider(names_from = c("Map Type"), values_from = c("Reps")) %>% 
+  ungroup() %>% 
+  knitr::kable(., format = "latex", booktabs = TRUE, caption = "Experimental design.") %>% kable_styling("striped") %>% 
+  collapse_rows(., columns = 1, custom_latex_hline = c(1:3))
+```
+
+The variables measured as a result of the changes were the probability of detection each display and the time taken to submit responses.
+To measure the accuracy of the detections, the plot chosen for each lineup evaluated was compared to the position of the real spatial trend plot in the lineup.
+A correct result occurs when the chosen plot matches the position of the real plot, this was recorded in an additional binary variable; 1 = correct; 0 = incorrect.
+High efficiency occurs when a small amount of time is taken to evaluate each lineup.
+This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.
+
+## Simulation process
+
+The underlying spatial correlation model was created to provide spatial autocorrelation between neighbouring areas using the longitude and latitude values for the Statistical Areas.
+formula = z ~ 1, locations = ~ longitude + latitude
+
+Simulated spatially dependent data using the model on the centroids of each area, for 12 null plots in 12 lineups.
+
+12 sets of data were created.
+In these 12 sets of data, each of the 144 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas.
+
+For each of the 144 individual maps, the values attributed to each geographic area are rescaled to show a similar colour scale from deep blue to dark red within each map.
+
+A random location was selected for each set of lineup data.
+In this location, a trend model was overlaid on the null set of spatially correlated data.
+Each set of lineup data was used to produce a choropleth maps and hexagon tile maps. These matched pairs were split between Group A and Group B.
+
+Replicate 2 of the All Cities distribution is shown in XXX.
+
+```{r cities_lineup, fig.cap = "The lineup of choropleth map displays shows a distribution that affects all capital cities.
+The values for the inner city areas in the capital cities result in them being coloured red.
+However, the colour blue dominates the display as the large rural areas are filled."}
+#knitr::include_graphics("figures/aus_cities_3_geo.png")
+```
+
+!["The lineup of choropleth map displays shows a distribution that affects all capital cities.
+The values for the inner city areas in the capital cities result in them being coloured red.
+However, the colour blue dominates the display as the large rural areas are filled."](figures/aus_cities_3_geo.png)
+
+```{r nwse_lineup, fig.cap = "A North-West to South East trend was hidden in this lineup of hexagon tile map displays."}
+#knitr::include_graphics("figures/aus_nwse_6_hex.png")
+```
+
+!["A North-West to South East trend was hidden in this lineup of hexagon tile map displays."](figures/aus_nwse_6_hex.png)
+
+## Participants
+
+There were 95 participants involved in the study. 
+We recruited participants using the Figure-Eight crowd source platform by advertising this survey to participants that fulfilled the following crtieria:
+
+- level 2 or level 3 on the Figure-Eight Platform.
+- at least 18 years old
+
+Participants then selected our task from the list of tasks available to them.
+
+Each participant was trained using three test displays orienting them to the evaluation task.
+Participants then proceeded to the survey, this involved evaluating 12 displays.
+
+## Experiment procudure and data collection
+
+The participant answered demographic questions and provided consent before evaluating the lineups.
+
+Demographics were collected regarding the study participants:
+- Gender (female / male / other),
+- Degree education level achieved (high school / bachelors / masters / doctorate / other),
+- Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
+- Lived at least for one year in Australia (Yes / No )
+
+Participants then moved to the evaulation phase.
+The set of images differed for Group A and Group B.
+After being allocated to a group, each individual was shown the 12 displays in randomised order.
+
+Three questions were asked regarding each display:
+- Plot choice
+- Reason
+- Difficulty
+
+After completing the 12 evaluations, the participants were asked to submit their responses.
+
+Data was collected through a web application containing the online survey.
+Each participant used the internet to access the survey.
+The data collection took place using a secure link between the survey web application and the googlesheet used to store results.
+The application would first connect to the googlesheet using the googlesheets [@sheets] R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
+
+## The methods of data analysis used
+The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R [@RCore].
+
+For each of the 12 lineup displays the researchers calculated:
+- accuracy: the proportion of subjects who detected the data plot
+- efficiency: average time taken to respond
+
+### Visualisations
+Side-by-side dot plots were made of accuracy (efficiency) against map type, facetted by trend model type.
+
+Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.
+
+Plots will be made in R (R Core Team 2019), with the ggplot2 package (Wickham 2016).
+
+### Modeling
+
+The results will be analysed using a generalised linear model, with a subject random effect to account for differences in individuals.
+There will be two main effects: map type and trend model, which gives the fixed effects part of the model to be
+
+$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3$$
+
+where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
+We are allowing for an interaction between map type and trend model. As the response for whether the participant detected the data plot is binary, a logistic model is used.
+
+A similar model will be constructed for the efficiency, using a log time, and normal errors.
+
+The feedback and demographic variables will possibly be incorporated as covariates.
+
+Computation will be done using R [@RCore], with the `lme4` package [@lme4].
+
+## Limitations of the data collection
+
+The demographics of the participants showed a skew towards male participants. 
+The randomness of the group allocation also resulted in more participants being allocated to Group B.
+Due to the allocation of lineup displays the participants all saw six Choropleth displays and six Hexagon Tile Map displays.
+
+Results
+============
+
+The survey responses from participants were kept only if the participant submitted answers for all 12 displays. This resulted in 92 participants.
+
+The contributors who gave various plot choices and reasons for the twelve displays were kept.
+The contributors who detected no plots correctly were analysed further. Three of these contribuotrs gave no choices for any of the twelve displays. They were also removed for the rest of the analysis.
+
+Of the 92 participants, 67 were male, and 25 female. Only two of the participants had lived in Australia before.
+The education level achieved by the participants was 70 Bachelors or Masters degree.
+
+# Accuracy
+
+The detection rate for participants reporting the real data trend model is used to calculate the accuracy of the responses of participants.
+
 ```{r detection_compare, fig.cap = "The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models.
@@
   mutate(Type = types) %>% select(Type, `NW-SE`, `Three Cities`, `All Cities`) %>%
-  knitr::kable(., format = "latex", align = "lccc")
+  knitr::kable(., format = "latex", align = "lccc", booktabs = TRUE)
 ```
@@
 
-```{r}
+```{r beeswarm, fig.cap = "The beeswarm plots show the distribution of the time taken to submit a response for each combination of trend and type of display.
+The time taken shown by the height of the point for each evaluationq1.
+The height of the histogram bars show how many evaulations were submitted within each time window.
+The orange regions of the bars show the amount of correct detections, and the green regions are the amount of incorrect detections."}
 # Di playing
@@
 
-The proportion of correct and incorrect responses within each 5 second time window.
+The proportion of correct and incorrect responsesis shown by the width used to distribute the points horizontally.
+Each point is randomly placed, but regions with more points require points to be placed further from center.
 For the NW-SE distribution, it is equally likely that quick responders will be correct or incorrect.
@@
 ```{r reason, fig.cap = "The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
-The facets show whether or not the choice was correct."}
-###########################################################
+The facets show whether or not the choice was correct.", results = "asis"}
+
 # Qualitative analysis of reason
@@
   mutate(reason = ifelse(reason =="0.0", "no reason", reason)) %>% 
-  mutate(Detected = gsub("Detected? ", "", detect_f)) %>% 
-  group_by(trend, Detected, type) %>% 
+  mutate(Detected = ifelse(detect_f == "Detected? Yes", "Yes", "No"),
+    Trend = trend) %>% 
+  group_by(Trend, Detected, type) %>% 
   count(reason) %>% 
@@
   top_n(1, n) %>% summarise(reasons = paste(reason, collapse=", ")) %>% 
-  pivot_wider(names_from = c("Detected"), values_from = c("reasons")) %>% 
-  arrange(trend, type) %>% 
-  select(Trend = trend, `Map Type` = type,
-    `Yes` = `Detected? Yes`, `No` = `Detected? No`) %>% 
-  knitr::kable(., format = "latex") %>% kable_styling("striped") %>%
-  add_header_above(c(" " = 2, "Detected:" = 2))
+  pivot_wider(names_from = c("type"), values_from = c("reasons")) %>% 
+  ungroup() %>% 
+  knitr::kable(., format = "latex", booktabs = TRUE) %>% kable_styling("striped") %>% 
+  collapse_rows(., columns = 1, custom_latex_hline = c(1:2, 3:4))
 ```
@@
 ```
+
+## Anomolies
+
+The choices made by participants are examined in Figure \@ref(fig:choices).
+Participants were misled by the choropleth display, but not the hexagon display for all cities displays except (2).
+The maps with a North West to South East trend was chosen with much greater frequency in all displays.
+All of three cities displays, except (4), were detected in the hexagon display.
+All except one lineup had at least one participant select the correct map in the lineup as shown in Figure \@ref(fig:choices).
 
@@
 
-The choices made by participants are examined in Figure \@ref(fig:choices).
-Participants were misled by the choropleth display, but not the hexagon display for all cities displays except (2).
-The maps with a North West to South East trend was chosen with much greater frequency in all displays.
-All of three cities displays, except (4), were detected in the hexagon display.
-All except one lineup had at least one participant select the correct map in the lineup as shown in Figure \@ref(fig:choices).
-
-## Anomolies
+One lineup had extremely similiar detection rates for the Choropleth and Hexagon displays.
 
@@
 
-```{r modeling_glm1}
+```{r modeling_glm1, results="asis"}
 # Modelling 
@@
 
-factors <- c("Design", "", "Trend", "", "Interactions", "")
 terms <- c("Intercept", "Hex", "Three cities", "All cities", "Hex : Three cities", "Hex : All cities")
@@
 tidy(glm1) %>%
-  mutate(p.value = round(p.value, 4)) %>%
-  mutate(sig = case_when(
-    p.value <= 0.001 ~ "***", 
-    p.value <= 0.01 ~ "**", 
-    p.value <= 0.05 ~ "*", 
-    p.value <= 0.01 ~ ".",
-    TRUE ~ " ")) %>% 
-  mutate(term = terms,
-    factors = factors) %>% 
-  select(`_` = factors, 
-    terms = term, 
+  mutate_if(is.numeric, round, 2) %>% 
+  rowwise() %>% 
+  mutate(estimate = case_when(
+    p.value <= 0.001 ~ paste0(estimate,"$^{***}$"),
+    p.value <= 0.01 ~ paste0(estimate, "$^{** }$"), 
+    p.value <= 0.05 ~ paste0(estimate, "$^{*  }$"), 
+    p.value <= 0.01 ~ paste0(estimate, "$^{.  }$"),
+    TRUE ~ paste0(estimate))) %>% 
+  ungroup() %>% 
+  mutate(term = terms) %>% 
+  select(Term = term, 
     Estimate = estimate, 
@@
     Stat = statistic,
-    p.value, sig) %>% knitr::kable(format = "latex", 
-      align = "lrrrrl")
-```
-
-```{r}
+    p.value) %>% knitr::kable(format = "latex", escape = FALSE, align= "rcrrr", booktabs = T)
+```
+
+```{r pred_glm1}
 d_glm <- d %>% select(group:certainty, detect, detect_f) %>%
@@
 
-```{r}
+```{r glm2}
 glm2 <- glm(formula = detect ~ type * trend + replicate_f,
@@
   ggplot(aes(x= replicate_f, y = prob, group = type)) + 
-  geom_point(aes(col = type)) + 
+  geom_point() + 
   geom_line(alpha = 0.5, lty = "dashed") + 
-  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL, col = replicate_f), 
-                width = 0.2) +
+  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL, col = type), width = 0.2) +
+  scale_color_manual(values = type_colours) +
   facet_grid(trend ~ .) +
-  ylab("Estimated Marginal Mean")
-```
-
-```{r}
+  labs(x = "Replicates", y = "Detection Rate")
+```
+
+```{r lmer1, results = "asis"}
 # Mixed effects models
@@
 
-glance(lmer1)
-tidy(lmer1)
+stargazer::stargazer(lmer1)
 
@@
     predicted = factor(predicted, levels = c(0,1), labels = c("No", "Yes")))
-
-table(d_lmer$predicted, d_lmer$detect_f)
-
 # Hexagon maps have better chance of correct detection
@@
 
-```{r}
+```{r lmer2, results = "asis"}
 # Mixed effects models
@@
 
-glance(lmer2)
-tidy(lmer2)
+stargazer::stargazer(lmer2)
 
@@
 
-table(d_lmer2$predicted, d_lmer2$detect_f)
 ```
@@
 
-```{r}
-# Modelling 
-lm1 <- lm(formula = as.numeric(certainty) ~ type, data = d)
-lm1_d <- augment(lm1, d)
-```
-
-```{r}
+```{r lmer1_model, results = "asis"}
 # Mixed effects models
 lmer1 <- lmer(detect ~ type*trend + (1|contributor), data = d)
-lmer1
+tidy(lmer1) %>% mutate_if(is.numeric, .f = round, 2) %>% stargazer::stargazer(.)
 
@@
 
-```{r demogs}
+```{r demogs, results = "asis"}
 # Create one record for each contributor, to examine demographics
@@
 
-###############################################################################
 # Demographics of contributors
@@
 dem_contribs %>% ggplot() + geom_bar(aes(age))
-dem_contribs %>% count(gender)
-dem_contribs %>% count(education)
-dem_contribs %>% count(gender, education) %>% 
-  spread(gender, n) %>% 
-  mutate(`Col. Total` = He + She) %>% 
-  gather("Gender", "Amount", He:`Col. Total`) %>% 
-  spread(education, Amount) %>% 
-  mutate(`Row Total` = Bach + `High School`, Masters,
-    Gender = factor(Gender, levels = c("He", "She", "Col. Total"), labels = c("He", "She", "Col. Total"))) %>% knitr::kable(format = "latex")
+dem_contribs %>% count(gender) %>% knitr::kable(format = "latex", booktabs = TRUE)
+dem_contribs %>% count(education) %>% knitr::kable(format = "latex", booktabs = TRUE)
 ```

### 2020-01-09 paper/paper.Rmd
draft

@@
 The choropleth map display is commonly used for communicating spatial data.
+However, when used to communicate the spatial distribution of a statistic the sizes of areas can lead to midinterpretation of the distribution.
 The visualisation method used to present geospatial data will influence the information derived by map users.
@@
   error = FALSE, 
-  message = FALSE)
+  message = FALSE,
+  cache = TRUE)
 ```
@@
 library(emmeans)
+library(knitr)
 library(kableExtra)
@@
 <!-- geographies on choropleth -->
-A geographic map base is commonly used to present geospatial statistics.
-The statistics presented may also be aggreagated statistics for geographic units, in this case the choropleth map is the common display used.
-Choropleth maps are often used to present statistics regarding the population.
-Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic. 
-The several sets of Australian statistical areas presents an example of a heterogrenous distribution.
-The rural communities in Australia operate on a much larger geographic space than small inner city communities.
-This has the negative effect of incorrectly showing the spatial distribution of the statistic, especially when a spatial distribution is related to the size of the areas, or the population density.
-An alternative display can be used to effectively communicate a spatial distribution for a set of heterogeneous areas.
+This study contrasts the use of two displays for geospatial statistics, the traditional choropleth map and an alternative tessellated hexagon tile map.
+The choropleth map is the common choice for visualising aggregated statistics and is familiar because of common administrative boundaries.
+A hexagon tile map forgoes the familiar boundaries, instead representing each geographic unit as an equally sized hexagon.
+This alternative display is suggested for communicating distributions that relate to the population values or density of the population in each geographic unit.
+This study uses the lineup protocol for visual inference testing of the recognition of spatial distributions.
+The Australian Cancer Atlas explores spatial distributions of cancer incidence and the burden on Australian communities.
+The spatial distributions of the cancers explored in this atlas inspired the trend models presented to participants in this study.
 
@@
 
-The Australian Cancer Atlas is an online interactive web tool created to explore the burden of cancer on Australian communities.
-There are many cancer types presented, and they can be explored on an individual or aggregate level.
-The Australian communities are examined at the Statistical Areas at Level 2 (SA2) [@abs2016] used by the Australian Bureau of Statistics.
-Bayesian spatial smoothing has been applied to incorporate the value of the statistics of the neighbouring areas.
-Spatial smoothing allows for the protection privacy and gives stability to the estimates.
-The statistics mapped are the diagnoses (Standardised Incidence Rates) and excess deaths for each SA2, communicated as the difference from the Australian average of the statistics.
-The values of the statistic for each geographic area is communicated through the colour used to fill the areas, the colours are chosen for the diverging colour scheme.
-The Australian Cancer Atlas communicates the trends in the distributions of cancer over geographic space.
+The Australian Cancer Atlas is an online interactive web tool created to explore the burden of cancer on Australian communities. There are many cancer types to be explored individually or aggregated. 
+The Atlas examines Australian communities at the Statistical Areas at Level 2 (SA2) [@abs2016] used by the Australian Bureau of Statistics.
+Bayesian spatial smoothing was applied to integrate the values of neighbouring areas.
+Spatial smoothing protects the privacy and gives stability to the estimated amounts in each SA2.
+Users of the Atlas can explore the difference of the statistic of each SA2 from the Australian average, for both diagnoses (Standardised Incidence Rates) and excess deaths.
+It communicates the value of the statistic for each SA2 geographic unit through colour, by filling the areas using the diverging colour scheme ranging from dark blue to red.
+The Australian Cancer Atlas allows users to explore the patterns in the distributions of cancer statistics over the geographic space of Australia.
 It uses a choropleth map display and diverging colour scheme to draw attention to relationships between neighbouring areas.
@@
 The most common display for spatial data is the choropleth map.
-However, the issue of using a choropleth map base becomes obvious when considering population related distributions.
-Map creators have the ability to present spatial statistics in alternative displays that can highlight the population.
+The choropleth map is the common display used to present aggregated statistics for geographic units such as the population.
+Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic.
+However, using a choropleth map base introduces biases when considering population related distributions.
+Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
+The rural communities in Australia operate on a much larger geographic space than small inner-city communities.
+When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
+This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention.
+An alternative display can be used to effectively communicate a spatial distribution for a set of heterogeneous areas.
 This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
-When presenting population statistics on a geographic map base, the size of the regions can allow errornous conclusions to be drawn about the state of the statistic over the entire population.
-This occurs as large regions filled with a consistent colour or pettern can draw the attention of map readers, and small regions are not paid equal attention.
+
 A choropleth map is not the only display that can be used for presenting geospatial data. 
-Alternative maps include various cartograms, and tesselated tile maps. They allow other variables to be included in the display to highlight the staistical values of various geographic areas.
+Alternative maps include various cartograms and tessellated tile maps. They allow other variables to be incorporated in the display to highlight the statistical values of various geographic areas.
 
 <!-- Cartogram -->
-
 A cartogram transforms the geographic map base.
-The transformation begins with a choropleth map base, and the associated populations.
-There are several algorithms for transforming, they all involve shifting boundaries to increase or descrease the area of the geographic units on the map depending on the statistics.
+The transformation begins with a choropleth map, and the values of a statistic such as population, for each geographic unit.
+There are several algorithms for transformation; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
 <!-- Why not a cartogram-->
-The shifts of the boundaries result in cartograms with accurate map area for each of the geographic units.
+The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units.
 The transformation will keep boundaries of neighbouring areas connected, but the result is unfamiliar shapes for each geographic unit.
@@
 Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units.
-The non-contiguous cartgoram method keep the shapes of geographic units intact, and change the size to communicate the values of statistics.
-This method breaks the spatial relationship between areas, and emphasises the difference between the statistic and the amount of land for each geographic unit.
+The non-contiguous cartgoram method keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics.
+This method disconnects areas when shrinking boundaries, and breaks the spatial relationship between areas.
+However, the empty space created emphasises the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
 The Dorling cartogram is another method that does not retain the boundaries of geographic units.
-Each unit becomes one circle on the cartogram dispaly, these can be sized according to the value of a variable.
-Their neighbours can be illustrated by connecting the boundaries of the circles.
+Each unit becomes one circle on the cartogram display; the circles are sized according to the value of a the statistic, such as population.
+The neighbour relationships can be illustrated by connecting the boundaries of the circles.
 These cartogram methods all allow two variables to be shown in the single display.
@@
 <!-- Specific problem for Australia -->
-Australia is an extreme case of heterogenous geographic units.
-To communicate information regarding the small inner city geographic units of Australian cities an alternative display must be employed.
-This will emphasise the value of the statistic that is relating to areas with high population levels.
-Figure \@ref(fig:liver) shows the distribution of the smoothed average amount of Liver cancer diagnoses for Australian Males from XXX years.
-The hexagon tile map (b) shows orange hexagons for the inner city Statistical Areas at Level 2 with higher than average levels of diagnoses in the capital cities of Melbourne and Sydney.
-These inner city areas are not visible on the choropleth map (a).
+Australia is an extreme case of heterogenous geographic units, with large difference between the smallest and largest geographic units across various granularities.
+To communicate information regarding the small inner-city geographic units of Australian cities an alternative display must be employed.
+This will emphasise the value of the statistic for areas with high population.
+Figure \@ref(fig:liver) shows the distribution of the smoothed average amount of Liver cancer diagnoses for Australian Males from 2005-2014.
+These inner-city areas are not visible on the choropleth map (a).
+The hexagon tile map (b) shows orange hexagons for the inner-city SA2s with higher than average levels of diagnoses in the capital cities of Melbourne and Sydney.
+The northern Queensland, and Northern Territory SA2's with higher than average rates are still visible but use less map space on the hexagon tile map.
 There are still many light blue areas in both displays.
-The northern Queensland, and Northern Territory SA2's with higher than average rates are still visible but utilise less map space on the hexagon tile map.
-
-## Methodology
-
-To test the
 
 ## Visual Inference
-- Communicating data through visualisations
-- Effective displays for types of data
-- Protocol for testing the effectiveness
-
-The same data were shown on a choropleth map, and on a hexagon tile map.
-Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.
+
+The hexagon tile map is suggested as an alternative display.
+To test the effectiveness of these displays there is a formal testing framework.
+Visual inference considers the communication of data or data summaries through visualisations.
+It considers these visualisations to be visual statistics, with observable features.
 
 Classical statistical inference involves hypothesis testing, the process of rejecting a null hypothesis in favour of an alternative.
-This approach relies on data, the appropriate distributions and their assumptions.
-Visual inference null hypothesis: independence in the variables (absence of all features), alternative hypothesis: Relationship between the variables (presence of some feature).
-<!--
-GTPCCD
-In visual inference, data plots are considered to be test statistics, and these are compared with plots of data generated from a null hypothesis using a lineup
-
-The null hypothesis underlying a
-lineup is that there is no real structure visible in the data plot, that any
-patterns seen are consistent with randomness, or from a known model.
-If the null hypothesis is true then the plot of the data will not be distinguishable
-from the plots of null data.
-
-Different lineups are created, using the same data, same null plots and
-positions within the lineup, but different plot designs.
-
-Comparing how
-long viewers take and how accurately they report the feature of interest
-will assess which design is better for the task.
--->
-
-<!--
-A null dataset
-is a sample from the null distribution, i.e. an example of an innocent
-dataset, and a null plot is a plot of a null dataset, showing what an
-innocent might look like.
-
-testing can be adapted to work visually instead of numerically.[@GIIV]
-Graphical Inference for Infovis
-Chloropleth maps Is there a spatial trend?
-
-Simulation. We might be interested in a more specific set of hypothesis:
-does time increase linearly with distance from target?
-Does accuracy decrease exponentially as number of distractors
-increases? In those cases we have a probabilistic model and we
-can generate null data sets by sampling from the distribution implied
-by the model. This approach is used in Section 4.2.
--->
-
-The lineup protocol is used for visual inference testing.
-1. simulate null plots 
-2. Insert data with structure into a random location
-3. Ask uninvolved person to select the most different plot
-4. If location is chosen correctly, the existence of a feature is significant at $\alpha = 1/N$.
-
-> "In this framework, plots take on the role of test statistics, and human cognition the role of statistical tests." @SIEDAMD
-
-The line up protocol involves placing a "guilty" data visualisation in a lineup of "innocents". Where the guilty data set contains structure, and the innocents are equivalent to a null data set. 
-In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the group innocents.
+This approach requires appropriate data, with the appropriate distributions and their assumptions.
+The lineup protocol was formalised as a test for the effectiveness of a visualisation.
+Rather than use classical statistical tests, human participants are tasked with finding the display that shows structure between the variables.
+If the structure is not detected, then it is not significantly different from the null data.
+
+Visual inference uses the general hypothesis structure:
+
+Null hypothesis: There is NO relationship between the variables,
+Alternative hypothesis: There is a relationship between the variables.
+
+To test these hypotheses, the line up protocol randomly places a "guilty" data visualisation in a lineup of "innocents".
+Where the guilty data set contains structure, and the innocents data sets do not.
+In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the  innocents [@GTPCCD].
 The guilty data is identified as different from the innocent data with probability $1/m$, where $m$ is the number of null plots plus 1 to account account for the guilty data set.
@@
 
-The lineup protocol can be used in a variety of testing scenarios. The choropleth map is best used for testing spatial structure in a data set.
-
-<!--
-The line-up protocol works like a police line-up: the suspect (test
-statistic plot) is hidden in a set of decoys. If the observer, who has not
-seen the suspect, can pick it out as being noticeably different, there is
-evidence that it is not innocent.
--->
-
-Study Design
+The lineup protocol can be used in a variety of testing scenarios for visualisations.
+@GIIV suggest the choropleth map for testing spatial structure in a data set.
+The lineup protocol allows for flexibility in the definition of null data.
+In the case of spatial visualisations it is likely that neighbours are related to some degree.
+To account for this, null data sets can be generated by sampling from a known model that accounts for spatial covariance.
+
+To contrast the effectiveness of two displays, the data set of null data plots with a hidden real data plot can be produced using the different plot designs.
+The time taken by participants to evaluate the same data in the different displays can be compared. Their accuracy in detecting the real data plot can also be calculated and contrasted.
+
+Methodology
 ============
 
-This study aims to answer several questions around the presentation of spatial distributions:
+This study aimed to answer two key questions around the presentation of spatial distributions:
 
@@
 
-2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when
-using a hexagon tile map display?
-
-additional considerations when completing this experimental task included exploration of the difficulty experienced by participants
-
-<!--
- Do people find hexagon tile maps more difficult to read than choropleth maps?
- Are the reasons for choosing a plot different depending on the type of display?
--->
-
-The mean of the detection rate for choropleth map, denoted as $\mu_C$, and the hexagon tile maps, $\mu_H$ will be contrasted. This leads to the following one sided hypothesis for this study:
+2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when using a hexagon tile map display?
+
+Additional considerations when completing this experimental task included exploration of the difficulty experienced by participants, and the certainty they felt about their decision.
+
+The mean of the detection rate for choropleth map, denoted as $\mu_C$, and the hexagon tile maps, $\mu_H$ will be contrasted. This leads to the following one sided hypothesis:
 
@@
 
-The difference in the detection rates for the two displays will be compared using the following:
-
-$$ \hat\pi_C - \hat\pi_H \pm t_{1-\alpha,n-1}\sqrt{\hat\pi_C(1-\hat\pi_C)/n_C + \hat\pi_H(1-\hat\pi_H)/n_H} $$
-
-## Experimental design
-
-The most common display for spatial cancer data is the choropleth map.
-This will be the comparative visualisation for presenting the lineups [@VVSIALM].
-Most geographic distributions will have some degree of spatial autcorrelation between neighbours.
-This feature will exist in all plots in the lineup displays, the plot that contains the trend feature shown in only one set of data will also be affected by spatial autocorrelation.
-A reasonable amount of null plots $N-1$ in the lineup was chosen to ensure data is well hidden. For the detailed choropleth of Australian SA2 areas, we set $N = 12$ to not overwhelm participants.
-A line up protocol was implemented to arrange 12 maps in each display. 
-Individual displays were created by a combination of map type, and spatial trend model.
-
-The hypotheses for each lineup are
-$H_0$ : All plots look the same
-$H_a$ : One plot looks different to the other plots
-
-Recruited participants to be uninvolved judges with no prior knowledge of the data to avoid discrimination or advantages.
-The online crowdsource platform Figure-Eight was used to recruit participants.
-
-The researchers contrasted the different plot designs, as hexagon tilemap and geography in the lineups were created using the same data, and same null positions within the lineup.
-
-Let $n$ be the number of independent observers and $x_i$ the
-number of observers who picked plot $i$, $i = \{1,...,m\}$
-
-Then $x_i, x_2, ..., x_m$ follows a multinomial
-distribution$Mult_{\pi_1, \pi_2, ...., \pi_m}(x_i, x_2, ..., x_m)$ with 
-$\sum_i \pi_i = 1$, where $\pi_i$ is the probability that plot $i$ is picked by an
-observer, which we can estimate as $\hat{\pi}_i = x_i/n$.
-The researchers compared the length of time taken, and the accuracy of the participants choices.
-The power of a lineup can therefore be estimated as the ratio of correct
-identifications $x$ out of $n$ viewings.
-
-## The variables being manipulated and measured
+The difference in the detection rates for the two displays will be compared using a two sample unpaired t-test.
+
+## Participants
+
+Participants were recruited for a survey style task to test the effectiveness of the hexagon tile map display.
+It was expected that the participants were uninvolved judges that had no prior knowledge of the data, to avoid discrimination or advantages.
+The Figure-Eight crowd source platform was used to advertise the survey to potential participants that had acheived level 2 or level 3 on the Figure-Eight Platform.
+The participants were chosen as they have experience with survey tasks that involve evaluating images. They participants on the platform are also required to be at least 18 years old.
+
+Participants were able to choose to participate by selecting this task from the list of tasks available to them.
+There were 95 participants involved in the study.
+All of these participants read the introductory materials and viewed example questions before proceeding to the survey.
+Each participant was trained using three test displays orienting them to the evaluation task, these displays are shown in supplementary materials section regarding [training].
+All participants who volunteered to take part were compensated for their time via the payment system of Figure-Eight.
+
+Participants were allocated to either group A or group B when they proceeded to the survey web application, hosted externally from the Figure-Eight website.
+
+## Variables
 
@@
 
+The twenty-four lineup displays were created by a combination of map type, and spatial trend model.
+This set of displays was split into a collection of twelve displays for Group A and twelve displays for Group B.
+
 Each participant was randomly allocated to either Group A or Group B when they begun the survey. This resulted in 42 participants allocated to Group A, and 53 participants allocated to Group B.
@@
 The levels of the factors measured in the experiment were:
+
   - Map type: *Choropleth, Hexagon tile*
@@
 
-Factor combinations examined by each participant amount to 6 (2x3) lineup displays.
-A participant did see the same data for both map types. Four simulated sets of data were generated for each treatment.
-This will generate 24 lineups (12 were geographic maps, and 12 were hexagon tile maps). Participants will evaluate 12 lineups, 6 of each map type. Appendix A shows the experimental design visually.
+Each Group did not see the same data for both map types. Four simulated sets of data were generated for each treatment.
+This will generate twenty-four lineups (twelve lineups of geographic maps, and twelve lineups of hexagon tile maps). Participants evaluated twelve lineups, siz of each map type.
 For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants.
@@
   ungroup() %>% 
-  knitr::kable(., format = "latex", booktabs = TRUE, caption = "Experimental design.") %>% kable_styling("striped") %>% 
-  collapse_rows(., columns = 1, custom_latex_hline = c(1:3))
+  knitr::kable(., format = "latex", booktabs = TRUE, caption = "Experimental design.") %>% kable_styling("striped")
+#%>% 
+#  collapse_rows(., columns = 1, custom_latex_hline = c(1:3))
 ```
@@
 
+The lineup protocol allows a known model to be imposed on the null data set plots.
 The underlying spatial correlation model was created to provide spatial autocorrelation between neighbouring areas using the longitude and latitude values for the Statistical Areas.
-formula = z ~ 1, locations = ~ longitude + latitude
-
-Simulated spatially dependent data using the model on the centroids of each area, for 12 null plots in 12 lineups.
-
-12 sets of data were created.
+
+$$z = 1$$
+$$locations = longitude + latitude$$
+
+The null model imposed suggests that neighbours are related.
+The randomness imposed was smoothed to mirror the practice taken by the Australian Cancer Atlas.
+This smoothing allowed neighbours to be related to each other and show distributions similar to the Liver cancer distribution shown in \@ref(fig:liver).
+
+Spatially dependent data sets were simulated using the variogram model on the centroids of each geographic unit.
+Twelve simulations from the variogram model were created for each of the twelve lineups.
+
 In these 12 sets of data, each of the 144 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas.
@@
 
-Replicate 2 of the All Cities distribution is shown in XXX.
-
-```{r cities_lineup, fig.cap = "The lineup of choropleth map displays shows a distribution that affects all capital cities.
-The values for the inner city areas in the capital cities result in them being coloured red.
-However, the colour blue dominates the display as the large rural areas are filled."}
-#knitr::include_graphics("figures/aus_cities_3_geo.png")
-```
-
-!["The lineup of choropleth map displays shows a distribution that affects all capital cities.
-The values for the inner city areas in the capital cities result in them being coloured red.
-However, the colour blue dominates the display as the large rural areas are filled."](figures/aus_cities_3_geo.png)
-
-```{r nwse_lineup, fig.cap = "A North-West to South East trend was hidden in this lineup of hexagon tile map displays."}
-#knitr::include_graphics("figures/aus_nwse_6_hex.png")
-```
-
-!["A North-West to South East trend was hidden in this lineup of hexagon tile map displays."](figures/aus_nwse_6_hex.png)
-
-## Participants
-
-There were 95 participants involved in the study. 
-We recruited participants using the Figure-Eight crowd source platform by advertising this survey to participants that fulfilled the following crtieria:
-
-- level 2 or level 3 on the Figure-Eight Platform.
-- at least 18 years old
-
-Participants then selected our task from the list of tasks available to them.
-
-Each participant was trained using three test displays orienting them to the evaluation task.
-Participants then proceeded to the survey, this involved evaluating 12 displays.
+Replicate 3 of the All Cities distribution is shown in \@ref(fig:compare).
+The same data set is shown in both displays, the difference is the land area of each SA3 is coloured in the choropleth and the hexagon representing the SA3 is coloured in the Hexagon Tile Map.
+Many maps in the Choropleth lineup (a) are coloured yellow, two are half light blue, and two are obviously blue.
+Only one of the maps looks red.
+
+```{r compare, fig.cap = "Comparing the same data presented in two map displays. The choropleth map display in (a) ", fig.height = 9, fig.width = 6}
+ggdraw(ylim = c(0,2), xlim = c(0,1), clip = "on") + 
+  draw_plot(rasterGrob(readPNG("figures/aus_cities_4_geo.png")), 0, 1, 1, 1) +
+  draw_plot(rasterGrob(readPNG("figures/aus_cities_4_hex.png")), 0, 0, 1, 1) +
+  draw_plot_label(c("a", "b"), 
+    c(0.05, 0.05), c(1.95, 1), size = 20, color = "white") + 
+  theme(plot.background = element_rect(fill = "black"))
+```
 
@@
 
+## Experimental design
+
+The choropleth map was used as the comparative visualisation for presenting the lineups [@VVSIALM] as this is the common display for spatial cancer data.
+Geographic distributions usually have some degree of spatial autcorrelation between neighbours.
+This feature was incorporated in all maps shown in the lineup displays, the map that contained the trend feature shown in only one set of data was also affected by spatial autocorrelation.
+A line up protocol was implemented to arrange $N$ maps in each display. 
+A reasonable amount of null plots $N-1$ in the lineup was chosen to ensure the real data map was well hidden.
+A reasonable number of plots to show in each lineup, $N = 12$ was chosen to not overwhelm participants due to the detailed choropleth maps of Australian SA3 areas.
+
+The hypotheses for each lineup are
+$H_0$ : All plots look the same
+$H_a$ : One plot looks different to the other plots
+
+The same data was visualised on a choropleth map, and on a hexagon tile map, however in this study the participants only saw one of these two displays.
+The accuracy and times taken were aggregated for Groups and.
+Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.
+
+Let $n$ be the number of independent observers and $x_i$ the
+number of observers who picked plot $i$, $i = \{1,...,m\}$
+
+Then $x_i, x_2, ..., x_m$ follows a multinomial
+distribution$Mult_{\pi_1, \pi_2, ...., \pi_m}(x_i, x_2, ..., x_m)$ with 
+$\sum_i \pi_i = 1$, where $\pi_i$ is the probability that plot $i$ is picked by an
+observer, which we can estimate as $\hat{\pi}_i = x_i/n$.
+The researchers compared the length of time taken, and the accuracy of the participants choices.
+The power of a lineup can therefore be estimated as the ratio of correct
+identifications $x$ out of $n$ viewings.
+
 ## The methods of data analysis used
@@
 
+A pilot study was conducted to determine whether the lineups were appropriate. All lineups in the pilot study were deemed viable as at least one participant detected the real data plot in each lineup.
 The demographics of the participants showed a skew towards male participants. 
@@
 
-The survey responses from participants were kept only if the participant submitted answers for all 12 displays. This resulted in 92 participants.
-
-The contributors who gave various plot choices and reasons for the twelve displays were kept.
-The contributors who detected no plots correctly were analysed further. Three of these contribuotrs gave no choices for any of the twelve displays. They were also removed for the rest of the analysis.
+The results section explores the [Accuracy] and contrasts the detection rate of the real data plot in the lineups.
+The second section considers the [Speed] participants had when submitting their responses to the three questions asked regarding each display.
+The [Certainty] participants felt about their decisions and the [Reason] for their choice in plot is also discussed.
+
+The survey responses from participants were kept only if the participant various submitted answers for all 12 displays. This resulted in 92 participants.
+The contributors who detected no plots correctly were analysed further. Three of these contribuotrs gave no choices for any of the twelve displays.
 
@@
 
-# Accuracy
+## Accuracy
 
 The detection rate for participants reporting the real data trend model is used to calculate the accuracy of the responses of participants.
+The accuracy is contrasted across the two displays with the following hypothesis:
+
+$H_0$ : $\mu_H$ = $\mu_C$
+$H_a$ : $\mu_H$ > $\mu_C$
+
+```{r ttest}
+# Probability of detection using map types
+test_dt <- d %>% mutate(type = factor(type, levels = c("Hex.", "Choro."))) %>% 
+  t.test(detect ~ type, data = ., alternative = "greater", paired = FALSE)
+
+```
+
+A two sample t-test was used to contrast the difference between the detection rates for the two types of displays.
+The value of `r test_dt$p.value` shows that it is very unlikely the difference in means is due to chance.
+The null hypothesis that the detection rate for the two groups is equal can be rejected in favour of the alternative, that the means are different.
 
@@
   ungroup()
+
+# Numerical summary
+diffs <- d_smry %>% spread(type, pdetect) %>%
+  mutate(dif = `Hex.` - `Choro.`)
 
@@
 
-The detection rates are usually higher when participants viewed the hexagon tile map displays.
+The detection rates were higher when participants viewed the hexagon tile map displays. The impact of the trend model is also considered and presented in table \@ref(tab:desc_stats).
 The difference was greater when viewing a three cities trend model.
@@
 The North West to South East data plot was detected with similar rates when viewing the choropleth and  hexagon tile map displays, though for three of the replicates the participants detected the data display more often.
-
-```{r ttest}
-# Numerical summary
-diffs <- d_smry %>% spread(type, pdetect) %>%
-  mutate(dif = `Hex.` - `Choro.`)
-
-# Probability of detection using map types
-test_dt <- t.test(pdetect ~ type, data = d_smry, alternative = "less")
-```
-
-A t-test shows the difference between the detection rates for the two types of displays.
-The value of `r test_dt$p.value` shows that it is very unlikely the difference is due to chance.
 
@@
   mutate(Type = types) %>% select(Type, `NW-SE`, `Three Cities`, `All Cities`) %>%
-  knitr::kable(., format = "latex", align = "lccc", booktabs = TRUE)
+  knitr::kable(., format = "latex", align = "lccc", booktabs = TRUE, caption = "")
 ```
@@
   ungroup() %>% 
-  knitr::kable(., format = "latex", booktabs = TRUE) %>% kable_styling("striped") %>% 
-  collapse_rows(., columns = 1, custom_latex_hline = c(1:2, 3:4))
+  knitr::kable(., format = "latex", booktabs = TRUE) %>% kable_styling("striped") 
+#%>% 
+#  collapse_rows(., columns = 1, custom_latex_hline = c(1:2, 3:4))
 ```
@@
 
+!["The lineup of choropleth map displays shows a distribution that affects all capital cities.
+The values for the inner city areas in the capital cities result in them being coloured red.
+However, the colour blue dominates the display as the large rural areas are filled.
+Replicate (2) for all cities."](figures/aus_cities_3_geo.png)
+
+!["A North-West to South East trend was hidden in this lineup of hexagon tile map displays."](figures/aus_nwse_6_hex.png)
+
 ## Modeling the difference
@@
 ============
-how do the results found generalise to other work
-- Not just for Aus (Canada new Zealand could also use this effective display)
-
-- For USA alternative methods can also be helpful
+
+The choropleth map display and the tessellated hexagon tile map have been contrasted in a visual inference study. 
+The hexagon tile map was significantly more effective for spotting a real data trend model hidden in a lineup.
+
+This hexagon tile map display should be considered as a visualisation method when communicating distributions that relate to the population in each geographic unit.
+Cancer Atlas products may benefit from the opportunity to allow exploration via the traditional choropleth map method as well as an alternative display.
+The spatial distributions used to test these displays were inspired by the real spatially smoothed estimates of the cancer burden on Australian communities.
+However, this technique may be extended to other population related distributions, such as other diseases.
+
+The increasing population densities of capital cities despite large land area exaserbates the difference in the smallest and largest communities.
+The population density structure of Australia can be considered similar to that of Canada, New Zealand and many others.
+Therefore, this display is not only relevant to Australia, but all nations or population collections that experience densely populated cities alongside vast rural expanses.
 
@@
 
-## Training
+## Training {#training}
+
+The participants were trained using three displays. There were relatively simple lineups and are shown in Figure XXX.
+<!--
+
+\begin{figure}[!t] 
+\centering 
+\includegraphics[width=2.5in]{figures/fig8_training1.png}
+\caption{The training lineups of choropleth maps.}
+\label{training1} 
+\end{figure}
+
+\begin{figure}[!t] 
+\centering 
+\includegraphics[width=2.5in]{figures/fig8_training1.png}
+\caption{The training lineups of hexagon tile maps.}
+\label{straining2} 
+\end{figure} 
+-->
 
@@
 
+The survey application was hosted on a website external to the Figure-Eight platform.
+Following suggestions in the documentation, the information and training required for a participant to make a decision was included  that survey
+
+The demonstrative images of the `shinydashboard` web application display the demographic and consent page in Figure \@ref(fig:survey1).
+
+<!--
+\begin{figure}[!t] 
+\centering 
+\includegraphics[width=2.5in]{figures/survey_demogs.png}
+\caption{The demographics questions tab of the shinydashboard survey application.}
+\label{survey_demogs} 
+\end{figure}
+
+\begin{figure}[!t] 
+\centering 
+\includegraphics[width=2.5in]{figures/survey_hex.png}
+\caption{An example of the hexagon tile map lineup shown in the survey tab of the shinydashboard app.}
+\label{survey_hex} 
+\end{figure}
+
+\begin{figure}[!t] 
+\centering 
+\includegraphics[width=2.5in]{figures/survey_choro.png}
+\caption{An example of the choropleth map lineup shown in the survey tab of the shinydashboard app.}
+\label{survey_choro} 
+\end{figure} 
+-->
 ## Overall Performance
@@
 
-Bibliography styles
-===================
+Bibliography
+=============
 

### 2020-01-10 paper/paper.Rmd
results

@@
 ---
-title: "Communicating human related spatial distributions: A comparison of spatial visualisations using visual inference."
+title: "Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics"
 affiliation:
@@
 
+<!--
 The results section explores the [Accuracy] and contrasts the detection rate of the real data plot in the lineups.
@@
 The [Certainty] participants felt about their decisions and the [Reason] for their choice in plot is also discussed.
-
-The survey responses from participants were kept only if the participant various submitted answers for all 12 displays. This resulted in 92 participants.
-The contributors who detected no plots correctly were analysed further. Three of these contribuotrs gave no choices for any of the twelve displays.
-
-Of the 92 participants, 67 were male, and 25 female. Only two of the participants had lived in Australia before.
-The education level achieved by the participants was 70 Bachelors or Masters degree.
+-->
+
+Responses from 95 participants were collected.
+Three participants provided no answers for any task, and their data was removed.
+Set A was evaluated by 42 participants, and 53 evaluated set B.
+This resulted in 1104 evaluations, corresponding to 92 subjects, each evaluating 12 lineups, that are analysed on accuracy and speed.
+
+## Participant demographics
+
+Of the 92 participants, 67 were male, and 25 female. Most participants (56) had a Bacherlors degree, 13 had a Masters degree, and the remaining 23 had high school diplomas.
 
@@
 
+<!--
 The detection rate for participants reporting the real data trend model is used to calculate the accuracy of the responses of participants.
@@
 The null hypothesis that the detection rate for the two groups is equal can be rejected in favour of the alternative, that the means are different.
+-->
+
+Figure \@ref{detection_compare} display the average detection rates by type of plot, separately for each trend model.
+Evaluations on the same data set are connected by a line segment.
+For both the Three Cities and All Cities trend models performance was substantially better for the hexagon tile map.
+Viewers detected the data plot substantially more often with the hexagon tile map.
+One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in a later section.
+Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map.
+We expected that the choropleth map would be superior for the type of spatial pattern, but the data suggests the hexagon tile map performs equally as well.
+
+Table \ref{tab:desc_stats} shows the means and standard deviations for type of plot and each trend model.
+
+<!-- The detection rates were higher when participants viewed the hexagon tile map displays. The impact of the trend model is also considered and presented in table \@ref(tab:desc_stats).
+The difference was greater when viewing a three cities trend model.
+When the trend model affected all cities participants also detected the data display in the lineup of null plots more often.
+The North West to South East data plot was detected with similar rates when viewing the choropleth and  hexagon tile map displays, though for three of the replicates the participants detected the data display more often.
+-->
 
@@
 
-The detection rates were higher when participants viewed the hexagon tile map displays. The impact of the trend model is also considered and presented in table \@ref(tab:desc_stats).
-The difference was greater when viewing a three cities trend model.
-When the trend model affected all cities participants also detected the data display in the lineup of null plots more often.
-The North West to South East data plot was detected with similar rates when viewing the choropleth and  hexagon tile map displays, though for three of the replicates the participants detected the data display more often.
-
 ```{r desc_stats, results = "asis"}
@@
 
-The probability of detection is explored for each of the combinations of trans and type of display.
+Table XXX is a summary of the mixed effects model. Blah, blah, what we learn.
 

### 2020-01-10 paper/paper.tex
results

@@
 \hypersetup{
-            pdftitle={Communicating human related spatial distributions: A comparison of spatial visualisations using visual inference.},
+            pdftitle={An Experiment Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics},
             pdfkeywords={statistics, visual inference, geospatial, population},
@@
 % Pandoc header
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 
@@
 % Do not put math or special symbols in the title.
-\title{Communicating human related spatial distributions: A comparison of
-spatial visualisations using visual inference.}
+\title{An Experiment Comparing the Effectiveness of the Choropleth Map with a
+Hexagon Tile Map for Communicating Cancer Statistics}
 
@@
 choropleth map display is commonly used for communicating spatial data.
-The visualisation method used to present geospatial data will influence
-the information derived by map users. Choosing an alternative display
-will influence the communication of the distribution. The hexagon tile
-map is presented as an alternative display. Visual inference is used to
-measure the power of design. The choropleth is used as a comparison
-point. The hexagon tile map display is an effective visualisation for
-communicatin=g population related distributions. The hexagon tile map
-display also allowed identification of the geographic distribution with
-values monotonically decreasing from North West toward South East areas
-of Australia.
+However, when used to communicate the spatial distribution of a
+statistic the sizes of areas can lead to midinterpretation of the
+distribution. The visualisation method used to present geospatial data
+will influence the information derived by map users. Choosing an
+alternative display will influence the communication of the
+distribution. The hexagon tile map is presented as an alternative
+display. Visual inference is used to measure the power of design. The
+choropleth is used as a comparison point. The hexagon tile map display
+is an effective visualisation for communicatin=g population related
+distributions. The hexagon tile map display also allowed identification
+of the geographic distribution with values monotonically decreasing from
+North West toward South East areas of Australia.
 \end{abstract}
@@
 
-A geographic map base is commonly used to present geospatial statistics.
-The statistics presented may also be aggreagated statistics for
-geographic units, in this case the choropleth map is the common display
-used. Choropleth maps are often used to present statistics regarding the
-population. Creating a choropleth map involves drawing the
-administrative boundaries and filling them with colour to communicate
-the value of the statistic. The several sets of Australian statistical
-areas presents an example of a heterogrenous distribution. The rural
-communities in Australia operate on a much larger geographic space than
-small inner city communities. This has the negative effect of
-incorrectly showing the spatial distribution of the statistic,
-especially when a spatial distribution is related to the size of the
-areas, or the population density. An alternative display can be used to
-effectively communicate a spatial distribution for a set of
-heterogeneous areas.
+This study contrasts the use of two displays for geospatial statistics,
+the traditional choropleth map and an alternative tessellated hexagon
+tile map. The choropleth map is the common choice for visualising
+aggregated statistics and is familiar because of common administrative
+boundaries. A hexagon tile map forgoes the familiar boundaries, instead
+representing each geographic unit as an equally sized hexagon. This
+alternative display is suggested for communicating distributions that
+relate to the population values or density of the population in each
+geographic unit. This study uses the lineup protocol for visual
+inference testing of the recognition of spatial distributions. The
+Australian Cancer Atlas explores spatial distributions of cancer
+incidence and the burden on Australian communities. The spatial
+distributions of the cancers explored in this atlas inspired the trend
+models presented to participants in this study.
 
@@
 explore the burden of cancer on Australian communities. There are many
-cancer types presented, and they can be explored on an individual or
-aggregate level. The Australian communities are examined at the
-Statistical Areas at Level 2 (SA2) (``Australian Statistical Geography
-Standard (ASGS)'' \protect\hyperlink{ref-abs2016}{2018}) used by the
-Australian Bureau of Statistics. Bayesian spatial smoothing has been
-applied to incorporate the value of the statistics of the neighbouring
-areas. Spatial smoothing allows for the protection privacy and gives
-stability to the estimates. The statistics mapped are the diagnoses
-(Standardised Incidence Rates) and excess deaths for each SA2,
-communicated as the difference from the Australian average of the
-statistics. The values of the statistic for each geographic area is
-communicated through the colour used to fill the areas, the colours are
-chosen for the diverging colour scheme. The Australian Cancer Atlas
-communicates the trends in the distributions of cancer over geographic
-space. It uses a choropleth map display and diverging colour scheme to
-draw attention to relationships between neighbouring areas.
+cancer types to be explored individually or aggregated. The Atlas
+examines Australian communities at the Statistical Areas at Level 2
+(SA2) (``Australian Statistical Geography Standard (ASGS)''
+\protect\hyperlink{ref-abs2016}{2018}) used by the Australian Bureau of
+Statistics. Bayesian spatial smoothing was applied to integrate the
+values of neighbouring areas. Spatial smoothing protects the privacy and
+gives stability to the estimated amounts in each SA2. Users of the Atlas
+can explore the difference of the statistic of each SA2 from the
+Australian average, for both diagnoses (Standardised Incidence Rates)
+and excess deaths. It communicates the value of the statistic for each
+SA2 geographic unit through colour, by filling the areas using the
+diverging colour scheme ranging from dark blue to red. The Australian
+Cancer Atlas allows users to explore the patterns in the distributions
+of cancer statistics over the geographic space of Australia. It uses a
+choropleth map display and diverging colour scheme to draw attention to
+relationships between neighbouring areas.
 
@@
 geographic space. The most common display for spatial data is the
-choropleth map. However, the issue of using a choropleth map base
-becomes obvious when considering population related distributions. Map
-creators have the ability to present spatial statistics in alternative
-displays that can highlight the population. This work aims to show that
-a hexagon tile map display is a viable alternative to the geographic map
-base for presenting population statistics. When presenting population
-statistics on a geographic map base, the size of the regions can allow
-errornous conclusions to be drawn about the state of the statistic over
-the entire population. This occurs as large regions filled with a
-consistent colour or pettern can draw the attention of map readers, and
-small regions are not paid equal attention. A choropleth map is not the
-only display that can be used for presenting geospatial data.
-Alternative maps include various cartograms, and tesselated tile maps.
-They allow other variables to be included in the display to highlight
-the staistical values of various geographic areas.
+choropleth map. The choropleth map is the common display used to present
+aggregated statistics for geographic units such as the population.
+Creating a choropleth map involves drawing the administrative boundaries
+and filling them with colour to communicate the value of the statistic.
+However, using a choropleth map base introduces biases when considering
+population related distributions. Many sets of Australian statistical
+areas have a large disparity between the smallest and largest units. The
+rural communities in Australia operate on a much larger geographic space
+than small inner-city communities. When a spatial distribution is
+related to the size of the areas, or the population density, the size of
+the regions can allow erroneous conclusions to be drawn about the state
+of the statistic over the entire population, when presenting the
+statistics on a geographic map base. This occurs as large regions filled
+with a consistent colour or pattern can draw the attention of map
+readers, and small regions are not paid equal attention. An alternative
+display can be used to effectively communicate a spatial distribution
+for a set of heterogeneous areas. This work aims to show that a hexagon
+tile map display is a viable alternative to the geographic map base for
+presenting population statistics.
+
+A choropleth map is not the only display that can be used for presenting
+geospatial data. Alternative maps include various cartograms and
+tessellated tile maps. They allow other variables to be incorporated in
+the display to highlight the statistical values of various geographic
+areas.
 
 A cartogram transforms the geographic map base. The transformation
-begins with a choropleth map base, and the associated populations. There
-are several algorithms for transforming, they all involve shifting
-boundaries to increase or descrease the area of the geographic units on
-the map depending on the statistics. The shifts of the boundaries result
-in cartograms with accurate map area for each of the geographic units.
-The transformation will keep boundaries of neighbouring areas connected,
-but the result is unfamiliar shapes for each geographic unit.
+begins with a choropleth map, and the values of a statistic such as
+population, for each geographic unit. There are several algorithms for
+transformation; they involve shifting the boundaries of geographic
+units, using the value of the statistic to increase or decrease the area
+taken by the geographic unit on the map. The changes to the boundaries
+result in cartograms that accurately communicate population by map area
+for each of the geographic units. The transformation will keep
+boundaries of neighbouring areas connected, but the result is unfamiliar
+shapes for each geographic unit.
 
@@
 representation of variables using the area of geographic units. The
-non-contiguous cartgoram method keep the shapes of geographic units
-intact, and change the size to communicate the values of statistics.
-This method breaks the spatial relationship between areas, and
-emphasises the difference between the statistic and the amount of land
-for each geographic unit. The Dorling cartogram is another method that
-does not retain the boundaries of geographic units. Each unit becomes
-one circle on the cartogram dispaly, these can be sized according to the
-value of a variable. Their neighbours can be illustrated by connecting
-the boundaries of the circles. These cartogram methods all allow two
-variables to be shown in the single display.
+non-contiguous cartgoram method keeps the shapes of geographic units
+intact, and change the size of the shape to communicate the values of
+statistics. This method disconnects areas when shrinking boundaries, and
+breaks the spatial relationship between areas. However, the empty space
+created emphasises the comparative density of the statistic, the
+difference between the statistic and the amount of land for each
+geographic unit. The Dorling cartogram is another method that does not
+retain the boundaries of geographic units. Each unit becomes one circle
+on the cartogram display; the circles are sized according to the value
+of a the statistic, such as population. The neighbour relationships can
+be illustrated by connecting the boundaries of the circles. These
+cartogram methods all allow two variables to be shown in the single
+display.
 
@@
 
-Australia is an extreme case of heterogenous geographic units. To
-communicate information regarding the small inner city geographic units
-of Australian cities an alternative display must be employed. This will
-emphasise the value of the statistic that is relating to areas with high
-population levels. Figure @ref(fig:liver) shows the distribution of the
-smoothed average amount of Liver cancer diagnoses for Australian Males
-from XXX years. The hexagon tile map (b) shows orange hexagons for the
-inner city Statistical Areas at Level 2 with higher than average levels
-of diagnoses in the capital cities of Melbourne and Sydney. These inner
-city areas are not visible on the choropleth map (a). There are still
-many light blue areas in both displays. The northern Queensland, and
-Northern Territory SA2's with higher than average rates are still
-visible but utilise less map space on the hexagon tile map.
-
-\hypertarget{methodology}{%
-\subsection{Methodology}\label{methodology}}
-
-To test the
+Australia is an extreme case of heterogenous geographic units, with
+large difference between the smallest and largest geographic units
+across various granularities. To communicate information regarding the
+small inner-city geographic units of Australian cities an alternative
+display must be employed. This will emphasise the value of the statistic
+for areas with high population. Figure @ref(fig:liver) shows the
+distribution of the smoothed average amount of Liver cancer diagnoses
+for Australian Males from 2005-2014. These inner-city areas are not
+visible on the choropleth map (a). The hexagon tile map (b) shows orange
+hexagons for the inner-city SA2s with higher than average levels of
+diagnoses in the capital cities of Melbourne and Sydney. The northern
+Queensland, and Northern Territory SA2's with higher than average rates
+are still visible but use less map space on the hexagon tile map. There
+are still many light blue areas in both displays.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Communicating data through visualisations
-\item
-  Effective displays for types of data
-\item
-  Protocol for testing the effectiveness
-\end{itemize}
-
-The same data were shown on a choropleth map, and on a hexagon tile map.
-Comparing the results of participants who see the choropleth to those
-who see a hexagon tile map will show that population related
-distributions are spotted more frequently in a hexagon tile map display.
+The hexagon tile map is suggested as an alternative display. To test the
+effectiveness of these displays there is a formal testing framework.
+Visual inference considers the communication of data or data summaries
+through visualisations. It considers these visualisations to be visual
+statistics, with observable features.
 
@@
 of rejecting a null hypothesis in favour of an alternative. This
-approach relies on data, the appropriate distributions and their
-assumptions. Visual inference null hypothesis: independence in the
-variables (absence of all features), alternative hypothesis:
-Relationship between the variables (presence of some feature).
-
-The lineup protocol is used for visual inference testing. 1. simulate
-null plots 2. Insert data with structure into a random location 3. Ask
-uninvolved person to select the most different plot 4. If location is
-chosen correctly, the existence of a feature is significant at
-\(\alpha = 1/N\).
-
-\begin{quote}
-``In this framework, plots take on the role of test statistics, and
-human cognition the role of statistical tests.'' Buja et al.
-(\protect\hyperlink{ref-SIEDAMD}{2009})
-\end{quote}
-
-The line up protocol involves placing a ``guilty'' data visualisation in
-a lineup of ``innocents''. Where the guilty data set contains structure,
-and the innocents are equivalent to a null data set. In a grid of
-visualisations, an observer is asked to pick the display that is most
-different, if they select the data set containing structure, they have
-identified the guilty hidden within the group innocents. The guilty data
+approach requires appropriate data, with the appropriate distributions
+and their assumptions. The lineup protocol was formalised as a test for
+the effectiveness of a visualisation. Rather than use classical
+statistical tests, human participants are tasked with finding the
+display that shows structure between the variables. If the structure is
+not detected, then it is not significantly different from the null data.
+
+Visual inference uses the general hypothesis structure:
+
+Null hypothesis: There is NO relationship between the variables,
+Alternative hypothesis: There is a relationship between the variables.
+
+To test these hypotheses, the line up protocol randomly places a
+``guilty'' data visualisation in a lineup of ``innocents''. Where the
+guilty data set contains structure, and the innocents data sets do not.
+In a grid of visualisations, an observer is asked to pick the display
+that is most different, if they select the data set containing
+structure, they have identified the guilty hidden within the innocents
+(Hofmann et al. \protect\hyperlink{ref-GTPCCD}{2012}). The guilty data
 is identified as different from the innocent data with probability
@@
 
-The lineup protocol can be used in a variety of testing scenarios. The
-choropleth map is best used for testing spatial structure in a data set.
-
-\hypertarget{study-design}{%
-\section{Study Design}\label{study-design}}
-
-This study aims to answer several questions around the presentation of
+The lineup protocol can be used in a variety of testing scenarios for
+visualisations. Wickham et al. (\protect\hyperlink{ref-GIIV}{2010})
+suggest the choropleth map for testing spatial structure in a data set.
+The lineup protocol allows for flexibility in the definition of null
+data. In the case of spatial visualisations it is likely that neighbours
+are related to some degree. To account for this, null data sets can be
+generated by sampling from a known model that accounts for spatial
+covariance.
+
+To contrast the effectiveness of two displays, the data set of null data
+plots with a hidden real data plot can be produced using the different
+plot designs. The time taken by participants to evaluate the same data
+in the different displays can be compared. Their accuracy in detecting
+the real data plot can also be calculated and contrasted.
+
+\hypertarget{methodology}{%
+\section{Methodology}\label{methodology}}
+
+This study aimed to answer two key questions around the presentation of
 spatial distributions:
@@
 
-additional considerations when completing this experimental task
-included exploration of the difficulty experienced by participants
+Additional considerations when completing this experimental task
+included exploration of the difficulty experienced by participants, and
+the certainty they felt about their decision.
 
@@
 and the hexagon tile maps, \(\mu_H\) will be contrasted. This leads to
-the following one sided hypothesis for this study:
+the following one sided hypothesis:
 
@@
 The difference in the detection rates for the two displays will be
-compared using the following:
-
-\[ \hat\pi_C - \hat\pi_H \pm t_{1-\alpha,n-1}\sqrt{\hat\pi_C(1-\hat\pi_C)/n_C + \hat\pi_H(1-\hat\pi_H)/n_H} \]
-
-\hypertarget{experimental-design}{%
-\subsection{Experimental design}\label{experimental-design}}
-
-The most common display for spatial cancer data is the choropleth map.
-This will be the comparative visualisation for presenting the lineups
-(Majumder, Hofmann, and Cook \protect\hyperlink{ref-VVSIALM}{2013}).
-Most geographic distributions will have some degree of spatial
-autcorrelation between neighbours. This feature will exist in all plots
-in the lineup displays, the plot that contains the trend feature shown
-in only one set of data will also be affected by spatial
-autocorrelation. A reasonable amount of null plots \(N-1\) in the lineup
-was chosen to ensure data is well hidden. For the detailed choropleth of
-Australian SA2 areas, we set \(N = 12\) to not overwhelm participants. A
-line up protocol was implemented to arrange 12 maps in each display.
-Individual displays were created by a combination of map type, and
-spatial trend model.
-
-The hypotheses for each lineup are \(H_0\) : All plots look the same
-\(H_a\) : One plot looks different to the other plots
-
-Recruited participants to be uninvolved judges with no prior knowledge
-of the data to avoid discrimination or advantages. The online
-crowdsource platform Figure-Eight was used to recruit participants.
-
-The researchers contrasted the different plot designs, as hexagon
-tilemap and geography in the lineups were created using the same data,
-and same null positions within the lineup.
-
-Let \(n\) be the number of independent observers and \(x_i\) the number
-of observers who picked plot \(i\), \(i = \{1,...,m\}\)
-
-Then \(x_i, x_2, ..., x_m\) follows a multinomial
-distribution\(Mult_{\pi_1, \pi_2, ...., \pi_m}(x_i, x_2, ..., x_m)\)
-with \(\sum_i \pi_i = 1\), where \(\pi_i\) is the probability that plot
-\(i\) is picked by an observer, which we can estimate as
-\(\hat{\pi}_i = x_i/n\). The researchers compared the length of time
-taken, and the accuracy of the participants choices. The power of a
-lineup can therefore be estimated as the ratio of correct
-identifications \(x\) out of \(n\) viewings.
-
-\hypertarget{the-variables-being-manipulated-and-measured}{%
-\subsection{The variables being manipulated and
-measured}\label{the-variables-being-manipulated-and-measured}}
+compared using a two sample unpaired t-test.
+
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+Participants were recruited for a survey style task to test the
+effectiveness of the hexagon tile map display. It was expected that the
+participants were uninvolved judges that had no prior knowledge of the
+data, to avoid discrimination or advantages. The Figure-Eight crowd
+source platform was used to advertise the survey to potential
+participants that had acheived level 2 or level 3 on the Figure-Eight
+Platform. The participants were chosen as they have experience with
+survey tasks that involve evaluating images. They participants on the
+platform are also required to be at least 18 years old.
+
+Participants were able to choose to participate by selecting this task
+from the list of tasks available to them. There were 95 participants
+involved in the study. All of these participants read the introductory
+materials and viewed example questions before proceeding to the survey.
+Each participant was trained using three test displays orienting them to
+the evaluation task, these displays are shown in supplementary materials
+section regarding \protect\hyperlink{training}{training}. All
+participants who volunteered to take part were compensated for their
+time via the payment system of Figure-Eight.
+
+Participants were allocated to either group A or group B when they
+proceeded to the survey web application, hosted externally from the
+Figure-Eight website.
+
+\hypertarget{variables}{%
+\subsection{Variables}\label{variables}}
 
@@
 shown and the trend model.
+
+The twenty-four lineup displays were created by a combination of map
+type, and spatial trend model. This set of displays was split into a
+collection of twelve displays for Group A and twelve displays for Group
+B.
 
@@
 
-The levels of the factors measured in the experiment were: - Map type:
-\emph{Choropleth, Hexagon tile} - Trend: \emph{Locations in three
-population centres, Locations in multiple population centres, South-East
-to North-West}
-
-Factor combinations examined by each participant amount to 6 (2x3)
-lineup displays. A participant did see the same data for both map types.
-Four simulated sets of data were generated for each treatment. This will
-generate 24 lineups (12 were geographic maps, and 12 were hexagon tile
-maps). Participants will evaluate 12 lineups, 6 of each map type.
-Appendix A shows the experimental design visually. For each of the six
-geographic displays and six hexagon displays, two of each trend model
-were shown to participants.
-
-\begin{table}[]
-\caption{The Experimental Design}
-\label{tab:my-table}
-\begin{tabular}{|l|l|l|}
-\hline
-Trend & Map type & Replicates \\ \hline
-NW-SE & Choropleth & 2 \\ \hline
- & Hexagon tile & 2 \\ \hline
-Three cities & Choropleth & 2 \\ \hline
- & Hexagon tile & 2 \\ \hline
-All cities & Choropleth & 2 \\ \hline
- & Hexagon tile & 2 \\ \hline
+The levels of the factors measured in the experiment were:
+
+\begin{itemize}
+\tightlist
+\item
+  Map type: \emph{Choropleth, Hexagon tile}
+\item
+  Trend: \emph{Locations in three population centres, Locations in
+  multiple population centres, South-East to North-West}
+\end{itemize}
+
+Each Group did not see the same data for both map types. Four simulated
+sets of data were generated for each treatment. This will generate
+twenty-four lineups (twelve lineups of geographic maps, and twelve
+lineups of hexagon tile maps). Participants evaluated twelve lineups,
+siz of each map type. For each of the six geographic displays and six
+hexagon displays, two of each trend model were shown to participants.
+
+\begin{table}
+
+\caption{\label{tab:exp_design}Experimental design.}
+\centering
+\begin{tabular}[t]{llll}
+\toprule
+Group & Trend & Choro. & Hex.\\
+\midrule
+A & NW-SE & 1, 2 & 3, 4\\
+A & Three Cities & 1, 2 & 3, 4\\
+A & All Cities & 2, 4 & 1, 3\\
+B & NW-SE & 3, 4 & 1, 2\\
+B & Three Cities & 3, 4 & 1, 2\\
+\addlinespace
+B & All Cities & 1, 3 & 2, 4\\
+\bottomrule
 \end{tabular}
@@
 
-The underlying spatial correlation model was created to provide spatial
-autocorrelation between neighbouring areas using the longitude and
-latitude values for the Statistical Areas. formula = z \textasciitilde{}
-1, locations = \textasciitilde{} longitude + latitude
-
-Simulated spatially dependent data using the model on the centroids of
-each area, for 12 null plots in 12 lineups.
-
-12 sets of data were created. In these 12 sets of data, each of the 144
-maps were smoothed several times to replicate the spatial
-autocorrelation seen in cancer data sets presented in the Australian
-Cancer Atlas.
+The lineup protocol allows a known model to be imposed on the null data
+set plots. The underlying spatial correlation model was created to
+provide spatial autocorrelation between neighbouring areas using the
+longitude and latitude values for the Statistical Areas.
+
+\[z = 1\] \[locations = longitude + latitude\]
+
+The null model imposed suggests that neighbours are related. The
+randomness imposed was smoothed to mirror the practice taken by the
+Australian Cancer Atlas. This smoothing allowed neighbours to be related
+to each other and show distributions similar to the Liver cancer
+distribution shown in @ref(fig:liver).
+
+Spatially dependent data sets were simulated using the variogram model
+on the centroids of each geographic unit. Twelve simulations from the
+variogram model were created for each of the twelve lineups.
+
+In these 12 sets of data, each of the 144 maps were smoothed several
+times to replicate the spatial autocorrelation seen in cancer data sets
+presented in the Australian Cancer Atlas.
 
@@
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-There were 95 participants involved in the study. We recruited
-participants using the Figure-Eight crowd source platform by advertising
-this survey to participants that fulfilled the following crtieria:
-
-\begin{itemize}
-\tightlist
-\item
-  level 2 or level 3 on the Figure-Eight Platform.
-\item
-  at least 18 years old
-\end{itemize}
-
-Participants then selected our task from the list of tasks available to
-them.
-
-Each participant was trained using three test displays orienting them to
-the evaluation task. Participants then proceeded to the survey, this
-involved evaluating 12 displays.
+Replicate 3 of the All Cities distribution is shown in
+@ref(fig:compare). The same data set is shown in both displays, the
+difference is the land area of each SA3 is coloured in the choropleth
+and the hexagon representing the SA3 is coloured in the Hexagon Tile
+Map. Many maps in the Choropleth lineup (a) are coloured yellow, two are
+half light blue, and two are obviously blue. Only one of the maps looks
+red.
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/compare-1.pdf}
+\caption{Comparing the same data presented in two map displays. The
+choropleth map display in (a)}
+\end{figure}
 
@@
 
+\hypertarget{experimental-design}{%
+\subsection{Experimental design}\label{experimental-design}}
+
+The choropleth map was used as the comparative visualisation for
+presenting the lineups (Majumder, Hofmann, and Cook
+\protect\hyperlink{ref-VVSIALM}{2013}) as this is the common display for
+spatial cancer data. Geographic distributions usually have some degree
+of spatial autcorrelation between neighbours. This feature was
+incorporated in all maps shown in the lineup displays, the map that
+contained the trend feature shown in only one set of data was also
+affected by spatial autocorrelation. A line up protocol was implemented
+to arrange \(N\) maps in each display. A reasonable amount of null plots
+\(N-1\) in the lineup was chosen to ensure the real data map was well
+hidden. A reasonable number of plots to show in each lineup, \(N = 12\)
+was chosen to not overwhelm participants due to the detailed choropleth
+maps of Australian SA3 areas.
+
+The hypotheses for each lineup are \(H_0\) : All plots look the same
+\(H_a\) : One plot looks different to the other plots
+
+The same data was visualised on a choropleth map, and on a hexagon tile
+map, however in this study the participants only saw one of these two
+displays. The accuracy and times taken were aggregated for Groups and.
+Comparing the results of participants who see the choropleth to those
+who see a hexagon tile map will show that population related
+distributions are spotted more frequently in a hexagon tile map display.
+
+Let \(n\) be the number of independent observers and \(x_i\) the number
+of observers who picked plot \(i\), \(i = \{1,...,m\}\)
+
+Then \(x_i, x_2, ..., x_m\) follows a multinomial
+distribution\(Mult_{\pi_1, \pi_2, ...., \pi_m}(x_i, x_2, ..., x_m)\)
+with \(\sum_i \pi_i = 1\), where \(\pi_i\) is the probability that plot
+\(i\) is picked by an observer, which we can estimate as
+\(\hat{\pi}_i = x_i/n\). The researchers compared the length of time
+taken, and the accuracy of the participants choices. The power of a
+lineup can therefore be estimated as the ratio of correct
+identifications \(x\) out of \(n\) viewings.
+
 \hypertarget{the-methods-of-data-analysis-used}{%
@@
 
-The demographics of the participants showed a skew towards male
+A pilot study was conducted to determine whether the lineups were
+appropriate. All lineups in the pilot study were deemed viable as at
+least one participant detected the real data plot in each lineup. The
+demographics of the participants showed a skew towards male
 participants. The randomness of the group allocation also resulted in
@@
 
-The survey responses from participants were kept only if the participant
-submitted answers for all 12 displays. This resulted in 92 participants.
-
-The contributors who gave various plot choices and reasons for the
-twelve displays were kept. The contributors who detected no plots
-correctly were analysed further. Three of these contribuotrs gave no
-choices for any of the twelve displays. They were also removed for the
-rest of the analysis.
-
-Of the 92 participants, 67 were male, and 25 female. Only two of the
-participants had lived in Australia before. The education level achieved
-by the participants was 70 Bachelors or Masters degree.
+Responses from 95 participants were collected. Three participants
+provided no answers for any task, and their data was removed. Set A was
+evaluated by 42 participants, and 53 evaluated set B. This resulted in
+1104 evaluations, corresponding to 92 subjects, each evaluating 12
+lineups, that are analysed on accuracy and speed.
+
+\hypertarget{participant-demographics}{%
+\subsection{Participant demographics}\label{participant-demographics}}
+
+Of the 92 participants, 67 were male, and 25 female. Most participants
+(56) had a Bacherlors degree, 13 had a Masters degree, and the remaining
+23 had high school diplomas.
 
 \hypertarget{accuracy}{%
-\section{Accuracy}\label{accuracy}}
-
-The detection rate for participants reporting the real data trend model
-is used to calculate the accuracy of the responses of participants.
+\subsection{Accuracy}\label{accuracy}}
+
+Figure @ref\{detection\_compare\} display the average detection rates by
+type of plot, separately for each trend model. Evaluations on the same
+data set are connected by a line segment. For both the Three Cities and
+All Cities trend models performance was substantially better for the
+hexagon tile map. Viewers detected the data plot substantially more
+often with the hexagon tile map. One replicate for the All Cities group,
+had similar detection rates for both plot types, and this is discussed
+in a later section. Surprisingly, participants could also detect the
+gradual spatial trend in the NW-SE group from the hexagon tile map. We
+expected that the choropleth map would be superior for the type of
+spatial pattern, but the data suggests the hexagon tile map performs
+equally as well.
+
+Table \ref{tab:desc_stats} shows the means and standard deviations for
+type of plot and each trend model.
 
@@
 
-The detection rates are usually higher when participants viewed the
-hexagon tile map displays. The difference was greater when viewing a
-three cities trend model. When the trend model affected all cities
-participants also detected the data display in the lineup of null plots
-more often. The North West to South East data plot was detected with
-similar rates when viewing the choropleth and hexagon tile map displays,
-though for three of the replicates the participants detected the data
-display more often.
-
-A t-test shows the difference between the detection rates for the two
-types of displays. The value of 0.0041593 shows that it is very unlikely
-the difference is due to chance.
+\begin{table}
+
+\caption{\label{tab:desc_stats}}
+\centering
+\begin{tabular}[t]{lccc}
+\toprule
+Type & NW-SE & Three Cities & All Cities\\
+\midrule
+Choro. & 0.505 & 0.038 & 0.228\\
+ & (0.5) & (0.19) & (0.42)\\
+Hex. & 0.609 & 0.391 & 0.571\\
+ & (0.49) & (0.49) & (0.5)\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Table XXX is a summary of the mixed effects model. Blah, blah, what we
+learn.
 
@@
 
-\includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}
-
-The proportion of correct and incorrect responses within each 5 second
-time window. For the NW-SE distribution, it is equally likely that quick
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/beeswarm-1.pdf}
+\caption{The beeswarm plots show the distribution of the time taken to
+submit a response for each combination of trend and type of display. The
+time taken shown by the height of the point for each evaluationq1. The
+height of the histogram bars show how many evaulations were submitted
+within each time window. The orange regions of the bars show the amount
+of correct detections, and the green regions are the amount of incorrect
+detections.}
+\end{figure}
+
+The proportion of correct and incorrect responsesis shown by the width
+used to distribute the points horizontally. Each point is randomly
+placed, but regions with more points require points to be placed further
+from center. For the NW-SE distribution, it is equally likely that quick
 responders will be correct or incorrect. It is more likely that
@@
 
-\begin{figure}
+\begin{table}[H]
 \centering
-\includegraphics{paper_files/figure-latex/reason-1.pdf}
-\caption{The amount of participants that selected each reason for their
-choice of plot when looking at each trend model shown in Choropleth and
-Hexagon Tile maps. The facets show whether or not the choice was
-correct.}
-\end{figure}
+\begin{tabular}{llll}
+\toprule
+Trend & Detected & Choro. & Hex.\\
+\midrule
+NW-SE & No & trend & clusters\\
+NW-SE & Yes & trend & clusters\\
+Three Cities & No & trend & clusters\\
+Three Cities & Yes & consistent & clusters\\
+All Cities & No & trend & clusters\\
+\addlinespace
+All Cities & Yes & clusters, consistent & clusters\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 \end{figure}
+
+\hypertarget{anomolies}{%
+\subsection{Anomolies}\label{anomolies}}
+
+The choices made by participants are examined in Figure
+@ref(fig:choices). Participants were misled by the choropleth display,
+but not the hexagon display for all cities displays except (2). The maps
+with a North West to South East trend was chosen with much greater
+frequency in all displays. All of three cities displays, except (4),
+were detected in the hexagon display. All except one lineup had at least
+one participant select the correct map in the lineup as shown in Figure
+@ref(fig:choices).
 
@@
 
-The choices made by participants are examined in Figure
-@ref(fig:choices). Participants were misled by the choropleth display,
-but not the hexagon display for all cities displays except (2). The maps
-with a North West to South East trend was chosen with much greater
-frequency in all displays. All of three cities displays, except (4),
-were detected in the hexagon display. All except one lineup had at least
-one participant select the correct map in the lineup as shown in Figure
-@ref(fig:choices\}.
-
-\hypertarget{anomolies}{%
-\subsection{Anomolies}\label{anomolies}}
+One lineup had extremely similiar detection rates for the Choropleth and
+Hexagon displays.
+
+\begin{figure}
+\centering
+\includegraphics{figures/aus_cities_3_geo.png}
+\caption{``The lineup of choropleth map displays shows a distribution
+that affects all capital cities. The values for the inner city areas in
+the capital cities result in them being coloured red. However, the
+colour blue dominates the display as the large rural areas are filled.
+Replicate (2) for all cities.''}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{figures/aus_nwse_6_hex.png}
+\caption{``A North-West to South East trend was hidden in this lineup of
+hexagon tile map displays.''}
+\end{figure}
 
@@
 
-\begin{tabular}{l|r|r|r|r|l|l}
-\hline
-\_ & terms & Estimate & Error & Stat & p.value & sig\\
-\hline
-Design & Intercept & 0.0217400 & 0.1474507 & 0.1474391 & 0.8828 & \\
-\hline
- & Hex & 0.4200928 & 0.2110904 & 1.9901083 & 0.0466 & *\\
-\hline
-Trend & Three cities & -3.2519793 & 0.4124809 & -7.8839514 & 0.0000 & ***\\
-\hline
- & All cities & -1.2398974 & 0.2293327 & -5.4065450 & 0.0000 & ***\\
-\hline
-Interactions & Hex : Three cities & 2.3683138 & 0.4645163 & 5.0984512 & 0.0000 & ***\\
-\hline
- & Hex : All cities & 1.0825772 & 0.3123987 & 3.4653698 & 0.0005 & ***\\
-\hline
+\begin{tabular}{rcrrr}
+\toprule
+Term & Estimate & Error & Stat & p.value\\
+\midrule
+Intercept & 0.02 & 0.15 & 0.15 & 0.88\\
+Hex & 0.42$^{*  }$ & 0.21 & 1.99 & 0.05\\
+Three cities & -3.25$^{***}$ & 0.41 & -7.88 & 0.00\\
+All cities & -1.24$^{***}$ & 0.23 & -5.41 & 0.00\\
+Hex : Three cities & 2.37$^{***}$ & 0.46 & 5.10 & 0.00\\
+\addlinespace
+Hex : All cities & 1.08$^{***}$ & 0.31 & 3.47 & 0.00\\
+\bottomrule
 \end{tabular}
@@
 
-The estimated marginal mean is the fitted value from a model over the
-treatment effects. The treatment effects considered in this model are
-map type displayed, trend model included, and the replicate. The
-\texttt{emmeans} package is used to calculate the estimated marginal
-mean. The value, between 0 and 1, can be interpretted as the probability
-of detecting the real data plot in the lineup, for each combination of
-map type, trend model and replicate.
-
-\includegraphics{paper_files/figure-latex/unnamed-chunk-3-1.pdf}
-
-\begin{verbatim}
-## # A tibble: 1 x 6
-##   sigma logLik   AIC   BIC deviance df.residual
-##   <dbl>  <dbl> <dbl> <dbl>    <dbl>       <int>
-## 1 0.430  -675. 1367. 1407.    1321.        1096
-\end{verbatim}
-
-\begin{verbatim}
-## # A tibble: 8 x 5
-##   term                       estimate std.error statistic group      
-##   <chr>                         <dbl>     <dbl>     <dbl> <chr>      
-## 1 (Intercept)                   0.505    0.0340     14.9  fixed      
-## 2 typeHex.                      0.103    0.0448      2.31 fixed      
-## 3 trendThree Cities            -0.467    0.0448    -10.4  fixed      
-## 4 trendAll Cities              -0.277    0.0448     -6.19 fixed      
-## 5 typeHex.:trendThree Cities    0.250    0.0633      3.95 fixed      
-## 6 typeHex.:trendAll Cities      0.239    0.0633      3.77 fixed      
-## 7 sd_(Intercept).contributor    0.118   NA          NA    contributor
-## 8 sd_Observation.Residual       0.430   NA          NA    Residual
-\end{verbatim}
-
-\begin{verbatim}
-##      
-##       Detected? No Detected? Yes
-##   No            49             1
-##   Yes          624           430
-\end{verbatim}
+\includegraphics{paper_files/figure-latex/glm2-1.pdf}
+
+\% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard
+University. E-mail: hlavac at fas.harvard.edu \% Date and time: Fri, Jan
+10, 2020 - 11:55:55
+
+\begin{table}[!htbp] \centering 
+  \caption{} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-2} 
+\\[-1.8ex] & detect \\ 
+\hline \\[-1.8ex] 
+ typeHex. & 0.103$^{**}$ \\ 
+  & (0.045) \\ 
+  & \\ 
+ trendThree Cities & $-$0.467$^{***}$ \\ 
+  & (0.045) \\ 
+  & \\ 
+ trendAll Cities & $-$0.277$^{***}$ \\ 
+  & (0.045) \\ 
+  & \\ 
+ typeHex.:trendThree Cities & 0.250$^{***}$ \\ 
+  & (0.063) \\ 
+  & \\ 
+ typeHex.:trendAll Cities & 0.239$^{***}$ \\ 
+  & (0.063) \\ 
+  & \\ 
+ Constant & 0.505$^{***}$ \\ 
+  & (0.034) \\ 
+  & \\ 
+\hline \\[-1.8ex] 
+Observations & 1,104 \\ 
+Log Likelihood & $-$675.359 \\ 
+Akaike Inf. Crit. & 1,366.719 \\ 
+Bayesian Inf. Crit. & 1,406.772 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
 
@@
 
-\begin{verbatim}
-## # A tibble: 1 x 6
-##   sigma logLik   AIC   BIC deviance df.residual
-##   <dbl>  <dbl> <dbl> <dbl>    <dbl>       <int>
-## 1 0.445  -685. 1380. 1405.    1365.        1099
-\end{verbatim}
-
-\begin{verbatim}
-## # A tibble: 5 x 5
-##   term                           estimate std.error statistic group   
-##   <chr>                             <dbl>     <dbl>     <dbl> <chr>   
-## 1 (Intercept)                       0.669    0.0501      13.4 fixed   
-## 2 sd_(Intercept).trend              0.456   NA           NA   trend   
-## 3 sd_typeHex..trend                 0.287   NA           NA   trend   
-## 4 cor_(Intercept).typeHex..trend   -0.989   NA           NA   trend   
-## 5 sd_Observation.Residual           0.445   NA           NA   Residual
-\end{verbatim}
-
-\begin{verbatim}
-##      
-##       Detected? No Detected? Yes
-##   No             0             0
-##   Yes          673           431
-\end{verbatim}
+\% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard
+University. E-mail: hlavac at fas.harvard.edu \% Date and time: Fri, Jan
+10, 2020 - 11:55:55
+
+\begin{table}[!htbp] \centering 
+  \caption{} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-2} 
+\\[-1.8ex] & detect \\ 
+\hline \\[-1.8ex] 
+ Constant & 0.669$^{***}$ \\ 
+  & (0.050) \\ 
+  & \\ 
+\hline \\[-1.8ex] 
+Observations & 1,104 \\ 
+Log Likelihood & $-$684.772 \\ 
+Akaike Inf. Crit. & 1,379.544 \\ 
+Bayesian Inf. Crit. & 1,404.578 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
 
@@
 
-\begin{verbatim}
-## Linear mixed model fit by REML ['lmerMod']
-## Formula: detect ~ type * trend + (1 | contributor)
-##    Data: d
-## REML criterion at convergence: 1350.719
-## Random effects:
-##  Groups      Name        Std.Dev.
-##  contributor (Intercept) 0.1179  
-##  Residual                0.4296  
-## Number of obs: 1104, groups:  contributor, 92
-## Fixed Effects:
-##                (Intercept)                    typeHex.  
-##                     0.5054                      0.1033  
-##          trendThree Cities             trendAll Cities  
-##                    -0.4674                     -0.2772  
-## typeHex.:trendThree Cities    typeHex.:trendAll Cities  
-##                     0.2500                      0.2391
-\end{verbatim}
+\% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard
+University. E-mail: hlavac at fas.harvard.edu \% Date and time: Fri, Jan
+10, 2020 - 11:55:55
+
+\begin{table}[!htbp] \centering 
+  \caption{} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
+Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
+\hline \\[-1.8ex] 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
 
@@
 
-how do the results found generalise to other work - Not just for Aus
-(Canada new Zealand could also use this effective display)
-
-\begin{itemize}
-\tightlist
-\item
-  For USA alternative methods can also be helpful
-\end{itemize}
+The choropleth map display and the tessellated hexagon tile map have
+been contrasted in a visual inference study. The hexagon tile map was
+significantly more effective for spotting a real data trend model hidden
+in a lineup.
+
+This hexagon tile map display should be considered as a visualisation
+method when communicating distributions that relate to the population in
+each geographic unit. Cancer Atlas products may benefit from the
+opportunity to allow exploration via the traditional choropleth map
+method as well as an alternative display. The spatial distributions used
+to test these displays were inspired by the real spatially smoothed
+estimates of the cancer burden on Australian communities. However, this
+technique may be extended to other population related distributions,
+such as other diseases.
+
+The increasing population densities of capital cities despite large land
+area exaserbates the difference in the smallest and largest communities.
+The population density structure of Australia can be considered similar
+to that of Canada, New Zealand and many others. Therefore, this display
+is not only relevant to Australia, but all nations or population
+collections that experience densely populated cities alongside vast
+rural expanses.
 
@@
 
+The participants were trained using three displays. There were
+relatively simple lineups and are shown in Figure XXX.
+
 \hypertarget{survey-application}{%
 \subsection{Survey application}\label{survey-application}}
+
+The survey application was hosted on a website external to the
+Figure-Eight platform. Following suggestions in the documentation, the
+information and training required for a participant to make a decision
+was included that survey
+
+The demonstrative images of the \texttt{shinydashboard} web application
+display the demographic and consent page in Figure @ref(fig:survey1).
 
@@
 
-\begin{verbatim}
-## # A tibble: 2 x 2
-##   gender     n
-##   <chr>  <int>
-## 1 He        67
-## 2 She       25
-\end{verbatim}
-
-\begin{verbatim}
-## # A tibble: 3 x 2
-##   education       n
-##   <chr>       <int>
-## 1 Bach           56
-## 2 High School    23
-## 3 Masters        13
-\end{verbatim}
-
-\begin{tabular}{l|r|r|r|r}
-\hline
-Gender & Bach & High School & Masters & Row Total\\
-\hline
-Col. Total & 56 & 23 & 13 & 79\\
-\hline
-He & 39 & 19 & 9 & 58\\
-\hline
-She & 17 & 4 & 4 & 21\\
-\hline
+\begin{tabular}{lr}
+\toprule
+gender & n\\
+\midrule
+He & 67\\
+She & 25\\
+\bottomrule
+\end{tabular}
+
+\begin{tabular}{lr}
+\toprule
+education & n\\
+\midrule
+Bach & 56\\
+High School & 23\\
+Masters & 13\\
+\bottomrule
 \end{tabular}
@@
 
-\hypertarget{bibliography-styles}{%
-\section{Bibliography styles}\label{bibliography-styles}}
+\hypertarget{bibliography}{%
+\section{Bibliography}\label{bibliography}}
 
@@
 
-\leavevmode\hypertarget{ref-SIEDAMD}{}%
-Buja, Andreas, Dianne Cook, Heike Hofmann, Michael Lawrence, Eun-Kyung
-Lee, Deborah F. Swayne, and Hadley Wlckham. 2009. ``Statistical
-Inference for Exploratory Data Analysis and Model Diagnostics.''
-\emph{Philosophical Transactions: Mathematical, Physical and Engineering
-Sciences} 367 (1906): 4361--83.
-\url{http://www.jstor.org/stable/40485732}.
+\leavevmode\hypertarget{ref-GTPCCD}{}%
+Hofmann, Heike, Lendie Follett, Mahbubul Majumder, and Dianne Cook.
+2012. ``Graphical Tests for Power Comparison of Competing Designs.''
+\emph{IEEE Transactions on Visualization and Computer Graphics} 18:
+2441--8.
 
@@
 
+\leavevmode\hypertarget{ref-GIIV}{}%
+Wickham, Hadley, Dianne Cook, Heike Hofmann, and Andreas Buja. 2010.
+``Graphical Inference for Infovis.'' \emph{IEEE Transactions on
+Visualization and Computer Graphics (Proc. InfoVis '10)} 16 (6):
+973--79.
+
 \end{document}

### 2020-01-10 paper/paper.Rmd
rearrange modelling information

@@
 This will emphasise the value of the statistic for areas with high population.
-Figure \@ref(fig:liver) shows the distribution of the smoothed average amount of Liver cancer diagnoses for Australian Males from 2005-2014.
+Figure \ref{fig:liver} shows the distribution of the smoothed average amount of Liver cancer diagnoses for Australian Males from 2005-2014.
 These inner-city areas are not visible on the choropleth map (a).
@@
 The randomness imposed was smoothed to mirror the practice taken by the Australian Cancer Atlas.
-This smoothing allowed neighbours to be related to each other and show distributions similar to the Liver cancer distribution shown in \@ref(fig:liver).
+This smoothing allowed neighbours to be related to each other and show distributions similar to the Liver cancer distribution shown in \ref{fig:liver}.
 
@@
 
-Replicate 3 of the All Cities distribution is shown in \@ref(fig:compare).
+Replicate 3 of the All Cities distribution is shown in \ref{fig:compare}.
 The same data set is shown in both displays, the difference is the land area of each SA3 is coloured in the choropleth and the hexagon representing the SA3 is coloured in the Hexagon Tile Map.
@@
 Only one of the maps looks red.
-
-```{r compare, fig.cap = "Comparing the same data presented in two map displays. The choropleth map display in (a) ", fig.height = 9, fig.width = 6}
-ggdraw(ylim = c(0,2), xlim = c(0,1), clip = "on") + 
-  draw_plot(rasterGrob(readPNG("figures/aus_cities_4_geo.png")), 0, 1, 1, 1) +
-  draw_plot(rasterGrob(readPNG("figures/aus_cities_4_hex.png")), 0, 0, 1, 1) +
-  draw_plot_label(c("a", "b"), 
-    c(0.05, 0.05), c(1.95, 1), size = 20, color = "white") + 
-  theme(plot.background = element_rect(fill = "black"))
-```
 
@@
 
-The results will be analysed using a generalised linear model, with a subject random effect to account for differences in individuals.
-There will be two main effects: map type and trend model, which gives the fixed effects part of the model to be
+The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model. 
+The base R [@RCore] `glm()` function implements generalised linear models. The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
+
+$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij} + \epsilon_{i,j}, ~~~ i=1,2; ~j=1,2,3$$
+
+where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
+We are allowing for an interaction between map type and trend model.
+Because the response is binary, a logistic model is used.
+This model can account for each individual participants’ abilities as it includes a subject-specific random intercept.
+As each participant provides results from 12 lineups.
+
+The results will be analysed using a linear mixed effects model, with a subject random effect to account for differences in individuals.
+There will be two main effects: map type and trend model, with an interaction between them, which gives the fixed effects part of the model to be:
 
@@
 where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
-We are allowing for an interaction between map type and trend model. As the response for whether the participant detected the data plot is binary, a logistic model is used.
+We are allowing for an interaction between map type and trend model. As the response for whether the participant detected the data plot is binary, a logistic link model is used.
+
+The model specifies a logistic link, this means the predicted values from the `glm` model should be back-transformed to fit between 0 and 1. They are transformed with the link specified below:
+
+$$\mu = \frac{e^{\eta}}{1 + e^{\eta}}$$
+$$\eta = f(\tau_i,\delta_j)$$
 
@@
 
-<!--
-The detection rate for participants reporting the real data trend model is used to calculate the accuracy of the responses of participants.
-The accuracy is contrasted across the two displays with the following hypothesis:
-
-$H_0$ : $\mu_H$ = $\mu_C$
-$H_a$ : $\mu_H$ > $\mu_C$
-
-```{r ttest}
-# Probability of detection using map types
-test_dt <- d %>% mutate(type = factor(type, levels = c("Hex.", "Choro."))) %>% 
-  t.test(detect ~ type, data = ., alternative = "greater", paired = FALSE)
-
-```
-
-A two sample t-test was used to contrast the difference between the detection rates for the two types of displays.
-The value of `r test_dt$p.value` shows that it is very unlikely the difference in means is due to chance.
-The null hypothesis that the detection rate for the two groups is equal can be rejected in favour of the alternative, that the means are different.
--->
-
-Figure \@ref{detection_compare} display the average detection rates by type of plot, separately for each trend model.
+Figure \ref{detection_compare} displays the average detection rates by type of plot, separately for each trend model.
 Evaluations on the same data set are connected by a line segment.
@@
 Viewers detected the data plot substantially more often with the hexagon tile map.
-One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in a later section.
+One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in the supplementary [Lineups] section.
 Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map.
-We expected that the choropleth map would be superior for the type of spatial pattern, but the data suggests the hexagon tile map performs equally as well.
-
-Table \ref{tab:desc_stats} shows the means and standard deviations for type of plot and each trend model.
-
-<!-- The detection rates were higher when participants viewed the hexagon tile map displays. The impact of the trend model is also considered and presented in table \@ref(tab:desc_stats).
-The difference was greater when viewing a three cities trend model.
-When the trend model affected all cities participants also detected the data display in the lineup of null plots more often.
-The North West to South East data plot was detected with similar rates when viewing the choropleth and  hexagon tile map displays, though for three of the replicates the participants detected the data display more often.
--->
+We expected that the choropleth map would be superior for the type of spatial pattern, but the data suggests the hexagon tile map performs slightly better, or equally as well.
+
+Table \ref{tab:desc_stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
+This also gives the standard errors, the smallest standard deviation is the Three Cities trend model shown in a Choropleth display.
+This group had a very small detection rate of 0.038.
 
@@
   summarise(m = round(mean(detect),3),
-    std.dev = paste0("(", round(sd(detect),2),")")) %>% 
+    std.dev = paste0("(", as.character(round(sd(detect),3)),")")) %>% 
   gather(stat, value, m, std.dev) %>% 
@@
 
-Table XXX is a summary of the mixed effects model. Blah, blah, what we learn.
+Table \ref{detect_glm1} is a summary of the generalised linear mixed effects model.
+The estimate of the intercept represents the detection rate for the Choropleth display of the NW-SE trend.
+
+```{r detect_glmer1, results="asis"}
+# Mixed effects models
+glmer1 <- glmer(detect ~ type*trend + (1|contributor), 
+              family = binomial, data = d)
+
+tidy(glmer1) %>%
+  mutate_at(.vars = c("estimate", "std.error"), round, 2) %>% 
+  mutate(p.value = round(p.value, 3)) %>% 
+  rowwise() %>% 
+  mutate(estimate = case_when(
+  p.value <= 0.001 ~ paste0(estimate,"$^{***}$"),
+  p.value <= 0.01 ~ paste0(estimate, "$^{** }$"),
+  p.value <= 0.05 ~ paste0(estimate, "$^{*  }$"),
+  p.value <= 0.01 ~ paste0(estimate, "$^{.  }$"),
+  TRUE ~ paste0(estimate))) %>%
+  ungroup() %>% 
+  filter(!is.na(std.error)) %>% 
+  select(Term = term, 
+    Estimate = estimate, 
+    `Std. Error` = std.error, 
+    `P value` = p.value) %>% 
+  knitr::kable(format = "latex", escape = FALSE, align= "rcrrr", booktabs = T)
+```
+
+The model summary in Table \ref{detect_glmer1} shows that the predicted log odds of the detection rate is 0.46 times that of the choropleth lineups, for the lineups of hexagon tile map. 
+The baseline trend model used is the NW-SE trend, the detection rate is expected to decrease comparatively for choropleth displays of the Three Cities and All Cities trends.
+However, when the interaction is considered the detection rate is expected to increase for the Three Cities and All Cities trends shows in the Hexagon tile map display.
 
@@
 
-The relationship between time taken to submit, and the correct detection by the participant of the real data display in a lineup is considered in Figure \@ref(fig:hist_height).
+The relationship between time taken to submit, and the correct detection by the participant of the real data display in a lineup is considered in Figure \ref{fig:hist_height}.
 The bimodal distributions are similar across the type of display and the trend model hidden in the real data plot.
@@
 
-The choropleth map displays that included a distribution of three cities was very difficult for participants.
+The choropleth map displays that included a distribution of Three Cities was very difficult for participants.
 
@@
 
-The most common choice made by participant was clusters, this response was expected when participants viewed the Hexagon display of the all cities and three cities distributions.
+The most common choice made by participant was clusters, this response was expected when participants viewed the Hexagon display of the All Cities and Three Cities distributions.
 
@@
 
-The choices made by participants are examined in Figure \@ref(fig:choices).
-Participants were misled by the choropleth display, but not the hexagon display for all cities displays except (2).
+The choices made by participants are examined in Figure \ref{fig:choices}.
+Participants were misled by the choropleth display, but not the hexagon display for All Cities displays except (2).
 The maps with a North West to South East trend was chosen with much greater frequency in all displays.
-All of three cities displays, except (4), were detected in the hexagon display.
-All except one lineup had at least one participant select the correct map in the lineup as shown in Figure \@ref(fig:choices).
+All of Three Cities displays, except (4), were detected in the hexagon display.
+All except one lineup had at least one participant select the correct map in the lineup as shown in Figure \ref{fig:choices}.
 
@@
 
-!["The lineup of choropleth map displays shows a distribution that affects all capital cities.
-The values for the inner city areas in the capital cities result in them being coloured red.
-However, the colour blue dominates the display as the large rural areas are filled.
-Replicate (2) for all cities."](figures/aus_cities_3_geo.png)
-
 !["A North-West to South East trend was hidden in this lineup of hexagon tile map displays."](figures/aus_nwse_6_hex.png)
 
-## Modeling the difference
-
-The likelihood of detecting the data plot in the lineup can be modelled using a generalized linear mixed effects model. 
-The base R [@RCore] `glm()` function implements generalised linear models. The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
-
-$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij} + \epsilon_{i,j}, ~~~ i=1,2; ~j=1,2,3$$
-
-where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
-We are allowing for an interaction between map type and trend model.
-Because the response is binary, a logistic model is used.
-This model can account for each individual participants’ abilities as it includes a subject-specific random intercept.
-As each participant provides results from 12 lineups.
-
-### Detection Rates
-
-The model specifies a logistic link, this means the predicted values from the `glm` model should be back-transformed to fit between 0 and 1. They are transformed with the link specified below:
-
-$$\mu = \frac{e^{\eta}}{1 + e^{\eta}}$$
-$$\eta = f(\tau_i,\delta_j)$$
-
-```{r modeling_glm1, results="asis"}
-# Modelling 
-glm1 <- glm(formula = detect ~ type * trend,
-  family = binomial(link = "logit"), data = d)
-
-preds <- predict(glm1, newdata = d, se=T)
-pfit <- exp(preds$fit)/(1+exp(preds$fit))
-se.bands.logit = tibble(upper = (preds$fit+2*preds$se.fit), lower = (preds$fit-2*preds$se.fit))
-se.bands = exp(se.bands.logit)/(1+exp(se.bands.logit))
-
-terms <- c("Intercept", "Hex", "Three cities", "All cities", "Hex : Three cities", "Hex : All cities")
-
-tidy(glm1) %>%
-  mutate_if(is.numeric, round, 2) %>% 
-  rowwise() %>% 
-  mutate(estimate = case_when(
-    p.value <= 0.001 ~ paste0(estimate,"$^{***}$"),
-    p.value <= 0.01 ~ paste0(estimate, "$^{** }$"), 
-    p.value <= 0.05 ~ paste0(estimate, "$^{*  }$"), 
-    p.value <= 0.01 ~ paste0(estimate, "$^{.  }$"),
-    TRUE ~ paste0(estimate))) %>% 
-  ungroup() %>% 
-  mutate(term = terms) %>% 
-  select(Term = term, 
-    Estimate = estimate, 
-    Error = std.error, 
-    Stat = statistic,
-    p.value) %>% knitr::kable(format = "latex", escape = FALSE, align= "rcrrr", booktabs = T)
-```
-
-```{r pred_glm1}
-d_glm <- d %>% select(group:certainty, detect, detect_f) %>%
-  bind_cols(as_tibble(se.bands)) %>% 
-  mutate(pfit, 
-    predicted = ifelse(pfit > 0.5, 1, 0),
-    predicted = factor(predicted, levels = c(0,1), 
-      labels = c("Predicted: No", "Predicted: Yes")))
-
-table(d_glm$predicted, d_glm$detect_f)
-```
-
-This gives the model:
-
-$$\widehat{y_{ij}} = 0.0217 + 0.42Hex -3.25_{three} -1.24_{all} + 2.37{Hex.three} + 1.08{Hex.all} $$
-
-```{r glm2}
-glm2 <- glm(formula = detect ~ type * trend + replicate_f,
-  family = binomial(link = "logit"), data = d)
-
-emmean2 <- emmeans(glm2, c("trend", "type", "replicate_f"),
-                        type = "response")
-
-int_2 <- confint(emmean2, by = c("type", "trend", "replicate_f"), adjust = "bonferroni")
-int_2 %>% 
-  ggplot(aes(x= replicate_f, y = prob, group = type)) + 
-  geom_point() + 
-  geom_line(alpha = 0.5, lty = "dashed") + 
-  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL, col = type), width = 0.2) +
-  scale_color_manual(values = type_colours) +
-  facet_grid(trend ~ .) +
-  labs(x = "Replicates", y = "Detection Rate")
-```
-
-```{r lmer1, results = "asis"}
-# Mixed effects models
-lmer1 <- lmer(detect ~ type*trend + (1|contributor), data = d)
-lmer1_d <- augment(lmer1, d)
-
-preds_lmer <- predict(lmer1, newdata = d)
-pfit_lmer <- exp(preds_lmer)/(1+exp(preds_lmer))
-
-stargazer::stargazer(lmer1)
-
-d_lmer <- d %>% select(group:certainty, detect, detect_f) %>%
-  bind_cols(as_tibble(se.bands)) %>% 
-  mutate(pfit_lmer, 
-    predicted = ifelse(pfit_lmer > 0.5, 1, 0),
-    predicted = factor(predicted, levels = c(0,1), labels = c("No", "Yes")))
-# Hexagon maps have better chance of correct detection
-# Allowing for contributor effects to vary: 0.12 strong residual
-```
-
-For a base model of Choropleth map, using a NW-SE trend model.
-The detection rate for Hexagon tile maps using a NW-SE trend model changes the log odds of the detection by 0.42.
-
-```{r lmer2, results = "asis"}
-# Mixed effects models
-lmer2 <- lmer(detect ~ (type|trend), data = d)
-lmer2_d <- augment(lmer2, d)
-
-preds_lmer2 <- predict(lmer2, newdata = d)
-pfit_lmer2 <- exp(preds_lmer2)/(1+exp(preds_lmer2))
-
-stargazer::stargazer(lmer2)
-
-d_lmer2 <- d %>% select(group:certainty, detect, detect_f) %>%
-  bind_cols(as_tibble(se.bands)) %>% 
-  mutate(pfit_lmer2, 
-    predicted = ifelse(pfit_lmer2 > 0.5, 1, 0),
-    predicted = factor(predicted, levels = c(0,1), labels = c("No", "Yes")))
-
-```
-
 ### Certainty
-
-```{r lmer1_model, results = "asis"}
-# Mixed effects models
-lmer1 <- lmer(detect ~ type*trend + (1|contributor), data = d)
-tidy(lmer1) %>% mutate_if(is.numeric, .f = round, 2) %>% stargazer::stargazer(.)
-
-# Hexagon maps have better chance of correct detection
-# Allowing for contributor effects to vary: 0.12 strong residual
-```
 
@@
 
+\newpage
 Supplementary Materials
@@
 
-The demonstrative images of the `shinydashboard` web application display the demographic and consent page in Figure \@ref(fig:survey1).
+The demonstrative images of the `shinydashboard` web application display the demographic and consent page in Figure \ref{fig:survey1}.
 
@@
 -->
+
+## Lineups
+
+Lineups were created using the Australian Statistical Areas at Level 3.
+
+![The lineup of choropleth map displays hides a distribution that affects all capital cities.](figures/aus_cities_3_geo.png)
+
+![The lineup of choropleth map displays shows a distribution that affects all capital cities.
+The values for the inner city areas in the capital cities result in them being coloured red.
+However, the colour blue dominates the display as the large rural areas are filled.
+Replicate (2) for All Cities.](figures/aus_cities_3_hex.png)
+
+The values for the inner city areas in the capital cities result in them being coloured red.
+However, the colour blue dominates the display as the large rural areas are filled.
+There were no other choropleth maps that were coloured as blue as map (3).
+This meant the detection rate was quite high, participants were able to select the correct distribution without being able to see the values of the capital cities.
+The same data showed in the hexagon tile map display shows varied distributions across the lineup.
+They are more diverse in colour than the choropleth counterparts.
+The same location holds the real data plot, the red city centres are now visible and surrounded by yellow, and then blue hexagons.
+
 ## Overall Performance
@@
 
-## Subject specific anomolies (0% detection)
-
 ## Demographics:
@@
 dem_contribs %>% ggplot() + geom_bar(aes(age))
+
 dem_contribs %>% count(gender) %>% knitr::kable(format = "latex", booktabs = TRUE)
+
 dem_contribs %>% count(education) %>% knitr::kable(format = "latex", booktabs = TRUE)
@@
 
-Acknowledgment {#acknowledgment}
+Acknowledgment
 ==============
@@
 All applicants provided informed consent in line with QUT regulations prior to participating in this research.
-
-Bibliography
-=============
 

### 2020-01-10 paper/paper.Rmd
figure

@@
   chunk_output_type: inline
-link-citations: yes
+link-citations: true
 ---
@@
 
-Figure \ref{detection_compare} displays the average detection rates by type of plot, separately for each trend model.
+Figure \ref{fig:detection_compare} displays the average detection rates by type of plot, separately for each trend model.
 Evaluations on the same data set are connected by a line segment.
@@
 
+glmer_terms <- c("Intercept", "Hex.", "Three Cities", "All Cities", 
+  "Hex:Three Cities", "Hex:All Cities")
+
 tidy(glmer1) %>%
@@
   filter(!is.na(std.error)) %>%
+  mutate(term = glmer_terms) %>% 
   select(Term = term, 
@@
 
-The model summary in Table \ref{detect_glmer1} shows that the predicted log odds of the detection rate is 0.46 times that of the choropleth lineups, for the lineups of hexagon tile map. 
+The model summary in Table \ref{tab:detect_glmer1} shows that the predicted log odds of the detection rate is 0.46 times that of the choropleth lineups, for the lineups of hexagon tile map. 
 The baseline trend model used is the NW-SE trend, the detection rate is expected to decrease comparatively for choropleth displays of the Three Cities and All Cities trends.

### 2020-01-10 paper/paper.Rmd
time taken results

@@
   message = FALSE,
-  cache = TRUE)
+  cache = FALSE)
 ```
@@
 This resulted in 1104 evaluations, corresponding to 92 subjects, each evaluating 12 lineups, that are analysed on accuracy and speed.
+The certainty and reasons of subjects in their answers is also examined.
 
@@
 
-Table \ref{detect_glm1} is a summary of the generalised linear mixed effects model.
-The estimate of the intercept represents the detection rate for the Choropleth display of the NW-SE trend.
+Table \ref{detect_glm1} is a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on detection rate.
+The results support the summary from Figure \@ref{detection_compare}.
+All terms are statistically significant.
+Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
+Detection rate is lower for the Three Cities and All Cities, than the NW-SE group.
+The hexagon tile map has a substantially higher detection rate than the choropleth for Three Cities and All Cities.
+XXX Put a number for each of these.
 
@@
 
-The model summary in Table \ref{tab:detect_glmer1} shows that the predicted log odds of the detection rate is 0.46 times that of the choropleth lineups, for the lineups of hexagon tile map. 
+<!-- The model summary in Table \ref{tab:detect_glmer1} shows that the predicted log odds of the detection rate is 0.46 times that of the choropleth lineups, for the lineups of hexagon tile map. 
 The baseline trend model used is the NW-SE trend, the detection rate is expected to decrease comparatively for choropleth displays of the Three Cities and All Cities trends.
 However, when the interaction is considered the detection rate is expected to increase for the Three Cities and All Cities trends shows in the Hexagon tile map display.
+-->
 
@@
 
-The amount of time taken for a participants to submit a response is explored. 
+Figure \ref{fig:beeswarm} shows the time taken for participants to evaluate each lineup, separately for trend model, whether the data plot was detected or not, and type of plot, as horizontally jittered dot plots.
+The time taken to complete an evaluation ranged from milliseconds to 60 seconds.
+The average time taken for type of display is displayed as a large colored dot on each plot.
+There is little difference in the average time taken to read a choropleth or hexgon tile map.
+There is also very little difference in evaluation time whether the data plot was detected or not.
+
+<!-- The amount of time taken for a participants to submit a response is explored. 
 The time considered was the amount of time it took for a participant to submit their choice of plot, the reason for their choice, and the perceived difficulty of the choice.
@@
 The longest a participant took to respond was 60 seconds.
+-->
 
@@
 
-```{r beeswarm, fig.cap = "The beeswarm plots show the distribution of the time taken to submit a response for each combination of trend and type of display.
-The time taken shown by the height of the point for each evaluationq1.
-The height of the histogram bars show how many evaulations were submitted within each time window.
-The orange regions of the bars show the amount of correct detections, and the green regions are the amount of incorrect detections."}
+```{r beeswarm, fig.cap = "The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots.
+The coloured point indicates average time taken for each plot type.
+Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between plot types.", fig.height=8}
 # Di playing
@@
   #geom_errorbar(data=s, aes(x=type, ymin=q1, ymax=q3, colour=type), width=0.3, size=2) +
-  scale_colour_brewer(palette = "Dark2") +
-  facet_grid(trend~detect)
+  scale_colour_brewer("", palette = "Dark2") +
+  facet_grid(trend~detect) + 
+  ylab("Time taken (seconds)") + xlab("") +
+  theme(legend.position="bottom")
 ```
 
-The proportion of correct and incorrect responsesis shown by the width used to distribute the points horizontally.
+<!-- The proportion of correct and incorrect responsesis shown by the width used to distribute the points horizontally.
 Each point is randomly placed, but regions with more points require points to be placed further from center.
@@
 The choropleth map displays that included a distribution of Three Cities was very difficult for participants. 
+-->
 

### 2020-01-10 paper/paper.tex
time taken results

@@
 \hypersetup{
-            pdftitle={An Experiment Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics},
+            pdftitle={Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics},
             pdfkeywords={statistics, visual inference, geospatial, population},
@@
 % Do not put math or special symbols in the title.
-\title{An Experiment Comparing the Effectiveness of the Choropleth Map with a
-Hexagon Tile Map for Communicating Cancer Statistics}
+\title{Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile
+Map for Communicating Cancer Statistics}
 
@@
 display must be employed. This will emphasise the value of the statistic
-for areas with high population. Figure @ref(fig:liver) shows the
+for areas with high population. Figure \ref{fig:liver} shows the
 distribution of the smoothed average amount of Liver cancer diagnoses
@@
 to each other and show distributions similar to the Liver cancer
-distribution shown in @ref(fig:liver).
+distribution shown in \ref{fig:liver}.
 
@@
 Replicate 3 of the All Cities distribution is shown in
-@ref(fig:compare). The same data set is shown in both displays, the
+\ref{fig:compare}. The same data set is shown in both displays, the
 difference is the land area of each SA3 is coloured in the choropleth
@@
 red.
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/compare-1.pdf}
-\caption{Comparing the same data presented in two map displays. The
-choropleth map display in (a)}
-\end{figure}
 
@@
 
-The results will be analysed using a generalised linear model, with a
+The likelihood of detecting the data plot in the lineup can be modelled
+using a linear mixed effects model. The base R (R Core Team
+\protect\hyperlink{ref-RCore}{2019}) \texttt{glm()} function implements
+generalised linear models. The model used includes the two main effects
+map type and trend model, which gives the fixed effects model to be:
+
+\[\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij} + \epsilon_{i,j}, ~~~ i=1,2; ~j=1,2,3\]
+
+where \(y_{ij} = 0, 1\) whether the subject detected the data plot,
+\(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect,
+\(\delta_j\) is the trend model effect. We are allowing for an
+interaction between map type and trend model. Because the response is
+binary, a logistic model is used. This model can account for each
+individual participants' abilities as it includes a subject-specific
+random intercept. As each participant provides results from 12 lineups.
+
+The results will be analysed using a linear mixed effects model, with a
 subject random effect to account for differences in individuals. There
-will be two main effects: map type and trend model, which gives the
-fixed effects part of the model to be
+will be two main effects: map type and trend model, with an interaction
+between them, which gives the fixed effects part of the model to be:
 
@@
 whether the participant detected the data plot is binary, a logistic
-model is used.
+link model is used.
+
+The model specifies a logistic link, this means the predicted values
+from the \texttt{glm} model should be back-transformed to fit between 0
+and 1. They are transformed with the link specified below:
+
+\[\mu = \frac{e^{\eta}}{1 + e^{\eta}}\] \[\eta = f(\tau_i,\delta_j)\]
 
@@
 
-Figure @ref\{detection\_compare\} display the average detection rates by
-type of plot, separately for each trend model. Evaluations on the same
-data set are connected by a line segment. For both the Three Cities and
-All Cities trend models performance was substantially better for the
+Figure \ref{fig:detection_compare} displays the average detection rates
+by type of plot, separately for each trend model. Evaluations on the
+same data set are connected by a line segment. For both the Three Cities
+and All Cities trend models performance was substantially better for the
 hexagon tile map. Viewers detected the data plot substantially more
@@
 had similar detection rates for both plot types, and this is discussed
-in a later section. Surprisingly, participants could also detect the
-gradual spatial trend in the NW-SE group from the hexagon tile map. We
-expected that the choropleth map would be superior for the type of
-spatial pattern, but the data suggests the hexagon tile map performs
+in the supplementary \protect\hyperlink{lineups}{Lineups} section.
+Surprisingly, participants could also detect the gradual spatial trend
+in the NW-SE group from the hexagon tile map. We expected that the
+choropleth map would be superior for the type of spatial pattern, but
+the data suggests the hexagon tile map performs slightly better, or
 equally as well.
 
-Table \ref{tab:desc_stats} shows the means and standard deviations for
-type of plot and each trend model.
+Table \ref{tab:desc_stats} shows the means and standard deviations of
+the detection rate for each type of plot and each trend model. This also
+gives the standard errors, the smallest standard deviation is the Three
+Cities trend model shown in a Choropleth display. This group had a very
+small detection rate of 0.038.
 
@@
 Choro. & 0.505 & 0.038 & 0.228\\
- & (0.5) & (0.19) & (0.42)\\
+ & (0.501) & (0.192) & (0.421)\\
 Hex. & 0.609 & 0.391 & 0.571\\
- & (0.49) & (0.49) & (0.5)\\
+ & (0.489) & (0.489) & (0.496)\\
 \bottomrule
@@
 
-Table XXX is a summary of the mixed effects model. Blah, blah, what we
-learn.
+Table \ref{detect_glm1} is a summary of the generalised linear mixed
+effects model, testing the effect of plot type and trend model on
+detection rate. The results support the summary from Figure
+@ref\{detection\_compare\}. All terms are statistically significant.
+Overall, the hexagon tile map performs marginally better than the
+choropleth for all trend models, which is a pleasant surprise. Detection
+rate is lower for the Three Cities and All Cities, than the NW-SE group.
+The hexagon tile map has a substantially higher detection rate than the
+choropleth for Three Cities and All Cities. XXX Put a number for each of
+these.
+
+\begin{tabular}{rcrr}
+\toprule
+Term & Estimate & Std. Error & P value\\
+\midrule
+Intercept & 0.02 & 0.17 & 0.896\\
+Hex. & 0.46$^{*  }$ & 0.22 & 0.037\\
+Three Cities & -3.43$^{***}$ & 0.42 & 0.000\\
+All Cities & -1.35$^{***}$ & 0.24 & 0.000\\
+Hex:Three Cities & 2.46$^{***}$ & 0.47 & 0.000\\
+\addlinespace
+Hex:All Cities & 1.17$^{***}$ & 0.33 & 0.000\\
+\bottomrule
+\end{tabular}
 
@@
 
-The amount of time taken for a participants to submit a response is
-explored. The time considered was the amount of time it took for a
-participant to submit their choice of plot, the reason for their choice,
-and the perceived difficulty of the choice. The time was taken when each
-participant hit ``Next''.
-
-The relationship between time taken to submit, and the correct detection
-by the participant of the real data display in a lineup is considered in
-Figure @ref(fig:hist\_height). The bimodal distributions are similar
-across the type of display and the trend model hidden in the real data
-plot. The hexagon map displays have a peak for the group that took up to
-5 seconds to submit a response. When viewing a choropleth map display,
-the second peak occured at around 20 seconds. The longest a participant
-took to respond was 60 seconds.
+Figure \ref{fig:beeswarm} shows the time taken for participants to
+evaluate each lineup, separately for trend model, whether the data plot
+was detected or not, and type of plot, as horizontally jittered dot
+plots. The time taken to complete an evaluation ranged from milliseconds
+to 60 seconds. The average time taken for type of display is displayed
+as a large colored dot on each plot. There is little difference in the
+average time taken to read a choropleth or hexgon tile map. There is
+also very little difference in evaluation time whether the data plot was
+detected or not.
 
@@
 \includegraphics{paper_files/figure-latex/beeswarm-1.pdf}
-\caption{The beeswarm plots show the distribution of the time taken to
-submit a response for each combination of trend and type of display. The
-time taken shown by the height of the point for each evaluationq1. The
-height of the histogram bars show how many evaulations were submitted
-within each time window. The orange regions of the bars show the amount
-of correct detections, and the green regions are the amount of incorrect
-detections.}
+\caption{The distribution of the time taken (seconds) to submit a
+response for each combination of trend, whether the data plot was
+detected, and type of display, shown using horizontally jittered
+dotplots. The coloured point indicates average time taken for each plot
+type. Although some participants take just a few seconds per evaluation,
+and some take as much as mcuh as 60 seconds, but there is very little
+difference in time taken between plot types.}
 \end{figure}
-
-The proportion of correct and incorrect responsesis shown by the width
-used to distribute the points horizontally. Each point is randomly
-placed, but regions with more points require points to be placed further
-from center. For the NW-SE distribution, it is equally likely that quick
-responders will be correct or incorrect. It is more likely that
-participants picked the correct response if they took longer to respond.
-For the Choropelth
-
-However, these quick responders were likely to be either correct or
-incorrect. The quick responders viewing a choropleth display were
-unlikely to choose correctly, unless viewing a NW-SE trend model.
-
-The choropleth map displays that included a distribution of three cities
-was very difficult for participants.
 
@@
 The most common choice made by participant was clusters, this response
-was expected when participants viewed the Hexagon display of the all
-cities and three cities distributions.
+was expected when participants viewed the Hexagon display of the All
+Cities and Three Cities distributions.
 
@@
 The choices made by participants are examined in Figure
-@ref(fig:choices). Participants were misled by the choropleth display,
-but not the hexagon display for all cities displays except (2). The maps
+\ref{fig:choices}. Participants were misled by the choropleth display,
+but not the hexagon display for All Cities displays except (2). The maps
 with a North West to South East trend was chosen with much greater
-frequency in all displays. All of three cities displays, except (4),
+frequency in all displays. All of Three Cities displays, except (4),
 were detected in the hexagon display. All except one lineup had at least
 one participant select the correct map in the lineup as shown in Figure
-@ref(fig:choices).
+\ref{fig:choices}.
 
@@
 \centering
-\includegraphics{figures/aus_cities_3_geo.png}
-\caption{``The lineup of choropleth map displays shows a distribution
-that affects all capital cities. The values for the inner city areas in
-the capital cities result in them being coloured red. However, the
-colour blue dominates the display as the large rural areas are filled.
-Replicate (2) for all cities.''}
-\end{figure}
-
-\begin{figure}
-\centering
 \includegraphics{figures/aus_nwse_6_hex.png}
@@
 
-\hypertarget{modeling-the-difference}{%
-\subsection{Modeling the difference}\label{modeling-the-difference}}
-
-The likelihood of detecting the data plot in the lineup can be modelled
-using a generalized linear mixed effects model. The base R (R Core Team
-\protect\hyperlink{ref-RCore}{2019}) \texttt{glm()} function implements
-generalised linear models. The model used includes the two main effects
-map type and trend model, which gives the fixed effects model to be:
-
-\[\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij} + \epsilon_{i,j}, ~~~ i=1,2; ~j=1,2,3\]
-
-where \(y_{ij} = 0, 1\) whether the subject detected the data plot,
-\(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect,
-\(\delta_j\) is the trend model effect. We are allowing for an
-interaction between map type and trend model. Because the response is
-binary, a logistic model is used. This model can account for each
-individual participants' abilities as it includes a subject-specific
-random intercept. As each participant provides results from 12 lineups.
-
-\hypertarget{detection-rates}{%
-\subsubsection{Detection Rates}\label{detection-rates}}
-
-The model specifies a logistic link, this means the predicted values
-from the \texttt{glm} model should be back-transformed to fit between 0
-and 1. They are transformed with the link specified below:
-
-\[\mu = \frac{e^{\eta}}{1 + e^{\eta}}\] \[\eta = f(\tau_i,\delta_j)\]
-
-\begin{tabular}{rcrrr}
-\toprule
-Term & Estimate & Error & Stat & p.value\\
-\midrule
-Intercept & 0.02 & 0.15 & 0.15 & 0.88\\
-Hex & 0.42$^{*  }$ & 0.21 & 1.99 & 0.05\\
-Three cities & -3.25$^{***}$ & 0.41 & -7.88 & 0.00\\
-All cities & -1.24$^{***}$ & 0.23 & -5.41 & 0.00\\
-Hex : Three cities & 2.37$^{***}$ & 0.46 & 5.10 & 0.00\\
-\addlinespace
-Hex : All cities & 1.08$^{***}$ & 0.31 & 3.47 & 0.00\\
-\bottomrule
-\end{tabular}
-
-\begin{verbatim}
-##                 
-##                  Detected? No Detected? Yes
-##   Predicted: No           431           121
-##   Predicted: Yes          242           310
-\end{verbatim}
-
-This gives the model:
-
-\[\widehat{y_{ij}} = 0.0217 + 0.42Hex -3.25_{three} -1.24_{all} + 2.37{Hex.three} + 1.08{Hex.all} \]
-
-\includegraphics{paper_files/figure-latex/glm2-1.pdf}
-
-\% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard
-University. E-mail: hlavac at fas.harvard.edu \% Date and time: Fri, Jan
-10, 2020 - 11:55:55
-
-\begin{table}[!htbp] \centering 
-  \caption{} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-2} 
-\\[-1.8ex] & detect \\ 
-\hline \\[-1.8ex] 
- typeHex. & 0.103$^{**}$ \\ 
-  & (0.045) \\ 
-  & \\ 
- trendThree Cities & $-$0.467$^{***}$ \\ 
-  & (0.045) \\ 
-  & \\ 
- trendAll Cities & $-$0.277$^{***}$ \\ 
-  & (0.045) \\ 
-  & \\ 
- typeHex.:trendThree Cities & 0.250$^{***}$ \\ 
-  & (0.063) \\ 
-  & \\ 
- typeHex.:trendAll Cities & 0.239$^{***}$ \\ 
-  & (0.063) \\ 
-  & \\ 
- Constant & 0.505$^{***}$ \\ 
-  & (0.034) \\ 
-  & \\ 
-\hline \\[-1.8ex] 
-Observations & 1,104 \\ 
-Log Likelihood & $-$675.359 \\ 
-Akaike Inf. Crit. & 1,366.719 \\ 
-Bayesian Inf. Crit. & 1,406.772 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
-For a base model of Choropleth map, using a NW-SE trend model. The
-detection rate for Hexagon tile maps using a NW-SE trend model changes
-the log odds of the detection by 0.42.
-
-\% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard
-University. E-mail: hlavac at fas.harvard.edu \% Date and time: Fri, Jan
-10, 2020 - 11:55:55
-
-\begin{table}[!htbp] \centering 
-  \caption{} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-2} 
-\\[-1.8ex] & detect \\ 
-\hline \\[-1.8ex] 
- Constant & 0.669$^{***}$ \\ 
-  & (0.050) \\ 
-  & \\ 
-\hline \\[-1.8ex] 
-Observations & 1,104 \\ 
-Log Likelihood & $-$684.772 \\ 
-Akaike Inf. Crit. & 1,379.544 \\ 
-Bayesian Inf. Crit. & 1,404.578 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
 \hypertarget{certainty-1}{%
 \subsubsection{Certainty}\label{certainty-1}}
-
-\% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard
-University. E-mail: hlavac at fas.harvard.edu \% Date and time: Fri, Jan
-10, 2020 - 11:55:55
-
-\begin{table}[!htbp] \centering 
-  \caption{} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
-Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
-\hline \\[-1.8ex] 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
 
@@
 
+\newpage
+
 \hypertarget{supplementary-materials}{%
@@
 The demonstrative images of the \texttt{shinydashboard} web application
-display the demographic and consent page in Figure @ref(fig:survey1).
+display the demographic and consent page in Figure \ref{fig:survey1}.
+
+\hypertarget{lineups}{%
+\subsection{Lineups}\label{lineups}}
+
+Lineups were created using the Australian Statistical Areas at Level 3.
+
+\begin{figure}
+\centering
+\includegraphics{figures/aus_cities_3_geo.png}
+\caption{The lineup of choropleth map displays hides a distribution that
+affects all capital cities.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{figures/aus_cities_3_hex.png}
+\caption{The lineup of choropleth map displays shows a distribution that
+affects all capital cities. The values for the inner city areas in the
+capital cities result in them being coloured red. However, the colour
+blue dominates the display as the large rural areas are filled.
+Replicate (2) for All Cities.}
+\end{figure}
+
+The values for the inner city areas in the capital cities result in them
+being coloured red. However, the colour blue dominates the display as
+the large rural areas are filled. There were no other choropleth maps
+that were coloured as blue as map (3). This meant the detection rate was
+quite high, participants were able to select the correct distribution
+without being able to see the values of the capital cities. The same
+data showed in the hexagon tile map display shows varied distributions
+across the lineup. They are more diverse in colour than the choropleth
+counterparts. The same location holds the real data plot, the red city
+centres are now visible and surrounded by yellow, and then blue
+hexagons.
 
@@
 \subsection{Overall Performance}\label{overall-performance}}
-
-\hypertarget{subject-specific-anomolies-0-detection}{%
-\subsection{Subject specific anomolies (0\%
-detection)}\label{subject-specific-anomolies-0-detection}}
 
@@
 
-\hypertarget{bibliography}{%
-\section{Bibliography}\label{bibliography}}
-
 \newpage

### 2020-01-10 paper/paper.Rmd
minor changes

--- 2020-01-10 paper/paper.Rmd
@@
 bibliography: mybibfile.bib
-output: rticles::ieee_article
+output:
+  bookdown::pdf_book: 
+      base_format: rticles::ieee_article
+      number_sections: false
 editor_options: 
@@
 link-citations: true
+citation_package: biblatex
 ---
@@
 library(kableExtra)
+
+options(knitr.kable.digits = "2")
 ```
@@
 This will generate twenty-four lineups (twelve lineups of geographic maps, and twelve lineups of hexagon tile maps). Participants evaluated twelve lineups, siz of each map type.
-For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants.
+For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants. The design is outlined in \@ref(tab:exp-design).
 
-```{r exp_design, results = "asis"}
+```{r exp-design, results = "asis"}
 d %>% 
@@
   ungroup() %>% 
-  knitr::kable(., format = "latex", booktabs = TRUE, caption = "Experimental design.") %>% kable_styling("striped")
-#%>% 
-#  collapse_rows(., columns = 1, custom_latex_hline = c(1:3))
+  knitr::kable(., format = "latex", booktabs = TRUE, 
+    linesep = c("", "", "\\addlinespace"),
+    caption = "The experimental design results in the following allocation of replicate data sets within each trend model to groups A and B.") %>% kable_styling("striped") %>% 
+  collapse_rows(., columns = 1, custom_latex_hline = c(1:3))
 ```
@@
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model. 
-The base R [@RCore] `glm()` function implements generalised linear models. The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
+The R [@RCore] `glmer()` function in the [@lme4] package implements generalised linear mixed effect models.
+The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
 
@@
 
-The results will be analysed using a linear mixed effects model, with a subject random effect to account for differences in individuals.
-There will be two main effects: map type and trend model, with an interaction between them, which gives the fixed effects part of the model to be:
-
-$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3$$
-
-where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
-We are allowing for an interaction between map type and trend model. As the response for whether the participant detected the data plot is binary, a logistic link model is used.
-
-The model specifies a logistic link, this means the predicted values from the `glm` model should be back-transformed to fit between 0 and 1. They are transformed with the link specified below:
+The model specifies a logistic link, this means the predicted values from the `glmer` model should be back-transformed to fit between 0 and 1. They are transformed with the link specified below:
 
@@
 
-Table \ref{tab:desc_stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
+Table \ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
 This also gives the standard errors, the smallest standard deviation is the Three Cities trend model shown in a Choropleth display.
@@
 
-```{r detection_compare, fig.cap = "The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models.
+```{r detection-compare, fig.cap = "The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models.
 Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup.
@@
 
-```{r desc_stats, results = "asis"}
+```{r desc-stats, results = "asis"}
 types <- c("Choro.", "", "Hex.", "")
@@
   mutate(Type = types) %>% select(Type, `NW-SE`, `Three Cities`, `All Cities`) %>%
-  knitr::kable(., format = "latex", align = "lccc", booktabs = TRUE, caption = "")
+  knitr::kable(., format = "latex", align = "lccc", booktabs = TRUE, caption = "The rate of detection for each trend model has been calculate for the choropleth and hexagon tile map displays.
+The associated standard errors are also included.")
 ```
 
-Table \ref{detect_glm1} is a summary of the generalised linear mixed effects model.
+Table \ref{detect-glm1} is a summary of the generalised linear mixed effects model.
 The estimate of the intercept represents the detection rate for the Choropleth display of the NW-SE trend.
 
-```{r detect_glmer1, results="asis"}
+```{r detect-glmer1, results="asis"}
 # Mixed effects models
@@
     `P value` = p.value) %>% 
-  knitr::kable(format = "latex", escape = FALSE, align= "rcrrr", booktabs = T)
+  knitr::kable(format = "latex", escape = FALSE, align= "rclrr", booktabs = T,
+    caption = "The model output for the generalised linear mixed effect model for detection rate.
+This model considers the type of display, the trend model hidden in the data plot, and accounts for contributor performance.")
 ```
 
-The model summary in Table \ref{tab:detect_glmer1} shows that the predicted log odds of the detection rate is 0.46 times that of the choropleth lineups, for the lineups of hexagon tile map. 
+The model summary in Table \ref{tab:detect-glmer1} shows that the predicted log odds of the detection rate is 0.46 times that of the choropleth lineups, for the lineups of hexagon tile map. 
 The baseline trend model used is the NW-SE trend, the detection rate is expected to decrease comparatively for choropleth displays of the Three Cities and All Cities trends.
@@
 
-The relationship between time taken to submit, and the correct detection by the participant of the real data display in a lineup is considered in Figure \ref{fig:hist_height}.
+The relationship between time taken to submit, and the correct detection by the participant of the real data display in a lineup is considered in Figure \ref{fig:hist-height}.
 The bimodal distributions are similar across the type of display and the trend model hidden in the real data plot.
@@
 
-```{r hist_height,  eval=FALSE, fig.cap = "Six histograms show the distribution of the time taken to submit a response for each combination of trend and type of display.
+```{r hist-height,  eval=FALSE, fig.cap = "Six histograms show the distribution of the time taken to submit a response for each combination of trend and type of display.
 The time taken to evaluate each display is broken into five second windows.
@@
 
-```{r hist_fill,  eval=FALSE, fig.cap = "The time taken to evaluate each display is broken into five second windows.
+```{r hist-fill,  eval=FALSE, fig.cap = "The time taken to evaluate each display is broken into five second windows.
 The height of the histogram bars show the proportion of evaulations that were submitted within each time window."}
@@
 The orange regions of the bars show the amount of correct detections, and the green regions are the amount of incorrect detections."}
-# Di playing
-s <- d %>% group_by(type, trend, detect) %>%
+s <- d %>% group_by(type, trend, detect_f) %>%
   summarise(m=median(time_taken), 
@@
   scale_colour_brewer(palette = "Dark2") +
-  facet_grid(trend~detect)
+  facet_grid(trend~detect_f)
 ```
 
-The proportion of correct and incorrect responsesis shown by the width used to distribute the points horizontally.
+The proportion of correct and incorrect responses is shown by the width used to distribute the points horizontally.
 Each point is randomly placed, but regions with more points require points to be placed further from center.
@@
 The choropleth map displays that included a distribution of Three Cities was very difficult for participants.
+
+```{r time-lmer1, eval = FALSE, results="asis"}
+# Mixed effects models
+d %>% mutate(ln_time = time_taken) %>% 
+time_lmer1 <- glmer(ln_time ~ type*trend + (1|contributor),data = .)
+
+lmer_terms <- c("Intercept", "Hex.", "Three Cities", "All Cities", 
+  "Hex:Three Cities", "Hex:All Cities")
+
+tidy(time_lmer1)
+```
 
@@
 
-```{r reason, fig.cap = "The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
-The facets show whether or not the choice was correct.", results = "asis"}
+```{r reason, results = "asis"}
 
@@
   ungroup() %>% 
-  knitr::kable(., format = "latex", booktabs = TRUE) %>% kable_styling("striped") 
+  knitr::kable(., format = "latex", booktabs = TRUE,
+    caption = "The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
+The facets show whether or not the choice was correct.") %>% kable_styling("striped")
 #%>% 

### 2020-01-10 paper/paper.Rmd

@@
 
-Null hypothesis: There is NO relationship between the variables,
-Alternative hypothesis: There is a relationship between the variables.
+- Null hypothesis: There is NO relationship between the variables,
+
+- Alternative hypothesis: There is a relationship between the variables.
 
@@
 Each set of lineup data was used to produce a choropleth maps and hexagon tile maps. These matched pairs were split between Group A and Group B.
-
-Replicate 3 of the All Cities distribution is shown in \ref{fig:compare}.
-The same data set is shown in both displays, the difference is the land area of each SA3 is coloured in the choropleth and the hexagon representing the SA3 is coloured in the Hexagon Tile Map.
-Many maps in the Choropleth lineup (a) are coloured yellow, two are half light blue, and two are obviously blue.
-Only one of the maps looks red.
 
@@
 
-```{r detection-compare, fig.cap = "The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models.
+```{r detect-compare, fig.cap = "The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models.
 Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup.
@@
   mutate(Type = types) %>% select(Type, `NW-SE`, `Three Cities`, `All Cities`) %>%
-  knitr::kable(., format = "latex", align = "lccc", booktabs = TRUE, caption = "The rate of detection for each trend model has been calculate for the choropleth and hexagon tile map displays.
-The associated standard errors are also included.")
+  knitr::kable(., format = "latex", align = "lccc", booktabs = TRUE, 
+    linesep = c("", "\\addlinespace"),
+    caption = "The rate of detection for each trend model has been calculate for the choropleth and hexagon tile map displays. The associated standard errors are also included.")
 ```
 
-Table \ref{detect-glm1} is a summary of the generalised linear mixed effects model.
-The estimate of the intercept represents the detection rate for the Choropleth display of the NW-SE trend.
+Table \ref{detect-glmer1} is a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on detection rate.
+The results support the summary from Figure \@ref{detect-compare}.
+All terms are statistically significant.
+Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
+Detection rate is lower for the Three Cities and All Cities, than the NW-SE group.
+The hexagon tile map has a substantially higher detection rate than the choropleth for Three Cities and All Cities.
+XXX Put a number for each of these.
 
@@
   mutate_at(.vars = c("estimate", "std.error"), round, 2) %>% 
-  mutate(p.value = round(p.value, 3)) %>% 
+  mutate(p.value = format(p.value, 2)) %>% 
   rowwise() %>% 
@@
     `P value` = p.value) %>% 
-  knitr::kable(format = "latex", escape = FALSE, align= "rclrr", booktabs = T,
+  knitr::kable(format = "latex", escape = FALSE, align= "rclrr", 
+    booktabs = T, linesep = c("", "\\addlinespace", "", "\\addlinespace", ""),
     caption = "The model output for the generalised linear mixed effect model for detection rate.
@@
 
-The model summary in Table \ref{tab:detect-glmer1} shows that the predicted log odds of the detection rate is 0.46 times that of the choropleth lineups, for the lineups of hexagon tile map. 
+<!-- The model summary in Table \ref{tab:detect-glmer1} shows that the predicted log odds of the detection rate is 0.46 times that of the choropleth lineups, for the lineups of hexagon tile map. 
 The baseline trend model used is the NW-SE trend, the detection rate is expected to decrease comparatively for choropleth displays of the Three Cities and All Cities trends.
 However, when the interaction is considered the detection rate is expected to increase for the Three Cities and All Cities trends shows in the Hexagon tile map display.
+-->
 
@@
 
-```{r beeswarm, fig.cap = "The beeswarm plots show the distribution of the time taken to submit a response for each combination of trend and type of display.
-The time taken shown by the height of the point for each evaluationq1.
-The height of the histogram bars show how many evaulations were submitted within each time window.
-The orange regions of the bars show the amount of correct detections, and the green regions are the amount of incorrect detections."}
+```{r beeswarm, fig.cap = "The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots.
+The coloured point indicates average time taken for each plot type.
+Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between plot types.", fig.height=8}
+# Di playing
 s <- d %>% group_by(type, trend, detect_f) %>%
@@
   #geom_errorbar(data=s, aes(x=type, ymin=q1, ymax=q3, colour=type), width=0.3, size=2) +
-  scale_colour_brewer(palette = "Dark2") +
-  facet_grid(trend~detect_f)
+  scale_colour_brewer("", palette = "Dark2") +
+  facet_grid(trend~detect_f) + 
+  ylab("Time taken (seconds)") + xlab("") +
+  theme(legend.position="bottom")
 ```
 
-The proportion of correct and incorrect responses is shown by the width used to distribute the points horizontally.
+<!-- The proportion of correct and incorrect responsesis shown by the width used to distribute the points horizontally.
 Each point is randomly placed, but regions with more points require points to be placed further from center.
@@
 For the Choropelth
-
 However, these quick responders were likely to be either correct or incorrect. The quick responders viewing a choropleth display were unlikely to choose correctly, unless viewing a NW-SE trend model.
@@
   knitr::kable(., format = "latex", booktabs = TRUE,
+    linesep = c("", "\\addlinespace", "", "\\addlinespace",""),
     caption = "The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
@@
 The most common choice made by participant was clusters, this response was expected when participants viewed the Hexagon display of the All Cities and Three Cities distributions.
-
-## Contributors
-
-```{r contributors, fig.cap = "The probablity of detection acheived by the contributors in each group is shown by the points.
-Group B has a larger range and a smaller inter-quartile range.
-Group A and  both had 3 people who did not find any of the data maps in the displays."}
-# Check contributor performance
-contribs <- d %>% group_by(group, contributor) %>% 
-  # pdetect measures the aggregated accuracy of the choices
-  summarise(pdetect = mean(detect, na.rm = TRUE))
-
-# Plot performance
-contribs %>% ggplot(aes(x = group, y = pdetect)) + 
-  geom_boxplot() + 
-  geom_jitter(width = 0.1, height = 0, alpha = 0.7) + 
-  ylab("Detection rate") + 
-  ylim(0,1)
-```
 
@@
 
+Replicate 3 of the All Cities distribution is shown in Figures .
+The same data set is shown in both displays, the difference is the land area of each SA3 is coloured in the choropleth and the hexagon representing the SA3 is coloured in the Hexagon Tile Map.
+Many maps in the Choropleth lineup (a) are coloured yellow, two are half light blue, and two are obviously blue.
+Only one of the maps looks red.
+
 Lineups were created using the Australian Statistical Areas at Level 3.
@@
   ylim(c(0,1))
+```
+
+## Contributor Performance
+
+```{r contributors, fig.cap = "The probablity of detection acheived by the contributors in each group is shown by the points.
+Group B has a larger range and a smaller inter-quartile range.
+Group A and  both had 3 people who did not find any of the data maps in the displays."}
+# Check contributor performance
+contribs <- d %>% group_by(group, contributor) %>% 
+  # pdetect measures the aggregated accuracy of the choices
+  summarise(pdetect = mean(detect, na.rm = TRUE))
+
+# Plot performance
+contribs %>% ggplot(aes(x = group, y = pdetect)) + 
+  geom_boxplot() + 
+  geom_jitter(width = 0.1, height = 0, alpha = 0.7) + 
+  ylab("Detection rate") + 
+  ylim(0,1)
 ```

### 2020-01-11 paper/paper.Rmd
references added

@@
 citation_package: biblatex
+header-includes: \usepackage{graphicx}
 ---
@@
   message = FALSE,
-  cache = FALSE)
+  cache = FALSE,
+  dpi = 300)
 ```
@@
 The most common display for spatial data is the choropleth map.
-The choropleth map is the common display used to present aggregated statistics for geographic units such as the population.
+It is used to present aggregated statistics for geographic units such as the population.
 Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic.
-However, using a choropleth map base introduces biases when considering population related distributions.
+However, using a choropleth map base introduces biases when considering population related distributions [@CBATCC].
 Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
@@
 When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
-This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention.
-An alternative display can be used to effectively communicate a spatial distribution for a set of heterogeneous areas.
+This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention [@CTTMB].
+An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas [@NISCC].
 This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
@@
 The transformation begins with a choropleth map, and the values of a statistic such as population, for each geographic unit.
-There are several algorithms for transformation; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
+There are several algorithms for transformation [@ACTUC], [@CBATCC]; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
 <!-- Why not a cartogram-->
@@
 Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units.
-The non-contiguous cartgoram method keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics.
+The non-contiguous cartgoram method [@NAC] keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics.
 This method disconnects areas when shrinking boundaries, and breaks the spatial relationship between areas.
 However, the empty space created emphasises the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
-The Dorling cartogram is another method that does not retain the boundaries of geographic units.
+The Dorling cartogram [@ACTUC] is another method that does not retain the boundaries of geographic units.
 Each unit becomes one circle on the cartogram display; the circles are sized according to the value of a the statistic, such as population.
 The neighbour relationships can be illustrated by connecting the boundaries of the circles.
-These cartogram methods all allow two variables to be shown in the single display.
+A similar approach was pioneered by Raisz [-@RSCW], using rectangles that tile to align borders of neighbours [@CDWCS].
+These cartogram methods all allow two variables to be shown in the single display. these methods are discussed further in XXX cite review paper
 
@@
 This will generate twenty-four lineups (twelve lineups of geographic maps, and twelve lineups of hexagon tile maps). Participants evaluated twelve lineups, siz of each map type.
-For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants. The design is outlined in \@ref(tab:exp-design).
+For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants. The design is outlined in \ref{tab:exp-design}.
 
@@
     linesep = c("", "", "\\addlinespace"),
-    caption = "The experimental design results in the following allocation of replicate data sets within each trend model to groups A and B.") %>% kable_styling("striped") %>% 
+    caption = "The experimental design results in the following allocation of replicate data sets within each trend model to groups A and B.") %>% kable_styling(bootstrap_options = "hold_position") %>%
   collapse_rows(., columns = 1, custom_latex_hline = c(1:3))
@@
 Demographics were collected regarding the study participants:
+
  - Gender (female / male / other),
@@
 Three questions were asked regarding each display:
+
  - Plot choice
@@
 For each of the 12 lineup displays the researchers calculated:
+
  - accuracy: the proportion of subjects who detected the data plot
@@
 
-Figure \ref{fig:detection_compare} displays the average detection rates by type of plot, separately for each trend model.
+Figure \ref{fig:detect-compare} displays the average detection rates for the two types of plot, separately for each trend model.
 Evaluations on the same data set are connected by a line segment.
@@
 Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup.
-The points for the same data set shown in a choroleth or haxgon tile map display are linked to show the difference in the detection rate."}
+The points for the same data set shown in a choroleth or haxgon tile map display are linked to show the difference in the detection rate.", fig.height=4}
 # Detectability rate for each lineup (image)
@@
 ggplot(d_smry, aes(x=type, y=pdetect, colour = trend)) +
-  geom_point(size = 3) +  
+  geom_point(size = 2) +  
   geom_line(size = 1, aes(group = replicate)) +  
@@
 d %>% group_by(type, trend) %>%
-  summarise(m = round(mean(detect),3),
-    std.dev = paste0("(", as.character(round(sd(detect),3)),")")) %>% 
+  summarise(m = round(mean(detect),2),
+    std.dev = round(sd(detect),2)) %>% 
+  mutate(std.dev = ifelse(std.dev == 0.5, "(0.50)", paste0("(", std.dev, ")"))) %>% 
   gather(stat, value, m, std.dev) %>% 
@@
 
-Table \ref{detect-glmer1} is a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on detection rate.
-The results support the summary from Figure \@ref{detect-compare}.
-All terms are statistically significant.
-Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
-Detection rate is lower for the Three Cities and All Cities, than the NW-SE group.
-The hexagon tile map has a substantially higher detection rate than the choropleth for Three Cities and All Cities.
-XXX Put a number for each of these.
-
 ```{r detect-glmer1, results="asis"}
@@
 
-glmer_terms <- c("Intercept", "Hex.", "Three Cities", "All Cities", 
-  "Hex:Three Cities", "Hex:All Cities")
+glmer_terms <- c("Intercept", "Hex.", "Three Cities", "All Cities", "Hex:Three Cities", "Hex:All Cities")
+
+detection_rates <- tidy(glmer1) %>%
+  mutate(detection_rates = round(exp(estimate)/(1+exp(estimate)),2)) %>%
+  select(term, estimate, detection_rates) %>% pull(detection_rates)
 
@@
   mutate_at(.vars = c("estimate", "std.error"), round, 2) %>% 
-  mutate(p.value = format(p.value, 2)) %>% 
+  mutate(p.value = round(p.value, digits=2)) %>% 
   rowwise() %>%
-  mutate(estimate = case_when(
-  p.value <= 0.001 ~ paste0(estimate,"$^{***}$"),
-  p.value <= 0.01 ~ paste0(estimate, "$^{** }$"),
-  p.value <= 0.05 ~ paste0(estimate, "$^{*  }$"),
-  p.value <= 0.01 ~ paste0(estimate, "$^{.  }$"),
-  TRUE ~ paste0(estimate))) %>%
+  mutate(sig = case_when(
+  p.value <= 0.001 ~ "$^{***}$",
+  p.value <= 0.01 ~  "$^{**}$",
+  p.value <= 0.05 ~  "$^{*}$",
+  p.value <= 0.01 ~  "$^{.}$",
+  TRUE ~ "$^{ }$")) %>%
   ungroup() %>% 
@@
   select(Term = term, 
-    Estimate = estimate, 
+    Est. = estimate, 
+    Sig. = sig,
     `Std. Error` = std.error, 
-    `P value` = p.value) %>% 
-  knitr::kable(format = "latex", escape = FALSE, align= "rclrr", 
+    `P val` = p.value) %>% 
+  knitr::kable(format = "latex", escape = FALSE, align= "rrlrr", 
     booktabs = T, linesep = c("", "\\addlinespace", "", "\\addlinespace", ""), 
@@
 
-<!-- The model summary in Table \ref{tab:detect-glmer1} shows that the predicted log odds of the detection rate is 0.46 times that of the choropleth lineups, for the lineups of hexagon tile map. 
-The baseline trend model used is the NW-SE trend, the detection rate is expected to decrease comparatively for choropleth displays of the Three Cities and All Cities trends.
-However, when the interaction is considered the detection rate is expected to increase for the Three Cities and All Cities trends shows in the Hexagon tile map display.
--->
+Table \ref{tab:detect-glmer1} is a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on detection rate.
+The results support the summary from Figure \ref{fig:detect-compare}.
+All terms are statistically significant.
+Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
+For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to `r round(exp(0.461+0.0220)/(1+exp(0.461+0.0220)), 2)` from `r round(exp(0.0220)/(1+exp(0.0220)),2)` for choropleths.
+
+When a choropleth map display is used, the predicted detection rate for the Three Cities trend, `r round(exp(0.0220-3.43)/(1+exp(0.0220-3.43)),2)`, is extremely low, especially compared to  the NW-SE trend.
+When the All Cities trend is presented in a choropleth display the predicted probability of detection is `r round(exp(0.0220-1.35)/(1+exp(0.0220-1.35)),2)`.
+The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend `r round(exp(0.461+0.0220-3.43+2.46)/(1+exp(0.461+0.0220-3.43+2.46)),2)` and All Cities trend `r round(exp(0.461+0.0220-1.35+1.17)/(1+exp(0.461+0.0220-1.35+1.17)),2)`.
 
@@
 There is also very little difference in evaluation time whether the data plot was detected or not.
-
-<!-- The amount of time taken for a participants to submit a response is explored. 
-The time considered was the amount of time it took for a participant to submit their choice of plot, the reason for their choice, and the perceived difficulty of the choice.
-The time was taken when each participant hit "Next".
-
-The relationship between time taken to submit, and the correct detection by the participant of the real data display in a lineup is considered in Figure \ref{fig:hist-height}.
-The bimodal distributions are similar across the type of display and the trend model hidden in the real data plot.
-The hexagon map displays have a peak for the group that took up to 5 seconds to submit a response.
-When viewing a choropleth map display, the second peak occured at around 20 seconds.
-The longest a participant took to respond was 60 seconds.
--->
-
-```{r hist-height,  eval=FALSE, fig.cap = "Six histograms show the distribution of the time taken to submit a response for each combination of trend and type of display.
-The time taken to evaluate each display is broken into five second windows.
-The height of the histogram bars show how many evaulations were submitted within each time window.
-The orange regions of the bars show the amount of correct detections, and the green regions are the amount of incorrect detections."}
-ggplot(d %>% rename(Detected = detect_f), 
-  aes(x = time_taken, fill = Detected, group = Detected)) + 
-  scale_fill_manual(values = detect_colours) +
-  geom_histogram(binwidth = 5, boundary = 0) +
-  facet_grid(type ~ trend) + 
-  theme(legend.position = "bottom") +
-  labs(x = "Time taken (Seconds)", y = "Amount of evaluations")
-```
-
-```{r hist-fill,  eval=FALSE, fig.cap = "The time taken to evaluate each display is broken into five second windows.
-The height of the histogram bars show the proportion of evaulations that were submitted within each time window."}
-ggplot(d %>% rename(Detected = detect_f), 
-  aes(x = time_taken, fill = Detected, group = Detected)) +  
-  scale_fill_manual(values = detect_colours) +
-  geom_histogram(binwidth = 5, boundary = 0, position = "fill") +
-  facet_grid(type ~ trend) +
-  labs(x = "Time taken (Seconds)", y = "Proportion of evaluations")
-
-ggplot(d, aes(x = time_taken, colour = detect_f, group = detect_f)) +  
-  scale_fill_manual(values = detect_colours) +
-  geom_freqpoly(binwidth = 3) +
-  facet_grid(type ~ trend) +
-  scale_fill_manual(values = detect_colours) +
-  labs(x = "Time taken (Seconds)", y = "Amount of evaluations") +
-  guides(colour = FALSE)
-```
 
@@
 
-<!-- The proportion of correct and incorrect responsesis shown by the width used to distribute the points horizontally.
-Each point is randomly placed, but regions with more points require points to be placed further from center.
-For the NW-SE distribution, it is equally likely that quick responders will be correct or incorrect.
-It is more likely that participants picked the correct response if they took longer to respond.
-For the Choropelth
-However, these quick responders were likely to be either correct or incorrect. The quick responders viewing a choropleth display were unlikely to choose correctly, unless viewing a NW-SE trend model.
-
-The choropleth map displays that included a distribution of Three Cities was very difficult for participants. 
--->
-
-```{r time-lmer1, eval = FALSE, results="asis"}
-# Mixed effects models
-d %>% mutate(ln_time = time_taken) %>% 
-time_lmer1 <- glmer(ln_time ~ type*trend + (1|contributor),data = .)
-
-lmer_terms <- c("Intercept", "Hex.", "Three Cities", "All Cities", 
-  "Hex:Three Cities", "Hex:All Cities")
-
-tidy(time_lmer1)
-```
-
 ## Certainty
@@
 Participants were more likely to choose a high certainty when considering a Choropleth map.
-The mid value of 3 was the default certainty, it was chosen most for the Hexagon tile map displays."}
+The mid value of 3 was the default certainty, it was chosen most for the Hexagon tile map displays.", fig.height=5}
 d <- d %>% 
@@
   geom_bar() + facet_grid(type ~ trend) +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom") + xlab("Level of certainty")
 ```
@@
 ```{r reason, results = "asis"}
-
 # Qualitative analysis of reason
@@
   count(reason) %>% 
-  mutate(prop = round(n/sum(n), 3), r_prop = paste0(reason, ":", prop)) %>% 
+  mutate(prop = round(n/sum(n), 2), r_prop = paste0(reason, ":", prop)) %>% 
   top_n(1, n) %>% summarise(reasons = paste(reason, collapse=", ")) %>% 
@@
     caption = "The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
-The facets show whether or not the choice was correct.") %>% kable_styling("striped")
-#%>% 
-#  collapse_rows(., columns = 1, custom_latex_hline = c(1:2, 3:4))
+The facets show whether or not the choice was correct.") %>%
+  #kable_styling(bootstrap_options = "hold_position") %>% 
+  collapse_rows(., columns = 1)
 ```
@@
 The numbers differentiate the replicates of each trend model and type of map display.
-Participants were able to select 0 to indicate they did not want to choose a map.", fig.height = 12, fig.width=10}
+Participants were able to select 0 to indicate they did not want to choose a map."}
 d %>% 
@@
 
-The demonstrative images of the `shinydashboard` web application display the demographic and consent page in Figure \ref{fig:survey1}.
+The demonstrative images of the `shinydashboard` web application display the demographic and consent page in Figure
+\ref{fig:survey_demogs}.
 
 <!--
+
 \begin{figure}[!t] 
 \centering 
-\includegraphics[width=2.5in]{figures/survey_demogs.png}
+\includegraphics[width=6in]{figures/survey_demogs.png}
 \caption{The demographics questions tab of the shinydashboard survey application.}
@@
 \centering 
-\includegraphics[width=2.5in]{figures/survey_hex.png}
+\includegraphics[width=6in]{figures/survey_hex.png}
 \caption{An example of the hexagon tile map lineup shown in the survey tab of the shinydashboard app.}
@@
 \centering 
-\includegraphics[width=2.5in]{figures/survey_choro.png}
+\includegraphics[width=6in]{figures/survey_choro.png}
 \caption{An example of the choropleth map lineup shown in the survey tab of the shinydashboard app.}

### 2020-01-11 paper/paper.tex
references added

@@
 
+\usepackage{longtable,booktabs}
 \usepackage{graphicx}
@@
 % Pandoc header
+\usepackage{graphicx}
 \usepackage{booktabs}
@@
 % Do not put math or special symbols in the title.
-\title{Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile
-Map for Communicating Cancer Statistics}
+\title{Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics}
 
@@
 \begin{abstract}
-Choosing a visualisation method may seem to be a simple task. The
-choropleth map display is commonly used for communicating spatial data.
-However, when used to communicate the spatial distribution of a
-statistic the sizes of areas can lead to midinterpretation of the
-distribution. The visualisation method used to present geospatial data
-will influence the information derived by map users. Choosing an
-alternative display will influence the communication of the
-distribution. The hexagon tile map is presented as an alternative
-display. Visual inference is used to measure the power of design. The
-choropleth is used as a comparison point. The hexagon tile map display
-is an effective visualisation for communicatin=g population related
-distributions. The hexagon tile map display also allowed identification
-of the geographic distribution with values monotonically decreasing from
-North West toward South East areas of Australia.
+Choosing a visualisation method may seem to be a simple task.
+The choropleth map display is commonly used for communicating spatial data.
+However, when used to communicate the spatial distribution of a statistic the sizes of areas can lead to midinterpretation of the distribution.
+The visualisation method used to present geospatial data will influence the information derived by map users.
+Choosing an alternative display will influence the communication of the distribution.
+The hexagon tile map is presented as an alternative display.
+Visual inference is used to measure the power of design.
+The choropleth is used as a comparison point.
+The hexagon tile map display is an effective visualisation for communicatin=g population related distributions.
+The hexagon tile map display also allowed identification of the geographic distribution with values monotonically decreasing from North West toward South East areas of Australia.
 \end{abstract}
@@
 
-This study contrasts the use of two displays for geospatial statistics,
-the traditional choropleth map and an alternative tessellated hexagon
-tile map. The choropleth map is the common choice for visualising
-aggregated statistics and is familiar because of common administrative
-boundaries. A hexagon tile map forgoes the familiar boundaries, instead
-representing each geographic unit as an equally sized hexagon. This
-alternative display is suggested for communicating distributions that
-relate to the population values or density of the population in each
-geographic unit. This study uses the lineup protocol for visual
-inference testing of the recognition of spatial distributions. The
-Australian Cancer Atlas explores spatial distributions of cancer
-incidence and the burden on Australian communities. The spatial
-distributions of the cancers explored in this atlas inspired the trend
-models presented to participants in this study.
+This study contrasts the use of two displays for geospatial statistics, the traditional choropleth map and an alternative tessellated hexagon tile map.
+The choropleth map is the common choice for visualising aggregated statistics and is familiar because of common administrative boundaries.
+A hexagon tile map forgoes the familiar boundaries, instead representing each geographic unit as an equally sized hexagon.
+This alternative display is suggested for communicating distributions that relate to the population values or density of the population in each geographic unit.
+This study uses the lineup protocol for visual inference testing of the recognition of spatial distributions.
+The Australian Cancer Atlas explores spatial distributions of cancer incidence and the burden on Australian communities.
+The spatial distributions of the cancers explored in this atlas inspired the trend models presented to participants in this study.
 
@@
 \hypertarget{the-australian-cancer-atlas}{%
-\subsection{The Australian Cancer
-Atlas}\label{the-australian-cancer-atlas}}
-
-The Australian Cancer Atlas is an online interactive web tool created to
-explore the burden of cancer on Australian communities. There are many
-cancer types to be explored individually or aggregated. The Atlas
-examines Australian communities at the Statistical Areas at Level 2
-(SA2) (``Australian Statistical Geography Standard (ASGS)''
-\protect\hyperlink{ref-abs2016}{2018}) used by the Australian Bureau of
-Statistics. Bayesian spatial smoothing was applied to integrate the
-values of neighbouring areas. Spatial smoothing protects the privacy and
-gives stability to the estimated amounts in each SA2. Users of the Atlas
-can explore the difference of the statistic of each SA2 from the
-Australian average, for both diagnoses (Standardised Incidence Rates)
-and excess deaths. It communicates the value of the statistic for each
-SA2 geographic unit through colour, by filling the areas using the
-diverging colour scheme ranging from dark blue to red. The Australian
-Cancer Atlas allows users to explore the patterns in the distributions
-of cancer statistics over the geographic space of Australia. It uses a
-choropleth map display and diverging colour scheme to draw attention to
-relationships between neighbouring areas.
+\subsection{The Australian Cancer Atlas}\label{the-australian-cancer-atlas}}
+
+The Australian Cancer Atlas is an online interactive web tool created to explore the burden of cancer on Australian communities. There are many cancer types to be explored individually or aggregated.
+The Atlas examines Australian communities at the Statistical Areas at Level 2 (SA2) (``Australian Statistical Geography Standard (ASGS)'' \protect\hyperlink{ref-abs2016}{2018}) used by the Australian Bureau of Statistics.
+Bayesian spatial smoothing was applied to integrate the values of neighbouring areas.
+Spatial smoothing protects the privacy and gives stability to the estimated amounts in each SA2.
+Users of the Atlas can explore the difference of the statistic of each SA2 from the Australian average, for both diagnoses (Standardised Incidence Rates) and excess deaths.
+It communicates the value of the statistic for each SA2 geographic unit through colour, by filling the areas using the diverging colour scheme ranging from dark blue to red.
+The Australian Cancer Atlas allows users to explore the patterns in the distributions of cancer statistics over the geographic space of Australia.
+It uses a choropleth map display and diverging colour scheme to draw attention to relationships between neighbouring areas.
 
@@
 \hypertarget{population-focussed-displays}{%
-\subsection{Population focussed
-displays}\label{population-focussed-displays}}
-
-Spatial visualisations communicate the distribution of statistics over
-geographic space. The most common display for spatial data is the
-choropleth map. The choropleth map is the common display used to present
-aggregated statistics for geographic units such as the population.
-Creating a choropleth map involves drawing the administrative boundaries
-and filling them with colour to communicate the value of the statistic.
-However, using a choropleth map base introduces biases when considering
-population related distributions. Many sets of Australian statistical
-areas have a large disparity between the smallest and largest units. The
-rural communities in Australia operate on a much larger geographic space
-than small inner-city communities. When a spatial distribution is
-related to the size of the areas, or the population density, the size of
-the regions can allow erroneous conclusions to be drawn about the state
-of the statistic over the entire population, when presenting the
-statistics on a geographic map base. This occurs as large regions filled
-with a consistent colour or pattern can draw the attention of map
-readers, and small regions are not paid equal attention. An alternative
-display can be used to effectively communicate a spatial distribution
-for a set of heterogeneous areas. This work aims to show that a hexagon
-tile map display is a viable alternative to the geographic map base for
-presenting population statistics.
-
-A choropleth map is not the only display that can be used for presenting
-geospatial data. Alternative maps include various cartograms and
-tessellated tile maps. They allow other variables to be incorporated in
-the display to highlight the statistical values of various geographic
-areas.
-
-A cartogram transforms the geographic map base. The transformation
-begins with a choropleth map, and the values of a statistic such as
-population, for each geographic unit. There are several algorithms for
-transformation; they involve shifting the boundaries of geographic
-units, using the value of the statistic to increase or decrease the area
-taken by the geographic unit on the map. The changes to the boundaries
-result in cartograms that accurately communicate population by map area
-for each of the geographic units. The transformation will keep
-boundaries of neighbouring areas connected, but the result is unfamiliar
-shapes for each geographic unit.
-
-Alternative displays make the trade off between familiar shapes and
-representation of variables using the area of geographic units. The
-non-contiguous cartgoram method keeps the shapes of geographic units
-intact, and change the size of the shape to communicate the values of
-statistics. This method disconnects areas when shrinking boundaries, and
-breaks the spatial relationship between areas. However, the empty space
-created emphasises the comparative density of the statistic, the
-difference between the statistic and the amount of land for each
-geographic unit. The Dorling cartogram is another method that does not
-retain the boundaries of geographic units. Each unit becomes one circle
-on the cartogram display; the circles are sized according to the value
-of a the statistic, such as population. The neighbour relationships can
-be illustrated by connecting the boundaries of the circles. These
-cartogram methods all allow two variables to be shown in the single
-display.
+\subsection{Population focussed displays}\label{population-focussed-displays}}
+
+Spatial visualisations communicate the distribution of statistics over geographic space.
+The most common display for spatial data is the choropleth map.
+It is used to present aggregated statistics for geographic units such as the population.
+Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic.
+However, using a choropleth map base introduces biases when considering population related distributions (Kocmoud and House \protect\hyperlink{ref-CBATCC}{1998}).
+Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
+The rural communities in Australia operate on a much larger geographic space than small inner-city communities.
+When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
+This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention (Griffin \protect\hyperlink{ref-CTTMB}{1980}).
+An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas (Dent \protect\hyperlink{ref-NISCC}{1972}).
+This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
+
+A choropleth map is not the only display that can be used for presenting geospatial data.
+Alternative maps include various cartograms and tessellated tile maps. They allow other variables to be incorporated in the display to highlight the statistical values of various geographic areas.
+
+A cartogram transforms the geographic map base.
+The transformation begins with a choropleth map, and the values of a statistic such as population, for each geographic unit.
+There are several algorithms for transformation (Dorling \protect\hyperlink{ref-ACTUC}{2011}), (Kocmoud and House \protect\hyperlink{ref-CBATCC}{1998}); they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
+The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units.
+The transformation will keep boundaries of neighbouring areas connected, but the result is unfamiliar shapes for each geographic unit.
+
+Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units.
+The non-contiguous cartgoram method (Olson \protect\hyperlink{ref-NAC}{1976}) keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics.
+This method disconnects areas when shrinking boundaries, and breaks the spatial relationship between areas.
+However, the empty space created emphasises the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
+The Dorling cartogram (Dorling \protect\hyperlink{ref-ACTUC}{2011}) is another method that does not retain the boundaries of geographic units.
+Each unit becomes one circle on the cartogram display; the circles are sized according to the value of a the statistic, such as population.
+The neighbour relationships can be illustrated by connecting the boundaries of the circles.
+A similar approach was pioneered by Raisz (\protect\hyperlink{ref-RSCW}{1963}), using rectangles that tile to align borders of neighbours (Monmonier \protect\hyperlink{ref-CDWCS}{2005}).
+These cartogram methods all allow two variables to be shown in the single display. these methods are discussed further in XXX cite review paper
 
@@
 \includegraphics{paper_files/figure-latex/liver-1.pdf}
-\caption{The smoothed average of liver cancer diagnoses for Australian
-males. The divering colour scheme shows dark blue areas with much lower
-than average diagnoses, yellow areas with diagnoses around the
-Australian average, orange with above average and red shows diagnoses
-much higher than average.}
+\caption{\label{fig:liver}The smoothed average of liver cancer diagnoses for Australian males.
+The divering colour scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average.}
 \end{figure}
 
-Australia is an extreme case of heterogenous geographic units, with
-large difference between the smallest and largest geographic units
-across various granularities. To communicate information regarding the
-small inner-city geographic units of Australian cities an alternative
-display must be employed. This will emphasise the value of the statistic
-for areas with high population. Figure \ref{fig:liver} shows the
-distribution of the smoothed average amount of Liver cancer diagnoses
-for Australian Males from 2005-2014. These inner-city areas are not
-visible on the choropleth map (a). The hexagon tile map (b) shows orange
-hexagons for the inner-city SA2s with higher than average levels of
-diagnoses in the capital cities of Melbourne and Sydney. The northern
-Queensland, and Northern Territory SA2's with higher than average rates
-are still visible but use less map space on the hexagon tile map. There
-are still many light blue areas in both displays.
+Australia is an extreme case of heterogenous geographic units, with large difference between the smallest and largest geographic units across various granularities.
+To communicate information regarding the small inner-city geographic units of Australian cities an alternative display must be employed.
+This will emphasise the value of the statistic for areas with high population.
+Figure \ref{fig:liver} shows the distribution of the smoothed average amount of Liver cancer diagnoses for Australian Males from 2005-2014.
+These inner-city areas are not visible on the choropleth map (a).
+The hexagon tile map (b) shows orange hexagons for the inner-city SA2s with higher than average levels of diagnoses in the capital cities of Melbourne and Sydney.
+The northern Queensland, and Northern Territory SA2's with higher than average rates are still visible but use less map space on the hexagon tile map.
+There are still many light blue areas in both displays.
 
@@
 
-The hexagon tile map is suggested as an alternative display. To test the
-effectiveness of these displays there is a formal testing framework.
-Visual inference considers the communication of data or data summaries
-through visualisations. It considers these visualisations to be visual
-statistics, with observable features.
-
-Classical statistical inference involves hypothesis testing, the process
-of rejecting a null hypothesis in favour of an alternative. This
-approach requires appropriate data, with the appropriate distributions
-and their assumptions. The lineup protocol was formalised as a test for
-the effectiveness of a visualisation. Rather than use classical
-statistical tests, human participants are tasked with finding the
-display that shows structure between the variables. If the structure is
-not detected, then it is not significantly different from the null data.
+The hexagon tile map is suggested as an alternative display.
+To test the effectiveness of these displays there is a formal testing framework.
+Visual inference considers the communication of data or data summaries through visualisations.
+It considers these visualisations to be visual statistics, with observable features.
+
+Classical statistical inference involves hypothesis testing, the process of rejecting a null hypothesis in favour of an alternative.
+This approach requires appropriate data, with the appropriate distributions and their assumptions.
+The lineup protocol was formalised as a test for the effectiveness of a visualisation.
+Rather than use classical statistical tests, human participants are tasked with finding the display that shows structure between the variables.
+If the structure is not detected, then it is not significantly different from the null data.
 
@@
 
+\begin{itemize}
+\item
   Null hypothesis: There is NO relationship between the variables,
+\item
   Alternative hypothesis: There is a relationship between the variables.
-
-To test these hypotheses, the line up protocol randomly places a
-``guilty'' data visualisation in a lineup of ``innocents''. Where the
-guilty data set contains structure, and the innocents data sets do not.
-In a grid of visualisations, an observer is asked to pick the display
-that is most different, if they select the data set containing
-structure, they have identified the guilty hidden within the innocents
-(Hofmann et al. \protect\hyperlink{ref-GTPCCD}{2012}). The guilty data
-is identified as different from the innocent data with probability
-\(1/m\), where \(m\) is the number of null plots plus 1 to account
-account for the guilty data set. When the guilty data set is chosen, the
-null hypothesis that it was innocent is rejected with a \(1/m\) chance
-or type I error of being wrong.
-
-The lineup protocol can be used in a variety of testing scenarios for
-visualisations. Wickham et al. (\protect\hyperlink{ref-GIIV}{2010})
-suggest the choropleth map for testing spatial structure in a data set.
-The lineup protocol allows for flexibility in the definition of null
-data. In the case of spatial visualisations it is likely that neighbours
-are related to some degree. To account for this, null data sets can be
-generated by sampling from a known model that accounts for spatial
-covariance.
-
-To contrast the effectiveness of two displays, the data set of null data
-plots with a hidden real data plot can be produced using the different
-plot designs. The time taken by participants to evaluate the same data
-in the different displays can be compared. Their accuracy in detecting
-the real data plot can also be calculated and contrasted.
+\end{itemize}
+
+To test these hypotheses, the line up protocol randomly places a ``guilty'' data visualisation in a lineup of ``innocents''.
+Where the guilty data set contains structure, and the innocents data sets do not.
+In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the innocents (Hofmann et al.
+\protect\hyperlink{ref-GTPCCD}{2012}).
+The guilty data is identified as different from the innocent data with probability \(1/m\), where \(m\) is the number of null plots plus 1 to account account for the guilty data set.
+When the guilty data set is chosen, the null hypothesis that it was innocent is rejected with a \(1/m\) chance or type I error of being wrong.
+
+The lineup protocol can be used in a variety of testing scenarios for visualisations.
+Wickham et al.
+(\protect\hyperlink{ref-GIIV}{2010}) suggest the choropleth map for testing spatial structure in a data set.
+The lineup protocol allows for flexibility in the definition of null data.
+In the case of spatial visualisations it is likely that neighbours are related to some degree.
+To account for this, null data sets can be generated by sampling from a known model that accounts for spatial covariance.
+
+To contrast the effectiveness of two displays, the data set of null data plots with a hidden real data plot can be produced using the different plot designs.
+The time taken by participants to evaluate the same data in the different displays can be compared. Their accuracy in detecting the real data plot can also be calculated and contrasted.
 
@@
 
-This study aimed to answer two key questions around the presentation of
-spatial distributions:
+This study aimed to answer two key questions around the presentation of spatial distributions:
 
@@
 \item
-  Are spatial disease trends, that impact highly populated small areas,
-  detected with higher accuracy when viewed in a hexagon tile map
-  display?
-\item
-  Are people faster in detecting spatial disease trends, that impact
-  highly populated small areas, when using a hexagon tile map display?
+  Are spatial disease trends, that impact highly populated small areas, detected with higher accuracy when viewed in a hexagon tile map display?
+\item
+  Are people faster in detecting spatial disease trends, that impact highly populated small areas, when using a hexagon tile map display?
 \end{enumerate}
 
-Additional considerations when completing this experimental task
-included exploration of the difficulty experienced by participants, and
-the certainty they felt about their decision.
-
-The mean of the detection rate for choropleth map, denoted as \(\mu_C\),
-and the hexagon tile maps, \(\mu_H\) will be contrasted. This leads to
-the following one sided hypothesis:
-
-\(H_0\) : \(\mu_H\) = \(\mu_C\) \(H_a\) : \(\mu_H\) \textgreater{}
-\(\mu_C\)
-
-The detection rate \(\hat\pi\) is calculated as the amount of people
-that made the choice of plot that contained the real data, out of the
-participants who saw data plot in the lineup of the null data plots.
-
-The difference in the detection rates for the two displays will be
-compared using a two sample unpaired t-test.
+Additional considerations when completing this experimental task included exploration of the difficulty experienced by participants, and the certainty they felt about their decision.
+
+The mean of the detection rate for choropleth map, denoted as \(\mu_C\), and the hexagon tile maps, \(\mu_H\) will be contrasted. This leads to the following one sided hypothesis:
+
+\(H_0\) : \(\mu_H\) = \(\mu_C\)
+\(H_a\) : \(\mu_H\) \textgreater{} \(\mu_C\)
+
+The detection rate \(\hat\pi\) is calculated as the amount of people that made the choice of plot that contained the real data, out of the participants who saw data plot in the lineup of the null data plots.
+
+The difference in the detection rates for the two displays will be compared using a two sample unpaired t-test.
 
@@
 
-Participants were recruited for a survey style task to test the
-effectiveness of the hexagon tile map display. It was expected that the
-participants were uninvolved judges that had no prior knowledge of the
-data, to avoid discrimination or advantages. The Figure-Eight crowd
-source platform was used to advertise the survey to potential
-participants that had acheived level 2 or level 3 on the Figure-Eight
-Platform. The participants were chosen as they have experience with
-survey tasks that involve evaluating images. They participants on the
-platform are also required to be at least 18 years old.
-
-Participants were able to choose to participate by selecting this task
-from the list of tasks available to them. There were 95 participants
-involved in the study. All of these participants read the introductory
-materials and viewed example questions before proceeding to the survey.
-Each participant was trained using three test displays orienting them to
-the evaluation task, these displays are shown in supplementary materials
-section regarding \protect\hyperlink{training}{training}. All
-participants who volunteered to take part were compensated for their
-time via the payment system of Figure-Eight.
-
-Participants were allocated to either group A or group B when they
-proceeded to the survey web application, hosted externally from the
-Figure-Eight website.
+Participants were recruited for a survey style task to test the effectiveness of the hexagon tile map display.
+It was expected that the participants were uninvolved judges that had no prior knowledge of the data, to avoid discrimination or advantages.
+The Figure-Eight crowd source platform was used to advertise the survey to potential participants that had acheived level 2 or level 3 on the Figure-Eight Platform.
+The participants were chosen as they have experience with survey tasks that involve evaluating images. They participants on the platform are also required to be at least 18 years old.
+
+Participants were able to choose to participate by selecting this task from the list of tasks available to them.
+There were 95 participants involved in the study.
+All of these participants read the introductory materials and viewed example questions before proceeding to the survey.
+Each participant was trained using three test displays orienting them to the evaluation task, these displays are shown in supplementary materials section regarding \protect\hyperlink{training}{training}.
+All participants who volunteered to take part were compensated for their time via the payment system of Figure-Eight.
+
+Participants were allocated to either group A or group B when they proceeded to the survey web application, hosted externally from the Figure-Eight website.
 
@@
 
-The variables that were changed between groups were the type of plot
-shown and the trend model.
-
-The twenty-four lineup displays were created by a combination of map
-type, and spatial trend model. This set of displays was split into a
-collection of twelve displays for Group A and twelve displays for Group
-B.
-
-Each participant was randomly allocated to either Group A or Group B
-when they begun the survey. This resulted in 42 participants allocated
-to Group A, and 53 participants allocated to Group B.
+The variables that were changed between groups were the type of plot shown and the trend model.
+
+The twenty-four lineup displays were created by a combination of map type, and spatial trend model.
+This set of displays was split into a collection of twelve displays for Group A and twelve displays for Group B.
+
+Each participant was randomly allocated to either Group A or Group B when they begun the survey. This resulted in 42 participants allocated to Group A, and 53 participants allocated to Group B.
 
@@
 \item
-  Trend: \emph{Locations in three population centres, Locations in
-  multiple population centres, South-East to North-West}
+  Trend: \emph{Locations in three population centres, Locations in multiple population centres, South-East to North-West}
 \end{itemize}
 
-Each Group did not see the same data for both map types. Four simulated
-sets of data were generated for each treatment. This will generate
-twenty-four lineups (twelve lineups of geographic maps, and twelve
-lineups of hexagon tile maps). Participants evaluated twelve lineups,
-siz of each map type. For each of the six geographic displays and six
-hexagon displays, two of each trend model were shown to participants.
+Each Group did not see the same data for both map types. Four simulated sets of data were generated for each treatment.
+This will generate twenty-four lineups (twelve lineups of geographic maps, and twelve lineups of hexagon tile maps). Participants evaluated twelve lineups, siz of each map type.
+For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants. The design is outlined in \ref{tab:exp-design}.
 
@@
 
-\caption{\label{tab:exp_design}Experimental design.}
+\caption{\label{tab:exp-design}The experimental design results in the following allocation of replicate data sets within each trend model to groups A and B.}
 \centering
@@
 \midrule
-A & NW-SE & 1, 2 & 3, 4\\
-A & Three Cities & 1, 2 & 3, 4\\
-A & All Cities & 2, 4 & 1, 3\\
-B & NW-SE & 3, 4 & 1, 2\\
-B & Three Cities & 3, 4 & 1, 2\\
-\addlinespace
-B & All Cities & 1, 3 & 2, 4\\
+ & NW-SE & 1, 2 & 3, 4\\
+\cmidrule{2-4}
+ & Three Cities & 1, 2 & 3, 4\\
+\cmidrule{2-4}
+\multirow{-3}{*}{\raggedright\arraybackslash A} & All Cities & 2, 4 & 1, 3\\
+\cmidrule{1-4}
+ & NW-SE & 3, 4 & 1, 2\\
+\cmidrule{2-4}
+ & Three Cities & 3, 4 & 1, 2\\
+\cmidrule{2-4}
+\multirow{-3}{*}{\raggedright\arraybackslash B} & All Cities & 1, 3 & 2, 4\\
 \bottomrule
@@
 
-The variables measured as a result of the changes were the probability
-of detection each display and the time taken to submit responses. To
-measure the accuracy of the detections, the plot chosen for each lineup
-evaluated was compared to the position of the real spatial trend plot in
-the lineup. A correct result occurs when the chosen plot matches the
-position of the real plot, this was recorded in an additional binary
-variable; 1 = correct; 0 = incorrect. High efficiency occurs when a
-small amount of time is taken to evaluate each lineup. This will be
-measured as the numeric variable measuring the length of time taken to
-submit the answers to the evaluation of each line up.
+The variables measured as a result of the changes were the probability of detection each display and the time taken to submit responses.
+To measure the accuracy of the detections, the plot chosen for each lineup evaluated was compared to the position of the real spatial trend plot in the lineup.
+A correct result occurs when the chosen plot matches the position of the real plot, this was recorded in an additional binary variable; 1 = correct; 0 = incorrect.
+High efficiency occurs when a small amount of time is taken to evaluate each lineup.
+This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.
 
@@
 
-The lineup protocol allows a known model to be imposed on the null data
-set plots. The underlying spatial correlation model was created to
-provide spatial autocorrelation between neighbouring areas using the
-longitude and latitude values for the Statistical Areas.
-
-\[z = 1\] \[locations = longitude + latitude\]
-
-The null model imposed suggests that neighbours are related. The
-randomness imposed was smoothed to mirror the practice taken by the
-Australian Cancer Atlas. This smoothing allowed neighbours to be related
-to each other and show distributions similar to the Liver cancer
-distribution shown in \ref{fig:liver}.
-
-Spatially dependent data sets were simulated using the variogram model
-on the centroids of each geographic unit. Twelve simulations from the
-variogram model were created for each of the twelve lineups.
-
-In these 12 sets of data, each of the 144 maps were smoothed several
-times to replicate the spatial autocorrelation seen in cancer data sets
-presented in the Australian Cancer Atlas.
-
-For each of the 144 individual maps, the values attributed to each
-geographic area are rescaled to show a similar colour scale from deep
-blue to dark red within each map.
-
-A random location was selected for each set of lineup data. In this
-location, a trend model was overlaid on the null set of spatially
-correlated data. Each set of lineup data was used to produce a
-choropleth maps and hexagon tile maps. These matched pairs were split
-between Group A and Group B.
-
-Replicate 3 of the All Cities distribution is shown in
-\ref{fig:compare}. The same data set is shown in both displays, the
-difference is the land area of each SA3 is coloured in the choropleth
-and the hexagon representing the SA3 is coloured in the Hexagon Tile
-Map. Many maps in the Choropleth lineup (a) are coloured yellow, two are
-half light blue, and two are obviously blue. Only one of the maps looks
-red.
+The lineup protocol allows a known model to be imposed on the null data set plots.
+The underlying spatial correlation model was created to provide spatial autocorrelation between neighbouring areas using the longitude and latitude values for the Statistical Areas.
+
+\[z = 1\]
+\[locations = longitude + latitude\]
+
+The null model imposed suggests that neighbours are related.
+The randomness imposed was smoothed to mirror the practice taken by the Australian Cancer Atlas.
+This smoothing allowed neighbours to be related to each other and show distributions similar to the Liver cancer distribution shown in \ref{fig:liver}.
+
+Spatially dependent data sets were simulated using the variogram model on the centroids of each geographic unit.
+Twelve simulations from the variogram model were created for each of the twelve lineups.
+
+In these 12 sets of data, each of the 144 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas.
+
+For each of the 144 individual maps, the values attributed to each geographic area are rescaled to show a similar colour scale from deep blue to dark red within each map.
+
+A random location was selected for each set of lineup data.
+In this location, a trend model was overlaid on the null set of spatially correlated data.
+Each set of lineup data was used to produce a choropleth maps and hexagon tile maps. These matched pairs were split between Group A and Group B.
 
 \hypertarget{experiment-procudure-and-data-collection}{%
-\subsection{Experiment procudure and data
-collection}\label{experiment-procudure-and-data-collection}}
-
-The participant answered demographic questions and provided consent
-before evaluating the lineups.
-
-Demographics were collected regarding the study participants: - Gender
-(female / male / other), - Degree education level achieved (high school
-/ bachelors / masters / doctorate / other), - Age range (18-24 / 25-34 /
-35-44 / 45-54 / 55+ / other) - Lived at least for one year in Australia
-(Yes / No )
-
-Participants then moved to the evaulation phase. The set of images
-differed for Group A and Group B. After being allocated to a group, each
-individual was shown the 12 displays in randomised order.
-
-Three questions were asked regarding each display: - Plot choice -
-Reason - Difficulty
-
-After completing the 12 evaluations, the participants were asked to
-submit their responses.
-
-Data was collected through a web application containing the online
-survey. Each participant used the internet to access the survey. The
-data collection took place using a secure link between the survey web
-application and the googlesheet used to store results. The application
-would first connect to the googlesheet using the googlesheets (Bryan and
-Zhao \protect\hyperlink{ref-sheets}{2018}) R package, and interacted
-again at the completion of the survey by adding the participant's
-responses to the 12 displays as 12 rows of data in the googlesheet.
+\subsection{Experiment procudure and data collection}\label{experiment-procudure-and-data-collection}}
+
+The participant answered demographic questions and provided consent before evaluating the lineups.
+
+Demographics were collected regarding the study participants:
+
+\begin{itemize}
+\tightlist
+\item
+  Gender (female / male / other),
+\item
+  Degree education level achieved (high school / bachelors / masters / doctorate / other),
+\item
+  Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
+\item
+  Lived at least for one year in Australia (Yes / No )
+\end{itemize}
+
+Participants then moved to the evaulation phase.
+The set of images differed for Group A and Group B.
+After being allocated to a group, each individual was shown the 12 displays in randomised order.
+
+Three questions were asked regarding each display:
+
+\begin{itemize}
+\tightlist
+\item
+  Plot choice
+\item
+  Reason
+\item
+  Difficulty
+\end{itemize}
+
+After completing the 12 evaluations, the participants were asked to submit their responses.
+
+Data was collected through a web application containing the online survey.
+Each participant used the internet to access the survey.
+The data collection took place using a secure link between the survey web application and the googlesheet used to store results.
+The application would first connect to the googlesheet using the googlesheets (Bryan and Zhao \protect\hyperlink{ref-sheets}{2018}) R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
 
@@
 
-The choropleth map was used as the comparative visualisation for
-presenting the lineups (Majumder, Hofmann, and Cook
-\protect\hyperlink{ref-VVSIALM}{2013}) as this is the common display for
-spatial cancer data. Geographic distributions usually have some degree
-of spatial autcorrelation between neighbours. This feature was
-incorporated in all maps shown in the lineup displays, the map that
-contained the trend feature shown in only one set of data was also
-affected by spatial autocorrelation. A line up protocol was implemented
-to arrange \(N\) maps in each display. A reasonable amount of null plots
-\(N-1\) in the lineup was chosen to ensure the real data map was well
-hidden. A reasonable number of plots to show in each lineup, \(N = 12\)
-was chosen to not overwhelm participants due to the detailed choropleth
-maps of Australian SA3 areas.
-
-The hypotheses for each lineup are \(H_0\) : All plots look the same
+The choropleth map was used as the comparative visualisation for presenting the lineups (Majumder, Hofmann, and Cook \protect\hyperlink{ref-VVSIALM}{2013}) as this is the common display for spatial cancer data.
+Geographic distributions usually have some degree of spatial autcorrelation between neighbours.
+This feature was incorporated in all maps shown in the lineup displays, the map that contained the trend feature shown in only one set of data was also affected by spatial autocorrelation.
+A line up protocol was implemented to arrange \(N\) maps in each display.
+A reasonable amount of null plots \(N-1\) in the lineup was chosen to ensure the real data map was well hidden.
+A reasonable number of plots to show in each lineup, \(N = 12\) was chosen to not overwhelm participants due to the detailed choropleth maps of Australian SA3 areas.
+
+The hypotheses for each lineup are
+\(H_0\) : All plots look the same
 \(H_a\) : One plot looks different to the other plots
 
-The same data was visualised on a choropleth map, and on a hexagon tile
-map, however in this study the participants only saw one of these two
-displays. The accuracy and times taken were aggregated for Groups and.
-Comparing the results of participants who see the choropleth to those
-who see a hexagon tile map will show that population related
-distributions are spotted more frequently in a hexagon tile map display.
-
-Let \(n\) be the number of independent observers and \(x_i\) the number
-of observers who picked plot \(i\), \(i = \{1,...,m\}\)
+The same data was visualised on a choropleth map, and on a hexagon tile map, however in this study the participants only saw one of these two displays.
+The accuracy and times taken were aggregated for Groups and.
+Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.
+
+Let \(n\) be the number of independent observers and \(x_i\) the
+number of observers who picked plot \(i\), \(i = \{1,...,m\}\)
 
 Then \(x_i, x_2, ..., x_m\) follows a multinomial
-distribution\(Mult_{\pi_1, \pi_2, ...., \pi_m}(x_i, x_2, ..., x_m)\)
-with \(\sum_i \pi_i = 1\), where \(\pi_i\) is the probability that plot
-\(i\) is picked by an observer, which we can estimate as
-\(\hat{\pi}_i = x_i/n\). The researchers compared the length of time
-taken, and the accuracy of the participants choices. The power of a
-lineup can therefore be estimated as the ratio of correct
+distribution\(Mult_{\pi_1, \pi_2, ...., \pi_m}(x_i, x_2, ..., x_m)\) with
+\(\sum_i \pi_i = 1\), where \(\pi_i\) is the probability that plot \(i\) is picked by an
+observer, which we can estimate as \(\hat{\pi}_i = x_i/n\).
+The researchers compared the length of time taken, and the accuracy of the participants choices.
+The power of a lineup can therefore be estimated as the ratio of correct
 identifications \(x\) out of \(n\) viewings.
@@
 \hypertarget{the-methods-of-data-analysis-used}{%
-\subsection{The methods of data analysis
-used}\label{the-methods-of-data-analysis-used}}
-
-The data analysis methods used in order to analyse and collate the
-results included downloading the survey submissions and opening them
-into the analysis software R (R Core Team
-\protect\hyperlink{ref-RCore}{2019}).
-
-For each of the 12 lineup displays the researchers calculated: -
-accuracy: the proportion of subjects who detected the data plot -
+\subsection{The methods of data analysis used}\label{the-methods-of-data-analysis-used}}
+
+The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R (R Core Team \protect\hyperlink{ref-RCore}{2019}).
+
+For each of the 12 lineup displays the researchers calculated:
+
+\begin{itemize}
+\tightlist
+\item
+  accuracy: the proportion of subjects who detected the data plot
+\item
   efficiency: average time taken to respond
+\end{itemize}
 
@@
 
-Side-by-side dot plots were made of accuracy (efficiency) against map
-type, facetted by trend model type.
-
-Similar plots were made of the feedback and demographic variables -
-reason for choice, reported difficulty, gender, age, education, having
-lived in Australia - against the design variables.
-
-Plots will be made in R (R Core Team 2019), with the ggplot2 package
-(Wickham 2016).
+Side-by-side dot plots were made of accuracy (efficiency) against map type, facetted by trend model type.
+
+Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.
+
+Plots will be made in R (R Core Team 2019), with the ggplot2 package (Wickham 2016).
 
@@
 
-The likelihood of detecting the data plot in the lineup can be modelled
-using a linear mixed effects model. The base R (R Core Team
-\protect\hyperlink{ref-RCore}{2019}) \texttt{glm()} function implements
-generalised linear models. The model used includes the two main effects
-map type and trend model, which gives the fixed effects model to be:
+The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
+The R (R Core Team \protect\hyperlink{ref-RCore}{2019}) \texttt{glmer()} function in the (Bates et al.
+\protect\hyperlink{ref-lme4}{2015}) package implements generalised linear mixed effect models.
+The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
 
@@
 
-where \(y_{ij} = 0, 1\) whether the subject detected the data plot,
-\(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect,
-\(\delta_j\) is the trend model effect. We are allowing for an
-interaction between map type and trend model. Because the response is
-binary, a logistic model is used. This model can account for each
-individual participants' abilities as it includes a subject-specific
-random intercept. As each participant provides results from 12 lineups.
-
-The results will be analysed using a linear mixed effects model, with a
-subject random effect to account for differences in individuals. There
-will be two main effects: map type and trend model, with an interaction
-between them, which gives the fixed effects part of the model to be:
-
-\[\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3\]
-
-where \(y_{ij} = 0, 1\) whether the subject detected the data plot,
-\(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect,
-\(\delta_j\) is the trend model effect. We are allowing for an
-interaction between map type and trend model. As the response for
-whether the participant detected the data plot is binary, a logistic
-link model is used.
-
-The model specifies a logistic link, this means the predicted values
-from the \texttt{glm} model should be back-transformed to fit between 0
-and 1. They are transformed with the link specified below:
-
-\[\mu = \frac{e^{\eta}}{1 + e^{\eta}}\] \[\eta = f(\tau_i,\delta_j)\]
-
-A similar model will be constructed for the efficiency, using a log
-time, and normal errors.
-
-The feedback and demographic variables will possibly be incorporated as
-covariates.
-
-Computation will be done using R (R Core Team
-\protect\hyperlink{ref-RCore}{2019}), with the \texttt{lme4} package
-(Bates et al. \protect\hyperlink{ref-lme4}{2015}).
+where \(y_{ij} = 0, 1\) whether the subject detected the data plot, \(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect, \(\delta_j\) is the trend model effect.
+We are allowing for an interaction between map type and trend model.
+Because the response is binary, a logistic model is used.
+This model can account for each individual participants' abilities as it includes a subject-specific random intercept.
+As each participant provides results from 12 lineups.
+
+The model specifies a logistic link, this means the predicted values from the \texttt{glmer} model should be back-transformed to fit between 0 and 1.
+They are transformed with the link specified below:
+
+\[\mu = \frac{e^{\eta}}{1 + e^{\eta}}\]
+\[\eta = f(\tau_i,\delta_j)\]
+
+A similar model will be constructed for the efficiency, using a log time, and normal errors.
+
+The feedback and demographic variables will possibly be incorporated as covariates.
+
+Computation will be done using R (R Core Team \protect\hyperlink{ref-RCore}{2019}), with the \texttt{lme4} package (Bates et al. \protect\hyperlink{ref-lme4}{2015}).
 
 \hypertarget{limitations-of-the-data-collection}{%
-\subsection{Limitations of the data
-collection}\label{limitations-of-the-data-collection}}
-
-A pilot study was conducted to determine whether the lineups were
-appropriate. All lineups in the pilot study were deemed viable as at
-least one participant detected the real data plot in each lineup. The
-demographics of the participants showed a skew towards male
-participants. The randomness of the group allocation also resulted in
-more participants being allocated to Group B. Due to the allocation of
-lineup displays the participants all saw six Choropleth displays and six
-Hexagon Tile Map displays.
+\subsection{Limitations of the data collection}\label{limitations-of-the-data-collection}}
+
+A pilot study was conducted to determine whether the lineups were appropriate. All lineups in the pilot study were deemed viable as at least one participant detected the real data plot in each lineup.
+The demographics of the participants showed a skew towards male participants.
+The randomness of the group allocation also resulted in more participants being allocated to Group B.
+Due to the allocation of lineup displays the participants all saw six Choropleth displays and six Hexagon Tile Map displays.
 
@@
 
-Responses from 95 participants were collected. Three participants
-provided no answers for any task, and their data was removed. Set A was
-evaluated by 42 participants, and 53 evaluated set B. This resulted in
-1104 evaluations, corresponding to 92 subjects, each evaluating 12
-lineups, that are analysed on accuracy and speed.
+Responses from 95 participants were collected.
+Three participants provided no answers for any task, and their data was removed.
+Set A was evaluated by 42 participants, and 53 evaluated set B.
+This resulted in 1104 evaluations, corresponding to 92 subjects, each evaluating 12 lineups, that are analysed on accuracy and speed.
+The certainty and reasons of subjects in their answers is also examined.
 
@@
 
-Of the 92 participants, 67 were male, and 25 female. Most participants
-(56) had a Bacherlors degree, 13 had a Masters degree, and the remaining
-23 had high school diplomas.
+Of the 92 participants, 67 were male, and 25 female. Most participants (56) had a Bacherlors degree, 13 had a Masters degree, and the remaining 23 had high school diplomas.
 
@@
 
-Figure \ref{fig:detection_compare} displays the average detection rates
-by type of plot, separately for each trend model. Evaluations on the
-same data set are connected by a line segment. For both the Three Cities
-and All Cities trend models performance was substantially better for the
-hexagon tile map. Viewers detected the data plot substantially more
-often with the hexagon tile map. One replicate for the All Cities group,
-had similar detection rates for both plot types, and this is discussed
-in the supplementary \protect\hyperlink{lineups}{Lineups} section.
-Surprisingly, participants could also detect the gradual spatial trend
-in the NW-SE group from the hexagon tile map. We expected that the
-choropleth map would be superior for the type of spatial pattern, but
-the data suggests the hexagon tile map performs slightly better, or
-equally as well.
-
-Table \ref{tab:desc_stats} shows the means and standard deviations of
-the detection rate for each type of plot and each trend model. This also
-gives the standard errors, the smallest standard deviation is the Three
-Cities trend model shown in a Choropleth display. This group had a very
-small detection rate of 0.038.
+Figure \ref{fig:detect-compare} displays the average detection rates for the two types of plot, separately for each trend model.
+Evaluations on the same data set are connected by a line segment.
+For both the Three Cities and All Cities trend models performance was substantially better for the hexagon tile map.
+Viewers detected the data plot substantially more often with the hexagon tile map.
+One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in the supplementary \protect\hyperlink{lineups}{Lineups} section.
+Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map.
+We expected that the choropleth map would be superior for the type of spatial pattern, but the data suggests the hexagon tile map performs slightly better, or equally as well.
+
+Table \ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
+This also gives the standard errors, the smallest standard deviation is the Three Cities trend model shown in a Choropleth display.
+This group had a very small detection rate of 0.038.
 
@@
 \centering
-\includegraphics{paper_files/figure-latex/detection_compare-1.pdf}
-\caption{The detection rates achieved by participants are contrasted
-when viewing the four replicates of the three trend models. Each point
-shows the probability of detection for the lineup display, the facets
-separate the trend models hidden in the lineup. The points for the same
-data set shown in a choroleth or haxgon tile map display are linked to
-show the difference in the detection rate.}
+\includegraphics{paper_files/figure-latex/detect-compare-1.pdf}
+\caption{\label{fig:detect-compare}The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models.
+Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup.
+The points for the same data set shown in a choroleth or haxgon tile map display are linked to show the difference in the detection rate.}
 \end{figure}
@@
 
-\caption{\label{tab:desc_stats}}
+\caption{\label{tab:desc-stats}The rate of detection for each trend model has been calculate for the choropleth and hexagon tile map displays. The associated standard errors are also included.}
 \centering
@@
 \midrule
-Choro. & 0.505 & 0.038 & 0.228\\
- & (0.501) & (0.192) & (0.421)\\
-Hex. & 0.609 & 0.391 & 0.571\\
- & (0.489) & (0.489) & (0.496)\\
+Choro. & 0.51 & 0.04 & 0.23\\
+ & (0.50) & (0.19) & (0.42)\\
+\addlinespace
+Hex. & 0.61 & 0.39 & 0.57\\
+ & (0.49) & (0.49) & (0.50)\\
 \bottomrule
@@
 
-Table \ref{detect_glm1} is a summary of the generalised linear mixed
-effects model, testing the effect of plot type and trend model on
-detection rate. The results support the summary from Figure
-@ref\{detection\_compare\}. All terms are statistically significant.
-Overall, the hexagon tile map performs marginally better than the
-choropleth for all trend models, which is a pleasant surprise. Detection
-rate is lower for the Three Cities and All Cities, than the NW-SE group.
-The hexagon tile map has a substantially higher detection rate than the
-choropleth for Three Cities and All Cities. XXX Put a number for each of
-these.
-
-\begin{tabular}{rcrr}
+\begin{table}
+
+\caption{\label{tab:detect-glmer1}The model output for the generalised linear mixed effect model for detection rate.
+This model considers the type of display, the trend model hidden in the data plot, and accounts for contributor performance.}
+\centering
+\begin{tabular}[t]{rrlrr}
 \toprule
-Term & Estimate & Std. Error & P value\\
+Term & Est. & Sig. & Std. Error & P val\\
 \midrule
-Intercept & 0.02 & 0.17 & 0.896\\
-Hex. & 0.46$^{*  }$ & 0.22 & 0.037\\
-Three Cities & -3.43$^{***}$ & 0.42 & 0.000\\
-All Cities & -1.35$^{***}$ & 0.24 & 0.000\\
-Hex:Three Cities & 2.46$^{***}$ & 0.47 & 0.000\\
+Intercept & 0.02 & $^{ }$ & 0.17 & 0.90\\
+Hex. & 0.46 & $^{*}$ & 0.22 & 0.04\\
 \addlinespace
-Hex:All Cities & 1.17$^{***}$ & 0.33 & 0.000\\
+Three Cities & -3.43 & $^{***}$ & 0.42 & 0.00\\
+All Cities & -1.35 & $^{***}$ & 0.24 & 0.00\\
+\addlinespace
+Hex:Three Cities & 2.46 & $^{***}$ & 0.47 & 0.00\\
+Hex:All Cities & 1.17 & $^{***}$ & 0.33 & 0.00\\
 \bottomrule
 \end{tabular}
+\end{table}
+
+Table \ref{tab:detect-glmer1} is a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on detection rate.
+The results support the summary from Figure \ref{fig:detect-compare}.
+All terms are statistically significant.
+Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
+For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to 0.62 from 0.51 for choropleths.
+
+When a choropleth map display is used, the predicted detection rate for the Three Cities trend, 0.03, is extremely low, especially compared to the NW-SE trend.
+When the All Cities trend is presented in a choropleth display the predicted probability of detection is 0.21.
+The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend 0.38 and All Cities trend 0.58.
 
@@
 
-Figure \ref{fig:beeswarm} shows the time taken for participants to
-evaluate each lineup, separately for trend model, whether the data plot
-was detected or not, and type of plot, as horizontally jittered dot
-plots. The time taken to complete an evaluation ranged from milliseconds
-to 60 seconds. The average time taken for type of display is displayed
-as a large colored dot on each plot. There is little difference in the
-average time taken to read a choropleth or hexgon tile map. There is
-also very little difference in evaluation time whether the data plot was
-detected or not.
+Figure \ref{fig:beeswarm} shows the time taken for participants to evaluate each lineup, separately for trend model, whether the data plot was detected or not, and type of plot, as horizontally jittered dot plots.
+The time taken to complete an evaluation ranged from milliseconds to 60 seconds.
+The average time taken for type of display is displayed as a large colored dot on each plot.
+There is little difference in the average time taken to read a choropleth or hexgon tile map.
+There is also very little difference in evaluation time whether the data plot was detected or not.
 
@@
 \includegraphics{paper_files/figure-latex/beeswarm-1.pdf}
-\caption{The distribution of the time taken (seconds) to submit a
-response for each combination of trend, whether the data plot was
-detected, and type of display, shown using horizontally jittered
-dotplots. The coloured point indicates average time taken for each plot
-type. Although some participants take just a few seconds per evaluation,
-and some take as much as mcuh as 60 seconds, but there is very little
-difference in time taken between plot types.}
+\caption{\label{fig:beeswarm}The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots.
+The coloured point indicates average time taken for each plot type.
+Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between plot types.}
 \end{figure}
@@
 \includegraphics{paper_files/figure-latex/certainty-1.pdf}
-\caption{The amount of times each level of certainty was chosen by
-participants when viewing hexagon tile map or choropleth displays.
-Participants were more likely to choose a high certainty when
-considering a Choropleth map. The mid value of 3 was the default
-certainty, it was chosen most for the Hexagon tile map displays.}
+\caption{\label{fig:certainty}The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
+Participants were more likely to choose a high certainty when considering a Choropleth map.
+The mid value of 3 was the default certainty, it was chosen most for the Hexagon tile map displays.}
 \end{figure}
 
-Certainty levels are measured on a five point scale---they are
-subjective assessments by the participant `How certain are you about
-your choice?'.
+Certainty levels are measured on a five point scale---they are subjective
+assessments by the participant `How certain are you about your choice?'.
 
@@
 
-\begin{table}[H]
-\centering
-\begin{tabular}{llll}
+\begin{table}
+
+\caption{\label{tab:reason}The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
+The facets show whether or not the choice was correct.}
+\centering
+\begin{tabular}[t]{llll}
 \toprule
@@
 \midrule
-NW-SE & No & trend & clusters\\
-NW-SE & Yes & trend & clusters\\
-Three Cities & No & trend & clusters\\
-Three Cities & Yes & consistent & clusters\\
-All Cities & No & trend & clusters\\
-\addlinespace
-All Cities & Yes & clusters, consistent & clusters\\
+ & No & trend & clusters\\
+\cmidrule{2-4}
+\multirow{-2}{*}{\raggedright\arraybackslash NW-SE} & Yes & trend & clusters\\
+\cmidrule{1-4}
+ & No & trend & clusters\\
+\cmidrule{2-4}
+\multirow{-2}{*}{\raggedright\arraybackslash Three Cities} & Yes & consistent & clusters\\
+\cmidrule{1-4}
+ & No & trend & clusters\\
+\cmidrule{2-4}
+\multirow{-2}{*}{\raggedright\arraybackslash All Cities} & Yes & clusters, consistent & clusters\\
 \bottomrule
@@
 
-The most common choice made by participant was clusters, this response
-was expected when participants viewed the Hexagon display of the All
-Cities and Three Cities distributions.
-
-\hypertarget{contributors}{%
-\subsection{Contributors}\label{contributors}}
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/contributors-1.pdf}
-\caption{The probablity of detection acheived by the contributors in
-each group is shown by the points. Group B has a larger range and a
-smaller inter-quartile range. Group A and both had 3 people who did not
-find any of the data maps in the displays.}
-\end{figure}
+The most common choice made by participant was clusters, this response was expected when participants viewed the Hexagon display of the All Cities and Three Cities distributions.
 
@@
 
-The choices made by participants are examined in Figure
-\ref{fig:choices}. Participants were misled by the choropleth display,
-but not the hexagon display for All Cities displays except (2). The maps
-with a North West to South East trend was chosen with much greater
-frequency in all displays. All of Three Cities displays, except (4),
-were detected in the hexagon display. All except one lineup had at least
-one participant select the correct map in the lineup as shown in Figure
-\ref{fig:choices}.
+The choices made by participants are examined in Figure \ref{fig:choices}.
+Participants were misled by the choropleth display, but not the hexagon display for All Cities displays except (2).
+The maps with a North West to South East trend was chosen with much greater frequency in all displays.
+All of Three Cities displays, except (4), were detected in the hexagon display.
+All except one lineup had at least one participant select the correct map in the lineup as shown in Figure \ref{fig:choices}.
 
@@
 \includegraphics{paper_files/figure-latex/choices-1.pdf}
-\caption{Each facet is associated with one lineup, the height of the
-points show the proportion of the participants that made each choice
-when considering each lineup. The points coloured orange show the map
-which contained a trend model, these are the correct choices. The
-numbers differentiate the replicates of each trend model and type of map
-display. Participants were able to select 0 to indicate they did not
-want to choose a map.}
+\caption{\label{fig:choices}Each facet is associated with one lineup, the height of the points show the proportion of the participants that made each choice when considering each lineup.
+The points coloured orange show the map which contained a trend model, these are the correct choices.
+The numbers differentiate the replicates of each trend model and type of map display.
+Participants were able to select 0 to indicate they did not want to choose a map.}
 \end{figure}
 
-One lineup had extremely similiar detection rates for the Choropleth and
-Hexagon displays.
+One lineup had extremely similiar detection rates for the Choropleth and Hexagon displays.
 
@@
 \includegraphics{figures/aus_nwse_6_hex.png}
-\caption{``A North-West to South East trend was hidden in this lineup of
-hexagon tile map displays.''}
+\caption{``A North-West to South East trend was hidden in this lineup of hexagon tile map displays.''}
 \end{figure}
@@
 
-The choropleth map display and the tessellated hexagon tile map have
-been contrasted in a visual inference study. The hexagon tile map was
-significantly more effective for spotting a real data trend model hidden
-in a lineup.
-
-This hexagon tile map display should be considered as a visualisation
-method when communicating distributions that relate to the population in
-each geographic unit. Cancer Atlas products may benefit from the
-opportunity to allow exploration via the traditional choropleth map
-method as well as an alternative display. The spatial distributions used
-to test these displays were inspired by the real spatially smoothed
-estimates of the cancer burden on Australian communities. However, this
-technique may be extended to other population related distributions,
-such as other diseases.
-
-The increasing population densities of capital cities despite large land
-area exaserbates the difference in the smallest and largest communities.
-The population density structure of Australia can be considered similar
-to that of Canada, New Zealand and many others. Therefore, this display
-is not only relevant to Australia, but all nations or population
-collections that experience densely populated cities alongside vast
-rural expanses.
+The choropleth map display and the tessellated hexagon tile map have been contrasted in a visual inference study.
+The hexagon tile map was significantly more effective for spotting a real data trend model hidden in a lineup.
+
+This hexagon tile map display should be considered as a visualisation method when communicating distributions that relate to the population in each geographic unit.
+Cancer Atlas products may benefit from the opportunity to allow exploration via the traditional choropleth map method as well as an alternative display.
+The spatial distributions used to test these displays were inspired by the real spatially smoothed estimates of the cancer burden on Australian communities.
+However, this technique may be extended to other population related distributions, such as other diseases.
+
+The increasing population densities of capital cities despite large land area exaserbates the difference in the smallest and largest communities.
+The population density structure of Australia can be considered similar to that of Canada, New Zealand and many others.
+Therefore, this display is not only relevant to Australia, but all nations or population collections that experience densely populated cities alongside vast rural expanses.
 
@@
 
-The participants were trained using three displays. There were
-relatively simple lineups and are shown in Figure XXX.
+The participants were trained using three displays. There were relatively simple lineups and are shown in Figure XXX.
 
@@
 
-The survey application was hosted on a website external to the
-Figure-Eight platform. Following suggestions in the documentation, the
-information and training required for a participant to make a decision
-was included that survey
-
-The demonstrative images of the \texttt{shinydashboard} web application
-display the demographic and consent page in Figure \ref{fig:survey1}.
+The survey application was hosted on a website external to the Figure-Eight platform.
+Following suggestions in the documentation, the information and training required for a participant to make a decision was included that survey
+
+The demonstrative images of the \texttt{shinydashboard} web application display the demographic and consent page in Figure
+\ref{fig:survey_demogs}.
 
@@
 \includegraphics{figures/aus_cities_3_geo.png}
-\caption{The lineup of choropleth map displays hides a distribution that
-affects all capital cities.}
+\caption{The lineup of choropleth map displays hides a distribution that affects all capital cities.}
 \end{figure}
@@
 \includegraphics{figures/aus_cities_3_hex.png}
-\caption{The lineup of choropleth map displays shows a distribution that
-affects all capital cities. The values for the inner city areas in the
-capital cities result in them being coloured red. However, the colour
-blue dominates the display as the large rural areas are filled.
+\caption{The lineup of choropleth map displays shows a distribution that affects all capital cities.
+The values for the inner city areas in the capital cities result in them being coloured red.
+However, the colour blue dominates the display as the large rural areas are filled.
 Replicate (2) for All Cities.}
@@
 
-The values for the inner city areas in the capital cities result in them
-being coloured red. However, the colour blue dominates the display as
-the large rural areas are filled. There were no other choropleth maps
-that were coloured as blue as map (3). This meant the detection rate was
-quite high, participants were able to select the correct distribution
-without being able to see the values of the capital cities. The same
-data showed in the hexagon tile map display shows varied distributions
-across the lineup. They are more diverse in colour than the choropleth
-counterparts. The same location holds the real data plot, the red city
-centres are now visible and surrounded by yellow, and then blue
-hexagons.
+The values for the inner city areas in the capital cities result in them being coloured red.
+However, the colour blue dominates the display as the large rural areas are filled.
+There were no other choropleth maps that were coloured as blue as map (3).
+This meant the detection rate was quite high, participants were able to select the correct distribution without being able to see the values of the capital cities.
+The same data showed in the hexagon tile map display shows varied distributions across the lineup.
+They are more diverse in colour than the choropleth counterparts.
+The same location holds the real data plot, the red city centres are now visible and surrounded by yellow, and then blue hexagons.
 
@@
 \subsection{Overall Performance}\label{overall-performance}}
+
+\hypertarget{contributor-performance}{%
+\subsection{Contributor Performance}\label{contributor-performance}}
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/contributors-1.pdf}
+\caption{\label{fig:contributors}The probablity of detection acheived by the contributors in each group is shown by the points.
+Group B has a larger range and a smaller inter-quartile range.
+Group A and both had 3 people who did not find any of the data maps in the displays.}
+\end{figure}
 
@@
 
-Ethics approval for the online survey was granted by QUT's Ethics
-Committee (Ethics Application Number: 1900000991). All applicants
-provided informed consent in line with QUT regulations prior to
-participating in this research.
+Ethics approval for the online survey was granted by QUT's Ethics Committee (Ethics Application Number: 1900000991).
+All applicants provided informed consent in line with QUT regulations prior to participating in this research.
 
@@
 ``Australian Statistical Geography Standard (ASGS).'' 2018.
-\emph{Australian Bureau of Statistics}. Australian Government.
+\emph{Australian Bureau of Statistics}.
+Australian Government.
 \url{\%7Bhttps://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)\%7D}.
@@
 \leavevmode\hypertarget{ref-lme4}{}%
-Bates, Douglas, Martin Mächler, Ben Bolker, and Steve Walker. 2015.
-``Fitting Linear Mixed-Effects Models Using lme4.'' \emph{Journal of
-Statistical Software} 67 (1): 1--48.
+Bates, Douglas, Martin Mächler, Ben Bolker, and Steve Walker.
+2015.
+``Fitting Linear Mixed-Effects Models Using lme4.'' \emph{Journal of Statistical Software} 67 (1): 1--48.
 \url{https://doi.org/10.18637/jss.v067.i01}.
@@
 \leavevmode\hypertarget{ref-sheets}{}%
-Bryan, Jennifer, and Joanna Zhao. 2018. \emph{Googlesheets: Manage
-Google Spreadsheets from R}.
-\url{https://CRAN.R-project.org/package=googlesheets}.
+Bryan, Jennifer, and Joanna Zhao. 2018. \emph{Googlesheets: Manage Google Spreadsheets from R}. \url{https://CRAN.R-project.org/package=googlesheets}.
+
+\leavevmode\hypertarget{ref-NISCC}{}%
+Dent, Borden D. 1972. ``A Note on the Importance of Shape in Cartogram Communication.'' \emph{Journal of Geography} 71 (7): 393--401. \url{https://doi.org/10.1080/00221347208981697}.
+
+\leavevmode\hypertarget{ref-ACTUC}{}%
+Dorling, Daniel. 2011. ``Area Cartograms: Their Use and Creation.'' In \emph{Concepts and Techniques in Modern Geography (Catmog)}, 59:252--60. \url{https://doi.org/10.1002/9780470979587.ch33}.
+
+\leavevmode\hypertarget{ref-CTTMB}{}%
+Griffin, T. L.C. 1980. ``Cartographic Transformation of the Thematic Map Base.'' \emph{Cartography} 11 (3): 163--74. \url{https://doi.org/10.1080/00690805.1980.10438102}.
 
@@
 Hofmann, Heike, Lendie Follett, Mahbubul Majumder, and Dianne Cook.
-2012. ``Graphical Tests for Power Comparison of Competing Designs.''
-\emph{IEEE Transactions on Visualization and Computer Graphics} 18:
-2441--8.
+2012.
+``Graphical Tests for Power Comparison of Competing Designs.'' \emph{IEEE Transactions on Visualization and Computer Graphics} 18: 2441--8.
+
+\leavevmode\hypertarget{ref-CBATCC}{}%
+Kocmoud, C, and D House. 1998. ``A Constraint-based Approach to Constructing Continuous Cartograms.'' In \emph{Proc. Symp. Spatial Data Handling}, 236--46.
 
 \leavevmode\hypertarget{ref-VVSIALM}{}%
-Majumder, Mahbubul, Heike Hofmann, and Dianne Cook. 2013. ``Validation
-of Visual Statistical Inference, Applied to Linear Models.''
-\emph{Journal of the American Statistical Association} 108 (503):
-942--56. \url{https://doi.org/10.1080/01621459.2013.808157}.
+Majumder, Mahbubul, Heike Hofmann, and Dianne Cook.
+2013.
+``Validation of Visual Statistical Inference, Applied to Linear Models.'' \emph{Journal of the American Statistical Association} 108 (503): 942--56.
+\url{https://doi.org/10.1080/01621459.2013.808157}.
+
+\leavevmode\hypertarget{ref-CDWCS}{}%
+Monmonier, Mark. 2005. ``Cartography: Distortions, World-views and Creative Solutions.'' \emph{Progress in Human Geography} 29 (2): 217--24. \url{https://doi.org/10.1191/0309132505ph540pr}.
+
+\leavevmode\hypertarget{ref-NAC}{}%
+Olson, Judy M. 1976. ``Noncontiguous Area Cartograms.'' \emph{The Professional Geographer} 28 (4): 371--80. \url{https://doi.org/10.1111/j.0033-0124.1976.00371.x}.
+
+\leavevmode\hypertarget{ref-RSCW}{}%
+Raisz, Erwin. 1963. ``Rectangular Statistical Cartograms of the World.'' Journal Article. \emph{Journal of Geography} 35 (1): 8--10. \url{https://doi.org/10.1080/00221343608987880}.
 
 \leavevmode\hypertarget{ref-RCore}{}%
-R Core Team. 2019. \emph{R: A Language and Environment for Statistical
-Computing}. Vienna, Austria: R Foundation for Statistical Computing.
-\url{https://www.R-project.org/}.
+R Core Team. 2019. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
 
 \leavevmode\hypertarget{ref-GIIV}{}%
-Wickham, Hadley, Dianne Cook, Heike Hofmann, and Andreas Buja. 2010.
-``Graphical Inference for Infovis.'' \emph{IEEE Transactions on
-Visualization and Computer Graphics (Proc. InfoVis '10)} 16 (6):
-973--79.
+Wickham, Hadley, Dianne Cook, Heike Hofmann, and Andreas Buja.
+2010.
+``Graphical Inference for Infovis.'' \emph{IEEE Transactions on Visualization and Computer Graphics (Proc.
+InfoVis '10)} 16 (6): 973--79.
 

### 2020-01-11 paper/paper.R

@@ -1,0 +1,440 @@
+## ----setup, include=FALSE-------------------------------------------------------------------------------------------
+knitr::opts_chunk$set(
+  echo = FALSE,
+  warning = FALSE,
+  error = FALSE, 
+  message = FALSE)
+
+
+## ----libraries------------------------------------------------------------------------------------------------------
+# Load Libraries
+library(tidyverse)
+library(cowplot)
+library(png)
+library(grid)
+library(lubridate)
+library(broom)
+library(readxl)
+library(lme4)
+library(ggthemes)
+library(RColorBrewer)
+library(visreg)
+library(emmeans)
+library(kableExtra)
+
+
+## ----liver, fig.height = 9, fig.width = 6, fig.cap = "The smoothed average of liver cancer diagnoses for Australian males. The divering colour scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average."----
+ggdraw(ylim = c(0,2), xlim = c(0,1.3), clip = "on") +
+  draw_plot(rasterGrob(readPNG("figures/aus_liver_m.png")), -0.15, 0.9, 1.6, 1.2) +
+  draw_plot(rasterGrob(readPNG("figures/aus_liver_m_hex.png")), -0.15, -0.1, 1.6, 1.2) +
+  draw_plot_label(c("a", "b"), 
+    c(0.05, 0.05), c(1.95, 1), size = 20, color = "white") + 
+  theme(plot.background = element_rect(fill = "black"))
+
+
+## ----exp_design, fig.cap = "Experimental design."-------------------------------------------------------------------
+count(d, trend, type) %>% mutate(Replicates = 2)
+
+d %>% 
+  mutate(Trend = trend) %>% 
+  group_by(Trend, type, group) %>% 
+  summarise(Reps = paste0(sort(unique(replicate)), collapse = ", ")) %>% 
+  mutate(prop = round(n/sum(n), 3), r_prop = paste0(reason, ":", prop)) %>% 
+  top_n(1, n) %>% summarise(reasons = paste(reason, collapse=", ")) %>% 
+  pivot_wider(names_from = c("type"), values_from = c("reasons")) %>% 
+  ungroup() %>% 
+  knitr::kable(., format = "latex", booktabs = TRUE) %>% kable_styling("striped") %>% 
+  collapse_rows(., columns = 1, custom_latex_hline = c(1:2, 3:4))
+
+
[…]

### 2020-01-11 paper/paper.Rmd
choice plot better dims

@@
 The numbers differentiate the replicates of each trend model and type of map display.
-Participants were able to select 0 to indicate they did not want to choose a map."}
+Participants were able to select 0 to indicate they did not want to choose a map.", fig.height = 8, fig.width =6}
 d %>% 
@@
   ggplot() + 
-  geom_point(aes(x = choice, y = prop, color = detect_f), size = 4) + 
+  geom_point(aes(x = choice, y = prop, color = detect_f), size = 3) + 
   geom_segment(aes(x = choice, xend = choice,y = bottom, yend = prop, colour = detect_f), size = 1) +

### 2020-01-11 paper/paper.Rmd
Abstract refining, reference style updated

@@
 abstract: |
-  Choosing a visualisation method may seem to be a simple task.
-The choropleth map display is commonly used for communicating spatial data.
-However, when used to communicate the spatial distribution of a statistic the sizes of areas can lead to midinterpretation of the distribution.
-The visualisation method used to present geospatial data will influence the information derived by map users.
-Choosing an alternative display will influence the communication of the distribution.
-The hexagon tile map is presented as an alternative display.
-Visual inference is used to measure the power of design.
-The choropleth is used as a comparison point.
-The hexagon tile map display is an effective visualisation for communicatin=g population related distributions.
-The hexagon tile map display also allowed identification of the geographic distribution with values monotonically decreasing from North West toward South East areas of Australia.
+  The choropleth map display is commonly used for communicating spatial distributions across geographic areas.
+However, when choropleths are used, the sizes of areas can lead to misinterpretation of the distribution.
+The visualisation method used to present geospatial data will influence the understanding of the distribution derived by map users.
+Choosing an effective alternative display could positively influence the communication of the spatial distribution.
+The hexagon tile map is presented as an alternative display for effectively visualising population related distributions.
+Visual inference is used to measure the power of design, and the choropleth is used as a comparison.
+The hexagon tile map display is also tested using a  distribution that is directly related to the geography, with values monotonically decreasing from the North West to South East areas of Australia.
+This study finds the single map in a hexagon tile map lineup that contains a population related distribution is detected with greater probability than the same data displayed in a choropleth map.
+These findings should encourage map creators to implement alternative displays, and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
 dev: png
@@
       base_format: rticles::ieee_article
-      number_sections: false
+      number_sections: true
 editor_options: 
@@
 citation_package: biblatex
+csl: springer-vancouver.csl
 header-includes: \usepackage{graphicx}
 ---
+
+<!-- Regular paper – 12 double column pages (Submissions may be up to 18 pages in length, subject to MOPC. All regular paper page limits include references and author biographies.) -->
 
@@
 This will emphasise the value of the statistic for areas with high population.
-Figure \ref{fig:liver} shows the distribution of the smoothed average amount of Liver cancer diagnoses for Australian Males from 2005-2014.
+Fig.
+\ref{fig:liver} shows the distribution of the smoothed average amount of Liver cancer diagnoses for Australian Males from 2005-2014.
 These inner-city areas are not visible on the choropleth map (a).
@@
 All of these participants read the introductory materials and viewed example questions before proceeding to the survey.
-Each participant was trained using three test displays orienting them to the evaluation task, these displays are shown in supplementary materials section regarding [training].
+Each participant was trained using three test displays orienting them to the evaluation task, these displays are shown in appendix section regarding [training].
 All participants who volunteered to take part were compensated for their time via the payment system of Figure-Eight.
@@
 This will generate twenty-four lineups (twelve lineups of geographic maps, and twelve lineups of hexagon tile maps). Participants evaluated twelve lineups, siz of each map type.
-For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants. The design is outlined in \ref{tab:exp-design}.
+For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants. The design is outlined in Table. \ref{tab:exp-design}.
 
@@
 
-Figure \ref{fig:detect-compare} displays the average detection rates for the two types of plot, separately for each trend model.
+Fig.
+\ref{fig:detect-compare} displays the average detection rates for the two types of plot, separately for each trend model.
 Evaluations on the same data set are connected by a line segment.
@@
 Viewers detected the data plot substantially more often with the hexagon tile map.
-One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in the supplementary [Lineups] section.
+One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in the appendix [Lineups] section.
 Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map.
@@
 
-Table \ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
+\ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
 This also gives the standard errors, the smallest standard deviation is the Three Cities trend model shown in a Choropleth display.
@@
 
-Table \ref{tab:detect-glmer1} is a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on detection rate.
-The results support the summary from Figure \ref{fig:detect-compare}.
+Table.
+\ref{tab:detect-glmer1} is a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on detection rate.
+The results support the summary from Fig.
+\ref{fig:detect-compare}.
 All terms are statistically significant.
@@
 
-Figure \ref{fig:beeswarm} shows the time taken for participants to evaluate each lineup, separately for trend model, whether the data plot was detected or not, and type of plot, as horizontally jittered dot plots.
+Fig.
+\ref{fig:beeswarm} shows the time taken for participants to evaluate each lineup, separately for trend model, whether the data plot was detected or not, and type of plot, as horizontally jittered dot plots.
 The time taken to complete an evaluation ranged from milliseconds to 60 seconds.
@@
 
-The choices made by participants are examined in Figure \ref{fig:choices}.
+The choices made by participants are examined in Fig. \ref{fig:choices}.
 Participants were misled by the choropleth display, but not the hexagon display for All Cities displays except (2).
@@
 All of Three Cities displays, except (4), were detected in the hexagon display.
-All except one lineup had at least one participant select the correct map in the lineup as shown in Figure \ref{fig:choices}.
+All except one lineup had at least one participant select the correct map in the lineup as shown in Fig.
+\ref{fig:choices}.
 
@@
 
-\newpage
-Supplementary Materials
+Appendix
 ============
@@
 
-The participants were trained using three displays. There were relatively simple lineups and are shown in Figure XXX.
+The participants were trained using three displays. There were relatively simple lineups and are shown in Fig.XXX.
 <!--
@@
 
-The authors would like to thank...
+The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualisations.
+They would also like to thank Kerrie Mengersen and Dr.
+Earl Duncan for suggestions and comments.
 

### 2020-01-11 paper/paper.tex
Abstract refining, reference style updated

@@
 % Pandoc toggle for numbering sections (defaults to be off)
-\setcounter{secnumdepth}{0}
+\setcounter{secnumdepth}{5}
 
@@
 \begin{abstract}
-Choosing a visualisation method may seem to be a simple task.
-The choropleth map display is commonly used for communicating spatial data.
-However, when used to communicate the spatial distribution of a statistic the sizes of areas can lead to midinterpretation of the distribution.
-The visualisation method used to present geospatial data will influence the information derived by map users.
-Choosing an alternative display will influence the communication of the distribution.
-The hexagon tile map is presented as an alternative display.
-Visual inference is used to measure the power of design.
-The choropleth is used as a comparison point.
-The hexagon tile map display is an effective visualisation for communicatin=g population related distributions.
-The hexagon tile map display also allowed identification of the geographic distribution with values monotonically decreasing from North West toward South East areas of Australia.
+The choropleth map display is commonly used for communicating spatial distributions across geographic areas.
+However, when choropleths are used, the sizes of areas can lead to misinterpretation of the distribution.
+The visualisation method used to present geospatial data will influence the understanding of the distribution derived by map users.
+Choosing an effective alternative display could positively influence the communication of the spatial distribution.
+The hexagon tile map is presented as an alternative display for effectively visualising population related distributions.
+Visual inference is used to measure the power of design, and the choropleth is used as a comparison.
+The hexagon tile map display is also tested using a distribution that is directly related to the geography, with values monotonically decreasing from the North West to South East areas of Australia.
+This study finds the single map in a hexagon tile map lineup that contains a population related distribution is detected with greater probability than the same data displayed in a choropleth map.
+These findings should encourage map creators to implement alternative displays, and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
 \end{abstract}
@@
 The Australian Cancer Atlas is an online interactive web tool created to explore the burden of cancer on Australian communities. There are many cancer types to be explored individually or aggregated.
-The Atlas examines Australian communities at the Statistical Areas at Level 2 (SA2) (``Australian Statistical Geography Standard (ASGS)'' \protect\hyperlink{ref-abs2016}{2018}) used by the Australian Bureau of Statistics.
+The Atlas examines Australian communities at the Statistical Areas at Level 2 (SA2) {[}\protect\hyperlink{ref-abs2016}{1}{]} used by the Australian Bureau of Statistics.
 Bayesian spatial smoothing was applied to integrate the values of neighbouring areas.
@@
 Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic.
-However, using a choropleth map base introduces biases when considering population related distributions (Kocmoud and House \protect\hyperlink{ref-CBATCC}{1998}).
+However, using a choropleth map base introduces biases when considering population related distributions {[}\protect\hyperlink{ref-CBATCC}{2}{]}.
 Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
@@
 When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
-This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention (Griffin \protect\hyperlink{ref-CTTMB}{1980}).
-An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas (Dent \protect\hyperlink{ref-NISCC}{1972}).
+This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention {[}\protect\hyperlink{ref-CTTMB}{3}{]}.
+An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas {[}\protect\hyperlink{ref-NISCC}{4}{]}.
 This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
@@
 The transformation begins with a choropleth map, and the values of a statistic such as population, for each geographic unit.
-There are several algorithms for transformation (Dorling \protect\hyperlink{ref-ACTUC}{2011}), (Kocmoud and House \protect\hyperlink{ref-CBATCC}{1998}); they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
+There are several algorithms for transformation {[}\protect\hyperlink{ref-ACTUC}{5}{]}, {[}\protect\hyperlink{ref-CBATCC}{2}{]}; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
 The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units.
@@
 Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units.
-The non-contiguous cartgoram method (Olson \protect\hyperlink{ref-NAC}{1976}) keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics.
+The non-contiguous cartgoram method {[}\protect\hyperlink{ref-NAC}{6}{]} keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics.
 This method disconnects areas when shrinking boundaries, and breaks the spatial relationship between areas.
 However, the empty space created emphasises the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
-The Dorling cartogram (Dorling \protect\hyperlink{ref-ACTUC}{2011}) is another method that does not retain the boundaries of geographic units.
+The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{5}{]} is another method that does not retain the boundaries of geographic units.
 Each unit becomes one circle on the cartogram display; the circles are sized according to the value of a the statistic, such as population.
 The neighbour relationships can be illustrated by connecting the boundaries of the circles.
-A similar approach was pioneered by Raisz (\protect\hyperlink{ref-RSCW}{1963}), using rectangles that tile to align borders of neighbours (Monmonier \protect\hyperlink{ref-CDWCS}{2005}).
+A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{7}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{8}{]}.
 These cartogram methods all allow two variables to be shown in the single display. these methods are discussed further in XXX cite review paper
@@
 Where the guilty data set contains structure, and the innocents data sets do not.
-In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the innocents (Hofmann et al.
-\protect\hyperlink{ref-GTPCCD}{2012}).
+In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the innocents {[}\protect\hyperlink{ref-GTPCCD}{9}{]}.
 The guilty data is identified as different from the innocent data with probability \(1/m\), where \(m\) is the number of null plots plus 1 to account account for the guilty data set.
@@
 The lineup protocol can be used in a variety of testing scenarios for visualisations.
-Wickham et al.
-(\protect\hyperlink{ref-GIIV}{2010}) suggest the choropleth map for testing spatial structure in a data set.
+{[}\protect\hyperlink{ref-GIIV}{10}{]} suggest the choropleth map for testing spatial structure in a data set.
 The lineup protocol allows for flexibility in the definition of null data.
@@
 All of these participants read the introductory materials and viewed example questions before proceeding to the survey.
-Each participant was trained using three test displays orienting them to the evaluation task, these displays are shown in supplementary materials section regarding \protect\hyperlink{training}{training}.
+Each participant was trained using three test displays orienting them to the evaluation task, these displays are shown in appendix section regarding \protect\hyperlink{training}{training}.
 All participants who volunteered to take part were compensated for their time via the payment system of Figure-Eight.
@@
 The data collection took place using a secure link between the survey web application and the googlesheet used to store results.
-The application would first connect to the googlesheet using the googlesheets (Bryan and Zhao \protect\hyperlink{ref-sheets}{2018}) R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
+The application would first connect to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{11}{]} R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
 
@@
 
-The choropleth map was used as the comparative visualisation for presenting the lineups (Majumder, Hofmann, and Cook \protect\hyperlink{ref-VVSIALM}{2013}) as this is the common display for spatial cancer data.
+The choropleth map was used as the comparative visualisation for presenting the lineups {[}\protect\hyperlink{ref-VVSIALM}{12}{]} as this is the common display for spatial cancer data.
 Geographic distributions usually have some degree of spatial autcorrelation between neighbours.
@@
 
-The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R (R Core Team \protect\hyperlink{ref-RCore}{2019}).
+The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R {[}\protect\hyperlink{ref-RCore}{13}{]}.
 
@@
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R (R Core Team \protect\hyperlink{ref-RCore}{2019}) \texttt{glmer()} function in the (Bates et al.
-\protect\hyperlink{ref-lme4}{2015}) package implements generalised linear mixed effect models.
+The R {[}\protect\hyperlink{ref-RCore}{13}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{14}{]} package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 
-Computation will be done using R (R Core Team \protect\hyperlink{ref-RCore}{2019}), with the \texttt{lme4} package (Bates et al. \protect\hyperlink{ref-lme4}{2015}).
+Computation will be done using R {[}\protect\hyperlink{ref-RCore}{13}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{14}{]}.
 
@@
 Viewers detected the data plot substantially more often with the hexagon tile map.
-One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in the supplementary \protect\hyperlink{lineups}{Lineups} section.
+One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in the appendix \protect\hyperlink{lineups}{Lineups} section.
 Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map.
@@
 
-\newpage
-
-\hypertarget{supplementary-materials}{%
-\section{Supplementary Materials}\label{supplementary-materials}}
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
 
@@
 
-The participants were trained using three displays. There were relatively simple lineups and are shown in Figure XXX.
+The participants were trained using three displays. There were relatively simple lineups and are shown in Fig.XXX.
 
@@
 
-The authors would like to thank\ldots{}
+The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualisations.
+They would also like to thank Kerrie Mengersen and Dr.~Earl Duncan for suggestions and comments.
 
@@
 \leavevmode\hypertarget{ref-abs2016}{}%
-``Australian Statistical Geography Standard (ASGS).'' 2018.
-\emph{Australian Bureau of Statistics}.
-Australian Government.
-\url{\%7Bhttps://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)\%7D}.
+1. (2018) Australian Statistical Geography Standard (ASGS). Australian Bureau of Statistics
+
+\leavevmode\hypertarget{ref-CBATCC}{}%
+2. Kocmoud C, House D (1998) A Constraint-based Approach to Constructing Continuous Cartograms. In: Proc. Symp. Spatial data handling. pp 236--246
+
+\leavevmode\hypertarget{ref-CTTMB}{}%
+3. Griffin TL (1980) Cartographic Transformation of the Thematic Map Base. Cartography 11:163--174
+
+\leavevmode\hypertarget{ref-NISCC}{}%
+4. Dent BD (1972) A Note on the Importance of Shape in Cartogram Communication. Journal of Geography 71:393--401
+
+\leavevmode\hypertarget{ref-ACTUC}{}%
+5. Dorling D (2011) Area Cartograms: Their Use and Creation. In: Concepts and techniques in modern geography (catmog). pp 252--260
+
+\leavevmode\hypertarget{ref-NAC}{}%
+6. Olson JM (1976) Noncontiguous Area Cartograms. The Professional Geographer 28:371--380
+
+\leavevmode\hypertarget{ref-RSCW}{}%
+7. Raisz E (1963) Rectangular Statistical Cartograms of the World. Journal of Geography 35:8--10
+
+\leavevmode\hypertarget{ref-CDWCS}{}%
+8. Monmonier M (2005) Cartography: Distortions, World-views and Creative Solutions. Progress in Human Geography 29:217--224
+
+\leavevmode\hypertarget{ref-GTPCCD}{}%
+9. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448
+
+\leavevmode\hypertarget{ref-GIIV}{}%
+10. Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979
+
+\leavevmode\hypertarget{ref-sheets}{}%
+11. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
+
+\leavevmode\hypertarget{ref-VVSIALM}{}%
+12. Majumder M, Hofmann H, Cook D (2013) Validation of visual statistical inference, applied to linear models. Journal of the American Statistical Association 108:942--956
+
+\leavevmode\hypertarget{ref-RCore}{}%
+13. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
 
 \leavevmode\hypertarget{ref-lme4}{}%
-Bates, Douglas, Martin Mächler, Ben Bolker, and Steve Walker.
-2015.
-``Fitting Linear Mixed-Effects Models Using lme4.'' \emph{Journal of Statistical Software} 67 (1): 1--48.
-\url{https://doi.org/10.18637/jss.v067.i01}.
-
-\leavevmode\hypertarget{ref-sheets}{}%
-Bryan, Jennifer, and Joanna Zhao. 2018. \emph{Googlesheets: Manage Google Spreadsheets from R}. \url{https://CRAN.R-project.org/package=googlesheets}.
-
-\leavevmode\hypertarget{ref-NISCC}{}%
-Dent, Borden D. 1972. ``A Note on the Importance of Shape in Cartogram Communication.'' \emph{Journal of Geography} 71 (7): 393--401. \url{https://doi.org/10.1080/00221347208981697}.
-
-\leavevmode\hypertarget{ref-ACTUC}{}%
-Dorling, Daniel. 2011. ``Area Cartograms: Their Use and Creation.'' In \emph{Concepts and Techniques in Modern Geography (Catmog)}, 59:252--60. \url{https://doi.org/10.1002/9780470979587.ch33}.
-
-\leavevmode\hypertarget{ref-CTTMB}{}%
-Griffin, T. L.C. 1980. ``Cartographic Transformation of the Thematic Map Base.'' \emph{Cartography} 11 (3): 163--74. \url{https://doi.org/10.1080/00690805.1980.10438102}.
-
-\leavevmode\hypertarget{ref-GTPCCD}{}%
-Hofmann, Heike, Lendie Follett, Mahbubul Majumder, and Dianne Cook.
-2012.
-``Graphical Tests for Power Comparison of Competing Designs.'' \emph{IEEE Transactions on Visualization and Computer Graphics} 18: 2441--8.
-
-\leavevmode\hypertarget{ref-CBATCC}{}%
-Kocmoud, C, and D House. 1998. ``A Constraint-based Approach to Constructing Continuous Cartograms.'' In \emph{Proc. Symp. Spatial Data Handling}, 236--46.
-
-\leavevmode\hypertarget{ref-VVSIALM}{}%
-Majumder, Mahbubul, Heike Hofmann, and Dianne Cook.
-2013.
-``Validation of Visual Statistical Inference, Applied to Linear Models.'' \emph{Journal of the American Statistical Association} 108 (503): 942--56.
-\url{https://doi.org/10.1080/01621459.2013.808157}.
-
-\leavevmode\hypertarget{ref-CDWCS}{}%
-Monmonier, Mark. 2005. ``Cartography: Distortions, World-views and Creative Solutions.'' \emph{Progress in Human Geography} 29 (2): 217--24. \url{https://doi.org/10.1191/0309132505ph540pr}.
-
-\leavevmode\hypertarget{ref-NAC}{}%
-Olson, Judy M. 1976. ``Noncontiguous Area Cartograms.'' \emph{The Professional Geographer} 28 (4): 371--80. \url{https://doi.org/10.1111/j.0033-0124.1976.00371.x}.
-
-\leavevmode\hypertarget{ref-RSCW}{}%
-Raisz, Erwin. 1963. ``Rectangular Statistical Cartograms of the World.'' Journal Article. \emph{Journal of Geography} 35 (1): 8--10. \url{https://doi.org/10.1080/00221343608987880}.
-
-\leavevmode\hypertarget{ref-RCore}{}%
-R Core Team. 2019. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
-
-\leavevmode\hypertarget{ref-GIIV}{}%
-Wickham, Hadley, Dianne Cook, Heike Hofmann, and Andreas Buja.
-2010.
-``Graphical Inference for Infovis.'' \emph{IEEE Transactions on Visualization and Computer Graphics (Proc.
-InfoVis '10)} 16 (6): 973--79.
+14. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
 

### 2020-01-11 paper/paper.Rmd
Appendix figures added, expanded accuracy

@@
 
-$$\mu = \frac{e^{\eta}}{1 + e^{\eta}}$$
+$$\mu = \frac{e^{\eta}}{1 + e^{\eta}}$$ \label{eq:transform}
 $$\eta = f(\tau_i,\delta_j)$$
-
-A similar model will be constructed for the efficiency, using a log time, and normal errors.
 
@@
 Fig.
-\ref{fig:detect-compare} displays the average detection rates for the two types of plot, separately for each trend model.
-Evaluations on the same data set are connected by a line segment.
-For both the Three Cities and All Cities trend models performance was substantially better for the hexagon tile map.
-Viewers detected the data plot substantially more often with the hexagon tile map.
+\ref{fig:detect-compare} displays the average detection rates for the two types of plot separately for each trend model.
+Each trend model was tested using four repetitions, evaluations on the same data set were seen as either choropleths or hexagon tile maps by each group as specified in Table.
+\ref{tab:exp-design}; the detection rates for each display are connected by a line segment.
+The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts.
 One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in the appendix [Lineups] section.
@@
 We expected that the choropleth map would be superior for the type of spatial pattern, but the data suggests the hexagon tile map performs slightly better, or equally as well.
-
-\ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
-This also gives the standard errors, the smallest standard deviation is the Three Cities trend model shown in a Choropleth display.
-This group had a very small detection rate of 0.038.
 
@@
 
+Table.
+\ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
+This also gives the standard errors, the smallest standard deviation for all sets of replicates is the Three Cities trend model shown in a Choropleth display.
+This group of displays had a very small detection rate of 0.04.
+The mean detection rate for the Three Cities trend model shown as choropleth map lineups was also the smallest at 0.39.
+The North West to South East (NW-SE) trend model unexpectedly had a higher mean detection rate for the hexagon tile map displays, but the difference in the means of detection rate was only 0.10.
+
 ```{r desc-stats, results = "asis"}
@@
 ```
+
+Table.
+\ref{tab:detect-glmer1} presents a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on the detection rate.
+The results support the summary from Fig.
+\ref{fig:detect-compare} and all terms are statistically significant despite the large standard deviations observed in Table.
+\ref{tab:desc-stats}.
+Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
+Allowing for the interaction effect, the difference in detection rate decreases for population related displays for a choroleth map lineup, but increases for a hexagon tile map display.
+The log odds of detection show in Table.
+\ref{tab:detect-glmer1} can be back transformed using \ref{eq:transform} after taking the sum of all terms for the trend and type of display that are of interest.
+For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to `r round(exp(0.461+0.0220)/(1+exp(0.461+0.0220)), 2)` from `r round(exp(0.0220)/(1+exp(0.0220)),2)` for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
+
+When a choropleth map display is used, the predicted detection rate for the Three Cities trend, `r round(exp(0.0220-3.43)/(1+exp(0.0220-3.43)),2)`; this is extremely low, especially compared to the NW-SE trend of `r round(exp(0.0220)/(1+exp(0.0220)),2)`.
+When the All Cities trend is presented in a choropleth display the predicted probability of detection is `r round(exp(0.0220-1.35)/(1+exp(0.0220-1.35)),2)`.
+The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend `r round(exp(0.461+0.0220-3.43+2.46)/(1+exp(0.461+0.0220-3.43+2.46)),2)` and All Cities trend `r round(exp(0.461+0.0220-1.35+1.17)/(1+exp(0.461+0.0220-1.35+1.17)),2)`.
 
@@
 
-Table.
-\ref{tab:detect-glmer1} is a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on detection rate.
-The results support the summary from Fig.
-\ref{fig:detect-compare}.
-All terms are statistically significant.
-Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
-For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to `r round(exp(0.461+0.0220)/(1+exp(0.461+0.0220)), 2)` from `r round(exp(0.0220)/(1+exp(0.0220)),2)` for choropleths.
-
-When a choropleth map display is used, the predicted detection rate for the Three Cities trend, `r round(exp(0.0220-3.43)/(1+exp(0.0220-3.43)),2)`, is extremely low, especially compared to  the NW-SE trend.
-When the All Cities trend is presented in a choropleth display the predicted probability of detection is `r round(exp(0.0220-1.35)/(1+exp(0.0220-1.35)),2)`.
-The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend `r round(exp(0.461+0.0220-3.43+2.46)/(1+exp(0.461+0.0220-3.43+2.46)),2)` and All Cities trend `r round(exp(0.461+0.0220-1.35+1.17)/(1+exp(0.461+0.0220-1.35+1.17)),2)`.
-
 ## Speed
@@
 Fig.
-\ref{fig:beeswarm} shows the time taken for participants to evaluate each lineup, separately for trend model, whether the data plot was detected or not, and type of plot, as horizontally jittered dot plots.
+\ref{fig:beeswarm} shows horizontally jittered dot plots to contrast the time taken by participants to evaluate each lineup when viewing each type of display.
+The time are also separated by trend model and whether the data plot was detected or not detected.
 The time taken to complete an evaluation ranged from milliseconds to 60 seconds.
-The average time taken for type of display is displayed as a large colored dot on each plot.
-There is little difference in the average time taken to read a choropleth or hexgon tile map.
-There is also very little difference in evaluation time whether the data plot was detected or not.
+The average time taken for type of display is shown as a large colored dot on each plot.
+when considering the heights of the green and orange dots, there is little difference in the average time taken to read a choropleth or hexgon tile map.
+Comparing the same coloured dot across each trend model row, there is a slight increase in the time taken to correctly detected the data plot in the hexagon tile map lineup, but little difference in evaluation time for the choropleth display.
+However, there were substantially less correct detections for choropleth lineups for the Three cities and All Cities trends.
 
@@
 
+Participants provided their level of certainty regarding their choice using a five point scale. 
+Unlike the accuracy and speed of reponses that were derived during the data processing phase, this was a subjective
+assessment by the participant prompted by the question: ‘How certain are you about your choice?’.
+Figure. \ref{certainty} shows that the
+
 ```{r certainty, fig.cap = "The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
@@
 ```
-
-Certainty levels are measured on a five point scale—they are subjective
-assessments by the participant ‘How certain are you about your choice?’.
 
@@
 
+```{r}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("figures/aus_nwse_6_hex.png")))
+```
+
 !["A North-West to South East trend was hidden in this lineup of hexagon tile map displays."](figures/aus_nwse_6_hex.png)
@@
 
-## Training {#training}
+## Training
 
 The participants were trained using three displays. There were relatively simple lineups and are shown in Fig.XXX.
-<!--
 
-\begin{figure}[!t] 
-\centering 
-\includegraphics[width=2.5in]{figures/fig8_training1.png}
-\caption{The training lineups of choropleth maps.}
-\label{training1} 
-\end{figure}
+```{r training1, results = "asis", fig.cap = "The training lineups of choropleth maps.", fig.width = 4, fig.height = 4}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("figures/fig8_training1.png")))
+```
 
-\begin{figure}[!t] 
-\centering 
-\includegraphics[width=2.5in]{figures/fig8_training1.png}
-\caption{The training lineups of hexagon tile maps.}
-\label{straining2} 
-\end{figure} 
--->
+```{r training2, results = "asis", fig.cap = "The training lineups of hexagon tile maps.", fig.width = 4, fig.height = 4}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("figures/fig8_training2.png")))
+```
 
@@
 The demonstrative images of the `shinydashboard` web application display the demographic and consent page in Figure
-\ref{fig:survey_demogs}.
+\ref{fig:survey-demogs}.
 
-<!--
+```{r survey-demogs, results = "asis", fig.cap = "The demographics questions tab of the shinydashboard survey application.", fig.width = 4, fig.height = 4}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("figures/survey_demogs.png")))
+```
 
-\begin{figure}[!t] 
-\centering 
-\includegraphics[width=6in]{figures/survey_demogs.png}
-\caption{The demographics questions tab of the shinydashboard survey application.}
-\label{survey_demogs} 
-\end{figure}
+```{r survey-hex, results = "asis", fig.cap = "An example of the hexagon tile map lineup shown in the survey tab of the shinydashboard app.", fig.width = 4, fig.height = 4}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("figures/survey_hex.png")))
+```
 
-\begin{figure}[!t] 
-\centering 
-\includegraphics[width=6in]{figures/survey_hex.png}
-\caption{An example of the hexagon tile map lineup shown in the survey tab of the shinydashboard app.}
-\label{survey_hex} 
-\end{figure}
-
-\begin{figure}[!t] 
-\centering 
-\includegraphics[width=6in]{figures/survey_choro.png}
-\caption{An example of the choropleth map lineup shown in the survey tab of the shinydashboard app.}
-\label{survey_choro} 
-\end{figure} 
--->
+```{r survey-choro, results = "asis", fig.cap = "An example of the choropleth map lineup shown in the survey tab of the shinydashboard app.", fig.width = 4, fig.height = 4}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("figures/survey_choro.png")))
+```
 

### 2020-01-11 paper/paper.tex
Appendix figures added, expanded accuracy

@@
 
-\[\mu = \frac{e^{\eta}}{1 + e^{\eta}}\]
+\[\mu = \frac{e^{\eta}}{1 + e^{\eta}}\] \label{eq:transform}
 \[\eta = f(\tau_i,\delta_j)\]
-
-A similar model will be constructed for the efficiency, using a log time, and normal errors.
 
@@
 Fig.
-\ref{fig:detect-compare} displays the average detection rates for the two types of plot, separately for each trend model.
-Evaluations on the same data set are connected by a line segment.
-For both the Three Cities and All Cities trend models performance was substantially better for the hexagon tile map.
-Viewers detected the data plot substantially more often with the hexagon tile map.
+\ref{fig:detect-compare} displays the average detection rates for the two types of plot separately for each trend model.
+Each trend model was tested using four repetitions, evaluations on the same data set were seen as either choropleths or hexagon tile maps by each group as specified in Table.
+\ref{tab:exp-design}; the detection rates for each display are connected by a line segment.
+The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts.
 One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in the appendix \protect\hyperlink{lineups}{Lineups} section.
@@
 \end{figure}
+
+Table.
+\ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
+This also gives the standard errors, the smallest standard deviation for all sets of replicates is the Three Cities trend model shown in a Choropleth display.
+This group of displays had a very small detection rate of 0.04.
+The mean detection rate for the Three Cities trend model shown as choropleth map lineups was also the smallest at 0.39.
+The North West to South East (NW-SE) trend model unexpectedly had a higher mean detection rate for the hexagon tile map displays, but the difference in the means of detection rate was only 0.10.
 
@@
 \end{table}
+
+Table.
+\ref{tab:detect-glmer1} presents a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on the detection rate.
+The results support the summary from Fig.
+\ref{fig:detect-compare} and all terms are statistically significant despite the large standard deviations observed in Table.
+\ref{tab:desc-stats}.
+Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
+Allowing for the interaction effect, the difference in detection rate decreases for population related displays for a choroleth map lineup, but increases for a hexagon tile map display.
+The log odds of detection show in Table.
+\ref{tab:detect-glmer1} can be back transformed using \ref{eq:transform} after taking the sum of all terms for the trend and type of display that are of interest.
+For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to 0.62 from 0.51 for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
+
+When a choropleth map display is used, the predicted detection rate for the Three Cities trend, 0.03; this is extremely low, especially compared to the NW-SE trend of 0.51.
+When the All Cities trend is presented in a choropleth display the predicted probability of detection is 0.21.
+The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend 0.38 and All Cities trend 0.58.
 
@@
 \end{table}
-
-Table.
-\ref{tab:detect-glmer1} is a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on detection rate.
-The results support the summary from Fig.
-\ref{fig:detect-compare}.
-All terms are statistically significant.
-Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
-For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to 0.62 from 0.51 for choropleths.
-
-When a choropleth map display is used, the predicted detection rate for the Three Cities trend, 0.03, is extremely low, especially compared to the NW-SE trend.
-When the All Cities trend is presented in a choropleth display the predicted probability of detection is 0.21.
-The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend 0.38 and All Cities trend 0.58.
 
@@
 
+\includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}
+
 \begin{figure}
@@
 
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/training1-1.pdf}
+\caption{\label{fig:training1}The training lineups of choropleth maps.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/training2-1.pdf}
+\caption{\label{fig:training2}The training lineups of hexagon tile maps.}
+\end{figure}
+
 \hypertarget{survey-application}{%
@@
 The demonstrative images of the \texttt{shinydashboard} web application display the demographic and consent page in Figure
-\ref{fig:survey_demogs}.
+\ref{fig:survey-demogs}.
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/survey-demogs-1.pdf}
+\caption{\label{fig:survey-demogs}The demographics questions tab of the shinydashboard survey application.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/survey-hex-1.pdf}
+\caption{\label{fig:survey-hex}An example of the hexagon tile map lineup shown in the survey tab of the shinydashboard app.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/survey-choro-1.pdf}
+\caption{\label{fig:survey-choro}An example of the choropleth map lineup shown in the survey tab of the shinydashboard app.}
+\end{figure}
 

### 2020-01-11 paper/paper.Rmd
certainty discussion

@@
 assessment by the participant prompted by the question: ‘How certain are you about your choice?’.
-Figure. \ref{certainty} shows that the
+Figure.
+\ref{certainty} shows the amount of times participants provided each level of certainty.
+This was separated for each combination of trend models and display type, and coloured depending on whether a participant correctly detected the data plot in the lineup.
+Participants chose 4 or 5 often when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
+This shows overconfidence in their detection ability when using a choropleth map display.
+Participants were less likely to be certain when their choice was incorrect and they were viewing a hexagon tile map.
+For each trend model, participants were more likely to doubt their choice and choose 1 or 2 in the hexagon tile map displays, even though many had made the correct choice.
 
@@
 ## Reason
+
+Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons. 
+"Colour trend across the areas" was the most common selection for NW-SE trend displays.
+The colour scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
+Due to the consisent colouring of rural areas in a choropleth display, the choice "All areas have similar colours" was most common reason.
+The All Cities displays coloured the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural colour consistency.
+
+The reasons used when viewing choropleth displays varied more than the hexagon tile map reasons.
+The hexagon tile map displays resulted in "Clusters of colour" as the most common choice made by participants.
+This response was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions.
+It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays.
+Due to the spatial covariance introduced in the smoothing, groups of similarly coloured hexagons were present in all of the hexagon tile map displays.
+All Cities and Three Cities distributions of real data trends had distinctly different patterns or red inner-city areas, while some of the plots in each lineup may have shared similar features.
+
+The choice "None of these reasons" was used as the default value to minimise noise from participants who did not select a response.
 
@@
 
-The most common choice made by participant was clusters, this response was expected when participants viewed the Hexagon display of the All Cities and Three Cities distributions.
-
-## Anomolies
+## Choices
 
@@
 
-One lineup had extremely similiar detection rates for the Choropleth and Hexagon displays.
-
-```{r}
-ggdraw() +
-  draw_plot(rasterGrob(readPNG("figures/aus_nwse_6_hex.png")))
-```
-
-!["A North-West to South East trend was hidden in this lineup of hexagon tile map displays."](figures/aus_nwse_6_hex.png)
-
-### Certainty
-
 Discussion
@@
 
-The participants were trained using three displays. There were relatively simple lineups and are shown in Fig.XXX.
+The participants were trained using three displays. There were relatively simple lineups and are shown in Fig. \ref{fig:training1} and Fig. \ref{fig:training2}.
 
@@
 
-The demonstrative images of the `shinydashboard` web application display the demographic and consent page in Figure
-\ref{fig:survey-demogs}.
+The demonstrative images of the `shinydashboard` web application display the demographic and consent page in Fig. \ref{fig:survey-demogs}.
 
@@
 
-![The lineup of choropleth map displays hides a distribution that affects all capital cities.](figures/aus_cities_3_geo.png)
+```{r cities-geo, results = "asis", fig.cap = "The lineup of choropleth map displays hides a distribution that affects all capital cities.", fig.width = 4, fig.height = 4}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("figures/aus_cities_3_geo.png")))
+```
 
-![The lineup of choropleth map displays shows a distribution that affects all capital cities.
+```{r cities-hex, results = "asis", fig.cap = "The lineup of choropleth map displays shows a distribution that affects all capital cities.
 The values for the inner city areas in the capital cities result in them being coloured red.
 However, the colour blue dominates the display as the large rural areas are filled.
-Replicate (2) for All Cities.](figures/aus_cities_3_hex.png)
+Replicate (2) for All Cities.", fig.width = 4, fig.height = 4}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("figures/aus_cities_3_hex.png")))
+```
 
-The values for the inner city areas in the capital cities result in them being coloured red.
+The higher values for the inner city areas in the capital cities result in them being coloured red.
 However, the colour blue dominates the display as the large rural areas are filled.
@@
 The same location holds the real data plot, the red city centres are now visible and surrounded by yellow, and then blue hexagons.
+For different reasons the participants were able to make the same correct choice.
 
@@
 
-```{r demogs, results = "asis"}
+```{r demogs, results = "asis", fig.cap = "The distribution of age groups of pariticpants."}
 # Create one record for each contributor, to examine demographics
@@
 dem_contribs %>% ggplot() + geom_bar(aes(age))
+```
 
-dem_contribs %>% count(gender) %>% knitr::kable(format = "latex", booktabs = TRUE)
+```{r gender, results = "asis", fig.cap = "The amount of participants who identify themselves by the pronouns He and She."}
+dem_contribs %>% mutate(Gender = gender) %>% 
+  count(Gender, name = "Amount") %>% knitr::kable(format = "latex", booktabs = TRUE)
+```
 
-dem_contribs %>% count(education) %>% knitr::kable(format = "latex", booktabs = TRUE)
+```{r education, results = "asis", fig.cap = "The highest level of education acheived by the participants "}
+dem_contribs %>%
+  mutate(Education = factor(education, levels = c("High School", "Bach", "Masters"), labels = c("High School Diploma", "Bachelors Degree", "Masters Degree"))) %>% 
+    count(Education, name =  "Amount") %>% knitr::kable(format = "latex", booktabs = TRUE)
 ```

### 2020-01-11 paper/paper.tex
certainty discussion

@@
 
+Participants provided their level of certainty regarding their choice using a five point scale.
+Unlike the accuracy and speed of reponses that were derived during the data processing phase, this was a subjective
+assessment by the participant prompted by the question: `How certain are you about your choice?'.
+Figure.
+\ref{certainty} shows the amount of times participants provided each level of certainty.
+This was separated for each combination of trend models and display type, and coloured depending on whether a participant correctly detected the data plot in the lineup.
+Participants chose 4 or 5 often when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
+This shows overconfidence in their detection ability when using a choropleth map display.
+Participants were less likely to be certain when their choice was incorrect and they were viewing a hexagon tile map.
+For each trend model, participants were more likely to doubt their choice and choose 1 or 2 in the hexagon tile map displays, even though many had made the correct choice.
+
 \begin{figure}
@@
 
-Certainty levels are measured on a five point scale---they are subjective
-assessments by the participant `How certain are you about your choice?'.
-
 \hypertarget{reason}{%
 \subsection{Reason}\label{reason}}
+
+Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons.
+``Colour trend across the areas'' was the most common selection for NW-SE trend displays.
+The colour scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
+Due to the consisent colouring of rural areas in a choropleth display, the choice ``All areas have similar colours'' was most common reason.
+The All Cities displays coloured the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural colour consistency.
+
+The reasons used when viewing choropleth displays varied more than the hexagon tile map reasons.
+The hexagon tile map displays resulted in ``Clusters of colour'' as the most common choice made by participants.
+This response was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions.
+It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays.
+Due to the spatial covariance introduced in the smoothing, groups of similarly coloured hexagons were present in all of the hexagon tile map displays.
+All Cities and Three Cities distributions of real data trends had distinctly different patterns or red inner-city areas, while some of the plots in each lineup may have shared similar features.
+
+The choice ``None of these reasons'' was used as the default value to minimise noise from participants who did not select a response.
 
@@
 
-The most common choice made by participant was clusters, this response was expected when participants viewed the Hexagon display of the All Cities and Three Cities distributions.
-
-\hypertarget{anomolies}{%
-\subsection{Anomolies}\label{anomolies}}
+\hypertarget{choices}{%
+\subsection{Choices}\label{choices}}
 
@@
 
-One lineup had extremely similiar detection rates for the Choropleth and Hexagon displays.
-
-\includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}
-
-\begin{figure}
-\centering
-\includegraphics{figures/aus_nwse_6_hex.png}
-\caption{``A North-West to South East trend was hidden in this lineup of hexagon tile map displays.''}
-\end{figure}
-
-\hypertarget{certainty-1}{%
-\subsubsection{Certainty}\label{certainty-1}}
-
 \hypertarget{discussion}{%
@@
 
-The demonstrative images of the \texttt{shinydashboard} web application display the demographic and consent page in Figure
-\ref{fig:survey-demogs}.
+The demonstrative images of the \texttt{shinydashboard} web application display the demographic and consent page in Fig. \ref{fig:survey-demogs}.
 
@@
 \centering
-\includegraphics{figures/aus_cities_3_geo.png}
-\caption{The lineup of choropleth map displays hides a distribution that affects all capital cities.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{figures/aus_cities_3_hex.png}
-\caption{The lineup of choropleth map displays shows a distribution that affects all capital cities.
+\includegraphics{paper_files/figure-latex/cities-geo-1.pdf}
+\caption{\label{fig:cities-geo}The lineup of choropleth map displays hides a distribution that affects all capital cities.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/cities-hex-1.pdf}
+\caption{\label{fig:cities-hex}The lineup of choropleth map displays shows a distribution that affects all capital cities.
 The values for the inner city areas in the capital cities result in them being coloured red.
@@
 
-The values for the inner city areas in the capital cities result in them being coloured red.
+The higher values for the inner city areas in the capital cities result in them being coloured red.
 However, the colour blue dominates the display as the large rural areas are filled.
@@
 
+\begin{figure}
+\centering
 \includegraphics{paper_files/figure-latex/demogs-1.pdf}
+\caption{\label{fig:demogs}The distribution of age groups of pariticpants.}
+\end{figure}
 
@@
 \toprule
-gender & n\\
+Gender & Amount\\
 \midrule
@@
 \toprule
-education & n\\
+Education & Amount\\
 \midrule
-Bach & 56\\
-High School & 23\\
-Masters & 13\\
+High School Diploma & 23\\
+Bachelors Degree & 56\\
+Masters Degree & 13\\
 \bottomrule

### 2020-01-11 paper/paper.Rmd
introduction

@@
 <!-- geographies on choropleth -->
-This study contrasts the use of two displays for geospatial statistics, the traditional choropleth map and an alternative tessellated hexagon tile map.
-The choropleth map is the common choice for visualising aggregated statistics and is familiar because of common administrative boundaries.
-A hexagon tile map forgoes the familiar boundaries, instead representing each geographic unit as an equally sized hexagon.
-This alternative display is suggested for communicating distributions that relate to the population values or density of the population in each geographic unit.
+This study compares the effectiveness of a new type of display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics.
+The choropleth map is the traditional  approach for visualising aggregated statistics across administrative boundaries.
+A hexagon tile map forgoes the familiar boundaries, in favor of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location.
+The hexagon tile map builds on existing displays, such as the cartogram, and tesselated hexagon displays.
+It differs in that it relaxes the requirement to have connected hexagons, and allows sparsely located hexagons.
+The algorithm to construct a hexagon tile map is available in the R package sugarbag (XXX ref).
+This type of display may be useful for other countries, and other purposes.
+
+The hexagon tile map was designed for Australia, motivated by a need to display spatial statistics for a new Australian Cancer Atlas.
+None of the existing approaches for creating cartograms or hexagon tiling perform well for the Australian landscape, which has vast open spaces and concentrations of population in small regions clustered on the coastlines.
+
+<!-- This alternative display is suggested for communicating distributions that relate to the population values or density of the population in each geographic unit.
 This study uses the lineup protocol for visual inference testing of the recognition of spatial distributions.
@@
 =============
-
-<!-- Find a new display for the Cancer Atlas -->
+!-- Find a new display for the Cancer Atlas --
 
 ## The Australian Cancer Atlas
+-->
 
-The Australian Cancer Atlas is an online interactive web tool created to explore the burden of cancer on Australian communities. There are many cancer types to be explored individually or aggregated. 
+The Australian Cancer Atlas (XXX ref) is an online interactive web tool created to explore the burden of cancer on Australian communities.
+There are many cancer types to be explored individually or aggregated.
+The Australian Cancer Atlas allows users to explore the patterns in the distributions of cancer statistics over the geographic space of Australia.
+It uses a choropleth map display and diverging colour scheme to draw attention to relationships between neighbouring areas.
+The hexagon tile map may be a useful alternative display for the atlas.
+
+The experiment was conducted using the lineup protocol, a visual inference procedure (XXX ref), to objectively test the effectiveness of the two displays.
+
+The paper is organised as follows.
+The next section discusses the background of georgraphic data display ane visual inference procedures.
+Section XXX describes the methods for conducting the experiment and analysing the results.
+The results are summarized in Section XXX.
+
+<!--
 The Atlas examines Australian communities at the Statistical Areas at Level 2 (SA2) [@abs2016] used by the Australian Bureau of Statistics.
@@
 It communicates the value of the statistic for each SA2 geographic unit through colour, by filling the areas using the diverging colour scheme ranging from dark blue to red.
-The Australian Cancer Atlas allows users to explore the patterns in the distributions of cancer statistics over the geographic space of Australia.
-It uses a choropleth map display and diverging colour scheme to draw attention to relationships between neighbouring areas.
+-->
 
@@
 
+Acknowledgment
+==============
+
+The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualisations.
+They would also like to thank Kerrie Mengersen and Dr.
+Earl Duncan for suggestions and comments.
+
+Ethics approval for the online survey was granted by QUT’s Ethics Committee (Ethics Application Number: 1900000991).
+All applicants provided informed consent in line with QUT regulations prior to participating in this research.
+
+References {#references .numbered}
+==========
+
+<!-- An example of a floating figure using the graphicx package. -->
+<!-- Note that \label must occur AFTER (or within) \caption. -->
+<!-- For figures, \caption should occur after the \includegraphics. -->
+<!-- Note that IEEEtran v1.7 and later has special internal code that -->
+<!-- is designed to preserve the operation of \label within \caption -->
+<!-- even when the captionsoff option is in effect. However, because -->
+<!-- of issues like this, it may be the safest practice to put all your -->
+<!-- \label just after \caption rather than within \caption{}. -->
+
+<!-- Reminder: the "draftcls" or "draftclsnofoot", not "draft", class -->
+<!-- option should be used if it is desired that the figures are to be -->
+<!-- displayed while in draft mode. -->
+
+<!-- \begin{figure}[!t] -->
+<!-- \centering -->
+<!-- \includegraphics[width=2.5in]{myfigure} -->
+<!-- where an .eps filename suffix were assumed under latex,  -->
+<!-- and a .pdf suffix were assumed for pdflatex; or what has been declared -->
+<!-- via \DeclareGraphicsExtensions. -->
+<!-- \caption{Simulation results for the network.} -->
+<!-- \label{fig_sim} -->
+<!-- \end{figure} -->
+
+<!-- Note that the IEEE typically puts floats only at the top, even when this -->
+<!-- results in a large percentage of a column being occupied by floats. -->
+
+<!-- An example of a double column floating figure using two subfigures. -->
+<!-- (The subfig.sty package must be loaded for this to work.) -->
+<!-- The subfigure \label commands are set within each subfloat command, -->
+<!-- and the \label for the overall figure must come after \caption. -->
+<!-- \hfil is used as a separator to get equal spacing. -->
+<!-- Watch out that the combined width of all the subfigures on a  -->
+<!-- line do not exceed the text width or a line break will occur. -->
+
+<!-- \begin{figure*}[!t] -->
+<!-- \centering -->
+<!-- \subfloat[Case I]{\includegraphics[width=2.5in]{box}% -->
+<!-- \label{fig_first_case}} -->
+<!-- \hfil -->
+<!-- \subfloat[Case II]{\includegraphics[width=2.5in]{box}% -->
+<!-- \label{fig_second_case}} -->
+<!-- \caption{Simulation results for the network.} -->
+<!-- \label{fig_sim} -->
+<!-- \end{figure*} -->
+
+<!-- Note that often IEEE papers with subfigures do not employ subfigure -->
+<!-- captions (using the optional argument to \subfloat[]), but instead will -->
+<!-- reference/describe all of them (a), (b), etc., within the main caption. -->
+<!-- Be aware that for subfig.sty to generate the (a), (b), etc., subfigure -->
+<!-- labels, the optional argument to \subfloat must be present. If a -->
+<!-- subcaption is not desired, just leave its contents blank, -->
+<!-- e.g., \subfloat[]. -->
+
+\newpage
 Appendix
@@
 
-## Contributor Performance
+## Individual performance
 
@@
 ```
-
-Acknowledgment
-==============
-
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualisations.
-They would also like to thank Kerrie Mengersen and Dr.
-Earl Duncan for suggestions and comments.
-
-Ethics approval for the online survey was granted by QUT’s Ethics Committee (Ethics Application Number: 1900000991).
-All applicants provided informed consent in line with QUT regulations prior to participating in this research.
-
-\newpage
-References {#references .numbered}
-==========
-
-<!-- An example of a floating figure using the graphicx package. -->
-<!-- Note that \label must occur AFTER (or within) \caption. -->
-<!-- For figures, \caption should occur after the \includegraphics. -->
-<!-- Note that IEEEtran v1.7 and later has special internal code that -->
-<!-- is designed to preserve the operation of \label within \caption -->
-<!-- even when the captionsoff option is in effect. However, because -->
-<!-- of issues like this, it may be the safest practice to put all your -->
-<!-- \label just after \caption rather than within \caption{}. -->
-
-<!-- Reminder: the "draftcls" or "draftclsnofoot", not "draft", class -->
-<!-- option should be used if it is desired that the figures are to be -->
-<!-- displayed while in draft mode. -->
-
-<!-- \begin{figure}[!t] -->
-<!-- \centering -->
-<!-- \includegraphics[width=2.5in]{myfigure} -->
-<!-- where an .eps filename suffix were assumed under latex,  -->
-<!-- and a .pdf suffix were assumed for pdflatex; or what has been declared -->
-<!-- via \DeclareGraphicsExtensions. -->
-<!-- \caption{Simulation results for the network.} -->
-<!-- \label{fig_sim} -->
-<!-- \end{figure} -->
-
-<!-- Note that the IEEE typically puts floats only at the top, even when this -->
-<!-- results in a large percentage of a column being occupied by floats. -->
-
-<!-- An example of a double column floating figure using two subfigures. -->
-<!-- (The subfig.sty package must be loaded for this to work.) -->
-<!-- The subfigure \label commands are set within each subfloat command, -->
-<!-- and the \label for the overall figure must come after \caption. -->
-<!-- \hfil is used as a separator to get equal spacing. -->
-<!-- Watch out that the combined width of all the subfigures on a  -->
-<!-- line do not exceed the text width or a line break will occur. -->
-
-<!-- \begin{figure*}[!t] -->
-<!-- \centering -->
-<!-- \subfloat[Case I]{\includegraphics[width=2.5in]{box}% -->
-<!-- \label{fig_first_case}} -->
-<!-- \hfil -->
-<!-- \subfloat[Case II]{\includegraphics[width=2.5in]{box}% -->
-<!-- \label{fig_second_case}} -->
-<!-- \caption{Simulation results for the network.} -->
-<!-- \label{fig_sim} -->
-<!-- \end{figure*} -->
-
-<!-- Note that often IEEE papers with subfigures do not employ subfigure -->
-<!-- captions (using the optional argument to \subfloat[]), but instead will -->
-<!-- reference/describe all of them (a), (b), etc., within the main caption. -->
-<!-- Be aware that for subfig.sty to generate the (a), (b), etc., subfigure -->
-<!-- labels, the optional argument to \subfloat must be present. If a -->
-<!-- subcaption is not desired, just leave its contents blank, -->
-<!-- e.g., \subfloat[]. -->

### 2020-01-11 paper/paper.tex
introduction

@@
 % Pandoc header
-\usepackage{graphicx}
 \usepackage{booktabs}
@@
 \usepackage{xcolor}
+
+\usepackage{graphicx}
 
@@
 
-This study contrasts the use of two displays for geospatial statistics, the traditional choropleth map and an alternative tessellated hexagon tile map.
-The choropleth map is the common choice for visualising aggregated statistics and is familiar because of common administrative boundaries.
-A hexagon tile map forgoes the familiar boundaries, instead representing each geographic unit as an equally sized hexagon.
-This alternative display is suggested for communicating distributions that relate to the population values or density of the population in each geographic unit.
-This study uses the lineup protocol for visual inference testing of the recognition of spatial distributions.
-The Australian Cancer Atlas explores spatial distributions of cancer incidence and the burden on Australian communities.
-The spatial distributions of the cancers explored in this atlas inspired the trend models presented to participants in this study.
-
-\hypertarget{motivation}{%
-\section{Motivation}\label{motivation}}
-
-\hypertarget{the-australian-cancer-atlas}{%
-\subsection{The Australian Cancer Atlas}\label{the-australian-cancer-atlas}}
-
-The Australian Cancer Atlas is an online interactive web tool created to explore the burden of cancer on Australian communities. There are many cancer types to be explored individually or aggregated.
-The Atlas examines Australian communities at the Statistical Areas at Level 2 (SA2) {[}\protect\hyperlink{ref-abs2016}{1}{]} used by the Australian Bureau of Statistics.
-Bayesian spatial smoothing was applied to integrate the values of neighbouring areas.
-Spatial smoothing protects the privacy and gives stability to the estimated amounts in each SA2.
-Users of the Atlas can explore the difference of the statistic of each SA2 from the Australian average, for both diagnoses (Standardised Incidence Rates) and excess deaths.
-It communicates the value of the statistic for each SA2 geographic unit through colour, by filling the areas using the diverging colour scheme ranging from dark blue to red.
+This study compares the effectiveness of a new type of display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics.
+The choropleth map is the traditional approach for visualising aggregated statistics across administrative boundaries.
+A hexagon tile map forgoes the familiar boundaries, in favor of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location.
+The hexagon tile map builds on existing displays, such as the cartogram, and tesselated hexagon displays.
+It differs in that it relaxes the requirement to have connected hexagons, and allows sparsely located hexagons.
+
+The hexagon tile map was designed for Australia, motivated by a need to display spatial statistics for a new Australian Cancer Atlas.
+None of the existing approaches for creating cartograms or hexagon tiling perform well for the Australian landscape, which has vast open spaces and concentrations of population in small regions clustered on the coastlines.
+
+The Australian Cancer Atlas (XXX ref) is an online interactive web tool created to explore the burden of cancer on Australian communities.
+There are many cancer types to be explored individually or aggregated.
 The Australian Cancer Atlas allows users to explore the patterns in the distributions of cancer statistics over the geographic space of Australia.
 It uses a choropleth map display and diverging colour scheme to draw attention to relationships between neighbouring areas.
+The hexagon tile map may be a useful alternative display for the atlas.
+
+The algorithm to construct a hexagon tile map is available in the R package sugarbag (XXX ref). This type of display may be useful for other countries, and other purposes.
+
+The paper is organised as follows. The next section
 
@@
 Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic.
-However, using a choropleth map base introduces biases when considering population related distributions {[}\protect\hyperlink{ref-CBATCC}{2}{]}.
+However, using a choropleth map base introduces biases when considering population related distributions {[}\protect\hyperlink{ref-CBATCC}{1}{]}.
 Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
@@
 When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
-This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention {[}\protect\hyperlink{ref-CTTMB}{3}{]}.
-An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas {[}\protect\hyperlink{ref-NISCC}{4}{]}.
+This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention {[}\protect\hyperlink{ref-CTTMB}{2}{]}.
+An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas {[}\protect\hyperlink{ref-NISCC}{3}{]}.
 This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
@@
 The transformation begins with a choropleth map, and the values of a statistic such as population, for each geographic unit.
-There are several algorithms for transformation {[}\protect\hyperlink{ref-ACTUC}{5}{]}, {[}\protect\hyperlink{ref-CBATCC}{2}{]}; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
+There are several algorithms for transformation {[}\protect\hyperlink{ref-ACTUC}{4}{]}, {[}\protect\hyperlink{ref-CBATCC}{1}{]}; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
 The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units.
@@
 Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units.
-The non-contiguous cartgoram method {[}\protect\hyperlink{ref-NAC}{6}{]} keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics.
+The non-contiguous cartgoram method {[}\protect\hyperlink{ref-NAC}{5}{]} keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics.
 This method disconnects areas when shrinking boundaries, and breaks the spatial relationship between areas.
 However, the empty space created emphasises the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
-The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{5}{]} is another method that does not retain the boundaries of geographic units.
+The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{4}{]} is another method that does not retain the boundaries of geographic units.
 Each unit becomes one circle on the cartogram display; the circles are sized according to the value of a the statistic, such as population.
 The neighbour relationships can be illustrated by connecting the boundaries of the circles.
-A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{7}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{8}{]}.
+A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{6}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{7}{]}.
 These cartogram methods all allow two variables to be shown in the single display. these methods are discussed further in XXX cite review paper
@@
 Where the guilty data set contains structure, and the innocents data sets do not.
-In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the innocents {[}\protect\hyperlink{ref-GTPCCD}{9}{]}.
+In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the innocents {[}\protect\hyperlink{ref-GTPCCD}{8}{]}.
 The guilty data is identified as different from the innocent data with probability \(1/m\), where \(m\) is the number of null plots plus 1 to account account for the guilty data set.
@@
 The lineup protocol can be used in a variety of testing scenarios for visualisations.
-{[}\protect\hyperlink{ref-GIIV}{10}{]} suggest the choropleth map for testing spatial structure in a data set.
+{[}\protect\hyperlink{ref-GIIV}{9}{]} suggest the choropleth map for testing spatial structure in a data set.
 The lineup protocol allows for flexibility in the definition of null data.
@@
 The data collection took place using a secure link between the survey web application and the googlesheet used to store results.
-The application would first connect to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{11}{]} R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
+The application would first connect to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{10}{]} R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
 
@@
 
-The choropleth map was used as the comparative visualisation for presenting the lineups {[}\protect\hyperlink{ref-VVSIALM}{12}{]} as this is the common display for spatial cancer data.
+The choropleth map was used as the comparative visualisation for presenting the lineups {[}\protect\hyperlink{ref-VVSIALM}{11}{]} as this is the common display for spatial cancer data.
 Geographic distributions usually have some degree of spatial autcorrelation between neighbours.
@@
 
-The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R {[}\protect\hyperlink{ref-RCore}{13}{]}.
+The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R {[}\protect\hyperlink{ref-RCore}{12}{]}.
 
@@
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R {[}\protect\hyperlink{ref-RCore}{13}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{14}{]} package implements generalised linear mixed effect models.
+The R {[}\protect\hyperlink{ref-RCore}{12}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{13}{]} package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 
-Computation will be done using R {[}\protect\hyperlink{ref-RCore}{13}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{14}{]}.
+Computation will be done using R {[}\protect\hyperlink{ref-RCore}{12}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{13}{]}.
 
@@
 
+\hypertarget{acknowledgment}{%
+\section{Acknowledgment}\label{acknowledgment}}
+
+The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualisations.
+They would also like to thank Kerrie Mengersen and Dr.~Earl Duncan for suggestions and comments.
+
+Ethics approval for the online survey was granted by QUT's Ethics Committee (Ethics Application Number: 1900000991).
+All applicants provided informed consent in line with QUT regulations prior to participating in this research.
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\newpage
+
 \hypertarget{appendix}{%
@@
 
-\hypertarget{contributor-performance}{%
-\subsection{Contributor Performance}\label{contributor-performance}}
+\hypertarget{individual-performance}{%
+\subsection{Individual performance}\label{individual-performance}}
 
@@
 
-\hypertarget{acknowledgment}{%
-\section{Acknowledgment}\label{acknowledgment}}
-
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualisations.
-They would also like to thank Kerrie Mengersen and Dr.~Earl Duncan for suggestions and comments.
-
-Ethics approval for the online survey was granted by QUT's Ethics Committee (Ethics Application Number: 1900000991).
-All applicants provided informed consent in line with QUT regulations prior to participating in this research.
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-abs2016}{}%
-1. (2018) Australian Statistical Geography Standard (ASGS). Australian Bureau of Statistics
-
 \leavevmode\hypertarget{ref-CBATCC}{}%
-2. Kocmoud C, House D (1998) A Constraint-based Approach to Constructing Continuous Cartograms. In: Proc. Symp. Spatial data handling. pp 236--246
+1. Kocmoud C, House D (1998) A Constraint-based Approach to Constructing Continuous Cartograms. In: Proc. Symp. Spatial data handling. pp 236--246
 
 \leavevmode\hypertarget{ref-CTTMB}{}%
-3. Griffin TL (1980) Cartographic Transformation of the Thematic Map Base. Cartography 11:163--174
+2. Griffin TL (1980) Cartographic Transformation of the Thematic Map Base. Cartography 11:163--174
 
 \leavevmode\hypertarget{ref-NISCC}{}%
-4. Dent BD (1972) A Note on the Importance of Shape in Cartogram Communication. Journal of Geography 71:393--401
+3. Dent BD (1972) A Note on the Importance of Shape in Cartogram Communication. Journal of Geography 71:393--401
 
 \leavevmode\hypertarget{ref-ACTUC}{}%
-5. Dorling D (2011) Area Cartograms: Their Use and Creation. In: Concepts and techniques in modern geography (catmog). pp 252--260
+4. Dorling D (2011) Area Cartograms: Their Use and Creation. In: Concepts and techniques in modern geography (catmog). pp 252--260
 
 \leavevmode\hypertarget{ref-NAC}{}%
-6. Olson JM (1976) Noncontiguous Area Cartograms. The Professional Geographer 28:371--380
+5. Olson JM (1976) Noncontiguous Area Cartograms. The Professional Geographer 28:371--380
 
 \leavevmode\hypertarget{ref-RSCW}{}%
-7. Raisz E (1963) Rectangular Statistical Cartograms of the World. Journal of Geography 35:8--10
+6. Raisz E (1963) Rectangular Statistical Cartograms of the World. Journal of Geography 35:8--10
 
 \leavevmode\hypertarget{ref-CDWCS}{}%
-8. Monmonier M (2005) Cartography: Distortions, World-views and Creative Solutions. Progress in Human Geography 29:217--224
+7. Monmonier M (2005) Cartography: Distortions, World-views and Creative Solutions. Progress in Human Geography 29:217--224
 
 \leavevmode\hypertarget{ref-GTPCCD}{}%
-9. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448
+8. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448
 
 \leavevmode\hypertarget{ref-GIIV}{}%
-10. Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979
+9. Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979
 
 \leavevmode\hypertarget{ref-sheets}{}%
-11. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
+10. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
 
 \leavevmode\hypertarget{ref-VVSIALM}{}%
-12. Majumder M, Hofmann H, Cook D (2013) Validation of visual statistical inference, applied to linear models. Journal of the American Statistical Association 108:942--956
+11. Majumder M, Hofmann H, Cook D (2013) Validation of visual statistical inference, applied to linear models. Journal of the American Statistical Association 108:942--956
 
 \leavevmode\hypertarget{ref-RCore}{}%
-13. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+12. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
 
 \leavevmode\hypertarget{ref-lme4}{}%
-14. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
+13. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
 

### 2020-01-12 paper/paper.Rmd
move supplementary materials to individual docs

--- 2020-01-11 paper/paper.Rmd
@@
 library(grid)
-library(lubridate)
-library(broom)
-library(readxl)
 library(lme4)
@@
 library(RColorBrewer)
-library(visreg)
-library(emmeans)
 library(knitr)
@@
 
-## Choices
-
-The choices made by participants are examined in Fig. \ref{fig:choices}.
-Participants were misled by the choropleth display, but not the hexagon display for All Cities displays except (2).
-The maps with a North West to South East trend was chosen with much greater frequency in all displays.
-All of Three Cities displays, except (4), were detected in the hexagon display.
-All except one lineup had at least one participant select the correct map in the lineup as shown in Fig.
-\ref{fig:choices}.
-
-```{r choices, fig.cap = "Each facet is associated with one lineup, the height of the points show the proportion of the participants that made each choice when considering each lineup.
-The points coloured orange show the map which contained a trend model, these are the correct choices.
-The numbers differentiate the replicates of each trend model and type of map display.
-Participants were able to select 0 to indicate they did not want to choose a map.", fig.height = 8, fig.width =6}
-d %>% 
-  count(type, trend, choice, replicate, choice, detect_f) %>% 
-  group_by(type, trend, replicate) %>% 
-  mutate(prop = n/sum(n)) %>% 
-  mutate(repl = paste("Rep:", replicate, ":\n", type,  sep = "")) %>%
-  mutate(bottom = 0) %>% 
-  ggplot() + 
-  geom_point(aes(x = choice, y = prop, color = detect_f), size = 3) + 
-  geom_segment(aes(x = choice, xend = choice,y = bottom, yend = prop, colour = detect_f), size = 1) +
-  facet_grid(repl ~ trend, 
-    drop = TRUE, as.table = TRUE, scales = "free_y") +
-  labs(x = "Choice of plot in lineup", y = "Amount of choices") +
-  scale_colour_manual(values = detect_colours) +
-  scale_x_continuous(breaks = seq(from = 0, to = 12)) +
-  scale_y_continuous(breaks = seq(from = 0.0, to = 1.0, by = 0.1)) +
-  theme(legend.position = "bottom") + 
-  guides(colour = FALSE, fill = FALSE) +
-  theme(strip.text.y = element_text(angle = 0))
-```
-
 Discussion
@@
 ============
-
-## Training
-
-The participants were trained using three displays. There were relatively simple lineups and are shown in Fig. \ref{fig:training1} and Fig. \ref{fig:training2}.
-
-```{r training1, results = "asis", fig.cap = "The training lineups of choropleth maps.", fig.width = 4, fig.height = 4}
-ggdraw() +
-  draw_plot(rasterGrob(readPNG("figures/fig8_training1.png")))
-```
-
-```{r training2, results = "asis", fig.cap = "The training lineups of hexagon tile maps.", fig.width = 4, fig.height = 4}
-ggdraw() +
-  draw_plot(rasterGrob(readPNG("figures/fig8_training2.png")))
-```
-
-## Survey application
-
-The survey application was hosted on a website external to the Figure-Eight platform.
-Following suggestions in the documentation, the information and training required for a participant to make a decision was included  that survey
-
-The demonstrative images of the `shinydashboard` web application display the demographic and consent page in Fig. \ref{fig:survey-demogs}.
-
-```{r survey-demogs, results = "asis", fig.cap = "The demographics questions tab of the shinydashboard survey application.", fig.width = 4, fig.height = 4}
-ggdraw() +
-  draw_plot(rasterGrob(readPNG("figures/survey_demogs.png")))
-```
-
-```{r survey-hex, results = "asis", fig.cap = "An example of the hexagon tile map lineup shown in the survey tab of the shinydashboard app.", fig.width = 4, fig.height = 4}
-ggdraw() +
-  draw_plot(rasterGrob(readPNG("figures/survey_hex.png")))
-```
-
-```{r survey-choro, results = "asis", fig.cap = "An example of the choropleth map lineup shown in the survey tab of the shinydashboard app.", fig.width = 4, fig.height = 4}
-ggdraw() +
-  draw_plot(rasterGrob(readPNG("figures/survey_choro.png")))
-```
-
-## Lineups
-
-Replicate 3 of the All Cities distribution is shown in Figures .
-The same data set is shown in both displays, the difference is the land area of each SA3 is coloured in the choropleth and the hexagon representing the SA3 is coloured in the Hexagon Tile Map.
-Many maps in the Choropleth lineup (a) are coloured yellow, two are half light blue, and two are obviously blue.
-Only one of the maps looks red.
-
-Lineups were created using the Australian Statistical Areas at Level 3.
-
-```{r cities-geo, results = "asis", fig.cap = "The lineup of choropleth map displays hides a distribution that affects all capital cities.", fig.width = 4, fig.height = 4}
-ggdraw() +
-  draw_plot(rasterGrob(readPNG("figures/aus_cities_3_geo.png")))
-```
-
-```{r cities-hex, results = "asis", fig.cap = "The lineup of choropleth map displays shows a distribution that affects all capital cities.
-The values for the inner city areas in the capital cities result in them being coloured red.
-However, the colour blue dominates the display as the large rural areas are filled.
-Replicate (2) for All Cities.", fig.width = 4, fig.height = 4}
-ggdraw() +
-  draw_plot(rasterGrob(readPNG("figures/aus_cities_3_hex.png")))
-```
-
-The higher values for the inner city areas in the capital cities result in them being coloured red.
-However, the colour blue dominates the display as the large rural areas are filled.
-There were no other choropleth maps that were coloured as blue as map (3).
-This meant the detection rate was quite high, participants were able to select the correct distribution without being able to see the values of the capital cities.
-The same data showed in the hexagon tile map display shows varied distributions across the lineup.
-They are more diverse in colour than the choropleth counterparts.
-The same location holds the real data plot, the red city centres are now visible and surrounded by yellow, and then blue hexagons.
-For different reasons the participants were able to make the same correct choice.
 
@@
 The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualisations.
-They would also like to thank Kerrie Mengersen and Dr.
-Earl Duncan for suggestions and comments.
+They would also like to thank Distinguished Professor Kerrie Mengersen and Doctor Earl Duncan for suggestions and comments.
+
+The source code to produce this document can be found on [GitHub](https://github.com/srkobakian/experiment/tree/master/paper).
+Supplementary materials have been included to discuss the survey procedures,
+
+The analysis of the work was completed in R [@RCore] with the use of the following packages:
+For document creation: rmarkdown, rticles, knitr.
+For lineup creation and data analysis: tidyverse, nullabor, ggthemes, RcolorBrewer.
+For image displays: cowplot, png, grid
+
+For modeling and presentation of models: lme4, kableExtra
 

### 2020-01-12 paper/supplementary/lineups.Rmd
move supplementary materials to individual docs

---
title: "Visual Inference Lineups"
author: "Stephanie Kobakian and Dianne Cook"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r data}
library(tidyverse)
library(cowplot)
library(png)
library(grid)
library(lme4)
library(ggthemes)
library(RColorBrewer)
library(knitr)
library(kableExtra)

trend_colours <- c(
  "NW-SE" = "#B2DF8A",
  "Three Cities" = "#A6CEE3",
  "All Cities" = "#1F78B4")

type_colours <- c(
  "Choro." = "#fcae91",
  "Hex." = "#a50f15")

detect_f_colours <- c(
  "No" = "#66C2A5",
  "Yes" = "#FC8D62")

detect_colours <- c(
  "Detected? No" = "#66C2A5",
  "Detected? Yes" = "#FC8D62")

  # Downloaded data
d <- read_xlsx("../data/experiment-export.xlsx", sheet=2) %>%
  filter(!is.na(contributor)) %>%
  mutate(contributor = factor(contributor))

# Check data set 
# Need to clean multiple entries, 48, 24
# remove duplicated entries due to submit button
d <- d %>% group_by(group, contributor, image_name) %>%
  slice(1) %>% ungroup() %>% 
  arrange(group, contributor, plot_order)

# Remove contributors who did not provide answers to most questions
keep <- d %>% count(contributor, sort = TRUE) %>% filter(n > 10)
d <- d %>% 
  filter(contributor %in% keep$contributor) %>%
  filter(contributor != "1234567890")

# Remove contributors who did not provide any choices
bad_contribs <- d %>% group_by(contributor) %>% 
  summarise(sum0 = sum(choice)) %>% 
  filter(sum0 == 0) %>% 
  pull(contributor)

d <- d %>% 
  filter(!(contributor %in% bad_contribs))

n_contributors <- d %>% count(contributor, sort=TRUE) %>% 
  summarise(n_contributors = length(contributor))

d <- d %>% mutate(certainty = factor(as.character(certainty),
  levels = c("1", "2", "3", "4","5"), ordered=TRUE))
```

```{r reps}
replicate <- tibble(image_name = c("aus_cities_12_geo.png", "aus_cities_12_hex.png", 
                                   "aus_cities_3_geo.png", "aus_cities_3_hex.png",
                                   "aus_cities_4_geo.png", "aus_cities_4_hex.png",
                                   "aus_cities_9_geo.png", "aus_cities_9_hex.png",
                                   "aus_nwse_2_geo.png", "aus_nwse_2_hex.png",
                                   "aus_nwse_3_geo.png", "aus_nwse_3_hex.png",
                                   "aus_nwse_5_geo.png", "aus_nwse_5_hex.png",
                                   "aus_nwse_6_geo.png", "aus_nwse_6_hex.png",
                                   "aus_three_12_geo.png", "aus_three_12_hex.png",
                                   "aus_three_5_geo.png", "aus_three_5_hex.png",
                                   "aus_three_8_geo.png", "aus_three_8_hex.png",
                                   "aus_three_9_geo.png", "aus_three_9_hex.png"),
                    replicate = c(1, 1, 2, 2, 3, 3, 4, 4, 
                                  1, 1, 2, 2, 3, 3, 4, 4,
                                  1, 1, 2, 2, 3, 3, 4, 4))
# Add rep info to data
d <- d %>% left_join(., replicate, by = "image_name")
```

```{r pdetection_group}
# Tidy for analysis
d <- d %>% 
  separate(image_name, c("nothing", "trend", "location", "type", "extra"), remove = FALSE) %>%
  select(-nothing, -extra) %>%
  mutate(location = as.numeric(location), 
    # detect measures the accuracy of the choice
         detect = ifelse(location == choice, 1, 0)) %>% 
  mutate(trend = case_when(
    trend == "nwse" ~ "NW-SE",
    trend == "cities" ~ "All Cities",
    trend == "three" ~ "Three Cities")) %>% 
  mutate(trend = fct_relevel(trend, "NW-SE","Three Cities","All Cities")) %>% 
  mutate(type = case_when(
    type == "hex" ~"Hex.",
    TRUE~"Choro.")) %>% 
    mutate(detect_f = factor(detect, levels = c(0,1), labels = c("Detected? No", "Detected? Yes")))

plots <- d %>% group_by(group, trend, type, location) %>%
  # pdetect measures the aggregated accuracy of the choices
  summarise(pdetect = length(detect[detect == 1])/length(detect)) 
```

## Lineups

The choices made by participants are examined in Fig. \ref{fig:choices}.
Participants were misled by the choropleth display, but not the hexagon display for All Cities displays except (2). The maps with a North West to South East trend was chosen with much greater frequency in all displays. All of Three Cities displays, except (4), were detected in the hexagon display. All except one lineup had at least one participant select the correct map in the lineup as shown in Fig. \ref{fig:choices}.

```{r choices, fig.cap = "Each facet is associated with one lineup, the height of the points show the proportion of the participants that made each choice when considering each lineup. The points coloured orange show the map which contained a trend model, these are the correct choices. The numbers differentiate the replicates of each trend model and type of map display. Participants were able to select 0 to indicate they did not want to choose a map.", fig.height = 8, fig.width =6}
d %>% 
  count(type, trend, choice, replicate, choice, detect_f) %>% 
  group_by(type, trend, replicate) %>% 
  mutate(prop = n/sum(n)) %>% 
  mutate(repl = paste("Rep:", replicate, ":\n", type,  sep = "")) %>%
  mutate(bottom = 0) %>% 
  ggplot() + 
  geom_point(aes(x = choice, y = prop, color = detect_f), size = 3) + 
  geom_segment(aes(x = choice, xend = choice,y = bottom, yend = prop, colour = detect_f), size = 1) +
  facet_grid(repl ~ trend, 
    drop = TRUE, as.table = TRUE, scales = "free_y") +
  labs(x = "Choice of plot in lineup", y = "Amount of choices") +
  scale_colour_manual(values = detect_colours) +
  scale_x_continuous(breaks = seq(from = 0, to = 12)) +
  scale_y_continuous(breaks = seq(from = 0.0, to = 1.0, by = 0.1)) +
  theme(legend.position = "bottom") + 
  guides(colour = FALSE, fill = FALSE) +
  theme(strip.text.y = element_text(angle = 0))
```

# All cities Example 1:

The same data set is shown in both displays, the difference is the land area of each SA3 is coloured in the choropleth and the hexagon representing the SA3 is coloured in the Hexagon Tile Map.

Lineups were created using the Australian Statistical Areas at Level 3.

Replicate 3 of the All Cities distribution is shown in Fig. \ref{fig:cities-geo4} and Fig. \ref{fig:cities-hex4}.

```{r cities-geo4, results = "asis", fig.cap = "The lineup of choropleth map displays hides a distribution that affects all capital cities.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/aus_cities_4_geo.png")))
```

```{r cities-hex4, results = "asis", fig.cap = "The lineup of choropleth map displays shows a distribution that affects all capital cities. The values for the inner city areas in the capital cities result in them being coloured red. However, the colour blue dominates the display as the large rural areas are filled. Replicate (2) for All Cities.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/aus_cities_4_hex.png")))
```

# All Citites Example 2:

The higher values for the inner city areas in the capital cities result in them being coloured red. However, the colour blue dominates the display as the large rural areas are filled. There were no other choropleth maps that were coloured as blue as the map at location 3. This meant the detection rate was quite high, participants were able to select the correct distribution, even without being able to see the colours of inner-city areas of the capital cities.

```{r cities-geo3, results = "asis", fig.cap = "The lineup of choropleth map displays hides a distribution that affects all capital cities.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/aus_cities_3_geo.png")))
```

The same data showed in the hexagon tile map display shows varied distributions across the lineup. They are more diverse in colour than the choropleth counterparts. The same location, 3, holds the real data plot, the red city centres are now visible and surrounded by yellow, and then blue hexagons. For different reasons the participants were able to make the same correct choice for this replicate, with a detection rate of .

```{r cities-hex3, results = "asis", fig.cap = "The lineup of choropleth map displays shows a distribution that affects all capital cities. The values for the inner city areas in the capital cities result in them being coloured red. However, the colour blue dominates the display as the large rural areas are filled. Replicate (2) for All Cities.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/aus_cities_3_hex.png")))
```

### 2020-01-12 paper/supplementary/survey_procedures.Rmd
move supplementary materials to individual docs

---
title: "Survey procedure and participant training"
author: "Stephanie Kobakian and Dianne Cook"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r libraries}
library(cowplot)
library(grid)
library(gridExtra)
library(png)
```

# Survey procedure

Participants were recruited via advertising on the Figure-Eight crowdsource platform.
Choosing the task from the list directed all potential participants to the page of instructions.
This page contained written instructions and is shown in Fig. \ref{fig:instruct}.

```{r instruct, results = "asis", fig.cap = "The training lineups of choropleth maps.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/fig8_instruct.png")))
```

## Training

The participants were trained using three displays. There were relatively simple lineups, they are displayed in Fig. \ref{fig:training1} and Fig. \ref{fig:training2}.

```{r training1, results = "asis", fig.cap = "The training lineups of choropleth maps.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/fig8_training1.png")))
```

```{r training2, results = "asis", fig.cap = "The training lineups of hexagon tile maps.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/fig8_training2.png")))
```

## Survey application

The survey application was a `shinydashboard` we application, hosted on a website external to the Figure-Eight platform. The link to the survey was located at the bottom of the instructions and training page. Only participants who had read all of the instructions and seen the example image sets continued to the survey via the link.
This page also contained a question that asked participants for a validation code. The participants unique validation code was generated upon them opening the web application. This code was released to participants when they had considered all twelve lineups and submitted their responses to the `googlesheets` data set. Their validation codes were contained in the data set and associated with each of their responses.

The demographic and consent page of the `shinydashboard` web application are displayed in Fig. \ref{fig:survey-demogs}. Two example lineups are shown, one choropleth map lineup in Fig. \ref{fig:survey-choro} and one heaxgon tile map lineup in Fig. \ref{fig:survey-hex}.

```{r survey-demogs, results = "asis", fig.cap = "The demographics questions tab of the shinydashboard survey application.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/survey_demogs.png")))
```

```{r survey-choro, results = "asis", fig.cap = "An example of the choropleth map lineup shown in the survey tab of the shinydashboard app.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/survey_choro.png")))
```

```{r survey-hex, results = "asis", fig.cap = "An example of the hexagon tile map lineup shown in the survey tab of the shinydashboard app.", fig.width = 4, fig.height = 4}
ggdraw() +
  draw_plot(rasterGrob(readPNG("../figures/survey_hex.png")))
```

### 2020-01-12 paper/paper.Rmd

@@
 library(tidyverse)
+library(readxl)
+library(broom)
 library(cowplot)
@@
 =============
-<!-- no \IEEEPARstart -->
-<!-- (should never be an issue) -->
-
 <!-- General: comparison of displays, motivate hexagon tile map, enough info to motivate aims -->
 <!-- geographies on choropleth -->
-This study contrasts the use of two displays for geospatial statistics, the traditional choropleth map and an alternative tessellated hexagon tile map.
-The choropleth map is the common choice for visualising aggregated statistics and is familiar because of common administrative boundaries.
-A hexagon tile map forgoes the familiar boundaries, instead representing each geographic unit as an equally sized hexagon.
-This alternative display is suggested for communicating distributions that relate to the population values or density of the population in each geographic unit.
+This study compares the effectiveness of a new type of display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics.
+The choropleth map is the traditional  approach for visualising aggregated statistics across administrative boundaries.
+A hexagon tile map forgoes the familiar boundaries, in favor of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location.
+The hexagon tile map builds on existing displays, such as the cartogram, and tesselated hexagon displays.
+It differs in that it relaxes the requirement to have connected hexagons, and allows sparsely located hexagons.
+The algorithm to construct a hexagon tile map is available in the R package sugarbag [@sugarbag].
+This type of display may be useful for other countries, and other purposes.
+
+The hexagon tile map was designed for Australia, motivated by a need to display spatial statistics for a new Australian Cancer Atlas.
+None of the existing approaches for creating cartograms or hexagon tiling perform well for the Australian landscape, which has vast open spaces and concentrations of population in small regions clustered on the coastlines.
+
+<!-- This alternative display is suggested for communicating distributions that relate to the population values or density of the population in each geographic unit.
 This study uses the lineup protocol for visual inference testing of the recognition of spatial distributions.
@@
 =============
-
-<!-- Find a new display for the Cancer Atlas -->
+!-- Find a new display for the Cancer Atlas --
 
 ## The Australian Cancer Atlas
+-->
 
-The Australian Cancer Atlas is an online interactive web tool created to explore the burden of cancer on Australian communities. There are many cancer types to be explored individually or aggregated. 
+The Australian Cancer Atlas [@atlas] is an online interactive web tool created to explore the burden of cancer on Australian communities.
+There are many cancer types to be explored individually or aggregated.
+The Australian Cancer Atlas allows users to explore the patterns in the distributions of cancer statistics over the geographic space of Australia.
+It uses a choropleth map display and diverging colour scheme to draw attention to relationships between neighbouring areas.
+The hexagon tile map may be a useful alternative display for the atlas.
+
+The experiment was conducted using the lineup protocol, a visual inference procedure [@GIIV], to objectively test the effectiveness of the two displays.
+
+The paper is organised as follows.
+The next section discusses the background of geographic data display and visual inference procedures.
+The [Methodology] Section describes the methods for conducting the experiment and analysing the results.
+The results are summarized in Section [Results].
+
+<!--
 The Atlas examines Australian communities at the Statistical Areas at Level 2 (SA2) [@abs2016] used by the Australian Bureau of Statistics.
@@
 A similar approach was pioneered by Raisz [-@RSCW], using rectangles that tile to align borders of neighbours [@CDWCS].
-These cartogram methods all allow two variables to be shown in the single display. these methods are discussed further in XXX cite review paper
+These cartogram methods all allow two variables to be shown in the single display. These methods are discussed further in XXX cite review paper.
 
@@
 The analysis of the work was completed in R [@RCore] with the use of the following packages:
-For document creation: rmarkdown, rticles, knitr.
-For lineup creation and data analysis: tidyverse, nullabor, ggthemes, RcolorBrewer.
-For image displays: cowplot, png, grid
-
-For modeling and presentation of models: lme4, kableExtra
+ - For document creation: rmarkdown [@rmarkdown], rticles [@rticles], knitr [@knitr].
+ - For lineup creation and data analysis: tidyverse [@tidyverse], nullabor [@nullabor], ggthemes [@ggthemes], RColorBrewer [@RColorBrewer].
+ - For image displays: cowplot [@cowplot], png [@png], grid [@grid].
+ - For modeling and presentation of models: lme4 [@lme4], kableExtra [@kableExtra].
 

### 2020-01-12 paper/paper.tex

@@
 \usepackage{xcolor}
-
-\usepackage{graphicx}
 
@@
 It differs in that it relaxes the requirement to have connected hexagons, and allows sparsely located hexagons.
+The algorithm to construct a hexagon tile map is available in the R package sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]}.
+This type of display may be useful for other countries, and other purposes.
 
@@
 
-The Australian Cancer Atlas (XXX ref) is an online interactive web tool created to explore the burden of cancer on Australian communities.
+The Australian Cancer Atlas {[}\protect\hyperlink{ref-atlas}{2}{]} is an online interactive web tool created to explore the burden of cancer on Australian communities.
 There are many cancer types to be explored individually or aggregated.
@@
 
-The algorithm to construct a hexagon tile map is available in the R package sugarbag (XXX ref). This type of display may be useful for other countries, and other purposes.
-
-The paper is organised as follows. The next section
+The experiment was conducted using the lineup protocol, a visual inference procedure {[}\protect\hyperlink{ref-GIIV}{3}{]}, to objectively test the effectiveness of the two displays.
+
+The paper is organised as follows.
+The next section discusses the background of geographic data display and visual inference procedures.
+The \protect\hyperlink{methodology}{Methodology} Section describes the methods for conducting the experiment and analysing the results.
+The results are summarized in Section \protect\hyperlink{results}{Results}.
 
@@
 Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic.
-However, using a choropleth map base introduces biases when considering population related distributions {[}\protect\hyperlink{ref-CBATCC}{1}{]}.
+However, using a choropleth map base introduces biases when considering population related distributions {[}\protect\hyperlink{ref-CBATCC}{4}{]}.
 Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
@@
 When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
-This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention {[}\protect\hyperlink{ref-CTTMB}{2}{]}.
-An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas {[}\protect\hyperlink{ref-NISCC}{3}{]}.
+This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention {[}\protect\hyperlink{ref-CTTMB}{5}{]}.
+An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas {[}\protect\hyperlink{ref-NISCC}{6}{]}.
 This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
@@
 The transformation begins with a choropleth map, and the values of a statistic such as population, for each geographic unit.
-There are several algorithms for transformation {[}\protect\hyperlink{ref-ACTUC}{4}{]}, {[}\protect\hyperlink{ref-CBATCC}{1}{]}; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
+There are several algorithms for transformation {[}\protect\hyperlink{ref-ACTUC}{7}{]}, {[}\protect\hyperlink{ref-CBATCC}{4}{]}; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
 The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units.
@@
 Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units.
-The non-contiguous cartgoram method {[}\protect\hyperlink{ref-NAC}{5}{]} keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics.
+The non-contiguous cartgoram method {[}\protect\hyperlink{ref-NAC}{8}{]} keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics.
 This method disconnects areas when shrinking boundaries, and breaks the spatial relationship between areas.
 However, the empty space created emphasises the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
-The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{4}{]} is another method that does not retain the boundaries of geographic units.
+The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{7}{]} is another method that does not retain the boundaries of geographic units.
 Each unit becomes one circle on the cartogram display; the circles are sized according to the value of a the statistic, such as population.
 The neighbour relationships can be illustrated by connecting the boundaries of the circles.
-A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{6}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{7}{]}.
-These cartogram methods all allow two variables to be shown in the single display. these methods are discussed further in XXX cite review paper
+A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{9}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{10}{]}.
+These cartogram methods all allow two variables to be shown in the single display. These methods are discussed further in XXX cite review paper.
 
@@
 Where the guilty data set contains structure, and the innocents data sets do not.
-In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the innocents {[}\protect\hyperlink{ref-GTPCCD}{8}{]}.
+In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the innocents {[}\protect\hyperlink{ref-GTPCCD}{11}{]}.
 The guilty data is identified as different from the innocent data with probability \(1/m\), where \(m\) is the number of null plots plus 1 to account account for the guilty data set.
@@
 The lineup protocol can be used in a variety of testing scenarios for visualisations.
-{[}\protect\hyperlink{ref-GIIV}{9}{]} suggest the choropleth map for testing spatial structure in a data set.
+{[}\protect\hyperlink{ref-GIIV}{3}{]} suggest the choropleth map for testing spatial structure in a data set.
 The lineup protocol allows for flexibility in the definition of null data.
@@
 All of these participants read the introductory materials and viewed example questions before proceeding to the survey.
-Each participant was trained using three test displays orienting them to the evaluation task, these displays are shown in appendix section regarding \protect\hyperlink{training}{training}.
+Each participant was trained using three test displays orienting them to the evaluation task, these displays are shown in appendix section regarding {[}training{]}.
 All participants who volunteered to take part were compensated for their time via the payment system of Figure-Eight.
@@
 The data collection took place using a secure link between the survey web application and the googlesheet used to store results.
-The application would first connect to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{10}{]} R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
+The application would first connect to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{12}{]} R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
 
@@
 
-The choropleth map was used as the comparative visualisation for presenting the lineups {[}\protect\hyperlink{ref-VVSIALM}{11}{]} as this is the common display for spatial cancer data.
+The choropleth map was used as the comparative visualisation for presenting the lineups {[}\protect\hyperlink{ref-VVSIALM}{13}{]} as this is the common display for spatial cancer data.
 Geographic distributions usually have some degree of spatial autcorrelation between neighbours.
@@
 
-The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R {[}\protect\hyperlink{ref-RCore}{12}{]}.
+The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R {[}\protect\hyperlink{ref-RCore}{14}{]}.
 
@@
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R {[}\protect\hyperlink{ref-RCore}{12}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{13}{]} package implements generalised linear mixed effect models.
+The R {[}\protect\hyperlink{ref-RCore}{14}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{15}{]} package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 
-Computation will be done using R {[}\protect\hyperlink{ref-RCore}{12}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{13}{]}.
+Computation will be done using R {[}\protect\hyperlink{ref-RCore}{14}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{15}{]}.
 
@@
 The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts.
-One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in the appendix \protect\hyperlink{lineups}{Lineups} section.
+One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in the appendix {[}Lineups{]} section.
 Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map.
@@
 
-\hypertarget{choices}{%
-\subsection{Choices}\label{choices}}
-
-The choices made by participants are examined in Fig. \ref{fig:choices}.
-Participants were misled by the choropleth display, but not the hexagon display for All Cities displays except (2).
-The maps with a North West to South East trend was chosen with much greater frequency in all displays.
-All of Three Cities displays, except (4), were detected in the hexagon display.
-All except one lineup had at least one participant select the correct map in the lineup as shown in Fig.
-\ref{fig:choices}.
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/choices-1.pdf}
-\caption{\label{fig:choices}Each facet is associated with one lineup, the height of the points show the proportion of the participants that made each choice when considering each lineup.
-The points coloured orange show the map which contained a trend model, these are the correct choices.
-The numbers differentiate the replicates of each trend model and type of map display.
-Participants were able to select 0 to indicate they did not want to choose a map.}
-\end{figure}
-
 \hypertarget{discussion}{%
@@
 \section{Appendix}\label{appendix}}
-
-\hypertarget{training}{%
-\subsection{Training}\label{training}}
-
-The participants were trained using three displays. There were relatively simple lineups and are shown in Fig. \ref{fig:training1} and Fig. \ref{fig:training2}.
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/training1-1.pdf}
-\caption{\label{fig:training1}The training lineups of choropleth maps.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/training2-1.pdf}
-\caption{\label{fig:training2}The training lineups of hexagon tile maps.}
-\end{figure}
-
-\hypertarget{survey-application}{%
-\subsection{Survey application}\label{survey-application}}
-
-The survey application was hosted on a website external to the Figure-Eight platform.
-Following suggestions in the documentation, the information and training required for a participant to make a decision was included that survey
-
-The demonstrative images of the \texttt{shinydashboard} web application display the demographic and consent page in Fig. \ref{fig:survey-demogs}.
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/survey-demogs-1.pdf}
-\caption{\label{fig:survey-demogs}The demographics questions tab of the shinydashboard survey application.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/survey-hex-1.pdf}
-\caption{\label{fig:survey-hex}An example of the hexagon tile map lineup shown in the survey tab of the shinydashboard app.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/survey-choro-1.pdf}
-\caption{\label{fig:survey-choro}An example of the choropleth map lineup shown in the survey tab of the shinydashboard app.}
-\end{figure}
-
-\hypertarget{lineups}{%
-\subsection{Lineups}\label{lineups}}
-
-Replicate 3 of the All Cities distribution is shown in Figures .
-The same data set is shown in both displays, the difference is the land area of each SA3 is coloured in the choropleth and the hexagon representing the SA3 is coloured in the Hexagon Tile Map.
-Many maps in the Choropleth lineup (a) are coloured yellow, two are half light blue, and two are obviously blue.
-Only one of the maps looks red.
-
-Lineups were created using the Australian Statistical Areas at Level 3.
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/cities-geo-1.pdf}
-\caption{\label{fig:cities-geo}The lineup of choropleth map displays hides a distribution that affects all capital cities.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/cities-hex-1.pdf}
-\caption{\label{fig:cities-hex}The lineup of choropleth map displays shows a distribution that affects all capital cities.
-The values for the inner city areas in the capital cities result in them being coloured red.
-However, the colour blue dominates the display as the large rural areas are filled.
-Replicate (2) for All Cities.}
-\end{figure}
-
-The higher values for the inner city areas in the capital cities result in them being coloured red.
-However, the colour blue dominates the display as the large rural areas are filled.
-There were no other choropleth maps that were coloured as blue as map (3).
-This meant the detection rate was quite high, participants were able to select the correct distribution without being able to see the values of the capital cities.
-The same data showed in the hexagon tile map display shows varied distributions across the lineup.
-They are more diverse in colour than the choropleth counterparts.
-The same location holds the real data plot, the red city centres are now visible and surrounded by yellow, and then blue hexagons.
-For different reasons the participants were able to make the same correct choice.
 
@@
 
+\hypertarget{acknowledgment-1}{%
+\section{Acknowledgment}\label{acknowledgment-1}}
+
+The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualisations.
+They would also like to thank Distinguished Professor Kerrie Mengersen and Doctor Earl Duncan for suggestions and comments.
+
+The source code to produce this document can be found on \href{https://github.com/srkobakian/experiment/tree/master/paper}{GitHub}.
+Supplementary materials have been included to discuss the survey procedures,
+
+The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{14}{]} with the use of the following packages:
+- For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{16}{]}, rticles {[}\protect\hyperlink{ref-rticles}{17}{]}, knitr {[}\protect\hyperlink{ref-knitr}{18}{]}.
+- For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{19}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{20}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{21}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{22}{]}.
+- For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{23}{]}, png {[}\protect\hyperlink{ref-png}{24}{]}, grid {[}\protect\hyperlink{ref-grid}{25}{]}.
+- For modeling and presentation of models: lme4 {[}\protect\hyperlink{ref-lme4}{15}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{26}{]}.
+
+Ethics approval for the online survey was granted by QUT's Ethics Committee (Ethics Application Number: 1900000991).
+All applicants provided informed consent in line with QUT regulations prior to participating in this research.
+
+\newpage
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-sugarbag}{}%
+1. Kobakian S, Cook D (2019) Sugarbag: Create tessellated hexagon maps.
+
+\leavevmode\hypertarget{ref-atlas}{}%
+2. Queensland CC Australian Cancer Atlas (https://atlas.cancer.org.au).
+
+\leavevmode\hypertarget{ref-GIIV}{}%
+3. Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979
+
 \leavevmode\hypertarget{ref-CBATCC}{}%
-1. Kocmoud C, House D (1998) A Constraint-based Approach to Constructing Continuous Cartograms. In: Proc. Symp. Spatial data handling. pp 236--246
+4. Kocmoud C, House D (1998) A Constraint-based Approach to Constructing Continuous Cartograms. In: Proc. Symp. Spatial data handling. pp 236--246
 
 \leavevmode\hypertarget{ref-CTTMB}{}%
-2. Griffin TL (1980) Cartographic Transformation of the Thematic Map Base. Cartography 11:163--174
+5. Griffin TL (1980) Cartographic Transformation of the Thematic Map Base. Cartography 11:163--174
 
 \leavevmode\hypertarget{ref-NISCC}{}%
-3. Dent BD (1972) A Note on the Importance of Shape in Cartogram Communication. Journal of Geography 71:393--401
+6. Dent BD (1972) A Note on the Importance of Shape in Cartogram Communication. Journal of Geography 71:393--401
 
 \leavevmode\hypertarget{ref-ACTUC}{}%
-4. Dorling D (2011) Area Cartograms: Their Use and Creation. In: Concepts and techniques in modern geography (catmog). pp 252--260
+7. Dorling D (2011) Area Cartograms: Their Use and Creation. In: Concepts and techniques in modern geography (catmog). pp 252--260
 
 \leavevmode\hypertarget{ref-NAC}{}%
-5. Olson JM (1976) Noncontiguous Area Cartograms. The Professional Geographer 28:371--380
+8. Olson JM (1976) Noncontiguous Area Cartograms. The Professional Geographer 28:371--380
 
 \leavevmode\hypertarget{ref-RSCW}{}%
-6. Raisz E (1963) Rectangular Statistical Cartograms of the World. Journal of Geography 35:8--10
+9. Raisz E (1963) Rectangular Statistical Cartograms of the World. Journal of Geography 35:8--10
 
 \leavevmode\hypertarget{ref-CDWCS}{}%
-7. Monmonier M (2005) Cartography: Distortions, World-views and Creative Solutions. Progress in Human Geography 29:217--224
+10. Monmonier M (2005) Cartography: Distortions, World-views and Creative Solutions. Progress in Human Geography 29:217--224
 
 \leavevmode\hypertarget{ref-GTPCCD}{}%
-8. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448
-
-\leavevmode\hypertarget{ref-GIIV}{}%
-9. Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979
+11. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448
 
 \leavevmode\hypertarget{ref-sheets}{}%
-10. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
+12. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
 
 \leavevmode\hypertarget{ref-VVSIALM}{}%
-11. Majumder M, Hofmann H, Cook D (2013) Validation of visual statistical inference, applied to linear models. Journal of the American Statistical Association 108:942--956
+13. Majumder M, Hofmann H, Cook D (2013) Validation of visual statistical inference, applied to linear models. Journal of the American Statistical Association 108:942--956
 
 \leavevmode\hypertarget{ref-RCore}{}%
-12. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+14. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
 
 \leavevmode\hypertarget{ref-lme4}{}%
-13. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
+15. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
+
+\leavevmode\hypertarget{ref-rmarkdown}{}%
+16. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida
+
+\leavevmode\hypertarget{ref-rticles}{}%
+17. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.
+
+\leavevmode\hypertarget{ref-knitr}{}%
+18. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research
+
+\leavevmode\hypertarget{ref-tidyverse}{}%
+19. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686
+
+\leavevmode\hypertarget{ref-nullabor}{}%
+20. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.
+
+\leavevmode\hypertarget{ref-ggthemes}{}%
+21. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.
+
+\leavevmode\hypertarget{ref-RColorBrewer}{}%
+22. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.
+
+\leavevmode\hypertarget{ref-cowplot}{}%
+23. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.
+
+\leavevmode\hypertarget{ref-png}{}%
+24. Urbanek S (2013) Png: Read and write png images.
+
+\leavevmode\hypertarget{ref-grid}{}%
+25. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+
+\leavevmode\hypertarget{ref-kableExtra}{}%
+26. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
 

### 2020-01-12 paper/supplementary/lineups.Rmd

@@
 author: "Stephanie Kobakian and Dianne Cook"
-output: pdf_document
+output: bookdown::pdf_document
+link_citatons: true
 ---
@@
 ```{r data}
+
 library(tidyverse)
+library(readxl)
 library(cowplot)
@@
 
+```{r}
+choice_tabs <- d %>% 
+  count(trend, type, choice, replicate, choice, detect) %>% 
+  group_by(trend, type, replicate) %>% 
+  mutate(prop = round(n/sum(n), 2)) %>% 
+  mutate(repl = paste("Rep:", replicate, ":\n", type,  sep = "")) %>%
+  mutate(bottom = 0) %>% 
+  select(Trend = trend, Rep = replicate, Type = type, prop, choice) %>% 
+  spread(choice, prop, fill = "0") %>% 
+  nest(-Trend)
+```
+
+```{r choice-nwse}
+knitr::kable(choice_tabs$data[[1]], format = "latex", align = "rrrrrrrrrrrrrr",
+  caption = "NW-SE") %>%
+  collapse_rows(., columns = c(1,2))
+```
+
+```{r choice-three}
+knitr::kable(choice_tabs$data[[2]], format = "latex", align = "rrrrrrrrrrrrrr",
+  caption = "Three Cities") %>%
+  collapse_rows(., columns = c(1,2))
+```
+
+```{r choice-all}
+knitr::kable(choice_tabs$data[[3]], format = "latex", align = "rrrrrrrrrrrrrr",
+  caption = "All Cities") %>%
+  collapse_rows(., columns = c(1,2))
+```
+
 # All cities Example 1:
@@
 
-```{r cities-geo4, results = "asis", fig.cap = "The lineup of choropleth map displays hides a distribution that affects all capital cities.", fig.width = 4, fig.height = 4}
+```{r cities-geo4, results = "asis", fig.cap = "The lineup of choropleth map displays hides a distribution that affects all capital cities.", fig.width = 5, fig.height = 4}
 ggdraw() +

### 2020-01-12 paper/paper.Rmd
rename bibs

@@
 These findings should encourage map creators to implement alternative displays, and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
-dev: png
-bibliography: mybibfile.bib
+dev: pdf
+bibliography: paper.bib
 output:
@@
 The analysis of the work was completed in R [@RCore] with the use of the following packages:
+
  - For document creation: rmarkdown [@rmarkdown], rticles [@rticles], knitr [@knitr].

### 2020-01-12 paper/supplementary/lineups.Rmd
rename bibs

@@
 author: "Stephanie Kobakian and Dianne Cook"
-output: bookdown::pdf_document
-link_citatons: true
+output: pdf_document
+bibliography: supplementary.bib
+link-citations: true
+citation_package: biblatex
+csl: springer-vancouver.csl
 ---
@@
 
-The choices made by participants are examined in Fig. \ref{fig:choices}.
-Participants were misled by the choropleth display, but not the hexagon display for All Cities displays except (2).
-The maps with a North West to South East trend was chosen with much greater frequency in all displays.
+Each lineup had twelve map displays, this gave participants the choice of any plot, and the choice to not provide a response. this non-reponse is indicated by 0.
+The choices made by participants are displayed in Fig.
+\ref{fig:choices}.
+The height of each orange lollipop indiates the proportion of participants that selected the map display of real data, they represent the correct choices.
+The green lollipops show the proportion of participants that selected the incorrect displays in each lineup.
+
+The proportion of choices are also presented separately for each trend model in Table. \ref{tab:choice-nwse}, Table. \ref{tab:choice-three}, and  Table. \ref{tab:choice-all}.
+The correct map display in lineups with a North West to South East trend was chosen correctly with much greater frequency. 
+In the lineups of All Cities displays, participants were misled by the choropleth display, but not the hexagon display for all except (2). 
 All of Three Cities displays, except (4), were detected in the hexagon display.
@@
 The numbers differentiate the replicates of each trend model and type of map display.
-Participants were able to select 0 to indicate they did not want to choose a map.", fig.height = 8, fig.width =6}
+Participants were able to select 0 to indicate they did not want to choose a map.", fig.height = 8, fig.width =6, results = "asis"}
 d %>% 
@@
   spread(choice, prop, fill = "0") %>% 
-  nest(-Trend)
+  nest(data = c(Rep, Type, `0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, 
+    `10`, `11`, `12`))
 ```

### 2020-01-12 paper/paper.Rmd
American English spelling

@@
   The choropleth map display is commonly used for communicating spatial distributions across geographic areas.
-However, when choropleths are used, the sizes of areas can lead to misinterpretation of the distribution.
-The visualisation method used to present geospatial data will influence the understanding of the distribution derived by map users.
+However, when choropleths are used, the sizes of areas can lead to the misinterpretation of the distribution.
+The visualization method used to present geospatial data will influence the understanding of the distribution derived by map users.
 Choosing an effective alternative display could positively influence the communication of the spatial distribution.
-The hexagon tile map is presented as an alternative display for effectively visualising population related distributions.
+The hexagon tile map is presented as an alternative display for visualizing population related distributions effectively.
 Visual inference is used to measure the power of design, and the choropleth is used as a comparison.
-The hexagon tile map display is also tested using a distribution that is directly related to the geography, with values monotonically decreasing from the North West to South East areas of Australia.
+The hexagon tile map display is also tested using a distribution that is directly related to the geography, with values monotonically decreasing from the North-West to South-East areas of Australia.
 This study finds the single map in a hexagon tile map lineup that contains a population related distribution is detected with greater probability than the same data displayed in a choropleth map.
-These findings should encourage map creators to implement alternative displays, and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
+These findings should encourage map creators to implement alternative displays and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
 dev: pdf
@@
 ```{r data}
-trend_colours <- c(
+trend_colors <- c(
   "NW-SE" = "#B2DF8A",
@@
 
-type_colours <- c(
+type_colors <- c(
   "Choro." = "#fcae91",
@@
 
-detect_f_colours <- c(
+detect_f_colors <- c(
   "No" = "#66C2A5",
@@
 
-detect_colours <- c(
+detect_colors <- c(
   "Detected? No" = "#66C2A5",
@@
 This study compares the effectiveness of a new type of display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics.
-The choropleth map is the traditional  approach for visualising aggregated statistics across administrative boundaries.
+The choropleth map is the traditional  approach for visualizing aggregated statistics across administrative boundaries.
 A hexagon tile map forgoes the familiar boundaries, in favor of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location.
@@
 The Australian Cancer Atlas allows users to explore the patterns in the distributions of cancer statistics over the geographic space of Australia.
-It uses a choropleth map display and diverging colour scheme to draw attention to relationships between neighbouring areas.
+It uses a choropleth map display and diverging color scheme to draw attention to relationships between neighboring areas.
 The hexagon tile map may be a useful alternative display for the atlas.
@@
 The Atlas examines Australian communities at the Statistical Areas at Level 2 (SA2) [@abs2016] used by the Australian Bureau of Statistics.
-Bayesian spatial smoothing was applied to integrate the values of neighbouring areas.
+Bayesian spatial smoothing was applied to integrate the values of neighboring areas.
 Spatial smoothing protects the privacy and gives stability to the estimated amounts in each SA2.
 Users of the Atlas can explore the difference of the statistic of each SA2 from the Australian average, for both diagnoses (Standardised Incidence Rates) and excess deaths.
-It communicates the value of the statistic for each SA2 geographic unit through colour, by filling the areas using the diverging colour scheme ranging from dark blue to red.
+It communicates the value of the statistic for each SA2 geographic unit through color, by filling the areas using the diverging color scheme ranging from dark blue to red.
 -->
@@
 
-Spatial visualisations communicate the distribution of statistics over geographic space.
+Spatial visualizations communicate the distribution of statistics over geographic space.
 The most common display for spatial data is the choropleth map.
 It is used to present aggregated statistics for geographic units such as the population.
-Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic.
+Creating a choropleth map involves drawing the administrative boundaries and filling them with color to communicate the value of the statistic.
 However, using a choropleth map base introduces biases when considering population related distributions [@CBATCC].
@@
 The rural communities in Australia operate on a much larger geographic space than small inner-city communities.
-When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
-This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention [@CTTMB].
+When a spatial distribution relates to the size of the areas, or the population density, the size of the regions can result in erroneous conclusions about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
+This occurs as large regions filled with a consistent color or pattern can draw the attention of map readers, and small regions are not paid equal attention [@CTTMB].
 An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas [@NISCC].
@@
 A cartogram transforms the geographic map base.
-The transformation begins with a choropleth map, and the values of a statistic such as population, for each geographic unit.
+The transformation begins with a choropleth map and the values of a statistic such as population for each geographic unit.
 There are several algorithms for transformation [@ACTUC], [@CBATCC]; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
@@
 The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units.
-The transformation will keep boundaries of neighbouring areas connected, but the result is unfamiliar shapes for each geographic unit.
+The transformation will keep boundaries of neighboring areas connected, but the result is unfamiliar shapes for each geographic unit.
 
@@
 Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units.
-The non-contiguous cartgoram method [@NAC] keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics.
-This method disconnects areas when shrinking boundaries, and breaks the spatial relationship between areas.
-However, the empty space created emphasises the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
-The Dorling cartogram [@ACTUC] is another method that does not retain the boundaries of geographic units.
-Each unit becomes one circle on the cartogram display; the circles are sized according to the value of a the statistic, such as population.
-The neighbour relationships can be illustrated by connecting the boundaries of the circles.
-A similar approach was pioneered by Raisz [-@RSCW], using rectangles that tile to align borders of neighbours [@CDWCS].
+The non-contiguous cartogram method [@NAC] keeps the shapes of geographic units intact and changes the size of the shape to communicate the values of statistics.
+This method disconnects areas when shrinking boundaries and breaks the spatial relationship between areas.
+However, the empty space created emphasizes the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
+The Dorling cartogram [@ACTUC] is another method that does not keep the boundaries of geographic units.
+Each unit becomes one circle on the cartogram display; it sizes the circles according to the value of the statistic, such as population.
+The neighbor relationships can be illustrated by connecting the boundaries of the circles.
+A similar approach was pioneered by Raisz [-@RSCW], using rectangles that tile to align borders of neighbors [@CDWCS].
 These cartogram methods all allow two variables to be shown in the single display. These methods are discussed further in XXX cite review paper.
@@
 ```{r liver, fig.height = 9, fig.width = 6, fig.cap = "The smoothed average of liver cancer diagnoses for Australian males.
-The divering colour scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average."}
+The divering color scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average."}
 ggdraw(ylim = c(0,2), xlim = c(0,1.3), clip = "on") +
@@
 <!-- Specific problem for Australia -->
-Australia is an extreme case of heterogenous geographic units, with large difference between the smallest and largest geographic units across various granularities.
-To communicate information regarding the small inner-city geographic units of Australian cities an alternative display must be employed.
-This will emphasise the value of the statistic for areas with high population.
+Australia is an extreme case of heterogeneous geographic units, with the large differences between the smallest and largest geographic units across various granularities.
+To communicate information regarding the small inner-city geographic units of Australian cities, an alternative display must be employed.
+This will emphasize the value of the statistic for areas with a high population.
 Fig.
-\ref{fig:liver} shows the distribution of the smoothed average amount of Liver cancer diagnoses for Australian Males from 2005-2014.
+\ref{fig:liver} shows the distribution of the smoothed average amount of liver cancer diagnoses for Australian Males from 2005 to 2014.
 These inner-city areas are not visible on the choropleth map (a).
 The hexagon tile map (b) shows orange hexagons for the inner-city SA2s with higher than average levels of diagnoses in the capital cities of Melbourne and Sydney.
-The northern Queensland, and Northern Territory SA2's with higher than average rates are still visible but use less map space on the hexagon tile map.
+The northern Queensland and Northern Territory SA2s with higher than average rates are still visible but use less map space on the hexagon tile map.
 There are still many light blue areas in both displays.
@@
 
-The hexagon tile map is suggested as an alternative display.
-To test the effectiveness of these displays there is a formal testing framework.
-Visual inference considers the communication of data or data summaries through visualisations.
-It considers these visualisations to be visual statistics, with observable features.
+We suggest the hexagon tile map as an alternative display.
+To test the effectiveness of these displays, there is a formal testing framework.
+Visual inference considers the communication of data or data summaries through visualizations.
+It considers these visualizations to be visual statistics, with observable features.
 
-Classical statistical inference involves hypothesis testing, the process of rejecting a null hypothesis in favour of an alternative.
-This approach requires appropriate data, with the appropriate distributions and their assumptions.
-The lineup protocol was formalised as a test for the effectiveness of a visualisation.
-Rather than use classical statistical tests, human participants are tasked with finding the display that shows structure between the variables.
-If the structure is not detected, then it is not significantly different from the null data.
+Classical statistical inference involves hypothesis testing,  rejecting a null hypothesis in favor of an alternative. This approach requires data with the appropriate distributions and assumptions. 
+The lineup protocol was formalized as a test for the effectiveness of a visualization.
+Rather than classical statistical tests, it tasks human participants with finding the display that shows structure between the variables.
+If they do not detect the structure, then it is not significantly different from the null data.
 
@@
 
-- Null hypothesis: There is NO relationship between the variables,
+ - Null hypothesis: There is \bf{no} relationship between the variables
+ - Alternative hypothesis: There is a relationship between the variables
 
-- Alternative hypothesis: There is a relationship between the variables.
+To test these hypotheses, the line up protocol randomly places a "guilty" data visualization in a lineup of "innocents".
+Where the guilty data set contains structure, and the innocents data sets do not.
+In a grid of visualizations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the  innocents [@GTPCCD].
+The participants identify the guilty data as different from the innocent data with probability $1/m$, where $m$ is the number of null plots plus 1 to account for the guilty data set.
+When the guilty data set is chosen we reject the null hypothesis that it was innocent is rejected with a $1/m$ chance or type I error of being wrong.
 
-To test these hypotheses, the line up protocol randomly places a "guilty" data visualisation in a lineup of "innocents".
-Where the guilty data set contains structure, and the innocents data sets do not.
-In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the  innocents [@GTPCCD].
-The guilty data is identified as different from the innocent data with probability $1/m$, where $m$ is the number of null plots plus 1 to account account for the guilty data set.
-When the guilty data set is chosen, the null hypothesis that it was innocent is rejected with a $1/m$ chance or type I error of being wrong.
-
-The lineup protocol can be used in a variety of testing scenarios for visualisations.
+The lineup protocol can be used in a variety of testing scenarios for visualizations.
 @GIIV suggest the choropleth map for testing spatial structure in a data set.
 The lineup protocol allows for flexibility in the definition of null data.
-In the case of spatial visualisations it is likely that neighbours are related to some degree.
+In the case of spatial visualizations, it is likely that neighbors are related.
 To account for this, null data sets can be generated by sampling from a known model that accounts for spatial covariance.
 
-To contrast the effectiveness of two displays, the data set of null data plots with a hidden real data plot can be produced using the different plot designs.
-The time taken by participants to evaluate the same data in the different displays can be compared. Their accuracy in detecting the real data plot can also be calculated and contrasted.
+To contrast the effectiveness of two displays, we can produce null data plots with a hidden real data plot using the different plot designs.
+We can compare the time taken by participants to evaluate the same data in the different displays. We can also contrast the accuracy achieved by participants in detecting the real data plot.
 
@@
 
-1. Are spatial disease trends, that impact highly populated small areas, detected with higher accuracy when viewed in a hexagon tile map display?
+1. Are spatial disease trends that impact highly populated small areas detected with higher accuracy, when viewed in a hexagon tile map display?
 
-2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when using a hexagon tile map display?
+2. Are people faster in detecting spatial disease trends that impact highly populated small areas when using a hexagon tile map display?
 
-Additional considerations when completing this experimental task included exploration of the difficulty experienced by participants, and the certainty they felt about their decision.
+Additional considerations when completing this experimental task included exploration of the difficulty experienced by participants and the certainty they felt about their decision.
 
@@
 
-The difference in the detection rates for the two displays will be compared using a two sample unpaired t-test.
-
 ## Participants
 
-Participants were recruited for a survey style task to test the effectiveness of the hexagon tile map display.
-It was expected that the participants were uninvolved judges that had no prior knowledge of the data, to avoid discrimination or advantages.
-The Figure-Eight crowd source platform was used to advertise the survey to potential participants that had acheived level 2 or level 3 on the Figure-Eight Platform.
-The participants were chosen as they have experience with survey tasks that involve evaluating images. They participants on the platform are also required to be at least 18 years old.
+We recruited participants for the survey style task to test the effectiveness of the hexagon tile map display.
+The lineup protocol expects that the participants are uninvolved judges that had no prior knowledge of the data to avoid discrimination or advantages.
+The Figure-Eight crowd source platform was used to advertise the survey to potential participants that had achieved level 2 or level 3 on the Figure-Eight Platform.
+The participants were chosen as they have experience with survey tasks that involve evaluating images. The participants were at least 18 years old, as it is a requirement of the platform.
 
 Participants were able to choose to participate by selecting this task from the list of tasks available to them.
+Participants were allocated to either group A or group B when they proceeded to the survey web application, hosted externally from the Figure-Eight website. 
 There were 95 participants involved in the study.
 All of these participants read the introductory materials and viewed example questions before proceeding to the survey.
-Each participant was trained using three test displays orienting them to the evaluation task, these displays are shown in appendix section regarding [training].
+Each participant was trained using three test displays orienting them to the evaluation task.
 All participants who volunteered to take part were compensated for their time via the payment system of Figure-Eight.
-
-Participants were allocated to either group A or group B when they proceeded to the survey web application, hosted externally from the Figure-Eight website.
 
@@
 
-The variables that were changed between groups were the type of plot shown and the trend model.
+The variables changed between groups were the type of plot shown and the trend model.
 
-The twenty-four lineup displays were created by a combination of map type, and spatial trend model.
-This set of displays was split into a collection of twelve displays for Group A and twelve displays for Group B.
-
-Each participant was randomly allocated to either Group A or Group B when they begun the survey. This resulted in 42 participants allocated to Group A, and 53 participants allocated to Group B.
+A combination of map type and spatial trend model created the twenty-four lineup displays.
+We split this set of displays into a collection of twelve displays for Group A and twelve displays for Group B.
+The random allocation of participants to Group A or Group B resulted in 42 participants allocated to Group A and 53 participants allocated to Group B.
 
@@
 
-Each Group did not see the same data for both map types. Four simulated sets of data were generated for each treatment.
-This will generate twenty-four lineups (twelve lineups of geographic maps, and twelve lineups of hexagon tile maps). Participants evaluated twelve lineups, siz of each map type.
-For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants. The design is outlined in Table. \ref{tab:exp-design}.
+Each group did not see the same data for both map types. We generated four simulated sets of data for each treatment.
+This will generate twenty-four lineups (twelve lineups of geographic maps and twelve lineups of hexagon tile maps). Participants evaluated twelve lineups, size of each map type.
+For each of the six geographic displays and six hexagon displays, two of each trend model were shown to the participants. We outline the design in Table. \ref{tab:exp-design}.
 
@@
 The lineup protocol allows a known model to be imposed on the null data set plots.
-The underlying spatial correlation model was created to provide spatial autocorrelation between neighbouring areas using the longitude and latitude values for the Statistical Areas.
+The underlying spatial correlation model was created to provide spatial autocorrelation between neighboring areas using the longitude and latitude values for the Statistical Areas.
 
@@
 
-The null model imposed suggests that neighbours are related.
+The null model imposed suggests that neighbors are related.
 The randomness imposed was smoothed to mirror the practice taken by the Australian Cancer Atlas.
-This smoothing allowed neighbours to be related to each other and show distributions similar to the Liver cancer distribution shown in \ref{fig:liver}.
+This smoothing allowed neighbors to be related to each other and show distributions similar to the Liver cancer distribution shown in \ref{fig:liver}.
 
@@
 
-For each of the 144 individual maps, the values attributed to each geographic area are rescaled to show a similar colour scale from deep blue to dark red within each map.
+For each of the 144 individual maps, the values attributed to each geographic area are rescaled to show a similar color scale from deep blue to dark red within each map.
 
@@
 
-The choropleth map was used as the comparative visualisation for presenting the lineups [@VVSIALM] as this is the common display for spatial cancer data.
-Geographic distributions usually have some degree of spatial autcorrelation between neighbours.
+The choropleth map was used as the comparative visualization for presenting the lineups [@VVSIALM] as this is the common display for spatial cancer data.
+Geographic distributions usually have some degree of spatial autcorrelation between neighbors.
 This feature was incorporated in all maps shown in the lineup displays, the map that contained the trend feature shown in only one set of data was also affected by spatial autocorrelation.
@@
 
-The same data was visualised on a choropleth map, and on a hexagon tile map, however in this study the participants only saw one of these two displays.
+The same data was visualized on a choropleth map, and on a hexagon tile map, however in this study the participants only saw one of these two displays.
 The accuracy and times taken were aggregated for Groups and.
@@
 
-### Visualisations
+### visualizations
 Side-by-side dot plots were made of accuracy (efficiency) against map type, facetted by trend model type.
@@
 # Plot summary
-ggplot(d_smry, aes(x=type, y=pdetect, colour = trend)) +
+ggplot(d_smry, aes(x=type, y=pdetect, color = trend)) +
   geom_point(size = 2) +  
@@
   facet_wrap(~trend) +
-  scale_colour_manual(values = trend_colours) +
-  xlab("Type of areas visualised") +
+  scale_color_manual(values = trend_colors) +
+  xlab("Type of areas visualized") +
   ylab("Detection rate") + 
   ylim(0,1) +
-  guides(colour = FALSE)
+  guides(color = FALSE)
 ```
@@
 The mean detection rate for the Three Cities trend model shown as choropleth map lineups was also the smallest at 0.39.
-The North West to South East (NW-SE) trend model unexpectedly had a higher mean detection rate for the hexagon tile map displays, but the difference in the means of detection rate was only 0.10.
+The North-West to South-East (NW-SE) trend model unexpectedly had a higher mean detection rate for the hexagon tile map displays, but the difference in the means of detection rate was only 0.10.
 
@@
 when considering the heights of the green and orange dots, there is little difference in the average time taken to read a choropleth or hexgon tile map.
-Comparing the same coloured dot across each trend model row, there is a slight increase in the time taken to correctly detected the data plot in the hexagon tile map lineup, but little difference in evaluation time for the choropleth display.
+Comparing the same colored dot across each trend model row, there is a slight increase in the time taken to correctly detected the data plot in the hexagon tile map lineup, but little difference in evaluation time for the choropleth display.
 However, there were substantially less correct detections for choropleth lineups for the Three cities and All Cities trends.
@@
 ```{r beeswarm, fig.cap = "The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots.
-The coloured point indicates average time taken for each plot type.
+The colored point indicates average time taken for each plot type.
 Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between plot types.", fig.height=8}
@@
   geom_quasirandom(data=d, aes(x=type, y=time_taken), alpha=0.9) + 
-  #geom_hline(data=s, aes(yintercept=m, colour=type)) +
-  geom_point(data=s, aes(x=type, y=m, colour=type), size=5, alpha=0.7) +
-  #geom_errorbar(data=s, aes(x=type, ymin=q1, ymax=q3, colour=type), width=0.3, size=2) +
-  scale_colour_brewer("", palette = "Dark2") +
+  #geom_hline(data=s, aes(yintercept=m, color=type)) +
+  geom_point(data=s, aes(x=type, y=m, color=type), size=5, alpha=0.7) +
+  #geom_errorbar(data=s, aes(x=type, ymin=q1, ymax=q3, color=type), width=0.3, size=2) +
+  scale_color_brewer("", palette = "Dark2") +
   facet_grid(trend~detect_f) + 
@@
 \ref{certainty} shows the amount of times participants provided each level of certainty.
-This was separated for each combination of trend models and display type, and coloured depending on whether a participant correctly detected the data plot in the lineup.
+This was separated for each combination of trend models and display type, and colored depending on whether a participant correctly detected the data plot in the lineup.
 Participants chose 4 or 5 often when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
@@
    aes(x = certainty, fill = Detected)) +  
-  scale_fill_manual(values = detect_colours) +
+  scale_fill_manual(values = detect_colors) +
   geom_bar() + facet_grid(type ~ trend) +
@@
 Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons. 
-"Colour trend across the areas" was the most common selection for NW-SE trend displays.
-The colour scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
-Due to the consisent colouring of rural areas in a choropleth display, the choice "All areas have similar colours" was most common reason.
-The All Cities displays coloured the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural colour consistency.
+"color trend across the areas" was the most common selection for NW-SE trend displays.
+The color scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
+Due to the consisent coloring of rural areas in a choropleth display, the choice "All areas have similar colors" was most common reason.
+The All Cities displays colored the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural color consistency.
 
 The reasons used when viewing choropleth displays varied more than the hexagon tile map reasons.
-The hexagon tile map displays resulted in "Clusters of colour" as the most common choice made by participants.
+The hexagon tile map displays resulted in "Clusters of color" as the most common choice made by participants.
 This response was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions.
 It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays.
-Due to the spatial covariance introduced in the smoothing, groups of similarly coloured hexagons were present in all of the hexagon tile map displays.
+Due to the spatial covariance introduced in the smoothing, groups of similarly colored hexagons were present in all of the hexagon tile map displays.
 All Cities and Three Cities distributions of real data trends had distinctly different patterns or red inner-city areas, while some of the plots in each lineup may have shared similar features.
@@
 
-This hexagon tile map display should be considered as a visualisation method when communicating distributions that relate to the population in each geographic unit.
+This hexagon tile map display should be considered as a visualization method when communicating distributions that relate to the population in each geographic unit.
 Cancer Atlas products may benefit from the opportunity to allow exploration via the traditional choropleth map method as well as an alternative display.
@@
 
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualisations.
+The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations.
 They would also like to thank Kerrie Mengersen and Dr.
@@
 \newpage
-Appendix
-============
-
-## Overall Performance
-
-```{r pdetection_trend, eval = FALSE}
-plots %>% ggplot(aes(x = group, y = pdetect)) + 
-  geom_boxplot() + 
-  geom_jitter(width = 0.1) +
-  ylab("Detection rate") + 
-  ylim(c(0,1))
-
-plots %>% ggplot(aes(x = trend, y = pdetect, fill = trend)) + 
-  geom_boxplot() + 
-  scale_fill_manual(values = trend_colours) +
-  geom_jitter(width = 0.1) +
-  ylab("Detection rate") + 
-  ylim(c(0,1))
-
-plots %>% ggplot(aes(x = type, y = pdetect)) + 
-  geom_boxplot() + 
-  geom_jitter(width = 0.1) +
-  ylab("Detection rate") + 
-  ylim(c(0,1))
-```
-
-## Individual performance
-
-```{r contributors, fig.cap = "The probablity of detection acheived by the contributors in each group is shown by the points.
-Group B has a larger range and a smaller inter-quartile range.
-Group A and  both had 3 people who did not find any of the data maps in the displays."}
-# Check contributor performance
-contribs <- d %>% group_by(group, contributor) %>% 
-  # pdetect measures the aggregated accuracy of the choices
-  summarise(pdetect = mean(detect, na.rm = TRUE))
-
-# Plot performance
-contribs %>% ggplot(aes(x = group, y = pdetect)) + 
-  geom_boxplot() + 
-  geom_jitter(width = 0.1, height = 0, alpha = 0.7) + 
-  ylab("Detection rate") + 
-  ylim(0,1)
-```
-
-## Demographics:
-
-```{r demogs, results = "asis", fig.cap = "The distribution of age groups of pariticpants."}
-# Create one record for each contributor, to examine demographics
-dem_contribs <- d %>%
-  group_by(contributor) %>%
-  slice(1) %>% ungroup()
-
-# Demographics of contributors
-#dem_contribs %>% count(gender)
-dem_contribs %>% ggplot() + geom_bar(aes(age))
-```
-
-```{r gender, results = "asis", fig.cap = "The amount of participants who identify themselves by the pronouns He and She."}
-dem_contribs %>% mutate(Gender = gender) %>% 
-  count(Gender, name = "Amount") %>% knitr::kable(format = "latex", booktabs = TRUE)
-```
-
-```{r education, results = "asis", fig.cap = "The highest level of education acheived by the participants "}
-dem_contribs %>%
-  mutate(Education = factor(education, levels = c("High School", "Bach", "Masters"), labels = c("High School Diploma", "Bachelors Degree", "Masters Degree"))) %>% 
-    count(Education, name =  "Amount") %>% knitr::kable(format = "latex", booktabs = TRUE)
-```
 
@@
 
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualisations.
+The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations.
 They would also like to thank Distinguished Professor Kerrie Mengersen and Doctor Earl Duncan for suggestions and comments.
@@
 \newpage
-References {#references .numbered}
+References {.numbered}
 ==========

### 2020-01-12 paper/paper.tex
American English spelling

@@
 The choropleth map display is commonly used for communicating spatial distributions across geographic areas.
-However, when choropleths are used, the sizes of areas can lead to misinterpretation of the distribution.
-The visualisation method used to present geospatial data will influence the understanding of the distribution derived by map users.
+However, when choropleths are used, the sizes of areas can lead to the misinterpretation of the distribution.
+The visualization method used to present geospatial data will influence the understanding of the distribution derived by map users.
 Choosing an effective alternative display could positively influence the communication of the spatial distribution.
-The hexagon tile map is presented as an alternative display for effectively visualising population related distributions.
+The hexagon tile map is presented as an alternative display for visualizing population related distributions effectively.
 Visual inference is used to measure the power of design, and the choropleth is used as a comparison.
-The hexagon tile map display is also tested using a distribution that is directly related to the geography, with values monotonically decreasing from the North West to South East areas of Australia.
+The hexagon tile map display is also tested using a distribution that is directly related to the geography, with values monotonically decreasing from the North-West to South-East areas of Australia.
 This study finds the single map in a hexagon tile map lineup that contains a population related distribution is detected with greater probability than the same data displayed in a choropleth map.
-These findings should encourage map creators to implement alternative displays, and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
+These findings should encourage map creators to implement alternative displays and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
 \end{abstract}
@@
 This study compares the effectiveness of a new type of display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics.
-The choropleth map is the traditional approach for visualising aggregated statistics across administrative boundaries.
+The choropleth map is the traditional approach for visualizing aggregated statistics across administrative boundaries.
 A hexagon tile map forgoes the familiar boundaries, in favor of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location.
@@
 
-Spatial visualisations communicate the distribution of statistics over geographic space.
+Spatial visualizations communicate the distribution of statistics over geographic space.
 The most common display for spatial data is the choropleth map.
 It is used to present aggregated statistics for geographic units such as the population.
-Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic.
+Creating a choropleth map involves drawing the administrative boundaries and filling them with color to communicate the value of the statistic.
 However, using a choropleth map base introduces biases when considering population related distributions {[}\protect\hyperlink{ref-CBATCC}{4}{]}.
@@
 The rural communities in Australia operate on a much larger geographic space than small inner-city communities.
-When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
-This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention {[}\protect\hyperlink{ref-CTTMB}{5}{]}.
+When a spatial distribution relates to the size of the areas, or the population density, the size of the regions can result in erroneous conclusions about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
+This occurs as large regions filled with a consistent color or pattern can draw the attention of map readers, and small regions are not paid equal attention {[}\protect\hyperlink{ref-CTTMB}{5}{]}.
 An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas {[}\protect\hyperlink{ref-NISCC}{6}{]}.
@@
 A cartogram transforms the geographic map base.
-The transformation begins with a choropleth map, and the values of a statistic such as population, for each geographic unit.
+The transformation begins with a choropleth map and the values of a statistic such as population for each geographic unit.
 There are several algorithms for transformation {[}\protect\hyperlink{ref-ACTUC}{7}{]}, {[}\protect\hyperlink{ref-CBATCC}{4}{]}; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
 The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units.
-The transformation will keep boundaries of neighbouring areas connected, but the result is unfamiliar shapes for each geographic unit.
+The transformation will keep boundaries of neighboring areas connected, but the result is unfamiliar shapes for each geographic unit.
 
 Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units.
-The non-contiguous cartgoram method {[}\protect\hyperlink{ref-NAC}{8}{]} keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics.
-This method disconnects areas when shrinking boundaries, and breaks the spatial relationship between areas.
-However, the empty space created emphasises the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
-The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{7}{]} is another method that does not retain the boundaries of geographic units.
-Each unit becomes one circle on the cartogram display; the circles are sized according to the value of a the statistic, such as population.
-The neighbour relationships can be illustrated by connecting the boundaries of the circles.
-A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{9}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{10}{]}.
+The non-contiguous cartogram method {[}\protect\hyperlink{ref-NAC}{8}{]} keeps the shapes of geographic units intact and changes the size of the shape to communicate the values of statistics.
+This method disconnects areas when shrinking boundaries and breaks the spatial relationship between areas.
+However, the empty space created emphasizes the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
+The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{7}{]} is another method that does not keep the boundaries of geographic units.
+Each unit becomes one circle on the cartogram display; it sizes the circles according to the value of the statistic, such as population.
+The neighbor relationships can be illustrated by connecting the boundaries of the circles.
+A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{9}{]}, using rectangles that tile to align borders of neighbors {[}\protect\hyperlink{ref-CDWCS}{10}{]}.
 These cartogram methods all allow two variables to be shown in the single display. These methods are discussed further in XXX cite review paper.
@@
 \caption{\label{fig:liver}The smoothed average of liver cancer diagnoses for Australian males.
-The divering colour scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average.}
+The divering color scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average.}
 \end{figure}
 
-Australia is an extreme case of heterogenous geographic units, with large difference between the smallest and largest geographic units across various granularities.
-To communicate information regarding the small inner-city geographic units of Australian cities an alternative display must be employed.
-This will emphasise the value of the statistic for areas with high population.
+Australia is an extreme case of heterogeneous geographic units, with the large differences between the smallest and largest geographic units across various granularities.
+To communicate information regarding the small inner-city geographic units of Australian cities, an alternative display must be employed.
+This will emphasize the value of the statistic for areas with a high population.
 Fig.
-\ref{fig:liver} shows the distribution of the smoothed average amount of Liver cancer diagnoses for Australian Males from 2005-2014.
+\ref{fig:liver} shows the distribution of the smoothed average amount of liver cancer diagnoses for Australian Males from 2005 to 2014.
 These inner-city areas are not visible on the choropleth map (a).
 The hexagon tile map (b) shows orange hexagons for the inner-city SA2s with higher than average levels of diagnoses in the capital cities of Melbourne and Sydney.
-The northern Queensland, and Northern Territory SA2's with higher than average rates are still visible but use less map space on the hexagon tile map.
+The northern Queensland and Northern Territory SA2s with higher than average rates are still visible but use less map space on the hexagon tile map.
 There are still many light blue areas in both displays.
@@
 
-The hexagon tile map is suggested as an alternative display.
-To test the effectiveness of these displays there is a formal testing framework.
-Visual inference considers the communication of data or data summaries through visualisations.
-It considers these visualisations to be visual statistics, with observable features.
-
-Classical statistical inference involves hypothesis testing, the process of rejecting a null hypothesis in favour of an alternative.
-This approach requires appropriate data, with the appropriate distributions and their assumptions.
-The lineup protocol was formalised as a test for the effectiveness of a visualisation.
-Rather than use classical statistical tests, human participants are tasked with finding the display that shows structure between the variables.
-If the structure is not detected, then it is not significantly different from the null data.
+We suggest the hexagon tile map as an alternative display.
+To test the effectiveness of these displays, there is a formal testing framework.
+Visual inference considers the communication of data or data summaries through visualizations.
+It considers these visualizations to be visual statistics, with observable features.
+
+Classical statistical inference involves hypothesis testing, rejecting a null hypothesis in favor of an alternative. This approach requires data with the appropriate distributions and assumptions.
+The lineup protocol was formalized as a test for the effectiveness of a visualization.
+Rather than classical statistical tests, it tasks human participants with finding the display that shows structure between the variables.
+If they do not detect the structure, then it is not significantly different from the null data.
 
@@
 \begin{itemize}
-\item
-  Null hypothesis: There is NO relationship between the variables,
-\item
-  Alternative hypothesis: There is a relationship between the variables.
+\tightlist
+\item
+  Null hypothesis: There is \bf{no} relationship between the variables
+\item
+  Alternative hypothesis: There is a relationship between the variables
 \end{itemize}
 
-To test these hypotheses, the line up protocol randomly places a ``guilty'' data visualisation in a lineup of ``innocents''.
+To test these hypotheses, the line up protocol randomly places a ``guilty'' data visualization in a lineup of ``innocents''.
 Where the guilty data set contains structure, and the innocents data sets do not.
-In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the innocents {[}\protect\hyperlink{ref-GTPCCD}{11}{]}.
-The guilty data is identified as different from the innocent data with probability \(1/m\), where \(m\) is the number of null plots plus 1 to account account for the guilty data set.
-When the guilty data set is chosen, the null hypothesis that it was innocent is rejected with a \(1/m\) chance or type I error of being wrong.
-
-The lineup protocol can be used in a variety of testing scenarios for visualisations.
+In a grid of visualizations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the innocents {[}\protect\hyperlink{ref-GTPCCD}{11}{]}.
+The participants identify the guilty data as different from the innocent data with probability \(1/m\), where \(m\) is the number of null plots plus 1 to account for the guilty data set.
+When the guilty data set is chosen we reject the null hypothesis that it was innocent is rejected with a \(1/m\) chance or type I error of being wrong.
+
+The lineup protocol can be used in a variety of testing scenarios for visualizations.
 {[}\protect\hyperlink{ref-GIIV}{3}{]} suggest the choropleth map for testing spatial structure in a data set.
 The lineup protocol allows for flexibility in the definition of null data.
-In the case of spatial visualisations it is likely that neighbours are related to some degree.
+In the case of spatial visualizations, it is likely that neighbors are related.
 To account for this, null data sets can be generated by sampling from a known model that accounts for spatial covariance.
 
-To contrast the effectiveness of two displays, the data set of null data plots with a hidden real data plot can be produced using the different plot designs.
-The time taken by participants to evaluate the same data in the different displays can be compared. Their accuracy in detecting the real data plot can also be calculated and contrasted.
+To contrast the effectiveness of two displays, we can produce null data plots with a hidden real data plot using the different plot designs.
+We can compare the time taken by participants to evaluate the same data in the different displays. We can also contrast the accuracy achieved by participants in detecting the real data plot.
 
@@
 \item
-  Are spatial disease trends, that impact highly populated small areas, detected with higher accuracy when viewed in a hexagon tile map display?
-\item
-  Are people faster in detecting spatial disease trends, that impact highly populated small areas, when using a hexagon tile map display?
+  Are spatial disease trends that impact highly populated small areas detected with higher accuracy, when viewed in a hexagon tile map display?
+\item
+  Are people faster in detecting spatial disease trends that impact highly populated small areas when using a hexagon tile map display?
 \end{enumerate}
 
-Additional considerations when completing this experimental task included exploration of the difficulty experienced by participants, and the certainty they felt about their decision.
+Additional considerations when completing this experimental task included exploration of the difficulty experienced by participants and the certainty they felt about their decision.
 
@@
 
-The difference in the detection rates for the two displays will be compared using a two sample unpaired t-test.
-
 \hypertarget{participants}{%
@@
 
-Participants were recruited for a survey style task to test the effectiveness of the hexagon tile map display.
-It was expected that the participants were uninvolved judges that had no prior knowledge of the data, to avoid discrimination or advantages.
-The Figure-Eight crowd source platform was used to advertise the survey to potential participants that had acheived level 2 or level 3 on the Figure-Eight Platform.
-The participants were chosen as they have experience with survey tasks that involve evaluating images. They participants on the platform are also required to be at least 18 years old.
+We recruited participants for the survey style task to test the effectiveness of the hexagon tile map display.
+The lineup protocol expects that the participants are uninvolved judges that had no prior knowledge of the data to avoid discrimination or advantages.
+The Figure-Eight crowd source platform was used to advertise the survey to potential participants that had achieved level 2 or level 3 on the Figure-Eight Platform.
+The participants were chosen as they have experience with survey tasks that involve evaluating images. The participants were at least 18 years old, as it is a requirement of the platform.
 
 Participants were able to choose to participate by selecting this task from the list of tasks available to them.
+Participants were allocated to either group A or group B when they proceeded to the survey web application, hosted externally from the Figure-Eight website.
 There were 95 participants involved in the study.
 All of these participants read the introductory materials and viewed example questions before proceeding to the survey.
-Each participant was trained using three test displays orienting them to the evaluation task, these displays are shown in appendix section regarding {[}training{]}.
+Each participant was trained using three test displays orienting them to the evaluation task.
 All participants who volunteered to take part were compensated for their time via the payment system of Figure-Eight.
-
-Participants were allocated to either group A or group B when they proceeded to the survey web application, hosted externally from the Figure-Eight website.
 
@@
 
-The variables that were changed between groups were the type of plot shown and the trend model.
-
-The twenty-four lineup displays were created by a combination of map type, and spatial trend model.
-This set of displays was split into a collection of twelve displays for Group A and twelve displays for Group B.
-
-Each participant was randomly allocated to either Group A or Group B when they begun the survey. This resulted in 42 participants allocated to Group A, and 53 participants allocated to Group B.
+The variables changed between groups were the type of plot shown and the trend model.
+
+A combination of map type and spatial trend model created the twenty-four lineup displays.
+We split this set of displays into a collection of twelve displays for Group A and twelve displays for Group B.
+The random allocation of participants to Group A or Group B resulted in 42 participants allocated to Group A and 53 participants allocated to Group B.
 
@@
 
-The choropleth map was used as the comparative visualisation for presenting the lineups {[}\protect\hyperlink{ref-VVSIALM}{13}{]} as this is the common display for spatial cancer data.
-Geographic distributions usually have some degree of spatial autcorrelation between neighbours.
+The choropleth map was used as the comparative visualization for presenting the lineups {[}\protect\hyperlink{ref-VVSIALM}{13}{]} as this is the common display for spatial cancer data.
+Geographic distributions usually have some degree of spatial autcorrelation between neighbors.
 This feature was incorporated in all maps shown in the lineup displays, the map that contained the trend feature shown in only one set of data was also affected by spatial autocorrelation.
@@
 
-\hypertarget{visualisations}{%
-\subsubsection{Visualisations}\label{visualisations}}
+\hypertarget{visualizations}{%
+\subsubsection{visualizations}\label{visualizations}}
 
@@
 \caption{\label{fig:beeswarm}The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots.
-The coloured point indicates average time taken for each plot type.
+The colored point indicates average time taken for each plot type.
 Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between plot types.}
@@
 Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons.
-``Colour trend across the areas'' was the most common selection for NW-SE trend displays.
-The colour scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
-Due to the consisent colouring of rural areas in a choropleth display, the choice ``All areas have similar colours'' was most common reason.
-The All Cities displays coloured the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural colour consistency.
+``color trend across the areas'' was the most common selection for NW-SE trend displays.
+The color scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
+Due to the consisent coloring of rural areas in a choropleth display, the choice ``All areas have similar colors'' was most common reason.
+The All Cities displays colored the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural color consistency.
 
 The reasons used when viewing choropleth displays varied more than the hexagon tile map reasons.
-The hexagon tile map displays resulted in ``Clusters of colour'' as the most common choice made by participants.
+The hexagon tile map displays resulted in ``Clusters of color'' as the most common choice made by participants.
 This response was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions.
 It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays.
-Due to the spatial covariance introduced in the smoothing, groups of similarly coloured hexagons were present in all of the hexagon tile map displays.
+Due to the spatial covariance introduced in the smoothing, groups of similarly colored hexagons were present in all of the hexagon tile map displays.
 All Cities and Three Cities distributions of real data trends had distinctly different patterns or red inner-city areas, while some of the plots in each lineup may have shared similar features.
@@
 
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualisations.
+The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations.
 They would also like to thank Kerrie Mengersen and Dr.~Earl Duncan for suggestions and comments.
@@
 \includegraphics{paper_files/figure-latex/contributors-1.pdf}
-\caption{\label{fig:contributors}The probablity of detection acheived by the contributors in each group is shown by the points.
+\caption{\label{fig:contributors}The probablity of detection achieved by the contributors in each group is shown by the points.
 Group B has a larger range and a smaller inter-quartile range.
@@
 The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{14}{]} with the use of the following packages:
-- For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{16}{]}, rticles {[}\protect\hyperlink{ref-rticles}{17}{]}, knitr {[}\protect\hyperlink{ref-knitr}{18}{]}.
-- For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{19}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{20}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{21}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{22}{]}.
-- For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{23}{]}, png {[}\protect\hyperlink{ref-png}{24}{]}, grid {[}\protect\hyperlink{ref-grid}{25}{]}.
-- For modeling and presentation of models: lme4 {[}\protect\hyperlink{ref-lme4}{15}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{26}{]}.
+
+\begin{itemize}
+\tightlist
+\item
+  For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{16}{]}, rticles {[}\protect\hyperlink{ref-rticles}{17}{]}, knitr {[}\protect\hyperlink{ref-knitr}{18}{]}.
+\item
+  For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{19}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{20}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{21}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{22}{]}.
+\item
+  For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{23}{]}, png {[}\protect\hyperlink{ref-png}{24}{]}, grid {[}\protect\hyperlink{ref-grid}{25}{]}.
+\item
+  For modeling and presentation of models: lme4 {[}\protect\hyperlink{ref-lme4}{15}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{26}{]}.
+\end{itemize}
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\hypertarget{references-1}{%
+\section{References}\label{references-1}}
 

### 2020-01-12 paper/supplementary/lineups.Rmd
American English spelling

@@
 ```{r data}
-
 library(tidyverse)
@@
 
-## Lineups
+# Overall Performance
+
+The detection rate is considered for each lineup.
+The detection rates for group A were less varied than the detection rates for the lineups seen by group B.
+Fig.
+\ref{fig:pdetection-group} shows the distribution using a boxplot.
+This shows the median value for detection rate was extremely similar.
+
+```{r pdetection-group}
+plots %>% ggplot(aes(x = group, y = pdetect)) + 
+  geom_boxplot() + 
+  geom_jitter(width = 0.1) +
+  ylab("Detection rate") + 
+  ylim(c(0,1))
+```
+
+The overall detection rate is considered for each trend model in Fig. \ref{fig:pdetect-trend}.
+The detection rates for the NW-SE trend model was less varied than the detection rates for the Three Cities and All Cities trends.
+Fig.
+\ref{fig:pdetection-group} shows the distribution using a boxplot.
+This shows the distributions of the rates do not overlap for NW-SE and Three Cities trends, the Three cities range was larger, but the median was much higher for the NW-SE trend.
+The All Cities trend model distribution overlaps with the NW-SE and All Cities trends.
+
+```{r pdetect-trend}
+plots %>% ggplot(aes(x = trend, y = pdetect, fill = trend)) + 
+  geom_boxplot() + 
+  scale_fill_manual(values = trend_colours) +
+  geom_jitter(width = 0.1) +
+  ylab("Detection rate") + 
+  ylim(c(0,1)) 
+```
+
+The boxplots in Fig. \ref{fig:pdetection-type} contrast the distribution of the detection rates for eah type of display.
+The detection rates across the lineups was less varied for the hexagon display. There was a large difference in the medians for the types of displays.
+Without considering the relationship for each lineup, the hexagon lineup display allowed the participants to achieve higher detection rates.
+
+```{r pdetection-type}
+plots %>% ggplot(aes(x = type, y = pdetect, fill = type)) + 
+  geom_boxplot() + 
+  geom_jitter(width = 0.1) +
+  scale_fill_manual(values = type_colours) +
+  ylab("Detection rate") + 
+  ylim(c(0,1))
+```
+
+# Lineups
 
@@
 knitr::kable(choice_tabs$data[[1]], format = "latex", align = "rrrrrrrrrrrrrr",
-  caption = "NW-SE") %>%
+  caption = "The proportion of participants who selected each of the twelve map choices in each lineup for NW-SE displays.") %>%
   collapse_rows(., columns = c(1,2))
@@
 knitr::kable(choice_tabs$data[[2]], format = "latex", align = "rrrrrrrrrrrrrr",
-  caption = "Three Cities") %>%
+  caption = "The proportion of participants who selected each of the twelve map choices in each lineup for Three Cities displays.") %>%
   collapse_rows(., columns = c(1,2))
@@
 knitr::kable(choice_tabs$data[[3]], format = "latex", align = "rrrrrrrrrrrrrr",
-  caption = "All Cities") %>%
+  caption = "The proportion of participants who selected each of the twelve map choices in each lineup for All Citiesdisplays.") %>%
   collapse_rows(., columns = c(1,2))
@@
 
-The same data set is shown in both displays, the difference is the land area of each SA3 is coloured in the choropleth and the hexagon representing the SA3 is coloured in the Hexagon Tile Map.
+The same data set is visualised in both displays, the difference is the land area of each SA3 is coloured in the choropleth and the hexagon representing the SA3 is coloured in the Hexagon Tile Map.
 
@@
 
-```{r cities-geo4, results = "asis", fig.cap = "The lineup of choropleth map displays hides a distribution that affects all capital cities.", fig.width = 5, fig.height = 4}
+```{r cities-geo4, results = "asis", fig.cap = "The lineup of choropleth map displays hides a distribution that affects all capital cities."}
 ggdraw() +
@@
 However, the colour blue dominates the display as the large rural areas are filled.
-Replicate (2) for All Cities.", fig.width = 4, fig.height = 4}
+Replicate (2) for All Cities."}
 ggdraw() +
@@
 
-```{r cities-geo3, results = "asis", fig.cap = "The lineup of choropleth map displays hides a distribution that affects all capital cities.", fig.width = 4, fig.height = 4}
+```{r cities-geo3, results = "asis", fig.cap = "The lineup of choropleth map displays hides a distribution that affects all capital cities."}
 ggdraw() +

### 2020-01-12 paper/paper.Rmd
background being revised, still need to add material on the hexagon tile map

--- 2020-01-12 paper/paper.Rmd
@@
 
-## Population focussed displays
+## Spatial data displays
 
-Spatial visualisations communicate the distribution of statistics over geographic space.
-The most common display for spatial data is the choropleth map.
-It is used to present aggregated statistics for geographic units such as the population.
-Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic.
-However, using a choropleth map base introduces biases when considering population related distributions [@CBATCC].
-Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
+<!-- foundation, tradition -->  
+Spatial visualisations communicate the distribution of statistics over geographic landscapes.
+The choropleth map (XXX REF) is a traditional display.
+It is used to present statistics that have been aggregated on geographic units.
+Creating a choropleth map involves drawing polygons representing the administrative boundaries, and filling with colour mapped to the value of the statistic.
+The choropleth map places the statistic in the context of the spatial domain, so that the reader can see whether there are spatial trends, clusters or anomalies.
+This is important for digesting disease patterns.
+If there is a trend it may imply that the disease is spreading from one location to another.
+If there is a cluster, or an anomaly, there may be a localized outbreak of the disease.
+Aggregating the statistic on administrative units, provides a level of privacy to individuals, while allowing the impact of the disease on the community to be analyzed.
+
+The choropleth map is effective if the size of the geographic units is relatively uniform.
+This is not the case for most countries.
+Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips.
+A choropleth map focuses attention on the geography, and for heterogeously sized areas it presents a biased view of the population related distribution of the statistic [@CBATCC].
+*Land doesn't get cancer, people do* -- a more effective way to communicate the spatial distributions of cancer statistics is needed.
+
+<!-- Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
 The rural communities in Australia operate on a much larger geographic space than small inner-city communities.
@@
 Alternative maps include various cartograms and tessellated tile maps. They allow other variables to be incorporated in the display to highlight the statistical values of various geographic areas.
+-->
 
 <!-- Cartogram -->
-A cartogram transforms the geographic map base.
-The transformation begins with a choropleth map, and the values of a statistic such as population, for each geographic unit.
-There are several algorithms for transformation [@ACTUC], [@CBATCC]; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
-<!-- Why not a cartogram-->
-The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units.
-The transformation will keep boundaries of neighbouring areas connected, but the result is unfamiliar shapes for each geographic unit.
+A cartogram is a general solution for better displaying a population-based statistic.
+It transforms the geographic map base to reflect the population in the geographic region, while preserving some aspects of the geographic location.
+There are several cartogram algorithms [@ACTUC], [@CBATCC]; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
+The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units but can result in losing the familiar geographic information.
+For Australia, the transformations warp the country so that it is no longer recognizable.
 
-<!-- Tesselated tile gram & hexagon tile map-->
-Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units.
-The non-contiguous cartgoram method [@NAC] keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics.
-This method disconnects areas when shrinking boundaries, and breaks the spatial relationship between areas.
-However, the empty space created emphasises the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
-The Dorling cartogram [@ACTUC] is another method that does not retain the boundaries of geographic units.
-Each unit becomes one circle on the cartogram display; the circles are sized according to the value of a the statistic, such as population.
-The neighbour relationships can be illustrated by connecting the boundaries of the circles.
+<!-- Tesselated tile gram -->
+Alternative algorithms make various trade offs between familiar shapes and representation of geographic units.
+The non-contiguous cartogram method [@NAC] keeps the shapes of geographic units intact, and changes the size of the shape.
+This method disconnects areas creating empty space on the display losing the continuity of the spatial display of the statistic.
+The Dorling cartogram [@ACTUC] represents each unit as a circle, sized according to the value of the statistic.
+The neighbour relationships are mostly maintained by how the circles touch.
 A similar approach was pioneered by Raisz [-@RSCW], using rectangles that tile to align borders of neighbours [@CDWCS].
-These cartogram methods all allow two variables to be shown in the single display. These methods are discussed further in XXX cite review paper.
+A thorough review of the array of methods, as suitable for cancer atlas displays is available in XXX.
 
 ```{r liver, fig.height = 9, fig.width = 6, fig.cap = "The smoothed average of liver cancer diagnoses for Australian males.
-The divering colour scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average."}
+The divering colour scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average.", fig.show="show"}
 ggdraw(ylim = c(0,2), xlim = c(0,1.3), clip = "on") +
@@
 ```
+<!--
+This will create the figure as needed in the paper, but I can't get the width argument to work properly.
+\begin{figure*}[!t]
+\centering
+\includegraphics{paper_files/figure-latex/liver-1.pdf}
+\caption{A choropleth map (a), and hexagon tile map (b) of the smoothed average of liver cancer diagnoses for Australian males.
+The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
+The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.}
+\label{fig:liver2}
+\end{figure*}
+-->
+
+<!-- hexagon tile map -->
 
@@
 There are still many light blue areas in both displays.
+-->
 

### 2020-01-12 paper/paper.tex
background being revised, still need to add material on the hexagon tile map

--- 2020-01-12 paper/paper.tex
@@
 
-\hypertarget{population-focussed-displays}{%
-\subsection{Population focussed displays}\label{population-focussed-displays}}
-
-Spatial visualisations communicate the distribution of statistics over geographic space.
-The most common display for spatial data is the choropleth map.
-It is used to present aggregated statistics for geographic units such as the population.
-Creating a choropleth map involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic.
-However, using a choropleth map base introduces biases when considering population related distributions {[}\protect\hyperlink{ref-CBATCC}{4}{]}.
-Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
-The rural communities in Australia operate on a much larger geographic space than small inner-city communities.
-When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
-This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention {[}\protect\hyperlink{ref-CTTMB}{5}{]}.
-An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas {[}\protect\hyperlink{ref-NISCC}{6}{]}.
-This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
-
-A choropleth map is not the only display that can be used for presenting geospatial data.
-Alternative maps include various cartograms and tessellated tile maps. They allow other variables to be incorporated in the display to highlight the statistical values of various geographic areas.
-
-A cartogram transforms the geographic map base.
-The transformation begins with a choropleth map, and the values of a statistic such as population, for each geographic unit.
-There are several algorithms for transformation {[}\protect\hyperlink{ref-ACTUC}{7}{]}, {[}\protect\hyperlink{ref-CBATCC}{4}{]}; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
-The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units.
-The transformation will keep boundaries of neighbouring areas connected, but the result is unfamiliar shapes for each geographic unit.
-
-Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units.
-The non-contiguous cartgoram method {[}\protect\hyperlink{ref-NAC}{8}{]} keeps the shapes of geographic units intact, and change the size of the shape to communicate the values of statistics.
-This method disconnects areas when shrinking boundaries, and breaks the spatial relationship between areas.
-However, the empty space created emphasises the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
-The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{7}{]} is another method that does not retain the boundaries of geographic units.
-Each unit becomes one circle on the cartogram display; the circles are sized according to the value of a the statistic, such as population.
-The neighbour relationships can be illustrated by connecting the boundaries of the circles.
-A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{9}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{10}{]}.
-These cartogram methods all allow two variables to be shown in the single display. These methods are discussed further in XXX cite review paper.
-
-\begin{figure}
-\centering
+\hypertarget{spatial-data-displays}{%
+\subsection{Spatial data displays}\label{spatial-data-displays}}
+
+Spatial visualisations communicate the distribution of statistics over geographic landscapes.
+The choropleth map (XXX REF) is a traditional display.
+It is used to present statistics that have been aggregated on geographic units.
+Creating a choropleth map involves drawing polygons representing the administrative boundaries, and filling with colour mapped to the value of the statistic.
+The choropleth map places the statistic in the context of the spatial domain, so that the reader can see whether there are spatial trends, clusters or anomalies.
+This is important for digesting disease patterns.
+If there is a trend it may imply that the disease is spreading from one location to another.
+If there is a cluster, or an anomaly, there may be a localized outbreak of the disease.
+Aggregating the statistic on administrative units, provides a level of privacy to individuals, while allowing the impact of the disease on the community to be analyzed.
+
+The choropleth map is effective if the size of the geographic units is relatively uniform.
+This is not the case for most countries.
+Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips.
+A choropleth map focuses attention on the geography, and for heterogeously sized areas it presents a biased view of the population related distribution of the statistic {[}\protect\hyperlink{ref-CBATCC}{4}{]}.
+\emph{Land doesn't get cancer, people do} -- a more effective way to communicate the spatial distributions of cancer statistics is needed.
+
+A cartogram is a general solution for better displaying a population-based statistic.
+It transforms the geographic map base to reflect the population in the geographic region, while preserving some aspects of the geographic location.
+There are several cartogram algorithms {[}\protect\hyperlink{ref-ACTUC}{5}{]}, {[}\protect\hyperlink{ref-CBATCC}{4}{]}; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
+The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units but can result in losing the familiar geographic information.
+For Australia, the transformations warp the country so that it is no longer recognizable.
+
+Alternative algorithms make various trade offs between familiar shapes and representation of geographic units.
+The non-contiguous cartogram method {[}\protect\hyperlink{ref-NAC}{6}{]} keeps the shapes of geographic units intact, and changes the size of the shape.
+This method disconnects areas creating empty space on the display losing the continuity of the spatial display of the statistic.
+The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{5}{]} represents each unit as a circle, sized according to the value of the statistic.
+The neighbour relationships are mostly maintained by how the circles touch.
+A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{7}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{8}{]}.
+A thorough review of the array of methods, as suitable for cancer atlas displays is available in XXX.
+
 \includegraphics{paper_files/figure-latex/liver-1.pdf}
-\caption{\label{fig:liver}The smoothed average of liver cancer diagnoses for Australian males.
-The divering colour scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average.}
-\end{figure}
 
@@
 There are still many light blue areas in both displays.
+--\textgreater{}
 
@@
 Where the guilty data set contains structure, and the innocents data sets do not.
-In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the innocents {[}\protect\hyperlink{ref-GTPCCD}{11}{]}.
+In a grid of visualisations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the innocents {[}\protect\hyperlink{ref-GTPCCD}{9}{]}.
 The guilty data is identified as different from the innocent data with probability \(1/m\), where \(m\) is the number of null plots plus 1 to account account for the guilty data set.
@@
 The data collection took place using a secure link between the survey web application and the googlesheet used to store results.
-The application would first connect to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{12}{]} R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
+The application would first connect to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{10}{]} R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
 
@@
 
-The choropleth map was used as the comparative visualisation for presenting the lineups {[}\protect\hyperlink{ref-VVSIALM}{13}{]} as this is the common display for spatial cancer data.
+The choropleth map was used as the comparative visualisation for presenting the lineups {[}\protect\hyperlink{ref-VVSIALM}{11}{]} as this is the common display for spatial cancer data.
 Geographic distributions usually have some degree of spatial autcorrelation between neighbours.
@@
 
-The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R {[}\protect\hyperlink{ref-RCore}{14}{]}.
+The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R {[}\protect\hyperlink{ref-RCore}{12}{]}.
 
@@
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R {[}\protect\hyperlink{ref-RCore}{14}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{15}{]} package implements generalised linear mixed effect models.
+The R {[}\protect\hyperlink{ref-RCore}{12}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{13}{]} package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 
-Computation will be done using R {[}\protect\hyperlink{ref-RCore}{14}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{15}{]}.
+Computation will be done using R {[}\protect\hyperlink{ref-RCore}{12}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{13}{]}.
 
@@
 
-The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{14}{]} with the use of the following packages:
-- For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{16}{]}, rticles {[}\protect\hyperlink{ref-rticles}{17}{]}, knitr {[}\protect\hyperlink{ref-knitr}{18}{]}.
-- For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{19}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{20}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{21}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{22}{]}.
-- For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{23}{]}, png {[}\protect\hyperlink{ref-png}{24}{]}, grid {[}\protect\hyperlink{ref-grid}{25}{]}.
-- For modeling and presentation of models: lme4 {[}\protect\hyperlink{ref-lme4}{15}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{26}{]}.
+The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{12}{]} with the use of the following packages:
+- For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{14}{]}, rticles {[}\protect\hyperlink{ref-rticles}{15}{]}, knitr {[}\protect\hyperlink{ref-knitr}{16}{]}.
+- For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{17}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{18}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{19}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{20}{]}.
+- For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{21}{]}, png {[}\protect\hyperlink{ref-png}{22}{]}, grid {[}\protect\hyperlink{ref-grid}{23}{]}.
+- For modeling and presentation of models: lme4 {[}\protect\hyperlink{ref-lme4}{13}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{24}{]}.
 
@@
 
-\leavevmode\hypertarget{ref-CTTMB}{}%
-5. Griffin TL (1980) Cartographic Transformation of the Thematic Map Base. Cartography 11:163--174
-
-\leavevmode\hypertarget{ref-NISCC}{}%
-6. Dent BD (1972) A Note on the Importance of Shape in Cartogram Communication. Journal of Geography 71:393--401
-
 \leavevmode\hypertarget{ref-ACTUC}{}%
-7. Dorling D (2011) Area Cartograms: Their Use and Creation. In: Concepts and techniques in modern geography (catmog). pp 252--260
+5. Dorling D (2011) Area Cartograms: Their Use and Creation. In: Concepts and techniques in modern geography (catmog). pp 252--260
 
 \leavevmode\hypertarget{ref-NAC}{}%
-8. Olson JM (1976) Noncontiguous Area Cartograms. The Professional Geographer 28:371--380
+6. Olson JM (1976) Noncontiguous Area Cartograms. The Professional Geographer 28:371--380
 
 \leavevmode\hypertarget{ref-RSCW}{}%
-9. Raisz E (1963) Rectangular Statistical Cartograms of the World. Journal of Geography 35:8--10
+7. Raisz E (1963) Rectangular Statistical Cartograms of the World. Journal of Geography 35:8--10
 
 \leavevmode\hypertarget{ref-CDWCS}{}%
-10. Monmonier M (2005) Cartography: Distortions, World-views and Creative Solutions. Progress in Human Geography 29:217--224
+8. Monmonier M (2005) Cartography: Distortions, World-views and Creative Solutions. Progress in Human Geography 29:217--224
 
 \leavevmode\hypertarget{ref-GTPCCD}{}%
-11. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448
+9. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448
 
 \leavevmode\hypertarget{ref-sheets}{}%
-12. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
+10. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
 
 \leavevmode\hypertarget{ref-VVSIALM}{}%
-13. Majumder M, Hofmann H, Cook D (2013) Validation of visual statistical inference, applied to linear models. Journal of the American Statistical Association 108:942--956
+11. Majumder M, Hofmann H, Cook D (2013) Validation of visual statistical inference, applied to linear models. Journal of the American Statistical Association 108:942--956
 
 \leavevmode\hypertarget{ref-RCore}{}%
-14. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+12. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
 
 \leavevmode\hypertarget{ref-lme4}{}%
-15. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
+13. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
 
 \leavevmode\hypertarget{ref-rmarkdown}{}%
-16. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida
+14. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida
 
 \leavevmode\hypertarget{ref-rticles}{}%
-17. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.
+15. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.
 
 \leavevmode\hypertarget{ref-knitr}{}%
-18. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research
+16. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research
 
 \leavevmode\hypertarget{ref-tidyverse}{}%
-19. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686
+17. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686
 
 \leavevmode\hypertarget{ref-nullabor}{}%
-20. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.
+18. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.
 
 \leavevmode\hypertarget{ref-ggthemes}{}%
-21. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.
+19. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.
 
 \leavevmode\hypertarget{ref-RColorBrewer}{}%
-22. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.
+20. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.
 
 \leavevmode\hypertarget{ref-cowplot}{}%
-23. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.
+21. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.
 
 \leavevmode\hypertarget{ref-png}{}%
-24. Urbanek S (2013) Png: Read and write png images.
+22. Urbanek S (2013) Png: Read and write png images.
 
 \leavevmode\hypertarget{ref-grid}{}%
-25. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+23. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
 
 \leavevmode\hypertarget{ref-kableExtra}{}%
-26. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
+24. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
 

### 2020-01-12 paper/paper.Rmd
Discussion draft

--- 2020-01-12 paper/paper.Rmd
@@
 The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts.
-One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in the appendix [Lineups] section.
+One replicate for the All Cities group, had similar detection rates for both plot type.
 Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map.
@@
 Allowing for the interaction effect, the difference in detection rate decreases for population related displays for a choroleth map lineup, but increases for a hexagon tile map display.
-The log odds of detection show in Table.
-\ref{tab:detect-glmer1} can be back transformed using \ref{eq:transform} after taking the sum of all terms for the trend and type of display that are of interest.
+The log odds of detection show in Table. \ref{tab:detect-glmer1} can be back transformed after taking the sum of all terms for the trend and type of display that are of interest.
 For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to `r round(exp(0.461+0.0220)/(1+exp(0.461+0.0220)), 2)` from `r round(exp(0.0220)/(1+exp(0.0220)),2)` for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
@@
 Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons. 
-"color trend across the areas" was the most common selection for NW-SE trend displays.
-The color scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
-Due to the consisent coloring of rural areas in a choropleth display, the choice "All areas have similar colors" was most common reason.
-The All Cities displays colored the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural color consistency.
+"Color trend across the areas" was the most common selection for NW-SE trend displays.
 
@@
 The hexagon tile map displays resulted in "Clusters of color" as the most common choice made by participants.
-This response was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions.
-It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays.
-Due to the spatial covariance introduced in the smoothing, groups of similarly colored hexagons were present in all of the hexagon tile map displays.
-All Cities and Three Cities distributions of real data trends had distinctly different patterns or red inner-city areas, while some of the plots in each lineup may have shared similar features.
 
@@
 
+The intention of this study was to contrast the use of the choropleth map and the hexagon tile map.
+The visual inference lineup protocol was employed to contrast the effectiveness of the displays.
+The results have shown that overall the use of the hexagon tile map display allows participants to find the data plot in the lineup more often.
+Using the visual inference protocol this result can be extended to show that it is a valid alternative display to communicate spatial distributions of population related data.
+
+We expected that the choropleth map would be superior for communicating the spatial pattern of geographic distributions.
+The data suggest that the participants perform slightly better or equally as well for each replicate in each trend model across the two displays.
+Table II shows that the difference in the mean detection rate for the two trend models was 0.10.
+
+The differences seen in the compare detect plot and Table.
+\ref{tab:desc-stats} are reflected in the model results.
+Surprisingly the difference scene for the geographic distribution was significant at the 0.05 level.
+It also showed that the hexagon tile map display performs marginally better than the choropleth for all trend models.
+Unexpectedly the detection rate suffers when using a choropleth map to display population related distributions.
+
+While the significance of the difference in detection was the key focus of this experiment, the secondary focus was the time taken by participants.
+it was expected that the disciplines may take longer to consider the hexagon tile map distribution but would be able to detect the data plot in the lineup.
+The bimodal distributions seen in the Fig.
+\ref{fig:choices} display showed very little difference in the mean evaluation times.
+As the ranges of all of the distributions approached 60 seconds it cannot be said that the participants' took longer to evaluate the hexagon tile map displays.
+
+The responses to the questions asked of participants included the reason for their choice and the certainty around their choice.
+Fig.
+\ref{fig:reason} shows high levels of certainty of 4 and 5 were chosen by participants when looking at the population distributions in a choropleth map display show that they were over confident when attempting to find the real data plot in the choropleth map displays.
+Participants performed better on the NW-SE distribution shown in the choropleth display and were reasonably confident about their decisions.
+The high levels of the mid range value of 3 could indicate that the participant did not want to provide a response, as this wasy the default value.
+Those who chose level 4 or 5 were equally likely to be correct for the three cities lineups, but more likely to be correct than incorrect for the other two trend models.
+
+The color scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
+Due to the consisent coloring of rural areas in a choropleth display, the choice "All areas have similar colors" was most common reason for a participants choice.
+The All Cities displays colored the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural color consistency.
+Choosing "Clusters of colour" was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions.
+It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays.
+Due to the spatial covariance introduced in the smoothing, groups of similarly colored hexagons were present in all of the hexagon tile map displays.
+All Cities and Three Cities distributions of real data trends had distinctly different patterns or red inner-city areas, while some of the plots in each lineup may have shared similar features.
+
 Conclusion
@@
 
-The choropleth map display and the tessellated hexagon tile map have been contrasted in a visual inference study. 
-The hexagon tile map was significantly more effective for spotting a real data trend model hidden in a lineup.
+The choropleth map display and the tessellated hexagon tile map have been contrasted using the lineup protocol.
+The hexagon tile map was significantly more effective for spotting a real population related data trend model hidden in a lineup.
 
-This hexagon tile map display should be considered as a visualization method when communicating distributions that relate to the population in each geographic unit.
-Cancer Atlas products may benefit from the opportunity to allow exploration via the traditional choropleth map method as well as an alternative display.
+The hexagon tile map display should be considered as an alternative visualization method when communicating distributions that relate to the population across a set of geographic units.
+As an additional display to the familiar choropleth map, Cancer Atlas products may benefit from the opportunity to allow exploration via an alternative display.
 The spatial distributions used to test these displays were inspired by the real spatially smoothed estimates of the cancer burden on Australian communities.
@@
 The population density structure of Australia can be considered similar to that of Canada, New Zealand and many others.
-Therefore, this display is not only relevant to Australia, but all nations or population collections that experience densely populated cities alongside vast rural expanses.
-
-<!-- conference papers do not normally have an appendix -->
+Therefore, this display is not only relevant to Australia, but all nations or population distributions that experience densely populated cities separated by vast rural expanses.
 

### 2020-01-12 paper/paper.tex
Discussion draft

--- 2020-01-12 paper/paper.tex
@@
 The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts.
-One replicate for the All Cities group, had similar detection rates for both plot types, and this is discussed in the appendix {[}Lineups{]} section.
+One replicate for the All Cities group, had similar detection rates for both plot type.
 Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map.
@@
 Allowing for the interaction effect, the difference in detection rate decreases for population related displays for a choroleth map lineup, but increases for a hexagon tile map display.
-The log odds of detection show in Table.
-\ref{tab:detect-glmer1} can be back transformed using \ref{eq:transform} after taking the sum of all terms for the trend and type of display that are of interest.
+The log odds of detection show in Table. \ref{tab:detect-glmer1} can be back transformed after taking the sum of all terms for the trend and type of display that are of interest.
 For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to 0.62 from 0.51 for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
@@
 Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons.
-``color trend across the areas'' was the most common selection for NW-SE trend displays.
-The color scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
-Due to the consisent coloring of rural areas in a choropleth display, the choice ``All areas have similar colors'' was most common reason.
-The All Cities displays colored the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural color consistency.
+``Color trend across the areas'' was the most common selection for NW-SE trend displays.
 
@@
 The hexagon tile map displays resulted in ``Clusters of color'' as the most common choice made by participants.
-This response was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions.
-It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays.
-Due to the spatial covariance introduced in the smoothing, groups of similarly colored hexagons were present in all of the hexagon tile map displays.
-All Cities and Three Cities distributions of real data trends had distinctly different patterns or red inner-city areas, while some of the plots in each lineup may have shared similar features.
 
@@
 
+The intention of this study was to contrast the use of the choropleth map and the hexagon tile map.
+The visual inference lineup protocol was employed to contrast the effectiveness of the displays.
+The results have shown that overall the use of the hexagon tile map display allows participants to find the data plot in the lineup more often.
+Using the visual inference protocol this result can be extended to show that it is a valid alternative display to communicate spatial distributions of population related data.
+
+We expected that the choropleth map would be superior for communicating the spatial pattern of geographic distributions.
+The data suggest that the participants perform slightly better or equally as well for each replicate in each trend model across the two displays.
+Table II shows that the difference in the mean detection rate for the two trend models was 0.10.
+
+The differences seen in the compare detect plot and Table.
+\ref{tab:desc-stats} are reflected in the model results.
+Surprisingly the difference scene for the geographic distribution was significant at the 0.05 level.
+It also showed that the hexagon tile map display performs marginally better than the choropleth for all trend models.
+Unexpectedly the detection rate suffers when using a choropleth map to display population related distributions.
+
+While the significance of the difference in detection was the key focus of this experiment, the secondary focus was the time taken by participants.
+it was expected that the disciplines may take longer to consider the hexagon tile map distribution but would be able to detect the data plot in the lineup.
+The bimodal distributions seen in the Fig.
+\ref{fig:choices} display showed very little difference in the mean evaluation times.
+As the ranges of all of the distributions approached 60 seconds it cannot be said that the participants' took longer to evaluate the hexagon tile map displays.
+
+The responses to the questions asked of participants included the reason for their choice and the certainty around their choice.
+Fig.
+\ref{fig:reason} shows high levels of certainty of 4 and 5 were chosen by participants when looking at the population distributions in a choropleth map display show that they were over confident when attempting to find the real data plot in the choropleth map displays.
+Participants performed better on the NW-SE distribution shown in the choropleth display and were reasonably confident about their decisions.
+The high levels of the mid range value of 3 could indicate that the participant did not want to provide a response, as this wasy the default value.
+Those who chose level 4 or 5 were equally likely to be correct for the three cities lineups, but more likely to be correct than incorrect for the other two trend models.
+
+The color scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
+Due to the consisent coloring of rural areas in a choropleth display, the choice ``All areas have similar colors'' was most common reason for a participants choice.
+The All Cities displays colored the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural color consistency.
+Choosing ``Clusters of colour'' was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions.
+It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays.
+Due to the spatial covariance introduced in the smoothing, groups of similarly colored hexagons were present in all of the hexagon tile map displays.
+All Cities and Three Cities distributions of real data trends had distinctly different patterns or red inner-city areas, while some of the plots in each lineup may have shared similar features.
+
 \hypertarget{conclusion}{%
@@
 
-The choropleth map display and the tessellated hexagon tile map have been contrasted in a visual inference study.
-The hexagon tile map was significantly more effective for spotting a real data trend model hidden in a lineup.
-
-This hexagon tile map display should be considered as a visualization method when communicating distributions that relate to the population in each geographic unit.
-Cancer Atlas products may benefit from the opportunity to allow exploration via the traditional choropleth map method as well as an alternative display.
+The choropleth map display and the tessellated hexagon tile map have been contrasted using the lineup protocol.
+The hexagon tile map was significantly more effective for spotting a real population related data trend model hidden in a lineup.
+
+The hexagon tile map display should be considered as an alternative visualization method when communicating distributions that relate to the population across a set of geographic units.
+As an additional display to the familiar choropleth map, Cancer Atlas products may benefit from the opportunity to allow exploration via an alternative display.
 The spatial distributions used to test these displays were inspired by the real spatially smoothed estimates of the cancer burden on Australian communities.
@@
 The population density structure of Australia can be considered similar to that of Canada, New Zealand and many others.
-Therefore, this display is not only relevant to Australia, but all nations or population collections that experience densely populated cities alongside vast rural expanses.
+Therefore, this display is not only relevant to Australia, but all nations or population distributions that experience densely populated cities separated by vast rural expanses.
 
@@
 \newpage
-
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-\hypertarget{overall-performance}{%
-\subsection{Overall Performance}\label{overall-performance}}
-
-\hypertarget{individual-performance}{%
-\subsection{Individual performance}\label{individual-performance}}
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/contributors-1.pdf}
-\caption{\label{fig:contributors}The probablity of detection achieved by the contributors in each group is shown by the points.
-Group B has a larger range and a smaller inter-quartile range.
-Group A and both had 3 people who did not find any of the data maps in the displays.}
-\end{figure}
-
-\hypertarget{demographics}{%
-\subsection{Demographics:}\label{demographics}}
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/demogs-1.pdf}
-\caption{\label{fig:demogs}The distribution of age groups of pariticpants.}
-\end{figure}
-
-\begin{tabular}{lr}
-\toprule
-Gender & Amount\\
-\midrule
-He & 67\\
-She & 25\\
-\bottomrule
-\end{tabular}
-
-\begin{tabular}{lr}
-\toprule
-Education & Amount\\
-\midrule
-High School Diploma & 23\\
-Bachelors Degree & 56\\
-Masters Degree & 13\\
-\bottomrule
-\end{tabular}
 

### 2020-01-12 paper/paper.Rmd

@@
 
-## Population focussed displays
+## Spatial data displays
 
-Spatial visualizations communicate the distribution of statistics over geographic space.
-The most common display for spatial data is the choropleth map.
-It is used to present aggregated statistics for geographic units such as the population.
-Creating a choropleth map involves drawing the administrative boundaries and filling them with color to communicate the value of the statistic.
-However, using a choropleth map base introduces biases when considering population related distributions [@CBATCC].
-Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
+<!-- foundation, tradition -->  
+Spatial visualisations communicate the distribution of statistics over geographic landscapes.
+The choropleth map [@EI], [@BCM] is a traditional display.
+It is used to present statistics that have been aggregated on geographic units.
+Creating a choropleth map involves drawing polygons representing the administrative boundaries, and filling with colour mapped to the value of the statistic.
+The choropleth map places the statistic in the context of the spatial domain, so that the reader can see whether there are spatial trends, clusters or anomalies.
+This is important for digesting disease patterns.
+If there is a trend it may imply that the disease is spreading from one location to another.
+If there is a cluster, or an anomaly, there may be a localized outbreak of the disease.
+Aggregating the statistic on administrative units, provides a level of privacy to individuals, while allowing the impact of the disease on the community to be analyzed.
+
+The choropleth map is effective if the size of the geographic units is relatively uniform.
+This is not the case for most countries.
+Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips.
+A choropleth map focuses attention on the geography, and for heterogeously sized areas it presents a biased view of the population related distribution of the statistic [@CBATCC].
+*Land doesn't get cancer, people do* -- a more effective way to communicate the spatial distributions of cancer statistics is needed.
+
+<!-- Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
 The rural communities in Australia operate on a much larger geographic space than small inner-city communities.
-When a spatial distribution relates to the size of the areas, or the population density, the size of the regions can result in erroneous conclusions about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
-This occurs as large regions filled with a consistent color or pattern can draw the attention of map readers, and small regions are not paid equal attention [@CTTMB].
+When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
+This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention [@CTTMB].
 An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas [@NISCC].
+>>>>>>> de6ff98be8766902375ed1f9fcdcea82b768d1ea
 This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
@@
 Alternative maps include various cartograms and tessellated tile maps. They allow other variables to be incorporated in the display to highlight the statistical values of various geographic areas.
+-->
 
 <!-- Cartogram -->
-A cartogram transforms the geographic map base.
-The transformation begins with a choropleth map and the values of a statistic such as population for each geographic unit.
-There are several algorithms for transformation [@ACTUC], [@CBATCC]; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
-<!-- Why not a cartogram-->
-The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units.
-The transformation will keep boundaries of neighboring areas connected, but the result is unfamiliar shapes for each geographic unit.
+A cartogram is a general solution for better displaying a population-based statistic.
+It transforms the geographic map base to reflect the population in the geographic region, while preserving some aspects of the geographic location.
+There are several cartogram algorithms [@ACTUC], [@CBATCC]; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
+The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units but can result in losing the familiar geographic information.
+For Australia, the transformations warp the country so that it is no longer recognizable.
 
-<!-- Tesselated tile gram & hexagon tile map-->
-Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units.
-The non-contiguous cartogram method [@NAC] keeps the shapes of geographic units intact and changes the size of the shape to communicate the values of statistics.
-This method disconnects areas when shrinking boundaries and breaks the spatial relationship between areas.
-However, the empty space created emphasizes the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
-The Dorling cartogram [@ACTUC] is another method that does not keep the boundaries of geographic units.
-Each unit becomes one circle on the cartogram display; it sizes the circles according to the value of the statistic, such as population.
-The neighbor relationships can be illustrated by connecting the boundaries of the circles.
-A similar approach was pioneered by Raisz [-@RSCW], using rectangles that tile to align borders of neighbors [@CDWCS].
-These cartogram methods all allow two variables to be shown in the single display. These methods are discussed further in XXX cite review paper.
+<!-- Tesselated tile gram -->
+Alternative algorithms make various trade offs between familiar shapes and representation of geographic units.
+The non-contiguous cartogram method [@NAC] keeps the shapes of geographic units intact, and changes the size of the shape.
+This method disconnects areas creating empty space on the display losing the continuity of the spatial display of the statistic.
+The Dorling cartogram [@ACTUC] represents each unit as a circle, sized according to the value of the statistic.
+The neighbour relationships are mostly maintained by how the circles touch.
+A similar approach was pioneered by Raisz [-@RSCW], using rectangles that tile to align borders of neighbours [@CDWCS].
+A thorough review of the array of methods, as suitable for cancer atlas displays is available in XXX.
 
 ```{r liver, fig.height = 9, fig.width = 6, fig.cap = "The smoothed average of liver cancer diagnoses for Australian males.
-The divering color scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average."}
+The divering colour scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average.", results = "asis"}
 ggdraw(ylim = c(0,2), xlim = c(0,1.3), clip = "on") +
@@
 ```
+<!--
+This will create the figure as needed in the paper, but I can't get the width argument to work properly.
+\begin{figure*}[!t]
+\centering
+\includegraphics{paper_files/figure-latex/liver-1.pdf}
+\caption{A choropleth map (a), and hexagon tile map (b) of the smoothed average of liver cancer diagnoses for Australian males.
+The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
+The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.}
+\label{fig:liver2}
+\end{figure*}
+-->
 
@@
 The bimodal distributions seen in the Fig.
-\ref{fig:choices} display showed very little difference in the mean evaluation times.
+\ref{fig:beeswarm} display showed very little difference in the mean evaluation times.
 As the ranges of all of the distributions approached 60 seconds it cannot be said that the participants' took longer to evaluate the hexagon tile map displays.

### 2020-01-12 paper/paper.tex

@@
 
-\hypertarget{population-focussed-displays}{%
-\subsection{Population focussed displays}\label{population-focussed-displays}}
-
-Spatial visualizations communicate the distribution of statistics over geographic space.
-The most common display for spatial data is the choropleth map.
-It is used to present aggregated statistics for geographic units such as the population.
-Creating a choropleth map involves drawing the administrative boundaries and filling them with color to communicate the value of the statistic.
-However, using a choropleth map base introduces biases when considering population related distributions {[}\protect\hyperlink{ref-CBATCC}{4}{]}.
-Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
-The rural communities in Australia operate on a much larger geographic space than small inner-city communities.
-When a spatial distribution relates to the size of the areas, or the population density, the size of the regions can result in erroneous conclusions about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
-This occurs as large regions filled with a consistent color or pattern can draw the attention of map readers, and small regions are not paid equal attention {[}\protect\hyperlink{ref-CTTMB}{5}{]}.
-An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas {[}\protect\hyperlink{ref-NISCC}{6}{]}.
-This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
-
-A choropleth map is not the only display that can be used for presenting geospatial data.
-Alternative maps include various cartograms and tessellated tile maps. They allow other variables to be incorporated in the display to highlight the statistical values of various geographic areas.
-
-A cartogram transforms the geographic map base.
-The transformation begins with a choropleth map and the values of a statistic such as population for each geographic unit.
-There are several algorithms for transformation {[}\protect\hyperlink{ref-ACTUC}{7}{]}, {[}\protect\hyperlink{ref-CBATCC}{4}{]}; they involve shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
-The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units.
-The transformation will keep boundaries of neighboring areas connected, but the result is unfamiliar shapes for each geographic unit.
-
-Alternative displays make the trade off between familiar shapes and representation of variables using the area of geographic units.
-The non-contiguous cartogram method {[}\protect\hyperlink{ref-NAC}{8}{]} keeps the shapes of geographic units intact and changes the size of the shape to communicate the values of statistics.
-This method disconnects areas when shrinking boundaries and breaks the spatial relationship between areas.
-However, the empty space created emphasizes the comparative density of the statistic, the difference between the statistic and the amount of land for each geographic unit.
-The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{7}{]} is another method that does not keep the boundaries of geographic units.
-Each unit becomes one circle on the cartogram display; it sizes the circles according to the value of the statistic, such as population.
-The neighbor relationships can be illustrated by connecting the boundaries of the circles.
-A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{9}{]}, using rectangles that tile to align borders of neighbors {[}\protect\hyperlink{ref-CDWCS}{10}{]}.
-These cartogram methods all allow two variables to be shown in the single display. These methods are discussed further in XXX cite review paper.
-
-\begin{figure}
-\centering
+\hypertarget{spatial-data-displays}{%
+\subsection{Spatial data displays}\label{spatial-data-displays}}
+
+Spatial visualisations communicate the distribution of statistics over geographic landscapes.
+The choropleth map {[}\protect\hyperlink{ref-EI}{4}{]}, {[}\protect\hyperlink{ref-BCM}{5}{]} is a traditional display.
+It is used to present statistics that have been aggregated on geographic units.
+Creating a choropleth map involves drawing polygons representing the administrative boundaries, and filling with colour mapped to the value of the statistic.
+The choropleth map places the statistic in the context of the spatial domain, so that the reader can see whether there are spatial trends, clusters or anomalies.
+This is important for digesting disease patterns.
+If there is a trend it may imply that the disease is spreading from one location to another.
+If there is a cluster, or an anomaly, there may be a localized outbreak of the disease.
+Aggregating the statistic on administrative units, provides a level of privacy to individuals, while allowing the impact of the disease on the community to be analyzed.
+
+The choropleth map is effective if the size of the geographic units is relatively uniform.
+This is not the case for most countries.
+Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips.
+A choropleth map focuses attention on the geography, and for heterogeously sized areas it presents a biased view of the population related distribution of the statistic {[}\protect\hyperlink{ref-CBATCC}{6}{]}.
+\emph{Land doesn't get cancer, people do} -- a more effective way to communicate the spatial distributions of cancer statistics is needed.
+
+A cartogram is a general solution for better displaying a population-based statistic.
+It transforms the geographic map base to reflect the population in the geographic region, while preserving some aspects of the geographic location.
+There are several cartogram algorithms {[}\protect\hyperlink{ref-ACTUC}{7}{]}, {[}\protect\hyperlink{ref-CBATCC}{6}{]}; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
+The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units but can result in losing the familiar geographic information.
+For Australia, the transformations warp the country so that it is no longer recognizable.
+
+Alternative algorithms make various trade offs between familiar shapes and representation of geographic units.
+The non-contiguous cartogram method {[}\protect\hyperlink{ref-NAC}{8}{]} keeps the shapes of geographic units intact, and changes the size of the shape.
+This method disconnects areas creating empty space on the display losing the continuity of the spatial display of the statistic.
+The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{7}{]} represents each unit as a circle, sized according to the value of the statistic.
+The neighbour relationships are mostly maintained by how the circles touch.
+A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{9}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{10}{]}.
+A thorough review of the array of methods, as suitable for cancer atlas displays is available in XXX.
+
 \includegraphics{paper_files/figure-latex/liver-1.pdf}
-\caption{\label{fig:liver}The smoothed average of liver cancer diagnoses for Australian males.
-The divering color scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average.}
-\end{figure}
 
@@
 
+\leavevmode\hypertarget{ref-EI}{}%
+4. Tufte ER (1990) Envisioning Information. Graphics Press
+
+\leavevmode\hypertarget{ref-BCM}{}%
+5.
+Skowronnek A (2016) Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata.
+In: Infovis Reading Group WS 2015/16.
+\url{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}.
+
 \leavevmode\hypertarget{ref-CBATCC}{}%
-4. Kocmoud C, House D (1998) A Constraint-based Approach to Constructing Continuous Cartograms. In: Proc. Symp. Spatial data handling. pp 236--246
-
-\leavevmode\hypertarget{ref-CTTMB}{}%
-5. Griffin TL (1980) Cartographic Transformation of the Thematic Map Base. Cartography 11:163--174
-
-\leavevmode\hypertarget{ref-NISCC}{}%
-6. Dent BD (1972) A Note on the Importance of Shape in Cartogram Communication. Journal of Geography 71:393--401
+6. Kocmoud C, House D (1998) A Constraint-based Approach to Constructing Continuous Cartograms. In: Proc. Symp. Spatial data handling. pp 236--246
 

### 2020-01-12 paper/paper.Rmd
done with spatial displays

@@
 
-The choropleth map is effective if the size of the geographic units is relatively uniform.
-This is not the case for most countries.
-Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips.
-A choropleth map focuses attention on the geography, and for heterogeously sized areas it presents a biased view of the population related distribution of the statistic [@CBATCC].
-*Land doesn't get cancer, people do* -- a more effective way to communicate the spatial distributions of cancer statistics is needed.
-
 <!-- Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
@@
 An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas [@NISCC].
->>>>>>> de6ff98be8766902375ed1f9fcdcea82b768d1ea
 This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
@@
 
-<!-- Cartogram -->
-A cartogram is a general solution for better displaying a population-based statistic.
-It transforms the geographic map base to reflect the population in the geographic region, while preserving some aspects of the geographic location.
-There are several cartogram algorithms [@ACTUC], [@CBATCC]; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
-The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units but can result in losing the familiar geographic information.
-For Australia, the transformations warp the country so that it is no longer recognizable.
-
-<!-- Tesselated tile gram -->
-Alternative algorithms make various trade offs between familiar shapes and representation of geographic units.
-The non-contiguous cartogram method [@NAC] keeps the shapes of geographic units intact, and changes the size of the shape.
-This method disconnects areas creating empty space on the display losing the continuity of the spatial display of the statistic.
-The Dorling cartogram [@ACTUC] represents each unit as a circle, sized according to the value of the statistic.
-The neighbour relationships are mostly maintained by how the circles touch.
-A similar approach was pioneered by Raisz [-@RSCW], using rectangles that tile to align borders of neighbours [@CDWCS].
-A thorough review of the array of methods, as suitable for cancer atlas displays is available in XXX.
-
-```{r liver, fig.height = 9, fig.width = 6, fig.cap = "The smoothed average of liver cancer diagnoses for Australian males.
-The divering colour scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average.", results = "asis"}
+```{r liver, fig.height = 6, fig.width = 4, fig.cap = "A choropleth map (a), and hexagon tile map (b) of the smoothed average of liver cancer diagnoses for Australian males.
+The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
+The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.", results = "asis"}
 ggdraw(ylim = c(0,2), xlim = c(0,1.3), clip = "on") +
@@
 
-<!-- Specific problem for Australia -->
+The choropleth map is effective if the size of the geographic units is relatively uniform.
+This is not the case for most countries.
+Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips.
+A choropleth map focuses attention on the geography, and for heterogeously sized areas it presents a biased view of the population related distribution of the statistic [@CBATCC].
+*Land doesn't get cancer, people do* -- a more effective way to communicate the spatial distributions of cancer statistics is needed.
+
+<!-- Cartogram -->
+A cartogram is a general solution for better displaying a population-based statistic.
+It transforms the geographic map base to reflect the population in the geographic region, while preserving some aspects of the geographic location.
+There are several cartogram algorithms [@ACTUC], [@CBATCC]; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
+The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units but can result in losing the familiar geographic information.
+For Australia, the transformations warp the country so that it is no longer recognizable.
+
+<!-- Other cartograms -->
+Alternative algorithms make various trade offs between familiar shapes and representation of geographic units.
+The non-contiguous cartogram method [@NAC] keeps the shapes of geographic units intact, and changes the size of the shape.
+This method disconnects areas creating empty space on the display losing the continuity of the spatial display of the statistic.
+The Dorling cartogram [@ACTUC] represents each unit as a circle, sized according to the value of the statistic.
+The neighbour relationships are mostly maintained by how the circles touch.
+A similar approach was pioneered by Raisz [-@RSCW], using rectangles that tile to align borders of neighbours [@CDWCS].
+A thorough review of the array of methods, as suitable for cancer atlas displays is available in XXX.
+
+<!-- Hexagon tile map -->
+The hexagon tile map algorithm, autmatically matches spatial regions to their nearest hexagon tile, from a grid of tiles.
+It has the effect of spreading out the inner city areas while maintaining the spatial locations or regions in remote areas.
+The algorithm is available in the R package, sugarbag (XXX REF).
+Figure \ref{fig:liver} shows the hexagon tile map, along with the choropleth map of liver cancer rates in Australia.
+Colour maps from substantially below average (blue) to substantially above average (red) rates.
+The inner city areas are expanded out, making it possible to see the cancer incidence in the small, densely populated areas.
+Remote regions are represented by isolated hexagons, which is not ideal, but maintains the spatial location of these data values.
+It is oof interest to know how well the spatial distribution is perceived for this display, in comparison to the choropleth.
+
+<!-- Specific problem for Australia 
 Australia is an extreme case of heterogeneous geographic units, with the large differences between the smallest and largest geographic units across various granularities.

### 2020-01-12 paper/paper.tex
done with spatial displays

@@
 
+\includegraphics{paper_files/figure-latex/liver-1.pdf}
+
 The choropleth map is effective if the size of the geographic units is relatively uniform.
@@
 
-\includegraphics{paper_files/figure-latex/liver-1.pdf}
-
-Australia is an extreme case of heterogeneous geographic units, with the large differences between the smallest and largest geographic units across various granularities.
-To communicate information regarding the small inner-city geographic units of Australian cities, an alternative display must be employed.
-This will emphasize the value of the statistic for areas with a high population.
-Fig.
-\ref{fig:liver} shows the distribution of the smoothed average amount of liver cancer diagnoses for Australian Males from 2005 to 2014.
-These inner-city areas are not visible on the choropleth map (a).
-The hexagon tile map (b) shows orange hexagons for the inner-city SA2s with higher than average levels of diagnoses in the capital cities of Melbourne and Sydney.
-The northern Queensland and Northern Territory SA2s with higher than average rates are still visible but use less map space on the hexagon tile map.
-There are still many light blue areas in both displays.
+The hexagon tile map algorithm, autmatically matches spatial regions to their nearest hexagon tile, from a grid of tiles.
+It has the effect of spreading out the inner city areas while maintaining the spatial locations or regions in remote areas.
+The algorithm is available in the R package, sugarbag (XXX REF).
+Figure \ref{fig:liver} shows the hexagon tile map, along with the choropleth map of liver cancer rates in Australia.
+Colour maps from substantially below average (blue) to substantially above average (red) rates.
+The inner city areas are expanded out, making it possible to see the cancer incidence in the small, densely populated areas.
+Remote regions are represented by isolated hexagons, which is not ideal, but maintains the spatial location of these data values.
+It is oof interest to know how well the spatial distribution is perceived for this display, in comparison to the choropleth.
 

### 2020-01-12 paper/paper.Rmd
visual inference

@@
 
-We suggest the hexagon tile map as an alternative display.
+In order to assess the effectiveness of the hexagon tile map, the lineup protocol [@GIIV,@BCHLLSW09] from visual inference procedures is employed.
+The procedures for doing a power comparison of competing plot designed, outlined in @GTPCCD, are followed.
+The approach mirrors classical statistical inference.
+
+<!--We suggest the hexagon tile map as an alternative display.
 To test the effectiveness of these displays, there is a formal testing framework.
@@
 It considers these visualizations to be visual statistics, with observable features.
+-->
 
-Classical statistical inference involves hypothesis testing,  rejecting a null hypothesis in favor of an alternative. This approach requires data with the appropriate distributions and assumptions. 
-The lineup protocol was formalized as a test for the effectiveness of a visualization.
+In classical statistical inference hypothesis testing is coonducted by comparing the value of a test statistic on a standard reference distribution, computed assuming the null hypothesis is true.
+If the value is extreme,  the null hypothesis is rejected, because the test statistic value is unlikely to have been so extreme if it was true.
+In the lineup protocol, the plot plays the role of the test statistic, and the data plot is embedded in a field of null plots.
+Defining the plot using a grammar of graphics [@ggplot2] makes it a functional mapping of the variables and thus, it can be considered to be a statistic.
+With the same data, two different plots can be considered to be competing statistics, one possibly a more powerful statistic than the other.
+
+To do hypothesis testing with the lineup protocol requires human evaluation.
+The human judge is required to identify the most different plot among the field of plots.
+If this corresponds to the data plot -- the test statistic -- the null hypothesis is rejected.
+It means that the data plot is extreme relative to the reference distribution of null plots.
+
+The null hypothesis is explicitly provided by the grammatical plot description.
+For example, if a histogram is the plot type being used, the null might be that the underlying distribution of the data is a Gaussian.
+Null data would be generated by simulating from a normal model, with the same mean and standard deviation as the data.
+In practice, the null hypothesis used is generic, such as *there is NO structure or a pattern in the plot*, and contrasted to an alternative that there is structure.
+
+The chance that an observer picks the data plot out of a lineup of size $m$ plots accidentally, if the null hypothesis is true is $/m$.
+With $K$ observers, the probability of $k$ randomly choosing the data plot, roughly follows a binomial distribution with $p=1/m$.
+Figure XXX (this needs to be placed near here) shows a lineup of the hexagon tile map, of size $m=12$.
+Plot XXX is the data plot, and the remaining 11 are plots of null data.
+
+In order to determine the effectiveness of a type of display, this probability is less relevant than the overall proportion of observers who pick the data plot, $k/K$.
+The power of the test statistic (data plot) is provided by this proportion.
+Power in a statistical sense is the ability oof the statistic to *produce a rejection* of the null hypothesis, if it is indeed *not true*.
+With the same data plotted using two different displays, the display with the highest proportion of people who choose the data plot would be considered to be the most powerful statistic.
+
+<!-- The lineup protocol was formalized as a test for the effectiveness of a visualization.
 Rather than classical statistical tests, it tasks human participants with finding the display that shows structure between the variables.
@@
 We can compare the time taken by participants to evaluate the same data in the different displays. We can also contrast the accuracy achieved by participants in detecting the real data plot.
+-->
 

### 2020-01-12 paper/paper.tex
visual inference

@@
 
-We suggest the hexagon tile map as an alternative display.
-To test the effectiveness of these displays, there is a formal testing framework.
-Visual inference considers the communication of data or data summaries through visualizations.
-It considers these visualizations to be visual statistics, with observable features.
-
-Classical statistical inference involves hypothesis testing, rejecting a null hypothesis in favor of an alternative. This approach requires data with the appropriate distributions and assumptions.
-The lineup protocol was formalized as a test for the effectiveness of a visualization.
-Rather than classical statistical tests, it tasks human participants with finding the display that shows structure between the variables.
-If they do not detect the structure, then it is not significantly different from the null data.
-
-Visual inference uses the general hypothesis structure:
-
-\begin{itemize}
-\tightlist
-\item
-  Null hypothesis: There is \bf{no} relationship between the variables
-\item
-  Alternative hypothesis: There is a relationship between the variables
-\end{itemize}
-
-To test these hypotheses, the line up protocol randomly places a ``guilty'' data visualization in a lineup of ``innocents''.
-Where the guilty data set contains structure, and the innocents data sets do not.
-In a grid of visualizations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the innocents {[}\protect\hyperlink{ref-GTPCCD}{11}{]}.
-The participants identify the guilty data as different from the innocent data with probability \(1/m\), where \(m\) is the number of null plots plus 1 to account for the guilty data set.
-When the guilty data set is chosen we reject the null hypothesis that it was innocent is rejected with a \(1/m\) chance or type I error of being wrong.
-
-The lineup protocol can be used in a variety of testing scenarios for visualizations.
-{[}\protect\hyperlink{ref-GIIV}{3}{]} suggest the choropleth map for testing spatial structure in a data set.
-The lineup protocol allows for flexibility in the definition of null data.
-In the case of spatial visualizations, it is likely that neighbors are related.
-To account for this, null data sets can be generated by sampling from a known model that accounts for spatial covariance.
-
-To contrast the effectiveness of two displays, we can produce null data plots with a hidden real data plot using the different plot designs.
-We can compare the time taken by participants to evaluate the same data in the different displays. We can also contrast the accuracy achieved by participants in detecting the real data plot.
+In order to assess the effectiveness of the hexagon tile map, the lineup protocol {[}\protect\hyperlink{ref-GIIV}{3}{]} from visual inference procedures is employed.
+The procedures for doing a power comparison of competing plot designed, outlined in {[}\protect\hyperlink{ref-GTPCCD}{12}{]}, are followed.
+The approach mirrors classical statistical inference.
+
+In classical statistical inference hypothesis testing is coonducted by comparing the value of a test statistic on a standard reference distribution, computed assuming the null hypothesis is true.
+If the value is extreme, the null hypothesis is rejected, because the test statistic value is unlikely to have been so extreme if it was true.
+In the lineup protocol, the plot plays the role of the test statistic, and the data plot is embedded in a field of null plots.
+Defining the plot using a grammar of graphics {[}\protect\hyperlink{ref-ggplot2}{13}{]} makes it a functional mapping of the variables and thus, it can be considered to be a statistic.
+With the same data, two different plots can be considered to be competing statistics, one possibly a more powerful statistic than the other.
+
+To do hypothesis testing with the lineup protocol requires human evaluation.
+The human judge is required to identify the most different plot among the field of plots.
+If this corresponds to the data plot -- the test statistic -- the null hypothesis is rejected.
+It means that the data plot is extreme relative to the reference distribution of null plots.
+
+The null hypothesis is explicitly provided by the grammatical plot description.
+For example, if a histogram is the plot type being used, the null might be that the underlying distribution of the data is a Gaussian.
+Null data would be generated by simulating from a normal model, with the same mean and standard deviation as the data.
+In practice, the null hypothesis used is generic, such as \emph{there is NO structure or a pattern in the plot}, and contrasted to an alternative that there is structure.
+
+The chance that an observer picks the data plot out of a lineup of size \(m\) plots accidentally, if the null hypothesis is true is \(/m\).
+With \(K\) observers, the probability of \(k\) randomly choosing the data plot, roughly follows a binomial distribution with \(p=1/m\).
+Figure XXX (this needs to be placed near here) shows a lineup of the hexagon tile map, of size \(m=12\).
+Plot XXX is the data plot, and the remaining 11 are plots of null data.
+
+In order to determine the effectiveness of a type of display, this probability is less relevant than the overall proportion of observers who pick the data plot, \(k/K\).
+The power of the test statistic (data plot) is provided by this proportion.
+Power in a statistical sense is the ability oof the statistic to \emph{produce a rejection} of the null hypothesis, if it is indeed \emph{not true}.
+With the same data plotted using two different displays, the display with the highest proportion of people who choose the data plot would be considered to be the most powerful statistic.
 
@@
 The data collection took place using a secure link between the survey web application and the googlesheet used to store results.
-The application would first connect to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{12}{]} R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
+The application would first connect to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{14}{]} R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
 
@@
 
-The choropleth map was used as the comparative visualization for presenting the lineups {[}\protect\hyperlink{ref-VVSIALM}{13}{]} as this is the common display for spatial cancer data.
+The choropleth map was used as the comparative visualization for presenting the lineups {[}\protect\hyperlink{ref-VVSIALM}{15}{]} as this is the common display for spatial cancer data.
 Geographic distributions usually have some degree of spatial autcorrelation between neighbors.
@@
 
-The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R {[}\protect\hyperlink{ref-RCore}{14}{]}.
+The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R {[}\protect\hyperlink{ref-RCore}{16}{]}.
 
@@
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R {[}\protect\hyperlink{ref-RCore}{14}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{15}{]} package implements generalised linear mixed effect models.
+The R {[}\protect\hyperlink{ref-RCore}{16}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{17}{]} package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 
-Computation will be done using R {[}\protect\hyperlink{ref-RCore}{14}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{15}{]}.
+Computation will be done using R {[}\protect\hyperlink{ref-RCore}{16}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{17}{]}.
 
@@
 
-The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{14}{]} with the use of the following packages:
+The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{16}{]} with the use of the following packages:
 
@@
 \item
-  For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{16}{]}, rticles {[}\protect\hyperlink{ref-rticles}{17}{]}, knitr {[}\protect\hyperlink{ref-knitr}{18}{]}.
-\item
-  For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{19}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{20}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{21}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{22}{]}.
-\item
-  For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{23}{]}, png {[}\protect\hyperlink{ref-png}{24}{]}, grid {[}\protect\hyperlink{ref-grid}{25}{]}.
-\item
-  For modeling and presentation of models: lme4 {[}\protect\hyperlink{ref-lme4}{15}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{26}{]}.
+  For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{18}{]}, rticles {[}\protect\hyperlink{ref-rticles}{19}{]}, knitr {[}\protect\hyperlink{ref-knitr}{20}{]}.
+\item
+  For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{21}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{22}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{23}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{24}{]}.
+\item
+  For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{25}{]}, png {[}\protect\hyperlink{ref-png}{26}{]}, grid {[}\protect\hyperlink{ref-grid}{27}{]}.
+\item
+  For modeling and presentation of models: lme4 {[}\protect\hyperlink{ref-lme4}{17}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{28}{]}.
 \end{itemize}
@@
 
+\leavevmode\hypertarget{ref-BCHLLSW09}{}%
+11.
+Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) Statistical inference for exploratory data analysis and model diagnostics.
+Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383
+
 \leavevmode\hypertarget{ref-GTPCCD}{}%
-11. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448
+12. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448
+
+\leavevmode\hypertarget{ref-ggplot2}{}%
+13. Wickham H (2009) Ggplot2: Elegant graphics for data analysis. Springer New York
 
 \leavevmode\hypertarget{ref-sheets}{}%
-12. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
+14. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
 
 \leavevmode\hypertarget{ref-VVSIALM}{}%
-13. Majumder M, Hofmann H, Cook D (2013) Validation of visual statistical inference, applied to linear models. Journal of the American Statistical Association 108:942--956
+15. Majumder M, Hofmann H, Cook D (2013) Validation of visual statistical inference, applied to linear models. Journal of the American Statistical Association 108:942--956
 
 \leavevmode\hypertarget{ref-RCore}{}%
-14. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+16. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
 
 \leavevmode\hypertarget{ref-lme4}{}%
-15. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
+17. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
 
 \leavevmode\hypertarget{ref-rmarkdown}{}%
-16. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida
+18. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida
 
 \leavevmode\hypertarget{ref-rticles}{}%
-17. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.
+19. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.
 
 \leavevmode\hypertarget{ref-knitr}{}%
-18. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research
+20. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research
 
 \leavevmode\hypertarget{ref-tidyverse}{}%
-19. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686
+21. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686
 
 \leavevmode\hypertarget{ref-nullabor}{}%
-20. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.
+22. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.
 
 \leavevmode\hypertarget{ref-ggthemes}{}%
-21. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.
+23. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.
 
 \leavevmode\hypertarget{ref-RColorBrewer}{}%
-22. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.
+24. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.
 
 \leavevmode\hypertarget{ref-cowplot}{}%
-23. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.
+25. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.
 
 \leavevmode\hypertarget{ref-png}{}%
-24. Urbanek S (2013) Png: Read and write png images.
+26. Urbanek S (2013) Png: Read and write png images.
 
 \leavevmode\hypertarget{ref-grid}{}%
-25. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+27. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
 
 \leavevmode\hypertarget{ref-kableExtra}{}%
-26. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
+28. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
 

### 2020-01-12 paper/paper.Rmd
participants

@@
 
-This study aimed to answer two key questions around the presentation of spatial distributions:
+This study aims to answer two key questions around the presentation of spatial distributions:
 
-1. Are spatial disease trends that impact highly populated small areas detected with higher accuracy, when viewed in a hexagon tile map display?
+1. Are spatial disease trends that impact highly populated small areas detected with higher accuracy, when viewed in a hexagon tile map?
+2. Are people faster in detecting spatial disease trends that impact highly populated small areas when using a hexagon tile map?
 
-2. Are people faster in detecting spatial disease trends that impact highly populated small areas when using a hexagon tile map display?
+Additional considerations when completing this experimental task included the difficulty experienced by participants and the certainty they had in their decision.
 
-Additional considerations when completing this experimental task included exploration of the difficulty experienced by participants and the certainty they felt about their decision.
-
+<!--
 The mean of the detection rate for choropleth map, denoted as $\mu_C$, and the hexagon tile maps, $\mu_H$ will be contrasted. This leads to the following one sided hypothesis:
@@
 The detection rate $\hat\pi$ is calculated as the amount of people that made the choice of plot that contained the real data, out of the participants who saw data plot in the lineup of the null data plots.
+-->
 
@@
 
-We recruited participants for the survey style task to test the effectiveness of the hexagon tile map display.
-The lineup protocol expects that the participants are uninvolved judges that had no prior knowledge of the data to avoid discrimination or advantages.
-The Figure-Eight crowd source platform was used to advertise the survey to potential participants that had achieved level 2 or level 3 on the Figure-Eight Platform.
-The participants were chosen as they have experience with survey tasks that involve evaluating images. The participants were at least 18 years old, as it is a requirement of the platform.
+Participants were recruited for to evaluate lineups from the Figure-Eight crowdsourcing platform (XXX REF).
+The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
+Potential participants needed to have achieved level 2 or level 3 from prior work.
+The participants were chosen as they have experience with survey tasks that involve evaluating images XXX Did we really choose participants this way??).
+All participants were at least 18 years old.
 
-Participants were able to choose to participate by selecting this task from the list of tasks available to them.
-Participants were allocated to either group A or group B when they proceeded to the survey web application, hosted externally from the Figure-Eight website. 
+Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure-Eight website.
 There were 95 participants involved in the study.
-All of these participants read the introductory materials and viewed example questions before proceeding to the survey.
-Each participant was trained using three test displays orienting them to the evaluation task.
-All participants who volunteered to take part were compensated for their time via the payment system of Figure-Eight.
+All participants read introductory materials, and was trained using three test displays, to orient them to the evaluation task.
+All participants who completed the task were compensated $USD5 for their time, via the Figure-Eight payment system.
 

### 2020-01-12 paper/paper.tex
participants

@@
 
-This study aimed to answer two key questions around the presentation of spatial distributions:
+This study aims to answer two key questions around the presentation of spatial distributions:
 
@@
 \def\labelenumi{\arabic{enumi}.}
-\item
-  Are spatial disease trends that impact highly populated small areas detected with higher accuracy, when viewed in a hexagon tile map display?
-\item
-  Are people faster in detecting spatial disease trends that impact highly populated small areas when using a hexagon tile map display?
+\tightlist
+\item
+  Are spatial disease trends that impact highly populated small areas detected with higher accuracy, when viewed in a hexagon tile map?
+\item
+  Are people faster in detecting spatial disease trends that impact highly populated small areas when using a hexagon tile map?
 \end{enumerate}
 
-Additional considerations when completing this experimental task included exploration of the difficulty experienced by participants and the certainty they felt about their decision.
-
-The mean of the detection rate for choropleth map, denoted as \(\mu_C\), and the hexagon tile maps, \(\mu_H\) will be contrasted. This leads to the following one sided hypothesis:
-
-\(H_0\) : \(\mu_H\) = \(\mu_C\)
-\(H_a\) : \(\mu_H\) \textgreater{} \(\mu_C\)
-
-The detection rate \(\hat\pi\) is calculated as the amount of people that made the choice of plot that contained the real data, out of the participants who saw data plot in the lineup of the null data plots.
+Additional considerations when completing this experimental task included the difficulty experienced by participants and the certainty they had in their decision.
 
@@
 
-We recruited participants for the survey style task to test the effectiveness of the hexagon tile map display.
-The lineup protocol expects that the participants are uninvolved judges that had no prior knowledge of the data to avoid discrimination or advantages.
-The Figure-Eight crowd source platform was used to advertise the survey to potential participants that had achieved level 2 or level 3 on the Figure-Eight Platform.
-The participants were chosen as they have experience with survey tasks that involve evaluating images. The participants were at least 18 years old, as it is a requirement of the platform.
-
-Participants were able to choose to participate by selecting this task from the list of tasks available to them.
-Participants were allocated to either group A or group B when they proceeded to the survey web application, hosted externally from the Figure-Eight website.
+Participants were recruited for to evaluate lineups from the Figure-Eight crowdsourcing platform (XXX REF).
+The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
+Potential participants needed to have achieved level 2 or level 3 from prior work.
+The participants were chosen as they have experience with survey tasks that involve evaluating images XXX Did we really choose participants this way??).
+All participants were at least 18 years old.
+
+Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure-Eight website.
 There were 95 participants involved in the study.
-All of these participants read the introductory materials and viewed example questions before proceeding to the survey.
-Each participant was trained using three test displays orienting them to the evaluation task.
-All participants who volunteered to take part were compensated for their time via the payment system of Figure-Eight.
+All participants read introductory materials, and was trained using three test displays, to orient them to the evaluation task.
+All participants who completed the task were compensated \$USD5 for their time, via the Figure-Eight payment system.
 

### 2020-01-12 paper/paper.Rmd
doone with design, need to look at null gen next

@@
 
-## Variables
+## Experimental factors
 
-The variables changed between groups were the type of plot shown and the trend model.
+<!-- The variables changed between groups were the type of plot shown and the trend model.-->
 
-A combination of map type and spatial trend model created the twenty-four lineup displays.
-We split this set of displays into a collection of twelve displays for Group A and twelve displays for Group B.
-The random allocation of participants to Group A or Group B resulted in 42 participants allocated to Group A and 53 participants allocated to Group B.
-
-The levels of the factors measured in the experiment were:
+The primary factor in the experiment is the plot type.
+The secondary factor is a trend model.
+Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to do well, and two with differing level of inner city hot spots.
+These latter two reflect the structure seen in the liver cancer data (Figure \ref{fig:liver}).
+This produces six treatment levels:
 
   - Map type: *Choropleth, Hexagon tile*
-  - Trend: *Locations in three population centres, Locations in multiple population centres, South-East to North-West*
+  - Trend: *South-East to North-West; Locations in three population centres; Locations in multiple population centres, *
 
-Each group did not see the same data for both map types. We generated four simulated sets of data for each treatment.
+Data is generated for each of the trend models, with four replicates, and each displayed both as a choropleth and as a hexagon tile map, which yields 12 data sets, and 24 data plots.
+This set of displays is divided in half, providing two sets of 12 displays, Group A and Group B.
+Participants were randomly allocated to Group A or B.
+Participants saw a data set only once, with as a choropleth or as a hexagon tile map.
+Table \ref{tab:exp-design} summarise the design.
+(XXX Maybe replace this table with your diagram illustrating the design??)
+
+<!-- Each group did not see the same data for both map types. We generated four simulated sets of data for each treatment.
 This will generate twenty-four lineups (twelve lineups of geographic maps and twelve lineups of hexagon tile maps). Participants evaluated twelve lineups, size of each map type.
-For each of the six geographic displays and six hexagon displays, two of each trend model were shown to the participants. We outline the design in Table. \ref{tab:exp-design}.
+For each of the six geographic displays and six hexagon displays, two of each trend model were shown to the participants. We outline the design in Table \ref{tab:exp-design}.
+-->
 
@@
 
-The variables measured as a result of the changes were the probability of detection each display and the time taken to submit responses.
+<!-- The variables measured as a result of the changes were the probability of detection each display and the time taken to submit responses.
 To measure the accuracy of the detections, the plot chosen for each lineup evaluated was compared to the position of the real spatial trend plot in the lineup.
@@
 High efficiency occurs when a small amount of time is taken to evaluate each lineup.
-This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.
+This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.-->
 
-## Simulation process
+## Generating null data
 

### 2020-01-12 paper/paper.tex
doone with design, need to look at null gen next

@@
 
-\hypertarget{variables}{%
-\subsection{Variables}\label{variables}}
-
-The variables changed between groups were the type of plot shown and the trend model.
-
-A combination of map type and spatial trend model created the twenty-four lineup displays.
-We split this set of displays into a collection of twelve displays for Group A and twelve displays for Group B.
-The random allocation of participants to Group A or Group B resulted in 42 participants allocated to Group A and 53 participants allocated to Group B.
-
-The levels of the factors measured in the experiment were:
+\hypertarget{experimental-factors}{%
+\subsection{Experimental factors}\label{experimental-factors}}
+
+The primary factor in the experiment is the plot type.
+The secondary factor is a trend model.
+Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to do well, and two with differing level of inner city hot spots.
+These latter two reflect the structure seen in the liver cancer data (Figure \ref{fig:liver}).
+This produces six treatment levels:
 
@@
 \item
-  Trend: \emph{Locations in three population centres, Locations in multiple population centres, South-East to North-West}
+  Trend: \emph{South-East to North-West; Locations in three population centres; Locations in multiple population centres, }
 \end{itemize}
 
-Each group did not see the same data for both map types. We generated four simulated sets of data for each treatment.
-This will generate twenty-four lineups (twelve lineups of geographic maps and twelve lineups of hexagon tile maps). Participants evaluated twelve lineups, size of each map type.
-For each of the six geographic displays and six hexagon displays, two of each trend model were shown to the participants. We outline the design in Table. \ref{tab:exp-design}.
+Data is generated for each of the trend models, with four replicates, and each displayed both as a choropleth and as a hexagon tile map, which yields 12 data sets, and 24 data plots.
+This set of displays is divided in half, providing two sets of 12 displays, Group A and Group B.
+Participants were randomly allocated to Group A or B.
+Participants saw a data set only once, with as a choropleth or as a hexagon tile map.
+Table \ref{tab:exp-design} summarise the design.
+(XXX Maybe replace this table with your diagram illustrating the design??)
 
@@
 
-The variables measured as a result of the changes were the probability of detection each display and the time taken to submit responses.
-To measure the accuracy of the detections, the plot chosen for each lineup evaluated was compared to the position of the real spatial trend plot in the lineup.
-A correct result occurs when the chosen plot matches the position of the real plot, this was recorded in an additional binary variable; 1 = correct; 0 = incorrect.
-High efficiency occurs when a small amount of time is taken to evaluate each lineup.
-This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.
-
-\hypertarget{simulation-process}{%
-\subsection{Simulation process}\label{simulation-process}}
+\hypertarget{generating-null-data}{%
+\subsection{Generating null data}\label{generating-null-data}}
 

### 2020-01-12 paper/paper.Rmd
methods section - loom for XXX to revise

@@
 
+Australia is used for the study, with Statistical Area 2 (SA2) (XXX REF) as the geographic units. The results shuold apply broadly to any other geographic area of interest.
+
 <!--
@@
 -->
-
-## Participants
-
-Participants were recruited for to evaluate lineups from the Figure-Eight crowdsourcing platform (XXX REF).
-The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
-Potential participants needed to have achieved level 2 or level 3 from prior work.
-The participants were chosen as they have experience with survey tasks that involve evaluating images XXX Did we really choose participants this way??).
-All participants were at least 18 years old.
-
-Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure-Eight website.
-There were 95 participants involved in the study.
-All participants read introductory materials, and was trained using three test displays, to orient them to the evaluation task.
-All participants who completed the task were compensated $USD5 for their time, via the Figure-Eight payment system.
 
@@
 
-The lineup protocol allows a known model to be imposed on the null data set plots.
+Null data needs to be data with no (interesting) structure.
+In most scenarios, permutation is the main approach for generating null plots.
+It is used to break association between variables, while maintaining marginal distributions.
+This is too simple for spatial data.
+In spatial data, a key feature is smoothness over the landscape corresponding spatial dependence.
+To do something simple, like permute the values relative to the goegraphic location would produce null plots which are too chaotic, and the data plot will be recognisable for its smoothness rather than any structure of interest.
+
+For spatial data, null data is staionary data, where the mean, variance and spatial dependence are constant over the geographic units.
+Stationary data is specified by a variogram model (XXX REF).
+Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots.
+A Gaussian The parameters for the model were sill=1, range=0.3 with the variance generated by a standard normal distribution (XXX What parameters were used?).
+
+The R package `gstat` (XXX REF) was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
+
+```{r eval=FALSE, echo=FALSE}
+var.g.dummy <- gstat(formula = z ~ 1, 
+                     locations = ~ longitude + latitude, 
+                     dummy = T, beta = 1, model = vgm(psill = 1, model = "Gau", range = 0.3),
+                     nmax = 12)
+```
+
+<!-- Spatially dependent data sets were simulated using the variogram model on the centroids of each geographic unit.
+Twelve simulations from the variogram model were created for each of the twelve lineups.
+
 The underlying spatial correlation model was created to provide spatial autocorrelation between neighboring areas using the longitude and latitude values for the Statistical Areas.
@@
 $$locations = longitude + latitude$$
+-->
+
+## Generating lineups
+
+XXX Fill in this structure - see commented text
+
+<!-- Discuss simulating the trend data -->
+
+<!-- Applying smoothing -->
+
+<!-- Scaling data within a lineup -->
+
+<!-- Location of data plot -->
 
@@
 
-## Experiment procudure and data collection
+For each lineup these statistics were calculated:
+
+ - accuracy: the proportion of subjects who detected the data plot
+ - efficiency: average time taken to respond
+
+## Web app collecting responses
+
+XXX Describe the details of the taipan app used to collect responses
+
+Data was collected through a web application containing the online survey.
+Each participant used the internet to access the survey.
+The data collection took place using a secure link between the survey web application and the googlesheet used to store results.
+The application would first connect to the googlesheet using the googlesheets [@sheets] R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
+
+## Participants
+
+Participants were recruited for to evaluate lineups from the Figure-Eight crowdsourcing platform (XXX REF).
+The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
+Potential participants needed to have achieved level 2 or level 3 from prior work.
+The participants were chosen as they have experience with survey tasks that involve evaluating images XXX Did we really choose participants this way??).
+All participants were at least 18 years old.
+
+Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure-Eight website.
+There were 95 participants involved in the study.
+All participants read introductory materials, and was trained using three test displays, to orient them to the evaluation task.
+All participants who completed the task were compensated $USD5 for their time, via the Figure-Eight payment system.
+
+XXX Sentence on pilot study which allowed us to estimate the effect size, and thus decide on number of participants to collect responses from
+
+## Demographic data collection
 
@@
 
-Data was collected through a web application containing the online survey.
-Each participant used the internet to access the survey.
-The data collection took place using a secure link between the survey web application and the googlesheet used to store results.
-The application would first connect to the googlesheet using the googlesheets [@sheets] R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
-
+<!--
 ## Experimental design
@@
  - efficiency: average time taken to respond
-
-### visualizations
+-->
+
+## Analysis
+
+### Descriptive statistics
+
+Mean, standard deviations for lineups, by participant, ...
+
 Side-by-side dot plots were made of accuracy (efficiency) against map type, facetted by trend model type.
@@
 
-## Limitations of the data collection
-
-A pilot study was conducted to determine whether the lineups were appropriate. All lineups in the pilot study were deemed viable as at least one participant detected the real data plot in each lineup.
+### Data cleaning
+
+<!-- A pilot study was conducted to determine whether the lineups were appropriate.
+All lineups in the pilot study were deemed viable as at least one participant detected the real data plot in each lineup.
 The demographics of the participants showed a skew towards male participants. 
@@
 Due to the allocation of lineup displays the participants all saw six Choropleth displays and six Hexagon Tile Map displays.
+-->
 
@@
 
-Acknowledgment
+Acknowledgements
 ==============
@@
 All applicants provided informed consent in line with QUT regulations prior to participating in this research.
+
+All code to generate the data, of the web app that collected participants responses, conduct the analysis, and produce this manuscript are available on XXX.
+
+The supplementary material contains:
+
+- Additonal analysis of the experimental results
+- Training materials used for the participants
+- 24 lineups used in the experiment
+- 12 data sets used to coonstruct the lineups
 

### 2020-01-12 paper/paper.tex
methods section - loom for XXX to revise

@@
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-Participants were recruited for to evaluate lineups from the Figure-Eight crowdsourcing platform (XXX REF).
-The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
-Potential participants needed to have achieved level 2 or level 3 from prior work.
-The participants were chosen as they have experience with survey tasks that involve evaluating images XXX Did we really choose participants this way??).
-All participants were at least 18 years old.
-
-Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure-Eight website.
-There were 95 participants involved in the study.
-All participants read introductory materials, and was trained using three test displays, to orient them to the evaluation task.
-All participants who completed the task were compensated \$USD5 for their time, via the Figure-Eight payment system.
+Australia is used for the study, with Statistical Area 2 (SA2) (XXX REF) as the geographic units. The results shuold apply broadly to any other geographic area of interest.
 
@@
 
-The lineup protocol allows a known model to be imposed on the null data set plots.
-The underlying spatial correlation model was created to provide spatial autocorrelation between neighboring areas using the longitude and latitude values for the Statistical Areas.
-
-\[z = 1\]
-\[locations = longitude + latitude\]
+Null data needs to be data with no (interesting) structure.
+In most scenarios, permutation is the main approach for generating null plots.
+It is used to break association between variables, while maintaining marginal distributions.
+This is too simple for spatial data.
+In spatial data, a key feature is smoothness over the landscape corresponding spatial dependence.
+To do something simple, like permute the values relative to the goegraphic location would produce null plots which are too chaotic, and the data plot will be recognisable for its smoothness rather than any structure of interest.
+
+For spatial data, null data is staionary data, where the mean, variance and spatial dependence are constant over the geographic units.
+Stationary data is specified by a variogram model (XXX REF).
+Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots.
+A Gaussian The parameters for the model were sill=1, range=0.3 with the variance generated by a standard normal distribution (XXX What parameters were used?).
+
+The R package \texttt{gstat} (XXX REF) was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
+
+\hypertarget{generating-lineups}{%
+\subsection{Generating lineups}\label{generating-lineups}}
+
+XXX Fill in this structure - see commented text
 
@@
 
-\hypertarget{experiment-procudure-and-data-collection}{%
-\subsection{Experiment procudure and data collection}\label{experiment-procudure-and-data-collection}}
-
-The participant answered demographic questions and provided consent before evaluating the lineups.
-
-Demographics were collected regarding the study participants:
+For each lineup these statistics were calculated:
 
@@
 \item
-  Gender (female / male / other),
-\item
-  Degree education level achieved (high school / bachelors / masters / doctorate / other),
-\item
-  Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
-\item
-  Lived at least for one year in Australia (Yes / No )
+  accuracy: the proportion of subjects who detected the data plot
+\item
+  efficiency: average time taken to respond
 \end{itemize}
 
-Participants then moved to the evaulation phase.
-The set of images differed for Group A and Group B.
-After being allocated to a group, each individual was shown the 12 displays in randomised order.
-
-Three questions were asked regarding each display:
-
-\begin{itemize}
-\tightlist
-\item
-  Plot choice
-\item
-  Reason
-\item
-  Difficulty
-\end{itemize}
-
-After completing the 12 evaluations, the participants were asked to submit their responses.
+\hypertarget{web-app-collecting-responses}{%
+\subsection{Web app collecting responses}\label{web-app-collecting-responses}}
+
+XXX Describe the details of the taipan app used to collect responses
 
@@
 
-\hypertarget{experimental-design}{%
-\subsection{Experimental design}\label{experimental-design}}
-
-The choropleth map was used as the comparative visualization for presenting the lineups {[}\protect\hyperlink{ref-VVSIALM}{15}{]} as this is the common display for spatial cancer data.
-Geographic distributions usually have some degree of spatial autcorrelation between neighbors.
-This feature was incorporated in all maps shown in the lineup displays, the map that contained the trend feature shown in only one set of data was also affected by spatial autocorrelation.
-A line up protocol was implemented to arrange \(N\) maps in each display.
-A reasonable amount of null plots \(N-1\) in the lineup was chosen to ensure the real data map was well hidden.
-A reasonable number of plots to show in each lineup, \(N = 12\) was chosen to not overwhelm participants due to the detailed choropleth maps of Australian SA3 areas.
-
-The hypotheses for each lineup are
-\(H_0\) : All plots look the same
-\(H_a\) : One plot looks different to the other plots
-
-The same data was visualized on a choropleth map, and on a hexagon tile map, however in this study the participants only saw one of these two displays.
-The accuracy and times taken were aggregated for Groups and.
-Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.
-
-Let \(n\) be the number of independent observers and \(x_i\) the
-number of observers who picked plot \(i\), \(i = \{1,...,m\}\)
-
-Then \(x_i, x_2, ..., x_m\) follows a multinomial
-distribution\(Mult_{\pi_1, \pi_2, ...., \pi_m}(x_i, x_2, ..., x_m)\) with
-\(\sum_i \pi_i = 1\), where \(\pi_i\) is the probability that plot \(i\) is picked by an
-observer, which we can estimate as \(\hat{\pi}_i = x_i/n\).
-The researchers compared the length of time taken, and the accuracy of the participants choices.
-The power of a lineup can therefore be estimated as the ratio of correct
-identifications \(x\) out of \(n\) viewings.
-
-\hypertarget{the-methods-of-data-analysis-used}{%
-\subsection{The methods of data analysis used}\label{the-methods-of-data-analysis-used}}
-
-The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R {[}\protect\hyperlink{ref-RCore}{16}{]}.
-
-For each of the 12 lineup displays the researchers calculated:
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+Participants were recruited for to evaluate lineups from the Figure-Eight crowdsourcing platform (XXX REF).
+The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
+Potential participants needed to have achieved level 2 or level 3 from prior work.
+The participants were chosen as they have experience with survey tasks that involve evaluating images XXX Did we really choose participants this way??).
+All participants were at least 18 years old.
+
+Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure-Eight website.
+There were 95 participants involved in the study.
+All participants read introductory materials, and was trained using three test displays, to orient them to the evaluation task.
+All participants who completed the task were compensated \$USD5 for their time, via the Figure-Eight payment system.
+
+XXX Sentence on pilot study which allowed us to estimate the effect size, and thus decide on number of participants to collect responses from
+
+\hypertarget{demographic-data-collection}{%
+\subsection{Demographic data collection}\label{demographic-data-collection}}
+
+The participant answered demographic questions and provided consent before evaluating the lineups.
+
+Demographics were collected regarding the study participants:
 
@@
 \item
-  accuracy: the proportion of subjects who detected the data plot
-\item
-  efficiency: average time taken to respond
+  Gender (female / male / other),
+\item
+  Degree education level achieved (high school / bachelors / masters / doctorate / other),
+\item
+  Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
+\item
+  Lived at least for one year in Australia (Yes / No )
 \end{itemize}
 
-\hypertarget{visualizations}{%
-\subsubsection{visualizations}\label{visualizations}}
+Participants then moved to the evaulation phase.
+The set of images differed for Group A and Group B.
+After being allocated to a group, each individual was shown the 12 displays in randomised order.
+
+Three questions were asked regarding each display:
+
+\begin{itemize}
+\tightlist
+\item
+  Plot choice
+\item
+  Reason
+\item
+  Difficulty
+\end{itemize}
+
+After completing the 12 evaluations, the participants were asked to submit their responses.
+
+\hypertarget{analysis}{%
+\subsection{Analysis}\label{analysis}}
+
+\hypertarget{descriptive-statistics}{%
+\subsubsection{Descriptive statistics}\label{descriptive-statistics}}
+
+Mean, standard deviations for lineups, by participant, \ldots{}
 
@@
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R {[}\protect\hyperlink{ref-RCore}{16}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{17}{]} package implements generalised linear mixed effect models.
+The R {[}\protect\hyperlink{ref-RCore}{15}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{16}{]} package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 
-Computation will be done using R {[}\protect\hyperlink{ref-RCore}{16}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{17}{]}.
-
-\hypertarget{limitations-of-the-data-collection}{%
-\subsection{Limitations of the data collection}\label{limitations-of-the-data-collection}}
-
-A pilot study was conducted to determine whether the lineups were appropriate. All lineups in the pilot study were deemed viable as at least one participant detected the real data plot in each lineup.
-The demographics of the participants showed a skew towards male participants.
-The randomness of the group allocation also resulted in more participants being allocated to Group B.
-Due to the allocation of lineup displays the participants all saw six Choropleth displays and six Hexagon Tile Map displays.
+Computation will be done using R {[}\protect\hyperlink{ref-RCore}{15}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{16}{]}.
+
+\hypertarget{data-cleaning}{%
+\subsubsection{Data cleaning}\label{data-cleaning}}
 
@@
 
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations.
+They would also like to thank Kerrie Mengersen and Dr.~Earl Duncan for suggestions and comments.
+
+Ethics approval for the online survey was granted by QUT's Ethics Committee (Ethics Application Number: 1900000991).
+All applicants provided informed consent in line with QUT regulations prior to participating in this research.
+
+All code to generate the data, of the web app that collected participants responses, conduct the analysis, and produce this manuscript are available on XXX.
+
+The supplementary material contains:
+
+\begin{itemize}
+\tightlist
+\item
+  Additonal analysis of the experimental results
+\item
+  Training materials used for the participants
+\item
+  24 lineups used in the experiment
+\item
+  12 data sets used to coonstruct the lineups
+\end{itemize}
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\newpage
+
 \hypertarget{acknowledgment}{%
@@
 The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations.
-They would also like to thank Kerrie Mengersen and Dr.~Earl Duncan for suggestions and comments.
-
-Ethics approval for the online survey was granted by QUT's Ethics Committee (Ethics Application Number: 1900000991).
-All applicants provided informed consent in line with QUT regulations prior to participating in this research.
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\newpage
-
-\hypertarget{acknowledgment-1}{%
-\section{Acknowledgment}\label{acknowledgment-1}}
-
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations.
 They would also like to thank Distinguished Professor Kerrie Mengersen and Doctor Earl Duncan for suggestions and comments.
@@
 
-The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{16}{]} with the use of the following packages:
+The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{15}{]} with the use of the following packages:
 
@@
 \item
-  For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{18}{]}, rticles {[}\protect\hyperlink{ref-rticles}{19}{]}, knitr {[}\protect\hyperlink{ref-knitr}{20}{]}.
-\item
-  For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{21}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{22}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{23}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{24}{]}.
-\item
-  For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{25}{]}, png {[}\protect\hyperlink{ref-png}{26}{]}, grid {[}\protect\hyperlink{ref-grid}{27}{]}.
-\item
-  For modeling and presentation of models: lme4 {[}\protect\hyperlink{ref-lme4}{17}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{28}{]}.
+  For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{17}{]}, rticles {[}\protect\hyperlink{ref-rticles}{18}{]}, knitr {[}\protect\hyperlink{ref-knitr}{19}{]}.
+\item
+  For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{20}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{21}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{22}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{23}{]}.
+\item
+  For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{24}{]}, png {[}\protect\hyperlink{ref-png}{25}{]}, grid {[}\protect\hyperlink{ref-grid}{26}{]}.
+\item
+  For modeling and presentation of models: lme4 {[}\protect\hyperlink{ref-lme4}{16}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{27}{]}.
 \end{itemize}
@@
 
-\leavevmode\hypertarget{ref-VVSIALM}{}%
-15. Majumder M, Hofmann H, Cook D (2013) Validation of visual statistical inference, applied to linear models. Journal of the American Statistical Association 108:942--956
-
 \leavevmode\hypertarget{ref-RCore}{}%
-16. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+15. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
 
 \leavevmode\hypertarget{ref-lme4}{}%
-17. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
+16. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
 
 \leavevmode\hypertarget{ref-rmarkdown}{}%
-18. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida
+17. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida
 
 \leavevmode\hypertarget{ref-rticles}{}%
-19. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.
+18. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.
 
 \leavevmode\hypertarget{ref-knitr}{}%
-20. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research
+19. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research
 
 \leavevmode\hypertarget{ref-tidyverse}{}%
-21. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686
+20. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686
 
 \leavevmode\hypertarget{ref-nullabor}{}%
-22. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.
+21. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.
 
 \leavevmode\hypertarget{ref-ggthemes}{}%
-23. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.
+22. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.
 
 \leavevmode\hypertarget{ref-RColorBrewer}{}%
-24. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.
+23. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.
 
 \leavevmode\hypertarget{ref-cowplot}{}%
-25. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.
+24. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.
 
 \leavevmode\hypertarget{ref-png}{}%
-26. Urbanek S (2013) Png: Read and write png images.
+25. Urbanek S (2013) Png: Read and write png images.
 
 \leavevmode\hypertarget{ref-grid}{}%
-27. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+26. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
 
 \leavevmode\hypertarget{ref-kableExtra}{}%
-28. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
+27. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
 

### 2020-01-12 paper/paper.Rmd
updated acknowledgements

@@
 
-Acknowledgment
+Acknowledgments
 ==============
 
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations.
-They would also like to thank Distinguished Professor Kerrie Mengersen and Doctor Earl Duncan for suggestions and comments.
+The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments.
+Mitch O'Hara-Wild was a co-developer of the taipan R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
+We are thankful for the numbats (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.
 

### 2020-01-12 paper/paper.tex
updated acknowledgements

@@
 
-\hypertarget{acknowledgment}{%
-\section{Acknowledgment}\label{acknowledgment}}
-
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations.
-They would also like to thank Distinguished Professor Kerrie Mengersen and Doctor Earl Duncan for suggestions and comments.
+\hypertarget{acknowledgments}{%
+\section{Acknowledgments}\label{acknowledgments}}
+
+The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments.
+Mitch O'Hara-Wild was a co-developer of the taipan R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
+We are thankful for the numbats (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.
 

### 2020-01-12 paper/paper.Rmd
Added lineup fig

@@
 
-<!-- This alternative display is suggested for communicating distributions that relate to the population values or density of the population in each geographic unit.
-This study uses the lineup protocol for visual inference testing of the recognition of spatial distributions.
-The Australian Cancer Atlas explores spatial distributions of cancer incidence and the burden on Australian communities.
-The spatial distributions of the cancers explored in this atlas inspired the trend models presented to participants in this study.
-
-Motivation
-=============
-!-- Find a new display for the Cancer Atlas --
-
-## The Australian Cancer Atlas
--->
-
 The Australian Cancer Atlas [@atlas] is an online interactive web tool created to explore the burden of cancer on Australian communities.
@@
 The results are summarized in Section [Results].
-
-<!--
-The Atlas examines Australian communities at the Statistical Areas at Level 2 (SA2) [@abs2016] used by the Australian Bureau of Statistics.
-Bayesian spatial smoothing was applied to integrate the values of neighboring areas.
-Spatial smoothing protects the privacy and gives stability to the estimated amounts in each SA2.
-Users of the Atlas can explore the difference of the statistic of each SA2 from the Australian average, for both diagnoses (Standardised Incidence Rates) and excess deaths.
-It communicates the value of the statistic for each SA2 geographic unit through color, by filling the areas using the diverging color scheme ranging from dark blue to red.
--->
-
 Background
@@
 It has the effect of spreading out the inner city areas while maintaining the spatial locations or regions in remote areas.
-The algorithm is available in the R package, sugarbag (XXX REF).
+The algorithm is available in the R package, sugarbag [@sugarbag].
 Figure \ref{fig:liver} shows the hexagon tile map, along with the choropleth map of liver cancer rates in Australia.
@@
 
-The chance that an observer picks the data plot out of a lineup of size $m$ plots accidentally, if the null hypothesis is true is $/m$.
+The chance that an observer picks the data plot out of a lineup of size $m$ plots accidentally, if the null hypothesis is true is $1/m$.
 With $K$ observers, the probability of $k$ randomly choosing the data plot, roughly follows a binomial distribution with $p=1/m$.
-Figure XXX (this needs to be placed near here) shows a lineup of the hexagon tile map, of size $m=12$.
-Plot XXX is the data plot, and the remaining 11 are plots of null data.
+Fig.
+\ref{fig:lineup} shows a lineup of the hexagon tile map, of size $m=12$.
+Plot 3 is the data plot, and the remaining 11 are plots of null data.
+
+```{r lineup, fig.cap = "This lineup of twelve hexagon tile map displays contains one map with a real population related structure.
+The rest are null plots that contain spatial correlation between neighbours.", fig.height = 8, fig.width = 8}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("figures/aus_cities_3_geo.png")))
+```
 
@@
 The power of the test statistic (data plot) is provided by this proportion.
-Power in a statistical sense is the ability oof the statistic to *produce a rejection* of the null hypothesis, if it is indeed *not true*.
+Power in a statistical sense is the ability of the statistic to *produce a rejection* of the null hypothesis, if it is indeed *not true*.
 With the same data plotted using two different displays, the display with the highest proportion of people who choose the data plot would be considered to be the most powerful statistic.
@@
 Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to do well, and two with differing level of inner city hot spots.
-These latter two reflect the structure seen in the liver cancer data (Figure \ref{fig:liver}).
+These latter two reflect the structure seen in the liver cancer data (Fig.
+\ref{fig:liver}).
 This produces six treatment levels:
@@
 Participants saw a data set only once, with as a choropleth or as a hexagon tile map.
-Table \ref{tab:exp-design} summarise the design.
+Table \ref{fig:exp-design} summarises the design.
 (XXX Maybe replace this table with your diagram illustrating the design??)
 
-<!-- Each group did not see the same data for both map types. We generated four simulated sets of data for each treatment.
-This will generate twenty-four lineups (twelve lineups of geographic maps and twelve lineups of hexagon tile maps). Participants evaluated twelve lineups, size of each map type.
-For each of the six geographic displays and six hexagon displays, two of each trend model were shown to the participants. We outline the design in Table \ref{tab:exp-design}.
--->
-
-```{r exp-design, results = "asis"}
-d %>% 
-  mutate(Trend = trend,
-    Group = group,
-    `Map Type` = type) %>% 
-  group_by(Group, Trend, `Map Type`) %>% 
-  summarise(Reps = paste0(sort(unique(replicate)), collapse = ", ")) %>% 
-  pivot_wider(names_from = c("Map Type"), values_from = c("Reps")) %>% 
-  ungroup() %>% 
-  knitr::kable(., format = "latex", booktabs = TRUE, 
-    linesep = c("", "", "\\addlinespace"),
-    caption = "The experimental design results in the following allocation of replicate data sets within each trend model to groups A and B.") %>% kable_styling(bootstrap_options = "hold_position") %>%
-  collapse_rows(., columns = 1, custom_latex_hline = c(1:3))
+```{r exp-design, results = "asis", fig.width = 8, fig.height = 8}
+ggdraw(xlim = c(0,1), ylim = c(0,1)) + draw_plot(rasterGrob(png::readPNG("figures/experiment_design.png")))
 ```
@@
 Each trend model was tested using four repetitions, evaluations on the same data set were seen as either choropleths or hexagon tile maps by each group as specified in Table.
-\ref{tab:exp-design}; the detection rates for each display are connected by a line segment.
+\ref{fig:exp-design}; the detection rates for each display are connected by a line segment.
 The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts.

### 2020-01-12 paper/paper.tex
Added lineup fig

@@
 The results are summarized in Section \protect\hyperlink{results}{Results}.
-
-\hypertarget{background}{%
-\section{Background}\label{background}}
+Background
+=============
 
@@
 It has the effect of spreading out the inner city areas while maintaining the spatial locations or regions in remote areas.
-The algorithm is available in the R package, sugarbag (XXX REF).
+The algorithm is available in the R package, sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]}.
 Figure \ref{fig:liver} shows the hexagon tile map, along with the choropleth map of liver cancer rates in Australia.
@@
 
-The chance that an observer picks the data plot out of a lineup of size \(m\) plots accidentally, if the null hypothesis is true is \(/m\).
+The chance that an observer picks the data plot out of a lineup of size \(m\) plots accidentally, if the null hypothesis is true is \(1/m\).
 With \(K\) observers, the probability of \(k\) randomly choosing the data plot, roughly follows a binomial distribution with \(p=1/m\).
-Figure XXX (this needs to be placed near here) shows a lineup of the hexagon tile map, of size \(m=12\).
-Plot XXX is the data plot, and the remaining 11 are plots of null data.
+Fig.
+\ref{fig:lineup} shows a lineup of the hexagon tile map, of size \(m=12\).
+Plot 3 is the data plot, and the remaining 11 are plots of null data.
+
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/lineup-1.pdf}
+\caption{\label{fig:lineup}This lineup of twelve hexagon tile map displays contains one map with a real population related structure.
+The rest are null plots that contain spatial correlation between neighbours.}
+\end{figure}
 
@@
 The power of the test statistic (data plot) is provided by this proportion.
-Power in a statistical sense is the ability oof the statistic to \emph{produce a rejection} of the null hypothesis, if it is indeed \emph{not true}.
+Power in a statistical sense is the ability of the statistic to \emph{produce a rejection} of the null hypothesis, if it is indeed \emph{not true}.
 With the same data plotted using two different displays, the display with the highest proportion of people who choose the data plot would be considered to be the most powerful statistic.
@@
 Participants saw a data set only once, with as a choropleth or as a hexagon tile map.
-Table \ref{tab:exp-design} summarise the design.
+Table \ref{fig:exp-design} summarises the design.
 (XXX Maybe replace this table with your diagram illustrating the design??)
 
-\begin{table}
-
-\caption{\label{tab:exp-design}The experimental design results in the following allocation of replicate data sets within each trend model to groups A and B.}
-\centering
-\begin{tabular}[t]{llll}
-\toprule
-Group & Trend & Choro. & Hex.\\
-\midrule
- & NW-SE & 1, 2 & 3, 4\\
-\cmidrule{2-4}
- & Three Cities & 1, 2 & 3, 4\\
-\cmidrule{2-4}
-\multirow{-3}{*}{\raggedright\arraybackslash A} & All Cities & 2, 4 & 1, 3\\
-\cmidrule{1-4}
- & NW-SE & 3, 4 & 1, 2\\
-\cmidrule{2-4}
- & Three Cities & 3, 4 & 1, 2\\
-\cmidrule{2-4}
-\multirow{-3}{*}{\raggedright\arraybackslash B} & All Cities & 1, 3 & 2, 4\\
-\bottomrule
-\end{tabular}
-\end{table}
+\includegraphics{paper_files/figure-latex/exp-design-1.pdf}
 

### 2020-01-13 paper/paper.Rmd
spelling check

@@
 A hexagon tile map forgoes the familiar boundaries, in favor of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location.
-The hexagon tile map builds on existing displays, such as the cartogram, and tesselated hexagon displays.
+The hexagon tile map builds on existing displays, such as the cartogram, and tessellated hexagon displays.
 It differs in that it relaxes the requirement to have connected hexagons, and allows sparsely located hexagons.
@@
 Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips.
-A choropleth map focuses attention on the geography, and for heterogeously sized areas it presents a biased view of the population related distribution of the statistic [@CBATCC].
+A choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population related distribution of the statistic [@CBATCC].
 *Land doesn't get cancer, people do* -- a more effective way to communicate the spatial distributions of cancer statistics is needed.
@@
 <!-- Hexagon tile map -->
-The hexagon tile map algorithm, autmatically matches spatial regions to their nearest hexagon tile, from a grid of tiles.
+The hexagon tile map algorithm, automatically matches spatial regions to their nearest hexagon tile, from a grid of tiles.
 It has the effect of spreading out the inner city areas while maintaining the spatial locations or regions in remote areas.
@@
 Remote regions are represented by isolated hexagons, which is not ideal, but maintains the spatial location of these data values.
-It is oof interest to know how well the spatial distribution is perceived for this display, in comparison to the choropleth.
+It is of interest to know how well the spatial distribution is perceived for this display, in comparison to the choropleth.
 
@@
 
-In classical statistical inference hypothesis testing is coonducted by comparing the value of a test statistic on a standard reference distribution, computed assuming the null hypothesis is true.
+In classical statistical inference hypothesis testing is conducted by comparing the value of a test statistic on a standard reference distribution, computed assuming the null hypothesis is true.
 If the value is extreme,  the null hypothesis is rejected, because the test statistic value is unlikely to have been so extreme if it was true.
@@
 
-Australia is used for the study, with Statistical Area 2 (SA2) (XXX REF) as the geographic units. The results shuold apply broadly to any other geographic area of interest.
+Australia is used for the study, with Statistical Area 2 (SA2) (XXX REF) as the geographic units. The results should apply broadly to any other geographic area of interest.
 
@@
 
-<!-- The variables measured as a result of the changes were the probability of detection each display and the time taken to submit responses.
-To measure the accuracy of the detections, the plot chosen for each lineup evaluated was compared to the position of the real spatial trend plot in the lineup.
-A correct result occurs when the chosen plot matches the position of the real plot, this was recorded in an additional binary variable; 1 = correct; 0 = incorrect.
-High efficiency occurs when a small amount of time is taken to evaluate each lineup.
-This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.-->
-
 ## Generating null data
@@
 In spatial data, a key feature is smoothness over the landscape corresponding spatial dependence.
-To do something simple, like permute the values relative to the goegraphic location would produce null plots which are too chaotic, and the data plot will be recognisable for its smoothness rather than any structure of interest.
-
-For spatial data, null data is staionary data, where the mean, variance and spatial dependence are constant over the geographic units.
+To do something simple, like permute the values relative to the geographic location would produce null plots which are too chaotic, and the data plot will be recognisable for its smoothness rather than any structure of interest.
+
+For spatial data, null data is stationary data, where the mean, variance and spatial dependence are constant over the geographic units.
 Stationary data is specified by a variogram model (XXX REF).
 Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots.
-A Gaussian The parameters for the model were sill=1, range=0.3 with the variance generated by a standard normal distribution (XXX What parameters were used?).
-
-The R package `gstat` (XXX REF) was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
+The parameters for the Gaussian model were sill=1, range=0.3 with the variance generated by a standard normal distribution.
+
+The R package `gstat` [@gstat] was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
 
@@
 
-Participants were recruited for to evaluate lineups from the Figure-Eight crowdsourcing platform (XXX REF).
+Participants were recruited for to evaluate lineups from the Figure Eight crowd sourcing platform [@figeight].
 The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
@@
 
-Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure-Eight website.
+Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure Eight website.
 There were 95 participants involved in the study.
 All participants read introductory materials, and was trained using three test displays, to orient them to the evaluation task.
-All participants who completed the task were compensated $USD5 for their time, via the Figure-Eight payment system.
+All participants who completed the task were compensated $USD5 for their time, via the Figure Eight payment system.
 
@@
 
-Participants then moved to the evaulation phase.
+Participants then moved to the evaluation phase.
 The set of images differed for Group A and Group B.
@@
 The choropleth map was used as the comparative visualization for presenting the lineups [@VVSIALM] as this is the common display for spatial cancer data.
-Geographic distributions usually have some degree of spatial autcorrelation between neighbors.
+Geographic distributions usually have some degree of spatial autocorrelation between neighbors.
 This feature was incorporated in all maps shown in the lineup displays, the map that contained the trend feature shown in only one set of data was also affected by spatial autocorrelation.
@@
 
-Side-by-side dot plots were made of accuracy (efficiency) against map type, facetted by trend model type.
+Side-by-side dot plots were made of accuracy (efficiency) against map type, faceted by trend model type.
 
@@
 
-### Modeling
+### Modelling
 
@@
 
-Of the 92 participants, 67 were male, and 25 female. Most participants (56) had a Bacherlors degree, 13 had a Masters degree, and the remaining 23 had high school diplomas.
+Of the 92 participants, 67 were male, and 25 female. Most participants (56) had a Bachelors degree, 13 had a Masters degree, and the remaining 23 had high school diplomas.
 
@@
 Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
-Allowing for the interaction effect, the difference in detection rate decreases for population related displays for a choroleth map lineup, but increases for a hexagon tile map display.
+Allowing for the interaction effect, the difference in detection rate decreases for population related displays for a choropleth map lineup, but increases for a hexagon tile map display.
 The log odds of detection show in Table. \ref{tab:detect-glmer1} can be back transformed after taking the sum of all terms for the trend and type of display that are of interest.
@@
 The average time taken for type of display is shown as a large colored dot on each plot.
-when considering the heights of the green and orange dots, there is little difference in the average time taken to read a choropleth or hexgon tile map.
+when considering the heights of the green and orange dots, there is little difference in the average time taken to read a choropleth or hexagon tile map.
 Comparing the same colored dot across each trend model row, there is a slight increase in the time taken to correctly detected the data plot in the hexagon tile map lineup, but little difference in evaluation time for the choropleth display.
@@
 Participants provided their level of certainty regarding their choice using a five point scale. 
-Unlike the accuracy and speed of reponses that were derived during the data processing phase, this was a subjective
+Unlike the accuracy and speed of responses that were derived during the data processing phase, this was a subjective
 assessment by the participant prompted by the question: ‘How certain are you about your choice?’.
@@
 Participants performed better on the NW-SE distribution shown in the choropleth display and were reasonably confident about their decisions.
-The high levels of the mid range value of 3 could indicate that the participant did not want to provide a response, as this wasy the default value.
+The high levels of the mid range value of 3 could indicate that the participant did not want to provide a response, as this was the default value.
 Those who chose level 4 or 5 were equally likely to be correct for the three cities lineups, but more likely to be correct than incorrect for the other two trend models.
@@
 The color scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
-Due to the consisent coloring of rural areas in a choropleth display, the choice "All areas have similar colors" was most common reason for a participants choice.
+Due to the consistent coloring of rural areas in a choropleth display, the choice "All areas have similar colors" was most common reason for a participants choice.
 The All Cities displays colored the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural color consistency.
@@
 
-The increasing population densities of capital cities despite large land area exaserbates the difference in the smallest and largest communities.
+The increasing population densities of capital cities despite large land area exacerbates the difference in the smallest and largest communities.
 The population density structure of Australia can be considered similar to that of Canada, New Zealand and many others.
@@
 
-- Additonal analysis of the experimental results
+- Additional analysis of the experimental results
 - Training materials used for the participants
 - 24 lineups used in the experiment
-- 12 data sets used to coonstruct the lineups
+- 12 data sets used to construct the lineups
 
@@
 
-Acknowledgments
+Acknowledgment
 ==============
@@
 The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments.
-Mitch O'Hara-Wild was a co-developer of the taipan R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
-We are thankful for the numbats (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.
+Mitchell O'Hara-Wild was a co-developer of the taipan [@taipan] R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
+We are thankful for the NUMBATs (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.
 
 The source code to produce this document can be found on [GitHub](https://github.com/srkobakian/experiment/tree/master/paper).
-Supplementary materials have been included to discuss the survey procedures,
+Supplementary materials have been included to discuss the survey procedures and the lineups that were used.
+The full set of images can also be found at: https://github.com/srkobakian/experiment/tree/master/figures/final.
 
@@
  - For image displays: cowplot [@cowplot], png [@png], grid [@grid].
- - For modeling and presentation of models: lme4 [@lme4], kableExtra [@kableExtra].
+ - For modelling and presentation of models: gstat [@gstat], lme4 [@lme4], kableExtra [@kableExtra].
 

### 2020-01-13 paper/paper.tex
spelling check

@@
 Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips.
-A choropleth map focuses attention on the geography, and for heterogeously sized areas it presents a biased view of the population related distribution of the statistic {[}\protect\hyperlink{ref-CBATCC}{6}{]}.
+A choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population related distribution of the statistic {[}\protect\hyperlink{ref-CBATCC}{6}{]}.
 \emph{Land doesn't get cancer, people do} -- a more effective way to communicate the spatial distributions of cancer statistics is needed.
@@
 
-The hexagon tile map algorithm, autmatically matches spatial regions to their nearest hexagon tile, from a grid of tiles.
+The hexagon tile map algorithm, automatically matches spatial regions to their nearest hexagon tile, from a grid of tiles.
 It has the effect of spreading out the inner city areas while maintaining the spatial locations or regions in remote areas.
@@
 
-In classical statistical inference hypothesis testing is coonducted by comparing the value of a test statistic on a standard reference distribution, computed assuming the null hypothesis is true.
+In classical statistical inference hypothesis testing is conducted by comparing the value of a test statistic on a standard reference distribution, computed assuming the null hypothesis is true.
 If the value is extreme, the null hypothesis is rejected, because the test statistic value is unlikely to have been so extreme if it was true.
@@
 In spatial data, a key feature is smoothness over the landscape corresponding spatial dependence.
-To do something simple, like permute the values relative to the goegraphic location would produce null plots which are too chaotic, and the data plot will be recognisable for its smoothness rather than any structure of interest.
-
-For spatial data, null data is staionary data, where the mean, variance and spatial dependence are constant over the geographic units.
+To do something simple, like permute the values relative to the geographic location would produce null plots which are too chaotic, and the data plot will be recognisable for its smoothness rather than any structure of interest.
+
+For spatial data, null data is stationary data, where the mean, variance and spatial dependence are constant over the geographic units.
 Stationary data is specified by a variogram model (XXX REF).
 Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots.
-A Gaussian The parameters for the model were sill=1, range=0.3 with the variance generated by a standard normal distribution (XXX What parameters were used?).
-
-The R package \texttt{gstat} (XXX REF) was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
+The parameters for the Gaussian model were sill=1, range=0.3 with the variance generated by a standard normal distribution.
+
+The R package \texttt{gstat} {[}\protect\hyperlink{ref-gstat}{14}{]} was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
 
@@
 The data collection took place using a secure link between the survey web application and the googlesheet used to store results.
-The application would first connect to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{14}{]} R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
+The application would first connect to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{15}{]} R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
 
@@
 
-Participants were recruited for to evaluate lineups from the Figure-Eight crowdsourcing platform (XXX REF).
+Participants were recruited for to evaluate lineups from the Figure Eight crowd sourcing platform {[}\protect\hyperlink{ref-figeight}{16}{]}.
 The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
@@
 
-Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure-Eight website.
+Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure Eight website.
 There were 95 participants involved in the study.
 All participants read introductory materials, and was trained using three test displays, to orient them to the evaluation task.
-All participants who completed the task were compensated \$USD5 for their time, via the Figure-Eight payment system.
+All participants who completed the task were compensated \$USD5 for their time, via the Figure Eight payment system.
 
@@
 
-\hypertarget{modeling}{%
-\subsubsection{Modeling}\label{modeling}}
+\hypertarget{modelling}{%
+\subsubsection{Modelling}\label{modelling}}
 
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R {[}\protect\hyperlink{ref-RCore}{15}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{16}{]} package implements generalised linear mixed effect models.
+The R {[}\protect\hyperlink{ref-RCore}{17}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{18}{]} package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 
-Computation will be done using R {[}\protect\hyperlink{ref-RCore}{15}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{16}{]}.
+Computation will be done using R {[}\protect\hyperlink{ref-RCore}{17}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{18}{]}.
 
@@
 Participants provided their level of certainty regarding their choice using a five point scale.
-Unlike the accuracy and speed of reponses that were derived during the data processing phase, this was a subjective
+Unlike the accuracy and speed of responses that were derived during the data processing phase, this was a subjective
 assessment by the participant prompted by the question: `How certain are you about your choice?'.
@@
 The color scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
-Due to the consisent coloring of rural areas in a choropleth display, the choice ``All areas have similar colors'' was most common reason for a participants choice.
+Due to the consistent coloring of rural areas in a choropleth display, the choice ``All areas have similar colors'' was most common reason for a participants choice.
 The All Cities displays colored the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural color consistency.
@@
 \item
-  Additonal analysis of the experimental results
+  Additional analysis of the experimental results
 \item
@@
 \item
-  12 data sets used to coonstruct the lineups
+  12 data sets used to construct the lineups
 \end{itemize}
@@
 
-\hypertarget{acknowledgments}{%
-\section{Acknowledgments}\label{acknowledgments}}
+\hypertarget{acknowledgment}{%
+\section{Acknowledgment}\label{acknowledgment}}
 
 The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments.
-Mitch O'Hara-Wild was a co-developer of the taipan R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
-We are thankful for the numbats (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.
+Mitchell O'Hara-Wild was a co-developer of the taipan {[}\protect\hyperlink{ref-taipan}{19}{]} R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
+We are thankful for the NUMBATs (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.
 
 The source code to produce this document can be found on \href{https://github.com/srkobakian/experiment/tree/master/paper}{GitHub}.
-Supplementary materials have been included to discuss the survey procedures,
-
-The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{15}{]} with the use of the following packages:
+Supplementary materials have been included to discuss the survey procedures and the lineups that were used.
+The full set of images can also be found at: https://github.com/srkobakian/experiment/tree/master/figures/final.
+
+The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{17}{]} with the use of the following packages:
 
@@
 \item
-  For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{17}{]}, rticles {[}\protect\hyperlink{ref-rticles}{18}{]}, knitr {[}\protect\hyperlink{ref-knitr}{19}{]}.
-\item
-  For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{20}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{21}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{22}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{23}{]}.
-\item
-  For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{24}{]}, png {[}\protect\hyperlink{ref-png}{25}{]}, grid {[}\protect\hyperlink{ref-grid}{26}{]}.
-\item
-  For modeling and presentation of models: lme4 {[}\protect\hyperlink{ref-lme4}{16}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{27}{]}.
+  For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{20}{]}, rticles {[}\protect\hyperlink{ref-rticles}{21}{]}, knitr {[}\protect\hyperlink{ref-knitr}{22}{]}.
+\item
+  For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{23}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{24}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{25}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{26}{]}.
+\item
+  For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{27}{]}, png {[}\protect\hyperlink{ref-png}{28}{]}, grid {[}\protect\hyperlink{ref-grid}{29}{]}.
+\item
+  For modelling and presentation of models: gstat {[}\protect\hyperlink{ref-gstat}{14}{]}, lme4 {[}\protect\hyperlink{ref-lme4}{18}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{30}{]}.
 \end{itemize}
@@
 
+\leavevmode\hypertarget{ref-gstat}{}%
+14. Gräler B, Pebesma E, Heuvelink G (2016) Spatio-temporal interpolation using gstat. The R Journal 8:204--218
+
 \leavevmode\hypertarget{ref-sheets}{}%
-14. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
+15. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
+
+\leavevmode\hypertarget{ref-figeight}{}%
+16. (2019) The essential high-quality data annotation platform. Figure Eight
 
 \leavevmode\hypertarget{ref-RCore}{}%
-15. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+17. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
 
 \leavevmode\hypertarget{ref-lme4}{}%
-16. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
+18. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
+
+\leavevmode\hypertarget{ref-taipan}{}%
+19. Kobakian S, O'Hara-Wild M (2018) Taipan: Tool for annotating images in preparation for analysis.
 
 \leavevmode\hypertarget{ref-rmarkdown}{}%
-17. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida
+20. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida
 
 \leavevmode\hypertarget{ref-rticles}{}%
-18. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.
+21. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.
 
 \leavevmode\hypertarget{ref-knitr}{}%
-19. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research
+22. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research
 
 \leavevmode\hypertarget{ref-tidyverse}{}%
-20. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686
+23. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686
 
 \leavevmode\hypertarget{ref-nullabor}{}%
-21. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.
+24. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.
 
 \leavevmode\hypertarget{ref-ggthemes}{}%
-22. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.
+25. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.
 
 \leavevmode\hypertarget{ref-RColorBrewer}{}%
-23. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.
+26. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.
 
 \leavevmode\hypertarget{ref-cowplot}{}%
-24. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.
+27. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.
 
 \leavevmode\hypertarget{ref-png}{}%
-25. Urbanek S (2013) Png: Read and write png images.
+28. Urbanek S (2013) Png: Read and write png images.
 
 \leavevmode\hypertarget{ref-grid}{}%
-26. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+29. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
 
 \leavevmode\hypertarget{ref-kableExtra}{}%
-27. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
+30. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
 

### 2020-01-13 paper/paper.Rmd
two references sections fixed

@@
 A similar approach was pioneered by Raisz [-@RSCW], using rectangles that tile to align borders of neighbours [@CDWCS].
-A thorough review of the array of methods, as suitable for cancer atlas displays is available in XXX.
+There have been thorough reviews of the array of methods, as suitable for cancer atlas displays [@review], [@BCM].
 
@@
 
-Australia is used for the study, with Statistical Area 2 (SA2) (XXX REF) as the geographic units. The results should apply broadly to any other geographic area of interest.
+Australia is used for the study, with Statistical Area 2 (SA2) [@abs2016] as the geographic units. The results should apply broadly to any other geographic area of interest.
 
@@
 Table \ref{fig:exp-design} summarises the design.
-(XXX Maybe replace this table with your diagram illustrating the design??)
 
@@
 For spatial data, null data is stationary data, where the mean, variance and spatial dependence are constant over the geographic units.
-Stationary data is specified by a variogram model (XXX REF).
+Stationary data is specified by a variogram model [@POG].
 Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots.
@@
 
-## Web app collecting responses
+## Web application to collect responses
 
-XXX Describe the details of the taipan app used to collect responses
+The taipan [@taipan] package for R was used to create the survey web application. 
+This structure was altered to collect responses regarding participants demographics and their survey responses.
+The survey app contained three tabs, participants were first shown the demographics and consent page.
+This asked participants for their Figure-Eight contributor ID, and their consent to the responses being used for analysis.
+The demographics collected included participants' preferred pronoun, the highest level of education achieved, their age range and whether they had lived in Australia.
 
-Data was collected through a web application containing the online survey.
+After submitting these responses, the survey application switched to the tab of lineups and associated questions.
+This allowed participants to easily move through the twelve displays and provide their choice, reason for their choice, and level of certainty.
+
+When participants completed the twelve evaluations the survey application triggered a data analysis script.
+This created a data set with one row per evaluation.
+Along with the responses to the three questions, the script added the title of the image, which indicated the type of map display, the type of distribution hidden in the lineup, and the location of the data plot.
+It also calculated the time taken by participant to view each lineup.
+
 Each participant used the internet to access the survey.
-The data collection took place using a secure link between the survey web application and the googlesheet used to store results.
-The application would first connect to the googlesheet using the googlesheets [@sheets] R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
+The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results.
+The application connected to the googlesheet using the googlesheets [@sheets] R package when participants opened the application, and interacted again when participants chosen to submit the survey and indicate their completion.
+At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.
 
@@
 
-Participants were recruited for to evaluate lineups from the Figure Eight crowd sourcing platform [@figeight].
+Participants were recruited to evaluate lineups from the Figure Eight crowdsourcing platform [@figeight].
 The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
@@
 
-Acknowledgements
-==============
-
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations.
-They would also like to thank Kerrie Mengersen and Dr.
-Earl Duncan for suggestions and comments.
-
-Ethics approval for the online survey was granted by QUT’s Ethics Committee (Ethics Application Number: 1900000991).
-All applicants provided informed consent in line with QUT regulations prior to participating in this research.
-
-All code to generate the data, of the web app that collected participants responses, conduct the analysis, and produce this manuscript are available on XXX.
-
-The supplementary material contains:
-
-- Additional analysis of the experimental results
-- Training materials used for the participants
-- 24 lineups used in the experiment
-- 12 data sets used to construct the lineups
-
-References {#references .numbered}
-==========
-
-<!-- An example of a floating figure using the graphicx package. -->
-<!-- Note that \label must occur AFTER (or within) \caption. -->
-<!-- For figures, \caption should occur after the \includegraphics. -->
-<!-- Note that IEEEtran v1.7 and later has special internal code that -->
-<!-- is designed to preserve the operation of \label within \caption -->
-<!-- even when the captionsoff option is in effect. However, because -->
-<!-- of issues like this, it may be the safest practice to put all your -->
-<!-- \label just after \caption rather than within \caption{}. -->
-
-<!-- Reminder: the "draftcls" or "draftclsnofoot", not "draft", class -->
-<!-- option should be used if it is desired that the figures are to be -->
-<!-- displayed while in draft mode. -->
-
-<!-- \begin{figure}[!t] -->
-<!-- \centering -->
-<!-- \includegraphics[width=2.5in]{myfigure} -->
-<!-- where an .eps filename suffix were assumed under latex,  -->
-<!-- and a .pdf suffix were assumed for pdflatex; or what has been declared -->
-<!-- via \DeclareGraphicsExtensions. -->
-<!-- \caption{Simulation results for the network.} -->
-<!-- \label{fig_sim} -->
-<!-- \end{figure} -->
-
-<!-- Note that the IEEE typically puts floats only at the top, even when this -->
-<!-- results in a large percentage of a column being occupied by floats. -->
-
-<!-- An example of a double column floating figure using two subfigures. -->
-<!-- (The subfig.sty package must be loaded for this to work.) -->
-<!-- The subfigure \label commands are set within each subfloat command, -->
-<!-- and the \label for the overall figure must come after \caption. -->
-<!-- \hfil is used as a separator to get equal spacing. -->
-<!-- Watch out that the combined width of all the subfigures on a  -->
-<!-- line do not exceed the text width or a line break will occur. -->
-
-<!-- \begin{figure*}[!t] -->
-<!-- \centering -->
-<!-- \subfloat[Case I]{\includegraphics[width=2.5in]{box}% -->
-<!-- \label{fig_first_case}} -->
-<!-- \hfil -->
-<!-- \subfloat[Case II]{\includegraphics[width=2.5in]{box}% -->
-<!-- \label{fig_second_case}} -->
-<!-- \caption{Simulation results for the network.} -->
-<!-- \label{fig_sim} -->
-<!-- \end{figure*} -->
-
-<!-- Note that often IEEE papers with subfigures do not employ subfigure -->
-<!-- captions (using the optional argument to \subfloat[]), but instead will -->
-<!-- reference/describe all of them (a), (b), etc., within the main caption. -->
-<!-- Be aware that for subfig.sty to generate the (a), (b), etc., subfigure -->
-<!-- labels, the optional argument to \subfloat must be present. If a -->
-<!-- subcaption is not desired, just leave its contents blank, -->
-<!-- e.g., \subfloat[]. -->
-
-\newpage
-
 Acknowledgment
@@
 The full set of images can also be found at: https://github.com/srkobakian/experiment/tree/master/figures/final.
+
+The supplementary material contains:
+
+- Additional analysis of the experimental results
+- Survey procedure including training materials for the participants
+- 24 lineups as images, that were used in the experiment
+- 12 data sets used to construct the lineups
 
@@
 ==========
-
-<!-- An example of a floating figure using the graphicx package. -->
-<!-- Note that \label must occur AFTER (or within) \caption. -->
-<!-- For figures, \caption should occur after the \includegraphics. -->
-<!-- Note that IEEEtran v1.7 and later has special internal code that -->
-<!-- is designed to preserve the operation of \label within \caption -->
-<!-- even when the captionsoff option is in effect. However, because -->
-<!-- of issues like this, it may be the safest practice to put all your -->
-<!-- \label just after \caption rather than within \caption{}. -->
-
-<!-- Reminder: the "draftcls" or "draftclsnofoot", not "draft", class -->
-<!-- option should be used if it is desired that the figures are to be -->
-<!-- displayed while in draft mode. -->
-
-<!-- \begin{figure}[!t] -->
-<!-- \centering -->
-<!-- \includegraphics[width=2.5in]{myfigure} -->
-<!-- where an .eps filename suffix were assumed under latex,  -->
-<!-- and a .pdf suffix were assumed for pdflatex; or what has been declared -->
-<!-- via \DeclareGraphicsExtensions. -->
-<!-- \caption{Simulation results for the network.} -->
-<!-- \label{fig_sim} -->
-<!-- \end{figure} -->
-
-<!-- Note that the IEEE typically puts floats only at the top, even when this -->
-<!-- results in a large percentage of a column being occupied by floats. -->
-
-<!-- An example of a double column floating figure using two subfigures. -->
-<!-- (The subfig.sty package must be loaded for this to work.) -->
-<!-- The subfigure \label commands are set within each subfloat command, -->
-<!-- and the \label for the overall figure must come after \caption. -->
-<!-- \hfil is used as a separator to get equal spacing. -->
-<!-- Watch out that the combined width of all the subfigures on a  -->
-<!-- line do not exceed the text width or a line break will occur. -->
-
-<!-- \begin{figure*}[!t] -->
-<!-- \centering -->
-<!-- \subfloat[Case I]{\includegraphics[width=2.5in]{box}% -->
-<!-- \label{fig_first_case}} -->
-<!-- \hfil -->
-<!-- \subfloat[Case II]{\includegraphics[width=2.5in]{box}% -->
-<!-- \label{fig_second_case}} -->
-<!-- \caption{Simulation results for the network.} -->
-<!-- \label{fig_sim} -->
-<!-- \end{figure*} -->
-
-<!-- Note that often IEEE papers with subfigures do not employ subfigure -->
-<!-- captions (using the optional argument to \subfloat[]), but instead will -->
-<!-- reference/describe all of them (a), (b), etc., within the main caption. -->
-<!-- Be aware that for subfig.sty to generate the (a), (b), etc., subfigure -->
-<!-- labels, the optional argument to \subfloat must be present. If a -->
-<!-- subcaption is not desired, just leave its contents blank, -->
-<!-- e.g., \subfloat[]. -->

### 2020-01-13 paper/paper.tex
two references sections fixed

@@
 A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{9}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{10}{]}.
-A thorough review of the array of methods, as suitable for cancer atlas displays is available in XXX.
+There have been thorough reviews of the array of methods, as suitable for cancer atlas displays {[}\protect\hyperlink{ref-review}{11}{]}, {[}\protect\hyperlink{ref-BCM}{5}{]}.
 
@@
 In order to assess the effectiveness of the hexagon tile map, the lineup protocol {[}\protect\hyperlink{ref-GIIV}{3}{]} from visual inference procedures is employed.
-The procedures for doing a power comparison of competing plot designed, outlined in {[}\protect\hyperlink{ref-GTPCCD}{12}{]}, are followed.
+The procedures for doing a power comparison of competing plot designed, outlined in {[}\protect\hyperlink{ref-GTPCCD}{13}{]}, are followed.
 The approach mirrors classical statistical inference.
@@
 In the lineup protocol, the plot plays the role of the test statistic, and the data plot is embedded in a field of null plots.
-Defining the plot using a grammar of graphics {[}\protect\hyperlink{ref-ggplot2}{13}{]} makes it a functional mapping of the variables and thus, it can be considered to be a statistic.
+Defining the plot using a grammar of graphics {[}\protect\hyperlink{ref-ggplot2}{14}{]} makes it a functional mapping of the variables and thus, it can be considered to be a statistic.
 With the same data, two different plots can be considered to be competing statistics, one possibly a more powerful statistic than the other.
@@
 
-Australia is used for the study, with Statistical Area 2 (SA2) (XXX REF) as the geographic units. The results should apply broadly to any other geographic area of interest.
+Australia is used for the study, with Statistical Area 2 (SA2) {[}\protect\hyperlink{ref-abs2016}{15}{]} as the geographic units.
+The results should apply broadly to any other geographic area of interest.
 
@@
 For spatial data, null data is stationary data, where the mean, variance and spatial dependence are constant over the geographic units.
-Stationary data is specified by a variogram model (XXX REF).
+Stationary data is specified by a variogram model {[}\protect\hyperlink{ref-POG}{16}{]}.
 Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots.
@@
 
-The R package \texttt{gstat} {[}\protect\hyperlink{ref-gstat}{14}{]} was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
+The R package \texttt{gstat} {[}\protect\hyperlink{ref-gstat}{17}{]} was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
 
@@
 
-\hypertarget{web-app-collecting-responses}{%
-\subsection{Web app collecting responses}\label{web-app-collecting-responses}}
-
-XXX Describe the details of the taipan app used to collect responses
-
-Data was collected through a web application containing the online survey.
+\hypertarget{web-application-to-collect-responses}{%
+\subsection{Web application to collect responses}\label{web-application-to-collect-responses}}
+
+The taipan {[}\protect\hyperlink{ref-taipan}{18}{]} package for R was used to create the survey web application.
+This structure was altered to collect responses regarding participants demographics and their survey responses.
+The survey app contained three tabs, participants were first shown the demographics and consent page.
+This asked participants for their Figure-Eight contributor ID, and their consent to the responses being used for analysis.
+The demographics collected included participants' preferred pronoun, the highest level of education achieved, their age range and whether they had lived in Australia.
+
+After submitting these responses, the survey application switched to the tab of lineups and associated questions.
+This allowed participants to easily move through the twelve displays and provide their choice, reason for their choice, and level of certainty.
+
+When participants completed the twelve evaluations the survey application triggered a data analysis script.
+This created a data set with one row per evaluation.
+Along with the responses to the three questions, the script added the title of the image, which indicated the type of map display, the type of distribution hidden in the lineup, and the location of the data plot.
+It also calculated the time taken by participant to view each lineup.
+
 Each participant used the internet to access the survey.
-The data collection took place using a secure link between the survey web application and the googlesheet used to store results.
-The application would first connect to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{15}{]} R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
+The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results.
+The application connected to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{19}{]} R package when participants opened the application, and interacted again when participants chosen to submit the survey and indicate their completion.
+At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.
 
@@
 
-Participants were recruited for to evaluate lineups from the Figure Eight crowd sourcing platform {[}\protect\hyperlink{ref-figeight}{16}{]}.
+Participants were recruited to evaluate lineups from the Figure Eight crowdsourcing platform {[}\protect\hyperlink{ref-figeight}{20}{]}.
 The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
@@
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R {[}\protect\hyperlink{ref-RCore}{17}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{18}{]} package implements generalised linear mixed effect models.
+The R {[}\protect\hyperlink{ref-RCore}{21}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{22}{]} package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 
-Computation will be done using R {[}\protect\hyperlink{ref-RCore}{17}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{18}{]}.
+Computation will be done using R {[}\protect\hyperlink{ref-RCore}{21}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{22}{]}.
 
@@
 
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
-
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations.
-They would also like to thank Kerrie Mengersen and Dr.~Earl Duncan for suggestions and comments.
-
-Ethics approval for the online survey was granted by QUT's Ethics Committee (Ethics Application Number: 1900000991).
-All applicants provided informed consent in line with QUT regulations prior to participating in this research.
-
-All code to generate the data, of the web app that collected participants responses, conduct the analysis, and produce this manuscript are available on XXX.
-
-The supplementary material contains:
-
-\begin{itemize}
-\tightlist
-\item
-  Additional analysis of the experimental results
-\item
-  Training materials used for the participants
-\item
-  24 lineups used in the experiment
-\item
-  12 data sets used to construct the lineups
-\end{itemize}
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
 \newpage
@@
 The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments.
-Mitchell O'Hara-Wild was a co-developer of the taipan {[}\protect\hyperlink{ref-taipan}{19}{]} R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
+Mitchell O'Hara-Wild was a co-developer of the taipan {[}\protect\hyperlink{ref-taipan}{18}{]} R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
 We are thankful for the NUMBATs (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.
@@
 
-The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{17}{]} with the use of the following packages:
+The supplementary material contains:
 
@@
 \item
-  For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{20}{]}, rticles {[}\protect\hyperlink{ref-rticles}{21}{]}, knitr {[}\protect\hyperlink{ref-knitr}{22}{]}.
-\item
-  For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{23}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{24}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{25}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{26}{]}.
-\item
-  For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{27}{]}, png {[}\protect\hyperlink{ref-png}{28}{]}, grid {[}\protect\hyperlink{ref-grid}{29}{]}.
-\item
-  For modelling and presentation of models: gstat {[}\protect\hyperlink{ref-gstat}{14}{]}, lme4 {[}\protect\hyperlink{ref-lme4}{18}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{30}{]}.
+  Additional analysis of the experimental results
+\item
+  Survey procedure including training materials for the participants
+\item
+  24 lineups as images, that were used in the experiment
+\item
+  12 data sets used to construct the lineups
+\end{itemize}
+
+The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{21}{]} with the use of the following packages:
+
+\begin{itemize}
+\tightlist
+\item
+  For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{23}{]}, rticles {[}\protect\hyperlink{ref-rticles}{24}{]}, knitr {[}\protect\hyperlink{ref-knitr}{25}{]}.
+\item
+  For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{26}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{27}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{28}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{29}{]}.
+\item
+  For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{30}{]}, png {[}\protect\hyperlink{ref-png}{31}{]}, grid {[}\protect\hyperlink{ref-grid}{32}{]}.
+\item
+  For modelling and presentation of models: gstat {[}\protect\hyperlink{ref-gstat}{17}{]}, lme4 {[}\protect\hyperlink{ref-lme4}{22}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{33}{]}.
 \end{itemize}
@@
 
-\hypertarget{references-1}{%
-\section{References}\label{references-1}}
+\hypertarget{references}{%
+\section{References}\label{references}}
 
@@
 
+\leavevmode\hypertarget{ref-review}{}%
+11. (2019) Cancer applications of choropleth maps, and the potential of cartograms and alternative map displays. Manuscript submitted for publication.
+
 \leavevmode\hypertarget{ref-BCHLLSW09}{}%
-11.
+12.
 Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) Statistical inference for exploratory data analysis and model diagnostics.
@@
 \leavevmode\hypertarget{ref-GTPCCD}{}%
-12. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448
+13. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448
 
 \leavevmode\hypertarget{ref-ggplot2}{}%
-13. Wickham H (2009) Ggplot2: Elegant graphics for data analysis. Springer New York
+14. Wickham H (2009) Ggplot2: Elegant graphics for data analysis. Springer New York
+
+\leavevmode\hypertarget{ref-abs2016}{}%
+15. (2018) Australian Statistical Geography Standard (ASGS). Australian Bureau of Statistics
+
+\leavevmode\hypertarget{ref-POG}{}%
+16. Matheron G (1963) Principles of geostatistics. Economic Geology 58:1246--1266
 
 \leavevmode\hypertarget{ref-gstat}{}%
-14. Gräler B, Pebesma E, Heuvelink G (2016) Spatio-temporal interpolation using gstat. The R Journal 8:204--218
+17. Gräler B, Pebesma E, Heuvelink G (2016) Spatio-temporal interpolation using gstat. The R Journal 8:204--218
+
+\leavevmode\hypertarget{ref-taipan}{}%
+18. Kobakian S, O'Hara-Wild M (2018) Taipan: Tool for annotating images in preparation for analysis.
 
 \leavevmode\hypertarget{ref-sheets}{}%
-15. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
+19. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
 
 \leavevmode\hypertarget{ref-figeight}{}%
-16. (2019) The essential high-quality data annotation platform. Figure Eight
+20. (2019) The essential high-quality data annotation platform. Figure Eight
 
 \leavevmode\hypertarget{ref-RCore}{}%
-17. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+21. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
 
 \leavevmode\hypertarget{ref-lme4}{}%
-18. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
-
-\leavevmode\hypertarget{ref-taipan}{}%
-19. Kobakian S, O'Hara-Wild M (2018) Taipan: Tool for annotating images in preparation for analysis.
+22. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
 
 \leavevmode\hypertarget{ref-rmarkdown}{}%
-20. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida
+23. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida
 
 \leavevmode\hypertarget{ref-rticles}{}%
-21. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.
+24. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.
 
 \leavevmode\hypertarget{ref-knitr}{}%
-22. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research
+25. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research
 
 \leavevmode\hypertarget{ref-tidyverse}{}%
-23. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686
+26. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686
 
 \leavevmode\hypertarget{ref-nullabor}{}%
-24. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.
+27. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.
 
 \leavevmode\hypertarget{ref-ggthemes}{}%
-25. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.
+28. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.
 
 \leavevmode\hypertarget{ref-RColorBrewer}{}%
-26. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.
+29. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.
 
 \leavevmode\hypertarget{ref-cowplot}{}%
-27. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.
+30. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.
 
 \leavevmode\hypertarget{ref-png}{}%
-28. Urbanek S (2013) Png: Read and write png images.
+31. Urbanek S (2013) Png: Read and write png images.
 
 \leavevmode\hypertarget{ref-grid}{}%
-29. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+32. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
 
 \leavevmode\hypertarget{ref-kableExtra}{}%
-30. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
+33. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
 

### 2020-01-13 paper/paper.Rmd
draft generating lineups section

@@
 
-<!-- Spatially dependent data sets were simulated using the variogram model on the centroids of each geographic unit.
-Twelve simulations from the variogram model were created for each of the twelve lineups.
-
-The underlying spatial correlation model was created to provide spatial autocorrelation between neighboring areas using the longitude and latitude values for the Statistical Areas.
-
-$$z = 1$$
-$$locations = longitude + latitude$$
--->
-
 ## Generating lineups
 
-XXX Fill in this structure - see commented text
+<!-- Discuss simulating the trend data -->
+One map display in each lineup showed a real trend model. 
+To created this real data display different methods were applied for each trend type.
 
-<!-- Discuss simulating the trend data -->
+The North West to Soth East (NW-SE) distribution was based on the centroid longitude and latitude values, for each of the each geographic units.
+First, the difference was found between the minimum latitude and longitude of all centroids, and the values of all other centroids in the set of SA3 geographic units.
+Using this difference the following formula was applied: $ (-2*latitude) + longitude $.
+
+The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia.
+For each geographic unit, the distance to the closest capital city can be found when creating the hexagon tile map using the sugarbag [@sugarbag] package.
+There are large geographic differences between the centroids of inner-city areas and the rural outback areas. 
+To find the geographic units closest to the capital cities, the distance to the closest capital city was rescaled to the power of 8.
+The distances were then scaled between 0 and 1, where very small distance from the capital city were near 0, and the farthest centroid from any capital city was allocated the value of 1.
+The inner-city geographic units were considered those with a scaled distance of less than 0.85.
+
+A similar process was applied to the three cities' trend model. First a random sample of capital cities was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart.
+Only the three sample cities needed to have larger values in the trend model.
+
+The twelve sets of data were split into three trend model groups, four per group.
 
 <!-- Applying smoothing -->
-
-<!-- Scaling data within a lineup -->
-
-<!-- Location of data plot -->
 
@@
 
-Spatially dependent data sets were simulated using the variogram model on the centroids of each geographic unit.
-Twelve simulations from the variogram model were created for each of the twelve lineups.
+For each of the 144 individual maps, the values attributed to each geographic area are rescaled to show a similar color scale from deep blue to dark red within each map.
 
@@
 
-For each of the 144 individual maps, the values attributed to each geographic area are rescaled to show a similar color scale from deep blue to dark red within each map.
+<!-- Scaling data within a lineup -->
+This resulted in the smallest values of the trend model (blue) occurring in Western Australia, the North West of Australia, and the largest values of the trend model (red) occurring in the South East.
+This resulted in Tasmania being colored completely red.
+For the Three cities lineups, scaling was applied separately to the random values simulated for geographic units that were closest to the cities that were not included in the sample.
+This ensured that the minimum simulated value for every map had a dark blue color, and the maximum value was colored red.
+However, the geographic units that were close to the three cities selected were scaled to a larger maximum value so that their greatest values would appear red.
+
+<!-- Location of data plot -->
 
 A random location was selected for each set of lineup data.
-In this location, a trend model was overlaid on the null set of spatially correlated data.
-Each set of lineup data was used to produce a choropleth maps and hexagon tile maps. These matched pairs were split between Group A and Group B.
-
-For each lineup these statistics were calculated:
-
- - accuracy: the proportion of subjects who detected the data plot
- - efficiency: average time taken to respond
+In this location, the trend model for each lineup was overlaid on the null set of spatially correlated data.
+Each set of lineup data was used to produce a choropleth maps and hexagon tile maps.
+These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
 

### 2020-01-13 paper/paper.tex
draft generating lineups section

@@
 
-XXX Fill in this structure - see commented text
+One map display in each lineup showed a real trend model.
+To created this real data display different methods were applied for each trend type.
+
+The North West to Soth East (NW-SE) distribution was based on the centroid longitude and latitude values, for each of the each geographic units.
+First, the difference was found between the minimum latitude and longitude of all centroids, and the values of all other centroids in the set of SA3 geographic units.
+Using this difference the following formula was applied: \$ (-2*latitude) + longitude \$.
+
+The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia.
+For each geographic unit, the distance to the closest capital city can be found when creating the hexagon tile map using the sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]} package.
+There are large geographic differences between the centroids of inner-city areas and the rural outback areas.
+To find the geographic units closest to the capital cities, the distance to the closest capital city was rescaled to the power of 8.
+The distances were then scaled between 0 and 1, where very small distance from the capital city were near 0, and the farthest centroid from any capital city was allocated the value of 1.
+The inner-city geographic units were considered those with a scaled distance of less than 0.85.
+
+A similar process was applied to the three cities' trend model. First a random sample of capital cities was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart.
+Only the three sample cities needed to have larger values in the trend model.
+
+The twelve sets of data were split into three trend model groups, four per group.
 
@@
 
-For each of the 144 individual maps, the values attributed to each geographic area are rescaled to show a similar color scale from deep blue to dark red within each map.
+This resulted in the smallest values of the trend model (blue) occurring in Western Australia, the North West of Australia, and the largest values of the trend model (red) occurring in the South East.
+This resulted in Tasmania being colored completely red.
+For the Three cities lineups, scaling was applied separately to the random values simulated for geographic units that were closest to the cities that were not included in the sample.
+This ensured that the minimum simulated value for every map had a dark blue color, and the maximum value was colored red.
+However, the geographic units that were close to the three cities selected were scaled to a larger maximum value so that their greatest values would appear red.
 
 A random location was selected for each set of lineup data.
-In this location, a trend model was overlaid on the null set of spatially correlated data.
-Each set of lineup data was used to produce a choropleth maps and hexagon tile maps. These matched pairs were split between Group A and Group B.
-
-For each lineup these statistics were calculated:
-
-\begin{itemize}
-\tightlist
-\item
-  accuracy: the proportion of subjects who detected the data plot
-\item
-  efficiency: average time taken to respond
-\end{itemize}
+In this location, the trend model for each lineup was overlaid on the null set of spatially correlated data.
+Each set of lineup data was used to produce a choropleth maps and hexagon tile maps.
+These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
 
@@
 
-\newpage
-
 \hypertarget{acknowledgment}{%
@@
 \hypertarget{references}{%
-\section{References}\label{references}}
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
 

### 2020-01-14 paper/paper.Rmd
generating trend models

--- 2020-01-13 paper/paper.Rmd
@@
 
-<!-- Spatially dependent data sets were simulated using the variogram model on the centroids of each geographic unit.
-Twelve simulations from the variogram model were created for each of the twelve lineups.
+<!-- Applying smoothing -->
 
-The underlying spatial correlation model was created to provide spatial autocorrelation between neighboring areas using the longitude and latitude values for the Statistical Areas.
+The null model imposed by our hypothesis suggests that neighbors are related.
+The randomness induced when generating the null data was smoothed to mirror the practices of the Australian Cancer Atlas statisticians.
+In these 12 sets of data, each of the 144 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas, without implementing uncertainty via transparency.
 
-$$z = 1$$
-$$locations = longitude + latitude$$
--->
+A list of neighbors for each geographic unit was generated to use when smoothing the distributions.
+For each geographic unit the same spatial smoother was applied in each layer of smoothing.
+It kept half of the units' previous value, and derived the new half as the mean of the values of its neighbors at the previous layer of smoothing.
+
+This smoothing allowed neighbors to be related to each other, but allowed outliers, and showed distributions similar to the Liver cancer distribution shown in \ref{fig:liver}.
 
@@
 
-XXX Fill in this structure - see commented text
+<!-- Discuss simulating the trend data -->
+The real data display for each trend type was created by applying different methods to the centroid values of each geographic unit.
 
-<!-- Discuss simulating the trend data -->
+The North West to Soth East (NW-SE) distribution was based on the centroid longitude and latitude values.
+First,  the minimum latitude and longitude value of all centroids were found.
+Then the difference was found between the minimums, and the centroid values of all other centroids in the set of SA3 geographic units.
+The following formula was applied to the difference from the minimums: $ (-2*latitude) + longitude $.
 
-<!-- Applying smoothing -->
+The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia.
+For each geographic unit, the distance to the closest capital city can be found when creating the hexagon tile map using the sugarbag [@sugarbag] package.
+There are large geographic differences between the centroids of greater capital city areas and the rural outback areas. 
+To find the geographic units closest to the capital cities, the distance to the closest capital city was rescaled to the power of 8 to help differentiate between the smallest distances.
+The distances were then scaled between 0 and 1, where very small distance from the capital city were near 0, and the farthest centroid from any capital city were near to 1.
+The greater capital city geographic units were considered those with a scaled distance of less than 0.85, this resulted in 201 units considered "close".
+This was chosen to make red spots around the cities visible, even if they were not overtly noticeable in the choropleth display.
+
+A similar process was applied to the three cities' trend model.
+For each of the four replicates for the Three Cities trend, a random sample of capital cities was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart.
+The same process used for the All Cities trend was applied, but only to the areas nearest to the three cities in the sample for each of the four replicates. 
+For the Three cities lineups, scaling was applied separately to the values for geographic units that were and were not closest to the cities that were included in the sample.
+The geographic units that were close to the three cities selected were scaled to a larger maximum value so that their greatest values would appear red.
+
+<!-- Location of data plot -->
+
+One of the lineup map locations was randomly chosen to embed the real trend model data, in each of the four replicates, for the three trend models.
+In this location, real data display of the trend model was added to the null values of the spatially correlated data for each lineup.
 
@@
 
-<!-- Location of data plot -->
+For each of the 144 individual maps, the values attributed to each geographic area are rescaled to show a similar color scale from deep blue to dark red within each map.
+This allowed at least one geographic unit to be colour dark blue, and at least one to be red, in every map display of every lineup.
 
-The null model imposed suggests that neighbors are related.
-The randomness imposed was smoothed to mirror the practice taken by the Australian Cancer Atlas.
-This smoothing allowed neighbors to be related to each other and show distributions similar to the Liver cancer distribution shown in \ref{fig:liver}.
+For the geographic NW-SE distribution, this resulted in the smallest values of the trend model (blue) occurring in Western Australia, the North West of Australia, and the largest values of the trend model (red) occurring in the South East.
+This resulted in Tasmania being colored completely red.
 
-Spatially dependent data sets were simulated using the variogram model on the centroids of each geographic unit.
-Twelve simulations from the variogram model were created for each of the twelve lineups.
-
-In these 12 sets of data, each of the 144 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas.
-
-For each of the 144 individual maps, the values attributed to each geographic area are rescaled to show a similar color scale from deep blue to dark red within each map.
-
-A random location was selected for each set of lineup data.
-In this location, a trend model was overlaid on the null set of spatially correlated data.
-Each set of lineup data was used to produce a choropleth maps and hexagon tile maps. These matched pairs were split between Group A and Group B.
-
-For each lineup these statistics were calculated:
-
- - accuracy: the proportion of subjects who detected the data plot
- - efficiency: average time taken to respond
+Each set of lineup data was used to produce a choropleth maps and hexagon tile maps.
+These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
 
@@
 Potential participants needed to have achieved level 2 or level 3 from prior work.
-The participants were chosen as they have experience with survey tasks that involve evaluating images XXX Did we really choose participants this way??).
 All participants were at least 18 years old.
@@
 
-XXX Sentence on pilot study which allowed us to estimate the effect size, and thus decide on number of participants to collect responses from
+A pilot study was conducted in the working group of the Econometrics and Business Statistics Department of Monash University.
+This allowed us to estimate the effect size, and thus decide on number of participants to collect responses from.
+From the pilot study amount of participants needed to acheieve a 0.05 power level was determined to be
 

### 2020-01-14 paper/paper.tex
generating trend models

--- 2020-01-13 paper/paper.tex
@@
 
+The null model imposed by our hypothesis suggests that neighbors are related.
+The randomness induced when generating the null data was smoothed to mirror the practices of the Australian Cancer Atlas statisticians.
+In these 12 sets of data, each of the 144 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas, without implementing uncertainty via transparency.
+
+A list of neighbors for each geographic unit was generated to use when smoothing the distributions.
+For each geographic unit the same spatial smoother was applied in each layer of smoothing.
+It kept half of the units' previous value, and derived the new half as the mean of the values of its neighbors at the previous layer of smoothing.
+
+This smoothing allowed neighbors to be related to each other, but allowed outliers, and showed distributions similar to the Liver cancer distribution shown in \ref{fig:liver}.
+
 \hypertarget{generating-lineups}{%
@@
 
-XXX Fill in this structure - see commented text
-
-The null model imposed suggests that neighbors are related.
-The randomness imposed was smoothed to mirror the practice taken by the Australian Cancer Atlas.
-This smoothing allowed neighbors to be related to each other and show distributions similar to the Liver cancer distribution shown in \ref{fig:liver}.
-
-Spatially dependent data sets were simulated using the variogram model on the centroids of each geographic unit.
-Twelve simulations from the variogram model were created for each of the twelve lineups.
-
-In these 12 sets of data, each of the 144 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas.
+The real data display for each trend type was created by applying different methods to the centroid values of each geographic unit.
+
+The North West to Soth East (NW-SE) distribution was based on the centroid longitude and latitude values.
+First, the minimum latitude and longitude value of all centroids were found.
+Then the difference was found between the minimums, and the centroid values of all other centroids in the set of SA3 geographic units.
+The following formula was applied to the difference from the minimums: \$ (-2*latitude) + longitude \$.
+
+The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia.
+For each geographic unit, the distance to the closest capital city can be found when creating the hexagon tile map using the sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]} package.
+There are large geographic differences between the centroids of greater capital city areas and the rural outback areas.
+To find the geographic units closest to the capital cities, the distance to the closest capital city was rescaled to the power of 8 to help differentiate between the smallest distances.
+The distances were then scaled between 0 and 1, where very small distance from the capital city were near 0, and the farthest centroid from any capital city were near to 1.
+The greater capital city geographic units were considered those with a scaled distance of less than 0.85, this resulted in 201 units considered ``close''.
+This was chosen to make red spots around the cities visible, even if they were not overtly noticeable in the choropleth display.
+
+A similar process was applied to the three cities' trend model.
+For each of the four replicates for the Three Cities trend, a random sample of capital cities was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart.
+The same process used for the All Cities trend was applied, but only to the areas nearest to the three cities in the sample for each of the four replicates.
+For the Three cities lineups, scaling was applied separately to the values for geographic units that were and were not closest to the cities that were included in the sample.
+The geographic units that were close to the three cities selected were scaled to a larger maximum value so that their greatest values would appear red.
+
+One of the lineup map locations was randomly chosen to embed the real trend model data, in each of the four replicates, for the three trend models.
+In this location, real data display of the trend model was added to the null values of the spatially correlated data for each lineup.
 
 For each of the 144 individual maps, the values attributed to each geographic area are rescaled to show a similar color scale from deep blue to dark red within each map.
-
-A random location was selected for each set of lineup data.
-In this location, a trend model was overlaid on the null set of spatially correlated data.
-Each set of lineup data was used to produce a choropleth maps and hexagon tile maps. These matched pairs were split between Group A and Group B.
-
-For each lineup these statistics were calculated:
-
-\begin{itemize}
-\tightlist
-\item
-  accuracy: the proportion of subjects who detected the data plot
-\item
-  efficiency: average time taken to respond
-\end{itemize}
+This allowed at least one geographic unit to be colour dark blue, and at least one to be red, in every map display of every lineup.
+
+For the geographic NW-SE distribution, this resulted in the smallest values of the trend model (blue) occurring in Western Australia, the North West of Australia, and the largest values of the trend model (red) occurring in the South East.
+This resulted in Tasmania being colored completely red.
+
+Each set of lineup data was used to produce a choropleth maps and hexagon tile maps.
+These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
 

### 2020-01-14 paper/supplementary/lineups.Rmd
Discussion draft
lineups

@@
   # Downloaded data
-d <- read_xlsx("../data/experiment-export.xlsx", sheet=2) %>%
+d <- read_xlsx("data/experiment-export.xlsx", sheet=2) %>%
   filter(!is.na(contributor)) %>%
@@
 
-# All cities Example 1:
+# Lineups
+
+## North West - South East
 
@@
 
-Replicate 3 of the All Cities distribution is shown in Fig. \ref{fig:cities-geo4} and Fig. \ref{fig:cities-hex4}.
+## All Cities
 
-```{r cities-geo4, results = "asis", fig.cap = "The lineup of choropleth map displays hides a distribution that affects all capital cities."}
+### Replicate 1
+
+```{r cities-geo12, results = "asis", fig.cap = "The lineup of choropleth map displays, location 12 contains a distribution that affects all capital cities."}
 ggdraw() +
-  draw_plot(rasterGrob(readPNG("../figures/aus_cities_4_geo.png")))
+  draw_plot(rasterGrob(readPNG("lineups/aus_cities_12_geo.png")))
 ```
 
-```{r cities-hex4, results = "asis", fig.cap = "The lineup of choropleth map displays shows a distribution that affects all capital cities.
-The values for the inner city areas in the capital cities result in them being coloured red.
-However, the colour blue dominates the display as the large rural areas are filled.
-Replicate (2) for All Cities."}
+```{r cities-hex12, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 12 contains a distribution that affects all capital cities."}
 ggdraw() +
-  draw_plot(rasterGrob(readPNG("../figures/aus_cities_4_hex.png")))
+  draw_plot(rasterGrob(readPNG("lineups/aus_cities_12_hex.png")))
 ```
 
-# All Citites Example 2:
+### Replicate 2
 
-The higher values for the inner city areas in the capital cities result in them being coloured red.
-However, the colour blue dominates the display as the large rural areas are filled.
-There were no other choropleth maps that were coloured as blue as the map at location 3.
-This meant the detection rate was quite high, participants were able to select the correct distribution, even without being able to see the colours of inner-city areas of the capital cities.
-
-```{r cities-geo3, results = "asis", fig.cap = "The lineup of choropleth map displays hides a distribution that affects all capital cities."}
+```{r cities-geo3, results = "asis", fig.cap = "The lineup of choropleth map displays, location 3 contains a distribution that affects all capital cities."}
 ggdraw() +
-  draw_plot(rasterGrob(readPNG("../figures/aus_cities_3_geo.png")))
+  draw_plot(rasterGrob(readPNG("lineups/aus_cities_3_geo.png")))
 ```
 
-The same data showed in the hexagon tile map display shows varied distributions across the lineup.
-They are more diverse in colour than the choropleth counterparts.
-The same location, 3, holds the real data plot, the red city centres are now visible and surrounded by yellow, and then blue hexagons.
-For different reasons the participants were able to make the same correct choice for this replicate, with a detection rate of .
+```{r cities-hex3, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 3 contains a distribution that affects all capital cities."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_cities_3_hex.png")))
+```
 
-```{r cities-hex3, results = "asis", fig.cap = "The lineup of choropleth map displays shows a distribution that affects all capital cities.
-The values for the inner city areas in the capital cities result in them being coloured red.
-However, the colour blue dominates the display as the large rural areas are filled.
-Replicate (2) for All Cities."}
+### Replicate 3
+
+```{r cities-geo4, results = "asis", fig.cap = "The lineup of choropleth map displays, location 4 contains a distribution that affects all capital cities."}
 ggdraw() +
-  draw_plot(rasterGrob(readPNG("../figures/aus_cities_3_hex.png")))
+  draw_plot(rasterGrob(readPNG("lineups/aus_cities_4_geo.png")))
 ```
+
+```{r cities-hex4, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 4 contains a distribution that affects all capital cities."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_cities_4_hex.png")))
+```
+
+### Replicate 4
+
+```{r cities-geo9, results = "asis", fig.cap = "The lineup of choropleth map displays, location 9 contains a distribution that affects all capital cities."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_cities_9_geo.png")))
+```
+
+```{r cities-hex9, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 9 contains a distribution that affects all capital cities."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_cities_9_hex.png")))
+```
+
+## Three Cities
+
+### Replicate 1
+
+```{r three-geo12, results = "asis", fig.cap = "The lineup of choropleth map displays, location 12 contains a distribution that affects three of the Australian capital cities."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_three_12_geo.png")))
+```
+
+```{r three-hex12, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 12 contains a distribution that affects three of the Australian capital cities."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_three_12_hex.png")))
+```
+
+### Replicate 2
+
+```{r three-geo5, results = "asis", fig.cap = "The lineup of choropleth map displays, location 3 contains a distribution that affects three of the Australian capital cities."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_three_5_geo.png")))
+```
+
+```{r three-hex5, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 3 contains a distribution that affects three of the Australian capital cities."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_three_5_hex.png")))
+```
+
+### Replicate 3
+
+```{r three-geo8, results = "asis", fig.cap = "The lineup of choropleth map displays, location 4 contains a distribution that affects three of the Australian capital cities."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_three_8_geo.png")))
+```
+
+```{r three-hex8, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 4 contains a distribution that affects three of the Australian capital cities."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_three_8_hex.png")))
+```
+
+### Replicate 4
+
+```{r three-geo9, results = "asis", fig.cap = "The lineup of choropleth map displays, location 9 contains a distribution that affects three of the Australian capital cities."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_three_9_geo.png")))
+```
+
+```{r three-hex9, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 9 contains a distribution that affects three of the Australian capital cities."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_three_9_hex.png")))
+```
+
+## North West to South East Geographic Trend
+
+### Replicate 1
+
+```{r nwse-geo2, results = "asis", fig.cap = "The lineup of choropleth map displays, location 12 contains a distribution that affects all capital nwse."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_2_geo.png")))
+```
+
+```{r nwse-hex2, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 12 contains a distribution that affects all capital nwse."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_2_geo.png")))
+```
+
+### Replicate 2
+
+```{r nwse-geo3, results = "asis", fig.cap = "The lineup of choropleth map displays, location 3 contains a distribution that affects all capital nwse."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_3_geo.png")))
+```
+
+```{r nwse-hex3, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 3 contains a distribution that affects all capital nwse."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_3_geo.png")))
+```
+
+### Replicate 3
+
+```{r nwse-geo5, results = "asis", fig.cap = "The lineup of choropleth map displays, location 4 contains a distribution that affects all capital nwse."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_5_geo.png")))
+```
+
+```{r nwse-hex5, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 4 contains a distribution that affects all capital nwse."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_5_geo.png")))
+```
+
+### Replicate 4
+
+```{r nwse-geo6, results = "asis", fig.cap = "The lineup of choropleth map displays, location 9 contains a distribution that affects all capital nwse."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_6_geo.png")))
+```
+
+```{r nwse-hex6, results = "asis", fig.cap = "The lineup of hexagon tile map displays, location 9 contains a distribution that affects all capital nwse."}
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_6_geo.png")))
+```

### 2020-01-14 paper/paper.Rmd
rearrange

@@
 The results are summarized in Section [Results].
+
 Background
@@
 
-<!-- Specific problem for Australia 
-Australia is an extreme case of heterogeneous geographic units, with the large differences between the smallest and largest geographic units across various granularities.
-To communicate information regarding the small inner-city geographic units of Australian cities, an alternative display must be employed.
-This will emphasize the value of the statistic for areas with a high population.
-Fig.
-\ref{fig:liver} shows the distribution of the smoothed average amount of liver cancer diagnoses for Australian Males from 2005 to 2014.
-These inner-city areas are not visible on the choropleth map (a).
-The hexagon tile map (b) shows orange hexagons for the inner-city SA2s with higher than average levels of diagnoses in the capital cities of Melbourne and Sydney.
-The northern Queensland and Northern Territory SA2s with higher than average rates are still visible but use less map space on the hexagon tile map.
-There are still many light blue areas in both displays.
--->
-
 ## Visual Inference
@@
 The approach mirrors classical statistical inference.
-
-<!--We suggest the hexagon tile map as an alternative display.
-To test the effectiveness of these displays, there is a formal testing framework.
-Visual inference considers the communication of data or data summaries through visualizations.
-It considers these visualizations to be visual statistics, with observable features.
--->
 
@@
 
-<!-- The lineup protocol was formalized as a test for the effectiveness of a visualization.
-Rather than classical statistical tests, it tasks human participants with finding the display that shows structure between the variables.
-If they do not detect the structure, then it is not significantly different from the null data.
-
-Visual inference uses the general hypothesis structure:
-
- - Null hypothesis: There is \bf{no} relationship between the variables
- - Alternative hypothesis: There is a relationship between the variables
-
-To test these hypotheses, the line up protocol randomly places a "guilty" data visualization in a lineup of "innocents".
-Where the guilty data set contains structure, and the innocents data sets do not.
-In a grid of visualizations, an observer is asked to pick the display that is most different, if they select the data set containing structure, they have identified the guilty hidden within the  innocents [@GTPCCD].
-The participants identify the guilty data as different from the innocent data with probability $1/m$, where $m$ is the number of null plots plus 1 to account for the guilty data set.
-When the guilty data set is chosen we reject the null hypothesis that it was innocent is rejected with a $1/m$ chance or type I error of being wrong.
-
-The lineup protocol can be used in a variety of testing scenarios for visualizations.
-@GIIV suggest the choropleth map for testing spatial structure in a data set.
-The lineup protocol allows for flexibility in the definition of null data.
-In the case of spatial visualizations, it is likely that neighbors are related.
-To account for this, null data sets can be generated by sampling from a known model that accounts for spatial covariance.
-
-To contrast the effectiveness of two displays, we can produce null data plots with a hidden real data plot using the different plot designs.
-We can compare the time taken by participants to evaluate the same data in the different displays. We can also contrast the accuracy achieved by participants in detecting the real data plot.
--->
-
 Methodology
@@
 Australia is used for the study, with Statistical Area 2 (SA2) [@abs2016] as the geographic units. The results should apply broadly to any other geographic area of interest.
-
-<!--
-The mean of the detection rate for choropleth map, denoted as $\mu_C$, and the hexagon tile maps, $\mu_H$ will be contrasted. This leads to the following one sided hypothesis:
-
-$H_0$ : $\mu_H$ = $\mu_C$
-$H_a$ : $\mu_H$ > $\mu_C$
-
-The detection rate $\hat\pi$ is calculated as the amount of people that made the choice of plot that contained the real data, out of the participants who saw data plot in the lineup of the null data plots.
--->
 
@@
 
+Each set of lineup data was used to produce a choropleth map lineup and hexagon tile map lineup.
+These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
+
 <!-- Discuss simulating the trend data -->
-The real data display for each trend type was created by applying different methods to the centroid values of each geographic unit.
+For each trend model, the real data display was created by manipulating the centroid values of each geographic unit.
 
-The North West to Soth East (NW-SE) distribution was based on the centroid longitude and latitude values.
-First,  the minimum latitude and longitude value of all centroids were found.
-Then the difference was found between the minimums, and the centroid values of all other centroids in the set of SA3 geographic units.
-The following formula was applied to the difference from the minimums: $ (-2*latitude) + longitude $.
+The North West to South East (NW-SE) distribution was created using a linear equation of the centroid longitude and latitude values.
 
 The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia.
-For each geographic unit, the distance to the closest capital city can be found when creating the hexagon tile map using the sugarbag [@sugarbag] package.
-There are large geographic differences between the centroids of greater capital city areas and the rural outback areas. 
-To find the geographic units closest to the capital cities, the distance to the closest capital city was rescaled to the power of 8 to help differentiate between the smallest distances.
-The distances were then scaled between 0 and 1, where very small distance from the capital city were near 0, and the farthest centroid from any capital city were near to 1.
-The greater capital city geographic units were considered those with a scaled distance of less than 0.85, this resulted in 201 units considered "close".
-This was chosen to make red spots around the cities visible, even if they were not overtly noticeable in the choropleth display.
+The distance to the closest capital city for each geographic unit was found when creating the hexagon tile map using the sugarbag [@sugarbag] package.
+201 Statistical Areas were considered greater capital city areas, the values of these areas were increased to create red clusters.
+They were chosen to make clusters around the cities visible, even if they were not overtly noticeable in the choropleth display.
 
-A similar process was applied to the three cities' trend model.
-For each of the four replicates for the Three Cities trend, a random sample of capital cities was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart.
-The same process used for the All Cities trend was applied, but only to the areas nearest to the three cities in the sample for each of the four replicates. 
-For the Three cities lineups, scaling was applied separately to the values for geographic units that were and were not closest to the cities that were included in the sample.
-The geographic units that were close to the three cities selected were scaled to a larger maximum value so that their greatest values would appear red.
+A similar selection process was applied to the Three Cities' trend model.
+However, for each of the four replicates for the Three Cities trend, a random sample of capital cities was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart.
+Only values of the areas nearest to the three cities were increased to create clusters.
 
@@
 
-One of the lineup map locations was randomly chosen to embed the real trend model data, in each of the four replicates, for the three trend models.
+One of the lineup map locations was chosen to embed the real trend model data, in each of the four replicates, for the three trend models.
 In this location, real data display of the trend model was added to the null values of the spatially correlated data for each lineup.
+This location, the associated trend values and the null data were used to create both a choropleth and hexagon tile map display.
+The choropleth and hexagon lineups were split between group A and B, according to the experimental design shown in \ref{fig:exp-design}.
+The location was chosen from a sub sample of the 12 possible locations.
+The chance of reptition using resampling was introduced to prevent participants from inducing the location by elimination, the locations 1, 7, 10 and 11 were not used.
 
@@
 
-For each of the 144 individual maps, the values attributed to each geographic area are rescaled to show a similar color scale from deep blue to dark red within each map.
+For each of the 144 individual maps, the values attributed to each geographic area were rescaled to create a similar color scale from deep blue to dark red within each map.
 This allowed at least one geographic unit to be colour dark blue, and at least one to be red, in every map display of every lineup.
@@
 
-Each set of lineup data was used to produce a choropleth maps and hexagon tile maps.
-These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
+For the population related displays, the clusters in the cities appeared more red than the rest of Australia.
+
+## Analysis
+
+### Data Cleaning
+
+The first step in the data cleaning process involved checking that survey responses collected for each participants were only included once in the data set. 
+The data cleaning process also involved filtering out participants' who did not provide any choices when considering each of the twelve lineups.
+These participants achieved a detection rate of 0.
+If participants had made various plot choices for the 12 displays they saw they were still included in the dataset.
+
+### Descriptive statistics
+
+Mean, standard deviations for lineups, by participant, ...
+
+Side-by-side dot plots were made of accuracy (efficiency) against map type, faceted by trend model type.
+
+Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.
+
+Plots will be made in R (R Core Team 2019), with the ggplot2 package (Wickham 2016).
+
+### Modelling
+
+The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model. 
+The R [@RCore] `glmer()` function in the [@lme4] package implements generalised linear mixed effect models.
+The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
+
+$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij} + \epsilon_{i,j}, ~~~ i=1,2; ~j=1,2,3$$
+
+where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
+We are allowing for an interaction between map type and trend model.
+Because the response is binary, a logistic model is used.
+This model can account for each individual participants’ abilities as it includes a subject-specific random intercept.
+As each participant provides results from 12 lineups.
+
+The model specifies a logistic link, this means the predicted values from the `glmer` model should be back-transformed to fit between 0 and 1. They are transformed with the link specified below:
+
+$$\mu = \frac{e^{\eta}}{1 + e^{\eta}}$$ \label{eq:transform}
+$$\eta = f(\tau_i,\delta_j)$$
+
+The feedback and demographic variables will possibly be incorporated as covariates.
+
+Computation will be done using R [@RCore], with the `lme4` package [@lme4].
 
@@
  - efficiency: average time taken to respond
--->
-
-## Analysis
-
-### Descriptive statistics
-
-Mean, standard deviations for lineups, by participant, ...
-
-Side-by-side dot plots were made of accuracy (efficiency) against map type, faceted by trend model type.
-
-Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.
-
-Plots will be made in R (R Core Team 2019), with the ggplot2 package (Wickham 2016).
-
-### Modelling
-
-The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model. 
-The R [@RCore] `glmer()` function in the [@lme4] package implements generalised linear mixed effect models.
-The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
-
-$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij} + \epsilon_{i,j}, ~~~ i=1,2; ~j=1,2,3$$
-
-where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
-We are allowing for an interaction between map type and trend model.
-Because the response is binary, a logistic model is used.
-This model can account for each individual participants’ abilities as it includes a subject-specific random intercept.
-As each participant provides results from 12 lineups.
-
-The model specifies a logistic link, this means the predicted values from the `glmer` model should be back-transformed to fit between 0 and 1. They are transformed with the link specified below:
-
-$$\mu = \frac{e^{\eta}}{1 + e^{\eta}}$$ \label{eq:transform}
-$$\eta = f(\tau_i,\delta_j)$$
-
-The feedback and demographic variables will possibly be incorporated as covariates.
-
-Computation will be done using R [@RCore], with the `lme4` package [@lme4].
-
-### Data cleaning
-
-<!-- A pilot study was conducted to determine whether the lineups were appropriate.
-All lineups in the pilot study were deemed viable as at least one participant detected the real data plot in each lineup.
-The demographics of the participants showed a skew towards male participants. 
-The randomness of the group allocation also resulted in more participants being allocated to Group B.
-Due to the allocation of lineup displays the participants all saw six Choropleth displays and six Hexagon Tile Map displays.
 -->

### 2020-01-14 paper/paper.tex
rearrange

@@
 The results are summarized in Section \protect\hyperlink{results}{Results}.
-Background
-=============
+
+\hypertarget{background}{%
+\section{Background}\label{background}}
 
@@
 
-The real data display for each trend type was created by applying different methods to the centroid values of each geographic unit.
-
-The North West to Soth East (NW-SE) distribution was based on the centroid longitude and latitude values.
-First, the minimum latitude and longitude value of all centroids were found.
-Then the difference was found between the minimums, and the centroid values of all other centroids in the set of SA3 geographic units.
-The following formula was applied to the difference from the minimums: \$ (-2*latitude) + longitude \$.
+Each set of lineup data was used to produce a choropleth map lineup and hexagon tile map lineup.
+These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
+
+For each trend model, the real data display was created by manipulating the centroid values of each geographic unit.
+
+The North West to South East (NW-SE) distribution was created using a linear equation of the centroid longitude and latitude values.
 
 The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia.
-For each geographic unit, the distance to the closest capital city can be found when creating the hexagon tile map using the sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]} package.
-There are large geographic differences between the centroids of greater capital city areas and the rural outback areas.
-To find the geographic units closest to the capital cities, the distance to the closest capital city was rescaled to the power of 8 to help differentiate between the smallest distances.
-The distances were then scaled between 0 and 1, where very small distance from the capital city were near 0, and the farthest centroid from any capital city were near to 1.
-The greater capital city geographic units were considered those with a scaled distance of less than 0.85, this resulted in 201 units considered ``close''.
-This was chosen to make red spots around the cities visible, even if they were not overtly noticeable in the choropleth display.
-
-A similar process was applied to the three cities' trend model.
-For each of the four replicates for the Three Cities trend, a random sample of capital cities was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart.
-The same process used for the All Cities trend was applied, but only to the areas nearest to the three cities in the sample for each of the four replicates.
-For the Three cities lineups, scaling was applied separately to the values for geographic units that were and were not closest to the cities that were included in the sample.
-The geographic units that were close to the three cities selected were scaled to a larger maximum value so that their greatest values would appear red.
-
-One of the lineup map locations was randomly chosen to embed the real trend model data, in each of the four replicates, for the three trend models.
+The distance to the closest capital city for each geographic unit was found when creating the hexagon tile map using the sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]} package.
+201 Statistical Areas were considered greater capital city areas, the values of these areas were increased to create red clusters.
+They were chosen to make clusters around the cities visible, even if they were not overtly noticeable in the choropleth display.
+
+A similar selection process was applied to the Three Cities' trend model.
+However, for each of the four replicates for the Three Cities trend, a random sample of capital cities was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart.
+Only values of the areas nearest to the three cities were increased to create clusters.
+
+One of the lineup map locations was chosen to embed the real trend model data, in each of the four replicates, for the three trend models.
 In this location, real data display of the trend model was added to the null values of the spatially correlated data for each lineup.
-
-For each of the 144 individual maps, the values attributed to each geographic area are rescaled to show a similar color scale from deep blue to dark red within each map.
+This location, the associated trend values and the null data were used to create both a choropleth and hexagon tile map display.
+The choropleth and hexagon lineups were split between group A and B, according to the experimental design shown in \ref{fig:exp-design}.
+The location was chosen from a sub sample of the 12 possible locations.
+The chance of reptition using resampling was introduced to prevent participants from inducing the location by elimination, the locations 1, 7, 10 and 11 were not used.
+
+For each of the 144 individual maps, the values attributed to each geographic area were rescaled to create a similar color scale from deep blue to dark red within each map.
 This allowed at least one geographic unit to be colour dark blue, and at least one to be red, in every map display of every lineup.
@@
 
-Each set of lineup data was used to produce a choropleth maps and hexagon tile maps.
-These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
-
-\hypertarget{web-application-to-collect-responses}{%
-\subsection{Web application to collect responses}\label{web-application-to-collect-responses}}
-
-The taipan {[}\protect\hyperlink{ref-taipan}{18}{]} package for R was used to create the survey web application.
-This structure was altered to collect responses regarding participants demographics and their survey responses.
-The survey app contained three tabs, participants were first shown the demographics and consent page.
-This asked participants for their Figure-Eight contributor ID, and their consent to the responses being used for analysis.
-The demographics collected included participants' preferred pronoun, the highest level of education achieved, their age range and whether they had lived in Australia.
-
-After submitting these responses, the survey application switched to the tab of lineups and associated questions.
-This allowed participants to easily move through the twelve displays and provide their choice, reason for their choice, and level of certainty.
-
-When participants completed the twelve evaluations the survey application triggered a data analysis script.
-This created a data set with one row per evaluation.
-Along with the responses to the three questions, the script added the title of the image, which indicated the type of map display, the type of distribution hidden in the lineup, and the location of the data plot.
-It also calculated the time taken by participant to view each lineup.
-
-Each participant used the internet to access the survey.
-The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results.
-The application connected to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{19}{]} R package when participants opened the application, and interacted again when participants chosen to submit the survey and indicate their completion.
-At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-Participants were recruited to evaluate lineups from the Figure Eight crowdsourcing platform {[}\protect\hyperlink{ref-figeight}{20}{]}.
-The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
-Potential participants needed to have achieved level 2 or level 3 from prior work.
-All participants were at least 18 years old.
-
-Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure Eight website.
-There were 95 participants involved in the study.
-All participants read introductory materials, and was trained using three test displays, to orient them to the evaluation task.
-All participants who completed the task were compensated \$USD5 for their time, via the Figure Eight payment system.
-
-A pilot study was conducted in the working group of the Econometrics and Business Statistics Department of Monash University.
-This allowed us to estimate the effect size, and thus decide on number of participants to collect responses from.
-From the pilot study amount of participants needed to acheieve a 0.05 power level was determined to be
-
-\hypertarget{demographic-data-collection}{%
-\subsection{Demographic data collection}\label{demographic-data-collection}}
-
-The participant answered demographic questions and provided consent before evaluating the lineups.
-
-Demographics were collected regarding the study participants:
-
-\begin{itemize}
-\tightlist
-\item
-  Gender (female / male / other),
-\item
-  Degree education level achieved (high school / bachelors / masters / doctorate / other),
-\item
-  Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
-\item
-  Lived at least for one year in Australia (Yes / No )
-\end{itemize}
-
-Participants then moved to the evaluation phase.
-The set of images differed for Group A and Group B.
-After being allocated to a group, each individual was shown the 12 displays in randomised order.
-
-Three questions were asked regarding each display:
-
-\begin{itemize}
-\tightlist
-\item
-  Plot choice
-\item
-  Reason
-\item
-  Difficulty
-\end{itemize}
-
-After completing the 12 evaluations, the participants were asked to submit their responses.
+For the population related displays, the clusters in the cities appeared more red than the rest of Australia.
 
@@
 
+\hypertarget{data-cleaning}{%
+\subsubsection{Data Cleaning}\label{data-cleaning}}
+
+The first step in the data cleaning process involved checking that survey responses collected for each participants were only included once in the data set.
+The data cleaning process also involved filtering out participants' who did not provide any choices when considering each of the twelve lineups.
+These participants achieved a detection rate of 0.
+If participants had made various plot choices for the 12 displays they saw they were still included in the dataset.
+
 \hypertarget{descriptive-statistics}{%
@@
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R {[}\protect\hyperlink{ref-RCore}{21}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{22}{]} package implements generalised linear mixed effect models.
+The R {[}\protect\hyperlink{ref-RCore}{18}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{19}{]} package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 
-Computation will be done using R {[}\protect\hyperlink{ref-RCore}{21}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{22}{]}.
-
-\hypertarget{data-cleaning}{%
-\subsubsection{Data cleaning}\label{data-cleaning}}
+Computation will be done using R {[}\protect\hyperlink{ref-RCore}{18}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{19}{]}.
+
+\hypertarget{web-application-to-collect-responses}{%
+\subsection{Web application to collect responses}\label{web-application-to-collect-responses}}
+
+The taipan {[}\protect\hyperlink{ref-taipan}{20}{]} package for R was used to create the survey web application.
+This structure was altered to collect responses regarding participants demographics and their survey responses.
+The survey app contained three tabs, participants were first shown the demographics and consent page.
+This asked participants for their Figure-Eight contributor ID, and their consent to the responses being used for analysis.
+The demographics collected included participants' preferred pronoun, the highest level of education achieved, their age range and whether they had lived in Australia.
+
+After submitting these responses, the survey application switched to the tab of lineups and associated questions.
+This allowed participants to easily move through the twelve displays and provide their choice, reason for their choice, and level of certainty.
+
+When participants completed the twelve evaluations the survey application triggered a data analysis script.
+This created a data set with one row per evaluation.
+Along with the responses to the three questions, the script added the title of the image, which indicated the type of map display, the type of distribution hidden in the lineup, and the location of the data plot.
+It also calculated the time taken by participant to view each lineup.
+
+Each participant used the internet to access the survey.
+The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results.
+The application connected to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{21}{]} R package when participants opened the application, and interacted again when participants chosen to submit the survey and indicate their completion.
+At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.
+
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+Participants were recruited to evaluate lineups from the Figure Eight crowdsourcing platform {[}\protect\hyperlink{ref-figeight}{22}{]}.
+The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
+Potential participants needed to have achieved level 2 or level 3 from prior work.
+All participants were at least 18 years old.
+
+Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure Eight website.
+There were 95 participants involved in the study.
+All participants read introductory materials, and was trained using three test displays, to orient them to the evaluation task.
+All participants who completed the task were compensated \$USD5 for their time, via the Figure Eight payment system.
+
+A pilot study was conducted in the working group of the Econometrics and Business Statistics Department of Monash University.
+This allowed us to estimate the effect size, and thus decide on number of participants to collect responses from.
+From the pilot study amount of participants needed to acheieve a 0.05 power level was determined to be
+
+\hypertarget{demographic-data-collection}{%
+\subsection{Demographic data collection}\label{demographic-data-collection}}
+
+The participant answered demographic questions and provided consent before evaluating the lineups.
+
+Demographics were collected regarding the study participants:
+
+\begin{itemize}
+\tightlist
+\item
+  Gender (female / male / other),
+\item
+  Degree education level achieved (high school / bachelors / masters / doctorate / other),
+\item
+  Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
+\item
+  Lived at least for one year in Australia (Yes / No )
+\end{itemize}
+
+Participants then moved to the evaluation phase.
+The set of images differed for Group A and Group B.
+After being allocated to a group, each individual was shown the 12 displays in randomised order.
+
+Three questions were asked regarding each display:
+
+\begin{itemize}
+\tightlist
+\item
+  Plot choice
+\item
+  Reason
+\item
+  Difficulty
+\end{itemize}
+
+After completing the 12 evaluations, the participants were asked to submit their responses.
 
@@
 The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments.
-Mitchell O'Hara-Wild was a co-developer of the taipan {[}\protect\hyperlink{ref-taipan}{18}{]} R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
+Mitchell O'Hara-Wild was a co-developer of the taipan {[}\protect\hyperlink{ref-taipan}{20}{]} R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
 We are thankful for the NUMBATs (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.
@@
 
-The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{21}{]} with the use of the following packages:
+The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{18}{]} with the use of the following packages:
 
@@
 \item
-  For modelling and presentation of models: gstat {[}\protect\hyperlink{ref-gstat}{17}{]}, lme4 {[}\protect\hyperlink{ref-lme4}{22}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{33}{]}.
+  For modelling and presentation of models: gstat {[}\protect\hyperlink{ref-gstat}{17}{]}, lme4 {[}\protect\hyperlink{ref-lme4}{19}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{33}{]}.
 \end{itemize}
@@
 
+\leavevmode\hypertarget{ref-RCore}{}%
+18. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+
+\leavevmode\hypertarget{ref-lme4}{}%
+19. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
+
 \leavevmode\hypertarget{ref-taipan}{}%
-18. Kobakian S, O'Hara-Wild M (2018) Taipan: Tool for annotating images in preparation for analysis.
+20. Kobakian S, O'Hara-Wild M (2018) Taipan: Tool for annotating images in preparation for analysis.
 
 \leavevmode\hypertarget{ref-sheets}{}%
-19. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
+21. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
 
 \leavevmode\hypertarget{ref-figeight}{}%
-20. (2019) The essential high-quality data annotation platform. Figure Eight
-
-\leavevmode\hypertarget{ref-RCore}{}%
-21. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
-
-\leavevmode\hypertarget{ref-lme4}{}%
-22. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
+22. (2019) The essential high-quality data annotation platform. Figure Eight
 

### 2020-01-15 paper/paper.Rmd
suggestions by Earl

@@
 # Remove contributors who did not provide any choices
+# Or an insufficient amount of responses
 bad_contribs <- d %>% group_by(contributor) %>% 
   summarise(sum0 = sum(choice)) %>% 
-  filter(sum0 == 0) %>% 
+  filter(sum0 < 13) %>% 
   pull(contributor)
@@
 
-In order to assess the effectiveness of the hexagon tile map, the lineup protocol [@GIIV,@BCHLLSW09] from visual inference procedures is employed.
+In order to assess the effectiveness of the hexagon tile map, the lineup protocol [@GIIV],[@BCHLLSW09] from visual inference procedures is employed.
 The procedures for doing a power comparison of competing plot designed, outlined in @GTPCCD, are followed.
@@
 
-Mean, standard deviations for lineups, by participant, ...
+Basic descriptive statistics were used to contrast the detection rate for the two types of displays.
+This was extended to consider the trend models, contrasting the mean and standard detection rate for each group, who had seen the different map display type for each trend model.
 
@@
 
-Plots will be made in R (R Core Team 2019), with the ggplot2 package (Wickham 2016).
+Plots will be made in R [@R], with the \pkg{ggplot2} package [@ggplot2].
 
@@
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model. 
-The R [@RCore] `glmer()` function in the [@lme4] package implements generalised linear mixed effect models.
+The R [@RCore] `glmer()` function in the \pkg{lme4} [@lme4] package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 
-Computation will be done using R [@RCore], with the `lme4` package [@lme4].
+Computation was performed using R [@RCore], with the `lme4` package [@lme4].
 
@@
 Responses from 95 participants were collected.
-Three participants provided no answers for any task, and their data was removed.
+Five participants did not provide more than three answers for the twelve lineups, and their data was removed.
 Set A was evaluated by 42 participants, and 53 evaluated set B.
@@
 Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup.
-The points for the same data set shown in a choroleth or haxgon tile map display are linked to show the difference in the detection rate.", fig.height=4}
+The points for the same data set shown in a choroleth or hexagon tile map display are linked to show the difference in the detection rate.", fig.height=4}
 # Detectability rate for each lineup (image)
@@
 # Plot summary
-ggplot(d_smry, aes(x=type, y=pdetect, color = trend)) +
+ggplot(d_smry, aes(x = type, y = pdetect, color = trend)) +
   geom_point(size = 2) +  
@@
 This group of displays had a very small detection rate of 0.04.
-The mean detection rate for the Three Cities trend model shown as choropleth map lineups was also the smallest at 0.39.
+The mean detection rate for the Three Cities trend model shown as choropleth map lineups was also the smallest at 0.40.
 The North-West to South-East (NW-SE) trend model unexpectedly had a higher mean detection rate for the hexagon tile map displays, but the difference in the means of detection rate was only 0.10.
@@
 The results support the summary from Fig.
-\ref{fig:detect-compare} and all terms are statistically significant despite the large standard deviations observed in Table.
+\ref{fig:detect-compare} and all parameters are statistically significant despite the large standard deviations observed in Table.
 \ref{tab:desc-stats}.
@@
 The log odds of detection show in Table. \ref{tab:detect-glmer1} can be back transformed after taking the sum of all terms for the trend and type of display that are of interest.
-For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to `r round(exp(0.461+0.0220)/(1+exp(0.461+0.0220)), 2)` from `r round(exp(0.0220)/(1+exp(0.0220)),2)` for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
+For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to `r round(exp(0.46+0.07)/(1+exp(0.46+0.07)), 2)` from `r round(exp(0.07)/(1+exp(0.07)),2)` for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
 
-When a choropleth map display is used, the predicted detection rate for the Three Cities trend, `r round(exp(0.0220-3.43)/(1+exp(0.0220-3.43)),2)`; this is extremely low, especially compared to the NW-SE trend of `r round(exp(0.0220)/(1+exp(0.0220)),2)`.
-When the All Cities trend is presented in a choropleth display the predicted probability of detection is `r round(exp(0.0220-1.35)/(1+exp(0.0220-1.35)),2)`.
-The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend `r round(exp(0.461+0.0220-3.43+2.46)/(1+exp(0.461+0.0220-3.43+2.46)),2)` and All Cities trend `r round(exp(0.461+0.0220-1.35+1.17)/(1+exp(0.461+0.0220-1.35+1.17)),2)`.
+When a choropleth map display is used, the predicted detection rate for the Three Cities trend, `r round(exp(0.07-3.41)/(1+exp(0.07-3.41)),2)`; this is extremely low, especially compared to the NW-SE trend of `r round(exp(0.07)/(1+exp(0.07)),2)`.
+When the All Cities trend is presented in a choropleth display the predicted probability of detection is `r round(exp(0.07-1.34)/(1+exp(0.07-1.34)),2)`.
+The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend `r round(exp(0.46+0.07-3.41+2.44)/(1+exp(0.46+0.07-3.41+2.44)),2)` and All Cities trend `r round(exp(0.46+0.07-1.34+1.16)/(1+exp(0.46+0.07-1.34+1.16)),2)`.
 
@@
 
-glmer_terms <- c("Intercept", "Hex.", "Three Cities", "All Cities", "Hex:Three Cities", "Hex:All Cities")
+glmer_terms <- c("Intercept", "Hex.", "Three Cities", "All Cities",
+  "Hex:Three Cities", "Hex:All Cities")
 
@@
 
-ggplot(d %>% rename(Detected = detect_f), 
-   aes(x = certainty, fill = Detected)) +  
-  scale_fill_manual(values = detect_colors) +
+d %>% 
+  mutate(Detected = factor(detect_f, 
+    levels = c("Detected? Yes", "Detected? No"), 
+    labels = c("Yes", "No"))) %>% 
+ggplot(aes(x = certainty, fill = Detected)) +  
+  scale_fill_manual(values = detect_f_colors) +
   geom_bar() + facet_grid(type ~ trend) +
@@
 
-The reasons used when viewing choropleth displays varied more than the hexagon tile map reasons.
+The reasons chosen by participants from the list provided to them varied more when viewing choropleth displays than the hexagon tile map.
 The hexagon tile map displays resulted in "Clusters of color" as the most common choice made by participants.
@@
 The increasing population densities of capital cities despite large land area exacerbates the difference in the smallest and largest communities.
-The population density structure of Australia can be considered similar to that of Canada, New Zealand and many others.
+The population density structure of Australia can be considered similar to that of Canada, New Zealand and many other countries.
 Therefore, this display is not only relevant to Australia, but all nations or population distributions that experience densely populated cities separated by vast rural expanses.

### 2020-01-15 paper/paper.tex
suggestions by Earl

@@
 
-In order to assess the effectiveness of the hexagon tile map, the lineup protocol {[}\protect\hyperlink{ref-GIIV}{3}{]} from visual inference procedures is employed.
+In order to assess the effectiveness of the hexagon tile map, the lineup protocol {[}\protect\hyperlink{ref-GIIV}{3}{]},{[}\protect\hyperlink{ref-BCHLLSW09}{12}{]} from visual inference procedures is employed.
 The procedures for doing a power comparison of competing plot designed, outlined in {[}\protect\hyperlink{ref-GTPCCD}{13}{]}, are followed.
@@
 
-Mean, standard deviations for lineups, by participant, \ldots{}
+Basic descriptive statistics were used to contrast the detection rate for the two types of displays.
+This was extended to consider the trend models, contrasting the mean and standard detection rate for each group, who had seen the different map display type for each trend model.
 
@@
 
-Plots will be made in R (R Core Team 2019), with the ggplot2 package (Wickham 2016).
+Plots will be made in R {[}{\textbf{???}}{]}, with the \pkg{ggplot2} package {[}\protect\hyperlink{ref-ggplot2}{14}{]}.
 
@@
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R {[}\protect\hyperlink{ref-RCore}{18}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{19}{]} package implements generalised linear mixed effect models.
+The R {[}\protect\hyperlink{ref-RCore}{18}{]} \texttt{glmer()} function in the \pkg{lme4} {[}\protect\hyperlink{ref-lme4}{19}{]} package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 
-Computation will be done using R {[}\protect\hyperlink{ref-RCore}{18}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{19}{]}.
+Computation was performed using R {[}\protect\hyperlink{ref-RCore}{18}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{19}{]}.
 
@@
 Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup.
-The points for the same data set shown in a choroleth or haxgon tile map display are linked to show the difference in the detection rate.}
+The points for the same data set shown in a choroleth or hexagon tile map display are linked to show the difference in the detection rate.}
 \end{figure}
@@
 \midrule
-Choro. & 0.51 & 0.04 & 0.23\\
+Choro. & 0.52 & 0.04 & 0.23\\
  & (0.50) & (0.19) & (0.42)\\
 \addlinespace
-Hex. & 0.61 & 0.39 & 0.57\\
- & (0.49) & (0.49) & (0.50)\\
+Hex. & 0.62 & 0.4 & 0.58\\
+ & (0.49) & (0.49) & (0.49)\\
 \bottomrule
@@
 The log odds of detection show in Table. \ref{tab:detect-glmer1} can be back transformed after taking the sum of all terms for the trend and type of display that are of interest.
-For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to 0.62 from 0.51 for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
-
-When a choropleth map display is used, the predicted detection rate for the Three Cities trend, 0.03; this is extremely low, especially compared to the NW-SE trend of 0.51.
-When the All Cities trend is presented in a choropleth display the predicted probability of detection is 0.21.
-The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend 0.38 and All Cities trend 0.58.
+For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to 0.63 from 0.52 for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
+
+When a choropleth map display is used, the predicted detection rate for the Three Cities trend, 0.03; this is extremely low, especially compared to the NW-SE trend of 0.52.
+When the All Cities trend is presented in a choropleth display the predicted probability of detection is 0.22.
+The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend 0.39 and All Cities trend 0.59.
 
@@
 \midrule
-Intercept & 0.02 & $^{ }$ & 0.17 & 0.90\\
+Intercept & 0.07 & $^{ }$ & 0.16 & 0.67\\
 Hex. & 0.46 & $^{*}$ & 0.22 & 0.04\\
 \addlinespace
-Three Cities & -3.43 & $^{***}$ & 0.42 & 0.00\\
-All Cities & -1.35 & $^{***}$ & 0.24 & 0.00\\
+Three Cities & -3.41 & $^{***}$ & 0.42 & 0.00\\
+All Cities & -1.34 & $^{***}$ & 0.24 & 0.00\\
 \addlinespace
-Hex:Three Cities & 2.46 & $^{***}$ & 0.47 & 0.00\\
-Hex:All Cities & 1.17 & $^{***}$ & 0.33 & 0.00\\
+Hex:Three Cities & 2.44 & $^{***}$ & 0.47 & 0.00\\
+Hex:All Cities & 1.16 & $^{***}$ & 0.33 & 0.00\\
 \bottomrule
@@
 
-The reasons used when viewing choropleth displays varied more than the hexagon tile map reasons.
+The reasons chosen by participants from the list provided to them varied more when viewing choropleth displays than the hexagon tile map.
 The hexagon tile map displays resulted in ``Clusters of color'' as the most common choice made by participants.

### 2020-01-16 paper/paper.Rmd
captions

@@
   cache = FALSE,
-  dpi = 300)
+  dpi = 300,
+  out.width = "100%")
 ```
@@
 
-```{r liver, fig.height = 6, fig.width = 4, fig.cap = "A choropleth map (a), and hexagon tile map (b) of the smoothed average of liver cancer diagnoses for Australian males.
+```{r liver, fig.height = 4, fig.width = 4, fig.cap = "A choropleth map of the smoothed average of liver cancer diagnoses for Australian males.
 The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
 The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.", results = "asis"}
-ggdraw(ylim = c(0,2), xlim = c(0,1.3), clip = "on") +
-  draw_plot(rasterGrob(readPNG("figures/aus_liver_m.png")), -0.15, 0.9, 1.6, 1.2) +
-  draw_plot(rasterGrob(readPNG("figures/aus_liver_m_hex.png")), -0.15, -0.1, 1.6, 1.2) +
-  draw_plot_label(c("a", "b"), 
-    c(0.05, 0.05), c(1.95, 1), size = 20, color = "white") + 
-  theme(plot.background = element_rect(fill = "black"))
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("figures/aus_liver_m.png")))
+```
+
+```{r liver-hex, fig.height = 4, fig.width = 4, fig.cap = "A hexagon tile map of the smoothed average of liver cancer diagnoses for Australian males.
+The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
+The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.", results = "asis"}
+
+ggdraw() +
+  draw_plot(rasterGrob(readPNG("figures/aus_liver_m_hex.png")))
 ```
@@
 
-```{r exp-design, results = "asis", fig.width = 8, fig.height = 8}
+```{r exp-design, results = "asis", fig.width = 8, fig.height = 8, fig.cap = "The experimental design used in the visual inference study."}
 ggdraw(xlim = c(0,1), ylim = c(0,1)) + draw_plot(rasterGrob(png::readPNG("figures/experiment_design.png")))
@@
 
-Plots will be made in R [@R], with the \pkg{ggplot2} package [@ggplot2].
+Plots will be made in R [@RCore], with the `ggplot2` package [@ggplot2].
 
@@
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model. 
-The R [@RCore] `glmer()` function in the \pkg{lme4} [@lme4] package implements generalised linear mixed effect models.
+The R [@RCore] `glmer()` function in the `lme4` [@lme4] package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 \ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
-This also gives the standard errors, the smallest standard deviation for all sets of replicates is the Three Cities trend model shown in a Choropleth display.
+This also gives the standard errors, the smallest standard deviation for all sets of replicates was the Three Cities trend model shown in a Choropleth display.
 This group of displays had a very small detection rate of 0.04.
@@
     std.dev = round(sd(detect),2)) %>% 
-  mutate(std.dev = ifelse(std.dev == 0.5, "(0.50)", paste0("(", std.dev, ")"))) %>% 
-  gather(stat, value, m, std.dev) %>% 
+  mutate(std.dev = ifelse(std.dev == 0.5, "(0.50)", paste0("(", std.dev, ")"))) %>%   mutate(m = ifelse(m == 0.4, "(0.40)", paste0("(", std.dev, ")"))) %>%   gather(stat, value, m, std.dev) %>% 
   pivot_wider(names_from = "trend", values_from = "value") %>% 
@@
     linesep = c("", "\\addlinespace"),
-    caption = "The rate of detection for each trend model has been calculate for the choropleth and hexagon tile map displays. The associated standard errors are also included.")
+    caption = "The mean and standard deviation of the rate of detection for each trend model, calculated for the choropleth and hexagon tile map displays.")
 ```

### 2020-01-16 paper/paper.tex
captions

@@
 \usepackage{longtable,booktabs}
-\usepackage{graphicx}
-% We will generate all images so they have a width \maxwidth. This means
-% that they will get their normal width if they fit onto the page, but
-% are scaled down if they would overflow the margins.
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
-\else\Gin@nat@width\fi}
-\makeatother
-\let\Oldincludegraphics\includegraphics
-\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
 
@@
 
-\includegraphics{paper_files/figure-latex/liver-1.pdf}
+\begin{figure}
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/liver-1} \caption{A choropleth map of the smoothed average of liver cancer diagnoses for Australian males.
+The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
+The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.}\label{fig:liver}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/liver-hex-1} \caption{A hexagon tile map of the smoothed average of liver cancer diagnoses for Australian males.
+The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
+The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.}\label{fig:liver-hex}
+\end{figure}
 
@@
 \begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/lineup-1.pdf}
-\caption{\label{fig:lineup}This lineup of twelve hexagon tile map displays contains one map with a real population related structure.
-The rest are null plots that contain spatial correlation between neighbours.}
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/lineup-1} \caption{This lineup of twelve hexagon tile map displays contains one map with a real population related structure.
+The rest are null plots that contain spatial correlation between neighbours.}\label{fig:lineup}
 \end{figure}
@@
 
-\includegraphics{paper_files/figure-latex/exp-design-1.pdf}
+\begin{figure}
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/exp-design-1} \caption{The experimental design used in the visual inference study.}\label{fig:exp-design}
+\end{figure}
 
@@
 
-Plots will be made in R {[}{\textbf{???}}{]}, with the \pkg{ggplot2} package {[}\protect\hyperlink{ref-ggplot2}{14}{]}.
+Plots will be made in R {[}\protect\hyperlink{ref-RCore}{18}{]}, with the \texttt{ggplot2} package {[}\protect\hyperlink{ref-ggplot2}{14}{]}.
 
@@
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R {[}\protect\hyperlink{ref-RCore}{18}{]} \texttt{glmer()} function in the \pkg{lme4} {[}\protect\hyperlink{ref-lme4}{19}{]} package implements generalised linear mixed effect models.
+The R {[}\protect\hyperlink{ref-RCore}{18}{]} \texttt{glmer()} function in the \texttt{lme4} {[}\protect\hyperlink{ref-lme4}{19}{]} package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 \begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/detect-compare-1.pdf}
-\caption{\label{fig:detect-compare}The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models.
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/detect-compare-1} \caption{The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models.
 Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup.
-The points for the same data set shown in a choroleth or hexagon tile map display are linked to show the difference in the detection rate.}
+The points for the same data set shown in a choroleth or hexagon tile map display are linked to show the difference in the detection rate.}\label{fig:detect-compare}
 \end{figure}
@@
 \midrule
-Choro. & 0.52 & 0.04 & 0.23\\
+Choro. & ((0.50)) & ((0.19)) & ((0.42))\\
  & (0.50) & (0.19) & (0.42)\\
 \addlinespace
-Hex. & 0.62 & 0.4 & 0.58\\
+Hex. & ((0.49)) & (0.40) & ((0.49))\\
  & (0.49) & (0.49) & (0.49)\\
@@
 \begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/beeswarm-1.pdf}
-\caption{\label{fig:beeswarm}The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots.
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/beeswarm-1} \caption{The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots.
 The colored point indicates average time taken for each plot type.
-Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between plot types.}
+Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between plot types.}\label{fig:beeswarm}
 \end{figure}
@@
 \begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/certainty-1.pdf}
-\caption{\label{fig:certainty}The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/certainty-1} \caption{The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
 Participants were more likely to choose a high certainty when considering a Choropleth map.
-The mid value of 3 was the default certainty, it was chosen most for the Hexagon tile map displays.}
+The mid value of 3 was the default certainty, it was chosen most for the Hexagon tile map displays.}\label{fig:certainty}
 \end{figure}

### 2020-12-18 R/00_pilot.R
Thesis chapter version

@@ -21,6 +21,14 @@ sa3 <- absmapsdata::sa32016
 sa3 <- rmapshaper::ms_simplify(sa3, 
   keep = 0.5, keep_shapes = TRUE, explode = FALSE, drop_null_geometries = TRUE)
 
+sa3_neighbours <- sf::st_intersects(sa3$geometry,sa3$geometry)  %>% 
+  as_tibble() %>% 
+  filter(row.id != col.id) %>% 
+  rename(sa3neighbours = col.id) %>% 
+  group_by(row.id) %>% 
+  count(name = "sa3")
+
+
 # filter out Islands
 Islands <- c("Cocos (Keeling) Islands",	"Christmas Island", "Norfolk Island", "Lord Howe Island")
 sa3 <- sa3 %>% 
@@ -74,10 +82,21 @@ hexagons_sf <- hexagons %>%
   st_cast("POLYGON") %>%
   st_cast("MULTIPOLYGON")
 
-# Add hexagons to cen
+# Add hexagons to centroids
 hex <- left_join(hexagons_sf, sa3_centroids)
 
+hex_neighbours <- st_intersects(hex, hex) %>% 
+  as_tibble() %>% 
+  filter(row.id != col.id) %>% 
+  rename(hexneighbours = col.id) %>% 
+  group_by(row.id) %>% 
+  count(name = "hex") 
 
+# Compare neighbours of hexmap and geo 
+hex_neighbours <- hex_neighbours %>%
+  left_join(sa3_neighbours, by = "row.id") %>% 
+  mutate(diff = sa3 - hex)
+  
 ###########################################################
 ###########################################################
 ############ CREATE SPATIAL RELATIONSHIPS #################

### 2020-12-18 R/sa2_plots.R

@@ -1,0 +1,267 @@
+#sa2_plots
+
+#sa2_plots
+
+# Create a choropleth of Australia
+library(sugarbag)
+library(tidyverse)
+library(readxl)
+library(spData)
+library(ggthemes)
+library(maptools)
+library(sf)
+library(cartogram)
+library(cowplot)
+
+
+# Filter for centroids only within longitudes
+checkgeom <- function(x){
+  xval <- st_coordinates(x)[[2]]
+  
+  if (xval < 109){return(FALSE)}
+  if (xval > 155){return(FALSE)}
+  return(TRUE)
+}
+
+sa2 <- absmapsdata::sa22011 %>% 
+  filter(!st_is_empty(geometry)) %>%
+  filter(checkgeom(x = geometry))
+
+sa2 <- sa2 %>% 
+  rmapshaper::ms_simplify(keep = 0.05, keep_shapes = TRUE)
+
+# Join with cancer data from Australian Cancer Atlas
+
+SIR <- read_csv("data/SIR Downloadable Data.csv") %>% 
+  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
+  filter(Cancer_name == "Lung", Sex_name == "Persons")
+ERP <- read_csv("data/ABS_ERP_ASGS_26112019122253900.csv") %>%
+  filter(REGIONTYPE == "SA2", Time == 2011, Sex == "Persons", Region %in% SIR$SA2_name) %>% 
+  dplyr::select(Region, Value)
+
+
+# function to allocate colours to regions
+aus_colours <- function(sir_p50){
+  value <- case_when(
+    sir_p50 < 0.5 ~ "#33809d",
+    sir_p50 >= 0.5 & sir_p50 < 1 ~ "#aec6c7",
+    sir_p50 >= 1 & sir_p50 < 1.5 ~ "#fff4bc",
+    sir_p50 >= 1.5 & sir_p50 < 2 ~ "#ff9a64",
+    sir_p50 >= 2 ~ "#ff3500",
+    TRUE ~ "#FFFFFF")
+  return(value)
+}
+
+# Join with sa2 sf object
+sa2lung_ERP <- SIR %>% 
+  left_join(sa2, ., by = c("sa2_name_2011" = "SA2_name")) %>%
+  left_join(., ERP %>% dplyr::select(Region, 
+                                     Population = Value), by = c("sa2_name_2011"= "Region")) %>% 
[…]

### 2021-01-11 paper.Rmd
darker figures

--- 2020-01-16 paper/paper.Rmd
@@
 affiliation:
-  author-columnar: true         ## one column per author
-  #institution-columnar: true  ## one column per institution (multiple autors eventually)
+  #author-columnar: true         ## one column per author
+  institution-columnar: true  ## one column per institution (multiple autors eventually)
   # wide: true                  ## one column wide author/affiliation fields
@@
   The choropleth map display is commonly used for communicating spatial distributions across geographic areas.
-However, when choropleths are used, the sizes of areas can lead to the misinterpretation of the distribution.
-The visualization method used to present geospatial data will influence the understanding of the distribution derived by map users.
-Choosing an effective alternative display could positively influence the communication of the spatial distribution.
+However, when choropleths are used the size of the geographic units will influence the understanding of the distribution derived by map users.
 The hexagon tile map is presented as an alternative display for visualizing population related distributions effectively.
-Visual inference is used to measure the power of design, and the choropleth is used as a comparison.
-The hexagon tile map display is also tested using a distribution that is directly related to the geography, with values monotonically decreasing from the North-West to South-East areas of Australia.
-This study finds the single map in a hexagon tile map lineup that contains a population related distribution is detected with greater probability than the same data displayed in a choropleth map.
+Visual inference is used to measure the power of the hexagon tile map design, and the choropleth is used as a comparison.
+The hexagon tile map display is tested using a distribution that is directly related to the geography, with values monotonically increasing from the North-West to South-East areas of Australia.
+This study finds in a hexagon tile map lineup the single map that contains a population related distribution is detected with greater probability than the same data displayed in a choropleth map.
 These findings should encourage map creators to implement alternative displays and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
@@
 <!-- geographies on choropleth -->
-This study compares the effectiveness of a new type of display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics.
-The choropleth map is the traditional  approach for visualizing aggregated statistics across administrative boundaries.
+This study compares the effectiveness of the spatial display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics.
+The choropleth map is the traditional method for visualizing aggregated statistics across administrative boundaries.
+The hexagon tile map builds on existing displays, such as the cartogram, and tessellated hexagon displays.
 A hexagon tile map forgoes the familiar boundaries, in favor of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location.
-The hexagon tile map builds on existing displays, such as the cartogram, and tessellated hexagon displays.
-It differs in that it relaxes the requirement to have connected hexagons, and allows sparsely located hexagons.
+It differs in the relaxed requirement to have connected hexagons, and allows sparsely located hexagons.
+This type of display may be useful for other countries, and other purposes.
 The algorithm to construct a hexagon tile map is available in the R package sugarbag [@sugarbag].
-This type of display may be useful for other countries, and other purposes.
 
-The hexagon tile map was designed for Australia, motivated by a need to display spatial statistics for a new Australian Cancer Atlas.
+The hexagon tile map was designed for Australia, motivated by a need to display spatial statistics for the Australian Cancer Atlas.
 None of the existing approaches for creating cartograms or hexagon tiling perform well for the Australian landscape, which has vast open spaces and concentrations of population in small regions clustered on the coastlines.
@@
 It uses a choropleth map display and diverging color scheme to draw attention to relationships between neighboring areas.
-The hexagon tile map may be a useful alternative display for the atlas.
+The hexagon tile map may be a useful alternative display to enhance the atlas.
 
@@
 The next section discusses the background of geographic data display and visual inference procedures.
-The [Methodology] Section describes the methods for conducting the experiment and analysing the results.
-The results are summarized in Section [Results].
+The [Methodology] section describes the methods for conducting the experiment and analysing the results.
+The results are summarized in the [Results] section.
 
@@
 
-The choropleth map is effective if the size of the geographic units is relatively uniform.
+The choropleth map is an effective spatial display if the size of the geographic units is relatively uniform.
 This is not the case for most countries.
@@
 The algorithm is available in the R package, sugarbag [@sugarbag].
-Figure \ref{fig:liver} shows the hexagon tile map, along with the choropleth map of liver cancer rates in Australia.
+Fig.
+\ref{fig:liver} shows the hexagon tile map, along with the choropleth map of liver cancer rates in Australia.
 Colour maps from substantially below average (blue) to substantially above average (red) rates.
-The inner city areas are expanded out, making it possible to see the cancer incidence in the small, densely populated areas.
+The inner city areas have expanded, making it possible to see the cancer incidence in the small, densely populated areas.
 Remote regions are represented by isolated hexagons, which is not ideal, but maintains the spatial location of these data values.
@@
 In order to assess the effectiveness of the hexagon tile map, the lineup protocol [@GIIV],[@BCHLLSW09] from visual inference procedures is employed.
+The approach mirrors classical statistical inference.
 The procedures for doing a power comparison of competing plot designed, outlined in @GTPCCD, are followed.
-The approach mirrors classical statistical inference.
 
@@
 
-Australia is used for the study, with Statistical Area 2 (SA2) [@abs2016] as the geographic units. The results should apply broadly to any other geographic area of interest.
+Australia is used for the study, with Statistical Area 3 (SA3) [@abs2016] as the geographic units. The results should apply broadly to any other geographic area of interest.
 
@@
 Participants were randomly allocated to Group A or B.
-Participants saw a data set only once, with as a choropleth or as a hexagon tile map.
-Table \ref{fig:exp-design} summarises the design.
+Participants saw a data set only once, either as a choropleth or as a hexagon tile map.
+Table \ref{fig:exp-design} summarises the design and the allocation of the displays.
 
 ```{r exp-design, results = "asis", fig.width = 8, fig.height = 8, fig.cap = "The experimental design used in the visual inference study."}
-ggdraw(xlim = c(0,1), ylim = c(0,1)) + draw_plot(rasterGrob(png::readPNG("figures/experiment_design.png")))
+ggdraw(xlim = c(0,1), ylim = c(0,1)) + draw_plot(rasterGrob(png::readPNG("figures/exp design chart.png")))
 ```
@@
 This is too simple for spatial data.
-In spatial data, a key feature is smoothness over the landscape corresponding spatial dependence.
+In spatial data, a key feature is the spatial dependence or smoothness over the landscape.
 To do something simple, like permute the values relative to the geographic location would produce null plots which are too chaotic, and the data plot will be recognisable for its smoothness rather than any structure of interest.
@@
 The null model imposed by our hypothesis suggests that neighbors are related.
-The randomness induced when generating the null data was smoothed to mirror the practices of the Australian Cancer Atlas statisticians.
-In these 12 sets of data, each of the 144 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas, without implementing uncertainty via transparency.
+The randomness induced when generating the null data was smoothed to mirror the practices employed by the Australian Cancer Atlas statisticians.
+In these 12 sets of data, each of the 12 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas, without implementing uncertainty via transparency.
 
@@
 
-This smoothing allowed neighbors to be related to each other, but allowed outliers, and showed distributions similar to the Liver cancer distribution shown in \ref{fig:liver}.
+This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the Liver cancer distribution (Fig. \ref{fig:liver}).
 
@@
 
-Each set of lineup data was used to produce a choropleth map lineup and hexagon tile map lineup.
-These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
-
 <!-- Discuss simulating the trend data -->
-For each trend model, the real data display was created by manipulating the centroid values of each geographic unit.
+For each trend model, four real data displays were created by manipulating the centroid values of each of the SA3 geographic units.
 
@@
 
-The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia.
-The distance to the closest capital city for each geographic unit was found when creating the hexagon tile map using the sugarbag [@sugarbag] package.
-201 Statistical Areas were considered greater capital city areas, the values of these areas were increased to create red clusters.
-They were chosen to make clusters around the cities visible, even if they were not overtly noticeable in the choropleth display.
+The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia, calculated when creating the hexagon tile map using the sugarbag [@sugarbag] package.
+201 of the 336 SA3s were considered greater capital city areas, the values of these areas were increased to create red clusters.
+The amount was chosen to make clusters around the cities visible in the choropleth display even if they were not overtly noticeable.
 
@@
 
-One of the lineup map locations was chosen to embed the real trend model data, in each of the four replicates, for the three trend models.
-In this location, real data display of the trend model was added to the null values of the spatially correlated data for each lineup.
-This location, the associated trend values and the null data were used to create both a choropleth and hexagon tile map display.
-The choropleth and hexagon lineups were split between group A and B, according to the experimental design shown in \ref{fig:exp-design}.
+One of the lineup locations was chosen to embed the real trend model map, in each of the four replicates, for the three trend models.
 The location was chosen from a sub sample of the 12 possible locations.
@@
 
+As seen in Fig \ref{fig:exp-design}, the choropleth and hexagon display used the same location for the real data display of the trend model was added to the spatially correlated null values for each lineup.
+Each set of lineup data was used to produce a choropleth map lineup and hexagon tile map lineup.
+These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
+
 <!-- Scaling data within a lineup -->
 
-For each of the 144 individual maps, the values attributed to each geographic area were rescaled to create a similar color scale from deep blue to dark red within each map.
-This allowed at least one geographic unit to be colour dark blue, and at least one to be red, in every map display of every lineup.
+For each of the 144 individual maps, the values for each geographic area were rescaled to create a similar color scale from deep blue to dark red within each map.
+This meant at least one geographic unit was coloured dark blue, and at least one was red, in every map display of every lineup.
 
@@
 The first step in the data cleaning process involved checking that survey responses collected for each participants were only included once in the data set. 
-The data cleaning process also involved filtering out participants' who did not provide any choices when considering each of the twelve lineups.
+The data cleaning process also involved filtering out participants' who did not provide at least three unique choices when considering each of the twelve lineups.
 These participants achieved a detection rate of 0.
@@
 Basic descriptive statistics were used to contrast the detection rate for the two types of displays.
-This was extended to consider the trend models, contrasting the mean and standard detection rate for each group, who had seen the different map display type for each trend model.
+Comparison was also made across the trend models, contrasting the mean and standard detection rate for each group, who had seen the different map display type for each replicate.
 
@@
 
-where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
-We are allowing for an interaction between map type and trend model.
-Because the response is binary, a logistic model is used.
-This model can account for each individual participants’ abilities as it includes a subject-specific random intercept.
-As each participant provides results from 12 lineups.
+where $y_{ij} = 0, 1$ is the logg odds for whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
+We are allowing for an interaction between map type and trend model as the response is binary, so a logistic model was used.
+As each participant provides results from 12 lineups, this model can account for each individual participants’ abilities as it includes a subject-specific random intercept.
 
-The model specifies a logistic link, this means the predicted values from the `glmer` model should be back-transformed to fit between 0 and 1. They are transformed with the link specified below:
+The model specifies a logistic link, this means the predicted values from the `glmer` model should be back-transformed to fit between 0 and 1.
+The predictions  $\widehat{p}(\eta)$ are transformed to be probabilities between 0 and 1 with the link specified below:
 
-$$\mu = \frac{e^{\eta}}{1 + e^{\eta}}$$ \label{eq:transform}
+$$\widehat{p}(\eta) = \frac{e^{\eta}}{1 + e^{\eta}}$$ \label{eq:transform}
 $$\eta = f(\tau_i,\delta_j)$$
-
-The feedback and demographic variables will possibly be incorporated as covariates.
-
-Computation was performed using R [@RCore], with the `lme4` package [@lme4].
 
@@
 This structure was altered to collect responses regarding participants demographics and their survey responses.
-The survey app contained three tabs, participants were first shown the demographics and consent page.
-This asked participants for their Figure-Eight contributor ID, and their consent to the responses being used for analysis.
+The survey app contained three tabs.
+Participants were first asked for their demographics their Figure Eight contributor ID, and their consent to the responses being used for analysis.
 The demographics collected included participants' preferred pronoun, the highest level of education achieved, their age range and whether they had lived in Australia.
@@
 This created a data set with one row per evaluation.
-Along with the responses to the three questions, the script added the title of the image, which indicated the type of map display, the type of distribution hidden in the lineup, and the location of the data plot.
+Containing the responses to the three questions.
+The script also added the title of the image, which indicated the type of map display, the type of distribution hidden in the lineup, and the location of the data plot.
 It also calculated the time taken by participant to view each lineup.
@@
 The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results.
-The application connected to the googlesheet using the googlesheets [@sheets] R package when participants opened the application, and interacted again when participants chosen to submit the survey and indicate their completion.
+The application connected to the googlesheet using the googlesheets [@sheets] R package when participants opened the application, and interacted again when participants chose to submit the survey.
 At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.
@@
 
-Participants were recruited to evaluate lineups from the Figure Eight crowdsourcing platform [@figeight].
+Participants were recruited from the Figure Eight crowdsourcing platform [@figeight] to evaluate lineups.
 The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
-Potential participants needed to have achieved level 2 or level 3 from prior work.
+Potential participants needed to have achieved level 2 or level 3 from prior work on the platform.
 All participants were at least 18 years old.
 
-Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure Eight website.
-There were 95 participants involved in the study.
-All participants read introductory materials, and was trained using three test displays, to orient them to the evaluation task.
-All participants who completed the task were compensated $USD5 for their time, via the Figure Eight payment system.
+Participants were allocated to either group A or group B when they proceeded to the survey web application.
+There were 92 participants involved in the study.
+All participants read introductory materials, and were trained using three test displays, to orient them to the evaluation task.
+All participants who completed the task were compensated $AUD5 for their time, via the Figure Eight payment system.
 
@@
 This allowed us to estimate the effect size, and thus decide on number of participants to collect responses from.
-From the pilot study amount of participants needed to acheieve a 0.05 power level was determined to be
 
@@
 
-The participant answered demographic questions and provided consent before evaluating the lineups.
+Each participant answered demographic questions and provided consent before evaluating the lineups.
 
@@
  - Gender (female / male / other),
- - Degree education level achieved (high school / bachelors / masters / doctorate / other),
+ - Education level achieved (high school / bachelors / masters / doctorate / other),
  - Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
@@
 
-Responses from 95 participants were collected.
-Five participants did not provide more than three answers for the twelve lineups, and their data was removed.
+Responses from 92 participants were collected.
+Five participants did not provide more than three unique choices for the twelve lineups, and their data was removed.
 Set A was evaluated by 42 participants, and 53 evaluated set B.
-This resulted in 1104 evaluations, corresponding to 92 subjects, each evaluating 12 lineups, that are analysed on accuracy and speed.
+This resulted in 1104 evaluations, corresponding to 92 subjects, each evaluating 12 lineups, that were analysed on accuracy and speed.
 The certainty and reasons of subjects in their answers is also examined.
@@
 The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts.
-One replicate for the All Cities group, had similar detection rates for both plot type.
+One replicate for the All Cities group had similar detection rates for both plot types, the rate of detection using the choropleth map was much higher than other replicates.
 Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map.
@@
 Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup.
-The points for the same data set shown in a choroleth or hexagon tile map display are linked to show the difference in the detection rate.", fig.height=4}
+The points for the same data set shown in a choroleth or hexagon tile map display are linked to show the difference in the detection rate.", fig.height=5}
 # Detectability rate for each lineup (image)
@@
 \ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
-This also gives the standard errors, the smallest standard deviation for all sets of replicates was the Three Cities trend model shown in a Choropleth display.
+This also gives the standard deviations, the smallest standard deviation for all sets of replicates was the Three Cities trend model shown in a Choropleth display.
 This group of displays had a very small detection rate of 0.04.
@@
 d %>% group_by(type, trend) %>%
-  summarise(m = round(mean(detect),2),
-    std.dev = round(sd(detect),2)) %>% 
-  mutate(std.dev = ifelse(std.dev == 0.5, "(0.50)", paste0("(", std.dev, ")"))) %>%   mutate(m = ifelse(m == 0.4, "(0.40)", paste0("(", std.dev, ")"))) %>%   gather(stat, value, m, std.dev) %>% 
+  summarise(m = as.character(round(mean(detect), 2)),
+      std.dev = as.character(round(sd(detect), 2))) %>% 
+  mutate(std.dev = ifelse(std.dev == 0.5, "(0.50)", paste0("(", std.dev, ")"))) %>%   mutate(m = ifelse(m == 0.4, "0.40", m)) %>% 
+  gather(stat, value, m, std.dev) %>% 
   pivot_wider(names_from = "trend", values_from = "value") %>% 
@@
 
-detection_rates <- tidy(glmer1) %>%
+detection_rates <- broom.mixed::tidy(glmer1) %>%
   mutate(detection_rates = round(exp(estimate)/(1+exp(estimate)),2)) %>%
@@
 
-tidy(glmer1) %>%
+broom.mixed::tidy(glmer1) %>%
   mutate_at(.vars = c("estimate", "std.error"), round, 2) %>% 
@@
 assessment by the participant prompted by the question: ‘How certain are you about your choice?’.
-Figure.
-\ref{certainty} shows the amount of times participants provided each level of certainty.
+Fig.
+\ref{fig:certainty} shows the amount of times participants provided each level of certainty.
 This was separated for each combination of trend models and display type, and colored depending on whether a participant correctly detected the data plot in the lineup.
-Participants chose 4 or 5 often when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
+Participants often chose 4 or 5 when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
 This shows overconfidence in their detection ability when using a choropleth map display.
@@
 
-The differences seen in the compare detect plot and Table.
+The differences seen in the \ref{fig:detect-compare} plot and Table.
 \ref{tab:desc-stats} are reflected in the model results.
-Surprisingly the difference scene for the geographic distribution was significant at the 0.05 level.
+Surprisingly the difference for the geographic distribution was significant at the 0.05 level.
 It also showed that the hexagon tile map display performs marginally better than the choropleth for all trend models.
@@
 While the significance of the difference in detection was the key focus of this experiment, the secondary focus was the time taken by participants.
-it was expected that the disciplines may take longer to consider the hexagon tile map distribution but would be able to detect the data plot in the lineup.
-The bimodal distributions seen in the Fig.
-\ref{fig:beeswarm} display showed very little difference in the mean evaluation times.
-As the ranges of all of the distributions approached 60 seconds it cannot be said that the participants' took longer to evaluate the hexagon tile map displays.
+it was expected that the participants may take longer to consider the hexagon tile map distribution but would be able to detect the data plot in the lineup.
+The bimodal distributions seen in Fig.
+\ref{fig:beeswarm} showed very little difference in the mean evaluation times.
+As the maximum time of all of the distributions approached 60 seconds it cannot be said that the participants' took longer to evaluate the hexagon tile map displays.
 
@@
 Fig.
-\ref{fig:reason} shows high levels of certainty of 4 and 5 were chosen by participants when looking at the population distributions in a choropleth map display show that they were over confident when attempting to find the real data plot in the choropleth map displays.
+\ref{tab:reason} shows high levels of certainty of 4 and 5 were chosen by participants when looking at the population distributions in a choropleth map display show that they were over confident when attempting to find the real data plot in the choropleth map displays.
 Participants performed better on the NW-SE distribution shown in the choropleth display and were reasonably confident about their decisions.
@@
 The hexagon tile map display should be considered as an alternative visualization method when communicating distributions that relate to the population across a set of geographic units.
-As an additional display to the familiar choropleth map, Cancer Atlas products may benefit from the opportunity to allow exploration via an alternative display.
+As an additional display to the familiar choropleth map, cancer atlas products may benefit from the opportunity to allow exploration via an alternative display.
 The spatial distributions used to test these displays were inspired by the real spatially smoothed estimates of the cancer burden on Australian communities.

### 2021-01-11 paper.tex
darker figures

--- 2020-01-16 paper/paper.tex
@@
 
+% Pandoc citation processing
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+% for Pandoc 2.8 to 2.10.1
+\newenvironment{cslreferences}%
+  {}%
+  {\par}
+% For Pandoc 2.11+
+\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry sp
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set line spacing
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#3\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc} % for \widthof, \maxof
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
 % Pandoc header
@@
 %% ---- classic IEEETrans one column per institution --------
- %% -- end if/affiliation.institution-columnar
-%% ----------------------------------------------------------
-
-%% ---- one column per author, classic/default IEEETrans ----
- % -- beg affiliation.author-columnar
+ %% -- beg if/affiliation.institution-columnar
+\IEEEauthorblockN{
   %% -- beg for/affiliation.institution.author
-\IEEEauthorblockN{
-Stephanie Kobakian
+Stephanie Kobakian %% -- end for/affiliation.institution.author
 }
-\IEEEauthorblockA{Queensland University of Technology\\
-Science and Engineering Faculty\\
+\IEEEauthorblockA{Science and Engineering Faculty\\
+Queensland University of Technology\\
 Brisbane, Australia
@@
 }
- %% -- end for/affiliation.institution.author
 \and
+\IEEEauthorblockN{
   %% -- beg for/affiliation.institution.author
-\IEEEauthorblockN{
-Dianne Cook
+Dianne Cook %% -- end for/affiliation.institution.author
 }
-\IEEEauthorblockA{Monash University\\
-Econometrics and Business Statistics Faculty\\
+\IEEEauthorblockA{Econometrics and Business Statistics Faculty\\
+Monash University\\
 Melbourne, Australia
@@
 }
- %% -- end for/affiliation.institution.author
  %% -- end for/affiliation.institution
+ %% -- end if/affiliation.institution-columnar
+%% ----------------------------------------------------------
+
+%% ---- one column per author, classic/default IEEETrans ----
  %% -- end if/affiliation.institution-columnar
@@
 The choropleth map display is commonly used for communicating spatial distributions across geographic areas.
-However, when choropleths are used, the sizes of areas can lead to the misinterpretation of the distribution.
-The visualization method used to present geospatial data will influence the understanding of the distribution derived by map users.
-Choosing an effective alternative display could positively influence the communication of the spatial distribution.
+However, when choropleths are used the size of the geographic units will influence the understanding of the distribution derived by map users.
 The hexagon tile map is presented as an alternative display for visualizing population related distributions effectively.
-Visual inference is used to measure the power of design, and the choropleth is used as a comparison.
-The hexagon tile map display is also tested using a distribution that is directly related to the geography, with values monotonically decreasing from the North-West to South-East areas of Australia.
-This study finds the single map in a hexagon tile map lineup that contains a population related distribution is detected with greater probability than the same data displayed in a choropleth map.
+Visual inference is used to measure the power of the hexagon tile map design, and the choropleth is used as a comparison.
+The hexagon tile map display is tested using a distribution that is directly related to the geography, with values monotonically increasing from the North-West to South-East areas of Australia.
+This study finds in a hexagon tile map lineup the single map that contains a population related distribution is detected with greater probability than the same data displayed in a choropleth map.
 These findings should encourage map creators to implement alternative displays and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
@@
 
-This study compares the effectiveness of a new type of display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics.
-The choropleth map is the traditional approach for visualizing aggregated statistics across administrative boundaries.
+This study compares the effectiveness of the spatial display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics.
+The choropleth map is the traditional method for visualizing aggregated statistics across administrative boundaries.
+The hexagon tile map builds on existing displays, such as the cartogram, and tessellated hexagon displays.
 A hexagon tile map forgoes the familiar boundaries, in favor of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location.
-The hexagon tile map builds on existing displays, such as the cartogram, and tessellated hexagon displays.
-It differs in that it relaxes the requirement to have connected hexagons, and allows sparsely located hexagons.
+It differs in the relaxed requirement to have connected hexagons, and allows sparsely located hexagons.
+This type of display may be useful for other countries, and other purposes.
 The algorithm to construct a hexagon tile map is available in the R package sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]}.
-This type of display may be useful for other countries, and other purposes.
-
-The hexagon tile map was designed for Australia, motivated by a need to display spatial statistics for a new Australian Cancer Atlas.
+
+The hexagon tile map was designed for Australia, motivated by a need to display spatial statistics for the Australian Cancer Atlas.
 None of the existing approaches for creating cartograms or hexagon tiling perform well for the Australian landscape, which has vast open spaces and concentrations of population in small regions clustered on the coastlines.
@@
 The next section discusses the background of geographic data display and visual inference procedures.
-The \protect\hyperlink{methodology}{Methodology} Section describes the methods for conducting the experiment and analysing the results.
-The results are summarized in Section \protect\hyperlink{results}{Results}.
+The \protect\hyperlink{methodology}{Methodology} section describes the methods for conducting the experiment and analysing the results.
+The results are summarized in the \protect\hyperlink{results}{Results} section.
 
@@
 The algorithm is available in the R package, sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]}.
-Figure \ref{fig:liver} shows the hexagon tile map, along with the choropleth map of liver cancer rates in Australia.
+Fig.
+\ref{fig:liver} shows the hexagon tile map, along with the choropleth map of liver cancer rates in Australia.
 Colour maps from substantially below average (blue) to substantially above average (red) rates.
-The inner city areas are expanded out, making it possible to see the cancer incidence in the small, densely populated areas.
+The inner city areas have expanded, making it possible to see the cancer incidence in the small, densely populated areas.
 Remote regions are represented by isolated hexagons, which is not ideal, but maintains the spatial location of these data values.
@@
 In order to assess the effectiveness of the hexagon tile map, the lineup protocol {[}\protect\hyperlink{ref-GIIV}{3}{]},{[}\protect\hyperlink{ref-BCHLLSW09}{12}{]} from visual inference procedures is employed.
+The approach mirrors classical statistical inference.
 The procedures for doing a power comparison of competing plot designed, outlined in {[}\protect\hyperlink{ref-GTPCCD}{13}{]}, are followed.
-The approach mirrors classical statistical inference.
 
@@
 
-Australia is used for the study, with Statistical Area 2 (SA2) {[}\protect\hyperlink{ref-abs2016}{15}{]} as the geographic units.
+Australia is used for the study, with Statistical Area 3 (SA3) {[}\protect\hyperlink{ref-abs2016}{15}{]} as the geographic units.
 The results should apply broadly to any other geographic area of interest.
@@
 Participants were randomly allocated to Group A or B.
-Participants saw a data set only once, with as a choropleth or as a hexagon tile map.
-Table \ref{fig:exp-design} summarises the design.
+Participants saw a data set only once, either as a choropleth or as a hexagon tile map.
+Table \ref{fig:exp-design} summarises the design and the allocation of the displays.
 
@@
 
-Each set of lineup data was used to produce a choropleth map lineup and hexagon tile map lineup.
-These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
-
-For each trend model, the real data display was created by manipulating the centroid values of each geographic unit.
+For each trend model, four real data displays were created by manipulating the centroid values of each of the SA3 geographic units.
 
@@
 
-The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia.
-The distance to the closest capital city for each geographic unit was found when creating the hexagon tile map using the sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]} package.
-201 Statistical Areas were considered greater capital city areas, the values of these areas were increased to create red clusters.
-They were chosen to make clusters around the cities visible, even if they were not overtly noticeable in the choropleth display.
+The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia, calculated when creating the hexagon tile map using the sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]} package.
+201 of the 336 SA3s were considered greater capital city areas, the values of these areas were increased to create red clusters.
+The amount was chosen to make clusters around the cities visible in the choropleth display even if they were not overtly noticeable.
 
@@
 
-For each of the 144 individual maps, the values attributed to each geographic area were rescaled to create a similar color scale from deep blue to dark red within each map.
-This allowed at least one geographic unit to be colour dark blue, and at least one to be red, in every map display of every lineup.
+As seen in Fig \ref{fig:exp-design}, the choropleth and hexagon display used the same location for the real data display of the trend model was added to the spatially correlated null values for each lineup.
+Each set of lineup data was used to produce a choropleth map lineup and hexagon tile map lineup.
+These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
+
+For each of the 144 individual maps, the values for each geographic area were rescaled to create a similar color scale from deep blue to dark red within each map.
+This meant at least one geographic unit was coloured dark blue, and at least one was red, in every map display of every lineup.
 
@@
 The first step in the data cleaning process involved checking that survey responses collected for each participants were only included once in the data set.
-The data cleaning process also involved filtering out participants' who did not provide any choices when considering each of the twelve lineups.
+The data cleaning process also involved filtering out participants' who did not provide at least three unique choices when considering each of the twelve lineups.
 These participants achieved a detection rate of 0.
@@
 
-where \(y_{ij} = 0, 1\) whether the subject detected the data plot, \(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect, \(\delta_j\) is the trend model effect.
-We are allowing for an interaction between map type and trend model.
-Because the response is binary, a logistic model is used.
-This model can account for each individual participants' abilities as it includes a subject-specific random intercept.
-As each participant provides results from 12 lineups.
+where \(y_{ij} = 0, 1\) is the logg odds for whether the subject detected the data plot, \(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect, \(\delta_j\) is the trend model effect.
+We are allowing for an interaction between map type and trend model as the response is binary, so a logistic model was used.
+As each participant provides results from 12 lineups, this model can account for each individual participants' abilities as it includes a subject-specific random intercept.
 
 The model specifies a logistic link, this means the predicted values from the \texttt{glmer} model should be back-transformed to fit between 0 and 1.
-They are transformed with the link specified below:
-
-\[\mu = \frac{e^{\eta}}{1 + e^{\eta}}\] \label{eq:transform}
+The predictions \(\widehat{p}(\eta)\) are transformed to be probabilities between 0 and 1 with the link specified below:
+
+\[\widehat{p}(\eta) = \frac{e^{\eta}}{1 + e^{\eta}}\] \label{eq:transform}
 \[\eta = f(\tau_i,\delta_j)\]
-
-The feedback and demographic variables will possibly be incorporated as covariates.
-
-Computation was performed using R {[}\protect\hyperlink{ref-RCore}{18}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{19}{]}.
 
@@
 The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results.
-The application connected to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{21}{]} R package when participants opened the application, and interacted again when participants chosen to submit the survey and indicate their completion.
+The application connected to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{21}{]} R package when participants opened the application, and interacted again when participants chose to submit the survey.
 At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.
@@
 
-Participants were recruited to evaluate lineups from the Figure Eight crowdsourcing platform {[}\protect\hyperlink{ref-figeight}{22}{]}.
+Participants were recruited from the Figure Eight crowdsourcing platform {[}\protect\hyperlink{ref-figeight}{22}{]} to evaluate lineups.
 The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
-Potential participants needed to have achieved level 2 or level 3 from prior work.
+Potential participants needed to have achieved level 2 or level 3 from prior work on the platform.
 All participants were at least 18 years old.
 
-Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure Eight website.
-There were 95 participants involved in the study.
-All participants read introductory materials, and was trained using three test displays, to orient them to the evaluation task.
-All participants who completed the task were compensated \$USD5 for their time, via the Figure Eight payment system.
+Participants were allocated to either group A or group B when they proceeded to the survey web application.
+There were 92 participants involved in the study.
+All participants read introductory materials, and were trained using three test displays, to orient them to the evaluation task.
+All participants who completed the task were compensated \$AUD5 for their time, via the Figure Eight payment system.
 
@@
 \item
-  Degree education level achieved (high school / bachelors / masters / doctorate / other),
+  Education level achieved (high school / bachelors / masters / doctorate / other),
 \item
@@
 
-\caption{\label{tab:desc-stats}The rate of detection for each trend model has been calculate for the choropleth and hexagon tile map displays. The associated standard errors are also included.}
+\caption{\label{tab:desc-stats}The mean and standard deviation of the rate of detection for each trend model, calculated for the choropleth and hexagon tile map displays.}
 \centering
@@
 \midrule
-Choro. & ((0.50)) & ((0.19)) & ((0.42))\\
+Choro. & 0.52 & 0.04 & 0.23\\
  & (0.50) & (0.19) & (0.42)\\
 \addlinespace
-Hex. & ((0.49)) & (0.40) & ((0.49))\\
+Hex. & 0.62 & 0.40 & 0.58\\
  & (0.49) & (0.49) & (0.49)\\
@@
 Unlike the accuracy and speed of responses that were derived during the data processing phase, this was a subjective
-assessment by the participant prompted by the question: `How certain are you about your choice?'.
-Figure.
-\ref{certainty} shows the amount of times participants provided each level of certainty.
+assessment by the participant prompted by the question: `How certain are you about your choice?'
+Fig.
+\ref{fig:certainty} shows the amount of times participants provided each level of certainty.
 This was separated for each combination of trend models and display type, and colored depending on whether a participant correctly detected the data plot in the lineup.
-Participants chose 4 or 5 often when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
+Participants often chose 4 or 5 when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
 This shows overconfidence in their detection ability when using a choropleth map display.
@@
 \hypertarget{refs}{}
+\begin{CSLReferences}{0}{0}
 \leavevmode\hypertarget{ref-sugarbag}{}%
-1. Kobakian S, Cook D (2019) Sugarbag: Create tessellated hexagon maps.
+\CSLLeftMargin{1. }
+\CSLRightInline{Kobakian S, Cook D (2019) Sugarbag: Create tessellated hexagon maps. }
 
 \leavevmode\hypertarget{ref-atlas}{}%
-2. Queensland CC Australian Cancer Atlas (https://atlas.cancer.org.au).
+\CSLLeftMargin{2. }
+\CSLRightInline{Cancer Council Queensland {Australian Cancer Atlas (https://atlas.cancer.org.au)}. }
 
 \leavevmode\hypertarget{ref-GIIV}{}%
-3. Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979
+\CSLLeftMargin{3. }
+\CSLRightInline{Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979}
 
 \leavevmode\hypertarget{ref-EI}{}%
-4. Tufte ER (1990) Envisioning Information. Graphics Press
+\CSLLeftMargin{4. }
+\CSLRightInline{Tufte ER (1990) {Envisioning Information}. Graphics Press}
 
 \leavevmode\hypertarget{ref-BCM}{}%
-5.
-Skowronnek A (2016) Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata.
-In: Infovis Reading Group WS 2015/16.
+\CSLLeftMargin{5. }
+\CSLRightInline{Skowronnek A (2016) {Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata}.
+In: {Infovis Reading Group WS 2015/16}.
 \url{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}.
+}
 
 \leavevmode\hypertarget{ref-CBATCC}{}%
-6. Kocmoud C, House D (1998) A Constraint-based Approach to Constructing Continuous Cartograms. In: Proc. Symp. Spatial data handling. pp 236--246
+\CSLLeftMargin{6. }
+\CSLRightInline{Kocmoud C, House D (1998) {A Constraint-based Approach to Constructing Continuous Cartograms}. In: Proc. Symp. Spatial data handling. pp 236--246}
 
 \leavevmode\hypertarget{ref-ACTUC}{}%
-7. Dorling D (2011) Area Cartograms: Their Use and Creation. In: Concepts and techniques in modern geography (catmog). pp 252--260
+\CSLLeftMargin{7. }
+\CSLRightInline{Dorling D (2011) {Area Cartograms: Their Use and Creation}. In: Concepts and techniques in modern geography (CATMOG). pp 252--260}
 
 \leavevmode\hypertarget{ref-NAC}{}%
-8. Olson JM (1976) Noncontiguous Area Cartograms. The Professional Geographer 28:371--380
+\CSLLeftMargin{8. }
+\CSLRightInline{Olson JM (1976) {Noncontiguous Area Cartograms}. The Professional Geographer 28:371--380}
 
 \leavevmode\hypertarget{ref-RSCW}{}%
-9. Raisz E (1963) Rectangular Statistical Cartograms of the World. Journal of Geography 35:8--10
+\CSLLeftMargin{9. }
+\CSLRightInline{Raisz E (1963) {Rectangular Statistical Cartograms of the World}. Journal of Geography 35:8--10}
 
 \leavevmode\hypertarget{ref-CDWCS}{}%
-10. Monmonier M (2005) Cartography: Distortions, World-views and Creative Solutions. Progress in Human Geography 29:217--224
+\CSLLeftMargin{10. }
+\CSLRightInline{Monmonier M (2005) {Cartography: Distortions, World-views and Creative Solutions}. Progress in Human Geography 29:217--224}
 
 \leavevmode\hypertarget{ref-review}{}%
-11. (2019) Cancer applications of choropleth maps, and the potential of cartograms and alternative map displays. Manuscript submitted for publication.
+\CSLLeftMargin{11. }
+\CSLRightInline{(2019) Cancer applications of choropleth maps, and the potential of cartograms and alternative map displays. Manuscript submitted for publication. }
 
 \leavevmode\hypertarget{ref-BCHLLSW09}{}%
-12.
-Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) Statistical inference for exploratory data analysis and model diagnostics.
-Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383
+\CSLLeftMargin{12. }
+\CSLRightInline{Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) Statistical inference for exploratory data analysis and model diagnostics.
+Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383}
 
 \leavevmode\hypertarget{ref-GTPCCD}{}%
-13. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448
+\CSLLeftMargin{13. }
+\CSLRightInline{Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448}
 
 \leavevmode\hypertarget{ref-ggplot2}{}%
-14. Wickham H (2009) Ggplot2: Elegant graphics for data analysis. Springer New York
+\CSLLeftMargin{14. }
+\CSLRightInline{Wickham H (2009) ggplot2: Elegant graphics for data analysis. Springer New York}
 
 \leavevmode\hypertarget{ref-abs2016}{}%
-15. (2018) Australian Statistical Geography Standard (ASGS). Australian Bureau of Statistics
+\CSLLeftMargin{15. }
+\CSLRightInline{(2018) {Australian Statistical Geography Standard (ASGS)}. Australian Bureau of Statistics }
 
 \leavevmode\hypertarget{ref-POG}{}%
-16. Matheron G (1963) Principles of geostatistics. Economic Geology 58:1246--1266
+\CSLLeftMargin{16. }
+\CSLRightInline{Matheron G (1963) Principles of geostatistics. Economic Geology 58:1246--1266}
 
 \leavevmode\hypertarget{ref-gstat}{}%
-17. Gräler B, Pebesma E, Heuvelink G (2016) Spatio-temporal interpolation using gstat. The R Journal 8:204--218
+\CSLLeftMargin{17. }
+\CSLRightInline{Gräler B, Pebesma E, Heuvelink G (2016) Spatio-temporal interpolation using gstat. The R Journal 8:204--218}
 
 \leavevmode\hypertarget{ref-RCore}{}%
-18. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+\CSLLeftMargin{18. }
+\CSLRightInline{R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria}
 
 \leavevmode\hypertarget{ref-lme4}{}%
-19. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
+\CSLLeftMargin{19. }
+\CSLRightInline{Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using {lme4}. Journal of Statistical Software 67:1--48}
 
 \leavevmode\hypertarget{ref-taipan}{}%
-20. Kobakian S, O'Hara-Wild M (2018) Taipan: Tool for annotating images in preparation for analysis.
+\CSLLeftMargin{20. }
+\CSLRightInline{Kobakian S, O'Hara-Wild M (2018) Taipan: Tool for annotating images in preparation for analysis. }
 
 \leavevmode\hypertarget{ref-sheets}{}%
-21. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
+\CSLLeftMargin{21. }
+\CSLRightInline{Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r. }
 
 \leavevmode\hypertarget{ref-figeight}{}%
-22. (2019) The essential high-quality data annotation platform. Figure Eight
+\CSLLeftMargin{22. }
+\CSLRightInline{(2019) The essential high-quality data annotation platform. Figure Eight }
 
 \leavevmode\hypertarget{ref-rmarkdown}{}%
-23. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida
+\CSLLeftMargin{23. }
+\CSLRightInline{Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida}
 
 \leavevmode\hypertarget{ref-rticles}{}%
-24. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.
+\CSLLeftMargin{24. }
+\CSLRightInline{Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown. }
 
 \leavevmode\hypertarget{ref-knitr}{}%
-25. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research
+\CSLLeftMargin{25. }
+\CSLRightInline{Xie Y (2014) Knitr: A comprehensive tool for reproducible research in {R}. Implementing reproducible computational research }
 
 \leavevmode\hypertarget{ref-tidyverse}{}%
-26. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686
+\CSLLeftMargin{26. }
+\CSLRightInline{Wickham H, Averick M, Bryan J, et al (2019) Welcome to the {tidyverse}. Journal of Open Source Software 4:1686}
 
 \leavevmode\hypertarget{ref-nullabor}{}%
-27. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.
+\CSLLeftMargin{27. }
+\CSLRightInline{Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference. }
 
 \leavevmode\hypertarget{ref-ggthemes}{}%
-28. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.
+\CSLLeftMargin{28. }
+\CSLRightInline{Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'. }
 
 \leavevmode\hypertarget{ref-RColorBrewer}{}%
-29. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.
+\CSLLeftMargin{29. }
+\CSLRightInline{Neuwirth E (2014) RColorBrewer: ColorBrewer palettes. }
 
 \leavevmode\hypertarget{ref-cowplot}{}%
-30. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.
+\CSLLeftMargin{30. }
+\CSLRightInline{Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'. }
 
 \leavevmode\hypertarget{ref-png}{}%
-31. Urbanek S (2013) Png: Read and write png images.
+\CSLLeftMargin{31. }
+\CSLRightInline{Urbanek S (2013) Png: Read and write PNG images. }
 
 \leavevmode\hypertarget{ref-grid}{}%
-32. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
+\CSLLeftMargin{32. }
+\CSLRightInline{R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria}
 
 \leavevmode\hypertarget{ref-kableExtra}{}%
-33. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
+\CSLLeftMargin{33. }
+\CSLRightInline{Zhu H (2019) kableExtra: Construct complex table with 'kable' and pipe syntax. }
+
+\end{CSLReferences}
 

### 2021-01-11 supplementary/lineups.Rmd
darker figures

--- 2020-01-14 paper/supplementary/lineups.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.path = "alldisplays/")
 ```
@@
 ggdraw() +
-  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_2_geo.png")))
+  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_2_hex.png")))
 ```
@@
 ggdraw() +
-  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_3_geo.png")))
+  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_3_hex.png")))
 ```
@@
 ggdraw() +
-  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_5_geo.png")))
+  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_5_hex.png")))
 ```
@@
 ggdraw() +
-  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_6_geo.png")))
+  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_6_hex.png")))
 ```

### 2021-01-11 survey/survey.Rmd
darker figures

--- 2019-12-19 survey/survey.Rmd
@@
 ---
-title: "Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference with crowdsourcing?"
+title: Visual Inference Test of the Hexagon Tile Map for Spatial Distributions
 affiliation:
@@
   # wide: true                  ## one column wide author/affiliation fields
+
   institution:
@@
   On multiple lines eventually.
-dev: png
+
 bibliography: mybibfile.bib
@@
 ---
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-  echo = FALSE,
-  warning = FALSE,
-  error = FALSE, 
-  message = FALSE)
-```
 
@@
 
+## Population focussed displays
+
+Map creators have the ability to present spatial statistics in alternative displays that can highlight the population.
+This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
+The same data will be shown on a choropleth map, and on a hexagon tile map.
+Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.
+
+Methodology
+============
+
+    Described the methods used to undertake the research including details of
+
+This methodology section explains the various aspects of the research:
+
+1. The overall structure of the research
+
+A survey was created to test the effectiveness of the hexagon tile map display.
+
+The online crowdsource platform Figure-Eight was used to recruit participants.   
+Each participant saw three test displays orienting them to the task.
+They then took an online survey evaluating 12 displays.
+A line up protocol was implemented to arrange 12 maps in each display. 
+Individual displays were created by a combination of plot type, and spatial trend model.
+The researchers contrasted the different plot designs, as hexagon tilemap
+and geography in the lineups were created using the same data, and same null positions within the lineup.
+
+The researchers compared the length of time taken, and the accuracy of the participants choices.
+
+2. The subject populations
+<!-- The groups studied in the research including the size of each group and any features of the subjects which may be relevant to the topic being researched. -->
+
+There were 95 participants in the study.
+Each participant was randomly allocated to either group A or group B when they begun the survey.
+This resulted in 42 participants allocated to group A, and 53 participants allocated to group B.
+
+Demographics were collected regarding the study participants.
+
+3. The variables being manipulated and measured?
+    The variables that were changed between groups were the type of plot shown and the trend.
+    The variables measured as a result of the changes were probability of detection and the time taken to submit responses.
+
+The levels of the factors measured in the experiment were:
+• Plot type: *Geography, Hexagons*
+• Trend: *Locations in two population centres, Locations in multiple population centres, South-East to North-West*
+
+Factor combinations to be examined by each participant amount to 6 (2x3) lineup displays.
+A participant cannot see the same data for both plot types. Four simulated sets of data will be generated for each treatment.
+This will generate 24 lineups (12 will be geographic maps, and 12 will be hexagon tile maps).
+Participants will evaluate 12 lineups, 6 of each plot type.
+Appendix A shows the experimental design visually.
+For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants.
+
+4. The conditions under which the research was conducted?
+Each participant used the internet to access the survey.
+The participants determined the setting and time of day of the survey.
+There were many factors that could have determined the conditions under which the research was undertaken.
+Many factors or variations in conditions may have had an impact on the results.
+
+5. The methods of data analysis used?
+The data analysis methods used in order to analyse and collate the results were ...
+
+6. Limitations of the data collection?
+The data collection may have been influenced by several limitations.
+
+Research Questions:
+1. Are spatial disease trends, that impact highly populated small areas, detected with higher accuracy
+when viewed in a hexagon tile map display?
+2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when
+using a hexagon tile map display?
+3. Do people find hexagon tile maps more difficult to read than choropleth maps?
+4. Are the reasons for choosing a plot different depending on the type of display?
+5. Does an Australian resident find the choropleth map easier to read than the hexagon tile map?
+
+For each plot evaluation the subject will provide these responses:
+- Their choice of plot from a lineup
+- Reason for choice of plot
+- Time taken to respond
+- Perceived difficulty in making a choice
+
 <!--
@@
 -->
-
-## Population focussed displays
-
-Map creators have the ability to present spatial statistics in alternative displays that can highlight the population.
-This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
-The same data were shown on a choropleth map, and on a hexagon tile map.
-Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.
-
-Study Design
-============
-
-## Aims
-
-This study aims to answer several questions around the presentation of spatial distributions:
-
-1. Are spatial disease trends, that impact highly populated small areas, detected with higher accuracy when viewed in a hexagon tile map display?
-
-2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when
-using a hexagon tile map display?
-3. Do people find hexagon tile maps more difficult to read than choropleth maps?
-4. Are the reasons for choosing a plot different depending on the type of display?
-5. Does an Australian resident find the choropleth map easier to read than the hexagon tile map?
-
-## Methodology
-
-A survey was created to test the effectiveness of the hexagon tile map display.
-
-The online crowdsource platform Figure-Eight was used to recruit participants. 
-A line up protocol was implemented to arrange 12 maps in each display. 
-Individual displays were created by a combination of plot type, and spatial trend model.
-
-The researchers contrasted the different plot designs, as hexagon tilemap
-and geography in the lineups were created using the same data, and same null positions within the lineup.
-
-The researchers compared the length of time taken, and the accuracy of the participants choices.
-
-## The participants
-
-There were 95 participants in the study. 
-We recruited participants using the Figure-Eight crowd source platform by advertising this survey to participants that fulfilled the following crtieria:
-
-• level 2 or level 3 on the Figure-Eight Platform.
-• at least 18 years old
-
-Participants then selected our task from the list of tasks available to them.
-
-## The variables being manipulated and measured?
-
-The variables that were changed between groups were the type of plot shown and the trend model.
-
-Each participant was randomly allocated to either group A or group B when they begun the survey. This resulted in 42 participants allocated to group A, and 53 participants allocated to group B.
-
-The levels of the factors measured in the experiment were:
-• Plot type: *Geography, Hexagons*
-• Trend: *Locations in two population centres, Locations in multiple population centres, South-East to North-West*
-
-Factor combinations examined by each participant amount to 6 (2x3) lineup displays.
-A participant did see the same data for both plot types. Four simulated sets of data were generated for each treatment.
-This will generate 24 lineups (12 were geographic maps, and 12 were hexagon tile maps). Participants will evaluate 12 lineups, 6 of each plot type. Appendix A shows the experimental design visually.
-For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants.
-
-The variables measured as a result of the changes were the probability of detection each display and the time taken to submit responses.
-To measure the accuracy of the detections, the plot chosen for each lineup evaluated was compared to the position of the real spatial trend plot in the lineup.
-A correct result occurs when the chosen plot matches the position of the real plot, this was recorded in an additional binary variable; 1 = correct; 0 = incorrect.
-High efficiency occurs when a small amount of time is taken to evaluate each lineup.
-This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.
-
-## Participant training
-Each participant saw three test displays orienting them to the task. Participants proceeded to the survey, this involved evaluating 12 displays.
-
-## Experiment procudure and data collection
-The participant submitted demographic questions and provided consent before evaluating the lineups.
-
-Demographics were collected regarding the study participants:
-• Gender (female / male / other),
-• Degree education level achieved (high school / bachelors / masters / doctorate / other),
-• Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
-• Lived at least for one year in Australia (Yes / No )
-
-Participants then moved to the evaulation phase.
-The set of images differed for group A and group B.
-After being allocated each individual was shown the 12 displays in randomised order.
-
-Three questions were asked regarding each display:
-- Plot choice
-- Reason
-- Difficulty
-
-After completing the 12 evaluations, the participants were asked to submit their responses.
-
-Data was collected through a web application containing the online survey.
-Each participant used the internet to access the survey.
-
-The data collection took place using a secure link between the survey web application and the googlesheet used to store results.
-The application would first connect to the googlesheet using the googlesheets [@sheets] R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.
-
-## The methods of data analysis used
-The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R [@RCore].
-
-For each of the 12 lineup displays the researchers calculated:
-• accuracy: the proportion of subjects who detected the data plot
-• efficiency: average time taken to respond
-
-### Visualisations
-Side-by-side dot plots were made of accuracy (efficiency) against plot type, facetted by trend model type.
-
-Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.
-
-Plots will be made in R (R Core Team 2019), with the ggplot2 package (Wickham 2016).
-
-### Modeling
-
-The results will be analysed using a generalised linear model, with a subject random effect.
-There will be two main effects: plot type and trend model, which gives the fixed effects part of the model to be
-
-$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3$$
-
-where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the plot type effect, $\delta_j$ is the trend model effect.
-We are allowing for an interaction between plot type and trend model.
-Because the response is binary, a logistic model is used.
-
-A similar model will be constructed for the efficiency, using a log time, and normal errors.
-
-The feedback and demographic variables will possibly be incorporated as covariates.
-
-Computation will be done using R [@RCore], with the `lme4` package [@lme4].
-
-## Limitations of the data collection
-
-This required internet connection for participants to access the survey
-
-Ethics approval for the online survey was granted by QUT’s Ethics Committee (Ethics Application Number: 1900000991).
-All applicants provided informed consent in line with QUT regulations prior to participating in this research.
 
@@
 ###############################################################################
-
-# Load Libraries
-library(tidyverse)
-library(lubridate)
-library(broom)
-library(readxl)
-library(lme4)
-library(ggthemes)
-
 invthm <- theme(
@@
 
+# Load Libraries
+library(tidyverse)
+library(lubridate)
+library(broom)
+library(readxl)
+library(lme4)
+library(ggthemes)
 # Downloaded data
-d <- read_xlsx("data/experiment-export.xlsx", sheet=2) %>%
+d <- read_xlsx("../experiment-export.xlsx", sheet=2) %>%
   filter(!is.na(contributor)) %>%
@@
 ```{r}
-##ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in", bg = "transparent")
-##ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in")
+#ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in", bg = "transparent")
+#ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in")
 
@@
 
+###########################################################
+
 d_time <- d %>% 
@@
 
-#ggsave(filename = "figures/pilot/replicate_change_time.png", plot = repl_plot_t, device = "png", dpi = 300, width = 12, height = 8, units = "in", bg = "transparent")
-##ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in")
+ggsave(filename = "figures/pilot/replicate_change_time.png", plot = repl_plot_t, device = "png", dpi = 300, width = 12, height = 8, units = "in", bg = "transparent")
+#ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in")
 
@@
 
+Here are two sample references: @Feynman1963118 [@Dirac1953888].
+
 \newpage
@@
 <!-- \includegraphics[width=2.5in]{myfigure} -->
-<!-- where an .eps filename suffix were assumed under latex,  -->
-<!-- and a .pdf suffix were assumed for pdflatex; or what has been declared -->
+<!-- where an .eps filename suffix will be assumed under latex,  -->
+<!-- and a .pdf suffix will be assumed for pdflatex; or what has been declared -->
 <!-- via \DeclareGraphicsExtensions. -->

### 2021-01-11 survey/survey.tex
darker figures

--- 2019-12-17 survey/survey.tex
@@
 
+\begin{verbatim}
+Described the methods used to undertake the research including details of 
+\end{verbatim}
+
+This methodology section explains the various aspects of the research:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  The overall structure of the research
+\end{enumerate}
+
 A survey was created to test the effectiveness of the hexagon tile map
@@
 
-Experimental Design: Three trends were tested, in each of the two
-displays. For each of the
+The online crowdsource platform Figure-Eight was used to recruit
+participants.\\
+Each participant saw three test displays orienting them to the task.
+They then took an online survey evaluating 12 displays. A line up
+protocol was implemented to arrange 12 maps in each display. Individual
+displays were created by a combination of plot type, and spatial trend
+model. The researchers contrasted the different plot designs, as hexagon
+tilemap and geography in the lineups were created using the same data,
+and same null positions within the lineup.
 
-Line up protocol:
+The researchers compared the length of time taken, and the accuracy of
+the participants choices.
 
-\begin{itemize}
-\item
-  Experimental design
-
-  \begin{itemize}
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
 \tightlist
 \item
-    The overall structure and operation of the experiment or
-    observational experience.
+  The subject populations 
+\end{enumerate}
+
+There were 97 participants in the study. Each participant was randomly
+allocated to either group A or group B when they begun the survey. This
+resulted in 42 participants allocated to group A, and 53 participants
+allocated to group B.
+
+Demographics were collected regarding the study participants.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{2}
+\tightlist
 \item
-    The subject populations: The groups studied in the research
-    including the size of each group and any features of the subjects
-    which may be relevant to the topic being researched.
+  The variables being manipulated and measured? The variables that were
+  changed between groups were the type of plot shown and the trend. The
+  variables measured as a result of the changes were probability of
+  detection and the time taken to submit responses.
+\end{enumerate}
+
+The levels of the factors measured in the experiment were: • Plot type:
+\emph{Geography, Hexagons} • Trend: \emph{Locations in two population
+centres, Locations in multiple population centres, South-East to
+North-West}
+
+Factor combinations to be examined by each participant amount to 6 (2x3)
+lineup displays. A participant cannot see the same data for both plot
+types. Four simulated sets of data will be generated for each treatment.
+This will generate 24 lineups (12 will be geographic maps, and 12 will
+be hexagon tile maps). Participants will evaluate 12 lineups, 6 of each
+plot type. Appendix A shows the experimental design visually.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{3}
 \item
-    The variables that were changed between groups and the variables
-    measured as a result of the changes.
+  The conditions under which the research was conducted? Each
+  participant used the internet to access the survey. The participants
+  determined the setting and time of day of the survey. There were many
+  factors that could have determined the conditions under which the
+  research was undertaken. Many factors or variations in conditions may
+  have had an impact on the results.
 \item
-    The conditions under which the research was undertaken and any
-    factors or variations in conditions which may have an impact on the
-    results.
+  The methods of data analysis used? The data analysis methods used in
+  order to analyse and collate the results were \ldots{}
 \item
-    The methods of data analysis used in order to analyse and collate
-    the results.
-  \item
-    Any limitations of the data collected
-  \end{itemize}
-\end{itemize}
+  Limitations of the data collection? The data collection may have been
+  influenced by several limitations.
+\end{enumerate}
+
+Research Questions: 1. Are spatial disease trends, that impact highly
+populated small areas, detected with higher accuracy when viewed in a
+hexagon tile map display? 2. Are people faster in detecting spatial
+disease trends, that impact highly populated small areas, when using a
+hexagon tile map display? 3. Do people find hexagon tile maps more
+difficult to read than choropleth maps? 4. Are the reasons for choosing
+a plot different depending on the type of display? 5. Does an Australian
+resident find the choropleth map easier to read than the hexagon tile
+map?
+
+For each plot evaluation the subject will provide these responses: -
+Their choice of plot from a lineup - Reason for choice of plot - Time
+taken to respond - Perceived difficulty in making a choice
 
@@
 \end{enumerate}
+
+The results section describes the findings of the research. When
+outlining these findings, it is best to give the most central findings
+first and then move on to the more peripheral results. For example, the
+overall measure of learning would be given first and then the measures
+of different types of learning.
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-abs2016}{}%
+``Australian Statistical Geography Standard (ASGS).'' 2018.
+\emph{Australian Bureau of Statistics}. Australian Government.
+\href{https://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)}{https://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian   Statistical Geography Standard (ASGS)}.
+
 \leavevmode\hypertarget{ref-SIEDAMD}{}%

### 2021-01-11 R/00_pilot.R

@@ -1,0 +1,198 @@
+# Create maps for pilot study
+# This script considers the sa3 areas of Australia.
+# It creates lineups by simulating a null model spatial for 20 plots,
+# It then adds a data with a spatial trend to a randomly selected plot 
+
+# libraries
+library(gstat)
+library(purrr)
+library(sp)
+library(sf)
+library(sugarbag)
+library(tidyverse)
+library(viridis)
+
+set.seed(19941030)
+
+###########################################################
+####################     DATA    ##########################
+# Geography of sa3 areas
+sa3 <- absmapsdata::sa32016
+sa3 <- rmapshaper::ms_simplify(sa3, 
+  keep = 0.5, keep_shapes = TRUE, explode = FALSE, drop_null_geometries = TRUE)
+
+sa3_neighbours <- sf::st_intersects(sa3$geometry,sa3$geometry)  %>% 
+  as_tibble() %>% 
+  filter(row.id != col.id) %>% 
+  rename(sa3neighbours = col.id) %>% 
+  group_by(row.id) %>% 
+  count(name = "sa3")
+
+
+# filter out Islands
+Islands <- c("Cocos (Keeling) Islands",	"Christmas Island", "Norfolk Island", "Lord Howe Island")
+sa3 <- sa3 %>% 
+  filter(!is.na(cent_long)) %>% 
+  filter(!(sa3_name_2016 %in% Islands))
+
+# Make list of Tasmanian sa3 areas
+Tasmania <- sa3 %>% st_drop_geometry() %>% 
+  filter(state_name_2016 == "Tasmania") %>%
+  select(sa3_name_2016) %>% pull()
+
+# derive centroids
+sa3_centroids <- sa3 %>%
+  select(sa3_name_2016, longitude = cent_long, latitude = cent_lat) %>%
+  sf::st_drop_geometry() %>% filter(!is.na(longitude))
+
+# add trend models to simulated errors
+sa3_centroids$logsize <- log(sa3$areasqkm_2016)
+
+
+###########################################################
+################    AUSTRALIA    ##########################
+
+aus_underlay <- st_union(sa3$geometry)
+
+
+###########################################################
+####################    HEXMAP   ##########################
+# Create hexagon map of sa3
+allocated <- create_hexmap(
+  shp = sa3,
+  buffer_dist = 2,
+  sf_id = "sa3_name_2016",
+  hex_size = 0.6, # same size used in create_grid
+  hex_filter = 10,
+  neighbours = sa3,
+  f_width = 30,
[…]

### 2021-01-11 R/sa2_plots.R

@@ -1,0 +1,267 @@
+#sa2_plots
+
+
+
+# Create a choropleth of Australia
+library(sugarbag)
+library(tidyverse)
+library(readxl)
+library(spData)
+library(ggthemes)
+library(maptools)
+library(sf)
+library(cartogram)
+library(cowplot)
+
+
+# Filter for centroids only within longitudes
+checkgeom <- function(x){
+  xval <- st_coordinates(x)[[2]]
+  
+  if (xval < 109){return(FALSE)}
+  if (xval > 155){return(FALSE)}
+  return(TRUE)
+}
+
+sa2 <- absmapsdata::sa22011 %>% 
+  filter(!st_is_empty(geometry)) %>%
+  filter(checkgeom(x = geometry))
+
+sa2 <- sa2 %>% 
+  rmapshaper::ms_simplify(keep = 0.05, keep_shapes = TRUE)
+
+# Join with cancer data from Australian Cancer Atlas
+
+SIR <- read_csv("data/SIR Downloadable Data.csv") %>% 
+  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
+  filter(Cancer_name == "Lung", Sex_name == "Persons")
+ERP <- read_csv("data/ABS_ERP_ASGS_26112019122253900.csv") %>%
+  filter(REGIONTYPE == "SA2", Time == 2011, Sex == "Persons", Region %in% SIR$SA2_name) %>% 
+  dplyr::select(Region, Value)
+
+
+# function to allocate colours to regions
+aus_colours <- function(sir_p50){
+  value <- case_when(
+    sir_p50 < 0.5 ~ "#33809d",
+    sir_p50 >= 0.5 & sir_p50 < 1 ~ "#aec6c7",
+    sir_p50 >= 1 & sir_p50 < 1.5 ~ "#fff4bc",
+    sir_p50 >= 1.5 & sir_p50 < 2 ~ "#ff9a64",
+    sir_p50 >= 2 ~ "#ff3500",
+    TRUE ~ "#FFFFFF")
+  return(value)
+}
+
+# Join with sa2 sf object
+sa2lung_ERP <- SIR %>% 
+  left_join(sa2, ., by = c("sa2_name_2011" = "SA2_name")) %>%
+  left_join(., ERP %>% dplyr::select(Region, 
+                                     Population = Value), by = c("sa2_name_2011"= "Region")) %>% 
[…]

### 2021-01-11 R/survey_app.R

@@ -1,0 +1,122 @@
+###############################################################################
+##############################    SURVEY APP     ##############################
+###############################################################################
+
+# demographics and scene questions
+
+surveyQuestions <- function(demographics, scene){
+  structure(
+    list(demographics = demographics, scene = scene),
+    class = "taipanQuestions"
+  )
+}
+questions <- surveyQuestions(
+  demographics =
+    div(
+      # Contributor ID
+      textInput("contributor", "For payment, provide Figure Eight Contributor ID:", 
+                placeholder = "id"),
+      p("For more information click the More Info button"),
+      radioButtons("consent", "Do you consent to your responses being analysed for this survey project?\n
+                   .", 
+                   choices = c("Yes, I consent" = 1,"No, I do not consent" = 2),
+                   selected = character(0)),
+      # Question 1, gender
+      selectInput("gender",
+                  "Select your preferred pronoun:",
+                  choices = list("Choose one" = 1, 
+                                 "She" = 2, 
+                                 "He" = 3,
+                                 "They" = 4,
+                                 "Other" = 5), 
+                  selected = 1),
+      # Question 2, education
+      selectInput("education",
+                  "Select the highest level of education achieved:",
+                  choices = list("Choose one" = 1, 
+                                 "High School Diploma" = 2,
+                                 "Bachelors Degree" = 3,
+                                 "Master Degree" = 4,
+                                 "Doctorate" = 5,
+                                 "Other" = 6
+                  ), 
+                  selected = 1),
+      # Question 3, age range
+      selectInput("age",
+                  "Select your age range:",
+                  choices = list("Choose one" = 1, 
+                                 "18 - 24" = 2,
+                                 "25 - 34" = 3,
+                                 "35 - 44" = 4,
+                                 "45 - 54" = 5,
+                                 "55+" = 6,
+                                 "Other" = 7
+                  ), 
+                  selected = 1),
+      # Question 4, Australia
+      selectInput("australia",
+                  "Have you lived in Australia?",
+                  choices = list("Choose one" = 1, 
+                                 "Yes" = 2,
+                                 "No" = 3, 
+                                 "Other" = 4), 
+                  selected = 1)
+    ),
+  scene =
+    div(
+      # Question 1, the choice of plot
+      selectInput("select",
+                  "Which map is most different from the others?",
[…]

### 2021-01-11 analysis/analysis.R

@@ -1,0 +1,253 @@
+###############################################################################
+# Analysis of experiment data - by Di
+###############################################################################
+
+# Read Data 
+#library(googlesheets)
+#gs_ls()
+#sheet <- gs_key("1PcKMmsojzljDZl4bftOu5lbG51AVYuiPIJFq2t7kiGg")
+
+###############################################################################
+invthm <- theme(
+  panel.background = element_rect(fill = "transparent", colour = NA), 
+  plot.background = element_rect(fill = "transparent", colour = NA),
+  legend.background = element_rect(fill = "transparent", colour = NA),
+  legend.key = element_rect(fill = "transparent", colour = NA),
+  text = element_text(colour = "white", size = 20),
+  axis.text = element_text(colour = "white", size = 20)
+)
+
+# Load Libraries
+library(tidyverse)
+library(lubridate)
+library(broom)
+library(readxl)
+library(lme4)
+library(ggthemes)
+# Downloaded data
+d <- read_xlsx("experiment-export.xlsx", sheet=2) %>%
+  filter(!is.na(contributor)) %>%
+  mutate(contributor = factor(contributor))
+
+###############################################################################
+# Check data set 
+d %>% count(contributor, sort=TRUE)
+# Need to clean multiple entries, 48, 24
+# remove duplicated entries due to submit button
+d <- d %>% group_by(group, contributor, image_name) %>%
+  slice(1) %>% ungroup() %>% 
+  arrange(group, contributor, plot_order)
+d %>% count(contributor, sort=TRUE)
+d %>% count(contributor, sort=TRUE) %>% summarise(n_contributors = length(contributor))
+
+# Now remove contributors who did not provide answers to most questions
+keep <- d %>% count(contributor) %>% filter(n > 10)
+d <- d %>% 
+  filter(contributor %in% keep$contributor) %>%
+  filter(contributor != "1234567890")
+
+###############################################################################
+# Augment
+# add data replication number
+d %>% count(image_name) %>% print(n=24)
+# image code <--> rep
+replicate <- tibble(image_name = c("aus_cities_12_geo.png", "aus_cities_12_hex.png", 
+                                   "aus_cities_3_geo.png", "aus_cities_3_hex.png",
[…]

### 2021-01-11 supplementary/R/pilot_nwse.R

@@ -1,0 +1,325 @@
+###############################################################################
+######################  NORTH WEST - SOUTH EAST TREND   #######################
+
+# Which map shows the most areas coloured red?
+
+set.seed(2016)
+var.g.dummy <- gstat(formula = z ~ 1, 
+                     locations = ~ longitude + latitude, 
+                     dummy = T, beta = 1, model = vgm(psill = 1, model = "Gau", range = 0.3),
+                     nmax = 12)
+
+# Create underlying spatially dependent data for 12 null plots
+# use an underlying spatial covariance model
+var.sim1 <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
+var.sim2 <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
+var.sim3 <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
+var.sim4 <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
+
+###############################################################################
+######################          SMOOTH        #########################
+
+sa3_sims1_1 <- as_tibble(var.sim1) %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
+                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+sa3_sims1_2 <- sa3_sims1_1 %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
+                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+sa3_sims1_3 <- sa3_sims1_2 %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
+                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+sa3_sims1_4 <- sa3_sims1_3 %>% 
[…]

### 2021-01-11 surveyapplication/server.R

@@ -1,0 +1,278 @@
+library(shiny)
+library(ggplot2)
+library(purrr)
+# Load survey questions
+questions <- readRDS("data/questions.Rds")
+
+
+getInputID <- function(input){
+  if(!inherits(input, "shiny.tag")){
+    return()
+  }
+  c(
+    if(!is.null(input$attribs$id)){list(list(id=input$attribs$id, type = input$name))}else{NULL},
+    do.call("c", map(input$children, getInputID))
+  )
+}
+
+shinyServer(
+  function(input, output, session) {
+    
+    # Check connection to google sheet
+    
+    sheet <- tryCatch({
+      gs_auth("data/authentication.rds")
+      sheet <- gs_key("1PcKMmsojzljDZl4bftOu5lbG51AVYuiPIJFq2t7kiGg")
+        }, error = function(e){ 
+          message("Access has not been granted, please try again in 5 minutes.")
+          return(NULL)
+          })
+    
+    # Unique identifier function:
+    create_unique_id <- function(char_len = 7){
+      set.seed(Sys.time())
+      pool <- c(letters, LETTERS, 0:9)
+      
+      this_res <- paste0(sample(pool, char_len, replace = TRUE), collapse = "")
+      this_res
+    }
+    
+    identifier <- create_unique_id()
+    
+    # Allocate to group A or B
+    group_allocation <- sample(c("A", "B"), 1)
+    
+    # Load survey images
+    image_list <- list.files(paste0("www/app_images/group", 
+                             group_allocation), full.names = TRUE)
+    image_list <- sample(image_list, length(image_list))
+    
+    
+    v <- reactiveValues(
+      imageNum = 1,
+      responses = list(),
+      start_time = Sys.time(),
+      finish_time = Sys.time(),
+      plot_order = 1,
+      group = group_allocation,
+      submitted = FALSE
+    )
+    
+    current_img <- reactive({
+      image_list[v$imageNum]
+    })
+    
+    
+    output$out_img <- renderImage({
+      list(src = current_img(), id = "taipan_current_img")
+    }, deleteFile = FALSE)
+    
+    sceneInputs <- getInputID(questions$scene)
+    demographicsInputs <- getInputID(questions$demographics)
+    
+    scene_vals <- reactive({
+      vals <- map(sceneInputs, function(id){input[[id$id]]})
+      names(vals) <- map_chr(sceneInputs, "id")
+      vals
+    })
+    
[…]

### 2021-01-11 R/sa2_plots.R
exp design chart and positions chart

@@ -34,7 +34,7 @@ sa2 <- sa2 %>%
 
 SIR <- read_csv("data/SIR Downloadable Data.csv") %>% 
   dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
-  filter(Cancer_name == "Lung", Sex_name == "Persons")
+  filter(Cancer_name == "Liver", Sex_name == "Persons")
 ERP <- read_csv("data/ABS_ERP_ASGS_26112019122253900.csv") %>%
   filter(REGIONTYPE == "SA2", Time == 2011, Sex == "Persons", Region %in% SIR$SA2_name) %>% 
   dplyr::select(Region, Value)
@@ -53,25 +53,25 @@ aus_colours <- function(sir_p50){
 }
 
 # Join with sa2 sf object
-sa2lung_ERP <- SIR %>% 
+sa2liver_ERP <- SIR %>% 
   left_join(sa2, ., by = c("sa2_name_2011" = "SA2_name")) %>%
   left_join(., ERP %>% dplyr::select(Region, 
                                      Population = Value), by = c("sa2_name_2011"= "Region")) %>% 
   filter(!st_is_empty(geometry))
 
 
-sa2lung_ERP <- sa2lung_ERP %>% 
+sa2liver_ERP <- sa2liver_ERP %>% 
   filter(!is.na(Population)) %>% 
   mutate(SIR = map_chr(p50, aus_colours)) %>% 
   st_as_sf() 
 
-sa2lung_ERP <- st_transform(sa2lung_ERP, 3112)
+sa2liver_ERP <- st_transform(sa2liver_ERP, 3112)
 
-b <- st_bbox(sa2lung_ERP)
+b <- st_bbox(sa2liver_ERP)
 b["xmin"]<- -2181807
 b["xmax"]<- 1933081
 
-sa2lung_ERP_fort <- fortify_sfc(sa2lung_ERP)
+sa2liver_ERP_fort <- fortify_sfc(sa2liver_ERP)
 
 aus <- absmapsdata::state2016 %>% 
   filter(!(state_name_2016 == "Other Territories"))
@@ -91,7 +91,7 @@ invthm <- theme_void() + theme(
 )
 
 # Create a choropleth
-aus_ggchoro <- ggplot(sa2lung_ERP) + 
+aus_ggchoro <- ggplot(sa2liver_ERP) + 
   geom_sf(aes(fill = SIR)) +
[…]

### 2021-01-11 04-experiment.Rmd

--- 2021-01-11 paper.Rmd
@@
 ---
-title: "Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics"
-affiliation:
-  #author-columnar: true         ## one column per author
-  institution-columnar: true  ## one column per institution (multiple autors eventually)
-  # wide: true                  ## one column wide author/affiliation fields
-  institution:
-    - name: Queensland University of Technology
-      department: Science and Engineering Faculty
-      location: Brisbane, Australia
-      email: stephanie.kobakian@qut.edu.au
-      mark: 1
-      author:
-        - name: Stephanie Kobakian
-    - name: Monash University
-      department: Econometrics and Business Statistics Faculty
-      location: Melbourne, Australia
-      email: dicook@monash.edu
-      mark: 1
-      author:
-        - name: Dianne Cook
-keywords: ["statistics", "visual inference", "geospatial", "population"]
-abstract: |
+chapter: 4
+knit: "bookdown::render_book"
+---
+
+# Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer {#experiment}
+
+This chapter tests the performance of the hexagon tile map display created using the algorithm discussed in Section \ref{algorithm}.
+It outlines the lineup protocol method of visual inference that can be used to test the effectiveness of information visualisations.
+Using a two factor experimental design, the experiment contrasts the performance of participants when they viewed a choropleth map, and their performance when viewing a hexagon tile map.
+The experiment also considered three types of spatial trends, one geographic trend, and two population related distributions. 
+The results showed that participants did in fact more frequently find the population related distributions when using the hexagon tile map.
+
+This chapter will be submitted to the journal *IEEE Transactions of Visualisation and Computer Graphics*.
+
+## Abstract {-}
+
 The choropleth map display is commonly used for communicating spatial distributions across geographic areas.
@@
 These findings should encourage map creators to implement alternative displays and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
-dev: pdf
-bibliography: paper.bib
-output:
-  bookdown::pdf_book: 
-      base_format: rticles::ieee_article
-      number_sections: true
-editor_options: 
-  chunk_output_type: inline
-link-citations: true
-citation_package: biblatex
-csl: springer-vancouver.csl
-header-includes: \usepackage{graphicx}
----
 
-<!-- Regular paper – 12 double column pages (Submissions may be up to 18 pages in length, subject to MOPC. All regular paper page limits include references and author biographies.) -->
+```{r setup-4, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE}
+library(knitcitations)
+library(RefManageR)
+library(sf)
+library(sugarbag)
 
-```{r setup, include=FALSE}
 knitr::opts_chunk$set(
@@
   dpi = 300,
-  out.width = "100%")
+  out.width = "80%")
+options("citation_format" = "pandoc")
+BibOptions(check.entries = FALSE, style = "markdown")
 ```
@@
 
-```{r data}
+```{r data-4}
 trend_colors <- c(
@@
 
-```{r reps}
+```{r reps4}
 replicate <- tibble(image_name = c("aus_cities_12_geo.png", "aus_cities_12_hex.png", 
@@
 
-Introduction
-=============
+## Introduction
 <!-- General: comparison of displays, motivate hexagon tile map, enough info to motivate aims -->
@@
 
-The Australian Cancer Atlas [@atlas] is an online interactive web tool created to explore the burden of cancer on Australian communities.
+The Australian Cancer Atlas [@TACA] is an online interactive web tool created to explore the burden of cancer on Australian communities.
 There are many cancer types to be explored individually or aggregated.
@@
 
-Background
-=============
+## Background
 
-## Spatial data displays
+### Spatial data displays
 
@@
 
-<!-- Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
-The rural communities in Australia operate on a much larger geographic space than small inner-city communities.
-When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
-This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention [@CTTMB].
-An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas [@NISCC].
-This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
-
-A choropleth map is not the only display that can be used for presenting geospatial data. 
-Alternative maps include various cartograms and tessellated tile maps. They allow other variables to be incorporated in the display to highlight the statistical values of various geographic areas.
--->
-
-```{r liver, fig.height = 4, fig.width = 4, fig.cap = "A choropleth map of the smoothed average of liver cancer diagnoses for Australian males.
-The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
-The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.", results = "asis"}
-ggdraw() +
-  draw_plot(rasterGrob(readPNG("figures/aus_liver_m.png")))
-```
-
-```{r liver-hex, fig.height = 4, fig.width = 4, fig.cap = "A hexagon tile map of the smoothed average of liver cancer diagnoses for Australian males.
-The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
-The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.", results = "asis"}
-
-ggdraw() +
-  draw_plot(rasterGrob(readPNG("figures/aus_liver_m_hex.png")))
-```
-<!--
-This will create the figure as needed in the paper, but I can't get the width argument to work properly.
-\begin{figure*}[!t]
+\begin{figure}[H]
 \centering
-\includegraphics{paper_files/figure-latex/liver-1.pdf}
-\caption{A choropleth map (a), and hexagon tile map (b) of the smoothed average of liver cancer diagnoses for Australian males.
+\includegraphics[width=16cm]{figures/aus_liver_m.pdf}
+\caption{\label{fig:liver-geo}A choropleth map of the smoothed average of liver cancer diagnoses for Australian males.
 The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
 The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.}
-\label{fig:liver2}
-\end{figure*}
--->
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=16cm]{figures/aus_liver_m_hex.pdf}
+\caption{\label{fig:liver-hex}A hexagon tile map of the smoothed average of liver cancer diagnoses for Australian males.
+The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
+The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.}
+\end{figure}
 
@@
 Fig.
-\ref{fig:liver} shows the hexagon tile map, along with the choropleth map of liver cancer rates in Australia.
+\ref{fig:liver-geo} shows the hexagon tile map, along with the choropleth map of liver cancer rates in Australia.
 Colour maps from substantially below average (blue) to substantially above average (red) rates.
@@
 
-## Visual Inference
+### Visual Inference
 
@@
 
-```{r lineup, fig.cap = "This lineup of twelve hexagon tile map displays contains one map with a real population related structure.
-The rest are null plots that contain spatial correlation between neighbours.", fig.height = 8, fig.width = 8}
-ggdraw() +
-  draw_plot(rasterGrob(readPNG("figures/aus_cities_3_geo.png")))
-```
+\begin{figure}[H]
+\centering
+\includegraphics[width=16cm]{figures/aus_cities_3_geo.png}
+\caption{\label{fig:lineup}This lineup of twelve hexagon tile map displays contains one map with a real population related structure.
+The rest are null plots that contain spatial correlation between neighbours.}
+\end{figure}
 
@@
 
-Methodology
-============
+### Methodology
 
@@
 
-## Experimental factors
+### Experimental factors
 
@@
 These latter two reflect the structure seen in the liver cancer data (Fig.
-\ref{fig:liver}).
+\ref{fig:liver-geo}).
 This produces six treatment levels:
@@
 
-```{r exp-design, results = "asis", fig.width = 8, fig.height = 8, fig.cap = "The experimental design used in the visual inference study."}
-ggdraw(xlim = c(0,1), ylim = c(0,1)) + draw_plot(rasterGrob(png::readPNG("figures/exp design chart.png")))
-```
+\begin{figure}[H]
+\centering
+\includegraphics[width=16cm]{figures/experiment_design.pdf}
+\caption{\label{fig:exp-design}The experimental design used in the visual inference study.}
+\end{figure}
 
-## Generating null data
+### Generating null data
 
@@
 
-This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the Liver cancer distribution (Fig. \ref{fig:liver}).
+This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the Liver cancer distribution (Fig. \ref{fig:liver-geo}).
 
-## Generating lineups
+### Generating lineups
 
@@
 The location was chosen from a sub sample of the 12 possible locations.
-The chance of reptition using resampling was introduced to prevent participants from inducing the location by elimination, the locations 1, 7, 10 and 11 were not used.
+The chance of repetition using resampling was introduced to prevent participants from inducing the location by elimination, the locations 1, 7, 10 and 11 were not used.
 
@@
 
-## Analysis
+### Analysis
 
-### Data Cleaning
+#### Data Cleaning
 
@@
 
-### Descriptive statistics
+#### Descriptive statistics
 
@@
 
-Plots will be made in R [@RCore], with the `ggplot2` package [@ggplot2].
+Plots will be made in R [@R], with the `ggplot2` package [@ggplot2].
 
-### Modelling
+#### Modelling
 
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model. 
-The R [@RCore] `glmer()` function in the `lme4` [@lme4] package implements generalised linear mixed effect models.
+The R [@R] `glmer()` function in the `lme4` [@lme4] package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 
-where $y_{ij} = 0, 1$ is the logg odds for whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
+where $y_{ij} = 0, 1$ is the log odds for whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
 We are allowing for an interaction between map type and trend model as the response is binary, so a logistic model was used.
@@
 
-## Web application to collect responses
+### Web application to collect responses
 
@@
 
-## Participants
+### Participants
 
@@
 
-## Demographic data collection
+### Demographic data collection
 
@@
 
-<!--
-## Experimental design
-
-The choropleth map was used as the comparative visualization for presenting the lineups [@VVSIALM] as this is the common display for spatial cancer data.
-Geographic distributions usually have some degree of spatial autocorrelation between neighbors.
-This feature was incorporated in all maps shown in the lineup displays, the map that contained the trend feature shown in only one set of data was also affected by spatial autocorrelation.
-A line up protocol was implemented to arrange $N$ maps in each display. 
-A reasonable amount of null plots $N-1$ in the lineup was chosen to ensure the real data map was well hidden.
-A reasonable number of plots to show in each lineup, $N = 12$ was chosen to not overwhelm participants due to the detailed choropleth maps of Australian SA3 areas.
-
-The hypotheses for each lineup are
-$H_0$ : All plots look the same
-$H_a$ : One plot looks different to the other plots
-
-The same data was visualized on a choropleth map, and on a hexagon tile map, however in this study the participants only saw one of these two displays.
-The accuracy and times taken were aggregated for Groups and.
-Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.
-
-Let $n$ be the number of independent observers and $x_i$ the
-number of observers who picked plot $i$, $i = \{1,...,m\}$
-
-Then $x_i, x_2, ..., x_m$ follows a multinomial
-distribution$Mult_{\pi_1, \pi_2, ...., \pi_m}(x_i, x_2, ..., x_m)$ with 
-$\sum_i \pi_i = 1$, where $\pi_i$ is the probability that plot $i$ is picked by an
-observer, which we can estimate as $\hat{\pi}_i = x_i/n$.
-The researchers compared the length of time taken, and the accuracy of the participants choices.
-The power of a lineup can therefore be estimated as the ratio of correct
-identifications $x$ out of $n$ viewings.
-
-## The methods of data analysis used
-The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R [@RCore].
-
-For each of the 12 lineup displays the researchers calculated:
-
- - accuracy: the proportion of subjects who detected the data plot
- - efficiency: average time taken to respond
--->
-
-Results
-============
-
-<!--
-The results section explores the [Accuracy] and contrasts the detection rate of the real data plot in the lineups.
-The second section considers the [Speed] participants had when submitting their responses to the three questions asked regarding each display.
-The [Certainty] participants felt about their decisions and the [Reason] for their choice in plot is also discussed.
--->
+## Results
 
@@
 
-## Participant demographics
+### Participant demographics
 
@@
 
-## Accuracy
+### Accuracy
 
@@
 The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts.
-One replicate for the All Cities group had similar detection rates for both plot types, the rate of detection using the choropleth map was much higher than other replicates.
-Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map.
-We expected that the choropleth map would be superior for the type of spatial pattern, but the data suggests the hexagon tile map performs slightly better, or equally as well.
+One replicate for the All Cities group had a similar detection rate for both the choropleth and the hexagon tile map.
+Interestingly, in post-analysis we found that participants chose the data display in the choropleth lineup for reasons unrelated to the All Cities data structure.
+Participants detected the gradual spatial trend in the NW-SE group equally well from both map types.
+This was a pleasant surprise; we expected that the choropleth map would be superior for the type of spatial pattern, but the data suggests the hexagon tile map performs equally as well.
 
@@
 The points for the same data set shown in a choroleth or hexagon tile map display are linked to show the difference in the detection rate.", fig.height=5}
-# Detectability rate for each lineup (image)
+## Detectability rate for each lineup (image)
 d_smry <- d %>% group_by(trend, type, replicate) %>%
-  # pdetect measures the aggregated accuracy of the choices
+  ## pdetect measures the aggregated accuracy of the choices
   summarise(pdetect = length(detect[detect == 1])/length(detect)) %>%
@@
 
-# Numerical summary
+## Numerical summary
 diffs <- d_smry %>% spread(type, pdetect) %>%
@@
 
-# Plot summary
+## Plot summary
 ggplot(d_smry, aes(x = type, y = pdetect, color = trend)) +
@@
 \ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
-This also gives the standard deviations, the smallest standard deviation for all sets of replicates was the Three Cities trend model shown in a Choropleth display.
+This also gives the standard deviations, the smallest standard deviation for all sets of replicates was the Three Cities trend model shown in a choropleth display.
 This group of displays had a very small detection rate of 0.04.
@@
     linesep = c("", "\\addlinespace"),
-    caption = "The mean and standard deviation of the rate of detection for each trend model, calculated for the choropleth and hexagon tile map displays.")
+    caption = "The mean and standard deviation of the rate of detection for each trend model, calculated for the choropleth and hexagon tile map displays.") %>% 
+  kable_styling(latex_options =c("hold_position"))
 ```
@@
 ```{r detect-glmer1, results="asis"}
-# Mixed effects models
+## Mixed effects models
 glmer1 <- glmer(detect ~ type*trend + (1|contributor), 
@@
 
-detection_rates <- broom.mixed::tidy(glmer1) %>%
+detection_rates <- tidy(glmer1) %>%
   mutate(detection_rates = round(exp(estimate)/(1+exp(estimate)),2)) %>%
@@
 
-broom.mixed::tidy(glmer1) %>%
+tidy(glmer1) %>%
   mutate_at(.vars = c("estimate", "std.error"), round, 2) %>% 
@@
     caption = "The model output for the generalised linear mixed effect model for detection rate.
-This model considers the type of display, the trend model hidden in the data plot, and accounts for contributor performance.")
+This model considers the type of display, the trend model hidden in the data plot, and accounts for contributor performance.") %>%
+  kable_styling(latex_options =c("hold_position"))
 ```
 
-## Speed
+### Speed
 
@@
 Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between plot types.", fig.height=8}
-# Di playing
+## Di playing
 s <- d %>% group_by(type, trend, detect_f) %>%
@@
 
-## Certainty
+### Certainty
 
@@
 ```{r certainty, fig.cap = "The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
-Participants were more likely to choose a high certainty when considering a Choropleth map.
-The mid value of 3 was the default certainty, it was chosen most for the Hexagon tile map displays.", fig.height=5}
+Participants were more likely to choose a high certainty when considering a choropleth map, but more likely to be wrong for the All Cities and Three Cities patterns.
+Participants were less certain in their responses for the hexagon tile map lineups, perhaps reflecting the lack of familiarity.", fig.height=5}
 d <- d %>% 
@@
 
-## Reason
+### Reason
 
@@
 ```{r reason, results = "asis"}
-# Qualitative analysis of reason
+## Qualitative analysis of reason
 d %>% 
@@
     linesep = c("", "\\addlinespace", "", "\\addlinespace",""),
-    caption = "The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
+    caption = "The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in choropleth and hexagon tile maps.
 The facets show whether or not the choice was correct.") %>%
-  #kable_styling(bootstrap_options = "hold_position") %>% 
-  collapse_rows(., columns = 1)
+  collapse_rows(., columns = 1) %>% 
+  kable_styling(latex_options = c("hold_position"))
 ```
 
-Discussion
-============
+## Discussion
 
@@
 The All Cities displays colored the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural color consistency.
-Choosing "Clusters of colour" was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions.
+Choosing "Clusters of colour" was expected when participants viewed the hexagon tile map display of the All Cities and Three Cities distributions.
 It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays.
@@
 
-Conclusion
-============
+## Conclusion
 
@@
 
-Acknowledgment
-==============
+## Supplementary meaterial
 
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments.
-Mitchell O'Hara-Wild was a co-developer of the taipan [@taipan] R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
-We are thankful for the NUMBATs (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.
-
-The source code to produce this document can be found on [GitHub](https://github.com/srkobakian/experiment/tree/master/paper).
-Supplementary materials have been included to discuss the survey procedures and the lineups that were used.
-The full set of images can also be found at: https://github.com/srkobakian/experiment/tree/master/figures/final.
-
-The supplementary material contains:
+The appendix \ref{appendix} contains:
 
@@
 - 12 data sets used to construct the lineups
-
-The analysis of the work was completed in R [@RCore] with the use of the following packages:
-
- - For document creation: rmarkdown [@rmarkdown], rticles [@rticles], knitr [@knitr].
- - For lineup creation and data analysis: tidyverse [@tidyverse], nullabor [@nullabor], ggthemes [@ggthemes], RColorBrewer [@RColorBrewer].
- - For image displays: cowplot [@cowplot], png [@png], grid [@grid].
- - For modelling and presentation of models: gstat [@gstat], lme4 [@lme4], kableExtra [@kableExtra].
-
-Ethics approval for the online survey was granted by QUT’s Ethics Committee (Ethics Application Number: 1900000991).
-All applicants provided informed consent in line with QUT regulations prior to participating in this research.
-
-\newpage
-References {.numbered}
-==========

### 2021-01-11 paper/paper.tex

@@
 assessment by the participant prompted by the question: `How certain are you about your choice?'.
-Figure.
-\ref{certainty} shows the amount of times participants provided each level of certainty.
+Fig.
+\ref{fig:certainty} shows the amount of times participants provided each level of certainty.
 This was separated for each combination of trend models and display type, and colored depending on whether a participant correctly detected the data plot in the lineup.
-Participants chose 4 or 5 often when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
+Participants often chose 4 or 5 when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
 This shows overconfidence in their detection ability when using a choropleth map display.
@@
 \leavevmode\hypertarget{ref-atlas}{}%
-2. Queensland CC Australian Cancer Atlas (https://atlas.cancer.org.au).
+2. Cancer Council Queensland Australian Cancer Atlas (https://atlas.cancer.org.au).
 

### 2021-01-11 protocol.Rmd

@@
 Participants will evaluate 12 lineups, 6 of each plot type.
+Appendix A shows the experimental design visually.
 
@@
 ##	Recruitment strategies, timeframe
-Recruitment will take place via advertising on the Figure-Eight dashboards.
+
+Recruitment will take place via advertising on the Figure-Eight site.
+On this site the available tasks like this survey, are advertised to participants by the addition to the list of tasks available to contributors on the platform.
+Participants must select our task from the list to read the description of the task, and what is expected of them to be able to participate.
+
+Removed:
+[Recruitment will take place via advertising on the Figure-Eight dashboards.
 The Figure-Eight platform will advertise this as a "job" to potential participants, they will not be under any obligation to complete this task.
-We keep advertising until enough participants have completed the survey, then remove the advertisements and close the survey.
+We keep advertising until enough participants have completed the survey, then remove the advertisements and close the survey.]
 
@@
 ##	Participant withdrawal
-Participants can withdraw from the experiment at any time by quitting the survey.
+Participants can withdraw from the experiment at any time by quitting the survey, they with also be withdrawn if they do not provide a choice for more than 50% of the displays.
 
@@
 Test questions are the most important quality control mechanism in the Figure-Eight Platform.
+Participants will complete them to practice and prepare for the experiment questions.
+in our analysis stage, to use the responses from a participant they will need to reach an accuracy threshold of at least one correct choice.
+
+Removed:
+[Test questions are the most important quality control mechanism in the Figure-Eight Platform.
 Participants will complete them to practice and prepare for the experiment questions, they will need to reach an accuracy threshold we will set, to be allowed to participate in answering the experiment survey questions.
@@
 The Figure Eight procedures are followed: *Contributors that fail quiz mode are not paid and are permanently disqualified from working on your job.
-Participants will need to achieve a pre-determined accuracy threshold to be allowed to answer the questions in our survey.*
+Participants will need to achieve a pre-determined accuracy threshold to be allowed to answer the questions in our survey.*]
 
@@
 Data will be collected through survey distribution via a web application.
-Participants will access the application via a link from the Figure-Eight "job".
+Information and illustrative displays regarding the survey have been included in the word document 01_O_ETH_Survey_Data_Collection_Tool_V1_20191023.
+Participants will access the application via a link from the Figure-Eight task site.
+This will lead them to the web page that currently hosts the pilot study: https://ebsmonash.shinyapps.io/dingo/
 
@@
 
-```{r echo=FALSE, eval=TRUE, fig.height=5, fig.width=6, out.width="70%"}
+```{r echo=FALSE, eval=FALSE, fig.height=5, fig.width=6, out.width="70%"}
 # Code to compute the power for given sample size and alternative p
@@
 #  mutate(prob = pbinom(k-1, n, pA, lower.tail=FALSE)) 
-ggplot(pow, aes(x=n, y=pA, fill=prob, group=pA)) + 
+sample_fig <- ggplot(pow, aes(x=n, y=pA, fill=prob, group=pA)) + 
   geom_tile() +
@@
   theme_bw()
+ggsave(filename = "figures/sample_size.jpg", plot = sample_fig, width = 10, height = 10, units = "in")
+
 pow %>% filter(near(pA, 0.167, 0.001)) %>% filter(prob>0.7) %>% top_n(n=10) %>% kable(digits=3)
+```
+
+```{r sample_size_fig, out.width = "90%", out.height="90%"}
+library(knitr)
+library(tidyverse)
+knitr::include_graphics("figures/sample_size.jpg")
+```
+
+```{r sample_size_table, fig.cap="Chance of detection for sample sizes of 48 and 49."}
+tibble(n = c(48, 49),
+  k = c(7, 7),
+  pA = c(0.167, 0.167),
+  prob = c(0.713, 0.734)) %>% kable(digits=3)
 ```
@@
 Research expectations today require that publications use reproducible research protocols, requiring data to be available.
-De-identified, and privatised data will be made available will be made available via QUT's Research Data Finder, and, if required by the publisher, once the results are published also available on the journal article web site.
+The external survey data will be made available via QUT’s Research Data Finder, on github, and, if required by the publisher, once the results are published also available on the journal article web site.
 
@@
 
-Datasets produced from the project and that will *not* be available for public access will contain original demographic information about the participants and only the anonymous Figure-Eight contributor ID.
+Datasets produced from the project and that will be available for public access on github will be de-identified and only contain the responses to survey, and information regarding the participant demographics: age range, education level, gender, and whether they have lived in Australia.
+ If there are participants with unique sets of demographics, their data will be combined with larger categories to minimise the risks of reidentification.
 
-Datasets produced from the project and that *will be* available for public access on github will be de-identified and only contain the responses to survey.
-If there are participants with unique sets of demographics, their data will be combined with larger categories to minimise the risks of reidentification.
+Responses to the survey will be stored securely using a google sheet owned by Stephanie’s Monash University google account drive, accessible only to the researchers during the study through their password protected google drive accounts.
+This will contain the demographic information, at the coarse resolution specified in the data collection.
+
+Removed:
+[Datasets produced from the project and that will not be available for public access will contain original
+demographic information about the participants and only the anonymous Figure-Eight contributor ID.
+Datasets produced from the project and that will be available for public access on github will be de-identified
+and only contain the responses to survey. If there are participants with unique sets of demographics, their
+data will be combined with larger categories to minimise the risks of reidentification.]
 
@@
 
+Removed: 
+[Responses to the survey will be stored securely using a private google drive accessible only to the researchers
+during the study through their password protected google drive accounts. This will contain the demographic
+information, at the coarse resolution specified in the data collection.]
+
 ##	Record retention
 
-To ensure records are retained during and following the study the responses will be stored on the google drive immediately following the submission by participants.
+To ensure records are retained during and following the study the responses will be stored on the google sheet immediately following the submission by participants.
 At the conclusion of the survey, the data will remain in the password protected google drive account.
 
+Immediately following the submission by participants. At the conclusion of the survey, the data will remain in the password protected google drive account and on github
 During the analysis phase the researchers Stephanie and Dianne will make copies of the survey responses to their work devices (laptop computers), that are password protected.
-
-This data set will also be de-identified, by removing the demographic data, and saved on the QUT network drives, which are automatically backed-up nightly in two physical locations.
-The records of data analysis undertaken and the de-identified data will be stored on github as well as on QUT network drives.
 
@@
 
-The analysis scripts and the de-identified data will be available for secondary use by other researchers to reproduce these results and also use in future studies.
+Research expectations today require that publications use reproducible research protocols, requiring data to be available.
+The external survey data will be made available will be made available via QUT’s Research Data Finder, on github, and, if required by the publisher, once the results are published also available on the journal article web site.
+
+The analysis scripts and the data will be available for secondary use by other researchers to reproduce these results and also use in future studies.
 Participants will be asked to provide consent for this usage in the consent form.
@@
 
-A document on the web app is attached.
+## Appendix A {#sec:appendix_design}
+
+The experimental design plan shows the distribution of the null data sets to each type of trend model that will be tested. 
+It also states the location of the trend model in the lineup of 12 plots in a three row, four column grid.
+
+```{r design, fig.width = 10, fig.height=8}
+knitr::include_graphics("figures/skobakian_design.pdf")
+```
 

### 2021-03-24 kobakiancook/kobakiancook.Rmd
asa format

--- 2021-01-11 paper/paper.Rmd
@@
 ---
-title: "Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics"
-affiliation:
-  author-columnar: true         ## one column per author
-  #institution-columnar: true  ## one column per institution (multiple autors eventually)
-  # wide: true                  ## one column wide author/affiliation fields
-  institution:
-    - name: Queensland University of Technology
-      department: Science and Engineering Faculty
-      location: Brisbane, Australia
-      email: stephanie.kobakian@qut.edu.au
-      mark: 1
-      author:
+title: Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics
+
+# to produce blinded version set to 1
+blinded: 0
+
+authors: 
 - name: Stephanie Kobakian
-    - name: Monash University
-      department: Econometrics and Business Statistics Faculty
-      location: Melbourne, Australia
-      email: dicook@monash.edu
-      mark: 1
-      author:
+  thanks: The authors gratefully acknowledge ACEMS, the Australian Centre for Excllence in Mathematical and Statistical Fronteirs
+  affiliation: |
+    | Science and Engineering Faculty, Queensland University of Technology
+    | Brisbane, QLD, Australia
+
 - name: Dianne Cook
-keywords: ["statistics", "visual inference", "geospatial", "population"]
+  affiliation: |
+    | Econometrics and Business Statistics Faculty, Monash University
+    | Melbourne, VIC, Australia
+
+keywords:
+- statistics
+- visual inference
+- geospatial
+- population
+
 abstract: |
@@
 These findings should encourage map creators to implement alternative displays and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
-dev: pdf
+
 bibliography: paper.bib
-output:
-  bookdown::pdf_book: 
-      base_format: rticles::ieee_article
-      number_sections: true
-editor_options: 
-  chunk_output_type: inline
-link-citations: true
-citation_package: biblatex
-csl: springer-vancouver.csl
-header-includes: \usepackage{graphicx}
+output: rticles::asa_article
 ---
 
-<!-- Regular paper – 12 double column pages (Submissions may be up to 18 pages in length, subject to MOPC. All regular paper page limits include references and author biographies.) -->
+\section{Introduction}
+\label{sec:intro}
 
@@
 # Load Libraries
+library(broom)
+library(broom.mixed)
+library(cowplot)
+library(grid)
+library(ggthemes)
+library(kableExtra)
+library(knitr)
+library(lme4)
+library(png)
+library(RColorBrewer)
+library(readxl)
 library(tidyverse)
-library(readxl)
-library(broom)
-library(cowplot)
-library(png)
-library(grid)
-library(lme4)
-library(ggthemes)
-library(RColorBrewer)
-library(knitr)
-library(kableExtra)
 
@@
 
-Introduction
-=============
+\subsection{Introduction}
+\label{sec:int}
+
   <!-- General: comparison of displays, motivate hexagon tile map, enough info to motivate aims -->
@@
 The next section discusses the background of geographic data display and visual inference procedures.
-The [Methodology] section describes the methods for conducting the experiment and analysing the results.
-The results are summarized in the [Results] section.
+The \ref{sec:met} section describes the methods for conducting the experiment and analysing the results.
+The results are summarized in the \ref{sec:res} section.
 
-Background
-=============
+\section{Background}
+\label{sec:bg}
 
-## Spatial data displays
+\subsection{Spatial data displays}
+\label{sec:sdd}
 
@@
 Aggregating the statistic on administrative units, provides a level of privacy to individuals, while allowing the impact of the disease on the community to be analyzed.
-
-<!-- Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
-The rural communities in Australia operate on a much larger geographic space than small inner-city communities.
-When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
-This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention [@CTTMB].
-An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas [@NISCC].
-This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
-
-A choropleth map is not the only display that can be used for presenting geospatial data. 
-Alternative maps include various cartograms and tessellated tile maps. They allow other variables to be incorporated in the display to highlight the statistical values of various geographic areas.
--->
 
@@
 ```
-<!--
-This will create the figure as needed in the paper, but I can't get the width argument to work properly.
-\begin{figure*}[!t]
-\centering
-\includegraphics{paper_files/figure-latex/liver-1.pdf}
-\caption{A choropleth map (a), and hexagon tile map (b) of the smoothed average of liver cancer diagnoses for Australian males.
-The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
-The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.}
-\label{fig:liver2}
-\end{figure*}
--->
 
@@
 
-## Visual Inference
+\subsection{Visual Inference}
+\label{sec:vi}
 
-In order to assess the effectiveness of the hexagon tile map, the lineup protocol [@GIIV],[@BCHLLSW09] from visual inference procedures is employed.
+In order to assess the effectiveness of the hexagon tile map, the lineup protocol [@GIIV], [@BCHLLSW09] from visual inference procedures is employed.
 The approach mirrors classical statistical inference.
@@
 
-Methodology
-============
+\section{Methodology}
+\label{sec:met}
 
@@
 
-## Experimental factors
+\subsection{Experimental Factors}
+\label{sec:ef}
 
@@
 
-## Generating null data
+\subsection{Generating Null Data}
+\label{sec:gnd}
 
@@
 
-The R package `gstat` [@gstat] was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
+The R package $`gstat`$ [@gstat] was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
 
@@
 
-## Generating lineups
+\subsection{Generating Lineups}
+\label{sec:gld}
 
@@
 
-## Analysis
+\subsection{Analysis}
+\label{sec:an}
 
@@
 
-Plots will be made in R [@RCore], with the `ggplot2` package [@ggplot2].
+Plots will be made in R [@RCore], with the $`ggplot2`$ package [@ggplot2].
 
@@
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model. 
-The R [@RCore] `glmer()` function in the `lme4` [@lme4] package implements generalised linear mixed effect models.
+The R [@RCore] $`glmer()`$ function in the $`lme4`$ [@lme4] package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 
-The model specifies a logistic link, this means the predicted values from the `glmer` model should be back-transformed to fit between 0 and 1.
+The model specifies a logistic link, this means the predicted values from the $`glmer`$ model should be back-transformed to fit between 0 and 1.
 The predictions  $\widehat{p}(\eta)$ are transformed to be probabilities between 0 and 1 with the link specified below:
@@
 
-## Web application to collect responses
+\subsection{Web application to collect responses}
+\label{sec:watcr}
 
@@
 
-## Participants
+\subsection{Participants}
+\label{sec:pa}
 
@@
 
-## Demographic data collection
+\subsection{Demographic data collection}
+\label{sec:ddc}
 
@@
 
-Results
-============
+\section{Results}
+\label{sec:res}
 
@@
 
-## Participant demographics
+\subsection{Participant demographics}
+\label{sec:pd}
 
+## 
 Of the 92 participants, 67 were male, and 25 female. Most participants (56) had a Bachelors degree, 13 had a Masters degree, and the remaining 23 had high school diplomas.
 
-## Accuracy
+\subsection{Accuracy}
+\label{sec:acc}
 
@@
 The log odds of detection show in Table. \ref{tab:detect-glmer1} can be back transformed after taking the sum of all terms for the trend and type of display that are of interest.
-For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to `r round(exp(0.46+0.07)/(1+exp(0.46+0.07)), 2)` from `r round(exp(0.07)/(1+exp(0.07)),2)` for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
+For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to $`r round(exp(0.46+0.07)/(1+exp(0.46+0.07)), 2)`$ from $`r round(exp(0.07)/(1+exp(0.07)),2)`$ for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
 
-When a choropleth map display is used, the predicted detection rate for the Three Cities trend, `r round(exp(0.07-3.41)/(1+exp(0.07-3.41)),2)`; this is extremely low, especially compared to the NW-SE trend of `r round(exp(0.07)/(1+exp(0.07)),2)`.
-When the All Cities trend is presented in a choropleth display the predicted probability of detection is `r round(exp(0.07-1.34)/(1+exp(0.07-1.34)),2)`.
-The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend `r round(exp(0.46+0.07-3.41+2.44)/(1+exp(0.46+0.07-3.41+2.44)),2)` and All Cities trend `r round(exp(0.46+0.07-1.34+1.16)/(1+exp(0.46+0.07-1.34+1.16)),2)`.
+When a choropleth map display is used, the predicted detection rate for the Three Cities trend, $`r round(exp(0.07-3.41)/(1+exp(0.07-3.41)),2)`$; this is extremely low, especially compared to the NW-SE trend of $`r round(exp(0.07)/(1+exp(0.07)),2)`$.
+When the All Cities trend is presented in a choropleth display the predicted probability of detection is $`r round(exp(0.07-1.34)/(1+exp(0.07-1.34)),2)`$.
+The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend $`r round(exp(0.46+0.07-3.41+2.44)/(1+exp(0.46+0.07-3.41+2.44)),2)`$ and All Cities trend $`r round(exp(0.46+0.07-1.34+1.16)/(1+exp(0.46+0.07-1.34+1.16)),2)`$.
 
@@
 
-## Speed
+\subsection{Speed}
+\label{sec:sp}
 
@@
 
-## Certainty
+\subsection{Certainty}
+\label{sec:cer}
 
@@
 
-## Reason
+\subsection{Reason}
+\label{sec:rea}
 
@@
 
-Discussion
-============
+\subsection{Discussion}
+\label{sec:dis}
 
@@
 
-Conclusion
-============
+\section{Conclusion}
+\label{sec:con}
 
@@
 
-Acknowledgment
-==============
+\section{Acknowledgments}
+\label{sec:ack}
 
@@
 \newpage
-References {.numbered}
-==========

### 2021-03-24 kobakiancook/kobakiancook.tex
asa format

--- 2021-01-11 paper/paper.tex
@@
-%% template.tex
-%% from
-%% bare_conf.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE!
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-\documentclass[conference,final,]{IEEEtran}
-% Some Computer Society conferences also require the compsoc mode option,
-% but others use the standard conference format.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at:
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-%\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-%% BEGIN MY ADDITIONS %%
-
-\usepackage{longtable,booktabs}
-
-\usepackage[unicode=true]{hyperref}
-
-\hypersetup{
-            pdftitle={Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics},
-            pdfkeywords={statistics, visual inference, geospatial, population},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-
-% Pandoc toggle for numbering sections (defaults to be off)
-\setcounter{secnumdepth}{5}
-
-% Pandoc syntax highlighting
-
-% Pandoc header
-\usepackage{graphicx}
+% !TeX program = pdfLaTeX
+\documentclass[12pt]{article}
+\usepackage{amsmath}
+\usepackage{graphicx,psfrag,epsf}
+\usepackage{enumerate}
+\usepackage{natbib}
+\usepackage{textcomp}
+\usepackage[hyphens]{url} % not crucial - just used below for the URL
+\usepackage{hyperref}
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+%\pdfminorversion=4
+% NOTE: To produce blinded version, replace "0" with "1" below.
+\newcommand{\blind}{0}
+
+% DON'T change margins - should be 1 inch all around.
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-.5in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{1.3in}%
+\addtolength{\topmargin}{-.8in}%
+
+%% load any required packages here
+
+% Pandoc citation processing
+
 \usepackage{booktabs}
@@
 
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-%% END MY ADDITIONS %%
-
-\hyphenation{op-tical net-works semi-conduc-tor}
-
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-\title{Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics}
-
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
+
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\if0\blind
+{
+  \title{\bf Comparing the Effectiveness of the Choropleth Map with a
+Hexagon Tile Map for Communicating Cancer Statistics}
 
   \author{
-
-%% ---- classic IEEETrans wide authors' list ----------------
- % -- end affiliation.wide
-%% ----------------------------------------------------------
-
-%% ---- classic IEEETrans one column per institution --------
- %% -- end if/affiliation.institution-columnar
-%% ----------------------------------------------------------
-
-%% ---- one column per author, classic/default IEEETrans ----
- % -- beg affiliation.author-columnar
-  %% -- beg for/affiliation.institution.author
-\IEEEauthorblockN{
-Stephanie Kobakian
+        Stephanie Kobakian \thanks{The authors gratefully acknowledge
+ACEMS, the Australian Centre for Excllence in Mathematical and
+Statistical Fronteirs} \\
+    Science and Engineering Faculty, Queensland University of
+Technology\\
+Brisbane, QLD, Australia\\
+     and \\     Dianne Cook \\
+    Econometrics and Business Statistics Faculty, Monash University\\
+Melbourne, VIC, Australia\\
       }
-\IEEEauthorblockA{Queensland University of Technology\\
-Science and Engineering Faculty\\
-Brisbane, Australia
-\\stephanie.kobakian@qut.edu.au
-}
- %% -- end for/affiliation.institution.author
-\and
-  %% -- beg for/affiliation.institution.author
-\IEEEauthorblockN{
-Dianne Cook
-}
-\IEEEauthorblockA{Monash University\\
-Econometrics and Business Statistics Faculty\\
-Melbourne, Australia
-\\dicook@monash.edu
-}
- %% -- end for/affiliation.institution.author
- %% -- end for/affiliation.institution
- %% -- end if/affiliation.institution-columnar
-%% ----------------------------------------------------------
-
-}
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-%
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3},
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
   \maketitle
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract
+} \fi
+
+\if1\blind
+{
+  \bigskip
+  \bigskip
+  \bigskip
+  \begin{center}
+    {\LARGE\bf Comparing the Effectiveness of the Choropleth Map with a
+Hexagon Tile Map for Communicating Cancer Statistics}
+  \end{center}
+  \medskip
+} \fi
+
+\bigskip
 \begin{abstract}
-The choropleth map display is commonly used for communicating spatial distributions across geographic areas.
-However, when choropleths are used the size of the geographic units will influence the understanding of the distribution derived by map users.
-The hexagon tile map is presented as an alternative display for visualizing population related distributions effectively.
-Visual inference is used to measure the power of the hexagon tile map design, and the choropleth is used as a comparison.
-The hexagon tile map display is tested using a distribution that is directly related to the geography, with values monotonically increasing from the North-West to South-East areas of Australia.
-This study finds in a hexagon tile map lineup the single map that contains a population related distribution is detected with greater probability than the same data displayed in a choropleth map.
-These findings should encourage map creators to implement alternative displays and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
+The choropleth map display is commonly used for communicating spatial
+distributions across geographic areas. However, when choropleths are
+used the size of the geographic units will influence the understanding
+of the distribution derived by map users. The hexagon tile map is
+presented as an alternative display for visualizing population related
+distributions effectively. Visual inference is used to measure the power
+of the hexagon tile map design, and the choropleth is used as a
+comparison. The hexagon tile map display is tested using a distribution
+that is directly related to the geography, with values monotonically
+increasing from the North-West to South-East areas of Australia. This
+study finds in a hexagon tile map lineup the single map that contains a
+population related distribution is detected with greater probability
+than the same data displayed in a choropleth map. These findings should
+encourage map creators to implement alternative displays and consider a
+hexagon tile map when presenting spatial distributions of heterogeneous
+areas.
 \end{abstract}
 
-% keywords
-\begin{IEEEkeywords}
-statistics; visual inference; geospatial; population
-\end{IEEEkeywords}
-
-% use for special paper notices
-
-% make the title area
-\maketitle
-
-% no keywords
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-This study compares the effectiveness of the spatial display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics.
-The choropleth map is the traditional method for visualizing aggregated statistics across administrative boundaries.
-The hexagon tile map builds on existing displays, such as the cartogram, and tessellated hexagon displays.
-A hexagon tile map forgoes the familiar boundaries, in favor of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location.
-It differs in the relaxed requirement to have connected hexagons, and allows sparsely located hexagons.
-This type of display may be useful for other countries, and other purposes.
-The algorithm to construct a hexagon tile map is available in the R package sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]}.
-
-The hexagon tile map was designed for Australia, motivated by a need to display spatial statistics for the Australian Cancer Atlas.
-None of the existing approaches for creating cartograms or hexagon tiling perform well for the Australian landscape, which has vast open spaces and concentrations of population in small regions clustered on the coastlines.
-
-The Australian Cancer Atlas {[}\protect\hyperlink{ref-atlas}{2}{]} is an online interactive web tool created to explore the burden of cancer on Australian communities.
+\noindent%
+{\it Keywords:} statistics, visual inference, geospatial, population
+\vfill
+
+\newpage
+\spacingset{1.45} % DON'T change the spacing!
+
+\section{Introduction}
+\label{sec:intro}
+
+\subsection{Introduction}
+\label{sec:int}
+
+This study compares the effectiveness of the spatial display, a hexagon
+tile map, against the standard, a choropleth map, for communicating
+information about disease statistics. The choropleth map is the
+traditional method for visualizing aggregated statistics across
+administrative boundaries. The hexagon tile map builds on existing
+displays, such as the cartogram, and tessellated hexagon displays. A
+hexagon tile map forgoes the familiar boundaries, in favor of
+representing each geographic unit as an equally sized hexagon, placed
+approximately in the correct spatial location. It differs in the relaxed
+requirement to have connected hexagons, and allows sparsely located
+hexagons. This type of display may be useful for other countries, and
+other purposes. The algorithm to construct a hexagon tile map is
+available in the R package sugarbag \citep{sugarbag}.
+
+The hexagon tile map was designed for Australia, motivated by a need to
+display spatial statistics for the Australian Cancer Atlas. None of the
+existing approaches for creating cartograms or hexagon tiling perform
+well for the Australian landscape, which has vast open spaces and
+concentrations of population in small regions clustered on the
+coastlines.
+
+The Australian Cancer Atlas \citep{atlas} is an online interactive web
+tool created to explore the burden of cancer on Australian communities.
 There are many cancer types to be explored individually or aggregated.
-The Australian Cancer Atlas allows users to explore the patterns in the distributions of cancer statistics over the geographic space of Australia.
-It uses a choropleth map display and diverging color scheme to draw attention to relationships between neighboring areas.
-The hexagon tile map may be a useful alternative display to enhance the atlas.
-
-The experiment was conducted using the lineup protocol, a visual inference procedure {[}\protect\hyperlink{ref-GIIV}{3}{]}, to objectively test the effectiveness of the two displays.
-
-The paper is organised as follows.
-The next section discusses the background of geographic data display and visual inference procedures.
-The \protect\hyperlink{methodology}{Methodology} section describes the methods for conducting the experiment and analysing the results.
-The results are summarized in the \protect\hyperlink{results}{Results} section.
-
-\hypertarget{background}{%
-\section{Background}\label{background}}
-
-\hypertarget{spatial-data-displays}{%
-\subsection{Spatial data displays}\label{spatial-data-displays}}
-
-Spatial visualisations communicate the distribution of statistics over geographic landscapes.
-The choropleth map {[}\protect\hyperlink{ref-EI}{4}{]}, {[}\protect\hyperlink{ref-BCM}{5}{]} is a traditional display.
-It is used to present statistics that have been aggregated on geographic units.
-Creating a choropleth map involves drawing polygons representing the administrative boundaries, and filling with colour mapped to the value of the statistic.
-The choropleth map places the statistic in the context of the spatial domain, so that the reader can see whether there are spatial trends, clusters or anomalies.
-This is important for digesting disease patterns.
-If there is a trend it may imply that the disease is spreading from one location to another.
-If there is a cluster, or an anomaly, there may be a localized outbreak of the disease.
-Aggregating the statistic on administrative units, provides a level of privacy to individuals, while allowing the impact of the disease on the community to be analyzed.
+The Australian Cancer Atlas allows users to explore the patterns in the
+distributions of cancer statistics over the geographic space of
+Australia. It uses a choropleth map display and diverging color scheme
+to draw attention to relationships between neighboring areas. The
+hexagon tile map may be a useful alternative display to enhance the
+atlas.
+
+The experiment was conducted using the lineup protocol, a visual
+inference procedure \citep{GIIV}, to objectively test the effectiveness
+of the two displays.
+
+The paper is organised as follows. The next section discusses the
+background of geographic data display and visual inference procedures.
+The \ref{sec:met} section describes the methods for conducting the
+experiment and analysing the results. The results are summarized in the
+\ref{sec:res} section.
+
+\section{Background}
+\label{sec:bg}
+
+\subsection{Spatial data displays}
+\label{sec:sdd}
+
+~\\
+Spatial visualisations communicate the distribution of statistics over
+geographic landscapes. The choropleth map \citep{EI}, \citep{BCM} is a
+traditional display. It is used to present statistics that have been
+aggregated on geographic units. Creating a choropleth map involves
+drawing polygons representing the administrative boundaries, and filling
+with colour mapped to the value of the statistic. The choropleth map
+places the statistic in the context of the spatial domain, so that the
+reader can see whether there are spatial trends, clusters or anomalies.
+This is important for digesting disease patterns. If there is a trend it
+may imply that the disease is spreading from one location to another. If
+there is a cluster, or an anomaly, there may be a localized outbreak of
+the disease. Aggregating the statistic on administrative units, provides
+a level of privacy to individuals, while allowing the impact of the
+disease on the community to be analyzed.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/liver-1} \caption{A choropleth map of the smoothed average of liver cancer diagnoses for Australian males.
+\includegraphics[width=1\linewidth]{kobakiancook_files/figure-latex/liver-1} \caption{A choropleth map of the smoothed average of liver cancer diagnoses for Australian males.
 The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/liver-hex-1} \caption{A hexagon tile map of the smoothed average of liver cancer diagnoses for Australian males.
+\includegraphics[width=1\linewidth]{kobakiancook_files/figure-latex/liver-hex-1} \caption{A hexagon tile map of the smoothed average of liver cancer diagnoses for Australian males.
 The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
@@
 
-The choropleth map is an effective spatial display if the size of the geographic units is relatively uniform.
-This is not the case for most countries.
-Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips.
-A choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population related distribution of the statistic {[}\protect\hyperlink{ref-CBATCC}{6}{]}.
-\emph{Land doesn't get cancer, people do} -- a more effective way to communicate the spatial distributions of cancer statistics is needed.
-
-A cartogram is a general solution for better displaying a population-based statistic.
-It transforms the geographic map base to reflect the population in the geographic region, while preserving some aspects of the geographic location.
-There are several cartogram algorithms {[}\protect\hyperlink{ref-ACTUC}{7}{]}, {[}\protect\hyperlink{ref-CBATCC}{6}{]}; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
-The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units but can result in losing the familiar geographic information.
-For Australia, the transformations warp the country so that it is no longer recognizable.
-
-Alternative algorithms make various trade offs between familiar shapes and representation of geographic units.
-The non-contiguous cartogram method {[}\protect\hyperlink{ref-NAC}{8}{]} keeps the shapes of geographic units intact, and changes the size of the shape.
-This method disconnects areas creating empty space on the display losing the continuity of the spatial display of the statistic.
-The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{7}{]} represents each unit as a circle, sized according to the value of the statistic.
-The neighbour relationships are mostly maintained by how the circles touch.
-A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{9}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{10}{]}.
-There have been thorough reviews of the array of methods, as suitable for cancer atlas displays {[}\protect\hyperlink{ref-review}{11}{]}, {[}\protect\hyperlink{ref-BCM}{5}{]}.
-
-The hexagon tile map algorithm, automatically matches spatial regions to their nearest hexagon tile, from a grid of tiles.
-It has the effect of spreading out the inner city areas while maintaining the spatial locations or regions in remote areas.
-The algorithm is available in the R package, sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]}.
-Fig.
-\ref{fig:liver} shows the hexagon tile map, along with the choropleth map of liver cancer rates in Australia.
-Colour maps from substantially below average (blue) to substantially above average (red) rates.
-The inner city areas have expanded, making it possible to see the cancer incidence in the small, densely populated areas.
-Remote regions are represented by isolated hexagons, which is not ideal, but maintains the spatial location of these data values.
-It is of interest to know how well the spatial distribution is perceived for this display, in comparison to the choropleth.
-
-\hypertarget{visual-inference}{%
-\subsection{Visual Inference}\label{visual-inference}}
-
-In order to assess the effectiveness of the hexagon tile map, the lineup protocol {[}\protect\hyperlink{ref-GIIV}{3}{]},{[}\protect\hyperlink{ref-BCHLLSW09}{12}{]} from visual inference procedures is employed.
-The approach mirrors classical statistical inference.
-The procedures for doing a power comparison of competing plot designed, outlined in {[}\protect\hyperlink{ref-GTPCCD}{13}{]}, are followed.
-
-In classical statistical inference hypothesis testing is conducted by comparing the value of a test statistic on a standard reference distribution, computed assuming the null hypothesis is true.
-If the value is extreme, the null hypothesis is rejected, because the test statistic value is unlikely to have been so extreme if it was true.
-In the lineup protocol, the plot plays the role of the test statistic, and the data plot is embedded in a field of null plots.
-Defining the plot using a grammar of graphics {[}\protect\hyperlink{ref-ggplot2}{14}{]} makes it a functional mapping of the variables and thus, it can be considered to be a statistic.
-With the same data, two different plots can be considered to be competing statistics, one possibly a more powerful statistic than the other.
-
-To do hypothesis testing with the lineup protocol requires human evaluation.
-The human judge is required to identify the most different plot among the field of plots.
-If this corresponds to the data plot -- the test statistic -- the null hypothesis is rejected.
-It means that the data plot is extreme relative to the reference distribution of null plots.
-
-The null hypothesis is explicitly provided by the grammatical plot description.
-For example, if a histogram is the plot type being used, the null might be that the underlying distribution of the data is a Gaussian.
-Null data would be generated by simulating from a normal model, with the same mean and standard deviation as the data.
-In practice, the null hypothesis used is generic, such as \emph{there is NO structure or a pattern in the plot}, and contrasted to an alternative that there is structure.
-
-The chance that an observer picks the data plot out of a lineup of size \(m\) plots accidentally, if the null hypothesis is true is \(1/m\).
-With \(K\) observers, the probability of \(k\) randomly choosing the data plot, roughly follows a binomial distribution with \(p=1/m\).
-Fig.
-\ref{fig:lineup} shows a lineup of the hexagon tile map, of size \(m=12\).
-Plot 3 is the data plot, and the remaining 11 are plots of null data.
+The choropleth map is an effective spatial display if the size of the
+geographic units is relatively uniform. This is not the case for most
+countries. Size heterogeneity in administrative units is particularly
+extreme in Australia: most of the landscape of Australia is sparsely
+settled, with the population densely clustered into the narrow coastal
+strips. A choropleth map focuses attention on the geography, and for
+heterogeneously sized areas it presents a biased view of the population
+related distribution of the statistic \citep{CBATCC}. \emph{Land doesn't
+get cancer, people do} -- a more effective way to communicate the
+spatial distributions of cancer statistics is needed.
+
+A cartogram is a general solution for better displaying a
+population-based statistic. It transforms the geographic map base to
+reflect the population in the geographic region, while preserving some
+aspects of the geographic location. There are several cartogram
+algorithms \citep{ACTUC}, \citep{CBATCC}; each involves shifting the
+boundaries of geographic units, using the value of the statistic to
+increase or decrease the area taken by the geographic unit on the map.
+The changes to the boundaries result in cartograms that accurately
+communicate population by map area for each of the geographic units but
+can result in losing the familiar geographic information. For Australia,
+the transformations warp the country so that it is no longer
+recognizable.
+
+Alternative algorithms make various trade offs between familiar shapes
+and representation of geographic units. The non-contiguous cartogram
+method \citep{NAC} keeps the shapes of geographic units intact, and
+changes the size of the shape. This method disconnects areas creating
+empty space on the display losing the continuity of the spatial display
+of the statistic. The Dorling cartogram \citep{ACTUC} represents each
+unit as a circle, sized according to the value of the statistic. The
+neighbour relationships are mostly maintained by how the circles touch.
+A similar approach was pioneered by Raisz \citeyearpar{RSCW}, using
+rectangles that tile to align borders of neighbours \citep{CDWCS}. There
+have been thorough reviews of the array of methods, as suitable for
+cancer atlas displays \citep{review}, \citep{BCM}.
+
+The hexagon tile map algorithm, automatically matches spatial regions to
+their nearest hexagon tile, from a grid of tiles. It has the effect of
+spreading out the inner city areas while maintaining the spatial
+locations or regions in remote areas. The algorithm is available in the
+R package, sugarbag \citep{sugarbag}. Fig. \ref{fig:liver} shows the
+hexagon tile map, along with the choropleth map of liver cancer rates in
+Australia. Colour maps from substantially below average (blue) to
+substantially above average (red) rates. The inner city areas have
+expanded, making it possible to see the cancer incidence in the small,
+densely populated areas. Remote regions are represented by isolated
+hexagons, which is not ideal, but maintains the spatial location of
+these data values. It is of interest to know how well the spatial
+distribution is perceived for this display, in comparison to the
+choropleth.
+
+\subsection{Visual Inference}
+\label{sec:vi}
+
+In order to assess the effectiveness of the hexagon tile map, the lineup
+protocol \citep{GIIV}, \citep{BCHLLSW09} from visual inference
+procedures is employed. The approach mirrors classical statistical
+inference. The procedures for doing a power comparison of competing plot
+designed, outlined in \citet{GTPCCD}, are followed.
+
+In classical statistical inference hypothesis testing is conducted by
+comparing the value of a test statistic on a standard reference
+distribution, computed assuming the null hypothesis is true. If the
+value is extreme, the null hypothesis is rejected, because the test
+statistic value is unlikely to have been so extreme if it was true. In
+the lineup protocol, the plot plays the role of the test statistic, and
+the data plot is embedded in a field of null plots. Defining the plot
+using a grammar of graphics \citep{ggplot2} makes it a functional
+mapping of the variables and thus, it can be considered to be a
+statistic. With the same data, two different plots can be considered to
+be competing statistics, one possibly a more powerful statistic than the
+other.
+
+To do hypothesis testing with the lineup protocol requires human
+evaluation. The human judge is required to identify the most different
+plot among the field of plots. If this corresponds to the data plot --
+the test statistic -- the null hypothesis is rejected. It means that the
+data plot is extreme relative to the reference distribution of null
+plots.
+
+The null hypothesis is explicitly provided by the grammatical plot
+description. For example, if a histogram is the plot type being used,
+the null might be that the underlying distribution of the data is a
+Gaussian. Null data would be generated by simulating from a normal
+model, with the same mean and standard deviation as the data. In
+practice, the null hypothesis used is generic, such as \emph{there is NO
+structure or a pattern in the plot}, and contrasted to an alternative
+that there is structure.
+
+The chance that an observer picks the data plot out of a lineup of size
+\(m\) plots accidentally, if the null hypothesis is true is \(1/m\).
+With \(K\) observers, the probability of \(k\) randomly choosing the
+data plot, roughly follows a binomial distribution with \(p=1/m\). Fig.
+\ref{fig:lineup} shows a lineup of the hexagon tile map, of size
+\(m=12\). Plot 3 is the data plot, and the remaining 11 are plots of
+null data.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/lineup-1} \caption{This lineup of twelve hexagon tile map displays contains one map with a real population related structure.
+\includegraphics[width=1\linewidth]{kobakiancook_files/figure-latex/lineup-1} \caption{This lineup of twelve hexagon tile map displays contains one map with a real population related structure.
 The rest are null plots that contain spatial correlation between neighbours.}\label{fig:lineup}
@@
 
-In order to determine the effectiveness of a type of display, this probability is less relevant than the overall proportion of observers who pick the data plot, \(k/K\).
-The power of the test statistic (data plot) is provided by this proportion.
-Power in a statistical sense is the ability of the statistic to \emph{produce a rejection} of the null hypothesis, if it is indeed \emph{not true}.
-With the same data plotted using two different displays, the display with the highest proportion of people who choose the data plot would be considered to be the most powerful statistic.
-
-\hypertarget{methodology}{%
-\section{Methodology}\label{methodology}}
-
-This study aims to answer two key questions around the presentation of spatial distributions:
+In order to determine the effectiveness of a type of display, this
+probability is less relevant than the overall proportion of observers
+who pick the data plot, \(k/K\). The power of the test statistic (data
+plot) is provided by this proportion. Power in a statistical sense is
+the ability of the statistic to \emph{produce a rejection} of the null
+hypothesis, if it is indeed \emph{not true}. With the same data plotted
+using two different displays, the display with the highest proportion of
+people who choose the data plot would be considered to be the most
+powerful statistic.
+
+\section{Methodology}
+\label{sec:met}
+
+This study aims to answer two key questions around the presentation of
+spatial distributions:
 
@@
 \item
-  Are spatial disease trends that impact highly populated small areas detected with higher accuracy, when viewed in a hexagon tile map?
-\item
-  Are people faster in detecting spatial disease trends that impact highly populated small areas when using a hexagon tile map?
+  Are spatial disease trends that impact highly populated small areas
+  detected with higher accuracy, when viewed in a hexagon tile map?
+\item
+  Are people faster in detecting spatial disease trends that impact
+  highly populated small areas when using a hexagon tile map?
 \end{enumerate}
 
-Additional considerations when completing this experimental task included the difficulty experienced by participants and the certainty they had in their decision.
-
-Australia is used for the study, with Statistical Area 3 (SA3) {[}\protect\hyperlink{ref-abs2016}{15}{]} as the geographic units.
-The results should apply broadly to any other geographic area of interest.
-
-\hypertarget{experimental-factors}{%
-\subsection{Experimental factors}\label{experimental-factors}}
-
-The primary factor in the experiment is the plot type.
-The secondary factor is a trend model.
-Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to do well, and two with differing level of inner city hot spots.
-These latter two reflect the structure seen in the liver cancer data (Fig.
-\ref{fig:liver}).
-This produces six treatment levels:
+Additional considerations when completing this experimental task
+included the difficulty experienced by participants and the certainty
+they had in their decision.
+
+Australia is used for the study, with Statistical Area 3 (SA3)
+\citep{abs2016} as the geographic units. The results should apply
+broadly to any other geographic area of interest.
+
+\subsection{Experimental Factors}
+\label{sec:ef}
+
+The primary factor in the experiment is the plot type. The secondary
+factor is a trend model. Three trend models were developed, one
+mirroring a large spatial trend for which the choropleth would be
+expected to do well, and two with differing level of inner city hot
+spots. These latter two reflect the structure seen in the liver cancer
+data (Fig. \ref{fig:liver}). This produces six treatment levels:
 
@@
 \item
-  Trend: \emph{South-East to North-West; Locations in three population centres; Locations in multiple population centres, }
+  Trend: \emph{South-East to North-West; Locations in three population
+  centres; Locations in multiple population centres, }
 \end{itemize}
 
-Data is generated for each of the trend models, with four replicates, and each displayed both as a choropleth and as a hexagon tile map, which yields 12 data sets, and 24 data plots.
-This set of displays is divided in half, providing two sets of 12 displays, Group A and Group B.
-Participants were randomly allocated to Group A or B.
-Participants saw a data set only once, either as a choropleth or as a hexagon tile map.
-Table \ref{fig:exp-design} summarises the design and the allocation of the displays.
+Data is generated for each of the trend models, with four replicates,
+and each displayed both as a choropleth and as a hexagon tile map, which
+yields 12 data sets, and 24 data plots. This set of displays is divided
+in half, providing two sets of 12 displays, Group A and Group B.
+Participants were randomly allocated to Group A or B. Participants saw a
+data set only once, either as a choropleth or as a hexagon tile map.
+Table \ref{fig:exp-design} summarises the design and the allocation of
+the displays.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/exp-design-1} \caption{The experimental design used in the visual inference study.}\label{fig:exp-design}
+\includegraphics[width=1\linewidth]{kobakiancook_files/figure-latex/exp-design-1} \caption{The experimental design used in the visual inference study.}\label{fig:exp-design}
 \end{figure}
 
-\hypertarget{generating-null-data}{%
-\subsection{Generating null data}\label{generating-null-data}}
-
-Null data needs to be data with no (interesting) structure.
-In most scenarios, permutation is the main approach for generating null plots.
-It is used to break association between variables, while maintaining marginal distributions.
-This is too simple for spatial data.
-In spatial data, a key feature is the spatial dependence or smoothness over the landscape.
-To do something simple, like permute the values relative to the geographic location would produce null plots which are too chaotic, and the data plot will be recognisable for its smoothness rather than any structure of interest.
-
-For spatial data, null data is stationary data, where the mean, variance and spatial dependence are constant over the geographic units.
-Stationary data is specified by a variogram model {[}\protect\hyperlink{ref-POG}{16}{]}.
-Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots.
-The parameters for the Gaussian model were sill=1, range=0.3 with the variance generated by a standard normal distribution.
-
-The R package \texttt{gstat} {[}\protect\hyperlink{ref-gstat}{17}{]} was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
-
-The null model imposed by our hypothesis suggests that neighbors are related.
-The randomness induced when generating the null data was smoothed to mirror the practices employed by the Australian Cancer Atlas statisticians.
-In these 12 sets of data, each of the 12 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas, without implementing uncertainty via transparency.
-
-A list of neighbors for each geographic unit was generated to use when smoothing the distributions.
-For each geographic unit the same spatial smoother was applied in each layer of smoothing.
-It kept half of the units' previous value, and derived the new half as the mean of the values of its neighbors at the previous layer of smoothing.
-
-This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the Liver cancer distribution (Fig. \ref{fig:liver}).
-
-\hypertarget{generating-lineups}{%
-\subsection{Generating lineups}\label{generating-lineups}}
-
-For each trend model, four real data displays were created by manipulating the centroid values of each of the SA3 geographic units.
-
-The North West to South East (NW-SE) distribution was created using a linear equation of the centroid longitude and latitude values.
-
-The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia, calculated when creating the hexagon tile map using the sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]} package.
-201 of the 336 SA3s were considered greater capital city areas, the values of these areas were increased to create red clusters.
-The amount was chosen to make clusters around the cities visible in the choropleth display even if they were not overtly noticeable.
-
-A similar selection process was applied to the Three Cities' trend model.
-However, for each of the four replicates for the Three Cities trend, a random sample of capital cities was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart.
-Only values of the areas nearest to the three cities were increased to create clusters.
-
-One of the lineup locations was chosen to embed the real trend model map, in each of the four replicates, for the three trend models.
-The location was chosen from a sub sample of the 12 possible locations.
-The chance of reptition using resampling was introduced to prevent participants from inducing the location by elimination, the locations 1, 7, 10 and 11 were not used.
-
-As seen in Fig \ref{fig:exp-design}, the choropleth and hexagon display used the same location for the real data display of the trend model was added to the spatially correlated null values for each lineup.
-Each set of lineup data was used to produce a choropleth map lineup and hexagon tile map lineup.
-These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
-
-For each of the 144 individual maps, the values for each geographic area were rescaled to create a similar color scale from deep blue to dark red within each map.
-This meant at least one geographic unit was coloured dark blue, and at least one was red, in every map display of every lineup.
-
-For the geographic NW-SE distribution, this resulted in the smallest values of the trend model (blue) occurring in Western Australia, the North West of Australia, and the largest values of the trend model (red) occurring in the South East.
-This resulted in Tasmania being colored completely red.
-
-For the population related displays, the clusters in the cities appeared more red than the rest of Australia.
-
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
+\subsection{Generating Null Data}
+\label{sec:gnd}
+
+Null data needs to be data with no (interesting) structure. In most
+scenarios, permutation is the main approach for generating null plots.
+It is used to break association between variables, while maintaining
+marginal distributions. This is too simple for spatial data. In spatial
+data, a key feature is the spatial dependence or smoothness over the
+landscape. To do something simple, like permute the values relative to
+the geographic location would produce null plots which are too chaotic,
+and the data plot will be recognisable for its smoothness rather than
+any structure of interest.
+
+For spatial data, null data is stationary data, where the mean, variance
+and spatial dependence are constant over the geographic units.
+Stationary data is specified by a variogram model \citep{POG}.
+Simulating from a variogram model, where the spatial dependence is
+specified, generates the stationary spatial data used for the null
+plots. The parameters for the Gaussian model were sill=1, range=0.3 with
+the variance generated by a standard normal distribution.
+
+The R package \(`gstat`\) \citep{gstat} was used to simulate 144 null
+sets, 12 data sets for each plot in a lineup, and 12 sets for 12
+lineups.
+
+The null model imposed by our hypothesis suggests that neighbors are
+related. The randomness induced when generating the null data was
+smoothed to mirror the practices employed by the Australian Cancer Atlas
+statisticians. In these 12 sets of data, each of the 12 maps were
+smoothed several times to replicate the spatial autocorrelation seen in
+cancer data sets presented in the Australian Cancer Atlas, without
+implementing uncertainty via transparency.
+
+A list of neighbors for each geographic unit was generated to use when
+smoothing the distributions. For each geographic unit the same spatial
+smoother was applied in each layer of smoothing. It kept half of the
+units' previous value, and derived the new half as the mean of the
+values of its neighbors at the previous layer of smoothing.
+
+This smoothing allowed neighbors to be related to each other, but also
+allowed outliers, and showed distributions similar to the Liver cancer
+distribution (Fig. \ref{fig:liver}).
+
+\subsection{Generating Lineups}
+\label{sec:gld}
+
+For each trend model, four real data displays were created by
+manipulating the centroid values of each of the SA3 geographic units.
+
+The North West to South East (NW-SE) distribution was created using a
+linear equation of the centroid longitude and latitude values.
+
+The All Cities trend model was created using the distance from the
+centroid of each geographic unit to the closest capital city in
+Australia, calculated when creating the hexagon tile map using the
+sugarbag \citep{sugarbag} package. 201 of the 336 SA3s were considered
+greater capital city areas, the values of these areas were increased to
+create red clusters. The amount was chosen to make clusters around the
+cities visible in the choropleth display even if they were not overtly
+noticeable.
+
+A similar selection process was applied to the Three Cities' trend
+model. However, for each of the four replicates for the Three Cities
+trend, a random sample of capital cities was taken from Sydney,
+Brisbane, Melbourne, Adelaide, Perth, and Hobart. Only values of the
+areas nearest to the three cities were increased to create clusters.
+
+One of the lineup locations was chosen to embed the real trend model
+map, in each of the four replicates, for the three trend models. The
+location was chosen from a sub sample of the 12 possible locations. The
+chance of reptition using resampling was introduced to prevent
+participants from inducing the location by elimination, the locations 1,
+7, 10 and 11 were not used.
+
+As seen in Fig \ref{fig:exp-design}, the choropleth and hexagon display
+used the same location for the real data display of the trend model was
+added to the spatially correlated null values for each lineup. Each set
+of lineup data was used to produce a choropleth map lineup and hexagon
+tile map lineup. These matched pairs were split between Group A and
+Group B according to the 2 x 3 factor experimental design depicted in
+\ref{fig:exp-design}.
+
+For each of the 144 individual maps, the values for each geographic area
+were rescaled to create a similar color scale from deep blue to dark red
+within each map. This meant at least one geographic unit was coloured
+dark blue, and at least one was red, in every map display of every
+lineup.
+
+For the geographic NW-SE distribution, this resulted in the smallest
+values of the trend model (blue) occurring in Western Australia, the
+North West of Australia, and the largest values of the trend model (red)
+occurring in the South East. This resulted in Tasmania being colored
+completely red.
+
+For the population related displays, the clusters in the cities appeared
+more red than the rest of Australia.
+
+\subsection{Analysis}
+\label{sec:an}
 
@@
 
-The first step in the data cleaning process involved checking that survey responses collected for each participants were only included once in the data set.
-The data cleaning process also involved filtering out participants' who did not provide at least three unique choices when considering each of the twelve lineups.
-These participants achieved a detection rate of 0.
-If participants had made various plot choices for the 12 displays they saw they were still included in the dataset.
+The first step in the data cleaning process involved checking that
+survey responses collected for each participants were only included once
+in the data set. The data cleaning process also involved filtering out
+participants' who did not provide at least three unique choices when
+considering each of the twelve lineups. These participants achieved a
+detection rate of 0. If participants had made various plot choices for
+the 12 displays they saw they were still included in the dataset.
 
@@
 
-Basic descriptive statistics were used to contrast the detection rate for the two types of displays.
-Comparison was also made across the trend models, contrasting the mean and standard detection rate for each group, who had seen the different map display type for each replicate.
-
-Side-by-side dot plots were made of accuracy (efficiency) against map type, faceted by trend model type.
-
-Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.
-
-Plots will be made in R {[}\protect\hyperlink{ref-RCore}{18}{]}, with the \texttt{ggplot2} package {[}\protect\hyperlink{ref-ggplot2}{14}{]}.
+Basic descriptive statistics were used to contrast the detection rate
+for the two types of displays. Comparison was also made across the trend
+models, contrasting the mean and standard detection rate for each group,
+who had seen the different map display type for each replicate.
+
+Side-by-side dot plots were made of accuracy (efficiency) against map
+type, faceted by trend model type.
+
+Similar plots were made of the feedback and demographic variables -
+reason for choice, reported difficulty, gender, age, education, having
+lived in Australia - against the design variables.
+
+Plots will be made in R \citep{RCore}, with the \(`ggplot2`\) package
+\citep{ggplot2}.
 
@@
 
-The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R {[}\protect\hyperlink{ref-RCore}{18}{]} \texttt{glmer()} function in the \texttt{lme4} {[}\protect\hyperlink{ref-lme4}{19}{]} package implements generalised linear mixed effect models.
-The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
+The likelihood of detecting the data plot in the lineup can be modelled
+using a linear mixed effects model. The R \citep{RCore} \(`glmer()`\)
+function in the \(`lme4`\) \citep{lme4} package implements generalised
+linear mixed effect models. The model used includes the two main effects
+map type and trend model, which gives the fixed effects model to be:
 
@@
 
-where \(y_{ij} = 0, 1\) is the logg odds for whether the subject detected the data plot, \(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect, \(\delta_j\) is the trend model effect.
-We are allowing for an interaction between map type and trend model as the response is binary, so a logistic model was used.
-As each participant provides results from 12 lineups, this model can account for each individual participants' abilities as it includes a subject-specific random intercept.
-
-The model specifies a logistic link, this means the predicted values from the \texttt{glmer} model should be back-transformed to fit between 0 and 1.
-The predictions \(\widehat{p}(\eta)\) are transformed to be probabilities between 0 and 1 with the link specified below:
-
-\[\widehat{p}(\eta) = \frac{e^{\eta}}{1 + e^{\eta}}\] \label{eq:transform}
-\[\eta = f(\tau_i,\delta_j)\]
-
-\hypertarget{web-application-to-collect-responses}{%
-\subsection{Web application to collect responses}\label{web-application-to-collect-responses}}
-
-The taipan {[}\protect\hyperlink{ref-taipan}{20}{]} package for R was used to create the survey web application.
-This structure was altered to collect responses regarding participants demographics and their survey responses.
-The survey app contained three tabs.
-Participants were first asked for their demographics their Figure Eight contributor ID, and their consent to the responses being used for analysis.
-The demographics collected included participants' preferred pronoun, the highest level of education achieved, their age range and whether they had lived in Australia.
-
-After submitting these responses, the survey application switched to the tab of lineups and associated questions.
-This allowed participants to easily move through the twelve displays and provide their choice, reason for their choice, and level of certainty.
-
-When participants completed the twelve evaluations the survey application triggered a data analysis script.
-This created a data set with one row per evaluation.
-Containing the responses to the three questions.
-The script also added the title of the image, which indicated the type of map display, the type of distribution hidden in the lineup, and the location of the data plot.
-It also calculated the time taken by participant to view each lineup.
-
-Each participant used the internet to access the survey.
-The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results.
-The application connected to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{21}{]} R package when participants opened the application, and interacted again when participants chose to submit the survey.
-At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-Participants were recruited from the Figure Eight crowdsourcing platform {[}\protect\hyperlink{ref-figeight}{22}{]} to evaluate lineups.
-The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
-Potential participants needed to have achieved level 2 or level 3 from prior work on the platform.
-All participants were at least 18 years old.
-
-Participants were allocated to either group A or group B when they proceeded to the survey web application.
-There were 92 participants involved in the study.
-All participants read introductory materials, and were trained using three test displays, to orient them to the evaluation task.
-All participants who completed the task were compensated \$AUD5 for their time, via the Figure Eight payment system.
-
-A pilot study was conducted in the working group of the Econometrics and Business Statistics Department of Monash University.
-This allowed us to estimate the effect size, and thus decide on number of participants to collect responses from.
-
-\hypertarget{demographic-data-collection}{%
-\subsection{Demographic data collection}\label{demographic-data-collection}}
-
-Each participant answered demographic questions and provided consent before evaluating the lineups.
+where \(y_{ij} = 0, 1\) is the logg odds for whether the subject
+detected the data plot, \(\mu\) is the overall mean, \(\tau_i, i=1,2\)
+is the map type effect, \(\delta_j\) is the trend model effect. We are
+allowing for an interaction between map type and trend model as the
+response is binary, so a logistic model was used. As each participant
+provides results from 12 lineups, this model can account for each
+individual participants' abilities as it includes a subject-specific
+random intercept.
+
+The model specifies a logistic link, this means the predicted values
+from the \(`glmer`\) model should be back-transformed to fit between 0
+and 1. The predictions \(\widehat{p}(\eta)\) are transformed to be
+probabilities between 0 and 1 with the link specified below:
+
+\[\widehat{p}(\eta) = \frac{e^{\eta}}{1 + e^{\eta}}\]
+\label{eq:transform} \[\eta = f(\tau_i,\delta_j)\]
+
+\subsection{Web application to collect responses}
+\label{sec:watcr}
+
+The taipan \citep{taipan} package for R was used to create the survey
+web application. This structure was altered to collect responses
+regarding participants demographics and their survey responses. The
+survey app contained three tabs. Participants were first asked for their
+demographics their Figure Eight contributor ID, and their consent to the
+responses being used for analysis. The demographics collected included
+participants' preferred pronoun, the highest level of education
+achieved, their age range and whether they had lived in Australia.
+
+After submitting these responses, the survey application switched to the
+tab of lineups and associated questions. This allowed participants to
+easily move through the twelve displays and provide their choice, reason
+for their choice, and level of certainty.
+
+When participants completed the twelve evaluations the survey
+application triggered a data analysis script. This created a data set
+with one row per evaluation. Containing the responses to the three
+questions. The script also added the title of the image, which indicated
+the type of map display, the type of distribution hidden in the lineup,
+and the location of the data plot. It also calculated the time taken by
+participant to view each lineup.
+
+Each participant used the internet to access the survey. The data
+transfer from the web application to the data set took place using a
+secure link to the googlesheet used to store results. The application
+connected to the googlesheet using the googlesheets \citep{sheets} R
+package when participants opened the application, and interacted again
+when participants chose to submit the survey. At this time it added the
+participant's responses to the twelve lineup displays as twelve rows of
+data in the googlesheet.
+
+\subsection{Participants}
+\label{sec:pa}
+
+Participants were recruited from the Figure Eight crowdsourcing platform
+\citep{figeight} to evaluate lineups. The lineup protocol expects that
+the participants are uninvolved judges with no prior knowledge of the
+data, to avoid inadvertently affecting results. Potential participants
+needed to have achieved level 2 or level 3 from prior work on the
+platform. All participants were at least 18 years old.
+
+Participants were allocated to either group A or group B when they
+proceeded to the survey web application. There were 92 participants
+involved in the study. All participants read introductory materials, and
+were trained using three test displays, to orient them to the evaluation
+task. All participants who completed the task were compensated \$AUD5
+for their time, via the Figure Eight payment system.
+
+A pilot study was conducted in the working group of the Econometrics and
+Business Statistics Department of Monash University. This allowed us to
+estimate the effect size, and thus decide on number of participants to
+collect responses from.
+
+\subsection{Demographic data collection}
+\label{sec:ddc}
+
+Each participant answered demographic questions and provided consent
+before evaluating the lineups.
 
@@
 \item
-  Education level achieved (high school / bachelors / masters / doctorate / other),
+  Education level achieved (high school / bachelors / masters /
+  doctorate / other),
 \item
@@
 
-Participants then moved to the evaluation phase.
-The set of images differed for Group A and Group B.
-After being allocated to a group, each individual was shown the 12 displays in randomised order.
+Participants then moved to the evaluation phase. The set of images
+differed for Group A and Group B. After being allocated to a group, each
+individual was shown the 12 displays in randomised order.
 
@@
 
-After completing the 12 evaluations, the participants were asked to submit their responses.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-Responses from 92 participants were collected.
-Five participants did not provide more than three unique choices for the twelve lineups, and their data was removed.
-Set A was evaluated by 42 participants, and 53 evaluated set B.
-This resulted in 1104 evaluations, corresponding to 92 subjects, each evaluating 12 lineups, that were analysed on accuracy and speed.
-The certainty and reasons of subjects in their answers is also examined.
-
-\hypertarget{participant-demographics}{%
-\subsection{Participant demographics}\label{participant-demographics}}
-
-Of the 92 participants, 67 were male, and 25 female. Most participants (56) had a Bachelors degree, 13 had a Masters degree, and the remaining 23 had high school diplomas.
-
-\hypertarget{accuracy}{%
-\subsection{Accuracy}\label{accuracy}}
-
-Fig.
-\ref{fig:detect-compare} displays the average detection rates for the two types of plot separately for each trend model.
-Each trend model was tested using four repetitions, evaluations on the same data set were seen as either choropleths or hexagon tile maps by each group as specified in Table.
-\ref{fig:exp-design}; the detection rates for each display are connected by a line segment.
-The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts.
-One replicate for the All Cities group had similar detection rates for both plot types, the rate of detection using the choropleth map was much higher than other replicates.
-Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map.
-We expected that the choropleth map would be superior for the type of spatial pattern, but the data suggests the hexagon tile map performs slightly better, or equally as well.
+After completing the 12 evaluations, the participants were asked to
+submit their responses.
+
+\section{Results}
+\label{sec:res}
+
+Responses from 92 participants were collected. Five participants did not
+provide more than three unique choices for the twelve lineups, and their
+data was removed. Set A was evaluated by 42 participants, and 53
+evaluated set B. This resulted in 1104 evaluations, corresponding to 92
+subjects, each evaluating 12 lineups, that were analysed on accuracy and
+speed. The certainty and reasons of subjects in their answers is also
+examined.
+
+\subsection{Participant demographics}
+\label{sec:pd}
+
+\hypertarget{section}{%
+\subsection{}\label{section}}
+
+Of the 92 participants, 67 were male, and 25 female. Most participants
+(56) had a Bachelors degree, 13 had a Masters degree, and the remaining
+23 had high school diplomas.
+
+\subsection{Accuracy}
+\label{sec:acc}
+
+Fig. \ref{fig:detect-compare} displays the average detection rates for
+the two types of plot separately for each trend model. Each trend model
+was tested using four repetitions, evaluations on the same data set were
+seen as either choropleths or hexagon tile maps by each group as
+specified in Table. \ref{fig:exp-design}; the detection rates for each
+display are connected by a line segment. The Three Cities and All Cities
+trend models shown in the hexagon tile map allowed viewers to detect the
+data plot substantially more often than the choropleth counterparts. One
+replicate for the All Cities group had similar detection rates for both
+plot types, the rate of detection using the choropleth map was much
+higher than other replicates. Surprisingly, participants could also
+detect the gradual spatial trend in the NW-SE group from the hexagon
+tile map. We expected that the choropleth map would be superior for the
+type of spatial pattern, but the data suggests the hexagon tile map
+performs slightly better, or equally as well.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/detect-compare-1} \caption{The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models.
+\includegraphics[width=1\linewidth]{kobakiancook_files/figure-latex/detect-compare-1} \caption{The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models.
 Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup.
@@
 
-Table.
-\ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
-This also gives the standard deviations, the smallest standard deviation for all sets of replicates was the Three Cities trend model shown in a Choropleth display.
-This group of displays had a very small detection rate of 0.04.
-The mean detection rate for the Three Cities trend model shown as choropleth map lineups was also the smallest at 0.40.
-The North-West to South-East (NW-SE) trend model unexpectedly had a higher mean detection rate for the hexagon tile map displays, but the difference in the means of detection rate was only 0.10.
+Table. \ref{tab:desc-stats} shows the means and standard deviations of
+the detection rate for each type of plot and each trend model. This also
+gives the standard deviations, the smallest standard deviation for all
+sets of replicates was the Three Cities trend model shown in a
+Choropleth display. This group of displays had a very small detection
+rate of 0.04. The mean detection rate for the Three Cities trend model
+shown as choropleth map lineups was also the smallest at 0.40. The
+North-West to South-East (NW-SE) trend model unexpectedly had a higher
+mean detection rate for the hexagon tile map displays, but the
+difference in the means of detection rate was only 0.10.
 
@@
 
-Table.
-\ref{tab:detect-glmer1} presents a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on the detection rate.
-The results support the summary from Fig.
-\ref{fig:detect-compare} and all parameters are statistically significant despite the large standard deviations observed in Table.
-\ref{tab:desc-stats}.
-Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
-Allowing for the interaction effect, the difference in detection rate decreases for population related displays for a choropleth map lineup, but increases for a hexagon tile map display.
-The log odds of detection show in Table. \ref{tab:detect-glmer1} can be back transformed after taking the sum of all terms for the trend and type of display that are of interest.
-For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to 0.63 from 0.52 for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
-
-When a choropleth map display is used, the predicted detection rate for the Three Cities trend, 0.03; this is extremely low, especially compared to the NW-SE trend of 0.52.
-When the All Cities trend is presented in a choropleth display the predicted probability of detection is 0.22.
-The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend 0.39 and All Cities trend 0.59.
+Table. \ref{tab:detect-glmer1} presents a summary of the generalised
+linear mixed effects model, testing the effect of plot type and trend
+model on the detection rate. The results support the summary from Fig.
+\ref{fig:detect-compare} and all parameters are statistically
+significant despite the large standard deviations observed in Table.
+\ref{tab:desc-stats}. Overall, the hexagon tile map performs marginally
+better than the choropleth for all trend models, which is a pleasant
+surprise. Allowing for the interaction effect, the difference in
+detection rate decreases for population related displays for a
+choropleth map lineup, but increases for a hexagon tile map display. The
+log odds of detection show in Table. \ref{tab:detect-glmer1} can be back
+transformed after taking the sum of all terms for the trend and type of
+display that are of interest. For the NW-SE distribution, the predicted
+detection rate for the hexagon tile map display increases the predicted
+probability of detection to \(0.63\) from \(0.52\) for choropleths, this
+is almost exactly the difference seen in the table of means and is
+significant only at the 0.05 level.
+
+When a choropleth map display is used, the predicted detection rate for
+the Three Cities trend, \(0.03\); this is extremely low, especially
+compared to the NW-SE trend of \(0.52\). When the All Cities trend is
+presented in a choropleth display the predicted probability of detection
+is \(0.22\). The hexagon tile map has a substantially high detection
+rate for the display of a Three Cities trend \(0.39\) and All Cities
+trend \(0.59\).
 
@@
 
-\hypertarget{speed}{%
-\subsection{Speed}\label{speed}}
-
-Fig.
-\ref{fig:beeswarm} shows horizontally jittered dot plots to contrast the time taken by participants to evaluate each lineup when viewing each type of display.
-The time are also separated by trend model and whether the data plot was detected or not detected.
-The time taken to complete an evaluation ranged from milliseconds to 60 seconds.
-The average time taken for type of display is shown as a large colored dot on each plot.
-when considering the heights of the green and orange dots, there is little difference in the average time taken to read a choropleth or hexagon tile map.
-Comparing the same colored dot across each trend model row, there is a slight increase in the time taken to correctly detected the data plot in the hexagon tile map lineup, but little difference in evaluation time for the choropleth display.
-However, there were substantially less correct detections for choropleth lineups for the Three cities and All Cities trends.
+\subsection{Speed}
+\label{sec:sp}
+
+Fig. \ref{fig:beeswarm} shows horizontally jittered dot plots to
+contrast the time taken by participants to evaluate each lineup when
+viewing each type of display. The time are also separated by trend model
+and whether the data plot was detected or not detected. The time taken
+to complete an evaluation ranged from milliseconds to 60 seconds. The
+average time taken for type of display is shown as a large colored dot
+on each plot. when considering the heights of the green and orange dots,
+there is little difference in the average time taken to read a
+choropleth or hexagon tile map. Comparing the same colored dot across
+each trend model row, there is a slight increase in the time taken to
+correctly detected the data plot in the hexagon tile map lineup, but
+little difference in evaluation time for the choropleth display.
+However, there were substantially less correct detections for choropleth
+lineups for the Three cities and All Cities trends.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/beeswarm-1} \caption{The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots.
+\includegraphics[width=1\linewidth]{kobakiancook_files/figure-latex/beeswarm-1} \caption{The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots.
 The colored point indicates average time taken for each plot type.
@@
 
-\hypertarget{certainty}{%
-\subsection{Certainty}\label{certainty}}
-
-Participants provided their level of certainty regarding their choice using a five point scale.
-Unlike the accuracy and speed of responses that were derived during the data processing phase, this was a subjective
-assessment by the participant prompted by the question: `How certain are you about your choice?'.
-Fig.
-\ref{fig:certainty} shows the amount of times participants provided each level of certainty.
-This was separated for each combination of trend models and display type, and colored depending on whether a participant correctly detected the data plot in the lineup.
-Participants often chose 4 or 5 when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
-This shows overconfidence in their detection ability when using a choropleth map display.
-Participants were less likely to be certain when their choice was incorrect and they were viewing a hexagon tile map.
-For each trend model, participants were more likely to doubt their choice and choose 1 or 2 in the hexagon tile map displays, even though many had made the correct choice.
+\subsection{Certainty}
+\label{sec:cer}
+
+Participants provided their level of certainty regarding their choice
+using a five point scale. Unlike the accuracy and speed of responses
+that were derived during the data processing phase, this was a
+subjective assessment by the participant prompted by the question: `How
+certain are you about your choice?'. Fig. \ref{fig:certainty} shows the
+amount of times participants provided each level of certainty. This was
+separated for each combination of trend models and display type, and
+colored depending on whether a participant correctly detected the data
+plot in the lineup. Participants often chose 4 or 5 when viewing the
+population related trends in the choropelth display, even though they
+were often incorrect when viewing an All Cities trend and overwhelmingly
+incorrect for the Three Cities trend. This shows overconfidence in their
+detection ability when using a choropleth map display. Participants were
+less likely to be certain when their choice was incorrect and they were
+viewing a hexagon tile map. For each trend model, participants were more
+likely to doubt their choice and choose 1 or 2 in the hexagon tile map
+displays, even though many had made the correct choice.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/certainty-1} \caption{The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
+\includegraphics[width=1\linewidth]{kobakiancook_files/figure-latex/certainty-1} \caption{The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
 Participants were more likely to choose a high certainty when considering a Choropleth map.
@@
 
-\hypertarget{reason}{%
-\subsection{Reason}\label{reason}}
-
-Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons.
-``Color trend across the areas'' was the most common selection for NW-SE trend displays.
-
-The reasons chosen by participants from the list provided to them varied more when viewing choropleth displays than the hexagon tile map.
-The hexagon tile map displays resulted in ``Clusters of color'' as the most common choice made by participants.
-
-The choice ``None of these reasons'' was used as the default value to minimise noise from participants who did not select a response.
+\subsection{Reason}
+\label{sec:rea}
+
+Participants were asked why they had made their plot choice and were
+able to select from a set of suggested reasons. ``Color trend across the
+areas'' was the most common selection for NW-SE trend displays.
+
+The reasons chosen by participants from the list provided to them varied
+more when viewing choropleth displays than the hexagon tile map. The
+hexagon tile map displays resulted in ``Clusters of color'' as the most
+common choice made by participants.
+
+The choice ``None of these reasons'' was used as the default value to
+minimise noise from participants who did not select a response.
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-The intention of this study was to contrast the use of the choropleth map and the hexagon tile map.
-The visual inference lineup protocol was employed to contrast the effectiveness of the displays.
-The results have shown that overall the use of the hexagon tile map display allows participants to find the data plot in the lineup more often.
-Using the visual inference protocol this result can be extended to show that it is a valid alternative display to communicate spatial distributions of population related data.
-
-We expected that the choropleth map would be superior for communicating the spatial pattern of geographic distributions.
-The data suggest that the participants perform slightly better or equally as well for each replicate in each trend model across the two displays.
-Table II shows that the difference in the mean detection rate for the two trend models was 0.10.
+\subsection{Discussion}
+\label{sec:dis}
+
+The intention of this study was to contrast the use of the choropleth
+map and the hexagon tile map. The visual inference lineup protocol was
+employed to contrast the effectiveness of the displays. The results have
+shown that overall the use of the hexagon tile map display allows
+participants to find the data plot in the lineup more often. Using the
+visual inference protocol this result can be extended to show that it is
+a valid alternative display to communicate spatial distributions of
+population related data.
+
+We expected that the choropleth map would be superior for communicating
+the spatial pattern of geographic distributions. The data suggest that
+the participants perform slightly better or equally as well for each
+replicate in each trend model across the two displays. Table II shows
+that the difference in the mean detection rate for the two trend models
+was 0.10.
 
 The differences seen in the \ref{fig:detect-compare} plot and Table.
-\ref{tab:desc-stats} are reflected in the model results.
-Surprisingly the difference for the geographic distribution was significant at the 0.05 level.
-It also showed that the hexagon tile map display performs marginally better than the choropleth for all trend models.
-Unexpectedly the detection rate suffers when using a choropleth map to display population related distributions.
-
-While the significance of the difference in detection was the key focus of this experiment, the secondary focus was the time taken by participants.
-it was expected that the participants may take longer to consider the hexagon tile map distribution but would be able to detect the data plot in the lineup.
-The bimodal distributions seen in Fig.
-\ref{fig:beeswarm} showed very little difference in the mean evaluation times.
-As the maximum time of all of the distributions approached 60 seconds it cannot be said that the participants' took longer to evaluate the hexagon tile map displays.
-
-The responses to the questions asked of participants included the reason for their choice and the certainty around their choice.
-Fig.
-\ref{tab:reason} shows high levels of certainty of 4 and 5 were chosen by participants when looking at the population distributions in a choropleth map display show that they were over confident when attempting to find the real data plot in the choropleth map displays.
-Participants performed better on the NW-SE distribution shown in the choropleth display and were reasonably confident about their decisions.
-The high levels of the mid range value of 3 could indicate that the participant did not want to provide a response, as this was the default value.
-Those who chose level 4 or 5 were equally likely to be correct for the three cities lineups, but more likely to be correct than incorrect for the other two trend models.
-
-The color scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
-Due to the consistent coloring of rural areas in a choropleth display, the choice ``All areas have similar colors'' was most common reason for a participants choice.
-The All Cities displays colored the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural color consistency.
-Choosing ``Clusters of colour'' was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions.
-It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays.
-Due to the spatial covariance introduced in the smoothing, groups of similarly colored hexagons were present in all of the hexagon tile map displays.
-All Cities and Three Cities distributions of real data trends had distinctly different patterns or red inner-city areas, while some of the plots in each lineup may have shared similar features.
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-The choropleth map display and the tessellated hexagon tile map have been contrasted using the lineup protocol.
-The hexagon tile map was significantly more effective for spotting a real population related data trend model hidden in a lineup.
-
-The hexagon tile map display should be considered as an alternative visualization method when communicating distributions that relate to the population across a set of geographic units.
-As an additional display to the familiar choropleth map, cancer atlas products may benefit from the opportunity to allow exploration via an alternative display.
-The spatial distributions used to test these displays were inspired by the real spatially smoothed estimates of the cancer burden on Australian communities.
-However, this technique may be extended to other population related distributions, such as other diseases.
-
-The increasing population densities of capital cities despite large land area exacerbates the difference in the smallest and largest communities.
-The population density structure of Australia can be considered similar to that of Canada, New Zealand and many other countries.
-Therefore, this display is not only relevant to Australia, but all nations or population distributions that experience densely populated cities separated by vast rural expanses.
-
-\hypertarget{acknowledgment}{%
-\section{Acknowledgment}\label{acknowledgment}}
-
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments.
-Mitchell O'Hara-Wild was a co-developer of the taipan {[}\protect\hyperlink{ref-taipan}{20}{]} R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
-We are thankful for the NUMBATs (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.
-
-The source code to produce this document can be found on \href{https://github.com/srkobakian/experiment/tree/master/paper}{GitHub}.
-Supplementary materials have been included to discuss the survey procedures and the lineups that were used.
-The full set of images can also be found at: https://github.com/srkobakian/experiment/tree/master/figures/final.
+\ref{tab:desc-stats} are reflected in the model results. Surprisingly
+the difference for the geographic distribution was significant at the
+0.05 level. It also showed that the hexagon tile map display performs
+marginally better than the choropleth for all trend models. Unexpectedly
+the detection rate suffers when using a choropleth map to display
+population related distributions.
+
+While the significance of the difference in detection was the key focus
+of this experiment, the secondary focus was the time taken by
+participants. it was expected that the participants may take longer to
+consider the hexagon tile map distribution but would be able to detect
+the data plot in the lineup. The bimodal distributions seen in Fig.
+\ref{fig:beeswarm} showed very little difference in the mean evaluation
+times. As the maximum time of all of the distributions approached 60
+seconds it cannot be said that the participants' took longer to evaluate
+the hexagon tile map displays.
+
+The responses to the questions asked of participants included the reason
+for their choice and the certainty around their choice. Fig.
+\ref{tab:reason} shows high levels of certainty of 4 and 5 were chosen
+by participants when looking at the population distributions in a
+choropleth map display show that they were over confident when
+attempting to find the real data plot in the choropleth map displays.
+Participants performed better on the NW-SE distribution shown in the
+choropleth display and were reasonably confident about their decisions.
+The high levels of the mid range value of 3 could indicate that the
+participant did not want to provide a response, as this was the default
+value. Those who chose level 4 or 5 were equally likely to be correct
+for the three cities lineups, but more likely to be correct than
+incorrect for the other two trend models.
+
+The color scaling applied in Three cities and All cities displays
+resulted in the rural areas of the real data plot appearing more blue or
+yellow than the other plots in the lineups. Due to the consistent
+coloring of rural areas in a choropleth display, the choice ``All areas
+have similar colors'' was most common reason for a participants choice.
+The All Cities displays colored the inner-city areas of all capital
+cities more red, this was observable to participants and explains the
+equal choice of the city clusters or rural color consistency. Choosing
+``Clusters of colour'' was expected when participants viewed the Hexagon
+tile map display of the All Cities and Three Cities distributions. It
+was unexpected that it was also the most common reason for the NW-SE
+hexagon tile map displays. Due to the spatial covariance introduced in
+the smoothing, groups of similarly colored hexagons were present in all
+of the hexagon tile map displays. All Cities and Three Cities
+distributions of real data trends had distinctly different patterns or
+red inner-city areas, while some of the plots in each lineup may have
+shared similar features.
+
+\section{Conclusion}
+\label{sec:con}
+
+The choropleth map display and the tessellated hexagon tile map have
+been contrasted using the lineup protocol. The hexagon tile map was
+significantly more effective for spotting a real population related data
+trend model hidden in a lineup.
+
+The hexagon tile map display should be considered as an alternative
+visualization method when communicating distributions that relate to the
+population across a set of geographic units. As an additional display to
+the familiar choropleth map, cancer atlas products may benefit from the
+opportunity to allow exploration via an alternative display. The spatial
+distributions used to test these displays were inspired by the real
+spatially smoothed estimates of the cancer burden on Australian
+communities. However, this technique may be extended to other population
+related distributions, such as other diseases.
+
+The increasing population densities of capital cities despite large land
+area exacerbates the difference in the smallest and largest communities.
+The population density structure of Australia can be considered similar
+to that of Canada, New Zealand and many other countries. Therefore, this
+display is not only relevant to Australia, but all nations or population
+distributions that experience densely populated cities separated by vast
+rural expanses.
+
+\section{Acknowledgments}
+\label{sec:ack}
+
+The authors would like to thank the Australian Cancer Atlas team for
+discussions regarding alternative spatial visualizations, and Professor
+Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with
+suggestions and comments. Mitchell O'Hara-Wild was a co-developer of the
+taipan \citep{taipan} R package for image tagging, used as the base for
+the web app constructed to collect participant evaluations of lineups.
+We are thankful for the NUMBATs (Non-Uniform Monash Business Analytics
+Team) for participating in the pilot study that helped to assess the
+experimental design and determine an appropriate sample size for the
+study.
+
+The source code to produce this document can be found on
+\href{https://github.com/srkobakian/experiment/tree/master/paper}{GitHub}.
+Supplementary materials have been included to discuss the survey
+procedures and the lineups that were used. The full set of images can
+also be found at:
+\url{https://github.com/srkobakian/experiment/tree/master/figures/final}.
 
@@
 
-The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{18}{]} with the use of the following packages:
+The analysis of the work was completed in R \citep{RCore} with the use
+of the following packages:
 
@@
 \item
-  For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{23}{]}, rticles {[}\protect\hyperlink{ref-rticles}{24}{]}, knitr {[}\protect\hyperlink{ref-knitr}{25}{]}.
-\item
-  For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{26}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{27}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{28}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{29}{]}.
-\item
-  For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{30}{]}, png {[}\protect\hyperlink{ref-png}{31}{]}, grid {[}\protect\hyperlink{ref-grid}{32}{]}.
-\item
-  For modelling and presentation of models: gstat {[}\protect\hyperlink{ref-gstat}{17}{]}, lme4 {[}\protect\hyperlink{ref-lme4}{19}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{33}{]}.
+  For document creation: rmarkdown \citep{rmarkdown}, rticles
+  \citep{rticles}, knitr \citep{knitr}.
+\item
+  For lineup creation and data analysis: tidyverse \citep{tidyverse},
+  nullabor \citep{nullabor}, ggthemes \citep{ggthemes}, RColorBrewer
+  \citep{RColorBrewer}.
+\item
+  For image displays: cowplot \citep{cowplot}, png \citep{png}, grid
+  \citep{grid}.
+\item
+  For modelling and presentation of models: gstat \citep{gstat}, lme4
+  \citep{lme4}, kableExtra \citep{kableExtra}.
 \end{itemize}
 
-Ethics approval for the online survey was granted by QUT's Ethics Committee (Ethics Application Number: 1900000991).
-All applicants provided informed consent in line with QUT regulations prior to participating in this research.
+Ethics approval for the online survey was granted by QUT's Ethics
+Committee (Ethics Application Number: 1900000991). All applicants
+provided informed consent in line with QUT regulations prior to
+participating in this research.
 
@@
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\leavevmode\hypertarget{ref-sugarbag}{}%
-1. Kobakian S, Cook D (2019) Sugarbag: Create tessellated hexagon maps.
-
-\leavevmode\hypertarget{ref-atlas}{}%
-2. Cancer Council Queensland Australian Cancer Atlas (https://atlas.cancer.org.au).
-
-\leavevmode\hypertarget{ref-GIIV}{}%
-3. Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979
-
-\leavevmode\hypertarget{ref-EI}{}%
-4. Tufte ER (1990) Envisioning Information. Graphics Press
-
-\leavevmode\hypertarget{ref-BCM}{}%
-5.
-Skowronnek A (2016) Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata.
-In: Infovis Reading Group WS 2015/16.
-\url{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}.
-
-\leavevmode\hypertarget{ref-CBATCC}{}%
-6. Kocmoud C, House D (1998) A Constraint-based Approach to Constructing Continuous Cartograms. In: Proc. Symp. Spatial data handling. pp 236--246
-
-\leavevmode\hypertarget{ref-ACTUC}{}%
-7. Dorling D (2011) Area Cartograms: Their Use and Creation. In: Concepts and techniques in modern geography (catmog). pp 252--260
-
-\leavevmode\hypertarget{ref-NAC}{}%
-8. Olson JM (1976) Noncontiguous Area Cartograms. The Professional Geographer 28:371--380
-
-\leavevmode\hypertarget{ref-RSCW}{}%
-9. Raisz E (1963) Rectangular Statistical Cartograms of the World. Journal of Geography 35:8--10
-
-\leavevmode\hypertarget{ref-CDWCS}{}%
-10. Monmonier M (2005) Cartography: Distortions, World-views and Creative Solutions. Progress in Human Geography 29:217--224
-
-\leavevmode\hypertarget{ref-review}{}%
-11. (2019) Cancer applications of choropleth maps, and the potential of cartograms and alternative map displays. Manuscript submitted for publication.
-
-\leavevmode\hypertarget{ref-BCHLLSW09}{}%
-12.
-Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) Statistical inference for exploratory data analysis and model diagnostics.
-Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383
-
-\leavevmode\hypertarget{ref-GTPCCD}{}%
-13. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448
-
-\leavevmode\hypertarget{ref-ggplot2}{}%
-14. Wickham H (2009) Ggplot2: Elegant graphics for data analysis. Springer New York
-
-\leavevmode\hypertarget{ref-abs2016}{}%
-15. (2018) Australian Statistical Geography Standard (ASGS). Australian Bureau of Statistics
-
-\leavevmode\hypertarget{ref-POG}{}%
-16. Matheron G (1963) Principles of geostatistics. Economic Geology 58:1246--1266
-
-\leavevmode\hypertarget{ref-gstat}{}%
-17. Gräler B, Pebesma E, Heuvelink G (2016) Spatio-temporal interpolation using gstat. The R Journal 8:204--218
-
-\leavevmode\hypertarget{ref-RCore}{}%
-18. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
-
-\leavevmode\hypertarget{ref-lme4}{}%
-19. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
-
-\leavevmode\hypertarget{ref-taipan}{}%
-20. Kobakian S, O'Hara-Wild M (2018) Taipan: Tool for annotating images in preparation for analysis.
-
-\leavevmode\hypertarget{ref-sheets}{}%
-21. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
-
-\leavevmode\hypertarget{ref-figeight}{}%
-22. (2019) The essential high-quality data annotation platform. Figure Eight
-
-\leavevmode\hypertarget{ref-rmarkdown}{}%
-23. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida
-
-\leavevmode\hypertarget{ref-rticles}{}%
-24. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.
-
-\leavevmode\hypertarget{ref-knitr}{}%
-25. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research
-
-\leavevmode\hypertarget{ref-tidyverse}{}%
-26. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686
-
-\leavevmode\hypertarget{ref-nullabor}{}%
-27. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.
-
-\leavevmode\hypertarget{ref-ggthemes}{}%
-28. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.
-
-\leavevmode\hypertarget{ref-RColorBrewer}{}%
-29. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.
-
-\leavevmode\hypertarget{ref-cowplot}{}%
-30. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.
-
-\leavevmode\hypertarget{ref-png}{}%
-31. Urbanek S (2013) Png: Read and write png images.
-
-\leavevmode\hypertarget{ref-grid}{}%
-32. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
-
-\leavevmode\hypertarget{ref-kableExtra}{}%
-33. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
+\bibliographystyle{agsm}
+\bibliography{paper.bib}
 

### 2021-03-24 kobakiancook/supplementary/survey_procedures.Rmd
asa format

--- 2020-01-12 paper/supplementary/survey_procedures.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 8)
 ```
@@
 
-```{r instruct, results = "asis", fig.cap = "The training lineups of choropleth maps.", fig.width = 4, fig.height = 4}
+```{r instruct, results = "asis", fig.cap = "The training lineups of choropleth maps."}
 ggdraw() +
@@
 
-```{r training1, results = "asis", fig.cap = "The training lineups of choropleth maps.", fig.width = 4, fig.height = 4}
+```{r training1, results = "asis", fig.cap = "The training lineups of choropleth maps."}
 ggdraw() +
@@
 
-```{r training2, results = "asis", fig.cap = "The training lineups of hexagon tile maps.", fig.width = 4, fig.height = 4}
+```{r training2, results = "asis", fig.cap = "The training lineups of hexagon tile maps."}
 ggdraw() +
@@
 
-```{r survey-demogs, results = "asis", fig.cap = "The demographics questions tab of the shinydashboard survey application.", fig.width = 4, fig.height = 4}
+```{r survey-demogs, results = "asis", fig.cap = "The demographics questions tab of the shinydashboard survey application."}
 ggdraw() +
@@
 
-```{r survey-choro, results = "asis", fig.cap = "An example of the choropleth map lineup shown in the survey tab of the shinydashboard app.", fig.width = 4, fig.height = 4}
+```{r survey-choro, results = "asis", fig.cap = "An example of the choropleth map lineup shown in the survey tab of the shinydashboard app."}
 ggdraw() +
@@
 
-```{r survey-hex, results = "asis", fig.cap = "An example of the hexagon tile map lineup shown in the survey tab of the shinydashboard app.", fig.width = 4, fig.height = 4}
+```{r survey-hex, results = "asis", fig.cap = "An example of the hexagon tile map lineup shown in the survey tab of the shinydashboard app."}
 ggdraw() +

### 2021-03-24 kobakiancook/supplementary/R/pilot_popdensity.R

@@ -1,0 +1,269 @@
+###############################################################################
+######################       POPULATION DENSITY       #########################
+
+# First source the simulated points
+#source('~/experiment/R/00_pilot.R', echo = TRUE)
+
+# only use the most smoothed
+ sa3_min <- sa3_long %>% 
+  filter(groups == "smooth5") %>%
+  pull(value) %>% min()
+ sa3_max <- sa3_long %>% 
+   filter(groups == "smooth5") %>%
+   pull(value) %>% max()
+
+# use an underlying spatial covariance model
+# add a population density model
+
+# Use the Estimated Residential Population (ERP)
+ERP <- read_csv("data/ERP.csv")
+ERP_sa3_16 <- ERP %>% 
+  filter(`Geography Level` == "Statistical Area Level 3") %>% 
+  filter(Time == 2016) %>% select(sa3_name_2016 = Region, ERP = Value)
+
+ERP_sa3_16 <- sa3 %>% st_drop_geometry() %>% select(sa3_name_2016, areasqkm_2016) %>% 
+  left_join(., ERP_sa3_16)
+
+ERP_sa3_16 <- ERP_sa3_16 %>% 
+  mutate(pop_density = (ERP/areasqkm_2016))  %>% 
+  mutate(pop_density = scales::rescale(pop_density, to = c(sa3_min,sa3_max)))
+
+###########################################################
+################# Smooth pop density ######################
+###########################################################
+
+# This distribution will be added to one of the null plots
+
+sa3_smooth_pop <- as_tibble(ERP_sa3_16) %>% 
+  mutate(s1_popdens16 = map_dbl(1:nrow(sa3), spatial_smoother, 
+    values_vector = pop_density, area_weight = 0.5, neighbours_list = sa3_neighbours)) %>% 
+  mutate(s2_popdens16 =  map_dbl(1:nrow(sa3), spatial_smoother, 
+    values_vector = s1_popdens16, area_weight = 0.5, neighbours_list = sa3_neighbours)) %>% 
+  mutate(s3_popdens16 =  map_dbl(1:nrow(sa3), spatial_smoother, 
+    values_vector = s2_popdens16, area_weight = 0.5, neighbours_list = sa3_neighbours)) %>% 
+  mutate(s4_popdens16 =  map_dbl(1:nrow(sa3), spatial_smoother, 
[…]

### 2023-03-14 paper/paper.Rmd
updated to use thyroid

@@
 editor_options: 
-  chunk_output_type: inline
+  chunk_output_type: console
 link-citations: true
@@
 <!-- Regular paper – 12 double column pages (Submissions may be up to 18 pages in length, subject to MOPC. All regular paper page limits include references and author biographies.) -->
+
+<!-- Changes: thyroid instead of liver - check; lineup need to be hexmap; check language with chatgpt/grammarly; get refs formatted and paper into 10 pages -->
 
@@
 library(broom)
+library(broom.mixed)
 library(cowplot)
@@
 
+```{r makethyroidplots}
+library(cartogram)
+library(sugarbag)
+library(sf)
+
+# Spatial polygons files sourced from: https://github.com/wfmackey/absmapsdata
+load("data/sa22011.rda")
+load("data/state2011.rda")
+
+invthm <- theme_map() + 
+  theme(
+    panel.background = element_rect(fill = "transparent", colour = NA), 
+    plot.background = element_rect(fill = "transparent", colour = NA),
+    legend.background = element_rect(fill = "transparent", colour = NA),
+    legend.key = element_rect(fill = "transparent", colour = NA),
+    text = element_text(colour = "white"),
+    axis.text = element_text(colour = "white")
+  )
+
+# function to allocate colours to regions
+aus_colours <- function(sir_p50){
+  value <- case_when(
+    sir_p50 <  0.74 ~ "#33809d",
+    sir_p50 >= 0.74 & sir_p50 < 0.98 ~ "#aec6c7",
+    sir_p50 >= 0.98 & sir_p50 < 1.05 ~ "#fff4bc",
+    sir_p50 >= 1.05 & sir_p50 < 1.45 ~ "#ff9a64",
+    sir_p50 >= 1.45 ~ "#ff3500",
+    TRUE ~ "#FFFFFF")
+  return(value)
+}
+
+sa2 <- sa22011 %>% 
+  filter(!st_is_empty(geometry)) %>% 
+  filter(!state_name_2011 == "Other Territories") %>% 
+  filter(!sa2_name_2011 == "Lord Howe Island")
+
+SIR <- read_csv("data/SIR Downloadable Data.csv") %>% 
+  filter(SA2_name %in% sa2$sa2_name_2011) %>% 
+  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
+  filter(Cancer_name == "Thyroid", Sex_name == "Females")
+ERP <- read_csv("data/ERP.csv") %>%
+  filter(REGIONTYPE == "SA2", Time == 2011, Region %in% SIR$SA2_name) %>% 
+  dplyr::select(Region, Value)
+# Alternative maps
+# Join with sa2 sf object
+sa2thyroid_ERP <- SIR %>% 
+  left_join(sa2, ., by = c("sa2_name_2011" = "SA2_name")) %>%
+  left_join(., ERP %>% 
+              dplyr::select(Region, 
+              Population = Value), by = c("sa2_name_2011"= "Region")) %>% 
+  filter(!st_is_empty(geometry))
+sa2thyroid_ERP <- sa2thyroid_ERP %>% 
+  #filter(!is.na(Population)) %>% 
+  filter(!sa2_name_2011 == "Lord Howe Island") %>% 
+  mutate(SIR = map_chr(p50, aus_colours)) %>% 
+  st_as_sf()
+
+# Make choropleth
+aus_ggchoro <- ggplot(sa2thyroid_ERP) + 
+  geom_sf(aes(fill = SIR), size = 0.1) + 
+  scale_fill_identity() + invthm
+
+# Make hexmap
+if (!file.exists("data/aus_hexmap.rda")) {
+
+## Check the projection uses long and lat
+## Create centroids set
+sa2centroids <- sa2 %>% 
+  create_centroids(., "sa2_name_2011")
+## Create hexagon grid
+# For speed, consider if the buffer distance beyond the centroids is necessary
+grid <- create_grid(centroids = sa2centroids,
+                    hex_size = 0.15,
+                    buffer_dist = 4, verbose = TRUE)
+## Allocate polygon centroids to hexagon grid points
+# This is a time consuming process for a large data set
+aus_hexmap <- allocate(
+  centroids = sa2centroids,
+  hex_grid = grid,
+  sf_id = "sa2_name_2011",
+  ## same column used in create_centroids
+  hex_size = 0.15,
+  hex_filter = 8,
+  focal_points = capital_cities,
+  width = 25,
+  verbose = TRUE)
+save(aus_hexmap, file = "data/aus_hexmap.rda") 
+}
+
+load("data/aus_hexmap.rda")
+
+## Prepare to plot
+fort_hex <- fortify_hexagon(data = aus_hexmap,
+                            sf_id = "sa2_name_2011",
+                            hex_size = 0.3) %>% 
+            left_join(sa2thyroid_ERP %>%
+            select(sa2_name_2011, SIR, p50))
+fort_aus <- sa2thyroid_ERP %>%
+  fortify_sfc()
+## Make a plot
+aus_hexmap_plot <- ggplot() +
+  geom_polygon(aes(x = long,  y = lat,  
+        group = interaction(sa2_name_2011, polygon)),
+               fill = "black",  colour = "darkgrey", 
+               linewidth = 0.1, data = fort_aus) +
+  geom_polygon(aes(x = long, y = lat, group = hex_id, 
+                   fill = SIR), data = fort_hex) +
+  scale_fill_identity() +
+  invthm + coord_equal()
+```
+
 Introduction
@@
 
-```{r liver, fig.height = 4, fig.width = 4, fig.cap = "A choropleth map of the smoothed average of liver cancer diagnoses for Australian males.
+```{r liver, eval=FALSE, fig.height = 4, fig.width = 4, fig.cap = "A choropleth map of the smoothed average of liver cancer diagnoses for Australian males.
 The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
@@
 
-```{r liver-hex, fig.height = 4, fig.width = 4, fig.cap = "A hexagon tile map of the smoothed average of liver cancer diagnoses for Australian males.
+```{r liver-hex, eval=FALSE, fig.height = 4, fig.width = 4, fig.cap = "A hexagon tile map of the smoothed average of liver cancer diagnoses for Australian males.
 The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
@@
 
+```{r thyroid-choro, out.height = "30%", fig.height = 3, fig.width = 4, fig.align='center', fig.cap = "A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2.
+Blue indicates lower than average and red indicates higher than average incidence.
+A cluster of high incidence is visible on the east coast."}
+aus_ggchoro
+```
+
 The choropleth map is an effective spatial display if the size of the geographic units is relatively uniform.
@@
 Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips.
-A choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population related distribution of the statistic [@CBATCC].
+Fig.
+\ref{fig:thyroid-choro} shows the choropleth map of thyroid cancer rates in Australia.
+The choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population related distribution of the statistic [@CBATCC].
 *Land doesn't get cancer, people do* -- a more effective way to communicate the spatial distributions of cancer statistics is needed.
@@
 
+```{r thyroid-hex, out.height = "30%", fig.height = 3, fig.width = 4, fig.align='center', fig.cap = "A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
+The high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) can now be seen, along with numerous isolated spots."}
+aus_hexmap_plot
+```
+
 <!-- Hexagon tile map -->
@@
 Fig.
-\ref{fig:liver} shows the hexagon tile map, along with the choropleth map of liver cancer rates in Australia.
+\ref{fig:thyroid-hex} shows the hexagon tile map.
 Colour maps from substantially below average (blue) to substantially above average (red) rates.
@@
 Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to do well, and two with differing level of inner city hot spots.
-These latter two reflect the structure seen in the liver cancer data (Fig.
-\ref{fig:liver}).
+These latter two reflect the structure seen in the thyroid cancer data (Fig.
+\ref{fig:thyroid}).
 This produces six treatment levels:
@@
 
-This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the Liver cancer distribution (Fig. \ref{fig:liver}).
+This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the thyroid cancer distribution (Fig. \ref{fig:thyroid}).
 
@@
   ylim(0,1) +
-  guides(color = FALSE)
+  guides(scale = "none")
 ```
@@
 
-The source code to produce this document can be found on [GitHub](https://github.com/srkobakian/experiment/tree/master/paper).
+The source code to produce this document can be found on [GitHub](https://github.com/srkobakian/experiment/paper).
 Supplementary materials have been included to discuss the survey procedures and the lineups that were used.
-The full set of images can also be found at: https://github.com/srkobakian/experiment/tree/master/figures/final.
+The full set of images can be found here, too.
 
@@
 
-\newpage
 References {.numbered}

### 2023-03-14 paper/paper.tex
updated to use thyroid

@@
 
+\usepackage{graphicx}
+
 % *** MATH PACKAGES ***
@@
 
-\usepackage{longtable,booktabs}
-
 \usepackage[unicode=true]{hyperref}
@@
 
-% Pandoc syntax highlighting
-
-% Pandoc header
+% tightlist command for lists without linebreak
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+% From pandoc table feature
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+
+% Pandoc citation processing
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+% for Pandoc 2.8 to 2.10.1
+\newenvironment{cslreferences}%
+  {}%
+  {\par}
+% For Pandoc 2.11+
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
 \usepackage{graphicx}
@@
 \usepackage{xcolor}
-
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/liver-1} \caption{A choropleth map of the smoothed average of liver cancer diagnoses for Australian males.
-The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
-The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.}\label{fig:liver}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/liver-hex-1} \caption{A hexagon tile map of the smoothed average of liver cancer diagnoses for Australian males.
-The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
-The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.}\label{fig:liver-hex}
+
+{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{paper_files/figure-latex/thyroid-choro-1}
+
+}
+
+\caption{A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2.
+Blue indicates lower than average and red indicates higher than average incidence.
+A cluster of high incidence is visible on the east coast.}\label{fig:thyroid-choro}
 \end{figure}
@@
 Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips.
-A choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population related distribution of the statistic {[}\protect\hyperlink{ref-CBATCC}{6}{]}.
+Fig.
+\ref{fig:thyroid-choro} shows the choropleth map of thyroid cancer rates in Australia.
+The choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population related distribution of the statistic {[}\protect\hyperlink{ref-CBATCC}{6}{]}.
 \emph{Land doesn't get cancer, people do} -- a more effective way to communicate the spatial distributions of cancer statistics is needed.
@@
 
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{paper_files/figure-latex/thyroid-hex-1}
+
+}
+
+\caption{A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
+The high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) can now be seen, along with numerous isolated spots.}\label{fig:thyroid-hex}
+\end{figure}
+
 The hexagon tile map algorithm, automatically matches spatial regions to their nearest hexagon tile, from a grid of tiles.
@@
 
-The source code to produce this document can be found on \href{https://github.com/srkobakian/experiment/tree/master/paper}{GitHub}.
+The source code to produce this document can be found on \href{https://github.com/srkobakian/experiment/paper}{GitHub}.
 Supplementary materials have been included to discuss the survey procedures and the lineups that were used.
-The full set of images can also be found at: https://github.com/srkobakian/experiment/tree/master/figures/final.
+The full set of images can be found here, too.
 
@@
 All applicants provided informed consent in line with QUT regulations prior to participating in this research.
-
-\newpage
 
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-sugarbag}{}%
-1. Kobakian S, Cook D (2019) Sugarbag: Create tessellated hexagon maps.
-
-\leavevmode\hypertarget{ref-atlas}{}%
-2. Cancer Council Queensland Australian Cancer Atlas (https://atlas.cancer.org.au).
-
-\leavevmode\hypertarget{ref-GIIV}{}%
-3. Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979
-
-\leavevmode\hypertarget{ref-EI}{}%
-4. Tufte ER (1990) Envisioning Information. Graphics Press
-
-\leavevmode\hypertarget{ref-BCM}{}%
-5.
-Skowronnek A (2016) Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata.
-In: Infovis Reading Group WS 2015/16.
-\url{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}.
-
-\leavevmode\hypertarget{ref-CBATCC}{}%
-6. Kocmoud C, House D (1998) A Constraint-based Approach to Constructing Continuous Cartograms. In: Proc. Symp. Spatial data handling. pp 236--246
-
-\leavevmode\hypertarget{ref-ACTUC}{}%
-7. Dorling D (2011) Area Cartograms: Their Use and Creation. In: Concepts and techniques in modern geography (catmog). pp 252--260
-
-\leavevmode\hypertarget{ref-NAC}{}%
-8. Olson JM (1976) Noncontiguous Area Cartograms. The Professional Geographer 28:371--380
-
-\leavevmode\hypertarget{ref-RSCW}{}%
-9. Raisz E (1963) Rectangular Statistical Cartograms of the World. Journal of Geography 35:8--10
-
-\leavevmode\hypertarget{ref-CDWCS}{}%
-10. Monmonier M (2005) Cartography: Distortions, World-views and Creative Solutions. Progress in Human Geography 29:217--224
-
-\leavevmode\hypertarget{ref-review}{}%
-11. (2019) Cancer applications of choropleth maps, and the potential of cartograms and alternative map displays. Manuscript submitted for publication.
-
-\leavevmode\hypertarget{ref-BCHLLSW09}{}%
-12.
-Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) Statistical inference for exploratory data analysis and model diagnostics.
-Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383
-
-\leavevmode\hypertarget{ref-GTPCCD}{}%
-13. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448
-
-\leavevmode\hypertarget{ref-ggplot2}{}%
-14. Wickham H (2009) Ggplot2: Elegant graphics for data analysis. Springer New York
-
-\leavevmode\hypertarget{ref-abs2016}{}%
-15. (2018) Australian Statistical Geography Standard (ASGS). Australian Bureau of Statistics
-
-\leavevmode\hypertarget{ref-POG}{}%
-16. Matheron G (1963) Principles of geostatistics. Economic Geology 58:1246--1266
-
-\leavevmode\hypertarget{ref-gstat}{}%
-17. Gräler B, Pebesma E, Heuvelink G (2016) Spatio-temporal interpolation using gstat. The R Journal 8:204--218
-
-\leavevmode\hypertarget{ref-RCore}{}%
-18. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
-
-\leavevmode\hypertarget{ref-lme4}{}%
-19. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
-
-\leavevmode\hypertarget{ref-taipan}{}%
-20. Kobakian S, O'Hara-Wild M (2018) Taipan: Tool for annotating images in preparation for analysis.
-
-\leavevmode\hypertarget{ref-sheets}{}%
-21. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
-
-\leavevmode\hypertarget{ref-figeight}{}%
-22. (2019) The essential high-quality data annotation platform. Figure Eight
-
-\leavevmode\hypertarget{ref-rmarkdown}{}%
-23. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida
-
-\leavevmode\hypertarget{ref-rticles}{}%
-24. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.
-
-\leavevmode\hypertarget{ref-knitr}{}%
-25. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research
-
-\leavevmode\hypertarget{ref-tidyverse}{}%
-26. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686
-
-\leavevmode\hypertarget{ref-nullabor}{}%
-27. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.
-
-\leavevmode\hypertarget{ref-ggthemes}{}%
-28. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.
-
-\leavevmode\hypertarget{ref-RColorBrewer}{}%
-29. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.
-
-\leavevmode\hypertarget{ref-cowplot}{}%
-30. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.
-
-\leavevmode\hypertarget{ref-png}{}%
-31. Urbanek S (2013) Png: Read and write png images.
-
-\leavevmode\hypertarget{ref-grid}{}%
-32. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
-
-\leavevmode\hypertarget{ref-kableExtra}{}%
-33. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-sugarbag}{}}%
+\CSLLeftMargin{1. }%
+\CSLRightInline{Kobakian S, Cook D (2019) Sugarbag: Create tessellated hexagon maps. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-atlas}{}}%
+\CSLLeftMargin{2. }%
+\CSLRightInline{Cancer Council Queensland {Australian Cancer Atlas (https://atlas.cancer.org.au)}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-GIIV}{}}%
+\CSLLeftMargin{3. }%
+\CSLRightInline{Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979}
+
+\leavevmode\vadjust pre{\hypertarget{ref-EI}{}}%
+\CSLLeftMargin{4. }%
+\CSLRightInline{Tufte ER (1990) {Envisioning Information}. Graphics Press}
+
+\leavevmode\vadjust pre{\hypertarget{ref-BCM}{}}%
+\CSLLeftMargin{5. }%
+\CSLRightInline{Skowronnek A (2016) {Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata}.
+In: {Infovis Reading Group WS 2015/16}.
+\href{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}{https://alsino.io/static/papers/BeyondChoropleths\_AlsinoSkowronnek.pdf.
+}}
+
+\leavevmode\vadjust pre{\hypertarget{ref-CBATCC}{}}%
+\CSLLeftMargin{6. }%
+\CSLRightInline{Kocmoud C, House D (1998) {A Constraint-based Approach to Constructing Continuous Cartograms}. In: Proc. Symp. Spatial data handling. pp 236--246}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ACTUC}{}}%
+\CSLLeftMargin{7. }%
+\CSLRightInline{Dorling D (2011) \href{https://doi.org/10.1002/9780470979587.ch33}{{Area Cartograms: Their Use and Creation}}. In: Concepts and techniques in modern geography (CATMOG). pp 252--260}
+
+\leavevmode\vadjust pre{\hypertarget{ref-NAC}{}}%
+\CSLLeftMargin{8. }%
+\CSLRightInline{Olson JM (1976) \href{https://doi.org/10.1111/j.0033-0124.1976.00371.x}{{Noncontiguous Area Cartograms}}. The Professional Geographer 28:371--380}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RSCW}{}}%
+\CSLLeftMargin{9. }%
+\CSLRightInline{Raisz E (1963) \href{https://doi.org/10.1080/00221343608987880}{{Rectangular Statistical Cartograms of the World}}. Journal of Geography 35:8--10}
+
+\leavevmode\vadjust pre{\hypertarget{ref-CDWCS}{}}%
+\CSLLeftMargin{10. }%
+\CSLRightInline{Monmonier M (2005) \href{https://doi.org/10.1191/0309132505ph540pr}{{Cartography: Distortions, World-views and Creative Solutions}}. Progress in Human Geography 29:217--224}
+
+\leavevmode\vadjust pre{\hypertarget{ref-review}{}}%
+\CSLLeftMargin{11. }%
+\CSLRightInline{(2019) Cancer applications of choropleth maps, and the potential of cartograms and alternative map displays. Manuscript submitted for publication. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-BCHLLSW09}{}}%
+\CSLLeftMargin{12. }%
+\CSLRightInline{Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) Statistical inference for exploratory data analysis and model diagnostics.
+Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383}
+
+\leavevmode\vadjust pre{\hypertarget{ref-GTPCCD}{}}%
+\CSLLeftMargin{13. }%
+\CSLRightInline{Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ggplot2}{}}%
+\CSLLeftMargin{14. }%
+\CSLRightInline{Wickham H (2009) \href{http://had.co.nz/ggplot2/book}{ggplot2: Elegant graphics for data analysis}. Springer New York}
+
+\leavevmode\vadjust pre{\hypertarget{ref-abs2016}{}}%
+\CSLLeftMargin{15. }%
+\CSLRightInline{(2018) \href{\%7Bhttps://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)\%7D}{{Australian Statistical Geography Standard (ASGS)}}.
+Australian Bureau of Statistics }
+
+\leavevmode\vadjust pre{\hypertarget{ref-POG}{}}%
+\CSLLeftMargin{16. }%
+\CSLRightInline{Matheron G (1963) \href{http://dx.doi.org/10.2113/gsecongeo.58.8.1246}{Principles of geostatistics}. Economic Geology 58:1246--1266}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gstat}{}}%
+\CSLLeftMargin{17. }%
+\CSLRightInline{Gräler B, Pebesma E, Heuvelink G (2016) \href{https://journal.r-project.org/archive/2016/RJ-2016-014/index.html}{Spatio-temporal interpolation using gstat}. The R Journal 8:204--218}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RCore}{}}%
+\CSLLeftMargin{18. }%
+\CSLRightInline{R Core Team (2019) \href{https://www.R-project.org/}{R: A language and environment for statistical computing}. R Foundation for Statistical Computing, Vienna, Austria}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lme4}{}}%
+\CSLLeftMargin{19. }%
+\CSLRightInline{Bates D, Mächler M, Bolker B, Walker S (2015) \href{https://doi.org/10.18637/jss.v067.i01}{Fitting linear mixed-effects models using {lme4}}. Journal of Statistical Software 67:1--48}
+
+\leavevmode\vadjust pre{\hypertarget{ref-taipan}{}}%
+\CSLLeftMargin{20. }%
+\CSLRightInline{Kobakian S, O'Hara-Wild M (2018) \href{https://CRAN.R-project.org/package=taipan}{Taipan: Tool for annotating images in preparation for analysis}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-sheets}{}}%
+\CSLLeftMargin{21. }%
+\CSLRightInline{Bryan J, Zhao J (2018) \href{https://CRAN.R-project.org/package=googlesheets}{Googlesheets: Manage google spreadsheets from r}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-figeight}{}}%
+\CSLLeftMargin{22. }%
+\CSLRightInline{(2019) \href{https://www.figure-eight.com/}{The essential high-quality data annotation platform}. Figure Eight }
+
+\leavevmode\vadjust pre{\hypertarget{ref-rmarkdown}{}}%
+\CSLLeftMargin{23. }%
+\CSLRightInline{Xie Y, Allaire JJ, Grolemund G (2018) \href{https://bookdown.org/yihui/rmarkdown}{R markdown: The definitive guide}. Chapman; Hall/CRC, Boca Raton, Florida}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rticles}{}}%
+\CSLLeftMargin{24. }%
+\CSLRightInline{Allaire J, Xie Y, R Foundation, et al (2019) \href{https://CRAN.R-project.org/package=rticles}{Rticles: Article formats for r markdown}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-knitr}{}}%
+\CSLLeftMargin{25. }%
+\CSLRightInline{Xie Y (2014) \href{http://www.crcpress.com/product/isbn/9781466561595}{Knitr: A comprehensive tool for reproducible research in {R}}. Implementing reproducible computational research }
+
+\leavevmode\vadjust pre{\hypertarget{ref-tidyverse}{}}%
+\CSLLeftMargin{26. }%
+\CSLRightInline{Wickham H, Averick M, Bryan J, et al (2019) \href{https://doi.org/10.21105/joss.01686}{Welcome to the {tidyverse}}. Journal of Open Source Software 4:1686}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nullabor}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) \href{https://CRAN.R-project.org/package=nullabor}{Nullabor: Tools for graphical inference}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-ggthemes}{}}%
+\CSLLeftMargin{28. }%
+\CSLRightInline{Arnold JB (2019) \href{https://CRAN.R-project.org/package=ggthemes}{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-RColorBrewer}{}}%
+\CSLLeftMargin{29. }%
+\CSLRightInline{Neuwirth E (2014) \href{https://CRAN.R-project.org/package=RColorBrewer}{RColorBrewer: ColorBrewer palettes}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-cowplot}{}}%
+\CSLLeftMargin{30. }%
+\CSLRightInline{Wilke CO (2019) \href{https://CRAN.R-project.org/package=cowplot}{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-png}{}}%
+\CSLLeftMargin{31. }%
+\CSLRightInline{Urbanek S (2013) \href{https://CRAN.R-project.org/package=png}{Png: Read and write PNG images}. }
+
+\leavevmode\vadjust pre{\hypertarget{ref-grid}{}}%
+\CSLLeftMargin{32. }%
+\CSLRightInline{R Core Team (2019) \href{https://www.R-project.org/}{R: A language and environment for statistical computing}. R Foundation for Statistical Computing, Vienna, Austria}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kableExtra}{}}%
+\CSLLeftMargin{33. }%
+\CSLRightInline{Zhu H (2019) \href{https://CRAN.R-project.org/package=kableExtra}{kableExtra: Construct complex table with 'kable' and pipe syntax}. }
+
+\end{CSLReferences}
 

### 2023-03-15 paper/paper.Rmd
paper for IEEE Vis

@@
 These findings should encourage map creators to implement alternative displays and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
-dev: pdf
 bibliography: paper.bib
@@
 
-<!-- Changes: thyroid instead of liver - check; lineup need to be hexmap; check language with chatgpt/grammarly; get refs formatted and paper into 10 pages -->
+<!-- Changes: thyroid instead of liver - check; lineup need to be hexmap; check language with chatgpt/grammarly; get refs formatted and paper into 10 pages; use new template -->
 
@@
 ggdraw() +
-  draw_plot(rasterGrob(readPNG("figures/aus_cities_3_geo.png")))
+  draw_plot(rasterGrob(readPNG("figures/aus_cities_3_hex.png")))
 ```

### 2023-03-15 paper/paper_vgtc.tex
paper for IEEE Vis

--- 2023-03-14 paper/paper.tex
@@
-%% template.tex
-%% from
-%% bare_conf.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE!
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-\documentclass[conference,final,]{IEEEtran}
-% Some Computer Society conferences also require the compsoc mode option,
-% but others use the standard conference format.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at:
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
+\documentclass[journal]{vgtc}                     % final (journal style)
+%\documentclass[journal,hideappendix]{vgtc}        % final (journal style) without appendices
+%\documentclass[review,journal]{vgtc}              % review (journal style)
+%\documentclass[review,journal,hideappendix]{vgtc} % review (journal style)
+%\documentclass[widereview]{vgtc}                  % wide-spaced review
+%\documentclass[preprint,journal]{vgtc}            % preprint (journal style)
+
+%% Uncomment one of the lines above depending on where your paper is
+%% in the conference process. ``review'' and ``widereview'' are for review
+%% submission, ``preprint'' is for pre-publication in an open access repository,
+%% and the final version doesn't use a specific qualifier.
+
+%% If you are submitting a paper to a conference for review with a double
+%% blind reviewing process, please use one of the ``review'' options and replace the value ``0'' below with your
+%% OnlineID. Otherwise, you may safely leave it at ``0''.
+\onlineid{0}
+
+%% In preprint mode you may define your own headline. If not, the default IEEE copyright message will appear in preprint mode.
+%\preprinttext{To appear in IEEE Transactions on Visualization and Computer Graphics.}
+
+%% In preprint mode, this adds a link to the version of the paper on IEEEXplore
+%% Uncomment this line when you produce a preprint version of the article 
+%% after the article receives a DOI for the paper from IEEE
+%\ieeedoi{xx.xxxx/TVCG.201x.xxxxxxx}
+
+%% declare the category of your paper, only shown in review mode
+\vgtccategory{Research}
+
+%% please declare the paper type of your paper to help reviewers, only shown in review mode
+%% choices:
+%% * algorithm/technique
+%% * application/design study
+%% * evaluation
+%% * system
+%% * theory/model
+\vgtcpapertype{please specify}
 
 \usepackage{graphicx}
-
-% *** MATH PACKAGES ***
-%
-%\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-%% BEGIN MY ADDITIONS %%
-
-\usepackage[unicode=true]{hyperref}
-
-\hypersetup{
-            pdftitle={Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics},
-            pdfkeywords={statistics, visual inference, geospatial, population},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-
-% Pandoc toggle for numbering sections (defaults to be off)
-\setcounter{secnumdepth}{5}
-
-% tightlist command for lists without linebreak
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% From pandoc table feature
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-
-% Pandoc citation processing
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-% for Pandoc 2.8 to 2.10.1
-\newenvironment{cslreferences}%
-  {}%
-  {\par}
-% For Pandoc 2.11+
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\usepackage{graphicx}
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
-
-%% END MY ADDITIONS %%
-
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
+\usepackage{multirow, booktabs}
+
 %
@@
 
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-
-\author{
-
-%% ---- classic IEEETrans wide authors' list ----------------
- % -- end affiliation.wide
-%% ----------------------------------------------------------
-
-%% ---- classic IEEETrans one column per institution --------
- %% -- end if/affiliation.institution-columnar
-%% ----------------------------------------------------------
-
-%% ---- one column per author, classic/default IEEETrans ----
- % -- beg affiliation.author-columnar
-  %% -- beg for/affiliation.institution.author
-\IEEEauthorblockN{
-Stephanie Kobakian
+\author{%
+  \authororcid{Stephanie Kobakian}{0000-0002-4616-0048}
+  and 
+  \authororcid{Dianne Cook}{0000-0002-3813-7155}
 }
-\IEEEauthorblockA{Queensland University of Technology\\
-Science and Engineering Faculty\\
-Brisbane, Australia
-\\stephanie.kobakian@qut.edu.au
+
+\authorfooter{
+  %% insert punctuation at end of each item
+  \item
+  	Stephanie Kobakian was with Queensland University of Technology.
+  	E-mail: stephanie.kobakian@gmail.com
+  \item
+  	Dianne Cook is with Monash University
+  	E-mail: dicook@monash.edu.
 }
- %% -- end for/affiliation.institution.author
-\and
-  %% -- beg for/affiliation.institution.author
-\IEEEauthorblockN{
-Dianne Cook
-}
-\IEEEauthorblockA{Monash University\\
-Econometrics and Business Statistics Faculty\\
-Melbourne, Australia
-\\dicook@monash.edu
-}
- %% -- end for/affiliation.institution.author
- %% -- end for/affiliation.institution
- %% -- end if/affiliation.institution-columnar
-%% ----------------------------------------------------------
-
-}
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-%
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3},
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
-\maketitle
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract
-\begin{abstract}
+
+%% Abstract section.
+\abstract{%
  The choropleth map display is commonly used for communicating spatial distributions across geographic areas.
@@
 These findings should encourage map creators to implement alternative displays and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
-\end{abstract}
+  %
+  %% We recommend that you link to your supplemental material here in the abstract, as well
+  %% as in the Supplemental Materials section at the end.
+  A free copy of this paper and all supplemental materials are available at \url{https://github.com/srkobakian/experiment}.
+}
 
 % keywords
-\begin{IEEEkeywords}
-statistics; visual inference; geospatial; population
-\end{IEEEkeywords}
-
-% use for special paper notices
+\keywords{statistics; visual inference; geospatial; population distribution, cartogram, experiment, power comparison}
+
+\teaser{
+  \centering
+   \includegraphics[width=0.45\linewidth,height=0.3\textheight]{paper_files/figure-latex/thyroid-choro-1} \hspace{1cm}\includegraphics[width=0.45\linewidth,height=0.3\textheight]{paper_files/figure-latex/thyroid-hex-1}
+  \caption{%
+  	Which plot type is better?
+Distribution of thyroid incidence among females across the Statistical Areas of Australia at Level 2, displayed as a choropleth map (left), and a hexagon tile map (right).
+Blue indicates lower than average and red indicates higher than average incidence.
+There is high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) that can now be seen in the hexagon tile map, along with numerous isolated spots, which were obscured in the choropleth.
+  }
+  \label{fig:teaser}
+}
+
+\begin{document}
 
@@
 % creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
+%\IEEEpeerreviewmaketitle
 
@@
 
-This study compares the effectiveness of the spatial display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics.
+This study compares the effectiveness of a new spatial display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics.
 The choropleth map is the traditional method for visualizing aggregated statistics across administrative boundaries.
@@
 A hexagon tile map forgoes the familiar boundaries, in favor of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location.
-It differs in the relaxed requirement to have connected hexagons, and allows sparsely located hexagons.
+It differs in the relaxed requirement to have connected hexagons and allows sparsely located hexagons.
 This type of display may be useful for other countries, and other purposes.
-The algorithm to construct a hexagon tile map is available in the R package sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]}.
-
-The hexagon tile map was designed for Australia, motivated by a need to display spatial statistics for the Australian Cancer Atlas.
-None of the existing approaches for creating cartograms or hexagon tiling perform well for the Australian landscape, which has vast open spaces and concentrations of population in small regions clustered on the coastlines.
-
-The Australian Cancer Atlas {[}\protect\hyperlink{ref-atlas}{2}{]} is an online interactive web tool created to explore the burden of cancer on Australian communities.
+The algorithm to construct a hexagon tile map is available in the R package \texttt{sugarbag}~\cite{sugarbag}.
+
+%The hexagon tile map was designed for Australia, motivated by a need to display spatial statistics for the Australian Cancer Atlas.
+None of the existing approaches for creating cartograms or hexagon tiling performs well for the Australian landscape, which has vast open spaces and concentrations of population in small regions clustered on the coastlines.
+The hexagon tile map was specifically designed for Australia to address the challenges of displaying spatial statistics for the Australian Cancer Atlas.
+Traditional approaches for creating cartograms or hexagon tiling were not suitable for the Australian landscape.
+The vast open spaces and small population clusters concentrated on the coastlines generate convergence problems for cartogram algorithms and even when they converge yield spatial displays that are no longer recognizable as Australia.
+There was a need for a new approach to displaying Australian geography to accurately represent the spatial distribution of cancer statistics.
+
+The Australian Cancer Atlas \cite{atlas} is an online interactive web tool created to explore the burden of cancer on Australian communities.
 There are many cancer types to be explored individually or aggregated.
@@
 It uses a choropleth map display and diverging color scheme to draw attention to relationships between neighboring areas.
-The hexagon tile map may be a useful alternative display to enhance the atlas.
-
-The experiment was conducted using the lineup protocol, a visual inference procedure {[}\protect\hyperlink{ref-GIIV}{3}{]}, to objectively test the effectiveness of the two displays.
-
-The paper is organised as follows.
-The next section discusses the background of geographic data display and visual inference procedures.
-The \protect\hyperlink{methodology}{Methodology} section describes the methods for conducting the experiment and analysing the results.
+The hexagon tile map may be a useful alternative display to enhance the Atlas.
+
+To objectively test the effectiveness of the two displays, this experiment was conducted using the lineup protocol, a visual inference procedure \cite{GIIV}.
+The design of the experiment includes several spatial patterns as seen in the cancer statistics data, several simulated sets of data to provide replication, and crowd-sourcing to collect responses from almost 100 people.
+The procedure follows that used in Hofmann et al.
+(2012)~\cite{GTPCCD}.
+
+The paper is organized as follows.
+The next section discusses the background of geographic data displays and visual inference procedures.
+The \protect\hyperlink{methodology}{Methodology} section describes the methods for conducting the experiment and analyzing the results.
 The results are summarized in the \protect\hyperlink{results}{Results} section.
+
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.9\linewidth]{paper_files/figure-latex/lineup-1} \caption{An example of the lineups shown to participants.
+This lineup of twelve hexagon tile map displays contains one map with a simulated population-related structure and the remainder are null plots that contain only spatial correlation between neighbors.
+In this lineup, the population structure is the concentration in all cities, and is located in position 3.}\label{fig:lineup}
+\end{figure*}
 
@@
 
-Spatial visualisations communicate the distribution of statistics over geographic landscapes.
-The choropleth map {[}\protect\hyperlink{ref-EI}{4}{]}, {[}\protect\hyperlink{ref-BCM}{5}{]} is a traditional display.
+Spatial visualizations communicate the distribution of statistics over geographic landscapes.
+The choropleth map \cite{EI,BCM} is a traditional display.
 It is used to present statistics that have been aggregated on geographic units.
-Creating a choropleth map involves drawing polygons representing the administrative boundaries, and filling with colour mapped to the value of the statistic.
-The choropleth map places the statistic in the context of the spatial domain, so that the reader can see whether there are spatial trends, clusters or anomalies.
+Creating a choropleth map involves drawing polygons representing the administrative boundaries, and filling them with color mapped to the value of the statistic.
+The choropleth map places the statistic in the context of the spatial domain so that the reader can see whether there are spatial trends, clusters, or anomalies.
 This is important for digesting disease patterns.
@@
 If there is a cluster, or an anomaly, there may be a localized outbreak of the disease.
-Aggregating the statistic on administrative units, provides a level of privacy to individuals, while allowing the impact of the disease on the community to be analyzed.
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{paper_files/figure-latex/thyroid-choro-1}
-
-}
-
-\caption{A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2.
+Aggregating the statistic on administrative units, provides a level of privacy to individuals while allowing the impact of the disease on the community to be analyzed.
+
+%\begin{figure}
+
+%{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{paper_files/figure-latex/thyroid-choro-1}
+
+%}
+
+%\caption{A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2.
 Blue indicates lower than average and red indicates higher than average incidence.
 A cluster of high incidence is visible on the east coast.}\label{fig:thyroid-choro}
-\end{figure}
+%\end{figure}
 
@@
 Fig.
-\ref{fig:thyroid-choro} shows the choropleth map of thyroid cancer rates in Australia.
-The choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population related distribution of the statistic {[}\protect\hyperlink{ref-CBATCC}{6}{]}.
+\ref{fig:teaser} shows the choropleth map of thyroid cancer rates in Australia.
+The choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population-related distribution of the statistic \cite{CBATCC}.
 \emph{Land doesn't get cancer, people do} -- a more effective way to communicate the spatial distributions of cancer statistics is needed.
@@
 A cartogram is a general solution for better displaying a population-based statistic.
-It transforms the geographic map base to reflect the population in the geographic region, while preserving some aspects of the geographic location.
-There are several cartogram algorithms {[}\protect\hyperlink{ref-ACTUC}{7}{]}, {[}\protect\hyperlink{ref-CBATCC}{6}{]}; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
-The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units but can result in losing the familiar geographic information.
+It transforms the geographic map base to reflect the population in the geographic region while preserving some aspects of the geographic location.
+There are several cartogram algorithms \cite{ACTUC,CBATCC}; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
+The changes to the boundaries result in cartograms that accurately communicate the population by mapping the area for each of the geographic units but can result in losing the familiar geographic information.
 For Australia, the transformations warp the country so that it is no longer recognizable.
 
-Alternative algorithms make various trade offs between familiar shapes and representation of geographic units.
-The non-contiguous cartogram method {[}\protect\hyperlink{ref-NAC}{8}{]} keeps the shapes of geographic units intact, and changes the size of the shape.
+Alternative algorithms make various trade-offs between familiar shapes and the representation of geographic units.
+The non-contiguous cartogram method \cite{NAC} keeps the shapes of geographic units intact and changes the size of the shape.
 This method disconnects areas creating empty space on the display losing the continuity of the spatial display of the statistic.
-The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{7}{]} represents each unit as a circle, sized according to the value of the statistic.
-The neighbour relationships are mostly maintained by how the circles touch.
-A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{9}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{10}{]}.
-There have been thorough reviews of the array of methods, as suitable for cancer atlas displays {[}\protect\hyperlink{ref-review}{11}{]}, {[}\protect\hyperlink{ref-BCM}{5}{]}.
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{paper_files/figure-latex/thyroid-hex-1}
-
-}
-
-\caption{A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
+The Dorling cartogram \cite{ACTUC} represents each unit as a circle, sized according to the value of the statistic.
+Neighbor relationships are mostly maintained by how the circles touch.
+A similar approach was pioneered by Raisz \cite{RSCW}, using rectangles that tile to align borders of neighbors \cite{CDWCS}.
+There have been thorough reviews of the array of methods, suitable for cancer atlas displays \cite{review,BCM}.
+
+%\begin{figure}
+
+%{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{paper_files/figure-latex/thyroid-hex-1}
+
+%}
+
+%\caption{A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
 The high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) can now be seen, along with numerous isolated spots.}\label{fig:thyroid-hex}
-\end{figure}
+%\end{figure}
 
@@
 It has the effect of spreading out the inner city areas while maintaining the spatial locations or regions in remote areas.
-The algorithm is available in the R package, sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]}.
+The algorithm is available in the R package, \texttt{sugarbag}~\cite{sugarbag}.
 Fig.
-\ref{fig:thyroid-hex} shows the hexagon tile map.
-Colour maps from substantially below average (blue) to substantially above average (red) rates.
+\ref{fig:teaser} shows the hexagon tile map.
+Color maps from substantially below average (blue) to substantially above average (red) rates.
 The inner city areas have expanded, making it possible to see the cancer incidence in the small, densely populated areas.
-Remote regions are represented by isolated hexagons, which is not ideal, but maintains the spatial location of these data values.
+Remote regions are represented by isolated hexagons, which is not ideal but maintains the spatial location of these data values.
 It is of interest to know how well the spatial distribution is perceived for this display, in comparison to the choropleth.
@@
 
-In order to assess the effectiveness of the hexagon tile map, the lineup protocol {[}\protect\hyperlink{ref-GIIV}{3}{]},{[}\protect\hyperlink{ref-BCHLLSW09}{12}{]} from visual inference procedures is employed.
+In order to assess the effectiveness of the hexagon tile map, the lineup protocol \cite{GIIV,BCHLLSW09} from visual inference procedures is employed.
 The approach mirrors classical statistical inference.
-The procedures for doing a power comparison of competing plot designed, outlined in {[}\protect\hyperlink{ref-GTPCCD}{13}{]}, are followed.
+The procedures for doing a power comparison of competing plot designs, outlined in Hofmann et al.
+(2012)~\cite{GTPCCD}, are followed.
 
@@
 In the lineup protocol, the plot plays the role of the test statistic, and the data plot is embedded in a field of null plots.
-Defining the plot using a grammar of graphics {[}\protect\hyperlink{ref-ggplot2}{14}{]} makes it a functional mapping of the variables and thus, it can be considered to be a statistic.
+Defining the plot using a grammar of graphics \cite{ggplot2} makes it a functional mapping of the variables and thus, it can be considered to be a statistic.
 With the same data, two different plots can be considered to be competing statistics, one possibly a more powerful statistic than the other.
@@
 The null hypothesis is explicitly provided by the grammatical plot description.
-For example, if a histogram is the plot type being used, the null might be that the underlying distribution of the data is a Gaussian.
+For example, if a histogram is the plot type being used, the null might be that the underlying distribution of the data is Gaussian.
 Null data would be generated by simulating from a normal model, with the same mean and standard deviation as the data.
@@
 \ref{fig:lineup} shows a lineup of the hexagon tile map, of size \(m=12\).
-Plot 3 is the data plot, and the remaining 11 are plots of null data.
-
-\begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/lineup-1} \caption{This lineup of twelve hexagon tile map displays contains one map with a real population related structure.
-The rest are null plots that contain spatial correlation between neighbours.}\label{fig:lineup}
-\end{figure}
+Plot 3 is the data plot, with data generated as described below, and the remaining 11 are plots of null data.
 
@@
 The power of the test statistic (data plot) is provided by this proportion.
-Power in a statistical sense is the ability of the statistic to \emph{produce a rejection} of the null hypothesis, if it is indeed \emph{not true}.
+Power in a statistical sense is the ability of the statistic to \emph{produce a rejection} of the null hypothesis if it is indeed \emph{not true}.
 With the same data plotted using two different displays, the display with the highest proportion of people who choose the data plot would be considered to be the most powerful statistic.
@@
 \def\labelenumi{\arabic{enumi}.}
-\tightlist
+%\tightlist
 \item
@@
 
-Australia is used for the study, with Statistical Area 3 (SA3) {[}\protect\hyperlink{ref-abs2016}{15}{]} as the geographic units.
-The results should apply broadly to any other geographic area of interest.
+Maps of Australia, with Statistical Area 3 (SA3)~\cite{abs2016} as the geographic units are used for the study. The results should apply broadly to any other geographic regions of interest.
+
+\begin{figure*}[h]
+\centering 
+  \includegraphics[width=0.9\linewidth]{figures/factors.pdf} 
+\caption{The three trend models, displayed as a hexagon tile map.
+One would expect the choropleth to do best only on the "northwest to southeast" pattern, and the hexagon tile map to perform better with the "all cities" and "three cities".}\label{fig:factors}
+\end{figure*}
 
@@
 The secondary factor is a trend model.
-Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to do well, and two with differing level of inner city hot spots.
+Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to do well, and two with differing levels of inner city hot spots.
 These latter two reflect the structure seen in the thyroid cancer data (Fig.
-\ref{fig:thyroid}).
+\ref{fig:teaser}).
+Fig.
+\ref{fig:factors}) shows examples of the different trend models displayed using a hexagon tile map.
 This produces six treatment levels:
 
-\begin{itemize}
-\tightlist
+\begin{itemize} \itemsep 0in
+%tightlist
 \item
@@
 
-Data is generated for each of the trend models, with four replicates, and each displayed both as a choropleth and as a hexagon tile map, which yields 12 data sets, and 24 data plots.
+Data is generated for each of the trend models, with four replicates, and each is displayed both as a choropleth and as a hexagon tile map, which yields 12 data sets, and 24 data plots.
 This set of displays is divided in half, providing two sets of 12 displays, Group A and Group B.
@@
 Participants saw a data set only once, either as a choropleth or as a hexagon tile map.
-Table \ref{fig:exp-design} summarises the design and the allocation of the displays.
-
-\begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/exp-design-1} \caption{The experimental design used in the visual inference study.}\label{fig:exp-design}
+Fig.
+\ref{fig:exp-design} summarises the design and the allocation of the displays.
+
+\begin{figure}[h]
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/exp-design-1} \caption{Schematic illustrating the experimental design used in this visual inference study.}\label{fig:exp-design}
 \end{figure}
@@
 In most scenarios, permutation is the main approach for generating null plots.
-It is used to break association between variables, while maintaining marginal distributions.
+It is used to break any associations between variables while maintaining marginal distributions.
 This is too simple for spatial data.
 In spatial data, a key feature is the spatial dependence or smoothness over the landscape.
-To do something simple, like permute the values relative to the geographic location would produce null plots which are too chaotic, and the data plot will be recognisable for its smoothness rather than any structure of interest.
-
-For spatial data, null data is stationary data, where the mean, variance and spatial dependence are constant over the geographic units.
-Stationary data is specified by a variogram model {[}\protect\hyperlink{ref-POG}{16}{]}.
-Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots.
+To do something simple, like permuting the values relative to the geographic location would produce null plots which are too chaotic, and the data plot will be recognizable for its smoothness rather than any structure of interest.
+
+For spatial data, null data is stationary data, where the mean, variance, and spatial dependence are constant over the geographic units.
+Stationary data is specified by a variogram model \cite{POG} Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots.
 The parameters for the Gaussian model were sill=1, range=0.3 with the variance generated by a standard normal distribution.
 
-The R package \texttt{gstat} {[}\protect\hyperlink{ref-gstat}{17}{]} was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
+The R package \texttt{gstat}~\cite{gstat} was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
 
@@
 The randomness induced when generating the null data was smoothed to mirror the practices employed by the Australian Cancer Atlas statisticians.
-In these 12 sets of data, each of the 12 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas, without implementing uncertainty via transparency.
+In these 12 sets of data, each of the 12 maps was smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas, without implementing uncertainty via transparency.
 
 A list of neighbors for each geographic unit was generated to use when smoothing the distributions.
-For each geographic unit the same spatial smoother was applied in each layer of smoothing.
-It kept half of the units' previous value, and derived the new half as the mean of the values of its neighbors at the previous layer of smoothing.
-
-This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the thyroid cancer distribution (Fig. \ref{fig:thyroid}).
+For each geographic unit, the same spatial smoother was applied in each layer of smoothing.
+It kept half of the units' previous value and derived the new half as the mean of the values of its neighbors at the previous layer of smoothing.
+
+This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the thyroid cancer distribution (Fig. \ref{fig:teaser}).
 
@@
 
-The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia, calculated when creating the hexagon tile map using the sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]} package.
-201 of the 336 SA3s were considered greater capital city areas, the values of these areas were increased to create red clusters.
-The amount was chosen to make clusters around the cities visible in the choropleth display even if they were not overtly noticeable.
+The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia, calculated when creating the hexagon tile map using the \texttt{sugarbag}~\cite{sugarbag} package.
+201 of the 336 SA3s were considered greater capital city areas, and the values of these areas were increased to create red clusters.
+The amount was chosen to make clusters around the cities visible in the choropleth display even if they were not overly noticeable.
 
@@
 However, for each of the four replicates for the Three Cities trend, a random sample of capital cities was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart.
-Only values of the areas nearest to the three cities were increased to create clusters.
+Only the values of the areas nearest to the three cities were increased to create clusters.
 
 One of the lineup locations was chosen to embed the real trend model map, in each of the four replicates, for the three trend models.
-The location was chosen from a sub sample of the 12 possible locations.
-The chance of reptition using resampling was introduced to prevent participants from inducing the location by elimination, the locations 1, 7, 10 and 11 were not used.
-
-As seen in Fig \ref{fig:exp-design}, the choropleth and hexagon display used the same location for the real data display of the trend model was added to the spatially correlated null values for each lineup.
+The location was chosen from a sub-sample of the 12 possible locations.
+The chance of repetition using resampling was introduced to prevent participants from inducing the location by elimination, the locations 1, 7, 10, and 11 were not used.
+
+As seen in Fig \ref{fig:exp-design}, the choropleth and hexagon display used the same location for the real data display of the trend model and was added to the spatially correlated null values for each lineup.
 Each set of lineup data was used to produce a choropleth map lineup and hexagon tile map lineup.
-These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
+These matched pairs were split between Group A and Group B according to the 2 x 3-factor experimental design depicted in \ref{fig:exp-design}.
 
 For each of the 144 individual maps, the values for each geographic area were rescaled to create a similar color scale from deep blue to dark red within each map.
-This meant at least one geographic unit was coloured dark blue, and at least one was red, in every map display of every lineup.
+This meant at least one geographic unit was colored dark blue, and at least one was red, in every map display of every lineup.
 
@@
 
-For the population related displays, the clusters in the cities appeared more red than the rest of Australia.
+For the population-related displays, the clusters in the cities appeared redder than the rest of Australia.
 
@@
 
-The first step in the data cleaning process involved checking that survey responses collected for each participants were only included once in the data set.
+The first step in the data cleaning process involved checking that survey responses collected for each participant was only included once in the data set.
 The data cleaning process also involved filtering out participants' who did not provide at least three unique choices when considering each of the twelve lineups.
@@
 Basic descriptive statistics were used to contrast the detection rate for the two types of displays.
-Comparison was also made across the trend models, contrasting the mean and standard detection rate for each group, who had seen the different map display type for each replicate.
+A comparison was also made across the trend models, contrasting the mean and standard detection rate for each group, which had seen the different map display types for each replicate.
 
@@
 
-Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.
-
-Plots will be made in R {[}\protect\hyperlink{ref-RCore}{18}{]}, with the \texttt{ggplot2} package {[}\protect\hyperlink{ref-ggplot2}{14}{]}.
+Similar plots were made of the feedback and demographic variables - the reason for the choice, reported difficulty, gender, age, education, and having lived in Australia - against the design variables.
+
+Plots will be made in R \cite{RCore}, with the \texttt{ggplot2} package~\cite{ggplot2}.
 
@@
 
-The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R {[}\protect\hyperlink{ref-RCore}{18}{]} \texttt{glmer()} function in the \texttt{lme4} {[}\protect\hyperlink{ref-lme4}{19}{]} package implements generalised linear mixed effect models.
+The likelihood of detecting the data plot in the lineup can be modeled using a linear mixed-effects model.
+The R \cite{RCore} \texttt{glmer()} function in the \texttt{lme4}~\cite{lme4} package implements generalized linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
@@
 
-where \(y_{ij} = 0, 1\) is the logg odds for whether the subject detected the data plot, \(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect, \(\delta_j\) is the trend model effect.
+\noindent where \(y_{ij} = 0, 1\) is the log odds for whether the subject detected the data plot, \(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect, \(\delta_j\) is the trend model effect.
 We are allowing for an interaction between map type and trend model as the response is binary, so a logistic model was used.
-As each participant provides results from 12 lineups, this model can account for each individual participants' abilities as it includes a subject-specific random intercept.
+As each participant provides results from 12 lineups, this model can account for each individual participant's abilities as it includes a subject-specific random intercept.
 
@@
 
-The taipan {[}\protect\hyperlink{ref-taipan}{20}{]} package for R was used to create the survey web application.
-This structure was altered to collect responses regarding participants demographics and their survey responses.
+The \texttt{taipan}~\cite{taipan} package for R was used to create the survey web application.
+This structure was altered to collect responses regarding participants' demographics and their survey responses.
 The survey app contained three tabs.
 Participants were first asked for their demographics their Figure Eight contributor ID, and their consent to the responses being used for analysis.
-The demographics collected included participants' preferred pronoun, the highest level of education achieved, their age range and whether they had lived in Australia.
+The demographics collected included participants' preferred pronouns, the highest level of education achieved, their age range, and whether they had lived in Australia.
 
 After submitting these responses, the survey application switched to the tab of lineups and associated questions.
-This allowed participants to easily move through the twelve displays and provide their choice, reason for their choice, and level of certainty.
+This allowed participants to easily move through the twelve displays and provide their choice, the reason for their choice, and the level of certainty.
 
@@
 The script also added the title of the image, which indicated the type of map display, the type of distribution hidden in the lineup, and the location of the data plot.
-It also calculated the time taken by participant to view each lineup.
+It also calculated the time taken by participants to view each lineup.
 
 Each participant used the internet to access the survey.
-The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results.
-The application connected to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{21}{]} R package when participants opened the application, and interacted again when participants chose to submit the survey.
-At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.
+The data transfer from the web application to the data set took place using a secure link to the google sheet used to store results.
+The application connected to the sheet using the \texttt{googlesheets}~\cite{sheets} R package when participants opened the application and interacted again when participants chose to submit the survey.
+At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the sheet.
 
@@
 
-Participants were recruited from the Figure Eight crowdsourcing platform {[}\protect\hyperlink{ref-figeight}{22}{]} to evaluate lineups.
+Participants were recruited from the Figure Eight crowdsourcing platform \cite{figeight} to evaluate lineups.
 The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
-Potential participants needed to have achieved level 2 or level 3 from prior work on the platform.
+Potential participants need to have achieved level 2 or level 3 from prior work on the platform.
 All participants were at least 18 years old.
@@
 There were 92 participants involved in the study.
-All participants read introductory materials, and were trained using three test displays, to orient them to the evaluation task.
+All participants read introductory materials and were trained using three test displays, to orient them to the evaluation task.
 All participants who completed the task were compensated \$AUD5 for their time, via the Figure Eight payment system.
@@
 A pilot study was conducted in the working group of the Econometrics and Business Statistics Department of Monash University.
-This allowed us to estimate the effect size, and thus decide on number of participants to collect responses from.
+This allowed us to estimate the effect size, and thus decide on a number of participants to collect responses from.
 
@@
 
-\begin{itemize}
-\tightlist
+\begin{itemize} \itemsep 0in
+%tightlist
 \item
@@
 Fig.
-\ref{fig:detect-compare} displays the average detection rates for the two types of plot separately for each trend model.
-Each trend model was tested using four repetitions, evaluations on the same data set were seen as either choropleths or hexagon tile maps by each group as specified in Table.
+\ref{fig:detect-compare} displays the average detection rates for the two types of plots separately for each trend model.
+Each trend model was tested using four repetitions, and evaluations on the same data set were seen as either choropleths or hexagon tile maps by each group as specified in Table.
 \ref{fig:exp-design}; the detection rates for each display are connected by a line segment.
@@
 Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup.
-The points for the same data set shown in a choroleth or hexagon tile map display are linked to show the difference in the detection rate.}\label{fig:detect-compare}
+The points for the same data set shown in a choropleth or hexagon tile map display are linked to show the difference in the detection rate.}\label{fig:detect-compare}
 \end{figure}
@@
 
-\begin{table}
-
+\begin{table}[h]
 \caption{\label{tab:desc-stats}The mean and standard deviation of the rate of detection for each trend model, calculated for the choropleth and hexagon tile map displays.}
@@
 Table.
-\ref{tab:detect-glmer1} presents a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on the detection rate.
+\ref{tab:detect-glmer1} presents a summary of the generalized linear mixed effects model, testing the effect of plot type and trend model on the detection rate.
 The results support the summary from Fig.
@@
 Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
-Allowing for the interaction effect, the difference in detection rate decreases for population related displays for a choropleth map lineup, but increases for a hexagon tile map display.
-The log odds of detection show in Table. \ref{tab:detect-glmer1} can be back transformed after taking the sum of all terms for the trend and type of display that are of interest.
+Allowing for the interaction effect, the difference in detection rate decreases for population-related displays for a choropleth map lineup, but increases for a hexagon tile map display.
+The log odds of detection are shown in Table. \ref{tab:detect-glmer1} can be back-transformed after taking the sum of all terms for the trend and type of display that are of interest.
 For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to 0.63 from 0.52 for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
@@
 
-\begin{table}
-
-\caption{\label{tab:detect-glmer1}The model output for the generalised linear mixed effect model for detection rate.
+\begin{table}[h]
+
+\caption{\label{tab:detect-glmer1}The model output for the generalized linear mixed effect model for detection rate.
 This model considers the type of display, the trend model hidden in the data plot, and accounts for contributor performance.}
@@
 \ref{fig:beeswarm} shows horizontally jittered dot plots to contrast the time taken by participants to evaluate each lineup when viewing each type of display.
-The time are also separated by trend model and whether the data plot was detected or not detected.
-The time taken to complete an evaluation ranged from milliseconds to 60 seconds.
-The average time taken for type of display is shown as a large colored dot on each plot.
+The time is also separated by the trend model and whether the data plot was detected or not detected.
+The time taken to complete an evaluation ranges from milliseconds to 60 seconds.
+The average time taken for the type of display is shown as a large colored dot on each plot.
 when considering the heights of the green and orange dots, there is little difference in the average time taken to read a choropleth or hexagon tile map.
 Comparing the same colored dot across each trend model row, there is a slight increase in the time taken to correctly detected the data plot in the hexagon tile map lineup, but little difference in evaluation time for the choropleth display.
-However, there were substantially less correct detections for choropleth lineups for the Three cities and All Cities trends.
+However, there were substantially fewer correct detections for choropleth lineups for the Three cities and All Cities trends.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/beeswarm-1} \caption{The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots.
-The colored point indicates average time taken for each plot type.
-Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between plot types.}\label{fig:beeswarm}
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/beeswarm-1} \caption{The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dot plots.
+The colored point indicates the average time taken for each plot type.
+Although some participants take just a few seconds per evaluation, and some take as much as much as 60 seconds, there is very little difference in time taken between plot types.}\label{fig:beeswarm}
 \end{figure}
@@
 
-Participants provided their level of certainty regarding their choice using a five point scale.
+Participants provided their level of certainty regarding their choice using a five-point scale.
 Unlike the accuracy and speed of responses that were derived during the data processing phase, this was a subjective
@@
 Fig.
-\ref{fig:certainty} shows the amount of times participants provided each level of certainty.
+\ref{fig:certainty} shows the number of times participants provided each level of certainty.
 This was separated for each combination of trend models and display type, and colored depending on whether a participant correctly detected the data plot in the lineup.
-Participants often chose 4 or 5 when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
+Participants often chose 4 or 5 when viewing the population-related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
 This shows overconfidence in their detection ability when using a choropleth map display.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/certainty-1} \caption{The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/certainty-1} \caption{The number of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
 Participants were more likely to choose a high certainty when considering a Choropleth map.
@@
 
-The choice ``None of these reasons'' was used as the default value to minimise noise from participants who did not select a response.
+The choice ``None of these reasons'' was used as the default value to minimize noise from participants who did not select a response.
 
@@
 
-\caption{\label{tab:reason}The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
+\caption{\label{tab:reason}The number of participants that selected each reason for their choice of a plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
 The facets show whether or not the choice was correct.}
@@
 \cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash NW-SE} & Yes & trend & clusters\\
+\multirow{-2}{*}{\raggedright NW-SE} & Yes & trend & clusters\\
 \cmidrule{1-4}
@@
 \cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash Three Cities} & Yes & consistent & clusters\\
+\multirow{-2}{*}{\raggedright Three Cities} & Yes & consistent & clusters\\
 \cmidrule{1-4}
@@
 \cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash All Cities} & Yes & clusters, consistent & clusters\\
+\multirow{-2}{*}{\raggedright All Cities} & Yes & clusters, consistent & clusters\\
 \bottomrule
@@
 The results have shown that overall the use of the hexagon tile map display allows participants to find the data plot in the lineup more often.
-Using the visual inference protocol this result can be extended to show that it is a valid alternative display to communicate spatial distributions of population related data.
+Using the visual inference protocol this result can be extended to show that it is a valid alternative display to communicate spatial distributions of population-related data.
 
@@
 
-The differences seen in the \ref{fig:detect-compare} plot and Table.
+The differences are seen in the \ref{fig:detect-compare} plot and Table.
 \ref{tab:desc-stats} are reflected in the model results.
-Surprisingly the difference for the geographic distribution was significant at the 0.05 level.
+Surprisingly the difference in the geographic distribution was significant at the 0.05 level.
 It also showed that the hexagon tile map display performs marginally better than the choropleth for all trend models.
-Unexpectedly the detection rate suffers when using a choropleth map to display population related distributions.
+Unexpectedly the detection rate suffers when using a choropleth map to display population-related distributions.
 
@@
 \ref{fig:beeswarm} showed very little difference in the mean evaluation times.
-As the maximum time of all of the distributions approached 60 seconds it cannot be said that the participants' took longer to evaluate the hexagon tile map displays.
+As the maximum time of all of the distributions approached 60 seconds it cannot be said that the participants took longer to evaluate the hexagon tile map displays.
 
@@
 Fig.
-\ref{tab:reason} shows high levels of certainty of 4 and 5 were chosen by participants when looking at the population distributions in a choropleth map display show that they were over confident when attempting to find the real data plot in the choropleth map displays.
+\ref{tab:reason} shows high levels of certainty of 4 and 5 were chosen by participants when looking at the population distributions in a choropleth map display showing that they were overconfident when attempting to find the real data plot in the choropleth map displays.
 Participants performed better on the NW-SE distribution shown in the choropleth display and were reasonably confident about their decisions.
-The high levels of the mid range value of 3 could indicate that the participant did not want to provide a response, as this was the default value.
+The high levels of the mid-range value of 3 could indicate that the participant did not want to provide a response, as this was the default value.
 Those who chose level 4 or 5 were equally likely to be correct for the three cities lineups, but more likely to be correct than incorrect for the other two trend models.
@@
 The color scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
-Due to the consistent coloring of rural areas in a choropleth display, the choice ``All areas have similar colors'' was most common reason for a participants choice.
-The All Cities displays colored the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural color consistency.
-Choosing ``Clusters of colour'' was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions.
+Due to the consistent coloring of rural areas in a choropleth display, the choice ``All areas have similar colors'' was the most common reason for a participant's choice.
+The All Cities displays colored the inner-city areas of all capital cities redder, this was observable to participants and explains the equal choice of the city clusters or rural color consistency.
+Choosing ``Clusters of color'' was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions.
 It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays.
@@
 The choropleth map display and the tessellated hexagon tile map have been contrasted using the lineup protocol.
-The hexagon tile map was significantly more effective for spotting a real population related data trend model hidden in a lineup.
+The hexagon tile map was significantly more effective for spotting a real population-related data trend model hidden in a lineup.
 
@@
 The spatial distributions used to test these displays were inspired by the real spatially smoothed estimates of the cancer burden on Australian communities.
-However, this technique may be extended to other population related distributions, such as other diseases.
-
-The increasing population densities of capital cities despite large land area exacerbates the difference in the smallest and largest communities.
-The population density structure of Australia can be considered similar to that of Canada, New Zealand and many other countries.
-Therefore, this display is not only relevant to Australia, but all nations or population distributions that experience densely populated cities separated by vast rural expanses.
+However, this technique may be extended to other population-related distributions, such as other diseases.
+
+The increasing population densities of capital cities despite small land areas exacerbates the difference between the smallest and largest communities.
+The population density structure of Australia can be considered similar to that of Canada, New Zealand, and many other countries.
+Therefore, this display is not only relevant to Australia but all nations or population distributions that experience densely populated cities separated by vast rural expanses.
 
@@
 
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments.
-Mitchell O'Hara-Wild was a co-developer of the taipan {[}\protect\hyperlink{ref-taipan}{20}{]} R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
-We are thankful for the NUMBATs (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.
-
-The source code to produce this document can be found on \href{https://github.com/srkobakian/experiment/paper}{GitHub}.
+The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations, and Professor Kerrie Mengersen and Dr.
+Earl Duncan for regular meetings filled with suggestions and comments.
+Mitchell O'Hara-Wild was a co-developer of the \texttt{taipan}~\cite{taipan} R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
+We are thankful to the NUMBATs (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.
+
+The source code to produce this document can be found at \url{https://github.com/srkobakian/experiment/paper}.
 Supplementary materials have been included to discuss the survey procedures and the lineups that were used.
@@
 
-The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{18}{]} with the use of the following packages:
-
-\begin{itemize}
-\tightlist
-\item
-  For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{23}{]}, rticles {[}\protect\hyperlink{ref-rticles}{24}{]}, knitr {[}\protect\hyperlink{ref-knitr}{25}{]}.
-\item
-  For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{26}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{27}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{28}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{29}{]}.
-\item
-  For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{30}{]}, png {[}\protect\hyperlink{ref-png}{31}{]}, grid {[}\protect\hyperlink{ref-grid}{32}{]}.
-\item
-  For modelling and presentation of models: gstat {[}\protect\hyperlink{ref-gstat}{17}{]}, lme4 {[}\protect\hyperlink{ref-lme4}{19}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{33}{]}.
+The analysis of the work was completed in R  \cite{RCore} with the use of the following packages:
+
+\begin{itemize} \itemsep 0in
+%tightlist
+\item
+  For document creation: \texttt{rmarkdown}~\cite{rmarkdown}, \texttt{rticles}~\cite{rticles}, \texttt{knitr}~\cite{knitr}.
+\item
+  For lineup creation and data analysis: \texttt{tidyverse}~\cite{tidyverse}, \texttt{nullabor}~\cite{nullabor}, \texttt{ggthemes}~\cite{ggthemes}, \texttt{RColorBrewer}~\cite{RColorBrewer}.
+\item
+  For image displays: \texttt{cowplot}~\cite{cowplot}, \texttt{png}~\cite{png}, \texttt{grid}~\cite{grid}.
+\item
+  For modelling and presentation of models: \texttt{gstat}~\cite{gstat}, \texttt{lme4}~\cite{lme4}, \texttt{kableExtra}~\cite{kableExtra}.
 \end{itemize}
@@
 All applicants provided informed consent in line with QUT regulations prior to participating in this research.
+
+\bibliographystyle{abbrv-doi-hyperref}
+\bibliography{paper.bib}
+
+\end{document}
 
@@
 \end{CSLReferences}
-
-\end{document}

### 2023-03-21 paper/paper.Rmd
figs revised and order of factor levels

@@
     trend == "three" ~ "Three Cities")) %>% 
-  mutate(trend = fct_relevel(trend, "NW-SE","Three Cities","All Cities")) %>% 
+  mutate(trend = fct_relevel(trend,"All Cities","Three Cities", "NW-SE")) %>% 
   mutate(type = case_when(
@@
     panel.background = element_rect(fill = "transparent", colour = NA), 
-    plot.background = element_rect(fill = "transparent", colour = NA),
+    plot.background = element_rect(fill = "black", colour = NA),
     legend.background = element_rect(fill = "transparent", colour = NA),
@@
     text = element_text(colour = "white"),
-    axis.text = element_text(colour = "white")
+    axis.text = element_blank()
   )

### 2023-03-21 paper/paper.tex
figs revised and order of factor levels

@@
 \midrule
-Intercept & 0.07 & $^{ }$ & 0.16 & 0.67\\
-Hex. & 0.46 & $^{*}$ & 0.22 & 0.04\\
+Intercept & -1.27 & $^{***}$ & 0.19 & 0.00\\
+Hex. & 1.63 & $^{***}$ & 0.24 & 0.00\\
 \addlinespace
-Three Cities & -3.41 & $^{***}$ & 0.42 & 0.00\\
-All Cities & -1.34 & $^{***}$ & 0.24 & 0.00\\
+Three Cities & -2.07 & $^{***}$ & 0.43 & 0.00\\
+All Cities & 1.34 & $^{***}$ & 0.24 & 0.00\\
 \addlinespace
-Hex:Three Cities & 2.44 & $^{***}$ & 0.47 & 0.00\\
-Hex:All Cities & 1.16 & $^{***}$ & 0.33 & 0.00\\
+Hex:Three Cities & 1.28 & $^{**}$ & 0.48 & 0.01\\
+Hex:All Cities & -1.16 & $^{***}$ & 0.33 & 0.00\\
 \bottomrule
@@
 \cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash NW-SE} & Yes & trend & clusters\\
+\multirow{-2}{*}{\raggedright\arraybackslash All Cities} & Yes & clusters, consistent & clusters\\
 \cmidrule{1-4}
@@
 \cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash All Cities} & Yes & clusters, consistent & clusters\\
+\multirow{-2}{*}{\raggedright\arraybackslash NW-SE} & Yes & trend & clusters\\
 \bottomrule
@@
 \CSLLeftMargin{2. }%
-\CSLRightInline{Cancer Council Queensland {Australian Cancer Atlas (https://atlas.cancer.org.au)}. }
+\CSLRightInline{Cancer Council Queensland {Australian Cancer Atlas}, publisher = {Queensland University of Technology, Cooperative Research Centre for Spatial Information}, issue = {Version 09}, url={https://atlas.cancer.org.au}, year = {2018}, accessed = {Jan 12 2020}.
+}
 
@@
 \CSLLeftMargin{5. }%
-\CSLRightInline{Skowronnek A (2016) {Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata}.
-In: {Infovis Reading Group WS 2015/16}.
-\href{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}{https://alsino.io/static/papers/BeyondChoropleths\_AlsinoSkowronnek.pdf.
-}}
+\CSLRightInline{Skowronnek A (2016) \href{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}{{Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata}}.
+{Infovis Reading Group WS 2015/16} }
 
@@
 \CSLLeftMargin{7. }%
-\CSLRightInline{Dorling D (2011) \href{https://doi.org/10.1002/9780470979587.ch33}{{Area Cartograms: Their Use and Creation}}. In: Concepts and techniques in modern geography (CATMOG). pp 252--260}
+\CSLRightInline{Dorling D (2011) \href{https://doi.org/10.1002/9780470979587.ch33}{{Area Cartograms: Their Use and Creation}}.
+In: Concepts and techniques in modern geography (CATMOG).
+University of East Anglia: Environmental Publications, pp 252--260}
 
@@
 \CSLLeftMargin{11. }%
-\CSLRightInline{(2019) Cancer applications of choropleth maps, and the potential of cartograms and alternative map displays. Manuscript submitted for publication. }
+\CSLRightInline{Kobakian S, Cook D, Roberts J (2020) \href{https://ace.amegroups.com/article/view/6040}{Mapping cancer: The potential of cartograms and alternative map displays}.
+Annals of Cancer Epidemiology 4:}
 
@@
 \CSLLeftMargin{12. }%
-\CSLRightInline{Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) Statistical inference for exploratory data analysis and model diagnostics.
+\CSLRightInline{Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) \href{https://doi.org/10.1098/rsta.2009.0120}{Statistical inference for exploratory data analysis and model diagnostics}.
 Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383}
@@
 \CSLLeftMargin{15. }%
-\CSLRightInline{(2018) \href{\%7Bhttps://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)\%7D}{{Australian Statistical Geography Standard (ASGS)}}.
-Australian Bureau of Statistics }
+\CSLRightInline{Australian Bureau of Statistics (2018) \href{https://www.abs.gov.au/statistics/statistical-geography/australian-statistical-geography-standard-asgs}{{Australian Statistical Geography Standard (ASGS)}}.
+}
 
@@
 \CSLLeftMargin{22. }%
-\CSLRightInline{(2019) \href{https://www.figure-eight.com/}{The essential high-quality data annotation platform}. Figure Eight }
+\CSLRightInline{Figure Eight Inc (2019) \href{https://www.figure-eight.com/}{The essential high-quality data annotation platform}. }
 

### 2023-03-21 paper/paper_vgtc.tex
figs revised and order of factor levels

@@
 However, when choropleths are used the size of the geographic units will influence the understanding of the distribution derived by map users.
-The hexagon tile map is presented as an alternative display for visualizing population related distributions effectively.
-Visual inference is used to measure the power of the hexagon tile map design, and the choropleth is used as a comparison.
+The hexagon tile map is presented as an alternative display for visualizing population-related distributions effectively.
+Visual inference is used to measure the power of the hexagon tile map design, in comparison to the choropleth.
 The hexagon tile map display is tested using a distribution that is directly related to the geography, with values monotonically increasing from the North-West to South-East areas of Australia.
-This study finds in a hexagon tile map lineup the single map that contains a population related distribution is detected with greater probability than the same data displayed in a choropleth map.
+This study finds in a hexagon tile map lineup the single map that contains a population-related distribution is detected with greater probability than the same data displayed in a choropleth map.
 These findings should encourage map creators to implement alternative displays and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
@@
   %% as in the Supplemental Materials section at the end.
-  A free copy of this paper and all supplemental materials are available at \url{https://github.com/srkobakian/experiment}.
+  %A copy of this paper and all supplemental materials are available at \url{https://github.com/srkobakian/experiment}.
 }
@@
 The secondary factor is a trend model.
-Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to do well, and two with differing levels of inner city hot spots.
-These latter two reflect the structure seen in the thyroid cancer data (Fig.
+Three trend models were developed:  two with differing levels of inner city hot spots, and one mirroring a large spatial trend for which the choropleth would be expected to do well.
+Fig.
+\ref{fig:factors} shows examples of the different trend models displayed using a hexagon tile map.
+The inner city hotspots trend model reflects the structure seen in the thyroid cancer data (Fig.
 \ref{fig:teaser}).
-Fig.
-\ref{fig:factors}) shows examples of the different trend models displayed using a hexagon tile map.
 This produces six treatment levels:
@@
 \item
-  Trend: \emph{South-East to North-West; Locations in three population centres; Locations in multiple population centres, }
+  Trend: \emph{North West to South East; Locations in three population centres; Locations in multiple population centres, }
 \end{itemize}
@@
 \ref{fig:detect-compare} displays the average detection rates for the two types of plots separately for each trend model.
-Each trend model was tested using four repetitions, and evaluations on the same data set were seen as either choropleths or hexagon tile maps by each group as specified in Table.
+Each trend model was tested using four repetitions, and evaluations on the same data set were seen as either choropleths or hexagon tile maps by each group as specified in Fig.
 \ref{fig:exp-design}; the detection rates for each display are connected by a line segment.
@@
 
-Table.
-\ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
+Table \ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
 This also gives the standard deviations, the smallest standard deviation for all sets of replicates was the Three Cities trend model shown in a Choropleth display.
@@
 
-Table.
-\ref{tab:detect-glmer1} presents a summary of the generalized linear mixed effects model, testing the effect of plot type and trend model on the detection rate.
+Table \ref{tab:detect-glmer1} presents a summary of the generalized linear mixed effects model, testing the effect of plot type and trend model on the detection rate.
 The results support the summary from Fig.
-\ref{fig:detect-compare} and all parameters are statistically significant despite the large standard deviations observed in Table.
-\ref{tab:desc-stats}.
+\ref{fig:detect-compare} and all parameters are statistically significant despite the large standard deviations observed in Table \ref{tab:desc-stats}.
 Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
-Allowing for the interaction effect, the difference in detection rate decreases for population-related displays for a choropleth map lineup, but increases for a hexagon tile map display.
-The log odds of detection are shown in Table. \ref{tab:detect-glmer1} can be back-transformed after taking the sum of all terms for the trend and type of display that are of interest.
+Allowing for the interaction effect, the difference in detection rate decreases for population-related displays for a choropleth map lineup but increases for a hexagon tile map display.
+The log odds of detection are shown in Table \ref{tab:detect-glmer1} can be back-transformed after taking the sum of all terms for the trend and type of display that are of interest.
 For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to 0.63 from 0.52 for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
@@
 
-The intention of this study was to contrast the use of the choropleth map and the hexagon tile map.
+%The intention of this study was to contrast the use of the choropleth map and the hexagon tile map.
 The visual inference lineup protocol was employed to contrast the effectiveness of the displays.
@@
 Using the visual inference protocol this result can be extended to show that it is a valid alternative display to communicate spatial distributions of population-related data.
+The objective of this study was to compare the effectiveness of the choropleth map and the hexagon tile map in displaying population-related data.
+To achieve this, we employed the visual inference lineup protocol, which helped us evaluate the efficacy of each display.
+Our results indicate that participants were more successful in identifying the data plot in the hexagon tile map display, making it a superior option for representing spatial distributions of population-related data.
+Thus, our study concludes that the hexagon tile map display is a valid and effective alternative to the choropleth map display for communicating this type of information.
 
-We expected that the choropleth map would be superior for communicating the spatial pattern of geographic distributions.
-The data suggest that the participants perform slightly better or equally as well for each replicate in each trend model across the two displays.
-Table II shows that the difference in the mean detection rate for the two trend models was 0.10.
-
+%We expected that the choropleth map would be superior for communicating a spatial dependence trend pattern across the geography.
+The data suggest that the participants perform slightly better, or equally as well, for each replicate in each trend model across the two displays.
+Table \ref{tab:desc-stats} shows that the difference in the mean detection rate for the two trend models was 0.10.
 The differences are seen in the \ref{fig:detect-compare} plot and Table.
@@
 
-While the significance of the difference in detection was the key focus of this experiment, the secondary focus was the time taken by participants.
-it was expected that the participants may take longer to consider the hexagon tile map distribution but would be able to detect the data plot in the lineup.
+Our initial expectation was that the hexagon tile map would be superior to the choropleth map for the two inner city hotspots pattern (All Cities, Three Cities), but that the choropleth would outperform the hexagon tile map for conveying a spatial dependence trend pattern across geography (NW-SE).
+We surprisingly found that the hexagon tile map was more effective in all three trend models.
+The detection rate was significantly higher for the hexagon tile map, although the margin was small for the NW-SE trend model.
+This was reflected in Fig.
+\ref{fig:detect-compare}, the descriptive statistics in Table \ref{fig:detect-compare}, and the linear model summary in Table \ref{tab:detect-glmer1}.
+
+While the significance of the difference in detection was the primary focus of this experiment, a secondary focus was the time taken by participants.
+It was expected that the participants may take longer to consider the hexagon tile map distribution but would be able to detect the data plot in the lineup.
 The bimodal distributions seen in Fig.
@@
 Fig.
-\ref{tab:reason} shows high levels of certainty of 4 and 5 were chosen by participants when looking at the population distributions in a choropleth map display showing that they were overconfident when attempting to find the real data plot in the choropleth map displays.
+\ref{fig:certainty} shows high levels of certainty of 4 and 5 were chosen by participants when looking at the population distributions in a choropleth map display showing that they were overconfident when attempting to find the real data plot in the choropleth map displays.
 Participants performed better on the NW-SE distribution shown in the choropleth display and were reasonably confident about their decisions.
@@
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
+%\hypertarget{conclusion}{%
+%\section{Conclusion}\label{conclusion}}
 
-The choropleth map display and the tessellated hexagon tile map have been contrasted using the lineup protocol.
+%The choropleth map display and the tessellated hexagon tile map have been contrasted using the lineup protocol.
 The hexagon tile map was significantly more effective for spotting a real population-related data trend model hidden in a lineup.
 
-The hexagon tile map display should be considered as an alternative visualization method when communicating distributions that relate to the population across a set of geographic units.
+%The hexagon tile map display should be considered as an alternative visualization method when communicating distributions that relate to the population across a set of geographic units.
 As an additional display to the familiar choropleth map, cancer atlas products may benefit from the opportunity to allow exploration via an alternative display.
@@
 
-The increasing population densities of capital cities despite small land areas exacerbates the difference between the smallest and largest communities.
-The population density structure of Australia can be considered similar to that of Canada, New Zealand, and many other countries.
+%The increasing population densities of capital cities despite small land areas exacerbates the difference between the smallest and largest communities.The population density structure of Australia can be considered similar to that of Canada, New Zealand, and many other countries.
 Therefore, this display is not only relevant to Australia but all nations or population distributions that experience densely populated cities separated by vast rural expanses.
@@
 \end{document}
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-sugarbag}{}}%
-\CSLLeftMargin{1. }%
-\CSLRightInline{Kobakian S, Cook D (2019) Sugarbag: Create tessellated hexagon maps. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-atlas}{}}%
-\CSLLeftMargin{2. }%
-\CSLRightInline{Cancer Council Queensland {Australian Cancer Atlas (https://atlas.cancer.org.au)}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-GIIV}{}}%
-\CSLLeftMargin{3. }%
-\CSLRightInline{Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979}
-
-\leavevmode\vadjust pre{\hypertarget{ref-EI}{}}%
-\CSLLeftMargin{4. }%
-\CSLRightInline{Tufte ER (1990) {Envisioning Information}. Graphics Press}
-
-\leavevmode\vadjust pre{\hypertarget{ref-BCM}{}}%
-\CSLLeftMargin{5. }%
-\CSLRightInline{Skowronnek A (2016) {Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata}.
-In: {Infovis Reading Group WS 2015/16}.
-\href{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}{https://alsino.io/static/papers/BeyondChoropleths\_AlsinoSkowronnek.pdf.
-}}
-
-\leavevmode\vadjust pre{\hypertarget{ref-CBATCC}{}}%
-\CSLLeftMargin{6. }%
-\CSLRightInline{Kocmoud C, House D (1998) {A Constraint-based Approach to Constructing Continuous Cartograms}. In: Proc. Symp. Spatial data handling. pp 236--246}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ACTUC}{}}%
-\CSLLeftMargin{7. }%
-\CSLRightInline{Dorling D (2011) \href{https://doi.org/10.1002/9780470979587.ch33}{{Area Cartograms: Their Use and Creation}}. In: Concepts and techniques in modern geography (CATMOG). pp 252--260}
-
-\leavevmode\vadjust pre{\hypertarget{ref-NAC}{}}%
-\CSLLeftMargin{8. }%
-\CSLRightInline{Olson JM (1976) \href{https://doi.org/10.1111/j.0033-0124.1976.00371.x}{{Noncontiguous Area Cartograms}}. The Professional Geographer 28:371--380}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RSCW}{}}%
-\CSLLeftMargin{9. }%
-\CSLRightInline{Raisz E (1963) \href{https://doi.org/10.1080/00221343608987880}{{Rectangular Statistical Cartograms of the World}}. Journal of Geography 35:8--10}
-
-\leavevmode\vadjust pre{\hypertarget{ref-CDWCS}{}}%
-\CSLLeftMargin{10. }%
-\CSLRightInline{Monmonier M (2005) \href{https://doi.org/10.1191/0309132505ph540pr}{{Cartography: Distortions, World-views and Creative Solutions}}. Progress in Human Geography 29:217--224}
-
-\leavevmode\vadjust pre{\hypertarget{ref-review}{}}%
-\CSLLeftMargin{11. }%
-\CSLRightInline{(2019) Cancer applications of choropleth maps, and the potential of cartograms and alternative map displays. Manuscript submitted for publication. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-BCHLLSW09}{}}%
-\CSLLeftMargin{12. }%
-\CSLRightInline{Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) Statistical inference for exploratory data analysis and model diagnostics.
-Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383}
-
-\leavevmode\vadjust pre{\hypertarget{ref-GTPCCD}{}}%
-\CSLLeftMargin{13. }%
-\CSLRightInline{Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ggplot2}{}}%
-\CSLLeftMargin{14. }%
-\CSLRightInline{Wickham H (2009) \href{http://had.co.nz/ggplot2/book}{ggplot2: Elegant graphics for data analysis}. Springer New York}
-
-\leavevmode\vadjust pre{\hypertarget{ref-abs2016}{}}%
-\CSLLeftMargin{15. }%
-\CSLRightInline{(2018) \href{\%7Bhttps://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)\%7D}{{Australian Statistical Geography Standard (ASGS)}}.
-Australian Bureau of Statistics }
-
-\leavevmode\vadjust pre{\hypertarget{ref-POG}{}}%
-\CSLLeftMargin{16. }%
-\CSLRightInline{Matheron G (1963) \href{http://dx.doi.org/10.2113/gsecongeo.58.8.1246}{Principles of geostatistics}. Economic Geology 58:1246--1266}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gstat}{}}%
-\CSLLeftMargin{17. }%
-\CSLRightInline{Gräler B, Pebesma E, Heuvelink G (2016) \href{https://journal.r-project.org/archive/2016/RJ-2016-014/index.html}{Spatio-temporal interpolation using gstat}. The R Journal 8:204--218}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RCore}{}}%
-\CSLLeftMargin{18. }%
-\CSLRightInline{R Core Team (2019) \href{https://www.R-project.org/}{R: A language and environment for statistical computing}. R Foundation for Statistical Computing, Vienna, Austria}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lme4}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{Bates D, Mächler M, Bolker B, Walker S (2015) \href{https://doi.org/10.18637/jss.v067.i01}{Fitting linear mixed-effects models using {lme4}}. Journal of Statistical Software 67:1--48}
-
-\leavevmode\vadjust pre{\hypertarget{ref-taipan}{}}%
-\CSLLeftMargin{20. }%
-\CSLRightInline{Kobakian S, O'Hara-Wild M (2018) \href{https://CRAN.R-project.org/package=taipan}{Taipan: Tool for annotating images in preparation for analysis}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-sheets}{}}%
-\CSLLeftMargin{21. }%
-\CSLRightInline{Bryan J, Zhao J (2018) \href{https://CRAN.R-project.org/package=googlesheets}{Googlesheets: Manage google spreadsheets from r}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-figeight}{}}%
-\CSLLeftMargin{22. }%
-\CSLRightInline{(2019) \href{https://www.figure-eight.com/}{The essential high-quality data annotation platform}. Figure Eight }
-
-\leavevmode\vadjust pre{\hypertarget{ref-rmarkdown}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{Xie Y, Allaire JJ, Grolemund G (2018) \href{https://bookdown.org/yihui/rmarkdown}{R markdown: The definitive guide}. Chapman; Hall/CRC, Boca Raton, Florida}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rticles}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{Allaire J, Xie Y, R Foundation, et al (2019) \href{https://CRAN.R-project.org/package=rticles}{Rticles: Article formats for r markdown}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-knitr}{}}%
-\CSLLeftMargin{25. }%
-\CSLRightInline{Xie Y (2014) \href{http://www.crcpress.com/product/isbn/9781466561595}{Knitr: A comprehensive tool for reproducible research in {R}}. Implementing reproducible computational research }
-
-\leavevmode\vadjust pre{\hypertarget{ref-tidyverse}{}}%
-\CSLLeftMargin{26. }%
-\CSLRightInline{Wickham H, Averick M, Bryan J, et al (2019) \href{https://doi.org/10.21105/joss.01686}{Welcome to the {tidyverse}}. Journal of Open Source Software 4:1686}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nullabor}{}}%
-\CSLLeftMargin{27. }%
-\CSLRightInline{Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) \href{https://CRAN.R-project.org/package=nullabor}{Nullabor: Tools for graphical inference}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-ggthemes}{}}%
-\CSLLeftMargin{28. }%
-\CSLRightInline{Arnold JB (2019) \href{https://CRAN.R-project.org/package=ggthemes}{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-RColorBrewer}{}}%
-\CSLLeftMargin{29. }%
-\CSLRightInline{Neuwirth E (2014) \href{https://CRAN.R-project.org/package=RColorBrewer}{RColorBrewer: ColorBrewer palettes}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-cowplot}{}}%
-\CSLLeftMargin{30. }%
-\CSLRightInline{Wilke CO (2019) \href{https://CRAN.R-project.org/package=cowplot}{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-png}{}}%
-\CSLLeftMargin{31. }%
-\CSLRightInline{Urbanek S (2013) \href{https://CRAN.R-project.org/package=png}{Png: Read and write PNG images}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-grid}{}}%
-\CSLLeftMargin{32. }%
-\CSLRightInline{R Core Team (2019) \href{https://www.R-project.org/}{R: A language and environment for statistical computing}. R Foundation for Statistical Computing, Vienna, Austria}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kableExtra}{}}%
-\CSLLeftMargin{33. }%
-\CSLRightInline{Zhu H (2019) \href{https://CRAN.R-project.org/package=kableExtra}{kableExtra: Construct complex table with 'kable' and pipe syntax}. }
-
-\end{CSLReferences}

### 2023-03-21 paper/supplementary/lineups.Rmd
supplementary material processed

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+knitr::opts_chunk$set(echo = FALSE, 
+                      message = FALSE, 
+                      warning = FALSE, 
+                      fig.path = "alldisplays/")
 ```
@@
   # Downloaded data
-d <- read_xlsx("data/experiment-export.xlsx", sheet=2) %>%
+d <- read_xlsx("../data/experiment-export.xlsx", sheet=2) %>%
   filter(!is.na(contributor)) %>%
@@
 Fig.
-\ref{fig:pdetection-group} shows the distribution using a boxplot.
+1 shows the distribution using a boxplot.
 This shows the median value for detection rate was extremely similar.
 
-```{r pdetection-group}
+```{r pdetection-group, fig.cap="Comparison of performance of groups A and B."}
 plots %>% ggplot(aes(x = group, y = pdetect)) + 
@@
 
-The overall detection rate is considered for each trend model in Fig. \ref{fig:pdetect-trend}.
+The overall detection rate is considered for each trend model in Fig. 2.
 The detection rates for the NW-SE trend model was less varied than the detection rates for the Three Cities and All Cities trends.
-Fig.
-\ref{fig:pdetection-group} shows the distribution using a boxplot.
 This shows the distributions of the rates do not overlap for NW-SE and Three Cities trends, the Three cities range was larger, but the median was much higher for the NW-SE trend.
@@
 
-```{r pdetect-trend}
+```{r pdetect-trend, fig.cap="Comparison of performance across trend models."}
 plots %>% ggplot(aes(x = trend, y = pdetect, fill = trend)) + 
@@
 
-The boxplots in Fig. \ref{fig:pdetection-type} contrast the distribution of the detection rates for eah type of display.
+The boxplots in Fig. 3 contrast the distribution of the detection rates for each type of display.
 The detection rates across the lineups was less varied for the hexagon display. There was a large difference in the medians for the types of displays.
@@
 
-```{r pdetection-type}
+```{r pdetection-type, fig.cap="Comparison of performance across display types."}
 plots %>% ggplot(aes(x = type, y = pdetect, fill = type)) + 
@@
 The choices made by participants are displayed in Fig.
-\ref{fig:choices}.
+4.
 The height of each orange lollipop indiates the proportion of participants that selected the map display of real data, they represent the correct choices.
@@
 
-The proportion of choices are also presented separately for each trend model in Table. \ref{tab:choice-nwse}, Table. \ref{tab:choice-three}, and  Table. \ref{tab:choice-all}.
+The proportion of choices are also presented separately for each trend model in Table.
 The correct map display in lineups with a North West to South East trend was chosen correctly with much greater frequency. 
 In the lineups of All Cities displays, participants were misled by the choropleth display, but not the hexagon display for all except (2). 
-All of Three Cities displays, except (4), were detected in the hexagon display.
-All except one lineup had at least one participant select the correct map in the lineup as shown in Fig.
-\ref{fig:choices}.
+All of Three Cities displays, except (4), were detected in the hexagon display. All except one lineup had at least one participant select the correct map in the lineup as shown in Fig. 4.
 
@@
 The numbers differentiate the replicates of each trend model and type of map display.
-Participants were able to select 0 to indicate they did not want to choose a map.", fig.height = 8, fig.width =6, results = "asis"}
+Participants were able to select 0 to indicate they did not want to choose a map.", fig.height = 8, fig.width = 6,}
 d %>% 
@@
 
-## North West - South East
+<!-- ## North West - South East-->
 
@@
 
-## All Cities
+<!-- ## All Cities
 
-### Replicate 1
+### Replicate 1-->
 
@@
 
-### Replicate 2
+<!-- ### Replicate 2-->
 
@@
 
-### Replicate 3
+<!-- ### Replicate 3-->
 
@@
 
-### Replicate 4
+<!--### Replicate 4-->
 
@@
 
-## Three Cities
+<!--## Three Cities
 
-### Replicate 1
+### Replicate 1-->
 
@@
 
-### Replicate 2
+<!--### Replicate 2-->
 
@@
 
-### Replicate 3
+<!--### Replicate 3-->
 
@@
 
-## North West to South East Geographic Trend
+<!--## North West to South East Geographic Trend
 
-### Replicate 1
+### Replicate 1-->
 
@@
 ggdraw() +
-  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_2_geo.png")))
+  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_2_hex.png")))
 ```
 
-### Replicate 2
+<!--### Replicate 2-->
 
@@
 ggdraw() +
-  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_3_geo.png")))
+  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_3_hex.png")))
 ```
 
-### Replicate 3
+<!--### Replicate 3-->
 
@@
 ggdraw() +
-  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_5_geo.png")))
+  draw_plot(rasterGrob(readPNG("lineups/aus_nwse_5_hex.png")))
 ```
 
-### Replicate 4
+<!--### Replicate 4-->
 

### 2023-03-21 paper/supplementary/survey_procedures.Rmd
supplementary material processed

@@
 Choosing the task from the list directed all potential participants to the page of instructions.
-This page contained written instructions and is shown in Fig. \ref{fig:instruct}.
+This page contained written instructions and is shown below.
 
-```{r instruct, results = "asis", fig.cap = "The training lineups of choropleth maps.", fig.width = 4, fig.height = 4}
+```{r instruct, results = "asis", fig.cap = "Introductory information provided to participants."}
 ggdraw() +
@@
 
-The participants were trained using three displays. There were relatively simple lineups, they are displayed in Fig. \ref{fig:training1} and Fig. \ref{fig:training2}.
+The participants were trained using simple lineups of three displays as shown in Figs. 2, 3.
 
-```{r training1, results = "asis", fig.cap = "The training lineups of choropleth maps.", fig.width = 4, fig.height = 4}
+```{r training1, results = "asis", fig.cap = "The training lineups of choropleth maps."}
 ggdraw() +
@@
 The demographic and consent page of the `shinydashboard` web application are displayed in Fig.
-\ref{fig:survey-demogs}.
+4.
 Two example lineups are shown, one choropleth map lineup in Fig.
-\ref{fig:survey-choro} and one heaxgon tile map lineup in Fig.
-\ref{fig:survey-hex}.
+5 and one heaxgon tile map lineup in Fig.
+6.
 
-```{r survey-demogs, results = "asis", fig.cap = "The demographics questions tab of the shinydashboard survey application.", fig.width = 4, fig.height = 4}
+```{r survey-demogs, results = "asis", fig.cap = "The demographics questions tab of the shinydashboard survey application."}
 ggdraw() +

### 2023-03-21 paper/paper.R

@@ -1,75 +1,47 @@
-## ----setup, include=FALSE-------------------------------------------------------------------------------------------
+## ----setup, include=FALSE-----------------------------------
 knitr::opts_chunk$set(
   echo = FALSE,
   warning = FALSE,
   error = FALSE, 
-  message = FALSE)
+  message = FALSE,
+  cache = FALSE,
+  dpi = 300,
+  out.width = "100%")
 
 
-## ----libraries------------------------------------------------------------------------------------------------------
+## ----libraries----------------------------------------------
 # Load Libraries
 library(tidyverse)
+library(readxl)
+library(broom)
+library(broom.mixed)
 library(cowplot)
 library(png)
 library(grid)
-library(lubridate)
-library(broom)
-library(readxl)
 library(lme4)
 library(ggthemes)
 library(RColorBrewer)
-library(visreg)
-library(emmeans)
+library(knitr)
 library(kableExtra)
 
-
-## ----liver, fig.height = 9, fig.width = 6, fig.cap = "The smoothed average of liver cancer diagnoses for Australian males. The divering colour scheme shows dark blue areas with much lower than average diagnoses, yellow areas with diagnoses around the Australian average, orange with above average and red shows diagnoses much higher than average."----
-ggdraw(ylim = c(0,2), xlim = c(0,1.3), clip = "on") +
-  draw_plot(rasterGrob(readPNG("figures/aus_liver_m.png")), -0.15, 0.9, 1.6, 1.2) +
-  draw_plot(rasterGrob(readPNG("figures/aus_liver_m_hex.png")), -0.15, -0.1, 1.6, 1.2) +
-  draw_plot_label(c("a", "b"), 
-    c(0.05, 0.05), c(1.95, 1), size = 20, color = "white") + 
-  theme(plot.background = element_rect(fill = "black"))
+options(knitr.kable.digits = "2")
 
 
-## ----exp_design, fig.cap = "Experimental design."-------------------------------------------------------------------
-count(d, trend, type) %>% mutate(Replicates = 2)
-
-d %>% 
-  mutate(Trend = trend) %>% 
-  group_by(Trend, type, group) %>% 
-  summarise(Reps = paste0(sort(unique(replicate)), collapse = ", ")) %>% 
-  mutate(prop = round(n/sum(n), 3), r_prop = paste0(reason, ":", prop)) %>% 
[…]

### 2024-09-30 anzjs/protoType.tex
anzjs format

% protoType.tex
%
%==+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===
% Rolf Turner 19 May 2016. 
%==+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===
%
% Note the use of "doublespace" in the optional arguments
% to the "\documentclass" command.  This, obviously, produces
% a double spaced document, as the Journal requires.
\documentclass[times, doublespace]{anzsauth}
\usepackage{moreverb}
\usepackage{url}
\usepackage{grffile}
\usepackage{lineno}
\input{undertilde}
% You will probably find it convenient to make use of
% the following new commands.  Note in particular "\E"
% for producing the expectation operator in accordance
% with Journal policy.
\newcommand{\utilde}{\undertilde}
\newcommand{\E}{\mbox{$\textrm{\textup{E}}$}}
\newcommand{\var}{\mbox{$\textrm{\textup{var}}$}}
\newcommand{\cov}{\mbox{$\textrm{\textup{cov}}$}}
\newcommand{\cor}{\mbox{$\textrm{\textup{cor}}$}}
\newcommand{\by}{\mbox{$\boldsymbol{y}$}}
\newcommand{\bX}{\mbox{$\boldsymbol{X}$}}
\newcommand{\bY}{\mbox{$\boldsymbol{Y}$}}
\newcommand{\bM}{\mbox{$\boldsymbol{M}$}}

% You probably *won't* need these new commands; they are designed
% for use in *this* particular document.
\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\newcommand\MiKTeX{{\rmfamily M\kern-.05em \textsc{i\kern-.025em K}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\newcommand\PracTeX{{\rmfamily P\kern-.05em \textsc{r\kern-.025em a\kern-.025em
c}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

% The year in the following may need to be updated!
\def\volumeyear{2017}
\linenumbers

\begin{document}
% Specifying a running head, title, author(s), and affiliation
% in the manner required by the Journal.
% Note that the first argument of "\runningheads" specifies the
% "brief" running title (which will appear on the even numbered
% pages) and the second argument specifies the format in which
% the authors' names will appear on the odd numbered pages.
% Do *not* use "\corrauth" if there is only one author.
% *Do* use "\addressnum{1}" even if there is only one author!
\runningheads{How I rose from the dead}{A~J~SPECKTOWSKY, P~K~DICK, AND R~TURNER}
\title{How I rose from the dead in my spare time and so can you}
\author{A. J. Specktowsky\addressnum{1}, Philip K. Dick\addressnum{2} and
Rolf Turner\addressnum{3}\corrauth}
\affiliation{School of Hard Knocks, Sirius Cybernetics Corporation and
the University of Orcland
}
% Specifying address(es) in the manner required by the Journal.
\address{
\addressnum{1} \hspace*{-2ex} Department of Redundancy Department,
School of Hard Knocks, Great Falls, MT 54321, USA\break
\addressnum{2} Complaints Division, 30102 East Rhode Island
School of Design Terrace, Small Planet, Near Betelgeuse\break
\addressnum{3} Department of Statistics, University of Auckland,
Private Bag 92019, Auckland 1142, New Zealand\\
\hspace*{1ex} Email: \texttt{r.turner@auckland.ac.nz}
}
% Note that the Journal requires that a paper must begin with a
% "Summary" not an "Abstract".  This is automatically taken care
% of by the anzsauth document style.  So even though the following
% says "\begin{abstract}" the heading "Summary" will appear in
% the processed version.
\begin{abstract}
This document serves to illustrate some of the main features of
the \LaTeX\ document class ``\texttt{anzsauth}'' which authors are
strongly encouraged to use when preparing papers for submission
to the \textit{Australian and New Zealand Journal of Statistics}.
The importance of clarity of exposition as well as a number of
issues that frequently arise in respect of the Journal's standards
and conventions are emphasised.  The Journal has precise requirements
for the format of bibliographic references and citations.  It is much
easier for authors to conform to these requirements if they use the
resources provided by \BibTeX\ and the \texttt{anzsj} bibliography
style.  Authors are very strongly encouraged to avail themselves
of these resources.  The use of \BibTeX\ syntax is illustrated.
This document emphasises a few of the notational conventions that
form an important part of the Journal's stylistic requirements.
A great deal more material about these requirements may be found
in the document ``\textit{ANZJS Style Guide for Authors}'' in the
file \texttt{styleGuide.pdf}.  That file is included in the zip
archive of material from which you obtained the document that you
are currently reading, i.e. \texttt{protoType.pdf}.
\end{abstract}

% Note that "keywords" should not include words and phrases
% that form part of the title of the paper.
% Also keywords (with the exception of proper names and
% certain abbreviations that conventionally appear all in
% capital letters) should *not* be capitalised.
\keywords{anzsauth; bibliographic references; bibtex; citations;
          document class; notational conventions; style guide}

% This shows how acknowledgements should appear in the Journal.
% Note that if you are acknowledging financial support, grant
% numbers should *not* usually be specified.
\ack{The author (singular!) --- and he is indeed singular ---
gratefully acknowledges input, advice, feedback and encouragement
from Alan Welsh, James Curran, Michael Martin, Martin Hazelton,
Petra Graham, Chris Triggs, Neville Bartlett, David Scott and
Ken Russell.  Any remaining errors or omissions are all their
fault.\\[1ex] Opinions and attitudes expressed in this document,
which are not explicitly designated as Journal policy, are those of
the author and are \emph{not} necessarily endorsed by the Journal,
its editorial board, its publisher Wiley or by the Australian
Statistical Publishing Association Inc.}

\maketitle
\section{Introduction}
% Example of section labelling.
\label{sec:intro}
The tone of this prototype and the examples used are flippant
(and meant to be humorous; I guess it all depends on your sense
of humour).  However the intent is quite serious:  to show clearly
how to use the \texttt{anzsauth} document class so as to be able to
produce an article conforming to the Journal's requirements with
a minimum of effort.  Spend a little while studying the examples.
\emph{Look carefully} at the source file \texttt{protoType.tex},
for the document \texttt{protoType.pdf} that you are currently
reading.  In particular, read the \emph{comments}.  The files
\texttt{protoType.tex} and \texttt{protoType.pdf} are included
in the zip archive \texttt{anzsauth.zip}.  See below for the URL
from which this zip archive may be obtained.  You will find that
if you make use of the resources provided, you will save yourself
an immense amount of time and an immense number of key strokes.

A primary requirement that the Journal imposes is that papers must
be written lucidly and in clear and grammatically correct English.
Consequently Section~\ref{sec:clarExpos} is devoted to issues that
arise in respect of good exposition.  Other requirements include
proper formatting of the title page.  This is done \emph{far}
more easily if you make use of the resources provided by the
\texttt{anzsauth} document class than if you attempt to do the
formatting ``by hand''.  (See Section~\ref{sec:titPage}).

The Journal insists that citations should be formed correctly and in
accordance with its conventions.  Likewise the list of references
must have the correct structure.  Again these requirements are
\emph{greatly} facilitated if you make use of the resources provided
(by means of \BibTeX\ and the \texttt{anzsj} bibliography style).
These matters are discussed in Section~\ref{sec:bibRef}.

Although this is \emph{not} handled in an automatic manner,
it is important to adhere to the Journal's notation conventions.
Most of the discussion of notational conventions has been placed in
``{\textit{ANZJS} Style Guide for Authors}'' to be found in the
file \texttt{styleGuide.pdf} which is included in the zip archive
\texttt{anzsauth.zip} referred to above.  That zip archive may be
obtained from\\
%==+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===
{\small
\url{http://onlinelibrary.wiley.com/journal/10.1111/%28ISSN%291467-842X}
}
%==+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===+===
\noindent
by clicking on ``Author Guidelines'', scrolling down to ``Latex
Template'' and then clicking on the appropriate link.  It is also
possible to obtain this zip archive by visiting your ScholarOne
``Author Centre'' (``Start New Submission'') and noting the bullet
point:
\begin{quote}
$\bullet$ Before submitting or revising your manuscript, please
download the zip archive anzsauth.zip by clicking \underline{here}.
\end{quote}
Clicking on ``\underline{here}'' duly produces the desired zip
archive.  (You may --- in fact probably!!! --- have already done
this to obtain the document that you are currently reading.)

Some of the more salient points about notation are dealt with in
Section~\ref{sec:noteConv} in the current document (thus overlapping
a bit with the style guide).  Displayed equations and their numbering
are dealt with in Section~\ref{sec:eqnNumb}.  In this section
some cogent advice is given about handling arrays of equations.
Issues that arise in respect of the inclusion of figures and
tables in a paper are discussed in Section~\ref{sec:figAndTab}.
Section~\ref{sec:prepDocs} provides a little bit of advice about
preparing and processing the ``source files'' that underlie the
use of \LaTeX.  Various exhortations are reiterated, and some
advice about how to make use of \texttt{protoType.tex} is given
in Section~\ref{sec:concComm}.  In this last Section you are
additionally exhorted to create a \emph{tidy} \LaTeX\ source file.

In addition to saving you time and effort on the initial creation
of the document, using the tools provided by the \texttt{anzsauth}
document class in particular and by \LaTeX\ in general facilitates
revising the document.  Appropriate adjustments to numbering,
cross-referencing, and the like are handled automatically.
There are many resources available to help beginning (and
not-so-beginning) users of \LaTeX.  For instance you will find
useful information and guidance in the books by \cite{KopkaDaly2003,
Lamport1994} and \cite{MittelbachGoossens2004}.  (Of course \cite{Lamport1994}
is the definitive source of information since Lamport is the
author of \LaTeX.)  The web is also replete with resources;
just do a Google\texttrademark\ search on ``\texttt{latex}''.
(Amazingly one gets the relevant web sites on the first few hits;
only later on do sites aimed at rubber-fetishists start to show up.)

A facility provided by \LaTeX\ that tends to be underused in submissions
to the Journal is automated cross-referencing as provided by the
\verb!\label{...}! and \verb!\ref{...}! commands.  It is highly recommended
that you learn to make use of these.  They make it much easier to keep
cross-references correct when you revise a paper.  It seems to me to be
a good idea to give a label to each section and subsection, as you are
composing it, even if you are not sure you will be referring to it
in other sections.  (There is no \emph{harm} in inserting a label.)

Likewise it is a good idea to give each figure and table (see
Section~\ref{sec:figAndTab}) a label so as to be able to refer to
it via the \verb!\ref{...}!  command.  Thus one can easily invite
the reader to ``see Section~\ref{sec:figAndTab}'', as I just did!
Only displayed equations that are \emph{actually referred to}
should be numbered (see Section~\ref{sec:eqnNumb}).  If the equation
\emph{is} referred to, then of course you should give it a label so
that you \emph{can} refer to it easily.

My personal practice is to label sections and subsections with labels
of the form \texttt{sec:string}, e.g. ``\verb!\label{sec:intro}!''.
Similarly I form such labels for figures and tables
as \texttt{fig:string} or \texttt{tab:string} (e.g.
\verb!\label{fig:ltdb}! or \verb!\label{tab:ltdb}!) and labels
for equations as \texttt{eq:string} (e.g. \verb!\label{eq:GNZ}!).
I find this practice convenient, but you are of course under no
obligation to follow it.

A practice that I have often seen and that I think should \emph{not}
be indulged in, is to use labels such as ``\texttt{Figure1}''.  There
is \emph{not necessarily} any harm in this, but to a large extent
such a practice defeats the purpose of using \verb!\label{...}! and
\verb!\ref{...}!.  If you decide to change the order in which
figures appear in your paper, then the label ``\texttt{Figure1}''
will probably no longer be appropriate.  At best you will confuse
yourself, and you run a serious risk of getting labels wrong.
Use labels that refer to \emph{content} (in a terse manner, of
course) and let \LaTeX\ handle the assignment of numbers!  If you
insist on using labels like unto ``\texttt{Figure1}'',
then take great care to make sure that the result is correct.

Authors are requested to \emph{double space} their documents
(particularly for the convenience of referees and technical
editors).  This is easily accomplished by invoking the
\texttt{anzsauth} document class via (e.g.): \label{pg:dsln}
\verb!\documentclass[times, doublespace]{anzsauth}!.  The document
that you are currently reading is double spaced in this way.
Authors are likewise requested to \emph{number} the lines of their
document so as to make it easier for referees and technical editors
to specify where corrections are required.  The document you are
currently reading exemplifies such line numbering.  The desired
effect is achieved by placing \verb!\usepackage{lineno}! and
\verb!\linenumbers!  in the preamble.  See \texttt{protoType.tex}.

% The following illustrates the use of \citeyear{} and \citep{}.
Readers might be interested to know about some of the ``literary''
allusions found in this document.  The title of this paper
is actually that of a (fictitious, of course) book that is
referred to in the (real) book \textit{A Maze of Death} by Philip
K. Dick (\citeyear{Dick1971}).  The aforesaid title exemplifies a
particularly egregious error in English usage that can be described
as ``faulty parallelism''.  It is an example of the sort of thing
that one \emph{shouldn't do}!  Philip K. Dick is perhaps best
known as the author of \textit{Do Androids Dream of Electric Sheep?}
\citep{Dick1968} upon which the movie \textit{Blade Runner} (starring
Harrison Ford) was based.  The fictitious book referred to above was
putatively written by one A. J. Specktowsky who is given the honour
of being first author of the current paper.  Philip K. Dick himself
has been made the second author.  The third author, my very good
self, is the real author.  (The repeated use of the word ``real''
in the foregoing paragraph invites the question ``What is reality?''
But let's not go there!)

The ``Department of Redundancy Department'' is an allusion to
the comedy recording \textit{Don't Crush that Dwarf, Hand Me the
Pliers} by the group \textit{Firesign Theatre} \citep{Firesign1970}.
``Sirius Cybernetics Corporation'' is an allusion to \textit{The
Hitch Hiker's Guide to the Galaxy} \citep{Adams1979}.  The address
of the Complaints Division of the Sirius Cybernetics Corporation
refers back, for no particularly good reason, to \cite{Firesign1970}.

\section{Clarity of exposition}
\label{sec:clarExpos}

Obviously the fundamental consideration in respect of assessing a
paper's quality is its actual content: its correctness and its value
in terms of the advancement of statistical science.  Second only to
content is the quality of the exposition of the ideas developed in
the paper.  There is little merit in having high quality content
if the paper is written in such a manner that its audience finds
it burdensome or even impossible to read.

The Journal has very exacting standards for the quality of English
expression in the papers it publishes.  Authors are expected to
think carefully about the way in which they present material.
Ideas should flow in a logical manner.  The connections between
successive segments of the material should be obvious and easy to
follow.  Succinct and well-organised examples, kept as uncomplicated
as possible, should be provided to clarify intricate concepts.
It is \emph{not} acceptable to throw down a jumble of ideas in random
order and expect the reader to sort them out.  Sufficient explanation
should be provided so that any reasonably well-educated statistician
who is willing to expend a reasonable amount of effort will be able
to understand the paper.  It is \emph{not} acceptable for the paper
to be comprehensible only to experts in the relevant field of study
(or, worse, only to the authors!).

Diligent attention must be paid to grammar.  For instance
\emph{articles}, definite (``the'') and indefinite (``a'' or
``an'') must be used appropriately.   It is not acceptable to omit
articles where they are required, to insert an article where none
is required, or to use a definite article where an indefinite one is
required or vice versa.  In a similar vein, agreement in ``number''
between subject and verb must be carefully maintained.  Authors must
guard vigilantly against the use of dangling or misplaced modifiers
(an unfortunately common type of error).

A typical example of a dangling modifier is ``The SE of the
correlation increased in size when changing from 4 to 5 quadrature
points.  This sounds as if the SE changed from 4 to 5 quadrature
points!  A grammatically correct phrasing might be something like
``The SE of the correlation increased in size when the number of
quadrature points was changed from 4 to 5.''  A typical example of a
misplaced modifier is ``A plot of the residuals from Specktowsky's
model shown in Figure~42 indicates the lack of an adequate fit.''
(The \emph{model} is not shown in Figure~42!)  Better would be
``A plot, shown in Figure~42, of the residuals from Specktowsky's
model indicates the lack of an adequate fit.''

Some might argue that grammatical issues like these ``don't
really matter'' and that ``the meaning is clear''.  The meaning
is \emph{sometimes} clear, and sometimes becomes  possible to
discern only after readers have expended considerable effort that
has been unnecessarily imposed upon them.  Grammatical errors are
distracting and confusing.  Reading a paper containing grammatical
errors is an unpleasant experience, and readers will be discouraged
from giving a paper containing such errors the attention that it may
otherwise well deserve.  Such errors are an unnecessary encumbrance
to a paper and can be avoided with a modicum of care and diligence.
The Journal insists that such diligence be exercised.

In addition to being written with logical clarity and being free
of grammatical errors, manuscripts should be concise and expressed
in a direct style. Sentences should be kept short; long sentences
are hard to follow and should always be judiciously broken into
a number of shorter sentences.  Distracting use of unnecessary
technical terms should be avoided.  Do not abbreviate terms
unless they are used repeatedly and the abbreviation is helpful
to the reader. Initially use the word in full, and follow it by
the abbreviation in parentheses.  Thereafter use the abbreviation
only. Do not abbreviate author names; for example ``Hall and Heyde
(HH)'' must \emph{not} be used.

Care must be taken with the tense of verbs.  Use the past tense
when describing something that was done in the past! In particular
simulations should be described in the past tense.  For example say
``We generated 1000 data sets from our parametric model \ldots''
and not ``We generate 1000 data sets \ldots''.  Use the past tense
when referring to results from existing literature.  For example,
use ``Smith \& Jones (2007) showed that two plus two equals four'',
not ``Smith \& Jones (2007) show that two plus two equals four''.
Use the present tense in referring to the content of the paper that
you are writing: ``In this paper we show that the convergence rate
is $o_P(n^{-2/3})$.''  (Not ``we showed that''.)

It is the responsibility of the authors to ensure that the use
of English language in the manuscript is of a quality suitable
for the Journal. If you are not absolutely confident that this
requirement is fully satisfied, then have your manuscript checked
and \emph{thoroughly} edited by a suitably qualified person.
Such a person (whose first language should preferably be English)
must have superior English language skills and also be qualified
in statistics so as to be able to assess and correct the expression
of statistical ideas.

Failure to ensure an adequate standard of English expression may
result in the paper's being rejected at the Technical Editing stage
\emph{even though} it has previously been assessed by referees
and and an associate editor as being acceptable for the Journal.
Referees are experts in the particular field addressed by a given
paper and they assess that paper for correctness and value of
statistical and scientific content. They rarely read the paper
carefully in respect of style and exposition, assuming that this is
not their responsibility.  This is why the Journal explicitly leaves
final acceptance to the Technical Editor.  The Journal also reserves
the right to modify an accepted paper so as to reduce inadequacies of
exposition.  Any such modifications will be discussed with authors,
where feasible.

The Journal's publisher, Wiley, provides a service that can assist
authors with English-language editing.  To find out about this
service you may visit:

{\small
\url{http://authorservices.wiley.com/bauthor/english_language.asp}
}
% Use "\noindent" where appropriate.
\noindent
Authors must be aware that there is a \emph{cost} associated with
this service, and this cost must be borne by the author(s) of the
paper in question.

\section{Formatting the title page}
\label{sec:titPage}

Do not try to create the list of authors, their affiliations
and their addresses by hand.  This is difficult, kludgy and
usually leads to results that are not in keeping with the
Journal's requirements (which eventually makes more work for
the typesetters).  Take a moment to learn to use the macros
that the \texttt{anzsauth} document class provides.  Look into
the \emph{source} file (\texttt{protoType.tex}) that was used to
produce this document.  Given that you are looking at this document
(file \texttt{protoType.pdf}) you presumably downloaded and unzipped
the zip archive \texttt{anzsauth.zip} from the Journal's web page.
The source file is to be found among the files obtained from
that zip archive, alongside the \texttt{*.pdf} file that you are
currently reading.  By looking at the structure of this source file,
you should be able to quickly discern the way in which these macros
should be used.

These macros include:
\begin{itemize}
\item \verb!\runningheads{...}!
\item \verb!\author{...}!
\item \verb!\affiliation{...}!
\item \verb!\address{...}!
\item \verb!\addressnum{...}!
\item \verb!\keywords{...}!
\item \verb!\ack{...}!
\end{itemize}
Note also that using the ``abstract'' environment, delimited by
``\verb!\begin{abstract}!'' and ``\verb!\end{abstract}!'',
produces the correct heading ``\textbf{Summary}'' as required by
the Journal.

By learning to use these resources you will in the long
run save a \emph{great} deal of time and dramatically reduce the
effort that you expend.

\section{Bibliographic References}
\label{sec:bibRef}

\subsection{The Journal's citation rules}
\label{sec:citeRules}

The Journal (for the sake of consistency; see
Section~\ref{sec:noteConv}) imposes a number of strict rules
or conventions on the way that citations are formed.  Authors
\emph{must} follow these conventions.  Just as you are advised not
to format the title page ``by hand'', you are strongly encouraged not
to produce your citations and your list of references in an ad hoc
one-by-one manner.  Instead use the (very well designed) tools that
are available for the purpose.  That is, make use of \BibTeX\ and
the \texttt{anzsj} bibliography style (see Section~\ref{sec:useBib}).
If you do so, then (most of) the Journal's required conventions will
be followed automatically, thereby saving you a great deal of work
and a great many headaches.

If you insist on ``doing things your own way'',
then you must \emph{read carefully} the relevant section of
``\textit{ANZJS} Style Guide for Authors'' (to be found in the
file \texttt{styleGuide.pdf} which is included in the zip archive
in which you found the document that you are currently reading)
and carefully follow the specifications given.

A rule that \BibTeX\ and the \texttt{anzsj} bibliography style will
\emph{not} automatically handle for you is that the names of journals
appearing in the reference list must be \emph{not be} abbreviated.
This is a
\begin{center}
{\large \textbf{CHANGE or REVERSAL}}
\end{center}
of Journal policy from what it has been in the past. (One might
be inclined to say that it is an ``about face'' or retreat, or
climb-down.)  If you have struggled to dutifully make your references
accord with the previous policy that demanded that journal names
be abbreviated in accordance with ``standard abbreviations'' and
have arduously combed the web to find out just what these standard
abbreviations are \ldots\ well, I can only apologise.  You are however
owed some explanation:

The Editorial Board were unanimously of the opinion that
the policy of demanding abbreviated Journal names was probably
adopted in the dim distant past to save time for typesetters,
and has little function in today's circumstance.  The only actual
benefit of this policy is that there is a tiny space saving,
and this tiny benefit comes at the cost of unnecessarily adding
tedious work to authors' responsibilities.  It also has the
disadvantage of making our papers less accessible to readers,
especially non-statisticians/mathematicians. Some readers may know
that \textit{Stat. Neerl.} is \textit{Statistica Neerlandica},
but many will not.  The change in policy is one small step toward
making statistics research more user-friendly.

Consequently \emph{please} do not abbreviate journal names.  At all.
Ever.  Please \emph{consistently} give journals their full title.
Again I apologise (on behalf of the Editorial Board) if this causes
you inconvenience and results in your having wasted (substantial)
time and effort.

Another rule that cannot be automatically handled is that reference
may not be made to a paper ``submitted for publication'' or to a
``personal communication''. The essential criterion for inclusion
in the reference list is that any such reference must be obtainable
by a reader: thus a Technical Report is OK and a paper accepted for
publication is OK.  You may, if you wish, put into the text a kind
of acknowledgement of the form ``It was pointed out to me by Fred
Nurk (\textit{pers. comm.}) that Bayesian statistics is a load
of dingos' kidneys.''  However such references must \emph{not}
be listed in your bibliography.

Likewise references to unpublished data may be cited in the text
(e.g. ``I. Poobah, unpublished data, 2000)'' but must not appear in
the list of references.  Otherwise all citations mentioned in the
text, tables or figures must be listed in the reference list. A
work must \emph{not} appear in the reference list \emph{unless}
it is cited in the text.

\subsection{Using \BibTeX}
\label{sec:useBib}

Authors are \textbf{\textit{STRONGLY}} encouraged to make use of
the resources provided by \BibTeX\ in preparing their lists of references
and in citing these references in their documents.  This is easy
to do and helps to make sure that the reference list and citation
conventions conform to the Journal's requirements.  The Journal
has its own ``bibliographic style'' (``\texttt{anzsj}'') which is
based upon the \texttt{natbib} package.

To use \BibTeX\ you need to do the following:
\begin{enumerate}
\item Prepare a ``bibliographic information'' (\texttt{*.bib})
file containing appropriately structured information about all of
the references that you will cite in your document.  Note that this
file can contain information about references that you \emph{do not
cite} in your document.  Only those references cited will appear
in the list of references.  This allows you to prepare a single
bibliographic information file that can be used for multiple papers
with overlapping but not identical reference lists.  Of course
when submitting a paper you may wish to upload only a cut-down
\texttt{*.bib} file that contains only the relevant references
(rather than a very large bibliographic information file with a
plethora of irrelevant entries).

The way that the information in your bibliographic information
file should be structured is illustrated by the example file
\texttt{protoRefs.bib} that accompanies the document that you are
currently reading.  Imitating the entries in this example file should
allow you to create just about any references you need to use.
More information may be found in \cite{MittelbachGoossens2004}.
There are also many resources to be found on the web by doing a
Google\texttrademark\ search on ``\texttt{bibtex}''.

\item At the end of your \LaTeX\ source for your document place the line
\verb!\bibliographystyle{anzsj}!.
\item Following this line place the line \verb!\bibliography{xxx}!
where ``\texttt{xxx}'' represents the \emph{stem} (without the \texttt{.bib}
extension) of the name of your bibliographic information file.
E.g. in preparing the current document I used the line
\verb!\bibliography{protoRefs}!.
\end{enumerate}

\subsection{Citing references}
\label{sec:citRef}
Cite references by using \verb!\cite{...}! and variants
thereof.  Some discussion of the possible variants is to be
found in Section~\ref{sec:citeVar}.  The \verb!...! ellipsis
in \verb!\cite{...}! represents the identifier for the item
being cited.  If you (sensibly) use \BibTeX, the identifier
is provided in the first line of the bibliographic information
about the item being cited.  For example \textit{The} \LaTeX\
\textit{Companion} referred to above was cited in this document
via \verb!\cite{MittelbachGoossens2004}!.  The relevant item in
\texttt{protoRefs.bib} begins
\begin{verbatim}
    @book{MittelbachGoossens2004,
\end{verbatim}
If you do not use \BibTeX, then the identifier
is given as the ``\verb!cite_key!'' for the appropriate item
in the list of references following \verb!\begin{thebibliography}{...}!
line in your \LaTeX\ document.

The way that the identifier is formed is fairly arbitrary; construct
identifiers in your bibliographic information file in whatever way
suits your fancy.  My personal paradigm is to construct identifiers
from the author's name (or authors' names) followed by the year as
in the example given above.  If there are more than two authors I
just use the first author's name followed by "EtAl" and the year.
E.g. for an article by Fred Nurk, Melvin Mingdinkler and Hoo Hee,
published in 1984, I use the identifier \texttt{NurkEtAl1984}.
I emphasise that this is just my personal convention that I have
found useful; you are under no obligation to follow it.

\subsection{Variants of the basic citation command}
\label{sec:citeVar}

In addition to the ``usual'' citation command ``\verb!\cite!''
there are a number of alternative citation commands that can be used
to create special punctuation structures in particular circumstances.
For example you can use \verb!\citeauthor{...}! to obtain just the
author's name (without the year) as in:
% Example of the use of \citeauthor.
\begin{quote}
The major results that have so far appeared in this area are due
to \cite{Mingdinkler1999}.  In this paper we further explore and
elaborate upon the ideas introduced by \citeauthor{Mingdinkler1999}
\ldots~.
\end{quote}
(The final ``Mingdinkler'' was produced using \verb!\citeauthor{...}!.)
Another example of the use of \verb!\citeauthor{...}! is
``This problem was addressed in the book by
\citeauthor{Thecowsoutside1984}.''

% Examples of the use of \citeyear.
Another variant of \verb!\cite{...}! is \verb!\citeyear{...}!
which is used to produce only the year of the reference being cited.
E.g. ``These ideas were also discussed in a number of papers by
Coyote which appeared in \citeyear{Coyote2001}, \citeyear{Coyote2007}
and \citeyear{Coyote2010}.''  A variant of this variant is
\verb!\citeyearpar{...}! which causes the cited year to be enclosed
in parentheses, e.g. ``S. Pussycat \citeyearpar{Pussycat1989}, in
a discussion of a read paper of the Royal Ornithological Society,
pointed out that there remain in the public mind a large number of
misconceptions about the behaviour patterns of canaries.''
Of course the same effect could be achieved by \emph{not}
keying in the text ``S. Pussycat'' and simply using
\verb!\cite{Pussycat1989}! so it's a bit hard to see when you
would actually need to use \verb!\citeyearpar!.

% Examples of the use of \citep.
Yet another variant of \verb!\cite{...}! is \verb!\citep{...}! which
encloses the whole citation, rather than just the year, in
parentheses.  E.g. ``Some authors prefer the hack \citep{Cook1966},
others the hew \citep{Moore1967}, and still others opt for a
combination \citep{CookMoore1968}.''

A couple of somewhat subtle variants are \verb!\citealt{...}! and
\verb!\citet{...}!.  In the second of these the ``t'' stands for
``text'' and produces a citation that is suitable for appearing
in a line of text.  Well, I hear you cry, doesn't just plain
\verb!\cite{...}! do that?  Yes it does, \emph{mostly}.  In
``simple'' usage \verb!\citet{...}! and \verb!\cite{...}! produce
exactly the same result.  However, if one supplies the optional
first argument to these commands (see Section~\ref{sec:locPrecise})
the results produced are different in an important way.  We defer
giving an example to Section~\ref{sec:locPrecise}.

The \verb!\citealt{...}! variant basically has the effect of removing
the parentheses from around the year (or from around the year and
``optional first argument'').  Compare \verb!\cite{Coyote2010}! which
produces ``\cite{Coyote2010}'' with \verb!\citealt{Coyote2010}! which
produces ``\citealt{Coyote2010}''.  An example of the use of
\verb!\citealt!  which involves its ``optional first argument''
is given in Section~\ref{sec:locPrecise}.

\subsection{Locating references precisely}
\label{sec:locPrecise}

Finally a desideratum, or a plea, rather than a rule as such: Where
you have referred to a book, or even a long paper, \emph{please}
give some indication (for example a page number or a section number)
to help your readers locate the precise reference.  This is part of
the general exhortation ``Have some consideration for your readers!''

% Use of the optional first argument of \cite.
References to specific locations (pages, sections, theorems etc.)
should take the form ``\cite[Section 2.4]{MittelbachGoossens2004}''.
That is, the citation should take the foregoing form rather than
``Section 2.4 of \cite{MittelbachGoossens2004}''.  This is
handled for you automatically by the \verb!\cite{...}! command
if you make use of the optional first argument of this command.
E.g. use \verb!\cite[Section 2.4]{MittelbachGoossens2004}! to get
the appropriate form of the citation referred to above.

This example produces (as you can see) a result entirely enclosed
in parentheses.  Suppose you want to say ``See for instance
\citet[Section 2.4]{MittelbachGoossens2004} for additional
commentary.''  As foreshadowed in Section~\ref{sec:citeVar}, to
achieve this effect you can invoke the command
\verb!\citet[Section 2.4]{MittelbachGoossens2004}!.  Another
possibility, which gets rid of parentheses completely, is to use
\verb!\citealt[Section 2.4]{MittelbachGoossens2004}!.  (This is
the example of the use of \verb!\citealt! with an optional first
argument, as promised in Section~\ref{sec:citeVar}.)  Use of this
command would serve to produce ``See for instance \citealt[Section
2.4]{MittelbachGoossens2004} for additional commentary.''

For page references you may use either the form ``p. 42'' as in
\verb!\cite[p. 42]{Dick1971}!, or ``page 42'' as in
\verb!\cite[page 42]{Dick1971}!.  Likewise for multiple pages you may
use either \verb!\cite[pp. 42--76]{Dick1971}!
or \verb!\cite[pages 42--76]{Dick1971}!.
However you must be consistent and stick with one form or the
other throughout the paper.  Note there must be a \emph{space}
between the full stop or period and the following page number.

Finally I would like to comment briefly on the convention with
regard to citing papers with multiple authors.  This convention
is followed automatically if you use \BibTeX\ and the \texttt{anzsj}
bibliography style, but if you don't, then you will
need to take explicit cognizance of this convention:
\begin{itemize}
\item For papers with three or fewer authors, all authors' names
must be given in a citation.  E.g. a paper with authors Fred Nurk,
Melvin Mingdinkler and Hoo Hee, cited via \verb!\cite{NurkEtAl1984}!,
would yield ``\cite{NurkEtAl1984}''.
\item For papers with four or more authors, only the first
author's name, followed by ``et al.'' should be given in a citation.
E.g. a paper with authors D. Trump, M. Rubio, T. Cruz, J. Bush, J. Kasich
and B. Carson, cited via \verb!\cite{TrumpEtAl2021}! 
would yield ``\cite{TrumpEtAl2021}''. 
\end{itemize}

This is a \textbf{change of policy} from what was previously stated
in the Author Guidelines provided on the Journal's web page.
Both the guidelines (which, by the way, were inconsistent with
what was actually implemented by the \texttt{anzsj} bibliography
style!) \emph{and} the \texttt{anzsj.bst} bibliography style file
have been adjusted.  The convention formerly stated in the guidelines
was intricate, slightly tricky to adhere to and rarely enforced.
The adjustment provides a simpler and ``cleaner'' protocol, achieves
an admirable consistency between guidelines and actual practice
and makes life a lot simpler for everyone.

\section{Notational Conventions}
\label{sec:noteConv}
It may seem dogmatic, but the Journal has some strict rules
about notational conventions that must be followed.  The reason
for these rules is simply \emph{consistency}.  One and only one
convention must be followed, otherwise the result is a visually
unpleasant hodge-podge.  Which convention is chosen does not
usually matter very much, but a single one must be chosen and
used consistently.  The choice is made by the Journal; authors
must follow it.

A few of the more important examples of these conventions are
listed below.  Many others are given in the document ``\textit{ANZJS}
Style Guide for Authors'' as mentioned in Section~\ref{sec:intro}.
\begin{enumerate}
\item The transpose operator:  This must be represented as a
sans-serif $\top$, which is most easily rendered in \LaTeX\
by \verb!\top!.
\item The symbols ``$\forall$'' and $\exists$: Do \emph{not}
use them!  Use \emph{words} --- ``for each'' or ``for all'' and
``there exist(s)''.
\item Random and non-random quantities:  (Scalar) random variables
should generally be denoted by upper case letters such as $X$ or $Y$.
Non-random quantities should be denoted by lower case letters. An
observed value of $Y$ would be denoted by $y$.
\item Vectors and matrices:  Vectors quantities should be indicated
by bold face font, e.g. $\by$.  Vectors of observations should
be presented as (boldface) lower case letters (such as the $\by$ example
just given) whereas vectors
of random variables should be presented as bold face upper case
letters: $\bY$.  Matrices should also be presented as bold face
upper case letters: $\bM$.
\item Expectation:  Use ``E'' (ordinary Roman font) for the
expectation operator, and enclose the argument of this operator in
\emph{parentheses} as in $\E(X)$. \label{op:expect}
\item Variance, covariance and correlation:  Likewise use ``var'',
``cov'' and ``cor'' (ordinary Roman font, all lower case) for the
variance, covariance and correlation operators.
operators, as in $\var(X)$, $\cov(X,Y)$ and $\cor(X,Y)$. \label{op:var}
\item Probability: Use ``$\Pr$'' for the probability function,
and enclose the argument of this function in \emph{parentheses}
as in $\Pr(A)$.  The probability function is best rendered
in \LaTeX\ by using \verb!\Pr!.
\item Do not begin sentences with symbols (mathematical or
otherwise).  A sentence \emph{must} begin with a \emph{word}
that can be capitalised. For example, instead of ``$\Phi(x)$ is
a cumulative distribution function \ldots'', use ``The function
$\Phi(x)$ is a cumulative distribution function \ldots''.
\end{enumerate}

Note that following the foregoing (and other) conventions can be
facilitated by defining the appropriate mathematical ``commands''
using the \verb!\newcommand{}! facility provide by \LaTeX.  Examples
of this use of \verb!\newcommand{}! are provided in the \LaTeX\
source file previously referred to.  In particular the expectation
operator and the variance, covariance and correlation operators
(items \ref{op:expect} and \ref{op:var} above) are defined in
the preamble of this source file.  By imitating these, and the
other examples in the preamble, you can construct a convenient
``shorthand'' that will allow you to produce notation conforming
to the Journal's convention using a minimal number of keystrokes.

\section{Equation numbering}
\label{sec:eqnNumb}
An equation should be given a number \textbf{\textit{ONLY IF}}
if it is referred to elsewhere in the paper.
Use \verb! \[ ... \]! to display an equation \emph{without} a number.
You can use \verb!\begin{eqnarray*} ... \end{eqnarray*}! (as I always
used to do until the error of my ways was recently pointed out to me) to
display an array of equations without numbers, but it is better (see
\cite{Madsen2006}) to use \verb!\begin{align*} ... \end{align*}!.
You will need to have the package \texttt{amsmath} loaded in order
to have access to the \texttt{align*} (and the \texttt{align}
and \texttt{split} --- see below) environments.  Examples:
\[
\Pr(K = k) = \binom{n}{k} p^k (1-p)^{n-k}
\]
and
\begin{align*}
P_0(x) &= 1 \\
P_1(x) &= x \\
P_2(x) &= (3x^2 - 1)/2 \\
P_3(x) &= (5x^3 - 3x)/2 \\
       & \ldots \\
P_{n+1}(x) &= ((2n+1)xP_n(x) - nP_{n-1}(x))/(n+1)
\end{align*}
Use \verb! \begin{equation} ... \end{equation}! to display an
equation \emph{with} a number.  You can use
\verb! \begin{eqnarray} ... \end{eqnarray}! to display an array of
equations with numbers, but as for un-numbered arrays of equations it
is better to use \verb! \begin{align} ... \end{align}!.  Very often
you will wish to have only one number associated with an array of
equations.  To suppress equation numbers you can use the
\verb!\nonumber! command with \texttt{align}, but you get a sexier
result if you use \texttt{split} inside an equation environment.
Examples:
\begin{equation}
\E \left (\sum_i h(x_i,\bX \setminus \{x_i\}) \right )
= \E \left ( \int_W h(u,\bX) \lambda(u,\bX) \; du \right )
\label{eq:GNZ}
\end{equation}
and
\begin{equation}
\begin{split}
\alpha \beta &= \bar{x} \\
\alpha \beta^2 &= s^2 \;\; .
\end{split}
\label{eq:gammaMM}
\end{equation}
Note how the label (i.e. ``(\ref{eq:gammaMM})'') is vertically
centred with respect to the array of equations.  See the \LaTeX\
source for the foregoing example in the file \texttt{protoType.tex}
for guidance as to how all this is done.

\noindent
Displayed equations which \emph{are} numbered should be numbered
consecutively (1), (2), \ldots, throughout the paper, including
in the appendices if any.  (I.e. they should \emph{not} be numbered
``within sections''.)  The required behaviour is the default in
\LaTeX.  As long as you do not take any overt action to mess it up,
you will get the appropriate style in your document.

\section{Figures and Tables}
\label{sec:figAndTab}

% Multipanel figures in single figure files.
Figures and tables often cause problems with the processing
of papers.  Here are a few comments on the preparation and
presentation of such displays, with an example of each type.
Of course the ``content'' of these examples is just flippant,
frivolous nonsense, as my examples usually are.  (These examples
are meant to be humorous; as I indicated previously, whether you
find them funny depends on your sense of humour.)

It can be a major annoyance if authors supply each panel of a
multi-panel figure as a separate figure file.  When this is done,
authors usually proceed by arranging the panels, within an array
that constitutes a single figure, by juxtaposing the commands used
to input the figures in an appropriate manner and inter-leafing
appropriate line breaks.  Although this is all do-able, and may
lead eventually to a visually acceptable figure, it makes extra
work both for the author and for the typesetters.  It also adds a
substantial amount of tedious work to the procedure of uploading
the final version of the paper to ScholarOne since each panel then
has to be uploaded individually.

It is much better to create a multi-panel figure in a single figure
file, using appropriate graphics techniques.  In \textsf{R} (the
recommended software for creating figures) this basically boils
down to making use of the \verb!\par(mfrow=c(n1,n2))! command
before issuing the \texttt{plot()} commands that produce the
graphical displays in each panel.  (In the foregoing, \texttt{n1}
and \texttt{n2} represent the dimensions of the array of panels.
In the example shown in Figure~\ref{fig:ltdb}, \texttt{n1} and
\texttt{n2} are both equal to 2.)

\begin{figure}[htp]
\centering
\makebox{\includegraphics[width=0.95\textwidth]{ltdbFigure}}
\caption{\label{fig:ltdb}
Characteristics of the Lesser Tasmanian Drop Bear (farkling
fraction, intracranial perspicacity and serendipity all in
furlongs per fortnight) plotted against body mass (kilograms).
The observations were made on samples obtained at four locations
in Tasmania. Plotted points represent the raw observed values;
plotted lines represent non-parametric fits to the raw data.}
\end{figure}

% Distinguishing line types and point types.
Another important issue is making sure that line types and
plotting symbols are \emph{distinguishable} in black and white.
Figures appear in the print version of the Journal in black and
white \emph{only} unless authors specifically request that some or
all of the figures appear in colour and are \emph{willing to pay
a charge} to cover the extra costs that are incurred in printing
colour figures.  So unless you wish to pay this charge --- roughly
speaking \$350 USD per figure --- you should prepare your figures
in black and white, and do this from the very start. (Figures
that are prepared in colour and then converted to black and white
in the printing process look awful! Consequently the Journal
does not countenance this practice.)  In particular, lines in
different categories should be distinguished by \emph{line type}
--- solid, dashed, dotted \ldots, and not by colour.  A modest
example is given in Figure~\ref{fig:ltdb}.  Sometimes it is useful,
or perhaps even necessary, to distinguish categories by means of
line \emph{thickness} but proceeding in this way requires a great
deal of care.

Note that colour figures can appear in the online version of the
paper for \emph{free}!  However care must be taken, since \emph{only
one} version of the text of the paper is produced.  Consequently
the online colour figures, and captions and references to figures
in the text, must be structured in such a way as to make sense
both to readers of the black-and-white (print) version and the
colour (online) version.  See \texttt{styleGuide.pdf}, Section
5.1, for a bit more detail.

A common error in respect of tables is making them overly elaborate.
Remember that the purpose of a table is to convey information! If
a table is excessively complex, the reader's eyes will glaze over
and he or she will skip the table, resulting in no information at
all being conveyed.  In particular, if a table is too wide to fit
on a page and has to be rotated 90$^\circ$ in order to be displayed,
then you are trying to put an excessive amount of information into
a single table.  The Journal will henceforth \emph{insist} that
tables fit vertically onto a single page.  If your paper contains
tables that do not satisfy this condition then you will be required
to re-design your table accordingly.  Possibilities for effecting the
re-design include eliminating some of the ``information'', splitting
the table into two or more smaller tables and putting all or part
of the table into the online supplementary material.  An example
of a reasonably perspicuous table is given in Table~\ref{tab:ltdb}.
\begin{table}[htp]
\caption{\label{tab:ltdb}
A load of dingos' kidneys in respect
of characteristics of the Lesser Tasmanian Drop Bear.  Standard
deviations are given in parentheses after the mean values.}
\centering
\begin{tabular}{|l|r|r|r|r|} \hline
Location & Body mass (kg.) & Farkling & Intracranial & Serendipity \\ 
         &                 & fraction & perspicacity &             \\ \hline
  Port Arthur &  3.95 ( 2.40) & 10.14 ( 2.43) &  9.91 ( 1.99) &  9.81 ( 2.24) \\ 
  Melaleuca   &  4.55 ( 2.41) & 10.48 ( 3.51) & 10.83 ( 2.94) & 10.54 ( 3.30) \\ 
  Wynyard     &  3.87 ( 2.70) &  9.51 ( 2.20) &  9.40 ( 2.44) &  9.50 ( 2.23) \\ 
  Bicheno     &  4.16 ( 2.41) & 10.46 ( 2.44) & 10.44 ( 2.64) & 10.20 ( 2.86) \\ 
   \hline
\end{tabular}
\end{table}
As stated in the ``\textit{ANZJS} Style Guide for Authors''
captions for tables and figures should be left-justified and not
centred unless the text of the caption fits on a single line.
However one-line captions should be centred.  For instance if the
caption of Table~\ref{tab:ltdb} were simply ``Dingos' kidneys'',
then centring would be preferable.  When the \texttt{anzsauth}
document class is used, captions are automatically centred if
the caption fits on a single line.  (Note that the document class
file \texttt{anzsauth.cls} has recently --- as of 06/11/2016 ---
been adjusted to make table captions more similar in appearance
to figure captions.  Because of this adjustment, the centring
of one-line table captions is now automatic whereas, previously,
overt measures were required.)

A table or figure that appears in the paper \emph{must} be referred
to in the text, even if only very briefly.  That is, there must
at the very least be something like ``see Figure~17''.  If there
is no such reference, then the corresponding table or figure must
not be included in the paper.

\section{Preparing \LaTeX\ and \BibTeX\ documents}
\label{sec:prepDocs}

\subsection{Editing \LaTeX\ source files}
\label{sec:editors}

There are a number of approaches to preparing your \texttt{*.tex}
and \texttt{*.bib} files. A primary consideration is that you should
use either a general \textbf{text editor}, or a specialised \LaTeX{}
editor for this task.  Do \emph{not} use a word-processing program as
an editor. Using a word-processor introduces a plethora of spurious
non-printing characters which will completely mess things up and
in all likelihood cause the universe to come to an end.

Good text editors include \texttt{vi} or \texttt{vim},
\texttt{emacs}, \texttt{gedit}, \texttt{pico}, \texttt{Crimson},
\texttt{Notepad++},~\ldots\ .  Good editors will have support
for editing of \LaTeX{} such as syntax highlighting and code
completion. The Windows\texttrademark\ editors \texttt{Notepad}
and \texttt{Wordpad} are distinctly inferior in this respect.

Among a number of possible specialised \LaTeX{} editors, one that
has been highly recommended to me by several reliable sources
is \texttt{TeXstudio}. This is an open-source, multi-platform,
fully-featured editor for \LaTeX{}. It allows for easy processing of
documents, has support for inclusion of a vast range of characters,
provides auto-completion of \LaTeX{} commands, has a built-in pdf
viewer and a number of other helpful facilities. Other similar
programs are \texttt{Texmaker} and (Windows\texttrademark\ only)
\texttt{WinEdt}.

Users of Windows\texttrademark\ will almost surely make use of
\LaTeX\ via \MiKTeX.  This is free open source software, and is
readily available and easy to install.

The integrated development environment (IDE) \texttt{proTeXt} is
described as being ``an easy-to-install \TeX{} distribution for
Windows\texttrademark, based on \texttt{MiKTeX}'', ``which adds
the \texttt{TeXstudio} front end to MiKTeX''.  Some authors may
find it helpful.

\subsection{Processing source files}
\label{sec:procBib}

One advantage of using specialised \LaTeX{} editors is the ease of
processing (``compiling'') source files, particularly in respect of
handling \BibTeX{} files. Such processing can be accomplished with
a single mouse click when \texttt{TeXstudio}, for example, is used.

If you use a ``general'' text editor and process the source
of your document by means of command line instructions, the procedure
requires more steps.  To compile a document which uses the \BibTeX\
protocols described in Section~\ref{sec:useBib}, you need to run
\LaTeX\ on the document, then run \BibTeX, then run \LaTeX\ again
(possibly several times) until it stops complaining that labels
may have changed.  Something like:
\begin{verbatim}
    latex magnumOpus
    bibtex magnumOpus
    latex magnumOpus
    latex magnumOpus
       .
       .
       .
\end{verbatim}
(In the foregoing ``\texttt{magnumOpus}'' represents the \emph{stem}
of the name of the file ``\texttt{magnumOpus.tex}'' containing
the source of your paper.  You may wish to use \texttt{pdflatex}
rather than \texttt{latex} as your ``compilation'' command.)

Whether you are using a general or a specialised editor, if you get
errors or warnings from the \texttt{bibtex} command you must edit
the \texttt{*.bib} file and fix whatever was causing the errors
(things like commas being left out).  After fixing the problem,
process the file again (if you are using a specialised editor)
or run \texttt{bibtex} again (otherwise).  After the initial
learning period, the processing procedure all goes very smoothly.
Try it. It really does make life a lot easier and saves a lot of
time and errors. Once you get used to it you'll never look back.

\section{Concluding comments}
\label{sec:concComm}

This document contains guidance on how to prepare a paper for
submission to \textit{ANZJS} by making use of the \texttt{anzsauth}
document class for \LaTeX.  You will find that by making use of this
document class and following the advice that is provided in the
foregoing material, you will be able to produce a paper that meets
the Journal's requirements and that requires much less revision and
adjustment than it otherwise might, thus speeding up the publication
process considerably.

This document also emphasises the importance of good exposition and
correct use of the English language.  The Journal has very high,
and strictly enforced, standards in this regard.  Please pay close
attention to this requirement and give careful thought to the way
in which you express yourself.  Doing so will, again, speed up the
publication process for you.

The accompanying file \texttt{protoType.tex} forms a template for
\LaTeX\ source files for papers that are to be submitted to the
Journal.  When preparing your own \LaTeX\ source file, you should
imitate the structure of the template closely.  You may find that
an effective way to proceed is to edit the template, \textit{mutatis
mutandis}, replacing authors' names, the title of the paper,
the abstract (summary) and the actual content as is appropriate.

Although it is not necessary to prepare the initial submission using
the \texttt{anzsauth} document class, it is very important that
the final version that you submit (after provisional acceptance of
your paper) should conform to the Journal's requirements.  This is
much more likely to be the case if you use the \texttt{anzsauth}
document class.  It is likely to be less work for you if you make
use of this document class and of the template from the outset,
if this is at all possible. Note that it \emph{is} necessary for
the initial submission to be double spaced and to be line-numbered.
These requirements are greatly facilitated by using the required
document class.  See page \pageref{pg:dsln}.

It is often the case that the Technical Editor will wish to make
some minor adjustments to the \LaTeX\ source file that you provide,
before putting the paper into production.  This saves having to
send the paper back to authors, yet one more time, to get these
adjustments made.  The process of making these adjustments is
a \emph{whole lot} easier if the source file is constructed in
a tidy and comprehensible manner.  Use appropriate line breaks
(keeping lines to a length of, e.g., at most 80 characters) and
ensure that there is appropriate \emph{spacing} between mathematical
constructions.  Do not embed \LaTeX\ commands to produce displayed
equations in on-running lines of text.  All of this will have of
course absolutely no impact on the \emph{output} file produced
by compiling the \LaTeX\ source, but it simplifies the process of
modifying and adjusting this source by orders of magnitude.

\newpage
\bibliographystyle{anzsj}
\bibliography{protoRefs}
\end{document}

### 2024-11-05 paper/paper-anzsj.tex
paper reformatted for ANZSJ

--- 2021-01-11 paper/paper.tex
@@
-%% template.tex
-%% from
-%% bare_conf.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE!
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-\documentclass[conference,final,]{IEEEtran}
-% Some Computer Society conferences also require the compsoc mode option,
-% but others use the standard conference format.
+\documentclass[times, doublespace]{anzsauth}
 %
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at:
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-%\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-%% BEGIN MY ADDITIONS %%
-
-\usepackage{longtable,booktabs}
-
-\usepackage[unicode=true]{hyperref}
-
-\hypersetup{
-            pdftitle={Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics},
-            pdfkeywords={statistics, visual inference, geospatial, population},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-
-% Pandoc toggle for numbering sections (defaults to be off)
-\setcounter{secnumdepth}{5}
-
-% Pandoc syntax highlighting
-
-% Pandoc header
+\usepackage{amsmath,amssymb}
+\usepackage{moreverb}
+\usepackage{url}
+\usepackage{grffile}
+\usepackage{lineno}
+% You will probably find it convenient to make use of
+% the following new commands.  Note in particular "\E"
+% for producing the expectation operator in accordance
+% with Journal policy.
+\newcommand{\utilde}{\undertilde}
+\newcommand{\E}{\mbox{$\textrm{\textup{E}}$}}
+\newcommand{\var}{\mbox{$\textrm{\textup{var}}$}}
+\newcommand{\cov}{\mbox{$\textrm{\textup{cov}}$}}
+\newcommand{\cor}{\mbox{$\textrm{\textup{cor}}$}}
+\newcommand{\by}{\mbox{$\boldsymbol{y}$}}
+\newcommand{\bX}{\mbox{$\boldsymbol{X}$}}
+\newcommand{\bY}{\mbox{$\boldsymbol{Y}$}}
+\newcommand{\bM}{\mbox{$\boldsymbol{M}$}}
 \usepackage{graphicx}
@@
 \usepackage{xcolor}
-
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-%% END MY ADDITIONS %%
-
-\hyphenation{op-tical net-works semi-conduc-tor}
+\usepackage{bookmark}
+% You probably *won't* need these new commands; they are designed
+% for use in *this* particular document.
+\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
+T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\newcommand\MiKTeX{{\rmfamily M\kern-.05em \textsc{i\kern-.025em K}\kern-.08em
+T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\newcommand\PracTeX{{\rmfamily P\kern-.05em \textsc{r\kern-.025em a\kern-.025em
+c}\kern-.08em
+T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
+% The year in the following may need to be updated!
+\def\volumeyear{2017}
+\linenumbers
+
+\runningheads{Comparing the Effectiveness of the Choropleth with Hexagon Tile}{S~KOBAKIAN and D~COOK}
+\title{Comparing the Effectiveness of the Choropleth Map with a Hexagon
+Tile Map for Communicating Cancer Statistics in Australia}
+\author{Stephanie Kobakian\addressnum{1} and Dianne Cook\addressnum{2}}
+\affiliation{Queensland University of Technology and
+Monash University}
+\address{
+\addressnum{1} \hspace*{-2ex} Science and Engineering Faculty,
+Queensland University of Technology, Brisbane, Queensland\break
+\addressnum{2} Department of Econometrics and Business Statistics, Monash University,
+Clayton, Victoria\\
+\hspace*{1ex} Email: \texttt{stephanie.kobakian@gmail.com}
+}
+\date{\vspace{-2.5em}}
 
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-\title{Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics}
-
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-
-\author{
-
-%% ---- classic IEEETrans wide authors' list ----------------
- % -- end affiliation.wide
-%% ----------------------------------------------------------
-
-%% ---- classic IEEETrans one column per institution --------
- %% -- end if/affiliation.institution-columnar
-%% ----------------------------------------------------------
-
-%% ---- one column per author, classic/default IEEETrans ----
- % -- beg affiliation.author-columnar
-  %% -- beg for/affiliation.institution.author
-\IEEEauthorblockN{
-Stephanie Kobakian
+\maketitle
+\begin{abstract}
+The choropleth map display is commonly used for communicating spatial
+distributions across geographic areas. However, when choropleths are
+used the size of the geographic units will influence the understanding
+of the distribution derived by map users. The hexagon tile map is
+presented as an alternative display for effectively visualizing population related
+distributions. Visual inference is used to measure the power
+of the hexagon tile map design, and the choropleth is used as a
+comparison. The hexagon tile map display is tested using a distribution
+that is directly related to the geography, with values monotonically
+increasing from the North-West to South-East areas of Australia. This
+study finds in a hexagon tile map lineup the single map that contains a
+population-related distribution is detected with greater probability
+than the same data displayed in a choropleth map. These findings should
+encourage map creators to implement alternative displays and consider a
+hexagon tile map when presenting spatial distributions of heterogeneous
+areas.
+\end{abstract}
+
+\section{Introduction}\label{introduction}
+
+This study compares the effectiveness of the spatial display, a hexagon
+tile map, against the standard, a choropleth map, for communicating
+information about disease statistics. The choropleth map is the
+traditional method for visualizing aggregated statistics across
+administrative boundaries. The hexagon tile map builds on existing
+displays, such as the cartogram, and tessellated hexagon displays. A
+hexagon tile map forgoes the familiar boundaries, in favor of
+representing each geographic unit as an equally sized hexagon, placed
+approximately in the correct spatial location. It differs in the relaxed
+requirement to have connected hexagons and allows sparsely located
+hexagons. This type of display may be useful for other countries, and
+other purposes. The algorithm to construct a hexagon tile map is
+available in the R package  \texttt{sugarbag} \citep{sugarbag}.
+
+The hexagon tile map was designed for Australia, motivated by a need to
+display spatial statistics for the Australian Cancer Atlas. None of the
+existing approaches for creating cartograms or hexagon tiling perform
+well for the Australian landscape, which has vast open spaces and
+concentrations of population in small regions clustered on the
+coastlines.
+
+The Australian Cancer Atlas \citep{atlas} is an online
+interactive web tool created to explore the burden of cancer on
+Australian communities. There are many cancer types to be explored
+individually or aggregated. The Australian Cancer Atlas allows users to
+explore the patterns in the distributions of cancer statistics over the
+geographic space of Australia. It uses a choropleth map display and
+diverging color scheme to draw attention to relationships between
+neighboring areas. The hexagon tile map may be a useful alternative
+display to enhance the atlas.
+
+The experiment was conducted using the lineup protocol, a visual
+inference procedure \citep{GIIV}, to objectively test
+the effectiveness of the two displays.
+
+The paper is organised as follows. The next section discusses the
+background of geographic data display and visual inference procedures.
+Section \ref{methodology} describes the methods
+for conducting the experiment and analysing the results. The results are
+summarized in the Section \ref{results}.
+
+\section{Background}\label{background}
+
+\subsection{Spatial data displays}\label{spatial-data-displays}
+
+Spatial visualisations communicate the distribution of statistics over
+geographic landscapes. The choropleth map \citep{EI},
+\citep{BCM} is a traditional display. It is used to
+present statistics that have been aggregated on geographic units.
+Creating a choropleth map involves drawing polygons representing the
+administrative boundaries, and filling with colour mapped to the value
+of the statistic. The choropleth map places the statistic in the context
+of the spatial domain, so that the reader can see whether there are
+spatial trends, clusters or anomalies. This is important for digesting
+disease patterns. If there is a trend it may imply that the disease is
+spreading from one location to another. If there is a cluster, or an
+anomaly, there may be a localized outbreak of the disease. Aggregating
+the statistic on administrative units, provides a level of privacy to
+individuals, while allowing the impact of the disease on the community
+to be analyzed.
+
+\begin{figure}
+
+{\centering 
+\includegraphics[width=0.46\linewidth]{paper_files/figure-latex/thyroid-choro-1} 
+\includegraphics[width=0.54\linewidth]{paper_files/figure-latex/thyroid-hex-1} 
 }
-\IEEEauthorblockA{Queensland University of Technology\\
-Science and Engineering Faculty\\
-Brisbane, Australia
-\\stephanie.kobakian@qut.edu.au
-}
- %% -- end for/affiliation.institution.author
-\and
-  %% -- beg for/affiliation.institution.author
-\IEEEauthorblockN{
-Dianne Cook
-}
-\IEEEauthorblockA{Monash University\\
-Econometrics and Business Statistics Faculty\\
-Melbourne, Australia
-\\dicook@monash.edu
-}
- %% -- end for/affiliation.institution.author
- %% -- end for/affiliation.institution
- %% -- end if/affiliation.institution-columnar
-%% ----------------------------------------------------------
-
-}
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-%
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3},
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
-\maketitle
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract
-\begin{abstract}
-The choropleth map display is commonly used for communicating spatial distributions across geographic areas.
-However, when choropleths are used the size of the geographic units will influence the understanding of the distribution derived by map users.
-The hexagon tile map is presented as an alternative display for visualizing population related distributions effectively.
-Visual inference is used to measure the power of the hexagon tile map design, and the choropleth is used as a comparison.
-The hexagon tile map display is tested using a distribution that is directly related to the geography, with values monotonically increasing from the North-West to South-East areas of Australia.
-This study finds in a hexagon tile map lineup the single map that contains a population related distribution is detected with greater probability than the same data displayed in a choropleth map.
-These findings should encourage map creators to implement alternative displays and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
-\end{abstract}
-
-% keywords
-\begin{IEEEkeywords}
-statistics; visual inference; geospatial; population
-\end{IEEEkeywords}
-
-% use for special paper notices
-
-% make the title area
-\maketitle
-
-% no keywords
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-This study compares the effectiveness of the spatial display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics.
-The choropleth map is the traditional method for visualizing aggregated statistics across administrative boundaries.
-The hexagon tile map builds on existing displays, such as the cartogram, and tessellated hexagon displays.
-A hexagon tile map forgoes the familiar boundaries, in favor of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location.
-It differs in the relaxed requirement to have connected hexagons, and allows sparsely located hexagons.
-This type of display may be useful for other countries, and other purposes.
-The algorithm to construct a hexagon tile map is available in the R package sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]}.
-
-The hexagon tile map was designed for Australia, motivated by a need to display spatial statistics for the Australian Cancer Atlas.
-None of the existing approaches for creating cartograms or hexagon tiling perform well for the Australian landscape, which has vast open spaces and concentrations of population in small regions clustered on the coastlines.
-
-The Australian Cancer Atlas {[}\protect\hyperlink{ref-atlas}{2}{]} is an online interactive web tool created to explore the burden of cancer on Australian communities.
-There are many cancer types to be explored individually or aggregated.
-The Australian Cancer Atlas allows users to explore the patterns in the distributions of cancer statistics over the geographic space of Australia.
-It uses a choropleth map display and diverging color scheme to draw attention to relationships between neighboring areas.
-The hexagon tile map may be a useful alternative display to enhance the atlas.
-
-The experiment was conducted using the lineup protocol, a visual inference procedure {[}\protect\hyperlink{ref-GIIV}{3}{]}, to objectively test the effectiveness of the two displays.
-
-The paper is organised as follows.
-The next section discusses the background of geographic data display and visual inference procedures.
-The \protect\hyperlink{methodology}{Methodology} section describes the methods for conducting the experiment and analysing the results.
-The results are summarized in the \protect\hyperlink{results}{Results} section.
-
-\hypertarget{background}{%
-\section{Background}\label{background}}
-
-\hypertarget{spatial-data-displays}{%
-\subsection{Spatial data displays}\label{spatial-data-displays}}
-
-Spatial visualisations communicate the distribution of statistics over geographic landscapes.
-The choropleth map {[}\protect\hyperlink{ref-EI}{4}{]}, {[}\protect\hyperlink{ref-BCM}{5}{]} is a traditional display.
-It is used to present statistics that have been aggregated on geographic units.
-Creating a choropleth map involves drawing polygons representing the administrative boundaries, and filling with colour mapped to the value of the statistic.
-The choropleth map places the statistic in the context of the spatial domain, so that the reader can see whether there are spatial trends, clusters or anomalies.
-This is important for digesting disease patterns.
-If there is a trend it may imply that the disease is spreading from one location to another.
-If there is a cluster, or an anomaly, there may be a localized outbreak of the disease.
-Aggregating the statistic on administrative units, provides a level of privacy to individuals, while allowing the impact of the disease on the community to be analyzed.
+
+\caption{Thyroid incidence among females across the Statistical Areas of Australia at Level 2, displayed using a choropleth (left) and a hexagon tile map (right).
+Blue indicates lower than average, and red indicates higher than average incidence.
+The choropleth suggests high incidence is clustered on the east coast but misses the high incidence in Perth and a few locations in inner Melbourne visible in the hexagon tile map.}\label{fig:thyroid}
+\end{figure}
+
+The choropleth map is an effective spatial display if the size of the
+geographic units is relatively uniform. This is not the case for most
+countries. Size heterogeneity in administrative units is particularly
+extreme in Australia: most of the landscape of Australia is sparsely
+settled, with the population densely clustered into the narrow coastal
+strips. Fig. \ref{fig:thyroid} shows the choropleth map of thyroid
+cancer rates in Australia. The choropleth map focuses attention on the
+geography, and for heterogeneously sized areas it presents a biased view
+of the population-related distribution of the statistic
+\citep{CBATCC}. \emph{Land doesn't get cancer, people
+do} -- a more effective way to communicate the spatial distributions of
+cancer statistics is needed.
+
+A cartogram is a general solution for better displaying a
+population-based statistic. It transforms the geographic map base to
+reflect the population in the geographic region while preserving some
+aspects of the geographic location. There are several cartogram
+algorithms \citep{ACTUC, CBATCC}; each involves shifting the boundaries of
+geographic units, using the value of the statistic to increase or
+decrease the area taken by the geographic unit on the map. The changes
+to the boundaries result in cartograms that accurately communicate
+population by map area for each of the geographic units but can result
+in losing the familiar geographic information. For Australia, the
+transformations warp the country so that it is no longer recognizable.
+
+Alternative algorithms make various trade-offs between familiar shapes
+and representation of geographic units. The non-contiguous cartogram
+method \citep{NAC} keeps the shapes of geographic units
+intact and changes the size of the shape. This method disconnects areas
+creating empty space on the display losing the continuity of the spatial
+display of the statistic. The Dorling cartogram
+\citep{ACTUC} represents each unit as a circle, sized
+according to the value of the statistic. The neighbour relationships are
+mostly maintained by how the circles touch. A similar approach was
+pioneered by \cite{RSCW}, using rectangles that
+tile to align borders of neighbours \citep{CDWCS}.
+There have been thorough reviews of the array of methods, as suitable
+for cancer atlas displays \citep{review},
+\citep{BCM}.
+
+%\begin{figure}
+
+%{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{paper_files/figure-latex/thyroid-hex-1}
+
+%}
+
+%\caption{A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
+The high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) can now be seen, along with numerous isolated spots.}\label{fig:thyroid-hex}
+%\end{figure}
+
+The hexagon tile map algorithm, automatically matches spatial regions to
+their nearest hexagon tile, from a grid of tiles. It has the effect of
+spreading out the inner city areas while maintaining the spatial
+locations or regions in remote areas. The algorithm is available in the
+R package,  \texttt{sugarbag} \citep{sugarbag}. Fig.
+\ref{fig:thyroid} shows the hexagon tile map. Colour maps from
+substantially below average (blue) to substantially above average (red)
+rates. The inner city areas have expanded, making it possible to see the
+cancer incidence in the small, densely populated areas. Remote regions
+are represented by isolated hexagons, which is not ideal, but maintains
+the spatial location of these data values. It is of interest to know how
+well the spatial distribution is perceived for this display, in
+comparison to the choropleth.
+
+\subsection{Visual Inference}\label{visual-inference}
+
+To assess the effectiveness of the hexagon tile map, the lineup
+protocol \citep{GIIV, BCHLLSW09}
+from visual inference procedures is employed. The approach mirrors
+classical statistical inference. The procedures for doing a power
+comparison of competing plot designed, outlined in
+\cite{GTPCCD}, are followed.
+
+In classical statistical inference hypothesis testing is conducted by
+comparing the value of a test statistic on a standard reference
+distribution, computed assuming the null hypothesis is true. If the
+value is extreme, the null hypothesis is rejected, because the test
+statistic value is unlikely to have been so extreme if it was true. In
+the lineup protocol, the plot plays the role of the test statistic, and
+the data plot is embedded in a field of null plots. Defining the plot
+using a grammar of graphics \citep{ggplot2} makes it a
+functional mapping of the variables and thus, it can be considered to be
+a statistic. With the same data, two different plots can be considered
+to be competing statistics, one possibly a more powerful statistic than
+the other.
+
+To do hypothesis testing with the lineup protocol requires human
+evaluation. The human judge is required to identify the most different
+plot among the field of plots. If this corresponds to the data plot --
+the test statistic -- the null hypothesis is rejected. It means that the
+data plot is extreme relative to the reference distribution of null
+plots.
+
+The null hypothesis is explicitly provided by the grammatical plot
+description. For example, if a histogram is the plot type being used,
+the null might be that the underlying distribution of the data is a
+Gaussian. Null data would be generated by simulating from a normal
+model, with the same mean and standard deviation as the data. In
+practice, the null hypothesis used is generic, such as \emph{there is NO
+structure or a pattern in the plot}, and contrasted to an alternative
+that there is structure.
+
+The chance that an observer picks the data plot out of a lineup of size
+\(m\) plots accidentally, if the null hypothesis is true is \(1/m\).
+With \(K\) observers, the probability of \(k\) randomly choosing the
+data plot, roughly follows a binomial distribution with \(p=1/m\). Fig.
+\ref{fig:lineup} shows a lineup of the hexagon tile map, of size
+\(m=12\). Plot 3 is the data plot, and the remaining 11 are plots of
+null data.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/liver-1} \caption{A choropleth map of the smoothed average of liver cancer diagnoses for Australian males.
-The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
-The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.}\label{fig:liver}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/liver-hex-1} \caption{A hexagon tile map of the smoothed average of liver cancer diagnoses for Australian males.
-The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average.
-The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.}\label{fig:liver-hex}
-\end{figure}
-
-The choropleth map is an effective spatial display if the size of the geographic units is relatively uniform.
-This is not the case for most countries.
-Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips.
-A choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population related distribution of the statistic {[}\protect\hyperlink{ref-CBATCC}{6}{]}.
-\emph{Land doesn't get cancer, people do} -- a more effective way to communicate the spatial distributions of cancer statistics is needed.
-
-A cartogram is a general solution for better displaying a population-based statistic.
-It transforms the geographic map base to reflect the population in the geographic region, while preserving some aspects of the geographic location.
-There are several cartogram algorithms {[}\protect\hyperlink{ref-ACTUC}{7}{]}, {[}\protect\hyperlink{ref-CBATCC}{6}{]}; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
-The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units but can result in losing the familiar geographic information.
-For Australia, the transformations warp the country so that it is no longer recognizable.
-
-Alternative algorithms make various trade offs between familiar shapes and representation of geographic units.
-The non-contiguous cartogram method {[}\protect\hyperlink{ref-NAC}{8}{]} keeps the shapes of geographic units intact, and changes the size of the shape.
-This method disconnects areas creating empty space on the display losing the continuity of the spatial display of the statistic.
-The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{7}{]} represents each unit as a circle, sized according to the value of the statistic.
-The neighbour relationships are mostly maintained by how the circles touch.
-A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{9}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{10}{]}.
-There have been thorough reviews of the array of methods, as suitable for cancer atlas displays {[}\protect\hyperlink{ref-review}{11}{]}, {[}\protect\hyperlink{ref-BCM}{5}{]}.
-
-The hexagon tile map algorithm, automatically matches spatial regions to their nearest hexagon tile, from a grid of tiles.
-It has the effect of spreading out the inner city areas while maintaining the spatial locations or regions in remote areas.
-The algorithm is available in the R package, sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]}.
-Fig.
-\ref{fig:liver} shows the hexagon tile map, along with the choropleth map of liver cancer rates in Australia.
-Colour maps from substantially below average (blue) to substantially above average (red) rates.
-The inner city areas have expanded, making it possible to see the cancer incidence in the small, densely populated areas.
-Remote regions are represented by isolated hexagons, which is not ideal, but maintains the spatial location of these data values.
-It is of interest to know how well the spatial distribution is perceived for this display, in comparison to the choropleth.
-
-\hypertarget{visual-inference}{%
-\subsection{Visual Inference}\label{visual-inference}}
-
-In order to assess the effectiveness of the hexagon tile map, the lineup protocol {[}\protect\hyperlink{ref-GIIV}{3}{]},{[}\protect\hyperlink{ref-BCHLLSW09}{12}{]} from visual inference procedures is employed.
-The approach mirrors classical statistical inference.
-The procedures for doing a power comparison of competing plot designed, outlined in {[}\protect\hyperlink{ref-GTPCCD}{13}{]}, are followed.
-
-In classical statistical inference hypothesis testing is conducted by comparing the value of a test statistic on a standard reference distribution, computed assuming the null hypothesis is true.
-If the value is extreme, the null hypothesis is rejected, because the test statistic value is unlikely to have been so extreme if it was true.
-In the lineup protocol, the plot plays the role of the test statistic, and the data plot is embedded in a field of null plots.
-Defining the plot using a grammar of graphics {[}\protect\hyperlink{ref-ggplot2}{14}{]} makes it a functional mapping of the variables and thus, it can be considered to be a statistic.
-With the same data, two different plots can be considered to be competing statistics, one possibly a more powerful statistic than the other.
-
-To do hypothesis testing with the lineup protocol requires human evaluation.
-The human judge is required to identify the most different plot among the field of plots.
-If this corresponds to the data plot -- the test statistic -- the null hypothesis is rejected.
-It means that the data plot is extreme relative to the reference distribution of null plots.
-
-The null hypothesis is explicitly provided by the grammatical plot description.
-For example, if a histogram is the plot type being used, the null might be that the underlying distribution of the data is a Gaussian.
-Null data would be generated by simulating from a normal model, with the same mean and standard deviation as the data.
-In practice, the null hypothesis used is generic, such as \emph{there is NO structure or a pattern in the plot}, and contrasted to an alternative that there is structure.
-
-The chance that an observer picks the data plot out of a lineup of size \(m\) plots accidentally, if the null hypothesis is true is \(1/m\).
-With \(K\) observers, the probability of \(k\) randomly choosing the data plot, roughly follows a binomial distribution with \(p=1/m\).
-Fig.
-\ref{fig:lineup} shows a lineup of the hexagon tile map, of size \(m=12\).
-Plot 3 is the data plot, and the remaining 11 are plots of null data.
-
-\begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/lineup-1} \caption{This lineup of twelve hexagon tile map displays contains one map with a real population related structure.
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/lineup-1} \caption{This lineup of twelve hexagon tile map displays contains one map with a real population-related structure.
 The rest are null plots that contain spatial correlation between neighbours.}\label{fig:lineup}
@@
 
-In order to determine the effectiveness of a type of display, this probability is less relevant than the overall proportion of observers who pick the data plot, \(k/K\).
-The power of the test statistic (data plot) is provided by this proportion.
-Power in a statistical sense is the ability of the statistic to \emph{produce a rejection} of the null hypothesis, if it is indeed \emph{not true}.
-With the same data plotted using two different displays, the display with the highest proportion of people who choose the data plot would be considered to be the most powerful statistic.
-
-\hypertarget{methodology}{%
-\section{Methodology}\label{methodology}}
-
-This study aims to answer two key questions around the presentation of spatial distributions:
+To determine the effectiveness of a type of display, this
+probability is less relevant than the overall proportion of observers
+who pick the data plot, \(k/K\). The power of the test statistic (data
+plot) is provided by this proportion. Power in a statistical sense is
+the ability of the statistic to \emph{produce a rejection} of the null
+hypothesis if it is indeed \emph{not true}. With the same data plotted
+using two different displays, the display with the highest proportion of
+people who choose the data plot would be considered to be the most
+powerful statistic.
+
+\section{Methodology}\label{methodology}
+
+This study aims to answer two key questions about the presentation of
+spatial distributions:
 
@@
 \def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Are spatial disease trends that impact highly populated small areas detected with higher accuracy, when viewed in a hexagon tile map?
-\item
-  Are people faster in detecting spatial disease trends that impact highly populated small areas when using a hexagon tile map?
+ \item
+  Are spatial disease trends that impact highly populated small areas
+  detected with higher accuracy, when viewed in a hexagon tile map?
+\item
+  Are people faster in detecting spatial disease trends that impact
+  highly populated small areas when using a hexagon tile map?
 \end{enumerate}
 
-Additional considerations when completing this experimental task included the difficulty experienced by participants and the certainty they had in their decision.
-
-Australia is used for the study, with Statistical Area 3 (SA3) {[}\protect\hyperlink{ref-abs2016}{15}{]} as the geographic units.
-The results should apply broadly to any other geographic area of interest.
-
-\hypertarget{experimental-factors}{%
-\subsection{Experimental factors}\label{experimental-factors}}
-
-The primary factor in the experiment is the plot type.
-The secondary factor is a trend model.
-Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to do well, and two with differing level of inner city hot spots.
-These latter two reflect the structure seen in the liver cancer data (Fig.
-\ref{fig:liver}).
-This produces six treatment levels:
+Additional considerations when completing this experimental task
+included the difficulty experienced by participants and the certainty
+they had in their decision.
+
+Australia is used for the study, with Statistical Area 3 (SA3)
+\citep{abs2016} as the geographic units. The results
+should apply broadly to any other geographic area of interest.
+
+\subsection{Experimental factors}\label{experimental-factors}
+
+The primary factor in the experiment is the plot type. The secondary
+factor is a trend model. Three trend models were developed, one
+mirroring a large spatial trend for which the choropleth would be
+expected to do well, and two with differing levels of inner-city hot
+spots. These latter two reflect the structure seen in thyroid cancer
+data (Fig. \ref{fig:thyroid}). This
+produces six treatment levels:
 
 \begin{itemize}
-\tightlist
  \item
@@
 \item
-  Trend: \emph{South-East to North-West; Locations in three population centres; Locations in multiple population centres, }
+  Trend: \emph{South-East to North-West; Locations in three population
+  centres; Locations in multiple population centres, }
 \end{itemize}
 
-Data is generated for each of the trend models, with four replicates, and each displayed both as a choropleth and as a hexagon tile map, which yields 12 data sets, and 24 data plots.
-This set of displays is divided in half, providing two sets of 12 displays, Group A and Group B.
-Participants were randomly allocated to Group A or B.
-Participants saw a data set only once, either as a choropleth or as a hexagon tile map.
-Table \ref{fig:exp-design} summarises the design and the allocation of the displays.
+Data is generated for each of the trend models, with four replicates,
+and each displayed both as a choropleth and as a hexagon tile map, which
+yields 12 data sets, and 24 data plots. This set of displays is divided
+in half, providing two sets of 12 displays, Group A and Group B.
+Participants were randomly allocated to Group A or B. Participants saw a
+data set only once, either as a choropleth or as a hexagon tile map.
+Table \ref{fig:exp-design} summarises the design and the allocation of
+the displays.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/exp-design-1} \caption{The experimental design used in the visual inference study.}\label{fig:exp-design}
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/exp-design-1} \caption{The experimental design used in the visual inference study.
+Twelve data sets, with four replications of each trend model, are composed into lineups and displayed as either a choropleth map or hexagon tile map.
+These are organised into two packets of plots, A and B, which are provided to participants to evaluate.}\label{fig:exp-design}
 \end{figure}
 
-\hypertarget{generating-null-data}{%
-\subsection{Generating null data}\label{generating-null-data}}
-
-Null data needs to be data with no (interesting) structure.
-In most scenarios, permutation is the main approach for generating null plots.
-It is used to break association between variables, while maintaining marginal distributions.
-This is too simple for spatial data.
-In spatial data, a key feature is the spatial dependence or smoothness over the landscape.
-To do something simple, like permute the values relative to the geographic location would produce null plots which are too chaotic, and the data plot will be recognisable for its smoothness rather than any structure of interest.
-
-For spatial data, null data is stationary data, where the mean, variance and spatial dependence are constant over the geographic units.
-Stationary data is specified by a variogram model {[}\protect\hyperlink{ref-POG}{16}{]}.
-Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots.
-The parameters for the Gaussian model were sill=1, range=0.3 with the variance generated by a standard normal distribution.
-
-The R package \texttt{gstat} {[}\protect\hyperlink{ref-gstat}{17}{]} was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
-
-The null model imposed by our hypothesis suggests that neighbors are related.
-The randomness induced when generating the null data was smoothed to mirror the practices employed by the Australian Cancer Atlas statisticians.
-In these 12 sets of data, each of the 12 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas, without implementing uncertainty via transparency.
-
-A list of neighbors for each geographic unit was generated to use when smoothing the distributions.
-For each geographic unit the same spatial smoother was applied in each layer of smoothing.
-It kept half of the units' previous value, and derived the new half as the mean of the values of its neighbors at the previous layer of smoothing.
-
-This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the Liver cancer distribution (Fig. \ref{fig:liver}).
-
-\hypertarget{generating-lineups}{%
-\subsection{Generating lineups}\label{generating-lineups}}
-
-For each trend model, four real data displays were created by manipulating the centroid values of each of the SA3 geographic units.
-
-The North West to South East (NW-SE) distribution was created using a linear equation of the centroid longitude and latitude values.
-
-The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia, calculated when creating the hexagon tile map using the sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]} package.
-201 of the 336 SA3s were considered greater capital city areas, the values of these areas were increased to create red clusters.
-The amount was chosen to make clusters around the cities visible in the choropleth display even if they were not overtly noticeable.
-
-A similar selection process was applied to the Three Cities' trend model.
-However, for each of the four replicates for the Three Cities trend, a random sample of capital cities was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart.
-Only values of the areas nearest to the three cities were increased to create clusters.
-
-One of the lineup locations was chosen to embed the real trend model map, in each of the four replicates, for the three trend models.
-The location was chosen from a sub sample of the 12 possible locations.
-The chance of reptition using resampling was introduced to prevent participants from inducing the location by elimination, the locations 1, 7, 10 and 11 were not used.
-
-As seen in Fig \ref{fig:exp-design}, the choropleth and hexagon display used the same location for the real data display of the trend model was added to the spatially correlated null values for each lineup.
-Each set of lineup data was used to produce a choropleth map lineup and hexagon tile map lineup.
-These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
-
-For each of the 144 individual maps, the values for each geographic area were rescaled to create a similar color scale from deep blue to dark red within each map.
-This meant at least one geographic unit was coloured dark blue, and at least one was red, in every map display of every lineup.
-
-For the geographic NW-SE distribution, this resulted in the smallest values of the trend model (blue) occurring in Western Australia, the North West of Australia, and the largest values of the trend model (red) occurring in the South East.
-This resulted in Tasmania being colored completely red.
-
-For the population related displays, the clusters in the cities appeared more red than the rest of Australia.
-
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
-
-\hypertarget{data-cleaning}{%
-\subsubsection{Data Cleaning}\label{data-cleaning}}
-
-The first step in the data cleaning process involved checking that survey responses collected for each participants were only included once in the data set.
-The data cleaning process also involved filtering out participants' who did not provide at least three unique choices when considering each of the twelve lineups.
-These participants achieved a detection rate of 0.
-If participants had made various plot choices for the 12 displays they saw they were still included in the dataset.
-
-\hypertarget{descriptive-statistics}{%
-\subsubsection{Descriptive statistics}\label{descriptive-statistics}}
-
-Basic descriptive statistics were used to contrast the detection rate for the two types of displays.
-Comparison was also made across the trend models, contrasting the mean and standard detection rate for each group, who had seen the different map display type for each replicate.
-
-Side-by-side dot plots were made of accuracy (efficiency) against map type, faceted by trend model type.
-
-Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.
-
-Plots will be made in R {[}\protect\hyperlink{ref-RCore}{18}{]}, with the \texttt{ggplot2} package {[}\protect\hyperlink{ref-ggplot2}{14}{]}.
-
-\hypertarget{modelling}{%
-\subsubsection{Modelling}\label{modelling}}
-
-The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R {[}\protect\hyperlink{ref-RCore}{18}{]} \texttt{glmer()} function in the \texttt{lme4} {[}\protect\hyperlink{ref-lme4}{19}{]} package implements generalised linear mixed effect models.
-The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
+\subsection{Generating null data}\label{generating-null-data}
+
+Null data needs to be data with no (interesting) structure. In most
+scenarios, permutation is the main approach for generating null plots.
+It is used to break association between variables while maintaining
+marginal distributions. This is too simple for spatial data. In spatial
+data, a key feature is the spatial dependence or smoothness over the
+landscape. To do something simple, like permuting the values relative to
+the geographic location would produce null plots which are too chaotic,
+and the data plot will be recognisable for its smoothness rather than
+any structure of interest.
+
+For spatial data, null data is stationary data, where the mean, variance
+and spatial dependence are constant over the geographic units.
+Stationary data is specified by a variogram model
+\citep{POG}. Simulating from a variogram model, where
+the spatial dependence is specified, generates the stationary spatial
+data used for the null plots. The parameters for the Gaussian model were
+sill=1, range=0.3 with the variance generated by a standard normal
+distribution.
+
+The R package  \texttt{gstat} \citep{gstat} was used to
+simulate 144 null sets, 12 data sets for each plot in a lineup, and 12
+sets for 12 lineups.
+
+The null model imposed by our hypothesis suggests that neighbours are
+related. The randomness induced when generating the null data was
+smoothed to mirror the practices employed by the Australian Cancer Atlas
+statisticians. In these 12 sets of data, each of the 12 maps was
+smoothed several times to replicate the spatial autocorrelation seen in
+cancer data sets presented in the Australian Cancer Atlas, without
+implementing uncertainty via transparency.
+
+A list of neighbours for each geographic unit was generated to use when
+smoothing the distributions. For each geographic unit, the same spatial
+smoother was applied in each layer of smoothing. It kept half of the
+units' previous value and derived the new half as the mean of the
+values of its neighbours at the previous layer of smoothing.
+
+This smoothing allowed neighbors to be related to each other, but also
+allowed outliers, and showed distributions similar to the thyroid cancer
+distribution (Fig. \ref{fig:thyroid}).
+
+\subsection{Generating lineups}\label{generating-lineups}
+
+For each trend model, four real data displays were created by
+manipulating the centroid values of each of the SA3 geographic units.
+
+The North West to South East (NW-SE) distribution was created using a
+linear equation of the centroid longitude and latitude values.
+
+The All Cities trend model was created using the distance from the
+centroid of each geographic unit to the closest capital city in
+Australia, calculated when creating the hexagon tile map using the
+ \texttt{sugarbag} \citep{sugarbag} package. 201 of the 336 SA3s
+were considered greater capital city areas, the values of these areas
+were increased to create red clusters. The amount was chosen to make
+clusters around the cities visible in the choropleth display even if
+they were not overtly noticeable.
+
+A similar selection process was applied to the Three Cities' trend
+model. However, for each of the four replicates for the Three Cities
+trend, a random sample of capital cities was taken from Sydney,
+Brisbane, Melbourne, Adelaide, Perth, and Hobart. Only the values of the
+areas nearest to the three cities were increased to create clusters.
+
+One of the lineup locations was chosen to embed the real trend model
+map, in each of the four replicates, for the three trend models. The
+location was chosen from a sub-sample of the 12 possible locations. The
+chance of repetition using resampling was introduced to prevent
+participants from inducing the location by elimination, the locations 1,
+7, 10 and 11 were not used.
+
+As seen in Fig \ref{fig:exp-design}, the choropleth and hexagon display
+used the same location for the real data display of the trend model was
+added to the spatially correlated null values for each lineup. Each set
+of lineup data was used to produce a choropleth map lineup and hexagon
+tile map lineup. These matched pairs were split between Group A and
+Group B according to the 2 x 3 factor experimental design depicted in
+\ref{fig:exp-design}.
+
+For each of the 144 individual maps, the values for each geographic area
+were rescaled to create a similar colour scale from deep blue to dark red
+within each map. This meant at least one geographic unit was coloured
+dark blue and at least one was red, in every map display of every
+lineup.
+
+For the geographic NW-SE distribution, this resulted in the smallest
+values of the trend model (blue) occurring in Western Australia, the
+North West of Australia, and the largest values of the trend model (red)
+occurring in the South East. This resulted in Tasmania being coloured
+completely red.
+
+For the population-related displays, the clusters in the cities appeared
+more red than the rest of Australia.
+
+\subsection{Analysis}\label{analysis}
+
+\subsubsection{Data Cleaning}\label{data-cleaning}
+
+The first step in the data cleaning process involved checking that
+survey responses collected for each participant were only included once
+in the data set. The data cleaning process also involved filtering out
+participants' who did not provide at least three unique choices when
+considering each of the twelve lineups. These participants achieved a
+detection rate of 0. If participants had made various plot choices for
+the 12 displays they saw they were still included in the dataset.
+
+\subsubsection{Descriptive statistics}\label{descriptive-statistics}
+
+Basic descriptive statistics were used to contrast the detection rate
+for the two types of displays. Comparison was also made across the trend
+models, contrasting the mean and standard detection rate for each group,
+who had seen the different map display types for each replicate.
+
+Side-by-side dot plots were made of accuracy (efficiency) against the map
+type, faceted by trend model type.
+
+Similar plots were made of the feedback and demographic variables -
+reason for choice, reported difficulty, gender, age, education, having
+lived in Australia - against the design variables.
+
+Plots will be made in R \citep{RCore}, with the
+ \texttt{ggplot2} package \citep{ggplot2}.
+
+\subsubsection{Modelling}\label{modelling}
+
+The likelihood of detecting the data plot in the lineup can be modelled
+using a linear mixed-effects model. The R \citep{RCore}
+ \texttt{glmer()} function in the  \texttt{lme4}
+\citep{lme4} package implements generalised linear
+mixed effect models. The model used includes the two main effects map
+type and trend model, which gives the fixed effects model to be:
 
@@
 
-where \(y_{ij} = 0, 1\) is the logg odds for whether the subject detected the data plot, \(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect, \(\delta_j\) is the trend model effect.
-We are allowing for an interaction between map type and trend model as the response is binary, so a logistic model was used.
-As each participant provides results from 12 lineups, this model can account for each individual participants' abilities as it includes a subject-specific random intercept.
-
-The model specifies a logistic link, this means the predicted values from the \texttt{glmer} model should be back-transformed to fit between 0 and 1.
-The predictions \(\widehat{p}(\eta)\) are transformed to be probabilities between 0 and 1 with the link specified below:
-
-\[\widehat{p}(\eta) = \frac{e^{\eta}}{1 + e^{\eta}}\] \label{eq:transform}
-\[\eta = f(\tau_i,\delta_j)\]
-
-\hypertarget{web-application-to-collect-responses}{%
-\subsection{Web application to collect responses}\label{web-application-to-collect-responses}}
-
-The taipan {[}\protect\hyperlink{ref-taipan}{20}{]} package for R was used to create the survey web application.
-This structure was altered to collect responses regarding participants demographics and their survey responses.
-The survey app contained three tabs.
-Participants were first asked for their demographics their Figure Eight contributor ID, and their consent to the responses being used for analysis.
-The demographics collected included participants' preferred pronoun, the highest level of education achieved, their age range and whether they had lived in Australia.
-
-After submitting these responses, the survey application switched to the tab of lineups and associated questions.
-This allowed participants to easily move through the twelve displays and provide their choice, reason for their choice, and level of certainty.
-
-When participants completed the twelve evaluations the survey application triggered a data analysis script.
-This created a data set with one row per evaluation.
-Containing the responses to the three questions.
-The script also added the title of the image, which indicated the type of map display, the type of distribution hidden in the lineup, and the location of the data plot.
-It also calculated the time taken by participant to view each lineup.
-
-Each participant used the internet to access the survey.
-The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results.
-The application connected to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{21}{]} R package when participants opened the application, and interacted again when participants chose to submit the survey.
-At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-Participants were recruited from the Figure Eight crowdsourcing platform {[}\protect\hyperlink{ref-figeight}{22}{]} to evaluate lineups.
-The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
-Potential participants needed to have achieved level 2 or level 3 from prior work on the platform.
-All participants were at least 18 years old.
-
-Participants were allocated to either group A or group B when they proceeded to the survey web application.
-There were 92 participants involved in the study.
-All participants read introductory materials, and were trained using three test displays, to orient them to the evaluation task.
-All participants who completed the task were compensated \$AUD5 for their time, via the Figure Eight payment system.
-
-A pilot study was conducted in the working group of the Econometrics and Business Statistics Department of Monash University.
-This allowed us to estimate the effect size, and thus decide on number of participants to collect responses from.
-
-\hypertarget{demographic-data-collection}{%
-\subsection{Demographic data collection}\label{demographic-data-collection}}
-
-Each participant answered demographic questions and provided consent before evaluating the lineups.
+where \(y_{ij} = 0, 1\) is the log odds for whether the subject
+detected the data plot, \(\mu\) is the overall mean, \(\tau_i, i=1,2\)
+is the map type effect, \(\delta_j\) is the trend model effect. We are
+allowing for an interaction between map type and trend model as the
+response is binary, so a logistic model was used. As each participant
+provides results from 12 lineups, this model can account for each
+individual participants' abilities as it includes a subject-specific
+random intercept.
+
+The model specifies a logistic link, this means the predicted values
+from the \texttt{glmer} model should be back-transformed to fit between
+0 and 1. The predictions \(\widehat{p}(\eta)\) are transformed to be
+probabilities between 0 and 1 with the link specified below:
+
+\[\widehat{p}(\eta) = \frac{e^{\eta}}{1 + e^{\eta}}\]
+\label{eq:transform} \[\eta = f(\tau_i,\delta_j)\]
+
+\subsection{Web application to collect
+responses}\label{web-application-to-collect-responses}
+
+The  \texttt{taipan} \citep{taipan} package for R was used to
+create the survey web application. This structure was altered to collect
+responses regarding participant's demographics and their survey
+responses. The survey app contained three tabs. Participants were first
+asked for their demographics their Figure Eight contributor ID, and
+their consent to the responses being used for analysis. The demographics
+collected included participants' preferred pronouns, the highest level of
+education achieved, their age range and whether they had lived in
+Australia.
+
+After submitting these responses, the survey application switched to the
+tab of lineups and associated questions. This allowed participants to
+easily move through the twelve displays and provide their choice, reason
+for their choice, and level of certainty.
+
+When participants completed the twelve evaluations the survey
+application triggered a data analysis script. This created a data set
+with one row per evaluation, containing the responses to the three
+questions. The script also added the title of the image, which indicated
+the type of map display, the type of distribution hidden in the lineup,
+and the location of the data plot. It also calculated the time taken by
+participants to view each lineup.
+
+Each participant used the internet to access the survey. The data
+transfer from the web application to the data set took place using a
+secure link to the Google sheet used to store results. The application
+connected to the Google sheet using the  \texttt{googlesheets}
+\citep{sheets} R package when participants opened the
+application, and interacted again when participants chose to submit the
+survey. At this time it added the participant's responses to the twelve
+lineup displays as twelve rows of data in the Google sheet.
+
+\subsection{Participants}\label{participants}
+
+Participants were recruited from the Figure Eight crowdsourcing platform
+\citep{figeight} to evaluate lineups. The lineup
+protocol expects that the participants are uninvolved judges with no
+prior knowledge of the data, to avoid inadvertently affecting results.
+Potential participants needed to have achieved level 2 or level 3 from
+prior work on the platform. All participants were at least 18 years old.
+
+Participants were allocated to either group A or group B when they
+proceeded to the survey web application. There were 92 participants
+involved in the study. All participants read introductory materials and
+were trained using three test displays, to orient them to the evaluation
+task. All participants who completed the task were compensated \$AUD5
+for their time, via the Figure Eight payment system.
+
+A pilot study was conducted in the working group of the Econometrics and
+Business Statistics Department of Monash University. This allowed us to
+estimate the effect size, and thus decide on the number of participants to
+collect responses from.
+
+\subsection{Demographic data
+collection}\label{demographic-data-collection}
+
+Each participant answered demographic questions and provided consent
+before evaluating the lineups.
 
@@
 \begin{itemize}
-\tightlist
  \item
@@
 
-After completing the 12 evaluations, the participants were asked to submit their responses.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-Responses from 92 participants were collected.
-Five participants did not provide more than three unique choices for the twelve lineups, and their data was removed.
-Set A was evaluated by 42 participants, and 53 evaluated set B.
-This resulted in 1104 evaluations, corresponding to 92 subjects, each evaluating 12 lineups, that were analysed on accuracy and speed.
-The certainty and reasons of subjects in their answers is also examined.
-
-\hypertarget{participant-demographics}{%
-\subsection{Participant demographics}\label{participant-demographics}}
-
-Of the 92 participants, 67 were male, and 25 female. Most participants (56) had a Bachelors degree, 13 had a Masters degree, and the remaining 23 had high school diplomas.
-
-\hypertarget{accuracy}{%
-\subsection{Accuracy}\label{accuracy}}
-
-Fig.
-\ref{fig:detect-compare} displays the average detection rates for the two types of plot separately for each trend model.
-Each trend model was tested using four repetitions, evaluations on the same data set were seen as either choropleths or hexagon tile maps by each group as specified in Table.
-\ref{fig:exp-design}; the detection rates for each display are connected by a line segment.
-The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts.
-One replicate for the All Cities group had similar detection rates for both plot types, the rate of detection using the choropleth map was much higher than other replicates.
-Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map.
-We expected that the choropleth map would be superior for the type of spatial pattern, but the data suggests the hexagon tile map performs slightly better, or equally as well.
+After completing the 12 evaluations, the participants were asked to
+submit their responses.
+
+\section{Results}\label{results}
+
+Responses from 92 participants were collected. Five participants did not
+provide more than three unique choices for the twelve lineups, and their
+data was removed. Set A was evaluated by 42 participants, and 53
+evaluated set B. This resulted in 1104 evaluations, corresponding to 92
+subjects, each evaluating 12 lineups, that were analysed on accuracy and
+speed. The certainty and reasons of subjects in their answers are also
+examined.
+
+\subsection{Participant demographics}\label{participant-demographics}
+
+Of the 92 participants, 67 were male, and 25 female. Most participants
+(56) had a Bachelors degree, 13 had a Masters degree, and the remaining
+23 had high school diplomas.
+
+\subsection{Accuracy}\label{accuracy}
+
+Fig. \ref{fig:detect-compare} displays the average detection rates for
+the two types of plot separately for each trend model. Each trend model
+was tested using four repetitions, evaluations on the same data set were
+seen as either choropleths or hexagon tile maps by each group as
+specified in Table. \ref{fig:exp-design}; the detection rates for each
+display are connected by a line segment. The Three Cities and All Cities
+trend models shown in the hexagon tile map allowed viewers to detect the
+data plot substantially more often than the choropleth counterparts. One
+replicate for the All Cities group had similar detection rates for both
+plot types, the rate of detection using the choropleth map was much
+higher than other replicates. Surprisingly, participants could also
+detect the gradual spatial trend in the NW-SE group from the hexagon
+tile map. We expected that the choropleth map would be superior for the
+type of spatial pattern, but the data suggests the hexagon tile map
+performs slightly better, or equally as well.
 
@@
 Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup.
-The points for the same data set shown in a choroleth or hexagon tile map display are linked to show the difference in the detection rate.}\label{fig:detect-compare}
+The points for the same data set shown in a choropleth or hexagon tile map display are linked to show the difference in the detection rate.}\label{fig:detect-compare}
 \end{figure}
 
-Table.
-\ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
-This also gives the standard deviations, the smallest standard deviation for all sets of replicates was the Three Cities trend model shown in a Choropleth display.
-This group of displays had a very small detection rate of 0.04.
-The mean detection rate for the Three Cities trend model shown as choropleth map lineups was also the smallest at 0.40.
-The North-West to South-East (NW-SE) trend model unexpectedly had a higher mean detection rate for the hexagon tile map displays, but the difference in the means of detection rate was only 0.10.
+Table. \ref{tab:desc-stats} shows the means and standard deviations of
+the detection rate for each type of plot and each trend model. This also
+gives the standard deviations, the smallest standard deviation for all
+sets of replicates was the Three Cities trend model shown in a
+Choropleth display. This group of displays had a very small detection
+rate of 0.04. The mean detection rate for the Three Cities trend model
+shown as choropleth map lineups was also the smallest at 0.40. The
+North-West to South-East (NW-SE) trend model unexpectedly had a higher
+mean detection rate for the hexagon tile map displays, but the
+difference in the means of detection rate was only 0.10.
 
@@
 
-Table.
-\ref{tab:detect-glmer1} presents a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on the detection rate.
-The results support the summary from Fig.
-\ref{fig:detect-compare} and all parameters are statistically significant despite the large standard deviations observed in Table.
-\ref{tab:desc-stats}.
-Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
-Allowing for the interaction effect, the difference in detection rate decreases for population related displays for a choropleth map lineup, but increases for a hexagon tile map display.
-The log odds of detection show in Table. \ref{tab:detect-glmer1} can be back transformed after taking the sum of all terms for the trend and type of display that are of interest.
-For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to 0.63 from 0.52 for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
-
-When a choropleth map display is used, the predicted detection rate for the Three Cities trend, 0.03; this is extremely low, especially compared to the NW-SE trend of 0.52.
-When the All Cities trend is presented in a choropleth display the predicted probability of detection is 0.22.
-The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend 0.39 and All Cities trend 0.59.
+Table. \ref{tab:detect-glmer1} presents a summary of the generalised
+linear mixed effects model, testing the effect of plot type and trend
+model on the detection rate. The results support the summary from Fig.
+\ref{fig:detect-compare} and all parameters are statistically
+significant despite the large standard deviations observed in Table.
+\ref{tab:desc-stats}. Overall, the hexagon tile map performs marginally
+better than the choropleth for all trend models, which is a pleasant
+surprise. Allowing for the interaction effect, the difference in
+detection rate decreases for population-related displays for a
+choropleth map lineup but increases for a hexagon tile map display. The
+log odds of detection shown in Table. \ref{tab:detect-glmer1} can be back-transformed after taking the sum of all terms for the trend and type of
+display that are of interest. For the NW-SE distribution, the predicted
+detection rate for the hexagon tile map display increases the predicted
+probability of detection to 0.63 from 0.52 for choropleths, this is
+almost exactly the difference seen in the table of means and is
+significant only at the 0.05 level.
+
+When a choropleth map display is used, the predicted detection rate for
+the Three Cities trend, 0.03; this is extremely low, especially compared
+to the NW-SE trend of 0.52. When the All Cities trend is presented in a
+choropleth display the predicted probability of detection is 0.22. The
+hexagon tile map has a substantially high detection rate for the display
+of a Three Cities trend 0.39 and All Cities trend 0.59.
 
@@
 
-\hypertarget{speed}{%
-\subsection{Speed}\label{speed}}
-
-Fig.
-\ref{fig:beeswarm} shows horizontally jittered dot plots to contrast the time taken by participants to evaluate each lineup when viewing each type of display.
-The time are also separated by trend model and whether the data plot was detected or not detected.
-The time taken to complete an evaluation ranged from milliseconds to 60 seconds.
-The average time taken for type of display is shown as a large colored dot on each plot.
-when considering the heights of the green and orange dots, there is little difference in the average time taken to read a choropleth or hexagon tile map.
-Comparing the same colored dot across each trend model row, there is a slight increase in the time taken to correctly detected the data plot in the hexagon tile map lineup, but little difference in evaluation time for the choropleth display.
-However, there were substantially less correct detections for choropleth lineups for the Three cities and All Cities trends.
+\subsection{Speed}\label{speed}
+
+Fig. \ref{fig:beeswarm} shows horizontally jittered dot plots to
+contrast the time taken by participants to evaluate each lineup when
+viewing each type of display. The time is also separated by the trend model
+and whether the data plot was detected or not detected. The time taken
+to complete an evaluation ranged from milliseconds to 60 seconds. The
+average time taken for each type of display is shown as a large coloured dot
+on each plot. when considering the heights of the green and orange dots,
+there is little difference in the average time taken to read a
+choropleth or hexagon tile map. Comparing the same coloured dot across
+each trend model row, there is a slight increase in the time taken to
+correctly detect the data plot in the hexagon tile map lineup, but
+little difference in evaluation time for the choropleth display.
+However, there were substantially fewer correct detections for choropleth
+lineups for the Three cities and All Cities trends.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/beeswarm-1} \caption{The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots.
-The colored point indicates average time taken for each plot type.
-Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between plot types.}\label{fig:beeswarm}
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/beeswarm-1} \caption{The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dot plots.
+The coloured point indicates the average time taken for each plot type.
+Although some participants take just a few seconds per evaluation, and some take as much as 60 seconds, there is very little difference in time taken between plot types.}\label{fig:beeswarm}
 \end{figure}
 
-\hypertarget{certainty}{%
-\subsection{Certainty}\label{certainty}}
-
-Participants provided their level of certainty regarding their choice using a five point scale.
-Unlike the accuracy and speed of responses that were derived during the data processing phase, this was a subjective
-assessment by the participant prompted by the question: `How certain are you about your choice?'.
-Fig.
-\ref{fig:certainty} shows the amount of times participants provided each level of certainty.
-This was separated for each combination of trend models and display type, and colored depending on whether a participant correctly detected the data plot in the lineup.
-Participants often chose 4 or 5 when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
-This shows overconfidence in their detection ability when using a choropleth map display.
-Participants were less likely to be certain when their choice was incorrect and they were viewing a hexagon tile map.
-For each trend model, participants were more likely to doubt their choice and choose 1 or 2 in the hexagon tile map displays, even though many had made the correct choice.
+\subsection{Certainty}\label{certainty}
+
+Participants provided their level of certainty regarding their choice
+using a five-point scale. Unlike the accuracy and speed of responses
+that were derived during the data processing phase, this was a
+subjective assessment by the participant prompted by the question: `How
+certain are you about your choice?'. Fig. \ref{fig:certainty} shows the
+number of times participants provided each level of certainty. This was
+separated for each combination of trend models and display type, and
+colored depending on whether a participant correctly detected the data
+plot in the lineup. Participants often chose 4 or 5 when viewing the
+population-related trends in the choropleth display, even though they
+were often incorrect when viewing an All Cities trend and overwhelmingly
+incorrect for the Three Cities trend. This shows overconfidence in their
+detection ability when using a choropleth map display. Participants were
+less likely to be certain when their choice was incorrect and they were
+viewing a hexagon tile map. For each trend model, participants were more
+likely to doubt their choice and choose 1 or 2 in the hexagon tile map
+displays, even though many had made the correct choice.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/certainty-1} \caption{The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/certainty-1} \caption{The number of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
 Participants were more likely to choose a high certainty when considering a Choropleth map.
@@
 
-\hypertarget{reason}{%
-\subsection{Reason}\label{reason}}
-
-Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons.
-``Color trend across the areas'' was the most common selection for NW-SE trend displays.
-
-The reasons chosen by participants from the list provided to them varied more when viewing choropleth displays than the hexagon tile map.
-The hexagon tile map displays resulted in ``Clusters of color'' as the most common choice made by participants.
-
-The choice ``None of these reasons'' was used as the default value to minimise noise from participants who did not select a response.
+\subsection{Reason}\label{reason}
+
+Participants were asked why they had made their plot choice and were
+able to select from a set of suggested reasons. ``Color trend across the
+areas'' was the most common selection for NW-SE trend displays.
+
+The reasons chosen by participants from the list provided to them varied
+more when viewing choropleth displays than the hexagon tile map. The
+hexagon tile map displays resulted in ``Clusters of colour'' as the most
+common choice made by participants.
+
+The choice ``None of these reasons'' was used as the default value to
+minimise noise from participants who did not select a response.
 
@@
 
-\caption{\label{tab:reason}The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
+\caption{\label{tab:reason}The number of participants that selected each reason for their choice of plot when looking at each trend model shown in choropleth and hexagon tile maps.
 The facets show whether or not the choice was correct.}
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-The intention of this study was to contrast the use of the choropleth map and the hexagon tile map.
-The visual inference lineup protocol was employed to contrast the effectiveness of the displays.
-The results have shown that overall the use of the hexagon tile map display allows participants to find the data plot in the lineup more often.
-Using the visual inference protocol this result can be extended to show that it is a valid alternative display to communicate spatial distributions of population related data.
-
-We expected that the choropleth map would be superior for communicating the spatial pattern of geographic distributions.
-The data suggest that the participants perform slightly better or equally as well for each replicate in each trend model across the two displays.
-Table II shows that the difference in the mean detection rate for the two trend models was 0.10.
-
-The differences seen in the \ref{fig:detect-compare} plot and Table.
-\ref{tab:desc-stats} are reflected in the model results.
-Surprisingly the difference for the geographic distribution was significant at the 0.05 level.
-It also showed that the hexagon tile map display performs marginally better than the choropleth for all trend models.
-Unexpectedly the detection rate suffers when using a choropleth map to display population related distributions.
-
-While the significance of the difference in detection was the key focus of this experiment, the secondary focus was the time taken by participants.
-it was expected that the participants may take longer to consider the hexagon tile map distribution but would be able to detect the data plot in the lineup.
-The bimodal distributions seen in Fig.
-\ref{fig:beeswarm} showed very little difference in the mean evaluation times.
-As the maximum time of all of the distributions approached 60 seconds it cannot be said that the participants' took longer to evaluate the hexagon tile map displays.
-
-The responses to the questions asked of participants included the reason for their choice and the certainty around their choice.
-Fig.
-\ref{tab:reason} shows high levels of certainty of 4 and 5 were chosen by participants when looking at the population distributions in a choropleth map display show that they were over confident when attempting to find the real data plot in the choropleth map displays.
-Participants performed better on the NW-SE distribution shown in the choropleth display and were reasonably confident about their decisions.
-The high levels of the mid range value of 3 could indicate that the participant did not want to provide a response, as this was the default value.
-Those who chose level 4 or 5 were equally likely to be correct for the three cities lineups, but more likely to be correct than incorrect for the other two trend models.
-
-The color scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
-Due to the consistent coloring of rural areas in a choropleth display, the choice ``All areas have similar colors'' was most common reason for a participants choice.
-The All Cities displays colored the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural color consistency.
-Choosing ``Clusters of colour'' was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions.
-It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays.
-Due to the spatial covariance introduced in the smoothing, groups of similarly colored hexagons were present in all of the hexagon tile map displays.
-All Cities and Three Cities distributions of real data trends had distinctly different patterns or red inner-city areas, while some of the plots in each lineup may have shared similar features.
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-The choropleth map display and the tessellated hexagon tile map have been contrasted using the lineup protocol.
-The hexagon tile map was significantly more effective for spotting a real population related data trend model hidden in a lineup.
-
-The hexagon tile map display should be considered as an alternative visualization method when communicating distributions that relate to the population across a set of geographic units.
-As an additional display to the familiar choropleth map, cancer atlas products may benefit from the opportunity to allow exploration via an alternative display.
-The spatial distributions used to test these displays were inspired by the real spatially smoothed estimates of the cancer burden on Australian communities.
-However, this technique may be extended to other population related distributions, such as other diseases.
-
-The increasing population densities of capital cities despite large land area exacerbates the difference in the smallest and largest communities.
-The population density structure of Australia can be considered similar to that of Canada, New Zealand and many other countries.
-Therefore, this display is not only relevant to Australia, but all nations or population distributions that experience densely populated cities separated by vast rural expanses.
-
-\hypertarget{acknowledgment}{%
-\section{Acknowledgment}\label{acknowledgment}}
-
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments.
-Mitchell O'Hara-Wild was a co-developer of the taipan {[}\protect\hyperlink{ref-taipan}{20}{]} R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
-We are thankful for the NUMBATs (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.
-
-The source code to produce this document can be found on \href{https://github.com/srkobakian/experiment/tree/master/paper}{GitHub}.
-Supplementary materials have been included to discuss the survey procedures and the lineups that were used.
-The full set of images can also be found at: https://github.com/srkobakian/experiment/tree/master/figures/final.
+\section{Discussion}\label{discussion}
+
+The intention of this study was to contrast the use of the choropleth
+map and the hexagon tile map. The visual inference lineup protocol was
+employed to contrast the effectiveness of the displays. The results have
+shown that overall the use of the hexagon tile map display allows
+participants to find the data plot in the lineup more often. Using the
+visual inference protocol this result can be extended to show that it is
+a valid alternative display to communicate spatial distributions of
+population related data.
+
+We expected that the choropleth map would be superior for communicating
+the spatial pattern of geographic distributions. The data suggest that
+the participants perform slightly better or equally as well for each
+replicate in each trend model across the two displays. Table II shows
+that the difference in the mean detection rate for the two trend models
+was 0.10.
+
+The differences are seen in the \ref{fig:detect-compare} plot and Table.
+\ref{tab:desc-stats} are reflected in the model results. Surprisingly
+the difference in the geographic distribution was significant at the
+0.05 level. It also showed that the hexagon tile map display performs
+marginally better than the choropleth for all trend models. Unexpectedly
+the detection rate suffers when using a choropleth map to display
+population-related distributions.
+
+While the significance of the difference in detection was the key focus
+of this experiment, the secondary focus was the time taken by
+participants. it was expected that the participants might take longer to
+consider the hexagon tile map distribution but would be able to detect
+the data plot in the lineup. The bimodal distributions seen in Fig.
+\ref{fig:beeswarm} showed very little difference in the mean evaluation
+times. As the maximum time of all of the distributions approached 60
+seconds it cannot be said that the participants took longer to evaluate
+the hexagon tile map displays.
+
+The responses to the questions asked of participants included the reason
+for their choice and the certainty around their choice. Fig.
+\ref{tab:reason} shows high levels of certainty of 4 and 5 were chosen
+by participants when looking at the population distributions in a
+choropleth map display showing that they were overconfident when
+attempting to find the real data plot in the choropleth map displays.
+Participants performed better on the NW-SE distribution shown in the
+choropleth display and were reasonably confident about their decisions.
+The high levels of the mid-range value of 3 could indicate that the
+participant did not want to provide a response, as this was the default
+value. Those who chose level 4 or 5 were equally likely to be correct
+for the three cities lineups, but more likely to be correct than
+incorrect for the other two trend models.
+
+The colour scaling applied in Three cities and All cities displays
+resulted in the rural areas of the real data plot appearing more blue or
+yellow than the other plots in the lineups. Due to the consistent
+colouring of rural areas in a choropleth display, the choice ``All areas
+have similar colours'' was the most common reason for a participant's choice.
+The All Cities displays coloured the inner-city areas of all capital
+cities redder, this was observable to participants and explains the
+equal choice of the city clusters or rural colour consistency. Choosing
+``Clusters of colour'' was expected when participants viewed the Hexagon
+tile map display of the All Cities and Three Cities distributions. It
+was unexpected that it was also the most common reason for the NW-SE
+hexagon tile map displays. Due to the spatial covariance introduced in
+the smoothing, groups of similarly coloured hexagons were present in all
+of the hexagon tile map displays. All Cities and Three Cities
+distributions of real data trends had distinctly different patterns or
+red inner-city areas, while some of the plots in each lineup may have
+shared similar features.
+
+\section{Conclusion}\label{conclusion}
+
+The choropleth map display and the tessellated hexagon tile map have
+been contrasted using the lineup protocol. The hexagon tile map was
+significantly more effective for spotting a real population-related data
+trend model hidden in a lineup.
+
+The hexagon tile map display should be considered as an alternative
+visualization method when communicating distributions that relate to the
+population across a set of geographic units. As an additional display to
+the familiar choropleth map, cancer atlas products may benefit from the
+opportunity to allow exploration via an alternative display. The spatial
+distributions used to test these displays were inspired by the real
+spatially smoothed estimates of the cancer burden on Australian
+communities. However, this technique may be extended to other population-related distributions, such as other diseases.
+
+The increasing population densities of capital cities despite large land
+area exacerbates the difference between the smallest and largest communities.
+The population density structure of Australia can be considered similar
+to that of Canada, New Zealand and many other countries. Therefore, this
+display is not only relevant to Australia but all nations or population
+distributions that experience densely populated cities separated by vast
+rural expanses.
+
+\section{Acknowledgment}\label{acknowledgment}
+
+The authors would like to thank the Australian Cancer Atlas team for
+discussions regarding alternative spatial visualizations, and Professor
+Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with
+suggestions and comments. Mitchell O'Hara-Wild was a co-developer of the
+ \texttt{taipan} \citep{taipan} R package for image tagging, used
+as the base for the web app constructed to collect participant
+evaluations of lineups. We are thankful for the NUMBATs (Non-Uniform
+Monash Business Analytics Team) for participating in the pilot study
+that helped to assess the experimental design and determine an
+appropriate sample size for the study.
+
+The source code to produce this document can be found on
+\href{https://github.com/srkobakian/experiment/paper}{GitHub}.
+Supplementary materials have been included to discuss the survey
+procedures and the lineups that were used. The full set of images can be
+found here, too.
 
@@
 \item
-  12 data sets used to construct the lineups
+  12 data sets were used to construct the lineups
 \end{itemize}
 
-The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{18}{]} with the use of the following packages:
+The analysis of the work was completed in R
+\citep{RCore} with the use of the following packages:
 
 \begin{itemize}
-\tightlist
-\item
-  For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{23}{]}, rticles {[}\protect\hyperlink{ref-rticles}{24}{]}, knitr {[}\protect\hyperlink{ref-knitr}{25}{]}.
-\item
-  For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{26}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{27}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{28}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{29}{]}.
-\item
-  For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{30}{]}, png {[}\protect\hyperlink{ref-png}{31}{]}, grid {[}\protect\hyperlink{ref-grid}{32}{]}.
-\item
-  For modelling and presentation of models: gstat {[}\protect\hyperlink{ref-gstat}{17}{]}, lme4 {[}\protect\hyperlink{ref-lme4}{19}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{33}{]}.
+ \item
+  For document creation:  \texttt{rmarkdown} \citep{rmarkdown},
+   \texttt{knitr}
+  \citep{knitr}.
+\item
+  For lineup creation and data analysis:  \texttt{tidyverse}
+  \citep{tidyverse},  \texttt{nullabor}
+  \citep{nullabor},  \texttt{ggthemes}
+  \citep{ggthemes},  \texttt{RColorBrewer}
+ \citep{RColorBrewer}.
+\item
+  For image displays:  \texttt{cowplot} \citep{cowplot},  \texttt{png}
+  \citep{png},  \texttt{grid }\citep{grid}.
+\item
+  For modelling and presentation of models:  \texttt{gstat}
+ \citep{gstat},  \texttt{lme4} \citep{lme4},
+   \texttt{kableExtra} \citep{kableExtra}.
 \end{itemize}
 
-Ethics approval for the online survey was granted by QUT's Ethics Committee (Ethics Application Number: 1900000991).
-All applicants provided informed consent in line with QUT regulations prior to participating in this research.
-
-\newpage
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\leavevmode\hypertarget{ref-sugarbag}{}%
-1. Kobakian S, Cook D (2019) Sugarbag: Create tessellated hexagon maps.
-
-\leavevmode\hypertarget{ref-atlas}{}%
-2. Cancer Council Queensland Australian Cancer Atlas (https://atlas.cancer.org.au).
-
-\leavevmode\hypertarget{ref-GIIV}{}%
-3. Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979
-
-\leavevmode\hypertarget{ref-EI}{}%
-4. Tufte ER (1990) Envisioning Information. Graphics Press
-
-\leavevmode\hypertarget{ref-BCM}{}%
-5.
-Skowronnek A (2016) Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata.
-In: Infovis Reading Group WS 2015/16.
-\url{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}.
-
-\leavevmode\hypertarget{ref-CBATCC}{}%
-6. Kocmoud C, House D (1998) A Constraint-based Approach to Constructing Continuous Cartograms. In: Proc. Symp. Spatial data handling. pp 236--246
-
-\leavevmode\hypertarget{ref-ACTUC}{}%
-7. Dorling D (2011) Area Cartograms: Their Use and Creation. In: Concepts and techniques in modern geography (catmog). pp 252--260
-
-\leavevmode\hypertarget{ref-NAC}{}%
-8. Olson JM (1976) Noncontiguous Area Cartograms. The Professional Geographer 28:371--380
-
-\leavevmode\hypertarget{ref-RSCW}{}%
-9. Raisz E (1963) Rectangular Statistical Cartograms of the World. Journal of Geography 35:8--10
-
-\leavevmode\hypertarget{ref-CDWCS}{}%
-10. Monmonier M (2005) Cartography: Distortions, World-views and Creative Solutions. Progress in Human Geography 29:217--224
-
-\leavevmode\hypertarget{ref-review}{}%
-11. (2019) Cancer applications of choropleth maps, and the potential of cartograms and alternative map displays. Manuscript submitted for publication.
-
-\leavevmode\hypertarget{ref-BCHLLSW09}{}%
-12.
-Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) Statistical inference for exploratory data analysis and model diagnostics.
-Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383
-
-\leavevmode\hypertarget{ref-GTPCCD}{}%
-13. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448
-
-\leavevmode\hypertarget{ref-ggplot2}{}%
-14. Wickham H (2009) Ggplot2: Elegant graphics for data analysis. Springer New York
-
-\leavevmode\hypertarget{ref-abs2016}{}%
-15. (2018) Australian Statistical Geography Standard (ASGS). Australian Bureau of Statistics
-
-\leavevmode\hypertarget{ref-POG}{}%
-16. Matheron G (1963) Principles of geostatistics. Economic Geology 58:1246--1266
-
-\leavevmode\hypertarget{ref-gstat}{}%
-17. Gräler B, Pebesma E, Heuvelink G (2016) Spatio-temporal interpolation using gstat. The R Journal 8:204--218
-
-\leavevmode\hypertarget{ref-RCore}{}%
-18. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
-
-\leavevmode\hypertarget{ref-lme4}{}%
-19. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48
-
-\leavevmode\hypertarget{ref-taipan}{}%
-20. Kobakian S, O'Hara-Wild M (2018) Taipan: Tool for annotating images in preparation for analysis.
-
-\leavevmode\hypertarget{ref-sheets}{}%
-21. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.
-
-\leavevmode\hypertarget{ref-figeight}{}%
-22. (2019) The essential high-quality data annotation platform. Figure Eight
-
-\leavevmode\hypertarget{ref-rmarkdown}{}%
-23. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida
-
-\leavevmode\hypertarget{ref-rticles}{}%
-24. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.
-
-\leavevmode\hypertarget{ref-knitr}{}%
-25. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research
-
-\leavevmode\hypertarget{ref-tidyverse}{}%
-26. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686
-
-\leavevmode\hypertarget{ref-nullabor}{}%
-27. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.
-
-\leavevmode\hypertarget{ref-ggthemes}{}%
-28. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.
-
-\leavevmode\hypertarget{ref-RColorBrewer}{}%
-29. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.
-
-\leavevmode\hypertarget{ref-cowplot}{}%
-30. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.
-
-\leavevmode\hypertarget{ref-png}{}%
-31. Urbanek S (2013) Png: Read and write png images.
-
-\leavevmode\hypertarget{ref-grid}{}%
-32. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria
-
-\leavevmode\hypertarget{ref-kableExtra}{}%
-33. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
+Ethics approval for the online survey was granted by QUT's Ethics
+Committee (Ethics Application Number: 1900000991). All applicants
+provided informed consent in line with QUT regulations prior to
+participating in this research.
+
+\bibliographystyle{anzsj}
+\bibliography{paper.bib}
 

### 2024-11-05 paper/vgtc/paper-vgtc.Rmd
paper reformatted for ANZSJ

--- 2023-03-21 paper/paper.Rmd
@@
       location: Brisbane, Australia
-      email: stephanie.kobakian@qut.edu.au
+      email: stephanie.kobakian@gmail.com
       mark: 1
@@
 Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to do well, and two with differing level of inner city hot spots.
-These latter two reflect the structure seen in the thyroid cancer data (Fig.
-\ref{fig:thyroid}).
+These latter two reflect the structure seen in the thyroid cancer data (Figures \ref{fig:thyroid-choro}, \ref{fig:thyroid-hex}).
 This produces six treatment levels:
@@
 
-This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the thyroid cancer distribution (Fig. \ref{fig:thyroid}).
+This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the thyroid cancer distribution (Figures \ref{fig:thyroid-choro}, \ref{fig:thyroid-hex}).
 

### 2024-11-05 paper/vgtc/paper_vgtc.tex
paper reformatted for ANZSJ

--- 2023-03-21 paper/paper_vgtc.tex
@@
 \centering
-\includegraphics[width=0.9\linewidth]{paper_files/figure-latex/lineup-1} \caption{An example of the lineups shown to participants.
+\includegraphics[width=0.98\linewidth]{paper_files/figure-latex/lineup-1} \caption{An example of the lineups shown to participants.
 This lineup of twelve hexagon tile map displays contains one map with a simulated population-related structure and the remainder are null plots that contain only spatial correlation between neighbors.
@@
 \centering 
-  \includegraphics[width=0.9\linewidth]{figures/factors.pdf} 
+  \includegraphics[width=0.98\linewidth]{figures/factors.pdf} 
 \caption{The three trend models, displayed as a hexagon tile map.
@@
 
+\begin{figure}
+\includegraphics[width=1\linewidth]{paper_files/figure-latex/certainty-1} \caption{The number of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
+Participants were more likely to choose a high certainty when considering a Choropleth map.
+The mid value of 3 was the default certainty, it was chosen mostly for the Hexagon tile map displays.}\label{fig:certainty}
+\end{figure}
+
 \hypertarget{certainty}{%
@@
 Fig.
-\ref{fig:certainty} shows the number of times participants provided each level of certainty.
-This was separated for each combination of trend models and display type, and colored depending on whether a participant correctly detected the data plot in the lineup.
-Participants often chose 4 or 5 when viewing the population-related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
-This shows overconfidence in their detection ability when using a choropleth map display.
-Participants were less likely to be certain when their choice was incorrect and they were viewing a hexagon tile map.
+\ref{fig:certainty} shows a bar chart of the participants' reported certainty, faceted by trend model and display type.
+Color indicates whether the data was detected or not.
+Participants often chose 4 or 5 (highly certain) more often for choropleth than the hexagon tile map, indicating that they were more certain they had the correct answer.
+This was especially strong with the All Cities and Three Cities trends.
+What is interesting is that they were more often wrong in their answer!
+This suggests that there is overconfidence in their detection ability when using a choropleth map.
+%Participants were less likely to be certain when their choice was incorrect and they were viewing a hexagon tile map.
 For each trend model, participants were more likely to doubt their choice and choose 1 or 2 in the hexagon tile map displays, even though many had made the correct choice.
-
-\begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/certainty-1} \caption{The number of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
-Participants were more likely to choose a high certainty when considering a Choropleth map.
-The mid value of 3 was the default certainty, it was chosen most for the Hexagon tile map displays.}\label{fig:certainty}
-\end{figure}
-
-\hypertarget{reason}{%
-\subsection{Reason}\label{reason}}
-
-Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons.
-``Color trend across the areas'' was the most common selection for NW-SE trend displays.
-
-The reasons chosen by participants from the list provided to them varied more when viewing choropleth displays than the hexagon tile map.
-The hexagon tile map displays resulted in ``Clusters of color'' as the most common choice made by participants.
-
-The choice ``None of these reasons'' was used as the default value to minimize noise from participants who did not select a response.
 
@@
 
+\hypertarget{reason}{%
+\subsection{Reason}\label{reason}}
+
+To understand how participants made their decisions they were asked to select from a fixed set of reasons for choosing a plot: "None of these reasons" (default), "Clusters of colour", "Colour trend across the areas", "Big differences between neighbours" or "All areas have similar colours".
+Table \ref{tab:reason} shows the top reason for the different trend models, whether the data plot was detected or not, and the two displays.
+
+Interestingly, regardless of the spatial trend model, or whether the data plot was detected, the most common reason for the hexagon tile map was "Clusters of colour".
+It is a bit surprising that "Colour trend across the areas" was not the top reason for the NW-SE model.
+
+For the choropleth map the reason for choosing varied substantially.
+For the NW-SE model, whether the data plot was detected or not, participants' top reason was "Colour trend across the areas", which is as expected.
+However, very interestingly, this was also the top reason given when the data plot was NOT detected for "All cities" and "Three cities".
+This suggests that the participants did not find the data because they were looking for the wrong pattern, perhaps people are pre-conditioned to read choropleths only in one way to the extent of missing other strong patterns.
+"Clusters of colour" was the top choice when participants detected the data plot in the "All Cities" pattern.
+It is also informative to see that ``All areas have similar colours'' was the top reason when participants detected the data plot in "All Cities" and "Three cities".
+It actually makes sense, because the color scaling applied in these models resulted in the rural areas of the data plot appearing more blue or yellow than the null plots in each lineup.
+
+%``Color trend across the areas'' was the most common selection for NW-SE trend displays.
+
+%The reasons chosen by participants from the list provided to them varied more when viewing choropleth displays than the hexagon tile map.The hexagon tile map displays resulted in ``Clusters of color'' as the most common choice made by participants.
+
+%The choice ``None of these reasons'' was used as the default value to minimize noise from participants who did not select a response.
+
 \hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\section{Conclusions}\label{discussion}}
 
@@
 
-Our initial expectation was that the hexagon tile map would be superior to the choropleth map for the two inner city hotspots pattern (All Cities, Three Cities), but that the choropleth would outperform the hexagon tile map for conveying a spatial dependence trend pattern across geography (NW-SE).
+Our initial expectation was that the hexagon tile map would be superior to the choropleth map for the two inner city hotspot patterns (All Cities, Three Cities), but that the choropleth would outperform the hexagon tile map for conveying a spatial dependence trend pattern across geography (NW-SE).
 We surprisingly found that the hexagon tile map was more effective in all three trend models.
@@
 
-While the significance of the difference in detection was the primary focus of this experiment, a secondary focus was the time taken by participants.
-It was expected that the participants may take longer to consider the hexagon tile map distribution but would be able to detect the data plot in the lineup.
-The bimodal distributions seen in Fig.
-\ref{fig:beeswarm} showed very little difference in the mean evaluation times.
-As the maximum time of all of the distributions approached 60 seconds it cannot be said that the participants took longer to evaluate the hexagon tile map displays.
+While detection was the primary focus of this experiment, a secondary focus was the time taken by participants.
+It was expected that the participants may take longer to evaluate the hexagon tile maps.
+Fig.
+\ref{fig:beeswarm} shows that this was not the case, because there is little difference in the mean evaluation times.
+The distribution of evaluation times is similar for both choropleths and hexagon tile maps.
 
-The responses to the questions asked of participants included the reason for their choice and the certainty around their choice.
-Fig.
+Some interesting behavior is revealed from the participants' responses for reason and certainty in their choices of plots.
+People were more confident in their choices when viewing the choropleth maps, but they were more often wrong.
+The reasons given for plot choices suggest that people may be misled by choropleth maps by tending to focus on spatial trends at the risk of failing to detect the clustering patterns.
+
+In summary, the hexagon tile map display should be considered an effective alternative visualization method when communicating distributions that relate to the population across a set of geographic units.
+Cancer atlas products may benefit from the inclusion of this type of display to more accurately report the incidence.
+Although the spatial distributions used to test these displays were inspired by the real spatially smoothed estimates of the cancer burden on Australian communities, the results likely extend to other population-related distributions and other diseases or statistics.
+This new display is especially valuable for countries like Australia that have huge sparsely populated areas.
+
+%The responses to the questions asked of participants included the reason for their choice and the certainty around their choice.Fig.
 \ref{fig:certainty} shows high levels of certainty of 4 and 5 were chosen by participants when looking at the population distributions in a choropleth map display showing that they were overconfident when attempting to find the real data plot in the choropleth map displays.
-Participants performed better on the NW-SE distribution shown in the choropleth display and were reasonably confident about their decisions.
-The high levels of the mid-range value of 3 could indicate that the participant did not want to provide a response, as this was the default value.
+Participants performed better on the NW-SE distribution shown in the choropleth display and were reasonably confident about their decisions.The high levels of the mid-range value of 3 could indicate that the participant did not want to provide a response, as this was the default value.
 Those who chose level 4 or 5 were equally likely to be correct for the three cities lineups, but more likely to be correct than incorrect for the other two trend models.
 
-The color scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
+%The color scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
 Due to the consistent coloring of rural areas in a choropleth display, the choice ``All areas have similar colors'' was the most common reason for a participant's choice.
@@
 
+The analysis of the work was completed in R  \cite{RCore} with the use of the following packages:
+
+\begin{itemize} \itemsep 0in
+%tightlist
+\item
+  For document creation: \texttt{rmarkdown}~\cite{rmarkdown}, \texttt{rticles}~\cite{rticles}, \texttt{knitr}~\cite{knitr}.
+\item
+  For lineup creation and data analysis: \texttt{tidyverse}~\cite{tidyverse}, \texttt{nullabor}~\cite{nullabor}, \texttt{ggthemes}~\cite{ggthemes}, \texttt{RColorBrewer}~\cite{RColorBrewer}.
+\item
+  For image displays: \texttt{cowplot}~\cite{cowplot}, \texttt{png}~\cite{png}, \texttt{grid}~\cite{grid}.
+\item
+  For modelling and presentation of models: \texttt{gstat}~\cite{gstat}, \texttt{lme4}~\cite{lme4}, \texttt{kableExtra}~\cite{kableExtra}.
+\end{itemize}
+
+Ethics approval for the online survey was granted by QUT's Ethics Committee (Ethics Application Number: 1900000991).
+All applicants provided informed consent in line with QUT regulations prior to participating in this research.
+
+\hypertarget{supplementary}{%
+\section{Supplementary Materialst}\label{supplementary}}
+
 The source code to produce this document can be found at \url{https://github.com/srkobakian/experiment/paper}.
@@
 
-The analysis of the work was completed in R  \cite{RCore} with the use of the following packages:
-
-\begin{itemize} \itemsep 0in
-%tightlist
-\item
-  For document creation: \texttt{rmarkdown}~\cite{rmarkdown}, \texttt{rticles}~\cite{rticles}, \texttt{knitr}~\cite{knitr}.
-\item
-  For lineup creation and data analysis: \texttt{tidyverse}~\cite{tidyverse}, \texttt{nullabor}~\cite{nullabor}, \texttt{ggthemes}~\cite{ggthemes}, \texttt{RColorBrewer}~\cite{RColorBrewer}.
-\item
-  For image displays: \texttt{cowplot}~\cite{cowplot}, \texttt{png}~\cite{png}, \texttt{grid}~\cite{grid}.
-\item
-  For modelling and presentation of models: \texttt{gstat}~\cite{gstat}, \texttt{lme4}~\cite{lme4}, \texttt{kableExtra}~\cite{kableExtra}.
-\end{itemize}
-
-Ethics approval for the online survey was granted by QUT's Ethics Committee (Ethics Application Number: 1900000991).
-All applicants provided informed consent in line with QUT regulations prior to participating in this research.
-
 \bibliographystyle{abbrv-doi-hyperref}

### 2024-11-06 paper/paper-anzsj.tex
shifted tables and made fig 1 into a single image

@@
 of the distribution derived by map users. The hexagon tile map is
-presented as an alternative display for effectively visualizing population related
+presented as an alternative display for effectively visualizing population-related
 distributions. Visual inference is used to measure the power
@@
 {\centering 
-\includegraphics[width=0.46\linewidth]{paper_files/figure-latex/thyroid-choro-1} 
-\includegraphics[width=0.54\linewidth]{paper_files/figure-latex/thyroid-hex-1} 
+%\includegraphics[width=0.46\linewidth]{paper_files/figure-latex/thyroid-choro-1} 
+%\includegraphics[width=0.54\linewidth]{paper_files/figure-latex/thyroid-hex-1} 
+\includegraphics[width=\linewidth]{figures/thyroid.pdf}
 }
@@
 settled, with the population densely clustered into the narrow coastal
-strips. Fig. \ref{fig:thyroid} shows the choropleth map of thyroid
+strips. Figure \ref{fig:thyroid} shows the choropleth map of thyroid
 cancer rates in Australia. The choropleth map focuses attention on the
@@
 locations or regions in remote areas. The algorithm is available in the
-R package,  \texttt{sugarbag} \citep{sugarbag}. Fig.
+R package,  \texttt{sugarbag} \citep{sugarbag}. Figure
 \ref{fig:thyroid} shows the hexagon tile map. Colour maps from
@@
 With \(K\) observers, the probability of \(k\) randomly choosing the
-data plot, roughly follows a binomial distribution with \(p=1/m\). Fig.
+data plot, roughly follows a binomial distribution with \(p=1/m\). Figure
 \ref{fig:lineup} shows a lineup of the hexagon tile map, of size
@@
 spots. These latter two reflect the structure seen in thyroid cancer
-data (Fig. \ref{fig:thyroid}). This
+data (Figure \ref{fig:thyroid}). This
 produces six treatment levels:
@@
 data set only once, either as a choropleth or as a hexagon tile map.
-Table \ref{fig:exp-design} summarises the design and the allocation of
+Figure \ref{fig:exp-design} summarises the design and the allocation of
 the displays.
@@
 allowed outliers, and showed distributions similar to the thyroid cancer
-distribution (Fig. \ref{fig:thyroid}).
+distribution (Figure \ref{fig:thyroid}).
 
@@
 
-Fig. \ref{fig:detect-compare} displays the average detection rates for
+Figure \ref{fig:detect-compare} displays the average detection rates for
 the two types of plot separately for each trend model. Each trend model
@@
 seen as either choropleths or hexagon tile maps by each group as
-specified in Table. \ref{fig:exp-design}; the detection rates for each
+specified in Figure \ref{fig:exp-design}; the detection rates for each
 display are connected by a line segment. The Three Cities and All Cities
@@
 
-Table. \ref{tab:desc-stats} shows the means and standard deviations of
+Table \ref{tab:desc-stats} shows the means and standard deviations of
 the detection rate for each type of plot and each trend model. This also
@@
 
-\begin{table}
-
-\caption{\label{tab:desc-stats}The mean and standard deviation of the rate of detection for each trend model, calculated for the choropleth and hexagon tile map displays.}
-\centering
-\begin{tabular}[t]{lccc}
-\toprule
-Type & NW-SE & Three Cities & All Cities\\
-\midrule
-Choro. & 0.52 & 0.04 & 0.23\\
- & (0.50) & (0.19) & (0.42)\\
-\addlinespace
-Hex. & 0.62 & 0.40 & 0.58\\
- & (0.49) & (0.49) & (0.49)\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-Table. \ref{tab:detect-glmer1} presents a summary of the generalised
+Table \ref{tab:detect-glmer1} presents a summary of the generalised
 linear mixed effects model, testing the effect of plot type and trend
-model on the detection rate. The results support the summary from Fig.
+model on the detection rate. The results support the summary from Figure
 \ref{fig:detect-compare} and all parameters are statistically
-significant despite the large standard deviations observed in Table.
+significant despite the large standard deviations observed in Table
 \ref{tab:desc-stats}. Overall, the hexagon tile map performs marginally
@@
 choropleth map lineup but increases for a hexagon tile map display. The
-log odds of detection shown in Table. \ref{tab:detect-glmer1} can be back-transformed after taking the sum of all terms for the trend and type of
+log odds of detection shown in Table \ref{tab:detect-glmer1} can be back-transformed after taking the sum of all terms for the trend and type of
 display that are of interest. For the NW-SE distribution, the predicted
@@
 
-\begin{table}
-
-\caption{\label{tab:detect-glmer1}The model output for the generalised linear mixed effect model for detection rate.
-This model considers the type of display, the trend model hidden in the data plot, and accounts for contributor performance.}
-\centering
-\begin{tabular}[t]{rrlrr}
-\toprule
-Term & Est. & Sig. & Std. Error & P val\\
-\midrule
-Intercept & -1.27 & $^{***}$ & 0.19 & 0.00\\
-Hex. & 1.63 & $^{***}$ & 0.24 & 0.00\\
-\addlinespace
-Three Cities & -2.07 & $^{***}$ & 0.43 & 0.00\\
-All Cities & 1.34 & $^{***}$ & 0.24 & 0.00\\
-\addlinespace
-Hex:Three Cities & 1.28 & $^{**}$ & 0.48 & 0.01\\
-Hex:All Cities & -1.16 & $^{***}$ & 0.33 & 0.00\\
-\bottomrule
-\end{tabular}
-\end{table}
-
 \subsection{Speed}\label{speed}
 
-Fig. \ref{fig:beeswarm} shows horizontally jittered dot plots to
+Figure \ref{fig:beeswarm} shows horizontally jittered dot plots to
 contrast the time taken by participants to evaluate each lineup when
@@
 subjective assessment by the participant prompted by the question: `How
-certain are you about your choice?'. Fig. \ref{fig:certainty} shows the
+certain are you about your choice?'. Figure \ref{fig:certainty} shows the
 number of times participants provided each level of certainty. This was
@@
 
-\begin{table}
-
-\caption{\label{tab:reason}The number of participants that selected each reason for their choice of plot when looking at each trend model shown in choropleth and hexagon tile maps.
-The facets show whether or not the choice was correct.}
-\centering
-\begin{tabular}[t]{llll}
-\toprule
-Trend & Detected & Choro. & Hex.\\
-\midrule
- & No & trend & clusters\\
-\cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash All Cities} & Yes & clusters, consistent & clusters\\
-\cmidrule{1-4}
- & No & trend & clusters\\
-\cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash Three Cities} & Yes & consistent & clusters\\
-\cmidrule{1-4}
- & No & trend & clusters\\
-\cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash NW-SE} & Yes & trend & clusters\\
-\bottomrule
-\end{tabular}
-\end{table}
-
 \section{Discussion}\label{discussion}
@@
 the participants perform slightly better or equally as well for each
-replicate in each trend model across the two displays. Table II shows
+replicate in each trend model across the two displays. Table \ref{tab:desc-stats} shows
 that the difference in the mean detection rate for the two trend models
@@
 
-The differences are seen in the \ref{fig:detect-compare} plot and Table.
+The differences are seen in Figure \ref{fig:detect-compare} and Table
 \ref{tab:desc-stats} are reflected in the model results. Surprisingly
@@
 consider the hexagon tile map distribution but would be able to detect
-the data plot in the lineup. The bimodal distributions seen in Fig.
+the data plot in the lineup. The bimodal distributions seen in Figure
 \ref{fig:beeswarm} showed very little difference in the mean evaluation
@@
 The responses to the questions asked of participants included the reason
-for their choice and the certainty around their choice. Fig.
+for their choice and the certainty around their choice. Figure
 \ref{tab:reason} shows high levels of certainty of 4 and 5 were chosen
@@
 
+\newpage
+
+\begin{table}[t]
+
+\caption{\label{tab:desc-stats}The mean and standard deviation of the rate of detection for each trend model, calculated for the choropleth and hexagon tile map displays.}
+\centering
+\begin{tabular}[t]{lccc}
+\toprule
+Type & NW-SE & Three Cities & All Cities\\
+\midrule
+Choro. & 0.52 & 0.04 & 0.23\\
+ & (0.50) & (0.19) & (0.42)\\
+\addlinespace
+Hex. & 0.62 & 0.40 & 0.58\\
+ & (0.49) & (0.49) & (0.49)\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[t]
+
+\caption{\label{tab:detect-glmer1}The model output for the generalised linear mixed effect model for detection rate.
+This model considers the type of display, the trend model hidden in the data plot, and accounts for contributor performance.}
+\centering
+\begin{tabular}[t]{rrlrr}
+\toprule
+Term & Est. & Sig. & Std. Error & P val\\
+\midrule
+Intercept & -1.27 & $^{***}$ & 0.19 & 0.00\\
+Hex. & 1.63 & $^{***}$ & 0.24 & 0.00\\
+\addlinespace
+Three Cities & -2.07 & $^{***}$ & 0.43 & 0.00\\
+All Cities & 1.34 & $^{***}$ & 0.24 & 0.00\\
+\addlinespace
+Hex:Three Cities & 1.28 & $^{**}$ & 0.48 & 0.01\\
+Hex:All Cities & -1.16 & $^{***}$ & 0.33 & 0.00\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[t]
+
+\caption{\label{tab:reason}The number of participants that selected each reason for their choice of plot when looking at each trend model shown in choropleth and hexagon tile maps.
+The facets show whether or not the choice was correct.}
+\centering
+\begin{tabular}[t]{llll}
+\toprule
+Trend & Detected & Choro. & Hex.\\
+\midrule
+ & No & trend & clusters\\
+\cmidrule{2-4}
+\multirow{-2}{*}{\raggedright\arraybackslash All Cities} & Yes & clusters, consistent & clusters\\
+\cmidrule{1-4}
+ & No & trend & clusters\\
+\cmidrule{2-4}
+\multirow{-2}{*}{\raggedright\arraybackslash Three Cities} & Yes & consistent & clusters\\
+\cmidrule{1-4}
+ & No & trend & clusters\\
+\cmidrule{2-4}
+\multirow{-2}{*}{\raggedright\arraybackslash NW-SE} & Yes & trend & clusters\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \end{document}

### 2025-03-26 paper/paper_review_response.Rmd
Suggested changes - to be converted to ANZJS format

---
title: "Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics"
affiliation:
  author-columnar: true         ## one column per author
  #institution-columnar: true  ## one column per institution (multiple autors eventually)
  # wide: true                  ## one column wide author/affiliation fields
  institution:
    - name: Queensland University of Technology
      department: Science and Engineering Faculty
      location: Brisbane, Australia
      email: stephanie.kobakian@gmail.com
      mark: 1
      author:
        - name: Stephanie Kobakian
    - name: Monash University
      department: Econometrics and Business Statistics Faculty
      location: Melbourne, Australia
      email: dicook@monash.edu
      mark: 1
      author:
        - name: Dianne Cook
keywords: ["statistics", "visual inference", "geospatial", "population"]
abstract: |
  The choropleth map display is commonly used for communicating spatial distributions across geographic areas. However, when choropleths are used the size of the geographic units will influence the understanding of the distribution derived by map users. The hexagon tile map is presented as an alternative display for visualizing population related distributions effectively. Visual inference is used to measure the power of the hexagon tile map design, and the choropleth is used as a comparison. The hexagon tile map display is tested using a distribution that is directly related to the geography, with values monotonically increasing from the North-West to South-East areas of Australia. This study finds in a hexagon tile map lineup the single map that contains a population related distribution is detected with greater probability than the same data displayed in a choropleth map. These findings should encourage map creators to implement alternative displays and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
bibliography: paper.bib
output:
  pdf_document: 
      number_sections: true
      keep_tex: true
editor_options: 
  chunk_output_type: console
link-citations: true
citation_package: biblatex
csl: springer-vancouver.csl
header-includes: \usepackage{graphicx}
---

<!-- Regular paper – 12 double column pages (Submissions may be up to 18 pages in length, subject to MOPC. All regular paper page limits include references and author biographies.) -->

<!-- Changes: thyroid instead of liver - check; lineup need to be hexmap; check language with chatgpt/grammarly; get refs formatted and paper into 10 pages; use new template -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  error = FALSE, 
  message = FALSE,
  cache = FALSE,
  dpi = 300,
  out.width = "100%")
```

```{r libraries}
# Load Libraries
library(tidyverse)
library(readxl)
library(broom)
library(broom.mixed)
library(cowplot)
library(png)
library(grid)
library(lme4)
library(ggthemes)
library(RColorBrewer)
library(knitr)
library(kableExtra)

options(knitr.kable.digits = "2")
```

```{r data}
trend_colors <- c(
  "NW-SE" = "#B2DF8A",
  "Three Cities" = "#A6CEE3",
  "All Cities" = "#1F78B4")

type_colors <- c(
  "Choro." = "#fcae91",
  "Hex." = "#a50f15")

detect_f_colors <- c(
  "No" = "#66C2A5",
  "Yes" = "#FC8D62")

detect_colors <- c(
  "Detected? No" = "#66C2A5",
  "Detected? Yes" = "#FC8D62")

  # Downloaded data
d <- read_csv("data/experiment-data.csv")

# Check data set 
# Need to clean multiple entries, 48, 24
# remove duplicated entries due to submit button
d <- d %>% group_by(group, pid, image_name) %>%
  slice(1) %>% ungroup() %>% 
  arrange(group, pid, plot_order)

# Remove pids who did not provide answers to most questions
keep <- d %>% count(pid, sort = TRUE) %>% filter(n > 10)
d <- d %>% 
  filter(pid %in% keep$pid) %>%
  filter(pid != "1234567890")

# Remove pids who did not provide any choices
# Or an insufficient amount of responses
bad_contribs <- d %>% group_by(pid) %>% 
  summarise(sum0 = sum(choice)) %>% 
  filter(sum0 < 13) %>% 
  pull(pid)

d <- d %>% 
  filter(!(pid %in% bad_contribs))

n_pids <- d %>% count(pid, sort=TRUE) %>% 
  summarise(n_pids = length(pid))

d <- d %>% mutate(certainty = factor(as.character(certainty),
  levels = c("1", "2", "3", "4","5"), ordered=TRUE))
```

```{r reps}
replicate <- tibble(image_name = c("aus_cities_12_geo.png", "aus_cities_12_hex.png", 
                                   "aus_cities_3_geo.png", "aus_cities_3_hex.png",
                                   "aus_cities_4_geo.png", "aus_cities_4_hex.png",
                                   "aus_cities_9_geo.png", "aus_cities_9_hex.png",
                                   "aus_nwse_2_geo.png", "aus_nwse_2_hex.png",
                                   "aus_nwse_3_geo.png", "aus_nwse_3_hex.png",
                                   "aus_nwse_5_geo.png", "aus_nwse_5_hex.png",
                                   "aus_nwse_6_geo.png", "aus_nwse_6_hex.png",
                                   "aus_three_12_geo.png", "aus_three_12_hex.png",
                                   "aus_three_5_geo.png", "aus_three_5_hex.png",
                                   "aus_three_8_geo.png", "aus_three_8_hex.png",
                                   "aus_three_9_geo.png", "aus_three_9_hex.png"),
                    replicate = c(1, 1, 2, 2, 3, 3, 4, 4, 
                                  1, 1, 2, 2, 3, 3, 4, 4,
                                  1, 1, 2, 2, 3, 3, 4, 4))
# Add rep info to data
d <- d %>% left_join(., replicate, by = "image_name")
```

```{r pdetection_group}
# Tidy for analysis
d <- d %>% 
  separate(image_name, c("nothing", "trend", "location", "type", "extra"), remove = FALSE) %>%
  select(-nothing, -extra) %>%
  mutate(location = as.numeric(location), 
    # detect measures the accuracy of the choice
         detect = ifelse(location == choice, 1, 0)) %>% 
  mutate(trend = case_when(
    trend == "nwse" ~ "NW-SE",
    trend == "cities" ~ "All Cities",
    trend == "three" ~ "Three Cities")) %>% 
  mutate(trend = fct_relevel(trend,"All Cities","Three Cities", "NW-SE")) %>% 
  mutate(type = case_when(
    type == "hex" ~"Hex.",
    TRUE~"Choro.")) %>% 
    mutate(detect_f = factor(detect, levels = c(0,1), labels = c("Detected? No", "Detected? Yes")))

plots <- d %>% group_by(group, trend, type, location) %>%
  # pdetect measures the aggregated accuracy of the choices
  summarise(pdetect = length(detect[detect == 1])/length(detect)) 
```

```{r makethyroidplots}
library(cartogram)
library(sugarbag)
library(sf)

# Spatial polygons files sourced from: https://github.com/wfmackey/absmapsdata
load("data/sa22011.rda")
load("data/state2011.rda")

invthm <- theme_map() + 
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA), 
    plot.background = element_rect(fill = "black", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.key = element_rect(fill = "transparent", colour = NA),
    text = element_text(colour = "white"),
    axis.text = element_blank()
  )

# function to allocate colours to regions
aus_colours <- function(sir_p50){
  value <- case_when(
    sir_p50 <  0.74 ~ "#33809d",
    sir_p50 >= 0.74 & sir_p50 < 0.98 ~ "#aec6c7",
    sir_p50 >= 0.98 & sir_p50 < 1.05 ~ "#fff4bc",
    sir_p50 >= 1.05 & sir_p50 < 1.45 ~ "#ff9a64",
    sir_p50 >= 1.45 ~ "#ff3500",
    TRUE ~ "#FFFFFF")
  return(value)
}

sa2 <- sa22011 %>% 
  filter(!st_is_empty(geometry)) %>% 
  filter(!state_name_2011 == "Other Territories") %>% 
  filter(!sa2_name_2011 == "Lord Howe Island")

SIR <- read_csv("data/SIR Downloadable Data.csv") %>% 
  filter(SA2_name %in% sa2$sa2_name_2011) %>% 
  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
  filter(Cancer_name == "Thyroid", Sex_name == "Females")
ERP <- read_csv("data/ERP.csv") %>%
  filter(REGIONTYPE == "SA2", Time == 2011, Region %in% SIR$SA2_name) %>% 
  dplyr::select(Region, Value)
# Alternative maps
# Join with sa2 sf object
sa2thyroid_ERP <- SIR %>% 
  left_join(sa2, ., by = c("sa2_name_2011" = "SA2_name")) %>%
  left_join(., ERP %>% 
              dplyr::select(Region, 
              Population = Value), by = c("sa2_name_2011"= "Region")) %>% 
  filter(!st_is_empty(geometry))
sa2thyroid_ERP <- sa2thyroid_ERP %>% 
  #filter(!is.na(Population)) %>% 
  filter(!sa2_name_2011 == "Lord Howe Island") %>% 
  mutate(SIR = map_chr(p50, aus_colours)) %>% 
  st_as_sf()

# Make choropleth
aus_ggchoro <- ggplot(sa2thyroid_ERP) + 
  geom_sf(aes(fill = SIR), size = 0.1) + 
  scale_fill_identity() + invthm

# Make hexmap
if (!file.exists("data/aus_hexmap.rda")) {

## Check the projection uses long and lat
## Create centroids set
sa2centroids <- sa2 %>% 
  create_centroids(., "sa2_name_2011")
## Create hexagon grid
# For speed, consider if the buffer distance beyond the centroids is necessary
grid <- create_grid(centroids = sa2centroids,
                    hex_size = 0.15,
                    buffer_dist = 4, verbose = TRUE)
## Allocate polygon centroids to hexagon grid points
# This is a time consuming process for a large data set
aus_hexmap <- allocate(
  centroids = sa2centroids,
  hex_grid = grid,
  sf_id = "sa2_name_2011",
  ## same column used in create_centroids
  hex_size = 0.15,
  hex_filter = 8,
  focal_points = capital_cities,
  width = 25,
  verbose = TRUE)
save(aus_hexmap, file = "data/aus_hexmap.rda") 
}

load("data/aus_hexmap.rda")

## Prepare to plot
fort_hex <- fortify_hexagon(data = aus_hexmap,
                            sf_id = "sa2_name_2011",
                            hex_size = 0.3) %>% 
            left_join(sa2thyroid_ERP %>%
            select(sa2_name_2011, SIR, p50))
fort_aus <- sa2thyroid_ERP %>%
  fortify_sfc()
## Make a plot
aus_hexmap_plot <- ggplot() +
  geom_polygon(aes(x = long,  y = lat,  
        group = interaction(sa2_name_2011, polygon)),
               fill = "black",  colour = "darkgrey", 
               linewidth = 0.1, data = fort_aus) +
  geom_polygon(aes(x = long, y = lat, group = hex_id, 
                   fill = SIR), data = fort_hex) +
  scale_fill_identity() +
  invthm + coord_equal()
```

Introduction
=============
<!-- General: comparison of displays, motivate hexagon tile map, enough info to motivate aims -->
<!-- geographies on choropleth -->
This study compares the effectiveness of the spatial display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics. The choropleth map is the traditional method for visualizing aggregated statistics across administrative boundaries. The hexagon tile map builds on existing displays, such as the cartogram, and tessellated hexagon displays. A hexagon tile map forgoes the familiar boundaries, in favour of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location.  It differs in the relaxed requirement to have connected hexagons, and allows sparsely located hexagons. This type of display may be useful for other countries, and other purposes. The algorithm to construct a hexagon tile map is available in the R package sugarbag [@sugarbag].

The hexagon tile map was designed for Australia, motivated by a need to display spatial statistics for the Australian Cancer Atlas. None of the existing approaches for creating cartograms or hexagon tiling perform well for the Australian landscape, which has vast open spaces and concentrations of population in small regions clustered on the coastlines. XXX cite Kobakian, Cook & Roberts 2020 and explain approach to reach this conclusion

The Australian Cancer Atlas [@atlas] is an online interactive web tool created to explore the burden of cancer on Australian communities. There are many cancer types to be explored individually or aggregated. XXX Who are the users of the Atlas

The Australian Cancer Atlas allows users to explore the patterns in the distributions of cancer statistics over the geographic space of Australia. It uses a choropleth map display and diverging colour scheme to draw attention to relationships between neighbouring areas. The hexagon tile map may be a useful alternative display to enhance the atlas.

The experiment was conducted using the lineup protocol, a visual inference procedure [@GIIV], to objectively test the effectiveness of the two displays. XXX explain lineup protocol with more detail

The paper is organised as follows. The next section discusses the background of geographic data display and visual inference procedures. The [Methodology] section describes the methods for conducting the experiment and analysing the results. The results are summarized in the [Results] section, followed by a discussion about the broader implications for the use of this map style.

Background
=============

## Spatial data displays

<!-- foundation, tradition -->  
Spatial visualisations communicate the distribution of statistics over geographic landscapes. The choropleth map [@EI], [@BCM] is a traditional display. It is used to present statistics that have been aggregated on geographic units. Creating a choropleth map involves drawing polygons representing the administrative boundaries, and filling with colour mapped to the value of the statistic. The choropleth map places the statistic in the context of the spatial domain, so that the reader can see whether there are spatial trends, clusters or anomalies.

XXX make it clear that visualizing communicable disease patterns is just one example use of a spatial data display.
This is important for digesting disease patterns. If there is a trend it may imply that the disease is spreading from one location to another. If there is a cluster, or an anomaly, there may be a localized outbreak of the disease. Aggregating the statistic on administrative units, provides a level of privacy to individuals, while allowing the impact of the disease on the community to be analysed.

<!-- Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
The rural communities in Australia operate on a much larger geographic space than small inner-city communities. When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base. This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention [@CTTMB]. An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas [@NISCC]. 
This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.

A choropleth map is not the only display that can be used for presenting geospatial data. 
Alternative maps include various cartograms and tessellated tile maps. They allow other variables to be incorporated in the display to highlight the statistical values of various geographic areas.
-->

```{r liver, eval=FALSE, fig.height = 4, fig.width = 4, fig.cap = "A choropleth map of the smoothed average of liver cancer diagnoses for Australian males. The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average. The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.", results = "asis"}
ggdraw() +
  draw_plot(rasterGrob(readPNG("figuresaus_liver_m.png")))
```

```{r liver-hex, eval=FALSE, fig.height = 4, fig.width = 4, fig.cap = "A hexagon tile map of the smoothed average of liver cancer diagnoses for Australian males. The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average. The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.", results = "asis"}

ggdraw() +
  draw_plot(rasterGrob(readPNG("figuresaus_liver_m_hex.png")))
```
<!--
This will create the figure as needed in the paper, but I can't get the width argument to work properly.
\begin{figure*}[!t]
\centering
\includegraphics{paper_files/figure-latex/liver-1.pdf}
\caption{A choropleth map (a), and hexagon tile map (b) of the smoothed average of liver cancer diagnoses for Australian males. The diverging colour scheme uses dark blue areas for much lower than average diagnoses, yellow areas with diagnoses around the Australian average, red shows diagnoses much higher than average. The hexagon tile map shows concentrations of higher than expected liver cancer rates in the cities of Melbourne and Sydney, which is not visible from the choropleth.}
\label{fig:liver2}
\end{figure*}
-->

```{r thyroid-choro, out.height = "30%", fig.height = 3, fig.width = 4, fig.align='center', fig.cap = "A choropleth map of thyroid cancer incidence among females across the Statistical Areas of Australia at Level 2. Blue indicates lower than average and red indicates higher than average incidence. A cluster of high incidence is visible on the east coast."}
aus_ggchoro
```

The choropleth map is an effective spatial display if the size of the geographic units is relatively uniform. This is not the case for most countries. Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips. Fig. \ref{fig:thyroid-choro} shows the choropleth map of thyroid cancer rates in Australia. The choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population related distribution of the statistic [@CBATCC]. *Land doesn't get cancer, people do* -- a more effective way to communicate the spatial distributions of cancer statistics is needed. XXX add reference

<!-- Cartogram -->
A cartogram is a general solution for adequately displaying a population-based statistic. It transforms the geographic map base to reflect the population in the geographic region, while preserving some aspects of the geographic location. There are several cartogram algorithms [@ACTUC], [@CBATCC]; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map. The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units but can result in losing the familiar geographic information. For Australia, the transformations warp the country so that it is no longer recognisable.

<!-- Other cartograms -->
Alternative algorithms make various trade offs between familiar shapes and representation of geographic units. The non-contiguous cartogram method [@NAC] keeps the shapes of geographic units intact, and changes the size of the shape. This method disconnects areas creating empty space on the display losing the continuity of the spatial display of the statistic. The Dorling cartogram [@ACTUC] represents each unit as a circle, sized according to the value of the statistic. The neighbour relationships are mostly maintained by how the circles touch. A similar approach was pioneered by Raisz [-@RSCW], using rectangles that tile to align borders of neighbours [@CDWCS]. There have been thorough reviews of the array of methods, as suitable for cancer atlas displays [@review], [@BCM].

```{r thyroid-hex, out.height = "30%", fig.height = 3, fig.width = 4, fig.align='center', fig.cap = "A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1. The high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) can now be seen, along with numerous isolated spots."}
aus_hexmap_plot
```

<!-- Hexagon tile map -->
The hexagon tile map algorithm, automatically matches spatial regions to their nearest hexagon tile, from a grid of tiles. It has the effect of spreading out the inner city areas while maintaining the spatial locations or regions in remote areas. The algorithm is available in the R package, sugarbag [@sugarbag]. Fig. \ref{fig:thyroid-hex} shows the hexagon tile map where the map is coloured according to the thyroid cancer incidence rate in the area. The colour scheme used is bidirectional, it ranges from substantially below average (blue) to substantially above average (red) for the cancer incidence rate within the geographic area. In the hexagon tile map display, the inner city areas have expanded, making it possible to see the cancer incidence in the small, densely populated areas. Remote regions are represented by isolated hexagons, which is not ideal, but maintains the spatial location of these data values and highlights the sparsity of residents. It is of interest to know how well the spatial distribution is perceived by map users for this display, in comparison to the choropleth.
XXX clarify who is doing the perceiving

## Visual Inference

In order to assess the effectiveness of the hexagon tile map, the lineup protocol [@GIIV],[@BCHLLSW09] from visual inference procedures is employed. The approach mirrors classical statistical inference. The procedures for doing a power comparison of competing plot designed, outlined in @GTPCCD, are followed. 
XXX reasoning for using this approach, over alternatives
eg. The lineup protocol allows a measurement of how easily participants can make the detection of a spatial pattern when two different map types are used. Data is simulated and then visualised in a way that one location shows the same significant result in the two different visualisations (hexagon and choropleth). The detection rate indicates how easily participants can make the detection with respect to the map type. Where the detection rate is the number of correct detections of the significant data pattern by participants.

In classical statistical inference hypothesis testing is conducted by comparing the value of a test statistic on a standard reference distribution, computed assuming the null hypothesis is true. If the value is extreme,  the null hypothesis is rejected, because the test statistic value is unlikely to have been so extreme if it was true. In the lineup protocol, the plot plays the role of the test statistic, and the data plot is embedded in a field of null plots. Defining the plot using a grammar of graphics [@ggplot2] makes it a functional mapping of the variables and thus, it can be considered to be a statistic. With the same data, two different plots can be considered to be competing statistics, one possibly a more powerful statistic than the other.

To do hypothesis testing with the lineup protocol requires human evaluation. The human judge is required to identify the most different plot among the field of plots. If this corresponds to the data plot -- the test statistic -- the null hypothesis is rejected. It means that the data plot is extreme relative to the reference distribution of null plots.

The null hypothesis is explicitly provided by the grammatical plot description. For example, if a histogram is the plot type being used, the null might be that the underlying distribution of the data is a Gaussian. Null data would be generated by simulating from a normal model, with the same mean and standard deviation as the data. In practice, the null hypothesis used is generic, such as *there is NO structure or a pattern in the plot*, and contrasted to an alternative that there is structure.

The chance that an observer picks the data plot out of a lineup of size $m$ plots accidentally, if the null hypothesis is true is $1/m$. With $K$ observers, the probability of $k$ randomly choosing the data plot, roughly follows a binomial distribution with $p=1/m$. Fig. \ref{fig:lineup} shows a lineup of the hexagon tile map, of size $m=12$. Plot 3 is the data plot, and the remaining 11 are plots of null data. XXX Add footnote, the same data is presented in aus_cities_3_geo

```{r lineup, fig.cap = "This lineup of twelve hexagon tile map displays contains one map with a real population related structure, it is located in plot 3. The rest are null plots that contain spatial correlation between neighbours.", fig.height = 8, fig.width = 8}
ggdraw() +
  draw_plot(rasterGrob(readPNG("figures/aus_cities_3_hex.png")))
# XXX include, in the supplementary materials, this same type of figure for a choropleth lineup aus_cities_3_geo
```

In order to determine the effectiveness of a type of display, this probability is less relevant than the overall proportion of observers who pick the data plot, $k/K$. The power of the test statistic (data plot) is provided by this proportion. Power in a statistical sense is the ability of the statistic to *produce a rejection* of the null hypothesis, if it is indeed *not true*. With the same data plotted using two different displays, the display with the highest proportion of people who choose the data plot would be considered to be the most powerful statistic.

Methodology
============

This study aims to answer two key questions around the presentation of spatial distributions:

1. Are spatial disease trends that impact highly populated small areas detected with higher accuracy, when viewed in a hexagon tile map?
2. Are people faster in detecting spatial disease trends that impact highly populated small areas when using a hexagon tile map?

Additional considerations when completing this experimental task included the difficulty experienced by participants and the certainty they had in their decision.

Australia is used for the study, with Statistical Area 3 (SA3) [@abs2016] as the geographic units. The results should apply broadly to any other geographic area of interest. XXX Specify the limits on broad application here
XXX what of areas with similar geographic v hex map displays
XXX hex map should perform similarly and not impede identification of population distributions when geo == hex
## Experimental factors

<!-- The variables changed between groups were the type of plot shown and the trend model.-->

The primary factor in the experiment is the plot type. The secondary factor is a trend model. Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to perform well, and two with differing level of inner city hot spots. These latter two reflect the structure seen in the thyroid cancer data (Figures \ref{fig:thyroid-choro}, \ref{fig:thyroid-hex}). This produces six treatment levels:

  - Map type: *Choropleth, Hexagon tile*
  - Trend: *South-East to North-West; Locations in three population centres; Locations in multiple population centres, *

Data is generated for each of the trend models, with four replicates, and each displayed both as a choropleth and as a hexagon tile map, which yields 12 data sets, and 24 data plots. This set of displays is divided in half, providing two sets of 12 displays, Group A and Group B. Participants were randomly allocated to Group A or B. Participants saw a data set only once, either as a choropleth or as a hexagon tile map. Table \ref{fig:exp-design} summarises the design and the allocation of the displays.

```{r exp-design, results = "asis", fig.width = 8, fig.height = 8, fig.cap = "The experimental design used in the visual inference study. XXX describe the location"}
ggdraw(xlim = c(0,1), ylim = c(0,1)) + draw_plot(rasterGrob(png::readPNG("figures/experiment_design.png")))
#XXX change names to “Hexagon Tile” and “Choropleth”
```

## Generating null data

Null data needs to be data with no (interesting) structure. In most scenarios, permutation is the main approach for generating null plots. It is used to break association between variables, while maintaining marginal distributions. This is too simple for spatial data. In spatial data, a key feature is the spatial dependence or smoothness over the landscape. To do something simple, like permute the values relative to the geographic location would produce null plots which are too chaotic, and the data plot will be recognisable for its smoothness rather than any structure of interest.

XXX watch the language here and make the description more clear 
For spatial data, null data is stationary data, where the mean, variance and spatial dependence are constant over the geographic units. Stationary data is specified by a variogram model [@POG]. Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots.  The parameters for the Gaussian model were sill=1, range=0.3 with the variance generated by a standard normal distribution.

The R package `gstat` [@gstat] was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.

```{r eval=FALSE, echo=FALSE}
var.g.dummy <- gstat(formula = z ~ 1, 
                     locations = ~ longitude + latitude, 
                     dummy = T, beta = 1, model = vgm(psill = 1, model = "Gau", range = 0.3),
                     nmax = 12)
```

<!-- Applying smoothing -->

The null model imposed by our hypothesis suggests that neighbours are related. The randomness induced when generating the null data was smoothed to mirror the practices employed by the Australian Cancer Atlas statisticians. 
In these 12 sets of data, each of the 12 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas, without implementing uncertainty via transparency. XXX reference paper describing this method or describe the smoothing method here

A list of neighbours for each geographic unit was generated to use when smoothing the distributions. For each geographic unit the same spatial smoother was applied in each layer of smoothing. It kept half of the units' previous value, and derived the new half as the mean of the values of its neighbours at the previous layer of smoothing. 
XXX expressed mathematically as: 
0.5 * value of area + 0.5 MEAN(value| area is neighbour)

This smoothing allowed neighbours to be related to each other, but also allowed outliers, and showed distributions similar to the thyroid cancer distribution (Figures \ref{fig:thyroid-choro}, \ref{fig:thyroid-hex}).

## Generating lineups

<!-- Discuss simulating the trend data -->
For each trend model, four real data displays were created by manipulating the centroid values of each of the SA3 geographic units.

The North West to South East (NW-SE) distribution was created using a linear equation of the centroid longitude and latitude values.

The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia, calculated when creating the hexagon tile map using the sugarbag [@sugarbag] package.
201 of the 336 SA3s were considered greater capital city areas, the values of these areas were increased to create red clusters. The amount was chosen to make clusters around the cities visible in the choropleth display even if they were not overtly noticeable. XXX check if this is aligned to the ABS GCC areas or if not, justify

A similar selection process was applied to the Three Cities' trend model. However, for each of the four replicates for the Three Cities trend, a random sample of capital cities was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart. Only values of the areas nearest to the three cities were increased to create clusters.

<!-- Location of data plot -->

One of the lineup locations was chosen to embed the real trend model map, in each of the four replicates, for the three trend models.
The location for the real data plot was randomly chosen from the 12 possible locations. The chance of repetition was introduced to prevent participants from deducing the remaining locations of real data plots, by process of elimination. Due to allowance re-sampling, the locations 1, 7, 10 and 11 happened to not be selected.

XXX
As seen in Fig \ref{fig:exp-design}, the choropleth and hexagon display used the same location for the real data display. To simulate a naturally occurring spatial trend, some variability was simulated for the data in all plots, using spatially correlated values. The trend model in the real plot was combined with the simulated spatially correlated values to determine the final value used to colour each area. 
Each set of lineup data was used to produce a pair choropleth map lineup and hexagon tile map lineup. These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.

<!-- Scaling data within a lineup -->

For each of the 144 individual maps, the values for each geographic area were rescaled to create a similar colour scale from deep blue to dark red within each map.
This meant at least one geographic unit was coloured dark blue, and at least one was red, in every map display of every lineup.

For the geographic NW-SE distribution, this resulted in the smallest values of the trend model (blue) occurring in Western Australia, the North West of Australia, and the largest values of the trend model (red) occurring in the South East. This resulted in Tasmania being coloured completely red.

For the population related displays, the clusters in the cities appeared more red than the rest of Australia.

## Analysis

### Data Cleaning

The data cleaning process considered the legitimacy of submissions and limited the results used to participants who met the standard for genuine engagement. This process involved removing data from the participants who did not provide at least three unique choices across the responses for each of the twelve lineups, and did not correctly identify the pattern in any of the 12 displays. Data was not removed if participants had made a variety of plot choices for the 12 displays, even if none were correctly detected.

XXX consider the timing of the last group above, if they got none right did they do it very quickly or actually engage?

### Descriptive statistics

Basic descriptive statistics were used to contrast the detection rate for the two types of displays. Comparison was also made across the trend models, contrasting the mean and standard detection rate for each group, who had seen the different map display type for each replicate.

Side-by-side dot plots were made of accuracy (efficiency) against map type, faceted by trend model type.

Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.

Plots were made in R [@RCore], with the `ggplot2` package [@ggplot2].

### Modelling

The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model. 
The R [@RCore] `glmer()` function in the `lme4` [@lme4] package implements generalised linear mixed effect models. The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:

$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij} + \epsilon_{i,j}, ~~~ i=1,2; ~j=1,2,3$$

where $y_{ij} = 0, 1$ is the log odds for whether the subject detected the data plot (1) or did not (0), $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect. We are allowing for an interaction between map type and trend model as the response is binary, so a logistic model was used.

The model specifies a logic link, this means the predicted values from the `glmer` model should be back-transformed to fit between 0 and 1. The predictions  $\widehat{p}(\eta)$ are transformed to be probabilities between 0 and 1 with the link specified below:

$$\widehat{p}(\eta) = \frac{e^{\eta}}{1 + e^{\eta}}$$ \label{eq:transform}
$$\eta = f(\tau_i,\delta_j)$$
XXX Add Random effects
 As each participant provides results from 12 lineups, this model can account for each individual participants’ abilities as it includes a subject-specific random intercept.

XXX move these sections to before the analysis?
## Web application to collect responses

The taipan [@taipan] package for R was used to create the survey web application. 
This structure was altered to collect responses regarding participants demographics and their survey responses.
The survey app contained three tabs. Participants were first asked for their demographics, and their consent to the responses being used for analysis. The demographics collected included participants' preferred pronoun, the highest level of education achieved, their age range and whether they had lived in Australia.

For each of the twelve displays every participant was asked three questions; their plot choice, the reason for their choice and the difficulty or certainty of deciding for each plot. The time taken by the participant to view each lineup and respond to these questions was recorded.

<!-- When participants completed the twelve evaluations the survey application triggered a data analysis script. This created a data set with one row per evaluation. Containing the responses to the three questions. The script also added the title of the image, which indicated the type of map display, the type of distribution hidden in the lineup, and the location of the data plot. It also calculated the time taken by participant to view each lineup. -->

Each participant used the internet to access the survey.
The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results. The application connected to the googlesheet using the googlesheets [@sheets] R package when participants opened the application, and interacted again when participants chose to submit the survey. At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.

## Participants

Participants were recruited from the Figure Eight crowd sourcing platform [@figeight] to evaluate lineups.
The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results. Potential participants needed to have achieved level 2 or level 3 from prior work on the platform. All participants were at least 18 years old.

Participants were allocated to either group A or group B when they proceeded to the survey web application. There were 92 participants involved in the study. All participants read introductory materials, and were trained using three test displays, to orient them to the evaluation task. All participants who completed the task were compensated $AUD5 for their time, via the Figure Eight payment system.

A pilot study was conducted in the working group of the Econometrics and Business Statistics Department of Monash University. This allowed us to estimate the effect size, and thus decide on number of participants to collect responses from.

## Demographic data collection

Each participant answered demographic questions and provided consent before evaluating the lineups.

Demographics were collected regarding the study participants:

 - Gender (female / male / other),
 - Education level achieved (high school / bachelors / masters / doctorate / other),
 - Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
 - Lived at least for one year in Australia (Yes / No )

Participants then moved to the evaluation phase.
The set of images differed for Group A and Group B.
After being allocated to a group, each individual was shown the 12 displays in randomised order.

<!--
## Experimental design

The choropleth map was used as the comparative visualisation for presenting the lineups [@VVSIALM] as this is the common display for spatial cancer data.
Geographic distributions usually have some degree of spatial autocorrelation between neighbours.
This feature was incorporated in all maps shown in the lineup displays, the map that contained the trend feature shown in only one set of data was also affected by spatial autocorrelation.
A line up protocol was implemented to arrange $N$ maps in each display. 
A reasonable amount of null plots $N-1$ in the lineup was chosen to ensure the real data map was well hidden. A reasonable number of plots to show in each lineup, $N = 12$ was chosen to not overwhelm participants due to the detailed choropleth maps of Australian SA3 areas.

The hypotheses for each lineup are
$H_0$ : All plots look the same
$H_a$ : One plot looks different to the other plots

The same data was visualized on a choropleth map, and on a hexagon tile map, however in this study the participants only saw one of these two displays. The accuracy and times taken were aggregated for Groups and.
Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.

Let $n$ be the number of independent observers and $x_i$ the
number of observers who picked plot $i$, $i = \{1,...,m\}$

Then $x_i, x_2, ..., x_m$ follows a multinomial
distribution$Mult_{\pi_1, \pi_2, ...., \pi_m}(x_i, x_2, ..., x_m)$ with 
$\sum_i \pi_i = 1$, where $\pi_i$ is the probability that plot $i$ is picked by an
observer, which we can estimate as $\hat{\pi}_i = x_i/n$.
The researchers compared the length of time taken, and the accuracy of the participants choices.
The power of a lineup can therefore be estimated as the ratio of correct
identifications $x$ out of $n$ viewings.

## The methods of data analysis used
The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R [@RCore].

For each of the 12 lineup displays the researchers calculated:

 - accuracy: the proportion of subjects who detected the data plot
 - efficiency: average time taken to respond
-->

Results
============

<!--
The results section explores the [Accuracy] and contrasts the detection rate of the real data plot in the lineups.
The second section considers the [Speed] participants had when submitting their responses to the three questions asked regarding each display.
The [Certainty] participants felt about their decisions and the [Reason] for their choice in plot is also discussed.
-->

Responses were collected from 92 participants, who each evaluated 12 lineups. Set A was evaluated by 42 participants, and 53 evaluated set B. 
Data was collected but not included in the analysis for five participants. Responses were analysed for accuracy and speed. The certainty in decision and reasons of subjects answers is also examined. 
XXXAre there differences between group A and B? This would be a good place to show that randomization is working. Underlying assumption: there a no group specific influences on test results.

## Participant demographics

Of the 92 participants, 67 were male, and 25 female. Most participants (56) had a Bachelors degree, 13 had a Masters degree, and the remaining 23 had high school diplomas.

## Accuracy

Fig. \ref{fig:detect-compare} displays the average detection rates for the two types of plot separately for each trend model. Each trend model was tested using four repetitions, evaluations on the same data set were seen as either choropleths or hexagon tile maps by each group as specified in Table. \ref{fig:exp-design}; the detection rates for each display are connected by a line segment. The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts.

One replicate for the All Cities group had similar detection rates for both plot types, the rate of detection using the choropleth map was much higher than other replicates.XXX potentially explain why
Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map. We expected that the choropleth map would be superior for the type of spatial pattern, but the data suggests the hexagon tile map performs slightly better, or equally as well.

XXX overall detection rates
While there is clearly a difference between map types (Page 12, Lines 306-316), the overall level of detection rates is low. I would expect some discussion of these low results. Are these a result of the data simulation process (i.e., the “true” signal might not be different enough)? How do the results compare to the expected detection rates if selected by chance, as discussed in Section 2.2?

```{r detect-compare, fig.cap = "The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models. Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup. The points for the same data set shown in a choroleth or hexagon tile map display are linked to show the difference in the detection rate.", fig.height=5}
# Detection rate for each lineup (image)
d_smry <- d %>% group_by(trend, type, replicate) %>%
  # pdetect measures the aggregated accuracy of the choices
  summarise(pdetect = length(detect[detect == 1])/length(detect)) %>%
  ungroup()

# Numerical summary
diffs <- d_smry %>% spread(type, pdetect) %>%
  mutate(dif = `Hex.` - `Choro.`)

# Plot summary
ggplot(d_smry, aes(x = type, y = pdetect, color = trend)) +
  geom_point(size = 2) +  
  geom_line(size = 1, aes(group = replicate)) +  
  facet_wrap(~trend) +
  scale_color_manual(values = trend_colors) +
  xlab("Type of areas visualized") +
  ylab("Detection rate") + 
  ylim(0,1) +
  guides(scale = "none")
# XXX remove legend
# use color to distinguish between replicates (facets and color for trend models is redundant)
```

Table. \ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model. This also gives the standard deviations, the smallest standard deviation for all sets of replicates was the Three Cities trend model shown in a Choropleth display. This group of displays had a very small detection rate of 0.04. The mean detection rate for the Three Cities trend model shown as choropleth map lineups was also the smallest at 0.40.
The geographic trend was expected to be detected equally in the two displays, however North-West to South-East (NW-SE) trend model had a higher mean detection rate for the hexagon tile map displays, but the difference in the means of detection rate was only 0.10.

```{r desc-stats, results = "asis"}
types <- c("Choro.", "", "Hex.", "")

d %>% group_by(type, trend) %>%
  summarise(m = as.character(round(mean(detect), 2)),
      std.dev = as.character(round(sd(detect), 2))) %>% 
  mutate(std.dev = ifelse(std.dev == 0.5, "(0.50)", paste0("(", std.dev, ")"))) %>%   mutate(m = ifelse(m == 0.4, "0.40", m)) %>% 
  gather(stat, value, m, std.dev) %>% 
  pivot_wider(names_from = "trend", values_from = "value") %>% 
  arrange(type) %>% ungroup() %>% 
  mutate(Type = types) %>% select(Type, `NW-SE`, `Three Cities`, `All Cities`) %>%
  knitr::kable(., format = "latex", align = "lccc", booktabs = TRUE, 
    linesep = c("", "\\addlinespace"),
    caption = "The mean and standard deviation of the rate of detection for each trend model, calculated for the choropleth and hexagon tile map displays.")
# XXX remove legend
```

Table. \ref{tab:detect-glmer1} presents a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on the detection rate. The results support the summary from Fig. \ref{fig:detect-compare} and all parameters are statistically significant despite the large standard deviations observed in Table. \ref{tab:desc-stats}. Overall, the hexagon tile map performs marginally better than the choropleth for all trend models.

XXX rephrased this sentence, when is it better/worse?
Population related distributions are more easily detected using a hexagon tile map display compared to when a choropleth map lineup was used.

XXX check the numbers on the calculations to make it possible to replicate the detection probabilities mentioned in the text,
The log odds of detection show in Table. \ref{tab:detect-glmer1} can be back transformed after taking the sum of all terms for the trend and type of display that are of interest.
For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to `r round(exp(0.46+0.07)/(1+exp(0.46+0.07)), 2)` from `r round(exp(0.07)/(1+exp(0.07)),2)` for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.

When a choropleth map display is used, the predicted detection rate for the Three Cities trend, `r round(exp(0.07-3.41)/(1+exp(0.07-3.41)),2)`; this is extremely low, especially compared to the NW-SE trend of `r round(exp(0.07)/(1+exp(0.07)),2)`.
When the All Cities trend is presented in a choropleth display the predicted probability of detection is `r round(exp(0.07-1.34)/(1+exp(0.07-1.34)),2)`.
The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend `r round(exp(0.46+0.07-3.41+2.44)/(1+exp(0.46+0.07-3.41+2.44)),2)` and All Cities trend `r round(exp(0.46+0.07-1.34+1.16)/(1+exp(0.46+0.07-1.34+1.16)),2)`.

```{r detect-glmer1, results="asis"}
# Mixed effects models
glmer1 <- glmer(detect ~ type*trend + (1|pid), 
              family = binomial, data = d)

glmer_terms <- c("Intercept", "Hex.", "Three Cities", "All Cities",
  "Hex:Three Cities", "Hex:All Cities")

detection_rates <- tidy(glmer1) %>%
  mutate(detection_rates = round(exp(estimate)/(1+exp(estimate)),2)) %>%
  select(term, estimate, detection_rates) %>% pull(detection_rates)

tidy(glmer1) %>%
  mutate_at(.vars = c("estimate", "std.error"), round, 2) %>% 
  mutate(p.value = round(p.value, digits=2)) %>% 
  rowwise() %>%
  mutate(sig = case_when(
  p.value <= 0.001 ~ "$^{***}$",
  p.value <= 0.01 ~  "$^{**}$",
  p.value <= 0.05 ~  "$^{*}$",
  p.value <= 0.01 ~  "$^{.}$",
  TRUE ~ "$^{ }$")) %>%
  ungroup() %>% 
  filter(!is.na(std.error)) %>%
  mutate(term = glmer_terms) %>% 
  select(Term = term, 
    Est. = estimate, 
    Sig. = sig,
    `Std. Error` = std.error, 
    `P val` = p.value) %>% 
  knitr::kable(format = "latex", escape = FALSE, align= "rrlrr", 
    booktabs = T, linesep = c("", "\\addlinespace", "", "\\addlinespace", ""), 
    caption = "The model output for the generalised linear mixed effect model for detection rate. This model considers the type of display, the trend model hidden in the data plot, and accounts for participant performance.")
# XXX remove legend
```

XXX see results under control of socio demographics. A second model including those variables could give some hints (direct effects, reduction intra-participant variance).  For reference see: (Vanderplas & Hofmann, 2016)

## Speed

Fig. \ref{fig:beeswarm} shows horizontally jittered dot plots to contrast the time taken by participants to evaluate each lineup when viewing each type of display. The time are also separated by trend model and whether the data plot was detected or not detected. The time taken to complete an evaluation ranged from milliseconds to 60 seconds. The average time taken for type of display is shown as a large coloured dot on each plot. when considering the heights of the green and orange dots, there is little difference in the average time taken to read a choropleth or hexagon tile map. Comparing the same coloured dot across each trend model row, there is a slight increase in the time taken to correctly detected the data plot in the hexagon tile map lineup, but little difference in evaluation time for the choropleth display. However, there were substantially less correct detections for choropleth lineups for the Three cities and All Cities trends.

XXX There is a clear gap between these participants and those who took longer to complete the experiment. Does the accuracy differ between these two groups? If the accuracy is significantly lower for the quicker participants, this might indicate that they chose a location by chance to finish the task as quickly as possible. What is the experience from the pilot study? Are these times taken plausible? If not, one might consider removing those cases with implausibly short decision times from the sample to eliminate randomly chosen locations. Regardless of how you deal with these cases, this detail should be discussed in the text.

```{r beeswarm, fig.cap = "The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots. The colored point indicates average time taken for each plot type. Although some participants take just a few seconds per evaluation, and some take as much as 60 seconds, but there is very little difference in time taken between plot types.", fig.height=8}
# Di playing
s <- d %>% group_by(type, trend, detect_f) %>%
  summarise(m=median(time_taken), 
            q1=quantile(time_taken, 0.25), 
            q3=quantile(time_taken, 0.75))
library(ggbeeswarm)
ggplot() + 
  geom_quasirandom(data=d, aes(x=type, y=time_taken), alpha=0.9) + 
  #geom_hline(data=s, aes(yintercept=m, colour=type)) +
  geom_point(data=s, aes(x=type, y=m, color=type), size=5, alpha=0.7) +
  #geom_errorbar(data=s, aes(x=type, ymin=q1, ymax=q3, colour=type), width=0.3, size=2) +
  scale_color_brewer("", palette = "Dark2") +
  facet_grid(trend~detect_f) + 
  ylab("Time taken (seconds)") + xlab("") +
  theme(legend.position="bottom")
```

## Certainty

Participants provided their level of certainty regarding their choice using a five point scale. 
Unlike the accuracy and speed of responses that were derived during the data processing phase, this was a subjective
assessment by the participant prompted by the question: ‘How certain are you about your choice?’.
Fig. \ref{fig:certainty} shows the amount of times participants provided each level of certainty. This was separated for each combination of trend models and display type, and coloured depending on whether a participant correctly detected the data plot in the lineup.
Participants often chose 4 or 5 when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend. This shows overconfidence in their detection ability when using a choropleth map display. Participants were less likely to be certain when their choice was incorrect and they were viewing a hexagon tile map.
For each trend model, participants were more likely to doubt their choice and choose 1 or 2 in the hexagon tile map displays, even though many had made the correct choice.

```{r certainty, fig.cap = "The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays. Participants were more likely to choose a high certainty when considering a Choropleth map. The mid value of 3 was the default certainty, it was chosen most for the Hexagon tile map displays.", fig.height=5}
d <- d %>% 
  mutate(certainty = as_factor(certainty)) %>% 
  mutate(replicate_f = as_factor(replicate))

d %>% 
  mutate(Detected = factor(detect_f, 
    levels = c("Detected? Yes", "Detected? No"), 
    labels = c("Yes", "No"))) %>% 
ggplot(aes(x = certainty, fill = Detected)) +  
  scale_fill_manual(values = detect_f_colors) +
  geom_bar() + facet_grid(type ~ trend) +
  theme(legend.position = "bottom") + xlab("Level of certainty")
```

## Reason

XXX merge with accuracy section above and link to table 3 
Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons. 
"Colour trend across the areas" was the most common selection for NW-SE trend displays.

The reasons chosen by participants from the list provided to them varied more when viewing choropleth displays than the hexagon tile map.
The hexagon tile map displays resulted in "Clusters of colour" as the most common choice made by participants.

The choice "None of these reasons" was used as the default value to minimise noise from participants who did not select a response.

```{r reason, results = "asis"}
# Qualitative analysis of reason
d %>% 
  mutate(reason = ifelse(reason =="0.0", "no reason", reason)) %>% 
  mutate(Detected = ifelse(detect_f == "Detected? Yes", "Yes", "No"),
    Trend = trend) %>% 
  group_by(Trend, Detected, type) %>% 
  count(reason) %>% 
  mutate(prop = round(n/sum(n), 2), r_prop = paste0(reason, ":", prop)) %>% 
  top_n(1, n) %>% summarise(reasons = paste(reason, collapse=", ")) %>% 
  pivot_wider(names_from = c("type"), values_from = c("reasons")) %>% 
  ungroup() %>% 
  knitr::kable(., format = "latex", booktabs = TRUE,
    linesep = c("", "\\addlinespace", "", "\\addlinespace",""),
    caption = "The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps. The facets show whether or not the choice was correct.") %>% 
  #kable_styling(bootstrap_options = "hold_position") %>% 
  collapse_rows(., columns = 1)
```

Discussion
============

The intention of this study was to contrast the use of the choropleth map and the hexagon tile map.
The visual inference lineup protocol was employed to contrast the effectiveness of the displays.
The results have shown that overall the use of the hexagon tile map display allows participants to find the data plot in the lineup more often.
Using the visual inference protocol this result can be extended to show that it is a valid alternative display to communicate spatial distributions of population related data.

We expected that the choropleth map would be superior for communicating the spatial pattern of geographic distributions. The data suggest that the participants perform slightly better or equally as well for each replicate in each trend model across the two displays. Table II shows that the difference in the mean detection rate for the two trend models was 0.10.

The differences seen in the \ref{fig:detect-compare} plot and Table. \ref{tab:desc-stats} are reflected in the model results. Surprisingly the difference for the geographic distribution was significant at the 0.05 level.
It also showed that the hexagon tile map display performs marginally better than the choropleth for all trend models. Unexpectedly the detection rate suffers when using a choropleth map to display population related distributions.

While the significance of the difference in detection was the key focus of this experiment, the secondary focus was the time taken by participants. it was expected that the participants may take longer to consider the hexagon tile map distribution but would be able to detect the data plot in the lineup.
The bimodal distributions seen in Fig. \ref{fig:beeswarm} showed very little difference in the mean evaluation times. As the maximum time of all of the distributions approached 60 seconds it cannot be said that the participants' took longer to evaluate the hexagon tile map displays.

The responses to the questions asked of participants included the reason for their choice and the certainty around their choice.
Fig. \ref{tab:reason} shows high levels of certainty of 4 and 5 were chosen by participants when looking at the population distributions in a choropleth map display show that they were over confident when attempting to find the real data plot in the choropleth map displays. Participants performed better on the NW-SE distribution shown in the choropleth display and were reasonably confident about their decisions.
The high levels of the mid range value of 3 could indicate that the participant did not want to provide a response, as this was the default value. Those who chose level 4 or 5 were equally likely to be correct for the three cities lineups, but more likely to be correct than incorrect for the other two trend models.

The colour scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
Due to the consistent colouring of rural areas in a choropleth display, the choice "All areas have similar colours" was most common reason for a participants choice. The All Cities displays coloured the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural colour consistency. 
Choosing "Clusters of colour" was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions. It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays. 
Due to the spatial covariance introduced in the smoothing, groups of similarly coloured hexagons were present in all of the hexagon tile map displays. All Cities and Three Cities distributions of real data trends had distinctly different patterns or red inner-city areas, while some of the plots in each lineup may have shared similar features.

XXX Add limitations - of the method used, and of application to other sets of  geographic areas
XXX extrapolate the results to other modelled outputs beyond cancer statistics to obtain broader coverage. There is considerable value in using a hexagon tile map for showing statistics and modelled output in statistical area levels across Australia or similar.

XXX Add discussion of future work, related to this study.

Conclusion
============

The choropleth map display and the tessellated hexagon tile map have been contrasted using the lineup protocol. The hexagon tile map was significantly more effective for spotting a real population related data trend model hidden in a lineup.

The hexagon tile map display should be considered as an alternative visualisation method when communicating distributions that relate to the population across a set of geographic units. As an additional display to the familiar choropleth map, cancer atlas products may benefit from the opportunity to allow exploration via an alternative display. The spatial distributions used to test these displays were inspired by the real spatially smoothed estimates of the cancer burden on Australian communities. However, this technique may be extended to other population related distributions, such as other diseases.

The increasing population densities of capital cities despite large land area exacerbates the difference in the smallest and largest communities.
The population density structure of Australia can be considered similar to that of Canada, New Zealand and many other countries. Therefore, this display is not only relevant to Australia, but all nations or population distributions that experience densely populated cities separated by vast rural expanses.

Acknowledgment
==============

The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualisations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments. Mitchell O'Hara-Wild was a co-developer of the taipan [@taipan] R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups. We are thankful for the NUMBATs (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.

XXX Decide where this information belongs
==============

The source code to produce this document can be found on [GitHub](https://github.com/srkobakian/experiment/paper).
Supplementary materials have been included to discuss the survey procedures and the lineups that were used.
The full set of images can be found here, too.

The supplementary material contains:

- Additional analysis of the experimental results
- Survey procedure including training materials for the participants
- 24 lineups as images, that were used in the experiment
- 12 data sets used to construct the lineups

The analysis of the work was completed in R [@RCore] with the use of the following packages:

 - For document creation: rmarkdown [@rmarkdown], rticles [@rticles], knitr [@knitr].
 - For lineup creation and data analysis: tidyverse [@tidyverse], nullabor [@nullabor], ggthemes [@ggthemes], RColorBrewer [@RColorBrewer].
 - For image displays: cowplot [@cowplot], png [@png], grid [@grid].
 - For modelling and presentation of models: gstat [@gstat], lme4 [@lme4], kableExtra [@kableExtra].

Ethics approval for the online survey was granted by QUT’s Ethics Committee (Ethics Application Number: 1900000991). All applicants provided informed consent in line with QUT regulations prior to participating in this research.

References {.numbered}
==========

### 2025-07-07 paper/paper.tex
review folder created

@@
-%% template.tex
-%% from
-%% bare_conf.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE!
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-\documentclass[conference,final,]{IEEEtran}
-% Some Computer Society conferences also require the compsoc mode option,
-% but others use the standard conference format.
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
 %
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
+\documentclass[
+]{article}
+\usepackage{amsmath,amssymb}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math} % this also loads fontspec
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at:
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\usepackage[margin=1in]{geometry}
 \usepackage{graphicx}
-
-% *** MATH PACKAGES ***
-%
-%\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-%% BEGIN MY ADDITIONS %%
-
-\usepackage[unicode=true]{hyperref}
-
-\hypersetup{
-            pdftitle={Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics},
-            pdfkeywords={statistics, visual inference, geospatial, population},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-
-% Pandoc toggle for numbering sections (defaults to be off)
-\setcounter{secnumdepth}{5}
-
-% tightlist command for lists without linebreak
+\makeatletter
+\newsavebox\pandoc@box
+\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
+  \sbox\pandoc@box{#1}%
+  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
+  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
+  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
+  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
+  \else\usebox{\pandoc@box}%
+  \fi%
+}
+% Set default figure placement to htbp
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% From pandoc table feature
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
+\setcounter{secnumdepth}{5}
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
 \makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
 \makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-
-% Pandoc citation processing
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-% for Pandoc 2.8 to 2.10.1
-\newenvironment{cslreferences}%
-  {}%
-  {\par}
-% For Pandoc 2.11+
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
 \usepackage{graphicx}
@@
 \usepackage{xcolor}
-
-%% END MY ADDITIONS %%
-
-\hyphenation{op-tical net-works semi-conduc-tor}
+\usepackage{bookmark}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same}
+\hypersetup{
+  pdftitle={Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics},
+  pdfkeywords={statistics, visual inference, geospatial, population},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+
+\title{Comparing the Effectiveness of the Choropleth Map with a Hexagon
+Tile Map for Communicating Cancer Statistics}
+\author{}
+\date{\vspace{-2.5em}}
 
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-\title{Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics}
-
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-
-\author{
-
-%% ---- classic IEEETrans wide authors' list ----------------
- % -- end affiliation.wide
-%% ----------------------------------------------------------
-
-%% ---- classic IEEETrans one column per institution --------
- %% -- end if/affiliation.institution-columnar
-%% ----------------------------------------------------------
-
-%% ---- one column per author, classic/default IEEETrans ----
- % -- beg affiliation.author-columnar
-  %% -- beg for/affiliation.institution.author
-\IEEEauthorblockN{
-Stephanie Kobakian
-}
-\IEEEauthorblockA{Queensland University of Technology\\
-Science and Engineering Faculty\\
-Brisbane, Australia
-\\stephanie.kobakian@qut.edu.au
-}
- %% -- end for/affiliation.institution.author
-\and
-  %% -- beg for/affiliation.institution.author
-\IEEEauthorblockN{
-Dianne Cook
-}
-\IEEEauthorblockA{Monash University\\
-Econometrics and Business Statistics Faculty\\
-Melbourne, Australia
-\\dicook@monash.edu
-}
- %% -- end for/affiliation.institution.author
- %% -- end for/affiliation.institution
- %% -- end if/affiliation.institution-columnar
-%% ----------------------------------------------------------
-
-}
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-%
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3},
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
 \maketitle
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract
 \begin{abstract}
-The choropleth map display is commonly used for communicating spatial distributions across geographic areas.
-However, when choropleths are used the size of the geographic units will influence the understanding of the distribution derived by map users.
-The hexagon tile map is presented as an alternative display for visualizing population related distributions effectively.
-Visual inference is used to measure the power of the hexagon tile map design, and the choropleth is used as a comparison.
-The hexagon tile map display is tested using a distribution that is directly related to the geography, with values monotonically increasing from the North-West to South-East areas of Australia.
-This study finds in a hexagon tile map lineup the single map that contains a population related distribution is detected with greater probability than the same data displayed in a choropleth map.
-These findings should encourage map creators to implement alternative displays and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
+The choropleth map display is commonly used for communicating spatial
+distributions across geographic areas. However, when choropleths are
+used the size of the geographic units will influence the understanding
+of the distribution derived by map users. The hexagon tile map is
+presented as an alternative display for visualizing population related
+distributions effectively. Visual inference is used to measure the power
+of the hexagon tile map design, and the choropleth is used as a
+comparison. The hexagon tile map display is tested using a distribution
+that is directly related to the geography, with values monotonically
+increasing from the North-West to South-East areas of Australia. This
+study finds in a hexagon tile map lineup the single map that contains a
+population related distribution is detected with greater probability
+than the same data displayed in a choropleth map. These findings should
+encourage map creators to implement alternative displays and consider a
+hexagon tile map when presenting spatial distributions of heterogeneous
+areas.
 \end{abstract}
 
-% keywords
-\begin{IEEEkeywords}
-statistics; visual inference; geospatial; population
-\end{IEEEkeywords}
-
-% use for special paper notices
-
-% make the title area
-\maketitle
-
-% no keywords
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-This study compares the effectiveness of the spatial display, a hexagon tile map, against the standard, a choropleth map, for communicating information about disease statistics.
-The choropleth map is the traditional method for visualizing aggregated statistics across administrative boundaries.
-The hexagon tile map builds on existing displays, such as the cartogram, and tessellated hexagon displays.
-A hexagon tile map forgoes the familiar boundaries, in favor of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location.
-It differs in the relaxed requirement to have connected hexagons, and allows sparsely located hexagons.
-This type of display may be useful for other countries, and other purposes.
-The algorithm to construct a hexagon tile map is available in the R package sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]}.
-
-The hexagon tile map was designed for Australia, motivated by a need to display spatial statistics for the Australian Cancer Atlas.
-None of the existing approaches for creating cartograms or hexagon tiling perform well for the Australian landscape, which has vast open spaces and concentrations of population in small regions clustered on the coastlines.
-
-The Australian Cancer Atlas {[}\protect\hyperlink{ref-atlas}{2}{]} is an online interactive web tool created to explore the burden of cancer on Australian communities.
-There are many cancer types to be explored individually or aggregated.
-The Australian Cancer Atlas allows users to explore the patterns in the distributions of cancer statistics over the geographic space of Australia.
-It uses a choropleth map display and diverging color scheme to draw attention to relationships between neighboring areas.
-The hexagon tile map may be a useful alternative display to enhance the atlas.
-
-The experiment was conducted using the lineup protocol, a visual inference procedure {[}\protect\hyperlink{ref-GIIV}{3}{]}, to objectively test the effectiveness of the two displays.
-
-The paper is organised as follows.
-The next section discusses the background of geographic data display and visual inference procedures.
-The \protect\hyperlink{methodology}{Methodology} section describes the methods for conducting the experiment and analysing the results.
-The results are summarized in the \protect\hyperlink{results}{Results} section.
-
-\hypertarget{background}{%
-\section{Background}\label{background}}
-
-\hypertarget{spatial-data-displays}{%
-\subsection{Spatial data displays}\label{spatial-data-displays}}
-
-Spatial visualisations communicate the distribution of statistics over geographic landscapes.
-The choropleth map {[}\protect\hyperlink{ref-EI}{4}{]}, {[}\protect\hyperlink{ref-BCM}{5}{]} is a traditional display.
-It is used to present statistics that have been aggregated on geographic units.
-Creating a choropleth map involves drawing polygons representing the administrative boundaries, and filling with colour mapped to the value of the statistic.
-The choropleth map places the statistic in the context of the spatial domain, so that the reader can see whether there are spatial trends, clusters or anomalies.
-This is important for digesting disease patterns.
-If there is a trend it may imply that the disease is spreading from one location to another.
-If there is a cluster, or an anomaly, there may be a localized outbreak of the disease.
-Aggregating the statistic on administrative units, provides a level of privacy to individuals, while allowing the impact of the disease on the community to be analyzed.
+\section{Introduction}\label{introduction}
+
+This study compares the effectiveness of the spatial display, a hexagon
+tile map, against the standard, a choropleth map, for communicating
+information about disease statistics. The choropleth map is the
+traditional method for visualizing aggregated statistics across
+administrative boundaries. The hexagon tile map builds on existing
+displays, such as the cartogram, and tessellated hexagon displays. A
+hexagon tile map forgoes the familiar boundaries, in favor of
+representing each geographic unit as an equally sized hexagon, placed
+approximately in the correct spatial location. It differs in the relaxed
+requirement to have connected hexagons, and allows sparsely located
+hexagons. This type of display may be useful for other countries, and
+other purposes. The algorithm to construct a hexagon tile map is
+available in the R package sugarbag {[}\citeproc{ref-sugarbag}{1}{]}.
+
+The hexagon tile map was designed for Australia, motivated by a need to
+display spatial statistics for the Australian Cancer Atlas. None of the
+existing approaches for creating cartograms or hexagon tiling perform
+well for the Australian landscape, which has vast open spaces and
+concentrations of population in small regions clustered on the
+coastlines.
+
+The Australian Cancer Atlas {[}\citeproc{ref-atlas}{2}{]} is an online
+interactive web tool created to explore the burden of cancer on
+Australian communities. There are many cancer types to be explored
+individually or aggregated. The Australian Cancer Atlas allows users to
+explore the patterns in the distributions of cancer statistics over the
+geographic space of Australia. It uses a choropleth map display and
+diverging color scheme to draw attention to relationships between
+neighboring areas. The hexagon tile map may be a useful alternative
+display to enhance the atlas.
+
+The experiment was conducted using the lineup protocol, a visual
+inference procedure {[}\citeproc{ref-GIIV}{3}{]}, to objectively test
+the effectiveness of the two displays.
+
+The paper is organised as follows. The next section discusses the
+background of geographic data display and visual inference procedures.
+The \hyperref[methodology]{Methodology} section describes the methods
+for conducting the experiment and analysing the results. The results are
+summarized in the \hyperref[results]{Results} section.
+
+\section{Background}\label{background}
+
+\subsection{Spatial data displays}\label{spatial-data-displays}
+
+Spatial visualisations communicate the distribution of statistics over
+geographic landscapes. The choropleth map {[}\citeproc{ref-EI}{4}{]},
+{[}\citeproc{ref-BCM}{5}{]} is a traditional display. It is used to
+present statistics that have been aggregated on geographic units.
+Creating a choropleth map involves drawing polygons representing the
+administrative boundaries, and filling with colour mapped to the value
+of the statistic. The choropleth map places the statistic in the context
+of the spatial domain, so that the reader can see whether there are
+spatial trends, clusters or anomalies. This is important for digesting
+disease patterns. If there is a trend it may imply that the disease is
+spreading from one location to another. If there is a cluster, or an
+anomaly, there may be a localized outbreak of the disease. Aggregating
+the statistic on administrative units, provides a level of privacy to
+individuals, while allowing the impact of the disease on the community
+to be analyzed.
 
@@
 
-The choropleth map is an effective spatial display if the size of the geographic units is relatively uniform.
-This is not the case for most countries.
-Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips.
-Fig.
-\ref{fig:thyroid-choro} shows the choropleth map of thyroid cancer rates in Australia.
-The choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population related distribution of the statistic {[}\protect\hyperlink{ref-CBATCC}{6}{]}.
-\emph{Land doesn't get cancer, people do} -- a more effective way to communicate the spatial distributions of cancer statistics is needed.
-
-A cartogram is a general solution for better displaying a population-based statistic.
-It transforms the geographic map base to reflect the population in the geographic region, while preserving some aspects of the geographic location.
-There are several cartogram algorithms {[}\protect\hyperlink{ref-ACTUC}{7}{]}, {[}\protect\hyperlink{ref-CBATCC}{6}{]}; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
-The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units but can result in losing the familiar geographic information.
-For Australia, the transformations warp the country so that it is no longer recognizable.
-
-Alternative algorithms make various trade offs between familiar shapes and representation of geographic units.
-The non-contiguous cartogram method {[}\protect\hyperlink{ref-NAC}{8}{]} keeps the shapes of geographic units intact, and changes the size of the shape.
-This method disconnects areas creating empty space on the display losing the continuity of the spatial display of the statistic.
-The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{7}{]} represents each unit as a circle, sized according to the value of the statistic.
-The neighbour relationships are mostly maintained by how the circles touch.
-A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{9}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{10}{]}.
-There have been thorough reviews of the array of methods, as suitable for cancer atlas displays {[}\protect\hyperlink{ref-review}{11}{]}, {[}\protect\hyperlink{ref-BCM}{5}{]}.
+The choropleth map is an effective spatial display if the size of the
+geographic units is relatively uniform. This is not the case for most
+countries. Size heterogeneity in administrative units is particularly
+extreme in Australia: most of the landscape of Australia is sparsely
+settled, with the population densely clustered into the narrow coastal
+strips. Fig. \ref{fig:thyroid-choro} shows the choropleth map of thyroid
+cancer rates in Australia. The choropleth map focuses attention on the
+geography, and for heterogeneously sized areas it presents a biased view
+of the population related distribution of the statistic
+{[}\citeproc{ref-CBATCC}{6}{]}. \emph{Land doesn't get cancer, people
+do} -- a more effective way to communicate the spatial distributions of
+cancer statistics is needed.
+
+A cartogram is a general solution for better displaying a
+population-based statistic. It transforms the geographic map base to
+reflect the population in the geographic region, while preserving some
+aspects of the geographic location. There are several cartogram
+algorithms {[}\citeproc{ref-ACTUC}{7}{]},
+{[}\citeproc{ref-CBATCC}{6}{]}; each involves shifting the boundaries of
+geographic units, using the value of the statistic to increase or
+decrease the area taken by the geographic unit on the map. The changes
+to the boundaries result in cartograms that accurately communicate
+population by map area for each of the geographic units but can result
+in losing the familiar geographic information. For Australia, the
+transformations warp the country so that it is no longer recognizable.
+
+Alternative algorithms make various trade offs between familiar shapes
+and representation of geographic units. The non-contiguous cartogram
+method {[}\citeproc{ref-NAC}{8}{]} keeps the shapes of geographic units
+intact, and changes the size of the shape. This method disconnects areas
+creating empty space on the display losing the continuity of the spatial
+display of the statistic. The Dorling cartogram
+{[}\citeproc{ref-ACTUC}{7}{]} represents each unit as a circle, sized
+according to the value of the statistic. The neighbour relationships are
+mostly maintained by how the circles touch. A similar approach was
+pioneered by Raisz {[}\citeproc{ref-RSCW}{9}{]}, using rectangles that
+tile to align borders of neighbours {[}\citeproc{ref-CDWCS}{10}{]}.
+There have been thorough reviews of the array of methods, as suitable
+for cancer atlas displays {[}\citeproc{ref-review}{11}{]},
+{[}\citeproc{ref-BCM}{5}{]}.
 
@@
 
-The hexagon tile map algorithm, automatically matches spatial regions to their nearest hexagon tile, from a grid of tiles.
-It has the effect of spreading out the inner city areas while maintaining the spatial locations or regions in remote areas.
-The algorithm is available in the R package, sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]}.
-Fig.
-\ref{fig:thyroid-hex} shows the hexagon tile map.
-Colour maps from substantially below average (blue) to substantially above average (red) rates.
-The inner city areas have expanded, making it possible to see the cancer incidence in the small, densely populated areas.
-Remote regions are represented by isolated hexagons, which is not ideal, but maintains the spatial location of these data values.
-It is of interest to know how well the spatial distribution is perceived for this display, in comparison to the choropleth.
-
-\hypertarget{visual-inference}{%
-\subsection{Visual Inference}\label{visual-inference}}
-
-In order to assess the effectiveness of the hexagon tile map, the lineup protocol {[}\protect\hyperlink{ref-GIIV}{3}{]},{[}\protect\hyperlink{ref-BCHLLSW09}{12}{]} from visual inference procedures is employed.
-The approach mirrors classical statistical inference.
-The procedures for doing a power comparison of competing plot designed, outlined in {[}\protect\hyperlink{ref-GTPCCD}{13}{]}, are followed.
-
-In classical statistical inference hypothesis testing is conducted by comparing the value of a test statistic on a standard reference distribution, computed assuming the null hypothesis is true.
-If the value is extreme, the null hypothesis is rejected, because the test statistic value is unlikely to have been so extreme if it was true.
-In the lineup protocol, the plot plays the role of the test statistic, and the data plot is embedded in a field of null plots.
-Defining the plot using a grammar of graphics {[}\protect\hyperlink{ref-ggplot2}{14}{]} makes it a functional mapping of the variables and thus, it can be considered to be a statistic.
-With the same data, two different plots can be considered to be competing statistics, one possibly a more powerful statistic than the other.
-
-To do hypothesis testing with the lineup protocol requires human evaluation.
-The human judge is required to identify the most different plot among the field of plots.
-If this corresponds to the data plot -- the test statistic -- the null hypothesis is rejected.
-It means that the data plot is extreme relative to the reference distribution of null plots.
-
-The null hypothesis is explicitly provided by the grammatical plot description.
-For example, if a histogram is the plot type being used, the null might be that the underlying distribution of the data is a Gaussian.
-Null data would be generated by simulating from a normal model, with the same mean and standard deviation as the data.
-In practice, the null hypothesis used is generic, such as \emph{there is NO structure or a pattern in the plot}, and contrasted to an alternative that there is structure.
-
-The chance that an observer picks the data plot out of a lineup of size \(m\) plots accidentally, if the null hypothesis is true is \(1/m\).
-With \(K\) observers, the probability of \(k\) randomly choosing the data plot, roughly follows a binomial distribution with \(p=1/m\).
-Fig.
-\ref{fig:lineup} shows a lineup of the hexagon tile map, of size \(m=12\).
-Plot 3 is the data plot, and the remaining 11 are plots of null data.
+The hexagon tile map algorithm, automatically matches spatial regions to
+their nearest hexagon tile, from a grid of tiles. It has the effect of
+spreading out the inner city areas while maintaining the spatial
+locations or regions in remote areas. The algorithm is available in the
+R package, sugarbag {[}\citeproc{ref-sugarbag}{1}{]}. Fig.
+\ref{fig:thyroid-hex} shows the hexagon tile map. Colour maps from
+substantially below average (blue) to substantially above average (red)
+rates. The inner city areas have expanded, making it possible to see the
+cancer incidence in the small, densely populated areas. Remote regions
+are represented by isolated hexagons, which is not ideal, but maintains
+the spatial location of these data values. It is of interest to know how
+well the spatial distribution is perceived for this display, in
+comparison to the choropleth.
+
+\subsection{Visual Inference}\label{visual-inference}
+
+In order to assess the effectiveness of the hexagon tile map, the lineup
+protocol {[}\citeproc{ref-GIIV}{3}{]},{[}\citeproc{ref-BCHLLSW09}{12}{]}
+from visual inference procedures is employed. The approach mirrors
+classical statistical inference. The procedures for doing a power
+comparison of competing plot designed, outlined in
+{[}\citeproc{ref-GTPCCD}{13}{]}, are followed.
+
+In classical statistical inference hypothesis testing is conducted by
+comparing the value of a test statistic on a standard reference
+distribution, computed assuming the null hypothesis is true. If the
+value is extreme, the null hypothesis is rejected, because the test
+statistic value is unlikely to have been so extreme if it was true. In
+the lineup protocol, the plot plays the role of the test statistic, and
+the data plot is embedded in a field of null plots. Defining the plot
+using a grammar of graphics {[}\citeproc{ref-ggplot2}{14}{]} makes it a
+functional mapping of the variables and thus, it can be considered to be
+a statistic. With the same data, two different plots can be considered
+to be competing statistics, one possibly a more powerful statistic than
+the other.
+
+To do hypothesis testing with the lineup protocol requires human
+evaluation. The human judge is required to identify the most different
+plot among the field of plots. If this corresponds to the data plot --
+the test statistic -- the null hypothesis is rejected. It means that the
+data plot is extreme relative to the reference distribution of null
+plots.
+
+The null hypothesis is explicitly provided by the grammatical plot
+description. For example, if a histogram is the plot type being used,
+the null might be that the underlying distribution of the data is a
+Gaussian. Null data would be generated by simulating from a normal
+model, with the same mean and standard deviation as the data. In
+practice, the null hypothesis used is generic, such as \emph{there is NO
+structure or a pattern in the plot}, and contrasted to an alternative
+that there is structure.
+
+The chance that an observer picks the data plot out of a lineup of size
+\(m\) plots accidentally, if the null hypothesis is true is \(1/m\).
+With \(K\) observers, the probability of \(k\) randomly choosing the
+data plot, roughly follows a binomial distribution with \(p=1/m\). Fig.
+\ref{fig:lineup} shows a lineup of the hexagon tile map, of size
+\(m=12\). Plot 3 is the data plot, and the remaining 11 are plots of
+null data.
 
@@
 
-In order to determine the effectiveness of a type of display, this probability is less relevant than the overall proportion of observers who pick the data plot, \(k/K\).
-The power of the test statistic (data plot) is provided by this proportion.
-Power in a statistical sense is the ability of the statistic to \emph{produce a rejection} of the null hypothesis, if it is indeed \emph{not true}.
-With the same data plotted using two different displays, the display with the highest proportion of people who choose the data plot would be considered to be the most powerful statistic.
-
-\hypertarget{methodology}{%
-\section{Methodology}\label{methodology}}
-
-This study aims to answer two key questions around the presentation of spatial distributions:
+In order to determine the effectiveness of a type of display, this
+probability is less relevant than the overall proportion of observers
+who pick the data plot, \(k/K\). The power of the test statistic (data
+plot) is provided by this proportion. Power in a statistical sense is
+the ability of the statistic to \emph{produce a rejection} of the null
+hypothesis, if it is indeed \emph{not true}. With the same data plotted
+using two different displays, the display with the highest proportion of
+people who choose the data plot would be considered to be the most
+powerful statistic.
+
+\section{Methodology}\label{methodology}
+
+This study aims to answer two key questions around the presentation of
+spatial distributions:
 
@@
 \item
-  Are spatial disease trends that impact highly populated small areas detected with higher accuracy, when viewed in a hexagon tile map?
-\item
-  Are people faster in detecting spatial disease trends that impact highly populated small areas when using a hexagon tile map?
+  Are spatial disease trends that impact highly populated small areas
+  detected with higher accuracy, when viewed in a hexagon tile map?
+\item
+  Are people faster in detecting spatial disease trends that impact
+  highly populated small areas when using a hexagon tile map?
 \end{enumerate}
 
-Additional considerations when completing this experimental task included the difficulty experienced by participants and the certainty they had in their decision.
-
-Australia is used for the study, with Statistical Area 3 (SA3) {[}\protect\hyperlink{ref-abs2016}{15}{]} as the geographic units.
-The results should apply broadly to any other geographic area of interest.
-
-\hypertarget{experimental-factors}{%
-\subsection{Experimental factors}\label{experimental-factors}}
-
-The primary factor in the experiment is the plot type.
-The secondary factor is a trend model.
-Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to do well, and two with differing level of inner city hot spots.
-These latter two reflect the structure seen in the thyroid cancer data (Fig.
-\ref{fig:thyroid}).
-This produces six treatment levels:
+Additional considerations when completing this experimental task
+included the difficulty experienced by participants and the certainty
+they had in their decision.
+
+Australia is used for the study, with Statistical Area 3 (SA3)
+{[}\citeproc{ref-abs2016}{15}{]} as the geographic units. The results
+should apply broadly to any other geographic area of interest.
+
+\subsection{Experimental factors}\label{experimental-factors}
+
+The primary factor in the experiment is the plot type. The secondary
+factor is a trend model. Three trend models were developed, one
+mirroring a large spatial trend for which the choropleth would be
+expected to do well, and two with differing level of inner city hot
+spots. These latter two reflect the structure seen in the thyroid cancer
+data (Figures \ref{fig:thyroid-choro}, \ref{fig:thyroid-hex}). This
+produces six treatment levels:
 
@@
 \item
-  Trend: \emph{South-East to North-West; Locations in three population centres; Locations in multiple population centres, }
+  Trend: \emph{South-East to North-West; Locations in three population
+  centres; Locations in multiple population centres, }
 \end{itemize}
 
-Data is generated for each of the trend models, with four replicates, and each displayed both as a choropleth and as a hexagon tile map, which yields 12 data sets, and 24 data plots.
-This set of displays is divided in half, providing two sets of 12 displays, Group A and Group B.
-Participants were randomly allocated to Group A or B.
-Participants saw a data set only once, either as a choropleth or as a hexagon tile map.
-Table \ref{fig:exp-design} summarises the design and the allocation of the displays.
+Data is generated for each of the trend models, with four replicates,
+and each displayed both as a choropleth and as a hexagon tile map, which
+yields 12 data sets, and 24 data plots. This set of displays is divided
+in half, providing two sets of 12 displays, Group A and Group B.
+Participants were randomly allocated to Group A or B. Participants saw a
+data set only once, either as a choropleth or as a hexagon tile map.
+Table \ref{fig:exp-design} summarises the design and the allocation of
+the displays.
 
@@
 
-\hypertarget{generating-null-data}{%
-\subsection{Generating null data}\label{generating-null-data}}
-
-Null data needs to be data with no (interesting) structure.
-In most scenarios, permutation is the main approach for generating null plots.
-It is used to break association between variables, while maintaining marginal distributions.
-This is too simple for spatial data.
-In spatial data, a key feature is the spatial dependence or smoothness over the landscape.
-To do something simple, like permute the values relative to the geographic location would produce null plots which are too chaotic, and the data plot will be recognisable for its smoothness rather than any structure of interest.
-
-For spatial data, null data is stationary data, where the mean, variance and spatial dependence are constant over the geographic units.
-Stationary data is specified by a variogram model {[}\protect\hyperlink{ref-POG}{16}{]}.
-Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots.
-The parameters for the Gaussian model were sill=1, range=0.3 with the variance generated by a standard normal distribution.
-
-The R package \texttt{gstat} {[}\protect\hyperlink{ref-gstat}{17}{]} was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
-
-The null model imposed by our hypothesis suggests that neighbors are related.
-The randomness induced when generating the null data was smoothed to mirror the practices employed by the Australian Cancer Atlas statisticians.
-In these 12 sets of data, each of the 12 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas, without implementing uncertainty via transparency.
-
-A list of neighbors for each geographic unit was generated to use when smoothing the distributions.
-For each geographic unit the same spatial smoother was applied in each layer of smoothing.
-It kept half of the units' previous value, and derived the new half as the mean of the values of its neighbors at the previous layer of smoothing.
-
-This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the thyroid cancer distribution (Fig. \ref{fig:thyroid}).
-
-\hypertarget{generating-lineups}{%
-\subsection{Generating lineups}\label{generating-lineups}}
-
-For each trend model, four real data displays were created by manipulating the centroid values of each of the SA3 geographic units.
-
-The North West to South East (NW-SE) distribution was created using a linear equation of the centroid longitude and latitude values.
-
-The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia, calculated when creating the hexagon tile map using the sugarbag {[}\protect\hyperlink{ref-sugarbag}{1}{]} package.
-201 of the 336 SA3s were considered greater capital city areas, the values of these areas were increased to create red clusters.
-The amount was chosen to make clusters around the cities visible in the choropleth display even if they were not overtly noticeable.
-
-A similar selection process was applied to the Three Cities' trend model.
-However, for each of the four replicates for the Three Cities trend, a random sample of capital cities was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart.
-Only values of the areas nearest to the three cities were increased to create clusters.
-
-One of the lineup locations was chosen to embed the real trend model map, in each of the four replicates, for the three trend models.
-The location was chosen from a sub sample of the 12 possible locations.
-The chance of reptition using resampling was introduced to prevent participants from inducing the location by elimination, the locations 1, 7, 10 and 11 were not used.
-
-As seen in Fig \ref{fig:exp-design}, the choropleth and hexagon display used the same location for the real data display of the trend model was added to the spatially correlated null values for each lineup.
-Each set of lineup data was used to produce a choropleth map lineup and hexagon tile map lineup.
-These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
-
-For each of the 144 individual maps, the values for each geographic area were rescaled to create a similar color scale from deep blue to dark red within each map.
-This meant at least one geographic unit was coloured dark blue, and at least one was red, in every map display of every lineup.
-
-For the geographic NW-SE distribution, this resulted in the smallest values of the trend model (blue) occurring in Western Australia, the North West of Australia, and the largest values of the trend model (red) occurring in the South East.
-This resulted in Tasmania being colored completely red.
-
-For the population related displays, the clusters in the cities appeared more red than the rest of Australia.
-
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
-
-\hypertarget{data-cleaning}{%
-\subsubsection{Data Cleaning}\label{data-cleaning}}
-
-The first step in the data cleaning process involved checking that survey responses collected for each participants were only included once in the data set.
-The data cleaning process also involved filtering out participants' who did not provide at least three unique choices when considering each of the twelve lineups.
-These participants achieved a detection rate of 0.
-If participants had made various plot choices for the 12 displays they saw they were still included in the dataset.
-
-\hypertarget{descriptive-statistics}{%
-\subsubsection{Descriptive statistics}\label{descriptive-statistics}}
-
-Basic descriptive statistics were used to contrast the detection rate for the two types of displays.
-Comparison was also made across the trend models, contrasting the mean and standard detection rate for each group, who had seen the different map display type for each replicate.
-
-Side-by-side dot plots were made of accuracy (efficiency) against map type, faceted by trend model type.
-
-Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.
-
-Plots will be made in R {[}\protect\hyperlink{ref-RCore}{18}{]}, with the \texttt{ggplot2} package {[}\protect\hyperlink{ref-ggplot2}{14}{]}.
-
-\hypertarget{modelling}{%
-\subsubsection{Modelling}\label{modelling}}
-
-The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R {[}\protect\hyperlink{ref-RCore}{18}{]} \texttt{glmer()} function in the \texttt{lme4} {[}\protect\hyperlink{ref-lme4}{19}{]} package implements generalised linear mixed effect models.
-The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
+\subsection{Generating null data}\label{generating-null-data}
+
+Null data needs to be data with no (interesting) structure. In most
+scenarios, permutation is the main approach for generating null plots.
+It is used to break association between variables, while maintaining
+marginal distributions. This is too simple for spatial data. In spatial
+data, a key feature is the spatial dependence or smoothness over the
+landscape. To do something simple, like permute the values relative to
+the geographic location would produce null plots which are too chaotic,
+and the data plot will be recognisable for its smoothness rather than
+any structure of interest.
+
+For spatial data, null data is stationary data, where the mean, variance
+and spatial dependence are constant over the geographic units.
+Stationary data is specified by a variogram model
+{[}\citeproc{ref-POG}{16}{]}. Simulating from a variogram model, where
+the spatial dependence is specified, generates the stationary spatial
+data used for the null plots. The parameters for the Gaussian model were
+sill=1, range=0.3 with the variance generated by a standard normal
+distribution.
+
+The R package \texttt{gstat} {[}\citeproc{ref-gstat}{17}{]} was used to
+simulate 144 null sets, 12 data sets for each plot in a lineup, and 12
+sets for 12 lineups.
+
+The null model imposed by our hypothesis suggests that neighbors are
+related. The randomness induced when generating the null data was
+smoothed to mirror the practices employed by the Australian Cancer Atlas
+statisticians. In these 12 sets of data, each of the 12 maps were
+smoothed several times to replicate the spatial autocorrelation seen in
+cancer data sets presented in the Australian Cancer Atlas, without
+implementing uncertainty via transparency.
+
+A list of neighbors for each geographic unit was generated to use when
+smoothing the distributions. For each geographic unit the same spatial
+smoother was applied in each layer of smoothing. It kept half of the
+units' previous value, and derived the new half as the mean of the
+values of its neighbors at the previous layer of smoothing.
+
+This smoothing allowed neighbors to be related to each other, but also
+allowed outliers, and showed distributions similar to the thyroid cancer
+distribution (Figures \ref{fig:thyroid-choro}, \ref{fig:thyroid-hex}).
+
+\subsection{Generating lineups}\label{generating-lineups}
+
+For each trend model, four real data displays were created by
+manipulating the centroid values of each of the SA3 geographic units.
+
+The North West to South East (NW-SE) distribution was created using a
+linear equation of the centroid longitude and latitude values.
+
+The All Cities trend model was created using the distance from the
+centroid of each geographic unit to the closest capital city in
+Australia, calculated when creating the hexagon tile map using the
+sugarbag {[}\citeproc{ref-sugarbag}{1}{]} package. 201 of the 336 SA3s
+were considered greater capital city areas, the values of these areas
+were increased to create red clusters. The amount was chosen to make
+clusters around the cities visible in the choropleth display even if
+they were not overtly noticeable.
+
+A similar selection process was applied to the Three Cities' trend
+model. However, for each of the four replicates for the Three Cities
+trend, a random sample of capital cities was taken from Sydney,
+Brisbane, Melbourne, Adelaide, Perth, and Hobart. Only values of the
+areas nearest to the three cities were increased to create clusters.
+
+One of the lineup locations was chosen to embed the real trend model
+map, in each of the four replicates, for the three trend models. The
+location was chosen from a sub sample of the 12 possible locations. The
+chance of reptition using resampling was introduced to prevent
+participants from inducing the location by elimination, the locations 1,
+7, 10 and 11 were not used.
+
+As seen in Fig \ref{fig:exp-design}, the choropleth and hexagon display
+used the same location for the real data display of the trend model was
+added to the spatially correlated null values for each lineup. Each set
+of lineup data was used to produce a choropleth map lineup and hexagon
+tile map lineup. These matched pairs were split between Group A and
+Group B according to the 2 x 3 factor experimental design depicted in
+\ref{fig:exp-design}.
+
+For each of the 144 individual maps, the values for each geographic area
+were rescaled to create a similar color scale from deep blue to dark red
+within each map. This meant at least one geographic unit was coloured
+dark blue, and at least one was red, in every map display of every
+lineup.
+
+For the geographic NW-SE distribution, this resulted in the smallest
+values of the trend model (blue) occurring in Western Australia, the
+North West of Australia, and the largest values of the trend model (red)
+occurring in the South East. This resulted in Tasmania being colored
+completely red.
+
+For the population related displays, the clusters in the cities appeared
+more red than the rest of Australia.
+
+\subsection{Analysis}\label{analysis}
+
+\subsubsection{Data Cleaning}\label{data-cleaning}
+
+The first step in the data cleaning process involved checking that
+survey responses collected for each participants were only included once
+in the data set. The data cleaning process also involved filtering out
+participants' who did not provide at least three unique choices when
+considering each of the twelve lineups. These participants achieved a
+detection rate of 0. If participants had made various plot choices for
+the 12 displays they saw they were still included in the dataset.
+
+\subsubsection{Descriptive statistics}\label{descriptive-statistics}
+
+Basic descriptive statistics were used to contrast the detection rate
+for the two types of displays. Comparison was also made across the trend
+models, contrasting the mean and standard detection rate for each group,
+who had seen the different map display type for each replicate.
+
+Side-by-side dot plots were made of accuracy (efficiency) against map
+type, faceted by trend model type.
+
+Similar plots were made of the feedback and demographic variables -
+reason for choice, reported difficulty, gender, age, education, having
+lived in Australia - against the design variables.
+
+Plots will be made in R {[}\citeproc{ref-RCore}{18}{]}, with the
+\texttt{ggplot2} package {[}\citeproc{ref-ggplot2}{14}{]}.
+
+\subsubsection{Modelling}\label{modelling}
+
+The likelihood of detecting the data plot in the lineup can be modelled
+using a linear mixed effects model. The R {[}\citeproc{ref-RCore}{18}{]}
+\texttt{glmer()} function in the \texttt{lme4}
+{[}\citeproc{ref-lme4}{19}{]} package implements generalised linear
+mixed effect models. The model used includes the two main effects map
+type and trend model, which gives the fixed effects model to be:
 
@@
 
-where \(y_{ij} = 0, 1\) is the logg odds for whether the subject detected the data plot, \(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect, \(\delta_j\) is the trend model effect.
-We are allowing for an interaction between map type and trend model as the response is binary, so a logistic model was used.
-As each participant provides results from 12 lineups, this model can account for each individual participants' abilities as it includes a subject-specific random intercept.
-
-The model specifies a logistic link, this means the predicted values from the \texttt{glmer} model should be back-transformed to fit between 0 and 1.
-The predictions \(\widehat{p}(\eta)\) are transformed to be probabilities between 0 and 1 with the link specified below:
-
-\[\widehat{p}(\eta) = \frac{e^{\eta}}{1 + e^{\eta}}\] \label{eq:transform}
-\[\eta = f(\tau_i,\delta_j)\]
-
-\hypertarget{web-application-to-collect-responses}{%
-\subsection{Web application to collect responses}\label{web-application-to-collect-responses}}
-
-The taipan {[}\protect\hyperlink{ref-taipan}{20}{]} package for R was used to create the survey web application.
-This structure was altered to collect responses regarding participants demographics and their survey responses.
-The survey app contained three tabs.
-Participants were first asked for their demographics their Figure Eight contributor ID, and their consent to the responses being used for analysis.
-The demographics collected included participants' preferred pronoun, the highest level of education achieved, their age range and whether they had lived in Australia.
-
-After submitting these responses, the survey application switched to the tab of lineups and associated questions.
-This allowed participants to easily move through the twelve displays and provide their choice, reason for their choice, and level of certainty.
-
-When participants completed the twelve evaluations the survey application triggered a data analysis script.
-This created a data set with one row per evaluation.
-Containing the responses to the three questions.
-The script also added the title of the image, which indicated the type of map display, the type of distribution hidden in the lineup, and the location of the data plot.
-It also calculated the time taken by participant to view each lineup.
-
-Each participant used the internet to access the survey.
-The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results.
-The application connected to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{21}{]} R package when participants opened the application, and interacted again when participants chose to submit the survey.
-At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-Participants were recruited from the Figure Eight crowdsourcing platform {[}\protect\hyperlink{ref-figeight}{22}{]} to evaluate lineups.
-The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
-Potential participants needed to have achieved level 2 or level 3 from prior work on the platform.
-All participants were at least 18 years old.
-
-Participants were allocated to either group A or group B when they proceeded to the survey web application.
-There were 92 participants involved in the study.
-All participants read introductory materials, and were trained using three test displays, to orient them to the evaluation task.
-All participants who completed the task were compensated \$AUD5 for their time, via the Figure Eight payment system.
-
-A pilot study was conducted in the working group of the Econometrics and Business Statistics Department of Monash University.
-This allowed us to estimate the effect size, and thus decide on number of participants to collect responses from.
-
-\hypertarget{demographic-data-collection}{%
-\subsection{Demographic data collection}\label{demographic-data-collection}}
-
-Each participant answered demographic questions and provided consent before evaluating the lineups.
+where \(y_{ij} = 0, 1\) is the logg odds for whether the subject
+detected the data plot, \(\mu\) is the overall mean, \(\tau_i, i=1,2\)
+is the map type effect, \(\delta_j\) is the trend model effect. We are
+allowing for an interaction between map type and trend model as the
+response is binary, so a logistic model was used. As each participant
+provides results from 12 lineups, this model can account for each
+individual participants' abilities as it includes a subject-specific
+random intercept.
+
+The model specifies a logistic link, this means the predicted values
+from the \texttt{glmer} model should be back-transformed to fit between
+0 and 1. The predictions \(\widehat{p}(\eta)\) are transformed to be
+probabilities between 0 and 1 with the link specified below:
+
+\[\widehat{p}(\eta) = \frac{e^{\eta}}{1 + e^{\eta}}\]
+\label{eq:transform} \[\eta = f(\tau_i,\delta_j)\]
+
+\subsection{Web application to collect
+responses}\label{web-application-to-collect-responses}
+
+The taipan {[}\citeproc{ref-taipan}{20}{]} package for R was used to
+create the survey web application. This structure was altered to collect
+responses regarding participants demographics and their survey
+responses. The survey app contained three tabs. Participants were first
+asked for their demographics their Figure Eight contributor ID, and
+their consent to the responses being used for analysis. The demographics
+collected included participants' preferred pronoun, the highest level of
+education achieved, their age range and whether they had lived in
+Australia.
+
+After submitting these responses, the survey application switched to the
+tab of lineups and associated questions. This allowed participants to
+easily move through the twelve displays and provide their choice, reason
+for their choice, and level of certainty.
+
+When participants completed the twelve evaluations the survey
+application triggered a data analysis script. This created a data set
+with one row per evaluation. Containing the responses to the three
+questions. The script also added the title of the image, which indicated
+the type of map display, the type of distribution hidden in the lineup,
+and the location of the data plot. It also calculated the time taken by
+participant to view each lineup.
+
+Each participant used the internet to access the survey. The data
+transfer from the web application to the data set took place using a
+secure link to the googlesheet used to store results. The application
+connected to the googlesheet using the googlesheets
+{[}\citeproc{ref-sheets}{21}{]} R package when participants opened the
+application, and interacted again when participants chose to submit the
+survey. At this time it added the participant's responses to the twelve
+lineup displays as twelve rows of data in the googlesheet.
+
+\subsection{Participants}\label{participants}
+
+Participants were recruited from the Figure Eight crowdsourcing platform
+{[}\citeproc{ref-figeight}{22}{]} to evaluate lineups. The lineup
+protocol expects that the participants are uninvolved judges with no
+prior knowledge of the data, to avoid inadvertently affecting results.
+Potential participants needed to have achieved level 2 or level 3 from
+prior work on the platform. All participants were at least 18 years old.
+
+Participants were allocated to either group A or group B when they
+proceeded to the survey web application. There were 92 participants
+involved in the study. All participants read introductory materials, and
+were trained using three test displays, to orient them to the evaluation
+task. All participants who completed the task were compensated \$AUD5
+for their time, via the Figure Eight payment system.
+
+A pilot study was conducted in the working group of the Econometrics and
+Business Statistics Department of Monash University. This allowed us to
+estimate the effect size, and thus decide on number of participants to
+collect responses from.
+
+\subsection{Demographic data
+collection}\label{demographic-data-collection}
+
+Each participant answered demographic questions and provided consent
+before evaluating the lineups.
 
@@
 
-After completing the 12 evaluations, the participants were asked to submit their responses.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-Responses from 92 participants were collected.
-Five participants did not provide more than three unique choices for the twelve lineups, and their data was removed.
-Set A was evaluated by 42 participants, and 53 evaluated set B.
-This resulted in 1104 evaluations, corresponding to 92 subjects, each evaluating 12 lineups, that were analysed on accuracy and speed.
-The certainty and reasons of subjects in their answers is also examined.
-
-\hypertarget{participant-demographics}{%
-\subsection{Participant demographics}\label{participant-demographics}}
-
-Of the 92 participants, 67 were male, and 25 female. Most participants (56) had a Bachelors degree, 13 had a Masters degree, and the remaining 23 had high school diplomas.
-
-\hypertarget{accuracy}{%
-\subsection{Accuracy}\label{accuracy}}
-
-Fig.
-\ref{fig:detect-compare} displays the average detection rates for the two types of plot separately for each trend model.
-Each trend model was tested using four repetitions, evaluations on the same data set were seen as either choropleths or hexagon tile maps by each group as specified in Table.
-\ref{fig:exp-design}; the detection rates for each display are connected by a line segment.
-The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts.
-One replicate for the All Cities group had similar detection rates for both plot types, the rate of detection using the choropleth map was much higher than other replicates.
-Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map.
-We expected that the choropleth map would be superior for the type of spatial pattern, but the data suggests the hexagon tile map performs slightly better, or equally as well.
+After completing the 12 evaluations, the participants were asked to
+submit their responses.
+
+\section{Results}\label{results}
+
+Responses from 92 participants were collected. Five participants did not
+provide more than three unique choices for the twelve lineups, and their
+data was removed. Set A was evaluated by 42 participants, and 53
+evaluated set B. This resulted in 1104 evaluations, corresponding to 92
+subjects, each evaluating 12 lineups, that were analysed on accuracy and
+speed. The certainty and reasons of subjects in their answers is also
+examined.
+
+\subsection{Participant demographics}\label{participant-demographics}
+
+Of the 92 participants, 67 were male, and 25 female. Most participants
+(56) had a Bachelors degree, 13 had a Masters degree, and the remaining
+23 had high school diplomas.
+
+\subsection{Accuracy}\label{accuracy}
+
+Fig. \ref{fig:detect-compare} displays the average detection rates for
+the two types of plot separately for each trend model. Each trend model
+was tested using four repetitions, evaluations on the same data set were
+seen as either choropleths or hexagon tile maps by each group as
+specified in Table. \ref{fig:exp-design}; the detection rates for each
+display are connected by a line segment. The Three Cities and All Cities
+trend models shown in the hexagon tile map allowed viewers to detect the
+data plot substantially more often than the choropleth counterparts. One
+replicate for the All Cities group had similar detection rates for both
+plot types, the rate of detection using the choropleth map was much
+higher than other replicates. Surprisingly, participants could also
+detect the gradual spatial trend in the NW-SE group from the hexagon
+tile map. We expected that the choropleth map would be superior for the
+type of spatial pattern, but the data suggests the hexagon tile map
+performs slightly better, or equally as well.
 
@@
 
-Table.
-\ref{tab:detect-glmer1} presents a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on the detection rate.
-The results support the summary from Fig.
-\ref{fig:detect-compare} and all parameters are statistically significant despite the large standard deviations observed in Table.
-\ref{tab:desc-stats}.
-Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
-Allowing for the interaction effect, the difference in detection rate decreases for population related displays for a choropleth map lineup, but increases for a hexagon tile map display.
-The log odds of detection show in Table. \ref{tab:detect-glmer1} can be back transformed after taking the sum of all terms for the trend and type of display that are of interest.
-For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to 0.63 from 0.52 for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
-
-When a choropleth map display is used, the predicted detection rate for the Three Cities trend, 0.03; this is extremely low, especially compared to the NW-SE trend of 0.52.
-When the All Cities trend is presented in a choropleth display the predicted probability of detection is 0.22.
-The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend 0.39 and All Cities trend 0.59.
+Table. \ref{tab:detect-glmer1} presents a summary of the generalised
+linear mixed effects model, testing the effect of plot type and trend
+model on the detection rate. The results support the summary from Fig.
+\ref{fig:detect-compare} and all parameters are statistically
+significant despite the large standard deviations observed in Table.
+\ref{tab:desc-stats}. Overall, the hexagon tile map performs marginally
+better than the choropleth for all trend models, which is a pleasant
+surprise. Allowing for the interaction effect, the difference in
+detection rate decreases for population related displays for a
+choropleth map lineup, but increases for a hexagon tile map display. The
+log odds of detection show in Table. \ref{tab:detect-glmer1} can be back
+transformed after taking the sum of all terms for the trend and type of
+display that are of interest. For the NW-SE distribution, the predicted
+detection rate for the hexagon tile map display increases the predicted
+probability of detection to 0.63 from 0.52 for choropleths, this is
+almost exactly the difference seen in the table of means and is
+significant only at the 0.05 level.
+
+When a choropleth map display is used, the predicted detection rate for
+the Three Cities trend, 0.03; this is extremely low, especially compared
+to the NW-SE trend of 0.52. When the All Cities trend is presented in a
+choropleth display the predicted probability of detection is 0.22. The
+hexagon tile map has a substantially high detection rate for the display
+of a Three Cities trend 0.39 and All Cities trend 0.59.
 
@@
 
-\hypertarget{speed}{%
-\subsection{Speed}\label{speed}}
-
-Fig.
-\ref{fig:beeswarm} shows horizontally jittered dot plots to contrast the time taken by participants to evaluate each lineup when viewing each type of display.
-The time are also separated by trend model and whether the data plot was detected or not detected.
-The time taken to complete an evaluation ranged from milliseconds to 60 seconds.
-The average time taken for type of display is shown as a large colored dot on each plot.
-when considering the heights of the green and orange dots, there is little difference in the average time taken to read a choropleth or hexagon tile map.
-Comparing the same colored dot across each trend model row, there is a slight increase in the time taken to correctly detected the data plot in the hexagon tile map lineup, but little difference in evaluation time for the choropleth display.
-However, there were substantially less correct detections for choropleth lineups for the Three cities and All Cities trends.
+\subsection{Speed}\label{speed}
+
+Fig. \ref{fig:beeswarm} shows horizontally jittered dot plots to
+contrast the time taken by participants to evaluate each lineup when
+viewing each type of display. The time are also separated by trend model
+and whether the data plot was detected or not detected. The time taken
+to complete an evaluation ranged from milliseconds to 60 seconds. The
+average time taken for type of display is shown as a large colored dot
+on each plot. when considering the heights of the green and orange dots,
+there is little difference in the average time taken to read a
+choropleth or hexagon tile map. Comparing the same colored dot across
+each trend model row, there is a slight increase in the time taken to
+correctly detected the data plot in the hexagon tile map lineup, but
+little difference in evaluation time for the choropleth display.
+However, there were substantially less correct detections for choropleth
+lineups for the Three cities and All Cities trends.
 
@@
 
-\hypertarget{certainty}{%
-\subsection{Certainty}\label{certainty}}
-
-Participants provided their level of certainty regarding their choice using a five point scale.
-Unlike the accuracy and speed of responses that were derived during the data processing phase, this was a subjective
-assessment by the participant prompted by the question: `How certain are you about your choice?'.
-Fig.
-\ref{fig:certainty} shows the amount of times participants provided each level of certainty.
-This was separated for each combination of trend models and display type, and colored depending on whether a participant correctly detected the data plot in the lineup.
-Participants often chose 4 or 5 when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
-This shows overconfidence in their detection ability when using a choropleth map display.
-Participants were less likely to be certain when their choice was incorrect and they were viewing a hexagon tile map.
-For each trend model, participants were more likely to doubt their choice and choose 1 or 2 in the hexagon tile map displays, even though many had made the correct choice.
+\subsection{Certainty}\label{certainty}
+
+Participants provided their level of certainty regarding their choice
+using a five point scale. Unlike the accuracy and speed of responses
+that were derived during the data processing phase, this was a
+subjective assessment by the participant prompted by the question: `How
+certain are you about your choice?'. Fig. \ref{fig:certainty} shows the
+amount of times participants provided each level of certainty. This was
+separated for each combination of trend models and display type, and
+colored depending on whether a participant correctly detected the data
+plot in the lineup. Participants often chose 4 or 5 when viewing the
+population related trends in the choropelth display, even though they
+were often incorrect when viewing an All Cities trend and overwhelmingly
+incorrect for the Three Cities trend. This shows overconfidence in their
+detection ability when using a choropleth map display. Participants were
+less likely to be certain when their choice was incorrect and they were
+viewing a hexagon tile map. For each trend model, participants were more
+likely to doubt their choice and choose 1 or 2 in the hexagon tile map
+displays, even though many had made the correct choice.
 
@@
 
-\hypertarget{reason}{%
-\subsection{Reason}\label{reason}}
-
-Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons.
-``Color trend across the areas'' was the most common selection for NW-SE trend displays.
-
-The reasons chosen by participants from the list provided to them varied more when viewing choropleth displays than the hexagon tile map.
-The hexagon tile map displays resulted in ``Clusters of color'' as the most common choice made by participants.
-
-The choice ``None of these reasons'' was used as the default value to minimise noise from participants who did not select a response.
+\subsection{Reason}\label{reason}
+
+Participants were asked why they had made their plot choice and were
+able to select from a set of suggested reasons. ``Color trend across the
+areas'' was the most common selection for NW-SE trend displays.
+
+The reasons chosen by participants from the list provided to them varied
+more when viewing choropleth displays than the hexagon tile map. The
+hexagon tile map displays resulted in ``Clusters of color'' as the most
+common choice made by participants.
+
+The choice ``None of these reasons'' was used as the default value to
+minimise noise from participants who did not select a response.
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-The intention of this study was to contrast the use of the choropleth map and the hexagon tile map.
-The visual inference lineup protocol was employed to contrast the effectiveness of the displays.
-The results have shown that overall the use of the hexagon tile map display allows participants to find the data plot in the lineup more often.
-Using the visual inference protocol this result can be extended to show that it is a valid alternative display to communicate spatial distributions of population related data.
-
-We expected that the choropleth map would be superior for communicating the spatial pattern of geographic distributions.
-The data suggest that the participants perform slightly better or equally as well for each replicate in each trend model across the two displays.
-Table II shows that the difference in the mean detection rate for the two trend models was 0.10.
+\section{Discussion}\label{discussion}
+
+The intention of this study was to contrast the use of the choropleth
+map and the hexagon tile map. The visual inference lineup protocol was
+employed to contrast the effectiveness of the displays. The results have
+shown that overall the use of the hexagon tile map display allows
+participants to find the data plot in the lineup more often. Using the
+visual inference protocol this result can be extended to show that it is
+a valid alternative display to communicate spatial distributions of
+population related data.
+
+We expected that the choropleth map would be superior for communicating
+the spatial pattern of geographic distributions. The data suggest that
+the participants perform slightly better or equally as well for each
+replicate in each trend model across the two displays. Table II shows
+that the difference in the mean detection rate for the two trend models
+was 0.10.
 
 The differences seen in the \ref{fig:detect-compare} plot and Table.
-\ref{tab:desc-stats} are reflected in the model results.
-Surprisingly the difference for the geographic distribution was significant at the 0.05 level.
-It also showed that the hexagon tile map display performs marginally better than the choropleth for all trend models.
-Unexpectedly the detection rate suffers when using a choropleth map to display population related distributions.
-
-While the significance of the difference in detection was the key focus of this experiment, the secondary focus was the time taken by participants.
-it was expected that the participants may take longer to consider the hexagon tile map distribution but would be able to detect the data plot in the lineup.
-The bimodal distributions seen in Fig.
-\ref{fig:beeswarm} showed very little difference in the mean evaluation times.
-As the maximum time of all of the distributions approached 60 seconds it cannot be said that the participants' took longer to evaluate the hexagon tile map displays.
-
-The responses to the questions asked of participants included the reason for their choice and the certainty around their choice.
-Fig.
-\ref{tab:reason} shows high levels of certainty of 4 and 5 were chosen by participants when looking at the population distributions in a choropleth map display show that they were over confident when attempting to find the real data plot in the choropleth map displays.
-Participants performed better on the NW-SE distribution shown in the choropleth display and were reasonably confident about their decisions.
-The high levels of the mid range value of 3 could indicate that the participant did not want to provide a response, as this was the default value.
-Those who chose level 4 or 5 were equally likely to be correct for the three cities lineups, but more likely to be correct than incorrect for the other two trend models.
-
-The color scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
-Due to the consistent coloring of rural areas in a choropleth display, the choice ``All areas have similar colors'' was most common reason for a participants choice.
-The All Cities displays colored the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural color consistency.
-Choosing ``Clusters of colour'' was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions.
-It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays.
-Due to the spatial covariance introduced in the smoothing, groups of similarly colored hexagons were present in all of the hexagon tile map displays.
-All Cities and Three Cities distributions of real data trends had distinctly different patterns or red inner-city areas, while some of the plots in each lineup may have shared similar features.
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-The choropleth map display and the tessellated hexagon tile map have been contrasted using the lineup protocol.
-The hexagon tile map was significantly more effective for spotting a real population related data trend model hidden in a lineup.
-
-The hexagon tile map display should be considered as an alternative visualization method when communicating distributions that relate to the population across a set of geographic units.
-As an additional display to the familiar choropleth map, cancer atlas products may benefit from the opportunity to allow exploration via an alternative display.
-The spatial distributions used to test these displays were inspired by the real spatially smoothed estimates of the cancer burden on Australian communities.
-However, this technique may be extended to other population related distributions, such as other diseases.
-
-The increasing population densities of capital cities despite large land area exacerbates the difference in the smallest and largest communities.
-The population density structure of Australia can be considered similar to that of Canada, New Zealand and many other countries.
-Therefore, this display is not only relevant to Australia, but all nations or population distributions that experience densely populated cities separated by vast rural expanses.
-
-\hypertarget{acknowledgment}{%
-\section{Acknowledgment}\label{acknowledgment}}
-
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments.
-Mitchell O'Hara-Wild was a co-developer of the taipan {[}\protect\hyperlink{ref-taipan}{20}{]} R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.
-We are thankful for the NUMBATs (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.
-
-The source code to produce this document can be found on \href{https://github.com/srkobakian/experiment/paper}{GitHub}.
-Supplementary materials have been included to discuss the survey procedures and the lineups that were used.
-The full set of images can be found here, too.
+\ref{tab:desc-stats} are reflected in the model results. Surprisingly
+the difference for the geographic distribution was significant at the
+0.05 level. It also showed that the hexagon tile map display performs
+marginally better than the choropleth for all trend models. Unexpectedly
+the detection rate suffers when using a choropleth map to display
+population related distributions.
+
+While the significance of the difference in detection was the key focus
+of this experiment, the secondary focus was the time taken by
+participants. it was expected that the participants may take longer to
+consider the hexagon tile map distribution but would be able to detect
+the data plot in the lineup. The bimodal distributions seen in Fig.
+\ref{fig:beeswarm} showed very little difference in the mean evaluation
+times. As the maximum time of all of the distributions approached 60
+seconds it cannot be said that the participants' took longer to evaluate
+the hexagon tile map displays.
+
+The responses to the questions asked of participants included the reason
+for their choice and the certainty around their choice. Fig.
+\ref{tab:reason} shows high levels of certainty of 4 and 5 were chosen
+by participants when looking at the population distributions in a
+choropleth map display show that they were over confident when
+attempting to find the real data plot in the choropleth map displays.
+Participants performed better on the NW-SE distribution shown in the
+choropleth display and were reasonably confident about their decisions.
+The high levels of the mid range value of 3 could indicate that the
+participant did not want to provide a response, as this was the default
+value. Those who chose level 4 or 5 were equally likely to be correct
+for the three cities lineups, but more likely to be correct than
+incorrect for the other two trend models.
+
+The color scaling applied in Three cities and All cities displays
+resulted in the rural areas of the real data plot appearing more blue or
+yellow than the other plots in the lineups. Due to the consistent
+coloring of rural areas in a choropleth display, the choice ``All areas
+have similar colors'' was most common reason for a participants choice.
+The All Cities displays colored the inner-city areas of all capital
+cities more red, this was observable to participants and explains the
+equal choice of the city clusters or rural color consistency. Choosing
+``Clusters of colour'' was expected when participants viewed the Hexagon
+tile map display of the All Cities and Three Cities distributions. It
+was unexpected that it was also the most common reason for the NW-SE
+hexagon tile map displays. Due to the spatial covariance introduced in
+the smoothing, groups of similarly colored hexagons were present in all
+of the hexagon tile map displays. All Cities and Three Cities
+distributions of real data trends had distinctly different patterns or
+red inner-city areas, while some of the plots in each lineup may have
+shared similar features.
+
+\section{Conclusion}\label{conclusion}
+
+The choropleth map display and the tessellated hexagon tile map have
+been contrasted using the lineup protocol. The hexagon tile map was
+significantly more effective for spotting a real population related data
+trend model hidden in a lineup.
+
+The hexagon tile map display should be considered as an alternative
+visualization method when communicating distributions that relate to the
+population across a set of geographic units. As an additional display to
+the familiar choropleth map, cancer atlas products may benefit from the
+opportunity to allow exploration via an alternative display. The spatial
+distributions used to test these displays were inspired by the real
+spatially smoothed estimates of the cancer burden on Australian
+communities. However, this technique may be extended to other population
+related distributions, such as other diseases.
+
+The increasing population densities of capital cities despite large land
+area exacerbates the difference in the smallest and largest communities.
+The population density structure of Australia can be considered similar
+to that of Canada, New Zealand and many other countries. Therefore, this
+display is not only relevant to Australia, but all nations or population
+distributions that experience densely populated cities separated by vast
+rural expanses.
+
+\section{Acknowledgment}\label{acknowledgment}
+
+The authors would like to thank the Australian Cancer Atlas team for
+discussions regarding alternative spatial visualizations, and Professor
+Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with
+suggestions and comments. Mitchell O'Hara-Wild was a co-developer of the
+taipan {[}\citeproc{ref-taipan}{20}{]} R package for image tagging, used
+as the base for the web app constructed to collect participant
+evaluations of lineups. We are thankful for the NUMBATs (Non-Uniform
+Monash Business Analytics Team) for participating in the pilot study
+that helped to assess the experimental design and determine an
+appropriate sample size for the study.
+
+The source code to produce this document can be found on
+\href{https://github.com/srkobakian/experiment/paper}{GitHub}.
+Supplementary materials have been included to discuss the survey
+procedures and the lineups that were used. The full set of images can be
+found here, too.
 
@@
 
-The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{18}{]} with the use of the following packages:
+The analysis of the work was completed in R
+{[}\citeproc{ref-RCore}{18}{]} with the use of the following packages:
 
@@
 \item
-  For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{23}{]}, rticles {[}\protect\hyperlink{ref-rticles}{24}{]}, knitr {[}\protect\hyperlink{ref-knitr}{25}{]}.
-\item
-  For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{26}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{27}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{28}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{29}{]}.
-\item
-  For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{30}{]}, png {[}\protect\hyperlink{ref-png}{31}{]}, grid {[}\protect\hyperlink{ref-grid}{32}{]}.
-\item
-  For modelling and presentation of models: gstat {[}\protect\hyperlink{ref-gstat}{17}{]}, lme4 {[}\protect\hyperlink{ref-lme4}{19}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{33}{]}.
+  For document creation: rmarkdown {[}\citeproc{ref-rmarkdown}{23}{]},
+  rticles {[}\citeproc{ref-rticles}{24}{]}, knitr
+  {[}\citeproc{ref-knitr}{25}{]}.
+\item
+  For lineup creation and data analysis: tidyverse
+  {[}\citeproc{ref-tidyverse}{26}{]}, nullabor
+  {[}\citeproc{ref-nullabor}{27}{]}, ggthemes
+  {[}\citeproc{ref-ggthemes}{28}{]}, RColorBrewer
+  {[}\citeproc{ref-RColorBrewer}{29}{]}.
+\item
+  For image displays: cowplot {[}\citeproc{ref-cowplot}{30}{]}, png
+  {[}\citeproc{ref-png}{31}{]}, grid {[}\citeproc{ref-grid}{32}{]}.
+\item
+  For modelling and presentation of models: gstat
+  {[}\citeproc{ref-gstat}{17}{]}, lme4 {[}\citeproc{ref-lme4}{19}{]},
+  kableExtra {[}\citeproc{ref-kableExtra}{33}{]}.
 \end{itemize}
 
-Ethics approval for the online survey was granted by QUT's Ethics Committee (Ethics Application Number: 1900000991).
-All applicants provided informed consent in line with QUT regulations prior to participating in this research.
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
+Ethics approval for the online survey was granted by QUT's Ethics
+Committee (Ethics Application Number: 1900000991). All applicants
+provided informed consent in line with QUT regulations prior to
+participating in this research.
+
+\section*{References}\label{references}
 \addcontentsline{toc}{section}{References}
 
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-sugarbag}{}}%
+\phantomsection\label{refs}
+\begin{CSLReferences}{0}{1}
+\bibitem[\citeproctext]{ref-sugarbag}
 \CSLLeftMargin{1. }%
-\CSLRightInline{Kobakian S, Cook D (2019) Sugarbag: Create tessellated hexagon maps. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-atlas}{}}%
+\CSLRightInline{Kobakian S, Cook D, Duncan E (2023)
+\href{https://doi.org/10.32614/RJ-2023-021}{A hexagon tile map algorithm
+for displaying spatial data}. The R Journal 15:6--16}
+
+\bibitem[\citeproctext]{ref-atlas}
 \CSLLeftMargin{2. }%
-\CSLRightInline{Cancer Council Queensland {Australian Cancer Atlas}, publisher = {Queensland University of Technology, Cooperative Research Centre for Spatial Information}, issue = {Version 09}, url={https://atlas.cancer.org.au}, year = {2018}, accessed = {Jan 12 2020}.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-GIIV}{}}%
+\CSLRightInline{Cancer Council Queensland (2018) {Australian Cancer
+Atlas}, publisher = {Queensland University of Technology, Cooperative
+Research Centre for Spatial Information}, issue = {Version 09},
+url={https://atlas.cancer.org.au}, accessed = {Jan 12 2020}. }
+
+\bibitem[\citeproctext]{ref-GIIV}
 \CSLLeftMargin{3. }%
-\CSLRightInline{Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical inference for infovis. IEEE Transactions on Visualization and Computer Graphics (Proc InfoVis '10) 16:973--979}
-
-\leavevmode\vadjust pre{\hypertarget{ref-EI}{}}%
+\CSLRightInline{Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical
+inference for infovis. IEEE Transactions on Visualization and Computer
+Graphics (Proc InfoVis '10) 16:973--979}
+
+\bibitem[\citeproctext]{ref-EI}
 \CSLLeftMargin{4. }%
-\CSLRightInline{Tufte ER (1990) {Envisioning Information}. Graphics Press}
-
-\leavevmode\vadjust pre{\hypertarget{ref-BCM}{}}%
+\CSLRightInline{Tufte ER (1990) {Envisioning Information}. Graphics
+Press}
+
+\bibitem[\citeproctext]{ref-BCM}
 \CSLLeftMargin{5. }%
-\CSLRightInline{Skowronnek A (2016) \href{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}{{Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata}}.
-{Infovis Reading Group WS 2015/16} }
-
-\leavevmode\vadjust pre{\hypertarget{ref-CBATCC}{}}%
+\CSLRightInline{Skowronnek A (2016)
+\href{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}{{Beyond
+Choropleth Maps -- A Review of Techniques to Visualize Quantitative
+Areal Geodata}}. {Infovis Reading Group WS 2015/16} }
+
+\bibitem[\citeproctext]{ref-CBATCC}
 \CSLLeftMargin{6. }%
-\CSLRightInline{Kocmoud C, House D (1998) {A Constraint-based Approach to Constructing Continuous Cartograms}. In: Proc. Symp. Spatial data handling. pp 236--246}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ACTUC}{}}%
+\CSLRightInline{Kocmoud C, House D (1998) {A Constraint-based Approach
+to Constructing Continuous Cartograms}. In: Proc. Symp. Spatial data
+handling. pp 236--246}
+
+\bibitem[\citeproctext]{ref-ACTUC}
 \CSLLeftMargin{7. }%
-\CSLRightInline{Dorling D (2011) \href{https://doi.org/10.1002/9780470979587.ch33}{{Area Cartograms: Their Use and Creation}}.
-In: Concepts and techniques in modern geography (CATMOG).
-University of East Anglia: Environmental Publications, pp 252--260}
-
-\leavevmode\vadjust pre{\hypertarget{ref-NAC}{}}%
+\CSLRightInline{Dorling D (2011)
+\href{https://doi.org/10.1002/9780470979587.ch33}{{Area Cartograms:
+Their Use and Creation}}. In: The map reader. John Wiley \& Sons, Ltd,
+pp 252--260}
+
+\bibitem[\citeproctext]{ref-NAC}
 \CSLLeftMargin{8. }%
-\CSLRightInline{Olson JM (1976) \href{https://doi.org/10.1111/j.0033-0124.1976.00371.x}{{Noncontiguous Area Cartograms}}. The Professional Geographer 28:371--380}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RSCW}{}}%
+\CSLRightInline{Olson JM (1976)
+\href{https://doi.org/10.1111/j.0033-0124.1976.00371.x}{{Noncontiguous
+Area Cartograms}}. The Professional Geographer 28:371--380}
+
+\bibitem[\citeproctext]{ref-RSCW}
 \CSLLeftMargin{9. }%
-\CSLRightInline{Raisz E (1963) \href{https://doi.org/10.1080/00221343608987880}{{Rectangular Statistical Cartograms of the World}}. Journal of Geography 35:8--10}
-
-\leavevmode\vadjust pre{\hypertarget{ref-CDWCS}{}}%
+\CSLRightInline{Raisz E (1963)
+\href{https://doi.org/10.1080/00221343608987880}{{Rectangular
+Statistical Cartograms of the World}}. Journal of Geography 35:8--10}
+
+\bibitem[\citeproctext]{ref-CDWCS}
 \CSLLeftMargin{10. }%
-\CSLRightInline{Monmonier M (2005) \href{https://doi.org/10.1191/0309132505ph540pr}{{Cartography: Distortions, World-views and Creative Solutions}}. Progress in Human Geography 29:217--224}
-
-\leavevmode\vadjust pre{\hypertarget{ref-review}{}}%
+\CSLRightInline{Monmonier M (2005)
+\href{https://doi.org/10.1191/0309132505ph540pr}{{Cartography:
+Distortions, World-views and Creative Solutions}}. Progress in Human
+Geography 29:217--224}
+
+\bibitem[\citeproctext]{ref-review}
 \CSLLeftMargin{11. }%
-\CSLRightInline{Kobakian S, Cook D, Roberts J (2020) \href{https://ace.amegroups.com/article/view/6040}{Mapping cancer: The potential of cartograms and alternative map displays}.
-Annals of Cancer Epidemiology 4:}
-
-\leavevmode\vadjust pre{\hypertarget{ref-BCHLLSW09}{}}%
+\CSLRightInline{Kobakian S, Cook D, Roberts J (2020)
+\href{https://ace.amegroups.com/article/view/6040}{Mapping cancer: The
+potential of cartograms and alternative map displays}. Annals of Cancer
+Epidemiology 4:}
+
+\bibitem[\citeproctext]{ref-BCHLLSW09}
 \CSLLeftMargin{12. }%
-\CSLRightInline{Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) \href{https://doi.org/10.1098/rsta.2009.0120}{Statistical inference for exploratory data analysis and model diagnostics}.
-Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383}
-
-\leavevmode\vadjust pre{\hypertarget{ref-GTPCCD}{}}%
+\CSLRightInline{Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne
+DF, Wickham H (2009)
+\href{https://doi.org/10.1098/rsta.2009.0120}{Statistical inference for
+exploratory data analysis and model diagnostics}. Philosophical
+Transactions of the Royal Society, A (Invited) 367:4361--4383}
+
+\bibitem[\citeproctext]{ref-GTPCCD}
 \CSLLeftMargin{13. }%
-\CSLRightInline{Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ggplot2}{}}%
+\CSLRightInline{Hofmann H, Follett L, Majumder M, Cook D (2012)
+Graphical tests for power comparison of competing designs. IEEE
+Transactions on Visualization and Computer Graphics 18:2441--2448}
+
+\bibitem[\citeproctext]{ref-ggplot2}
 \CSLLeftMargin{14. }%
-\CSLRightInline{Wickham H (2009) \href{http://had.co.nz/ggplot2/book}{ggplot2: Elegant graphics for data analysis}. Springer New York}
-
-\leavevmode\vadjust pre{\hypertarget{ref-abs2016}{}}%
+\CSLRightInline{Wickham H (2009)
+\href{http://had.co.nz/ggplot2/book}{ggplot2: Elegant graphics for data
+analysis}. Springer New York}
+
+\bibitem[\citeproctext]{ref-abs2016}
 \CSLLeftMargin{15. }%
-\CSLRightInline{Australian Bureau of Statistics (2018) \href{https://www.abs.gov.au/statistics/statistical-geography/australian-statistical-geography-standard-asgs}{{Australian Statistical Geography Standard (ASGS)}}.
-}
-
-\leavevmode\vadjust pre{\hypertarget{ref-POG}{}}%
+\CSLRightInline{Australian Bureau of Statistics (2018)
+\href{https://www.abs.gov.au/statistics/statistical-geography/australian-statistical-geography-standard-asgs}{{Australian
+Statistical Geography Standard (ASGS)}}. }
+
+\bibitem[\citeproctext]{ref-POG}
 \CSLLeftMargin{16. }%
-\CSLRightInline{Matheron G (1963) \href{http://dx.doi.org/10.2113/gsecongeo.58.8.1246}{Principles of geostatistics}. Economic Geology 58:1246--1266}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gstat}{}}%
+\CSLRightInline{Matheron G (1963)
+\href{http://dx.doi.org/10.2113/gsecongeo.58.8.1246}{Principles of
+geostatistics}. Economic Geology 58:1246--1266}
+
+\bibitem[\citeproctext]{ref-gstat}
 \CSLLeftMargin{17. }%
-\CSLRightInline{Gräler B, Pebesma E, Heuvelink G (2016) \href{https://journal.r-project.org/archive/2016/RJ-2016-014/index.html}{Spatio-temporal interpolation using gstat}. The R Journal 8:204--218}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RCore}{}}%
+\CSLRightInline{Gräler B, Pebesma E, Heuvelink G (2016)
+\href{https://journal.r-project.org/archive/2016/RJ-2016-014/index.html}{Spatio-temporal
+interpolation using gstat}. The R Journal 8:204--218}
+
+\bibitem[\citeproctext]{ref-RCore}
 \CSLLeftMargin{18. }%
-\CSLRightInline{R Core Team (2019) \href{https://www.R-project.org/}{R: A language and environment for statistical computing}. R Foundation for Statistical Computing, Vienna, Austria}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lme4}{}}%
+\CSLRightInline{R Core Team (2019) \href{https://www.R-project.org/}{R:
+A language and environment for statistical computing}. R Foundation for
+Statistical Computing, Vienna, Austria}
+
+\bibitem[\citeproctext]{ref-lme4}
 \CSLLeftMargin{19. }%
-\CSLRightInline{Bates D, Mächler M, Bolker B, Walker S (2015) \href{https://doi.org/10.18637/jss.v067.i01}{Fitting linear mixed-effects models using {lme4}}. Journal of Statistical Software 67:1--48}
-
-\leavevmode\vadjust pre{\hypertarget{ref-taipan}{}}%
+\CSLRightInline{Bates D, Mächler M, Bolker B, Walker S (2015)
+\href{https://doi.org/10.18637/jss.v067.i01}{Fitting linear
+mixed-effects models using {lme4}}. Journal of Statistical Software
+67:1--48}
+
+\bibitem[\citeproctext]{ref-taipan}
 \CSLLeftMargin{20. }%
-\CSLRightInline{Kobakian S, O'Hara-Wild M (2018) \href{https://CRAN.R-project.org/package=taipan}{Taipan: Tool for annotating images in preparation for analysis}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-sheets}{}}%
+\CSLRightInline{Kobakian S, O'Hara-Wild M (2018)
+\href{https://CRAN.R-project.org/package=taipan}{Taipan: Tool for
+annotating images in preparation for analysis}. }
+
+\bibitem[\citeproctext]{ref-sheets}
 \CSLLeftMargin{21. }%
-\CSLRightInline{Bryan J, Zhao J (2018) \href{https://CRAN.R-project.org/package=googlesheets}{Googlesheets: Manage google spreadsheets from r}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-figeight}{}}%
+\CSLRightInline{Bryan J, Zhao J (2018)
+\href{https://CRAN.R-project.org/package=googlesheets}{Googlesheets:
+Manage google spreadsheets from r}. }
+
+\bibitem[\citeproctext]{ref-figeight}
 \CSLLeftMargin{22. }%
-\CSLRightInline{Figure Eight Inc (2019) \href{https://www.figure-eight.com/}{The essential high-quality data annotation platform}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-rmarkdown}{}}%
+\CSLRightInline{Figure Eight Inc (2019)
+\href{https://www.figure-eight.com/}{The essential high-quality data
+annotation platform}. }
+
+\bibitem[\citeproctext]{ref-rmarkdown}
 \CSLLeftMargin{23. }%
-\CSLRightInline{Xie Y, Allaire JJ, Grolemund G (2018) \href{https://bookdown.org/yihui/rmarkdown}{R markdown: The definitive guide}. Chapman; Hall/CRC, Boca Raton, Florida}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rticles}{}}%
+\CSLRightInline{Xie Y, Allaire JJ, Grolemund G (2018)
+\href{https://bookdown.org/yihui/rmarkdown}{R markdown: The definitive
+guide}. Chapman; Hall/CRC, Boca Raton, Florida}
+
+\bibitem[\citeproctext]{ref-rticles}
 \CSLLeftMargin{24. }%
-\CSLRightInline{Allaire J, Xie Y, R Foundation, et al (2019) \href{https://CRAN.R-project.org/package=rticles}{Rticles: Article formats for r markdown}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-knitr}{}}%
+\CSLRightInline{Allaire J, Xie Y, R Foundation, et al (2019)
+\href{https://CRAN.R-project.org/package=rticles}{Rticles: Article
+formats for r markdown}. }
+
+\bibitem[\citeproctext]{ref-knitr}
 \CSLLeftMargin{25. }%
-\CSLRightInline{Xie Y (2014) \href{http://www.crcpress.com/product/isbn/9781466561595}{Knitr: A comprehensive tool for reproducible research in {R}}. Implementing reproducible computational research }
-
-\leavevmode\vadjust pre{\hypertarget{ref-tidyverse}{}}%
+\CSLRightInline{Xie Y (2015) \href{https://yihui.org/knitr/}{Dynamic
+documents with {R} and knitr}, 2nd ed. Chapman; Hall/CRC, Boca Raton,
+Florida}
+
+\bibitem[\citeproctext]{ref-tidyverse}
 \CSLLeftMargin{26. }%
-\CSLRightInline{Wickham H, Averick M, Bryan J, et al (2019) \href{https://doi.org/10.21105/joss.01686}{Welcome to the {tidyverse}}. Journal of Open Source Software 4:1686}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nullabor}{}}%
+\CSLRightInline{Wickham H, Averick M, Bryan J, et al (2019)
+\href{https://doi.org/10.21105/joss.01686}{Welcome to the {tidyverse}}.
+Journal of Open Source Software 4:1686}
+
+\bibitem[\citeproctext]{ref-nullabor}
 \CSLLeftMargin{27. }%
-\CSLRightInline{Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) \href{https://CRAN.R-project.org/package=nullabor}{Nullabor: Tools for graphical inference}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-ggthemes}{}}%
+\CSLRightInline{Wickham H, Chowdhury NR, Cook D, Hofmann H (2018)
+\href{https://CRAN.R-project.org/package=nullabor}{Nullabor: Tools for
+graphical inference}. }
+
+\bibitem[\citeproctext]{ref-ggthemes}
 \CSLLeftMargin{28. }%
-\CSLRightInline{Arnold JB (2019) \href{https://CRAN.R-project.org/package=ggthemes}{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-RColorBrewer}{}}%
+\CSLRightInline{Arnold JB (2019)
+\href{https://CRAN.R-project.org/package=ggthemes}{Ggthemes: Extra
+themes, scales and geoms for 'ggplot2'}. }
+
+\bibitem[\citeproctext]{ref-RColorBrewer}
 \CSLLeftMargin{29. }%
-\CSLRightInline{Neuwirth E (2014) \href{https://CRAN.R-project.org/package=RColorBrewer}{RColorBrewer: ColorBrewer palettes}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-cowplot}{}}%
+\CSLRightInline{Neuwirth E (2014)
+\href{https://CRAN.R-project.org/package=RColorBrewer}{RColorBrewer:
+ColorBrewer palettes}. }
+
+\bibitem[\citeproctext]{ref-cowplot}
 \CSLLeftMargin{30. }%
-\CSLRightInline{Wilke CO (2019) \href{https://CRAN.R-project.org/package=cowplot}{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-png}{}}%
+\CSLRightInline{Wilke CO (2019)
+\href{https://CRAN.R-project.org/package=cowplot}{Cowplot: Streamlined
+plot theme and plot annotations for 'ggplot2'}. }
+
+\bibitem[\citeproctext]{ref-png}
 \CSLLeftMargin{31. }%
-\CSLRightInline{Urbanek S (2013) \href{https://CRAN.R-project.org/package=png}{Png: Read and write PNG images}. }
-
-\leavevmode\vadjust pre{\hypertarget{ref-grid}{}}%
+\CSLRightInline{Urbanek S (2013)
+\href{https://CRAN.R-project.org/package=png}{Png: Read and write PNG
+images}. }
+
+\bibitem[\citeproctext]{ref-grid}
 \CSLLeftMargin{32. }%
-\CSLRightInline{R Core Team (2019) \href{https://www.R-project.org/}{R: A language and environment for statistical computing}. R Foundation for Statistical Computing, Vienna, Austria}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kableExtra}{}}%
+\CSLRightInline{Murrell P (2002) The grid graphics package. R News
+2:14--19}
+
+\bibitem[\citeproctext]{ref-kableExtra}
 \CSLLeftMargin{33. }%
-\CSLRightInline{Zhu H (2019) \href{https://CRAN.R-project.org/package=kableExtra}{kableExtra: Construct complex table with 'kable' and pipe syntax}. }
+\CSLRightInline{Zhu H (2019)
+\href{https://CRAN.R-project.org/package=kableExtra}{kableExtra:
+Construct complex table with 'kable' and pipe syntax}. }
 

### 2025-07-07 paper/review1/ReponseToReviewers2025.qmd
review folder created

---
title: "Response to Reviewers"
format: pdf
editor: visual
---

## Response to Editor and reviewers

Add letter format

Add introductory thank you to reviewers for their work, and the editor for their consideration.

## To Do

Make a release version on github of current copy before changes

all points made be reviewers, must be addressed with a response using different font types for review comment v our response

In our Rmd file use XXX for difficult change to make - allocated to Di or Steph

# Review of “Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map  for Communicating Cancer Statistics”

Associate Editor

Dear associate editor XXX,

Thank you for the opportunity to improve this paper with the suggestions made in the comments provided. Please find our responses to the comments provided in *italics* below each paragraph or comment.

Comments to the Author:

While the contents and findings are interesting, and it is great to see more research done in the areas of visual inference and visualization of spatial areal data, all three reviewers expressed serious concerns about the writing and the lack of clarity throughout. I must say I agree: the manuscript is let down greatly by sloppiness and unpolished writing, lack of clarity in the mathematics and statistical modeling details (two reviewers pointed out potential basic mistakes in the maths), and occasional claims and statements which appear unsubstantiated.

I encourage the authors to respond to all the comments by the three reviewers in a substantive manner, and in doing so go through the manuscript with a very "fine pen" to ensure the writing and overall messaging is as clear as possible.

Referee(s)' Comments to Author:

## Referee: 1

Comments to the Author

Please see attached review.

## Referee: 2

Comments to the Author

SUMMARY

This paper contributes a lineup protocol study that assesses the utility of the hexagon tile map (as an alternative to the choropleth map) for communicating Australian cancer statistics. Unlike choropleth maps, hexagon tile maps represent each geographic/administrative area with the same amount of space on the map. In turn, densely populated areas of interest, which are small geographically (and thus hard to see), become more visible to the map reader. Ultimately, the study provides compelling evidence to support the use of the hexagon tile map as an alternative to the choropleth map, in the context of communicating cancer statistics in Australia.

WRITING

Please thoroughly fix the following writing issues, which appear throughout the manuscript and distract from its good content.

Inconsistent use of Australian vs. American spelling (e.g., visualise and visualize, neighbour and neighbor, colour and color, etc.). Please pick one (or check on ANZJS guidelines) and stick with it throughout the entire paper.

*Australian English has now been consistently used in the writing of this article, except where it is necessary in the code to use American English.*

Comma splices (e.g., lines 181, 239, 312, etc.).

Other random errors (e.g., uncapitalized start in line 347, unneeded apostrophe in line 212, missing verb in lines 337-338, etc.).

FIGURES

Figure 1. This is a nice figure! My only suggestion is to adjust the caption to say “Thyroid cancer incidence” instead of “Thyroid incidence.”

*This change has been applied.*

Figure 2. In the caption, do you want to say which of the twelve plots is the real data plot? Also, is it possible to include, in the supplementary materials, this same type of figure for a choropleth lineup? I am curious to see what that looks like.

*The location has now been mentioned in the caption, and a reference has been added in the text to direct readers to the alternative view.*

Figure 3. Would it be clearer to use “Hexagon Tile” and “Choropleth” for the map display labels? In the caption, can you make a note of what “Location” refers to? (It took me a while to figure that out.)

Figure 4. I think the trend legend is unnecessary, given that there is a separate panel in the plot for each trend model.

Figure 5. I think the green/orange dot legend for “Choro.” And “Hex.” is unnecessary.

Figure 6. Have you tried placing the bars next to each other instead of overlaying them? What does that look like?

PAPER

Introduction.

A couple more sentences about the lineup protocol might be nice.

Background.

Lines 41-45. This part feels out of place, if you do not make it clear that visualizing communicable disease patterns is just one example use of a spatial data display. This is especially the case because the rest of the paper is about visualizing noncommunicable diseases (i.e., cancer).

Line 82. The word “perceived” here made me think about who is doing the perceiving and whether a discussion somewhere about the different audiences of spatial data displays is warranted / would be helpful. For example, who are the users of the Australian Cancer Atlas?

Methodology.

Lines 128-129. I am not sure this claim is legitimate: “The results should apply broadly to any other geographic area of interest.” What about a choropleth map in which the geographic areas are more equally sized? (Not all choropleth maps are as extreme as the SA3 Australian one!)

Sections 3.5 - 3.7. Why are these sections, which cover data collection, located after Section 3.4, which covers the analysis? Would it make more sense to place them before Section 3.4?

Section 3.7, lines 291-293. Please provide more information about the nature and structure of these three questions: plot choice, reason, and difficulty. You do not provide information until Section 4, which feels too late. Additionally, should the “certainty” question, referenced in Section 4.4, also be included here? I also wonder if Section 3.7 should be renamed, given that it is about more than just demographic data collection.

Results.

Lines 361-368. This is an interesting finding!

Discussion.

Please spend some time discussing limitations of the study. Please also spend some time discussing future work, related to this study.

Acknowledgment.

Please move the pointers to the supplementary and replication materials out of this section to a more appropriate place. Please also move the ethics approval out of this section to a more appropriate place.

CONCLUDING THOUGHTS

I think the conducted study is well-done, interesting, and an important contribution to the literature. However, the writing of the manuscript requires substantial revision/work. Please spend some time cleaning up the paper, so that the content can be better understood, assessed, appreciated, and utilized!

Referee: 3

Comments to the Author

I appreciate the opportunity to review this interesting paper that describes an experimental study comparing the effectiveness of hexagon tile maps against choropleth maps using “the lineup protocol.” While choropleth maps are a widely used visualization technique, newly proposed methods of displaying spatial data, such as hexagon tile maps, are not widely known to recipients of such data displays. In this context, the paper addresses the important question of the usability of this new plot type. With the exception of Kawakami et al., 2024, which analyzes a different type of hexagon maps, there are to my knowledge no findings on the effectiveness of hexagon tile maps so far.

The paper analyzes the effectiveness of different types of plots with respect to two aspects: First, whether a specific type of spatial distribution, namely disease trends that impact highly populated small areas, is detected with higher accuracy when viewed in a hexagon tile map compared to a choropleth map. Additionally, the paper aims to analyze whether recipients detect these disease trends faster in hexagon tile maps than in choropleth maps. The paper focuses on the first question and uses an innovative methodological approach. Findings from a lineup experiment using simulated data for Australia suggest that the probability of detecting this specific type of spatial distribution in hexagon tile maps is higher than in choropleth maps.

I enjoyed reading the manuscript and commend the authors for several strengths of their work, especially their research question, which covers an often neglected aspect in visualization practice, and their thoughtful experimental setup.

Considering these strengths, though, as I read the manuscript I found some areas in which I would have appreciated greater clarity. Starting with some major concerns, I’ll list my comments in order of appearance:

1\) The section “Visual Inference” (Page 4) covers the background of visual inference and the lineup protocol, focusing on its use as a tool for statistical inference. I would like to see the reasoning for using it as a method to compare effectiveness made more clear. From the later text, I understand the argumentation as follows: Because the data is simulated in a way that one location shows the same significant result in two different visualizations (hexagon and choropleth), the detection rate indicates how easily participants can make the detection with respect to the map type.

2\) I had some difficulties following the data simulation process in section 3.2 (Page 6). Specifically, the smoothing process and the reasoning behind this process should be explained more thoroughly.

3\) The analysis of detection accuracy and the presentation of the findings could be improved:

While there is clearly a difference between map types (Page 12, Lines 306-316), the overall level of detection rates is low. I would expect some discussion of these low results. Are these a result of the data simulation process (i.e., the “true” signal might not be different enough)? How do the results compare to the expected detection rates if selected by chance, as discussed in Section 2.2?

The model definition in Section 3.4.3 on Page 9, as well as the reporting of the results (Page 12 and Table 2), need some work.

First: The model formulation on Page 9 is confusing. I would expect a model formulation of this form

hat(y_ij) = mu + beta1 \* maptype + beta2\*trend + beta3\*maptype\*trend + alpha_j + epsilon_ij with i=1,2, …,n decisions from j=1,2, …, 92 participants.

Table 2 on Page 22 should include the variance of the random error.

Second: The interpretation of the interaction effects on Page 13 Line 329 is a as follows:  “Allowing for the interaction effect, the difference in detection rate decreases for population-related displays for a choropleth map lineup but increases for a hexagon tile map display.“

I’m not sure if I understand that statement correctly. In my understanding, the interaction in Table 2 shows that the difference between choropleth and hexagon tiles differs between trend models, but it’s in favor of the hexagon models among all trends (full effect for hexagon with NW-SE trend:  1.63; full effect for hexagon all cities trend: 1.63 + 1.34 -1.16 = 1.81; full effect for hexagon tree cities trend 1.63 – 2.07 + 1.28 = 0.84).

Additionally, I can’t replicate the detection probabilities mentioned in the text, e.g., Page 13, Lines 333f.: “For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection

to 0.63 from 0.52 for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.”

Are these fixed effects estimates? I can’t replicate this and the following results from Table 2, but maybe I’m missing something?

P(detection =1 \| choropleth; NWSE) = exp(-1.27)/(1 + exp(-1.27)) = 0.22

P(detection =1 \| hex; NWSE) = exp(-1.27 + 1.63)/(1 + exp(-1.27 + 1.63)) = 0.59

P(detection =1 \| choropleth; three cities) = exp(-1.27 -2.07)/(1 + exp(-1.27 -2.07)) = 0.03

P(detection =1 \| hex; three cities) = exp(-1.27 + 1.63 -2.07 +1.28)/(1 + exp(-1.27 + 1.63 -2.07 + 1.28)) = 0.39

P(detection =1 \| choropleth; all cities) = exp(-1.27 + 1.34)/(1 + exp(-1.27 +1.34)) = 0.52

P(detection =1 \| hex; all cities) = exp(-1.27 + 1.63  +1.34 -1.16)/(1 + exp(-1.27 + 1.63 +1.34 -1.16)) = 0.63

4\) My last major concern is the discussion of data quality from the experiment. While data from participants with fewer than three uniquely chosen locations were excluded from the results, the findings for detection speed on Page 14 made me curious about the participants who took only a few seconds. There is a clear gap between these participants and those who took longer to complete the experiment. Does the accuracy differ between these two groups? If the accuracy is significantly lower for the quicker participants, this might indicate that they chose a location by chance to finish the task as quickly as possible. What is the experience from the pilot study? Are these times taken plausible? If not, one might consider removing those cases with implausibly short decision times from the sample to eliminate randomly chosen locations. Regardless of how you deal with these cases, this detail should be discussed in the text.

Here are some additional comments, that might be useful to improve the paper:

Page 1 line 16: “None of the existing approaches for creating cartograms or hexagon tiling perform well for the Australian landscape”

and

Page 3 62 “For Australia, the transformations warp the country so that it is no longer recognizable” -\> maybe cite Kobakian, Cook & Roberts 2020 to make clear why this statement is made?

Page 3 Line 78: what’s “substantially above”?

Figure 3: Explain term location in caption

Page 7 Line 164: “smoothed several times”; specify

Page 7 Line 169: express smoothing process in math: 0.5 \* value of area + 0.5 MEAN(value\| area is neighbour)

Page 9 Line 206: population-related displays; explain which displays

Page 9 Line 201: “The first step in the data cleaning process involved checking that survey responses collected for each participant were only included once in the data set.” Why is this necessary? Without context this sentence is confusing.

Page 10 Lines 259 – 264 could be shortened

Page 11: Line 269 what’s the meaning of the levels of Figure Eight participants?

Page 11 3.7 Demographic data collection -\> section could be merged with 3.5 “Web application” the reduce redundancies

Page 12 Lines 297 – 301: 5 participants where remove because they provided not more than 3 unique choices -\> please state a reason for that. The assumption is these participants just “clicked through” the experiment and choose a single location all the time? (see my major concern).

Page 12 section 4.1: Are there differences between group A and B? This would be a good place to show that randomization is working. Underlying assumption: there a no group specific influences on test results.

Page 12 Line 322. Any explanation why the choropleth performed not better?

Page 18, section 4.2

It would be interesting to see results under control of socio demographics. A second model including those variables could give some hints (direct effects, reduction intra-participant variance).  For reference see: (Vanderplas & Hofmann, 2016)

Figure 4: use color to distinguish between replicates (facets and color for trend models is redundant)

Page 14: The section “Reason” is extremely short and might be merged with section 4.3 (Speed) on page 14.

There is no reference to table 3 on page 22 in the text.

Literature

Kawakami, Y., Yuniar, S., & Ma, K.-L. (2024). HexTiles and Semantic Icons for MAUP-Aware Multivariate Geospatial Visualizations. https://doi.org/10.48550/arXiv.2407.16897

Reference as broader lit:

Vanderplas, S., & Hofmann, H. (2016). Spatial Reasoning and Data Displays. IEEE Transactions on Visualization and Computer Graphics, 22(1), 459–468. IEEE Transactions on Visualization and Computer Graphics. https://doi.org/10.1109/TVCG.2015.2469125

Overall Comments:

This paper performs a user study to compare and contrast the ability of two visual  displays, a choropleth map and a hexagon tile map. It uses a line up protocol to test the  effectiveness of the two displays. The study showed that the hexagon tile map was  significantly more effective than the choropleth map with the authors advocating for its  use in the cancer atlas.

The authors do a nice job introducing each map, the benefits of both and outlined how  each would be applied to communicate cancer statistics as part of the Cancer Atlas. I  think that Section 3 could be tightened up in places, especially with regards to  generating the lineups and the section that outlines the analysis (see below for  specifics).

Overall, I see this as an important contribution not only to the visualisation community  but also to the statistics community who often leave the communication of statistics  and modelled outputs as an afterthought. I therefore recommend this paper be  published after the authors consider my comments and revisions below, largely relating  tao Section 3. I also believe the Cancer Atlas could benefit from such a visualisation and  would encourage the authors to work with the authors of the Atlas to have this  considered. As the acknowledgements suggest the Cancer Atlas team were involved in  discussions, I suspect this would be an easy ask.

Specific Comments:

P7,L7 While the introduction focuses specifically on the maps communicating disease  statistics, it would be good in the conclusion to extrapolate beyond that to gain a  broader interest.

P8, L31-32. I would consider adding to the last sentence to write the following: “The  results are summarized in Section 4, followed by a discussion about the broader  implications for the use of this map style.

P9, L52. I’m on sure if the text in italics appears in the literature or if this is the author’s  view. If the author’s view then I would replace “doesn’t” with “does not”. If it appears in  the literature, please reference.

P9, L55. I would suggest replacing “better” with “adequately”.

P9, L77-78. Consider the following: “Figure 1 shows the hexagon tile map, where the  map is coloured from …

*Completed*

P10, L97. Omit the words “To do”.

*Completed*

P13, L167-170. Are you able to outline the smoothing procedure. This seems a little  vague.

P14, L178-183. The process here seems a little subjective. Can you provide some  reasoning as to why these decisions were made?

P14, L191-192. Why were the locations 1, 7, 10 and 11 not used?

*Completed*

P14, L193-195. This sentence does not make sense. Please revise.

P15, L226. Replace “will be” with “were”.

*Completed*

P15, L234. y_ij = 0,1 represents whether the subject detected the data plot (1) or did not  (0). Please fix.

P15, L239-240. This could be written better. Should read a “logit” link. I would consider  writing the model as follows:

y_ij \~ Bernoulli(p_ij), where

logit(p_ij) = mu + tau_i + delta_j + (tau delta)\_ij i=1,2. J=1,2,3.

Then discuss the random effects.

P16, L247. What is a “Figure Eight contributor ID”? : *This was used by the respondent to uniquely identify themselves and allow us to link them to the paid account we used for recruitment and payment. This reference has been removed, and in other places has been replaced with a unique identifier created for each participant.*

P11, Section 3.7. Could this information be captured more succinctly in a table  perhaps? Line 290-293 just lists words. There are no questions relating to these 3  dotpoints. I’m also wondering why participants do not submit their responses as they  go? Do they also have a chance to go back and change a response? It is difficult to  determine what this process is.

P18, L297-301. The math does not seem to work unless I’m missing something.  Responses were collected from 92 participants. Five were removed which leaves 87 for  evaluation. However you go on to say that Set A were evaluated by 42 participants and  set B, 53 which adds up to 95 participants. Then you go on to say this resulted in 1104  evaluations. Could you please revise and provide a more detailed outline of the  evaluations you performed?

P22 Discussion through to Conclusions. As highlighted earlier, it would be good to  extrapolate the results to other modelled outputs beyond cancer statistics to obtain  broader coverage. There is considerable value in using a hexagon tile map for showing  statistics and modelled output in statistical area levels across Australia or similar.

### 2025-07-07 paper/kobakian-cook-anzjs.qmd
part way through revising paper

--- 2023-03-21 paper/paper.Rmd
@@
 title: "Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics"
+format:
+  quarto-anzjs-pdf:
+    keep-tex: true  
+    shorttitle: "Automated Residual Plot Assessment"
+    double-space: true
+    line-numbers: true
+    # You can specify extra preamble in the file below.
+    include-in-header:
+      - header.tex
+date: today
+date-format: "YYYY" # used to define volumeyear
+author:
+    - name: Stephanie Kobakian  
+      email: stephanie.kobakian@gmail.com
       affiliation:
-  author-columnar: true         ## one column per author
-  #institution-columnar: true  ## one column per institution (multiple autors eventually)
-  # wide: true                  ## one column wide author/affiliation fields
-  institution:
           - name: Queensland University of Technology
             department: Science and Engineering Faculty
-      location: Brisbane, Australia
-      email: stephanie.kobakian@qut.edu.au
-      mark: 1
-      author:
-        - name: Stephanie Kobakian
+            address: 2 George St, Brisbane, Australia
+    - name: Dianne Cook
+      email: dicook@monash.edu
+      affiliation: 
           - name: Monash University
             department: Econometrics and Business Statistics Faculty
-      location: Melbourne, Australia
-      email: dicook@monash.edu
-      mark: 1
-      author:
-        - name: Dianne Cook
+            address: 29 Ancora Imparo Way, Clayton, VIC 3800, Australia
 keywords: ["statistics", "visual inference", "geospatial", "population"]
@@
 bibliography: paper.bib
-output:
-  bookdown::pdf_book: 
-      base_format: rticles::ieee_article
-      number_sections: true
-editor_options: 
-  chunk_output_type: console
-link-citations: true
-citation_package: biblatex
-csl: springer-vancouver.csl
-header-includes: \usepackage{graphicx}
 ---
-
-<!-- Regular paper – 12 double column pages (Submissions may be up to 18 pages in length, subject to MOPC. All regular paper page limits include references and author biographies.) -->
-
-<!-- Changes: thyroid instead of liver - check; lineup need to be hexmap; check language with chatgpt/grammarly; get refs formatted and paper into 10 pages; use new template -->
 
@@
 library(kableExtra)
+library(patchwork)
 
@@
   theme(
-    panel.background = element_rect(fill = "transparent", colour = NA), 
-    plot.background = element_rect(fill = "black", colour = NA),
+    panel.background = element_rect(fill = "black", colour = NA), 
     legend.background = element_rect(fill = "transparent", colour = NA),
     legend.key = element_rect(fill = "transparent", colour = NA),
-    text = element_text(colour = "white"),
     axis.text = element_blank()
@@
   geom_sf(aes(fill = SIR), size = 0.1) + 
-  scale_fill_identity() + invthm
+  scale_fill_identity() + invthm +
+  ggtitle("a. choropleth map")
 
@@
   scale_fill_identity() +
-  invthm + coord_equal()
-```
-
-Introduction
-=============
+  invthm + coord_equal() +
+  ggtitle("b. hexagon tile map")
+```
+
+# Introduction {#sec-introduction}
+
 <!-- General: comparison of displays, motivate hexagon tile map, enough info to motivate aims -->
@@
 The next section discusses the background of geographic data display and visual inference procedures.
-The [Methodology] section describes the methods for conducting the experiment and analysing the results.
-The results are summarized in the [Results] section.
-
-Background
-=============
+The @sec-methodology describes the methods for conducting the experiment and analysing the results.
+The results are summarized in the @sec-results, followed by a discussion about the broader implications for the use of this map style.
+
+# Background {#sec-background}
 
@@
 Spatial visualisations communicate the distribution of statistics over geographic landscapes.
-The choropleth map [@EI], [@BCM] is a traditional display.
+The choropleth map [@EI, @BCM] is a traditional display.
 It is used to present statistics that have been aggregated on geographic units.
@@
 
-```{r thyroid-choro, out.height = "30%", fig.height = 3, fig.width = 4, fig.align='center', fig.cap = "A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2.
+```{r}
+#| label: fig-thyroid
+#| fig-cap: "Thyroid incidence among females across the Statistical Areas of Australia at Level 2, displayed using a choropleth (a) and a hexagon tile map (b).
+Blue indicates lower than average, and red indicates higher than average incidence.
+The choropleth suggests high incidence is clustered on the east coast but misses the high incidence in Perth and a few locations in inner Melbourne visible in the hexagon tile map."
+#| out-width: 100%
+#| fig-width: 8
+#| fig-height: 3
+aus_ggchoro + aus_hexmap_plot + plot_layout(ncol=2)
+```
+
+```{r thyroid-choro, eval=FALSE, out.height = "30%", fig.height = 3, fig.width = 4, fig.align='center', fig.cap = "A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2.
 Blue indicates lower than average and red indicates higher than average incidence.
@@
 Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips.
-Fig.
-\ref{fig:thyroid-choro} shows the choropleth map of thyroid cancer rates in Australia.
+@fig-thyroid a shows the choropleth map of thyroid cancer rates in Australia.
 The choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population related distribution of the statistic [@CBATCC].
-*Land doesn't get cancer, people do* -- a more effective way to communicate the spatial distributions of cancer statistics is needed.
+*Land does not get cancer, people do* -- a more effective way to communicate the spatial distributions of cancer statistics is needed (sentiment motivated by  @monmonier2018how).
 
 <!-- Cartogram -->
-A cartogram is a general solution for better displaying a population-based statistic.
+A cartogram is a general solution for adequately displaying a population-based statistic.
 It transforms the geographic map base to reflect the population in the geographic region, while preserving some aspects of the geographic location.
-There are several cartogram algorithms [@ACTUC], [@CBATCC]; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
+There are several cartogram algorithms [@ACTUC, @CBATCC]; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
 The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units but can result in losing the familiar geographic information.
@@
 The neighbour relationships are mostly maintained by how the circles touch.
-A similar approach was pioneered by Raisz [-@RSCW], using rectangles that tile to align borders of neighbours [@CDWCS].
-There have been thorough reviews of the array of methods, as suitable for cancer atlas displays [@review], [@BCM].
-
-```{r thyroid-hex, out.height = "30%", fig.height = 3, fig.width = 4, fig.align='center', fig.cap = "A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
+A similar approach was pioneered by @RSCW, using rectangles that tile to align borders of neighbours [@CDWCS].
+There have been thorough reviews of the array of methods, as suitable for cancer atlas displays [@review, @BCM].
+
+```{r thyroid-hex, eval=FALSE, out.height = "30%", fig.height = 3, fig.width = 4, fig.align='center', fig.cap = "A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
 The high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) can now be seen, along with numerous isolated spots."}
@@
 The algorithm is available in the R package, sugarbag [@sugarbag].
-Fig.
-\ref{fig:thyroid-hex} shows the hexagon tile map.
-Colour maps from substantially below average (blue) to substantially above average (red) rates.
+@fig-thyroid b shows the hexagon tile map, where the map is coloured from substantially below average (blue) to substantially above average (red) rates.
 The inner city areas have expanded, making it possible to see the cancer incidence in the small, densely populated areas.
@@
 
-In order to assess the effectiveness of the hexagon tile map, the lineup protocol [@GIIV],[@BCHLLSW09] from visual inference procedures is employed.
+In order to assess the effectiveness of the hexagon tile map, the lineup protocol [@BCHLLSW09, @GIIV] from visual inference procedures is employed.
 The approach mirrors classical statistical inference.
@@
 
-To do hypothesis testing with the lineup protocol requires human evaluation.
+Hypothesis testing with the lineup protocol requires human evaluation.
 The human judge is required to identify the most different plot among the field of plots.
@@
 The null hypothesis is explicitly provided by the grammatical plot description.
-For example, if a histogram is the plot type being used, the null might be that the underlying distribution of the data is a Gaussian.
+For example, if a histogram is the map type being used, the null might be that the underlying distribution of the data is a Gaussian.
 Null data would be generated by simulating from a normal model, with the same mean and standard deviation as the data.
@@
 With $K$ observers, the probability of $k$ randomly choosing the data plot, roughly follows a binomial distribution with $p=1/m$.
-Fig.
-\ref{fig:lineup} shows a lineup of the hexagon tile map, of size $m=12$.
+@fig-lineup shows a lineup of the hexagon tile map, of size $m=12$.
 Plot 3 is the data plot, and the remaining 11 are plots of null data.
 
-```{r lineup, fig.cap = "This lineup of twelve hexagon tile map displays contains one map with a real population related structure.
-The rest are null plots that contain spatial correlation between neighbours.", fig.height = 8, fig.width = 8}
+```{r}
+#| label: fig-lineup
+#| fig-cap: "This lineup of twelve hexagon tile map displays contains one map with a real population related structure. The rest are null plots that contain only spatial dependence."
+#| fig-height: 8
+#| fig-width: 8
 ggdraw() +
@@
 
-Methodology
-============
+# Methodology {#sec-methodology}
 
@@
 
-The primary factor in the experiment is the plot type.
+The primary factor in the experiment is the map type.
 The secondary factor is a trend model.
 Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to do well, and two with differing level of inner city hot spots.
-These latter two reflect the structure seen in the thyroid cancer data (Fig.
-\ref{fig:thyroid}).
+These latter two reflect the structure seen in the thyroid cancer data (@fig-thyroid).
 This produces six treatment levels:
@@
 Participants saw a data set only once, either as a choropleth or as a hexagon tile map.
-Table \ref{fig:exp-design} summarises the design and the allocation of the displays.
-
-```{r exp-design, results = "asis", fig.width = 8, fig.height = 8, fig.cap = "The experimental design used in the visual inference study."}
+@fig-exp-design summarises the design and the allocation of the displays.
+
+```{r}
+#| label: fig-exp-design
+#| results: "asis" 
+#| fig-width: 8 
+#| fig-height: 8
+#| out-width: 80%
+#| fig-cap: "The experimental design used in the study. Participants are allocated to with group A or B, to evaluate either the choropleth or hexagon tile map lineup of each simulated data set."
 ggdraw(xlim = c(0,1), ylim = c(0,1)) + draw_plot(rasterGrob(png::readPNG("figures/experiment_design.png")))
@@
 The R package `gstat` [@gstat] was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
+Each null set was further processed to produce maps with similar spatial dependence as those produced by the methods in @atlas-methods, by averaging a small number of spatial neighbours.
 
 ```{r eval=FALSE, echo=FALSE}
+# This is example code illustrating the null data generation
 var.g.dummy <- gstat(formula = z ~ 1, 
@@
                      nmax = 12)
+
+spatial_smoother <- function(area_number, 
+                             values_vector, 
+                             area_weight = 0.5, 
+                             neighbours_list){
+
+  stopifnot( area_weight >= 0 && area_weight <= 1)
+  # List of the neighbours
+  neighbours <- as.vector(neighbours_list[[area_number]])
+  # Remove the current area
+  neighbours <- neighbours[!neighbours == area_number]
+  if ((length(values_vector[neighbours]))==0){
+    smoothed_value <- values_vector[area_number]
+  } else {
+    # Weighted value: area value and neighbours
+    ave_of_neighbours <- mean(values_vector[neighbours], na.rm = TRUE)
+    smoothed_value <- (area_weight)*values_vector[area_number] + (1-area_weight)*ave_of_neighbours
+  }
+  return(smoothed_value)
+}
+
+var.sim1 <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+  left_join(sa3_centroids, ., by=c("longitude", "latitude"))
+
+sa3_sims1_1 <- as_tibble(var.sim1) %>% 
+  mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
+                           values_vector = ., area_weight = 0.5, neighbours_list = sa3_neighbours))
+
 ```
@@
 
-The null model imposed by our hypothesis suggests that neighbors are related.
+<!-- The null model imposed by our hypothesis suggests that neighbors are related.
 The randomness induced when generating the null data was smoothed to mirror the practices employed by the Australian Cancer Atlas statisticians.
@@
 
-This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the thyroid cancer distribution (Fig. \ref{fig:thyroid}).
+This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the thyroid cancer distribution (@fig-thyroid). -->
+
+<!-- methods for smoothing spatial_smoother() in 00_pilot.R and used in all the  pilot_cities.R ... files -->
 
@@
 For each trend model, four real data displays were created by manipulating the centroid values of each of the SA3 geographic units.
-
-The North West to South East (NW-SE) distribution was created using a linear equation of the centroid longitude and latitude values.
-
-The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia, calculated when creating the hexagon tile map using the sugarbag [@sugarbag] package.
-201 of the 336 SA3s were considered greater capital city areas, the values of these areas were increased to create red clusters.
-The amount was chosen to make clusters around the cities visible in the choropleth display even if they were not overtly noticeable.
-
+Each trend model is motivated by patterns observed in spatial data: North West to South East (NW-SE) is a basic spatial trend across the entire country, Three Cities is the existence of clusters of high values, and All Cities is also clusters, but more of them.
+We would expect that clusters pattern to be more visible with a hexagon tile map but the large spatial trend to be more visible in the choropleth map.
+
+The NW-SE distribution was created using a linear equation of the centroid longitude and latitude values.
+The All Cities trend model was created using the distance from the centroid of each geographic unit to the closest capital city in Australia, calculated when creating the hexagon tile map produced by the sugarbag [@sugarbag] package.
+Two-thirds of SA3s (201/336) were considered greater capital city areas, the values of these areas were increased to create red clusters.
+The amount was chosen to make clusters around the cities visible, even in the choropleth with careful inspection.
 A similar selection process was applied to the Three Cities' trend model.
@@
 One of the lineup locations was chosen to embed the real trend model map, in each of the four replicates, for the three trend models.
-The location was chosen from a sub sample of the 12 possible locations.
-The chance of reptition using resampling was introduced to prevent participants from inducing the location by elimination, the locations 1, 7, 10 and 11 were not used.
-
-As seen in Fig \ref{fig:exp-design}, the choropleth and hexagon display used the same location for the real data display of the trend model was added to the spatially correlated null values for each lineup.
-Each set of lineup data was used to produce a choropleth map lineup and hexagon tile map lineup.
-These matched pairs were split between Group A and Group B according to the 2 x 3 factor experimental design depicted in \ref{fig:exp-design}.
+The locations were chosen by random sampling.
+Using random locations reduces the chance that participants might inducing the location coincidentally.
+Locations 1, 7, 10 and 11 were not in the sample.
+
+The lineup locations were the same for both map types, because each set of lineup data was used to produce a choropleth map lineup and hexagon tile map lineup.
+Lineups were grouped into A or B, so that a participant saw only one version.
+Participants were assigned to group A or B, randomly, and thus evaluated either the choropleth or the hexagon tile map lineup.
+Because there were four replicates of each lineup, each participant evaluated two choropleth and two hexagon tile map lineups, for each trend model.
+This design is illustrated in @fig-exp-design.
 
@@
 
-Plots will be made in R [@RCore], with the `ggplot2` package [@ggplot2].
-
+<!-- Plots will be made in R [@RCore], with the `ggplot2` package [@ggplot2].-->   
 ### Modelling
@@
 The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R [@RCore] `glmer()` function in the `lme4` [@lme4] package implements generalised linear mixed effect models.
+The R `glmer()` function in the `lme4` [@lme4] package implements generalised linear mixed effect models.
 The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
 
-$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij} + \epsilon_{i,j}, ~~~ i=1,2; ~j=1,2,3$$
-
-where $y_{ij} = 0, 1$ is the logg odds for whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
+$$
+\hat{y}_{ij} \sim Bernoulli(p_ij)
+$$
+with
+
+$$
+\text{logit}(p_{ij}) = \mu + \tau_i + \delta_j + (\tau \delta)_{ij} ~~~~ i=1,2; ~~ j=1,2,3
+$$
+
+<!--
+$$y_{ij} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij} + \varepsilon_{i,j}, ~~~ i=1,2; ~j=1,2,3$$
+-->
+
+where $y_{ij} = 0, 1$ represents whether the subject detected the data plot (1) or did not (0), $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
 We are allowing for an interaction between map type and trend model as the response is binary, so a logistic model was used.
@@
 
-The model specifies a logistic link, this means the predicted values from the `glmer` model should be back-transformed to fit between 0 and 1.
+The model specifies a logit link, this means the predicted values from the `glmer` model should be back-transformed to fit between 0 and 1.
 The predictions  $\widehat{p}(\eta)$ are transformed to be probabilities between 0 and 1 with the link specified below:
@@
 The survey app contained three tabs.
-Participants were first asked for their demographics their Figure Eight contributor ID, and their consent to the responses being used for analysis.
+Participants were first asked for their demographics their unique identifier and their consent to the responses being used for analysis.
 The demographics collected included participants' preferred pronoun, the highest level of education achieved, their age range and whether they had lived in Australia.
@@
 The set of images differed for Group A and Group B.
-After being allocated to a group, each individual was shown the 12 displays in randomised order.
-
-Three questions were asked regarding each display:
-
- - Plot choice
- - Reason
- - Difficulty
-
-After completing the 12 evaluations, the participants were asked to submit their responses.
+After being allocated to a group, each individual was shown the 12 lineups in randomised order, and asked to report:
+
+ - Plot choice: the number of the plot that they deemed to be most different from the others.
+ - Reason: one of "Clusters of colour", "Colour trend across the areas", "Big differences between neighbouring areas", "All areas have similar colours" or "None of these reasons". 
+ - Certainty: how certain that their choice is different from the others, on a scale of 1-5.
+
+on each of lineup. These responses are saved after entering, but only recorded in the results sheet when the participants clicked the submit button on the final page.
 
@@
 
-Results
-============
+# Results {#sec-results}
 
@@
 
-Fig.
-\ref{fig:detect-compare} displays the average detection rates for the two types of plot separately for each trend model.
-Each trend model was tested using four repetitions, evaluations on the same data set were seen as either choropleths or hexagon tile maps by each group as specified in Table.
-\ref{fig:exp-design}; the detection rates for each display are connected by a line segment.
+@fig-detect-compare displays the average detection rates for the two types of plot separately for each trend model.
+Each trend model was tested using four repetitions, evaluations on the same data set were seen as either choropleths or hexagon tile maps by each group as specified in @fig-exp-design; the detection rates for each display are connected by a line segment.
 The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts.
-One replicate for the All Cities group had similar detection rates for both plot types, the rate of detection using the choropleth map was much higher than other replicates.
+One replicate for the All Cities group had similar detection rates for both map types, the rate of detection using the choropleth map was much higher than other replicates.
 Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map.
@@
 
-```{r detect-compare, fig.cap = "The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models.
+```{r}
+#| label: fig-detect-compare
+#| fig-cap: "The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models.
 Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup.
-The points for the same data set shown in a choroleth or hexagon tile map display are linked to show the difference in the detection rate.", fig.height=5}
+The points for the same data set shown in a choroleth or hexagon tile map display are linked to show the difference in the detection rate."
+#| fig-height: 5
 # Detectability rate for each lineup (image)
@@
 
-Table.
-\ref{tab:desc-stats} shows the means and standard deviations of the detection rate for each type of plot and each trend model.
+@tbl-desc-stats shows the means and standard deviations of the detection rate for each type of plot and each trend model.
 This also gives the standard deviations, the smallest standard deviation for all sets of replicates was the Three Cities trend model shown in a Choropleth display.
@@
 
-```{r desc-stats, results = "asis"}
+```{r}
+#| label: tbl-desc-stats
+#| results: "asis"
 types <- c("Choro.", "", "Hex.", "")
@@
 
-Table.
-\ref{tab:detect-glmer1} presents a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on the detection rate.
-The results support the summary from Fig.
-\ref{fig:detect-compare} and all parameters are statistically significant despite the large standard deviations observed in Table.
-\ref{tab:desc-stats}.
+@tbl-detect-glmer1 presents a summary of the generalised linear mixed effects model, testing the effect of map type and trend model on the detection rate.
+The results support the summary from @fig-detect-compare and all parameters are statistically significant despite the large standard deviations observed in @tbl-desc-stats.
 Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
 Allowing for the interaction effect, the difference in detection rate decreases for population related displays for a choropleth map lineup, but increases for a hexagon tile map display.
-The log odds of detection show in Table. \ref{tab:detect-glmer1} can be back transformed after taking the sum of all terms for the trend and type of display that are of interest.
+The log odds of detection show in @tbl-detect-glmer1 can be back transformed after taking the sum of all terms for the trend and type of display that are of interest.
 For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to `r round(exp(0.46+0.07)/(1+exp(0.46+0.07)), 2)` from `r round(exp(0.07)/(1+exp(0.07)),2)` for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
@@
 
-```{r detect-glmer1, results="asis"}
+```{r}
+#| label: tbl-detect-glmer1
+#| results: "asis"
 # Mixed effects models
@@
 
-Fig.
-\ref{fig:beeswarm} shows horizontally jittered dot plots to contrast the time taken by participants to evaluate each lineup when viewing each type of display.
+@fig-beeswarm shows horizontally jittered dot plots to contrast the time taken by participants to evaluate each lineup when viewing each type of display.
 The time are also separated by trend model and whether the data plot was detected or not detected.
@@
 
-```{r beeswarm, fig.cap = "The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots.
-The colored point indicates average time taken for each plot type.
-Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between plot types.", fig.height=8}
-# Di playing
+```{r}
+#| label: fig-beeswarm
+#| fig-cap: "The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots.
+The colored point indicates average time taken for each map type.
+Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between map types."
+#| fig-height: 8
 s <- d %>% group_by(type, trend, detect_f) %>%
@@
 assessment by the participant prompted by the question: ‘How certain are you about your choice?’.
-Fig.
-\ref{fig:certainty} shows the amount of times participants provided each level of certainty.
+@fig-certainty shows the amount of times participants provided each level of certainty.
 This was separated for each combination of trend models and display type, and colored depending on whether a participant correctly detected the data plot in the lineup.
@@
 
-```{r certainty, fig.cap = "The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
+```{r}
+#| label: fig-certainty 
+#| fig-cap: "The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
 Participants were more likely to choose a high certainty when considering a Choropleth map.
-The mid value of 3 was the default certainty, it was chosen most for the Hexagon tile map displays.", fig.height=5}
+The mid value of 3 was the default certainty, it was chosen most for the Hexagon tile map displays."
+#| fig-height: 5
 d <- d %>% 
@@
 Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons. 
-"Color trend across the areas" was the most common selection for NW-SE trend displays.
+"Color trend across the areas" was the most common selection for NW-SE trend displays (@tbl-reason).
 
@@
 
-```{r reason, results = "asis"}
+```{r}
+#| label: tbl-reason
+#| results: "asis"
 # Qualitative analysis of reason
@@
 
-Discussion
-============
+# Discussion
 
@@
 
-The differences seen in the \ref{fig:detect-compare} plot and Table.
-\ref{tab:desc-stats} are reflected in the model results.
+The differences seen in the @fig-detect-compare plot and @tbl-desc-stats are reflected in the model results.
 Surprisingly the difference for the geographic distribution was significant at the 0.05 level.
@@
 it was expected that the participants may take longer to consider the hexagon tile map distribution but would be able to detect the data plot in the lineup.
-The bimodal distributions seen in Fig.
-\ref{fig:beeswarm} showed very little difference in the mean evaluation times.
+The bimodal distributions seen in @fig-beeswarm showed very little difference in the mean evaluation times.
 As the maximum time of all of the distributions approached 60 seconds it cannot be said that the participants' took longer to evaluate the hexagon tile map displays.
@@
 The responses to the questions asked of participants included the reason for their choice and the certainty around their choice.
-Fig.
-\ref{tab:reason} shows high levels of certainty of 4 and 5 were chosen by participants when looking at the population distributions in a choropleth map display show that they were over confident when attempting to find the real data plot in the choropleth map displays.
+@tbl-reason shows high levels of certainty of 4 and 5 were chosen by participants when looking at the population distributions in a choropleth map display show that they were over confident when attempting to find the real data plot in the choropleth map displays.
 Participants performed better on the NW-SE distribution shown in the choropleth display and were reasonably confident about their decisions.
@@
 
-Conclusion
-============
+# Conclusion
 
@@
 
-Acknowledgment
-==============
+# Acknowledgments {-}
 
@@
 
- - For document creation: rmarkdown [@rmarkdown], rticles [@rticles], knitr [@knitr].
- - For lineup creation and data analysis: tidyverse [@tidyverse], nullabor [@nullabor], ggthemes [@ggthemes], RColorBrewer [@RColorBrewer].
- - For image displays: cowplot [@cowplot], png [@png], grid [@grid].
- - For modelling and presentation of models: gstat [@gstat], lme4 [@lme4], kableExtra [@kableExtra].
+ - Document creation: quarto [@Allaire_Quarto_2025], anzjs template [@quarto-anzjs], knitr [@knitr].
+ - Lineup creation: nullabor [@nullabor], gstat [@gstat].
+ - Data analysis: tidyverse [@tidyverse], ggthemes [@ggthemes], RColorBrewer [@RColorBrewer].
+ - Plots: ggplot2 [@ggplot2], cowplot [@cowplot], png [@png], grid [@grid].
+ - Modelling and summary presentation: lme4 [@lme4], kableExtra [@kableExtra].
 
@@
 All applicants provided informed consent in line with QUT regulations prior to participating in this research.
-
-References {.numbered}
-==========

### 2025-07-07 paper/kobakian-cook-anzjs.tex
part way through revising paper

--- 2025-07-07 paper/paper.tex
@@
+% Options for packages loaded elsewhere
 % Options for packages loaded elsewhere
@@
 \PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
 %
 \documentclass[
-]{article}
+doublespace,
+  times]{anzsauth}
+\usepackage{xcolor}
 \usepackage{amsmath,amssymb}
+\setcounter{secnumdepth}{5}
 \usepackage{iftex}
@@
 \makeatother
-\usepackage{xcolor}
-\usepackage[margin=1in]{geometry}
+% Make \paragraph and \subparagraph free-standing
+\makeatletter
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+\makeatother
+
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 \makeatother
+
 \setlength{\emergencystretch}{3em} % prevent overfull lines
+
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-% definitions for citeproc citations
-\NewDocumentCommand\citeproctext{}{}
-\NewDocumentCommand\citeproc{mm}{%
-  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
-\makeatletter
- % allow citations to break across lines
- \let\@cite@ofmt\@firstofone
- % avoid brackets around text for \cite:
- \def\@biblabel#1{}
- \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
-\makeatother
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
- {\begin{list}{}{%
-  \setlength{\itemindent}{0pt}
-  \setlength{\leftmargin}{0pt}
-  \setlength{\parsep}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-   \setlength{\leftmargin}{\cslhangindent}
-   \setlength{\itemindent}{-1\cslhangindent}
-  \fi
-  % set entry spacing
-  \setlength{\itemsep}{#2\baselineskip}}}
- {\end{list}}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\usepackage{graphicx}
+
+\usepackage[]{natbib}
+\bibliographystyle{anzsj}
+
+\usepackage{pmboxdraw}
 \usepackage{booktabs}
@@
 \usepackage{xcolor}
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
 \usepackage{bookmark}
@@
   pdftitle={Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics},
+  pdfauthor={Stephanie Kobakian; Dianne Cook},
   pdfkeywords={statistics, visual inference, geospatial, population},
-  hidelinks,
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
   pdfcreator={LaTeX via pandoc}}
+
+\usepackage{moreverb}
+\usepackage{url}
+\usepackage{grffile}
+\usepackage[UKenglish]{isodate}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% The year in the following may need to be updated!
+\def\volumeyear{2025}
+
+% The following command ("obviously") effects line numbering
+% of the document.
+
+\usepackage{lineno}
+\linenumbers
+
+\def\firstletters{\bgroup \catcode`-=10 \catcode`(=10 \filA}
+\def\filA#1{\filB#1 {\end} }
+\def\filB#1#2 {\ifx\end#1\egroup \else#1 \expandafter\filB\fi}
+
+\runningheads{
+Automated Residual Plot Assessment
+}{
+\firstletters{STEPHANIE}KOBAKIAN, AND  \firstletters{DIANNE}COOK
+}
 
@@
 Tile Map for Communicating Cancer Statistics}
-\author{}
-\date{\vspace{-2.5em}}
-
+
+\author{
+Stephanie Kobakian\addressnum{1} and
+Dianne Cook\addressnum{2}
+}
+\affiliation{
+Queensland University of Technology and
+Monash University
+}
+
+\address{
+\addressnum{1} Science and Engineering Faculty, Queensland University of
+Technology, 2 George St, Brisbane, Australia\\
+\addressnum{2} Econometrics and Business Statistics Faculty, Monash
+University, 29 Ancora Imparo Way, Clayton, VIC 3800, Australia\\
+\hspace*{1ex} Email:  
+}
+
+\date{2025}
 \begin{document}
-\maketitle
+
 \begin{abstract}
@@
 
-\section{Introduction}\label{introduction}
+\keywords{statistics; visual inference; geospatial; population}
+
+\maketitle
+
+\section{Introduction}\label{sec-introduction}
 
@@
 other purposes. The algorithm to construct a hexagon tile map is
-available in the R package sugarbag {[}\citeproc{ref-sugarbag}{1}{]}.
+available in the R package sugarbag \citep{sugarbag}.
 
@@
 
-The Australian Cancer Atlas {[}\citeproc{ref-atlas}{2}{]} is an online
-interactive web tool created to explore the burden of cancer on
-Australian communities. There are many cancer types to be explored
-individually or aggregated. The Australian Cancer Atlas allows users to
-explore the patterns in the distributions of cancer statistics over the
-geographic space of Australia. It uses a choropleth map display and
-diverging color scheme to draw attention to relationships between
-neighboring areas. The hexagon tile map may be a useful alternative
-display to enhance the atlas.
+The Australian Cancer Atlas \citep{atlas} is an online interactive web
+tool created to explore the burden of cancer on Australian communities.
+There are many cancer types to be explored individually or aggregated.
+The Australian Cancer Atlas allows users to explore the patterns in the
+distributions of cancer statistics over the geographic space of
+Australia. It uses a choropleth map display and diverging color scheme
+to draw attention to relationships between neighboring areas. The
+hexagon tile map may be a useful alternative display to enhance the
+atlas.
 
 The experiment was conducted using the lineup protocol, a visual
-inference procedure {[}\citeproc{ref-GIIV}{3}{]}, to objectively test
-the effectiveness of the two displays.
+inference procedure \citep{GIIV}, to objectively test the effectiveness
+of the two displays.
 
@@
 background of geographic data display and visual inference procedures.
-The \hyperref[methodology]{Methodology} section describes the methods
-for conducting the experiment and analysing the results. The results are
-summarized in the \hyperref[results]{Results} section.
-
-\section{Background}\label{background}
+The Section~\ref{sec-methodology} describes the methods for conducting
+the experiment and analysing the results. The results are summarized in
+the Section~\ref{sec-results}, followed by a discussion about the
+broader implications for the use of this map style.
+
+\section{Background}\label{sec-background}
 
@@
 Spatial visualisations communicate the distribution of statistics over
-geographic landscapes. The choropleth map {[}\citeproc{ref-EI}{4}{]},
-{[}\citeproc{ref-BCM}{5}{]} is a traditional display. It is used to
-present statistics that have been aggregated on geographic units.
-Creating a choropleth map involves drawing polygons representing the
-administrative boundaries, and filling with colour mapped to the value
-of the statistic. The choropleth map places the statistic in the context
-of the spatial domain, so that the reader can see whether there are
-spatial trends, clusters or anomalies. This is important for digesting
-disease patterns. If there is a trend it may imply that the disease is
-spreading from one location to another. If there is a cluster, or an
-anomaly, there may be a localized outbreak of the disease. Aggregating
-the statistic on administrative units, provides a level of privacy to
-individuals, while allowing the impact of the disease on the community
-to be analyzed.
+geographic landscapes. The choropleth map \citep[\citet{BCM}]{EI} is a
+traditional display. It is used to present statistics that have been
+aggregated on geographic units. Creating a choropleth map involves
+drawing polygons representing the administrative boundaries, and filling
+with colour mapped to the value of the statistic. The choropleth map
+places the statistic in the context of the spatial domain, so that the
+reader can see whether there are spatial trends, clusters or anomalies.
+This is important for digesting disease patterns. If there is a trend it
+may imply that the disease is spreading from one location to another. If
+there is a cluster, or an anomaly, there may be a localized outbreak of
+the disease. Aggregating the statistic on administrative units, provides
+a level of privacy to individuals, while allowing the impact of the
+disease on the community to be analyzed.
 
@@
 
-{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{paper_files/figure-latex/thyroid-choro-1}
-
-}
-
-\caption{A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2.
-Blue indicates lower than average and red indicates higher than average incidence.
-A cluster of high incidence is visible on the east coast.}\label{fig:thyroid-choro}
-\end{figure}
+\centering{
+
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-thyroid-1.pdf}
+
+}
+
+\caption{\label{fig-thyroid}Thyroid incidence among females across the
+Statistical Areas of Australia at Level 2, displayed using a choropleth
+(a) and a hexagon tile map (b). Blue indicates lower than average, and
+red indicates higher than average incidence. The choropleth suggests
+high incidence is clustered on the east coast but misses the high
+incidence in Perth and a few locations in inner Melbourne visible in the
+hexagon tile map.}
+
+\end{figure}%
 
@@
 settled, with the population densely clustered into the narrow coastal
-strips. Fig. \ref{fig:thyroid-choro} shows the choropleth map of thyroid
+strips. Figure~\ref{fig-thyroid} a shows the choropleth map of thyroid
 cancer rates in Australia. The choropleth map focuses attention on the
 geography, and for heterogeneously sized areas it presents a biased view
-of the population related distribution of the statistic
-{[}\citeproc{ref-CBATCC}{6}{]}. \emph{Land doesn't get cancer, people
-do} -- a more effective way to communicate the spatial distributions of
-cancer statistics is needed.
-
-A cartogram is a general solution for better displaying a
+of the population related distribution of the statistic \citep{CBATCC}.
+\emph{Land does not get cancer, people do} -- a more effective way to
+communicate the spatial distributions of cancer statistics is needed
+(sentiment motivated by \citet{monmonier2018how}).
+
+A cartogram is a general solution for adequately displaying a
 population-based statistic. It transforms the geographic map base to
@@
 aspects of the geographic location. There are several cartogram
-algorithms {[}\citeproc{ref-ACTUC}{7}{]},
-{[}\citeproc{ref-CBATCC}{6}{]}; each involves shifting the boundaries of
-geographic units, using the value of the statistic to increase or
-decrease the area taken by the geographic unit on the map. The changes
-to the boundaries result in cartograms that accurately communicate
-population by map area for each of the geographic units but can result
-in losing the familiar geographic information. For Australia, the
-transformations warp the country so that it is no longer recognizable.
+algorithms \citep[\citet{CBATCC}]{ACTUC}; each involves shifting the
+boundaries of geographic units, using the value of the statistic to
+increase or decrease the area taken by the geographic unit on the map.
+The changes to the boundaries result in cartograms that accurately
+communicate population by map area for each of the geographic units but
+can result in losing the familiar geographic information. For Australia,
+the transformations warp the country so that it is no longer
+recognizable.
 
@@
 and representation of geographic units. The non-contiguous cartogram
-method {[}\citeproc{ref-NAC}{8}{]} keeps the shapes of geographic units
-intact, and changes the size of the shape. This method disconnects areas
-creating empty space on the display losing the continuity of the spatial
-display of the statistic. The Dorling cartogram
-{[}\citeproc{ref-ACTUC}{7}{]} represents each unit as a circle, sized
-according to the value of the statistic. The neighbour relationships are
-mostly maintained by how the circles touch. A similar approach was
-pioneered by Raisz {[}\citeproc{ref-RSCW}{9}{]}, using rectangles that
-tile to align borders of neighbours {[}\citeproc{ref-CDWCS}{10}{]}.
-There have been thorough reviews of the array of methods, as suitable
-for cancer atlas displays {[}\citeproc{ref-review}{11}{]},
-{[}\citeproc{ref-BCM}{5}{]}.
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth,height=0.3\textheight]{paper_files/figure-latex/thyroid-hex-1}
-
-}
-
-\caption{A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
-The high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) can now be seen, along with numerous isolated spots.}\label{fig:thyroid-hex}
-\end{figure}
+method \citep{NAC} keeps the shapes of geographic units intact, and
+changes the size of the shape. This method disconnects areas creating
+empty space on the display losing the continuity of the spatial display
+of the statistic. The Dorling cartogram \citep{ACTUC} represents each
+unit as a circle, sized according to the value of the statistic. The
+neighbour relationships are mostly maintained by how the circles touch.
+A similar approach was pioneered by \citet{RSCW}, using rectangles that
+tile to align borders of neighbours \citep{CDWCS}. There have been
+thorough reviews of the array of methods, as suitable for cancer atlas
+displays \citep[\citet{BCM}]{review}.
 
@@
 locations or regions in remote areas. The algorithm is available in the
-R package, sugarbag {[}\citeproc{ref-sugarbag}{1}{]}. Fig.
-\ref{fig:thyroid-hex} shows the hexagon tile map. Colour maps from
-substantially below average (blue) to substantially above average (red)
-rates. The inner city areas have expanded, making it possible to see the
-cancer incidence in the small, densely populated areas. Remote regions
-are represented by isolated hexagons, which is not ideal, but maintains
-the spatial location of these data values. It is of interest to know how
-well the spatial distribution is perceived for this display, in
-comparison to the choropleth.
+R package, sugarbag \citep{sugarbag}. Figure~\ref{fig-thyroid} b shows
+the hexagon tile map, where the map is coloured from substantially below
+average (blue) to substantially above average (red) rates. The inner
+city areas have expanded, making it possible to see the cancer incidence
+in the small, densely populated areas. Remote regions are represented by
+isolated hexagons, which is not ideal, but maintains the spatial
+location of these data values. It is of interest to know how well the
+spatial distribution is perceived for this display, in comparison to the
+choropleth.
 
@@
 In order to assess the effectiveness of the hexagon tile map, the lineup
-protocol {[}\citeproc{ref-GIIV}{3}{]},{[}\citeproc{ref-BCHLLSW09}{12}{]}
-from visual inference procedures is employed. The approach mirrors
-classical statistical inference. The procedures for doing a power
-comparison of competing plot designed, outlined in
-{[}\citeproc{ref-GTPCCD}{13}{]}, are followed.
+protocol \citep[\citet{GIIV}]{BCHLLSW09} from visual inference
+procedures is employed. The approach mirrors classical statistical
+inference. The procedures for doing a power comparison of competing plot
+designed, outlined in \citet{GTPCCD}, are followed.
 
@@
 the data plot is embedded in a field of null plots. Defining the plot
-using a grammar of graphics {[}\citeproc{ref-ggplot2}{14}{]} makes it a
-functional mapping of the variables and thus, it can be considered to be
-a statistic. With the same data, two different plots can be considered
-to be competing statistics, one possibly a more powerful statistic than
-the other.
-
-To do hypothesis testing with the lineup protocol requires human
-evaluation. The human judge is required to identify the most different
-plot among the field of plots. If this corresponds to the data plot --
-the test statistic -- the null hypothesis is rejected. It means that the
-data plot is extreme relative to the reference distribution of null
-plots.
+using a grammar of graphics \citep{ggplot2} makes it a functional
+mapping of the variables and thus, it can be considered to be a
+statistic. With the same data, two different plots can be considered to
+be competing statistics, one possibly a more powerful statistic than the
+other.
+
+Hypothesis testing with the lineup protocol requires human evaluation.
+The human judge is required to identify the most different plot among
+the field of plots. If this corresponds to the data plot -- the test
+statistic -- the null hypothesis is rejected. It means that the data
+plot is extreme relative to the reference distribution of null plots.
 
 The null hypothesis is explicitly provided by the grammatical plot
-description. For example, if a histogram is the plot type being used,
-the null might be that the underlying distribution of the data is a
+description. For example, if a histogram is the map type being used, the
+null might be that the underlying distribution of the data is a
 Gaussian. Null data would be generated by simulating from a normal
@@
 With \(K\) observers, the probability of \(k\) randomly choosing the
-data plot, roughly follows a binomial distribution with \(p=1/m\). Fig.
-\ref{fig:lineup} shows a lineup of the hexagon tile map, of size
+data plot, roughly follows a binomial distribution with \(p=1/m\).
+Figure~\ref{fig-lineup} shows a lineup of the hexagon tile map, of size
 \(m=12\). Plot 3 is the data plot, and the remaining 11 are plots of
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/lineup-1} \caption{This lineup of twelve hexagon tile map displays contains one map with a real population related structure.
-The rest are null plots that contain spatial correlation between neighbours.}\label{fig:lineup}
-\end{figure}
+
+\centering{
+
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-lineup-1.pdf}
+
+}
+
+\caption{\label{fig-lineup}This lineup of twelve hexagon tile map
+displays contains one map with a real population related structure. The
+rest are null plots that contain only spatial dependence.}
+
+\end{figure}%
 
@@
 
-\section{Methodology}\label{methodology}
+\section{Methodology}\label{sec-methodology}
 
@@
 Australia is used for the study, with Statistical Area 3 (SA3)
-{[}\citeproc{ref-abs2016}{15}{]} as the geographic units. The results
-should apply broadly to any other geographic area of interest.
+\citep{abs2016} as the geographic units. The results should apply
+broadly to any other geographic area of interest.
 
@@
 
-The primary factor in the experiment is the plot type. The secondary
+The primary factor in the experiment is the map type. The secondary
 factor is a trend model. Three trend models were developed, one
@@
 spots. These latter two reflect the structure seen in the thyroid cancer
-data (Figures \ref{fig:thyroid-choro}, \ref{fig:thyroid-hex}). This
-produces six treatment levels:
+data (Figure~\ref{fig-thyroid}). This produces six treatment levels:
 
@@
 data set only once, either as a choropleth or as a hexagon tile map.
-Table \ref{fig:exp-design} summarises the design and the allocation of
+Figure~\ref{fig-exp-design} summarises the design and the allocation of
 the displays.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/exp-design-1} \caption{The experimental design used in the visual inference study.}\label{fig:exp-design}
-\end{figure}
+
+\centering{
+
+\includegraphics[width=0.8\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-exp-design-1.pdf}
+
+}
+
+\caption{\label{fig-exp-design}The experimental design used in the
+study. Participants are allocated to with group A or B, to evaluate
+either the choropleth or hexagon tile map lineup of each simulated data
+set.}
+
+\end{figure}%
 
@@
 and spatial dependence are constant over the geographic units.
-Stationary data is specified by a variogram model
-{[}\citeproc{ref-POG}{16}{]}. Simulating from a variogram model, where
-the spatial dependence is specified, generates the stationary spatial
-data used for the null plots. The parameters for the Gaussian model were
-sill=1, range=0.3 with the variance generated by a standard normal
-distribution.
-
-The R package \texttt{gstat} {[}\citeproc{ref-gstat}{17}{]} was used to
-simulate 144 null sets, 12 data sets for each plot in a lineup, and 12
-sets for 12 lineups.
-
-The null model imposed by our hypothesis suggests that neighbors are
-related. The randomness induced when generating the null data was
-smoothed to mirror the practices employed by the Australian Cancer Atlas
-statisticians. In these 12 sets of data, each of the 12 maps were
-smoothed several times to replicate the spatial autocorrelation seen in
-cancer data sets presented in the Australian Cancer Atlas, without
-implementing uncertainty via transparency.
-
-A list of neighbors for each geographic unit was generated to use when
-smoothing the distributions. For each geographic unit the same spatial
-smoother was applied in each layer of smoothing. It kept half of the
-units' previous value, and derived the new half as the mean of the
-values of its neighbors at the previous layer of smoothing.
-
-This smoothing allowed neighbors to be related to each other, but also
-allowed outliers, and showed distributions similar to the thyroid cancer
-distribution (Figures \ref{fig:thyroid-choro}, \ref{fig:thyroid-hex}).
+Stationary data is specified by a variogram model \citep{POG}.
+Simulating from a variogram model, where the spatial dependence is
+specified, generates the stationary spatial data used for the null
+plots. The parameters for the Gaussian model were sill=1, range=0.3 with
+the variance generated by a standard normal distribution.
+
+The R package \texttt{gstat} \citep{gstat} was used to simulate 144 null
+sets, 12 data sets for each plot in a lineup, and 12 sets for 12
+lineups. Each null set was further processed to produce maps with
+similar spatial dependence as those produced by the methods in
+\citet{atlas-methods}, by averaging a small number of spatial
+neighbours.
 
@@
 manipulating the centroid values of each of the SA3 geographic units.
-
-The North West to South East (NW-SE) distribution was created using a
-linear equation of the centroid longitude and latitude values.
-
-The All Cities trend model was created using the distance from the
-centroid of each geographic unit to the closest capital city in
-Australia, calculated when creating the hexagon tile map using the
-sugarbag {[}\citeproc{ref-sugarbag}{1}{]} package. 201 of the 336 SA3s
-were considered greater capital city areas, the values of these areas
-were increased to create red clusters. The amount was chosen to make
-clusters around the cities visible in the choropleth display even if
-they were not overtly noticeable.
-
-A similar selection process was applied to the Three Cities' trend
-model. However, for each of the four replicates for the Three Cities
-trend, a random sample of capital cities was taken from Sydney,
-Brisbane, Melbourne, Adelaide, Perth, and Hobart. Only values of the
-areas nearest to the three cities were increased to create clusters.
+Each trend model is motivated by patterns observed in spatial data:
+North West to South East (NW-SE) is a basic spatial trend across the
+entire country, Three Cities is the existence of clusters of high
+values, and All Cities is also clusters, but more of them. We would
+expect that clusters pattern to be more visible with a hexagon tile map
+but the large spatial trend to be more visible in the choropleth map.
+
+The NW-SE distribution was created using a linear equation of the
+centroid longitude and latitude values. The All Cities trend model was
+created using the distance from the centroid of each geographic unit to
+the closest capital city in Australia, calculated when creating the
+hexagon tile map produced by the sugarbag \citep{sugarbag} package.
+Two-thirds of SA3s (201/336) were considered greater capital city areas,
+the values of these areas were increased to create red clusters. The
+amount was chosen to make clusters around the cities visible, even in
+the choropleth with careful inspection. A similar selection process was
+applied to the Three Cities' trend model. However, for each of the four
+replicates for the Three Cities trend, a random sample of capital cities
+was taken from Sydney, Brisbane, Melbourne, Adelaide, Perth, and Hobart.
+Only values of the areas nearest to the three cities were increased to
+create clusters.
 
@@
 map, in each of the four replicates, for the three trend models. The
-location was chosen from a sub sample of the 12 possible locations. The
-chance of reptition using resampling was introduced to prevent
-participants from inducing the location by elimination, the locations 1,
-7, 10 and 11 were not used.
-
-As seen in Fig \ref{fig:exp-design}, the choropleth and hexagon display
-used the same location for the real data display of the trend model was
-added to the spatially correlated null values for each lineup. Each set
+locations were chosen by random sampling. Using random locations reduces
+the chance that participants might inducing the location coincidentally.
+Locations 1, 7, 10 and 11 were not in the sample.
+
+The lineup locations were the same for both map types, because each set
 of lineup data was used to produce a choropleth map lineup and hexagon
-tile map lineup. These matched pairs were split between Group A and
-Group B according to the 2 x 3 factor experimental design depicted in
-\ref{fig:exp-design}.
+tile map lineup. Lineups were grouped into A or B, so that a participant
+saw only one version. Participants were assigned to group A or B,
+randomly, and thus evaluated either the choropleth or the hexagon tile
+map lineup. Because there were four replicates of each lineup, each
+participant evaluated two choropleth and two hexagon tile map lineups,
+for each trend model. This design is illustrated in
+Figure~\ref{fig-exp-design}.
 
@@
 
-Plots will be made in R {[}\citeproc{ref-RCore}{18}{]}, with the
-\texttt{ggplot2} package {[}\citeproc{ref-ggplot2}{14}{]}.
-
 \subsubsection{Modelling}\label{modelling}
@@
 The likelihood of detecting the data plot in the lineup can be modelled
-using a linear mixed effects model. The R {[}\citeproc{ref-RCore}{18}{]}
-\texttt{glmer()} function in the \texttt{lme4}
-{[}\citeproc{ref-lme4}{19}{]} package implements generalised linear
+using a linear mixed effects model. The R \texttt{glmer()} function in
+the \texttt{lme4} \citep{lme4} package implements generalised linear
 mixed effect models. The model used includes the two main effects map
@@
 
-\[\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij} + \epsilon_{i,j}, ~~~ i=1,2; ~j=1,2,3\]
-
-where \(y_{ij} = 0, 1\) is the logg odds for whether the subject
-detected the data plot, \(\mu\) is the overall mean, \(\tau_i, i=1,2\)
+\[
+\hat{y}_{ij} \sim Bernoulli(p_ij)
+\] with
+
+\[
+\text{logit}(p_{ij}) = \mu + \tau_i + \delta_j + (\tau \delta)_{ij} ~~~~ i=1,2; ~~ j=1,2,3
+\]
+
+where \(y_{ij} = 0, 1\) represents whether the subject detected the data
+plot (1) or did not (0), \(\mu\) is the overall mean, \(\tau_i, i=1,2\)
 is the map type effect, \(\delta_j\) is the trend model effect. We are
@@
 
-The model specifies a logistic link, this means the predicted values
-from the \texttt{glmer} model should be back-transformed to fit between
-0 and 1. The predictions \(\widehat{p}(\eta)\) are transformed to be
+The model specifies a logit link, this means the predicted values from
+the \texttt{glmer} model should be back-transformed to fit between 0 and
+1. The predictions \(\widehat{p}(\eta)\) are transformed to be
 probabilities between 0 and 1 with the link specified below:
@@
 
-The taipan {[}\citeproc{ref-taipan}{20}{]} package for R was used to
-create the survey web application. This structure was altered to collect
-responses regarding participants demographics and their survey
-responses. The survey app contained three tabs. Participants were first
-asked for their demographics their Figure Eight contributor ID, and
-their consent to the responses being used for analysis. The demographics
-collected included participants' preferred pronoun, the highest level of
-education achieved, their age range and whether they had lived in
-Australia.
+The taipan \citep{taipan} package for R was used to create the survey
+web application. This structure was altered to collect responses
+regarding participants demographics and their survey responses. The
+survey app contained three tabs. Participants were first asked for their
+demographics their unique identifier and their consent to the responses
+being used for analysis. The demographics collected included
+participants' preferred pronoun, the highest level of education
+achieved, their age range and whether they had lived in Australia.
 
@@
 secure link to the googlesheet used to store results. The application
-connected to the googlesheet using the googlesheets
-{[}\citeproc{ref-sheets}{21}{]} R package when participants opened the
-application, and interacted again when participants chose to submit the
-survey. At this time it added the participant's responses to the twelve
-lineup displays as twelve rows of data in the googlesheet.
+connected to the googlesheet using the googlesheets \citep{sheets} R
+package when participants opened the application, and interacted again
+when participants chose to submit the survey. At this time it added the
+participant's responses to the twelve lineup displays as twelve rows of
+data in the googlesheet.
 
@@
 Participants were recruited from the Figure Eight crowdsourcing platform
-{[}\citeproc{ref-figeight}{22}{]} to evaluate lineups. The lineup
-protocol expects that the participants are uninvolved judges with no
-prior knowledge of the data, to avoid inadvertently affecting results.
-Potential participants needed to have achieved level 2 or level 3 from
-prior work on the platform. All participants were at least 18 years old.
+\citep{figeight} to evaluate lineups. The lineup protocol expects that
+the participants are uninvolved judges with no prior knowledge of the
+data, to avoid inadvertently affecting results. Potential participants
+needed to have achieved level 2 or level 3 from prior work on the
+platform. All participants were at least 18 years old.
 
@@
 differed for Group A and Group B. After being allocated to a group, each
-individual was shown the 12 displays in randomised order.
-
-Three questions were asked regarding each display:
+individual was shown the 12 lineups in randomised order, and asked to
+report:
 
@@
 \item
-  Plot choice
-\item
-  Reason
-\item
-  Difficulty
+  Plot choice: the number of the plot that they deemed to be most
+  different from the others.
+\item
+  Reason: one of ``Clusters of colour'', ``Colour trend across the
+  areas'', ``Big differences between neighbouring areas'', ``All areas
+  have similar colours'' or ``None of these reasons''.
+\item
+  Certainty: how certain that their choice is different from the others,
+  on a scale of 1-5.
 \end{itemize}
 
-After completing the 12 evaluations, the participants were asked to
-submit their responses.
-
-\section{Results}\label{results}
+on each of lineup. These responses are saved after entering, but only
+recorded in the results sheet when the participants clicked the submit
+button on the final page.
+
+\section{Results}\label{sec-results}
 
@@
 
-Fig. \ref{fig:detect-compare} displays the average detection rates for
+Figure~\ref{fig-detect-compare} displays the average detection rates for
 the two types of plot separately for each trend model. Each trend model
@@
 seen as either choropleths or hexagon tile maps by each group as
-specified in Table. \ref{fig:exp-design}; the detection rates for each
+specified in Figure~\ref{fig-exp-design}; the detection rates for each
 display are connected by a line segment. The Three Cities and All Cities
@@
 replicate for the All Cities group had similar detection rates for both
-plot types, the rate of detection using the choropleth map was much
+map types, the rate of detection using the choropleth map was much
 higher than other replicates. Surprisingly, participants could also
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/detect-compare-1} \caption{The detection rates achieved by participants are contrasted when viewing the four replicates of the three trend models.
-Each point shows the probability of detection for the lineup display, the facets separate the trend models hidden in the lineup.
-The points for the same data set shown in a choroleth or hexagon tile map display are linked to show the difference in the detection rate.}\label{fig:detect-compare}
-\end{figure}
-
-Table. \ref{tab:desc-stats} shows the means and standard deviations of
+
+\centering{
+
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-detect-compare-1.pdf}
+
+}
+
+\caption{\label{fig-detect-compare}The detection rates achieved by
+participants are contrasted when viewing the four replicates of the
+three trend models. Each point shows the probability of detection for
+the lineup display, the facets separate the trend models hidden in the
+lineup. The points for the same data set shown in a choroleth or hexagon
+tile map display are linked to show the difference in the detection
+rate.}
+
+\end{figure}%
+
+Table~\ref{tbl-desc-stats} shows the means and standard deviations of
 the detection rate for each type of plot and each trend model. This also
@@
 
-\caption{\label{tab:desc-stats}The mean and standard deviation of the rate of detection for each trend model, calculated for the choropleth and hexagon tile map displays.}
+\caption{\label{tbl-desc-stats}}
+
+\centering{
+
+\caption{\label{tab:tbl-desc-stats}The mean and standard deviation of the rate of detection for each trend model, calculated for the choropleth and hexagon tile map displays.}
 \centering
@@
 \end{tabular}
-\end{table}
-
-Table. \ref{tab:detect-glmer1} presents a summary of the generalised
-linear mixed effects model, testing the effect of plot type and trend
-model on the detection rate. The results support the summary from Fig.
-\ref{fig:detect-compare} and all parameters are statistically
-significant despite the large standard deviations observed in Table.
-\ref{tab:desc-stats}. Overall, the hexagon tile map performs marginally
-better than the choropleth for all trend models, which is a pleasant
-surprise. Allowing for the interaction effect, the difference in
-detection rate decreases for population related displays for a
+
+}
+
+\end{table}%
+
+Table~\ref{tbl-detect-glmer1} presents a summary of the generalised
+linear mixed effects model, testing the effect of map type and trend
+model on the detection rate. The results support the summary from
+Figure~\ref{fig-detect-compare} and all parameters are statistically
+significant despite the large standard deviations observed in
+Table~\ref{tbl-desc-stats}. Overall, the hexagon tile map performs
+marginally better than the choropleth for all trend models, which is a
+pleasant surprise. Allowing for the interaction effect, the difference
+in detection rate decreases for population related displays for a
 choropleth map lineup, but increases for a hexagon tile map display. The
-log odds of detection show in Table. \ref{tab:detect-glmer1} can be back
+log odds of detection show in Table~\ref{tbl-detect-glmer1} can be back
 transformed after taking the sum of all terms for the trend and type of
@@
 
-\caption{\label{tab:detect-glmer1}The model output for the generalised linear mixed effect model for detection rate.
+\caption{\label{tbl-detect-glmer1}}
+
+\centering{
+
+\caption{\label{tab:tbl-detect-glmer1}The model output for the generalised linear mixed effect model for detection rate.
 This model considers the type of display, the trend model hidden in the data plot, and accounts for contributor performance.}
@@
 \end{tabular}
-\end{table}
+
+}
+
+\end{table}%
 
@@
 
-Fig. \ref{fig:beeswarm} shows horizontally jittered dot plots to
+Figure~\ref{fig-beeswarm} shows horizontally jittered dot plots to
 contrast the time taken by participants to evaluate each lineup when
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/beeswarm-1} \caption{The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots.
-The colored point indicates average time taken for each plot type.
-Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between plot types.}\label{fig:beeswarm}
-\end{figure}
+
+\centering{
+
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-beeswarm-1.pdf}
+
+}
+
+\caption{\label{fig-beeswarm}The distribution of the time taken
+(seconds) to submit a response for each combination of trend, whether
+the data plot was detected, and type of display, shown using
+horizontally jittered dotplots. The colored point indicates average time
+taken for each map type. Although some participants take just a few
+seconds per evaluation, and some take as much as mcuh as 60 seconds, but
+there is very little difference in time taken between map types.}
+
+\end{figure}%
 
@@
 subjective assessment by the participant prompted by the question: `How
-certain are you about your choice?'. Fig. \ref{fig:certainty} shows the
-amount of times participants provided each level of certainty. This was
-separated for each combination of trend models and display type, and
+certain are you about your choice?'. Figure~\ref{fig-certainty} shows
+the amount of times participants provided each level of certainty. This
+was separated for each combination of trend models and display type, and
 colored depending on whether a participant correctly detected the data
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figure-latex/certainty-1} \caption{The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
-Participants were more likely to choose a high certainty when considering a Choropleth map.
-The mid value of 3 was the default certainty, it was chosen most for the Hexagon tile map displays.}\label{fig:certainty}
-\end{figure}
+
+\centering{
+
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-certainty-1.pdf}
+
+}
+
+\caption{\label{fig-certainty}The amount of times each level of
+certainty was chosen by participants when viewing hexagon tile map or
+choropleth displays. Participants were more likely to choose a high
+certainty when considering a Choropleth map. The mid value of 3 was the
+default certainty, it was chosen most for the Hexagon tile map
+displays.}
+
+\end{figure}%
 
@@
 able to select from a set of suggested reasons. ``Color trend across the
-areas'' was the most common selection for NW-SE trend displays.
+areas'' was the most common selection for NW-SE trend displays
+(Table~\ref{tbl-reason}).
 
@@
 
-\caption{\label{tab:reason}The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
+\caption{\label{tbl-reason}}
+
+\centering{
+
+\caption{\label{tab:tbl-reason}The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
 The facets show whether or not the choice was correct.}
@@
 
-The differences seen in the \ref{fig:detect-compare} plot and Table.
-\ref{tab:desc-stats} are reflected in the model results. Surprisingly
-the difference for the geographic distribution was significant at the
-0.05 level. It also showed that the hexagon tile map display performs
-marginally better than the choropleth for all trend models. Unexpectedly
-the detection rate suffers when using a choropleth map to display
-population related distributions.
+The differences seen in the Figure~\ref{fig-detect-compare} plot and
+Table~\ref{tbl-desc-stats} are reflected in the model results.
+Surprisingly the difference for the geographic distribution was
+significant at the 0.05 level. It also showed that the hexagon tile map
+display performs marginally better than the choropleth for all trend
+models. Unexpectedly the detection rate suffers when using a choropleth
+map to display population related distributions.
 
@@
 consider the hexagon tile map distribution but would be able to detect
-the data plot in the lineup. The bimodal distributions seen in Fig.
-\ref{fig:beeswarm} showed very little difference in the mean evaluation
-times. As the maximum time of all of the distributions approached 60
-seconds it cannot be said that the participants' took longer to evaluate
-the hexagon tile map displays.
+the data plot in the lineup. The bimodal distributions seen in
+Figure~\ref{fig-beeswarm} showed very little difference in the mean
+evaluation times. As the maximum time of all of the distributions
+approached 60 seconds it cannot be said that the participants' took
+longer to evaluate the hexagon tile map displays.
 
 The responses to the questions asked of participants included the reason
-for their choice and the certainty around their choice. Fig.
-\ref{tab:reason} shows high levels of certainty of 4 and 5 were chosen
-by participants when looking at the population distributions in a
+for their choice and the certainty around their choice.
+Table~\ref{tbl-reason} shows high levels of certainty of 4 and 5 were
+chosen by participants when looking at the population distributions in a
 choropleth map display show that they were over confident when
@@
 
-\section{Acknowledgment}\label{acknowledgment}
+\section*{Acknowledgments}\label{acknowledgments}
+\addcontentsline{toc}{section}{Acknowledgments}
 
@@
 suggestions and comments. Mitchell O'Hara-Wild was a co-developer of the
-taipan {[}\citeproc{ref-taipan}{20}{]} R package for image tagging, used
-as the base for the web app constructed to collect participant
-evaluations of lineups. We are thankful for the NUMBATs (Non-Uniform
-Monash Business Analytics Team) for participating in the pilot study
-that helped to assess the experimental design and determine an
-appropriate sample size for the study.
+taipan \citep{taipan} R package for image tagging, used as the base for
+the web app constructed to collect participant evaluations of lineups.
+We are thankful for the NUMBATs (Non-Uniform Monash Business Analytics
+Team) for participating in the pilot study that helped to assess the
+experimental design and determine an appropriate sample size for the
+study.
 
@@
 
-The analysis of the work was completed in R
-{[}\citeproc{ref-RCore}{18}{]} with the use of the following packages:
+The analysis of the work was completed in R \citep{RCore} with the use
+of the following packages:
 
@@
 \item
-  For document creation: rmarkdown {[}\citeproc{ref-rmarkdown}{23}{]},
-  rticles {[}\citeproc{ref-rticles}{24}{]}, knitr
-  {[}\citeproc{ref-knitr}{25}{]}.
-\item
-  For lineup creation and data analysis: tidyverse
-  {[}\citeproc{ref-tidyverse}{26}{]}, nullabor
-  {[}\citeproc{ref-nullabor}{27}{]}, ggthemes
-  {[}\citeproc{ref-ggthemes}{28}{]}, RColorBrewer
-  {[}\citeproc{ref-RColorBrewer}{29}{]}.
-\item
-  For image displays: cowplot {[}\citeproc{ref-cowplot}{30}{]}, png
-  {[}\citeproc{ref-png}{31}{]}, grid {[}\citeproc{ref-grid}{32}{]}.
-\item
-  For modelling and presentation of models: gstat
-  {[}\citeproc{ref-gstat}{17}{]}, lme4 {[}\citeproc{ref-lme4}{19}{]},
-  kableExtra {[}\citeproc{ref-kableExtra}{33}{]}.
+  Document creation: quarto \citep{Allaire_Quarto_2025}, anzjs template
+  \citep{quarto-anzjs}, knitr \citep{knitr}.
+\item
+  Lineup creation: nullabor \citep{nullabor}, gstat \citep{gstat}.
+\item
+  Data analysis: tidyverse \citep{tidyverse}, ggthemes \citep{ggthemes},
+  RColorBrewer \citep{RColorBrewer}.
+\item
+  Plots: ggplot2 \citep{ggplot2}, cowplot \citep{cowplot}, png
+  \citep{png}, grid \citep{grid}.
+\item
+  Modelling and summary presentation: lme4 \citep{lme4}, kableExtra
+  \citep{kableExtra}.
 \end{itemize}
@@
 
-\section*{References}\label{references}
-\addcontentsline{toc}{section}{References}
-
-\phantomsection\label{refs}
-\begin{CSLReferences}{0}{1}
-\bibitem[\citeproctext]{ref-sugarbag}
-\CSLLeftMargin{1. }%
-\CSLRightInline{Kobakian S, Cook D, Duncan E (2023)
-\href{https://doi.org/10.32614/RJ-2023-021}{A hexagon tile map algorithm
-for displaying spatial data}. The R Journal 15:6--16}
-
-\bibitem[\citeproctext]{ref-atlas}
-\CSLLeftMargin{2. }%
-\CSLRightInline{Cancer Council Queensland (2018) {Australian Cancer
-Atlas}, publisher = {Queensland University of Technology, Cooperative
-Research Centre for Spatial Information}, issue = {Version 09},
-url={https://atlas.cancer.org.au}, accessed = {Jan 12 2020}. }
-
-\bibitem[\citeproctext]{ref-GIIV}
-\CSLLeftMargin{3. }%
-\CSLRightInline{Wickham H, Cook D, Hofmann H, Buja A (2010) Graphical
-inference for infovis. IEEE Transactions on Visualization and Computer
-Graphics (Proc InfoVis '10) 16:973--979}
-
-\bibitem[\citeproctext]{ref-EI}
-\CSLLeftMargin{4. }%
-\CSLRightInline{Tufte ER (1990) {Envisioning Information}. Graphics
-Press}
-
-\bibitem[\citeproctext]{ref-BCM}
-\CSLLeftMargin{5. }%
-\CSLRightInline{Skowronnek A (2016)
-\href{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}{{Beyond
-Choropleth Maps -- A Review of Techniques to Visualize Quantitative
-Areal Geodata}}. {Infovis Reading Group WS 2015/16} }
-
-\bibitem[\citeproctext]{ref-CBATCC}
-\CSLLeftMargin{6. }%
-\CSLRightInline{Kocmoud C, House D (1998) {A Constraint-based Approach
-to Constructing Continuous Cartograms}. In: Proc. Symp. Spatial data
-handling. pp 236--246}
-
-\bibitem[\citeproctext]{ref-ACTUC}
-\CSLLeftMargin{7. }%
-\CSLRightInline{Dorling D (2011)
-\href{https://doi.org/10.1002/9780470979587.ch33}{{Area Cartograms:
-Their Use and Creation}}. In: The map reader. John Wiley \& Sons, Ltd,
-pp 252--260}
-
-\bibitem[\citeproctext]{ref-NAC}
-\CSLLeftMargin{8. }%
-\CSLRightInline{Olson JM (1976)
-\href{https://doi.org/10.1111/j.0033-0124.1976.00371.x}{{Noncontiguous
-Area Cartograms}}. The Professional Geographer 28:371--380}
-
-\bibitem[\citeproctext]{ref-RSCW}
-\CSLLeftMargin{9. }%
-\CSLRightInline{Raisz E (1963)
-\href{https://doi.org/10.1080/00221343608987880}{{Rectangular
-Statistical Cartograms of the World}}. Journal of Geography 35:8--10}
-
-\bibitem[\citeproctext]{ref-CDWCS}
-\CSLLeftMargin{10. }%
-\CSLRightInline{Monmonier M (2005)
-\href{https://doi.org/10.1191/0309132505ph540pr}{{Cartography:
-Distortions, World-views and Creative Solutions}}. Progress in Human
-Geography 29:217--224}
-
-\bibitem[\citeproctext]{ref-review}
-\CSLLeftMargin{11. }%
-\CSLRightInline{Kobakian S, Cook D, Roberts J (2020)
-\href{https://ace.amegroups.com/article/view/6040}{Mapping cancer: The
-potential of cartograms and alternative map displays}. Annals of Cancer
-Epidemiology 4:}
-
-\bibitem[\citeproctext]{ref-BCHLLSW09}
-\CSLLeftMargin{12. }%
-\CSLRightInline{Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne
-DF, Wickham H (2009)
-\href{https://doi.org/10.1098/rsta.2009.0120}{Statistical inference for
-exploratory data analysis and model diagnostics}. Philosophical
-Transactions of the Royal Society, A (Invited) 367:4361--4383}
-
-\bibitem[\citeproctext]{ref-GTPCCD}
-\CSLLeftMargin{13. }%
-\CSLRightInline{Hofmann H, Follett L, Majumder M, Cook D (2012)
-Graphical tests for power comparison of competing designs. IEEE
-Transactions on Visualization and Computer Graphics 18:2441--2448}
-
-\bibitem[\citeproctext]{ref-ggplot2}
-\CSLLeftMargin{14. }%
-\CSLRightInline{Wickham H (2009)
-\href{http://had.co.nz/ggplot2/book}{ggplot2: Elegant graphics for data
-analysis}. Springer New York}
-
-\bibitem[\citeproctext]{ref-abs2016}
-\CSLLeftMargin{15. }%
-\CSLRightInline{Australian Bureau of Statistics (2018)
-\href{https://www.abs.gov.au/statistics/statistical-geography/australian-statistical-geography-standard-asgs}{{Australian
-Statistical Geography Standard (ASGS)}}. }
-
-\bibitem[\citeproctext]{ref-POG}
-\CSLLeftMargin{16. }%
-\CSLRightInline{Matheron G (1963)
-\href{http://dx.doi.org/10.2113/gsecongeo.58.8.1246}{Principles of
-geostatistics}. Economic Geology 58:1246--1266}
-
-\bibitem[\citeproctext]{ref-gstat}
-\CSLLeftMargin{17. }%
-\CSLRightInline{Gräler B, Pebesma E, Heuvelink G (2016)
-\href{https://journal.r-project.org/archive/2016/RJ-2016-014/index.html}{Spatio-temporal
-interpolation using gstat}. The R Journal 8:204--218}
-
-\bibitem[\citeproctext]{ref-RCore}
-\CSLLeftMargin{18. }%
-\CSLRightInline{R Core Team (2019) \href{https://www.R-project.org/}{R:
-A language and environment for statistical computing}. R Foundation for
-Statistical Computing, Vienna, Austria}
-
-\bibitem[\citeproctext]{ref-lme4}
-\CSLLeftMargin{19. }%
-\CSLRightInline{Bates D, Mächler M, Bolker B, Walker S (2015)
-\href{https://doi.org/10.18637/jss.v067.i01}{Fitting linear
-mixed-effects models using {lme4}}. Journal of Statistical Software
-67:1--48}
-
-\bibitem[\citeproctext]{ref-taipan}
-\CSLLeftMargin{20. }%
-\CSLRightInline{Kobakian S, O'Hara-Wild M (2018)
-\href{https://CRAN.R-project.org/package=taipan}{Taipan: Tool for
-annotating images in preparation for analysis}. }
-
-\bibitem[\citeproctext]{ref-sheets}
-\CSLLeftMargin{21. }%
-\CSLRightInline{Bryan J, Zhao J (2018)
-\href{https://CRAN.R-project.org/package=googlesheets}{Googlesheets:
-Manage google spreadsheets from r}. }
-
-\bibitem[\citeproctext]{ref-figeight}
-\CSLLeftMargin{22. }%
-\CSLRightInline{Figure Eight Inc (2019)
-\href{https://www.figure-eight.com/}{The essential high-quality data
-annotation platform}. }
-
-\bibitem[\citeproctext]{ref-rmarkdown}
-\CSLLeftMargin{23. }%
-\CSLRightInline{Xie Y, Allaire JJ, Grolemund G (2018)
-\href{https://bookdown.org/yihui/rmarkdown}{R markdown: The definitive
-guide}. Chapman; Hall/CRC, Boca Raton, Florida}
-
-\bibitem[\citeproctext]{ref-rticles}
-\CSLLeftMargin{24. }%
-\CSLRightInline{Allaire J, Xie Y, R Foundation, et al (2019)
-\href{https://CRAN.R-project.org/package=rticles}{Rticles: Article
-formats for r markdown}. }
-
-\bibitem[\citeproctext]{ref-knitr}
-\CSLLeftMargin{25. }%
-\CSLRightInline{Xie Y (2015) \href{https://yihui.org/knitr/}{Dynamic
-documents with {R} and knitr}, 2nd ed. Chapman; Hall/CRC, Boca Raton,
-Florida}
-
-\bibitem[\citeproctext]{ref-tidyverse}
-\CSLLeftMargin{26. }%
-\CSLRightInline{Wickham H, Averick M, Bryan J, et al (2019)
-\href{https://doi.org/10.21105/joss.01686}{Welcome to the {tidyverse}}.
-Journal of Open Source Software 4:1686}
-
-\bibitem[\citeproctext]{ref-nullabor}
-\CSLLeftMargin{27. }%
-\CSLRightInline{Wickham H, Chowdhury NR, Cook D, Hofmann H (2018)
-\href{https://CRAN.R-project.org/package=nullabor}{Nullabor: Tools for
-graphical inference}. }
-
-\bibitem[\citeproctext]{ref-ggthemes}
-\CSLLeftMargin{28. }%
-\CSLRightInline{Arnold JB (2019)
-\href{https://CRAN.R-project.org/package=ggthemes}{Ggthemes: Extra
-themes, scales and geoms for 'ggplot2'}. }
-
-\bibitem[\citeproctext]{ref-RColorBrewer}
-\CSLLeftMargin{29. }%
-\CSLRightInline{Neuwirth E (2014)
-\href{https://CRAN.R-project.org/package=RColorBrewer}{RColorBrewer:
-ColorBrewer palettes}. }
-
-\bibitem[\citeproctext]{ref-cowplot}
-\CSLLeftMargin{30. }%
-\CSLRightInline{Wilke CO (2019)
-\href{https://CRAN.R-project.org/package=cowplot}{Cowplot: Streamlined
-plot theme and plot annotations for 'ggplot2'}. }
-
-\bibitem[\citeproctext]{ref-png}
-\CSLLeftMargin{31. }%
-\CSLRightInline{Urbanek S (2013)
-\href{https://CRAN.R-project.org/package=png}{Png: Read and write PNG
-images}. }
-
-\bibitem[\citeproctext]{ref-grid}
-\CSLLeftMargin{32. }%
-\CSLRightInline{Murrell P (2002) The grid graphics package. R News
-2:14--19}
-
-\bibitem[\citeproctext]{ref-kableExtra}
-\CSLLeftMargin{33. }%
-\CSLRightInline{Zhu H (2019)
-\href{https://CRAN.R-project.org/package=kableExtra}{kableExtra:
-Construct complex table with 'kable' and pipe syntax}. }
-
-\end{CSLReferences}
+\bibliography{paper.bib}
 

### 2025-07-07 paper/review1/ReponseToReviewers2025.qmd
part way through revising paper

@@
 
-Add letter format
-
-Add introductory thank you to reviewers for their work, and the editor for their consideration.
-
-## To Do
-
-Make a release version on github of current copy before changes
-
-all points made be reviewers, must be addressed with a response using different font types for review comment v our response
-
-In our Rmd file use XXX for difficult change to make - allocated to Di or Steph
-
-# Review of “Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map  for Communicating Cancer Statistics”
-
-Associate Editor
-
-Dear associate editor XXX,
-
-Thank you for the opportunity to improve this paper with the suggestions made in the comments provided. Please find our responses to the comments provided in *italics* below each paragraph or comment.
+Thank you for the careful reviews of our paper. Please find *our responses to provided in italics* point-by-point with the comments.
 
@@
 
-Comments to the Author
+Overall Comments:
 
-Please see attached review.
+This paper performs a user study to compare and contrast the ability of two visual displays, a choropleth map and a hexagon tile map.
+It uses a line up protocol to test the effectiveness of the two displays.
+The study showed that the hexagon tile map was significantly more effective than the choropleth map with the authors advocating for its use in the cancer atlas.
+
+The authors do a nice job introducing each map, the benefits of both and outlined how each would be applied to communicate cancer statistics as part of the Cancer Atlas.
+I think that Section 3 could be tightened up in places, especially with regards to generating the lineups and the section that outlines the analysis (see below for specifics).
+
+Overall, I see this as an important contribution not only to the visualisation community but also to the statistics community who often leave the communication of statistics and modelled outputs as an afterthought.
+I therefore recommend this paper be published after the authors consider my comments and revisions below, largely relating tao Section 3.
+I also believe the Cancer Atlas could benefit from such a visualisation and  would encourage the authors to work with the authors of the Atlas to have this considered.
+As the acknowledgements suggest the Cancer Atlas team were involved in discussions, I suspect this would be an easy ask.
+
+Specific Comments:
+
+P7,L7 While the introduction focuses specifically on the maps communicating disease statistics, it would be good in the conclusion to extrapolate beyond that to gain a broader interest.
+
+XXX
+
+P8, L31-32.
+I would consider adding to the last sentence to write the following: "The results are summarized in Section 4, followed by a discussion about the broader implications for the use of this map style."
+
+*Done*
+
+P9, L52.
+I'm on sure if the text in italics appears in the literature or if this is the author's view.
+If the author's view then I would replace "doesn't" with "does not".
+If it appears in the literature, please reference.
+
+*Attributed to sentiment suggested by Monmonier (2018) How to Lie with Maps*
+
+P9, L55. I would suggest replacing "better" with "adequately".
+
+*Done*
+
+P9, L77-78. Consider the following: "Figure 1 shows the hexagon tile map, where the map is coloured from …"
+
+*Done*
+
+P10, L97. Omit the words "To do".
+
+*Done*
+
+P13, L167-170. Are you able to outline the smoothing procedure. This seems a little vague.
+
+*We've reduced this part to a single sentence.
+The exact smoothing procedures for processing the null data sets can be found in the code on the GitHub repo.
+It is not important enough to report in detail.
+The `gstat` function produced null sets with insufficient spatial dependence, despite substantial adjusting parameters,  and so further simple smoothing was done.
+These were compared with the Atlas plots, which had very complicated procedures to produce the cancer maps, that also ensured privacy of information.*
+
+P14, L178-183. The process here seems a little subjective. Can you provide some reasoning as to why these decisions were made?
+
+*Several sentences have been added explaining why these three trend models was used.*
+
+P14, L191-192. Why were the locations 1, 7, 10 and 11 not used?
+
+*Explained. It is because locations were randomly sampled.*
+
+P14, L193-195. This sentence does not make sense. Please revise.
+
+*Paragraph revised*
+
+P15, L226. Replace "will be" with "were".
+
+*Sentence removed because software is cited in the Acknowledgements.*
+
+P15, L234. y_ij = 0,1 represents whether the subject detected the data plot (1) or did not (0). Please fix.
+
+*Done*
+
+P15, L239-240. This could be written better. Should read a "logit" link. I would consider writing the model as follows:
+
+y_ij \~ Bernoulli(p_ij), where
+
+logit(p_ij) = mu + tau_i + delta_j + (tau delta)\_ij i=1,2. J=1,2,3.
+
+Then discuss the random effects.
+
+*Done*
+
+P16, L247. What is a "Figure Eight contributor ID"?:
+
+*This was used by the respondent to uniquely identify themselves and allow us to link them to the paid account we used for recruitment and payment.
+This reference has been replaced with a unique identifier created for each participant.*
+
+P11, Section 3.7.
+Could this information be captured more succinctly in a table perhaps?
+Line 290-293 just lists words.
+There are no questions relating to these 3 dotpoints.
+I'm also wondering why participants do not submit their responses as they go?
+Do they also have a chance to go back and change a response?
+It is difficult to determine what this process is.
+
+*Re-written. Responses were recorded on each lineup evaluation, but not saved in the Google sheet until the participant clicked Submit.*
+
+P18, L297-301.
+The math does not seem to work unless I’m missing something.  Responses were collected from 92 participants.
+Five were removed which leaves 87 for  evaluation.
+However you go on to say that Set A were evaluated by 42 participants and  set B, 53 which adds up to 95 participants.
+Then you go on to say this resulted in 1104  evaluations.
+Could you please revise and provide a more detailed outline of the  evaluations you performed?
+
+P22 Discussion through to Conclusions.
+As highlighted earlier, it would be good to  extrapolate the results to other modelled outputs beyond cancer statistics to obtain  broader coverage.
+There is considerable value in using a hexagon tile map for showing  statistics and modelled output in statistical area levels across Australia or similar.
 
@@
 https://doi.org/10.1109/TVCG.2015.2469125
-
-Overall Comments:
-
-This paper performs a user study to compare and contrast the ability of two visual  displays, a choropleth map and a hexagon tile map.
-It uses a line up protocol to test the  effectiveness of the two displays.
-The study showed that the hexagon tile map was  significantly more effective than the choropleth map with the authors advocating for its  use in the cancer atlas.
-
-The authors do a nice job introducing each map, the benefits of both and outlined how  each would be applied to communicate cancer statistics as part of the Cancer Atlas.
-I  think that Section 3 could be tightened up in places, especially with regards to  generating the lineups and the section that outlines the analysis (see below for  specifics).
-
-Overall, I see this as an important contribution not only to the visualisation community  but also to the statistics community who often leave the communication of statistics  and modelled outputs as an afterthought.
-I therefore recommend this paper be  published after the authors consider my comments and revisions below, largely relating  tao Section 3.
-I also believe the Cancer Atlas could benefit from such a visualisation and  would encourage the authors to work with the authors of the Atlas to have this  considered.
-As the acknowledgements suggest the Cancer Atlas team were involved in  discussions, I suspect this would be an easy ask.
-
-Specific Comments:
-
-P7,L7 While the introduction focuses specifically on the maps communicating disease  statistics, it would be good in the conclusion to extrapolate beyond that to gain a  broader interest.
-
-P8, L31-32.
-I would consider adding to the last sentence to write the following: “The  results are summarized in Section 4, followed by a discussion about the broader  implications for the use of this map style.
-
-P9, L52.
-I’m on sure if the text in italics appears in the literature or if this is the author’s  view.
-If the author’s view then I would replace “doesn’t” with “does not”.
-If it appears in  the literature, please reference.
-
-P9, L55. I would suggest replacing “better” with “adequately”.
-
-P9, L77-78. Consider the following: “Figure 1 shows the hexagon tile map, where the  map is coloured from …
-
-*Completed*
-
-P10, L97. Omit the words “To do”.
-
-*Completed*
-
-P13, L167-170. Are you able to outline the smoothing procedure. This seems a little  vague.
-
-P14, L178-183. The process here seems a little subjective. Can you provide some  reasoning as to why these decisions were made?
-
-P14, L191-192. Why were the locations 1, 7, 10 and 11 not used?
-
-*Completed*
-
-P14, L193-195. This sentence does not make sense. Please revise.
-
-P15, L226. Replace “will be” with “were”.
-
-*Completed*
-
-P15, L234. y_ij = 0,1 represents whether the subject detected the data plot (1) or did not  (0). Please fix.
-
-P15, L239-240. This could be written better. Should read a “logit” link. I would consider  writing the model as follows:
-
-y_ij \~ Bernoulli(p_ij), where
-
-logit(p_ij) = mu + tau_i + delta_j + (tau delta)\_ij i=1,2. J=1,2,3.
-
-Then discuss the random effects.
-
-P16, L247.
-What is a “Figure Eight contributor ID”? : *This was used by the respondent to uniquely identify themselves and allow us to link them to the paid account we used for recruitment and payment.
-This reference has been removed, and in other places has been replaced with a unique identifier created for each participant.*
-
-P11, Section 3.7.
-Could this information be captured more succinctly in a table  perhaps?
-Line 290-293 just lists words.
-There are no questions relating to these 3  dotpoints.
-I’m also wondering why participants do not submit their responses as they  go?
-Do they also have a chance to go back and change a response?
-It is difficult to  determine what this process is.
-
-P18, L297-301.
-The math does not seem to work unless I’m missing something.  Responses were collected from 92 participants.
-Five were removed which leaves 87 for  evaluation.
-However you go on to say that Set A were evaluated by 42 participants and  set B, 53 which adds up to 95 participants.
-Then you go on to say this resulted in 1104  evaluations.
-Could you please revise and provide a more detailed outline of the  evaluations you performed?
-
-P22 Discussion through to Conclusions.
-As highlighted earlier, it would be good to  extrapolate the results to other modelled outputs beyond cancer statistics to obtain  broader coverage.
-There is considerable value in using a hexagon tile map for showing  statistics and modelled output in statistical area levels across Australia or similar.

### 2025-07-07 paper/paper.R

@@ -1,397 +1,0 @@
-## ----setup, include=FALSE-----------------------------------
-knitr::opts_chunk$set(
-  echo = FALSE,
-  warning = FALSE,
-  error = FALSE, 
-  message = FALSE,
-  cache = FALSE,
-  dpi = 300,
-  out.width = "100%")
-
-
-## ----libraries----------------------------------------------
-# Load Libraries
-library(tidyverse)
-library(readxl)
-library(broom)
-library(broom.mixed)
-library(cowplot)
-library(png)
-library(grid)
-library(lme4)
-library(ggthemes)
-library(RColorBrewer)
-library(knitr)
-library(kableExtra)
-
-options(knitr.kable.digits = "2")
-
-
-## ----data---------------------------------------------------
-trend_colors <- c(
-  "NW-SE" = "#B2DF8A",
-  "Three Cities" = "#A6CEE3",
-  "All Cities" = "#1F78B4")
-  
-type_colors <- c(
-  "Choro." = "#fcae91",
-  "Hex." = "#a50f15")
-
-detect_f_colors <- c(
-  "No" = "#66C2A5",
-  "Yes" = "#FC8D62")
-
-detect_colors <- c(
-  "Detected? No" = "#66C2A5",
-  "Detected? Yes" = "#FC8D62")
-
-  # Downloaded data
-d <- read_xlsx("data/experiment-export.xlsx", sheet=2) %>%
-  filter(!is.na(contributor)) %>%
-  mutate(contributor = factor(contributor))
-
-# Check data set 
-# Need to clean multiple entries, 48, 24
-# remove duplicated entries due to submit button
-d <- d %>% group_by(group, contributor, image_name) %>%
-  slice(1) %>% ungroup() %>% 
-  arrange(group, contributor, plot_order)
-
-# Remove contributors who did not provide answers to most questions
-keep <- d %>% count(contributor, sort = TRUE) %>% filter(n > 10)
-d <- d %>% 
-  filter(contributor %in% keep$contributor) %>%
-  filter(contributor != "1234567890")
-
-# Remove contributors who did not provide any choices
-# Or an insufficient amount of responses
-bad_contribs <- d %>% group_by(contributor) %>% 
-  summarise(sum0 = sum(choice)) %>% 
-  filter(sum0 < 13) %>% 
-  pull(contributor)
-
-d <- d %>% 
-  filter(!(contributor %in% bad_contribs))
-
-
[…]

### 2025-07-08 paper/kobakian-cook-anzjs.qmd
done with reviewer 1 and most of reviewer 2 comments

@@
 
+type2_colors <- c(
+  "Choropleth" = "#fcae91",
+  "Hexagon tile" = "#a50f15")
+
 detect_f_colors <- c(
@@
   mutate(contributor = factor(contributor))
+
+n_all_contributors <- d %>% count(contributor, sort=TRUE) %>% 
+  summarise(n_contributors = length(contributor))
+
+n_all_evals <- nrow(d)
 
@@
   filter(contributor %in% keep$contributor) %>%
-  filter(contributor != "1234567890")
+  filter(contributor != "1234567890") # Testing id
 
@@
 bad_contribs <- d %>% group_by(contributor) %>% 
-  summarise(sum0 = sum(choice)) %>% 
-  filter(sum0 < 13) %>% 
+  #summarise(sum0 = sum(choice)) %>% 
+  summarise(n_zero = sum(if_else(choice == 0, 1, 0))) %>%
+  #filter(sum0 < 13) %>% 
+  filter(n_zero > 8) %>%
   pull(contributor)
+
+# Person is in list above
+same_answer <- d %>% group_by(contributor) %>% 
+  summarise(v = sd(choice))
+
+# check range of choices
+choice_range <- d |> group_by(contributor) |> summarise(m1 = min(choice), m2 = max(choice))
 
@@
   summarise(n_contributors = length(contributor))
+
+n_AB <- d |> count(contributor, group) |> count(group) 
+n_gender <- d |> count(contributor, gender) |> count(gender)
+n_educ <- d |> count(contributor, education) |> count(education)
+n_age <- d |> count(contributor, age) |> count(age)
+n_aus <- d |> count(contributor, australia) |> count(australia)
+
+n_evals <- nrow(d)
 
@@
 #| label: fig-thyroid
-#| fig-cap: "Thyroid incidence among females across the Statistical Areas of Australia at Level 2, displayed using a choropleth (a) and a hexagon tile map (b).
+#| fig-cap: "Thyroid cancer incidence among females across the Statistical Areas of Australia at Level 2, displayed using a choropleth (a) and a hexagon tile map (b).
 Blue indicates lower than average, and red indicates higher than average incidence.
@@
 Plot 3 is the data plot, and the remaining 11 are plots of null data.
+The supplementary materials contain all lineups used in the study, including the corresponding lineup to this one made using choropleth maps.
 
@@
 #| label: fig-lineup
-#| fig-cap: "This lineup of twelve hexagon tile map displays contains one map with a real population related structure. The rest are null plots that contain only spatial dependence."
+#| fig-cap: "This lineup of twelve hexagon tile map displays contains one map with a real population related structure (location 3). The rest are null plots that contain only spatial dependence."
 #| fig-height: 8
@@
 #| out-width: 80%
-#| fig-cap: "The experimental design used in the study. Participants are allocated to with group A or B, to evaluate either the choropleth or hexagon tile map lineup of each simulated data set."
+#| fig-cap: "The experimental design used in the study.
+Participants are allocated to with group A or B, to evaluate either the choropleth or hexagon tile map lineup of each simulated data set.
+Place in the lineup is recorded as 'Location'."
 ggdraw(xlim = c(0,1), ylim = c(0,1)) + draw_plot(rasterGrob(png::readPNG("figures/experiment_design.png")))
@@
 $$
-\hat{y}_{ij} \sim Bernoulli(p_ij)
+\hat{y}_{ijk} \sim Bernoulli(p_{ijk})
 $$
@@
 $$
-\text{logit}(p_{ij}) = \mu + \tau_i + \delta_j + (\tau \delta)_{ij} ~~~~ i=1,2; ~~ j=1,2,3
+\text{logit}(p_{ijk}) = \mu_i + \tau_j + \delta_k + (\tau \delta)_{jk} ~~~~ j=1,2; ~~ k=1,2,3
 $$
@@
 
-where $y_{ij} = 0, 1$ represents whether the subject detected the data plot (1) or did not (0), $\mu$ is the overall mean, $\tau_i, i=1,2$ is the map type effect, $\delta_j$ is the trend model effect.
-We are allowing for an interaction between map type and trend model as the response is binary, so a logistic model was used.
-As each participant provides results from 12 lineups, this model can account for each individual participants’ abilities as it includes a subject-specific random intercept.
-
+where $y_{ijk} = 0, 1$ represents whether subject $i$ detected the data plot (1) or did not (0), $\mu_$ is the subject-specific random intercept, $\tau_j$ is the map type effect, $\delta_k$ is the trend model effect.
+The interaction between map type and trend model allows for any map type effect to differ between trend models.
+As each participant provides results from 12 lineups, this model can account for each individual participants' abilities with the subject-specific random intercept.
+
+<!-- 
 The model specifies a logit link, this means the predicted values from the `glmer` model should be back-transformed to fit between 0 and 1.
@@
 $$\eta = f(\tau_i,\delta_j)$$
+-->
 
@@
 
-## Demographic data collection
+## Data collection
 
@@
 
-on each of lineup. These responses are saved after entering, but only recorded in the results sheet when the participants clicked the submit button on the final page.
+on each of lineup. These responses are saved after entering. Participants were expected to click the submit button on the final page.
 
@@
 
-Responses from 92 participants were collected.
-Five participants did not provide more than three unique choices for the twelve lineups, and their data was removed.
-Set A was evaluated by 42 participants, and 53 evaluated set B.
-This resulted in 1104 evaluations, corresponding to 92 subjects, each evaluating 12 lineups, that were analysed on accuracy and speed.
+A total of `r n_all_evals` responses were collected from `r n_all_contributors` participants.
+A small number of participants, `r n_all_contributors-n_contributors`,  were removed because they did not provide at least 11 responses, or left more than 3 at the default value of 0.
+These are participants that stopped early or clicked through without doing the evaluation.
+Set A was evaluated by `r n_AB$n[1]` participants, and `r n_AB$n[2]` evaluated set B.
+This resulted in `r n_evals` evaluations, corresponding to `r n_contributors` subjects, each evaluating 12 lineups, that were analysed on accuracy and speed.
 The certainty and reasons of subjects in their answers is also examined.
@@
 
-Of the 92 participants, 67 were male, and 25 female. Most participants (56) had a Bachelors degree, 13 had a Masters degree, and the remaining 23 had high school diplomas.
+Of the `r n_contributors` participants, `r n_gender$n[1]` were male, and `r n_gender$n[2]` female.
+Most participants (`r n_educ$n[1]`) had a Bachelors degree, `r n_educ$n[3]` had a Masters degree, and the remaining `r n_educ$n[2]` had high school diplomas.
+The age distribution was `r paste(n_age$n[1:5], collapse=", ")` for age groups 18-24, 25-34, 35-44, 45-54, 55+, with `r n_age$n[6]` preferring not to answer.
+Only `r n_aus$n[2]` reported having lived in Australia.
 
@@
 The points for the same data set shown in a choroleth or hexagon tile map display are linked to show the difference in the detection rate."
-#| fig-height: 5
+#| fig-height: 4
+#| fig-width: 6
+#| out-width: 100%
 # Detectability rate for each lineup (image)
@@
   scale_color_manual(values = trend_colors) +
-  xlab("Type of areas visualized") +
+  xlab("") +
   ylab("Detection rate") + 
   ylim(0,1) +
-  guides(scale = "none")
+  guides(scale = "none") +
+  theme(legend.position = "none")
+```
+
+```{r}
+#| eval: false
+# Check detection rate across groups
+d %>% group_by(group) %>%
+    # pdetect measures the aggregated accuracy of the choices
+    summarise(pdetect = length(detect[detect == 1])/length(detect)) %>%
+    ungroup()
 ```
@@
 Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between map types."
-#| fig-height: 8
+#| fig-height: 6
+#| fig-width: 5
+#| out-width: 80%
 s <- d %>% group_by(type, trend, detect_f) %>%
@@
   #geom_errorbar(data=s, aes(x=type, ymin=q1, ymax=q3, color=type), width=0.3, size=2) +
-  scale_color_brewer("", palette = "Dark2") +
+  scale_color_manual("", values = type_colors) +
   facet_grid(trend~detect_f) + 
   ylab("Time taken (seconds)") + xlab("") +
-  theme(legend.position="bottom")
+  theme(legend.position="none")
 ```
@@
 #| label: fig-certainty 
-#| fig-cap: "The amount of times each level of certainty was chosen by participants when viewing hexagon tile map or choropleth displays.
-Participants were more likely to choose a high certainty when considering a Choropleth map.
-The mid value of 3 was the default certainty, it was chosen most for the Hexagon tile map displays."
+#| fig-cap: "The distribution of certainty chosen by participants when viewing hexagon tile map or choropleth displays, shown as a mosaic plot, faceted by the trend model and whether the plot was detected or not.
+At most trend models and whether the plot was detected or not, participants were more likely to choose a high certainty when evaluating a choropleth map."
 #| fig-height: 5
+#| fig-width: 10
+#| out-width: 100%
 d <- d %>% 
@@
 
-d %>% 
+#d %>% 
+#  mutate(Detected = factor(detect_f, 
+#    levels = c("Detected? Yes", "Detected? No"), 
+#    labels = c("Yes", "No"))) %>% 
+#ggplot(aes(x = certainty, fill = Detected)) +  
+#  scale_fill_manual(values = detect_f_colors) +
+#  geom_bar(position="dodge") + 
+#  facet_grid(type ~ trend) +
+#  theme(legend.position = "bottom") + xlab("Level of certainty")
+
+# devtools::install_github("haleyjeppson/ggmosaic")
+library(ggmosaic)
+d |> 
   mutate(Detected = factor(detect_f, 
     levels = c("Detected? Yes", "Detected? No"), 
-    labels = c("Yes", "No"))) %>% 
-ggplot(aes(x = certainty, fill = Detected)) +  
-  scale_fill_manual(values = detect_f_colors) +
-  geom_bar() + facet_grid(type ~ trend) +
-  theme(legend.position = "bottom") + xlab("Level of certainty")
+    labels = c("Detected? Yes", "Detected? No"))) |>
+  mutate(type = fct_recode(type, "Choropleth" = "Choro.", "Hexagon tile" = "Hex.")) |>
+  ggplot() +
+    geom_mosaic(aes(x = certainty, fill = type)) +  
+    scale_fill_manual("", values = type2_colors) +
+    scale_y_continuous("proportion", breaks=seq(0,1,0.25)) +
+    facet_grid(Detected ~ trend) +
+    theme(aspect.ratio = 0.8, 
+      axis.text = element_text(size="10"),
+      legend.position = "bottom")
 ```
@@
 
-The hexagon tile map display should be considered as an alternative visualization method when communicating distributions that relate to the population across a set of geographic units.
+The hexagon tile map display should be considered as an alternative visualisation method when communicating distributions that relate to the population across a set of geographic units.
 As an additional display to the familiar choropleth map, cancer atlas products may benefit from the opportunity to allow exploration via an alternative display.
@@
 
+Add Election results data + plus other statistics, other hexagon layout software
+
 # Acknowledgments {-}
 
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments.
+The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualisations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments.
 Mitchell O'Hara-Wild was a co-developer of the taipan [@taipan] R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups.

### 2025-07-08 paper/kobakian-cook-anzjs.tex
done with reviewer 1 and most of reviewer 2 comments

@@
 
-\caption{\label{fig-thyroid}Thyroid incidence among females across the
-Statistical Areas of Australia at Level 2, displayed using a choropleth
-(a) and a hexagon tile map (b). Blue indicates lower than average, and
-red indicates higher than average incidence. The choropleth suggests
-high incidence is clustered on the east coast but misses the high
-incidence in Perth and a few locations in inner Melbourne visible in the
-hexagon tile map.}
+\caption{\label{fig-thyroid}Thyroid cancer incidence among females
+across the Statistical Areas of Australia at Level 2, displayed using a
+choropleth (a) and a hexagon tile map (b). Blue indicates lower than
+average, and red indicates higher than average incidence. The choropleth
+suggests high incidence is clustered on the east coast but misses the
+high incidence in Perth and a few locations in inner Melbourne visible
+in the hexagon tile map.}
 
@@
 \(m=12\). Plot 3 is the data plot, and the remaining 11 are plots of
-null data.
+null data. The supplementary materials contain all lineups used in the
+study, including the corresponding lineup to this one made using
+choropleth maps.
 
@@
 \caption{\label{fig-lineup}This lineup of twelve hexagon tile map
-displays contains one map with a real population related structure. The
-rest are null plots that contain only spatial dependence.}
+displays contains one map with a real population related structure
+(location 3). The rest are null plots that contain only spatial
+dependence.}
 
@@
 either the choropleth or hexagon tile map lineup of each simulated data
-set.}
+set. Place in the lineup is recorded as `Location'.}
 
@@
 \[
-\hat{y}_{ij} \sim Bernoulli(p_ij)
+\hat{y}_{ijk} \sim Bernoulli(p_{ijk})
 \] with
@@
 \[
-\text{logit}(p_{ij}) = \mu + \tau_i + \delta_j + (\tau \delta)_{ij} ~~~~ i=1,2; ~~ j=1,2,3
+\text{logit}(p_{ijk}) = \mu_i + \tau_j + \delta_k + (\tau \delta)_{jk} ~~~~ j=1,2; ~~ k=1,2,3
 \]
 
-where \(y_{ij} = 0, 1\) represents whether the subject detected the data
-plot (1) or did not (0), \(\mu\) is the overall mean, \(\tau_i, i=1,2\)
-is the map type effect, \(\delta_j\) is the trend model effect. We are
-allowing for an interaction between map type and trend model as the
-response is binary, so a logistic model was used. As each participant
-provides results from 12 lineups, this model can account for each
-individual participants' abilities as it includes a subject-specific
-random intercept.
-
-The model specifies a logit link, this means the predicted values from
-the \texttt{glmer} model should be back-transformed to fit between 0 and
-1. The predictions \(\widehat{p}(\eta)\) are transformed to be
-probabilities between 0 and 1 with the link specified below:
-
-\[\widehat{p}(\eta) = \frac{e^{\eta}}{1 + e^{\eta}}\]
-\label{eq:transform} \[\eta = f(\tau_i,\delta_j)\]
+where \(y_{ijk} = 0, 1\) represents whether subject \(i\) detected the
+data plot (1) or did not (0), \(\mu_\) is the subject-specific random
+intercept, \(\tau_j\) is the map type effect, \(\delta_k\) is the trend
+model effect. The interaction between map type and trend model allows
+for any map type effect to differ between trend models. As each
+participant provides results from 12 lineups, this model can account for
+each individual participants' abilities with the subject-specific random
+intercept.
 
@@
 
-\subsection{Demographic data
-collection}\label{demographic-data-collection}
+\subsection{Data collection}\label{data-collection}
 
@@
 
-on each of lineup. These responses are saved after entering, but only
-recorded in the results sheet when the participants clicked the submit
-button on the final page.
+on each of lineup. These responses are saved after entering.
+Participants were expected to click the submit button on the final page.
 
@@
 
-Responses from 92 participants were collected. Five participants did not
-provide more than three unique choices for the twelve lineups, and their
-data was removed. Set A was evaluated by 42 participants, and 53
-evaluated set B. This resulted in 1104 evaluations, corresponding to 92
-subjects, each evaluating 12 lineups, that were analysed on accuracy and
-speed. The certainty and reasons of subjects in their answers is also
-examined.
+A total of 1273 responses were collected from 97 participants. A small
+number of participants, 7, were removed because they did not provide at
+least 11 responses, or left more than 3 at the default value of 0. These
+are participants that stopped early or clicked through without doing the
+evaluation. Set A was evaluated by 39 participants, and 51 evaluated set
+B. This resulted in 1080 evaluations, corresponding to 90 subjects, each
+evaluating 12 lineups, that were analysed on accuracy and speed. The
+certainty and reasons of subjects in their answers is also examined.
 
@@
 
-Of the 92 participants, 67 were male, and 25 female. Most participants
-(56) had a Bachelors degree, 13 had a Masters degree, and the remaining
-23 had high school diplomas.
+Of the 90 participants, 66 were male, and 24 female. Most participants
+(55) had a Bachelors degree, 13 had a Masters degree, and the remaining
+22 had high school diplomas. The age distribution was 13, 36, 21, 11, 6
+for age groups 18-24, 25-34, 35-44, 45-54, 55+, with 3 preferring not to
+answer. Only 1 reported having lived in Australia.
 
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-beeswarm-1.pdf}
+\includegraphics[width=0.8\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-beeswarm-1.pdf}
 
@@
 
-\caption{\label{fig-certainty}The amount of times each level of
-certainty was chosen by participants when viewing hexagon tile map or
-choropleth displays. Participants were more likely to choose a high
-certainty when considering a Choropleth map. The mid value of 3 was the
-default certainty, it was chosen most for the Hexagon tile map
-displays.}
+\caption{\label{fig-certainty}The distribution of certainty chosen by
+participants when viewing hexagon tile map or choropleth displays, shown
+as a mosaic plot, faceted by the trend model and whether the plot was
+detected or not. At most trend models and whether the plot was detected
+or not, participants were more likely to choose a high certainty when
+evaluating a choropleth map.}
 
@@
 The hexagon tile map display should be considered as an alternative
-visualization method when communicating distributions that relate to the
+visualisation method when communicating distributions that relate to the
 population across a set of geographic units. As an additional display to
@@
 
+Add Election results data + plus other statistics, other hexagon layout
+software
+
 \section*{Acknowledgments}\label{acknowledgments}
@@
 The authors would like to thank the Australian Cancer Atlas team for
-discussions regarding alternative spatial visualizations, and Professor
+discussions regarding alternative spatial visualisations, and Professor
 Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with

### 2025-07-08 paper/review1/ReponseToReviewers2025.qmd
done with reviewer 1 and most of reviewer 2 comments

@@
 
-XXX
+*XXX*
 
@@
 P18, L297-301.
-The math does not seem to work unless I’m missing something.  Responses were collected from 92 participants.
+The math does not seem to work unless I'm missing something.
+Responses were collected from 92 participants.
 Five were removed which leaves 87 for evaluation.
@@
 
+*Fixed. Now generated automatically from the code in the qmd.*
+
 P22 Discussion through to Conclusions.
@@
 There is considerable value in using a hexagon tile map for showing statistics and modelled output in statistical area levels across Australia or similar.
+
+*XXX*
 
@@
 
-Figure 1. This is a nice figure! My only suggestion is to adjust the caption to say “Thyroid cancer incidence” instead of “Thyroid incidence.”
+Figure 1. This is a nice figure! My only suggestion is to adjust the caption to say "Thyroid cancer incidence" instead of "Thyroid incidence."
 
-*This change has been applied.*
+*Done.*
 
@@
 
-*The location has now been mentioned in the caption, and a reference has been added in the text to direct readers to the alternative view.*
+*The location has now been mentioned in the caption, and a sentence has been added in the text to direct readers to the supplementary materials.*
 
 Figure 3.
-Would it be clearer to use “Hexagon Tile” and “Choropleth” for the map display labels?
-In the caption, can you make a note of what “Location” refers to?
+Would it be clearer to use "Hexagon Tile" and "Choropleth" for the map display labels?
+In the caption, can you make a note of what "Location" refers to?
 (It took me a while to figure that out.)
+
+*XXX re-make figure*
 
@@
 
-Figure 5. I think the green/orange dot legend for “Choro.” And “Hex.” is unnecessary.
+*Done*
+
+Figure 5. I think the green/orange dot legend for "Choro." And "Hex." is unnecessary.
+
+*Legend removed*
 
 Figure 6. Have you tried placing the bars next to each other instead of overlaying them? What does that look like?
+
+*We have changed this to be a mosaic plot, to focus on the proportion of times the participant chose the different certainty levels relative to both map types.
+This is better than the side-by-side bars which are hard to read because of different counts.*
 
@@
 
-Page 11 3.7 Demographic data collection -\> section could be merged with 3.5 “Web application” the reduce redundancies
+Page 11 3.7 Demographic data collection -\> section could be merged with 3.5 "Web application" the reduce redundancies
+
+*Kept in this section but section renamed to be "Data collection" because it concerns all the information recorded.*
 
 Page 12 Lines 297 – 301: 5 participants where remove because they provided not more than 3 unique choices -\> please state a reason for that.
-The assumption is these participants just “clicked through” the experiment and choose a single location all the time?
+The assumption is these participants just "clicked through" the experiment and choose a single location all the time?
 (see my major concern).
+
+*Explanation is improved, and numbers reported are now automatically calculated in the analysis script, which is part of the qmd file generating the paper.*
 
@@
 
+*There is no difference in results from group A and B. XXX*
+
 Page 12 Line 322. Any explanation why the choropleth performed not better?
+
+*The difference is small, at least relative to the other two patterns.
+We expect it might be due to the large rural polygons might also play a role in obscuring large simple spatial trend, too.
+But we don't want to speculate.*
 

### 2025-07-08 paper/kobakian-cook-anzjs.qmd
typo in equation fixed

@@
 type2_colors <- c(
-  "Choropleth" = "#fcae91",
-  "Hexagon tile" = "#a50f15")
+  "choropleth" = "#fcae91",
+  "hexagon tile" = "#a50f15")
 
@@
 The Australian Cancer Atlas allows users to explore the patterns in the distributions of cancer statistics over the geographic space of Australia.
-It uses a choropleth map display and diverging color scheme to draw attention to relationships between neighboring areas.
+It uses a choropleth map display and diverging color scheme to draw attention to relationships between neighbouring areas.
 The hexagon tile map may be a useful alternative display to enhance the atlas.
 
-The experiment was conducted using the lineup protocol, a visual inference procedure [@GIIV], to objectively test the effectiveness of the two displays.
+The experiment was conducted using the lineup protocol, a visual inference procedure [@BCHLLSW09;@GIIV], that can be used to objectively test the effectiveness of the two displays [@GTPCCD].
+A lineup embeds the data plot among a field of null data plots, and an independent observer is asked to select the most different plot.
+It was shown by @VVSIALM to be an effective way to conduct a hypothesis test where a plot is treated as a test statistic.
+If the data plot is selected it is analogous to a rejection of the null hypothesis (no structure), and the observed data plot is unlikely to arise from the null scenario.
 
@@
 Spatial visualisations communicate the distribution of statistics over geographic landscapes.
-The choropleth map [@EI, @BCM] is a traditional display.
+The choropleth map [@EI;@BCM] is a traditional display.
 It is used to present statistics that have been aggregated on geographic units.
@@
 This is important for digesting disease patterns.
-If there is a trend it may imply that the disease is spreading from one location to another.
+If there is a linear trend it may imply a relationship between disease and geographic location.
 If there is a cluster, or an anomaly, there may be a localized outbreak of the disease.
-Aggregating the statistic on administrative units, provides a level of privacy to individuals, while allowing the impact of the disease on the community to be analyzed.
+<!--Aggregating the statistic on administrative units, provides a level of privacy to individuals, while allowing the impact of the disease on the community to be analyzed.-->
 
@@
 It transforms the geographic map base to reflect the population in the geographic region, while preserving some aspects of the geographic location.
-There are several cartogram algorithms [@ACTUC, @CBATCC]; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
+There are several cartogram algorithms [@ACTUC;@CBATCC]; each involves shifting the boundaries of geographic units, using the value of the statistic to increase or decrease the area taken by the geographic unit on the map.
 The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units but can result in losing the familiar geographic information.
@@
 A similar approach was pioneered by @RSCW, using rectangles that tile to align borders of neighbours [@CDWCS].
-There have been thorough reviews of the array of methods, as suitable for cancer atlas displays [@review, @BCM].
+There have been thorough reviews of the array of methods, as suitable for cancer atlas displays [@review;@BCM].
 
@@
 Remote regions are represented by isolated hexagons, which is not ideal, but maintains the spatial location of these data values.
-It is of interest to know how well the spatial distribution is perceived for this display, in comparison to the choropleth.
+It is of interest to know how well the spatial distribution patterns are seen from this display, in comparison to how they are seen from the choropleth.
 
@@
 
-In order to assess the effectiveness of the hexagon tile map, the lineup protocol [@BCHLLSW09, @GIIV] from visual inference procedures is employed.
+In order to assess the effectiveness of the hexagon tile map, the lineup protocol [@BCHLLSW09;@GIIV] from visual inference procedures is employed.
 The approach mirrors classical statistical inference.
@@
 
-Australia is used for the study, with Statistical Area 3 (SA3) [@abs2016] as the geographic units. The results should apply broadly to any other geographic area of interest.
+Australia is used for the study, with Statistical Area 3 (SA3) [@abs2016] as the geographic units.
+The results should apply broadly to any other geographic areas of interest, if there are large differences in area and population size.
 
@@
 
-  - Map type: *Choropleth, Hexagon tile*
+  - Map type: *choropleth, hexagon tile*
   - Trend: *South-East to North-West; Locations in three population centres; Locations in multiple population centres, *
@@
 #| results: "asis" 
-#| fig-width: 8 
-#| fig-height: 8
-#| out-width: 80%
+#| fig-width: 6 
+#| fig-height: 4
+#| out-width: 100%
 #| fig-cap: "The experimental design used in the study.
 Participants are allocated to with group A or B, to evaluate either the choropleth or hexagon tile map lineup of each simulated data set.
-Place in the lineup is recorded as 'Location'."
-ggdraw(xlim = c(0,1), ylim = c(0,1)) + draw_plot(rasterGrob(png::readPNG("figures/experiment_design.png")))
+The text 'loc' refers to the location of the data plot in the lineup."
+#ggdraw(xlim = c(0,1), ylim = c(0,1)) + #draw_plot(rasterGrob(png::readPNG("figures/experiment_design.png")))
+
+expt_design <- d |>
+  count(group, trend, location, type, replicate)
+
+ggplot(expt_design, ) +
+  geom_tile(aes(x=group, y=1, fill=type)) +
+  geom_text(aes(x=group, y=1, label = paste("loc:", location))) + 
+  facet_grid(replicate~trend, axes = "all", labeller = labeller(replicate = label_both, trend = label_both)) +
+  ylab("") +
+  scale_fill_manual("", values = type_colors) +
+  theme_minimal() +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank())
 ```
@@
 
-For each of the 144 individual maps, the values for each geographic area were rescaled to create a similar color scale from deep blue to dark red within each map.
+For each of the 144 individual maps, the values for each geographic area were rescaled to create a similar colour scale from deep blue to dark red within each map.
 This meant at least one geographic unit was coloured dark blue, and at least one was red, in every map display of every lineup.
@@
 For the geographic NW-SE distribution, this resulted in the smallest values of the trend model (blue) occurring in Western Australia, the North West of Australia, and the largest values of the trend model (red) occurring in the South East.
-This resulted in Tasmania being colored completely red.
+This resulted in Tasmania being coloured completely red.
 
 For the population related displays, the clusters in the cities appeared more red than the rest of Australia.
-
-## Analysis
-
-### Data Cleaning
-
-The first step in the data cleaning process involved checking that survey responses collected for each participants were only included once in the data set. 
-The data cleaning process also involved filtering out participants' who did not provide at least three unique choices when considering each of the twelve lineups.
-These participants achieved a detection rate of 0.
-If participants had made various plot choices for the 12 displays they saw they were still included in the dataset.
-
-### Descriptive statistics
-
-Basic descriptive statistics were used to contrast the detection rate for the two types of displays.
-Comparison was also made across the trend models, contrasting the mean and standard detection rate for each group, who had seen the different map display type for each replicate.
-
-Side-by-side dot plots were made of accuracy (efficiency) against map type, faceted by trend model type.
-
-Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.
-
-<!-- Plots will be made in R [@RCore], with the `ggplot2` package [@ggplot2].-->   
-### Modelling
-
-The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
-The R `glmer()` function in the `lme4` [@lme4] package implements generalised linear mixed effect models.
-The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
-
-$$
-\hat{y}_{ijk} \sim Bernoulli(p_{ijk})
-$$
-with
-
-$$
-\text{logit}(p_{ijk}) = \mu_i + \tau_j + \delta_k + (\tau \delta)_{jk} ~~~~ j=1,2; ~~ k=1,2,3
-$$
-
-<!--
-$$y_{ij} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij} + \varepsilon_{i,j}, ~~~ i=1,2; ~j=1,2,3$$
--->
-
-where $y_{ijk} = 0, 1$ represents whether subject $i$ detected the data plot (1) or did not (0), $\mu_$ is the subject-specific random intercept, $\tau_j$ is the map type effect, $\delta_k$ is the trend model effect.
-The interaction between map type and trend model allows for any map type effect to differ between trend models.
-As each participant provides results from 12 lineups, this model can account for each individual participants' abilities with the subject-specific random intercept.
-
-<!-- 
-The model specifies a logit link, this means the predicted values from the `glmer` model should be back-transformed to fit between 0 and 1.
-The predictions  $\widehat{p}(\eta)$ are transformed to be probabilities between 0 and 1 with the link specified below:
-
-$$\widehat{p}(\eta) = \frac{e^{\eta}}{1 + e^{\eta}}$$ \label{eq:transform}
-$$\eta = f(\tau_i,\delta_j)$$
--->
 
@@
 
- - Plot choice: the number of the plot that they deemed to be most different from the others.
- - Reason: one of "Clusters of colour", "Colour trend across the areas", "Big differences between neighbouring areas", "All areas have similar colours" or "None of these reasons". 
- - Certainty: how certain that their choice is different from the others, on a scale of 1-5.
+ - **Plot choice**: the number of the plot that they deemed to be most different from the others.
+ - **Reason**: one of "Clusters of colour", "Colour trend across the areas", "Big differences between neighbouring areas", "All areas have similar colours" or "None of these reasons". 
+ - **Certainty**: how certain that their choice is different from the others, on a scale of 1-5.
 
 on each of lineup. These responses are saved after entering. Participants were expected to click the submit button on the final page.
+
+## Analysis
+
+### Data Cleaning
+
+Data is checked to ensure that survey responses collected for each participants were only included once.
+Technically it is possible to submit results more than once if the submit button is clicked multiple times in short sequence.
+Participants who did not finish the evaluation of all lineups or clicked through without providing their evaluation are filtered.
+
+### Descriptive statistics
+
+Basic descriptive statistics were used to contrast the detection rate for the two types of displays.
+Comparison was also made across the trend models, contrasting the mean and standard detection rate for each group, who had seen the different map display type for each replicate.
+
+Side-by-side dot plots were made of accuracy (efficiency) against map type, faceted by trend model type.
+
+Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.
+
+<!-- Plots will be made in R [@RCore], with the `ggplot2` package [@ggplot2].-->
+
+### Modelling
+
+The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
+The R `glmer()` function in the `lme4` [@lme4] package implements generalised linear mixed effect models.
+The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:
+
+$$
+\hat{y}_{ijk} \sim Bernoulli(p_{ijk})
+$$
+with
+
+$$
+\text{logit}(p_{ijk}) = \mu_i + \tau_j + \delta_k + (\tau \delta)_{jk}
+$$
+
+<!--
+$$y_{ij} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij} + \varepsilon_{i,j}, ~~~ i=1,2; ~j=1,2,3$$
+-->
+
+where $y_{ijk} = 0, 1$ represents whether subject $i$ detected the data plot (1) or did not (0), $\mu_i, ~i=1, \dots n$ is the subject-specific random intercept, $n$ is the number of subjects, $\tau_j, ~j=1,2$ is the map type effect, $\delta_k, ~k=1,2,3$ is the trend model effect.
+The interaction between map type and trend model allows for any map type effect to differ between trend models.
+As each participant provides results from 12 lineups, this model can account for each individual participants' abilities with the subject-specific random intercept.
+
+<!-- 
+The model specifies a logit link, this means the predicted values from the `glmer` model should be back-transformed to fit between 0 and 1.
+The predictions  $\widehat{p}(\eta)$ are transformed to be probabilities between 0 and 1 with the link specified below:
+
+$$\widehat{p}(\eta) = \frac{e^{\eta}}{1 + e^{\eta}}$$ \label{eq:transform}
+$$\eta = f(\tau_i,\delta_j)$$
+-->
 
@@
 The Three Cities and All Cities trend models shown in the hexagon tile map allowed viewers to detect the data plot substantially more often than the choropleth counterparts.
-One replicate for the All Cities group had similar detection rates for both map types, the rate of detection using the choropleth map was much higher than other replicates.
+One replicate for the All Cities group had similar detection rates for both map types - the rate of detection using the choropleth map was much higher than other replicates.
 Surprisingly, participants could also detect the gradual spatial trend in the NW-SE group from the hexagon tile map.
@@
 #| label: tbl-desc-stats
-#| results: "asis"
+#| tbl-cap: "The mean and standard deviation of the rate of detection for each trend model, calculated for the choropleth and hexagon tile map displays."
 types <- c("Choro.", "", "Hex.", "")
@@
   knitr::kable(., format = "latex", align = "lccc", booktabs = TRUE, 
-    linesep = c("", "\\addlinespace"),
-    caption = "The mean and standard deviation of the rate of detection for each trend model, calculated for the choropleth and hexagon tile map displays.")
+    linesep = c("", "\\addlinespace"))
 ```
@@
 
-When a choropleth map display is used, the predicted detection rate for the Three Cities trend, `r round(exp(0.07-3.41)/(1+exp(0.07-3.41)),2)`; this is extremely low, especially compared to the NW-SE trend of `r round(exp(0.07)/(1+exp(0.07)),2)`.
+When a choropleth map display is used, the predicted detection rate for the Three Cities trend, `r round(exp(0.07-3.41)/(1+exp(0.07-3.41)),2)` is extremely low, especially compared to the NW-SE trend of `r round(exp(0.07)/(1+exp(0.07)),2)`.
 When the All Cities trend is presented in a choropleth display the predicted probability of detection is `r round(exp(0.07-1.34)/(1+exp(0.07-1.34)),2)`.
@@
 #| label: tbl-detect-glmer1
-#| results: "asis"
+#| tbl-cap: "Parameter estimates of the fitted model fit for  detection rate. All terms are statistically significant  ($^{**}=0.01$, $^{***}=0.001$)."
 # Mixed effects models
@@
     Est. = estimate,
-    Sig. = sig,
-    `Std. Error` = std.error, 
-    `P val` = p.value) %>% 
+    `Std. Err.` = std.error, 
+    `P-val.` = p.value, 
+    Sig. = sig) %>% 
   knitr::kable(format = "latex", escape = FALSE, align= "rrlrr", 
-    booktabs = T, linesep = c("", "\\addlinespace", "", "\\addlinespace", ""), 
-    caption = "The model output for the generalised linear mixed effect model for detection rate.
-This model considers the type of display, the trend model hidden in the data plot, and accounts for contributor performance.")
+    booktabs = T, linesep = c("", "\\addlinespace", "", "\\addlinespace", ""))
 ```
@@
 The time taken to complete an evaluation ranged from milliseconds to 60 seconds.
-The average time taken for type of display is shown as a large colored dot on each plot.
-when considering the heights of the green and orange dots, there is little difference in the average time taken to read a choropleth or hexagon tile map.
-Comparing the same colored dot across each trend model row, there is a slight increase in the time taken to correctly detected the data plot in the hexagon tile map lineup, but little difference in evaluation time for the choropleth display.
+The average time taken for type of display is shown as a large coloured dot on each plot.
+When considering the heights of the green and orange dots, there is little difference in the average time taken to read a choropleth or hexagon tile map.
+Comparing the same coloured dot across each trend model row, there is a slight increase in the time taken to correctly detected the data plot in the hexagon tile map lineup, but little difference in evaluation time for the choropleth display.
 However, there were substantially less correct detections for choropleth lineups for the Three cities and All Cities trends.
@@
 #| fig-cap: "The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots.
-The colored point indicates average time taken for each map type.
-Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between map types."
+The coloured point indicates average time taken for each map type.
+Although some participants take just a few seconds per evaluation, and some take as much as 60 seconds, but there is very little difference in time taken between map types."
 #| fig-height: 6
@@
 Participants provided their level of certainty regarding their choice using a five point scale.
-Unlike the accuracy and speed of responses that were derived during the data processing phase, this was a subjective
-assessment by the participant prompted by the question: ‘How certain are you about your choice?’.
-@fig-certainty shows the amount of times participants provided each level of certainty.
-This was separated for each combination of trend models and display type, and colored depending on whether a participant correctly detected the data plot in the lineup.
-Participants often chose 4 or 5 when viewing the population related trends in the choropelth display, even though they were often incorrect when viewing an All Cities trend and overwhelmingly incorrect for the Three Cities trend.
-This shows overconfidence in their detection ability when using a choropleth map display.
+Unlike the accuracy and speed of responses that were derived during the data processing phase, this was a subjective assessment by the participant prompted by the question: "How certain are you about your choice?".
+@fig-certainty shows a mosaic plot summarising how participants reported their certainty with their decision.
+The plots are made separately for each combination of trend models and whether the data plot was detected or not.
+Colour indicates the type of map display.
+The proportion of subjects evaluating the choropleth version increases as certainty increases, which suggests overconfidence in their detection ability when using a choropleth map display.
 Participants were less likely to be certain when their choice was incorrect and they were viewing a hexagon tile map.
-For each trend model, participants were more likely to doubt their choice and choose 1 or 2 in the hexagon tile map displays, even though many had made the correct choice.
 
@@
     labels = c("Detected? Yes", "Detected? No"))) |>
-  mutate(type = fct_recode(type, "Choropleth" = "Choro.", "Hexagon tile" = "Hex.")) |>
+  mutate(type = fct_recode(type, "choropleth" = "Choro.", "hexagon tile" = "Hex.")) |>
   ggplot() +
@@
 Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons. 
-"Color trend across the areas" was the most common selection for NW-SE trend displays (@tbl-reason).
+"Colour trend across the areas" was the most common selection for NW-SE trend displays (@tbl-reason).
 
 The reasons chosen by participants from the list provided to them varied more when viewing choropleth displays than the hexagon tile map.
-The hexagon tile map displays resulted in "Clusters of color" as the most common choice made by participants.
+The hexagon tile map displays resulted in "Clusters of colour" as the most common choice made by participants.
 
@@
 #| label: tbl-reason
-#| results: "asis"
+#| tbl-cap: "The main reason that participants wrote for their choice of plot when looking at each trend model shown in choropleth and hexagon tile maps."
 # Qualitative analysis of reason
@@
   knitr::kable(., format = "latex", booktabs = TRUE,
-    linesep = c("", "\\addlinespace", "", "\\addlinespace",""),
-    caption = "The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
-The facets show whether or not the choice was correct.") %>%
+    linesep = c("", "\\addlinespace", "", "\\addlinespace","")) %>% 
   #kable_styling(bootstrap_options = "hold_position") %>% 
@@
 
-The color scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
-Due to the consistent coloring of rural areas in a choropleth display, the choice "All areas have similar colors" was most common reason for a participants choice.
-The All Cities displays colored the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural color consistency.
+The colour scaling applied in Three cities and All cities displays resulted in the rural areas of the real data plot appearing more blue or yellow than the other plots in the lineups.
+Due to the consistent colouring of rural areas in a choropleth display, the choice "All areas have similar colours" was most common reason for a participants choice.
+The All Cities displays coloured the inner-city areas of all capital cities more red, this was observable to participants and explains the equal choice of the city clusters or rural colour consistency.
 Choosing "Clusters of colour" was expected when participants viewed the Hexagon tile map display of the All Cities and Three Cities distributions.
 It was unexpected that it was also the most common reason for the NW-SE hexagon tile map displays.
-Due to the spatial covariance introduced in the smoothing, groups of similarly colored hexagons were present in all of the hexagon tile map displays.
+Due to the spatial covariance introduced in the smoothing, groups of similarly coloured hexagons were present in all of the hexagon tile map displays.
 All Cities and Three Cities distributions of real data trends had distinctly different patterns or red inner-city areas, while some of the plots in each lineup may have shared similar features.
@@
 We are thankful for the NUMBATs (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.
+
+# Supplementary materials and reproducibility {-}
 
@@
 
+# Ethics Declaration {-}
+
 Ethics approval for the online survey was granted by QUT’s Ethics Committee (Ethics Application Number: 1900000991).

### 2025-07-08 paper/kobakian-cook-anzjs.tex
typo in equation fixed

@@
 Australia. It uses a choropleth map display and diverging color scheme
-to draw attention to relationships between neighboring areas. The
+to draw attention to relationships between neighbouring areas. The
 hexagon tile map may be a useful alternative display to enhance the
@@
 The experiment was conducted using the lineup protocol, a visual
-inference procedure \citep{GIIV}, to objectively test the effectiveness
-of the two displays.
+inference procedure \citep{BCHLLSW09, GIIV}, that can be used to
+objectively test the effectiveness of the two displays \citep{GTPCCD}. A
+lineup embeds the data plot among a field of null data plots, and an
+independent observer is asked to select the most different plot. It was
+shown by \citet{VVSIALM} to be an effective way to conduct a hypothesis
+test where a plot is treated as a test statistic. If the data plot is
+selected it is analogous to a rejection of the null hypothesis (no
+structure), and the observed data plot is unlikely to arise from the
+null scenario.
 
@@
 Spatial visualisations communicate the distribution of statistics over
-geographic landscapes. The choropleth map \citep[\citet{BCM}]{EI} is a
+geographic landscapes. The choropleth map \citep{EI, BCM} is a
 traditional display. It is used to present statistics that have been
@@
 reader can see whether there are spatial trends, clusters or anomalies.
-This is important for digesting disease patterns. If there is a trend it
-may imply that the disease is spreading from one location to another. If
-there is a cluster, or an anomaly, there may be a localized outbreak of
-the disease. Aggregating the statistic on administrative units, provides
-a level of privacy to individuals, while allowing the impact of the
-disease on the community to be analyzed.
+This is important for digesting disease patterns. If there is a linear
+trend it may imply a relationship between disease and geographic
+location. If there is a cluster, or an anomaly, there may be a localized
+outbreak of the disease.
 
@@
 aspects of the geographic location. There are several cartogram
-algorithms \citep[\citet{CBATCC}]{ACTUC}; each involves shifting the
-boundaries of geographic units, using the value of the statistic to
-increase or decrease the area taken by the geographic unit on the map.
-The changes to the boundaries result in cartograms that accurately
-communicate population by map area for each of the geographic units but
-can result in losing the familiar geographic information. For Australia,
-the transformations warp the country so that it is no longer
-recognizable.
+algorithms \citep{ACTUC, CBATCC}; each involves shifting the boundaries
+of geographic units, using the value of the statistic to increase or
+decrease the area taken by the geographic unit on the map. The changes
+to the boundaries result in cartograms that accurately communicate
+population by map area for each of the geographic units but can result
+in losing the familiar geographic information. For Australia, the
+transformations warp the country so that it is no longer recognizable.
 
@@
 thorough reviews of the array of methods, as suitable for cancer atlas
-displays \citep[\citet{BCM}]{review}.
+displays \citep{review, BCM}.
 
@@
 location of these data values. It is of interest to know how well the
-spatial distribution is perceived for this display, in comparison to the
-choropleth.
+spatial distribution patterns are seen from this display, in comparison
+to how they are seen from the choropleth.
 
@@
 In order to assess the effectiveness of the hexagon tile map, the lineup
-protocol \citep[\citet{GIIV}]{BCHLLSW09} from visual inference
-procedures is employed. The approach mirrors classical statistical
-inference. The procedures for doing a power comparison of competing plot
-designed, outlined in \citet{GTPCCD}, are followed.
+protocol \citep{BCHLLSW09, GIIV} from visual inference procedures is
+employed. The approach mirrors classical statistical inference. The
+procedures for doing a power comparison of competing plot designed,
+outlined in \citet{GTPCCD}, are followed.
 
@@
 \citep{abs2016} as the geographic units. The results should apply
-broadly to any other geographic area of interest.
+broadly to any other geographic areas of interest, if there are large
+differences in area and population size.
 
@@
 \item
-  Map type: \emph{Choropleth, Hexagon tile}
+  Map type: \emph{choropleth, hexagon tile}
 \item
@@
 
-\includegraphics[width=0.8\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-exp-design-1.pdf}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-exp-design-1.pdf}
 
@@
 either the choropleth or hexagon tile map lineup of each simulated data
-set. Place in the lineup is recorded as `Location'.}
+set. The text `loc' refers to the location of the data plot in the
+lineup.}
 
@@
 For each of the 144 individual maps, the values for each geographic area
-were rescaled to create a similar color scale from deep blue to dark red
-within each map. This meant at least one geographic unit was coloured
-dark blue, and at least one was red, in every map display of every
-lineup.
+were rescaled to create a similar colour scale from deep blue to dark
+red within each map. This meant at least one geographic unit was
+coloured dark blue, and at least one was red, in every map display of
+every lineup.
 
@@
 North West of Australia, and the largest values of the trend model (red)
-occurring in the South East. This resulted in Tasmania being colored
+occurring in the South East. This resulted in Tasmania being coloured
 completely red.
@@
 more red than the rest of Australia.
-
-\subsection{Analysis}\label{analysis}
-
-\subsubsection{Data Cleaning}\label{data-cleaning}
-
-The first step in the data cleaning process involved checking that
-survey responses collected for each participants were only included once
-in the data set. The data cleaning process also involved filtering out
-participants' who did not provide at least three unique choices when
-considering each of the twelve lineups. These participants achieved a
-detection rate of 0. If participants had made various plot choices for
-the 12 displays they saw they were still included in the dataset.
-
-\subsubsection{Descriptive statistics}\label{descriptive-statistics}
-
-Basic descriptive statistics were used to contrast the detection rate
-for the two types of displays. Comparison was also made across the trend
-models, contrasting the mean and standard detection rate for each group,
-who had seen the different map display type for each replicate.
-
-Side-by-side dot plots were made of accuracy (efficiency) against map
-type, faceted by trend model type.
-
-Similar plots were made of the feedback and demographic variables -
-reason for choice, reported difficulty, gender, age, education, having
-lived in Australia - against the design variables.
-
-\subsubsection{Modelling}\label{modelling}
-
-The likelihood of detecting the data plot in the lineup can be modelled
-using a linear mixed effects model. The R \texttt{glmer()} function in
-the \texttt{lme4} \citep{lme4} package implements generalised linear
-mixed effect models. The model used includes the two main effects map
-type and trend model, which gives the fixed effects model to be:
-
-\[
-\hat{y}_{ijk} \sim Bernoulli(p_{ijk})
-\] with
-
-\[
-\text{logit}(p_{ijk}) = \mu_i + \tau_j + \delta_k + (\tau \delta)_{jk} ~~~~ j=1,2; ~~ k=1,2,3
-\]
-
-where \(y_{ijk} = 0, 1\) represents whether subject \(i\) detected the
-data plot (1) or did not (0), \(\mu_\) is the subject-specific random
-intercept, \(\tau_j\) is the map type effect, \(\delta_k\) is the trend
-model effect. The interaction between map type and trend model allows
-for any map type effect to differ between trend models. As each
-participant provides results from 12 lineups, this model can account for
-each individual participants' abilities with the subject-specific random
-intercept.
 
@@
 \item
-  Plot choice: the number of the plot that they deemed to be most
-  different from the others.
-\item
-  Reason: one of ``Clusters of colour'', ``Colour trend across the
-  areas'', ``Big differences between neighbouring areas'', ``All areas
-  have similar colours'' or ``None of these reasons''.
-\item
-  Certainty: how certain that their choice is different from the others,
-  on a scale of 1-5.
+  \textbf{Plot choice}: the number of the plot that they deemed to be
+  most different from the others.
+\item
+  \textbf{Reason}: one of ``Clusters of colour'', ``Colour trend across
+  the areas'', ``Big differences between neighbouring areas'', ``All
+  areas have similar colours'' or ``None of these reasons''.
+\item
+  \textbf{Certainty}: how certain that their choice is different from
+  the others, on a scale of 1-5.
 \end{itemize}
@@
 Participants were expected to click the submit button on the final page.
+
+\subsection{Analysis}\label{analysis}
+
+\subsubsection{Data Cleaning}\label{data-cleaning}
+
+Data is checked to ensure that survey responses collected for each
+participants were only included once. Technically it is possible to
+submit results more than once if the submit button is clicked multiple
+times in short sequence. Participants who did not finish the evaluation
+of all lineups or clicked through without providing their evaluation are
+filtered.
+
+\subsubsection{Descriptive statistics}\label{descriptive-statistics}
+
+Basic descriptive statistics were used to contrast the detection rate
+for the two types of displays. Comparison was also made across the trend
+models, contrasting the mean and standard detection rate for each group,
+who had seen the different map display type for each replicate.
+
+Side-by-side dot plots were made of accuracy (efficiency) against map
+type, faceted by trend model type.
+
+Similar plots were made of the feedback and demographic variables -
+reason for choice, reported difficulty, gender, age, education, having
+lived in Australia - against the design variables.
+
+\subsubsection{Modelling}\label{modelling}
+
+The likelihood of detecting the data plot in the lineup can be modelled
+using a linear mixed effects model. The R \texttt{glmer()} function in
+the \texttt{lme4} \citep{lme4} package implements generalised linear
+mixed effect models. The model used includes the two main effects map
+type and trend model, which gives the fixed effects model to be:
+
+\[
+\hat{y}_{ijk} \sim Bernoulli(p_{ijk})
+\] with
+
+\[
+\text{logit}(p_{ijk}) = \mu_i + \tau_j + \delta_k + (\tau \delta)_{jk}
+\]
+
+where \(y_{ijk} = 0, 1\) represents whether subject \(i\) detected the
+data plot (1) or did not (0), \(\mu_i, ~i=1, \dots n\) is the
+subject-specific random intercept, \(n\) is the number of subjects,
+\(\tau_j, ~j=1,2\) is the map type effect, \(\delta_k, ~k=1,2,3\) is the
+trend model effect. The interaction between map type and trend model
+allows for any map type effect to differ between trend models. As each
+participant provides results from 12 lineups, this model can account for
+each individual participants' abilities with the subject-specific random
+intercept.
 
@@
 replicate for the All Cities group had similar detection rates for both
-map types, the rate of detection using the choropleth map was much
+map types - the rate of detection using the choropleth map was much
 higher than other replicates. Surprisingly, participants could also
@@
 
-\caption{\label{tbl-desc-stats}}
+\caption{\label{tbl-desc-stats}The mean and standard deviation of the
+rate of detection for each trend model, calculated for the choropleth
+and hexagon tile map displays.}
 
@@
 
-\caption{\label{tab:tbl-desc-stats}The mean and standard deviation of the rate of detection for each trend model, calculated for the choropleth and hexagon tile map displays.}
-\centering
-\begin{tabular}[t]{lccc}
+\begin{tabular}{lccc}
 \toprule
@@
 When a choropleth map display is used, the predicted detection rate for
-the Three Cities trend, 0.03; this is extremely low, especially compared
-to the NW-SE trend of 0.52. When the All Cities trend is presented in a
+the Three Cities trend, 0.03 is extremely low, especially compared to
+the NW-SE trend of 0.52. When the All Cities trend is presented in a
 choropleth display the predicted probability of detection is 0.22. The
@@
 
-\caption{\label{tbl-detect-glmer1}}
+\caption{\label{tbl-detect-glmer1}Parameter estimates of the fitted
+model fit for detection rate. All terms are statistically significant
+(\(^{**}=0.01\), \(^{***}=0.001\)).}
 
@@
 
-\caption{\label{tab:tbl-detect-glmer1}The model output for the generalised linear mixed effect model for detection rate.
-This model considers the type of display, the trend model hidden in the data plot, and accounts for contributor performance.}
-\centering
-\begin{tabular}[t]{rrlrr}
+\begin{tabular}{rrlrr}
 \toprule
-Term & Est. & Sig. & Std. Error & P val\\
+Term & Est. & Std. Err. & P-val. & Sig.\\
 \midrule
-Intercept & -1.27 & $^{***}$ & 0.19 & 0.00\\
-Hex. & 1.63 & $^{***}$ & 0.24 & 0.00\\
+Intercept & -1.27 & 0.19 & 0.00 & $^{***}$\\
+Hex. & 1.63 & 0.24 & 0.00 & $^{***}$\\
 \addlinespace
-Three Cities & -2.07 & $^{***}$ & 0.43 & 0.00\\
-All Cities & 1.34 & $^{***}$ & 0.24 & 0.00\\
+Three Cities & -2.07 & 0.43 & 0.00 & $^{***}$\\
+All Cities & 1.34 & 0.24 & 0.00 & $^{***}$\\
 \addlinespace
-Hex:Three Cities & 1.28 & $^{**}$ & 0.48 & 0.01\\
-Hex:All Cities & -1.16 & $^{***}$ & 0.33 & 0.00\\
+Hex:Three Cities & 1.28 & 0.48 & 0.01 & $^{**}$\\
+Hex:All Cities & -1.16 & 0.33 & 0.00 & $^{***}$\\
 \bottomrule
@@
 to complete an evaluation ranged from milliseconds to 60 seconds. The
-average time taken for type of display is shown as a large colored dot
-on each plot. when considering the heights of the green and orange dots,
+average time taken for type of display is shown as a large coloured dot
+on each plot. When considering the heights of the green and orange dots,
 there is little difference in the average time taken to read a
-choropleth or hexagon tile map. Comparing the same colored dot across
+choropleth or hexagon tile map. Comparing the same coloured dot across
 each trend model row, there is a slight increase in the time taken to
@@
 the data plot was detected, and type of display, shown using
-horizontally jittered dotplots. The colored point indicates average time
-taken for each map type. Although some participants take just a few
-seconds per evaluation, and some take as much as mcuh as 60 seconds, but
-there is very little difference in time taken between map types.}
+horizontally jittered dotplots. The coloured point indicates average
+time taken for each map type. Although some participants take just a few
+seconds per evaluation, and some take as much as 60 seconds, but there
+is very little difference in time taken between map types.}
 
@@
 that were derived during the data processing phase, this was a
-subjective assessment by the participant prompted by the question: `How
-certain are you about your choice?'. Figure~\ref{fig-certainty} shows
-the amount of times participants provided each level of certainty. This
-was separated for each combination of trend models and display type, and
-colored depending on whether a participant correctly detected the data
-plot in the lineup. Participants often chose 4 or 5 when viewing the
-population related trends in the choropelth display, even though they
-were often incorrect when viewing an All Cities trend and overwhelmingly
-incorrect for the Three Cities trend. This shows overconfidence in their
-detection ability when using a choropleth map display. Participants were
-less likely to be certain when their choice was incorrect and they were
-viewing a hexagon tile map. For each trend model, participants were more
-likely to doubt their choice and choose 1 or 2 in the hexagon tile map
-displays, even though many had made the correct choice.
+subjective assessment by the participant prompted by the question: ``How
+certain are you about your choice?''. Figure~\ref{fig-certainty} shows a
+mosaic plot summarising how participants reported their certainty with
+their decision. The plots are made separately for each combination of
+trend models and whether the data plot was detected or not. Colour
+indicates the type of map display. The proportion of subjects evaluating
+the choropleth version increases as certainty increases, which suggests
+overconfidence in their detection ability when using a choropleth map
+display. Participants were less likely to be certain when their choice
+was incorrect and they were viewing a hexagon tile map.
 
@@
 Participants were asked why they had made their plot choice and were
-able to select from a set of suggested reasons. ``Color trend across the
-areas'' was the most common selection for NW-SE trend displays
+able to select from a set of suggested reasons. ``Colour trend across
+the areas'' was the most common selection for NW-SE trend displays
 (Table~\ref{tbl-reason}).
@@
 more when viewing choropleth displays than the hexagon tile map. The
-hexagon tile map displays resulted in ``Clusters of color'' as the most
+hexagon tile map displays resulted in ``Clusters of colour'' as the most
 common choice made by participants.
@@
 
-\caption{\label{tbl-reason}}
+\caption{\label{tbl-reason}The main reason that participants wrote for
+their choice of plot when looking at each trend model shown in
+choropleth and hexagon tile maps.}
 
@@
 
-\caption{\label{tab:tbl-reason}The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps.
-The facets show whether or not the choice was correct.}
-\centering
-\begin{tabular}[t]{llll}
+\begin{tabular}{llll}
 \toprule
@@
 
-The color scaling applied in Three cities and All cities displays
+The colour scaling applied in Three cities and All cities displays
 resulted in the rural areas of the real data plot appearing more blue or
 yellow than the other plots in the lineups. Due to the consistent
-coloring of rural areas in a choropleth display, the choice ``All areas
-have similar colors'' was most common reason for a participants choice.
-The All Cities displays colored the inner-city areas of all capital
+colouring of rural areas in a choropleth display, the choice ``All areas
+have similar colours'' was most common reason for a participants choice.
+The All Cities displays coloured the inner-city areas of all capital
 cities more red, this was observable to participants and explains the
-equal choice of the city clusters or rural color consistency. Choosing
+equal choice of the city clusters or rural colour consistency. Choosing
 ``Clusters of colour'' was expected when participants viewed the Hexagon
@@
 hexagon tile map displays. Due to the spatial covariance introduced in
-the smoothing, groups of similarly colored hexagons were present in all
+the smoothing, groups of similarly coloured hexagons were present in all
 of the hexagon tile map displays. All Cities and Three Cities
@@
 
+\section*{Supplementary materials and
+reproducibility}\label{supplementary-materials-and-reproducibility}
+\addcontentsline{toc}{section}{Supplementary materials and
+reproducibility}
+
 The source code to produce this document can be found on
@@
 
+\section*{Ethics Declaration}\label{ethics-declaration}
+\addcontentsline{toc}{section}{Ethics Declaration}
+
 Ethics approval for the online survey was granted by QUT's Ethics

### 2025-07-08 paper/review1/ReponseToReviewers2025.qmd
typo in equation fixed

@@
 
+*Done.*
+
 Inconsistent use of Australian vs.
@@
 Other random errors (e.g., uncapitalized start in line 347, unneeded apostrophe in line 212, missing verb in lines 337-338, etc.).
+
+*Fixed and checked.*
 
@@
 
-*XXX re-make figure*
+*This figure has been re-designed. Location is explained in the caption, also.*
 
@@
 
+*Done.*
+
 Background.
@@
 
+*Rephrased*
+
 Line 82.
-The word “perceived” here made me think about who is doing the perceiving and whether a discussion somewhere about the different audiences of spatial data displays is warranted / would be helpful.
+The word "perceived" here made me think about who is doing the perceiving and whether a discussion somewhere about the different audiences of spatial data displays is warranted / would be helpful.
 For example, who are the users of the Australian Cancer Atlas?
+
+*This is not especially about the Atlas, albeit motivated and grounded by the Atlas.
+We don't think it is relevant to discuss users of the Atlas.
+From our perspective, though, it would be ideal if the Atlas adopted this different display, and perhaps publication of this study might help to achieve this.
+We have modified the text in this paragraph to put the focus on the hexagon tile map vs the choropleth.*
 
@@
 Lines 128-129.
-I am not sure this claim is legitimate: “The results should apply broadly to any other geographic area of interest.” What about a choropleth map in which the geographic areas are more equally sized?
+I am not sure this claim is legitimate: "The results should apply broadly to any other geographic area of interest." What about a choropleth map in which the geographic areas are more equally sized?
 (Not all choropleth maps are as extreme as the SA3 Australian one!)
 
+*Language has been modified.*
+
 Sections 3.5 - 3.7. Why are these sections, which cover data collection, located after Section 3.4, which covers the analysis? Would it make more sense to place them before Section 3.4?
+
+*Sections have been re-organised.*
 
@@
 You do not provide information until Section 4, which feels too late.
-Additionally, should the “certainty” question, referenced in Section 4.4, also be included here?
+Additionally, should the "certainty" question, referenced in Section 4.4, also be included here?
 I also wonder if Section 3.7 should be renamed, given that it is about more than just demographic data collection.
+
+*Done. The section was re-named to "Data collection". "Difficulty" was replaced by "Certainty", making terminology consistent.*
 
@@
 
+*Yes, but it is relatively weak. It's something found from other studies that people were often more confident with sub-optimal plots!*
+
 Discussion.
@@
 Please spend some time discussing limitations of the study. Please also spend some time discussing future work, related to this study.
+
+*XXX*
 
@@
 Please also move the ethics approval out of this section to a more appropriate place.
+
+*Done.*
 
@@
 
+*Thanks and we appreciate the careful reading.*
+
 Referee: 3
@@
 
-I appreciate the opportunity to review this interesting paper that describes an experimental study comparing the effectiveness of hexagon tile maps against choropleth maps using “the lineup protocol.” While choropleth maps are a widely used visualization technique, newly proposed methods of displaying spatial data, such as hexagon tile maps, are not widely known to recipients of such data displays.
+I appreciate the opportunity to review this interesting paper that describes an experimental study comparing the effectiveness of hexagon tile maps against choropleth maps using "the lineup protocol." While choropleth maps are a widely used visualization technique, newly proposed methods of displaying spatial data, such as hexagon tile maps, are not widely known to recipients of such data displays.
 In this context, the paper addresses the important question of the usability of this new plot type.
@@
 
+*Thank you.*
+
 Considering these strengths, though, as I read the manuscript I found some areas in which I would have appreciated greater clarity.
@@
 
-1\) The section “Visual Inference” (Page 4) covers the background of visual inference and the lineup protocol, focusing on its use as a tool for statistical inference.
+1\) The section "Visual Inference" (Page 4) covers the background of visual inference and the lineup protocol, focusing on its use as a tool for statistical inference.
 I would like to see the reasoning for using it as a method to compare effectiveness made more clear.
@@
 
+*XXX*
+
 2\) I had some difficulties following the data simulation process in section 3.2 (Page 6).
 Specifically, the smoothing process and the reasoning behind this process should be explained more thoroughly.
+
+*XXX*
 
@@
 
+*XXX*
+
 The model definition in Section 3.4.3 on Page 9, as well as the reporting of the results (Page 12 and Table 2), need some work.
@@
 
+*XXX*
+
 Table 2 on Page 22 should include the variance of the random error.
 
-Second: The interpretation of the interaction effects on Page 13 Line 329 is a as follows:  “Allowing for the interaction effect, the difference in detection rate decreases for population-related displays for a choropleth map lineup but increases for a hexagon tile map display.“
+*XXX*
+
+Second: The interpretation of the interaction effects on Page 13 Line 329 is a as follows: "Allowing for the interaction effect, the difference in detection rate decreases for population-related displays for a choropleth map lineup but increases for a hexagon tile map display."
 
@@
 
-Additionally, I can’t replicate the detection probabilities mentioned in the text, e.g., Page 13, Lines 333f.: “For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection
+Additionally, I can’t replicate the detection probabilities mentioned in the text, e.g., Page 13, Lines 333f.: "For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection
 
-to 0.63 from 0.52 for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.”
+to 0.63 from 0.52 for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level."
 
-Are these fixed effects estimates? I can’t replicate this and the following results from Table 2, but maybe I’m missing something?
+*XXX*
+
+Are these fixed effects estimates? I can't replicate this and the following results from Table 2, but maybe I’m missing something?
 
@@
 
+*XXX*
+
 4\) My last major concern is the discussion of data quality from the experiment.
@@
 
+*XXX*
+
 Here are some additional comments, that might be useful to improve the paper:
 
-Page 1 line 16: “None of the existing approaches for creating cartograms or hexagon tiling perform well for the Australian landscape”
+Page 1 line 16: "None of the existing approaches for creating cartograms or hexagon tiling perform well for the Australian landscape"
 
@@
 
-Page 3 62 “For Australia, the transformations warp the country so that it is no longer recognizable” -\> maybe cite Kobakian, Cook & Roberts 2020 to make clear why this statement is made?
+Page 3 62 "For Australia, the transformations warp the country so that it is no longer recognizable" -\> maybe cite Kobakian, Cook & Roberts 2020 to make clear why this statement is made?
 
-Page 3 Line 78: what’s “substantially above”?
+*XXX*
+
+Page 3 Line 78: what's "substantially above"?
+
+*XXX*
 
@@
 
-Page 7 Line 164: “smoothed several times”; specify
+*Done.*
+
+Page 7 Line 164: "smoothed several times"; specify
+
+*Re-worded.*
 
@@
 
+*Re-worded.*
+
 Page 9 Line 206: population-related displays; explain which displays
 
-Page 9 Line 201: “The first step in the data cleaning process involved checking that survey responses collected for each participant were only included once in the data set.” Why is this necessary?
+*XXX*
+
+Page 9 Line 201: "The first step in the data cleaning process involved checking that survey responses collected for each participant were only included once in the data set." Why is this necessary?
 Without context this sentence is confusing.
+
+*XXX*
 
@@
 
-Page 11: Line 269 what’s the meaning of the levels of Figure Eight participants?
+*XXX*
+
+Page 11: Line 269 what's the meaning of the levels of Figure Eight participants?
+
+*XXX*
 
@@
 It would be interesting to see results under control of socio demographics.
-A second model including those variables could give some hints (direct effects, reduction intra-participant variance).  For reference see: (Vanderplas & Hofmann, 2016)
+A second model including those variables could give some hints (direct effects, reduction intra-participant variance).
+For reference see: (Vanderplas & Hofmann, 2016)
+
+*XXX*
 
@@
 
-Page 14: The section “Reason” is extremely short and might be merged with section 4.3 (Speed) on page 14.
+*XXX*
+
+Page 14: The section "Reason" is extremely short and might be merged with section 4.3 (Speed) on page 14.
+
+*XXX*
 
 There is no reference to table 3 on page 22 in the text.
+
+*Fixed.*
 
@@
 https://doi.org/10.1109/TVCG.2015.2469125
+
+*XXX*

### 2025-07-09 paper/kobakian-cook-anzjs.qmd
still to finish conclusion and working on the reason summary

@@
 ---
-title: "Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics"
+title: "Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Patterns in Australian Spatial Statistics"
 format:
@@
             address: 29 Ancora Imparo Way, Clayton, VIC 3800, Australia
-keywords: ["statistics", "visual inference", "geospatial", "population"]
+keywords: ["data visualisation", "visual inference", "geospatial", "statistical graphics"]
 abstract: |
@@
 library(cowplot)
+library(ggbeeswarm)
 library(png)
@@
 library(lme4)
+library(cartogram)
+library(sugarbag)
+library(sf)
+library(ggmosaic)
+library(emmeans)
 library(ggthemes)
@@
 ```{r makethyroidplots}
-library(cartogram)
-library(sugarbag)
-library(sf)
-
 # Spatial polygons files sourced from: https://github.com/wfmackey/absmapsdata
@@
 A lineup embeds the data plot among a field of null data plots, and an independent observer is asked to select the most different plot.
-It was shown by @VVSIALM to be an effective way to conduct a hypothesis test where a plot is treated as a test statistic.
-If the data plot is selected it is analogous to a rejection of the null hypothesis (no structure), and the observed data plot is unlikely to arise from the null scenario.
+It was shown by @VVSIALM to be an effective way to conduct a hypothesis test where a plot is treated as a test statistic, and utilised for this purpose in numerous studies [@FFS;@Green2021;@LCTV].
+If the data plot is selected it is analogous to a rejection of the null hypothesis (specifying no structure), and the observed data plot is unlikely to arise from the null scenario.
+The work of @VH2016 compares the lineup protocol to performance on statndard tests of visual ability, concluding that participants' performance is related to general visual aptitude, to classification rather than spatial reasoning.
 
@@
 The changes to the boundaries result in cartograms that accurately communicate population by map area for each of the geographic units but can result in losing the familiar geographic information.
-For Australia, the transformations warp the country so that it is no longer recognizable.
+For Australia, the transformations warp the country so that it is no longer recognisable (see @KCR for details).
 
@@
 The algorithm is available in the R package, sugarbag [@sugarbag].
-@fig-thyroid b shows the hexagon tile map, where the map is coloured from substantially below average (blue) to substantially above average (red) rates.
+@fig-thyroid b shows the hexagon tile map, where the map is coloured from low (blue) to high (red).
 The inner city areas have expanded, making it possible to see the cancer incidence in the small, densely populated areas.
@@
 The procedures for doing a power comparison of competing plot designed, outlined in @GTPCCD, are followed.
+It is the only current human subjects testing protocol which quantitatively compares plot designs on the basis of detection of structure relative to null distributions [@VCH;@VanderPlas2021Designing].
+The premise for comparing two designs is that the only difference between the two lineups is the plot design, and hence difference in detection rate and time to detect is due to the effectiveness of the plot design for differentiating between data plot and null plots.
+The protocol has been used in  to quantitatively test plot designs numerous studies [e.g.
+@LHC;@VH2016;@KTV;@RS2021].
 
@@
 
+There are several practical considerations when deploying the lineup protocol: (1) determining the appropriate null distribution to compute null samples, (2) employing independent observers to conduct the evaluations, (3) varying location of the data plot in a lineup, (4) how many null sets to include in the lineup, (5) construction of all lineups in the experiment (see @VRCH), (6) questions presented to participants to solicit evaluations, in addition to the usual experimental design issues.
+These are described in detail in the next section.
+
 # Methodology {#sec-methodology}
@@
 
-  - Map type: *choropleth, hexagon tile*
-  - Trend: *South-East to North-West; Locations in three population centres; Locations in multiple population centres, *
+  - Map type: *Choropleth, Hexagon tile*
+  - Trend:
+
+      - *NW-SE*: Large spatial trend running diagonally across Australia
+      - *Three Cities*: Locations in three population centres
+      - *All Cities*: Locations in all state and territory capitals
 
@@
 The R package `gstat` [@gstat] was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.
-Each null set was further processed to produce maps with similar spatial dependence as those produced by the methods in @atlas-methods, by averaging a small number of spatial neighbours.
+Simulating spatial dependence is difficult as discussed by @BDMSTW as a blockage for using the lineup protocol for testing map displays.
+Because the result from `gstat` was inadequate to mirror the spatial dependence patterns results in the @atlas, each null set was further smoothed.
+This was done by averaging a small number of spatial neighbours, approximating the methods described in @atlas-methods.
 
@@
 
-One of the lineup locations was chosen to embed the real trend model map, in each of the four replicates, for the three trend models.
-The locations were chosen by random sampling.
+One of the plot locations (1-20) is chosen to embed the data plot, in each of the four replicates, for the three trend models.
+These locations were chosen by random sampling.
 Using random locations reduces the chance that participants might inducing the location coincidentally.
 Locations 1, 7, 10 and 11 were not in the sample.
+@YMCCSG used the lineup protocol for a genomics study and similarly varied the the location of the data plot in replicates of treatments.
+Their results demonstrated that the actual location of the data plot didn't affect performance.
+So we don't expect that the location affects results but randomising locations among different lineups is to guard against participants expecting the data plot to be in a particular location.
 
 The lineup locations were the same for both map types, because each set of lineup data was used to produce a choropleth map lineup and hexagon tile map lineup.
+This ensures that performance on the two map types can be directly compared.
 Lineups were grouped into A or B, so that a participant saw only one version.
@@
 This resulted in Tasmania being coloured completely red.
-
-For the population related displays, the clusters in the cities appeared more red than the rest of Australia.
+For the other two trend types, clusters localised in the cities appeared more red than the rest of Australia.
 
@@
 
-Each participant used the internet to access the survey.
-The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results.
+Each participant used the internet to access the survey, and data was transferred by secure link from the web app to a Google sheet using the `googlesheets` package tools [@sheets].
+<!-- The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results.
 The application connected to the googlesheet using the googlesheets [@sheets] R package when participants opened the application, and interacted again when participants chose to submit the survey.
-At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.
+At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.-->
 
@@
 The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results.
-Potential participants needed to have achieved level 2 or level 3 from prior work on the platform.
+Potential participants needed to have achieved level 2 or level 3 from prior work on the platform, ensuring only participants with a good record on prior tasks could provide evaluations.
 All participants were at least 18 years old.
@@
 
-Basic descriptive statistics were used to contrast the detection rate for the two types of displays.
-Comparison was also made across the trend models, contrasting the mean and standard detection rate for each group, who had seen the different map display type for each replicate.
-
-Side-by-side dot plots were made of accuracy (efficiency) against map type, faceted by trend model type.
-
-Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.
+Basic descriptive statistics were computed for the different experimental treatments.
+Basic plots summarising detection rates by map type and trend model type, and feedback and demographic variables against the different experimental design elements.
+
+<!-- Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.-->
 
@@
 The certainty and reasons of subjects in their answers is also examined.
-
-## Participant demographics
-
-Of the `r n_contributors` participants, `r n_gender$n[1]` were male, and `r n_gender$n[2]` female.
-Most participants (`r n_educ$n[1]`) had a Bachelors degree, `r n_educ$n[3]` had a Masters degree, and the remaining `r n_educ$n[2]` had high school diplomas.
-The age distribution was `r paste(n_age$n[1:5], collapse=", ")` for age groups 18-24, 25-34, 35-44, 45-54, 55+, with `r n_age$n[6]` preferring not to answer.
-Only `r n_aus$n[2]` reported having lived in Australia.
 
@@
 
-@tbl-desc-stats shows the means and standard deviations of the detection rate for each type of plot and each trend model.
+<!-- @tbl-desc-stats shows the means and standard deviations of the detection rate for each type of plot and each trend model.
 This also gives the standard deviations, the smallest standard deviation for all sets of replicates was the Three Cities trend model shown in a Choropleth display.
@@
 The North-West to South-East (NW-SE) trend model unexpectedly had a higher mean detection rate for the hexagon tile map displays, but the difference in the means of detection rate was only 0.10.
+-->
 
 ```{r}
+#| eval: false
 #| label: tbl-desc-stats
@@
 
-@tbl-detect-glmer1 presents a summary of the generalised linear mixed effects model, testing the effect of map type and trend model on the detection rate.
-The results support the summary from @fig-detect-compare and all parameters are statistically significant despite the large standard deviations observed in @tbl-desc-stats.
-Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise.
-Allowing for the interaction effect, the difference in detection rate decreases for population related displays for a choropleth map lineup, but increases for a hexagon tile map display.
-The log odds of detection show in @tbl-detect-glmer1 can be back transformed after taking the sum of all terms for the trend and type of display that are of interest.
-For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to `r round(exp(0.46+0.07)/(1+exp(0.46+0.07)), 2)` from `r round(exp(0.07)/(1+exp(0.07)),2)` for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level.
-
-When a choropleth map display is used, the predicted detection rate for the Three Cities trend, `r round(exp(0.07-3.41)/(1+exp(0.07-3.41)),2)` is extremely low, especially compared to the NW-SE trend of `r round(exp(0.07)/(1+exp(0.07)),2)`.
-When the All Cities trend is presented in a choropleth display the predicted probability of detection is `r round(exp(0.07-1.34)/(1+exp(0.07-1.34)),2)`.
-The hexagon tile map has a substantially high detection rate for the display of a Three Cities trend `r round(exp(0.46+0.07-3.41+2.44)/(1+exp(0.46+0.07-3.41+2.44)),2)` and All Cities trend `r round(exp(0.46+0.07-1.34+1.16)/(1+exp(0.46+0.07-1.34+1.16)),2)`.
-
 ```{r}
@@
 # Mixed effects models
-glmer1 <- glmer(detect ~ type*trend + (1|contributor), 
+detect_fit <- glmer(detect ~ type*trend + (1|contributor), 
               family = binomial, data = d)
@@
 
-detection_rates <- tidy(glmer1) %>%
+detection_rates <- tidy(detect_fit) %>%
   mutate(detection_rates = round(exp(estimate)/(1+exp(estimate)),2)) %>%
@@
 
-tidy(glmer1) %>%
+detect_fit_smry <- summary(detect_fit)
+
+tidy(detect_fit) %>%
   mutate_at(.vars = c("estimate", "std.error"), round, 2) %>% 
@@
 
+```{r}
+#| label: tbl-detect-prop
+#| tbl-cap: "Model estimates for the proportion of detection in each of the trend models (standard error). Note that selecting the data plot by chance would produce a detection rate of 0.05."
+# Proportions of detections, estimated from model
+detect_props <- emmeans(detect_fit, specs = ~ type*trend, type = "response") |>
+  as_tibble() |>
+  select(type, trend, prob, SE) |>
+  pivot_wider(names_from = trend, values_from = c(prob, SE)) |>
+  pivot_longer(cols = `prob_All Cities`:`SE_NW-SE`, 
+               names_to = "stat", values_to = "value") |>
+  separate(stat, into = c("prop", "trend"), sep="_") |>
+  pivot_wider(names_from = trend, values_from = value) 
+detect_props <- detect_props |>
+  mutate(`All Cities` = as.character(round(`All Cities`, 2)),
+         `Three Cities` = as.character(round(`Three Cities`, 2)),
+         `NW-SE` = as.character(round(`NW-SE`, 2))) |>
+  mutate(type = as.character(type))
+detect_props[2,1] <- ""
+detect_props[4,1] <- ""
+detect_props[2, 3] <- paste0("(", detect_props[2, 3], ")")
+detect_props[4, 3] <- paste0("(", detect_props[4, 3], ")")
+detect_props[2, 4] <- paste0("(", detect_props[2, 4], ")")
+detect_props[4, 4] <- paste0("(", detect_props[4, 4], ")")
+detect_props[2, 5] <- paste0("(", detect_props[2, 5], ")")
+detect_props[4, 5] <- paste0("(", detect_props[4, 5], ")")
+detect_props |>
+  select(type, `All Cities`, 
+                  `Three Cities`, `NW-SE`) |>
+  knitr::kable(format = "latex", escape = FALSE, align= "lccc", 
+    booktabs = T, 
+    col.names = c("Map type", "All Cities", 
+                  "Three Cities", "NW-SE"), 
+    linesep = c("", "\\addlinespace", "", "\\addlinespace", ""))
+```
+
+@tbl-detect-glmer1 presents a summary of the generalised linear mixed effects model, testing the effect of map type and trend model on the detection rate.
+The results support the summary from @fig-detect-compare.
+Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, and with differing magnitudes of effects.
+The subject-specific random intercepts have mean `r round(detect_fit_smry$varcor$contributor[[1]], 2)` and standard devation `r round(attr(detect_fit_smry$varcor$contributor, "stddev")[[1]], 2)`.
+
+The estimated detection proportion from the model fit, computed using the `emmeans` package [@Lenth2025] are shown in @tbl-detect-prop.
+For the All Cities trend participants were about three times more likely to detect the cluster pattern with the hexagon tile map than the choropleth.
+The Three Cities trend was practically not detectable in the choropleth map.
+The dection rates were more similar for the NW-SE trend, but slightly higher for the hexagon tile map, which was a surprise.
+Note that, these detection rates are all substantially higher than chance, except for the choropleth map on the Three Cities.
+For a single evaluation the detection rate of the data plot selected by chance is $1/20=0.05$ because the lineups used in this experiment had 20 plots.
+When designing an experiment like this it is important to produce lineups that strike a balance between simple and hard, so that there is a chance of discovering the effect of interest.
+This experiment has managed to do this extremely well, which is a result of pilot studies, careful null data generation, and power calculations to determine appropriate sample size.
+
 ## Speed
@@
             q3=quantile(time_taken, 0.75))
-library(ggbeeswarm)
 ggplot() + 
@@
   theme(legend.position="none")
+```
+
+```{r}
+#| eval: false
+# Check groups and demographics
+d %>% group_by(group) %>%   
+  summarise(m=mean(time_taken), 
+            s=sd(time_taken))
+d %>% group_by(gender) %>%   
+  summarise(m=mean(time_taken), 
+            s=sd(time_taken))
+d %>% group_by(age) %>%   
+  summarise(m=mean(time_taken), 
+            s=sd(time_taken))
+d %>% group_by(education) %>%   
+  summarise(m=mean(time_taken), 
+            s=sd(time_taken))
+
+# Check time difference between default choice
+d %>% mutate(zeros = if_else(choice == 0, 0, 1)) %>%
+  group_by(zeros) %>%   
+  summarise(m=median(time_taken), 
+            mn=min(time_taken),
+            mx=max(time_taken),
+            q1=quantile(time_taken, 0.25), 
+            q3=quantile(time_taken, 0.75),
+            n=n())
+
+d %>% mutate(zeros = if_else(choice == 0, 0, 1)) %>%
+  group_by(zeros, detect_f) %>%   
+  summarise(m=median(time_taken), 
+            mn=min(time_taken),
+            mx=max(time_taken),
+            q1=quantile(time_taken, 0.25), 
+            q3=quantile(time_taken, 0.75),
+            n=n())
+
+# Summarise across subjects
+contributor_smry <- d %>% group_by(contributor) %>%   
+  summarise(m_d=mean(detect), 
+            s_d=sd(detect),
+            m_t=mean(time_taken), 
+            s_t=sd(time_taken)) 
+ggplot(contributor_smry, aes(m_t, m_d)) +
+  geom_point() +
+  ylab("Detection rate") +
+  xlab("Time taken") +
+  xlim(c(0, 45)) +
+  theme(aspect.ratio = 1)
+ggplot(contributor_smry, aes(m_t, s_t)) +
+  geom_point() +
+  xlab("Average") +
+  ylab("SD") +
+  theme(aspect.ratio = 1)
+ggplot(contributor_smry, aes(m_d, s_d)) +
+  geom_point() +
+  xlab("Average") +
+  ylab("SD") +
+  theme(aspect.ratio = 1)
 ```
@@
 # devtools::install_github("haleyjeppson/ggmosaic")
-library(ggmosaic)
 d |> 
@@
 #| label: tbl-reason
-#| tbl-cap: "The main reason that participants wrote for their choice of plot when looking at each trend model shown in choropleth and hexagon tile maps."
+#| tbl-cap: "Summary of the reasons that participants wrote for their choice of plot when looking at each trend model shown in choropleth and hexagon tile maps."
 # Qualitative analysis of reason
-d %>% 
+reasons_smry <- d %>% 
   mutate(reason = ifelse(reason =="0.0", "no reason", reason)) %>% 
@@
   count(reason) %>%
-  mutate(prop = round(n/sum(n), 2), r_prop = paste0(reason, ":", prop)) %>% 
-  top_n(1, n) %>% summarise(reasons = paste(reason, collapse=", ")) %>% 
-  pivot_wider(names_from = c("type"), values_from = c("reasons")) %>% 
-  ungroup() %>% 
-  knitr::kable(., format = "latex", booktabs = TRUE,
+  mutate(prop = round(n/sum(n), 2)) %>% 
+  pivot_wider(names_from = reason, 
+              values_from = prop, 
+              values_fill = 0)
+
+#  mutate(prop = round(n/sum(n), 2), r_prop = paste0(reason, ":", prop)) %>% 
+#  top_n(1, n) %>% summarise(reasons = paste(reason, collapse=", ")) %>% 
+#  pivot_wider(names_from = c("type"), values_from = c("reasons")) %>% 
+#  ungroup() %>% 
+reasons_smry |>  
+  knitr::kable(format = "latex", booktabs = TRUE,
     linesep = c("", "\\addlinespace", "", "\\addlinespace","")) %>% 
@@
 ```
+
+## Participant demographics
+
+Of the `r n_contributors` participants, `r n_gender$n[1]` were male, and `r n_gender$n[2]` female.
+Most participants (`r n_educ$n[1]`) had a Bachelors degree, `r n_educ$n[3]` had a Masters degree, and the remaining `r n_educ$n[2]` had high school diplomas.
+The age distribution was `r paste(n_age$n[1:5], collapse=", ")` for age groups 18-24, 25-34, 35-44, 45-54, 55+, with `r n_age$n[6]` preferring not to answer.
+Only `r n_aus$n[2]` reported having lived in Australia.
+Note that, the purpose of reporting these numbers is to illustrate the reasonable variety of demographic background of participants.
+However, $n=$`r n_contributors` is insufficient fit a model including this demographic information.
+@MHC (published in 2025 but conducted in 2012) showed that there is little difference in performance on lineup experiments between demographic groups.
+@VH2016 found that visual aptitude for reading data plots was associated with math skills, but this study was done on statistical plots of data, not maps.
+Assessing math ability requires substantially more data collection, and does not necessarily correlate with education level.
+
+Summary statistics (not included here, but available in the analysis code) show no differences in results between sets A and B in detection rate or time taken.
+Similarly, detection rates and time taken vary little across age, education and gender.
 
@@
 
-The differences seen in the @fig-detect-compare plot and @tbl-desc-stats are reflected in the model results.
-Surprisingly the difference for the geographic distribution was significant at the 0.05 level.
+The differences seen in the @fig-detect-compare plot.
+Surprisingly the difference between map types for the geographic distribution was significant at the 0.05 level, even though the effect difference is small.
 It also showed that the hexagon tile map display performs marginally better than the choropleth for all trend models.
-Unexpectedly the detection rate suffers when using a choropleth map to display population related distributions.
 
@@
 The spatial distributions used to test these displays were inspired by the real spatially smoothed estimates of the cancer burden on Australian communities.
-However, this technique may be extended to other population related distributions, such as other diseases.
+However, this technique may be extended to other population related distributions, such as other diseases, or election results or socioeconomic indicators.
 
@@
 
-Add Election results data + plus other statistics, other hexagon layout software
+- Add Election results data + plus other statistics, 
+- new and better hexagon layout software 
+- Other plot/map type comparisons, insets, cartograms, statistical plots along with maps, especially interactive
+- eye-tracking in association with lineups
 

### 2025-07-09 paper/kobakian-cook-anzjs.tex
still to finish conclusion and working on the reason summary

@@
 \hypersetup{
-  pdftitle={Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics},
+  pdftitle={Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Patterns in Australian Spatial Statistics},
   pdfauthor={Stephanie Kobakian; Dianne Cook},
-  pdfkeywords={statistics, visual inference, geospatial, population},
+  pdfkeywords={data visualisation, visual
+inference, geospatial, statistical graphics},
   colorlinks=true,
@@
 \title{Comparing the Effectiveness of the Choropleth Map with a Hexagon
-Tile Map for Communicating Cancer Statistics}
+Tile Map for Communicating Patterns in Australian Spatial Statistics}
 
@@
 
-\keywords{statistics; visual inference; geospatial; population}
+\keywords{data visualisation; visual inference; geospatial; statistical
+graphics}
 
@@
 shown by \citet{VVSIALM} to be an effective way to conduct a hypothesis
-test where a plot is treated as a test statistic. If the data plot is
-selected it is analogous to a rejection of the null hypothesis (no
-structure), and the observed data plot is unlikely to arise from the
-null scenario.
+test where a plot is treated as a test statistic, and utilised for this
+purpose in numerous studies \citep{FFS, Green2021, LCTV}. If the data
+plot is selected it is analogous to a rejection of the null hypothesis
+(specifying no structure), and the observed data plot is unlikely to
+arise from the null scenario. The work of \citet{VH2016} compares the
+lineup protocol to performance on statndard tests of visual ability,
+concluding that participants' performance is related to general visual
+aptitude, to classification rather than spatial reasoning.
 
@@
 in losing the familiar geographic information. For Australia, the
-transformations warp the country so that it is no longer recognizable.
+transformations warp the country so that it is no longer recognisable
+(see \citet{KCR} for details).
 
@@
 R package, sugarbag \citep{sugarbag}. Figure~\ref{fig-thyroid} b shows
-the hexagon tile map, where the map is coloured from substantially below
-average (blue) to substantially above average (red) rates. The inner
-city areas have expanded, making it possible to see the cancer incidence
-in the small, densely populated areas. Remote regions are represented by
-isolated hexagons, which is not ideal, but maintains the spatial
-location of these data values. It is of interest to know how well the
-spatial distribution patterns are seen from this display, in comparison
-to how they are seen from the choropleth.
+the hexagon tile map, where the map is coloured from low (blue) to high
+(red). The inner city areas have expanded, making it possible to see the
+cancer incidence in the small, densely populated areas. Remote regions
+are represented by isolated hexagons, which is not ideal, but maintains
+the spatial location of these data values. It is of interest to know how
+well the spatial distribution patterns are seen from this display, in
+comparison to how they are seen from the choropleth.
 
@@
 procedures for doing a power comparison of competing plot designed,
-outlined in \citet{GTPCCD}, are followed.
+outlined in \citet{GTPCCD}, are followed. It is the only current human
+subjects testing protocol which quantitatively compares plot designs on
+the basis of detection of structure relative to null distributions
+\citep{VCH, VanderPlas2021Designing}. The premise for comparing two
+designs is that the only difference between the two lineups is the plot
+design, and hence difference in detection rate and time to detect is due
+to the effectiveness of the plot design for differentiating between data
+plot and null plots. The protocol has been used in to quantitatively
+test plot designs numerous studies
+\citep[e.g.][]{LHC, VH2016, KTV, RS2021}.
 
@@
 
+There are several practical considerations when deploying the lineup
+protocol: (1) determining the appropriate null distribution to compute
+null samples, (2) employing independent observers to conduct the
+evaluations, (3) varying location of the data plot in a lineup, (4) how
+many null sets to include in the lineup, (5) construction of all lineups
+in the experiment (see \citet{VRCH}), (6) questions presented to
+participants to solicit evaluations, in addition to the usual
+experimental design issues. These are described in detail in the next
+section.
+
 \section{Methodology}\label{sec-methodology}
@@
 \begin{itemize}
+\item
+  Map type: \emph{Choropleth, Hexagon tile}
+\item
+  Trend:
+
+  \begin{itemize}
   \tightlist
   \item
-  Map type: \emph{choropleth, hexagon tile}
-\item
-  Trend: \emph{South-East to North-West; Locations in three population
-  centres; Locations in multiple population centres, }
+    \emph{NW-SE}: Large spatial trend running diagonally across
+    Australia
+  \item
+    \emph{Three Cities}: Locations in three population centres
+  \item
+    \emph{All Cities}: Locations in all state and territory capitals
+  \end{itemize}
 \end{itemize}
@@
 sets, 12 data sets for each plot in a lineup, and 12 sets for 12
-lineups. Each null set was further processed to produce maps with
-similar spatial dependence as those produced by the methods in
-\citet{atlas-methods}, by averaging a small number of spatial
-neighbours.
+lineups. Simulating spatial dependence is difficult as discussed by
+\citet{BDMSTW} as a blockage for using the lineup protocol for testing
+map displays. Because the result from \texttt{gstat} was inadequate to
+mirror the spatial dependence patterns results in the \citet{atlas},
+each null set was further smoothed. This was done by averaging a small
+number of spatial neighbours, approximating the methods described in
+\citet{atlas-methods}.
 
@@
 
-One of the lineup locations was chosen to embed the real trend model
-map, in each of the four replicates, for the three trend models. The
-locations were chosen by random sampling. Using random locations reduces
-the chance that participants might inducing the location coincidentally.
-Locations 1, 7, 10 and 11 were not in the sample.
+One of the plot locations (1-20) is chosen to embed the data plot, in
+each of the four replicates, for the three trend models. These locations
+were chosen by random sampling. Using random locations reduces the
+chance that participants might inducing the location coincidentally.
+Locations 1, 7, 10 and 11 were not in the sample. \citet{YMCCSG} used
+the lineup protocol for a genomics study and similarly varied the the
+location of the data plot in replicates of treatments. Their results
+demonstrated that the actual location of the data plot didn't affect
+performance. So we don't expect that the location affects results but
+randomising locations among different lineups is to guard against
+participants expecting the data plot to be in a particular location.
 
@@
 of lineup data was used to produce a choropleth map lineup and hexagon
-tile map lineup. Lineups were grouped into A or B, so that a participant
-saw only one version. Participants were assigned to group A or B,
-randomly, and thus evaluated either the choropleth or the hexagon tile
-map lineup. Because there were four replicates of each lineup, each
+tile map lineup. This ensures that performance on the two map types can
+be directly compared. Lineups were grouped into A or B, so that a
+participant saw only one version. Participants were assigned to group A
+or B, randomly, and thus evaluated either the choropleth or the hexagon
+tile map lineup. Because there were four replicates of each lineup, each
 participant evaluated two choropleth and two hexagon tile map lineups,
@@
 occurring in the South East. This resulted in Tasmania being coloured
-completely red.
-
-For the population related displays, the clusters in the cities appeared
-more red than the rest of Australia.
+completely red. For the other two trend types, clusters localised in the
+cities appeared more red than the rest of Australia.
 
@@
 
-Each participant used the internet to access the survey. The data
-transfer from the web application to the data set took place using a
-secure link to the googlesheet used to store results. The application
-connected to the googlesheet using the googlesheets \citep{sheets} R
-package when participants opened the application, and interacted again
-when participants chose to submit the survey. At this time it added the
-participant's responses to the twelve lineup displays as twelve rows of
-data in the googlesheet.
+Each participant used the internet to access the survey, and data was
+transferred by secure link from the web app to a Google sheet using the
+\texttt{googlesheets} package tools \citep{sheets}.
 
@@
 needed to have achieved level 2 or level 3 from prior work on the
-platform. All participants were at least 18 years old.
+platform, ensuring only participants with a good record on prior tasks
+could provide evaluations. All participants were at least 18 years old.
 
@@
 
-Basic descriptive statistics were used to contrast the detection rate
-for the two types of displays. Comparison was also made across the trend
-models, contrasting the mean and standard detection rate for each group,
-who had seen the different map display type for each replicate.
-
-Side-by-side dot plots were made of accuracy (efficiency) against map
-type, faceted by trend model type.
-
-Similar plots were made of the feedback and demographic variables -
-reason for choice, reported difficulty, gender, age, education, having
-lived in Australia - against the design variables.
+Basic descriptive statistics were computed for the different
+experimental treatments. Basic plots summarising detection rates by map
+type and trend model type, and feedback and demographic variables
+against the different experimental design elements.
 
@@
 certainty and reasons of subjects in their answers is also examined.
-
-\subsection{Participant demographics}\label{participant-demographics}
-
-Of the 90 participants, 66 were male, and 24 female. Most participants
-(55) had a Bachelors degree, 13 had a Masters degree, and the remaining
-22 had high school diplomas. The age distribution was 13, 36, 21, 11, 6
-for age groups 18-24, 25-34, 35-44, 45-54, 55+, with 3 preferring not to
-answer. Only 1 reported having lived in Australia.
 
@@
 
-Table~\ref{tbl-desc-stats} shows the means and standard deviations of
-the detection rate for each type of plot and each trend model. This also
-gives the standard deviations, the smallest standard deviation for all
-sets of replicates was the Three Cities trend model shown in a
-Choropleth display. This group of displays had a very small detection
-rate of 0.04. The mean detection rate for the Three Cities trend model
-shown as choropleth map lineups was also the smallest at 0.40. The
-North-West to South-East (NW-SE) trend model unexpectedly had a higher
-mean detection rate for the hexagon tile map displays, but the
-difference in the means of detection rate was only 0.10.
-
-\begin{table}
-
-\caption{\label{tbl-desc-stats}The mean and standard deviation of the
-rate of detection for each trend model, calculated for the choropleth
-and hexagon tile map displays.}
-
-\centering{
-
-\begin{tabular}{lccc}
-\toprule
-Type & NW-SE & Three Cities & All Cities\\
-\midrule
-Choro. & 0.52 & 0.04 & 0.23\\
- & (0.50) & (0.19) & (0.42)\\
-\addlinespace
-Hex. & 0.62 & 0.40 & 0.58\\
- & (0.49) & (0.49) & (0.49)\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{table}%
-
-Table~\ref{tbl-detect-glmer1} presents a summary of the generalised
-linear mixed effects model, testing the effect of map type and trend
-model on the detection rate. The results support the summary from
-Figure~\ref{fig-detect-compare} and all parameters are statistically
-significant despite the large standard deviations observed in
-Table~\ref{tbl-desc-stats}. Overall, the hexagon tile map performs
-marginally better than the choropleth for all trend models, which is a
-pleasant surprise. Allowing for the interaction effect, the difference
-in detection rate decreases for population related displays for a
-choropleth map lineup, but increases for a hexagon tile map display. The
-log odds of detection show in Table~\ref{tbl-detect-glmer1} can be back
-transformed after taking the sum of all terms for the trend and type of
-display that are of interest. For the NW-SE distribution, the predicted
-detection rate for the hexagon tile map display increases the predicted
-probability of detection to 0.63 from 0.52 for choropleths, this is
-almost exactly the difference seen in the table of means and is
-significant only at the 0.05 level.
-
-When a choropleth map display is used, the predicted detection rate for
-the Three Cities trend, 0.03 is extremely low, especially compared to
-the NW-SE trend of 0.52. When the All Cities trend is presented in a
-choropleth display the predicted probability of detection is 0.22. The
-hexagon tile map has a substantially high detection rate for the display
-of a Three Cities trend 0.39 and All Cities trend 0.59.
-
 \begin{table}
@@
 
+\begin{table}
+
+\caption{\label{tbl-detect-prop}Model estimates for the proportion of
+detection in each of the trend models (standard error). Note that
+selecting the data plot by chance would produce a detection rate of
+0.05.}
+
+\centering{
+
+\begin{tabular}{lccc}
+\toprule
+Map type & All Cities & Three Cities & NW-SE\\
+\midrule
+Choro. & 0.22 & 0.03 & 0.52\\
+ & (0.03) & (0.01) & (0.04)\\
+\addlinespace
+Hex. & 0.59 & 0.39 & 0.63\\
+ & (0.04) & (0.04) & (0.04)\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{table}%
+
+Table~\ref{tbl-detect-glmer1} presents a summary of the generalised
+linear mixed effects model, testing the effect of map type and trend
+model on the detection rate. The results support the summary from
+Figure~\ref{fig-detect-compare}. Overall, the hexagon tile map performs
+marginally better than the choropleth for all trend models, and with
+differing magnitudes of effects. The subject-specific random intercepts
+have mean 0.3 and standard devation 0.55.
+
+The estimated detection proportion from the model fit, computed using
+the \texttt{emmeans} package \citep{Lenth2025} are shown in
+Table~\ref{tbl-detect-prop}. For the All Cities trend participants were
+about three times more likely to detect the cluster pattern with the
+hexagon tile map than the choropleth. The Three Cities trend was
+practically not detectable in the choropleth map. The dection rates were
+more similar for the NW-SE trend, but slightly higher for the hexagon
+tile map, which was a surprise. Note that, these detection rates are all
+substantially higher than chance, except for the choropleth map on the
+Three Cities. For a single evaluation the detection rate of the data
+plot selected by chance is \(1/20=0.05\) because the lineups used in
+this experiment had 20 plots. When designing an experiment like this it
+is important to produce lineups that strike a balance between simple and
+hard, so that there is a chance of discovering the effect of interest.
+This experiment has managed to do this extremely well, which is a result
+of pilot studies, careful null data generation, and power calculations
+to determine appropriate sample size.
+
 \subsection{Speed}\label{speed}
@@
 
-\caption{\label{tbl-reason}The main reason that participants wrote for
-their choice of plot when looking at each trend model shown in
+\caption{\label{tbl-reason}Summary of the reasons that participants
+wrote for their choice of plot when looking at each trend model shown in
 choropleth and hexagon tile maps.}
@@
 
-\begin{tabular}{llll}
+\begin{tabular}{lllrrrrr}
 \toprule
-Trend & Detected & Choro. & Hex.\\
+Trend & Detected & type & clusters & consistent & hotspots & no reason & trend\\
 \midrule
- & No & trend & clusters\\
-\cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash All Cities} & Yes & clusters, consistent & clusters\\
-\cmidrule{1-4}
- & No & trend & clusters\\
-\cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash Three Cities} & Yes & consistent & clusters\\
-\cmidrule{1-4}
- & No & trend & clusters\\
-\cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash NW-SE} & Yes & trend & clusters\\
+ & No & Choro. & 50 & 12 & 11 & 9 & 56\\
+\cmidrule{2-8}
+ & No & Hex. & 27 & 6 & 5 & 15 & 22\\
+\cmidrule{2-8}
+ & Yes & Choro. & 14 & 14 & 3 & 4 & 7\\
+\cmidrule{2-8}
+\multirow{-4}{*}{\raggedright\arraybackslash All Cities} & Yes & Hex. & 44 & 4 & 14 & 8 & 35\\
+\cmidrule{1-8}
+ & No & Choro. & 54 & 12 & 17 & 16 & 74\\
+\cmidrule{2-8}
+ & No & Hex. & 42 & 6 & 11 & 15 & 34\\
+\cmidrule{2-8}
+ & Yes & Choro. & 1 & 4 & 0 & 0 & 2\\
+\cmidrule{2-8}
+\multirow{-4}{*}{\raggedright\arraybackslash Three Cities} & Yes & Hex. & 35 & 0 & 10 & 4 & 23\\
+\cmidrule{1-8}
+ & No & Choro. & 20 & 14 & 11 & 8 & 34\\
+\cmidrule{2-8}
+ & No & Hex. & 27 & 3 & 5 & 15 & 18\\
+\cmidrule{2-8}
+ & Yes & Choro. & 32 & 2 & 15 & 7 & 37\\
+\cmidrule{2-8}
+\multirow{-4}{*}{\raggedright\arraybackslash NW-SE} & Yes & Hex. & 56 & 12 & 6 & 6 & 32\\
 \bottomrule
@@
 \end{table}%
+
+\subsection{Participant demographics}\label{participant-demographics}
+
+Of the 90 participants, 66 were male, and 24 female. Most participants
+(55) had a Bachelors degree, 13 had a Masters degree, and the remaining
+22 had high school diplomas. The age distribution was 13, 36, 21, 11, 6
+for age groups 18-24, 25-34, 35-44, 45-54, 55+, with 3 preferring not to
+answer. Only 1 reported having lived in Australia. Note that, the
+purpose of reporting these numbers is to illustrate the reasonable
+variety of demographic background of participants. However, \$n=\$90 is
+insufficient fit a model including this demographic information.
+\citet{MHC} (published in 2025 but conducted in 2012) showed that there
+is little difference in performance on lineup experiments between
+demographic groups. \citet{VH2016} found that visual aptitude for
+reading data plots was associated with math skills, but this study was
+done on statistical plots of data, not maps. Assessing math ability
+requires substantially more data collection, and does not necessarily
+correlate with education level.
+
+Summary statistics (not included here, but available in the analysis
+code) show no differences in results between sets A and B in detection
+rate or time taken. Similarly, detection rates and time taken vary
+little across age, education and gender.
 
@@
 
-The differences seen in the Figure~\ref{fig-detect-compare} plot and
-Table~\ref{tbl-desc-stats} are reflected in the model results.
-Surprisingly the difference for the geographic distribution was
-significant at the 0.05 level. It also showed that the hexagon tile map
-display performs marginally better than the choropleth for all trend
-models. Unexpectedly the detection rate suffers when using a choropleth
-map to display population related distributions.
+The differences seen in the Figure~\ref{fig-detect-compare} plot.
+Surprisingly the difference between map types for the geographic
+distribution was significant at the 0.05 level, even though the effect
+difference is small. It also showed that the hexagon tile map display
+performs marginally better than the choropleth for all trend models.
 
@@
 communities. However, this technique may be extended to other population
-related distributions, such as other diseases.
+related distributions, such as other diseases, or election results or
+socioeconomic indicators.
 
@@
 
-Add Election results data + plus other statistics, other hexagon layout
-software
+\begin{itemize}
+\tightlist
+\item
+  Add Election results data + plus other statistics,
+\item
+  new and better hexagon layout software
+\item
+  Other plot/map type comparisons, insets, cartograms, statistical plots
+  along with maps, especially interactive
+\item
+  eye-tracking in association with lineups
+\end{itemize}
 

### 2025-07-09 paper/review1/ReponseToReviewers2025.qmd
still to finish conclusion and working on the reason summary

@@
 
+*Note that we have changed the title slightly to make it more general than cancer statistics, and we have added many more references in response to the review comments.
+This has made the paper longer by three pages.
+The revision has also been converted to a quarto document, which means that all numbers are automatically calculated from the analysis code in the document.*
+
 Comments to the Author:
@@
 I encourage the authors to respond to all the comments by the three reviewers in a substantive manner, and in doing so go through the manuscript with a very "fine pen" to ensure the writing and overall messaging is as clear as possible.
+
+*We are very sorry that the reviewers found the writing to be inadequate.
+We did not expect this!
+In this revision, we have tightened up the language substantially, provided additional references to support statements, and tidied the math and calculations.*
 
@@
 Considering these strengths, though, as I read the manuscript I found some areas in which I would have appreciated greater clarity.
-Starting with some major concerns, I’ll list my comments in order of appearance:
+Starting with some major concerns, I'll list my comments in order of appearance:
 
@@
 
-*XXX*
+*Added additional text.*
 
@@
 
-*XXX*
+*This has been revised.*
 
@@
 I would expect some discussion of these low results.
-Are these a result of the data simulation process (i.e., the “true” signal might not be different enough)?
+Are these a result of the data simulation process (i.e., the "true" signal might not be different enough)?
 How do the results compare to the expected detection rates if selected by chance, as discussed in Section 2.2?
 
-*XXX*
+*Sentence added to results explaining this.*
 
@@
 
-*XXX*
+*The model formulation has been revised.*
 
@@
 
-*XXX*
+*Done, in the text.*
 
@@
 
-I’m not sure if I understand that statement correctly.
+I'm not sure if I understand that statement correctly.
 In my understanding, the interaction in Table 2 shows that the difference between choropleth and hexagon tiles differs between trend models, but it’s in favor of the hexagon models among all trends (full effect for hexagon with NW-SE trend: 1.63; full effect for hexagon all cities trend: 1.63 + 1.34 -1.16 = 1.81; full effect for hexagon tree cities trend 1.63 – 2.07 + 1.28 = 0.84).
 
-Additionally, I can’t replicate the detection probabilities mentioned in the text, e.g., Page 13, Lines 333f.: "For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection
+*Statement on interactions is removed, because the summary of the model estimates shows the different effects between the different treatments.*
 
-to 0.63 from 0.52 for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level."
-
-*XXX*
+Additionally, I can't replicate the detection probabilities mentioned in the text, e.g., Page 13, Lines 333f.: "For the NW-SE distribution, the predicted detection rate for the hexagon tile map display increases the predicted probability of detection to 0.63 from 0.52 for choropleths, this is almost exactly the difference seen in the table of means and is significant only at the 0.05 level."
 
@@
 
-*XXX*
+*There were errors in the hand-coded numbers. All of these are now computed using the emmeans package now.*
 
@@
 
-*XXX*
+*The explanation of data cleaning has been revised to make it clearer. There is no difference in XXX*
 
@@
 
-*XXX*
+*Done.*
 
@@
 
-*XXX*
+*Language changed.*
 
@@
 
-*XXX*
+*Re-worded*
 
@@
 
-*XXX*
+*Explained.*
 
@@
 We expect it might be due to the large rural polygons might also play a role in obscuring large simple spatial trend, too.
-But we don't want to speculate.*
+We don't want to speculate.*
 
@@
 
-*XXX*
+*A reference to Majumder, Cook and Hofmann (2025) showing that demographic background has little effect on performance of participants reading lineups.
+The primary variation is individual.
+This study was actually done in 2012 but only just published.
+The Vanderplas paper reports on a different type of experiment where math ability is collected as part of a larger visual testing process, and the type of plots used were ones typically seen in statistics classes.
+Maps are a bit different from this.
+Anyway, we did not collect enough data to fit demographics, because it is not the main purpose of this experiment.
+Majumder et al suggests that as long as a suitable range of backgrounds is included in the study results are reliable and replicable.
+This has been explained in the text.*
 
@@
 
-*XXX*
+*We disagree with this comment.
+Replicates are indicated by line segments.
+The primary factor, map type, is represented by a point, with paired measurements (replicates) connected by lines.
+This maps the primary information to position along a common axis, which is best graphical practice.
+Colour redundant with the facets draws attention to the secondary key element of the design, the different types of spatial patterns, and makes the plot more interesting to read.*
 
@@
 
-*XXX*
+*We have kept is separate for clarity. Speed is qute different from reason.*
 
@@
 
-*XXX*
+*Thank you for the suggestions.
+The Kawakami reference is out of scope.
+The Vanderplas et al has been included in the Introduction to point to work on how ability to read a lineup it most related to a subject's visual aptitude.
+Many more references to the visual inference literature have been added.*

### 2025-07-09 paper/kobakian-cook-anzjs.qmd
done with all - needs a careful read and references cleaned up

@@
 A similar approach was pioneered by @RSCW, using rectangles that tile to align borders of neighbours [@CDWCS].
-There have been thorough reviews of the array of methods, as suitable for cancer atlas displays [@review;@BCM].
+There have been thorough reviews of the array of methods, as suitable for cancer atlas displays [e.g.
+@KCR;@BCM], and experiments demonstrating cartograms to be more effective than choropleth maps [@KFIF].
 
@@
  - **Reason**: one of "Clusters of colour", "Colour trend across the areas", "Big differences between neighbouring areas", "All areas have similar colours" or "None of these reasons".
+Note providing restricted list of reasons rather than free text encourages a response because it is easy.
+The list needs to contain the primary expected reasons and other potential reasons need to be added so that it does not bias the participants' behaviour.
  - **Certainty**: how certain that their choice is different from the others, on a scale of 1-5.
@@
 
-## Speed
-
-@fig-beeswarm shows horizontally jittered dot plots to contrast the time taken by participants to evaluate each lineup when viewing each type of display.
-The time are also separated by trend model and whether the data plot was detected or not detected.
-The time taken to complete an evaluation ranged from milliseconds to 60 seconds.
-The average time taken for type of display is shown as a large coloured dot on each plot.
-When considering the heights of the green and orange dots, there is little difference in the average time taken to read a choropleth or hexagon tile map.
-Comparing the same coloured dot across each trend model row, there is a slight increase in the time taken to correctly detected the data plot in the hexagon tile map lineup, but little difference in evaluation time for the choropleth display.
-However, there were substantially less correct detections for choropleth lineups for the Three cities and All Cities trends.
-
 ```{r}
@@
 
-## Certainty
-
-Participants provided their level of certainty regarding their choice using a five point scale.
-Unlike the accuracy and speed of responses that were derived during the data processing phase, this was a subjective assessment by the participant prompted by the question: "How certain are you about your choice?".
-@fig-certainty shows a mosaic plot summarising how participants reported their certainty with their decision.
-The plots are made separately for each combination of trend models and whether the data plot was detected or not.
-Colour indicates the type of map display.
-The proportion of subjects evaluating the choropleth version increases as certainty increases, which suggests overconfidence in their detection ability when using a choropleth map display.
-Participants were less likely to be certain when their choice was incorrect and they were viewing a hexagon tile map.
+## Speed
+
+@fig-beeswarm shows horizontally jittered dot plots to contrast the time taken by participants to evaluate each lineup when viewing each type of display.
+The time are also separated by trend model and whether the data plot was detected or not detected.
+The time taken to complete an evaluation ranged from milliseconds to 60 seconds.
+The average time taken for type of display is shown as a large coloured dot on each plot.
+When considering the heights of the green and orange dots, there is little difference in the average time taken to read a choropleth or hexagon tile map.
+Comparing the same coloured dot across each trend model row, there is a slight increase in the time taken to correctly detected the data plot in the hexagon tile map lineup, but little difference in evaluation time for the choropleth display.
+However, there were substantially less correct detections for choropleth lineups for the Three cities and All Cities trends.
 
@@
 
+## Certainty
+
+Participants provided their level of certainty regarding their choice using a five point scale.
+Unlike the accuracy and speed of responses that were derived during the data processing phase, this was a subjective assessment by the participant prompted by the question: "How certain are you about your choice?".
+@fig-certainty shows a mosaic plot summarising how participants reported their certainty with their decision.
+The plots are made separately for each combination of trend models and whether the data plot was detected or not.
+Colour indicates the type of map display.
+The proportion of subjects evaluating the choropleth version increases as certainty increases, which suggests overconfidence in their detection ability when using a choropleth map display.
+Participants were less likely to be certain when their choice was incorrect and they were viewing a hexagon tile map.
+
 ## Reason
 
-Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons. 
+@tbl-reason summarises the reasons that participants gave for their choices: "clusters" = "Clusters of colour", "trend" = "Colour trend across the areas", "consistent" = "All areas have similar colours", "hotpots" = "Big differences between neighbouring areas", "none" = "None of these reasons".
+These proportions are computed separately for each trend, map type and whether the participant detected the data plot.
+With All Cities and Three Cities, when correct, participants tended to select 'consistent' with the choropleth, and 'clusters' with the hexagon tile map.
+With the NW-SE trend, 'trend' was primarily selected for the choropleth, but 'clusters' was the primary reason for the hexgon tile map.
+The primary reasons are similar when the participant did not detect the data plot.
+
+The results when the data plot was detected are as expected, but that they are similar to the not detected group is interesting.
+It suggests that with the choropleth people are trying to read contiguous patterns, while the hexagon tile map is being read for pockets of differences.
+This may be due the hexagon tile map being non-contiguous.
+
+<!--Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons. 
 "Colour trend across the areas" was the most common selection for NW-SE trend displays (@tbl-reason).
@@
 
-The choice "None of these reasons" was used as the default value to minimise noise from participants who did not select a response.
+The choice "None of these reasons" was used as the default value to minimise noise from participants who did not select a response. -->
 
@@
 #| label: tbl-reason
-#| tbl-cap: "Summary of the reasons that participants wrote for their choice of plot when looking at each trend model shown in choropleth and hexagon tile maps."
+#| tbl-cap: "Proportion of participants chose each reason for their choice of plot, computed separately for each Trend and Map Type level, and whether the data plot was detected.
+The primary reason when participants were evaluating the choropleth map was 'consistent' or 'trend', but for the hexagon tile map it was 'clusters', when they detected the data plot."
 # Qualitative analysis of reason
@@
   count(reason) %>%
-  mutate(prop = round(n/sum(n), 2)) %>% 
+  ungroup() %>%
+  group_by(Trend, Detected, type) %>%
+  mutate(prop = n/sum(n)) %>% 
+  ungroup() %>%
+  select(Trend, Detected, type, reason, prop) %>%
+  mutate(prop = round(prop, 2)) %>%
   pivot_wider(names_from = reason, 
               values_from = prop, 
-              values_fill = 0)
+              values_fill = 0) %>%
+  select(Trend, Detected, type, clusters, trend, consistent, hotspots, `no reason`)
 
@@
 reasons_smry |>  
+  arrange(desc(Detected), Trend, type) |>
   knitr::kable(format = "latex", booktabs = TRUE,
-    linesep = c("", "\\addlinespace", "", "\\addlinespace","")) %>% 
+               col.names = c("Trend", "Detect", "Type", 
+                             "clusters", "trend", "consistent",
+                             "hotspots", "none"),
+                 align = "lllrrrrr",
+    linesep = c("", "\\addlinespace", "", "\\addlinespace","", "\\addlinespace","", "\\addlinespace","", "\\addlinespace","")) #%>% 
   #kable_styling(bootstrap_options = "hold_position") %>% 
-  collapse_rows(., columns = 1)
+  #collapse_rows(., columns = 1)
 ```
@@
 
-The intention of this study was to contrast the use of the choropleth map and the hexagon tile map.
-The visual inference lineup protocol was employed to contrast the effectiveness of the displays.
+This study provides evidence that the hexagon tile map is superior to a choropleth map for communicating population statistics, for Australia.
+While the cartogram has been established as better than a choropleth map, cartograms do not work for the vast disparity between population density and geographic area in Australia.
+The hexagon tile map was developed to provide a possible solution, and this study demonstrates that it has potential.
+
+The R package `sugarbag` can be used to generate a hexagon tile map. It can be used for any spatial polygon data, so is applicable to other countries or geographic areas.
+
+One of the strengths but weaknesses of the hexagon tile map is that it is non-contiguous.
+Large rural areas are represented by isolated hexagons.
+This is why we expected that the hexagon tile map might not work well to detect large-scale spatial trend ("NW-SE").
+The primary reason for producing the non-contiguous display was to preserve geography sufficiently for the reader to easily recognise the location.
+This is a strength, and allows a map of the country to be drawn underneath the hexagons.
+It appears to not inhibit reading of the spatial distribution based on this experiment.
+However, there is considerable room for improving the algorithm and exploring some variations.
+These might include increasing the size of isolated hexagons, or collecting multiple hexagons together.
+
+The manner in which hexagons are exploded out from the city centres is another direction of research.
+Ideally, the location of the hexagons should be close to their original location but this is hard to control and measure.
+The current algorithm works sequentially to place hexagons, radially from a provided centre.
+There are likely better optimisation procedures that could impve the layout.
+For reading the spatial distribution, this is less important, but if the hexagon tile map is provided to users as an interactive tool, they will want to locate themselves in the plot.
+If the hexagon is not close to the true location it could be disconcerting.
+
+Hexagon displays are growing in popularity.
+Two media outlets used variations of the hexagon displays to communicate the 2025 Australian federal election results [@abc-election2025;guardian-election2025].
+Both are effective, but have inadequacies.
+The Guardian preserves geography and allows inner city results to be seen but the overall sense of the result is skewed because the large rural areas dominate the display.
+The ABC's contiguous hexagon tile map gives the correct sense of the final results but loses the shape of Australia, and some hexagons are far from their true location.
+
+This experiment focused on comparing a new display, the hexagon tile map, against the standard display, choropleth.
+There are other options that could have been included in the study, such as the use of insets of dense population areas along with the chorpleth map, or the use of interactive graphics linking statistical charts with the choropleth.
+Keeping the scope of the study small was important to understand whether it was reasonable to recommend use of the hexagon tile map.
+Although we only tested on the Australian geography, the results should hold for other regions that have similarly disparities between population size and geographic size.
+
+We would recommend doing follow-up studies that allow deeper understanding of how the different displays are read.
+For example, to understand the differences in how people read the choropleth map and the hexagon tile map as indicated by the different reasons given, could be done using an eyetracking experiment.
+@ZCHMR is an example of such an experiment where the manner in which people read lineups was examined.
+
+<!--The visual inference lineup protocol was employed to contrast the effectiveness of the displays.
 The results have shown that overall the use of the hexagon tile map display allows participants to find the data plot in the lineup more often.
@@
 Therefore, this display is not only relevant to Australia, but all nations or population distributions that experience densely populated cities separated by vast rural expanses.
-
-- Add Election results data + plus other statistics, 
-- new and better hexagon layout software 
-- Other plot/map type comparisons, insets, cartograms, statistical plots along with maps, especially interactive
-- eye-tracking in association with lineups
+-->
 

### 2025-07-09 paper/kobakian-cook-anzjs.tex
done with all - needs a careful read and references cleaned up

@@
 thorough reviews of the array of methods, as suitable for cancer atlas
-displays \citep{review, BCM}.
+displays \citep[e.g.][]{KCR, BCM}, and experiments demonstrating
+cartograms to be more effective than choropleth maps \citep{KFIF}.
 
@@
   the areas'', ``Big differences between neighbouring areas'', ``All
-  areas have similar colours'' or ``None of these reasons''.
+  areas have similar colours'' or ``None of these reasons''. Note
+  providing restricted list of reasons rather than free text encourages
+  a response because it is easy. The list needs to contain the primary
+  expected reasons and other potential reasons need to be added so that
+  it does not bias the participants' behaviour.
 \item
@@
 
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=0.8\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-beeswarm-1.pdf}
+
+}
+
+\caption{\label{fig-beeswarm}The distribution of the time taken
+(seconds) to submit a response for each combination of trend, whether
+the data plot was detected, and type of display, shown using
+horizontally jittered dotplots. The coloured point indicates average
+time taken for each map type. Although some participants take just a few
+seconds per evaluation, and some take as much as 60 seconds, but there
+is very little difference in time taken between map types.}
+
+\end{figure}%
+
 \subsection{Speed}\label{speed}
@@
 
-\includegraphics[width=0.8\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-beeswarm-1.pdf}
-
-}
-
-\caption{\label{fig-beeswarm}The distribution of the time taken
-(seconds) to submit a response for each combination of trend, whether
-the data plot was detected, and type of display, shown using
-horizontally jittered dotplots. The coloured point indicates average
-time taken for each map type. Although some participants take just a few
-seconds per evaluation, and some take as much as 60 seconds, but there
-is very little difference in time taken between map types.}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-certainty-1.pdf}
+
+}
+
+\caption{\label{fig-certainty}The distribution of certainty chosen by
+participants when viewing hexagon tile map or choropleth displays, shown
+as a mosaic plot, faceted by the trend model and whether the plot was
+detected or not. At most trend models and whether the plot was detected
+or not, participants were more likely to choose a high certainty when
+evaluating a choropleth map.}
 
@@
 
-\begin{figure}
-
-\centering{
-
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-certainty-1.pdf}
-
-}
-
-\caption{\label{fig-certainty}The distribution of certainty chosen by
-participants when viewing hexagon tile map or choropleth displays, shown
-as a mosaic plot, faceted by the trend model and whether the plot was
-detected or not. At most trend models and whether the plot was detected
-or not, participants were more likely to choose a high certainty when
-evaluating a choropleth map.}
-
-\end{figure}%
-
 \subsection{Reason}\label{reason}
 
-Participants were asked why they had made their plot choice and were
-able to select from a set of suggested reasons. ``Colour trend across
-the areas'' was the most common selection for NW-SE trend displays
-(Table~\ref{tbl-reason}).
-
-The reasons chosen by participants from the list provided to them varied
-more when viewing choropleth displays than the hexagon tile map. The
-hexagon tile map displays resulted in ``Clusters of colour'' as the most
-common choice made by participants.
-
-The choice ``None of these reasons'' was used as the default value to
-minimise noise from participants who did not select a response.
+Table~\ref{tbl-reason} summarises the reasons that participants gave for
+their choices: ``clusters'' = ``Clusters of colour'', ``trend'' =
+``Colour trend across the areas'', ``consistent'' = ``All areas have
+similar colours'', ``hotpots'' = ``Big differences between neighbouring
+areas'', ``none'' = ``None of these reasons''. These proportions are
+computed separately for each trend, map type and whether the participant
+detected the data plot. With All Cities and Three Cities, when correct,
+participants tended to select `consistent' with the choropleth, and
+`clusters' with the hexagon tile map. With the NW-SE trend, `trend' was
+primarily selected for the choropleth, but `clusters' was the primary
+reason for the hexgon tile map. The primary reasons are similar when the
+participant did not detect the data plot.
+
+The results when the data plot was detected are as expected, but that
+they are similar to the not detected group is interesting. It suggests
+that with the choropleth people are trying to read contiguous patterns,
+while the hexagon tile map is being read for pockets of differences.
+This may be due the hexagon tile map being non-contiguous.
 
@@
 
-\caption{\label{tbl-reason}Summary of the reasons that participants
-wrote for their choice of plot when looking at each trend model shown in
-choropleth and hexagon tile maps.}
+\caption{\label{tbl-reason}Proportion of participants chose each reason
+for their choice of plot, computed separately for each Trend and Map
+Type level, and whether the data plot was detected. The primary reason
+when participants were evaluating the choropleth map was `consistent' or
+`trend', but for the hexagon tile map it was `clusters', when they
+detected the data plot.}
 
@@
 \toprule
-Trend & Detected & type & clusters & consistent & hotspots & no reason & trend\\
+Trend & Detect & Type & clusters & trend & consistent & hotspots & none\\
 \midrule
- & No & Choro. & 50 & 12 & 11 & 9 & 56\\
-\cmidrule{2-8}
- & No & Hex. & 27 & 6 & 5 & 15 & 22\\
-\cmidrule{2-8}
- & Yes & Choro. & 14 & 14 & 3 & 4 & 7\\
-\cmidrule{2-8}
-\multirow{-4}{*}{\raggedright\arraybackslash All Cities} & Yes & Hex. & 44 & 4 & 14 & 8 & 35\\
-\cmidrule{1-8}
- & No & Choro. & 54 & 12 & 17 & 16 & 74\\
-\cmidrule{2-8}
- & No & Hex. & 42 & 6 & 11 & 15 & 34\\
-\cmidrule{2-8}
- & Yes & Choro. & 1 & 4 & 0 & 0 & 2\\
-\cmidrule{2-8}
-\multirow{-4}{*}{\raggedright\arraybackslash Three Cities} & Yes & Hex. & 35 & 0 & 10 & 4 & 23\\
-\cmidrule{1-8}
- & No & Choro. & 20 & 14 & 11 & 8 & 34\\
-\cmidrule{2-8}
- & No & Hex. & 27 & 3 & 5 & 15 & 18\\
-\cmidrule{2-8}
- & Yes & Choro. & 32 & 2 & 15 & 7 & 37\\
-\cmidrule{2-8}
-\multirow{-4}{*}{\raggedright\arraybackslash NW-SE} & Yes & Hex. & 56 & 12 & 6 & 6 & 32\\
+All Cities & Yes & Choro. & 0.33 & 0.17 & 0.33 & 0.07 & 0.10\\
+All Cities & Yes & Hex. & 0.42 & 0.33 & 0.04 & 0.13 & 0.08\\
+\addlinespace
+Three Cities & Yes & Choro. & 0.14 & 0.29 & 0.57 & 0.00 & 0.00\\
+Three Cities & Yes & Hex. & 0.49 & 0.32 & 0.00 & 0.14 & 0.06\\
+\addlinespace
+NW-SE & Yes & Choro. & 0.34 & 0.40 & 0.02 & 0.16 & 0.08\\
+NW-SE & Yes & Hex. & 0.50 & 0.29 & 0.11 & 0.05 & 0.05\\
+\addlinespace
+All Cities & No & Choro. & 0.36 & 0.41 & 0.09 & 0.08 & 0.07\\
+All Cities & No & Hex. & 0.36 & 0.29 & 0.08 & 0.07 & 0.20\\
+\addlinespace
+Three Cities & No & Choro. & 0.31 & 0.43 & 0.07 & 0.10 & 0.09\\
+Three Cities & No & Hex. & 0.39 & 0.31 & 0.06 & 0.10 & 0.14\\
+\addlinespace
+NW-SE & No & Choro. & 0.23 & 0.39 & 0.16 & 0.13 & 0.09\\
+NW-SE & No & Hex. & 0.40 & 0.26 & 0.04 & 0.07 & 0.22\\
 \bottomrule
@@
 
-The intention of this study was to contrast the use of the choropleth
-map and the hexagon tile map. The visual inference lineup protocol was
-employed to contrast the effectiveness of the displays. The results have
-shown that overall the use of the hexagon tile map display allows
-participants to find the data plot in the lineup more often. Using the
-visual inference protocol this result can be extended to show that it is
-a valid alternative display to communicate spatial distributions of
-population related data.
-
-We expected that the choropleth map would be superior for communicating
-the spatial pattern of geographic distributions. The data suggest that
-the participants perform slightly better or equally as well for each
-replicate in each trend model across the two displays. Table II shows
-that the difference in the mean detection rate for the two trend models
-was 0.10.
-
-The differences seen in the Figure~\ref{fig-detect-compare} plot.
-Surprisingly the difference between map types for the geographic
-distribution was significant at the 0.05 level, even though the effect
-difference is small. It also showed that the hexagon tile map display
-performs marginally better than the choropleth for all trend models.
-
-While the significance of the difference in detection was the key focus
-of this experiment, the secondary focus was the time taken by
-participants. it was expected that the participants may take longer to
-consider the hexagon tile map distribution but would be able to detect
-the data plot in the lineup. The bimodal distributions seen in
-Figure~\ref{fig-beeswarm} showed very little difference in the mean
-evaluation times. As the maximum time of all of the distributions
-approached 60 seconds it cannot be said that the participants' took
-longer to evaluate the hexagon tile map displays.
-
-The responses to the questions asked of participants included the reason
-for their choice and the certainty around their choice.
-Table~\ref{tbl-reason} shows high levels of certainty of 4 and 5 were
-chosen by participants when looking at the population distributions in a
-choropleth map display show that they were over confident when
-attempting to find the real data plot in the choropleth map displays.
-Participants performed better on the NW-SE distribution shown in the
-choropleth display and were reasonably confident about their decisions.
-The high levels of the mid range value of 3 could indicate that the
-participant did not want to provide a response, as this was the default
-value. Those who chose level 4 or 5 were equally likely to be correct
-for the three cities lineups, but more likely to be correct than
-incorrect for the other two trend models.
-
-The colour scaling applied in Three cities and All cities displays
-resulted in the rural areas of the real data plot appearing more blue or
-yellow than the other plots in the lineups. Due to the consistent
-colouring of rural areas in a choropleth display, the choice ``All areas
-have similar colours'' was most common reason for a participants choice.
-The All Cities displays coloured the inner-city areas of all capital
-cities more red, this was observable to participants and explains the
-equal choice of the city clusters or rural colour consistency. Choosing
-``Clusters of colour'' was expected when participants viewed the Hexagon
-tile map display of the All Cities and Three Cities distributions. It
-was unexpected that it was also the most common reason for the NW-SE
-hexagon tile map displays. Due to the spatial covariance introduced in
-the smoothing, groups of similarly coloured hexagons were present in all
-of the hexagon tile map displays. All Cities and Three Cities
-distributions of real data trends had distinctly different patterns or
-red inner-city areas, while some of the plots in each lineup may have
-shared similar features.
-
-\section{Conclusion}\label{conclusion}
-
-The choropleth map display and the tessellated hexagon tile map have
-been contrasted using the lineup protocol. The hexagon tile map was
-significantly more effective for spotting a real population related data
-trend model hidden in a lineup.
-
-The hexagon tile map display should be considered as an alternative
-visualisation method when communicating distributions that relate to the
-population across a set of geographic units. As an additional display to
-the familiar choropleth map, cancer atlas products may benefit from the
-opportunity to allow exploration via an alternative display. The spatial
-distributions used to test these displays were inspired by the real
-spatially smoothed estimates of the cancer burden on Australian
-communities. However, this technique may be extended to other population
-related distributions, such as other diseases, or election results or
-socioeconomic indicators.
-
-The increasing population densities of capital cities despite large land
-area exacerbates the difference in the smallest and largest communities.
-The population density structure of Australia can be considered similar
-to that of Canada, New Zealand and many other countries. Therefore, this
-display is not only relevant to Australia, but all nations or population
-distributions that experience densely populated cities separated by vast
-rural expanses.
-
-\begin{itemize}
-\tightlist
-\item
-  Add Election results data + plus other statistics,
-\item
-  new and better hexagon layout software
-\item
-  Other plot/map type comparisons, insets, cartograms, statistical plots
-  along with maps, especially interactive
-\item
-  eye-tracking in association with lineups
-\end{itemize}
+This study provides evidence that the hexagon tile map is superior to a
+choropleth map for communicating population statistics, for Australia.
+While the cartogram has been established as better than a choropleth
+map, cartograms do not work for the vast disparity between population
+density and geographic area in Australia. The hexagon tile map was
+developed to provide a possible solution, and this study demonstrates
+that it has potential.
+
+The R package \texttt{sugarbag} can be used to generate a hexagon tile
+map. It can be used for any spatial polygon data, so is applicable to
+other countries or geographic areas.
+
+One of the strengths but weaknesses of the hexagon tile map is that it
+is non-contiguous. Large rural areas are represented by isolated
+hexagons. This is why we expected that the hexagon tile map might not
+work well to detect large-scale spatial trend (``NW-SE''). The primary
+reason for producing the non-contiguous display was to preserve
+geography sufficiently for the reader to easily recognise the location.
+This is a strength, and allows a map of the country to be drawn
+underneath the hexagons. It appears to not inhibit reading of the
+spatial distribution based on this experiment. However, there is
+considerable room for improving the algorithm and exploring some
+variations. These might include increasing the size of isolated
+hexagons, or collecting multiple hexagons together.
+
+The manner in which hexagons are exploded out from the city centres is
+another direction of research. Ideally, the location of the hexagons
+should be close to their original location but this is hard to control
+and measure. The current algorithm works sequentially to place hexagons,
+radially from a provided centre. There are likely better optimisation
+procedures that could impve the layout. For reading the spatial
+distribution, this is less important, but if the hexagon tile map is
+provided to users as an interactive tool, they will want to locate
+themselves in the plot. If the hexagon is not close to the true location
+it could be disconcerting.
+
+Hexagon displays are growing in popularity. Two media outlets used
+variations of the hexagon displays to communicate the 2025 Australian
+federal election results
+{[}\citet{abc-election2025};guardian-election2025{]}. Both are
+effective, but have inadequacies. The Guardian preserves geography and
+allows inner city results to be seen but the overall sense of the result
+is skewed because the large rural areas dominate the display. The ABC's
+contiguous hexagon tile map gives the correct sense of the final results
+but loses the shape of Australia, and some hexagons are far from their
+true location.
+
+This experiment focused on comparing a new display, the hexagon tile
+map, against the standard display, choropleth. There are other options
+that could have been included in the study, such as the use of insets of
+dense population areas along with the chorpleth map, or the use of
+interactive graphics linking statistical charts with the choropleth.
+Keeping the scope of the study small was important to understand whether
+it was reasonable to recommend use of the hexagon tile map. Although we
+only tested on the Australian geography, the results should hold for
+other regions that have similarly disparities between population size
+and geographic size.
+
+We would recommend doing follow-up studies that allow deeper
+understanding of how the different displays are read. For example, to
+understand the differences in how people read the choropleth map and the
+hexagon tile map as indicated by the different reasons given, could be
+done using an eyetracking experiment. \citet{ZCHMR} is an example of
+such an experiment where the manner in which people read lineups was
+examined.
 

### 2025-07-09 paper/kobakian-cook-anzjs.qmd
tidied up speed section

@@
     TRUE~"Choro.")) %>% 
-    mutate(detect_f = factor(detect, levels = c(0,1), labels = c("Detected? No", "Detected? Yes")))
+    mutate(detect_f = factor(detect, levels = c(1, 0), labels = c("Detected? Yes", "Detected? No")))
 
@@
 Although some participants take just a few seconds per evaluation, and some take as much as 60 seconds, but there is very little difference in time taken between map types."
-#| fig-height: 6
-#| fig-width: 5
-#| out-width: 80%
+#| fig-height: 4
+#| fig-width: 6
+#| out-width: 100%
 s <- d %>% group_by(type, trend, detect_f) %>%
@@
   #geom_hline(data=s, aes(yintercept=m, color=type)) +
-  geom_point(data=s, aes(x=type, y=m, color=type), size=5, alpha=0.7) +
+  geom_point(data=s, aes(x=type, y=m, color=type), size=3, alpha=0.7) +
   #geom_errorbar(data=s, aes(x=type, ymin=q1, ymax=q3, color=type), width=0.3, size=2) +
   scale_color_manual("", values = type_colors) +
-  facet_grid(trend~detect_f) + 
+  facet_grid(detect_f~trend) + 
   ylab("Time taken (seconds)") + xlab("") +
@@
 
+```
+
+```{r}
 # Check time difference between default choice
-d %>% mutate(zeros = if_else(choice == 0, 0, 1)) %>%
+d_zeros <- d %>% mutate(zeros = if_else(choice == 0, 0, 1)) %>%
   group_by(zeros) %>%   
@@
 
-d %>% mutate(zeros = if_else(choice == 0, 0, 1)) %>%
+d_zeros_detect <- d %>% mutate(zeros = if_else(choice == 0, 0, 1)) %>%
   group_by(zeros, detect_f) %>%   
@@
             n=n())
-
 # Summarise across subjects
@@
             s_t=sd(time_taken)) 
+```
+
+```{r}
+#| eval: false
 ggplot(contributor_smry, aes(m_t, m_d)) +
@@
 
-@fig-beeswarm shows horizontally jittered dot plots to contrast the time taken by participants to evaluate each lineup when viewing each type of display.
-The time are also separated by trend model and whether the data plot was detected or not detected.
-The time taken to complete an evaluation ranged from milliseconds to 60 seconds.
-The average time taken for type of display is shown as a large coloured dot on each plot.
-When considering the heights of the green and orange dots, there is little difference in the average time taken to read a choropleth or hexagon tile map.
-Comparing the same coloured dot across each trend model row, there is a slight increase in the time taken to correctly detected the data plot in the hexagon tile map lineup, but little difference in evaluation time for the choropleth display.
-However, there were substantially less correct detections for choropleth lineups for the Three cities and All Cities trends.
+@fig-beeswarm shows horizontally jittered dot plots to contrast the time taken by participants to evaluate each lineup facetted by map type and trend model.
+Each dot is an evaluation.
+The time taken to complete an evaluation ranged from fractions of a second to 60 seconds.
+The average time taken for type of display is shown as a large coloured dot on each plot, and show there is little difference in the average time taken to read a lineup made with either a choropleth or hexagon tile map.
+
+That some evaluations occurred within milliseconds is a little surprising.
+Investigating whether this was related the `r d_zeros$n[1]` of `r d_zeros$n[1]+d_zeros$n[2]` evaluations where participants left the default choice of 0, and we find it is not; most of these people took the routine time to examine, and then left it at the default suggesting that they just could not pick one as different.
+This is the same as a non-detect.
+On a per participant basis, the average time per lineup over the 12 evaluations ranged between `r round(min(contributor_smry$m_t), 2)` and `r round(max(contributor_smry$m_t), 2)` seconds.
+The correlation between average detection rate and time taken across subjects `r round(cor(contributor_smry$m_d, contributor_smry$m_t), 2)` which is weakly positive.
+This is similar to what we have found in other studies, some subjects are especially fast and accurate in visual evaluation, and conversely some subjects are quite slow but inaccurate.
 
@@
   mutate(reason = ifelse(reason =="0.0", "no reason", reason)) %>% 
-  mutate(Detected = ifelse(detect_f == "Detected? Yes", "Yes", "No"),
+  mutate(Detected = ifelse(detect_f == "Detected? Yes", 
+                           "Yes", "No"),
     Trend = trend) %>% 
@@
  - Data analysis: tidyverse [@tidyverse], ggthemes [@ggthemes], RColorBrewer [@RColorBrewer].
- - Plots: ggplot2 [@ggplot2], cowplot [@cowplot], png [@png], grid [@grid].
+ - Plots: ggplot2 [@ggplot2], cowplot [@cowplot], png [@png], grid [@grid], ggbeeswarm [@ggbeeswarm], ggmosaic [@ggmosaic].
  - Modelling and summary presentation: lme4 [@lme4], kableExtra [@kableExtra].

### 2025-07-09 paper/kobakian-cook-anzjs.tex
tidied up speed section

@@
 
-\includegraphics[width=0.8\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-beeswarm-1.pdf}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{kobakian-cook-anzjs_files/figure-pdf/fig-beeswarm-1.pdf}
 
@@
 Figure~\ref{fig-beeswarm} shows horizontally jittered dot plots to
-contrast the time taken by participants to evaluate each lineup when
-viewing each type of display. The time are also separated by trend model
-and whether the data plot was detected or not detected. The time taken
-to complete an evaluation ranged from milliseconds to 60 seconds. The
-average time taken for type of display is shown as a large coloured dot
-on each plot. When considering the heights of the green and orange dots,
-there is little difference in the average time taken to read a
-choropleth or hexagon tile map. Comparing the same coloured dot across
-each trend model row, there is a slight increase in the time taken to
-correctly detected the data plot in the hexagon tile map lineup, but
-little difference in evaluation time for the choropleth display.
-However, there were substantially less correct detections for choropleth
-lineups for the Three cities and All Cities trends.
+contrast the time taken by participants to evaluate each lineup facetted
+by map type and trend model. Each dot is an evaluation. The time taken
+to complete an evaluation ranged from fractions of a second to 60
+seconds. The average time taken for type of display is shown as a large
+coloured dot on each plot, and show there is little difference in the
+average time taken to read a lineup made with either a choropleth or
+hexagon tile map.
+
+That some evaluations occurred within milliseconds is a little
+surprising. Investigating whether this was related the 28 of 1080
+evaluations where participants left the default choice of 0, and we find
+it is not; most of these people took the routine time to examine, and
+then left it at the default suggesting that they just could not pick one
+as different. This is the same as a non-detect. On a per participant
+basis, the average time per lineup over the 12 evaluations ranged
+between 3.91 and 40.42 seconds. The correlation between average
+detection rate and time taken across subjects 0.3 which is weakly
+positive. This is similar to what we have found in other studies, some
+subjects are especially fast and accurate in visual evaluation, and
+conversely some subjects are quite slow but inaccurate.
 
@@
   Plots: ggplot2 \citep{ggplot2}, cowplot \citep{cowplot}, png
-  \citep{png}, grid \citep{grid}.
+  \citep{png}, grid \citep{grid}, ggbeeswarm \citep{ggbeeswarm},
+  ggmosaic \citep{ggmosaic}.
 \item

### 2025-07-10 paper/kobakian-cook-anzjs.qmd
fixed references - all titlecase now

@@
   # Downloaded data
-d <- read_xlsx("data/experiment-export.xlsx", sheet=2) %>%
-  filter(!is.na(contributor)) %>%
+d <- read_xlsx("data/experiment-export.xlsx", sheet=2) |>
+  filter(!is.na(contributor)) |>
   mutate(contributor = factor(contributor))
 
-n_all_contributors <- d %>% count(contributor, sort=TRUE) %>% 
+n_all_contributors <- d |> count(contributor, sort=TRUE) |> 
   summarise(n_contributors = length(contributor))
@@
 # remove duplicated entries due to submit button
-d <- d %>% group_by(group, contributor, image_name) %>%
-  slice(1) %>% ungroup() %>% 
+d <- d |> group_by(group, contributor, image_name) |>
+  slice(1) |> ungroup() |> 
   arrange(group, contributor, plot_order)
@@
 # Remove contributors who did not provide answers to most questions
-keep <- d %>% count(contributor, sort = TRUE) %>% filter(n > 10)
-d <- d %>% 
-  filter(contributor %in% keep$contributor) %>%
+keep <- d |> count(contributor, sort = TRUE) |> filter(n > 10)
+d <- d |> 
+  filter(contributor %in% keep$contributor) |>
   filter(contributor != "1234567890") # Testing id
@@
 # Or an insufficient amount of responses
-bad_contribs <- d %>% group_by(contributor) %>% 
-  #summarise(sum0 = sum(choice)) %>% 
-  summarise(n_zero = sum(if_else(choice == 0, 1, 0))) %>%
-  #filter(sum0 < 13) %>% 
-  filter(n_zero > 8) %>%
+bad_contribs <- d |> group_by(contributor) |> 
+  #summarise(sum0 = sum(choice)) |> 
+  summarise(n_zero = sum(if_else(choice == 0, 1, 0))) |>
+  #filter(sum0 < 13) |> 
+  filter(n_zero > 8) |>
   pull(contributor)
@@
 # Person is in list above
-same_answer <- d %>% group_by(contributor) %>% 
+same_answer <- d |> group_by(contributor) |> 
   summarise(v = sd(choice))
@@
 
-d <- d %>% 
+d <- d |> 
   filter(!(contributor %in% bad_contribs))
 
-n_contributors <- d %>% count(contributor, sort=TRUE) %>% 
+n_contributors <- d |> count(contributor, sort=TRUE) |> 
   summarise(n_contributors = length(contributor))
@@
 
-d <- d %>% mutate(certainty = factor(as.character(certainty),
+d <- d |> mutate(certainty = factor(as.character(certainty),
   levels = c("1", "2", "3", "4","5"), ordered=TRUE))
@@
 # Add rep info to data
-d <- d %>% left_join(., replicate, by = "image_name")
+d <- d |> left_join(replicate, by = "image_name")
 ```
@@
 # Tidy for analysis
-d <- d %>% 
-  separate(image_name, c("nothing", "trend", "location", "type", "extra"), remove = FALSE) %>%
-  select(-nothing, -extra) %>%
+d <- d |> 
+  separate(image_name, c("nothing", "trend", "location", "type", "extra"), remove = FALSE) |>
+  select(-nothing, -extra) |>
   mutate(location = as.numeric(location), 
     # detect measures the accuracy of the choice
-         detect = ifelse(location == choice, 1, 0)) %>% 
+         detect = ifelse(location == choice, 1, 0)) |> 
   mutate(trend = case_when(
@@
     trend == "cities" ~ "All Cities",
-    trend == "three" ~ "Three Cities")) %>% 
-  mutate(trend = fct_relevel(trend,"All Cities","Three Cities", "NW-SE")) %>% 
+    trend == "three" ~ "Three Cities")) |> 
+  mutate(trend = fct_relevel(trend,"All Cities","Three Cities", "NW-SE")) |> 
   mutate(type = case_when(
     type == "hex" ~"Hex.",
-    TRUE~"Choro.")) %>% 
+    TRUE~"Choro.")) |> 
     mutate(detect_f = factor(detect, levels = c(1, 0), labels = c("Detected? Yes", "Detected? No")))
 
-plots <- d %>% group_by(group, trend, type, location) %>%
+plots <- d |> group_by(group, trend, type, location) |>
   # pdetect measures the aggregated accuracy of the choices
@@
 
-sa2 <- sa22011 %>% 
-  filter(!st_is_empty(geometry)) %>% 
-  filter(!state_name_2011 == "Other Territories") %>% 
+sa2 <- sa22011 |> 
+  filter(!st_is_empty(geometry)) |> 
+  filter(!state_name_2011 == "Other Territories") |> 
   filter(!sa2_name_2011 == "Lord Howe Island")
 
-SIR <- read_csv("data/SIR Downloadable Data.csv") %>% 
-  filter(SA2_name %in% sa2$sa2_name_2011) %>% 
-  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
+SIR <- read_csv("data/SIR Downloadable Data.csv") |> 
+  filter(SA2_name %in% sa2$sa2_name_2011) |> 
+  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) |> 
   filter(Cancer_name == "Thyroid", Sex_name == "Females")
-ERP <- read_csv("data/ERP.csv") %>%
-  filter(REGIONTYPE == "SA2", Time == 2011, Region %in% SIR$SA2_name) %>% 
+ERP <- read_csv("data/ERP.csv") |>
+  filter(REGIONTYPE == "SA2", Time == 2011, Region %in% SIR$SA2_name) |> 
   dplyr::select(Region, Value)
@@
 # Join with sa2 sf object
-sa2thyroid_ERP <- SIR %>% 
-  left_join(sa2, ., by = c("sa2_name_2011" = "SA2_name")) %>%
-  left_join(., ERP %>% 
+sa2thyroid_ERP <- left_join(sa2, SIR, by = c("sa2_name_2011" = "SA2_name")) |>
+  left_join(ERP |> 
               dplyr::select(Region, 
-              Population = Value), by = c("sa2_name_2011"= "Region")) %>% 
+              Population = Value), by = c("sa2_name_2011"= "Region")) |> 
   filter(!st_is_empty(geometry))
-sa2thyroid_ERP <- sa2thyroid_ERP %>% 
-  #filter(!is.na(Population)) %>% 
-  filter(!sa2_name_2011 == "Lord Howe Island") %>% 
-  mutate(SIR = map_chr(p50, aus_colours)) %>% 
+sa2thyroid_ERP <- sa2thyroid_ERP |> 
+  #filter(!is.na(Population)) |> 
+  filter(!sa2_name_2011 == "Lord Howe Island") |> 
+  mutate(SIR = map_chr(p50, aus_colours)) |> 
   st_as_sf()
@@
 ## Create centroids set
-sa2centroids <- sa2 %>% 
-  create_centroids(., "sa2_name_2011")
+sa2centroids <- create_centroids(sa2, "sa2_name_2011")
 ## Create hexagon grid
@@
                             sf_id = "sa2_name_2011",
-                            hex_size = 0.3) %>% 
-            left_join(sa2thyroid_ERP %>%
+                            hex_size = 0.3) |> 
+            left_join(sa2thyroid_ERP |>
             select(sa2_name_2011, SIR, p50))
-fort_aus <- sa2thyroid_ERP %>%
+fort_aus <- sa2thyroid_ERP |>
   fortify_sfc()
@@
   theme(axis.text.y = element_blank(),
-        axis.ticks.y = element_blank())
+        axis.ticks = element_blank())
 ```
@@
 
-var.sim1 <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) %>% 
+var.sim1 <- predict(var.g.dummy, newdata = sa3_centroids, nsim = 12) |> 
   left_join(sa3_centroids, ., by=c("longitude", "latitude"))
 
-sa3_sims1_1 <- as_tibble(var.sim1) %>% 
+sa3_sims1_1 <- as_tibble(var.sim1) |> 
   mutate_at(sims, ~map_dbl(1:nrow(sa3), spatial_smoother, 
@@
 # Detectability rate for each lineup (image)
-d_smry <- d %>% group_by(trend, type, replicate) %>%
+d_smry <- d |> group_by(trend, type, replicate) |>
   # pdetect measures the aggregated accuracy of the choices
-  summarise(pdetect = length(detect[detect == 1])/length(detect)) %>%
+  summarise(pdetect = length(detect[detect == 1])/length(detect)) |>
   ungroup()
@@
 # Numerical summary
-diffs <- d_smry %>% spread(type, pdetect) %>%
+diffs <- d_smry |> spread(type, pdetect) |>
   mutate(dif = `Hex.` - `Choro.`)
@@
 # Check detection rate across groups
-d %>% group_by(group) %>%
+d |> group_by(group) |>
     # pdetect measures the aggregated accuracy of the choices
-    summarise(pdetect = length(detect[detect == 1])/length(detect)) %>%
+    summarise(pdetect = length(detect[detect == 1])/length(detect)) |>
     ungroup()
@@
 
-d %>% group_by(type, trend) %>%
+d |> group_by(type, trend) |>
   summarise(m = as.character(round(mean(detect), 2)),
-      std.dev = as.character(round(sd(detect), 2))) %>% 
-  mutate(std.dev = ifelse(std.dev == 0.5, "(0.50)", paste0("(", std.dev, ")"))) %>%   mutate(m = ifelse(m == 0.4, "0.40", m)) %>% 
-  gather(stat, value, m, std.dev) %>% 
-  pivot_wider(names_from = "trend", values_from = "value") %>% 
-  arrange(type) %>% ungroup() %>% 
-  mutate(Type = types) %>% select(Type, `NW-SE`, `Three Cities`, `All Cities`) %>%
+      std.dev = as.character(round(sd(detect), 2))) |> 
+  mutate(std.dev = ifelse(std.dev == 0.5, "(0.50)", paste0("(", std.dev, ")"))) |>   mutate(m = ifelse(m == 0.4, "0.40", m)) |> 
+  gather(stat, value, m, std.dev) |> 
+  pivot_wider(names_from = "trend", values_from = "value") |> 
+  arrange(type) |> ungroup() |> 
+  mutate(Type = types) |> select(Type, `NW-SE`, `Three Cities`, `All Cities`) |>
   knitr::kable(., format = "latex", align = "lccc", booktabs = TRUE, 
@@
 
-detection_rates <- tidy(detect_fit) %>%
-  mutate(detection_rates = round(exp(estimate)/(1+exp(estimate)),2)) %>%
-  select(term, estimate, detection_rates) %>% pull(detection_rates)
+detection_rates <- tidy(detect_fit) |>
+  mutate(detection_rates = round(exp(estimate)/(1+exp(estimate)),2)) |>
+  select(term, estimate, detection_rates) |> pull(detection_rates)
 
@@
 
-tidy(detect_fit) %>%
-  mutate_at(.vars = c("estimate", "std.error"), round, 2) %>% 
-  mutate(p.value = round(p.value, digits=2)) %>% 
-  rowwise() %>%
+tidy(detect_fit) |>
+  mutate_at(.vars = c("estimate", "std.error"), round, 2) |> 
+  mutate(p.value = round(p.value, digits=2)) |> 
+  rowwise() |>
   mutate(sig = case_when(
@@
   p.value <= 0.01 ~  "$^{.}$",
-  TRUE ~ "$^{ }$")) %>%
-  ungroup() %>% 
-  filter(!is.na(std.error)) %>%
-  mutate(term = glmer_terms) %>% 
+  TRUE ~ "$^{ }$")) |>
+  ungroup() |> 
+  filter(!is.na(std.error)) |>
+  mutate(term = glmer_terms) |> 
   select(Term = term, 
@@
     `P-val.` = p.value, 
-    Sig. = sig) %>% 
+    Sig. = sig) |> 
   knitr::kable(format = "latex", escape = FALSE, align= "rrlrr", 
@@
 #| out-width: 100%
-s <- d %>% group_by(type, trend, detect_f) %>%
+s <- d |> group_by(type, trend, detect_f) |>
   summarise(m=median(time_taken), 
@@
 # Check groups and demographics
-d %>% group_by(group) %>%   
+d |> group_by(group) |>   
   summarise(m=mean(time_taken), 
             s=sd(time_taken))
-d %>% group_by(gender) %>%   
+d |> group_by(gender) |>   
   summarise(m=mean(time_taken), 
             s=sd(time_taken))
-d %>% group_by(age) %>%   
+d |> group_by(age) |>   
   summarise(m=mean(time_taken), 
             s=sd(time_taken))
-d %>% group_by(education) %>%   
+d |> group_by(education) |>   
   summarise(m=mean(time_taken), 
@@
 # Check time difference between default choice
-d_zeros <- d %>% mutate(zeros = if_else(choice == 0, 0, 1)) %>%
-  group_by(zeros) %>%   
+d_zeros <- d |> mutate(zeros = if_else(choice == 0, 0, 1)) |>
+  group_by(zeros) |>   
   summarise(m=median(time_taken), 
@@
 
-d_zeros_detect <- d %>% mutate(zeros = if_else(choice == 0, 0, 1)) %>%
-  group_by(zeros, detect_f) %>%   
+d_zeros_detect <- d |> mutate(zeros = if_else(choice == 0, 0, 1)) |>
+  group_by(zeros, detect_f) |>   
   summarise(m=median(time_taken), 
@@
 # Summarise across subjects
-contributor_smry <- d %>% group_by(contributor) %>%   
+contributor_smry <- d |> group_by(contributor) |>   
   summarise(m_d=mean(detect), 
@@
 #| out-width: 100%
-d <- d %>% 
-  mutate(certainty = as_factor(certainty)) %>% 
+d <- d |> 
+  mutate(certainty = as_factor(certainty)) |> 
   mutate(replicate_f = as_factor(replicate))
 
-#d %>% 
+#d |> 
 #  mutate(Detected = factor(detect_f, 
 #    levels = c("Detected? Yes", "Detected? No"), 
-#    labels = c("Yes", "No"))) %>% 
+#    labels = c("Yes", "No"))) |> 
 #ggplot(aes(x = certainty, fill = Detected)) +  
@@
 # Qualitative analysis of reason
-reasons_smry <- d %>% 
-  mutate(reason = ifelse(reason =="0.0", "no reason", reason)) %>% 
+reasons_smry <- d |> 
+  mutate(reason = ifelse(reason =="0.0", "no reason", reason)) |> 
   mutate(Detected = ifelse(detect_f == "Detected? Yes", 
                            "Yes", "No"),
-    Trend = trend) %>% 
-  group_by(Trend, Detected, type) %>% 
-  count(reason) %>%
-  ungroup() %>%
-  group_by(Trend, Detected, type) %>%
-  mutate(prop = n/sum(n)) %>% 
-  ungroup() %>%
-  select(Trend, Detected, type, reason, prop) %>%
-  mutate(prop = round(prop, 2)) %>%
+    Trend = trend) |> 
+  group_by(Trend, Detected, type) |> 
+  count(reason) |>
+  ungroup() |>
+  group_by(Trend, Detected, type) |>
+  mutate(prop = n/sum(n)) |> 
+  ungroup() |>
+  select(Trend, Detected, type, reason, prop) |>
+  mutate(prop = round(prop, 2)) |>
   pivot_wider(names_from = reason, 
               values_from = prop, 
-              values_fill = 0) %>%
+              values_fill = 0) |>
   select(Trend, Detected, type, clusters, trend, consistent, hotspots, `no reason`)
 
-#  mutate(prop = round(n/sum(n), 2), r_prop = paste0(reason, ":", prop)) %>% 
-#  top_n(1, n) %>% summarise(reasons = paste(reason, collapse=", ")) %>% 
-#  pivot_wider(names_from = c("type"), values_from = c("reasons")) %>% 
-#  ungroup() %>% 
+#  mutate(prop = round(n/sum(n), 2), r_prop = paste0(reason, ":", prop)) |> 
+#  top_n(1, n) |> summarise(reasons = paste(reason, collapse=", ")) |> 
+#  pivot_wider(names_from = c("type"), values_from = c("reasons")) |> 
+#  ungroup() |> 
 reasons_smry |>  
@@
                  align = "lllrrrrr",
-    linesep = c("", "\\addlinespace", "", "\\addlinespace","", "\\addlinespace","", "\\addlinespace","", "\\addlinespace","")) #%>% 
-  #kable_styling(bootstrap_options = "hold_position") %>% 
+    linesep = c("", "\\addlinespace", "", "\\addlinespace","", "\\addlinespace","", "\\addlinespace","", "\\addlinespace","")) #|> 
+  #kable_styling(bootstrap_options = "hold_position") |> 
   #collapse_rows(., columns = 1)
@@
 
-The source code to produce this document can be found on [GitHub](https://github.com/srkobakian/experiment/paper).
+This document was written using quarto.
+This document contains the code to produce the summaries, plots and additional checks in the paper.
+and all the code to reproduce the analysis, and do additional checks can be found on [GitHub](https://github.com/srkobakian/experiment/paper).
 Supplementary materials have been included to discuss the survey procedures and the lineups that were used.
@@
  - Data analysis: tidyverse [@tidyverse], ggthemes [@ggthemes], RColorBrewer [@RColorBrewer].
- - Plots: ggplot2 [@ggplot2], cowplot [@cowplot], png [@png], grid [@grid], ggbeeswarm [@ggbeeswarm], ggmosaic [@ggmosaic].
+ - Plots: ggplot2 [@ggplot2], cowplot [@cowplot], png [@png], ggbeeswarm [@ggbeeswarm], ggmosaic [@ggmosaic].
  - Modelling and summary presentation: lme4 [@lme4], kableExtra [@kableExtra].

### 2025-07-10 paper/kobakian-cook-anzjs.tex
fixed references - all titlecase now

@@
 
-The source code to produce this document can be found on
-\href{https://github.com/srkobakian/experiment/paper}{GitHub}.
+This document was written using quarto. This document contains the code
+to produce the summaries, plots and additional checks in the paper. and
+all the code to reproduce the analysis, and do additional checks can be
+found on \href{https://github.com/srkobakian/experiment/paper}{GitHub}.
 Supplementary materials have been included to discuss the survey
@@
   Plots: ggplot2 \citep{ggplot2}, cowplot \citep{cowplot}, png
-  \citep{png}, grid \citep{grid}, ggbeeswarm \citep{ggbeeswarm},
-  ggmosaic \citep{ggmosaic}.
+  \citep{png}, ggbeeswarm \citep{ggbeeswarm}, ggmosaic \citep{ggmosaic}.
 \item

### 2025-07-14 paper/kobakian-cook-anzjs.qmd
Final review of kobakian-cook-anzjs.qmd

@@
 The hexagon tile map builds on existing displays, such as the cartogram, and tessellated hexagon displays.
-A hexagon tile map forgoes the familiar boundaries, in favor of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location.
+A hexagon tile map forgoes the familiar boundaries, in favour of representing each geographic unit as an equally sized hexagon, placed approximately in the correct spatial location.
 It differs in the relaxed requirement to have connected hexagons, and allows sparsely located hexagons.
@@
 The Australian Cancer Atlas allows users to explore the patterns in the distributions of cancer statistics over the geographic space of Australia.
-It uses a choropleth map display and diverging color scheme to draw attention to relationships between neighbouring areas.
+It uses a choropleth map display and diverging colour scheme to draw attention to relationships between neighbouring areas.
 The hexagon tile map may be a useful alternative display to enhance the atlas.
@@
 If the data plot is selected it is analogous to a rejection of the null hypothesis (specifying no structure), and the observed data plot is unlikely to arise from the null scenario.
-The work of @VH2016 compares the lineup protocol to performance on statndard tests of visual ability, concluding that participants' performance is related to general visual aptitude, to classification rather than spatial reasoning.
+The work of @VH2016 compares the lineup protocol to performance on standard tests of visual ability, concluding that participants' performance is related to general visual aptitude, to classification rather than spatial reasoning.
 
@@
 Size heterogeneity in administrative units is particularly extreme in Australia: most of the landscape of Australia is sparsely settled, with the population densely clustered into the narrow coastal strips.
-@fig-thyroid a shows the choropleth map of thyroid cancer rates in Australia.
+@fig-thyroid a shows the choropleth map of thyroid cancer incidence rates in Australia.
 The choropleth map focuses attention on the geography, and for heterogeneously sized areas it presents a biased view of the population related distribution of the statistic [@CBATCC].
@@
 <!-- Other cartograms -->
-Alternative algorithms make various trade offs between familiar shapes and representation of geographic units.
+Alternative algorithms make various trade-offs between familiar shapes and representation of geographic units.
 The non-contiguous cartogram method [@NAC] keeps the shapes of geographic units intact, and changes the size of the shape.
@@
 The algorithm is available in the R package, sugarbag [@sugarbag].
-@fig-thyroid b shows the hexagon tile map, where the map is coloured from low (blue) to high (red).
+@fig-thyroid b shows the hexagon tile map, where the map is coloured from low incidence (blue) to high (red).
 The inner city areas have expanded, making it possible to see the cancer incidence in the small, densely populated areas.
@@
 Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to do well, and two with differing level of inner city hot spots.
-These latter two reflect the structure seen in the thyroid cancer data (@fig-thyroid).
+These latter two reflect the structure seen in the thyroid cancer incidence data (@fig-thyroid).
 This produces six treatment levels:
@@
 #| fig-cap: "The experimental design used in the study.
-Participants are allocated to with group A or B, to evaluate either the choropleth or hexagon tile map lineup of each simulated data set.
+Participants are allocated to group A or B, to evaluate either the choropleth or hexagon tile map lineup of each simulated data set.
 The text 'loc' refers to the location of the data plot in the lineup."
@@
 
-This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the thyroid cancer distribution (@fig-thyroid). -->
+This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the thyroid cancer incidence distribution (@fig-thyroid). -->
 
@@
 
-on each of lineup. These responses are saved after entering. Participants were expected to click the submit button on the final page.
+on each of lineup. These responses are saved after entering. 
+<!-- Participants were expected to click the submit button on the final page.-->
 
@@
 Technically it is possible to submit results more than once if the submit button is clicked multiple times in short sequence.
-Participants who did not finish the evaluation of all lineups or clicked through without providing their evaluation are filtered.
+Participants who did not finish the evaluation of all lineups or clicked through without providing their evaluation are removed.
 
@@
 The Three Cities trend was practically not detectable in the choropleth map.
-The dection rates were more similar for the NW-SE trend, but slightly higher for the hexagon tile map, which was a surprise.
+The detection rates were more similar for the NW-SE trend, but slightly higher for the hexagon tile map, which was a surprise.
 Note that, these detection rates are all substantially higher than chance, except for the choropleth map on the Three Cities.
@@
 
-@fig-beeswarm shows horizontally jittered dot plots to contrast the time taken by participants to evaluate each lineup facetted by map type and trend model.
+@fig-beeswarm shows horizontally jittered dot plots to contrast the time taken by participants to evaluate each lineup faceted by map type and trend model.
 Each dot is an evaluation.
@@
 
-@tbl-reason summarises the reasons that participants gave for their choices: "clusters" = "Clusters of colour", "trend" = "Colour trend across the areas", "consistent" = "All areas have similar colours", "hotpots" = "Big differences between neighbouring areas", "none" = "None of these reasons".
+@tbl-reason summarises the reasons that participants gave for their choices: "clusters" = "Clusters of colour", "trend" = "Colour trend across the areas", "consistent" = "All areas have similar colours", "hotspots" = "Big differences between neighbouring areas", "none" = "None of these reasons".
 These proportions are computed separately for each trend, map type and whether the participant detected the data plot.
 With All Cities and Three Cities, when correct, participants tended to select 'consistent' with the choropleth, and 'clusters' with the hexagon tile map.
-With the NW-SE trend, 'trend' was primarily selected for the choropleth, but 'clusters' was the primary reason for the hexgon tile map.
+With the NW-SE trend, 'trend' was primarily selected for the choropleth, but 'clusters' was the primary reason for the hexagon tile map.
 The primary reasons are similar when the participant did not detect the data plot.
@@
 Note that, the purpose of reporting these numbers is to illustrate the reasonable variety of demographic background of participants.
-However, $n=$`r n_contributors` is insufficient fit a model including this demographic information.
+However, $n=$`r n_contributors` is insufficient to fit a model including this demographic information.
 @MHC (published in 2025 but conducted in 2012) showed that there is little difference in performance on lineup experiments between demographic groups.
-@VH2016 found that visual aptitude for reading data plots was associated with math skills, but this study was done on statistical plots of data, not maps.
-Assessing math ability requires substantially more data collection, and does not necessarily correlate with education level.
+@VH2016 found that visual aptitude for reading data plots was associated with mathematical skills, but this study was done on statistical plots of data, not maps.
+Assessing mathematical ability requires substantially more data collection, and does not necessarily correlate with education level.
 
@@
 
-One of the strengths but weaknesses of the hexagon tile map is that it is non-contiguous.
-Large rural areas are represented by isolated hexagons.
+One of the strengths but potential limitations of the hexagon tile map is that it is non-contiguous; large rural areas are represented by isolated hexagons.
 This is why we expected that the hexagon tile map might not work well to detect large-scale spatial trend ("NW-SE").
@@
 The current algorithm works sequentially to place hexagons, radially from a provided centre.
-There are likely better optimisation procedures that could impve the layout.
+There are likely better optimisation procedures that could improve the layout.
 For reading the spatial distribution, this is less important, but if the hexagon tile map is provided to users as an interactive tool, they will want to locate themselves in the plot.
@@
 This experiment focused on comparing a new display, the hexagon tile map, against the standard display, choropleth.
-There are other options that could have been included in the study, such as the use of insets of dense population areas along with the chorpleth map, or the use of interactive graphics linking statistical charts with the choropleth.
+There are other options that could have been included in the study, such as the use of insets of dense population areas along with the choropleth map, or the use of interactive graphics linking statistical charts with the choropleth.
 Keeping the scope of the study small was important to understand whether it was reasonable to recommend use of the hexagon tile map.

### 2025-07-15 paper/kobakian-cook-anzjs.qmd
small tweaks plus abstract revision

@@
             address: 29 Ancora Imparo Way, Clayton, VIC 3800, Australia
-keywords: ["data visualisation", "visual inference", "geospatial", "statistical graphics"]
+keywords: ["data visualisation", "visual inference", "geospatial", "statistical graphics", "designed experiment"]
 abstract: |
-  The choropleth map display is commonly used for communicating spatial distributions across geographic areas.
-However, when choropleths are used the size of the geographic units will influence the understanding of the distribution derived by map users.
-The hexagon tile map is presented as an alternative display for visualizing population related distributions effectively.
-Visual inference is used to measure the power of the hexagon tile map design, and the choropleth is used as a comparison.
-The hexagon tile map display is tested using a distribution that is directly related to the geography, with values monotonically increasing from the North-West to South-East areas of Australia.
-This study finds in a hexagon tile map lineup the single map that contains a population related distribution is detected with greater probability than the same data displayed in a choropleth map.
-These findings should encourage map creators to implement alternative displays and consider a hexagon tile map when presenting spatial distributions of heterogeneous areas.
+  The choropleth map is a common tool for communicating spatial distributions across geographic areas.
+However, the size of geographic units can distort interpretation, influencing how users perceive the distribution.
+A common alternative is the cartogram, which resizes areas based on population.
+Yet, in Australia, the stark disparities in geography and population make cartograms less suitable.
+This study explores the hexagon tile map as an alternative.
+We report results from a task-based experiment involving human participants, using the lineup protocol to assess how well hexagon tile maps and choropleths convey spatial patterns.
+Three spatial patterns were tested: one reflecting geography, with values increasing monotonically from the northwest to southeast of Australia, and two with clustered high concentrations.
+Results show that the hexagon tile map outperforms the choropleth.
+These findings support the use of alternative map displays and suggest that hexagon tile maps are effective for visualising spatial distributions in heterogeneous regions.
 bibliography: paper.bib
@@
 #| label: tbl-detect-prop
-#| tbl-cap: "Model estimates for the proportion of detection in each of the trend models (standard error). Note that selecting the data plot by chance would produce a detection rate of 0.05."
+#| tbl-cap: "Model estimates for the proportion of detection in each of the trend models (standard error).
+Note that selecting the data plot by chance would produce a detection rate of 0.083, for each lineup."
 # Proportions of detections, estimated from model
@@
 Note that, these detection rates are all substantially higher than chance, except for the choropleth map on the Three Cities.
-For a single evaluation the detection rate of the data plot selected by chance is $1/20=0.05$ because the lineups used in this experiment had 20 plots.
+For a single evaluation, the detection rate of the data plot selected by chance is $1/12=0.083$ because the lineups used in this experiment had 12 plots.
+The choice of 12 plots in the lineups instead of the usual 20, which would have produced the by chance detection rate of 0.05, is because reading a map is relatively complex, and pilot studies suggested that 12 was a reasonable cognitive load but 20 was not.
 When designing an experiment like this it is important to produce lineups that strike a balance between simple and hard, so that there is a chance of discovering the effect of interest.
@@
     facet_grid(Detected ~ trend) +
+    theme_bw() +
     theme(aspect.ratio = 0.8, 
@@
 #| label: tbl-reason
-#| tbl-cap: "Proportion of participants chose each reason for their choice of plot, computed separately for each Trend and Map Type level, and whether the data plot was detected.
+#| tbl-cap: "Proportion of reasons provided by participants for their plot choice, broken down by Trend, Map Type, and data plot detection.
 The primary reason when participants were evaluating the choropleth map was 'consistent' or 'trend', but for the hexagon tile map it was 'clusters', when they detected the data plot."

### 2025-07-15 paper/kobakian-cook-anzjs.tex
small tweaks plus abstract revision

@@
   pdfkeywords={data visualisation, visual
-inference, geospatial, statistical graphics},
+inference, geospatial, statistical graphics, designed experiment},
   colorlinks=true,
@@
 \begin{abstract}
-The choropleth map display is commonly used for communicating spatial
-distributions across geographic areas. However, when choropleths are
-used the size of the geographic units will influence the understanding
-of the distribution derived by map users. The hexagon tile map is
-presented as an alternative display for visualizing population related
-distributions effectively. Visual inference is used to measure the power
-of the hexagon tile map design, and the choropleth is used as a
-comparison. The hexagon tile map display is tested using a distribution
-that is directly related to the geography, with values monotonically
-increasing from the North-West to South-East areas of Australia. This
-study finds in a hexagon tile map lineup the single map that contains a
-population related distribution is detected with greater probability
-than the same data displayed in a choropleth map. These findings should
-encourage map creators to implement alternative displays and consider a
-hexagon tile map when presenting spatial distributions of heterogeneous
-areas.
+The choropleth map is a common tool for communicating spatial
+distributions across geographic areas. However, the size of geographic
+units can distort interpretation, influencing how users perceive the
+distribution. A common alternative is the cartogram, which resizes areas
+based on population. Yet, in Australia, the stark disparities in
+geography and population make cartograms less suitable. This study
+explores the hexagon tile map as an alternative. We report results from
+a task-based experiment involving human participants, using the lineup
+protocol to assess how well hexagon tile maps and choropleths convey
+spatial patterns. Three spatial patterns were tested: one reflecting
+geography, with values increasing monotonically from the northwest to
+southeast of Australia, and two with clustered high concentrations.
+Results show that the hexagon tile map outperforms the choropleth. These
+findings support the use of alternative map displays and suggest that
+hexagon tile maps are effective for visualising spatial distributions in
+heterogeneous regions.
 \end{abstract}
@@
 \keywords{data visualisation; visual inference; geospatial; statistical
-graphics}
+graphics; designed experiment}
 
@@
 displays, such as the cartogram, and tessellated hexagon displays. A
-hexagon tile map forgoes the familiar boundaries, in favor of
+hexagon tile map forgoes the familiar boundaries, in favour of
 representing each geographic unit as an equally sized hexagon, placed
@@
 distributions of cancer statistics over the geographic space of
-Australia. It uses a choropleth map display and diverging color scheme
+Australia. It uses a choropleth map display and diverging colour scheme
 to draw attention to relationships between neighbouring areas. The
@@
 arise from the null scenario. The work of \citet{VH2016} compares the
-lineup protocol to performance on statndard tests of visual ability,
+lineup protocol to performance on standard tests of visual ability,
 concluding that participants' performance is related to general visual
@@
 strips. Figure~\ref{fig-thyroid} a shows the choropleth map of thyroid
-cancer rates in Australia. The choropleth map focuses attention on the
-geography, and for heterogeneously sized areas it presents a biased view
-of the population related distribution of the statistic \citep{CBATCC}.
-\emph{Land does not get cancer, people do} -- a more effective way to
-communicate the spatial distributions of cancer statistics is needed
-(sentiment motivated by \citet{monmonier2018how}).
+cancer incidence rates in Australia. The choropleth map focuses
+attention on the geography, and for heterogeneously sized areas it
+presents a biased view of the population related distribution of the
+statistic \citep{CBATCC}. \emph{Land does not get cancer, people do} --
+a more effective way to communicate the spatial distributions of cancer
+statistics is needed (sentiment motivated by \citet{monmonier2018how}).
 
@@
 
-Alternative algorithms make various trade offs between familiar shapes
+Alternative algorithms make various trade-offs between familiar shapes
 and representation of geographic units. The non-contiguous cartogram
@@
 R package, sugarbag \citep{sugarbag}. Figure~\ref{fig-thyroid} b shows
-the hexagon tile map, where the map is coloured from low (blue) to high
-(red). The inner city areas have expanded, making it possible to see the
-cancer incidence in the small, densely populated areas. Remote regions
-are represented by isolated hexagons, which is not ideal, but maintains
-the spatial location of these data values. It is of interest to know how
-well the spatial distribution patterns are seen from this display, in
-comparison to how they are seen from the choropleth.
+the hexagon tile map, where the map is coloured from low incidence
+(blue) to high (red). The inner city areas have expanded, making it
+possible to see the cancer incidence in the small, densely populated
+areas. Remote regions are represented by isolated hexagons, which is not
+ideal, but maintains the spatial location of these data values. It is of
+interest to know how well the spatial distribution patterns are seen
+from this display, in comparison to how they are seen from the
+choropleth.
 
@@
 spots. These latter two reflect the structure seen in the thyroid cancer
-data (Figure~\ref{fig-thyroid}). This produces six treatment levels:
+incidence data (Figure~\ref{fig-thyroid}). This produces six treatment
+levels:
 
@@
 \caption{\label{fig-exp-design}The experimental design used in the
-study. Participants are allocated to with group A or B, to evaluate
-either the choropleth or hexagon tile map lineup of each simulated data
-set. The text `loc' refers to the location of the data plot in the
-lineup.}
+study. Participants are allocated to group A or B, to evaluate either
+the choropleth or hexagon tile map lineup of each simulated data set.
+The text `loc' refers to the location of the data plot in the lineup.}
 
@@
 on each of lineup. These responses are saved after entering.
-Participants were expected to click the submit button on the final page.
 
@@
 of all lineups or clicked through without providing their evaluation are
-filtered.
+removed.
 
@@
 selecting the data plot by chance would produce a detection rate of
-0.05.}
+0.083, for each lineup.}
 
@@
 hexagon tile map than the choropleth. The Three Cities trend was
-practically not detectable in the choropleth map. The dection rates were
-more similar for the NW-SE trend, but slightly higher for the hexagon
-tile map, which was a surprise. Note that, these detection rates are all
-substantially higher than chance, except for the choropleth map on the
-Three Cities. For a single evaluation the detection rate of the data
-plot selected by chance is \(1/20=0.05\) because the lineups used in
-this experiment had 20 plots. When designing an experiment like this it
-is important to produce lineups that strike a balance between simple and
-hard, so that there is a chance of discovering the effect of interest.
-This experiment has managed to do this extremely well, which is a result
-of pilot studies, careful null data generation, and power calculations
-to determine appropriate sample size.
+practically not detectable in the choropleth map. The detection rates
+were more similar for the NW-SE trend, but slightly higher for the
+hexagon tile map, which was a surprise. Note that, these detection rates
+are all substantially higher than chance, except for the choropleth map
+on the Three Cities. For a single evaluation, the detection rate of the
+data plot selected by chance is \(1/12=0.083\) because the lineups used
+in this experiment had 12 plots. The choice of 12 plots in the lineups
+instead of the usual 20, which would have produced the by chance
+detection rate of 0.05, is because reading a map is relatively complex,
+and pilot studies suggested that 12 was a reasonable cognitive load but
+20 was not. When designing an experiment like this it is important to
+produce lineups that strike a balance between simple and hard, so that
+there is a chance of discovering the effect of interest. This experiment
+has managed to do this extremely well, which is a result of pilot
+studies, careful null data generation, and power calculations to
+determine appropriate sample size.
 
@@
 Figure~\ref{fig-beeswarm} shows horizontally jittered dot plots to
-contrast the time taken by participants to evaluate each lineup facetted
+contrast the time taken by participants to evaluate each lineup faceted
 by map type and trend model. Each dot is an evaluation. The time taken
@@
 ``Colour trend across the areas'', ``consistent'' = ``All areas have
-similar colours'', ``hotpots'' = ``Big differences between neighbouring
+similar colours'', ``hotspots'' = ``Big differences between neighbouring
 areas'', ``none'' = ``None of these reasons''. These proportions are
@@
 primarily selected for the choropleth, but `clusters' was the primary
-reason for the hexgon tile map. The primary reasons are similar when the
-participant did not detect the data plot.
+reason for the hexagon tile map. The primary reasons are similar when
+the participant did not detect the data plot.
 
@@
 
-\caption{\label{tbl-reason}Proportion of participants chose each reason
-for their choice of plot, computed separately for each Trend and Map
-Type level, and whether the data plot was detected. The primary reason
-when participants were evaluating the choropleth map was `consistent' or
-`trend', but for the hexagon tile map it was `clusters', when they
-detected the data plot.}
+\caption{\label{tbl-reason}Proportion of reasons provided by
+participants for their plot choice, broken down by Trend, Map Type, and
+data plot detection. The primary reason when participants were
+evaluating the choropleth map was `consistent' or `trend', but for the
+hexagon tile map it was `clusters', when they detected the data plot.}
 
@@
 variety of demographic background of participants. However, \$n=\$90 is
-insufficient fit a model including this demographic information.
+insufficient to fit a model including this demographic information.
 \citet{MHC} (published in 2025 but conducted in 2012) showed that there
@@
 demographic groups. \citet{VH2016} found that visual aptitude for
-reading data plots was associated with math skills, but this study was
-done on statistical plots of data, not maps. Assessing math ability
-requires substantially more data collection, and does not necessarily
-correlate with education level.
+reading data plots was associated with mathematical skills, but this
+study was done on statistical plots of data, not maps. Assessing
+mathematical ability requires substantially more data collection, and
+does not necessarily correlate with education level.
 
@@
 
-One of the strengths but weaknesses of the hexagon tile map is that it
-is non-contiguous. Large rural areas are represented by isolated
-hexagons. This is why we expected that the hexagon tile map might not
-work well to detect large-scale spatial trend (``NW-SE''). The primary
-reason for producing the non-contiguous display was to preserve
+One of the strengths but potential limitations of the hexagon tile map
+is that it is non-contiguous; large rural areas are represented by
+isolated hexagons. This is why we expected that the hexagon tile map
+might not work well to detect large-scale spatial trend (``NW-SE''). The
+primary reason for producing the non-contiguous display was to preserve
 geography sufficiently for the reader to easily recognise the location.
@@
 radially from a provided centre. There are likely better optimisation
-procedures that could impve the layout. For reading the spatial
+procedures that could improve the layout. For reading the spatial
 distribution, this is less important, but if the hexagon tile map is
@@
 that could have been included in the study, such as the use of insets of
-dense population areas along with the chorpleth map, or the use of
+dense population areas along with the choropleth map, or the use of
 interactive graphics linking statistical charts with the choropleth.

### 2025-07-15 paper/kobakian-cook-anzjs.qmd
commented text removed

@@
 If there is a cluster, or an anomaly, there may be a localized outbreak of the disease.
-<!--Aggregating the statistic on administrative units, provides a level of privacy to individuals, while allowing the impact of the disease on the community to be analyzed.-->
-
-<!-- Many sets of Australian statistical areas have a large disparity between the smallest and largest units.
-The rural communities in Australia operate on a much larger geographic space than small inner-city communities.
-When a spatial distribution is related to the size of the areas, or the population density, the size of the regions can allow erroneous conclusions to be drawn about the state of the statistic over the entire population, when presenting the statistics on a geographic map base.
-This occurs as large regions filled with a consistent colour or pattern can draw the attention of map readers, and small regions are not paid equal attention [@CTTMB].
-An alternative display can be used to honestly communicate a spatial distribution for a set of heterogeneous areas [@NISCC].
-This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
-
-A choropleth map is not the only display that can be used for presenting geospatial data. 
-Alternative maps include various cartograms and tessellated tile maps. They allow other variables to be incorporated in the display to highlight the statistical values of various geographic areas.
--->
 
@@
 ## Experimental factors
-
-<!-- The variables changed between groups were the type of plot shown and the trend model.-->
 
@@
 
-<!-- Applying smoothing -->
-
-<!-- The null model imposed by our hypothesis suggests that neighbors are related.
-The randomness induced when generating the null data was smoothed to mirror the practices employed by the Australian Cancer Atlas statisticians.
-In these 12 sets of data, each of the 12 maps were smoothed several times to replicate the spatial autocorrelation seen in cancer data sets presented in the Australian Cancer Atlas, without implementing uncertainty via transparency.
-
-A list of neighbors for each geographic unit was generated to use when smoothing the distributions.
-For each geographic unit the same spatial smoother was applied in each layer of smoothing.
-It kept half of the units' previous value, and derived the new half as the mean of the values of its neighbors at the previous layer of smoothing.
-
-This smoothing allowed neighbors to be related to each other, but also allowed outliers, and showed distributions similar to the thyroid cancer incidence distribution (@fig-thyroid). -->
-
-<!-- methods for smoothing spatial_smoother() in 00_pilot.R and used in all the  pilot_cities.R ... files -->
-
 ## Generating lineups
@@
 Each participant used the internet to access the survey, and data was transferred by secure link from the web app to a Google sheet using the `googlesheets` package tools [@sheets].
-<!-- The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results.
-The application connected to the googlesheet using the googlesheets [@sheets] R package when participants opened the application, and interacted again when participants chose to submit the survey.
-At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.-->
 
@@
 on each of lineup. These responses are saved after entering.
-<!-- Participants were expected to click the submit button on the final page.-->
 
@@
 Basic plots summarising detection rates by map type and trend model type, and feedback and demographic variables against the different experimental design elements.
-
-<!-- Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.-->
-
-<!-- Plots will be made in R [@RCore], with the `ggplot2` package [@ggplot2].-->
 
@@
 
-<!--
-$$y_{ij} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij} + \varepsilon_{i,j}, ~~~ i=1,2; ~j=1,2,3$$
--->
-
 where $y_{ijk} = 0, 1$ represents whether subject $i$ detected the data plot (1) or did not (0), $\mu_i, ~i=1, \dots n$ is the subject-specific random intercept, $n$ is the number of subjects, $\tau_j, ~j=1,2$ is the map type effect, $\delta_k, ~k=1,2,3$ is the trend model effect.
@@
 
-<!-- 
-The model specifies a logit link, this means the predicted values from the `glmer` model should be back-transformed to fit between 0 and 1.
-The predictions  $\widehat{p}(\eta)$ are transformed to be probabilities between 0 and 1 with the link specified below:
-
-$$\widehat{p}(\eta) = \frac{e^{\eta}}{1 + e^{\eta}}$$ \label{eq:transform}
-$$\eta = f(\tau_i,\delta_j)$$
--->
-
-<!--
-## Experimental design
-
-The choropleth map was used as the comparative visualization for presenting the lineups [@VVSIALM] as this is the common display for spatial cancer data.
-Geographic distributions usually have some degree of spatial autocorrelation between neighbors.
-This feature was incorporated in all maps shown in the lineup displays, the map that contained the trend feature shown in only one set of data was also affected by spatial autocorrelation.
-A line up protocol was implemented to arrange $N$ maps in each display. 
-A reasonable amount of null plots $N-1$ in the lineup was chosen to ensure the real data map was well hidden.
-A reasonable number of plots to show in each lineup, $N = 12$ was chosen to not overwhelm participants due to the detailed choropleth maps of Australian SA3 areas.
-
-The hypotheses for each lineup are
-$H_0$ : All plots look the same
-$H_a$ : One plot looks different to the other plots
-
-The same data was visualized on a choropleth map, and on a hexagon tile map, however in this study the participants only saw one of these two displays.
-The accuracy and times taken were aggregated for Groups and.
-Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.
-
-Let $n$ be the number of independent observers and $x_i$ the
-number of observers who picked plot $i$, $i = \{1,...,m\}$
-
-Then $x_i, x_2, ..., x_m$ follows a multinomial
-distribution$Mult_{\pi_1, \pi_2, ...., \pi_m}(x_i, x_2, ..., x_m)$ with 
-$\sum_i \pi_i = 1$, where $\pi_i$ is the probability that plot $i$ is picked by an
-observer, which we can estimate as $\hat{\pi}_i = x_i/n$.
-The researchers compared the length of time taken, and the accuracy of the participants choices.
-The power of a lineup can therefore be estimated as the ratio of correct
-identifications $x$ out of $n$ viewings.
-
-## The methods of data analysis used
-The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R [@RCore].
-
-For each of the 12 lineup displays the researchers calculated:
-
- - accuracy: the proportion of subjects who detected the data plot
- - efficiency: average time taken to respond
--->
-
 # Results {#sec-results}
-
-<!--
-The results section explores the [Accuracy] and contrasts the detection rate of the real data plot in the lineups.
-The second section considers the [Speed] participants had when submitting their responses to the three questions asked regarding each display.
-The [Certainty] participants felt about their decisions and the [Reason] for their choice in plot is also discussed.
--->
 
@@
     ungroup()
-```
-
-<!-- @tbl-desc-stats shows the means and standard deviations of the detection rate for each type of plot and each trend model.
-This also gives the standard deviations, the smallest standard deviation for all sets of replicates was the Three Cities trend model shown in a Choropleth display.
-This group of displays had a very small detection rate of 0.04.
-The mean detection rate for the Three Cities trend model shown as choropleth map lineups was also the smallest at 0.40.
-The North-West to South-East (NW-SE) trend model unexpectedly had a higher mean detection rate for the hexagon tile map displays, but the difference in the means of detection rate was only 0.10.
--->
-
-```{r}
-#| eval: false
-#| label: tbl-desc-stats
-#| tbl-cap: "The mean and standard deviation of the rate of detection for each trend model, calculated for the choropleth and hexagon tile map displays."
-types <- c("Choro.", "", "Hex.", "")
-
-d |> group_by(type, trend) |>
-  summarise(m = as.character(round(mean(detect), 2)),
-      std.dev = as.character(round(sd(detect), 2))) |> 
-  mutate(std.dev = ifelse(std.dev == 0.5, "(0.50)", paste0("(", std.dev, ")"))) |>   mutate(m = ifelse(m == 0.4, "0.40", m)) |> 
-  gather(stat, value, m, std.dev) |> 
-  pivot_wider(names_from = "trend", values_from = "value") |> 
-  arrange(type) |> ungroup() |> 
-  mutate(Type = types) |> select(Type, `NW-SE`, `Three Cities`, `All Cities`) |>
-  knitr::kable(., format = "latex", align = "lccc", booktabs = TRUE, 
-    linesep = c("", "\\addlinespace"))
 ```
@@
 
-<!--Participants were asked why they had made their plot choice and were able to select from a set of suggested reasons. 
-"Colour trend across the areas" was the most common selection for NW-SE trend displays (@tbl-reason).
-
-The reasons chosen by participants from the list provided to them varied more when viewing choropleth displays than the hexagon tile map.
-The hexagon tile map displays resulted in "Clusters of colour" as the most common choice made by participants.
-
-The choice "None of these reasons" was used as the default value to minimise noise from participants who did not select a response. -->
-
 ```{r}
@@
 
-<!--The visual inference lineup protocol was employed to contrast the effectiveness of the displays.
-The results have shown that overall the use of the hexagon tile map display allows participants to find the data plot in the lineup more often.
-Using the visual inference protocol this result can be extended to show that it is a valid alternative display to communicate spatial distributions of population related data.
-
 We expected that the choropleth map would be superior for communicating the spatial pattern of geographic distributions.

### 2025-07-15 paper/kobakian-cook-anzjs.tex
commented text removed

@@
 
+We expected that the choropleth map would be superior for communicating
+the spatial pattern of geographic distributions. The data suggest that
+the participants perform slightly better or equally as well for each
+replicate in each trend model across the two displays. Table II shows
+that the difference in the mean detection rate for the two trend models
+was 0.10.
+
+The differences seen in the Figure~\ref{fig-detect-compare} plot.
+Surprisingly the difference between map types for the geographic
+distribution was significant at the 0.05 level, even though the effect
+difference is small. It also showed that the hexagon tile map display
+performs marginally better than the choropleth for all trend models.
+
+While the significance of the difference in detection was the key focus
+of this experiment, the secondary focus was the time taken by
+participants. it was expected that the participants may take longer to
+consider the hexagon tile map distribution but would be able to detect
+the data plot in the lineup. The bimodal distributions seen in
+Figure~\ref{fig-beeswarm} showed very little difference in the mean
+evaluation times. As the maximum time of all of the distributions
+approached 60 seconds it cannot be said that the participants' took
+longer to evaluate the hexagon tile map displays.
+
+The responses to the questions asked of participants included the reason
+for their choice and the certainty around their choice.
+Table~\ref{tbl-reason} shows high levels of certainty of 4 and 5 were
+chosen by participants when looking at the population distributions in a
+choropleth map display show that they were over confident when
+attempting to find the real data plot in the choropleth map displays.
+Participants performed better on the NW-SE distribution shown in the
+choropleth display and were reasonably confident about their decisions.
+The high levels of the mid range value of 3 could indicate that the
+participant did not want to provide a response, as this was the default
+value. Those who chose level 4 or 5 were equally likely to be correct
+for the three cities lineups, but more likely to be correct than
+incorrect for the other two trend models.
+
+The colour scaling applied in Three cities and All cities displays
+resulted in the rural areas of the real data plot appearing more blue or
+yellow than the other plots in the lineups. Due to the consistent
+colouring of rural areas in a choropleth display, the choice ``All areas
+have similar colours'' was most common reason for a participants choice.
+The All Cities displays coloured the inner-city areas of all capital
+cities more red, this was observable to participants and explains the
+equal choice of the city clusters or rural colour consistency. Choosing
+``Clusters of colour'' was expected when participants viewed the Hexagon
+tile map display of the All Cities and Three Cities distributions. It
+was unexpected that it was also the most common reason for the NW-SE
+hexagon tile map displays. Due to the spatial covariance introduced in
+the smoothing, groups of similarly coloured hexagons were present in all
+of the hexagon tile map displays. All Cities and Three Cities
+distributions of real data trends had distinctly different patterns or
+red inner-city areas, while some of the plots in each lineup may have
+shared similar features.
+
+\section{Conclusion}\label{conclusion}
+
+The choropleth map display and the tessellated hexagon tile map have
+been contrasted using the lineup protocol. The hexagon tile map was
+significantly more effective for spotting a real population related data
+trend model hidden in a lineup.
+
+The hexagon tile map display should be considered as an alternative
+visualisation method when communicating distributions that relate to the
+population across a set of geographic units. As an additional display to
+the familiar choropleth map, cancer atlas products may benefit from the
+opportunity to allow exploration via an alternative display. The spatial
+distributions used to test these displays were inspired by the real
+spatially smoothed estimates of the cancer burden on Australian
+communities. However, this technique may be extended to other population
+related distributions, such as other diseases, or election results or
+socioeconomic indicators.
+
+The increasing population densities of capital cities despite large land
+area exacerbates the difference in the smallest and largest communities.
+The population density structure of Australia can be considered similar
+to that of Canada, New Zealand and many other countries. Therefore, this
+display is not only relevant to Australia, but all nations or population
+distributions that experience densely populated cities separated by vast
+rural expanses. --\textgreater{}
+
 \section*{Acknowledgments}\label{acknowledgments}

### 2025-07-15 paper/review1/ReponseToReviewers2025.qmd
done with all - needs a careful read and references cleaned up
added code file and checked response

@@
 ---
-title: "Response to Reviewers"
+title: "Response to Reviews"
+author: "Stephanie Kobakian and Dianne Cook"
 format: pdf
@@
 
-## Response to Editor and reviewers
-
-Thank you for the careful reviews of our paper. Please find *our responses to provided in italics* point-by-point with the comments.
+Thank you for the careful reviews of our paper. Please find *our responses provided point-by-point with the comments in italics*.
 
@@
 
-*Done*
+*Done.*
 
@@
 
-*The explanation of data cleaning has been revised to make it clearer. There is no difference in XXX*
+*The explanation of data cleaning has been revised to make it clearer.
+There is no difference in in groups or participant demographics.
+This is written in the text now bu results not included.
+The code for these checks is in the unevaluated chunks the qmd file.*
 
@@
 
-*There is no difference in results from group A and B. XXX*
+*There is no difference in results from group A and B.
+There is no difference in in groups or participant demographics.
+This is written in the text now bu results not included.
+The code for these checks is in the unevaluated chunks the qmd file.*
 

### 2025-07-15 paper/kobakian-cook-anzjs.R

@@ -1,0 +1,631 @@
+## ----setup, include=FALSE----------------------------------------------------
+knitr::opts_chunk$set(
+  echo = FALSE,
+  warning = FALSE,
+  error = FALSE, 
+  message = FALSE,
+  cache = FALSE,
+  dpi = 300,
+  out.width = "100%")
+
+
+## ----libraries---------------------------------------------------------------
+# Load Libraries
+library(tidyverse)
+library(readxl)
+library(broom)
+library(broom.mixed)
+library(cowplot)
+library(ggbeeswarm)
+library(png)
+library(grid)
+library(lme4)
+library(cartogram)
+library(sugarbag)
+library(sf)
+library(ggmosaic)
+library(emmeans)
+library(ggthemes)
+library(RColorBrewer)
+library(knitr)
+library(kableExtra)
+library(patchwork)
+
+options(knitr.kable.digits = "2")
+
+
+## ----data--------------------------------------------------------------------
+trend_colors <- c(
+  "NW-SE" = "#B2DF8A",
+  "Three Cities" = "#A6CEE3",
+  "All Cities" = "#1F78B4")
+  
+type_colors <- c(
+  "Choro." = "#fcae91",
+  "Hex." = "#a50f15")
+
+type2_colors <- c(
+  "choropleth" = "#fcae91",
+  "hexagon tile" = "#a50f15")
+
+detect_f_colors <- c(
+  "No" = "#66C2A5",
+  "Yes" = "#FC8D62")
+
+detect_colors <- c(
+  "Detected? No" = "#66C2A5",
+  "Detected? Yes" = "#FC8D62")
+
+  # Downloaded data
+d <- read_xlsx("data/experiment-export.xlsx", sheet=2) |>
+  filter(!is.na(contributor)) |>
+  mutate(contributor = factor(contributor))
+
+n_all_contributors <- d |> count(contributor, sort=TRUE) |> 
+  summarise(n_contributors = length(contributor))
+  
+n_all_evals <- nrow(d)
+
+# Check data set 
+# Need to clean multiple entries, 48, 24
+# remove duplicated entries due to submit button
+d <- d |> group_by(group, contributor, image_name) |>
+  slice(1) |> ungroup() |> 
+  arrange(group, contributor, plot_order)
+
+# Remove contributors who did not provide answers to most questions
+keep <- d |> count(contributor, sort = TRUE) |> filter(n > 10)
+d <- d |> 
+  filter(contributor %in% keep$contributor) |>
[…]
